### 2022-02-16 moduletwoanalysis.Rmd
uploaded data for module 2 and coded answers into numbers

---
title: "module2_eco_pol_factors"
output:
  output: 
  html_document:
    fig_width: 7
    fig_height: 6
    fig_caption: true
    keep_md: true
    theme: paper
    df_print: paged
---

```{r load packages, warning = FALSE, message = FALSE}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(hablar))
suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(DT))
suppressPackageStartupMessages(library(ggplot2))
```

```{r cars}
moduletwo <- read_excel( "~/Desktop/thesis_surveydata/political_factors_complete.xlsx")
module2 <- data.frame(moduletwo)
module2 %>%
  filter(!row_number() %in% c(1,2))

# loaded data set for module 2 eco -pol variables and removes the rows with question number and question text
```

```{r, eval =TRUE}
#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
codedmodule2 <- module2 %>%

#remove row 1
  filter(!row_number() %in% c(1,2)) %>%

# replace risky likert scale with numbers
  mutate_at(vars(starts_with("Risky")), funs(case_when(. =="Not at all risky" ~ 1, 
                                                       . =="Slightly risky" ~ 2, 
                                                       . =="Moderately risky" ~ 3, 
                                                       . =="Very risky" ~ 4, 
                                                       . =="Extremely risky" ~ 5))) %>%

# replace beneficial likert scale with numbers  
  mutate_at(vars(starts_with("Ben")), funs(case_when(. =="Not at all beneficial" ~ 1,
                                                     . =="Slightly beneficial" ~ 2,
                                                     . =="Moderately beneficial" ~ 3,
                                                     . =="Very beneficial" ~ 4,
                                                     . =="Extremely beneficial" ~ 5 ))) %>%

# replace nuclear acceptance likert scale with numbers
  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                                        . == "Somewhat disagree" ~ 2,
                                                                        . == "Neither agree nor disagree" ~3,
                                                                        . == "Somewhat agree" ~ 4,
                                                                        . == "Strongly agree" ~ 5))) %>%

# code likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_I","K_H","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE", "DEV", "PROSPER", "RELY"))), funs(case_when(. == "Strongly disagree" ~ 1, 
               . == "Somewhat disagree" ~ 2,
               . == "Neither agree nor disagree" ~3,
               . == "Somewhat agree" ~ 4,
               . == "Strongly agree" ~ 5))) %>%

# reverse code for likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_S","K_E"))), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                               . == "Somewhat disagree" ~ 4,
                                                               . == "Neither agree nor disagree" ~3,
                                                               . == "Somewhat agree" ~ 2,
                                                               . == "Strongly agree" ~ 1))) %>%

# code eco-pol scale variables into numbers
  mutate_at(vars(SYSTEMDEMO,SYSTEMRELIGION,SYSTEMTECHNO,SYSTEMTOTAL,WEALTHLIM,MECHANISATION,DECISIONDECEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG), funs(case_when(. == "Strongly disagree" ~ 1, 
                        . == "Somewhat disagree" ~ 2,
                        . == "Neither agree nor disagree" ~3,
                        . == "Somewhat agree" ~ 4,
                        . == "Strongly agree" ~ 5))) %>%

# reverse code eco-pol scale variables into numbers 
 mutate_at(vars(DECISIONCEN, INDUSTRYSMALL, ECONOMYLOCAL, ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                                                                         . == "Somewhat disagree" ~ 4,
                                                                                                         . == "Neither agree nor disagree" ~3,
                                                                                                         . == "Somewhat agree" ~ 2,
                                                                                                         . == "Strongly agree" ~ 1)))

```

```{r}
codedmodule2 %>%
  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #add row index so later spreading indexed correctly
  add_rownames()%>%
  #melt to long format
  gather(technology, value, -rowname) %>%
  # separate risky from variable suffix
  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "summary")) %>%
  # spread summary values back to wide form
  spread(summary,value) %>%
  #clean up
  select(-rowname, -Risky) %>%
  arrange(mean)
```

### 2022-02-17 moduleoneanalysis.Rmd
coding module one

---
title: "moduleoneanalysis"
output:
  html_document:
    fig_width: 7
    fig_height: 6
    fig_caption: true
    keep_md: true
    theme: paper
    df_print: paged
---

```{r setup, include=FALSE}

```

```{r}

```

```{r}

```

### 2022-02-17 moduletwoanalysis.Rmd
coding module one
chisq test on demographic variables and perceived risk

@@
 title: "module2_eco_pol_factors"
-output:
 output:
@@
 
-```{r cars}
+```{r}
 moduletwo <- read_excel( "~/Desktop/thesis_surveydata/political_factors_complete.xlsx")
@@
 
+codedmodule2
+
 ```
 
-```{r}
+```{r, eval=TRUE}
+
+# summary statistics for risks from different energy sources
+
 codedmodule2 %>%
@@
 ```
+
+```{r}
+
+# summary statistics for benefits from different energy sources
+
+codedmodule2 %>%
+  summarize_at(vars(starts_with(c("Ben"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
+  #add row index so later spreading indexed correctly
+  add_rownames()%>%
+  #melt to long format
+  gather(technology, value, -rowname) %>%
+  # separate Ben from variable suffix
+  separate(technology, c("Ben", "var"), extra = "merge", fill = "left") %>%
+  #separate mean from variable prefix
+  separate(var, c("technology", "summary")) %>%
+  # spread summary values back to wide form
+  spread(summary,value) %>%
+  #clean up
+  select(-rowname, -Ben) %>%
+  arrange(mean)
+
+#round off to two decimal places
+```
+
+```{r}
+#summary statistics for nuclear energy accept, reject and reluctantly accept scale
+codedmodule2 %>%
+  summarize_at(vars(N_accept,N_reject,N_reluctantlyaccept), list(~mean(., na.rm = TRUE),~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE),~n())) %>%
+  add_rownames() %>%
+  gather(acceptance, value, -rowname) %>%
+  separate(acceptance, c("N_accept", "var") ,  extra = "merge", fill = "left") %>%
+  separate(var, c("Acceptance", "summary")) %>%
+  spread(summary, value) %>%
+  select(-rowname, -N_accept)%>%
+  arrange(mean)
+
+```
+
+```{r}
+
+# chi square test for risk perception from nuclear energy and gender, race
+
+# first combine gender and caste variables
+
+chitest <- codedmodule2 %>%
+  select(Risky_Nuclear,Risky_Hydro, Risky_Hydro, Risky_Solar,Urban_Rural, Gender, Caste) %>%
+  na.omit() %>%
+  filter(!Caste=="Rather not say/Don't know")%>%
+  unite(gendercaste, Gender, Caste, sep = "_", remove = FALSE)
+
+chitest
+
+```
+
+```{r}
+
+chisq.test(chitest$Risky_Nuclear, chitest$Urban_Rural)
+```
+
+```{r}
+
+```

### 2022-02-18 moduleoneanalysis.Rmd
save data sheets into rda format

@@
 
-```{r setup, include=FALSE}
+```{r load packages, warning = FALSE, message = FALSE}
+suppressPackageStartupMessages(library(tidyverse))
+suppressPackageStartupMessages(library(readxl))
+suppressPackageStartupMessages(library(hablar))
+suppressPackageStartupMessages(library(tsibble))
+suppressPackageStartupMessages(library(dplyr))
+suppressPackageStartupMessages(library(DT))
+suppressPackageStartupMessages(library(ggplot2))
+
+```
+
+```{r, eval=TRUE}
+
+moduleone <- read_excel( "~/Desktop/thesis_surveydata/livelihood_insecurity_complete.xlsx")
+module1 <- data.frame(moduleone)
+module1 %>%
+  filter(!row_number() %in% c(1,2))
+
+# loaded data set for module 2 eco -pol variables and removes the rows with question number and question text
+```
+
+```{r, eval =TRUE}
+#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
+codedmodule1 <- module1 %>%
+
+#remove row 1
+  filter(!row_number() %in% c(1,2)) %>%
+
+# replace risky likert scale with numbers
+  mutate_at(vars(starts_with("Risky")), funs(case_when(. =="Not at all risky" ~ 1, 
+                                                       . =="Slightly risky" ~ 2, 
+                                                       . =="Moderately risky" ~ 3, 
+                                                       . =="Very risky" ~ 4, 
+                                                       . =="Extremely risky" ~ 5))) %>%
+
+# replace beneficial likert scale with numbers  
+  mutate_at(vars(starts_with("Ben")), funs(case_when(. =="Not at all beneficial" ~ 1,
+                                                     . =="Slightly beneficial" ~ 2,
+                                                     . =="Moderately beneficial" ~ 3,
+                                                     . =="Very beneficial" ~ 4,
+                                                     . =="Extremely beneficial" ~ 5 ))) %>%
+
+# replace nuclear acceptance likert scale with numbers
+  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
+                                                                        . == "Somewhat disagree" ~ 2,
+                                                                        . == "Neither agree nor disagree" ~3,
+                                                                        . == "Somewhat agree" ~ 4,
+                                                                        . == "Strongly agree" ~ 5)))
+
+codedmodule1
+
+#coded dependent variables for module 1 livelihood and income security survey
 
@@
 ```{r}
+# normalize quantitative livelihood-income security variables
 
 ```
-
-```{r}
-
-```

### 2022-02-23 moduleoneanalysis.Rmd
attempting stacked bar plot for perceived risk

@@
 moduleone <- read_excel( "~/Desktop/thesis_surveydata/livelihood_insecurity_complete.xlsx")
+save(moduleone, file = "moduleone.rda")
 module1 <- data.frame(moduleone)

### 2022-02-23 moduletwoanalysis.Rmd
attempting stacked bar plot for perceived risk

@@
 moduletwo <- read_excel( "~/Desktop/thesis_surveydata/political_factors_complete.xlsx")
+save(moduletwo, file = "moduletwo.rda")
 module2 <- data.frame(moduletwo)
@@
 ```
-
 ```{r, eval=TRUE}
@@
   arrange(mean)
+```
+```{r}
+#plotting perceived risk from different technologies
+
+module2%>%
+  filter(!row_number() %in% c(1,2)) %>% 
+  select(starts_with("RISKY"))%>%
+  gather(Technology, Perceived_Risk, Risky_Hydro:Risky_INDLPG, factor_key = TRUE)%>%
+  separate(Technology, c("Risky", "Technology"), extra = "merge", fill = "left")%>%
+  select(-Risky) %>%
+  group_by(Technology, Perceived_Risk) %>%
+  summarise(n=n())
+
+```
+```{r}
+levels(module2)
+```
+
+```{r}
+%>%
+  spread(Perceived_Risk, n)%>%
+  select("Technology", "Extremely risky", "Very risky", "Moderately risky", "Slightly risky", "Not at all risky", "Rather not say/Don't know")
+```
+
+```{r}
+
+module2%>%
+  filter(!row_number() %in% c(1,2)) %>% 
+  select(starts_with("RISKY"))%>%
+  gather(Technology, Perceived_Risk, Risky_Hydro:Risky_INDLPG, factor_key = TRUE)%>%
+  separate(Technology, c("Risky", "Technology"), extra = "merge", fill = "left")%>%
+  select(-Risky) %>%
+  group_by(Technology, Perceived_Risk) %>%
+  summarise(n=n())%>%
+ggplot(aes(fill= Perceived_Risk, y=n, x=Technology)) + 
+  geom_bar(position="fill", stat="identity")+
+  coord_flip()
+
 ```
@@
 ```
+
+```{r}
+
+```

### 2022-02-26 moduletwoanalysis.Rmd
more graphs on risk and benefit

@@
 ```
-```{r}
-levels(module2)
-```
-
-```{r}
-%>%
-  spread(Perceived_Risk, n)%>%
-  select("Technology", "Extremely risky", "Very risky", "Moderately risky", "Slightly risky", "Not at all risky", "Rather not say/Don't know")
-```
 
@@
   coord_flip()
+
+# fix ugly visual. Rearrange from extremely risky to not at all risky. Red to green, rather not say/Don't know should be grey
 
@@
 #round off to two decimal places
+```
+
+```{r}
+
+module2%>%
+  filter(!row_number() %in% c(1,2)) %>% 
+  select(starts_with("Ben"))%>%
+  gather(Technology, Perceived_Benefit, Ben_Hydro:Ben_INDLPG, factor_key = TRUE)%>%
+  separate(Technology, c("Ben", "Technology"), extra = "merge", fill = "left")%>%
+  select(-Ben) %>%
+  group_by(Technology, Perceived_Benefit) %>%
+  summarise(n=n())%>%
+ggplot(aes(fill= Perceived_Benefit, y=n, x=Technology)) + 
+  geom_bar(position="fill", stat="identity")+
+  coord_flip()
+
+# fix ugly visual.
+Rearrange from extremely beneficial to not at all beneficial.
+Green to red, rather not say/Don't know should be grey.
+Also facet wrap by INDividually owned and centrally owned technology.
+
+```
+
+```{r}
+
 ```
@@
 ```
-
-```{r}
-
-```
-
-```{r}
-
-```

### 2022-02-27 moduletwoanalysis.Rmd
improved perceived risk graph

@@
 
-codedmodule2 %>%
+risksummary <- codedmodule2 %>%
   summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
@@
   select(-rowname, -Risky) %>%
-  arrange(mean)
+  arrange(mean)%>%
+  setNames(paste0('perceivedrisk.', names(.)))%>%
+  rename(technology = perceivedrisk.technology)
+
+risksummary
+
 ```
+
 ```{r}
@@
 
-module2%>%
+colorsequence<- c("#8C4646","#D9695F","#F2A679","#F2D091","#5D8C7B","#808080")
+df_barplot<-module2%>%
   filter(!row_number() %in% c(1,2)) %>% 
@@
   group_by(Technology, Perceived_Risk) %>%
-  summarise(n=n())%>%
-ggplot(aes(fill= Perceived_Risk, y=n, x=Technology)) + 
-  geom_bar(position="fill", stat="identity")+
-  coord_flip()
+  summarise(n=n())
 
-# fix ugly visual. Rearrange from extremely risky to not at all risky. Red to green, rather not say/Don't know should be grey
+df_barplot %>% ggplot(aes(fill= fct_rev(factor(Perceived_Risk, levels=c("Extremely risky", "Very risky","Moderately risky","Slightly risky","Not at all risky","Rather not say/Don't know"))), y=n , x=Technology)) +
+  geom_bar(position="fill",stat="identity")+
+  scale_fill_manual("legend", values = c("Extremely risky" = "#8C4646", "Very risky" = "#D9695F", "Moderately risky" = "#F2A679", "Slightly risky" = "#F2D091","Not at all risky" = "#5D8C7B", "Rather not say/Don't know" = "#808080"))+
+  coord_flip()+
+  theme_classic()
+
+# fix ugly visual. Rearrange from extremely risky to not at all risky. Red to green, rather not say/Don't know should be grey. Also facet wrap by INDividually owned and centrally owned technology.
 
@@
 
-codedmodule2 %>%
+benefitsummary <- codedmodule2 %>%
   summarize_at(vars(starts_with(c("Ben"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
@@
   select(-rowname, -Ben) %>%
-  arrange(mean)
+  arrange(mean)%>%
+  setNames(paste0('perceivedbenefit.', names(.))) %>%
+  rename(technology = perceivedbenefit.technology)
+benefitsummary
 
@@
 Also facet wrap by INDividually owned and centrally owned technology.
-
-```
-
-```{r}
+Also arrange descending from most beneficial to least beneficial.
 
@@
 ```{r}
+full_join(risksummary,benefitsummary, by = NULL, copy = FALSE, keep = FALSE) %>%
+  select(technology, perceivedrisk.mean, perceivedbenefit.mean) %>%
+   gather(key = "level", value = "mean",
+       perceivedrisk.mean, perceivedbenefit.mean) %>%
+  ggplot(aes(x=technology, y= mean, fill = level))+
+  geom_bar(stat="identity", position=position_dodge())+
+  coord_flip()
+
+# arrange descending and facet wrap by IND prefix
+
+```
+
+```{r}
+full_join(risksummary,benefitsummary, by = NULL, copy = FALSE, keep = FALSE) %>%
+  select(technology, perceivedrisk.median, perceivedbenefit.median) %>%
+   gather(key = "level", value = "median",
+       perceivedrisk.median, perceivedbenefit.median) %>%
+  ggplot(aes(x=technology, y= median, fill = level))+
+  geom_bar(stat="identity", position=position_dodge())+
+  coord_flip()
+
+# arrange descending and facet wrap by IND prefix
+
+```
+
+```{r}
 

### 2022-03-09 moduletwoanalysis.Rmd
fixed risk-benefit graphs in desceding order

@@
 
+likertstack <- module2%>%
+  filter(!row_number() %in% c(1,2)) %>% 
+  select(starts_with("RISKY"))%>%
+  gather(Technology, Perceived_Risk, Risky_Hydro:Risky_INDLPG, factor_key = TRUE)%>%
+  separate(Technology, c("Risky", "Technology"), extra = "merge", fill = "left")%>%
+  select(-Risky) %>% 
+  group_by(Technology, Perceived_Risk) %>%
+  summarise(n=n()) %>%
+  pivot_wider(names_from = "Perceived_Risk", values_from = "n")
+
+likert(Measure ~ ., data=likertstack, ylab=NULL,
+       ReferenceZero=3, as.percent=TRUE,
+       positive.order=TRUE, 
+       main = list("Pereived risk from energy technologies in India",x=unit(.55, "npc")), 
+       sub= list("Perceived risk",x=unit(.57, "npc")), 
+       xlim=c(-40,-20,0,20,40,60,80,100),
+       strip=FALSE, 
+       par.strip.text=list(cex=.7))
+```
+
+```{r}
+
 # summary statistics for benefits from different energy sources
@@
 
-module2%>%
+colorsequence<- c("#8C4646","#D9695F","#F2A679","#F2D091","#5D8C7B","#808080")
+df_barplotben <- module2%>%
   filter(!row_number() %in% c(1,2)) %>% 
@@
   group_by(Technology, Perceived_Benefit) %>%
-  summarise(n=n())%>%
-ggplot(aes(fill= Perceived_Benefit, y=n, x=Technology)) + 
-  geom_bar(position="fill", stat="identity")+
-  coord_flip()
+  summarise(n=n())
+
+df_barplotben %>% ggplot(aes(fill= factor(Perceived_Benefit, levels=c("Extremely beneficial", "Very beneficial","Moderately beneficial","Slightly beneficial","Not at all beneficial","Rather not say/Don't know")), y=n , x=Technology)) +
+  geom_bar(position="fill",stat="identity")+
+  scale_fill_manual("legend", values = c("Extremely beneficial" = "#5D8C7B", "Very beneficial" = "#F2D091", "Moderately beneficial" = "#F2A679", "Slightly beneficial" = "#D9695F","Not at all beneficial" = "#8C4646", "Rather not say/Don't know" = "#808080"))+
+  coord_flip()+
+  theme_classic()
 

### 2022-03-09 moduletwoanalysis.Rmd
fixed graphs

@@
 
+#trying to work with likert packages here
+
 likertstack <- module2%>%
@@
   select(technology, perceivedrisk.mean, perceivedbenefit.mean) %>%
+  mutate(technology = fct_reorder(technology, perceivedrisk.mean, .desc = TRUE))%>%
    gather(key = "level", value = "mean",
        perceivedrisk.mean, perceivedbenefit.mean) %>%
-  ggplot(aes(x=technology, y= mean, fill = level))+
+  ggplot(aes(x=technology, y= mean, fill = level, ))+
   geom_bar(stat="identity", position=position_dodge())+
-  coord_flip()
+  ylim(0,4)+
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
+  scale_fill_manual("legend", values = c("perceivedbenefit.mean" = "palegreen3", "perceivedrisk.mean" = "firebrick2"))
 
@@
 ```
+```{r}
+full_join(risksummary,benefitsummary, by = NULL, copy = FALSE, keep = FALSE) %>%
+  select(technology, perceivedrisk.mean, perceivedbenefit.mean) %>%
+  mutate(technology = fct_reorder(technology, perceivedbenefit.mean, .desc = TRUE))%>%
+   gather(key = "level", value = "mean",
+       perceivedrisk.mean, perceivedbenefit.mean) %>%
+  ggplot(aes(x=technology, y= mean, fill = level, ))+
+  geom_bar(stat="identity", position=position_dodge())+
+  ylim(0,4)+
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
+  scale_fill_manual("legend", values = c("perceivedbenefit.mean" = "palegreen3", "perceivedrisk.mean" = "firebrick2"))
+```
 
 ```{r}
+
 full_join(risksummary,benefitsummary, by = NULL, copy = FALSE, keep = FALSE) %>%
   select(technology, perceivedrisk.median, perceivedbenefit.median) %>%
+  mutate(technology = fct_reorder(technology, perceivedrisk.median, .desc = TRUE))%>%
    gather(key = "level", value = "median",
        perceivedrisk.median, perceivedbenefit.median) %>%
-  ggplot(aes(x=technology, y= median, fill = level))+
+  ggplot(aes(x=technology, y= median, fill = level, ))+
   geom_bar(stat="identity", position=position_dodge())+
-  coord_flip()
+  ylim(0,4)+
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
+  scale_fill_manual("legend", values = c("perceivedbenefit.median" = "palegreen3", "perceivedrisk.median" = "firebrick2"))
+
+# arrange descending and facet wrap by IND prefix
 

### 2022-03-10 moduletwoanalysis.Rmd
distributiion graphs for Kahan scale

@@
 output:
+  word_document: default
   html_document:
@@
     fig_height: 6
-    fig_caption: true
-    keep_md: true
+    fig_caption: yes
+    keep_md: yes
     theme: paper
@@
 
-#trying to work with likert packages here
-
-likertstack <- module2%>%
-  filter(!row_number() %in% c(1,2)) %>% 
-  select(starts_with("RISKY"))%>%
-  gather(Technology, Perceived_Risk, Risky_Hydro:Risky_INDLPG, factor_key = TRUE)%>%
-  separate(Technology, c("Risky", "Technology"), extra = "merge", fill = "left")%>%
-  select(-Risky) %>% 
-  group_by(Technology, Perceived_Risk) %>%
-  summarise(n=n()) %>%
-  pivot_wider(names_from = "Perceived_Risk", values_from = "n")
-
-likert(Measure ~ ., data=likertstack, ylab=NULL,
-       ReferenceZero=3, as.percent=TRUE,
-       positive.order=TRUE, 
-       main = list("Pereived risk from energy technologies in India",x=unit(.55, "npc")), 
-       sub= list("Perceived risk",x=unit(.57, "npc")), 
-       xlim=c(-40,-20,0,20,40,60,80,100),
-       strip=FALSE, 
-       par.strip.text=list(cex=.7))
-```
-
-```{r}
-
 # summary statistics for benefits from different energy sources
@@
 ```
+```{r}
+ #median score for Kahan invidualism scale
+
+codedmodule2 %>%
+  select((starts_with(c("K_I", "K_S"))))%>%
+  gather(key = "K_I", value = "score")%>%
+  na.omit()%>%
+  summarise(median = median(c(score)))
+
+```
+```{r}
+
+# Kahan scale median score for Hierarchy scale
+codedmodule2 %>%
+  select((starts_with(c("K_H", "K_E"))))%>%
+  gather(key = "K_H", value = "score")%>%
+  na.omit()%>%
+  summarise(median = median(c(score)))
+```
+
+```{r}
+#calculating individualism score for each respondent
+
+Kscalescores <- codedmodule2 %>%
+  select(starts_with(c("Risky","K_I","K_S", "K_H", "K_E")))%>%
+  rowwise()%>%
+  na.omit()%>%
+  mutate(Individualism_score = mean(c_across(K_IINTRFER:K_SPROTECT)))%>%
+  mutate(Hierarchy_score = mean(c_across(K_HEQUAL:K_ERADEQ2)))%>%
+  select(!starts_with(c("K_I","K_S", "K_H", "K_E")))
+
+Kscalescores
+
+```
+
+```{r}
+
+#scatter plot of Kahan scale scores around the median scores on Individualism and Hierarchy scales.
+
+Kscalescores %>%
+  ggplot(aes(Individualism_score, Hierarchy_score))+
+  geom_point()+
+  geom_hline(yintercept=2, colour="black", lwd=1)+
+  geom_vline(xintercept=3, colour="black", lwd=1)
+
+```
+
+```{r}
+# checking distribution of scores on Individualism scale
+
+Kscalescores %>%
+  ggplot(aes(x=Individualism_score, y = ..count..), fill = "lightgray")+
+  geom_density()
+
+```
+
+```{r}
+# checking distribution of scores on Hierarchy scale 
+Kscalescores %>%
+  ggplot(aes(x=Hierarchy_score, y = ..count..), fill = "lightgray")+
+  geom_density()
+```
+
+```{r}
+
+```
 

### 2022-03-11 module2extra.Rmd
PCAs and screeplots

---
title: "module2extra"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2022-03-11 moduleoneanalysis.Rmd
PCAs and screeplots

@@
 ```
+
+```{r}
+#trying to work with likert packages here
+
+likertstack <- module2%>%
+  filter(!row_number() %in% c(1,2)) %>% 
+  select(starts_with("RISKY"))%>%
+  gather(Technology, Perceived_Risk, Risky_Hydro:Risky_INDLPG, factor_key = TRUE)%>%
+  separate(Technology, c("Risky", "Technology"), extra = "merge", fill = "left")%>%
+  select(-Risky) %>% 
+  group_by(Technology, Perceived_Risk) %>%
+  summarise(n=n()) %>%
+  pivot_wider(names_from = "Perceived_Risk", values_from = "n")
+
+likert(Measure ~ ., data=likertstack, ylab=NULL,
+       ReferenceZero=3, as.percent=TRUE,
+       positive.order=TRUE, 
+       main = list("Pereived risk from energy technologies in India",x=unit(.55, "npc")), 
+       sub= list("Perceived risk",x=unit(.57, "npc")), 
+       xlim=c(-40,-20,0,20,40,60,80,100),
+       strip=FALSE, 
+       par.strip.text=list(cex=.7))
+```

### 2022-03-11 moduletwoanalysis.Rmd
PCAs and screeplots

@@
 suppressPackageStartupMessages(library(ggplot2))
+suppressPackageStartupMessages(library(ggbiplot))
+
 ```
+
+The module2 of the survey on the perception of risk and benefit from energy technologies in India.
+
+Following is the complete data set with 1099 responses.
 
@@
 ```
+
+Following graphs show the distribution of percerived risk and benefit on the likert scale
+
+```{r}
+
+#plotting perceived risk from different technologies
+
+module2%>%
+  filter(!row_number() %in% c(1,2)) %>% 
+  select(starts_with("RISKY"))%>%
+  gather(Technology, Perceived_Risk, Risky_Hydro:Risky_INDLPG, factor_key = TRUE)%>%
+  separate(Technology, c("Risky", "Technology"), extra = "merge", fill = "left")%>%
+  select(-Risky) %>%
+  group_by(Technology, Perceived_Risk) %>%
+  dplyr::summarise(n=n())
+
+colorsequence<- c("#8C4646","#D9695F","#F2A679","#F2D091","#5D8C7B","#808080")
+df_barplot<-module2%>%
+  filter(!row_number() %in% c(1,2)) %>% 
+  select(starts_with("RISKY"))%>%
+  gather(Technology, Perceived_Risk, Risky_Hydro:Risky_INDLPG, factor_key = TRUE)%>%
+  separate(Technology, c("Risky", "Technology"), extra = "merge", fill = "left")%>%
+  select(-Risky) %>% 
+  group_by(Technology, Perceived_Risk) %>%
+  dplyr::summarise(n=n())
+
+df_barplot %>% ggplot(aes(fill= fct_rev(factor(Perceived_Risk, levels=c("Extremely risky", "Very risky","Moderately risky","Slightly risky","Not at all risky","Rather not say/Don't know"))), y=n , x=Technology)) +
+  geom_bar(position="fill",stat="identity")+
+  scale_x_discrete(limits = c("Solar", "INDSolar", "INDFirewoodetc" ,"Wind" , "Hydro", "INDWind", "INDHydro", "INDDiesel" , "INDBiogas","INDKerosene", "Oil", "Coal","Gas", "INDLPG","Nuclear"))+
+  scale_fill_manual("legend", values = c("Extremely risky" = "#8C4646", "Very risky" = "#D9695F", "Moderately risky" = "#F2A679", "Slightly risky" = "#F2D091","Not at all risky" = "#5D8C7B", "Rather not say/Don't know" = "#808080"))+
+  coord_flip()+
+  theme_classic()
+
+```
+
+```{r}
+
+colorsequence<- c("#8C4646","#D9695F","#F2A679","#F2D091","#5D8C7B","#808080")
+
+df_barplotben <- module2%>%
+  filter(!row_number() %in% c(1,2)) %>% 
+  select(starts_with("Ben"))%>%
+  gather(Technology, Perceived_Benefit, Ben_Hydro:Ben_INDKerosene, factor_key = TRUE)%>%
+  separate(Technology, c("Ben", "Technology"), extra = "merge", fill = "left")%>%
+  select(-Ben) %>% 
+  group_by(Technology, Perceived_Benefit) %>%
+  dplyr::summarise(n=n())
+
+df_barplotben %>% ggplot(aes(fill= factor(Perceived_Benefit, levels=c("Rather not say/Don't know","Not at all beneficial","Slightly beneficial","Moderately beneficial","Very beneficial", "Extremely beneficial")), y=n , x=Technology)) +
+  geom_bar(position="fill",stat="identity")+
+  scale_fill_manual("legend", values = c("Rather not say/Don't know" = "grey94" ,"Not at all beneficial" = "orange","Slightly beneficial"="yellow" ,"Moderately beneficial" = "palegreen","Very beneficial"= "green3", "Extremely beneficial"= "green4"))+
+  theme_classic()+
+  coord_flip()
+
+# fix Rather not say issue.
+
+```
+
+Now I am converting the likert scale for various scales used in the survey to numeric values from 1 to 5, Rather Not Say/Don't know is printed as NA. Some variables had to be reverse coded as well.
 
@@
 codedmodule2
+```
 
-```
+Following table shows the summary statistics of perceived risk from different energy technologies.
+
 ```{r, eval=TRUE}
@@
   select(-rowname, -Risky) %>%
-  arrange(mean)%>%
-  setNames(paste0('perceivedrisk.', names(.)))%>%
-  rename(technology = perceivedrisk.technology)
+  arrange(mean) %>%
+  setNames(paste0('perceivedrisk.', names(.))) %>%
+  dplyr::rename(technology= perceivedrisk.technology)
 
@@
 
-```{r}
-#plotting perceived risk from different technologies
-
-module2%>%
-  filter(!row_number() %in% c(1,2)) %>% 
-  select(starts_with("RISKY"))%>%
-  gather(Technology, Perceived_Risk, Risky_Hydro:Risky_INDLPG, factor_key = TRUE)%>%
-  separate(Technology, c("Risky", "Technology"), extra = "merge", fill = "left")%>%
-  select(-Risky) %>%
-  group_by(Technology, Perceived_Risk) %>%
-  summarise(n=n())
-
-```
-
-```{r}
-
-colorsequence<- c("#8C4646","#D9695F","#F2A679","#F2D091","#5D8C7B","#808080")
-df_barplot<-module2%>%
-  filter(!row_number() %in% c(1,2)) %>% 
-  select(starts_with("RISKY"))%>%
-  gather(Technology, Perceived_Risk, Risky_Hydro:Risky_INDLPG, factor_key = TRUE)%>%
-  separate(Technology, c("Risky", "Technology"), extra = "merge", fill = "left")%>%
-  select(-Risky) %>% 
-  group_by(Technology, Perceived_Risk) %>%
-  summarise(n=n())
-
-df_barplot %>% ggplot(aes(fill= fct_rev(factor(Perceived_Risk, levels=c("Extremely risky", "Very risky","Moderately risky","Slightly risky","Not at all risky","Rather not say/Don't know"))), y=n , x=Technology)) +
-  geom_bar(position="fill",stat="identity")+
-  scale_fill_manual("legend", values = c("Extremely risky" = "#8C4646", "Very risky" = "#D9695F", "Moderately risky" = "#F2A679", "Slightly risky" = "#F2D091","Not at all risky" = "#5D8C7B", "Rather not say/Don't know" = "#808080"))+
-  coord_flip()+
-  theme_classic()
-
-# fix ugly visual. Rearrange from extremely risky to not at all risky. Red to green, rather not say/Don't know should be grey. Also facet wrap by INDividually owned and centrally owned technology.
-
-```
+Following table shows the summary statistics of perceived benefit from different energy technologies.
 
@@
   setNames(paste0('perceivedbenefit.', names(.))) %>%
-  rename(technology = perceivedbenefit.technology)
+  dplyr::rename(technology = perceivedbenefit.technology)
 benefitsummary
@@
 
-```{r}
-
-colorsequence<- c("#8C4646","#D9695F","#F2A679","#F2D091","#5D8C7B","#808080")
-df_barplotben <- module2%>%
-  filter(!row_number() %in% c(1,2)) %>% 
-  select(starts_with("Ben"))%>%
-  gather(Technology, Perceived_Benefit, Ben_Hydro:Ben_INDLPG, factor_key = TRUE)%>%
-  separate(Technology, c("Ben", "Technology"), extra = "merge", fill = "left")%>%
-  select(-Ben) %>% 
-  group_by(Technology, Perceived_Benefit) %>%
-  summarise(n=n())
-
-df_barplotben %>% ggplot(aes(fill= factor(Perceived_Benefit, levels=c("Extremely beneficial", "Very beneficial","Moderately beneficial","Slightly beneficial","Not at all beneficial","Rather not say/Don't know")), y=n , x=Technology)) +
-  geom_bar(position="fill",stat="identity")+
-  scale_fill_manual("legend", values = c("Extremely beneficial" = "#5D8C7B", "Very beneficial" = "#F2D091", "Moderately beneficial" = "#F2A679", "Slightly beneficial" = "#D9695F","Not at all beneficial" = "#8C4646", "Rather not say/Don't know" = "#808080"))+
-  coord_flip()+
-  theme_classic()
-
-# fix ugly visual.
-Rearrange from extremely beneficial to not at all beneficial.
-Green to red, rather not say/Don't know should be grey.
-Also facet wrap by INDividually owned and centrally owned technology.
-Also arrange descending from most beneficial to least beneficial.
-
-```
-
-```{r}
-#summary statistics for nuclear energy accept, reject and reluctantly accept scale
-codedmodule2 %>%
-  summarize_at(vars(N_accept,N_reject,N_reluctantlyaccept), list(~mean(., na.rm = TRUE),~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE),~n())) %>%
-  add_rownames() %>%
-  gather(acceptance, value, -rowname) %>%
-  separate(acceptance, c("N_accept", "var") ,  extra = "merge", fill = "left") %>%
-  separate(var, c("Acceptance", "summary")) %>%
-  spread(summary, value) %>%
-  select(-rowname, -N_accept)%>%
-  arrange(mean)
-
-```
-
-```{r}
-
-# chi square test for risk perception from nuclear energy and gender, race
-
-# first combine gender and caste variables
-
-chitest <- codedmodule2 %>%
-  select(Risky_Nuclear,Risky_Hydro, Risky_Hydro, Risky_Solar,Urban_Rural, Gender, Caste) %>%
-  na.omit() %>%
-  filter(!Caste=="Rather not say/Don't know")%>%
-  unite(gendercaste, Gender, Caste, sep = "_", remove = FALSE)
-
-chitest
-
-```
+bar plots for means of perceived risk and benefit from various energy technologies
 
@@
 
-# arrange descending and facet wrap by IND prefix
-
 ```
-```{r}
-full_join(risksummary,benefitsummary, by = NULL, copy = FALSE, keep = FALSE) %>%
-  select(technology, perceivedrisk.mean, perceivedbenefit.mean) %>%
-  mutate(technology = fct_reorder(technology, perceivedbenefit.mean, .desc = TRUE))%>%
-   gather(key = "level", value = "mean",
-       perceivedrisk.mean, perceivedbenefit.mean) %>%
-  ggplot(aes(x=technology, y= mean, fill = level, ))+
-  geom_bar(stat="identity", position=position_dodge())+
-  ylim(0,4)+
-  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
-  scale_fill_manual("legend", values = c("perceivedbenefit.mean" = "palegreen3", "perceivedrisk.mean" = "firebrick2"))
-```
+bar plots for median of perceived risk and benefit from various energy technologies
 
@@
 
-# arrange descending and facet wrap by IND prefix
+```
+PCA on all indepdendent variables in the data set
 
-# arrange descending and facet wrap by IND prefix
+```{r}
+#PCA on all variables
+
+pcaresults <- codedmodule2 %>%
+  select(!starts_with(c("Risky","BEN", "Gender","Caste","Religion","State", "Age", "Otherreligion", "Urban_Rural","Language", "Survey_Date", "N_accept", "N_reject", "N_reluctantlyaccept")))%>%
+  na.omit()%>%
+  prcomp(center = TRUE, scale. = TRUE)
+
+summary(pcaresults)
+
+var_explained = pcaresults$sdev^2 / sum(pcaresults$sdev^2)
+
+pcaresults
 
 ```
+
+Scree plot of results from PCA
+
+```{r}
+
+qplot(c(1:90), var_explained) + 
+  geom_line() + 
+  xlab("Principal Component") + 
+  ylab("Variance Explained") +
+  ggtitle("Scree Plot") +
+  ylim(0, 0.20)+
+  xlim(1,7)
+
+```
+
+Coding and Combining items on Kahan scale
+
 ```{r}
@@
 ```{r}
-#calculating individualism score for each respondent
+#calculating individualism score and hierarchy score for each respondent
 
@@
   na.omit()%>%
-  mutate(Individualism_score = mean(c_across(K_IINTRFER:K_SPROTECT)))%>%
-  mutate(Hierarchy_score = mean(c_across(K_HEQUAL:K_ERADEQ2)))%>%
-  select(!starts_with(c("K_I","K_S", "K_H", "K_E")))
+  dplyr::mutate(Individualism_score = mean(c_across(K_IINTRFER:K_SPROTECT)))%>%
+  dplyr::mutate(Hierarchy_score = mean(c_across(K_HEQUAL:K_ERADEQ2)))%>%
+  dplyr::select(!starts_with(c("K_I","K_S", "K_H", "K_E")))
 
@@
 
+Coding and combining items on the eco-political scale - characteristics of the perceiver
+
+```{r}
+ecopolscalescores <- codedmodule2 %>%
+  select(starts_with(c("Risky","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG", "Gender","Caste","Religion", "State")))%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(Pro_decentralisation = mean(c_across("DECISIONDECEN":"DECISIONCEN")))%>%
+   dplyr::mutate(Pro_largescale = mean(c_across("INDUSTRYLARGE":"INDUSTRYSMALL")))%>%
+   dplyr::mutate(Pro_global = mean(c_across("ECONOMYGLOBAL":"ECONOMYLOCAL")))%>%
+   dplyr::mutate(Pro_ecogrowth = mean(c_across("ENVOVERDEV":"DEVOVERENV")))%>%
+   dplyr::mutate(Pro_private = mean(c_across("OWNERPVT":"OWNERREG")))%>%
+  dplyr::select(!c("DECISIONDECEN","DECISIONCEN", "INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL", "ECONOMYLOCAL","ENVOVERDEV",     "DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG"))
+
+ecopolscalescores
+```
+
+PCA test on the new eco-pol scale - characteristics of the perceiver
+
+```{r}
+# PCA test on qualities of the perceiver
+
+ecopolscalepca <- ecopolscalescores %>%
+  select(!starts_with(c("Risky","Gender","Caste","Religion","State")))%>%
+  prcomp(center = TRUE,scale. = TRUE)
+
+var_explained_ecopol = ecopolscalepca$sdev^2 / sum(ecopolscalepca$sdev^2)
+
+summary(ecopolscale_pca)
+
+```
 ```{r}
 
+qplot(c(1:11), var_explained_ecopol) + 
+  geom_line() + 
+  xlab("Principal Component") + 
+  ylab("Variance Explained") +
+  ggtitle("Scree Plot") +
+  ylim(0.05, 0.20)+
+  xlim(1,7)
+
 ```
-
-```{r}
-
-chisq.test(chitest$Risky_Nuclear, chitest$Urban_Rural)
-```

### 2022-03-11 moduletwoanalysis.Rmd
knit to html

@@
 output:
-  word_document: default
   html_document:
@@
 
-summary(ecopolscale_pca)
+summary(ecopolscalepca)
 

### 2022-03-11 moduletwoanalysis.Rmd
remove printing of pcaresults
spacing issues in HTML file fixed
fixed visuals and PCA tables

@@
     df_print: paged
+
 ---
 
-```{r load packages, warning = FALSE, message = FALSE}
+```{r load packages, warning = FALSE, message = FALSE, echo=FALSE}
+  knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+
 suppressPackageStartupMessages(library(tidyverse))
@@
 
-```{r}
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
 moduletwo <- read_excel( "~/Desktop/thesis_surveydata/political_factors_complete.xlsx")
@@
 module2 <- data.frame(moduletwo)
+module2[module2 == "Rather not say/ Don't know"] <- "Rather not say/Don't know"
 module2 %>%
@@
 
-Following graphs show the distribution of percerived risk and benefit on the likert scale
+Following graph show the distribution of perceived risk on the likert scale
 
-```{r}
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
 
@@
   scale_x_discrete(limits = c("Solar", "INDSolar", "INDFirewoodetc" ,"Wind" , "Hydro", "INDWind", "INDHydro", "INDDiesel" , "INDBiogas","INDKerosene", "Oil", "Coal","Gas", "INDLPG","Nuclear"))+
-  scale_fill_manual("legend", values = c("Extremely risky" = "#8C4646", "Very risky" = "#D9695F", "Moderately risky" = "#F2A679", "Slightly risky" = "#F2D091","Not at all risky" = "#5D8C7B", "Rather not say/Don't know" = "#808080"))+
+  scale_fill_manual("legend", values = c("Extremely risky" = "#8C4646", "Very risky" = "#D9695F", "Moderately risky" = "#F2A679", "Slightly risky" = "#F2D091","Not at all risky" = "#5D8C7B", "Rather not say/Don't know" = "grey94"))+
   coord_flip()+
@@
 
-```{r}
+Following graph show the distribution of perceived  benefit on the likert scale
 
-colorsequence<- c("#8C4646","#D9695F","#F2A679","#F2D091","#5D8C7B","#808080")
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
 
@@
   scale_fill_manual("legend", values = c("Rather not say/Don't know" = "grey94" ,"Not at all beneficial" = "orange","Slightly beneficial"="yellow" ,"Moderately beneficial" = "palegreen","Very beneficial"= "green3", "Extremely beneficial"= "green4"))+
+  scale_x_discrete(limits = c("Solar", "INDSolar", "INDFirewoodetc" , "INDLPG", "Wind" , "Hydro", "INDWind", "INDHydro", "INDDiesel" , "INDBiogas","INDKerosene", "Oil", "Coal","Gas","Nuclear"))+
   theme_classic()+
@@
 
-```{r, eval =TRUE}
+```{r, eval =TRUE, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
 #This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
@@
 
-```{r, eval=TRUE}
+```{r, eval=TRUE, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
 
@@
 
-```{r}
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
 
@@
 
-```{r}
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+
 full_join(risksummary,benefitsummary, by = NULL, copy = FALSE, keep = FALSE) %>%
@@
   ylim(0,4)+
-  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
-  scale_fill_manual("legend", values = c("perceivedbenefit.mean" = "palegreen3", "perceivedrisk.mean" = "firebrick2"))
+  scale_fill_manual("legend", values = c("perceivedbenefit.mean" = "palegreen3", "perceivedrisk.mean" = "firebrick2"))+
+  coord_flip()
 
 ```
+
 bar plots for median of perceived risk and benefit from various energy technologies
 
-```{r}
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
 
@@
   ylim(0,4)+
-  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
-  scale_fill_manual("legend", values = c("perceivedbenefit.median" = "palegreen3", "perceivedrisk.median" = "firebrick2"))
+  scale_fill_manual("legend", values = c("perceivedbenefit.median" = "palegreen3", "perceivedrisk.median" = "firebrick2"))+
+  coord_flip()
 
 ```
-PCA on all indepdendent variables in the data set
 
-```{r}
+Conducted PCA on all independent variables in the data set. The following table shows the variables that are part of the resultant principal components.
+
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+
 #PCA on all variables
@@
 
-summary(pcaresults)
+rotations = pcaresults["rotation"]
 
-var_explained = pcaresults$sdev^2 / sum(pcaresults$sdev^2)
+#calculate total variance explained by each principal component
+var_explained <- pcaresults$sdev^2 / sum(pcaresults$sdev^2)
 
-pcaresults
+rotationsDF <- do.call(rbind.data.frame, rotations)
+rotationsDF
+```
+
+Following tibble shows variance explained by each Principal component
+
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+
+data.frame(var_explained, row.names=names(rotationsDF))
 
@@
 
-Scree plot of results from PCA
+Scree plot of the previous table. Including only till PC7
 
-```{r}
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
 
@@
 
-```{r}
+Median score for Kahan on invidualism scale
+
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+
 #median score for Kahan invidualism scale
@@
 ```
-```{r}
+
+Kahan scale median score for Hierarchy scale
+
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
 
@@
 
-```{r}
+Calculating individualism score and hierarchy score for each respondent
+
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
 #calculating individualism score and hierarchy score for each respondent
@@
 
-```{r}
+scatter plot of Kahan scale scores around the median scores on Individualism and Hierarchy scales.
+
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
 
@@
 
-```{r}
+checking distribution of scores on Individualism scale
+
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
 # checking distribution of scores on Individualism scale
@@
 
-```{r}
+checking distribution of scores on Hierarchy scale 
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
 # checking distribution of scores on Hierarchy scale 
@@
 
-```{r}
+```{r, echo= FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
 ecopolscalescores <- codedmodule2 %>%
@@
 
-```{r}
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
 # PCA test on qualities of the perceiver
@@
 ```
-```{r}
+
+```{r, echo=FALSE}
+
+rotationsecopol = ecopolscalepca["rotation"]
+rotationsDFecopol <- do.call(rbind.data.frame, rotationsecopol)
+rotationsDFecopol
+```
+
+```{r, echo=FALSE}
 

### 2022-03-14 module2extra.Rmd
Terre's suggestion

@@
 title: "module2extra"
-output: html_document
+output:
+  html_document:
+    fig_width: 7
+    fig_height: 6
+    fig_caption: yes
+    keep_md: yes
+    theme: paper
+    df_print: paged
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+```{r}
+
+likertmodule2 <- module2%>%
+  filter(!row_number() %in% c(1,2)) %>% 
+  select(starts_with("Ben"))%>%
+  gather(Technology, Perceived_Benefit, Ben_Hydro:Ben_INDKerosene)%>%
+  separate(Technology, c("Ben", "Technology"), extra = "merge", fill = "left")%>%
+  select(-Ben) %>% 
+  group_by(Technology, Perceived_Benefit) %>%
+  dplyr::summarise(n=n())%>%
+  mutate(Perceived_Benefit = factor(Perceived_Benefit,  levels = c("Rather not say/Don't know","Not at all beneficial","Slightly beneficial","Moderately beneficial","Very beneficial", "Extremely beneficial")))%>%
+  pivot_wider(names_from = Perceived_Benefit, values_from = n)%>%
+  rename("NA1"="Rather not say/Don't know")%>%
+  select("Technology","Not at all beneficial","Slightly beneficial","Moderately beneficial","Very beneficial", "Extremely beneficial", "NA1","NA")%>%
+  unite("Rather not say/Don't know", "NA1":"NA", na.rm = TRUE, remove = FALSE)%>%
+  select(!c("NA1","NA"))
+
 ```
 
-## R Markdown
+```{r}
+#summary statistics for nuclear energy accept, reject and reluctantly accept scale
+codedmodule2 %>%
+  summarize_at(vars(N_accept,N_reject,N_reluctantlyaccept), list(~mean(., na.rm = TRUE),~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE),~n())) %>%
+  add_rownames() %>%
+  gather(acceptance, value, -rowname) %>%
+  separate(acceptance, c("N_accept", "var") ,  extra = "merge", fill = "left") %>%
+  separate(var, c("Acceptance", "summary")) %>%
+  spread(summary, value) %>%
+  select(-rowname, -N_accept)%>%
+  arrange(mean)
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
-
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
-```{r cars}
-summary(cars)
 ```
 
-## Including Plots
+```{r}
 
-You can also embed plots, for example:
+# chi square test for risk perception from nuclear energy and gender, race
 
-```{r pressure, echo=FALSE}
-plot(pressure)
+# first combine gender and caste variables
+
+chitest <- codedmodule2 %>%
+  select(Risky_Nuclear,Risky_Hydro, Risky_Hydro, Risky_Solar,Urban_Rural, Gender, Caste) %>%
+  na.omit() %>%
+  filter(!Caste=="Rather not say/Don't know")%>%
+  unite(gendercaste, Gender, Caste, sep = "_", remove = FALSE)
+
+chitest
+
 ```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2022-03-14 module2graphsandPCA.Rmd
Terre's suggestion

---
title: "module2graphsandPCA"
output: 
output:
  html_document:
    fig_width: 7
    fig_height: 6
    fig_caption: yes
    keep_md: yes
    theme: paper
    df_print: paged

---

```{r load packages, warning = FALSE, message = FALSE, echo=FALSE}
  knitr::opts_chunk$set(warning = FALSE, message = FALSE)

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(hablar))
suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(DT))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(ggbiplot))

```

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
moduletwo <- read_excel( "~/Desktop/thesis_surveydata/political_factors_complete.xlsx")
save(moduletwo, file = "moduletwo.rda")
module2 <- data.frame(moduletwo)
module2[module2 == "Rather not say/ Don't know"] <- "Rather not say/Don't know"
module2 %>%
  filter(!row_number() %in% c(1,2))

# loaded data set for module 2 eco -pol variables and removes the rows with question number and question text
```

```{r, eval =TRUE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
codedmodule2 <- module2 %>%

#remove row 1
  filter(!row_number() %in% c(1,2)) %>%

# replace risky likert scale with numbers
  mutate_at(vars(starts_with("Risky")), funs(case_when(. =="Not at all risky" ~ 1, 
                                                       . =="Slightly risky" ~ 2, 
                                                       . =="Moderately risky" ~ 3, 
                                                       . =="Very risky" ~ 4, 
                                                       . =="Extremely risky" ~ 5))) %>%

# replace beneficial likert scale with numbers  
  mutate_at(vars(starts_with("Ben")), funs(case_when(. =="Not at all beneficial" ~ 1,
                                                     . =="Slightly beneficial" ~ 2,
                                                     . =="Moderately beneficial" ~ 3,
                                                     . =="Very beneficial" ~ 4,
                                                     . =="Extremely beneficial" ~ 5 ))) %>%

# replace nuclear acceptance likert scale with numbers
  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                                        . == "Somewhat disagree" ~ 2,
                                                                        . == "Neither agree nor disagree" ~3,
                                                                        . == "Somewhat agree" ~ 4,
                                                                        . == "Strongly agree" ~ 5))) %>%

# code likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_I","K_H","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE", "DEV", "PROSPER", "RELY"))), funs(case_when(. == "Strongly disagree" ~ 1, 
               . == "Somewhat disagree" ~ 2,
               . == "Neither agree nor disagree" ~3,
               . == "Somewhat agree" ~ 4,
               . == "Strongly agree" ~ 5))) %>%

# reverse code for likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_S","K_E"))), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                               . == "Somewhat disagree" ~ 4,
                                                               . == "Neither agree nor disagree" ~3,
                                                               . == "Somewhat agree" ~ 2,
                                                               . == "Strongly agree" ~ 1))) %>%

# code eco-pol scale variables into numbers
  mutate_at(vars(SYSTEMDEMO,SYSTEMRELIGION,SYSTEMTECHNO,SYSTEMTOTAL,WEALTHLIM,MECHANISATION,DECISIONDECEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG), funs(case_when(. == "Strongly disagree" ~ 1, 
                        . == "Somewhat disagree" ~ 2,
                        . == "Neither agree nor disagree" ~3,
                        . == "Somewhat agree" ~ 4,
                        . == "Strongly agree" ~ 5))) %>%

# reverse code eco-pol scale variables into numbers 
 mutate_at(vars(DECISIONCEN, INDUSTRYSMALL, ECONOMYLOCAL, ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                                                                         . == "Somewhat disagree" ~ 4,
                                                                                                         . == "Neither agree nor disagree" ~3,
                                                                                                         . == "Somewhat agree" ~ 2,
                                                                                                         . == "Strongly agree" ~ 1)))

codedmodule2
```

1. Plot the  mean risk scores (Q1)as histogram ordered from high to low risk – so basically the red bars only in reverse order (aka nuclear as high risk).

```{r, eval=TRUE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

# summary statistics for risks from different energy sources

risksumcentral <- codedmodule2 %>%
  select(!starts_with(c("RISKY_IND")))%>%
  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #add row index so later spreading indexed correctly
  add_rownames()%>%
  #melt to long format
  gather(technology, value, -rowname) %>%
  # separate risky from variable suffix
  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "summary")) %>%
  # spread summary values back to wide form
  spread(summary,value) %>%
  #clean up
  select(-rowname, -Risky) %>%
  arrange(mean) %>%
  setNames(paste0('perceivedrisk.', names(.))) %>%
  dplyr::rename(technology= perceivedrisk.technology)

risksumcentral

```

```{r, echo=FALSE}

knitr::opts_chunk$set(warning = FALSE, message = FALSE)

risksumcentral %>%
  select(technology, perceivedrisk.mean) %>%
  mutate(technology = fct_reorder(technology, perceivedrisk.mean, .desc = FALSE))%>%
  ggplot(aes(x=technology, y= perceivedrisk.mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
  ylim(0,4)+
  labs(y = "Mean Values of Perceived Risk", x = "Energy Technologies")+
  ggtitle("Your Title Here")+
  coord_flip()

```

```{r, eval=TRUE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

# summary statistics for risks from different energy sources

risksumIND <- codedmodule2 %>%
  summarize_at(vars(starts_with(c("RISKY_IND"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #add row index so later spreading indexed correctly
  add_rownames()%>%
  #melt to long format
  gather(technology, value, -rowname) %>%
  # separate risky from variable suffix
  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "summary")) %>%
  # spread summary values back to wide form
  spread(summary,value) %>%
  #clean up
  select(-rowname, -Risky) %>%
  arrange(mean) %>%
  setNames(paste0('perceivedrisk.', names(.))) %>%
  dplyr::rename(technology= perceivedrisk.technology)

risksumIND

```

```{r, echo=FALSE}

knitr::opts_chunk$set(warning = FALSE, message = FALSE)

risksumIND %>%
  select(technology, perceivedrisk.mean) %>%
  mutate(technology = fct_reorder(technology, perceivedrisk.mean, .desc = FALSE))%>%
  ggplot(aes(x=technology, y= perceivedrisk.mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
  ylim(0,4)+
  labs(y = "Mean Values of Perceived Risk", x = "Energy Technologies")+
  ggtitle("Your Title Here")+
  coord_flip()

```

```{r, eval=TRUE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

# summary statistics for risks from different energy sources

bensumcentral <- codedmodule2 %>%
  select(!starts_with(c("Ben_IND")))%>%
  summarize_at(vars(starts_with(c("Ben"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #add row index so later spreading indexed correctly
  add_rownames()%>%
  #melt to long format
  gather(technology, value, -rowname) %>%
  # separate risky from variable suffix
  separate(technology, c("Ben", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "summary")) %>%
  # spread summary values back to wide form
  spread(summary,value) %>%
  #clean up
  select(-rowname, -Ben) %>%
  arrange(mean) %>%
  setNames(paste0('perceivedbenefit.', names(.))) %>%
  dplyr::rename(technology= perceivedbenefit.technology)

bensumcentral

```

```{r, echo=FALSE}

knitr::opts_chunk$set(warning = FALSE, message = FALSE)

bensumcentral %>%
  select(technology, perceivedbenefit.mean) %>%
  mutate(technology = fct_reorder(technology, perceivedbenefit.mean, .desc = FALSE))%>%
  ggplot(aes(x=technology, y= perceivedbenefit.mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
  ylim(0,4)+
  labs(y = "Mean Values of Perceived Benefit", x = "Energy Technologies")+
  ggtitle("Your Title Here")+
  coord_flip()

```

```{r, eval=TRUE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

# summary statistics for risks from different energy sources

bensumIND <- codedmodule2 %>%
  summarize_at(vars(starts_with(c("Ben_IND"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #add row index so later spreading indexed correctly
  add_rownames()%>%
  #melt to long format
  gather(technology, value, -rowname) %>%
  # separate risky from variable suffix
  separate(technology, c("Ben", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "summary")) %>%
  # spread summary values back to wide form
  spread(summary,value) %>%
  #clean up
  select(-rowname, -Ben) %>%
  arrange(mean) %>%
  setNames(paste0('perceivedbenefit.', names(.))) %>%
  dplyr::rename(technology= perceivedbenefit.technology)

bensumIND

```

```{r, echo=FALSE}

knitr::opts_chunk$set(warning = FALSE, message = FALSE)

bensumIND %>%
  select(technology, perceivedbenefit.mean) %>%
  mutate(technology = fct_reorder(technology, perceivedbenefit.mean, .desc = FALSE))%>%
  ggplot(aes(x=technology, y= perceivedbenefit.mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
  ylim(0,4)+
  labs(y = "Mean Values of Perceived Benefit", x = "Energy Technologies")+
  ggtitle("Your Title Here")+
  coord_flip()

```

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

center_barplot <- full_join( bensumcentral,risksumcentral, by = NULL, copy = FALSE, keep = FALSE) %>%
  select(technology, perceivedbenefit.mean, perceivedrisk.mean) %>%
  mutate(technology = fct_reorder(technology, perceivedbenefit.mean, .desc = FALSE))%>%
   gather(key = "level", value = "mean", perceivedbenefit.mean, perceivedrisk.mean)

center_barplot$level <- as.factor(center_barplot$level)                                          
class(center_barplot$level)
levels(center_barplot$level)

 center_barplot%>% mutate(level = fct_relevel(level, 
            "perceivedbenefit.mean", "perceivedrisk.mean"))+
  ggplot(aes(y=technology, x= mean, fill =  level))+
  geom_bar(stat="identity", position=position_dodge())+
  xlim(0,4)+
  scale_fill_manual("legend", values = c("perceivedbenefit.mean" = "palegreen3","perceivedrisk.mean" = "firebrick2"))

```

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

full_join(bensumIND,risksumIND, by = NULL, copy = FALSE, keep = FALSE) %>%
  select(technology, perceivedbenefit.mean, perceivedrisk.mean) %>%
  mutate(technology = fct_reorder(technology, perceivedbenefit.mean, .desc = FALSE))%>%
  gather(key = "level", value = "mean", perceivedbenefit.mean, perceivedrisk.mean) %>%
  ggplot(aes(x=technology, y= mean, fill = level ))+
  geom_bar(stat="identity", position=position_dodge())+
  ylim(0,4)+
  scale_fill_manual("legend", values = c("perceivedbenefit.mean" = "palegreen3","perceivedrisk.mean" = "firebrick2"))+
  coord_flip()

```

### 2022-03-14 module2graphsandPCA.Rmd
attempts to fix value types in PCA tables

@@
 
- center_barplot%>% mutate(level = fct_relevel(level, 
-            "perceivedbenefit.mean", "perceivedrisk.mean"))+
-  ggplot(aes(y=technology, x= mean, fill =  level))+
+ center_barplot%>% 
+  ggplot(aes(x=technology, y= mean, fill =  center_barplot$level))+
   geom_bar(stat="identity", position=position_dodge())+
-  xlim(0,4)+
-  scale_fill_manual("legend", values = c("perceivedbenefit.mean" = "palegreen3","perceivedrisk.mean" = "firebrick2"))
+  ylim(0,4)+
+  scale_fill_manual("legend", values = c("perceivedbenefit.mean" = "palegreen3","perceivedrisk.mean" = "firebrick2"))+
+  coord_flip()
 
@@
 ```
+
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+
+#PCA on all variables
+
+pcaresultsK <- codedmodule2 %>%
+  select(starts_with(c("K_")))%>%
+  na.omit()%>%
+  prcomp(center = TRUE, scale. = TRUE)
+
+rotations = pcaresultsK["rotation"]
+
+#calculate total variance explained by each principal component
+var_explainedK <- pcaresultsK$sdev^2 / sum(pcaresultsK$sdev^2)
+
+rotationsK <- do.call(rbind.data.frame, rotations)
+
+rotationsK
+```
+
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+
+KPC_var <-data.frame(var_explainedK, row.names=names(rotationsK)) %>%
+  tibble::rownames_to_column("Principal Component")
+
+```
+
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+
+ + 
+  geom_line() + 
+  xlab("Principal Component") + 
+  ylab("Variance Explained") +
+  ggtitle("Scree Plot") +
+  ylim(0, 0.20)+
+  xlim(0,5)
+
+```
+
+```{r, echo= FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+ecopolscalescores <- codedmodule2 %>%
+  select(starts_with(c("Risky","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG", "Gender","Caste","Religion", "State")))%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(Pro_decentralisation = mean(c_across("DECISIONDECEN":"DECISIONCEN")))%>%
+   dplyr::mutate(Pro_largescale = mean(c_across("INDUSTRYLARGE":"INDUSTRYSMALL")))%>%
+   dplyr::mutate(Pro_global = mean(c_across("ECONOMYGLOBAL":"ECONOMYLOCAL")))%>%
+   dplyr::mutate(Pro_ecogrowth = mean(c_across("ENVOVERDEV":"DEVOVERENV")))%>%
+   dplyr::mutate(Pro_private = mean(c_across("OWNERPVT":"OWNERREG")))%>%
+  dplyr::select(!c("DECISIONDECEN","DECISIONCEN", "INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL", "ECONOMYLOCAL","ENVOVERDEV",     "DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG"))
+
+ecopolscalescores
+```

### 2022-03-14 module2graphsandPCA.Rmd
did PCA on all scales

@@
 
-#PCA on all variables
+#PCA on Kahan scale
 
@@
 rotationsK
+
 ```
@@
 KPC_var <-data.frame(var_explainedK, row.names=names(rotationsK)) %>%
-  tibble::rownames_to_column("Principal Component")
+          tibble::rownames_to_column("PC")
+
+KPC_var
 
@@
 
- + 
+qplot(c(1:12), var_explainedK) + 
   geom_line() + 
@@
   ggtitle("Scree Plot") +
-  ylim(0, 0.20)+
-  xlim(0,5)
+  ylim(0, 0.30)+
+  xlim(1,7)
 
@@
 ```
+
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+# PCA test on qualities of the perceiver
+
+ecopolscalepca <- ecopolscalescores %>%
+  select(!starts_with(c("Risky","Gender","Caste","Religion","State")))%>%
+  prcomp(center = TRUE,scale. = TRUE)
+
+var_explained_ecopol = ecopolscalepca$sdev^2 / sum(ecopolscalepca$sdev^2)
+
+summary(ecopolscalepca)
+
+```
+```{r, echo=FALSE}
+
+rotationsecopol = ecopolscalepca["rotation"]
+rotationsDFecopol <- do.call(rbind.data.frame, rotationsecopol)
+rotationsDFecopol
+```
+
+```{r, echo=FALSE}
+
+qplot(c(1:11), var_explained_ecopol) + 
+  geom_line() + 
+  xlab("Principal Component") + 
+  ylab("Variance Explained") +
+  ggtitle("Scree Plot") +
+  ylim(0.05, 0.20)+
+  xlim(1,7)
+
+```
+
+```{r}
+
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+
+#PCA on Kahan scale
+
+Solar <- codedmodule2 %>%
+  select("DISPLACESOLAR":"RELYSOLAR")
+
+#%>%
+  separate(Var, c("prefix", "Var", "technology"), sep = c(0,-5), remove = T)%>%
+  select(!"prefix")
+
+ROOFS<- codedmodule2 %>%
+  select("DISPLACEROOFS":"RELYROOFS")
+
+# %>%
+  pivot_longer(cols ="DISPLACEROOFS":"RELYROOFS", names_to = "Var", values_to = "score") %>%
+  separate(Var, c("prefix", "Var", "technology"), sep = c(0,-5), remove = T)%>%
+  select(!"prefix")
+
+DIESEL<- codedmodule2 %>%
+  select("DISPLACEDIESEL":"RELYDIESEL")%>%
+  pivot_longer(cols ="DISPLACEDIESEL":"RELYDIESEL", names_to = "Var", values_to = "score") %>%
+  separate(Var, c("prefix", "Var", "technology"), sep = c(0,-6), remove = T)%>%
+  select(!"prefix")
+
+FIREWOOD<- codedmodule2 %>%
+  select("DISPLACEFIRE":"RELYFIRE")%>%
+  pivot_longer(cols ="DISPLACEFIRE":"RELYFIRE", names_to = "Var", values_to = "score") %>%
+  separate(Var, c("prefix", "Var", "technology"), sep = c(0,-8), remove = T)%>%
+  select(!"prefix")
+
+COAL<- codedmodule2 %>%
+  select("DISPLACECOAL":"RELYCOAL")%>%
+  pivot_longer(cols ="DISPLACECOAL":"RELYCOAL", names_to = "Var", values_to = "score") %>%
+  separate(Var, c("prefix", "Var", "technology"), sep = c(0,-4), remove = T)%>%
+  select(!"prefix")
+
+NUCLEAR<- codedmodule2 %>%
+  select("DISPLACENUCLEAR":"RELYNUCLEAR")%>%
+  pivot_longer(cols ="DISPLACENUCLEAR":"RELYNUCLEAR", names_to = "Var", values_to = "score") %>%
+  separate(Var, c("prefix", "Var", "technology"), sep = c(0,-7), remove = T)%>%
+  select(!"prefix")
+
+Solar.pca <- Solar %>%
+  na.omit()%>%
+  prcomp(center = TRUE, scale. = TRUE)
+
+rotations = Solar.pca["rotation"]
+
+#calculate total variance explained by each principal component
+var_explainedSolar <- Solar.pca$sdev^2 / sum(Solar.pca$sdev^2)
+
+rotationsSolar <- do.call(rbind.data.frame, rotations)
+
+rotationsSolar
+
+```
+
+```{r, echo=FALSE}
+
+qplot(c(1:10), var_explainedSolar) + 
+  geom_line() + 
+  xlab("Principal Component") + 
+  ylab("Variance Explained") +
+  ggtitle("Scree Plot") +
+  ylim(0.01, 0.40)+
+  xlim(1,7)
+
+```

### 2022-03-15 module2graphsandPCA.Rmd
added decriptions to graphs

@@
 title: "module2graphsandPCA"
-output: 
 output:
@@
     df_print: paged
-
 ---
@@
 
-1. Plot the  mean risk scores (Q1)as histogram ordered from high to low risk – so basically the red bars only in reverse order (aka nuclear as high risk).
+Q1.
+Below is a list of various centrally managed sources of energy.
+How risky are each of these energy technologies according to you?
+Please tell me whether you see each technology as: not at all risky, slightly risky, moderately risky, very risky, or extremely risky
 
@@
   labs(y = "Mean Values of Perceived Risk", x = "Energy Technologies")+
-  ggtitle("Your Title Here")+
+  ggtitle("Perceived risk from centrally managed energy technologies")+
   coord_flip()
@@
 ```
+
+Q2.
+Following is a list of various individually or community-owned and managed sources of energy.
+How risky are each of these energy technologies according to you?
+Please tell me whether you see each technology as: not at all risky, slightly risky, moderately risky, very risky, or extremely risky.
 
@@
   labs(y = "Mean Values of Perceived Risk", x = "Energy Technologies")+
-  ggtitle("Your Title Here")+
+  ggtitle("Perceived risk from individually or community owned energy technologies")+
   coord_flip()
@@
 ```
+
+Q3.
+Following is a list of centrally managed sources of energy.
+How beneficial are each of these according to you?
+Please tell me whether you see each technology as: not at all beneficial, slightly beneficial, moderately beneficial, very beneficial, or extremely beneficial?
 
@@
   labs(y = "Mean Values of Perceived Benefit", x = "Energy Technologies")+
-  ggtitle("Your Title Here")+
+  ggtitle("Perceived benefit from centrally managed energy technologies")+
   coord_flip()
@@
 ```
+
+Q4.
+Following is a list of various individually or community owned and managed sources of energy.
+How beneficial are each of these according to you?
+Please tell me whether you see each technology as: not at all beneficial, slightly beneficial, moderately beneficial, very beneficial or extremely beneficial ?
 
@@
   labs(y = "Mean Values of Perceived Benefit", x = "Energy Technologies")+
-  ggtitle("Your Title Here")+
+  ggtitle("Perceived benefit from individually or community owned energy technologies")+
   coord_flip()
@@
   scale_fill_manual("legend", values = c("perceivedbenefit.mean" = "palegreen3","perceivedrisk.mean" = "firebrick2"))+
+  labs(y = "Mean Values", x = "Energy Technologies")+
+  ggtitle("Perceived risk and benefit from centrally owned energy technologies")+
   coord_flip()
@@
   scale_fill_manual("legend", values = c("perceivedbenefit.mean" = "palegreen3","perceivedrisk.mean" = "firebrick2"))+
+  labs(y = "Mean Values", x = "Energy Technologies")+
+  ggtitle("Perceived risk and benefit from individually owned energy technologies")+
   coord_flip()
@@
 ```
+
+Principal Component Analysis on Kahan et al (2007) scale
+
+K_IINTRFER	The government interferes far too much in our everyday lives.
+K_IPRIVACY	The government should stop telling people how to live their lives.
+K_SHARM	    Sometimes the government needs to make laws that keep people from hurting themselves.
+K_IPROTECT	It’s not the government’s business to try to protect people from themselves.
+K_SLIMCHOI	The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.
+K_SPROTECT	The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.
+K_HEQUAL	  We have gone too far in pushing equal rights in this country.
+K_HREVDIS1	Nowadays it seems like there is just as much discrimination against upper castes as there is against Dalits.
+K_EDISCRIM	Discrimination against minorities is still a very serious problem in our society.
+K_ERADEQ1	  We need to dramatically reduce inequalities between the rich and the poor.
+K_EWEALTH	  Our society would be better off if the distribution of wealth was more equal.
+K_ERADEQ2	  We need to dramatically reduce inequalities between men and women.
 
@@
 ```
+
+PCA on the economic -political values of the perceiver
+
+DECISIONDECEN	 Local politicians shouldn't have to ask permission from the central government to implement policies
+DECISIONCEN	   Laws and policies would be implemented more smoothly if more power lay with the central government.
+SYSTEMTOTAL	   It is good to have a strong leader who does not have to bother with elections.
+SYSTEMTECHNO	 Experts, not the government, should make decisions according to what they think is best for the country.
+SYSTEMDEMO	   It is very important to have a democratic political system because it ensures that no individual leader has too much power.
+SYSTEMRELIGION There should be a system governed by religious law.
+INDUSTRYSMALL	 Large corporations are destroying the local industries in India and benefiting only a handful of people.
+INDUSTRYLARGE	 Large scale industries are required for the development of the country that will benefit everyone
+ECONOMYLOCAL	 India would be better off if foreign companies didn't come to here
+ECONOMYGLOBAL	 Foreign companies have led to a range of benefits for the Indian people and society
+DEVOVERENV	   Economic growth and creating jobs should be prioritized over environmental protection
+ENVOVERDEV	   Polluting industries that spoil the environment should be shut down even if it costs people their jobs
+OWNERPVT	     All businesses and industries should be owned privately
+OWNERPUB	     The government should own most large businesses and industries
+OWNERREG	     Regardless of ownership, the government should pass strong regulations and implement them
+OWNERNOREG	   There is too much red-tape and the government should not interfere with businesses and industries
+WEALTHLIM	     A limit should be put to how much wealth a person can amass
+MECHANISATION	 Rapid mechanization of work is taking away jobs from workers in this country
 
@@
 
+PCA on eco-pol characteristics of the technology -  Solar Energy
+
+DISPLACESOLAR	 Solar energy is leading to displacement of people from their land
+POLLUTESOLAR	 Solar energy increases pollution of air/water/land
+HEALTHSOLAR	   Solar energy poses a great risk to the health of people living around it
+JOBSSOLAR	     Solar energy will bring jobs to the local community
+BEAUTYSOLAR	   Solar energy spoils the natural beauty of the landscape
+PRIDESOLAR	   I would be proud if my community used solar energy
+NPRIDESOLAR	   Solar energy is a mark of pride for our nation
+DEVSOLAR	     Solar energy pushes forward the country's development
+PROSPERSOLAR	 Solar energy brings economic prosperity to the surrounding regions
+RELYSOLAR	     I don't like the idea that I have to rely on the government for electricity from (large scale) solar energy
+
 ```{r}
@@
 
-#PCA on Kahan scale
+#PCA on eco-pol characterisitics of the technology
 
@@
 
-#%>%
-  separate(Var, c("prefix", "Var", "technology"), sep = c(0,-5), remove = T)%>%
-  select(!"prefix")
-
 ROOFS<- codedmodule2 %>%
@@
 
+#%>%
+  #separate(Var, c("prefix", "Var", "technology"), sep = c(0,-5), remove = T)%>%
+ # select(!"prefix")
 # %>%
-  pivot_longer(cols ="DISPLACEROOFS":"RELYROOFS", names_to = "Var", values_to = "score") %>%
-  separate(Var, c("prefix", "Var", "technology"), sep = c(0,-5), remove = T)%>%
-  select(!"prefix")
+  #pivot_longer(cols ="DISPLACEROOFS":"RELYROOFS", names_to = "Var", values_to = "score") %>%
+  #separate(Var, c("prefix", "Var", "technology"), sep = c(0,-5), remove = T)%>%
+  #select(!"prefix")
 
-DIESEL<- codedmodule2 %>%
-  select("DISPLACEDIESEL":"RELYDIESEL")%>%
-  pivot_longer(cols ="DISPLACEDIESEL":"RELYDIESEL", names_to = "Var", values_to = "score") %>%
-  separate(Var, c("prefix", "Var", "technology"), sep = c(0,-6), remove = T)%>%
-  select(!"prefix")
-
-FIREWOOD<- codedmodule2 %>%
-  select("DISPLACEFIRE":"RELYFIRE")%>%
-  pivot_longer(cols ="DISPLACEFIRE":"RELYFIRE", names_to = "Var", values_to = "score") %>%
-  separate(Var, c("prefix", "Var", "technology"), sep = c(0,-8), remove = T)%>%
-  select(!"prefix")
-
-COAL<- codedmodule2 %>%
-  select("DISPLACECOAL":"RELYCOAL")%>%
-  pivot_longer(cols ="DISPLACECOAL":"RELYCOAL", names_to = "Var", values_to = "score") %>%
-  separate(Var, c("prefix", "Var", "technology"), sep = c(0,-4), remove = T)%>%
-  select(!"prefix")
-
-NUCLEAR<- codedmodule2 %>%
-  select("DISPLACENUCLEAR":"RELYNUCLEAR")%>%
-  pivot_longer(cols ="DISPLACENUCLEAR":"RELYNUCLEAR", names_to = "Var", values_to = "score") %>%
-  separate(Var, c("prefix", "Var", "technology"), sep = c(0,-7), remove = T)%>%
-  select(!"prefix")
+#DIESEL<- codedmodule2 %>%
+  #select("DISPLACEDIESEL":"RELYDIESEL")%>%
+  #pivot_longer(cols ="DISPLACEDIESEL":"RELYDIESEL", names_to = "Var", values_to = "score") %>%
+  #separate(Var, c("prefix", "Var", "technology"), sep = c(0,-6), remove = T)%>%
+  #select(!"prefix")
 
@@
 ```
+
+PCA on eco-pol characteristics of the technology -  Nuclear Energy
+
+```{r, echo = FALSE}
+
+Nuclear<- codedmodule2 %>%
+  select("DISPLACENUCLEAR":"RELYNUCLEAR")
+
+Nuclear.pca <- Nuclear %>%
+  na.omit()%>%
+  prcomp(center = TRUE, scale. = TRUE)
+
+rotations = Nuclear.pca["rotation"]
+
+#calculate total variance explained by each principal component
+var_explainedNuclear <- Nuclear.pca$sdev^2 / sum(Nuclear.pca$sdev^2)
+
+rotationsNuclear <- do.call(rbind.data.frame, rotations)
+
+rotationsNuclear
+
+```
+
+```{r, echo=FALSE}
+
+qplot(c(1:10), var_explainedNuclear) + 
+  geom_line() + 
+  xlab("Principal Component") + 
+  ylab("Variance Explained") +
+  ggtitle("Scree Plot") +
+  ylim(0.01, 0.30)+
+  xlim(1,7)
+
+```

### 2022-03-15 module2graphsandPCA.Rmd
added headers to the HTML document and some formatting

@@
   html_document:
-    fig_width: 7
-    fig_height: 6
+    fig_width: 10
+    fig_height: 7
     fig_caption: yes
@@
 
+## Original Dataset
 ```{r, echo=FALSE}
@@
 ```
+
+## Coded Dataset
 
@@
 
-Q1.
+## Q1.
 Below is a list of various centrally managed sources of energy.
@@
 
-Q2.
+## Q2.
 Following is a list of various individually or community-owned and managed sources of energy.
@@
 
-Q3.
+## Q3.
 Following is a list of centrally managed sources of energy.
@@
 
-Q4.
+## Q4.
 Following is a list of various individually or community owned and managed sources of energy.
@@
 
-Principal Component Analysis on Kahan et al (2007) scale
+## Principal Component Analysis on Kahan et al (2007) scale
 
-K_IINTRFER	The government interferes far too much in our everyday lives.
-K_IPRIVACY	The government should stop telling people how to live their lives.
-K_SHARM	    Sometimes the government needs to make laws that keep people from hurting themselves.
-K_IPROTECT	It’s not the government’s business to try to protect people from themselves.
-K_SLIMCHOI	The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.
-K_SPROTECT	The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.
-K_HEQUAL	  We have gone too far in pushing equal rights in this country.
-K_HREVDIS1	Nowadays it seems like there is just as much discrimination against upper castes as there is against Dalits.
-K_EDISCRIM	Discrimination against minorities is still a very serious problem in our society.
-K_ERADEQ1	  We need to dramatically reduce inequalities between the rich and the poor.
-K_EWEALTH	  Our society would be better off if the distribution of wealth was more equal.
-K_ERADEQ2	  We need to dramatically reduce inequalities between men and women.
+- **K_IINTRFER**	The government interferes far too much in our everyday lives.
+- **K_IPRIVACY**	The government should stop telling people how to live their lives.
+- **K_SHARM**	    Sometimes the government needs to make laws that keep people from hurting themselves.
+- **K_IPROTECT**	It’s not the government’s business to try to protect people from themselves.
+- **K_SLIMCHOI**	The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.
+- **K_SPROTECT**	The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.
+- **K_HEQUAL**	  We have gone too far in pushing equal rights in this country.
+- **K_HREVDIS1**	Nowadays it seems like there is just as much discrimination against upper castes as there is against Dalits.
+- **K_EDISCRIM**	Discrimination against minorities is still a very serious problem in our society.
+- **K_ERADEQ1**	  We need to dramatically reduce inequalities between the rich and the poor.
+- **K_EWEALTH**	  Our society would be better off if the distribution of wealth was more equal.
+- **K_ERADEQ2**	  We need to dramatically reduce inequalities between men and women.
 
@@
 
-PCA on the economic -political values of the perceiver
+## PCA on the economic -political values of the perceiver
 
-DECISIONDECEN	 Local politicians shouldn't have to ask permission from the central government to implement policies
-DECISIONCEN	   Laws and policies would be implemented more smoothly if more power lay with the central government.
-SYSTEMTOTAL	   It is good to have a strong leader who does not have to bother with elections.
-SYSTEMTECHNO	 Experts, not the government, should make decisions according to what they think is best for the country.
-SYSTEMDEMO	   It is very important to have a democratic political system because it ensures that no individual leader has too much power.
-SYSTEMRELIGION There should be a system governed by religious law.
-INDUSTRYSMALL	 Large corporations are destroying the local industries in India and benefiting only a handful of people.
-INDUSTRYLARGE	 Large scale industries are required for the development of the country that will benefit everyone
-ECONOMYLOCAL	 India would be better off if foreign companies didn't come to here
-ECONOMYGLOBAL	 Foreign companies have led to a range of benefits for the Indian people and society
-DEVOVERENV	   Economic growth and creating jobs should be prioritized over environmental protection
-ENVOVERDEV	   Polluting industries that spoil the environment should be shut down even if it costs people their jobs
-OWNERPVT	     All businesses and industries should be owned privately
-OWNERPUB	     The government should own most large businesses and industries
-OWNERREG	     Regardless of ownership, the government should pass strong regulations and implement them
-OWNERNOREG	   There is too much red-tape and the government should not interfere with businesses and industries
-WEALTHLIM	     A limit should be put to how much wealth a person can amass
-MECHANISATION	 Rapid mechanization of work is taking away jobs from workers in this country
+- **DECISIONDECEN**	 Local politicians shouldn't have to ask permission from the central government to implement policies
+- **DECISIONCEN**	   Laws and policies would be implemented more smoothly if more power lay with the central government.
+- **SYSTEMTOTAL**	   It is good to have a strong leader who does not have to bother with elections.
+- **SYSTEMTECHNO**	 Experts, not the government, should make decisions according to what they think is best for the country.
+- **SYSTEMDEMO**	   It is very important to have a democratic political system because it ensures that no individual leader has too much power.
+- **SYSTEMRELIGION** There should be a system governed by religious law.
+- **INDUSTRYSMALL**	 Large corporations are destroying the local industries in India and benefiting only a handful of people.
+- **INDUSTRYLARGE**	 Large scale industries are required for the development of the country that will benefit everyone
+- **ECONOMYLOCAL**	 India would be better off if foreign companies didn't come to here
+- **ECONOMYGLOBAL**	 Foreign companies have led to a range of benefits for the Indian people and society
+- **DEVOVERENV**	   Economic growth and creating jobs should be prioritized over environmental protection
+- **ENVOVERDEV**	   Polluting industries that spoil the environment should be shut down even if it costs people their jobs
+- **OWNERPVT**	     All businesses and industries should be owned privately
+- **OWNERPUB**	     The government should own most large businesses and industries
+- **OWNERREG**	     Regardless of ownership, the government should pass strong regulations and implement them
+- **OWNERNOREG**	   There is too much red-tape and the government should not interfere with businesses and industries
+- **WEALTHLIM**	     A limit should be put to how much wealth a person can amass
+- **MECHANISATION**	 Rapid mechanization of work is taking away jobs from workers in this country
 
@@
 
-PCA on eco-pol characteristics of the technology -  Solar Energy
+## PCA on eco-pol characteristics of the technology -  Solar Energy
 
-DISPLACESOLAR	 Solar energy is leading to displacement of people from their land
-POLLUTESOLAR	 Solar energy increases pollution of air/water/land
-HEALTHSOLAR	   Solar energy poses a great risk to the health of people living around it
-JOBSSOLAR	     Solar energy will bring jobs to the local community
-BEAUTYSOLAR	   Solar energy spoils the natural beauty of the landscape
-PRIDESOLAR	   I would be proud if my community used solar energy
-NPRIDESOLAR	   Solar energy is a mark of pride for our nation
-DEVSOLAR	     Solar energy pushes forward the country's development
-PROSPERSOLAR	 Solar energy brings economic prosperity to the surrounding regions
-RELYSOLAR	     I don't like the idea that I have to rely on the government for electricity from (large scale) solar energy
+- **DISPLACESOLAR**	 Solar energy is leading to displacement of people from their land
+- **POLLUTESOLAR**	 Solar energy increases pollution of air/water/land
+- **HEALTHSOLAR**	   Solar energy poses a great risk to the health of people living around it
+- **JOBSSOLAR**	     Solar energy will bring jobs to the local community
+- **BEAUTYSOLAR**	   Solar energy spoils the natural beauty of the landscape
+- **PRIDESOLAR**	   I would be proud if my community used solar energy
+- **NPRIDESOLAR**	   Solar energy is a mark of pride for our nation
+- **DEVSOLAR**	     Solar energy pushes forward the country's development
+- **PROSPERSOLAR**	 Solar energy brings economic prosperity to the surrounding regions
+- **RELYSOLAR**	     I don't like the idea that I have to rely on the government for electricity from (large scale) solar energy
 
-```{r}
+```{r, echo=FALSE}
 
@@
 
-PCA on eco-pol characteristics of the technology -  Nuclear Energy
+## PCA on eco-pol characteristics of the technology -  Nuclear Energy
 

### 2022-03-15 module2graphsandPCA.Rmd
more formatiing changes in rmd
knitting to pdf

@@
 output:
+  pdf_document: 
+    toc: true
+    number_sections: true
+    toc_depth: 2
+    fig_width: 9
+    fig_height: 6
+    fig_caption: yes
+    df_print: paged
   html_document:
-    fig_width: 10
-    fig_height: 7
+    fig_width: 9
+    fig_height: 6
     fig_caption: yes
@@
 
-ecopolscalescores
 ```

### 2022-03-15 module2graphsandPCA.Rmd
fixed combined risk and benefit bar plots

--- 2022-03-15 module2graphsandPCA.Rmd
@@
   html_document:
-    fig_width: 10
-    fig_height: 7
+    fig_width: 9
+    fig_height: 6
     fig_caption: yes
@@
     theme: paper
+    df_print: paged
+  pdf_document:
+
+    toc: true
+    number_sections: true
+    toc_depth: 2
+    fig_width: 9
+    fig_height: 6
+    fig_caption: yes
     df_print: paged
@@
 risksumcentral <- codedmodule2 %>%
-  select(!starts_with(c("RISKY_IND")))%>%
+  dplyr::select(!starts_with(c("RISKY_IND")))%>%
   summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
@@
   #clean up
-  select(-rowname, -Risky) %>%
+  dplyr::select(-rowname, -Risky) %>%
   arrange(mean) %>%
@@
 risksumcentral %>%
-  select(technology, perceivedrisk.mean) %>%
+  dplyr::select(technology, perceivedrisk.mean) %>%
   mutate(technology = fct_reorder(technology, perceivedrisk.mean, .desc = FALSE))%>%
@@
 risksumIND %>%
-  select(technology, perceivedrisk.mean) %>%
+  dplyr::select(technology, perceivedrisk.mean) %>%
   mutate(technology = fct_reorder(technology, perceivedrisk.mean, .desc = FALSE))%>%
@@
 bensumcentral <- codedmodule2 %>%
-  select(!starts_with(c("Ben_IND")))%>%
+  dplyr::select(!starts_with(c("Ben_IND")))%>%
   summarize_at(vars(starts_with(c("Ben"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
@@
   #clean up
-  select(-rowname, -Ben) %>%
+  dplyr::select(-rowname, -Ben) %>%
   arrange(mean) %>%
@@
 bensumcentral %>%
-  select(technology, perceivedbenefit.mean) %>%
+  dplyr::select(technology, perceivedbenefit.mean) %>%
   mutate(technology = fct_reorder(technology, perceivedbenefit.mean, .desc = FALSE))%>%
@@
 bensumIND %>%
-  select(technology, perceivedbenefit.mean) %>%
+  dplyr::select(technology, perceivedbenefit.mean) %>%
   mutate(technology = fct_reorder(technology, perceivedbenefit.mean, .desc = FALSE))%>%
@@
 center_barplot <- full_join( bensumcentral,risksumcentral, by = NULL, copy = FALSE, keep = FALSE) %>%
-  select(technology, perceivedbenefit.mean, perceivedrisk.mean) %>%
+ dplyr::select(technology, perceivedbenefit.mean, perceivedrisk.mean) %>%
   mutate(technology = fct_reorder(technology, perceivedbenefit.mean, .desc = FALSE))%>%
@@
 center_barplot$level <- as.factor(center_barplot$level)
-class(center_barplot$level)
-levels(center_barplot$level)
 
@@
 full_join(bensumIND,risksumIND, by = NULL, copy = FALSE, keep = FALSE) %>%
-  select(technology, perceivedbenefit.mean, perceivedrisk.mean) %>%
+ dplyr::select(technology, perceivedbenefit.mean, perceivedrisk.mean) %>%
   mutate(technology = fct_reorder(technology, perceivedbenefit.mean, .desc = FALSE))%>%
@@
 
-## Principal Component Analysis on Kahan et al (2007) scale
+\newpage
+
+# **Kahan et al (2007) scale**
 
@@
 
+## Cronbach's alpha test on the Kahan et al (2007) scale
+
 ```{r, echo=FALSE}
@@
 
+library(ltm)
+
+#cronbach alpha
+
+Kahanscale <- codedmodule2 %>%
+  dplyr::select(starts_with(c("K_")))
+
+cronbach.alpha(Kahanscale, na.rm = TRUE, CI=TRUE, standardized=TRUE)
+
+```
+
+## Principal Component Analysis on Kahan et al (2007) scale
+
+```{r, echo=FALSE}
+
 #PCA on Kahan scale
-
 pcaresultsK <- codedmodule2 %>%
-  select(starts_with(c("K_")))%>%
+  dplyr::select(starts_with(c("K_")))%>%
   na.omit()%>%
@@
 
-rotationsK <- do.call(rbind.data.frame, rotations)
+rotationsK <- do.call(rbind.data.frame, rotations)%>%
+              tibble::rownames_to_column("Variables")
 
@@
 
-```
+pcatableK  <- summary(pcaresultsK)
 
-```{r, echo=FALSE}
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+UnclassedK <- unclass(pcatableK)
 
-KPC_var <-data.frame(var_explainedK, row.names=names(rotationsK)) %>%
-          tibble::rownames_to_column("PC")
+ImportanceK <- UnclassedK["importance"]
 
-KPC_var
+varexplK <- do.call(rbind.data.frame, ImportanceK)
+
+KPCAtable <- data.frame(t(varexplK), row.names=names(varexplK))
+
+as_tibble(KPCAtable) %>%
+ add_column("Principal Components" = c("PC1", "PC2", "PC3", "PC4", "PC5", "PC6", "PC7", "PC8", "PC9", "PC10", "PC11", "PC12"))%>%
+ dplyr::select("Principal Components",  importance.Proportion.of.Variance, importance.Cumulative.Proportion ) %>%  
+ dplyr::rename(Proportion_of_Variance = importance.Proportion.of.Variance, Cumulative_Proportion = importance.Cumulative.Proportion)
 
@@
 
-## PCA on the economic -political values of the perceiver
+\newpage
+
+# **The economic -political values of the perceiver scale**
 
@@
 
+## Cronbach's alpha test on the economic -political values of the perceiver
 ```{r, echo= FALSE}
@@
 ecopolscalescores <- codedmodule2 %>%
-  select(starts_with(c("Risky","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG", "Gender","Caste","Religion", "State")))%>%
+ dplyr::select(starts_with(c("Risky","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG", "Gender","Caste","Religion", "State")))%>%
   rowwise()%>%
@@
 
-ecopolscalescores
+#cronbach alpha
+
+cronbach.alpha(ecopolscalescores, na.rm = TRUE, CI=TRUE, standardized=TRUE)
+
 ```
+
+## PCA on the economic -political values of the perceiver
 
@@
 ecopolscalepca <- ecopolscalescores %>%
-  select(!starts_with(c("Risky","Gender","Caste","Religion","State")))%>%
+  dplyr::select(!starts_with(c("Risky","Gender","Caste","Religion","State")))%>%
   prcomp(center = TRUE,scale. = TRUE)
@@
 
-summary(ecopolscalepca)
+pcatableecopol  <- summary(ecopolscalepca)
+
+Unclassedecopol <- unclass(pcatableecopol)
+
+Importanceecopol <- Unclassedecopol["importance"]
+
+varexplecopol <- do.call(rbind.data.frame, Importanceecopol)
+
+ecopolPCAtable <- data.frame(t(varexplecopol), row.names=names(varexplecopol))
+
+as_tibble(ecopolPCAtable) %>%
+ add_column("Principal Components" = c("PC1", "PC2", "PC3", "PC4", "PC5", "PC6", "PC7", "PC8", "PC9", "PC10", "PC11"))%>%
+ dplyr::select("Principal Components",  importance.Proportion.of.Variance, importance.Cumulative.Proportion ) %>%  
+ dplyr::rename(Proportion_of_Variance = importance.Proportion.of.Variance, Cumulative_Proportion = importance.Cumulative.Proportion)
 
 ```
+
+## Variables in the PCs
+
 ```{r, echo=FALSE}
@@
 
-## PCA on eco-pol characteristics of the technology -  Solar Energy
+\newpage
+
+# **eco - pol characteristics of the technology scale-  Solar Energy and Nuclear Energy**
 
@@
 
+## Cronbach's alpha test on eco-pol characteristics of the technology -  Solar Energy
+
 ```{r, echo=FALSE}
-
 knitr::opts_chunk$set(warning = FALSE, message = FALSE)
@@
 Solar <- codedmodule2 %>%
-  select("DISPLACESOLAR":"RELYSOLAR")
+ dplyr::select("DISPLACESOLAR":"RELYSOLAR")
+
+cronbach.alpha(Solar, na.rm = TRUE, CI=TRUE, standardized=TRUE)
 
 ROOFS<- codedmodule2 %>%
-  select("DISPLACEROOFS":"RELYROOFS")
+ dplyr::select("DISPLACEROOFS":"RELYROOFS")
 
-#%>%
-  #separate(Var, c("prefix", "Var", "technology"), sep = c(0,-5), remove = T)%>%
- # select(!"prefix")
-# %>%
-  #pivot_longer(cols ="DISPLACEROOFS":"RELYROOFS", names_to = "Var", values_to = "score") %>%
-  #separate(Var, c("prefix", "Var", "technology"), sep = c(0,-5), remove = T)%>%
-  #select(!"prefix")
+```
 
-#DIESEL<- codedmodule2 %>%
-  #select("DISPLACEDIESEL":"RELYDIESEL")%>%
-  #pivot_longer(cols ="DISPLACEDIESEL":"RELYDIESEL", names_to = "Var", values_to = "score") %>%
-  #separate(Var, c("prefix", "Var", "technology"), sep = c(0,-6), remove = T)%>%
-  #select(!"prefix")
+## PCA on eco-pol characteristics of the technology -  Solar Energy
+
+```{r, echo = FALSE}
 
@@
   prcomp(center = TRUE, scale. = TRUE)
+
+pcatablesolar  <- summary(Solar.pca)
+
+Unclassedsolar <- unclass(pcatablesolar)
+
+Importancesolar <- Unclassedsolar["importance"]
+
+varexplsolar <- do.call(rbind.data.frame, Importancesolar)
+
+solarPCAtable <- data.frame(t(varexplsolar), row.names=names(varexplsolar))
+
+as_tibble(solarPCAtable) %>%
+ add_column("Principal Components" = c("PC1", "PC2", "PC3", "PC4", "PC5", "PC6", "PC7", "PC8", "PC9", "PC10"))%>%
+ dplyr::select("Principal Components",  importance.Proportion.of.Variance, importance.Cumulative.Proportion ) %>%  
+ dplyr::rename(Proportion_of_Variance = importance.Proportion.of.Variance, Cumulative_Proportion = importance.Cumulative.Proportion)
+```
+
+```{r, echo=FALSE}
 
@@
 Nuclear<- codedmodule2 %>%
-  select("DISPLACENUCLEAR":"RELYNUCLEAR")
+ dplyr::select("DISPLACENUCLEAR":"RELYNUCLEAR")
+
+cronbach.alpha(Nuclear, na.rm = TRUE, CI=TRUE, standardized=TRUE)
+
+```
+
+```{r, echo = FALSE}
 
@@
   prcomp(center = TRUE, scale. = TRUE)
+
+pcatablenuclear  <- summary(Nuclear.pca)
+
+Unclassednuclear <- unclass(pcatablenuclear)
+
+Importancenuclear <- Unclassednuclear["importance"]
+
+varexplnuclear <- do.call(rbind.data.frame, Importancenuclear)
+
+nuclearPCAtable <- data.frame(t(varexplnuclear), row.names=names(varexplnuclear))
+
+as_tibble(nuclearPCAtable) %>%
+ add_column("Principal Components" = c("PC1", "PC2", "PC3", "PC4", "PC5", "PC6", "PC7", "PC8", "PC9", "PC10"))%>%
+ dplyr::select("Principal Components",  importance.Proportion.of.Variance, importance.Cumulative.Proportion ) %>%  
+ dplyr::rename(Proportion_of_Variance = importance.Proportion.of.Variance, Cumulative_Proportion = importance.Cumulative.Proportion)
+
+```
+
+```{r, echo=FALSE}
 

### 2022-03-16 module2graphsandPCA.Rmd
knitted to pdf

@@
     df_print: paged
+
 pdf_document:
@@
  center_barplot%>% 
-  ggplot(aes(x=technology, y= mean, fill =  center_barplot$level))+
+  ggplot(aes(x=technology, y= mean, fill =  (factor(center_barplot$level, levels = c("perceivedrisk.mean", "perceivedbenefit.mean")))))+
   geom_bar(stat="identity", position=position_dodge())+
@@
 
-full_join(bensumIND,risksumIND, by = NULL, copy = FALSE, keep = FALSE) %>%
+IND_barplot <- full_join(bensumIND,risksumIND, by = NULL, copy = FALSE, keep = FALSE) %>%
  dplyr::select(technology, perceivedbenefit.mean, perceivedrisk.mean) %>%
   mutate(technology = fct_reorder(technology, perceivedbenefit.mean, .desc = FALSE))%>%
-  gather(key = "level", value = "mean", perceivedbenefit.mean, perceivedrisk.mean) %>%
-  ggplot(aes(x=technology, y= mean, fill = level ))+
+  gather(key = "level", value = "mean", perceivedbenefit.mean, perceivedrisk.mean)
+
+IND_barplot$level <- as.factor(IND_barplot$level)
+
+IND_barplot%>%  ggplot(aes(x=technology, y= mean, fill = (factor(IND_barplot$level, levels = c("perceivedrisk.mean", "perceivedbenefit.mean")))))+
   geom_bar(stat="identity", position=position_dodge())+

### 2022-03-17 module2extra.Rmd
added error bars to graphs

@@
 ```
+
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+
+KPC_var <-data.frame(var_explainedK, row.names=names(rotationsK)) %>%
+          tibble::rownames_to_column("PC")
+
+KPC_var
+
+```
+
+```{r}
+#%>%
+  #separate(Var, c("prefix", "Var", "technology"), sep = c(0,-5), remove = T)%>%
+ # select(!"prefix")
+# %>%
+  #pivot_longer(cols ="DISPLACEROOFS":"RELYROOFS", names_to = "Var", values_to = "score") %>%
+  #separate(Var, c("prefix", "Var", "technology"), sep = c(0,-5), remove = T)%>%
+  #select(!"prefix")
+
+#DIESEL<- codedmodule2 %>%
+  #select("DISPLACEDIESEL":"RELYDIESEL")%>%
+  #pivot_longer(cols ="DISPLACEDIESEL":"RELYDIESEL", names_to = "Var", values_to = "score") %>%
+  #separate(Var, c("prefix", "Var", "technology"), sep = c(0,-6), remove = T)%>%
+  #select(!"prefix")
+```

### 2022-03-17 module2graphsandPCA.Rmd
added error bars to graphs

@@
     fig_caption: yes
-    df_print: paged
+    df_print: 
 ---
@@
 risksumcentral %>%
-  dplyr::select(technology, perceivedrisk.mean) %>%
+  dplyr::select(technology, perceivedrisk.mean, perceivedrisk.sd) %>%
   mutate(technology = fct_reorder(technology, perceivedrisk.mean, .desc = FALSE))%>%
@@
   geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
-  ylim(0,4)+
+  ylim(0,5)+
+  geom_errorbar(aes(ymin=perceivedrisk.mean-perceivedrisk.sd, ymax=perceivedrisk.mean + perceivedrisk.sd), width=.2,
+                 position=position_dodge(.9))+
   labs(y = "Mean Values of Perceived Risk", x = "Energy Technologies")+
@@
 risksumIND %>%
-  dplyr::select(technology, perceivedrisk.mean) %>%
+  dplyr::select(technology, perceivedrisk.mean,perceivedrisk.sd) %>%
   mutate(technology = fct_reorder(technology, perceivedrisk.mean, .desc = FALSE))%>%
@@
   geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
-  ylim(0,4)+
+  geom_errorbar(aes(ymin=perceivedrisk.mean-perceivedrisk.sd, ymax=perceivedrisk.mean + perceivedrisk.sd), width=.2,
+                 position=position_dodge(.9))+
+  ylim(0,5)+
   labs(y = "Mean Values of Perceived Risk", x = "Energy Technologies")+
@@
 bensumcentral %>%
-  dplyr::select(technology, perceivedbenefit.mean) %>%
+  dplyr::select(technology, perceivedbenefit.mean,perceivedbenefit.sd) %>%
   mutate(technology = fct_reorder(technology, perceivedbenefit.mean, .desc = FALSE))%>%
@@
   geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
-  ylim(0,4)+
+   geom_errorbar(aes(ymin=perceivedbenefit.mean-perceivedbenefit.sd, ymax=perceivedbenefit.mean + perceivedbenefit.sd), width=.2,
+                 position=position_dodge(.9))+
+  ylim(0,5)+
   labs(y = "Mean Values of Perceived Benefit", x = "Energy Technologies")+
@@
 bensumIND %>%
-  dplyr::select(technology, perceivedbenefit.mean) %>%
+  dplyr::select(technology, perceivedbenefit.mean, perceivedbenefit.sd) %>%
   mutate(technology = fct_reorder(technology, perceivedbenefit.mean, .desc = FALSE))%>%
@@
   geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
-  ylim(0,4)+
+  geom_errorbar(aes(ymin=perceivedbenefit.mean-perceivedbenefit.sd, ymax=perceivedbenefit.mean + perceivedbenefit.sd), width=.2,
+                 position=position_dodge(.9))+
+  ylim(0,5)+
   labs(y = "Mean Values of Perceived Benefit", x = "Energy Technologies")+

### 2022-03-21 module2/PCAs/module2PCAs.Rmd
moved files into folders

--- 2022-03-15 module2graphsandPCA.Rmd
@@
 ---
-title: "module2graphsandPCA"
+title: "PCAs"
+output: 
   output:
@@
     df_print: paged
-  pdf_document:
 
-    toc: true
-    number_sections: true
-    toc_depth: 2
-    fig_width: 9
-    fig_height: 6
-    fig_caption: yes
-    df_print: paged
 ---
@@
 suppressPackageStartupMessages(library(readxl))
-suppressPackageStartupMessages(library(hablar))
+
 suppressPackageStartupMessages(library(tsibble))
@@
 suppressPackageStartupMessages(library(DT))
-suppressPackageStartupMessages(library(ggplot2))
-suppressPackageStartupMessages(library(ggbiplot))
+
+suppressPackageStartupMessages(library(psych)) # psychometrics
 
@@
 
-## Original Dataset
 ```{r, echo=FALSE}
@@
 module2[module2 == "Rather not say/ Don't know"] <- "Rather not say/Don't know"
-module2 %>%
-  filter(!row_number() %in% c(1,2))
+#module2 %>% filter(!row_number() %in% c(1,2))
 
@@
 # reverse code for likert scale for variables for Kahan scale into numbers
-  mutate_at(vars(starts_with (c("K_S","K_E"))), funs(case_when(. == "Strongly disagree" ~ 5, 
-                                                               . == "Somewhat disagree" ~ 4,
+mutate_at(vars(starts_with (c("K_S","K_E"))), funs(case_when(. == "Strongly disagree" ~ 1, 
+                                                               . == "Somewhat disagree" ~ 2,
                                                                . == "Neither agree nor disagree" ~3,
-                                                               . == "Somewhat agree" ~ 2,
-                                                               . == "Strongly agree" ~ 1))) %>%
+                                                               . == "Somewhat agree" ~ 4,
+                                                               . == "Strongly agree" ~ 5))) %>%
 
@@
 # reverse code eco-pol scale variables into numbers 
- mutate_at(vars(DECISIONCEN, INDUSTRYSMALL, ECONOMYLOCAL, ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(. == "Strongly disagree" ~ 5, 
-                                                                                                         . == "Somewhat disagree" ~ 4,
+ mutate_at(vars(DECISIONCEN, INDUSTRYSMALL, ECONOMYLOCAL, ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(. == "Strongly disagree" ~ 1, 
+                                                                                                         . == "Somewhat disagree" ~ 2,
                                                                                                          . == "Neither agree nor disagree" ~3,
-                                                                                                         . == "Somewhat agree" ~ 2,
-                                                                                                         . == "Strongly agree" ~ 1)))
+                                                                                                         . == "Somewhat agree" ~ 4,
+                                                                                                         . == "Strongly agree" ~ 5)))
 
@@
 ```
-
-## Q1.
-Below is a list of various centrally managed sources of energy.
-How risky are each of these energy technologies according to you?
-Please tell me whether you see each technology as: not at all risky, slightly risky, moderately risky, very risky, or extremely risky
-
-```{r, eval=TRUE, echo=FALSE}
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-
-# summary statistics for risks from different energy sources
-
-risksumcentral <- codedmodule2 %>%
-  dplyr::select(!starts_with(c("RISKY_IND")))%>%
-  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
-  #add row index so later spreading indexed correctly
-  add_rownames()%>%
-  #melt to long format
-  gather(technology, value, -rowname) %>%
-  # separate risky from variable suffix
-  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
-  #separate mean from variable prefix
-  separate(var, c("technology", "summary")) %>%
-  # spread summary values back to wide form
-  spread(summary,value) %>%
-  #clean up
-  dplyr::select(-rowname, -Risky) %>%
-  arrange(mean) %>%
-  setNames(paste0('perceivedrisk.', names(.))) %>%
-  dplyr::rename(technology= perceivedrisk.technology)
-
-risksumcentral
-
-```
-
-```{r, echo=FALSE}
-
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-
-risksumcentral %>%
-  dplyr::select(technology, perceivedrisk.mean) %>%
-  mutate(technology = fct_reorder(technology, perceivedrisk.mean, .desc = FALSE))%>%
-  ggplot(aes(x=technology, y= perceivedrisk.mean))+
-  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
-  ylim(0,4)+
-  labs(y = "Mean Values of Perceived Risk", x = "Energy Technologies")+
-  ggtitle("Perceived risk from centrally managed energy technologies")+
-  coord_flip()
-
-```
-
-## Q2.
-Following is a list of various individually or community-owned and managed sources of energy.
-How risky are each of these energy technologies according to you?
-Please tell me whether you see each technology as: not at all risky, slightly risky, moderately risky, very risky, or extremely risky.
-
-```{r, eval=TRUE, echo=FALSE}
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-
-# summary statistics for risks from different energy sources
-
-risksumIND <- codedmodule2 %>%
-  summarize_at(vars(starts_with(c("RISKY_IND"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
-  #add row index so later spreading indexed correctly
-  add_rownames()%>%
-  #melt to long format
-  gather(technology, value, -rowname) %>%
-  # separate risky from variable suffix
-  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
-  #separate mean from variable prefix
-  separate(var, c("technology", "summary")) %>%
-  # spread summary values back to wide form
-  spread(summary,value) %>%
-  #clean up
-  dplyr::select(-rowname, -Risky) %>%
-  arrange(mean) %>%
-  setNames(paste0('perceivedrisk.', names(.))) %>%
-  dplyr::rename(technology= perceivedrisk.technology)
-
-risksumIND
-
-```
-
-```{r, echo=FALSE}
-
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-
-risksumIND %>%
-  dplyr::select(technology, perceivedrisk.mean) %>%
-  mutate(technology = fct_reorder(technology, perceivedrisk.mean, .desc = FALSE))%>%
-  ggplot(aes(x=technology, y= perceivedrisk.mean))+
-  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
-  ylim(0,4)+
-  labs(y = "Mean Values of Perceived Risk", x = "Energy Technologies")+
-  ggtitle("Perceived risk from individually or community owned energy technologies")+
-  coord_flip()
-
-```
-
-## Q3.
-Following is a list of centrally managed sources of energy.
-How beneficial are each of these according to you?
-Please tell me whether you see each technology as: not at all beneficial, slightly beneficial, moderately beneficial, very beneficial, or extremely beneficial?
-
-```{r, eval=TRUE, echo=FALSE}
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-
-# summary statistics for risks from different energy sources
-
-bensumcentral <- codedmodule2 %>%
-  dplyr::select(!starts_with(c("Ben_IND")))%>%
-  summarize_at(vars(starts_with(c("Ben"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
-  #add row index so later spreading indexed correctly
-  add_rownames()%>%
-  #melt to long format
-  gather(technology, value, -rowname) %>%
-  # separate risky from variable suffix
-  separate(technology, c("Ben", "var"), extra = "merge", fill = "left") %>%
-  #separate mean from variable prefix
-  separate(var, c("technology", "summary")) %>%
-  # spread summary values back to wide form
-  spread(summary,value) %>%
-  #clean up
-  dplyr::select(-rowname, -Ben) %>%
-  arrange(mean) %>%
-  setNames(paste0('perceivedbenefit.', names(.))) %>%
-  dplyr::rename(technology= perceivedbenefit.technology)
-
-bensumcentral
-
-```
-
-```{r, echo=FALSE}
-
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-
-bensumcentral %>%
-  dplyr::select(technology, perceivedbenefit.mean) %>%
-  mutate(technology = fct_reorder(technology, perceivedbenefit.mean, .desc = FALSE))%>%
-  ggplot(aes(x=technology, y= perceivedbenefit.mean))+
-  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
-  ylim(0,4)+
-  labs(y = "Mean Values of Perceived Benefit", x = "Energy Technologies")+
-  ggtitle("Perceived benefit from centrally managed energy technologies")+
-  coord_flip()
-
-```
-
-## Q4.
-Following is a list of various individually or community owned and managed sources of energy.
-How beneficial are each of these according to you?
-Please tell me whether you see each technology as: not at all beneficial, slightly beneficial, moderately beneficial, very beneficial or extremely beneficial ?
-
-```{r, eval=TRUE, echo=FALSE}
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-
-# summary statistics for risks from different energy sources
-
-bensumIND <- codedmodule2 %>%
-  summarize_at(vars(starts_with(c("Ben_IND"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
-  #add row index so later spreading indexed correctly
-  add_rownames()%>%
-  #melt to long format
-  gather(technology, value, -rowname) %>%
-  # separate risky from variable suffix
-  separate(technology, c("Ben", "var"), extra = "merge", fill = "left") %>%
-  #separate mean from variable prefix
-  separate(var, c("technology", "summary")) %>%
-  # spread summary values back to wide form
-  spread(summary,value) %>%
-  #clean up
-  dplyr::select(-rowname, -Ben) %>%
-  arrange(mean) %>%
-  setNames(paste0('perceivedbenefit.', names(.))) %>%
-  dplyr::rename(technology= perceivedbenefit.technology)
-
-bensumIND
-
-```
-
-```{r, echo=FALSE}
-
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-
-bensumIND %>%
-  dplyr::select(technology, perceivedbenefit.mean) %>%
-  mutate(technology = fct_reorder(technology, perceivedbenefit.mean, .desc = FALSE))%>%
-  ggplot(aes(x=technology, y= perceivedbenefit.mean))+
-  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
-  ylim(0,4)+
-  labs(y = "Mean Values of Perceived Benefit", x = "Energy Technologies")+
-  ggtitle("Perceived benefit from individually or community owned energy technologies")+
-  coord_flip()
-
-```
-
-```{r, echo=FALSE}
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-
-center_barplot <- full_join( bensumcentral,risksumcentral, by = NULL, copy = FALSE, keep = FALSE) %>%
- dplyr::select(technology, perceivedbenefit.mean, perceivedrisk.mean) %>%
-  mutate(technology = fct_reorder(technology, perceivedbenefit.mean, .desc = FALSE))%>%
-   gather(key = "level", value = "mean", perceivedbenefit.mean, perceivedrisk.mean)
-
-center_barplot$level <- as.factor(center_barplot$level)
-
- center_barplot%>% 
-  ggplot(aes(x=technology, y= mean, fill =  center_barplot$level))+
-  geom_bar(stat="identity", position=position_dodge())+
-  ylim(0,4)+
-  scale_fill_manual("legend", values = c("perceivedbenefit.mean" = "palegreen3","perceivedrisk.mean" = "firebrick2"))+
-  labs(y = "Mean Values", x = "Energy Technologies")+
-  ggtitle("Perceived risk and benefit from centrally owned energy technologies")+
-  coord_flip()
-
-```
-
-```{r, echo=FALSE}
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-
-full_join(bensumIND,risksumIND, by = NULL, copy = FALSE, keep = FALSE) %>%
- dplyr::select(technology, perceivedbenefit.mean, perceivedrisk.mean) %>%
-  mutate(technology = fct_reorder(technology, perceivedbenefit.mean, .desc = FALSE))%>%
-  gather(key = "level", value = "mean", perceivedbenefit.mean, perceivedrisk.mean) %>%
-  ggplot(aes(x=technology, y= mean, fill = level ))+
-  geom_bar(stat="identity", position=position_dodge())+
-  ylim(0,4)+
-  scale_fill_manual("legend", values = c("perceivedbenefit.mean" = "palegreen3","perceivedrisk.mean" = "firebrick2"))+
-  labs(y = "Mean Values", x = "Energy Technologies")+
-  ggtitle("Perceived risk and benefit from individually owned energy technologies")+
-  coord_flip()
-
-```
-
-\newpage
 
@@
 - **K_SPROTECT**	The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.
+
 - **K_HEQUAL**	  We have gone too far in pushing equal rights in this country.
@@
 
-Kahanscale <- codedmodule2 %>%
-  dplyr::select(starts_with(c("K_")))
+KahanI <- codedmodule2 %>%
+  dplyr::select(starts_with(c("K_S")))%>%
+  na.omit()
 
-cronbach.alpha(Kahanscale, na.rm = TRUE, CI=TRUE, standardized=TRUE)
+#K_S items produce a strong alpha but not K_I
+
+psych::alpha(KahanI)
+
+KahanE <- codedmodule2 %>%
+  dplyr::select(starts_with(c("K_H", "K_E")))%>%
+  na.omit()
+psych::alpha(KahanE)
 
@@
 
-## Principal Component Analysis on Kahan et al (2007) scale
+## Factor Analysis on Kahan et al (2007) scale
 
@@
 
-#PCA on Kahan scale
-pcaresultsK <- codedmodule2 %>%
+#factor analysis on Kahan scale
+Kahan <- codedmodule2 %>%
   dplyr::select(starts_with(c("K_")))%>%
-  na.omit()%>%
-  prcomp(center = TRUE, scale. = TRUE)
+  na.omit()
 
-rotations = pcaresultsK["rotation"]
-
-#calculate total variance explained by each principal component
-var_explainedK <- pcaresultsK$sdev^2 / sum(pcaresultsK$sdev^2)
-
-rotationsK <- do.call(rbind.data.frame, rotations)%>%
-              tibble::rownames_to_column("Variables")
-
-rotationsK
-
-pcatableK  <- summary(pcaresultsK)
-
-UnclassedK <- unclass(pcatableK)
-
-ImportanceK <- UnclassedK["importance"]
-
-varexplK <- do.call(rbind.data.frame, ImportanceK)
-
-KPCAtable <- data.frame(t(varexplK), row.names=names(varexplK))
-
-as_tibble(KPCAtable) %>%
- add_column("Principal Components" = c("PC1", "PC2", "PC3", "PC4", "PC5", "PC6", "PC7", "PC8", "PC9", "PC10", "PC11", "PC12"))%>%
- dplyr::select("Principal Components",  importance.Proportion.of.Variance, importance.Cumulative.Proportion ) %>%  
- dplyr::rename(Proportion_of_Variance = importance.Proportion.of.Variance, Cumulative_Proportion = importance.Cumulative.Proportion)
+pcaresultsK <- fa(Kahan, nfactors=4, scores=TRUE, rotate="varimax", fm="pa")
+print.psych(pcaresultsK, cut = 0.3, sort = TRUE)
+fa.diagram(pcaresultsK)
 
 ```
-
-```{r, echo=FALSE}
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-
-qplot(c(1:12), var_explainedK) + 
-  geom_line() + 
-  xlab("Principal Component") + 
-  ylab("Variance Explained") +
-  ggtitle("Scree Plot") +
-  ylim(0, 0.30)+
-  xlim(1,7)
-
-```
-
-\newpage
 
@@
 ecopolscalescores <- codedmodule2 %>%
- dplyr::select(starts_with(c("Risky","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG", "Gender","Caste","Religion", "State")))%>%
+ dplyr::select(starts_with(c("SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
   rowwise()%>%
@@
 
-cronbach.alpha(ecopolscalescores, na.rm = TRUE, CI=TRUE, standardized=TRUE)
+psych::alpha(ecopolscalescores, check.keys = TRUE)
 
-```
-
-## PCA on the economic -political values of the perceiver
-
-```{r, echo=FALSE}
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-# PCA test on qualities of the perceiver
-
-ecopolscalepca <- ecopolscalescores %>%
-  dplyr::select(!starts_with(c("Risky","Gender","Caste","Religion","State")))%>%
-  prcomp(center = TRUE,scale. = TRUE)
-
-var_explained_ecopol = ecopolscalepca$sdev^2 / sum(ecopolscalepca$sdev^2)
-
-pcatableecopol  <- summary(ecopolscalepca)
-
-Unclassedecopol <- unclass(pcatableecopol)
-
-Importanceecopol <- Unclassedecopol["importance"]
-
-varexplecopol <- do.call(rbind.data.frame, Importanceecopol)
-
-ecopolPCAtable <- data.frame(t(varexplecopol), row.names=names(varexplecopol))
-
-as_tibble(ecopolPCAtable) %>%
- add_column("Principal Components" = c("PC1", "PC2", "PC3", "PC4", "PC5", "PC6", "PC7", "PC8", "PC9", "PC10", "PC11"))%>%
- dplyr::select("Principal Components",  importance.Proportion.of.Variance, importance.Cumulative.Proportion ) %>%  
- dplyr::rename(Proportion_of_Variance = importance.Proportion.of.Variance, Cumulative_Proportion = importance.Cumulative.Proportion)
-
-```
-
-## Variables in the PCs
-
-```{r, echo=FALSE}
-
-rotationsecopol = ecopolscalepca["rotation"]
-rotationsDFecopol <- do.call(rbind.data.frame, rotationsecopol)
-rotationsDFecopol
 ```
@@
 
-qplot(c(1:11), var_explained_ecopol) + 
-  geom_line() + 
-  xlab("Principal Component") + 
-  ylab("Variance Explained") +
-  ggtitle("Scree Plot") +
-  ylim(0.05, 0.20)+
-  xlim(1,7)
+#factor analysis with 2, 4 and 6 factor spaces
+
+ecopolscale.fa <- fa(ecopolscalescores, nfactors=2, scores=TRUE, rotate="varimax", fm="pa")
+print.psych(ecopolscale.fa, cut = 0.3, sort = TRUE)
+fa.diagram(ecopolscale.fa)
 
@@
 
-# **eco - pol characteristics of the technology scale-  Solar Energy and Nuclear Energy**
+# **Economic and Political characteristics of the energy technology scale -  Solar Energy and Nuclear Energy**
 
@@
 
-#PCA on eco-pol characterisitics of the technology
+#alpha test on Eco-pol characteristics of the technology
 
 Solar <- codedmodule2 %>%
- dplyr::select("DISPLACESOLAR":"RELYSOLAR")
+dplyr::select("DISPLACESOLAR":"RELYSOLAR") %>%
+dplyr::rename("Solar energy is leading to displacement of people from their land" = "DISPLACESOLAR") %>%
+dplyr::rename("Solar energy increases pollution of air/water/land" = "POLLUTESOLAR")%>%
+dplyr::rename("Solar energy poses a great risk to the health of people living around it" = "HEALTHSOLAR")%>%
+dplyr::rename("Solar energy will bring jobs to the local community" = "JOBSSOLAR")%>%
+dplyr::rename("Solar energy spoils the natural beauty of the landscape" = "BEAUTYSOLAR")%>%
+dplyr::rename("I would be proud if my community used solar energy" = "PRIDESOLAR")%>%
+dplyr::rename("Solar energy is a mark of pride for our nation" = "NPRIDESOLAR") %>%
+dplyr::rename("Solar energy pushes forward the country's development" = "DEVSOLAR")%>%
+dplyr::rename("Solar energy brings economic prosperity to the surrounding regions" = "PROSPERSOLAR")%>%
+dplyr::rename("I don't like the idea that I have to rely on the government for electricity from (large scale solar energy)" = "RELYSOLAR")
 
-cronbach.alpha(Solar, na.rm = TRUE, CI=TRUE, standardized=TRUE)
-
-ROOFS<- codedmodule2 %>%
- dplyr::select("DISPLACEROOFS":"RELYROOFS")
-
-```
-
-## PCA on eco-pol characteristics of the technology -  Solar Energy
-
-```{r, echo = FALSE}
-
-Solar.pca <- Solar %>%
-  na.omit()%>%
-  prcomp(center = TRUE, scale. = TRUE)
-
-pcatablesolar  <- summary(Solar.pca)
-
-Unclassedsolar <- unclass(pcatablesolar)
-
-Importancesolar <- Unclassedsolar["importance"]
-
-varexplsolar <- do.call(rbind.data.frame, Importancesolar)
-
-solarPCAtable <- data.frame(t(varexplsolar), row.names=names(varexplsolar))
-
-as_tibble(solarPCAtable) %>%
- add_column("Principal Components" = c("PC1", "PC2", "PC3", "PC4", "PC5", "PC6", "PC7", "PC8", "PC9", "PC10"))%>%
- dplyr::select("Principal Components",  importance.Proportion.of.Variance, importance.Cumulative.Proportion ) %>%  
- dplyr::rename(Proportion_of_Variance = importance.Proportion.of.Variance, Cumulative_Proportion = importance.Cumulative.Proportion)
-```
-
-```{r, echo=FALSE}
-
-rotations = Solar.pca["rotation"]
-
-#calculate total variance explained by each principal component
-var_explainedSolar <- Solar.pca$sdev^2 / sum(Solar.pca$sdev^2)
-
-rotationsSolar <- do.call(rbind.data.frame, rotations)
-
-rotationsSolar
+psych::alpha(Solar, check.keys = TRUE)
 
@@
 
-qplot(c(1:10), var_explainedSolar) + 
-  geom_line() + 
-  xlab("Principal Component") + 
-  ylab("Variance Explained") +
-  ggtitle("Scree Plot") +
-  ylim(0.01, 0.40)+
-  xlim(1,7)
+#factor analysis with 2, 4 and 6 factor spaces
+
+solar.fa <- fa(Solar, nfactors=2, scores=TRUE, rotate="varimax", fm="pa")
+print.psych(solar.fa, cut = 0.4, sort = TRUE)
+fa.diagram(solar.fa)
+
+```
+```{r}
+ROOFS<- codedmodule2 %>%
+ dplyr::select("DISPLACEROOFS":"RELYROOFS")
+
+psych::alpha(ROOFS, check.keys = TRUE)
 
@@
 
-## PCA on eco-pol characteristics of the technology -  Nuclear Energy
+```{r}
+#factor analysis with 2, 4 and 6 factor spaces
 
-```{r, echo = FALSE}
+roofs.fa <- fa(ROOFS, nfactors=4, scores=TRUE, rotate="varimax", fm="pa")
+print.psych(roofs.fa, cut = 0.4, sort = TRUE)
+fa.diagram(roofs.fa)
 
-Nuclear<- codedmodule2 %>%
- dplyr::select("DISPLACENUCLEAR":"RELYNUCLEAR")
-
-cronbach.alpha(Nuclear, na.rm = TRUE, CI=TRUE, standardized=TRUE)
-
+unclass(roofs.fa)
 ```
-
-```{r, echo = FALSE}
-
-Nuclear.pca <- Nuclear %>%
-  na.omit()%>%
-  prcomp(center = TRUE, scale. = TRUE)
-
-pcatablenuclear  <- summary(Nuclear.pca)
-
-Unclassednuclear <- unclass(pcatablenuclear)
-
-Importancenuclear <- Unclassednuclear["importance"]
-
-varexplnuclear <- do.call(rbind.data.frame, Importancenuclear)
-
-nuclearPCAtable <- data.frame(t(varexplnuclear), row.names=names(varexplnuclear))
-
-as_tibble(nuclearPCAtable) %>%
- add_column("Principal Components" = c("PC1", "PC2", "PC3", "PC4", "PC5", "PC6", "PC7", "PC8", "PC9", "PC10"))%>%
- dplyr::select("Principal Components",  importance.Proportion.of.Variance, importance.Cumulative.Proportion ) %>%  
- dplyr::rename(Proportion_of_Variance = importance.Proportion.of.Variance, Cumulative_Proportion = importance.Cumulative.Proportion)
-
-```
-
-```{r, echo=FALSE}
-
-rotations = Nuclear.pca["rotation"]
-
-#calculate total variance explained by each principal component
-var_explainedNuclear <- Nuclear.pca$sdev^2 / sum(Nuclear.pca$sdev^2)
-
-rotationsNuclear <- do.call(rbind.data.frame, rotations)
-
-rotationsNuclear
-
-```
-
-```{r, echo=FALSE}
-
-qplot(c(1:10), var_explainedNuclear) + 
-  geom_line() + 
-  xlab("Principal Component") + 
-  ylab("Variance Explained") +
-  ggtitle("Scree Plot") +
-  ylim(0.01, 0.30)+
-  xlim(1,7)
-
-```

### 2022-03-21 module2/module2extra.Rmd
moved files into folders

--- 2022-03-15 module2graphsandPCA.Rmd
@@
 ---
-title: "module2graphsandPCA"
+title: "module2extra"
 output:
   html_document:
-    fig_width: 9
+    fig_width: 7
     fig_height: 6
@@
     df_print: paged
-  pdf_document:
-
-    toc: true
-    number_sections: true
-    toc_depth: 2
-    fig_width: 9
-    fig_height: 6
-    fig_caption: yes
-    df_print: paged
 ---
 
-```{r load packages, warning = FALSE, message = FALSE, echo=FALSE}
-  knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+```{r}
 
-suppressPackageStartupMessages(library(tidyverse))
-suppressPackageStartupMessages(library(readxl))
-suppressPackageStartupMessages(library(hablar))
-suppressPackageStartupMessages(library(tsibble))
-suppressPackageStartupMessages(library(dplyr))
-suppressPackageStartupMessages(library(DT))
-suppressPackageStartupMessages(library(ggplot2))
-suppressPackageStartupMessages(library(ggbiplot))
+likertmodule2 <- module2%>%
+  filter(!row_number() %in% c(1,2)) %>% 
+  select(starts_with("Ben"))%>%
+  gather(Technology, Perceived_Benefit, Ben_Hydro:Ben_INDKerosene)%>%
+  separate(Technology, c("Ben", "Technology"), extra = "merge", fill = "left")%>%
+  select(-Ben) %>% 
+  group_by(Technology, Perceived_Benefit) %>%
+  dplyr::summarise(n=n())%>%
+  mutate(Perceived_Benefit = factor(Perceived_Benefit,  levels = c("Rather not say/Don't know","Not at all beneficial","Slightly beneficial","Moderately beneficial","Very beneficial", "Extremely beneficial")))%>%
+  pivot_wider(names_from = Perceived_Benefit, values_from = n)%>%
+  rename("NA1"="Rather not say/Don't know")%>%
+  select("Technology","Not at all beneficial","Slightly beneficial","Moderately beneficial","Very beneficial", "Extremely beneficial", "NA1","NA")%>%
+  unite("Rather not say/Don't know", "NA1":"NA", na.rm = TRUE, remove = FALSE)%>%
+  select(!c("NA1","NA"))
 
@@
 
-## Original Dataset
-```{r, echo=FALSE}
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-moduletwo <- read_excel( "~/Desktop/thesis_surveydata/political_factors_complete.xlsx")
-save(moduletwo, file = "moduletwo.rda")
-module2 <- data.frame(moduletwo)
-module2[module2 == "Rather not say/ Don't know"] <- "Rather not say/Don't know"
-module2 %>%
-  filter(!row_number() %in% c(1,2))
-
-# loaded data set for module 2 eco -pol variables and removes the rows with question number and question text
-```
-
-## Coded Dataset
-
-```{r, eval =TRUE, echo=FALSE}
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
-codedmodule2 <- module2 %>%
-
-#remove row 1
-  filter(!row_number() %in% c(1,2)) %>%
-
-# replace risky likert scale with numbers
-  mutate_at(vars(starts_with("Risky")), funs(case_when(. =="Not at all risky" ~ 1, 
-                                                       . =="Slightly risky" ~ 2, 
-                                                       . =="Moderately risky" ~ 3, 
-                                                       . =="Very risky" ~ 4, 
-                                                       . =="Extremely risky" ~ 5))) %>%
-
-# replace beneficial likert scale with numbers  
-  mutate_at(vars(starts_with("Ben")), funs(case_when(. =="Not at all beneficial" ~ 1,
-                                                     . =="Slightly beneficial" ~ 2,
-                                                     . =="Moderately beneficial" ~ 3,
-                                                     . =="Very beneficial" ~ 4,
-                                                     . =="Extremely beneficial" ~ 5 ))) %>%
-
-# replace nuclear acceptance likert scale with numbers
-  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
-                                                                        . == "Somewhat disagree" ~ 2,
-                                                                        . == "Neither agree nor disagree" ~3,
-                                                                        . == "Somewhat agree" ~ 4,
-                                                                        . == "Strongly agree" ~ 5))) %>%
-
-# code likert scale for variables for Kahan scale into numbers
-  mutate_at(vars(starts_with (c("K_I","K_H","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE", "DEV", "PROSPER", "RELY"))), funs(case_when(. == "Strongly disagree" ~ 1, 
-               . == "Somewhat disagree" ~ 2,
-               . == "Neither agree nor disagree" ~3,
-               . == "Somewhat agree" ~ 4,
-               . == "Strongly agree" ~ 5))) %>%
-
-# reverse code for likert scale for variables for Kahan scale into numbers
-  mutate_at(vars(starts_with (c("K_S","K_E"))), funs(case_when(. == "Strongly disagree" ~ 5, 
-                                                               . == "Somewhat disagree" ~ 4,
-                                                               . == "Neither agree nor disagree" ~3,
-                                                               . == "Somewhat agree" ~ 2,
-                                                               . == "Strongly agree" ~ 1))) %>%
-
-# code eco-pol scale variables into numbers
-  mutate_at(vars(SYSTEMDEMO,SYSTEMRELIGION,SYSTEMTECHNO,SYSTEMTOTAL,WEALTHLIM,MECHANISATION,DECISIONDECEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG), funs(case_when(.
-== "Strongly disagree" ~ 1,
-                        . == "Somewhat disagree" ~ 2,
-                        . == "Neither agree nor disagree" ~3,
-                        . == "Somewhat agree" ~ 4,
-                        . == "Strongly agree" ~ 5))) %>%
-
-# reverse code eco-pol scale variables into numbers 
- mutate_at(vars(DECISIONCEN, INDUSTRYSMALL, ECONOMYLOCAL, ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(. == "Strongly disagree" ~ 5, 
-                                                                                                         . == "Somewhat disagree" ~ 4,
-                                                                                                         . == "Neither agree nor disagree" ~3,
-                                                                                                         . == "Somewhat agree" ~ 2,
-                                                                                                         . == "Strongly agree" ~ 1)))
-
-codedmodule2
-```
-
-## Q1.
-Below is a list of various centrally managed sources of energy.
-How risky are each of these energy technologies according to you?
-Please tell me whether you see each technology as: not at all risky, slightly risky, moderately risky, very risky, or extremely risky
-
-```{r, eval=TRUE, echo=FALSE}
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-
-# summary statistics for risks from different energy sources
-
-risksumcentral <- codedmodule2 %>%
-  dplyr::select(!starts_with(c("RISKY_IND")))%>%
-  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
-  #add row index so later spreading indexed correctly
-  add_rownames()%>%
-  #melt to long format
-  gather(technology, value, -rowname) %>%
-  # separate risky from variable suffix
-  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
-  #separate mean from variable prefix
-  separate(var, c("technology", "summary")) %>%
-  # spread summary values back to wide form
-  spread(summary,value) %>%
-  #clean up
-  dplyr::select(-rowname, -Risky) %>%
-  arrange(mean) %>%
-  setNames(paste0('perceivedrisk.', names(.))) %>%
-  dplyr::rename(technology= perceivedrisk.technology)
-
-risksumcentral
+```{r}
+#summary statistics for nuclear energy accept, reject and reluctantly accept scale
+codedmodule2 %>%
+  summarize_at(vars(N_accept,N_reject,N_reluctantlyaccept), list(~mean(., na.rm = TRUE),~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE),~n())) %>%
+  add_rownames() %>%
+  gather(acceptance, value, -rowname) %>%
+  separate(acceptance, c("N_accept", "var") ,  extra = "merge", fill = "left") %>%
+  separate(var, c("Acceptance", "summary")) %>%
+  spread(summary, value) %>%
+  select(-rowname, -N_accept)%>%
+  arrange(mean)
 
@@
 
-```{r, echo=FALSE}
+```{r}
 
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+# chi square test for risk perception from nuclear energy and gender, race
 
-risksumcentral %>%
-  dplyr::select(technology, perceivedrisk.mean) %>%
-  mutate(technology = fct_reorder(technology, perceivedrisk.mean, .desc = FALSE))%>%
-  ggplot(aes(x=technology, y= perceivedrisk.mean))+
-  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
-  ylim(0,4)+
-  labs(y = "Mean Values of Perceived Risk", x = "Energy Technologies")+
-  ggtitle("Perceived risk from centrally managed energy technologies")+
-  coord_flip()
+# first combine gender and caste variables
 
-```
+chitest <- codedmodule2 %>%
+  select(Risky_Nuclear,Risky_Hydro, Risky_Hydro, Risky_Solar,Urban_Rural, Gender, Caste) %>%
+  na.omit() %>%
+  filter(!Caste=="Rather not say/Don't know")%>%
+  unite(gendercaste, Gender, Caste, sep = "_", remove = FALSE)
 
-## Q2.
-Following is a list of various individually or community-owned and managed sources of energy.
-How risky are each of these energy technologies according to you?
-Please tell me whether you see each technology as: not at all risky, slightly risky, moderately risky, very risky, or extremely risky.
-
-```{r, eval=TRUE, echo=FALSE}
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-
-# summary statistics for risks from different energy sources
-
-risksumIND <- codedmodule2 %>%
-  summarize_at(vars(starts_with(c("RISKY_IND"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
-  #add row index so later spreading indexed correctly
-  add_rownames()%>%
-  #melt to long format
-  gather(technology, value, -rowname) %>%
-  # separate risky from variable suffix
-  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
-  #separate mean from variable prefix
-  separate(var, c("technology", "summary")) %>%
-  # spread summary values back to wide form
-  spread(summary,value) %>%
-  #clean up
-  dplyr::select(-rowname, -Risky) %>%
-  arrange(mean) %>%
-  setNames(paste0('perceivedrisk.', names(.))) %>%
-  dplyr::rename(technology= perceivedrisk.technology)
-
-risksumIND
-
-```
-
-```{r, echo=FALSE}
-
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-
-risksumIND %>%
-  dplyr::select(technology, perceivedrisk.mean) %>%
-  mutate(technology = fct_reorder(technology, perceivedrisk.mean, .desc = FALSE))%>%
-  ggplot(aes(x=technology, y= perceivedrisk.mean))+
-  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
-  ylim(0,4)+
-  labs(y = "Mean Values of Perceived Risk", x = "Energy Technologies")+
-  ggtitle("Perceived risk from individually or community owned energy technologies")+
-  coord_flip()
-
-```
-
-## Q3.
-Following is a list of centrally managed sources of energy.
-How beneficial are each of these according to you?
-Please tell me whether you see each technology as: not at all beneficial, slightly beneficial, moderately beneficial, very beneficial, or extremely beneficial?
-
-```{r, eval=TRUE, echo=FALSE}
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-
-# summary statistics for risks from different energy sources
-
-bensumcentral <- codedmodule2 %>%
-  dplyr::select(!starts_with(c("Ben_IND")))%>%
-  summarize_at(vars(starts_with(c("Ben"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
-  #add row index so later spreading indexed correctly
-  add_rownames()%>%
-  #melt to long format
-  gather(technology, value, -rowname) %>%
-  # separate risky from variable suffix
-  separate(technology, c("Ben", "var"), extra = "merge", fill = "left") %>%
-  #separate mean from variable prefix
-  separate(var, c("technology", "summary")) %>%
-  # spread summary values back to wide form
-  spread(summary,value) %>%
-  #clean up
-  dplyr::select(-rowname, -Ben) %>%
-  arrange(mean) %>%
-  setNames(paste0('perceivedbenefit.', names(.))) %>%
-  dplyr::rename(technology= perceivedbenefit.technology)
-
-bensumcentral
-
-```
-
-```{r, echo=FALSE}
-
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-
-bensumcentral %>%
-  dplyr::select(technology, perceivedbenefit.mean) %>%
-  mutate(technology = fct_reorder(technology, perceivedbenefit.mean, .desc = FALSE))%>%
-  ggplot(aes(x=technology, y= perceivedbenefit.mean))+
-  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
-  ylim(0,4)+
-  labs(y = "Mean Values of Perceived Benefit", x = "Energy Technologies")+
-  ggtitle("Perceived benefit from centrally managed energy technologies")+
-  coord_flip()
-
-```
-
-## Q4.
-Following is a list of various individually or community owned and managed sources of energy.
-How beneficial are each of these according to you?
-Please tell me whether you see each technology as: not at all beneficial, slightly beneficial, moderately beneficial, very beneficial or extremely beneficial ?
-
-```{r, eval=TRUE, echo=FALSE}
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-
-# summary statistics for risks from different energy sources
-
-bensumIND <- codedmodule2 %>%
-  summarize_at(vars(starts_with(c("Ben_IND"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
-  #add row index so later spreading indexed correctly
-  add_rownames()%>%
-  #melt to long format
-  gather(technology, value, -rowname) %>%
-  # separate risky from variable suffix
-  separate(technology, c("Ben", "var"), extra = "merge", fill = "left") %>%
-  #separate mean from variable prefix
-  separate(var, c("technology", "summary")) %>%
-  # spread summary values back to wide form
-  spread(summary,value) %>%
-  #clean up
-  dplyr::select(-rowname, -Ben) %>%
-  arrange(mean) %>%
-  setNames(paste0('perceivedbenefit.', names(.))) %>%
-  dplyr::rename(technology= perceivedbenefit.technology)
-
-bensumIND
-
-```
-
-```{r, echo=FALSE}
-
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-
-bensumIND %>%
-  dplyr::select(technology, perceivedbenefit.mean) %>%
-  mutate(technology = fct_reorder(technology, perceivedbenefit.mean, .desc = FALSE))%>%
-  ggplot(aes(x=technology, y= perceivedbenefit.mean))+
-  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
-  ylim(0,4)+
-  labs(y = "Mean Values of Perceived Benefit", x = "Energy Technologies")+
-  ggtitle("Perceived benefit from individually or community owned energy technologies")+
-  coord_flip()
+chitest
 
@@
 
-center_barplot <- full_join( bensumcentral,risksumcentral, by = NULL, copy = FALSE, keep = FALSE) %>%
- dplyr::select(technology, perceivedbenefit.mean, perceivedrisk.mean) %>%
-  mutate(technology = fct_reorder(technology, perceivedbenefit.mean, .desc = FALSE))%>%
-   gather(key = "level", value = "mean", perceivedbenefit.mean, perceivedrisk.mean)
+KPC_var <-data.frame(var_explainedK, row.names=names(rotationsK)) %>%
+          tibble::rownames_to_column("PC")
 
-center_barplot$level <- as.factor(center_barplot$level)
-
- center_barplot%>% 
-  ggplot(aes(x=technology, y= mean, fill =  center_barplot$level))+
-  geom_bar(stat="identity", position=position_dodge())+
-  ylim(0,4)+
-  scale_fill_manual("legend", values = c("perceivedbenefit.mean" = "palegreen3","perceivedrisk.mean" = "firebrick2"))+
-  labs(y = "Mean Values", x = "Energy Technologies")+
-  ggtitle("Perceived risk and benefit from centrally owned energy technologies")+
-  coord_flip()
+KPC_var
 
@@
 
-```{r, echo=FALSE}
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+```{r}
+#%>%
+  #separate(Var, c("prefix", "Var", "technology"), sep = c(0,-5), remove = T)%>%
+ # select(!"prefix")
+# %>%
+  #pivot_longer(cols ="DISPLACEROOFS":"RELYROOFS", names_to = "Var", values_to = "score") %>%
+  #separate(Var, c("prefix", "Var", "technology"), sep = c(0,-5), remove = T)%>%
+  #select(!"prefix")
 
-full_join(bensumIND,risksumIND, by = NULL, copy = FALSE, keep = FALSE) %>%
- dplyr::select(technology, perceivedbenefit.mean, perceivedrisk.mean) %>%
-  mutate(technology = fct_reorder(technology, perceivedbenefit.mean, .desc = FALSE))%>%
-  gather(key = "level", value = "mean", perceivedbenefit.mean, perceivedrisk.mean) %>%
-  ggplot(aes(x=technology, y= mean, fill = level ))+
-  geom_bar(stat="identity", position=position_dodge())+
-  ylim(0,4)+
-  scale_fill_manual("legend", values = c("perceivedbenefit.mean" = "palegreen3","perceivedrisk.mean" = "firebrick2"))+
-  labs(y = "Mean Values", x = "Energy Technologies")+
-  ggtitle("Perceived risk and benefit from individually owned energy technologies")+
-  coord_flip()
-
+#DIESEL<- codedmodule2 %>%
+  #select("DISPLACEDIESEL":"RELYDIESEL")%>%
+  #pivot_longer(cols ="DISPLACEDIESEL":"RELYDIESEL", names_to = "Var", values_to = "score") %>%
+  #separate(Var, c("prefix", "Var", "technology"), sep = c(0,-6), remove = T)%>%
+  #select(!"prefix")
 ```
 
-\newpage
-
-# **Kahan et al (2007) scale**
-
-- **K_IINTRFER**	The government interferes far too much in our everyday lives.
-- **K_IPRIVACY**	The government should stop telling people how to live their lives.
-- **K_SHARM**	    Sometimes the government needs to make laws that keep people from hurting themselves.
-- **K_IPROTECT**	It’s not the government’s business to try to protect people from themselves.
-- **K_SLIMCHOI**	The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.
-- **K_SPROTECT**	The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.
-- **K_HEQUAL**	  We have gone too far in pushing equal rights in this country.
-- **K_HREVDIS1**	Nowadays it seems like there is just as much discrimination against upper castes as there is against Dalits.
-- **K_EDISCRIM**	Discrimination against minorities is still a very serious problem in our society.
-- **K_ERADEQ1**	  We need to dramatically reduce inequalities between the rich and the poor.
-- **K_EWEALTH**	  Our society would be better off if the distribution of wealth was more equal.
-- **K_ERADEQ2**	  We need to dramatically reduce inequalities between men and women.
-
-## Cronbach's alpha test on the Kahan et al (2007) scale
-
-```{r, echo=FALSE}
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-
-library(ltm)
-
-#cronbach alpha
-
-Kahanscale <- codedmodule2 %>%
-  dplyr::select(starts_with(c("K_")))
-
-cronbach.alpha(Kahanscale, na.rm = TRUE, CI=TRUE, standardized=TRUE)
-
-```
-
-## Principal Component Analysis on Kahan et al (2007) scale
-
-```{r, echo=FALSE}
-
-#PCA on Kahan scale
-pcaresultsK <- codedmodule2 %>%
-  dplyr::select(starts_with(c("K_")))%>%
-  na.omit()%>%
-  prcomp(center = TRUE, scale. = TRUE)
-
+```{r}
 rotations = pcaresultsK["rotation"]
@@
  dplyr::rename(Proportion_of_Variance = importance.Proportion.of.Variance, Cumulative_Proportion = importance.Cumulative.Proportion)
+```
 
-```
+\newpage
 

### 2022-03-21 module2/module2graphsandPCA.Rmd
moved files into folders

--- 2022-03-17 module2graphsandPCA.Rmd
@@
 suppressPackageStartupMessages(library(ggbiplot))
+suppressPackageStartupMessages(library(psych)) # psychometrics
 
@@
 center_barplot <- full_join( bensumcentral,risksumcentral, by = NULL, copy = FALSE, keep = FALSE) %>%
- dplyr::select(technology, perceivedbenefit.mean, perceivedrisk.mean) %>%
+ dplyr::select(technology, perceivedbenefit.mean, perceivedrisk.mean, perceivedbenefit.sd, perceivedrisk.sd) %>%
   mutate(technology = fct_reorder(technology, perceivedbenefit.mean, .desc = FALSE))%>%
    gather(key = "level", value = "mean", perceivedbenefit.mean, perceivedrisk.mean)
+
+#%>%gather(key = "riskben", value = "sd", perceivedrisk.sd, perceivedbenefit.sd)
 
@@
   geom_bar(stat="identity", position=position_dodge())+
+#geom_errorbar(aes(ymin= mean - sd, ymax= mean + sd), width =.2, position=position_dodge(.9))+
   ylim(0,4)+
@@
 ```
-
-\newpage
-
-# **Kahan et al (2007) scale**
-
-- **K_IINTRFER**	The government interferes far too much in our everyday lives.
-- **K_IPRIVACY**	The government should stop telling people how to live their lives.
-- **K_SHARM**	    Sometimes the government needs to make laws that keep people from hurting themselves.
-- **K_IPROTECT**	It’s not the government’s business to try to protect people from themselves.
-- **K_SLIMCHOI**	The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.
-- **K_SPROTECT**	The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.
-- **K_HEQUAL**	  We have gone too far in pushing equal rights in this country.
-- **K_HREVDIS1**	Nowadays it seems like there is just as much discrimination against upper castes as there is against Dalits.
-- **K_EDISCRIM**	Discrimination against minorities is still a very serious problem in our society.
-- **K_ERADEQ1**	  We need to dramatically reduce inequalities between the rich and the poor.
-- **K_EWEALTH**	  Our society would be better off if the distribution of wealth was more equal.
-- **K_ERADEQ2**	  We need to dramatically reduce inequalities between men and women.
-
-## Cronbach's alpha test on the Kahan et al (2007) scale
-
-```{r, echo=FALSE}
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-
-library(ltm)
-
-#cronbach alpha
-
-Kahanscale <- codedmodule2 %>%
-  dplyr::select(starts_with(c("K_")))
-
-cronbach.alpha(Kahanscale, na.rm = TRUE, CI=TRUE, standardized=TRUE)
-
-```
-
-## Principal Component Analysis on Kahan et al (2007) scale
-
-```{r, echo=FALSE}
-
-#PCA on Kahan scale
-pcaresultsK <- codedmodule2 %>%
-  dplyr::select(starts_with(c("K_")))%>%
-  na.omit()%>%
-  prcomp(center = TRUE, scale. = TRUE)
-
-rotations = pcaresultsK["rotation"]
-
-#calculate total variance explained by each principal component
-var_explainedK <- pcaresultsK$sdev^2 / sum(pcaresultsK$sdev^2)
-
-rotationsK <- do.call(rbind.data.frame, rotations)%>%
-              tibble::rownames_to_column("Variables")
-
-rotationsK
-
-pcatableK  <- summary(pcaresultsK)
-
-UnclassedK <- unclass(pcatableK)
-
-ImportanceK <- UnclassedK["importance"]
-
-varexplK <- do.call(rbind.data.frame, ImportanceK)
-
-KPCAtable <- data.frame(t(varexplK), row.names=names(varexplK))
-
-as_tibble(KPCAtable) %>%
- add_column("Principal Components" = c("PC1", "PC2", "PC3", "PC4", "PC5", "PC6", "PC7", "PC8", "PC9", "PC10", "PC11", "PC12"))%>%
- dplyr::select("Principal Components",  importance.Proportion.of.Variance, importance.Cumulative.Proportion ) %>%  
- dplyr::rename(Proportion_of_Variance = importance.Proportion.of.Variance, Cumulative_Proportion = importance.Cumulative.Proportion)
-
-```
-
-```{r, echo=FALSE}
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-
-qplot(c(1:12), var_explainedK) + 
-  geom_line() + 
-  xlab("Principal Component") + 
-  ylab("Variance Explained") +
-  ggtitle("Scree Plot") +
-  ylim(0, 0.30)+
-  xlim(1,7)
-
-```
-
-\newpage
-
-# **The economic -political values of the perceiver scale**
-
-- **DECISIONDECEN**	 Local politicians shouldn't have to ask permission from the central government to implement policies
-- **DECISIONCEN**	   Laws and policies would be implemented more smoothly if more power lay with the central government.
-- **SYSTEMTOTAL**	   It is good to have a strong leader who does not have to bother with elections.
-- **SYSTEMTECHNO**	 Experts, not the government, should make decisions according to what they think is best for the country.
-- **SYSTEMDEMO**	   It is very important to have a democratic political system because it ensures that no individual leader has too much power.
-- **SYSTEMRELIGION** There should be a system governed by religious law.
-- **INDUSTRYSMALL**	 Large corporations are destroying the local industries in India and benefiting only a handful of people.
-- **INDUSTRYLARGE**	 Large scale industries are required for the development of the country that will benefit everyone
-- **ECONOMYLOCAL**	 India would be better off if foreign companies didn't come to here
-- **ECONOMYGLOBAL**	 Foreign companies have led to a range of benefits for the Indian people and society
-- **DEVOVERENV**	   Economic growth and creating jobs should be prioritized over environmental protection
-- **ENVOVERDEV**	   Polluting industries that spoil the environment should be shut down even if it costs people their jobs
-- **OWNERPVT**	     All businesses and industries should be owned privately
-- **OWNERPUB**	     The government should own most large businesses and industries
-- **OWNERREG**	     Regardless of ownership, the government should pass strong regulations and implement them
-- **OWNERNOREG**	   There is too much red-tape and the government should not interfere with businesses and industries
-- **WEALTHLIM**	     A limit should be put to how much wealth a person can amass
-- **MECHANISATION**	 Rapid mechanization of work is taking away jobs from workers in this country
-
-## Cronbach's alpha test on the economic -political values of the perceiver
-```{r, echo= FALSE}
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-ecopolscalescores <- codedmodule2 %>%
- dplyr::select(starts_with(c("Risky","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG", "Gender","Caste","Religion", "State")))%>%
-  rowwise()%>%
-  na.omit()%>%
-  dplyr::mutate(Pro_decentralisation = mean(c_across("DECISIONDECEN":"DECISIONCEN")))%>%
-   dplyr::mutate(Pro_largescale = mean(c_across("INDUSTRYLARGE":"INDUSTRYSMALL")))%>%
-   dplyr::mutate(Pro_global = mean(c_across("ECONOMYGLOBAL":"ECONOMYLOCAL")))%>%
-   dplyr::mutate(Pro_ecogrowth = mean(c_across("ENVOVERDEV":"DEVOVERENV")))%>%
-   dplyr::mutate(Pro_private = mean(c_across("OWNERPVT":"OWNERREG")))%>%
-  dplyr::select(!c("DECISIONDECEN","DECISIONCEN", "INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL", "ECONOMYLOCAL","ENVOVERDEV",     "DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG"))
-
-#cronbach alpha
-
-cronbach.alpha(ecopolscalescores, na.rm = TRUE, CI=TRUE, standardized=TRUE)
-
-```
-
-## PCA on the economic -political values of the perceiver
-
-```{r, echo=FALSE}
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-# PCA test on qualities of the perceiver
-
-ecopolscalepca <- ecopolscalescores %>%
-  dplyr::select(!starts_with(c("Risky","Gender","Caste","Religion","State")))%>%
-  prcomp(center = TRUE,scale. = TRUE)
-
-var_explained_ecopol = ecopolscalepca$sdev^2 / sum(ecopolscalepca$sdev^2)
-
-pcatableecopol  <- summary(ecopolscalepca)
-
-Unclassedecopol <- unclass(pcatableecopol)
-
-Importanceecopol <- Unclassedecopol["importance"]
-
-varexplecopol <- do.call(rbind.data.frame, Importanceecopol)
-
-ecopolPCAtable <- data.frame(t(varexplecopol), row.names=names(varexplecopol))
-
-as_tibble(ecopolPCAtable) %>%
- add_column("Principal Components" = c("PC1", "PC2", "PC3", "PC4", "PC5", "PC6", "PC7", "PC8", "PC9", "PC10", "PC11"))%>%
- dplyr::select("Principal Components",  importance.Proportion.of.Variance, importance.Cumulative.Proportion ) %>%  
- dplyr::rename(Proportion_of_Variance = importance.Proportion.of.Variance, Cumulative_Proportion = importance.Cumulative.Proportion)
-
-```
-
-## Variables in the PCs
-
-```{r, echo=FALSE}
-
-rotationsecopol = ecopolscalepca["rotation"]
-rotationsDFecopol <- do.call(rbind.data.frame, rotationsecopol)
-rotationsDFecopol
-```
-
-```{r, echo=FALSE}
-
-qplot(c(1:11), var_explained_ecopol) + 
-  geom_line() + 
-  xlab("Principal Component") + 
-  ylab("Variance Explained") +
-  ggtitle("Scree Plot") +
-  ylim(0.05, 0.20)+
-  xlim(1,7)
-
-```
-
-\newpage
-
-# **eco - pol characteristics of the technology scale-  Solar Energy and Nuclear Energy**
-
-- **DISPLACESOLAR**	 Solar energy is leading to displacement of people from their land
-- **POLLUTESOLAR**	 Solar energy increases pollution of air/water/land
-- **HEALTHSOLAR**	   Solar energy poses a great risk to the health of people living around it
-- **JOBSSOLAR**	     Solar energy will bring jobs to the local community
-- **BEAUTYSOLAR**	   Solar energy spoils the natural beauty of the landscape
-- **PRIDESOLAR**	   I would be proud if my community used solar energy
-- **NPRIDESOLAR**	   Solar energy is a mark of pride for our nation
-- **DEVSOLAR**	     Solar energy pushes forward the country's development
-- **PROSPERSOLAR**	 Solar energy brings economic prosperity to the surrounding regions
-- **RELYSOLAR**	     I don't like the idea that I have to rely on the government for electricity from (large scale) solar energy
-
-## Cronbach's alpha test on eco-pol characteristics of the technology -  Solar Energy
-
-```{r, echo=FALSE}
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-
-#PCA on eco-pol characterisitics of the technology
-
-Solar <- codedmodule2 %>%
- dplyr::select("DISPLACESOLAR":"RELYSOLAR")
-
-cronbach.alpha(Solar, na.rm = TRUE, CI=TRUE, standardized=TRUE)
-
-ROOFS<- codedmodule2 %>%
- dplyr::select("DISPLACEROOFS":"RELYROOFS")
-
-```
-
-## PCA on eco-pol characteristics of the technology -  Solar Energy
-
-```{r, echo = FALSE}
-
-Solar.pca <- Solar %>%
-  na.omit()%>%
-  prcomp(center = TRUE, scale. = TRUE)
-
-pcatablesolar  <- summary(Solar.pca)
-
-Unclassedsolar <- unclass(pcatablesolar)
-
-Importancesolar <- Unclassedsolar["importance"]
-
-varexplsolar <- do.call(rbind.data.frame, Importancesolar)
-
-solarPCAtable <- data.frame(t(varexplsolar), row.names=names(varexplsolar))
-
-as_tibble(solarPCAtable) %>%
- add_column("Principal Components" = c("PC1", "PC2", "PC3", "PC4", "PC5", "PC6", "PC7", "PC8", "PC9", "PC10"))%>%
- dplyr::select("Principal Components",  importance.Proportion.of.Variance, importance.Cumulative.Proportion ) %>%  
- dplyr::rename(Proportion_of_Variance = importance.Proportion.of.Variance, Cumulative_Proportion = importance.Cumulative.Proportion)
-```
-
-```{r, echo=FALSE}
-
-rotations = Solar.pca["rotation"]
-
-#calculate total variance explained by each principal component
-var_explainedSolar <- Solar.pca$sdev^2 / sum(Solar.pca$sdev^2)
-
-rotationsSolar <- do.call(rbind.data.frame, rotations)
-
-rotationsSolar
-
-```
-
-```{r, echo=FALSE}
-
-qplot(c(1:10), var_explainedSolar) + 
-  geom_line() + 
-  xlab("Principal Component") + 
-  ylab("Variance Explained") +
-  ggtitle("Scree Plot") +
-  ylim(0.01, 0.40)+
-  xlim(1,7)
-
-```
-
-## PCA on eco-pol characteristics of the technology -  Nuclear Energy
-
-```{r, echo = FALSE}
-
-Nuclear<- codedmodule2 %>%
- dplyr::select("DISPLACENUCLEAR":"RELYNUCLEAR")
-
-cronbach.alpha(Nuclear, na.rm = TRUE, CI=TRUE, standardized=TRUE)
-
-```
-
-```{r, echo = FALSE}
-
-Nuclear.pca <- Nuclear %>%
-  na.omit()%>%
-  prcomp(center = TRUE, scale. = TRUE)
-
-pcatablenuclear  <- summary(Nuclear.pca)
-
-Unclassednuclear <- unclass(pcatablenuclear)
-
-Importancenuclear <- Unclassednuclear["importance"]
-
-varexplnuclear <- do.call(rbind.data.frame, Importancenuclear)
-
-nuclearPCAtable <- data.frame(t(varexplnuclear), row.names=names(varexplnuclear))
-
-as_tibble(nuclearPCAtable) %>%
- add_column("Principal Components" = c("PC1", "PC2", "PC3", "PC4", "PC5", "PC6", "PC7", "PC8", "PC9", "PC10"))%>%
- dplyr::select("Principal Components",  importance.Proportion.of.Variance, importance.Cumulative.Proportion ) %>%  
- dplyr::rename(Proportion_of_Variance = importance.Proportion.of.Variance, Cumulative_Proportion = importance.Cumulative.Proportion)
-
-```
-
-```{r, echo=FALSE}
-
-rotations = Nuclear.pca["rotation"]
-
-#calculate total variance explained by each principal component
-var_explainedNuclear <- Nuclear.pca$sdev^2 / sum(Nuclear.pca$sdev^2)
-
-rotationsNuclear <- do.call(rbind.data.frame, rotations)
-
-rotationsNuclear
-
-```
-
-```{r, echo=FALSE}
-
-qplot(c(1:10), var_explainedNuclear) + 
-  geom_line() + 
-  xlab("Principal Component") + 
-  ylab("Variance Explained") +
-  ggtitle("Scree Plot") +
-  ylim(0.01, 0.30)+
-  xlim(1,7)
-
-```

### 2022-03-23 module1/moduleoneanalysis.Rmd
moved files into folders
knitted all tables to word doc

--- 2022-02-23 moduleoneanalysis.Rmd
@@
                                                                         . == "Somewhat agree" ~ 4,
-                                                                        . == "Strongly agree" ~ 5)))
+                                                                        . == "Strongly agree" ~ 5))) %>%
+
+  mutate_at(vars(Livelihood_Income), funs(case_when(. == "(a) own farming/fishing/animal rearing/business" ~ "LSI", 
+                                                    . == "(b) employed for wages/salary" ~ "ISI",
+                                                    . == "(c) student" ~"student",
+                                                    . == "(d) currently unemployed" ~ "unemployed",
+                                                    . == "(e) homemaker" ~ "homemaker",
+                                                    . == "(f) retired" ~ "retired",
+                                                    . == "(g) unable to work" ~ "unable to work" ))) %>%
+
+   mutate_at(vars(education), funs(case_when(. == "No schooling completed" ~ 0, 
+                                                                        . == "Primary school" ~ 1,
+                                                                        . == "Grade 10th" ~ 2,
+                                                                        . == "Grade 12th" ~ 3,
+                                                                        . == "Some college, no degree" ~ 4,
+                                                                        . == "Trade/technical/vocational training" ~ 5,
+                                                                        . == "Bachelor's degree" ~ 6,
+                                                                        . == "Master's degree" ~ 7,
+                                                                        . == "Professional degree" ~ 8,
+                                                                        . == "Doctorate degree" ~ 9 ))) %>%
 
 codedmodule1
-
 #coded dependent variables for module 1 livelihood and income security survey

### 2022-03-23 module2/factor analysis/module2PCAs.Rmd
knitted all tables to word doc

---
title: "PCAs"
output: word_document

---

```{r load packages, warning = FALSE, message = FALSE, echo=FALSE}
  knitr::opts_chunk$set(warning = FALSE, message = FALSE)

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))

suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(DT))

suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(psych)) # psychometrics

```

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
moduletwo <- read_excel( "~/Desktop/thesis_surveydata/political_factors_complete.xlsx")
save(moduletwo, file = "moduletwo.rda")
module2 <- data.frame(moduletwo)
module2[module2 == "Rather not say/ Don't know"] <- "Rather not say/Don't know"
#module2 %>% filter(!row_number() %in% c(1,2))

# loaded data set for module 2 eco -pol variables and removes the rows with question number and question text
```

```{r, eval =TRUE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
codedmodule2 <- module2 %>%

#remove row 1
  filter(!row_number() %in% c(1,2)) %>%

# replace risky likert scale with numbers
  mutate_at(vars(starts_with("Risky")), funs(case_when(. =="Not at all risky" ~ 1, 
                                                       . =="Slightly risky" ~ 2, 
                                                       . =="Moderately risky" ~ 3, 
                                                       . =="Very risky" ~ 4, 
                                                       . =="Extremely risky" ~ 5))) %>%

# replace beneficial likert scale with numbers  
  mutate_at(vars(starts_with("Ben")), funs(case_when(. =="Not at all beneficial" ~ 1,
                                                     . =="Slightly beneficial" ~ 2,
                                                     . =="Moderately beneficial" ~ 3,
                                                     . =="Very beneficial" ~ 4,
                                                     . =="Extremely beneficial" ~ 5 ))) %>%

# replace nuclear acceptance likert scale with numbers
  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                                        . == "Somewhat disagree" ~ 2,
                                                                        . == "Neither agree nor disagree" ~3,
                                                                        . == "Somewhat agree" ~ 4,
                                                                        . == "Strongly agree" ~ 5))) %>%

# code likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_I","K_H","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE", "DEV", "PROSPER", "RELY"))), funs(case_when(. == "Strongly disagree" ~ 1, 
               . == "Somewhat disagree" ~ 2,
               . == "Neither agree nor disagree" ~3,
               . == "Somewhat agree" ~ 4,
               . == "Strongly agree" ~ 5))) %>%

# reverse code for likert scale for variables for Kahan scale into numbers
mutate_at(vars(starts_with (c("K_S","K_E"))), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                               . == "Somewhat disagree" ~ 2,
                                                               . == "Neither agree nor disagree" ~3,
                                                               . == "Somewhat agree" ~ 4,
                                                               . == "Strongly agree" ~ 5))) %>%

# code eco-pol scale variables into numbers
  mutate_at(vars(SYSTEMDEMO,SYSTEMRELIGION,SYSTEMTECHNO,SYSTEMTOTAL,WEALTHLIM,MECHANISATION,DECISIONDECEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG), funs(case_when(. == "Strongly disagree" ~ 1, 
                        . == "Somewhat disagree" ~ 2,
                        . == "Neither agree nor disagree" ~3,
                        . == "Somewhat agree" ~ 4,
                        . == "Strongly agree" ~ 5))) %>%

# reverse code eco-pol scale variables into numbers 
 mutate_at(vars(DECISIONCEN, INDUSTRYSMALL, ECONOMYLOCAL, ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                                                                         . == "Somewhat disagree" ~ 2,
                                                                                                         . == "Neither agree nor disagree" ~3,
                                                                                                         . == "Somewhat agree" ~ 4,
                                                                                                         . == "Strongly agree" ~ 5)))
```

**Kahan et al (2007) scale**

Individualism - Communitarinism

- **K_IINTRFER**	The government interferes far too much in our everyday lives.
- **K_IPRIVACY**	The government should stop telling people how to live their lives.
- **K_SHARM**	    Sometimes the government needs to make laws that keep people from hurting themselves.
- **K_IPROTECT**	It’s not the government’s business to try to protect people from themselves.
- **K_SLIMCHOI**	The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.
- **K_SPROTECT**	The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.

Hierarchy -Egalitarianism

- **K_HEQUAL**	  We have gone too far in pushing equal rights in this country.
- **K_HREVDIS1**	Nowadays it seems like there is just as much discrimination against upper castes as there is against Dalits.
- **K_EDISCRIM**	Discrimination against minorities is still a very serious problem in our society.
- **K_ERADEQ1**	  We need to dramatically reduce inequalities between the rich and the poor.
- **K_EWEALTH**	  Our society would be better off if the distribution of wealth was more equal.
- **K_ERADEQ2**	  We need to dramatically reduce inequalities between men and women.

Cronbach's alpha test on the Kahan et al (2007) scale

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

library(ltm)

#cronbach alpha

KahanS <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_S", "K_I")))%>%
  na.omit()

KahanI <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_I")))%>%
  na.omit()

#K_S items produce a strong alpha but not K_I

KahanI.alpha <- psych::alpha(KahanI)

KahanS.alpha <- psych::alpha(KahanS, check.keys = TRUE)

KahanE <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_H", "K_E")))%>%
  na.omit()

KahanE.alpha <- psych::alpha(KahanE, check.keys = TRUE)

```

Factor Analysis on Kahan et al (2007) scale: 2 factor spaces

```{r, echo=FALSE}

#factor analysis on Kahan scale: 2 factor spaces
Kahan <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_")))%>%
  na.omit()

Kahan.fa <- fa(Kahan, nfactors=2, scores=TRUE, rotate="varimax", fm="pa")
#print.psych(Kahan.fa, cut = 0.3, sort = TRUE)
#fa.diagram(Kahan.fa)

loadingskahan <- unclass(Kahan.fa$loadings)

loadingstablekahan <- cbind(loadingskahan)

twofakahan <- as_tibble(loadingstablekahan) %>%
add_column("Items" = c("The government interferes far too much in our everyday lives", 
"The government should stop telling people how to live their lives", 
"Sometimes the government needs to make laws that keep people from hurting themselves" , 
"It’s not the government’s business to try to protect people from themselves", 
"The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society", 
"The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals", 
"We have gone too far in pushing equal rights in this country",
"Nowadays it seems like there is just as much discrimination against upper castes as there is against Dalits",
"Discrimination against minorities is still a very serious problem in our society", 
"We need to dramatically reduce inequalities between the rich and the poor",
"Our society would be better off if the distribution of wealth was more equal",
"We need to dramatically reduce inequalities between men and women")) %>%
dplyr::select("Items",  PA1, PA2) %>%
  arrange(desc(PA1))

knitr::kable(twofakahan, digits = 2)

VarexplK <- unclass(Kahan.fa$Vaccounted)

knitr::kable(VarexplK, digits = 2)
```

Factor Analysis on Kahan et al (2007) scale: 4 factor spaces

```{r, echo=FALSE}
#factor analysis on Kahan scale: 4 factor spaces 
Kahan <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_")))%>%
  na.omit()

fourKahan.fa <- fa(Kahan, nfactors=4, scores=TRUE, rotate="varimax", fm="pa")
#print.psych(Kahan.fa, cut = 0.3, sort = TRUE)
#fa.diagram(Kahan.fa)

fourloadingskahan <- unclass(fourKahan.fa$loadings)

fourloadingstablekahan <- cbind(fourloadingskahan)

fourfakahan <- as_tibble(fourloadingstablekahan) %>%
add_column("Items" = c("The government interferes far too much in our everyday lives", 
"The government should stop telling people how to live their lives", 
"Sometimes the government needs to make laws that keep people from hurting themselves" , 
"It’s not the government’s business to try to protect people from themselves", 
"The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society", 
"The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals", 
"We have gone too far in pushing equal rights in this country",
"Nowadays it seems like there is just as much discrimination against upper castes as there is against Dalits",
"Discrimination against minorities is still a very serious problem in our society", 
"We need to dramatically reduce inequalities between the rich and the poor",
"Our society would be better off if the distribution of wealth was more equal",
"We need to dramatically reduce inequalities between men and women")) %>%
dplyr::select("Items",  PA1, PA2, PA3, PA4)%>%
  arrange(desc(PA1))

knitr::kable(fourfakahan, digits= 2)

VarexplK <- unclass(fourKahan.fa$Vaccounted)

knitr::kable(VarexplK, digits = 2)
```

**The economic -political values of the perceiver scale**

- **DECISIONDECEN**	 Local politicians shouldn't have to ask permission from the central government to implement policies
- **DECISIONCEN**	   Laws and policies would be implemented more smoothly if more power lay with the central government.
- **SYSTEMTOTAL**	   It is good to have a strong leader who does not have to bother with elections.
- **SYSTEMTECHNO**	 Experts, not the government, should make decisions according to what they think is best for the country.
- **SYSTEMDEMO**	   It is very important to have a democratic political system because it ensures that no individual leader has too much power.
- **SYSTEMRELIGION** There should be a system governed by religious law.
- **INDUSTRYSMALL**	 Large corporations are destroying the local industries in India and benefiting only a handful of people.
- **INDUSTRYLARGE**	 Large scale industries are required for the development of the country that will benefit everyone
- **ECONOMYLOCAL**	 India would be better off if foreign companies didn't come to here
- **ECONOMYGLOBAL**	 Foreign companies have led to a range of benefits for the Indian people and society
- **DEVOVERENV**	   Economic growth and creating jobs should be prioritized over environmental protection
- **ENVOVERDEV**	   Polluting industries that spoil the environment should be shut down even if it costs people their jobs
- **OWNERPVT**	     All businesses and industries should be owned privately
- **OWNERPUB**	     The government should own most large businesses and industries
- **OWNERREG**	     Regardless of ownership, the government should pass strong regulations and implement them
- **OWNERNOREG**	   There is too much red-tape and the government should not interfere with businesses and industries
- **WEALTHLIM**	     A limit should be put to how much wealth a person can amass
- **MECHANISATION**	 Rapid mechanization of work is taking away jobs from workers in this country

Cronbach's alpha test on the economic -political values of the perceiver

```{r, echo= FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
ecopolscalescores <- codedmodule2 %>%
 dplyr::select(starts_with(c("SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
  rowwise()%>%
  na.omit()#%>%
  #dplyr::mutate(Pro_decentralisation = mean(c_across("DECISIONDECEN":"DECISIONCEN")))%>%
   #dplyr::mutate(Pro_largescale = mean(c_across("INDUSTRYLARGE":"INDUSTRYSMALL")))%>%
   #dplyr::mutate(Pro_global = mean(c_across("ECONOMYGLOBAL":"ECONOMYLOCAL")))%>%
   #dplyr::mutate(Pro_ecogrowth = mean(c_across("ENVOVERDEV":"DEVOVERENV")))%>%
   #dplyr::mutate(Pro_private = mean(c_across("OWNERPVT":"OWNERREG")))%>%
  #dplyr::select(!c("DECISIONDECEN","DECISIONCEN", "INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL", "ECONOMYLOCAL","ENVOVERDEV",     "DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG"))

#cronbach alpha

psych::alpha(ecopolscalescores, check.keys = TRUE)

```

Factor Analysis on the economic and political values scale: 2 factor spaces

```{r, echo=FALSE}

#factor analysis with 2, 4 and 6 factor spaces

ecopolscale.fa <- fa(ecopolscalescores, nfactors=2, scores=TRUE, rotate="varimax", fm="pa")
#print.psych(ecopolscale.fa, cut = 0.3, sort = TRUE)
#fa.diagram(ecopolscale.fa)

loadingsecopol <- unclass(ecopolscale.fa$loadings)

loadingstableecopol <- cbind(loadingsecopol)

twofaecopol <- as_tibble(loadingstableecopol) %>%
add_column("Items" = c("Local politicians shouldn't have to ask permission from the central government to implement policies",
 "Laws and policies would be implemented more smoothly if more power lay with the central government",
"It is good to have a strong leader who does not have to bother with elections", 
 "Experts, not the government, should make decisions according to what they think is best for the country" , 
"It is very important to have a democratic political system because it ensures that no individual leader has too much power" , 
"There should be a system governed by religious law" , 
"Large corporations are destroying the local industries in India and benefiting only a handful of people" , 
"Large scale industries are required for the development of the country that will benefit everyone" , 
"India would be better off if foreign companies didn't come to here" , 
"Foreign companies have led to a range of benefits for the Indian people and society", 
"Economic growth and creating jobs should be prioritized over environmental protection" , 
"Polluting industries that spoil the environment should be shut down even if it costs people their jobs", 
"All businesses and industries should be owned privately", 
"The government should own most large businesses and industries", 
"Regardless of ownership, the government should pass strong regulations and implement them", 
"There is too much red-tape and the government should not interfere with businesses and industries" , 
"A limit should be put to how much wealth a person can amass",
 "Rapid mechanization of work is taking away jobs from workers in this country"))%>%
dplyr::select("Items",PA1, PA2)%>%
arrange(desc(PA1))

knitr::kable(twofaecopol, digits= 2)

Varexplecopol <- unclass(ecopolscale.fa$Vaccounted)

knitr::kable(Varexplecopol, digits = 2)

```

Factor Analysis on the economic and political values scale: 4 factor spaces

```{r, echo=FALSE}
#factor analysis with 4 factor spaces

ecopolscale4.fa <- fa(ecopolscalescores, nfactors=4, scores=TRUE, rotate="varimax", fm="pa")
#print.psych(ecopolscale.fa, cut = 0.3, sort = TRUE)
#fa.diagram(ecopolscale.fa)

loadingsecopol4 <- unclass(ecopolscale4.fa$loadings)

loadingstableecopol4 <- cbind(loadingsecopol4)

faecopol4 <- as_tibble(loadingstableecopol4) %>%
add_column("Items" = c("Local politicians shouldn't have to ask permission from the central government to implement policies",
 "Laws and policies would be implemented more smoothly if more power lay with the central government",
"It is good to have a strong leader who does not have to bother with elections", 
 "Experts, not the government, should make decisions according to what they think is best for the country" , 
"It is very important to have a democratic political system because it ensures that no individual leader has too much power" , 
"There should be a system governed by religious law" , 
"Large corporations are destroying the local industries in India and benefiting only a handful of people" , 
"Large scale industries are required for the development of the country that will benefit everyone" , 
"India would be better off if foreign companies didn't come to here" , 
"Foreign companies have led to a range of benefits for the Indian people and society", 
"Economic growth and creating jobs should be prioritized over environmental protection" , 
"Polluting industries that spoil the environment should be shut down even if it costs people their jobs", 
"All businesses and industries should be owned privately", 
"The government should own most large businesses and industries", 
"Regardless of ownership, the government should pass strong regulations and implement them", 
"There is too much red-tape and the government should not interfere with businesses and industries" , 
"A limit should be put to how much wealth a person can amass",
 "Rapid mechanization of work is taking away jobs from workers in this country"))%>%
dplyr::select("Items",PA1, PA2, PA3, PA4) %>%
  arrange(desc(PA1))

knitr::kable(faecopol4, digits= 2)

Varexplecopol4 <- unclass(ecopolscale4.fa$Vaccounted)

knitr::kable(Varexplecopol4, digits = 2)

```

Factor Analysis on the economic and political values scale: 6 factor spaces

```{r, echo=FALSE}

ecopolscale6.fa <- fa(ecopolscalescores, nfactors=6, scores=TRUE, rotate="varimax", fm="pa")
#print.psych(ecopolscale.fa, cut = 0.3, sort = TRUE)
#fa.diagram(ecopolscale.fa)

loadingsecopol6 <- unclass(ecopolscale6.fa$loadings)

loadingstableecopol6 <- cbind(loadingsecopol6)

faecopol6 <- as_tibble(loadingstableecopol6) %>%
add_column("Items" = c("Local politicians shouldn't have to ask permission from the central government to implement policies",
 "Laws and policies would be implemented more smoothly if more power lay with the central government",
"It is good to have a strong leader who does not have to bother with elections", 
 "Experts, not the government, should make decisions according to what they think is best for the country" , 
"It is very important to have a democratic political system because it ensures that no individual leader has too much power" , 
"There should be a system governed by religious law" , 
"Large corporations are destroying the local industries in India and benefiting only a handful of people" , 
"Large scale industries are required for the development of the country that will benefit everyone" , 
"India would be better off if foreign companies didn't come to here" , 
"Foreign companies have led to a range of benefits for the Indian people and society", 
"Economic growth and creating jobs should be prioritized over environmental protection" , 
"Polluting industries that spoil the environment should be shut down even if it costs people their jobs", 
"All businesses and industries should be owned privately", 
"The government should own most large businesses and industries", 
"Regardless of ownership, the government should pass strong regulations and implement them", 
"There is too much red-tape and the government should not interfere with businesses and industries" , 
"A limit should be put to how much wealth a person can amass",
 "Rapid mechanization of work is taking away jobs from workers in this country"))%>%
dplyr::select("Items",PA1, PA2, PA3, PA4, PA5, PA6) %>%
  arrange(desc(PA1))

knitr::kable(faecopol6, digits= 2)

Varexplecopol6 <- unclass(ecopolscale6.fa$Vaccounted)

knitr::kable(Varexplecopol6, digits = 2)
```

**Economic and Political characteristics of the energy technology scale -  Solar Energy and rooftop solar energy**

- **DISPLACESOLAR**	 Solar energy is leading to displacement of people from their land
- **POLLUTESOLAR**	 Solar energy increases pollution of air/water/land
- **HEALTHSOLAR**	   Solar energy poses a great risk to the health of people living around it
- **JOBSSOLAR**	     Solar energy will bring jobs to the local community
- **BEAUTYSOLAR**	   Solar energy spoils the natural beauty of the landscape
- **PRIDESOLAR**	   I would be proud if my community used solar energy
- **NPRIDESOLAR**	   Solar energy is a mark of pride for our nation
- **DEVSOLAR**	     Solar energy pushes forward the country's development
- **PROSPERSOLAR**	 Solar energy brings economic prosperity to the surrounding regions
- **RELYSOLAR**	     I don't like the idea that I have to rely on the government for electricity from (large scale) solar energy

Cronbach's alpha test on the Eco-Pol characteristics of the technology -  Solar Energy

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

#alpha test on Eco-pol characteristics of the technology

Solar <- codedmodule2 %>%
dplyr::select("DISPLACESOLAR":"RELYSOLAR") %>%
dplyr::rename("Solar energy is leading to displacement of people from their land" = "DISPLACESOLAR") %>%
dplyr::rename("Solar energy increases pollution of air/water/land" = "POLLUTESOLAR")%>%
dplyr::rename("Solar energy poses a great risk to the health of people living around it" = "HEALTHSOLAR")%>%
dplyr::rename("Solar energy will bring jobs to the local community" = "JOBSSOLAR")%>%
dplyr::rename("Solar energy spoils the natural beauty of the landscape" = "BEAUTYSOLAR")%>%
dplyr::rename("I would be proud if my community used solar energy" = "PRIDESOLAR")%>%
dplyr::rename("Solar energy is a mark of pride for our nation" = "NPRIDESOLAR") %>%
dplyr::rename("Solar energy pushes forward the country's development" = "DEVSOLAR")%>%
dplyr::rename("Solar energy brings economic prosperity to the surrounding regions" = "PROSPERSOLAR")%>%
dplyr::rename("I don't like the idea that I have to rely on the government for electricity from (large scale solar energy)" = "RELYSOLAR")%>%
  na.omit()

psych::alpha(Solar, check.keys = TRUE)

```

Factor Analysis on the eco- pol characteristics of the technology, Solar Energy : 2 factor spaces

```{r, echo=FALSE}

#factor analysis with 2 factor spaces

solar.fa <- fa(Solar, nfactors=2, scores=TRUE, rotate="varimax", fm="pa")
#print.psych(solar.fa, cut = 0.4, sort = TRUE)
#fa.diagram(solar.fa)

loadingssolar <- unclass(solar.fa$loadings)

loadingstablesolar <- cbind(loadingssolar)

fasolar <- as_tibble(loadingstablesolar) %>%
add_column("Items" = c("Solar energy is leading to displacement of people from their land",
"Solar energy increases pollution of air/water/land",
"Solar energy poses a great risk to the health of people living around it",
"Solar energy will bring jobs to the local community",
"Solar energy spoils the natural beauty of the landscape",
"I would be proud if my community used solar energy",
"Solar energy is a mark of pride for our nation",
"Solar energy pushes forward the country's development",
"Solar energy brings economic prosperity to the surrounding regions",
"I don't like the idea that I have to rely on the government for electricity from (large scale) solar energy"))%>%
dplyr::select("Items",PA1, PA2)%>%
arrange(desc(PA1))

knitr::kable(fasolar, digits= 2)

Varexplsolar <- unclass(solar.fa$Vaccounted)

knitr::kable(Varexplsolar, digits = 2)
```

Factor Analysis on the eco- pol characteristics of the technology, Solar Energy : 4 factor spaces

```{r, echo=FALSE}

#factor analysis with  4 a factor spaces

solar4.fa <- fa(Solar, nfactors=4, scores=TRUE, rotate="varimax", fm="pa")
#print.psych(solar.fa, cut = 0.4, sort = TRUE)
#fa.diagram(solar.fa)

loadingssolar4 <- unclass(solar4.fa$loadings)

loadingstablesolar4 <- cbind(loadingssolar4)

fasolar4 <- as_tibble(loadingstablesolar4) %>%
add_column("Items" = c("Solar energy is leading to displacement of people from their land",
"Solar energy increases pollution of air/water/land",
"Solar energy poses a great risk to the health of people living around it",
"Solar energy will bring jobs to the local community",
"Solar energy spoils the natural beauty of the landscape",
"I would be proud if my community used solar energy",
"Solar energy is a mark of pride for our nation",
"Solar energy pushes forward the country's development",
"Solar energy brings economic prosperity to the surrounding regions",
"I don't like the idea that I have to rely on the government for electricity from (large scale) solar energy"))%>%
dplyr::select("Items",PA1, PA2, PA3, PA4) %>%
  arrange(desc(PA1))

knitr::kable(fasolar4, digits= 2)

Varexplsolar4 <- unclass(solar4.fa$Vaccounted)

knitr::kable(Varexplsolar4, digits = 2)
```

```{r, echo=FALSE}
ROOFS<- codedmodule2 %>%
 dplyr::select("DISPLACEROOFS":"RELYROOFS")

psych::alpha(ROOFS, check.keys = TRUE)

```

```{r, echo=FALSE}
#factor analysis with 2, 4 and 6 factor spaces

roofs.fa <- fa(ROOFS, nfactors=2, scores=TRUE, rotate="varimax", fm="pa")
#print.psych(roofs.fa, cut = 0.4, sort = TRUE)
#fa.diagram(roofs.fa)

loadingsroofs <- unclass(roofs.fa$loadings)

loadingstableroofs <- cbind(loadingsroofs)

faroofs <- as_tibble(loadingstableroofs) %>%
add_column("Items" = c("Rooftop solar is leading to displacement of people from their land",
"Rooftop solar increases pollution of air/water/land", 
"Rooftop solar poses a great risk to the health of people living around it",
"Rooftop solar will bring jobs to the local community",
"Rooftop solar spoils the natural beauty of the landscape" , 
"I would be proud if my community used Rooftop solar" , 
"Rooftop solar is a mark of pride for our nation", 
"Rooftop solar pushes forward the country's development" , 
"Rooftop solar brings economic prosperity to the surrounding regions" , 
"I don't like the idea that I have to rely on the government for electricity from (large scale) Rooftop solar")) %>%
dplyr::select("Items",  PA1, PA2)%>%
  arrange(desc(PA1))

knitr::kable(faroofs, digits = 2)

Varexplroofs <- unclass(roofs.fa$Vaccounted)

knitr::kable(Varexplroofs, digits = 2)

```

### 2022-03-27 module2/WMEIndia.Rmd
new file on graphs on demographic variables

--- 2022-03-11 moduletwoanalysis.Rmd
@@
 ---
-title: "module2_eco_pol_factors"
+title: "WMEIndia"
 output:
   html_document:
-    fig_width: 7
+    fig_width: 9
     fig_height: 6
@@
 
-```{r load packages, warning = FALSE, message = FALSE}
+```{r load packages, warning = FALSE, message = FALSE, echo=FALSE}
+  knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+
 suppressPackageStartupMessages(library(tidyverse))
 suppressPackageStartupMessages(library(readxl))
-suppressPackageStartupMessages(library(hablar))
-suppressPackageStartupMessages(library(tsibble))
 suppressPackageStartupMessages(library(dplyr))
-suppressPackageStartupMessages(library(DT))
+suppressPackageStartupMessages(library(tidyr))
 suppressPackageStartupMessages(library(ggplot2))
-suppressPackageStartupMessages(library(ggbiplot))
 
@@
 
-The module2 of the survey on the perception of risk and benefit from energy technologies in India.
-
-Following is the complete data set with 1099 responses.
-
-```{r}
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
 moduletwo <- read_excel( "~/Desktop/thesis_surveydata/political_factors_complete.xlsx")
@@
 
-Following graphs show the distribution of percerived risk and benefit on the likert scale
-
-```{r}
-
-#plotting perceived risk from different technologies
-
-module2%>%
-  filter(!row_number() %in% c(1,2)) %>% 
-  select(starts_with("RISKY"))%>%
-  gather(Technology, Perceived_Risk, Risky_Hydro:Risky_INDLPG, factor_key = TRUE)%>%
-  separate(Technology, c("Risky", "Technology"), extra = "merge", fill = "left")%>%
-  select(-Risky) %>%
-  group_by(Technology, Perceived_Risk) %>%
-  dplyr::summarise(n=n())
-
-colorsequence<- c("#8C4646","#D9695F","#F2A679","#F2D091","#5D8C7B","#808080")
-df_barplot<-module2%>%
-  filter(!row_number() %in% c(1,2)) %>% 
-  select(starts_with("RISKY"))%>%
-  gather(Technology, Perceived_Risk, Risky_Hydro:Risky_INDLPG, factor_key = TRUE)%>%
-  separate(Technology, c("Risky", "Technology"), extra = "merge", fill = "left")%>%
-  select(-Risky) %>% 
-  group_by(Technology, Perceived_Risk) %>%
-  dplyr::summarise(n=n())
-
-df_barplot %>% ggplot(aes(fill= fct_rev(factor(Perceived_Risk, levels=c("Extremely risky", "Very risky","Moderately risky","Slightly risky","Not at all risky","Rather not say/Don't know"))), y=n , x=Technology)) +
-  geom_bar(position="fill",stat="identity")+
-  scale_x_discrete(limits = c("Solar", "INDSolar", "INDFirewoodetc" ,"Wind" , "Hydro", "INDWind", "INDHydro", "INDDiesel" , "INDBiogas","INDKerosene", "Oil", "Coal","Gas", "INDLPG","Nuclear"))+
-  scale_fill_manual("legend", values = c("Extremely risky" = "#8C4646", "Very risky" = "#D9695F", "Moderately risky" = "#F2A679", "Slightly risky" = "#F2D091","Not at all risky" = "#5D8C7B", "Rather not say/Don't know" = "#808080"))+
-  coord_flip()+
-  theme_classic()
-
-```
-
-```{r}
-
-colorsequence<- c("#8C4646","#D9695F","#F2A679","#F2D091","#5D8C7B","#808080")
-
-df_barplotben <- module2%>%
-  filter(!row_number() %in% c(1,2)) %>% 
-  select(starts_with("Ben"))%>%
-  gather(Technology, Perceived_Benefit, Ben_Hydro:Ben_INDKerosene, factor_key = TRUE)%>%
-  separate(Technology, c("Ben", "Technology"), extra = "merge", fill = "left")%>%
-  select(-Ben) %>% 
-  group_by(Technology, Perceived_Benefit) %>%
-  dplyr::summarise(n=n())
-
-df_barplotben %>% ggplot(aes(fill= factor(Perceived_Benefit, levels=c("Rather not say/Don't know","Not at all beneficial","Slightly beneficial","Moderately beneficial","Very beneficial", "Extremely beneficial")), y=n , x=Technology)) +
-  geom_bar(position="fill",stat="identity")+
-  scale_fill_manual("legend", values = c("Rather not say/Don't know" = "grey94" ,"Not at all beneficial" = "orange","Slightly beneficial"="yellow" ,"Moderately beneficial" = "palegreen","Very beneficial"= "green3", "Extremely beneficial"= "green4"))+
-  theme_classic()+
-  coord_flip()
-
-# fix Rather not say issue.
-
-```
-
-Now I am converting the likert scale for various scales used in the survey to numeric values from 1 to 5, Rather Not Say/Don't know is printed as NA. Some variables had to be reverse coded as well.
-
-```{r, eval =TRUE}
+```{r, eval =TRUE, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
 #This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
@@
 
-Following table shows the summary statistics of perceived risk from different energy technologies.
+```{r, eval =TRUE, echo=FALSE}
 
-```{r, eval=TRUE}
+castegendereffect <- codedmodule2 %>%
+  select(starts_with(c("Risky", "Gender", "Caste")))%>%
+  unite("Gender_Caste", c("Gender", "Caste")) %>%
+  na.omit()
 
-# summary statistics for risks from different energy sources
+castegendereffect$Gender_Caste <- as.factor(castegendereffect$Gender_Caste)
+levels(castegendereffect$Gender_Caste)
 
-risksummary <- codedmodule2 %>%
-  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
-  #add row index so later spreading indexed correctly
-  add_rownames()%>%
-  #melt to long format
-  gather(technology, value, -rowname) %>%
-  # separate risky from variable suffix
-  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
-  #separate mean from variable prefix
-  separate(var, c("technology", "summary")) %>%
-  # spread summary values back to wide form
-  spread(summary,value) %>%
-  #clean up
-  select(-rowname, -Risky) %>%
-  arrange(mean) %>%
-  setNames(paste0('perceivedrisk.', names(.))) %>%
-  dplyr::rename(technology= perceivedrisk.technology)
+castegendereffect %>%
+  mutate(Gender_Caste = factor(Gender_Caste, levels = c("Female_Brahmin", "Female_SC", "Male_Brahmin", "Male_General","Male_OBC", "Male_SC", "Male_ST", "Female_General", "Female_OBC", "Female_ST")))%>%
+  select(!starts_with(c("Risky_IND")))%>%
+  #select("Risky_Hydro", "Risky_Nuclear", "Risky_Coal","Gender_Caste")%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(riskscore = mean(c_across(Risky_Hydro:Risky_Oil))) %>%
+  select(Gender_Caste, riskscore) %>%
+  dplyr::group_by(Gender_Caste)%>%
+  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
+  arrange(desc(mean))%>%
+  ggplot(aes(y = Gender_Caste, x = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
+  geom_errorbar(aes(xmin=mean-sd, xmax=mean + sd), width=.2,
+                 position=position_dodge(.9))
+#%>%
 
-risksummary
+#group_by("Gender_Caste") %>%
+ #summarise_at(vars("Risky_Nuclear"), list(Riskscore = mean))
+    #mutate(Gender_Caste = factor(Gender_Caste, levels = c("Male_Brahmin", "Male_General","Male_OBC", "Male_SC", "Male_ST","Female_Brahmin", "Female_General", "Female_OBC","Female_SC", "Female_ST")))
 
@@
 
-Following table shows the summary statistics of perceived benefit from different energy technologies.
+```{r, echo=FALSE}
 
-```{r}
-
-# summary statistics for benefits from different energy sources
-
-benefitsummary <- codedmodule2 %>%
-  summarize_at(vars(starts_with(c("Ben"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
-  #add row index so later spreading indexed correctly
-  add_rownames()%>%
-  #melt to long format
-  gather(technology, value, -rowname) %>%
-  # separate Ben from variable suffix
-  separate(technology, c("Ben", "var"), extra = "merge", fill = "left") %>%
-  #separate mean from variable prefix
-  separate(var, c("technology", "summary")) %>%
-  # spread summary values back to wide form
-  spread(summary,value) %>%
-  #clean up
-  select(-rowname, -Ben) %>%
-  arrange(mean)%>%
-  setNames(paste0('perceivedbenefit.', names(.))) %>%
-  dplyr::rename(technology = perceivedbenefit.technology)
-benefitsummary
-
-#round off to two decimal places
-```
-
-bar plots for means of perceived risk and benefit from various energy technologies
-
-```{r}
-full_join(risksummary,benefitsummary, by = NULL, copy = FALSE, keep = FALSE) %>%
-  select(technology, perceivedrisk.mean, perceivedbenefit.mean) %>%
-  mutate(technology = fct_reorder(technology, perceivedrisk.mean, .desc = TRUE))%>%
-   gather(key = "level", value = "mean",
-       perceivedrisk.mean, perceivedbenefit.mean) %>%
-  ggplot(aes(x=technology, y= mean, fill = level, ))+
-  geom_bar(stat="identity", position=position_dodge())+
-  ylim(0,4)+
-  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
-  scale_fill_manual("legend", values = c("perceivedbenefit.mean" = "palegreen3", "perceivedrisk.mean" = "firebrick2"))
-
-```
-bar plots for median of perceived risk and benefit from various energy technologies
-
-```{r}
-
-full_join(risksummary,benefitsummary, by = NULL, copy = FALSE, keep = FALSE) %>%
-  select(technology, perceivedrisk.median, perceivedbenefit.median) %>%
-  mutate(technology = fct_reorder(technology, perceivedrisk.median, .desc = TRUE))%>%
-   gather(key = "level", value = "median",
-       perceivedrisk.median, perceivedbenefit.median) %>%
-  ggplot(aes(x=technology, y= median, fill = level, ))+
-  geom_bar(stat="identity", position=position_dodge())+
-  ylim(0,4)+
-  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
-  scale_fill_manual("legend", values = c("perceivedbenefit.median" = "palegreen3", "perceivedrisk.median" = "firebrick2"))
-
-```
-PCA on all indepdendent variables in the data set
-
-```{r}
-#PCA on all variables
-
-pcaresults <- codedmodule2 %>%
-  select(!starts_with(c("Risky","BEN", "Gender","Caste","Religion","State", "Age", "Otherreligion", "Urban_Rural","Language", "Survey_Date", "N_accept", "N_reject", "N_reluctantlyaccept")))%>%
+castegendereffect %>%
+  mutate(Gender_Caste = factor(Gender_Caste, levels = c("Female_Brahmin", "Female_SC", "Male_Brahmin", "Male_General","Male_OBC", "Male_SC", "Male_ST", "Female_General", "Female_OBC", "Female_ST")))%>%
+  select(!starts_with(c("Risky_IND")))%>%
+  select("Risky_Hydro", "Risky_Nuclear", "Risky_Coal","Gender_Caste")%>%
   na.omit()%>%
-  prcomp(center = TRUE, scale. = TRUE)
-
-summary(pcaresults)
-
-var_explained = pcaresults$sdev^2 / sum(pcaresults$sdev^2)
-
-pcaresults
-
-```
-
-Scree plot of results from PCA
-
-```{r}
-
-qplot(c(1:90), var_explained) + 
-  geom_line() + 
-  xlab("Principal Component") + 
-  ylab("Variance Explained") +
-  ggtitle("Scree Plot") +
-  ylim(0, 0.20)+
-  xlim(1,7)
-
-```
-
-Coding and Combining items on Kahan scale
-
-```{r}
- #median score for Kahan invidualism scale
-
-codedmodule2 %>%
-  select((starts_with(c("K_I", "K_S"))))%>%
-  gather(key = "K_I", value = "score")%>%
-  na.omit()%>%
-  summarise(median = median(c(score)))
-
-```
-```{r}
-
-# Kahan scale median score for Hierarchy scale
-codedmodule2 %>%
-  select((starts_with(c("K_H", "K_E"))))%>%
-  gather(key = "K_H", value = "score")%>%
-  na.omit()%>%
-  summarise(median = median(c(score)))
-```
-
-```{r}
-#calculating individualism score and hierarchy score for each respondent
-
-Kscalescores <- codedmodule2 %>%
-  select(starts_with(c("Risky","K_I","K_S", "K_H", "K_E")))%>%
-  rowwise()%>%
-  na.omit()%>%
-  dplyr::mutate(Individualism_score = mean(c_across(K_IINTRFER:K_SPROTECT)))%>%
-  dplyr::mutate(Hierarchy_score = mean(c_across(K_HEQUAL:K_ERADEQ2)))%>%
-  dplyr::select(!starts_with(c("K_I","K_S", "K_H", "K_E")))
-
-Kscalescores
+  dplyr::group_by(Gender_Caste)%>%
+  summarise(hydro_m=mean(Risky_Hydro), hydro_sd=sd(Risky_Hydro), nuclear_m=mean(Risky_Nuclear), nuclear_sd=sd(Risky_Nuclear), coal_m=mean(Risky_Coal),   coal_sd=sd(Risky_Coal))%>%
+  arrange(desc(nuclear_m))%>%
+  ggplot(aes(y = Gender_Caste, x = hydro_m))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
+  geom_errorbar(aes(xmin=hydro_m-hydro_sd, xmax=hydro_m + hydro_sd), width=.2,
+                 position=position_dodge(.9))
 
@@
 
-#scatter plot of Kahan scale scores around the median scores on Individualism and Hierarchy scales.
+codedmodule2$Urban_Rural <- as.factor(codedmodule2$Urban_Rural)
+class(codedmodule2$Urban_Rural)
+levels(codedmodule2$Urban_Rural)
 
-Kscalescores %>%
-  ggplot(aes(Individualism_score, Hierarchy_score))+
-  geom_point()+
-  geom_hline(yintercept=2, colour="black", lwd=1)+
-  geom_vline(xintercept=3, colour="black", lwd=1)
-
-```
-
-```{r}
-# checking distribution of scores on Individualism scale
-
-Kscalescores %>%
-  ggplot(aes(x=Individualism_score, y = ..count..), fill = "lightgray")+
-  geom_density()
-
-```
-
-```{r}
-# checking distribution of scores on Hierarchy scale 
-Kscalescores %>%
-  ggplot(aes(x=Hierarchy_score, y = ..count..), fill = "lightgray")+
-  geom_density()
-```
-
-Coding and combining items on the eco-political scale - characteristics of the perceiver
-
-```{r}
-ecopolscalescores <- codedmodule2 %>%
-  select(starts_with(c("Risky","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG", "Gender","Caste","Religion", "State")))%>%
+urban_rural <- codedmodule2 %>%
+  select(starts_with(c("Risky", "Urban_Rural")))%>%
+  select(!starts_with(c("Risky_IND")))%>%
+  select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","Urban_Rural")%>%
   rowwise()%>%
   na.omit()%>%
-  dplyr::mutate(Pro_decentralisation = mean(c_across("DECISIONDECEN":"DECISIONCEN")))%>%
-   dplyr::mutate(Pro_largescale = mean(c_across("INDUSTRYLARGE":"INDUSTRYSMALL")))%>%
-   dplyr::mutate(Pro_global = mean(c_across("ECONOMYGLOBAL":"ECONOMYLOCAL")))%>%
-   dplyr::mutate(Pro_ecogrowth = mean(c_across("ENVOVERDEV":"DEVOVERENV")))%>%
-   dplyr::mutate(Pro_private = mean(c_across("OWNERPVT":"OWNERREG")))%>%
-  dplyr::select(!c("DECISIONDECEN","DECISIONCEN", "INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL", "ECONOMYLOCAL","ENVOVERDEV",     "DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG"))
-
-ecopolscalescores
+  dplyr::mutate(riskscore = mean(c(Risky_Hydro))) %>%
+  select(Urban_Rural, riskscore) %>%
+  dplyr::group_by(Urban_Rural)%>%
+  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
+  arrange(desc(mean))%>%
+  ggplot(aes(x= Urban_Rural, y = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
+                 position=position_dodge(.9))
 ```
-
-PCA test on the new eco-pol scale - characteristics of the perceiver
-
-```{r}
-# PCA test on qualities of the perceiver
-
-ecopolscalepca <- ecopolscalescores %>%
-  select(!starts_with(c("Risky","Gender","Caste","Religion","State")))%>%
-  prcomp(center = TRUE,scale. = TRUE)
-
-var_explained_ecopol = ecopolscalepca$sdev^2 / sum(ecopolscalepca$sdev^2)
-
-summary(ecopolscalepca)
-
-```
-```{r}
-
-qplot(c(1:11), var_explained_ecopol) + 
-  geom_line() + 
-  xlab("Principal Component") + 
-  ylab("Variance Explained") +
-  ggtitle("Scree Plot") +
-  ylim(0.05, 0.20)+
-  xlim(1,7)
-
-```

### 2022-03-27 module2/module2graphsandPCA.Rmd
new file on graphs on demographic variables

@@
 ---
-title: "module2graphsandPCA"
+title: "Survey 2 : Dependent Variable Graphs"
 output:
@@
     fig_caption: yes
-    df_print: 
 ---
@@
 
-#%>%gather(key = "riskben", value = "sd", perceivedrisk.sd, perceivedbenefit.sd)
-
 center_barplot$level <- as.factor(center_barplot$level)

### 2022-03-31 module2/WMEIndia.Rmd
using here package for excel files

@@
 knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-moduletwo <- read_excel( "~/Desktop/thesis_surveydata/political_factors_complete.xlsx")
+moduletwo <- read_excel(here::here("thesis_surveydata/political_factors_complete.xlsx"))
 save(moduletwo, file = "moduletwo.rda")
@@
 castegendereffect %>%
-  mutate(Gender_Caste = factor(Gender_Caste, levels = c("Female_Brahmin", "Female_SC", "Male_Brahmin", "Male_General","Male_OBC", "Male_SC", "Male_ST", "Female_General", "Female_OBC", "Female_ST")))%>%
+  mutate(Gender_Caste = factor(Gender_Caste, levels = c("Female_Brahmin","Male_General", "Male_OBC", "Female_SC","Male_ST", "Male_SC","Female_ST", "Female_General", "Female_OBC","Male_Brahmin")))%>%
   select(!starts_with(c("Risky_IND")))%>%

### 2022-03-31 module2/module2DVgraphs.Rmd
using here package for excel files

--- 2022-03-27 module2/module2graphsandPCA.Rmd
@@
 knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-moduletwo <- read_excel( "~/Desktop/thesis_surveydata/political_factors_complete.xlsx")
+moduletwo <- read_excel(here::here("thesis_surveydata/political_factors_complete.xlsx"))
 save(moduletwo, file = "moduletwo.rda")
+
 module2 <- data.frame(moduletwo)

### 2022-03-31 module2/moduletwoanalysis.Rmd
using here package for excel files

--- 2022-03-11 moduletwoanalysis.Rmd
@@
     fig_caption: yes
-    keep_md: yes
     theme: paper
-    df_print: paged
+    df_print: kable
 

### 2022-04-05 module1/moduleoneanalysis.Rmd
coded some LSI and ISI variables

@@
 suppressPackageStartupMessages(library(readxl))
-suppressPackageStartupMessages(library(hablar))
-suppressPackageStartupMessages(library(tsibble))
 suppressPackageStartupMessages(library(dplyr))
-suppressPackageStartupMessages(library(DT))
-suppressPackageStartupMessages(library(ggplot2))
 
@@
 
-moduleone <- read_excel( "~/Desktop/thesis_surveydata/livelihood_insecurity_complete.xlsx")
+moduleone <- read_excel(here::here("thesis_surveydata/livelihood_insecurity_complete.xlsx"))
 save(moduleone, file = "moduleone.rda")
@@
 
+# coding education
    mutate_at(vars(education), funs(case_when(. == "No schooling completed" ~ 0, 
@@
                                                                         . == "Doctorate degree" ~ 9 ))) %>%
+# coding yes and no questions
+  mutate_at(vars(Iassociation, govtscheme, wateravail, polposition, polparty), funs(case_when(.== "Yes" ~ 1,
+                                            .== "No" ~ 0))) %>%
+# reverse coding yes and no questions
+  mutate_at(vars(illness,severeillness), funs(case_when(.== "Yes" ~ 0,
+                                            .== "No" ~ 1))) %>%
+
+# coding How confident are you that you can continue your current livelihood if you want to? 
+ mutate_at(vars(Lconfidence), funs(case_when(. == "Not at all confident" ~ 1, 
+                                                                        . == "Not much confident" ~ 2,
+                                                                        . == "Neutral" ~3,
+                                                                        . == "Somewhat confident" ~ 4,
+                                                                        . == "Very confident" ~ 5))) %>%
+
+ mutate_at(vars(Lboat, houseown), funs(case_when(.== "Own it" ~ 1,
+                                                 .== "Rent it" ~ 0)))%>%
+
+# J security index coding
+
+ mutate_at(vars(JISRkeep), funs(case_when(. == "Strongly disagree" ~ 1, 
+                                                                        . == "Somewhat disagree" ~ 2,
+                                                                        . == "Neither agree nor disagree" ~3,
+                                                                        . == "Somewhat agree" ~ 4,
+                                                                        . == "Strongly agree" ~ 5))) %>%
+
+# reverse code JIS 
+  mutate_at(vars(JISlosefuture, JISlose, JISfuture), funs(case_when(. == "Strongly disagree" ~ 5, 
+                                                                        . == "Somewhat disagree" ~ 4,
+                                                                        . == "Neither agree nor disagree" ~3,
+                                                                        . == "Somewhat agree" ~ 2,
+                                                                        . == "Strongly agree" ~ 1))) %>%
+
+  mutate_at(vars(totalincome, otherincome), funs(case_when(. == "Less than Rs 1,00,000" ~ 1,
+                                                                        . == "Rs 1,00,000 to Rs 2,50,000"  ~ 2,
+                                                                        . == "Rs 2,50,001 to Rs 5,00,000" ~ 3,
+                                                                        . == "Rs 5,00,001 to Rs 10,00,000" ~ 4,
+                                                                        . == "Rs 10,00,001 and above"  ~ 5))) %>%
+
+  mutate_at(vars(workknowledge, subsidyknow), funs(case_when(. == "Very poor" ~ 1, 
+                                                                        . == "Poor" ~ 2,
+                                                                        . == "Fair" ~3,
+                                                                        . == "Good" ~ 4,
+                                                                        . == "Very good" ~ 5))) %>%
+
+mutate_at(vars(drinkingwater, cookingwater), funs(case_when(. == "Bottled water/ Filtered Water" ~ 1,                                       
+                                                          .  == "Piped into dwelling" ~ 2,                                                  
+                                                          .  == "Piped to neighbour" ~ 3,                                                   
+                                                          .  == "Piped to yard/plot" ~ 4, 
+                                                          .  == "Protected well" ~ 5, 
+                                                          .  == "Public tap/standpipe" ~6,
+                                                          .  == "Surface Water  (River/Dam/Lake/Pond/Stream/Canal/Irrigation Channel)" ~7, 
+                                                          .  == "Tanker Truck" ~ 8,
+                                                          .  == "Tubewell/borehole" ~ 9,
+                                                          .  == "Unprotected Spring" ~ 10))) %>%
+
+  mutate_at(vars(toilet), funs(case_when(. == "No facility/bush/field" ~ 1,                                       
+                                                          .  == "Hanging toilet/hanging latrine" ~ 2,                                             
+                                                          .  == "Bucket toilet"  ~ 3,                                                   
+                                                          .  == "Composting toilet"  ~ 4, 
+                                                          .  == "Pit latrine without slab/open pit" ~ 5, 
+                                                          .  == "Pit latrine with slab" ~6,
+                                                          .  == "Ventilated improved pit laterine"  ~7, 
+                                                          .  == "Flush to somewhere else"  ~ 8,
+                                                          .  == "Flush to pit latrine"  ~ 9,
+                                                          .  == "Flush to septic tank" ~ 10,
+                                                          .  == "Flush to piped sewer system" ~ 11))) %>%
+
+  mutate_at(vars(house), funs(case_when(. == "Hut made of mud, bamboo, straw etc. (kutcha house)" ~ 1, 
+                                        . == "Permanent single story house (pukka house)" ~ 2,
+                                        . == "Apartment/Flat in a multi-story building"  ~3,
+                                        . == "Multi-story house" ~ 4)))
+
+#coded dependent variables for module 1 livelihood and income security survey
 
 codedmodule1
-#coded dependent variables for module 1 livelihood and income security survey
-
 ```
@@
 ```{r}
-# normalize quantitative livelihood-income security variables
+# combining quantitative livelihood-income security variables
+
+# Livelihood security
+
+x <- as.factor(codedmodule1$cookstove)
+
+levels(x)
 

### 2022-04-08 module1/moduleoneanalysis.Rmd
demographic graphs in WME

@@
                                         . == "Apartment/Flat in a multi-story building"  ~3,
-                                        . == "Multi-story house" ~ 4)))
+                                        . == "Multi-story house" ~ 4))) %>%
+
+  mutate_at(vars(foodtrouble), funs(case_when(. == "8 or more months" ~ 1,                                       
+                                                          .  == "6-8 months"  ~ 2,                                                  
+                                                          .  == "4-6 months"  ~ 3,                                                   
+                                                          .  == "2-4 months"  ~ 4, 
+                                                          .  == "1-2 months" ~ 5, 
+                                                          .  == "0 months"  ~6))) %>%
+
+   mutate_at(vars(foodadequacy), funs(case_when(. == "Extremely inadequate" ~ 1, 
+                                                                        . == "Moderately inadequate" ~ 2,
+                                                                        . == "Slightly inadequate" ~3,
+                                                                        . == "Neither adequate nor inadequate" ~ 4,
+                                                                        . == "Slightly adequate" ~ 5,
+                                                                        . == "Moderately adequate" ~ 6,
+                                                                        . == "Extremely adequate" ~ 7)))%>%
+
+separate( col = cookstove, into = c("cook1", "cook2", "cook3", "cook4"), sep = ",") %>%
+separate( col = vehicle, into = c("vehicle1", "vehicle2", "vehicle3", "vehicle4"), sep = ",")%>%
+separate( col = foodsource, into = c("food1", "food2", "food3", "food4"), sep = ",")
 
@@
 ```{r}
-# combining quantitative livelihood-income security variables
+# solving the problem of multiple answers  to a questions 
+codedmodule1
 
-# Livelihood security
+```
 
-x <- as.factor(codedmodule1$cookstove)
+```{r}
+
+x <- as.factor(codedmodule1$vehicle)
 
@@
 ```
+
+```{r}
+
+```
+
+```{r}
+
+```

### 2022-04-08 module2/moduletwoanalysis.Rmd
demographic graphs in WME

@@
 suppressPackageStartupMessages(library(ggbiplot))
+suppressPackageStartupMessages(library(readr))
 
@@
 codedmodule2
+
+write_csv(codedmodule2,"Macintosh HD\\Users\\prernagupta\\my documents\\codedmodule2.csv")
 ```

### 2022-04-08 module2/WMEIndia.Rmd
more graphs with demographic variables

@@
 moduletwo <- read_excel(here::here("thesis_surveydata/political_factors_complete.xlsx"))
-save(moduletwo, file = "moduletwo.rda")
 module2 <- data.frame(moduletwo)
@@
 codedmodule2
+
+```
+
+```{r, eval=TRUE}
+
+moduleone <- read_excel(here::here("thesis_surveydata/livelihood_insecurity_complete.xlsx"))
+save(moduleone, file = "moduleone.rda")
+module1 <- data.frame(moduleone)
+module1 %>%
+  filter(!row_number() %in% c(1,2))
+
+# loaded data set for module 2 eco -pol variables and removes the rows with question number and question text
+```
+
+```{r, eval =TRUE}
+#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
+codedmodule1 <- module1 %>%
+
+#remove row 1
+  filter(!row_number() %in% c(1,2)) %>%
+
+# replace risky likert scale with numbers
+  mutate_at(vars(starts_with("Risky")), funs(case_when(. =="Not at all risky" ~ 1, 
+                                                       . =="Slightly risky" ~ 2, 
+                                                       . =="Moderately risky" ~ 3, 
+                                                       . =="Very risky" ~ 4, 
+                                                       . =="Extremely risky" ~ 5))) %>%
+
+# replace beneficial likert scale with numbers  
+  mutate_at(vars(starts_with("Ben")), funs(case_when(. =="Not at all beneficial" ~ 1,
+                                                     . =="Slightly beneficial" ~ 2,
+                                                     . =="Moderately beneficial" ~ 3,
+                                                     . =="Very beneficial" ~ 4,
+                                                     . =="Extremely beneficial" ~ 5 ))) %>%
+
+# replace nuclear acceptance likert scale with numbers
+  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
+                                                                        . == "Somewhat disagree" ~ 2,
+                                                                        . == "Neither agree nor disagree" ~3,
+                                                                        . == "Somewhat agree" ~ 4,
+                                                                        . == "Strongly agree" ~ 5))) %>%
+
+  mutate_at(vars(Livelihood_Income), funs(case_when(. == "(a) own farming/fishing/animal rearing/business" ~ "LSI", 
+                                                    . == "(b) employed for wages/salary" ~ "ISI",
+                                                    . == "(c) student" ~"student",
+                                                    . == "(d) currently unemployed" ~ "unemployed",
+                                                    . == "(e) homemaker" ~ "homemaker",
+                                                    . == "(f) retired" ~ "retired",
+                                                    . == "(g) unable to work" ~ "unable to work" ))) %>%
+
+# coding education
+   mutate_at(vars(education), funs(case_when(. == "No schooling completed" ~ 0, 
+                                                                        . == "Primary school" ~ 1,
+                                                                        . == "Grade 10th" ~ 2,
+                                                                        . == "Grade 12th" ~ 3,
+                                                                        . == "Some college, no degree" ~ 4,
+                                                                        . == "Trade/technical/vocational training" ~ 5,
+                                                                        . == "Bachelor's degree" ~ 6,
+                                                                        . == "Master's degree" ~ 7,
+                                                                        . == "Professional degree" ~ 8,
+                                                                        . == "Doctorate degree" ~ 9 ))) %>%
+# coding yes and no questions
+  mutate_at(vars(Iassociation, govtscheme, wateravail, polposition, polparty), funs(case_when(.== "Yes" ~ 1,
+                                            .== "No" ~ 0))) %>%
+# reverse coding yes and no questions
+  mutate_at(vars(illness,severeillness), funs(case_when(.== "Yes" ~ 0,
+                                            .== "No" ~ 1))) %>%
+
+# coding How confident are you that you can continue your current livelihood if you want to? 
+ mutate_at(vars(Lconfidence), funs(case_when(. == "Not at all confident" ~ 1, 
+                                                                        . == "Not much confident" ~ 2,
+                                                                        . == "Neutral" ~3,
+                                                                        . == "Somewhat confident" ~ 4,
+                                                                        . == "Very confident" ~ 5))) %>%
+
+ mutate_at(vars(Lboat, houseown), funs(case_when(.== "Own it" ~ 1,
+                                                 .== "Rent it" ~ 0)))%>%
+
+# J security index coding
+
+ mutate_at(vars(JISRkeep), funs(case_when(. == "Strongly disagree" ~ 1, 
+                                                                        . == "Somewhat disagree" ~ 2,
+                                                                        . == "Neither agree nor disagree" ~3,
+                                                                        . == "Somewhat agree" ~ 4,
+                                                                        . == "Strongly agree" ~ 5))) %>%
+
+# reverse code JIS 
+  mutate_at(vars(JISlosefuture, JISlose, JISfuture), funs(case_when(. == "Strongly disagree" ~ 5, 
+                                                                        . == "Somewhat disagree" ~ 4,
+                                                                        . == "Neither agree nor disagree" ~3,
+                                                                        . == "Somewhat agree" ~ 2,
+                                                                        . == "Strongly agree" ~ 1))) %>%
+
+  mutate_at(vars(totalincome, otherincome), funs(case_when(. == "Less than Rs 1,00,000" ~ 1,
+                                                                        . == "Rs 1,00,000 to Rs 2,50,000"  ~ 2,
+                                                                        . == "Rs 2,50,001 to Rs 5,00,000" ~ 3,
+                                                                        . == "Rs 5,00,001 to Rs 10,00,000" ~ 4,
+                                                                        . == "Rs 10,00,001 and above"  ~ 5))) %>%
+
+  mutate_at(vars(workknowledge, subsidyknow), funs(case_when(. == "Very poor" ~ 1, 
+                                                                        . == "Poor" ~ 2,
+                                                                        . == "Fair" ~3,
+                                                                        . == "Good" ~ 4,
+                                                                        . == "Very good" ~ 5))) %>%
+
+mutate_at(vars(drinkingwater, cookingwater), funs(case_when(. == "Bottled water/ Filtered Water" ~ 1,                                       
+                                                          .  == "Piped into dwelling" ~ 2,                                                  
+                                                          .  == "Piped to neighbour" ~ 3,                                                   
+                                                          .  == "Piped to yard/plot" ~ 4, 
+                                                          .  == "Protected well" ~ 5, 
+                                                          .  == "Public tap/standpipe" ~6,
+                                                          .  == "Surface Water  (River/Dam/Lake/Pond/Stream/Canal/Irrigation Channel)" ~7, 
+                                                          .  == "Tanker Truck" ~ 8,
+                                                          .  == "Tubewell/borehole" ~ 9,
+                                                          .  == "Unprotected Spring" ~ 10))) %>%
+
+  mutate_at(vars(toilet), funs(case_when(. == "No facility/bush/field" ~ 1,                                       
+                                                          .  == "Hanging toilet/hanging latrine" ~ 2,                                             
+                                                          .  == "Bucket toilet"  ~ 3,                                                   
+                                                          .  == "Composting toilet"  ~ 4, 
+                                                          .  == "Pit latrine without slab/open pit" ~ 5, 
+                                                          .  == "Pit latrine with slab" ~6,
+                                                          .  == "Ventilated improved pit laterine"  ~7, 
+                                                          .  == "Flush to somewhere else"  ~ 8,
+                                                          .  == "Flush to pit latrine"  ~ 9,
+                                                          .  == "Flush to septic tank" ~ 10,
+                                                          .  == "Flush to piped sewer system" ~ 11))) %>%
+
+  mutate_at(vars(house), funs(case_when(. == "Hut made of mud, bamboo, straw etc. (kutcha house)" ~ 1, 
+                                        . == "Permanent single story house (pukka house)" ~ 2,
+                                        . == "Apartment/Flat in a multi-story building"  ~3,
+                                        . == "Multi-story house" ~ 4))) %>%
+
+  mutate_at(vars(foodtrouble), funs(case_when(. == "8 or more months" ~ 1,                                       
+                                                          .  == "6-8 months"  ~ 2,                                                  
+                                                          .  == "4-6 months"  ~ 3,                                                   
+                                                          .  == "2-4 months"  ~ 4, 
+                                                          .  == "1-2 months" ~ 5, 
+                                                          .  == "0 months"  ~6))) %>%
+
+   mutate_at(vars(foodadequacy), funs(case_when(. == "Extremely inadequate" ~ 1, 
+                                                                        . == "Moderately inadequate" ~ 2,
+                                                                        . == "Slightly inadequate" ~3,
+                                                                        . == "Neither adequate nor inadequate" ~ 4,
+                                                                        . == "Slightly adequate" ~ 5,
+                                                                        . == "Moderately adequate" ~ 6,
+                                                                        . == "Extremely adequate" ~ 7)))%>%
+
+separate( col = cookstove, into = c("cook1", "cook2", "cook3", "cook4"), sep = ",") %>%
+separate( col = vehicle, into = c("vehicle1", "vehicle2", "vehicle3", "vehicle4"), sep = ",")%>%
+separate( col = foodsource, into = c("food1", "food2", "food3", "food4"), sep = ",")
+
+#coded dependent variables for module 1 livelihood and income security survey
+
+codedmodule1 
+```
+
+```{r}
+
+suppressPackageStartupMessages(library(tidyselect))
+# combine codedmodule1 and codedmodule2
+
+numcol2 <- codedmodule2 %>% add_column(Respondent = 1:1099, .before = "Language") 
+numcol1 <- codedmodule1 %>% add_column(Respondent = 1099:2160, .before = "Language")
+
+joineddf <-  full_join(numcol2, numcol1, by = c("Respondent", "Language", "Survey_Date", "State", "Risky_Hydro", "Risky_Solar", "Risky_Wind", "Risky_Nuclear", "Risky_Coal", "Risky_Gas", "Risky_Oil", "Risky_INDHydro", "Risky_INDSolar", "Risky_INDWind", "Risky_INDBiogas", "Risky_INDDiesel", "Risky_INDKerosene", "Risky_INDFirewoodetc", "Risky_INDLPG", "Ben_Hydro", "Ben_Solar", "Ben_Wind", "Ben_Nuclear", "Ben_Coal", "Ben_Gas", "Ben_Oil", "Ben_INDHydro", "Ben_INDSolar", "Ben_INDWind", "Ben_INDDiesel", "Ben_INDBiogas", "Ben_INDFirewoodetc", "Ben_INDLPG", "Ben_INDKerosene", "N_accept", "N_reluctantlyaccept", "N_reject", "age", "urban_rural", "gender", "caste", "religion", "religiontext"))
+
+joineddf
 ```
@@
 
-castegendereffect <- codedmodule2 %>%
-  select(starts_with(c("Risky", "Gender", "Caste")))%>%
-  unite("Gender_Caste", c("Gender", "Caste")) %>%
+castegendereffect <- joineddf %>%
+  select(starts_with(c("Risky", "gender", "caste")))%>%
+  unite("Gender_Caste", c("gender", "caste")) %>%
   na.omit()
@@
 
+ # mean risk from centrally controlled energy technologies
+
 castegendereffect %>%
-  mutate(Gender_Caste = factor(Gender_Caste, levels = c("Female_Brahmin", "Female_SC", "Male_Brahmin", "Male_General","Male_OBC", "Male_SC", "Male_ST", "Female_General", "Female_OBC", "Female_ST")))%>%
+  mutate(Gender_Caste = factor(Gender_Caste, levels = c("Female_Brahmin", "Female_SC", "Female_OBC", "Male_SC","Male_ST", "Male_General", "Female_General","Female_ST" ,"Male_OBC", "Male_Brahmin")))%>%
   select(!starts_with(c("Risky_IND")))%>%
@@
 
+```{r, eval =TRUE, echo=FALSE}
+
+ # mean risk from indicidually or community owned energy technologies
+
+castegendereffect %>%
+  mutate(Gender_Caste = factor(Gender_Caste, levels = c("Female_OBC","Female_SC", "Female_ST" ,"Female_Brahmin", "Male_ST",  "Male_SC","Female_General", "Male_General", "Male_OBC", "Male_Brahmin")))%>%
+  select(starts_with(c("Risky_IND", "Gender_Caste")))%>%
+  #select("Risky_Hydro", "Risky_Nuclear", "Risky_Coal","Gender_Caste")%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(riskscore = mean(c_across(Risky_INDHydro:Risky_INDLPG))) %>%
+  select(Gender_Caste, riskscore) %>%
+  dplyr::group_by(Gender_Caste)%>%
+  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
+  arrange(desc(mean))%>%
+  ggplot(aes(y = Gender_Caste, x = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
+  geom_errorbar(aes(xmin=mean-sd, xmax=mean + sd), width=.2,
+                 position=position_dodge(.9))
+
+#%>%
+
+#group_by("Gender_Caste") %>%
+ #summarise_at(vars("Risky_Nuclear"), list(Riskscore = mean))
+    #mutate(Gender_Caste = factor(Gender_Caste, levels = c("Male_Brahmin", "Male_General","Male_OBC", "Male_SC", "Male_ST","Female_Brahmin", "Female_General", "Female_OBC","Female_SC", "Female_ST")))
+
+```
+
 ```{r, echo=FALSE}
@@
   summarise(hydro_m=mean(Risky_Hydro), hydro_sd=sd(Risky_Hydro), nuclear_m=mean(Risky_Nuclear), nuclear_sd=sd(Risky_Nuclear),            coal_m=mean(Risky_Coal),   coal_sd=sd(Risky_Coal))%>%
-  arrange(desc(nuclear_m))%>%
+  arrange(desc(hydro_m))%>%
   ggplot(aes(y = Gender_Caste, x = hydro_m))+
@@
                  position=position_dodge(.9))
+```
 
+# centrally managed by urban and rural
+
+```{r}
+
+joineddf$urban_rural <- as.factor(joineddf$urban_rural)
+class(joineddf$urban_rural)
+levels(joineddf$urban_rural)
+
+joineddf %>%
+  select(starts_with(c("Risky", "urban_rural")))%>%
+  select(!starts_with(c("Risky_IND")))%>%
+  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(riskscore = mean(c_across(Risky_Hydro:Risky_Oil))) %>%
+  select(urban_rural, riskscore) %>%
+  dplyr::group_by(urban_rural)%>%
+  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
+  arrange(desc(mean))%>%
+  ggplot(aes(x= urban_rural, y = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
+                 position=position_dodge(.9))
 ```
@@
 
-codedmodule2$Urban_Rural <- as.factor(codedmodule2$Urban_Rural)
-class(codedmodule2$Urban_Rural)
-levels(codedmodule2$Urban_Rural)
+joineddf$gender <- as.factor(joineddf$gender)
+class(joineddf$gender)
+levels(joineddf$gender)
 
-urban_rural <- codedmodule2 %>%
-  select(starts_with(c("Risky", "Urban_Rural")))%>%
+joineddf %>%
+  select(starts_with(c("Risky", "gender")))%>%
   select(!starts_with(c("Risky_IND")))%>%
-  select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","Urban_Rural")%>%
+  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
   rowwise()%>%
   na.omit()%>%
-  dplyr::mutate(riskscore = mean(c(Risky_Hydro))) %>%
-  select(Urban_Rural, riskscore) %>%
-  dplyr::group_by(Urban_Rural)%>%
+  dplyr::mutate(riskscore = mean(c_across(Risky_Hydro:Risky_Oil))) %>%
+  select(gender, riskscore) %>%
+  dplyr::group_by(gender)%>%
   summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
   arrange(desc(mean))%>%
-  ggplot(aes(x= Urban_Rural, y = mean))+
+  ggplot(aes(x= gender, y = mean))+
   geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
@@
 ```
+
+```{r, echo=FALSE}
+
+joineddf$gender <- as.factor(joineddf$gender)
+class(joineddf$gender)
+levels(joineddf$gender)
+
+joineddf %>%
+  select(starts_with(c("Risky", "gender")))%>%
+  select(starts_with(c("Risky_IND", "gender")))%>%
+  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(riskscore = mean(c_across(Risky_INDHydro:Risky_INDLPG))) %>%
+  select(gender, riskscore) %>%
+  dplyr::group_by(gender)%>%
+  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
+  arrange(desc(mean))%>%
+  ggplot(aes(x= gender, y = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
+                 position=position_dodge(.9))
+```
+
+```{r, echo=FALSE}
+
+joineddf$religion <- as.factor(joineddf$religion)
+class(joineddf$religion)
+levels(joineddf$religion)
+
+joineddf %>%
+  select(starts_with(c("Risky", "religion")))%>%
+  select(!starts_with(c("Risky_IND", "religiontext")))%>%
+ mutate(religion = factor(religion, levels = c("Agnostism/ Atheism","Other (Please mention)" ,  "Jainism", "Buddhism", "Islam",              "Hinduism", "Christanity", "Sikhism"))) %>%
+  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(riskscore = mean(c_across(Risky_Hydro:Risky_Oil))) %>%
+  select(religion, riskscore) %>%
+  dplyr::group_by(religion)%>%
+  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
+  arrange(desc(mean))%>%
+  ggplot(aes(x= religion, y = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  coord_flip()
+```
+
+```{r, echo=FALSE}
+
+joineddf$religion <- as.factor(joineddf$religion)
+class(joineddf$religion)
+levels(joineddf$religion)
+
+joineddf %>%
+  select(!starts_with(c("religiontext")))%>%
+  select(starts_with(c("Risky_IND", "religion")))%>%
+ mutate(religion = factor(religion, levels = c("Agnostism/ Atheism", "Jainism","Other (Please mention)" ,  "Buddhism", "Islam",              "Hinduism", "Christanity", "Sikhism"))) %>%
+  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(riskscore = mean(c_across(Risky_INDHydro:Risky_INDLPG))) %>%
+  select(religion, riskscore) %>%
+  dplyr::group_by(religion)%>%
+  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
+  arrange(desc(mean))%>%
+  ggplot(aes(x= religion, y = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  coord_flip()
+```
+
+```{r, echo=FALSE}
+
+joineddf$age <- as.factor(joineddf$age)
+class(joineddf$age)
+levels(joineddf$age)
+
+joineddf %>%
+  select(starts_with(c("Risky", "age")))%>%
+  select(!starts_with(c("Risky_IND")))%>%
+ mutate(age = factor(age, levels = c("18-24 years old", "25-34 years old", "35-44 years old", "45-54 years old" , "55-64 years old" ,  "65-74 years old", "75 years or older"))) %>%
+  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(riskscore = mean(c_across(Risky_Hydro:Risky_Oil))) %>%
+  select(age, riskscore) %>%
+  dplyr::group_by(age)%>%
+  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
+  arrange(desc(mean))%>%
+  ggplot(aes(x= age, y = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  coord_flip()
+```
+
+```{r, echo=FALSE}
+
+joineddf$age <- as.factor(joineddf$age)
+class(joineddf$age)
+levels(joineddf$age)
+
+joineddf %>%
+  select(starts_with(c("Risky", "age")))%>%
+  select(starts_with(c("Risky_IND", "age")))%>%
+ mutate(age = factor(age, levels = c("18-24 years old", "25-34 years old", "35-44 years old", "45-54 years old" , "55-64 years old" ,  "65-74 years old", "75 years or older"))) %>%
+  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(riskscore = mean(c_across(Risky_INDHydro:Risky_INDLPG))) %>%
+  select(age, riskscore) %>%
+  dplyr::group_by(age)%>%
+  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
+  arrange(desc(mean))%>%
+  ggplot(aes(x= age, y = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  coord_flip()
+```
+
+```{r, echo=FALSE}
+
+joineddf$State <- as.factor(joineddf$State)
+class(joineddf$State)
+levels(joineddf$State)
+
+joineddf %>%
+  select(starts_with(c("Risky", "State")))%>%
+  select(!starts_with(c("Risky_IND")))%>%
+ mutate(State = factor(State, levels = c("Maharashtra",  "West Bengal","UP" , "Rajasthan" , "Tamilnadu"))) %>%
+  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(riskscore = mean(c(Risky_Hydro:Risky_Oil))) %>%
+  select(State, riskscore) %>%
+  dplyr::group_by(State)%>%
+  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
+  arrange(desc(mean))
+
+%>%
+  ggplot(aes(x= technology, y = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  coord_flip()
+```
+
+#Distribution checks
+
+```{r}
+joineddf %>%
+  filter(urban_rural == "Rural") %>%
+  ggplot(aes(x=Risky_Hydro, y = ..count..), fill = "lightgray")+
+  geom_density()
+```

### 2022-04-09 module2/WMEIndia.Rmd
state wise mean risk graphs

@@
 
+```{r, echo=FALSE}
+cenrisksummary <- joineddf %>%
+  group_by(State)%>%
+  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
+  #melt to long format
+  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd) %>%
+  select(State, technology, summary) %>%
+  # separate risky from variable suffix
+  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
+  #separate mean from variable prefix
+  separate(var, c("technology", "meansd")) %>%
+  # spread summary values back to wide form
+  spread(meansd,summary) %>%
+  #clean up
+  select(-Risky)%>%
+  arrange(mean) #%>%
+  #setNames(paste0('perceivedrisk.', names(.))) %>%
+  #dplyr::rename(technology= perceivedrisk.technology)
+
+cenrisksummary
+```
+
 ```{r, eval =TRUE, echo=FALSE}
@@
 
-joineddf %>%
-  select(starts_with(c("Risky", "State")))%>%
-  select(!starts_with(c("Risky_IND")))%>%
- mutate(State = factor(State, levels = c("Maharashtra",  "West Bengal","UP" , "Rajasthan" , "Tamilnadu"))) %>%
-  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
-  rowwise()%>%
-  na.omit()%>%
-  dplyr::mutate(riskscore = mean(c(Risky_Hydro:Risky_Oil))) %>%
-  select(State, riskscore) %>%
-  dplyr::group_by(State)%>%
-  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
-  arrange(desc(mean))
-
-%>%
-  ggplot(aes(x= technology, y = mean))+
-  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
+cenrisksummary %>%
+  mutate(technology = fct_reorder(technology, mean, .desc = TRUE))%>%
+  ggplot(aes(x= technology, y= mean))+
+  geom_bar(stat="identity", position=position_dodge())+
   geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
                  position=position_dodge(.9))+
+  ylim(0,5)+
+  facet_wrap(~ State)+
+  #scale_fill_manual(y, values =))+
   coord_flip()
+
 ```

### 2022-04-09 module2/module2IVgraphs.Rmd
governance preference graphs

---
title: "module2IVgraphs"
output: 
html_document:
    fig_width: 9
    fig_height: 6
    fig_caption: yes
    keep_md: yes
    theme: paper
    df_print: paged

pdf_document:

    toc: true
    number_sections: true
    toc_depth: 2
    fig_width: 9
    fig_height: 6
    fig_caption: yes
---

```{r load packages, warning = FALSE, message = FALSE, echo=FALSE}
  knitr::opts_chunk$set(warning = FALSE, message = FALSE)

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(hablar))
suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(DT))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(ggbiplot))
suppressPackageStartupMessages(library(psych)) # psychometrics

```

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
moduletwo <- read_excel(here::here("thesis_surveydata/political_factors_complete.xlsx"))
save(moduletwo, file = "moduletwo.rda")
module2 <- data.frame(moduletwo)
module2[module2 == "Rather not say/ Don't know"] <- "Rather not say/Don't know"
module2 %>%
  filter(!row_number() %in% c(1,2))

# loaded data set for module 2 eco -pol variables and removes the rows with question number and question text
```

```{r, echo = FALSE}

#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
codedmodule2 <- module2 %>%

#remove row 1
  filter(!row_number() %in% c(1,2)) %>%

# replace risky likert scale with numbers
  mutate_at(vars(starts_with("Risky")), funs(case_when(. =="Not at all risky" ~ 1, 
                                                       . =="Slightly risky" ~ 2, 
                                                       . =="Moderately risky" ~ 3, 
                                                       . =="Very risky" ~ 4, 
                                                       . =="Extremely risky" ~ 5))) %>%

# replace beneficial likert scale with numbers  
  mutate_at(vars(starts_with("Ben")), funs(case_when(. =="Not at all beneficial" ~ 1,
                                                     . =="Slightly beneficial" ~ 2,
                                                     . =="Moderately beneficial" ~ 3,
                                                     . =="Very beneficial" ~ 4,
                                                     . =="Extremely beneficial" ~ 5 ))) %>%

# replace nuclear acceptance likert scale with numbers
  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                                        . == "Somewhat disagree" ~ 2,
                                                                        . == "Neither agree nor disagree" ~3,
                                                                        . == "Somewhat agree" ~ 4,
                                                                        . == "Strongly agree" ~ 5))) %>%

# code likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_I","K_H","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE", "DEV", "PROSPER", "RELY"))), funs(case_when(. == "Strongly disagree" ~ 1, 
               . == "Somewhat disagree" ~ 2,
               . == "Neither agree nor disagree" ~3,
               . == "Somewhat agree" ~ 4,
               . == "Strongly agree" ~ 5))) %>%

# reverse code for likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_S","K_E"))), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                               . == "Somewhat disagree" ~ 4,
                                                               . == "Neither agree nor disagree" ~3,
                                                               . == "Somewhat agree" ~ 2,
                                                               . == "Strongly agree" ~ 1))) %>%

# code eco-pol scale variables into numbers
  mutate_at(vars(SYSTEMDEMO,SYSTEMRELIGION,SYSTEMTECHNO,SYSTEMTOTAL,WEALTHLIM,MECHANISATION,DECISIONDECEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG), funs(case_when(. == "Strongly disagree" ~ 1, 
                        . == "Somewhat disagree" ~ 2,
                        . == "Neither agree nor disagree" ~3,
                        . == "Somewhat agree" ~ 4,
                        . == "Strongly agree" ~ 5))) %>%

# reverse code eco-pol scale variables into numbers 
 mutate_at(vars(DECISIONCEN, INDUSTRYSMALL, ECONOMYLOCAL, ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                                                                         . == "Somewhat disagree" ~ 4,
                                                                                                         . == "Neither agree nor disagree" ~3,
                                                                                                         . == "Somewhat agree" ~ 2,
                                                                                                         . == "Strongly agree" ~ 1)))

codedmodule2

```

```{r}
demorisk <- codedmodule2%>%
  group_by(SYSTEMDEMO)%>%
  filter(SYSTEMDEMO == 5)%>%
  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #melt to long format
  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd) %>%
  select(SYSTEMDEMO, technology, summary) %>%
  # separate risky from variable suffix
  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "meansd")) %>%
  # spread summary values back to wide form
  spread(meansd,summary) %>%
  #clean up
  select(-Risky)%>%
  arrange(mean)
```

```{r, echo=FALSE}
techrisk <- codedmodule2%>%
  group_by(SYSTEMTECHNO)%>%
  filter(SYSTEMTECHNO == 5)%>%
  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #melt to long format
  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd) %>%
  select(SYSTEMTECHNO, technology, summary) %>%
  # separate risky from variable suffix
  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "meansd")) %>%
  # spread summary values back to wide form
  spread(meansd,summary) %>%
  #clean up
  select(-Risky)%>%
  arrange(mean)
```

```{r, echo=FALSE}
religionrisk <- codedmodule2%>%
  group_by(SYSTEMRELIGION)%>%
  filter(SYSTEMRELIGION == 5)%>%
  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #melt to long format
  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd) %>%
  select(SYSTEMRELIGION, technology, summary) %>%
  # separate risky from variable suffix
  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "meansd")) %>%
  # spread summary values back to wide form
  spread(meansd,summary) %>%
  #clean up
  select(-Risky)%>%
  arrange(mean)
```

```{r, echo=FALSE}
totalrisk <- codedmodule2%>%
  group_by(SYSTEMTOTAL)%>%
  filter(SYSTEMTOTAL == 5)%>%
  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #melt to long format
  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd) %>%
  select(SYSTEMTOTAL, technology, summary) %>%
  # separate risky from variable suffix
  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "meansd")) %>%
  # spread summary values back to wide form
  spread(meansd,summary) %>%
  #clean up
  select(-Risky)%>%
  arrange(mean)
```

```{r, echo=FALSE}

df1 <- left_join(religionrisk, totalrisk, by = "technology")
df2 <- left_join(demorisk, techrisk, by = "technology" )
```

```{r, echo=FALSE}

codedmodule2 %>%
   select(starts_with(c("Risky", "SYSTEM"))) %>%
  select(!starts_with(c("Risky_IND")))%>%
  filter(SYSTEMTOTAL == 5) +
  ggplot(aes(x= ))
  +
  #filter(SYSTEMTOTAL ==  "5"), "SYSTEMTEHNO" == 5, "SYSTEMDEMO" == 5, "SYSTEMRELIGION" == 5)
  ggplot(subset("SYSTEMTOTAL" == 5))

```

### 2022-04-09 module2/module2IVgraphs.Rmd
more graphs

@@
 
-```{r}
+```{r, echo = FALSE}
 demorisk <- codedmodule2%>%
@@
   select(-Risky)%>%
-  arrange(mean)
-```
+  arrange(mean) %>%
+  mutate_at(vars(SYSTEMDEMO), funs(case_when(. == 5 ~ "democractic"))) %>%
+  dplyr::rename(Govt = SYSTEMDEMO)
 
-```{r, echo=FALSE}
 techrisk <- codedmodule2%>%
@@
   select(-Risky)%>%
-  arrange(mean)
-```
+  arrange(mean) %>%
+  mutate_at(vars(SYSTEMTECHNO), funs(case_when(. == 5 ~ "technocratic"))) %>%
+  dplyr::rename(Govt = SYSTEMTECHNO)
 
-```{r, echo=FALSE}
 religionrisk <- codedmodule2%>%
@@
   select(-Risky)%>%
-  arrange(mean)
-```
+  arrange(mean)%>%
+  mutate_at(vars(SYSTEMRELIGION), funs(case_when(. == 5 ~ "religious"))) %>%
+  dplyr::rename(Govt = SYSTEMRELIGION)
 
-```{r, echo=FALSE}
 totalrisk <- codedmodule2%>%
@@
   select(-Risky)%>%
-  arrange(mean)
+  arrange(mean)%>%
+  mutate_at(vars(SYSTEMTOTAL), funs(case_when(. == 5 ~ "totalitarian"))) %>%
+  dplyr::rename(Govt = SYSTEMTOTAL)
 ```
@@
 
-df1 <- left_join(religionrisk, totalrisk, by = "technology")
-df2 <- left_join(demorisk, techrisk, by = "technology" )
+df1 <- full_join(religionrisk, totalrisk)
+df2 <- full_join(demorisk, techrisk)
+govtgraph <- full_join(df1, df2) %>%
+  group_by(technology)
+
+ggplot(govtgraph, aes(x = technology, y= mean, group = Govt))+
+  geom_line(aes(colour = Govt, line = Govt)) 
+  #ylim(0,4)
+  #scale_color_manual(values = c("darkred", "steelblue"))
+
 ```
@@
 
-codedmodule2 %>%
-   select(starts_with(c("Risky", "SYSTEM"))) %>%
-  select(!starts_with(c("Risky_IND")))%>%
-  filter(SYSTEMTOTAL == 5) +
-  ggplot(aes(x= ))
-  +
-  #filter(SYSTEMTOTAL ==  "5"), "SYSTEMTEHNO" == 5, "SYSTEMDEMO" == 5, "SYSTEMRELIGION" == 5)
-  ggplot(subset("SYSTEMTOTAL" == 5))
+ecopolscalescores <- codedmodule2 %>%
+  select(starts_with(c("Risky","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
+  rowwise()%>%
+  dplyr::mutate(Pro_decentralisation = mean(c_across("DECISIONDECEN":"DECISIONCEN")))%>%
+   dplyr::mutate(Pro_largescale = mean(c_across("INDUSTRYLARGE":"INDUSTRYSMALL")))%>%
+   dplyr::mutate(Pro_global = mean(c_across("ECONOMYGLOBAL":"ECONOMYLOCAL")))%>%
+   dplyr::mutate(Pro_ecogrowth = mean(c_across("ENVOVERDEV":"DEVOVERENV")))%>%
+   dplyr::mutate(Pro_private = mean(c_across("OWNERPVT":"OWNERREG")))%>%
+  dplyr::select(!c("DECISIONDECEN","DECISIONCEN", "INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL", "ECONOMYLOCAL","ENVOVERDEV",     "DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")) %>%
+    na.omit()
+
+ggplot(ecopolscalescores, aes(Pro_decentralisation, Risky_Hydro))+
+  geom_point()
 

### 2022-04-10 module2/module2DVgraphs.Rmd
combined dataset for DV graphs and finalised headings

@@
 module2[module2 == "Rather not say/ Don't know"] <- "Rather not say/Don't know"
-module2 %>%
-  filter(!row_number() %in% c(1,2))
 
@@
 ```
-
-## Coded Dataset
 
@@
                                                                                                          . == "Strongly agree" ~ 1)))
+```
 
-codedmodule2
+```{r, eval=TRUE}
+
+moduleone <- read_excel(here::here("thesis_surveydata/livelihood_insecurity_complete.xlsx"))
+save(moduleone, file = "moduleone.rda")
+module1 <- data.frame(moduleone)
+
+# loaded data set for module 2 eco -pol variables and removes the rows with question number and question text
+```
+
+```{r, eval =TRUE}
+#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
+codedmodule1 <- module1 %>%
+
+#remove row 1
+  filter(!row_number() %in% c(1,2)) %>%
+
+# replace risky likert scale with numbers
+  mutate_at(vars(starts_with("Risky")), funs(case_when(. =="Not at all risky" ~ 1, 
+                                                       . =="Slightly risky" ~ 2, 
+                                                       . =="Moderately risky" ~ 3, 
+                                                       . =="Very risky" ~ 4, 
+                                                       . =="Extremely risky" ~ 5))) %>%
+
+# replace beneficial likert scale with numbers  
+  mutate_at(vars(starts_with("Ben")), funs(case_when(. =="Not at all beneficial" ~ 1,
+                                                     . =="Slightly beneficial" ~ 2,
+                                                     . =="Moderately beneficial" ~ 3,
+                                                     . =="Very beneficial" ~ 4,
+                                                     . =="Extremely beneficial" ~ 5 ))) %>%
+
+# replace nuclear acceptance likert scale with numbers
+  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
+                                                                        . == "Somewhat disagree" ~ 2,
+                                                                        . == "Neither agree nor disagree" ~3,
+                                                                        . == "Somewhat agree" ~ 4,
+                                                                        . == "Strongly agree" ~ 5)))
+
+#coded dependent variables for module 1 livelihood and income security survey
+
+```
+
+```{r}
+
+suppressPackageStartupMessages(library(tidyselect))
+# combine codedmodule1 and codedmodule2
+
+numcol2 <- codedmodule2 %>% add_column(Respondent = 1:1099, .before = "Language") 
+numcol1 <- codedmodule1 %>% add_column(Respondent = 1099:2160, .before = "Language")
+
+joineddf <-  full_join(numcol2, numcol1, by = c("Respondent", "Language", "Survey_Date", "State", "Risky_Hydro", "Risky_Solar", "Risky_Wind", "Risky_Nuclear", "Risky_Coal", "Risky_Gas", "Risky_Oil", "Risky_INDHydro", "Risky_INDSolar", "Risky_INDWind", "Risky_INDBiogas", "Risky_INDDiesel", "Risky_INDKerosene", "Risky_INDFirewoodetc", "Risky_INDLPG", "Ben_Hydro", "Ben_Solar", "Ben_Wind", "Ben_Nuclear", "Ben_Coal", "Ben_Gas", "Ben_Oil", "Ben_INDHydro", "Ben_INDSolar", "Ben_INDWind", "Ben_INDDiesel", "Ben_INDBiogas", "Ben_INDFirewoodetc", "Ben_INDLPG", "Ben_INDKerosene", "N_accept", "N_reluctantlyaccept", "N_reject", "age", "urban_rural", "gender", "caste", "religion", "religiontext"))
+
 ```
@@
 How risky are each of these energy technologies according to you?
-Please tell me whether you see each technology as: not at all risky, slightly risky, moderately risky, very risky, or extremely risky
+Please tell me whether you see each technology as: not at all risky(1), slightly risky(2), moderately risky(3), very risky(4), or extremely risky(5)
 
@@
 
-risksumcentral <- codedmodule2 %>%
+risksumcentral <- joineddf %>%
   dplyr::select(!starts_with(c("RISKY_IND")))%>%
@@
 How risky are each of these energy technologies according to you?
-Please tell me whether you see each technology as: not at all risky, slightly risky, moderately risky, very risky, or extremely risky.
+Please tell me whether you see each technology as: not at all risky(1), slightly risky(2), moderately risky(3), very risky(4), or extremely risky(5).
+
+prefix IND stands for individually or community-owned and managed.
 
@@
 
-risksumIND <- codedmodule2 %>%
+risksumIND <- joineddf %>%
   summarize_at(vars(starts_with(c("RISKY_IND"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
@@
 How beneficial are each of these according to you?
-Please tell me whether you see each technology as: not at all beneficial, slightly beneficial, moderately beneficial, very beneficial, or extremely beneficial?
+Please tell me whether you see each technology as: not at all beneficial(1), slightly beneficial(2), moderately beneficial(3), very beneficial(4), or extremely beneficial(5)?
 
@@
 
-bensumcentral <- codedmodule2 %>%
+bensumcentral <- joineddf %>%
   dplyr::select(!starts_with(c("Ben_IND")))%>%
@@
 How beneficial are each of these according to you?
-Please tell me whether you see each technology as: not at all beneficial, slightly beneficial, moderately beneficial, very beneficial or extremely beneficial ?
+Please tell me whether you see each technology as: not at all beneficial(1), slightly beneficial(2), moderately beneficial(3), very beneficial(4) or extremely beneficial(5) ?
+
+prefix IND stands for individually or community-owned and managed.
 
@@
 
-bensumIND <- codedmodule2 %>%
+bensumIND <- joineddf %>%
   summarize_at(vars(starts_with(c("Ben_IND"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
@@
   geom_bar(stat="identity", position=position_dodge())+
+
 #geom_errorbar(aes(ymin= mean - sd, ymax= mean + sd), width =.2, position=position_dodge(.9))+
@@
 ```
+
+Prefix IND stands for individually or community-owned and managed.
 

### 2022-04-10 combined data set/DVgraphs.Rmd
created combined data set folder and moved files

--- 2022-04-10 module2/module2DVgraphs.Rmd
@@
 ---
-title: "Survey 2 : Dependent Variable Graphs"
+title: "Dependent Variable Graphs"
 output:

### 2022-04-10 combined data set/DVgraphs.Rmd
knitted DV graphs to html

@@
 output:
+  pdf_document:
+    toc: yes
+    number_sections: yes
+    toc_depth: 2
+    fig_width: 9
+    fig_height: 6
+    fig_caption: yes
+
   html_document:
@@
 
-pdf_document:
-
-    toc: true
-    number_sections: true
-    toc_depth: 2
-    fig_width: 9
-    fig_height: 6
-    fig_caption: yes
 ---
@@
 moduletwo <- read_excel(here::here("thesis_surveydata/political_factors_complete.xlsx"))
-save(moduletwo, file = "moduletwo.rda")
 
@@
 
-```{r, eval=TRUE}
+```{r, eval=TRUE, echo=FALSE}
 
 moduleone <- read_excel(here::here("thesis_surveydata/livelihood_insecurity_complete.xlsx"))
-save(moduleone, file = "moduleone.rda")
+
 module1 <- data.frame(moduleone)
@@
 
-```{r, eval =TRUE}
+```{r, eval =TRUE, echo=FALSE}
 #This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
@@
 
-```{r}
+```{r, echo=FALSE}
 

### 2022-04-10 combined data set/demographicvariables.Rmd
add colour to state wise graph

--- 2022-03-31 module2/WMEIndia.Rmd
@@
 ---
-title: "WMEIndia"
+title: "demographic variables"
 output:
@@
 moduletwo <- read_excel(here::here("thesis_surveydata/political_factors_complete.xlsx"))
-save(moduletwo, file = "moduletwo.rda")
 module2 <- data.frame(moduletwo)
 module2[module2 == "Rather not say/ Don't know"] <- "Rather not say/Don't know"
-module2 %>%
-  filter(!row_number() %in% c(1,2))
 
@@
 
-codedmodule2
 ```
+
+```{r, eval=TRUE}
+
+moduleone <- read_excel(here::here("thesis_surveydata/livelihood_insecurity_complete.xlsx"))
+module1 <- data.frame(moduleone)
+
+# loaded data set for module 2 eco -pol variables and removes the rows with question number and question text
+```
+
+```{r, eval =TRUE}
+#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
+codedmodule1 <- module1 %>%
+
+#remove row 1
+  filter(!row_number() %in% c(1,2)) %>%
+
+# replace risky likert scale with numbers
+  mutate_at(vars(starts_with("Risky")), funs(case_when(. =="Not at all risky" ~ 1, 
+                                                       . =="Slightly risky" ~ 2, 
+                                                       . =="Moderately risky" ~ 3, 
+                                                       . =="Very risky" ~ 4, 
+                                                       . =="Extremely risky" ~ 5))) %>%
+
+# replace beneficial likert scale with numbers  
+  mutate_at(vars(starts_with("Ben")), funs(case_when(. =="Not at all beneficial" ~ 1,
+                                                     . =="Slightly beneficial" ~ 2,
+                                                     . =="Moderately beneficial" ~ 3,
+                                                     . =="Very beneficial" ~ 4,
+                                                     . =="Extremely beneficial" ~ 5 ))) %>%
+
+# replace nuclear acceptance likert scale with numbers
+  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
+                                                                        . == "Somewhat disagree" ~ 2,
+                                                                        . == "Neither agree nor disagree" ~3,
+                                                                        . == "Somewhat agree" ~ 4,
+                                                                        . == "Strongly agree" ~ 5)))
+
+```
+
+```{r}
+
+suppressPackageStartupMessages(library(tidyselect))
+# combine codedmodule1 and codedmodule2
+
+numcol2 <- codedmodule2 %>% add_column(Respondent = 1:1099, .before = "Language") 
+numcol1 <- codedmodule1 %>% add_column(Respondent = 1099:2160, .before = "Language")
+
+joineddf <-  full_join(numcol2, numcol1, by = c("Respondent", "Language", "Survey_Date", "State", "Risky_Hydro", "Risky_Solar", "Risky_Wind", "Risky_Nuclear", "Risky_Coal", "Risky_Gas", "Risky_Oil", "Risky_INDHydro", "Risky_INDSolar", "Risky_INDWind", "Risky_INDBiogas", "Risky_INDDiesel", "Risky_INDKerosene", "Risky_INDFirewoodetc", "Risky_INDLPG", "Ben_Hydro", "Ben_Solar", "Ben_Wind", "Ben_Nuclear", "Ben_Coal", "Ben_Gas", "Ben_Oil", "Ben_INDHydro", "Ben_INDSolar", "Ben_INDWind", "Ben_INDDiesel", "Ben_INDBiogas", "Ben_INDFirewoodetc", "Ben_INDLPG", "Ben_INDKerosene", "N_accept", "N_reluctantlyaccept", "N_reject", "age", "urban_rural", "gender", "caste", "religion", "religiontext"))
+
+```
+
+```{r, echo=FALSE}
+cenrisksummary <- joineddf %>%
+  group_by(State)%>%
+  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
+  #melt to long format
+  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd) %>%
+  select(State, technology, summary) %>%
+  # separate risky from variable suffix
+  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
+  #separate mean from variable prefix
+  separate(var, c("technology", "meansd")) %>%
+  # spread summary values back to wide form
+  spread(meansd,summary) %>%
+  #clean up
+  select(-Risky)%>%
+  arrange(mean) #%>%
+  #setNames(paste0('perceivedrisk.', names(.))) %>%
+  #dplyr::rename(technology= perceivedrisk.technology)
+
+cenrisksummary
+```
+
+##Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by gender and caste groups
+
+OBC = Other Backward Classes
+SC = Scheduled Castes
+ST = Scheduled Tribes
 
@@
 
+ # mean risk from centrally controlled energy technologies
+
 castegendereffect %>%
-  mutate(Gender_Caste = factor(Gender_Caste, levels = c("Female_Brahmin", "Female_SC", "Male_Brahmin", "Male_General","Male_OBC", "Male_SC", "Male_ST", "Female_General", "Female_OBC", "Female_ST")))%>%
+  mutate(Gender_Caste = factor(castegendereffect$Gender_Caste, levels = c("Female_Brahmin", "Female_SC", "Female_OBC", "Male_SC","Male_ST", "Male_General", "Female_General","Female_ST" ,"Male_OBC", "Male_Brahmin")))%>%
   select(!starts_with(c("Risky_IND")))%>%
-  #select("Risky_Hydro", "Risky_Nuclear", "Risky_Coal","Gender_Caste")%>%
   rowwise()%>%
@@
   geom_errorbar(aes(xmin=mean-sd, xmax=mean + sd), width=.2,
-                 position=position_dodge(.9))
+                 position=position_dodge(.9))+
+  labs(x = "mean perceived risk", y = "GenderXCaste groups")
+
+```
+
+##Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by gender and caste groups
+
+OBC = Other Backward Classes
+SC = Scheduled Castes
+ST = Scheduled Tribes
+
+```{r, eval =TRUE, echo=FALSE}
+
+# mean risk from individually or community owned energy technologies
+
+castegendereffect %>%
+  mutate(Gender_Caste = factor(Gender_Caste, levels = c("Female_OBC","Female_SC", "Female_ST" ,"Female_Brahmin", "Male_ST",  "Male_SC","Female_General", "Male_General", "Male_OBC", "Male_Brahmin")))%>%
+  select(starts_with(c("Risky_IND", "Gender_Caste")))%>%
+  #select("Risky_Hydro", "Risky_Nuclear", "Risky_Coal","Gender_Caste")%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(riskscore = mean(c_across(Risky_INDHydro:Risky_INDLPG))) %>%
+  select(Gender_Caste, riskscore) %>%
+  dplyr::group_by(Gender_Caste)%>%
+  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
+  arrange(desc(mean))%>%
+  ggplot(aes(y = Gender_Caste, x = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
+  geom_errorbar(aes(xmin=mean-sd, xmax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  labs(x = "mean perceived risk", y = "GenderXCaste groups")
+
 #%>%
@@
 
+##Perceived Risk Scores for centrally managed hydroelectric dams by gender and caste groups
+
+OBC = Other Backward Classes
+SC = Scheduled Castes
+ST = Scheduled Tribes
+
 ```{r, echo=FALSE}
@@
 castegendereffect %>%
-  mutate(Gender_Caste = factor(Gender_Caste, levels = c("Female_Brahmin","Male_General", "Male_OBC", "Female_SC","Male_ST", "Male_SC","Female_ST", "Female_General", "Female_OBC","Male_Brahmin")))%>%
+  mutate(Gender_Caste = factor(Gender_Caste, levels = c("Female_Brahmin","Male_ST","Male_Brahmin", "Male_SC","Female_General","Male_General", "Female_OBC", "Female_ST","Female_SC", "Male_OBC")))%>%
   select(!starts_with(c("Risky_IND")))%>%
@@
   geom_errorbar(aes(xmin=hydro_m-hydro_sd, xmax=hydro_m + hydro_sd), width=.2,
-                 position=position_dodge(.9))
+                 position=position_dodge(.9))+
+  labs(x = "mean perceived risk", y = "GenderXCaste groups")
+```
+
+##Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by urban or rural location of the respondent
+
+```{r}
+
+joineddf$urban_rural <- as.factor(joineddf$urban_rural)
+class(joineddf$urban_rural)
+levels(joineddf$urban_rural)
+
+joineddf %>%
+  select(starts_with(c("Risky", "urban_rural")))%>%
+  select(!starts_with(c("Risky_IND")))%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(riskscore = mean(c_across(Risky_Hydro:Risky_Oil))) %>%
+  select(urban_rural, riskscore) %>%
+  dplyr::group_by(urban_rural)%>%
+  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
+  arrange(desc(mean))%>%
+  ggplot(aes(x= urban_rural, y = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  labs(x = "urban or rural", y = "mean risk")
+```
+
+##Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by gender
+
+```{r}
+
+joineddf$gender <- as.factor(joineddf$gender)
+class(joineddf$gender)
+levels(joineddf$gender)
+
+joineddf %>%
+  select(starts_with(c("Risky", "gender")))%>%
+  select(!starts_with(c("Risky_IND")))%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(riskscore = mean(c_across(Risky_Hydro:Risky_Oil))) %>%
+  select(gender, riskscore) %>%
+  dplyr::group_by(gender)%>%
+  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
+  arrange(desc(mean))%>%
+  ggplot(aes(x= gender, y = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  labs(y = "mean risk")
+```
+
+##Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by gender.
+
+```{r, echo=FALSE}
+
+joineddf$gender <- as.factor(joineddf$gender)
+class(joineddf$gender)
+levels(joineddf$gender)
+
+joineddf %>%
+  select(starts_with(c("Risky", "gender")))%>%
+  select(starts_with(c("Risky_IND", "gender")))%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(riskscore = mean(c_across(Risky_INDHydro:Risky_INDLPG))) %>%
+  select(gender, riskscore) %>%
+  dplyr::group_by(gender)%>%
+  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
+  arrange(desc(mean))%>%
+  ggplot(aes(x= gender, y = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  labs(y = "mean risk")
+```
+
+##Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by religion
+
+```{r, echo=FALSE}
+
+joineddf$religion <- as.factor(joineddf$religion)
+class(joineddf$religion)
+levels(joineddf$religion)
+
+joineddf %>%
+  select(starts_with(c("Risky", "religion")))%>%
+  select(!starts_with(c("Risky_IND", "religiontext")))%>%
+ mutate(religion = factor(religion, levels = c("Agnostism/ Atheism","Other (Please mention)" ,  "Jainism", "Buddhism", "Islam",              "Hinduism", "Christanity", "Sikhism"))) %>%
+  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(riskscore = mean(c_across(Risky_Hydro:Risky_Oil))) %>%
+  select(religion, riskscore) %>%
+  dplyr::group_by(religion)%>%
+  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
+  arrange(desc(mean))%>%
+  ggplot(aes(x= religion, y = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  coord_flip()
+```
+
+##Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by religion.
+
+```{r, echo=FALSE}
+
+joineddf$religion <- as.factor(joineddf$religion)
+class(joineddf$religion)
+levels(joineddf$religion)
+
+joineddf %>%
+  select(!starts_with(c("religiontext")))%>%
+  select(starts_with(c("Risky_IND", "religion")))%>%
+ mutate(religion = factor(religion, levels = c("Agnostism/ Atheism", "Jainism","Other (Please mention)" ,  "Buddhism", "Islam",              "Hinduism", "Christanity", "Sikhism"))) %>%
+  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(riskscore = mean(c_across(Risky_INDHydro:Risky_INDLPG))) %>%
+  select(religion, riskscore) %>%
+  dplyr::group_by(religion)%>%
+  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
+  arrange(desc(mean))%>%
+  ggplot(aes(x= religion, y = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  coord_flip()
+```
+
+##Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by age
+
+```{r, echo=FALSE}
+
+joineddf$age <- as.factor(joineddf$age)
+class(joineddf$age)
+levels(joineddf$age)
+
+joineddf %>%
+  select(starts_with(c("Risky", "age")))%>%
+  select(!starts_with(c("Risky_IND")))%>%
+ mutate(age = factor(age, levels = c("18-24 years old", "25-34 years old", "35-44 years old", "45-54 years old" , "55-64 years old" ,  "65-74 years old", "75 years or older"))) %>%
+  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(riskscore = mean(c_across(Risky_Hydro:Risky_Oil))) %>%
+  select(age, riskscore) %>%
+  dplyr::group_by(age)%>%
+  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
+  arrange(desc(mean))%>%
+  ggplot(aes(x= age, y = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  coord_flip()
+```
+
+##Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by age.
+
+```{r, echo=FALSE}
+
+joineddf$age <- as.factor(joineddf$age)
+class(joineddf$age)
+levels(joineddf$age)
+
+joineddf %>%
+  select(starts_with(c("Risky", "age")))%>%
+  select(starts_with(c("Risky_IND", "age")))%>%
+ mutate(age = factor(age, levels = c("18-24 years old", "25-34 years old", "35-44 years old", "45-54 years old" , "55-64 years old" ,  "65-74 years old", "75 years or older"))) %>%
+  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(riskscore = mean(c_across(Risky_INDHydro:Risky_INDLPG))) %>%
+  select(age, riskscore) %>%
+  dplyr::group_by(age)%>%
+  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
+  arrange(desc(mean))%>%
+  ggplot(aes(x= age, y = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  coord_flip()
+```
+
+##Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by state
+
+```{r, echo=FALSE}
+
+joineddf$State <- as.factor(joineddf$State)
+class(joineddf$State)
+levels(joineddf$State)
+
+cenrisksummary %>%
+  mutate(technology = fct_reorder(technology, mean, .desc = TRUE))%>%
+  ggplot(aes(y= technology, x= mean, fill = technology))+
+  geom_bar(stat="identity", position=position_dodge())+
+  theme_minimal()+
+  geom_errorbar(aes(xmin=mean-sd, xmax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  scale_fill_manual(values=c("#74238B", "#FEF102","#484349","#BA5C12", "#4D9DE0","#CFEBDF", "#FA6728"))+
+  xlim(0,5)+
+  facet_wrap(~ State)
+  #scale_fill_manual(y, values =))+
 
@@
 
+#Distribution checks
+
 ```{r}
-
-codedmodule2$Urban_Rural <- as.factor(codedmodule2$Urban_Rural)
-class(codedmodule2$Urban_Rural)
-levels(codedmodule2$Urban_Rural)
-
-urban_rural <- codedmodule2 %>%
-  select(starts_with(c("Risky", "Urban_Rural")))%>%
-  select(!starts_with(c("Risky_IND")))%>%
-  select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","Urban_Rural")%>%
-  rowwise()%>%
-  na.omit()%>%
-  dplyr::mutate(riskscore = mean(c(Risky_Hydro))) %>%
-  select(Urban_Rural, riskscore) %>%
-  dplyr::group_by(Urban_Rural)%>%
-  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
-  arrange(desc(mean))%>%
-  ggplot(aes(x= Urban_Rural, y = mean))+
-  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
-  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
-                 position=position_dodge(.9))
+joineddf %>%
+  filter(urban_rural == "Rural") %>%
+  ggplot(aes(x=Risky_Hydro, y = ..count..), fill = "lightgray")+
+  geom_density()
 ```

### 2022-04-10 module2/module2IVgraphs.Rmd
add colour to state wise graph

@@
 suppressPackageStartupMessages(library(readxl))
-suppressPackageStartupMessages(library(hablar))
 suppressPackageStartupMessages(library(tsibble))
@@
 suppressPackageStartupMessages(library(ggplot2))
-suppressPackageStartupMessages(library(ggbiplot))
-suppressPackageStartupMessages(library(psych)) # psychometrics
 

### 2022-04-10 combined data set/demographicvariables.Rmd
added benefit graphs to demographic variables file. knitted both files to pdf

@@
 ---
-title: "demographic variables"
+title: "Demographic Variables Plotted Against DVs(combined dataset)"
 output:
+  pdf_document: 
+    toc: yes
+    number_sections: yes
+    toc_depth: 2
+    fig_width: 9
+    fig_height: 6
+    fig_caption: yes
+
   html_document:
@@
 
-```{r, eval=TRUE}
+```{r, eval=TRUE, echo=FALSE}
 
@@
 
-```{r}
+```{r, echo = FALSE}
 
@@
 
-```{r, echo=FALSE}
-cenrisksummary <- joineddf %>%
-  group_by(State)%>%
-  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
-  #melt to long format
-  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd) %>%
-  select(State, technology, summary) %>%
-  # separate risky from variable suffix
-  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
-  #separate mean from variable prefix
-  separate(var, c("technology", "meansd")) %>%
-  # spread summary values back to wide form
-  spread(meansd,summary) %>%
-  #clean up
-  select(-Risky)%>%
-  arrange(mean) #%>%
-  #setNames(paste0('perceivedrisk.', names(.))) %>%
-  #dplyr::rename(technology= perceivedrisk.technology)
-
-cenrisksummary
-```
-
-##Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by gender and caste groups
+## Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by gender and caste groups
 
@@
 castegendereffect$Gender_Caste <- as.factor(castegendereffect$Gender_Caste)
-levels(castegendereffect$Gender_Caste)
+#levels(castegendereffect$Gender_Caste)
 
@@
 
-##Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by gender and caste groups
+## Perceived Benefit Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by gender and caste groups
+
+OBC = Other Backward Classes
+SC = Scheduled Castes
+ST = Scheduled Tribes
+
+```{r, eval =TRUE, echo=FALSE}
+
+castegenderben <- joineddf %>%
+  select(starts_with(c("Ben", "gender", "caste")))%>%
+  unite("Gender_Caste", c("gender", "caste")) %>%
+  na.omit()
+
+ # mean benefit from centrally controlled energy technologies
+
+castegenderben %>%
+  mutate(Gender_Caste = factor(castegenderben$Gender_Caste, levels = c("Male_OBC","Female_Brahmin","Male_SC","Male_ST", "Male_General", "Female_SC", "Female_OBC",  "Female_General" , "Male_Brahmin","Female_ST")))%>%
+  select(!starts_with(c("Ben_IND")))%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(benscore = mean(c_across(Ben_Hydro:Ben_Oil))) %>%
+  select(Gender_Caste, benscore) %>%
+  dplyr::group_by(Gender_Caste)%>%
+  summarise(mean=mean(benscore), sd=sd(benscore))%>%
+  arrange(desc(mean))%>%
+  ggplot(aes(y = Gender_Caste, x = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
+  geom_errorbar(aes(xmin=mean-sd, xmax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  labs(x = "mean perceived risk", y = "GenderXCaste groups")
+
+```
+
+## Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by gender and caste groups
 
@@
 
-##Perceived Risk Scores for centrally managed hydroelectric dams by gender and caste groups
+## Perceived Benefit Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by gender and caste groups
+
+OBC = Other Backward Classes
+SC = Scheduled Castes
+ST = Scheduled Tribes
+
+```{r, eval =TRUE, echo=FALSE}
+
+# mean benefit from individually or community owned energy technologies
+
+castegenderben %>%
+  mutate(Gender_Caste = factor(Gender_Caste, levels = c("Male_OBC","Female_SC","Female_Brahmin","Female_OBC","Male_SC", "Male_General","Male_ST","Female_General","Male_Brahmin", "Female_ST")))%>%
+  select(starts_with(c("Ben_IND", "Gender_Caste")))%>%
+  #select("Risky_Hydro", "Risky_Nuclear", "Risky_Coal","Gender_Caste")%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(benscore = mean(c_across(Ben_INDHydro:Ben_INDLPG))) %>%
+  select(Gender_Caste, benscore) %>%
+  dplyr::group_by(Gender_Caste)%>%
+  summarise(mean=mean(benscore), sd=sd(benscore))%>%
+  arrange(desc(mean))%>%
+  ggplot(aes(y = Gender_Caste, x = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
+  geom_errorbar(aes(xmin=mean-sd, xmax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  labs(x = "mean perceived benefit", y = "GenderXCaste groups")
+
+```
+
+## Perceived Risk Scores for centrally managed hydroelectric dams by gender and caste groups
 
@@
 ```
+## Perceived Benefit Scores for centrally managed hydroelectric dams by gender and caste groups
 
-##Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by urban or rural location of the respondent
+OBC = Other Backward Classes
+SC = Scheduled Castes
+ST = Scheduled Tribes
 
-```{r}
+```{r, echo=FALSE}
+
+castegenderben %>%
+  mutate(Gender_Caste = factor(Gender_Caste, levels = c("Male_OBC","Male_ST", "Female_Brahmin","Male_SC","Male_General", "Female_SC","Female_General","Female_OBC","Male_Brahmin",  "Female_ST")))%>%
+  select(!starts_with(c("Ben_IND")))%>%
+  select("Ben_Hydro", "Ben_Nuclear", "Ben_Coal","Gender_Caste")%>%
+  na.omit()%>%
+  dplyr::group_by(Gender_Caste)%>%
+  summarise(hydro_m=mean(Ben_Hydro), hydro_sd=sd(Ben_Hydro), nuclear_m=mean(Ben_Nuclear), nuclear_sd=sd(Ben_Nuclear),            coal_m=mean(Ben_Coal),   coal_sd=sd(Ben_Coal))%>%
+  arrange(desc(hydro_m))%>%
+  ggplot(aes(y = Gender_Caste, x = hydro_m))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
+  geom_errorbar(aes(xmin=hydro_m-hydro_sd, xmax=hydro_m + hydro_sd), width=.2,
+                 position=position_dodge(.9))+
+  labs(x = "mean perceived benefit", y = "GenderXCaste groups")
+```
+
+## Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by urban or rural location of the respondent
+
+```{r, echo=FALSE}
 
 joineddf$urban_rural <- as.factor(joineddf$urban_rural)
-class(joineddf$urban_rural)
-levels(joineddf$urban_rural)
+#class(joineddf$urban_rural)
+#levels(joineddf$urban_rural)
 
@@
 
-##Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by gender
+## Perceived Benefit Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by urban or rural location of the respondent
 
-```{r}
+```{r, echo=FALSE}
+
+joineddf %>%
+  select(starts_with(c("Ben", "urban_rural")))%>%
+  select(!starts_with(c("Ben_IND")))%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(benscore = mean(c_across(Ben_Hydro:Ben_Oil))) %>%
+  select(urban_rural, benscore) %>%
+  dplyr::group_by(urban_rural)%>%
+  summarise(mean=mean(benscore), sd=sd(benscore))%>%
+  arrange(desc(mean))%>%
+  ggplot(aes(x= urban_rural, y = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  labs(x = "urban or rural", y = "mean benefit")
+```
+
+## Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by gender
+
+```{r, echo =FALSE}
 
 joineddf$gender <- as.factor(joineddf$gender)
-class(joineddf$gender)
-levels(joineddf$gender)
+#class(joineddf$gender)
+#levels(joineddf$gender)
 
@@
 
-##Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by gender.
+## Perceived Benefit Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by gender
+
+```{r, echo =FALSE}
+
+joineddf %>%
+  select(starts_with(c("Ben", "gender")))%>%
+  select(!starts_with(c("Ben_IND")))%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(benscore = mean(c_across(Ben_Hydro:Ben_Oil))) %>%
+  select(gender, benscore) %>%
+  dplyr::group_by(gender)%>%
+  summarise(mean=mean(benscore), sd=sd(benscore))%>%
+  arrange(desc(mean))%>%
+  ggplot(aes(x= gender, y = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  labs(y = "mean benefit")
+```
+
+## Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by gender.
 
@@
 joineddf$gender <- as.factor(joineddf$gender)
-class(joineddf$gender)
-levels(joineddf$gender)
+#class(joineddf$gender)
+#levels(joineddf$gender)
 
@@
 
-##Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by religion
+## Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by gender.
+
+```{r, echo=FALSE}
+
+joineddf %>%
+  select(starts_with(c("Ben", "gender")))%>%
+  select(starts_with(c("Ben_IND", "gender")))%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(benscore = mean(c_across(Ben_INDHydro:Ben_INDLPG))) %>%
+  select(gender, benscore) %>%
+  dplyr::group_by(gender)%>%
+  summarise(mean=mean(benscore), sd=sd(benscore))%>%
+  arrange(desc(mean))%>%
+  ggplot(aes(x= gender, y = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  labs(y = "mean benefit")
+```
+
+## Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by religion
 
@@
 joineddf$religion <- as.factor(joineddf$religion)
-class(joineddf$religion)
-levels(joineddf$religion)
+#class(joineddf$religion)
+#levels(joineddf$religion)
 
@@
                  position=position_dodge(.9))+
+  labs(y= "mean perceived risk")+
   coord_flip()
@@
 
-##Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by religion.
+## Perceived Benefit Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by religion
+
+```{r, echo=FALSE}
+
+joineddf %>%
+  select(starts_with(c("Ben", "religion")))%>%
+  select(!starts_with(c("Ben_IND", "religiontext")))%>%
+ mutate(religion = factor(religion, levels = c("Other (Please mention)" ,"Agnostism/ Atheism",  "Christanity","Hinduism", "Islam","Jainism", "Sikhism" ,"Buddhism"))) %>%
+  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(benscore = mean(c_across(Ben_Hydro:Ben_Oil))) %>%
+  select(religion, benscore) %>%
+  dplyr::group_by(religion)%>%
+  summarise(mean=mean(benscore), sd=sd(benscore))%>%
+  arrange(desc(mean))%>%
+  ggplot(aes(x= religion, y = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  labs(y= "mean perceived benefit")+
+  coord_flip()
+```
+
+## Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by religion.
 
@@
 
-##Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by age
+## Perceived Benefit Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by religion.
+
+```{r, echo=FALSE}
+
+joineddf %>%
+  select(!starts_with(c("religiontext")))%>%
+  select(starts_with(c("Ben_IND", "religion")))%>%
+ mutate(religion = factor(religion, levels = c( "Jainism","Other (Please mention)" , "Hinduism","Agnostism/ Atheism", "Islam",   "Christanity","Buddhism", "Sikhism"))) %>%
+  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(benscore = mean(c_across(Ben_INDHydro:Ben_INDLPG))) %>%
+  select(religion, benscore) %>%
+  dplyr::group_by(religion)%>%
+  summarise(mean=mean(benscore), sd=sd(benscore))%>%
+  arrange(desc(mean))%>%
+  ggplot(aes(x= religion, y = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  labs(y= "mean perceived benefit")+
+  coord_flip()
+```
+
+## Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by age
 
@@
 joineddf$age <- as.factor(joineddf$age)
-class(joineddf$age)
-levels(joineddf$age)
+#class(joineddf$age)
+#levels(joineddf$age)
 
@@
                  position=position_dodge(.9))+
+  labs(y = "mean perceived risk")+
   coord_flip()
@@
 
-##Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by age.
+## Perceived Benefit Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by age
+```{r, echo=FALSE}
+
+joineddf %>%
+  select(starts_with(c("Ben", "age")))%>%
+  select(!starts_with(c("Ben_IND")))%>%
+ mutate(age = factor(age, levels = c("18-24 years old", "25-34 years old", "35-44 years old", "45-54 years old" , "55-64 years old" ,  "65-74 years old", "75 years or older"))) %>%
+  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(benscore = mean(c_across(Ben_Hydro:Ben_Oil))) %>%
+  select(age, benscore) %>%
+  dplyr::group_by(age)%>%
+  summarise(mean=mean(benscore), sd=sd(benscore))%>%
+  arrange(desc(mean))%>%
+  ggplot(aes(x= age, y = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  labs(y = "mean perceived benefit")+
+  coord_flip()
+```
+
+## Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by age.
 
 ```{r, echo=FALSE}
-
-joineddf$age <- as.factor(joineddf$age)
-class(joineddf$age)
-levels(joineddf$age)
 
@@
 
-##Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by state
+## Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by age.
+
+```{r, echo=FALSE}
+
+joineddf %>%
+  select(starts_with(c("Ben", "age")))%>%
+  select(starts_with(c("Ben_IND", "age")))%>%
+ mutate(age = factor(age, levels = c("18-24 years old", "25-34 years old", "35-44 years old", "45-54 years old" , "55-64 years old" ,  "65-74 years old", "75 years or older"))) %>%
+  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(benscore = mean(c_across(Ben_INDHydro:Ben_INDLPG))) %>%
+  select(age, benscore) %>%
+  dplyr::group_by(age)%>%
+  summarise(mean=mean(benscore), sd=sd(benscore))%>%
+  arrange(desc(mean))%>%
+  ggplot(aes(x= age, y = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  labs(y = "mean perceived benefit")+
+  coord_flip()
+```
+
+```{r, echo=FALSE}
+cenrisksummary <- joineddf %>%
+  group_by(State)%>%
+  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
+  #melt to long format
+  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd) %>%
+  select(State, technology, summary) %>%
+  # separate risky from variable suffix
+  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
+  #separate mean from variable prefix
+  separate(var, c("technology", "meansd")) %>%
+  # spread summary values back to wide form
+  spread(meansd,summary) %>%
+  #clean up
+  select(-Risky)%>%
+  arrange(mean) #%>%
+  #setNames(paste0('perceivedrisk.', names(.))) %>%
+  #dplyr::rename(technology= perceivedrisk.technology)
+
+```
+
+```{r, echo=FALSE}
+cenbensummary <- joineddf %>%
+  group_by(State)%>%
+  summarize_at(vars(starts_with(c("Ben"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
+  #melt to long format
+  gather(key = "technology", value = "summary", Ben_Hydro_mean, Ben_Solar_mean, Ben_Wind_mean, Ben_Nuclear_mean, Ben_Coal_mean, Ben_Gas_mean, Ben_Oil_mean, Ben_Hydro_sd, Ben_Solar_sd, Ben_Wind_sd, Ben_Nuclear_sd, Ben_Coal_sd, Ben_Gas_sd, Ben_Oil_sd) %>%
+  select(State, technology, summary) %>%
+  # separate risky from variable suffix
+  separate(technology, c("Ben", "var"), extra = "merge", fill = "left") %>%
+  #separate mean from variable prefix
+  separate(var, c("technology", "meansd")) %>%
+  # spread summary values back to wide form
+  spread(meansd,summary) %>%
+  #clean up
+  select(-Ben)%>%
+  arrange(mean) #%>%
+  #setNames(paste0('perceivedrisk.', names(.))) %>%
+  #dplyr::rename(technology= perceivedrisk.technology)
+
+```
+
+## Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by state
 
@@
 joineddf$State <- as.factor(joineddf$State)
-class(joineddf$State)
-levels(joineddf$State)
+#class(joineddf$State)
+#levels(joineddf$State)
 
@@
   xlim(0,5)+
-  facet_wrap(~ State)
+  facet_wrap(~ State)+
+  labs(x = "mean perceived risk", y = "energy technologies")
   #scale_fill_manual(y, values =))+
@@
 
+## Perceived Benefit Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by state
+
+```{r, echo=FALSE}
+
+joineddf$State <- as.factor(joineddf$State)
+#class(joineddf$State)
+#levels(joineddf$State)
+
+cenbensummary %>%
+  mutate(technology = fct_reorder(technology, mean, .desc = TRUE))%>%
+  ggplot(aes(y= technology, x= mean, fill = technology))+
+  geom_bar(stat="identity", position=position_dodge())+
+  theme_minimal()+
+  geom_errorbar(aes(xmin=mean-sd, xmax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  scale_fill_manual(values=c("#74238B", "#FEF102","#484349","#BA5C12", "#4D9DE0","#CFEBDF", "#FA6728"))+
+  xlim(0,5)+
+  facet_wrap(~ State)+
+  labs(x = "mean perceived benefit", y = "energy technologies")
+  #scale_fill_manual(y, values =))+
+
+```
+
+```{r, echo=FALSE}
+INDrisksummary <- joineddf %>%
+  group_by(State)%>%
+  summarize_at(vars(starts_with(c("RISKY_IND"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
+  #melt to long format
+  gather(key = "technology", value = "summary", Risky_INDHydro_mean, Risky_INDSolar_mean, Risky_INDWind_mean, Risky_INDDiesel_mean, Risky_INDKerosene_mean, Risky_INDFirewoodetc_mean, Risky_INDLPG_mean,  Risky_INDBiogas_mean, Risky_INDHydro_sd, Risky_INDSolar_sd, Risky_INDWind_sd, Risky_INDDiesel_sd, Risky_INDKerosene_sd, Risky_INDBiogas_sd, Risky_INDKerosene_sd, Risky_INDFirewoodetc_sd, Risky_INDLPG_sd) %>%
+  select(State, technology, summary) %>%
+  # separate risky from variable suffix
+  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
+  #separate mean from variable prefix
+  separate(var, c("technology", "meansd")) %>%
+  # spread summary values back to wide form
+  spread(meansd,summary) %>%
+  #clean up
+  select(-Risky)%>%
+  arrange(mean) #%>%
+  #setNames(paste0('perceivedrisk.', names(.))) %>%
+  #dplyr::rename(technology= perceivedrisk.technology)
+
+```
+
+```{r, echo=FALSE}
+INDbensummary <- joineddf %>%
+  group_by(State)%>%
+  summarize_at(vars(starts_with(c("Ben_IND"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
+  #melt to long format
+  gather(key = "technology", value = "summary", Ben_INDHydro_mean, Ben_INDSolar_mean, Ben_INDWind_mean, Ben_INDDiesel_mean, Ben_INDKerosene_mean, Ben_INDFirewoodetc_mean, Ben_INDLPG_mean,  Ben_INDBiogas_mean, Ben_INDHydro_sd, Ben_INDSolar_sd, Ben_INDWind_sd, Ben_INDDiesel_sd, Ben_INDKerosene_sd, Ben_INDBiogas_sd, Ben_INDKerosene_sd, Ben_INDFirewoodetc_sd, Ben_INDLPG_sd) %>%
+  select(State, technology, summary) %>%
+  # separate risky from variable suffix
+  separate(technology, c("Ben", "var"), extra = "merge", fill = "left") %>%
+  #separate mean from variable prefix
+  separate(var, c("technology", "meansd")) %>%
+  # spread summary values back to wide form
+  spread(meansd,summary) %>%
+  #clean up
+  select(-Ben)%>%
+  arrange(mean) #%>%
+  #setNames(paste0('perceivedrisk.', names(.))) %>%
+  #dplyr::rename(technology= perceivedrisk.technology)
+
+```
+
+## Perceived Risk Scores for all individually or community owned/managed energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by state
+```{r, echo=FALSE}
+
+INDrisksummary %>%
+  mutate(technology = fct_reorder(technology, mean, .desc = TRUE))%>%
+  ggplot(aes(y= technology, x= mean, fill = technology))+
+  geom_bar(stat="identity", position=position_dodge())+
+  theme_minimal()+
+  geom_errorbar(aes(xmin=mean-sd, xmax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  scale_fill_manual(values=c("red","#74238B", "#4D9DE0", "#CFEBDF","#FEF102","#484349","#BA5C12", "#FA6728"))+
+  xlim(0,5)+
+  facet_wrap(~ State)+
+  labs(x = "mean perceived risk", y = "energy technologies")
+  #scale_fill_manual(y, values =))+
+
+```
+
+## Perceived Benefit Scores for all individually or community owned/managed energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by state
+
+```{r, echo=FALSE}
+
+INDbensummary %>%
+  mutate(technology = fct_reorder(technology, mean, .desc = TRUE))%>%
+  ggplot(aes(y= technology, x= mean, fill = technology))+
+  geom_bar(stat="identity", position=position_dodge())+
+  theme_minimal()+
+  geom_errorbar(aes(xmin=mean-sd, xmax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  scale_fill_manual(values=c("red","#74238B", "#4D9DE0", "#CFEBDF","#FEF102","#484349","#BA5C12", "#FA6728"))+
+  xlim(0,5)+
+  facet_wrap(~ State)+
+  labs(x = "mean perceived benefit", y = "energy technologies")
+  #scale_fill_manual(y, values =))+
+
+```
+
+```{r, echo =FALSE}
 #Distribution checks 
-
-```{r}
-joineddf %>%
-  filter(urban_rural == "Rural") %>%
-  ggplot(aes(x=Risky_Hydro, y = ..count..), fill = "lightgray")+
-  geom_density()
+#joineddf %>%
+  #filter(urban_rural == "Rural") %>%
+  #ggplot(aes(x=Risky_Hydro, y = ..count..), fill = "lightgray")+
+  #geom_density()
 ```

### 2022-04-11 module2/module2IVgraphs.Rmd
figuring out graphs for eco-pol variables

@@
 
-ggplot(govtgraph, aes(x = technology, y= mean, group = Govt))+
-  geom_line(aes(colour = Govt, line = Govt)) 
+p <- ggplot(govtgraph, aes(x = technology, y= mean, group = Govt))+
+  geom_line(aes(colour = Govt, line = Govt)) +
+  labs(y = "mean perceived risk", x = "energy technology")
+
+update_labels(p, list(colour = "Preferred Government Type"))
   #ylim(0,4)
@@
 
+demorisk2 <- codedmodule2%>%
+  group_by(SYSTEMDEMO)%>%
+  filter(SYSTEMDEMO %in% c(1, 5))%>%
+  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
+  #melt to long format
+  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd) %>%
+  select(SYSTEMDEMO, technology, summary) %>%
+  # separate risky from variable suffix
+  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
+  #separate mean from variable prefix
+  separate(var, c("technology", "meansd")) %>%
+  # spread summary values back to wide form
+  spread(meansd,summary) %>%
+  #clean up
+  select(-Risky)%>%
+  arrange(mean)
+
+demorisk2 %>%
+  group_by(technology) %>%
+  ggplot(aes(x = technology, y= mean, group = SYSTEMDEMO))+
+  geom_line(aes(colour = SYSTEMDEMO, line = SYSTEMDEMO))
+
+```
+
+```{r, echo=FALSE}
+
+decenrisk2 <- codedmodule2%>%
+    select(starts_with(c("Risky","Ben","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
+  rowwise()%>%
+  dplyr::mutate(Pro_decentralisation = sum(c_across("DECISIONDECEN":"DECISIONCEN"))) %>%
+  group_by(Pro_decentralisation)%>%
+  filter(Pro_decentralisation %in% c(2, 10))%>%
+  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
+  #melt to long format
+  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd) %>%
+  select(Pro_decentralisation, technology, summary) %>%
+  # separate risky from variable suffix
+  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
+  #separate mean from variable prefix
+  separate(var, c("technology", "meansd")) %>%
+  # spread summary values back to wide form
+  spread(meansd,summary) %>%
+  #clean up
+  select(-Risky)%>%
+  arrange(mean)
+
+decenrisk2 %>%
+  group_by(technology) %>%
+  ggplot(aes(x = technology, y= mean, group = Pro_decentralisation))+
+  geom_line(aes(colour = Pro_decentralisation, line = Pro_decentralisation))+
+  ylim(1,4)
+```
+
+```{r, echo=FALSE}
+
+largerisk2 <- codedmodule2%>%
+    select(starts_with(c("Risky","Ben","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
+  rowwise()%>%
+  dplyr::mutate(Pro_largescale = sum(c_across("INDUSTRYLARGE":"INDUSTRYSMALL"))) %>%
+  group_by(Pro_largescale)%>%
+  filter(Pro_largescale%in% c(2, 10))%>%
+  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
+  #melt to long format
+  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd) %>%
+  select(Pro_largescale, technology, summary) %>%
+  # separate risky from variable suffix
+  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
+  #separate mean from variable prefix
+  separate(var, c("technology", "meansd")) %>%
+  # spread summary values back to wide form
+  spread(meansd,summary) %>%
+  #clean up
+  select(-Risky)%>%
+  arrange(mean)
+
+largerisk2 %>%
+  group_by(technology) %>%
+  ggplot(aes(x = technology, y= mean, group = Pro_largescale))+
+  geom_line(aes(colour = Pro_largescale, line = Pro_largescale))+
+  ylim(1,4)
+```
+
+```{r, echo=FALSE}
+
+globalrisk2 <- codedmodule2%>%
+    select(starts_with(c("Risky","Ben","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
+  rowwise()%>%
+  dplyr::mutate(Pro_global = sum(c_across("ECONOMYGLOBAL":"ECONOMYLOCAL"))) %>%
+  group_by(Pro_global)%>%
+  filter(Pro_global%in% c(2, 10))%>%
+  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
+  #melt to long format
+  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd) %>%
+  select(Pro_global, technology, summary) %>%
+  # separate risky from variable suffix
+  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
+  #separate mean from variable prefix
+  separate(var, c("technology", "meansd")) %>%
+  # spread summary values back to wide form
+  spread(meansd,summary) %>%
+  #clean up
+  select(-Risky)%>%
+  arrange(mean)
+
+globalrisk2 %>%
+  group_by(technology) %>%
+  ggplot(aes(x = technology, y= mean, group = Pro_global))+
+  geom_line(aes(colour = Pro_global, line = Pro_global))+
+  ylim(1,4)
+```
+
+```{r, echo=FALSE}
+
+envrisk2 <- codedmodule2%>%
+    select(starts_with(c("Risky","Ben","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
+  rowwise()%>%
+  group_by(ENVOVERDEV)%>%
+  filter(ENVOVERDEV%in% c(1, 5))%>%
+  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
+  #melt to long format
+  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd) %>%
+  select(ENVOVERDEV, technology, summary) %>%
+  # separate risky from variable suffix
+  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
+  #separate mean from variable prefix
+  separate(var, c("technology", "meansd")) %>%
+  # spread summary values back to wide form
+  spread(meansd,summary) %>%
+  #clean up
+  select(-Risky)%>%
+  arrange(mean)
+
+envrisk2 %>%
+  group_by(technology) %>%
+  ggplot(aes(x = technology, y= mean, group = ENVOVERDEV))+
+  geom_line(aes(colour = ENVOVERDEV, line = ENVOVERDEV))+
+  ylim(1,4)
+```
+
+```{r, echo=FALSE}
+
+devrisk2 <- codedmodule2%>%
+    select(starts_with(c("Risky","Ben","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
+  rowwise()%>%
+  group_by(DEVOVERENV)%>%
+  filter(DEVOVERENV%in% c(1, 5))%>%
+  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
+  #melt to long format
+  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd) %>%
+  select(DEVOVERENV, technology, summary) %>%
+  # separate risky from variable suffix
+  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
+  #separate mean from variable prefix
+  separate(var, c("technology", "meansd")) %>%
+  # spread summary values back to wide form
+  spread(meansd,summary) %>%
+  #clean up
+  select(-Risky)%>%
+  arrange(mean)
+
+devrisk2 %>%
+  group_by(technology) %>%
+  ggplot(aes(x = technology, y= mean, group = DEVOVERENV))+
+  geom_line(aes(colour = DEVOVERENV, line = DEVOVERENV))+
+  ylim(1,4)
+```
+
+```{r, echo=FALSE}
+
 ecopolscalescores <- codedmodule2 %>%
-  select(starts_with(c("Risky","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
+  select(starts_with(c("Risky","Ben","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
   rowwise()%>%
-  dplyr::mutate(Pro_decentralisation = mean(c_across("DECISIONDECEN":"DECISIONCEN")))%>%
+  dplyr::mutate(Pro_decentralisation = sum(c_across("DECISIONDECEN":"DECISIONCEN")))%>%
    dplyr::mutate(Pro_largescale = mean(c_across("INDUSTRYLARGE":"INDUSTRYSMALL")))%>%
@@
    dplyr::mutate(Pro_private = mean(c_across("OWNERPVT":"OWNERREG")))%>%
-  dplyr::select(!c("DECISIONDECEN","DECISIONCEN", "INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL", "ECONOMYLOCAL","ENVOVERDEV",     "DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")) %>%
+  #dplyr::select(!c("DECISIONDECEN","DECISIONCEN", "INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL", "ECONOMYLOCAL","ENVOVERDEV",     "DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")) %>%
     na.omit()
 
-ggplot(ecopolscalescores, aes(Pro_decentralisation, Risky_Hydro))+
-  geom_point()
+ggplot(ecopolscalescores, aes(Pro_decentralisation, Ben_Nuclear))+
+  geom_count()
 

### 2022-04-12 combined data set/DVgraphs.Rmd
data frame tables for DV graphs html file

@@
 output:
+  html_document:
+    fig_width: 9
+    fig_height: 6
+    fig_caption: yes
+    keep_md: yes
+    theme: paper
+    df_print: paged
   pdf_document:
@@
     fig_caption: yes
-
-  html_document:
-    fig_width: 9
-    fig_height: 6
-    fig_caption: yes
-    keep_md: yes
-    theme: paper
-    df_print: paged
-
 ---
@@
 
-risksumcentral
+data.frame(risksumcentral)
 
@@
 
-risksumIND
+data.frame(risksumIND)
 
@@
 
-bensumcentral
+data.frame(bensumcentral)
 
@@
 
-bensumIND
+data.frame(bensumIND)
 

### 2022-04-12 combined data set/demographicvariables.Rmd
data frame tables for DV graphs html file

@@
 
-castegendereffect %>%
+a <- castegendereffect %>%
   mutate(Gender_Caste = factor(castegendereffect$Gender_Caste, levels = c("Female_Brahmin", "Female_SC", "Female_OBC", "Male_SC","Male_ST", "Male_General", "Female_General","Female_ST" ,"Male_OBC", "Male_Brahmin")))%>%
@@
   dplyr::group_by(Gender_Caste)%>%
-  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
-  arrange(desc(mean))%>%
-  ggplot(aes(y = Gender_Caste, x = mean))+
+  summarise(mean=mean(riskscore), sd=sd(riskscore), n=n(), median= median(riskscore))%>%
+  arrange(desc(mean))
+
+a %>%  ggplot(aes(y = Gender_Caste, x = mean))+
   geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
@@
   labs(x = "mean perceived risk", y = "GenderXCaste groups")
+
+a %>%
 
@@
 #Distribution checks 
-#joineddf %>%
-  #filter(urban_rural == "Rural") %>%
-  #ggplot(aes(x=Risky_Hydro, y = ..count..), fill = "lightgray")+
-  #geom_density()
+joineddf %>%
+  filter(urban_rural == "Urban") %>%
+  ggplot(aes(x=Risky_Hydro, y = ..count..), fill = "lightgray")+
+  geom_bar()
 ```

### 2022-04-12 combined data set/demographicvariables.Rmd
dictributions of demographic variables

--- 2022-04-10 combined data set/demographicvariables.Rmd
@@
 ---
-title: "demographic variables"
+title: "Demographic Variables Plotted Against DVs(combined dataset)"
 output:
@@
     df_print: paged
+  pdf_document:
+
+    toc: yes
+    number_sections: yes
+    toc_depth: 2
+    fig_width: 9
+    fig_height: 6
+    fig_caption: yes
 ---
@@
 
-```{r, echo=FALSE}
-cenrisksummary <- joineddf %>%
-  group_by(State)%>%
-  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
-  #melt to long format
-  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd) %>%
-  select(State, technology, summary) %>%
-  # separate risky from variable suffix
-  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
-  #separate mean from variable prefix
-  separate(var, c("technology", "meansd")) %>%
-  # spread summary values back to wide form
-  spread(meansd,summary) %>%
-  #clean up
-  select(-Risky)%>%
-  arrange(mean) #%>%
-  #setNames(paste0('perceivedrisk.', names(.))) %>%
-  #dplyr::rename(technology= perceivedrisk.technology)
+## Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by gender and caste groups
 
-cenrisksummary
-```
-
-##Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by gender and caste groups
-
-OBC = Other Backward Classes
-SC = Scheduled Castes
+OBC = Other Backward Classes;
+SC = Scheduled Castes;
 ST = Scheduled Tribes
@@
 
-castegendereffect %>%
+caste_gender <- castegendereffect %>%
   mutate(Gender_Caste = factor(castegendereffect$Gender_Caste, levels = c("Female_Brahmin", "Female_SC", "Female_OBC", "Male_SC","Male_ST", "Male_General", "Female_General","Female_ST" ,"Male_OBC", "Male_Brahmin")))%>%
@@
   dplyr::group_by(Gender_Caste)%>%
-  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
-  arrange(desc(mean))%>%
-  ggplot(aes(y = Gender_Caste, x = mean))+
+  summarise(mean=mean(riskscore),median= median(riskscore), sd=sd(riskscore), n=n())%>%
+  arrange(desc(mean))
+
+data.frame(caste_gender)
+
+caste_gender %>%  ggplot(aes(y = Gender_Caste, x = mean))+
   geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
@@
 
-##Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by gender and caste groups
+## Perceived Benefit Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by gender and caste groups
+
+OBC = Other Backward Classes;
+SC = Scheduled Castes;
+ST = Scheduled Tribes;
+
+```{r, eval =TRUE, echo=FALSE}
+
+castegenderben <- joineddf %>%
+  select(starts_with(c("Ben", "gender", "caste")))%>%
+  unite("Gender_Caste", c("gender", "caste")) %>%
+  na.omit()
+
+caste_gender2 <- castegenderben%>%
+  mutate(Gender_Caste = factor(castegenderben$Gender_Caste, levels = c("Male_OBC","Female_Brahmin","Male_SC","Male_ST", "Male_General", "Female_SC", "Female_OBC",  "Female_General" , "Male_Brahmin","Female_ST")))%>%
+  select(!starts_with(c("Ben_IND")))%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(benscore = mean(c_across(Ben_Hydro:Ben_Oil))) %>%
+  select(Gender_Caste, benscore) %>%
+  dplyr::group_by(Gender_Caste)%>%
+  summarise(mean=mean(benscore), sd=sd(benscore), median = median (benscore), n= n())%>%
+  arrange(desc(mean))
+
+data.frame(caste_gender2)
+
+ # mean benefit from centrally controlled energy technologies
+
+caste_gender2 %>%
+  ggplot(aes(y = Gender_Caste, x = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
+  geom_errorbar(aes(xmin=mean-sd, xmax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  labs(x = "mean perceived risk", y = "GenderXCaste groups")
+
+```
+
+## Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by gender and caste groups
 
@@
 
-castegendereffect %>%
+caste_gender3 <- castegendereffect %>%
   mutate(Gender_Caste = factor(Gender_Caste, levels = c("Female_OBC","Female_SC", "Female_ST" ,"Female_Brahmin", "Male_ST",  "Male_SC","Female_General", "Male_General", "Male_OBC", "Male_Brahmin")))%>%
@@
   summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
-  arrange(desc(mean))%>%
+  arrange(desc(mean))
+
+data.frame(caste_gender3)
+
+caste_gender3%>%
   ggplot(aes(y = Gender_Caste, x = mean))+
@@
 
-##Perceived Risk Scores for centrally managed hydroelectric dams by gender and caste groups
+## Perceived Benefit Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by gender and caste groups
 
-OBC = Other Backward Classes
-SC = Scheduled Castes
+OBC = Other Backward Classes;
+SC = Scheduled Castes;
+ST = Scheduled Tribes
+
+```{r, eval =TRUE, echo=FALSE}
+
+# mean benefit from individually or community owned energy technologies
+
+caste_gender4 <- castegenderben %>%
+  mutate(Gender_Caste = factor(Gender_Caste, levels = c("Male_OBC","Female_SC","Female_Brahmin","Female_OBC","Male_SC", "Male_General","Male_ST","Female_General","Male_Brahmin", "Female_ST")))%>%
+  select(starts_with(c("Ben_IND", "Gender_Caste")))%>%
+  #select("Risky_Hydro", "Risky_Nuclear", "Risky_Coal","Gender_Caste")%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(benscore = mean(c_across(Ben_INDHydro:Ben_INDLPG))) %>%
+  select(Gender_Caste, benscore) %>%
+  dplyr::group_by(Gender_Caste)%>%
+  summarise(mean=mean(benscore), sd=sd(benscore), median= median(benscore), n = n())%>%
+  arrange(desc(mean))
+
+data.frame(caste_gender4)
+
+caste_gender4%>%
+  ggplot(aes(y = Gender_Caste, x = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
+  geom_errorbar(aes(xmin=mean-sd, xmax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  labs(x = "mean perceived benefit", y = "GenderXCaste groups")
+
+```
+
+## Perceived Risk Scores for centrally managed hydroelectric dams by gender and caste groups
+
+OBC = Other Backward Classes;
+SC = Scheduled Castes;
 ST = Scheduled Tribes
@@
 
-castegendereffect %>%
+caste_genderh <- castegendereffect %>%
   mutate(Gender_Caste = factor(Gender_Caste, levels = c("Female_Brahmin","Male_ST","Male_Brahmin", "Male_SC","Female_General","Male_General", "Female_OBC", "Female_ST","Female_SC", "Male_OBC")))%>%
@@
   summarise(hydro_m=mean(Risky_Hydro), hydro_sd=sd(Risky_Hydro), nuclear_m=mean(Risky_Nuclear), nuclear_sd=sd(Risky_Nuclear),            coal_m=mean(Risky_Coal),   coal_sd=sd(Risky_Coal))%>%
-  arrange(desc(hydro_m))%>%
+  arrange(desc(hydro_m))
+
+data.frame(caste_genderh)
+
+caste_genderh%>%
   ggplot(aes(y = Gender_Caste, x = hydro_m))+
@@
 ```
+## Perceived Benefit Scores for centrally managed hydroelectric dams by gender and caste groups
 
-##Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by urban or rural location of the respondent
+OBC = Other Backward Classes;
+SC = Scheduled Castes;
+ST = Scheduled Tribes
 
-```{r}
+```{r, echo=FALSE}
+
+caste_genderh2 <- castegenderben %>%
+  mutate(Gender_Caste = factor(Gender_Caste, levels = c("Male_OBC","Male_ST", "Female_Brahmin","Male_SC","Male_General", "Female_SC","Female_General","Female_OBC","Male_Brahmin",  "Female_ST")))%>%
+  select(!starts_with(c("Ben_IND")))%>%
+  select("Ben_Hydro", "Ben_Nuclear", "Ben_Coal","Gender_Caste")%>%
+  na.omit()%>%
+  dplyr::group_by(Gender_Caste)%>%
+  summarise(hydro_m=mean(Ben_Hydro), hydro_sd=sd(Ben_Hydro), nuclear_m=mean(Ben_Nuclear), nuclear_sd=sd(Ben_Nuclear),            coal_m=mean(Ben_Coal),   coal_sd=sd(Ben_Coal))%>%
+  arrange(desc(hydro_m))
+
+data.frame(caste_genderh2)
+
+caste_genderh2 %>%
+  ggplot(aes(y = Gender_Caste, x = hydro_m))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
+  geom_errorbar(aes(xmin=hydro_m-hydro_sd, xmax=hydro_m + hydro_sd), width=.2,
+                 position=position_dodge(.9))+
+  labs(x = "mean perceived benefit", y = "GenderXCaste groups")
+```
+
+## Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by urban or rural location of the respondent
+
+```{r, echo=FALSE}
 
 joineddf$urban_rural <- as.factor(joineddf$urban_rural)
-class(joineddf$urban_rural)
-levels(joineddf$urban_rural)
+#class(joineddf$urban_rural)
+#levels(joineddf$urban_rural)
 
-joineddf %>%
+urbanrural <- joineddf %>%
   select(starts_with(c("Risky", "urban_rural")))%>%
@@
   dplyr::group_by(urban_rural)%>%
-  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
-  arrange(desc(mean))%>%
+  summarise(mean=mean(riskscore), sd=sd(riskscore), median = median (riskscore), n=n())%>%
+  arrange(desc(mean))
+
+data.frame(urbanrural)
+
+urbanrural%>%
   ggplot(aes(x= urban_rural, y = mean))+
@@
 
-##Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by gender
+## Perceived Benefit Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by urban or rural location of the respondent
 
-```{r}
+```{r, echo=FALSE}
+
+urbanrural2 <- joineddf %>%
+  select(starts_with(c("Ben", "urban_rural")))%>%
+  select(!starts_with(c("Ben_IND")))%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(benscore = mean(c_across(Ben_Hydro:Ben_Oil))) %>%
+  select(urban_rural, benscore) %>%
+  dplyr::group_by(urban_rural)%>%
+  summarise(mean=mean(benscore), sd=sd(benscore), median= median(benscore), n= n())%>%
+  arrange(desc(mean))
+
+data.frame(urbanrural2)
+
+urbanrural2%>%
+  ggplot(aes(x= urban_rural, y = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  labs(x = "urban or rural", y = "mean benefit")
+```
+
+## Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by gender
+
+```{r, echo =FALSE}
 
 joineddf$gender <- as.factor(joineddf$gender)
-class(joineddf$gender)
-levels(joineddf$gender)
+#class(joineddf$gender)
+#levels(joineddf$gender)
 
-joineddf %>%
+genderrisk <- joineddf %>%
   select(starts_with(c("Risky", "gender")))%>%
@@
   dplyr::group_by(gender)%>%
-  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
-  arrange(desc(mean))%>%
+  summarise(mean=mean(riskscore), sd=sd(riskscore), median= median(riskscore), n=n())%>%
+  arrange(desc(mean))
+
+data.frame(genderrisk)
+
+genderrisk%>%
   ggplot(aes(x= gender, y = mean))+
@@
 
-##Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by gender.
+## Perceived Benefit Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by gender
+
+```{r, echo =FALSE}
+
+genderben <- joineddf %>%
+  select(starts_with(c("Ben", "gender")))%>%
+  select(!starts_with(c("Ben_IND")))%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(benscore = mean(c_across(Ben_Hydro:Ben_Oil))) %>%
+  select(gender, benscore) %>%
+  dplyr::group_by(gender)%>%
+  summarise(mean=mean(benscore), sd=sd(benscore), median = median(benscore), n=n())%>%
+  arrange(desc(mean))
+
+data.frame(genderben)
+
+genderben %>%
+  ggplot(aes(x= gender, y = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  labs(y = "mean benefit")
+```
+
+## Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by gender.
 
@@
 joineddf$gender <- as.factor(joineddf$gender)
-class(joineddf$gender)
-levels(joineddf$gender)
+#class(joineddf$gender)
+#levels(joineddf$gender)
 
-joineddf %>%
+genderrisk2 <- joineddf %>%
   select(starts_with(c("Risky", "gender")))%>%
@@
   dplyr::group_by(gender)%>%
-  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
-  arrange(desc(mean))%>%
+  summarise(mean=mean(riskscore), sd=sd(riskscore), median= median(riskscore), n=n())%>%
+  arrange(desc(mean))
+
+data.frame(genderrisk2)
+
+genderrisk2%>%
   ggplot(aes(x= gender, y = mean))+
@@
 
-##Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by religion
+## Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by gender.
+
+```{r, echo=FALSE}
+
+genderben2 <- joineddf %>%
+  select(starts_with(c("Ben", "gender")))%>%
+  select(starts_with(c("Ben_IND", "gender")))%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(benscore = mean(c_across(Ben_INDHydro:Ben_INDLPG))) %>%
+  select(gender, benscore) %>%
+  dplyr::group_by(gender)%>%
+  summarise(mean=mean(benscore), sd=sd(benscore), median = median (benscore), n=n())%>%
+  arrange(desc(mean))
+
+data.frame(genderben2)
+
+genderben2%>%
+  ggplot(aes(x= gender, y = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  labs(y = "mean benefit")
+```
+
+## Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by religion
 
@@
 joineddf$religion <- as.factor(joineddf$religion)
-class(joineddf$religion)
-levels(joineddf$religion)
+#class(joineddf$religion)
+#levels(joineddf$religion)
 
-joineddf %>%
+religionrisk1 <- joineddf %>%
   select(starts_with(c("Risky", "religion")))%>%
@@
   dplyr::group_by(religion)%>%
-  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
-  arrange(desc(mean))%>%
+  summarise(mean=mean(riskscore), sd=sd(riskscore), median= median(riskscore), n=n())%>%
+  arrange(desc(mean))
+
+data.frame(religionrisk1)
+
+religionrisk1%>%
   ggplot(aes(x= religion, y = mean))+
@@
 
-##Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by religion.
+## Perceived Benefit Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by religion
+
+```{r, echo=FALSE}
+
+religionben1 <- joineddf %>%
+  select(starts_with(c("Ben", "religion")))%>%
+  select(!starts_with(c("Ben_IND", "religiontext")))%>%
+ mutate(religion = factor(religion, levels = c("Other (Please mention)" ,"Agnostism/ Atheism",  "Christanity","Hinduism", "Islam","Jainism", "Sikhism" ,"Buddhism"))) %>%
+  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(benscore = mean(c_across(Ben_Hydro:Ben_Oil))) %>%
+  select(religion, benscore) %>%
+  dplyr::group_by(religion)%>%
+  summarise(mean=mean(benscore), sd=sd(benscore), median=median(benscore), n=n())%>%
+  arrange(desc(mean))
+
+data.frame(religionben1)
+
+religionben1%>%
+  ggplot(aes(x= religion, y = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  labs(y= "mean perceived benefit")+
+  coord_flip()
+```
+
+## Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by religion.
 
@@
 joineddf$religion <- as.factor(joineddf$religion)
-class(joineddf$religion)
-levels(joineddf$religion)
+#class(joineddf$religion)
+#levels(joineddf$religion)
 
-joineddf %>%
+religionrisk2 <- joineddf %>%
   select(!starts_with(c("religiontext")))%>%
@@
   dplyr::group_by(religion)%>%
-  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
-  arrange(desc(mean))%>%
+  summarise(mean=mean(riskscore), sd=sd(riskscore), median = median(riskscore), n=n())%>%
+  arrange(desc(mean))
+
+data.frame(religionrisk2)
+
+religionrisk2%>%
   ggplot(aes(x= religion, y = mean))+
@@
 
-##Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by age
+## Perceived Benefit Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by religion.
+
+```{r, echo=FALSE}
+
+religionben2 <- joineddf %>%
+  select(!starts_with(c("religiontext")))%>%
+  select(starts_with(c("Ben_IND", "religion")))%>%
+ mutate(religion = factor(religion, levels = c( "Jainism","Other (Please mention)" , "Hinduism","Agnostism/ Atheism", "Islam",   "Christanity","Buddhism", "Sikhism"))) %>%
+  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(benscore = mean(c_across(Ben_INDHydro:Ben_INDLPG))) %>%
+  select(religion, benscore) %>%
+  dplyr::group_by(religion)%>%
+  summarise(mean=mean(benscore), sd=sd(benscore), median = median(benscore), n=n())%>%
+  arrange(desc(mean))
+
+data.frame(religionben2)
+
+religionben2%>%
+  ggplot(aes(x= religion, y = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  labs(y= "mean perceived benefit")+
+  coord_flip()
+```
+
+## Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by age
 
@@
 joineddf$age <- as.factor(joineddf$age)
-class(joineddf$age)
-levels(joineddf$age)
+#class(joineddf$age)
+#levels(joineddf$age)
 
-joineddf %>%
+agerisk1<- joineddf %>%
   select(starts_with(c("Risky", "age")))%>%
@@
   dplyr::group_by(age)%>%
-  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
-  arrange(desc(mean))%>%
+  summarise(mean=mean(riskscore), sd=sd(riskscore), median= median(riskscore), n=n())%>%
+  arrange(desc(mean))
+
+data.frame(agerisk1)
+
+agerisk1%>%
   ggplot(aes(x= age, y = mean))+
@@
 
-##Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by age.
+## Perceived Benefit Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by age
+```{r, echo=FALSE}
+
+ageben1 <- joineddf %>%
+  select(starts_with(c("Ben", "age")))%>%
+  select(!starts_with(c("Ben_IND")))%>%
+ mutate(age = factor(age, levels = c("18-24 years old", "25-34 years old", "35-44 years old", "45-54 years old" , "55-64 years old" ,  "65-74 years old", "75 years or older"))) %>%
+  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(benscore = mean(c_across(Ben_Hydro:Ben_Oil))) %>%
+  select(age, benscore) %>%
+  dplyr::group_by(age)%>%
+  summarise(mean=mean(benscore), sd=sd(benscore),median= median(benscore), n=n())%>%
+  arrange(desc(mean))
+
+data.frame(ageben1)
+
+ageben1%>%
+  ggplot(aes(x= age, y = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  labs(y = "mean perceived benefit")+
+  coord_flip()
+```
+
+## Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by age.
 
@@
 
-joineddf$age <- as.factor(joineddf$age)
-class(joineddf$age)
-levels(joineddf$age)
-
-joineddf %>%
+agerisk2 <- joineddf %>%
   select(starts_with(c("Risky", "age")))%>%
@@
   dplyr::group_by(age)%>%
-  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
-  arrange(desc(mean))%>%
+  summarise(mean=mean(riskscore), sd=sd(riskscore), median= median(riskscore), n=n())%>%
+  arrange(desc(mean))
+
+data.frame(agerisk2)
+
+agerisk2%>%
   ggplot(aes(x= age, y = mean))+
@@
 
-##Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by state
+## Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by age.
+
+```{r, echo=FALSE}
+
+ageben2 <- joineddf %>%
+  select(starts_with(c("Ben", "age")))%>%
+  select(starts_with(c("Ben_IND", "age")))%>%
+ mutate(age = factor(age, levels = c("18-24 years old", "25-34 years old", "35-44 years old", "45-54 years old" , "55-64 years old" ,  "65-74 years old", "75 years or older"))) %>%
+  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(benscore = mean(c_across(Ben_INDHydro:Ben_INDLPG))) %>%
+  select(age, benscore) %>%
+  dplyr::group_by(age)%>%
+  summarise(mean=mean(benscore), sd=sd(benscore), median=median(benscore), n=n())%>%
+  arrange(desc(mean))
+
+data.frame(ageben2)
+
+ageben2%>%
+  ggplot(aes(x= age, y = mean))+
+  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  labs(y = "mean perceived benefit")+
+  coord_flip()
+```
+
+## Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by state
+
+```{r, echo=FALSE}
+cenrisksummary <- joineddf %>%
+  group_by(State)%>%
+  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
+  #melt to long format
+  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd,  Risky_Hydro_median, Risky_Solar_median, Risky_Wind_median, Risky_Nuclear_median, Risky_Coal_median, Risky_Gas_median, Risky_Oil_median, Risky_Hydro_n, Risky_Solar_n, Risky_Wind_n, Risky_Nuclear_n, Risky_Coal_n, Risky_Gas_n, Risky_Oil_n,) %>%
+  select(State, technology, summary) %>%
+  # separate risky from variable suffix
+  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
+  #separate mean from variable prefix
+  separate(var, c("technology", "meansd")) %>%
+  # spread summary values back to wide form
+  spread(meansd,summary) %>%
+  #clean up
+  select(-Risky)%>%
+  arrange(State) #%>%
+  #setNames(paste0('perceivedrisk.', names(.))) %>%
+  #dplyr::rename(technology= perceivedrisk.technology)
+
+data.frame(cenrisksummary)
+
+```
 
@@
 
-#Distribution checks
+## Perceived Benefit Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by state
 
-```{r}
-joineddf %>%
-  filter(urban_rural == "Rural") %>%
-  ggplot(aes(x=Risky_Hydro, y = ..count..), fill = "lightgray")+
-  geom_density()
+```{r, echo=FALSE}
+cenbensummary <- joineddf %>%
+  group_by(State)%>%
+  summarize_at(vars(starts_with(c("Ben"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
+  #melt to long format
+  gather(key = "technology", value = "summary", Ben_Hydro_mean, Ben_Solar_mean, Ben_Wind_mean, Ben_Nuclear_mean, Ben_Coal_mean, Ben_Gas_mean, Ben_Oil_mean, Ben_Hydro_sd, Ben_Solar_sd, Ben_Wind_sd, Ben_Nuclear_sd, Ben_Coal_sd, Ben_Gas_sd, Ben_Oil_sd, Ben_Hydro_median, Ben_Solar_median, Ben_Wind_median, Ben_Nuclear_median, Ben_Coal_median, Ben_Gas_median, Ben_Oil_median, Ben_Hydro_n, Ben_Solar_n, Ben_Wind_n, Ben_Nuclear_n, Ben_Coal_n, Ben_Gas_n, Ben_Oil_n) %>%
+  select(State, technology, summary) %>%
+  # separate risky from variable suffix
+  separate(technology, c("Ben", "var"), extra = "merge", fill = "left") %>%
+  #separate mean from variable prefix
+  separate(var, c("technology", "meansd")) %>%
+  # spread summary values back to wide form
+  spread(meansd,summary) %>%
+  #clean up
+  select(-Ben)%>%
+  arrange(State) #%>%
+  #setNames(paste0('perceivedrisk.', names(.))) %>%
+  #dplyr::rename(technology= perceivedrisk.technology)
+
+data.frame(cenbensummary)
+
 ```
+
+```{r, echo=FALSE}
+
+joineddf$State <- as.factor(joineddf$State)
+#class(joineddf$State)
+#levels(joineddf$State)
+
+cenbensummary %>%
+  mutate(technology = fct_reorder(technology, mean, .desc = TRUE))%>%
+  ggplot(aes(y= technology, x= mean, fill = technology))+
+  geom_bar(stat="identity", position=position_dodge())+
+  theme_minimal()+
+  geom_errorbar(aes(xmin=mean-sd, xmax=mean + sd), width=.2,
+                 position=position_dodge(.9))+
+  scale_fill_manual(values=c("#74238B", "#FEF102","#484349","#BA5C12", "#4D9DE0","#CFEBDF", "#FA6728"))+
+  xlim(0,5)+
+  facet_wrap(~ State)+
+  labs(x = "mean perceived benefit", y = "energy technologies")
+  #scale_fill_manual(y, values =))+
+
+```
+
+```{r, echo=FALSE}
+#INDrisksummary <- joineddf %>%
+  #group_by(State)%>%
+ # summarize_at(vars(starts_with(c("RISKY_IND"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
+  #melt to long format
+  #gather(key = "technology", value = "summary", Risky_INDHydro_mean, Risky_INDSolar_mean, Risky_INDWind_mean, Risky_INDDiesel_mean, Risky_INDKerosene_mean, Risky_INDFirewoodetc_mean, Risky_INDLPG_mean,  Risky_INDBiogas_mean, Risky_INDHydro_sd, Risky_INDSolar_sd, Risky_INDWind_sd, Risky_INDDiesel_sd, Risky_INDKerosene_sd, Risky_INDBiogas_sd, Risky_INDKerosene_sd, Risky_INDFirewoodetc_sd, Risky_INDLPG_sd) %>%
+  #select(State, technology, summary) %>%
+  # separate risky from variable suffix
+  #separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
+  #separate mean from variable prefix
+  #separate(var, c("technology", "meansd")) %>%
+  # spread summary values back to wide form
+  #spread(meansd,summary) %>%
+  #clean up
+  #select(-Risky)%>%
+  #arrange(mean) #%>%
+  #setNames(paste0('perceivedrisk.', names(.))) %>%
+  #dplyr::rename(technology= perceivedrisk.technology)
+
+```
+
+```{r, echo=FALSE}
+INDbensummary <- joineddf %>%
+  group_by(State)%>%
+  summarize_at(vars(starts_with(c("Ben_IND"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
+  #melt to long format
+  gather(key = "technology", value = "summary", Ben_INDHydro_mean, Ben_INDSolar_mean, Ben_INDWind_mean, Ben_INDDiesel_mean, Ben_INDKerosene_mean, Ben_INDFirewoodetc_mean, Ben_INDLPG_mean,  Ben_INDBiogas_mean, Ben_INDHydro_sd, Ben_INDSolar_sd, Ben_INDWind_sd, Ben_INDDiesel_sd, Ben_INDKerosene_sd, Ben_INDBiogas_sd, Ben_INDKerosene_sd, Ben_INDFirewoodetc_sd, Ben_INDLPG_sd) %>%
+  select(State, technology, summary) %>%
+  # separate risky from variable suffix
+  separate(technology, c("Ben", "var"), extra = "merge", fill = "left") %>%
+  #separate mean from variable prefix
+  separate(var, c("technology", "meansd")) %>%
+  # spread summary values back to wide form
+  spread(meansd,summary) %>%
+  #clean up
+  select(-Ben)%>%
+  arrange(mean) #%>%
+  #setNames(paste0('perceivedrisk.', names(.))) %>%
+  #dplyr::rename(technology= perceivedrisk.technology)
+
+```
+
+```{r, echo=FALSE}
+
+#INDrisksummary %>%
+  #mutate(technology = fct_reorder(technology, mean, .desc = TRUE))%>%
+  #ggplot(aes(y= technology, x= mean, fill = technology))+
+  #geom_bar(stat="identity", position=position_dodge())+
+  #theme_minimal()+
+  #geom_errorbar(aes(xmin=mean-sd, xmax=mean + sd), width=.2,
+                 #position=position_dodge(.9))+
+  #scale_fill_manual(values=c("red","#74238B", "#4D9DE0", "#CFEBDF","#FEF102","#484349","#BA5C12", "#FA6728"))+
+  #xlim(0,5)+
+  #facet_wrap(~ State)+
+  #labs(x = "mean perceived risk", y = "energy technologies")
+  #scale_fill_manual(y, values =))+
+
+```
+
+```{r, echo=FALSE}
+
+#INDbensummary %>%
+  #mutate(technology = fct_reorder(technology, mean, .desc = TRUE))%>%
+  #ggplot(aes(y= technology, x= mean, fill = technology))+
+  #geom_bar(stat="identity", position=position_dodge())+
+  #theme_minimal()+
+  #geom_errorbar(aes(xmin=mean-sd, xmax=mean + sd), width=.2,
+                # position=position_dodge(.9))+
+  #scale_fill_manual(values=c("red","#74238B", "#4D9DE0", "#CFEBDF","#FEF102","#484349","#BA5C12", "#FA6728"))+
+ # xlim(0,5)+
+ # facet_wrap(~ State)+
+ # labs(x = "mean perceived benefit", y = "energy technologies")
+  #scale_fill_manual(y, values =))+
+
+```

### 2022-04-12 combined data set/distributions.Rmd
dictributions of demographic variables

---
title: "distributions"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2022-04-12 combined data set/distributions.Rmd
enter explanatory text for module2IV graphs

@@
 title: "distributions"
-output: html_document
+output:
+  html_document:
+    fig_width: 9
+    fig_height: 6
+    fig_caption: yes
+    keep_md: yes
+    theme: paper
+    df_print: paged
+  pdf_document:
+
+    toc: yes
+    number_sections: yes
+    toc_depth: 2
+    fig_width: 9
+    fig_height: 6
+    fig_caption: yes
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+```{r load packages, warning = FALSE, message = FALSE, echo=FALSE}
+  knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+
+suppressPackageStartupMessages(library(tidyverse))
+suppressPackageStartupMessages(library(readxl))
+suppressPackageStartupMessages(library(dplyr))
+suppressPackageStartupMessages(library(tidyr))
+suppressPackageStartupMessages(library(ggplot2))
+
 ```
 
-## R Markdown
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+moduletwo <- read_excel(here::here("thesis_surveydata/political_factors_complete.xlsx"))
+module2 <- data.frame(moduletwo)
+module2[module2 == "Rather not say/ Don't know"] <- "Rather not say/Don't know"
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
-
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
-```{r cars}
-summary(cars)
+# loaded data set for module 2 eco -pol variables and removes the rows with question number and question text
 ```
 
-## Including Plots
+```{r, eval =TRUE, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
+codedmodule2 <- module2 %>%
 
-You can also embed plots, for example:
+#remove row 1
+  filter(!row_number() %in% c(1,2)) %>%
 
-```{r pressure, echo=FALSE}
-plot(pressure)
+# replace risky likert scale with numbers
+  mutate_at(vars(starts_with("Risky")), funs(case_when(. =="Not at all risky" ~ 1, 
+                                                       . =="Slightly risky" ~ 2, 
+                                                       . =="Moderately risky" ~ 3, 
+                                                       . =="Very risky" ~ 4, 
+                                                       . =="Extremely risky" ~ 5))) %>%
+
+# replace beneficial likert scale with numbers  
+  mutate_at(vars(starts_with("Ben")), funs(case_when(. =="Not at all beneficial" ~ 1,
+                                                     . =="Slightly beneficial" ~ 2,
+                                                     . =="Moderately beneficial" ~ 3,
+                                                     . =="Very beneficial" ~ 4,
+                                                     . =="Extremely beneficial" ~ 5 ))) %>%
+
+# replace nuclear acceptance likert scale with numbers
+  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
+                                                                        . == "Somewhat disagree" ~ 2,
+                                                                        . == "Neither agree nor disagree" ~3,
+                                                                        . == "Somewhat agree" ~ 4,
+                                                                        . == "Strongly agree" ~ 5))) %>%
+
+# code likert scale for variables for Kahan scale into numbers
+  mutate_at(vars(starts_with (c("K_I","K_H","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE", "DEV", "PROSPER", "RELY"))), funs(case_when(. == "Strongly disagree" ~ 1, 
+               . == "Somewhat disagree" ~ 2,
+               . == "Neither agree nor disagree" ~3,
+               . == "Somewhat agree" ~ 4,
+               . == "Strongly agree" ~ 5))) %>%
+
+# reverse code for likert scale for variables for Kahan scale into numbers
+  mutate_at(vars(starts_with (c("K_S","K_E"))), funs(case_when(. == "Strongly disagree" ~ 5, 
+                                                               . == "Somewhat disagree" ~ 4,
+                                                               . == "Neither agree nor disagree" ~3,
+                                                               . == "Somewhat agree" ~ 2,
+                                                               . == "Strongly agree" ~ 1))) %>%
+
+# code eco-pol scale variables into numbers
+  mutate_at(vars(SYSTEMDEMO,SYSTEMRELIGION,SYSTEMTECHNO,SYSTEMTOTAL,WEALTHLIM,MECHANISATION,DECISIONDECEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG), funs(case_when(.
+== "Strongly disagree" ~ 1,
+                        . == "Somewhat disagree" ~ 2,
+                        . == "Neither agree nor disagree" ~3,
+                        . == "Somewhat agree" ~ 4,
+                        . == "Strongly agree" ~ 5))) %>%
+
+# reverse code eco-pol scale variables into numbers 
+ mutate_at(vars(DECISIONCEN, INDUSTRYSMALL, ECONOMYLOCAL, ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(. == "Strongly disagree" ~ 5, 
+                                                                                                         . == "Somewhat disagree" ~ 4,
+                                                                                                         . == "Neither agree nor disagree" ~3,
+                                                                                                         . == "Somewhat agree" ~ 2,
+                                                                                                         . == "Strongly agree" ~ 1)))
+
 ```
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+```{r, eval=TRUE, echo=FALSE}
+
+moduleone <- read_excel(here::here("thesis_surveydata/livelihood_insecurity_complete.xlsx"))
+module1 <- data.frame(moduleone)
+
+# loaded data set for module 2 eco -pol variables and removes the rows with question number and question text
+```
+
+```{r, eval =TRUE, echo=FALSE}
+#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
+codedmodule1 <- module1 %>%
+
+#remove row 1
+  filter(!row_number() %in% c(1,2)) %>%
+
+# replace risky likert scale with numbers
+  mutate_at(vars(starts_with("Risky")), funs(case_when(. =="Not at all risky" ~ 1, 
+                                                       . =="Slightly risky" ~ 2, 
+                                                       . =="Moderately risky" ~ 3, 
+                                                       . =="Very risky" ~ 4, 
+                                                       . =="Extremely risky" ~ 5))) %>%
+
+# replace beneficial likert scale with numbers  
+  mutate_at(vars(starts_with("Ben")), funs(case_when(. =="Not at all beneficial" ~ 1,
+                                                     . =="Slightly beneficial" ~ 2,
+                                                     . =="Moderately beneficial" ~ 3,
+                                                     . =="Very beneficial" ~ 4,
+                                                     . =="Extremely beneficial" ~ 5 ))) %>%
+
+# replace nuclear acceptance likert scale with numbers
+  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
+                                                                        . == "Somewhat disagree" ~ 2,
+                                                                        . == "Neither agree nor disagree" ~3,
+                                                                        . == "Somewhat agree" ~ 4,
+                                                                        . == "Strongly agree" ~ 5)))
+
+```
+
+```{r, echo = FALSE}
+
+suppressPackageStartupMessages(library(tidyselect))
+# combine codedmodule1 and codedmodule2
+
+numcol2 <- codedmodule2 %>% add_column(Respondent = 1:1099, .before = "Language") 
+numcol1 <- codedmodule1 %>% add_column(Respondent = 1099:2160, .before = "Language")
+
+joineddf <-  full_join(numcol2, numcol1, by = c("Respondent", "Language", "Survey_Date", "State", "Risky_Hydro", "Risky_Solar", "Risky_Wind", "Risky_Nuclear", "Risky_Coal", "Risky_Gas", "Risky_Oil", "Risky_INDHydro", "Risky_INDSolar", "Risky_INDWind", "Risky_INDBiogas", "Risky_INDDiesel", "Risky_INDKerosene", "Risky_INDFirewoodetc", "Risky_INDLPG", "Ben_Hydro", "Ben_Solar", "Ben_Wind", "Ben_Nuclear", "Ben_Coal", "Ben_Gas", "Ben_Oil", "Ben_INDHydro", "Ben_INDSolar", "Ben_INDWind", "Ben_INDDiesel", "Ben_INDBiogas", "Ben_INDFirewoodetc", "Ben_INDLPG", "Ben_INDKerosene", "N_accept", "N_reluctantlyaccept", "N_reject", "age", "urban_rural", "gender", "caste", "religion", "religiontext"))
+
+```
+
+#Urban population
+
+```{r, echo =FALSE}
+#Distribution checks 
+joineddf %>%
+  filter(urban_rural == "Urban") %>%
+  ggplot(aes(x=Risky_Nuclear, y = ..count..))+
+  geom_bar(fill = "firebrick2")+
+  labs(x= "Perceived Risk from Nuclear Energy", y = "Urban population")
+```
+
+```{r, echo =FALSE}
+
+joineddf %>%
+  filter(urban_rural == "Urban") %>%
+  ggplot(aes(x=Risky_Hydro, y = ..count..))+
+  geom_bar(fill = "firebrick2")+
+  labs(x= "Perceived Risk from Hydroelectric Dams", y = "Urban population")
+```
+
+```{r, echo =FALSE}
+
+joineddf %>%
+  filter(urban_rural == "Rural") %>%
+  ggplot(aes(x=Risky_Hydro, y = ..count..))+
+  geom_bar(fill = "firebrick2")+
+  labs(x= "Perceived Risk from Hydroelectric Dams", y = "Rural population")
+```
+
+```{r, echo =FALSE}
+#Distribution checks 
+joineddf %>%
+  filter(gender == "Male") %>%
+  ggplot(aes(x=Risky_Nuclear, y = ..count..))+
+  geom_bar(fill = "firebrick2")+
+  labs(x= "Perceived Risk from Nuclear Energy", y = "male population")
+```
+
+```{r, echo =FALSE}
+#Distribution checks 
+joineddf %>%
+  filter(gender == "Female") %>%
+  ggplot(aes(x=Risky_Nuclear, y = ..count..))+
+  geom_bar(fill = "firebrick2")+
+  labs(x= "Perceived Risk from Nuclear Energy", y = "Female population")
+```

### 2022-04-12 module2/module2IVgraphs.Rmd
data frame tables for DV graphs html file
enter explanatory text for module2IV graphs

--- 2022-04-10 module2/module2IVgraphs.Rmd
@@
 
+# **Coded Dataset for survey module 2**
 ```{r, echo = FALSE}
@@
 
-codedmodule2
+data.frame(codedmodule2)
 
@@
   #melt to long format
-  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd) %>%
+  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd,Risky_Hydro_n, Risky_Solar_n, Risky_Wind_n, Risky_Nuclear_n, Risky_Coal_n, Risky_Gas_n, Risky_Oil_n) %>%
   select(SYSTEMDEMO, technology, summary) %>%
@@
   #melt to long format
-  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd) %>%
+  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd, Risky_Hydro_n, Risky_Solar_n, Risky_Wind_n, Risky_Nuclear_n, Risky_Coal_n, Risky_Gas_n, Risky_Oil_n) %>%
   select(SYSTEMTECHNO, technology, summary) %>%
@@
   #melt to long format
-  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd) %>%
+  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd, Risky_Hydro_n, Risky_Solar_n, Risky_Wind_n, Risky_Nuclear_n, Risky_Coal_n, Risky_Gas_n, Risky_Oil_n) %>%
   select(SYSTEMRELIGION, technology, summary) %>%
@@
   #melt to long format
-  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd) %>%
+  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd, Risky_Hydro_n, Risky_Solar_n, Risky_Wind_n, Risky_Nuclear_n, Risky_Coal_n, Risky_Gas_n, Risky_Oil_n) %>%
   select(SYSTEMTOTAL, technology, summary) %>%
@@
 
+# **Perceived risk by Preferred Government Type**
+
+The following is a list of statements about governance.
+How strongly do you agree or disagree with each of these statements?
+Do you strongly disagree(1), somewhat disagree(2), neither agree nor disagree(3), somewhat agree(4) or strongly agree(5)?
+
+Plotted only strongly agree(5) for four government types.
+
 ```{r, echo=FALSE}
@@
 
-ggplot(govtgraph, aes(x = technology, y= mean, group = Govt))+
-  geom_line(aes(colour = Govt, line = Govt)) 
+data.frame(govtgraph)
+
+p <- ggplot(govtgraph, aes(x = technology, y= mean, group = Govt))+
+  geom_line(aes(colour = Govt, line = Govt)) +
+  labs(y = "mean perceived risk", x = "energy technology")
+
+update_labels(p, list(colour = "Preferred Government Type"))
   #ylim(0,4)
@@
 
+# **Perceived risk by Support for Democratic government**
+
+The following is a list of statements about governance.
+How strongly do you agree or disagree with each of these statements?
+Do you strongly disagree(1), somewhat disagree(2), neither agree nor disagree(3), somewhat agree(4) or strongly agree(5)?
+- It is very important to have a democratic political system because it ensures that no individual leader has too much power.
+
+Plotted only strongly disagree(1) and strongly agree(5)
+
+```{r, echo=FALSE}
+
+demorisk2 <- codedmodule2%>%
+  group_by(SYSTEMDEMO)%>%
+  filter(SYSTEMDEMO %in% c(1, 5))%>%
+  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
+  #melt to long format
+  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd, Risky_Hydro_n, Risky_Solar_n, Risky_Wind_n, Risky_Nuclear_n, Risky_Coal_n, Risky_Gas_n, Risky_Oil_n) %>%
+  select(SYSTEMDEMO, technology, summary) %>%
+  # separate risky from variable suffix
+  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
+  #separate mean from variable prefix
+  separate(var, c("technology", "meansd")) %>%
+  # spread summary values back to wide form
+  spread(meansd,summary) %>%
+  #clean up
+  select(-Risky)%>%
+  arrange(SYSTEMDEMO)
+
+data.frame(demorisk2)
+
+d <- demorisk2 %>%
+  group_by(technology) %>%
+  ggplot(aes(x = technology, y= mean, group = SYSTEMDEMO))+
+  geom_line(aes(colour = SYSTEMDEMO, line = SYSTEMDEMO)) +
+   labs(y = "mean perceived risk", x = "energy technology")
+
+update_labels(d, list(colour = "Support for Democratic Government"))
+
+```
+
+# **Perceived risk by Support for decentralised governance**
+
+```{r, echo=FALSE}
+
+decenrisk2 <- codedmodule2%>%
+    select(starts_with(c("Risky","Ben","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
+  rowwise()%>%
+  dplyr::mutate(Pro_decentralisation = mean(c_across("DECISIONDECEN":"DECISIONCEN"))) %>%
+  group_by(Pro_decentralisation)%>%
+  filter(Pro_decentralisation %in% c(1, 5))%>%
+  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
+  #melt to long format
+  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd,Risky_Hydro_n, Risky_Solar_n, Risky_Wind_n, Risky_Nuclear_n, Risky_Coal_n, Risky_Gas_n, Risky_Oil_n ) %>%
+  select(Pro_decentralisation, technology, summary) %>%
+  # separate risky from variable suffix
+  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
+  #separate mean from variable prefix
+  separate(var, c("technology", "meansd")) %>%
+  # spread summary values back to wide form
+  spread(meansd,summary) %>%
+  #clean up
+  select(-Risky)%>%
+  arrange(Pro_decentralisation)
+
+data.frame(decenrisk2)
+
+decen <- decenrisk2 %>%
+  group_by(technology) %>%
+  ggplot(aes(x = technology, y= mean, group = Pro_decentralisation))+
+  geom_line(aes(colour = Pro_decentralisation, line = Pro_decentralisation))+
+  ylim(1,4)+
+  labs(y = "mean perceived risk", x = "energy technology")
+
+update_labels(decen, list(colour = "Pro decentralised governance"))
+```
+
+# **Perceived risk by Support for large scale industry**
+
+```{r, echo=FALSE}
+
+largerisk2 <- codedmodule2%>%
+    select(starts_with(c("Risky","Ben","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
+  rowwise()%>%
+  dplyr::mutate(Pro_largescale = sum(c_across("INDUSTRYLARGE":"INDUSTRYSMALL"))) %>%
+  group_by(Pro_largescale)%>%
+  filter(Pro_largescale%in% c(2, 10))%>%
+  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
+  #melt to long format
+  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd, Risky_Hydro_n, Risky_Solar_n, Risky_Wind_n, Risky_Nuclear_n, Risky_Coal_n, Risky_Gas_n, Risky_Oil_n) %>%
+  select(Pro_largescale, technology, summary) %>%
+  # separate risky from variable suffix
+  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
+  #separate mean from variable prefix
+  separate(var, c("technology", "meansd")) %>%
+  # spread summary values back to wide form
+  spread(meansd,summary) %>%
+  #clean up
+  select(-Risky)%>%
+  arrange(Pro_largescale)
+
+data.frame(largerisk2)
+
+l<- largerisk2 %>%
+  group_by(technology) %>%
+  ggplot(aes(x = technology, y= mean, group = Pro_largescale))+
+  geom_line(aes(colour = Pro_largescale, line = Pro_largescale))+
+  ylim(1,4)+
+  labs(y = "mean perceived risk", x = "energy technology")
+
+update_labels(l, list(colour = "Pro large scale industry"))
+```
+
+```{r, echo=FALSE}
+
+#globalrisk2 <- codedmodule2%>%
+#    select(starts_with(c("Risky","Ben","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
+#  rowwise()%>%
+#  dplyr::mutate(Pro_global = sum(c_across("ECONOMYGLOBAL":"ECONOMYLOCAL"))) %>%
+#  group_by(Pro_global)%>%
+#  filter(Pro_global%in% c(2, 10))%>%
+#  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
+  #melt to long format
+#  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd) %>%
+#  select(Pro_global, technology, summary) %>%
+  # separate risky from variable suffix
+#  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
+  #separate mean from variable prefix
+#  separate(var, c("technology", "meansd")) %>%
+  # spread summary values back to wide form
+#  spread(meansd,summary) %>%
+  #clean up
+#  select(-Risky)%>%
+#  arrange(mean)
+
+#globalrisk2 %>%
+#  group_by(technology) %>%
+#  ggplot(aes(x = technology, y= mean, group = Pro_global))+
+#  geom_line(aes(colour = Pro_global, line = Pro_global))+
+#  ylim(1,4)
+```
+
+```{r, echo=FALSE}
+
+#envrisk2 <- codedmodule2%>%
+#    select(starts_with(c("Risky","Ben","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
+#  rowwise()%>%
+#  group_by(ENVOVERDEV)%>%
+#  filter(ENVOVERDEV%in% c(1, 5))%>%
+#  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
+  #melt to long format
+#  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd) %>%
+#  select(ENVOVERDEV, technology, summary) %>%
+  # separate risky from variable suffix
+#  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
+  #separate mean from variable prefix
+#  separate(var, c("technology", "meansd")) %>%
+  # spread summary values back to wide form
+#  spread(meansd,summary) %>%
+  #clean up
+#  select(-Risky)%>%
+#  arrange(mean)
+
+#envrisk2 %>%
+#  group_by(technology) %>%
+#  ggplot(aes(x = technology, y= mean, group = ENVOVERDEV))+
+#  geom_line(aes(colour = ENVOVERDEV, line = ENVOVERDEV))+
+#  ylim(1,4)
+```
+
+```{r, echo=FALSE}
+
+#devrisk2 <- codedmodule2%>%
+#    select(starts_with(c("Risky","Ben","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
+#  rowwise()%>%
+#  group_by(DEVOVERENV)%>%
+#  filter(DEVOVERENV%in% c(1, 5))%>%
+#  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
+  #melt to long format
+#  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd) %>%
+#  select(DEVOVERENV, technology, summary) %>%
+  # separate risky from variable suffix
+#  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
+  #separate mean from variable prefix
+#  separate(var, c("technology", "meansd")) %>%
+  # spread summary values back to wide form
+#  spread(meansd,summary) %>%
+  #clean up
+#  select(-Risky)%>%
+#  arrange(mean)
+
+#devrisk2 %>%
+#  group_by(technology) %>%
+#  ggplot(aes(x = technology, y= mean, group = DEVOVERENV))+
+#  geom_line(aes(colour = DEVOVERENV, line = DEVOVERENV))+
+#  ylim(1,4)
+```
+
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+#calculating individualism score and hierarchy score for each respondent
+
+Kscalescores <- codedmodule2 %>%
+  select(starts_with(c("Risky","K_I","K_S", "K_H", "K_E")))%>%
+  rowwise()%>%
+  na.omit()%>%
+  dplyr::mutate(Individualism_score = mean(c_across(K_IINTRFER:K_SPROTECT)))%>%
+  dplyr::mutate(Hierarchy_score = mean(c_across(K_HEQUAL:K_ERADEQ2)))%>%
+  dplyr::select(!starts_with(c("K_I","K_S", "K_H", "K_E")))
+
+```
+
+# **Scatter plot of Kahan scale scores around the median scores on Individualism and Hierarchy scales**
+
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+
+#scatter plot of Kahan scale scores around the median scores on Individualism and Hierarchy scales.
+
+Kscalescores %>%
+  ggplot(aes(Individualism_score, Hierarchy_score))+
+  geom_count(aes(color = ..n.., size = ..n..))+
+  guides(color = 'legend')+
+  geom_hline(yintercept=2, colour="black", lwd=1)+
+  geom_vline(xintercept=3, colour="black", lwd=1)+
+  labs(x = " Communitarianism to Individualism", y = "Egalitarianism to Hierarchy")
+
+```
+
+# **Scatter plot for pro decentralised governance against perceived risks from rooftop solar**
+
 ```{r, echo=FALSE}
@@
 ecopolscalescores <- codedmodule2 %>%
-  select(starts_with(c("Risky","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
+  select(starts_with(c("Risky","Ben","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
   rowwise()%>%
-  dplyr::mutate(Pro_decentralisation = mean(c_across("DECISIONDECEN":"DECISIONCEN")))%>%
+  dplyr::mutate(Pro_decentralisation = sum(c_across("DECISIONDECEN":"DECISIONCEN")))%>%
    dplyr::mutate(Pro_largescale = mean(c_across("INDUSTRYLARGE":"INDUSTRYSMALL")))%>%
@@
    dplyr::mutate(Pro_private = mean(c_across("OWNERPVT":"OWNERREG")))%>%
-  dplyr::select(!c("DECISIONDECEN","DECISIONCEN", "INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL", "ECONOMYLOCAL","ENVOVERDEV",     "DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")) %>%
+  #dplyr::select(!c("DECISIONDECEN","DECISIONCEN", "INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL", "ECONOMYLOCAL","ENVOVERDEV",     "DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")) %>%
     na.omit()
 
-ggplot(ecopolscalescores, aes(Pro_decentralisation, Risky_Hydro))+
-  geom_point()
+ggplot(ecopolscalescores, aes(Pro_decentralisation, Risky_INDSolar))+
+  geom_count()+
+  labs(x = "Pro decentralised governance", y = " Perceived risks from rooftop solar")
 

### 2022-04-12 module2/moduletwoanalysis.Rmd
enter explanatory text for module2IV graphs

@@
 
-write_csv(codedmodule2,"Macintosh HD\\Users\\prernagupta\\my documents\\codedmodule2.csv")
 ```
@@
   ggplot(aes(Individualism_score, Hierarchy_score))+
-  geom_point()+
+  geom_count(aes(color = ..n.., size = ..n..))+
+  guides(color = 'legend')+
   geom_hline(yintercept=2, colour="black", lwd=1)+

### 2023-02-04 combined data set/DVgraphs.Rmd
conducting the Kruskal wallis test on DVs

@@
 output:
+  pdf_document:
+    toc: yes
+    number_sections: yes
+    toc_depth: 2
+    fig_width: 9
+    fig_height: 6
+    fig_caption: yes
   html_document:
@@
     df_print: paged
-  pdf_document:
-    toc: yes
-    number_sections: yes
-    toc_depth: 2
-    fig_width: 9
-    fig_height: 6
-    fig_caption: yes
 ---
@@
 suppressPackageStartupMessages(library(ggplot2))
-suppressPackageStartupMessages(library(ggbiplot))
 suppressPackageStartupMessages(library(psych)) # psychometrics
@@
 suppressPackageStartupMessages(library(tidyselect))
-# combine codedmodule1 and codedmodule2
+# combine codedmodule1 and codedmodule2. Therefore these graphs are made on the combined data set from both the surveys.
 
@@
 ```
+
+\newpage
 
@@
 
+\newpage
+
 ## Q2.
@@
 ```
+\newpage
 
@@
 
+\newpage
+
 ```{r, echo=FALSE}
@@
  center_barplot%>% 
-  ggplot(aes(x=technology, y= mean, fill =  (factor(center_barplot$level, levels = c("perceivedrisk.mean", "perceivedbenefit.mean")))))+
+  ggplot(aes(x=technology, y= mean, fill =  (factor(level, levels = c("perceivedrisk.mean", "perceivedbenefit.mean")))))+
   geom_bar(stat="identity", position=position_dodge())+
@@
 ```
+
+```{r, echo=FALSE}
+
+library(dplyr)
+library(tidyr)
+
+perceivedrisk <-joineddf %>% select(starts_with("Risky")) %>%
+  gather(key = "technology", value = "perceived_risk") %>% 
+  mutate(technology = gsub("Risky_", "", technology)) %>%
+  na.omit()
+
+perceivedrisk
+
+```
+
+```{r}
+# checking assumptions for kruskal wallis test
+
+duplicated(joineddf)
+sum(duplicated(joineddf))
+
+# there are no duplicate responses in our dataframe :).
+
+ggplot(perceivedrisk, aes(x = perceived_risk, y = technology)) + 
+  geom_boxplot()
+
+levels(perceivedrisk$technology)
+
+bartlett.test(perceived_risk ~ technology, data = perceivedrisk)
+
+str(perceivedrisk)
+
+```
+
+```{r, echo=FALSE}
+# create a list of technology levels
+tech_levels <- unique(perceivedrisk$technology)
+
+# perform Shapiro test for each technology
+shapiro_results <- lapply(tech_levels, function(x) {
+  shapiro.test(perceivedrisk$perceived_risk[perceivedrisk$technology == x])
+})
+
+#extract the W and p-value from the htest object 
+shapiro_results_df <- data.frame(W = sapply(shapiro_results, function(x) x$statistic),
+                                  p.value = sapply(shapiro_results, function(x) x$p.value), 
+                                  technology = tech_levels)
+
+```
+
+```{r}
+# load the stats package
+library(stats)
+
+perceivedrisk$technology <- factor(perceivedrisk$technology)
+
+# perform the Kruskal-Wallis H-test, the technologies are treated as independent groups and the mean of perceived risk is of interest. 
+kruskal_result <- kruskal.test(perceived_risk ~ technology, data = perceivedrisk)
+
+# print the test statistic and p-value
+print(kruskal_result)
+
+library(emmeans)
+emm_results <- emmeans(kruskal_results, ~ technology)
+summary(emm_results, infer = c(T, T))
+
+```
+
+```{r}
+
+library(dplyr)
+ggplot(perceivedrisk %>%
+  mutate(technology = reorder(technology, perceived_risk, FUN = median)), 
+         aes(x = technology, y = perceived_risk)) +
+  geom_boxplot(width = 0.5) +
+  geom_hline(aes(yintercept = median(perceived_risk)), linetype = "dashed", color = "red") +
+  coord_flip()
+
+```
+
+```{r}
+library(dplyr)
+perceivedrisk %>%
+  group_by(technology) %>%
+  summarise(
+    count = n(),
+    mean = mean(perceived_risk, na.rm = TRUE),
+    sd = sd(perceived_risk, na.rm = TRUE),
+    median = median(perceived_risk, na.rm = TRUE),
+    IQR = IQR(perceived_risk, na.rm = TRUE)
+  )
+
+```
+```{r}
+
+pairwise.wilcox.test(perceivedrisk$perceived_risk, perceivedrisk$technology, p.adjust.method = "BH")
+
+```
+
+```{r}
+
+# visualising the pairwaise wilcox test results. the non significant pairs are grey
+
+library(broom)
+result <- pairwise.wilcox.test(perceivedrisk$perceived_risk, perceivedrisk$technology, p.adjust.method = "BH")
+tidy_result <- tidy(result)
+
+library(ggplot2)
+ggplot(tidy_result, aes(x = group1, y = group2, fill = p.value)) + 
+  geom_tile(color = "white") + 
+  scale_fill_gradient2(low = "red", high = "white", midpoint = 0.025, 
+                       limits = c(0, 0.05), space = "Lab", 
+                       name = "P-value") + 
+  theme_classic() + 
+  labs(x = "Technology 1", y = "Technology 2") + 
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+
+```
+
+```{r}
+#now do the same for perceived benefit
+#null hypothesis - no sognificant difference between perceived benefit from technologies. 
+#push to github - figure out what happened! why not pushing anymore yaar 
+#
+
+```
+
+```{r, echo=FALSE}
+library(dplyr)
+library(tidyr)
+
+perceivedbenefit <-joineddf %>% select(starts_with("Ben")) %>%
+  gather(key = "technology", value = "perceived_benefit") %>% 
+  mutate(technology = gsub("Ben_", "", technology)) %>%
+  na.omit()
+
+perceivedbenefit
+
+```
+
+```{r}
+# checking assumptions for kruskal wallis test
+
+duplicated(joineddf)
+sum(duplicated(joineddf))
+
+# there are no duplicate responses in our dataframe :).
+
+#what was I doing here - check again ? assumptions for running it on perceived benefit
+
+ggplot(perceivedbenefit, aes(x = perceived_benefit, y = technology)) + 
+  geom_boxplot()
+
+levels(perceivedbenefit$technology)
+
+bartlett.test(perceived_benefit ~ technology, data = perceivedbenefit)
+
+str(perceivedbenefit)
+
+```
+
+```{r}
+# load the stats package
+library(stats)
+
+perceivedbenefit$technology <- factor(perceivedbenefit$technology)
+
+# perform the Kruskal-Wallis H-test, the technologies are treated as independent groups and the mean of perceived risk is of interest. 
+kruskal_resultben <- kruskal.test(perceived_benefit ~ technology, data = perceivedbenefit)
+
+# print the test statistic and p-value
+print(kruskal_resultben)
+
+```
+
+```{r}
+
+library(dplyr)
+ggplot(perceivedbenefit %>%
+  mutate(technology = reorder(technology, perceived_benefit, FUN = median)), 
+         aes(x = technology, y = perceived_benefit)) +
+  geom_boxplot(width = 0.5) +
+  geom_hline(aes(yintercept = median(perceived_benefit)), linetype = "dashed", color = "red") +
+  coord_flip()
+
+```
+```{r}
+library(dplyr)
+perceivedbenefit %>%
+  group_by(technology) %>%
+  summarise(
+    count = n(),
+    mean = mean(perceived_benefit, na.rm = TRUE),
+    sd = sd(perceived_benefit, na.rm = TRUE),
+    median = median(perceived_benefit, na.rm = TRUE),
+    IQR = IQR(perceived_benefit, na.rm = TRUE)
+  )
+
+```
+
+```{r}
+
+pairwise.wilcox.test(perceivedbenefit$perceived_benefit, perceivedbenefit$technology, p.adjust.method = "BH")
+
+```
+
+```{r}
+
+# visualising the pairwaise wilcox test results. the non significant pairs are grey
+
+library(broom)
+result <- pairwise.wilcox.test(perceivedbenefit$perceived_benefit, perceivedbenefit$technology, p.adjust.method = "BH")
+tidy_result <- tidy(result)
+
+library(ggplot2)
+ggplot(tidy_result, aes(x = group1, y = group2, fill = p.value)) + 
+  geom_tile(color = "white") + 
+  scale_fill_gradient2(low = "green", high = "white", midpoint = 0.025, 
+                       limits = c(0, 0.05), space = "Lab", 
+                       name = "P-value") + 
+  theme_classic() + 
+  labs(x = "Technology 1", y = "Technology 2") + 
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+
+```

### 2023-02-04 combined data set/demographicvariables.Rmd
conducting the Kruskal wallis test on DVs

@@
 
+\newpage
+
 ## Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by gender and caste groups
@@
 
+\newpage
+
 ## Perceived Benefit Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by gender and caste groups
@@
 
+\newpage
+
 ## Perceived Benefit Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by gender and caste groups
@@
 
+\newpage
 ## Perceived Risk Scores for centrally managed hydroelectric dams by gender and caste groups
@@
 ```
+
+\newpage
+
 ## Perceived Benefit Scores for centrally managed hydroelectric dams by gender and caste groups
@@
 
+\newpage
 ## Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by urban or rural location of the respondent
@@
 
+\newpage
 ## Perceived Benefit Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by urban or rural location of the respondent
@@
 
+\newpage
+
 ## Perceived Benefit Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by gender
@@
 
-## Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by gender.
+\newpage
+
+## Perceived Benefit Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by gender.
 
@@
 
+\newpage
+
 ## Perceived Benefit Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by religion
@@
 
+\newpage
 ## Perceived Benefit Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by religion.
@@
 
+\newpage
+
 ## Perceived Benefit Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by age
@@
 
-## Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by age.
+\newpage
+
+## Perceived Benefit Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by age.
 
@@
 
+\newpage
 ## Perceived Benefit Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by state

### 2023-02-04 module2/module2IVgraphs.Rmd
conducting the Kruskal wallis test on DVs

@@
 output:
-  html_document:
-    fig_width: 9
-    fig_height: 6
-    fig_caption: yes
-    keep_md: yes
-    theme: paper
-    df_print: paged
 
@@
     fig_caption: yes
+  html_document:
+    fig_width: 9
+    fig_height: 6
+    fig_caption: yes
+    keep_md: yes
+    theme: paper
+    df_print: paged
 ---
@@
 
-# **Coded Dataset for survey module 2**
 ```{r, echo = FALSE}
@@
                                                                                                          . == "Strongly agree" ~ 1)))
-
-data.frame(codedmodule2)
 
@@
 
+\newpage
+
 # **Perceived risk by Preferred Government Type**
@@
 
+\newpage
 # **Perceived risk by Support for decentralised governance**

### 2023-02-09 combined data set/demographicvariables.Rmd
non parametric tests added for gender

@@
 
+```{r}
+#checking distribution of age
+
+library(ggplot2)
+
+ggplot(joineddf, aes(x = age)) +
+  geom_bar(fill = "blue", alpha = 0.5) +
+  labs(x = "Age", y = "Frequency") +
+  ggtitle("Distribution of Age")
+
+```
+
 \newpage
@@
                  position=position_dodge(.9))+
-  labs(x = "mean perceived risk", y = "GenderXCaste groups")
+  labs(x = "mean perceived benefit", y = "GenderXCaste groups")
 

### 2023-02-09 combined data set/demovariablesregression.Rmd
non parametric tests added for gender

--- 2022-04-12 combined data set/distributions.Rmd
@@
 ---
-title: "distributions"
+title: "demographicvariablesregression"
+
 output:
@@
 
+summary(joineddf)
+
 ```
 
-#Urban population
+```{r}
+library(dplyr)
 
-```{r, echo =FALSE}
-#Distribution checks 
-joineddf %>%
-  filter(urban_rural == "Urban") %>%
-  ggplot(aes(x=Risky_Nuclear, y = ..count..))+
-  geom_bar(fill = "firebrick2")+
-  labs(x= "Perceived Risk from Nuclear Energy", y = "Urban population")
+demovars <- joineddf %>%
+  select(starts_with("Risky"), starts_with("Ben"),urban_rural, gender, caste, religion, age, State)%>%
+  mutate(religion = ifelse(religion == "Other (Please mention)", "Other", religion))
+
+summary(demovars)
+table(demovars$gender)
+
 ```
 
-```{r, echo =FALSE}
+```{r}
+library(dplyr)
 
-joineddf %>%
-  filter(urban_rural == "Urban") %>%
-  ggplot(aes(x=Risky_Hydro, y = ..count..))+
-  geom_bar(fill = "firebrick2")+
-  labs(x= "Perceived Risk from Hydroelectric Dams", y = "Urban population")
+demovars_frisk <- demovars %>%
+  select(starts_with("Risky"), gender) %>%
+  filter(gender == "Female")%>%
+  na.omit()
+
+demovars_mrisk <- demovars %>%
+  select(starts_with("Risky"), gender) %>%
+  filter(gender == "Male") %>%
+  na.omit()
+
+sum_frisk <- demovars_frisk %>% 
+    summarise(across(starts_with("Risky"), list(mean = mean, sd = sd, median = median, n = nrow))) %>%
+    pivot_longer(cols = starts_with("Risky"), 
+                                          names_to = c("Risky", "Technology", "stat"), 
+                                          names_sep =  "_",
+                                          values_to = "Value")%>%
+    select(-Risky) %>%
+    pivot_wider(names_from = stat, values_from = Value)%>%
+    mutate(gender = "f")
+
+sum_mrisk <- demovars_mrisk %>% 
+    summarise(across(starts_with("Risky"), list(mean = mean, sd = sd, median = median, n = nrow))) %>%
+    pivot_longer(cols = starts_with("Risky"), 
+                                          names_to = c("Risky", "Technology", "stat"), 
+                                          names_sep =  "_",
+                                          values_to = "Value")%>%
+
+    select(-Risky) %>%
+    pivot_wider(names_from = stat, values_from = Value)%>%
+    mutate(gender = "m")
+
 ```
 
-```{r, echo =FALSE}
+```{r}
+library(ggplot2)
 
-joineddf %>%
-  filter(urban_rural == "Rural") %>%
-  ggplot(aes(x=Risky_Hydro, y = ..count..))+
-  geom_bar(fill = "firebrick2")+
-  labs(x= "Perceived Risk from Hydroelectric Dams", y = "Rural population")
+# Combine the two datasets
+sum_gender <- rbind(sum_frisk, sum_mrisk)
+
+# Plot
+
+p1 <- sum_gender%>% 
+  filter(Technology %in% c("Wind","Nuclear","Solar","Oil","Hydro","Gas","Coal")) %>%
+  ggplot(aes(x=Technology, y= mean, fill = gender))+
+  geom_bar(stat="identity", position=position_dodge())+
+  #geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=0.2, position=position_dodge(0.9)) +
+  ylim(0,5)+
+  scale_fill_manual(values=c("red", "blue"), name="legend")+
+  labs(y = "Mean perceivd risk", x = "Energy Technologies")+
+  ggtitle("Perceived risk and benefit from centrally owned energy technologies by gender")+
+  theme(axis.text.x = element_text(angle=90, hjust=1, vjust=0.5))
+
+p2 <- sum_gender%>% 
+  filter(Technology %in% c("INDHydro", "INDSolar", "INDWind", "INDBiogas","INDDiesel", "INDKerosene","INDFirewoodetc","INDLPG")) %>%
+  ggplot(aes(x=Technology, y= mean, fill = gender))+
+  geom_bar(stat="identity", position=position_dodge())+
+  #geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=0.2, position=position_dodge(0.9)) +
+  ylim(0,5)+
+  scale_fill_manual(values=c("red", "blue"), name="legend")+
+  labs(y = "Mean perceived risk", x = "Energy Technologies")+
+  ggtitle("Perceived risk and benefit from individually owned energy technologies by gender")+
+  theme(axis.text.x = element_text(angle=90, hjust=1, vjust=0.5))
+
+library(gridExtra)
+grid.arrange(p1, p2, ncol = 2)
+
 ```
 
-```{r, echo =FALSE}
-#Distribution checks 
-joineddf %>%
-  filter(gender == "Male") %>%
-  ggplot(aes(x=Risky_Nuclear, y = ..count..))+
-  geom_bar(fill = "firebrick2")+
-  labs(x= "Perceived Risk from Nuclear Energy", y = "male population")
+```{r}
+
+# conducting 
+library(stats)
+
+male_risk <- demovars[demovars$gender == "Male",]$Risky_Nuclear
+female_risk <- demovars[demovars$gender == "Female",]$Risky_Nuclear
+
+wilcox.test(male_risk, female_risk, alternative = "two.sided")
+
+library(dplyr)
+library(purrr)
+
+demovars %>% 
+  filter(gender %in% c("Male", "Female"))%>%
+  select(starts_with("Risky")) %>% 
+  lapply(function(col) wilcox.test(col ~ gender, data = demovars))
+
 ```
-
-```{r, echo =FALSE}
-#Distribution checks 
-joineddf %>%
-  filter(gender == "Female") %>%
-  ggplot(aes(x=Risky_Nuclear, y = ..count..))+
-  geom_bar(fill = "firebrick2")+
-  labs(x= "Perceived Risk from Nuclear Energy", y = "Female population")
-```

### 2023-02-10 combined data set/demovariablesregression.Rmd
mean to median in graphs

@@
   filter(Technology %in% c("Wind","Nuclear","Solar","Oil","Hydro","Gas","Coal")) %>%
-  ggplot(aes(x=Technology, y= mean, fill = gender))+
+  ggplot(aes(x=Technology, y= median, fill = gender))+
   geom_bar(stat="identity", position=position_dodge())+
@@
   scale_fill_manual(values=c("red", "blue"), name="legend")+
-  labs(y = "Mean perceivd risk", x = "Energy Technologies")+
+  labs(y = "Median perceivd risk", x = "Energy Technologies")+
   ggtitle("Perceived risk and benefit from centrally owned energy technologies by gender")+
@@
   filter(Technology %in% c("INDHydro", "INDSolar", "INDWind", "INDBiogas","INDDiesel", "INDKerosene","INDFirewoodetc","INDLPG")) %>%
-  ggplot(aes(x=Technology, y= mean, fill = gender))+
+  ggplot(aes(x=Technology, y= median, fill = gender))+
   geom_bar(stat="identity", position=position_dodge())+
@@
   scale_fill_manual(values=c("red", "blue"), name="legend")+
-  labs(y = "Mean perceived risk", x = "Energy Technologies")+
+  labs(y = "Median perceived risk", x = "Energy Technologies")+
   ggtitle("Perceived risk and benefit from individually owned energy technologies by gender")+
@@
 
-# conducting 
+# conducting non-parametric procedure : "Wilcoxon rank-sum test" to see how perception of risk may differ according to gender. 
 library(stats)
+library(dplyr)
+library(purrr)
+library(broom)
 
@@
 
-library(dplyr)
-library(purrr)
-
-demovars %>% 
+wilcox_gender <- demovars %>% 
   filter(gender %in% c("Male", "Female"))%>%
@@
 
+wilcox_gender <- do.call(rbind, wilcox_gender)
+
+wilcox_gender
+
 ```
+```{r}
+
+# for making a data frame from wilcox test
+#wilcox_gender <- demovars %>% 
+  #filter(gender %in% c("Male", "Female"))%>%
+  #select(starts_with("Risky")) %>% 
+  #lapply(function(col) broom::tidy(wilcox.test(col ~ gender, data = demovars)))
+
+#wilcox_gender <- do.call(rbind, wilcox_gender)
+
+#wilcox_gender$variable <- rownames(wilcox_gender)
+
+#wilcox_gender <- as.data.frame(wilcox_gender)
+```

### 2023-02-15 combined data set/demovariablesregression.Rmd
wilcoxon rank sum test on caste and urban_rural

--- 2023-02-09 combined data set/demovariablesregression.Rmd
@@
 
-summary(joineddf)
-
 ```
@@
   mutate(religion = ifelse(religion == "Other (Please mention)", "Other", religion))
-
-summary(demovars)
-table(demovars$gender)
 
@@
   scale_fill_manual(values=c("red", "blue"), name="legend")+
-  labs(y = "Mean perceivd risk", x = "Energy Technologies")+
+  labs(y = "Median perceivd risk", x = "Energy Technologies")+
   ggtitle("Perceived risk and benefit from centrally owned energy technologies by gender")+
-  theme(axis.text.x = element_text(angle=90, hjust=1, vjust=0.5))
+  theme(axis.text.x = element_text(angle=90, hjust=1, vjust=0.5))+
+  annotate("text", x=c("Solar", "Nuclear", "Coal"), y=4.8, label="*", size=10, fontface="bold") +
+  theme(axis.text.x = element_text(angle=90, hjust=1, vjust=0.5, size=12, margin=margin(l=50)))
 
@@
   scale_fill_manual(values=c("red", "blue"), name="legend")+
-  labs(y = "Mean perceived risk", x = "Energy Technologies")+
+  labs(y = "Median perceived risk", x = "Energy Technologies")+
   ggtitle("Perceived risk and benefit from individually owned energy technologies by gender")+
-  theme(axis.text.x = element_text(angle=90, hjust=1, vjust=0.5))
+  theme(axis.text.x = element_text(angle=90, hjust=1, vjust=0.5)) +
+  annotate("text", x=c("INDSolar", "INDBiogas", "INDDiesel"), y=4.8, label="*", size=10, fontface="bold") +
+  theme(axis.text.x = element_text(angle=90, hjust=1, vjust=0.5, size=12, margin=margin(l=50)))
 
 library(gridExtra)
-grid.arrange(p1, p2, ncol = 2)
+grid.arrange(p1, p2, ncol = 2, widths = NULL)
 
@@
 
-# conducting 
+# conducting non-parametric procedure : "Wilcoxon rank-sum test" to see how perception of risk may differ according to gender.
+
+library(broom)
 library(stats)
+library(dplyr)
 
-male_risk <- demovars[demovars$gender == "Male",]$Risky_Nuclear
+male_risk<- demovars[demovars$gender == "Male",]$Risky_Nuclear 
 female_risk <- demovars[demovars$gender == "Female",]$Risky_Nuclear
@@
 
-library(dplyr)
-library(purrr)
+Cmale_risk<- demovars[demovars$gender == "Male",]$Risky_Coal 
+Cfemale_risk <- demovars[demovars$gender == "Female",]$Risky_Coal
 
-demovars %>% 
-  filter(gender %in% c("Male", "Female"))%>%
+wilcox.test(Cmale_risk, Cfemale_risk, alternative = "two.sided")
+
+demovars_mf <- demovars %>% 
+  filter(gender %in% c("Male", "Female"))
+
+wilcox_gender <- demovars_mf %>%
   select(starts_with("Risky")) %>%
-  lapply(function(col) wilcox.test(col ~ gender, data = demovars))
+  lapply(function(col) wilcox.test(col ~ gender, data = demovars_mf))
+
+wilcox_mf <- do.call(rbind, wilcox_gender)
+
+# results from this are used to mark significant differences in the bar graph above.
 
 ```
+
+```{r}
+library(ggplot2)
+library(dplyr)
+library(tidyr)
+
+demovars_caste_long <- demovars_caste %>%
+  pivot_longer(cols = starts_with("Risky_"), names_to = "technology", values_to = "perceived_risk") %>%
+  mutate(technology = gsub("Risky_", "", technology)) %>%
+        mutate(caste = ifelse(grepl("SC|Scheduled caste", caste), "SC", caste),
+              caste = ifelse(grepl("ST|Scheduled Tribe", caste), "ST", caste),
+              caste = ifelse(grepl("OBC|Other Backward Classes", caste), "OBC", caste))
+
+```
+
+```{r}
+
+library(ggplot2)
+
+# Subset dataframe with IND prefix
+demovars_caste_long_ind <- demovars_caste_long %>% 
+  filter(str_starts(technology, "IND"))%>%
+   group_by(caste, technology) %>% 
+  summarize(median_perceived_risk = median(perceived_risk))
+
+table(demovars_caste_long_ind)
+
+# Create bar graph with IND prefix 
+ggplot(demovars_caste_long_ind, aes(x = technology, y = median_perceived_risk, fill = caste)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  labs(title = "Median Perceived Risk by Caste Groups for Technologies with IND Prefix",
+       x = "Technology", y = "Median Perceived Risk") +
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) # Rotate x-axis labels
+
+# Subset dataframe without IND prefix
+demovars_caste_long_not_ind <- demovars_caste_long %>% 
+  filter(!str_starts(technology, "IND"))%>%
+   group_by(caste, technology) %>% 
+  summarize(median_perceived_risk = median(perceived_risk))
+
+# Create bar graph without IND prefix
+
+ggplot(demovars_caste_long_not_ind, aes(x = technology, y = median_perceived_risk, fill = caste)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  labs(title = "Median Perceived Risk by Caste Groups for Technologies without IND Prefix",
+       x = "Technology", y = "Median Perceived Risk") +
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) # Rotate x-axis labels
+
+```
+```{r}
+
+# print the head of the file
+head(demovars_caste_long)
+
+# Show the group/caste levels
+
+demovars_caste_long$caste <- factor(demovars_caste_long$caste)
+levels(demovars_caste_long$caste)
+
+# compute summary statistic by groups 
+library(dplyr)
+summary_caste <- group_by(demovars_caste_long, caste) %>%
+  summarise(
+    count = n(),
+    mean = mean(perceived_risk, na.rm = TRUE),
+    sd = sd(perceived_risk, na.rm = TRUE),
+    median = median(perceived_risk, na.rm = TRUE),
+    IQR = IQR(perceived_risk, na.rm = TRUE)
+  )
+
+summary(summary_caste)
+
+library(ggplot2)
+
+# Create the box plot with median values
+
+```
+
+```{r}
+
+demovars_caste_long$technology <- factor(demovars_caste_long$technology)
+levels(demovars_caste_long$technology)
+
+kruskal.test(perceived_risk ~ caste, data = demovars_caste_long)
+
+pairwise.wilcox.test(demovars_caste_long$perceived_risk, demovars_caste_long$caste,
+                 p.adjust.method = "BH")
+
+library(dplyr)
+#for Nuclear
+Nuclear_caste <- demovars_caste_long %>%
+  filter(technology == "Nuclear")
+
+pairwise.wilcox.test(Nuclear_caste$perceived_risk, Nuclear_caste$caste,
+                 p.adjust.method = "BH")
+
+# For Coal
+Coal_caste <- demovars_caste_long %>%
+  filter(technology == "Coal")
+pairwise.wilcox.test(Coal_caste$perceived_risk, Coal_caste$caste, p.adjust.method = "BH")
+
+# For Gas
+Gas_caste <- demovars_caste_long %>%
+  filter(technology == "Gas")
+pairwise.wilcox.test(Gas_caste$perceived_risk, Gas_caste$caste, p.adjust.method = "BH")
+
+# For Hydro
+Hydro_caste <- demovars_caste_long %>%
+  filter(technology == "Hydro")
+pairwise.wilcox.test(Hydro_caste$perceived_risk, Hydro_caste$caste, p.adjust.method = "BH")
+
+# For INDBiogas
+INDBiogas_caste <- demovars_caste_long %>%
+  filter(technology == "INDBiogas")
+pairwise.wilcox.test(INDBiogas_caste$perceived_risk, INDBiogas_caste$caste, p.adjust.method = "BH")
+
+# For INDDiesel
+INDDiesel_caste <- demovars_caste_long %>%
+  filter(technology == "INDDiesel")
+pairwise.wilcox.test(INDDiesel_caste$perceived_risk, INDDiesel_caste$caste, p.adjust.method = "BH")
+
+# For INDFirewoodetc
+INDFirewoodetc_caste <- demovars_caste_long %>%
+  filter(technology == "INDFirewoodetc")
+pairwise.wilcox.test(INDFirewoodetc_caste$perceived_risk, INDFirewoodetc_caste$caste, p.adjust.method = "BH")
+
+# For INDHydro
+INDHydro_caste <- demovars_caste_long %>%
+  filter(technology == "INDHydro")
+pairwise.wilcox.test(INDHydro_caste$perceived_risk, INDHydro_caste$caste, p.adjust.method = "BH")
+
+# For INDKerosene
+INDKerosene_caste <- demovars_caste_long %>%
+  filter(technology == "INDKerosene")
+pairwise.wilcox.test(INDKerosene_caste$perceived_risk, INDKerosene_caste$caste, p.adjust.method = "BH")
+
+# For INDLPG
+INDLPG_caste <- demovars_caste_long %>%
+  filter(technology == "INDLPG")
+pairwise.wilcox.test(INDLPG_caste$perceived_risk, INDLPG_caste$caste, p.adjust.method = "BH")
+
+# For INDSolar
+INDSolar_caste <- demovars_caste_long %>%
+  filter(technology == "INDSolar")
+pairwise.wilcox.test(INDSolar_caste$perceived_risk, INDSolar_caste$caste, p.adjust.method = "BH")
+
+# For INDWind
+INDWind_caste <- demovars_caste_long %>%
+  filter(technology == "INDWind")
+pairwise.wilcox.test(INDWind_caste$perceived_risk, INDWind_caste$caste, p.adjust.method = "BH")
+
+# For Oil
+Oil_caste <- demovars_caste_long %>%
+  filter(technology == "Oil")
+pairwise.wilcox.test(Oil_caste$perceived_risk, Oil_caste$caste, p.adjust.method = "BH")
+
+# For Solar
+Solar_caste <- demovars_caste_long %>%
+  filter(technology == "Solar")
+pairwise.wilcox.test(Solar_caste$perceived_risk, Solar_caste$caste, p.adjust.method = "BH")
+
+# For Wind
+Wind_caste <- demovars_caste_long %>%
+  filter(technology == "Wind")
+pairwise.wilcox.test(Wind_caste$perceived_risk, Wind_caste$caste, p.adjust.method = "BH")
+
+#not finding any significant differences in the medians
+
+```
+```{r}
+
+demovars_urban_rural <-  demovars %>%
+  select(starts_with("Risky"), urban_rural) %>%
+  pivot_longer(cols = starts_with("Risky_"), names_to = "technology", values_to = "perceived_risk") %>%
+  mutate(technology = gsub("Risky_", "", technology)) %>%
+  na.omit()
+
+pairwise.wilcox.test(demovars_urban_rural$perceived_risk, demovars_urban_rural$urban_rural, p.adjust.method = "BH")
+
+```

### 2023-09-20 FAoptions.Rmd
lot of changes because I wasn't opening the project file.

---
title: "FAoptions"
output:
  word_document: null
  keep_md: yes
---

```{r load packages, warning = FALSE, message = FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(psych))
library(officer)
library(magrittr)

```

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
moduletwo <- read_excel(here::here("thesis_surveydata/political_factors_complete.xlsx"))
save(moduletwo, file = "moduletwo.rda")
module2 <- data.frame(moduletwo)
module2[module2 == "Rather not say/ Don't know"] <- "Rather not say/Don't know"
#module2 %>% filter(!row_number() %in% c(1,2))

# loaded data set for module 2 eco -pol variables and removes the rows with question number and question text
```

```{r, eval =TRUE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
codedmodule2 <- module2 %>%

#remove row 1
  filter(!row_number() %in% c(1,2)) %>%

# replace risky likert scale with numbers
  mutate_at(vars(starts_with("Risky")), funs(case_when(. =="Not at all risky" ~ 1, 
                                                       . =="Slightly risky" ~ 2, 
                                                       . =="Moderately risky" ~ 3, 
                                                       . =="Very risky" ~ 4, 
                                                       . =="Extremely risky" ~ 5))) %>%

# replace beneficial likert scale with numbers  
  mutate_at(vars(starts_with("Ben")), funs(case_when(. =="Not at all beneficial" ~ 1,
                                                     . =="Slightly beneficial" ~ 2,
                                                     . =="Moderately beneficial" ~ 3,
                                                     . =="Very beneficial" ~ 4,
                                                     . =="Extremely beneficial" ~ 5 ))) %>%

# replace nuclear acceptance likert scale with numbers
  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                                        . == "Somewhat disagree" ~ 2,
                                                                        . == "Neither agree nor disagree" ~3,
                                                                        . == "Somewhat agree" ~ 4,
                                                                        . == "Strongly agree" ~ 5))) %>%

# code likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_I","K_H","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE", "DEV", "PROSPER", "RELY"))), funs(case_when(. == "Strongly disagree" ~ 1, 
               . == "Somewhat disagree" ~ 2,
               . == "Neither agree nor disagree" ~3,
               . == "Somewhat agree" ~ 4,
               . == "Strongly agree" ~ 5))) %>%

# reverse code for likert scale for variables for Kahan scale into numbers
mutate_at(vars(starts_with (c("K_S","K_E"))), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                               . == "Somewhat disagree" ~ 4,
                                                               . == "Neither agree nor disagree" ~3,
                                                               . == "Somewhat agree" ~ 2,
                                                               . == "Strongly agree" ~ 1))) %>%

# code eco-pol scale variables into numbers
  mutate_at(vars(SYSTEMDEMO,SYSTEMRELIGION,SYSTEMTECHNO,SYSTEMTOTAL,WEALTHLIM,MECHANISATION,DECISIONDECEN,INDUSTRYSMALL,ECONOMYLOCAL,ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(. == "Strongly disagree" ~ 1, 
                        . == "Somewhat disagree" ~ 2,
                        . == "Neither agree nor disagree" ~3,
                        . == "Somewhat agree" ~ 4,
                        . == "Strongly agree" ~ 5))) %>%

# reverse code eco-pol scale variables into numbers 
 mutate_at(vars(DECISIONCEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                                                                         . == "Somewhat disagree" ~ 4,
                                                                                                         . == "Neither agree nor disagree" ~3,
                                                                                                         . == "Somewhat agree" ~ 2,
                                                                                                         . == "Strongly agree" ~ 1)))
```

# Two factor solution is slightly different for Nuclear, Solar and Coal.

## Nuclear

```{r, echo=FALSE}

library(psych)
library(tidyverse)

fascales <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_","Risky_Nuclear","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%
  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
                                      . == "25-34 years old" ~ 2,
                                      . ==  "35-44 years old" ~3,
                                      . == "45-54 years old" ~ 4,
                                      . == "55-64 years old" ~ 5,
                                      . == "65-74 years old" ~ 6,
                                      . == "75 years or older" ~ 7))) %>%
  na.omit()
ecopolall <- fascales %>%
        dplyr::select("WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR")%>%
    rename(
      "Limits on Wealth " = "WEALTHLIM",
      "Anti Mechanisation of work" = "MECHANISATION",
      "Pro Decentralisation" = "DECISIONDECEN",
      "Pro Centralisation" = "DECISIONCEN",
      "Pro Large Industries" = "INDUSTRYLARGE",
      "Anti Large Industries " = "INDUSTRYSMALL",
      "Pro Globaleconomy" = "ECONOMYGLOBAL",
      "Pro Localeconomy" = "ECONOMYLOCAL",
      "Environment over Development" = "ENVOVERDEV",
      "Development over Environment" = "DEVOVERENV",
      "Pro Private ownership " = "OWNERPVT",
      "Anti Regulations" = "OWNERNOREG",
      "Pro Public ownership" = "OWNERPUB",
      "Pro Regulations" = "OWNERREG",
      "Displacement risk(nuclear)" = "DISPLACENUCLEAR",
      "Pollution risk(nuclear) " = "POLLUTENUCLEAR",
      "Health risk(nuclear)" = "HEALTHNUCLEAR",
      "Job opportunities(nuclear)" = "JOBSNUCLEAR",
      "Spoils Natural Beauty(nuclear)" = "BEAUTYNUCLEAR",
      "Community pride(nuclear)" = "PRIDENUCLEAR",
      "National pride(nuclear)" = "NPRIDENUCLEAR",
      "National development(nuclear)" = "DEVNUCLEAR",
      "Local prosperity(nuclear)" = "PROSPERNUCLEAR",
      "Reliance on government(nuclear)" = "RELYNUCLEAR"
    )

ecopolall2.fa <- fa(ecopolall, nfactors = 2, rotate = "varimax")

```

```{r, echo=FALSE}

library(flextable)

set_flextable_defaults(docx.landscape = TRUE)

flex <- function(data, title=NULL) {
  # this grabs the data and converts it to a flextbale
  flextable(data) %>%
  # this makes the table fill the page width
  set_table_properties(layout = "autofit", width = 1) %>%
  # font size
  fontsize(size=10, part="all") %>%
    #this adds a ttitlecreates an automatic table number
      set_caption(title, 
                  autonum = officer::run_autonum(seq_id = "tab", 
                                                 pre_label = "Table ", 
                                                 post_label = "\n", 
                                                 bkm = "anytable")) #%>%
  # font type
  #font(fontname="Times New Roman", part="all")
}

rename_map <- c(
  "Limits on Wealth" = "A limit should be put to how much wealth a person can amass",
  "Anti Mechanisation of work" = "Rapid mechanization of work is taking away jobs from workers in this country",
  "Pro Decentralisation" = "Local politicians shouldn't have to ask permission from the central government to implement policies",
  "Pro Centralisation" = "Laws and policies would be implemented more smoothly if more power lay with the central government",
  "Pro Large Industries" = "Large scale industries are required for the development of the country that will benefit everyone",
  "Anti Large Industries" = "Large corporations are destroying the local industries in India and benefiting only a handful of people",
  "Pro Globaleconomy" = "Foreign companies have led to a range of benefits for the Indian people and society",
  "Pro Localeconomy" = "India would be better off if foreign companies didn't come to here",
  "Environment over Development" = "Polluting industries that spoil the environment should be shut down even if it costs people their jobs",
  "Development over Environment" = "Economic growth and creating jobs should be prioritized over environmental protection",
  "Pro Private ownership" = "All businesses and industries should be owned privately",
  "Anti Regulations" = "There is too much red-tape and the government should not interfere with businesses and industries",
  "Pro Public ownership" = "The government should own most large businesses and industries",
  "Pro Regulations" = " Regardless of ownership, the government should pass strong regulations and implement them",
  "Displacement risk(nuclear)" = "Nuclear energy is leading to displacement of people from their land",
  "Spoils Natural Beauty(nuclear)" = "Nuclear energy spoils the natural beauty of the landscape",
  "Pollution risk(nuclear)" = "Nuclear energy increases pollution of air/water/land",
  "Health risk(nuclear)" = "Nuclear energy poses a great risk to the health of people living around it",
  "Job opportunities(nuclear)" = "Nuclear energy will bring jobs to the local community",
  "Community pride(nuclear)" = "I would be proud if my community used nuclear energy",
  "National pride(nuclear)" = "Nuclear energy is a mark of pride for our nation",
  "National development(nuclear)" = "Nuclear energy pushes forward the country's development",
  "Local prosperity(nuclear)" = "Nuclear energy brings economic prosperity to the surrounding regions",
  "Reliance on government(nuclear)" = "I don't like the idea that I have to rely on the government for electricity from nuclear energy"
)

fa_table <- function(x, cut) {
  #get sorted loadings
  loadings <- fa.sort(x)$loadings %>% round(3)
  #suppress loadings
  loadings[loadings > -cut & loadings < cut] <- ""
  #get additional info  
  add_info <- cbind(x$communalities, 
                    x$uniquenesses,
                    x$complexity) %>%
    # make it a data frame
    as.data.frame() %>%
    # column names
    rename("Communality" = V1,
           "Uniqueness" = V2,
           "Complexity" = V3) %>%
    #get the item names from the vector
    rownames_to_column("item")

  #build table
  loadings %>%
    unclass() %>%
    as.data.frame() %>%
    rownames_to_column("item") %>%
    left_join(add_info) %>%
    mutate(
      item = if_else(item %in% names(rename_map), rename_map[item], item),
      code = names(rename_map)[match(item, rename_map)], # extracting short form
      across(where(is.numeric), round, 3)
    ) %>%
    select(code, everything()) # reorder columns to bring code to the front
}

fa_table(ecopolall2.fa, .4) %>%
  rename(Pdevelop = MR1, Ndevelop = MR2, Items= item) %>%
  flex("2 factor solution") %>%
  autofit()

```

```{r, echo = FALSE}
ecopolall2.fa[["Vaccounted"]] %>%
  as.data.frame() %>%
  rownames_to_column("Property") %>%
  rename(Pdevelop = MR1, Ndevelop = MR2) %>%
    mutate(across(where(is.numeric), round, 3)) %>%
    flex("Eigenvalues and Variance Explained for 2 Factor Solution")
```

\newpage
## Solar

```{r, echo=FALSE}
library(psych)
library(tidyverse)

sfascales <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_","Risky_Solar","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACESOLAR", "POLLUTESOLAR", "HEALTHSOLAR", "JOBSSOLAR", "BEAUTYSOLAR", "PRIDESOLAR", "NPRIDESOLAR", "DEVSOLAR", "PROSPERSOLAR", "RELYSOLAR", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%
  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
                                      . == "25-34 years old" ~ 2,
                                      . ==  "35-44 years old" ~3,
                                      . == "45-54 years old" ~ 4,
                                      . == "55-64 years old" ~ 5,
                                      . == "65-74 years old" ~ 6,
                                      . == "75 years or older" ~ 7))) %>%
  na.omit()

secopolall <- sfascales %>%
        dplyr::select("WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACESOLAR", "POLLUTESOLAR", "HEALTHSOLAR", "JOBSSOLAR", "BEAUTYSOLAR", "PRIDESOLAR", "NPRIDESOLAR", "DEVSOLAR", "PROSPERSOLAR", "RELYSOLAR")%>%
    rename(
      "Limits on Wealth " = "WEALTHLIM",
      "Anti Mechanisation of work" = "MECHANISATION",
      "Pro Decentralisation" = "DECISIONDECEN",
      "Pro Centralisation" = "DECISIONCEN",
      "Pro Large Industries" = "INDUSTRYLARGE",
      "Anti Large Industries " = "INDUSTRYSMALL",
      "Pro Globaleconomy" = "ECONOMYGLOBAL",
      "Pro Localeconomy" = "ECONOMYLOCAL",
      "Environment over Development" = "ENVOVERDEV",
      "Development over Environment" = "DEVOVERENV",
      "Pro Private ownership " = "OWNERPVT",
      "Anti Regulations" = "OWNERNOREG",
      "Pro Public ownership" = "OWNERPUB",
      "Pro Regulations" = "OWNERREG",
      "Displacement risk(solar)" = "DISPLACESOLAR",
      "Pollution risk(solar) " = "POLLUTESOLAR",
      "Health risk(solar)" = "HEALTHSOLAR",
      "Job opportunities(solar)" = "JOBSSOLAR",
      "Spoils Natural Beauty(solar)" = "BEAUTYSOLAR",
      "Community pride(solar)" = "PRIDESOLAR",
      "National pride(solar)" = "NPRIDESOLAR",
      "National development(solar)" = "DEVSOLAR",
      "Local prosperity(solar)" = "PROSPERSOLAR",
      "Reliance on government(solar)" = "RELYSOLAR"
    )

secopolall2.fa <- fa(secopolall, nfactors = 2, rotate = "varimax")

```

```{r, echo=FALSE}

library(flextable)

set_flextable_defaults(docx.landscape = TRUE)

flex <- function(data, title=NULL) {
  # this grabs the data and converts it to a flextbale
  flextable(data) %>%
  # this makes the table fill the page width
  set_table_properties(layout = "autofit", width = 1) %>%
  # font size
  fontsize(size=10, part="all") %>%
    #this adds a ttitlecreates an automatic table number
      set_caption(title, 
                  autonum = officer::run_autonum(seq_id = "tab", 
                                                 pre_label = "Table ", 
                                                 post_label = "\n", 
                                                 bkm = "anytable")) #%>%
  # font type
  #font(fontname="Times New Roman", part="all")
}

srename_map <- c(
  "Limits on Wealth" = "A limit should be put to how much wealth a person can amass",
  "Anti Mechanisation of work" = "Rapid mechanization of work is taking away jobs from workers in this country",
  "Pro Decentralisation" = "Local politicians shouldn't have to ask permission from the central government to implement policies",
  "Pro Centralisation" = "Laws and policies would be implemented more smoothly if more power lay with the central government",
  "Pro Large Industries" = "Large scale industries are required for the development of the country that will benefit everyone",
  "Anti Large Industries" = "Large corporations are destroying the local industries in India and benefiting only a handful of people",
  "Pro Globaleconomy" = "Foreign companies have led to a range of benefits for the Indian people and society",
  "Pro Localeconomy" = "India would be better off if foreign companies didn't come to here",
  "Environment over Development" = "Polluting industries that spoil the environment should be shut down even if it costs people their jobs",
  "Development over Environment" = "Economic growth and creating jobs should be prioritized over environmental protection",
  "Pro Private ownership" = "All businesses and industries should be owned privately",
  "Anti Regulations" = "There is too much red-tape and the government should not interfere with businesses and industries",
  "Pro Public ownership" = "The government should own most large businesses and industries",
  "Pro Regulations" = "Regardless of ownership, the government should pass strong regulations and implement them",
  "Displacement risk(solar)" = "Solar energy is leading to displacement of people from their land",
  "Spoils Natural Beauty(solar)" = "Solar energy spoils the natural beauty of the landscape",
  "Pollution risk(solar)" = "Solar energy increases pollution of air/water/land",
  "Health risk(solar)" = "Solar energy poses a great risk to the health of people living around it",
  "Job opportunities(solar)" = "Solar energy will bring jobs to the local community",
  "Community pride(solar)" = "I would be proud if my community used solar energy",
  "National pride(solar)" = "Solar energy is a mark of pride for our nation",
  "National development(solar)" = "Solar energy pushes forward the country's development",
  "Local prosperity(solar)" = "Solar energy brings economic prosperity to the surrounding regions",
  "Reliance on government(solar)" = "I don't like the idea that I have to rely on the government for electricity from solar energy"
)

fa_table <- function(x, cut) {
  #get sorted loadings
  loadings <- fa.sort(x)$loadings %>% round(3)
  #suppress loadings
  loadings[loadings > -cut & loadings < cut] <- ""
  #get additional info  
  add_info <- cbind(x$communalities, 
                    x$uniquenesses,
                    x$complexity) %>%
    # make it a data frame
    as.data.frame() %>%
    # column names
    rename("Communality" = V1,
           "Uniqueness" = V2,
           "Complexity" = V3) %>%
    #get the item names from the vector
    rownames_to_column("item")

  #build table
  loadings %>%
    unclass() %>%
    as.data.frame() %>%
    rownames_to_column("item") %>%
    left_join(add_info) %>%
    mutate(
      item = if_else(item %in% names(srename_map), srename_map[item], item),
      code = names(srename_map)[match(item, srename_map)], # extracting short form
      across(where(is.numeric), round, 3)
    ) %>%
    select(code, everything()) # reorder columns to bring code to the front
}

fa_table(secopolall2.fa, .4) %>%
  #rename(Pdevelop = MR1, Ndevelop = MR2, Items= item) %>%
  flex("2 factor solution") %>%
  autofit()

```

```{r, echo = FALSE}
secopolall2.fa[["Vaccounted"]] %>%
  as.data.frame() %>%
  rownames_to_column("Property") %>%
  #rename(Pdevelop = MR1, Ndevelop = MR2) %>%
    mutate(across(where(is.numeric), round, 3)) %>%
    flex("Solar: Eigenvalues and Variance Explained for 2 Factor Solution")
```

\newpage
## Coal

```{r, echo = FALSE}

cecopolall <- codedmodule2 %>%
        dplyr::select("WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACECOAL", "POLLUTECOAL", "HEALTHCOAL", "JOBSCOAL", "BEAUTYCOAL", "PRIDECOAL", "NPRIDECOAL", "DEVCOAL", "PROSPERCOAL", "RELYCOAL")%>%
      rename(
      "Limits on Wealth " = "WEALTHLIM",
      "Anti Mechanisation of work" = "MECHANISATION",
      "Pro Decentralisation" = "DECISIONDECEN",
      "Pro Centralisation" = "DECISIONCEN",
      "Pro Large Industries" = "INDUSTRYLARGE",
      "Anti Large Industries " = "INDUSTRYSMALL",
      "Pro Globaleconomy" = "ECONOMYGLOBAL",
      "Pro Localeconomy" = "ECONOMYLOCAL",
      "Environment over Development" = "ENVOVERDEV",
      "Development over Environment" = "DEVOVERENV",
      "Pro Private ownership " = "OWNERPVT",
      "Anti Regulations" = "OWNERNOREG",
      "Pro Public ownership" = "OWNERPUB",
      "Pro Regulations" = "OWNERREG",
      "Displacement risk(coal)" = "DISPLACECOAL",
      "Pollution risk(coal) " = "POLLUTECOAL",
      "Health risk(coal)" = "HEALTHCOAL",
      "Job opportunities(coal)" = "JOBSCOAL",
      "Spoils Natural Beauty(coal)" = "BEAUTYCOAL",
      "Community pride(coal)" = "PRIDECOAL",
      "National pride(coal)" = "NPRIDECOAL",
      "National development(coal)" = "DEVCOAL",
      "Local prosperity(coal)" = "PROSPERCOAL",
      "Reliance on government(coal)" = "RELYCOAL"
    )%>%
  na.omit()

cecopolall2.fa <- fa(cecopolall, nfactors = 2, rotate = "varimax")

```

```{r, echo=FALSE}

library(flextable)

set_flextable_defaults(docx.landscape = TRUE)

flex <- function(data, title=NULL) {
  # this grabs the data and converts it to a flextbale
  flextable(data) %>%
  # this makes the table fill the page width
  set_table_properties(layout = "autofit", width = 1) %>%
  # font size
  fontsize(size=10, part="all") %>%
    #this adds a ttitlecreates an automatic table number
      set_caption(title, 
                  autonum = officer::run_autonum(seq_id = "tab", 
                                                 pre_label = "Table ", 
                                                 post_label = "\n", 
                                                 bkm = "anytable")) #%>%
  # font type
  #font(fontname="Times New Roman", part="all")
}

crename_map <- c(
  "Limits on Wealth" = "A limit should be put to how much wealth a person can amass",
  "Anti Mechanisation of work" = "Rapid mechanization of work is taking away jobs from workers in this country",
  "Pro Decentralisation" = "Local politicians shouldn't have to ask permission from the central government to implement policies",
  "Pro Centralisation" = "Laws and policies would be implemented more smoothly if more power lay with the central government",
  "Pro Large Industries" = "Large scale industries are required for the development of the country that will benefit everyone",
  "Anti Large Industries" = "Large corporations are destroying the local industries in India and benefiting only a handful of people",
  "Pro Globaleconomy" = "Foreign companies have led to a range of benefits for the Indian people and society",
  "Pro Localeconomy" = "India would be better off if foreign companies didn't come to here",
  "Environment over Development" = "Polluting industries that spoil the environment should be shut down even if it costs people their jobs",
  "Development over Environment" = "Economic growth and creating jobs should be prioritized over environmental protection",
  "Pro Private ownership" = "All businesses and industries should be owned privately",
  "Anti Regulations" = "There is too much red-tape and the government should not interfere with businesses and industries",
  "Pro Public ownership" = "The government should own most large businesses and industries",
  "Pro Regulations" = "Regardless of ownership, the government should pass strong regulations and implement them",
  "Displacement risk(coal)" = "Coal powered plants are leading to displacement of people from their land",
  "Spoils Natural Beauty(coal)" = "Coal powered plants spoil the natural beauty of the landscape",
  "Pollution risk(coal)" = "Coal powered plants increase pollution of air/water/land",
  "Health risk(coal)" = "Coal powered plants pose a great risk to the health of people living around it",
  "Job opportunities(coal)" = "Coal powered plants will bring jobs to the local community",
  "Community pride(coal)" = "I would be proud if my community used coal powered plants",
  "National pride(coal)" = "Coal powered plants are a mark of pride for our nation",
  "National development(coal)" = "Coal powered plants push forward the country's development",
  "Local prosperity(coal)" = "Coal powered plants bring economic prosperity to the surrounding regions",
  "Reliance on government(coal)" = "I don't like the idea that I have to rely on the government for electricity from coal powered plants"
)

fa_table <- function(x, cut) {
  #get sorted loadings
  loadings <- fa.sort(x)$loadings %>% round(3)
  #suppress loadings
  loadings[loadings > -cut & loadings < cut] <- ""
  #get additional info  
  add_info <- cbind(x$communalities, 
                    x$uniquenesses,
                    x$complexity) %>%
    # make it a data frame
    as.data.frame() %>%
    # column names
    rename("Communality" = V1,
           "Uniqueness" = V2,
           "Complexity" = V3) %>%
    #get the item names from the vector
    rownames_to_column("item")

  #build table
  loadings %>%
    unclass() %>%
    as.data.frame() %>%
    rownames_to_column("item") %>%
    left_join(add_info) %>%
    mutate(
      item = if_else(item %in% names(crename_map), crename_map[item], item),
      code = names(crename_map)[match(item, crename_map)], # extracting short form
      across(where(is.numeric), round, 3)
    ) %>%
    select(code, everything()) # reorder columns to bring code to the front
}

fa_table(cecopolall2.fa, .4) %>%
  #rename(Pdevelop = MR1, Ndevelop = MR2, Items= item) %>%
  flex("2 factor solution") %>%
  autofit()

```

```{r, echo = FALSE}
cecopolall2.fa[["Vaccounted"]] %>%
  as.data.frame() %>%
  rownames_to_column("Property") %>%
  #rename(Pdevelop = MR1, Ndevelop = MR2) %>%
    mutate(across(where(is.numeric), round, 3)) %>%
    flex("Coal: Eigenvalues and Variance Explained for 2 Factor Solution")
```

\newpage
# Alternative Solution :  FA on Two Separate scales

## Scale 1: Factor analysis on Eco-political values of the perceiver scale
 4 factor solution

```{r, echo = FALSE}

# below are only eco-pol values of the perceiver scale.

ecopolval <- codedmodule2 %>%
        dplyr::select("WEALTHLIM","MECHANISATION","INDUSTRYSMALL","ECONOMYGLOBAL", "ENVOVERDEV","OWNERNOREG","OWNERPUB", "OWNERREG", "DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","ECONOMYLOCAL", "DEVOVERENV","OWNERPVT")%>%
  na.omit() %>%
    rename(
      "Limits on Wealth" = "WEALTHLIM",
      "Anti Mechanisation of work" = "MECHANISATION",
      "Pro Decentralisation" = "DECISIONDECEN",
      "Pro Centralisation" = "DECISIONCEN",
      "Pro Large Industries" = "INDUSTRYLARGE",
      "Anti Large Industries " = "INDUSTRYSMALL",
      "Pro Globaleconomy" = "ECONOMYGLOBAL",
      "Pro Localeconomy" = "ECONOMYLOCAL",
      "Environment over Development" = "ENVOVERDEV",
      "Development over Environment" = "DEVOVERENV",
      "Pro Private ownership " = "OWNERPVT",
      "Anti Regulations" = "OWNERNOREG",
      "Pro Public ownership" = "OWNERPUB",
      "Pro Regulations" = "OWNERREG"
    )

#alpha(ecopolval, check.keys = TRUE) # 0.71

#ncol(ecopolval)  number of cols is 14

#ecopolval_cor <- cor(ecopolval)
#PCA14 <- principal(ecopolval, nfactors = 14, rotate = "none") # no rotation to start with.

#print(PCA14)

#PCA14$loadings

#fa.parallel(ecopolval_cor)

ecopolval4.fa <- fa(ecopolval, nfactors = 4, rotate = "varimax")

#cor(ecopolval)

# questions for Terre , 2) 4 factors/3 factors/2 factors - variation explained how should i deal with that. 
# four factor analysis - MR1 - problems of industrialisation MR2 - local economy and decision making MR3 - centralised and large industry MR4- dev/ownership
```

```{r, echo=FALSE}

library(flextable)

set_flextable_defaults(docx.landscape = TRUE)

flex <- function(data, title=NULL) {
  # this grabs the data and converts it to a flextbale
  flextable(data) %>%
  # this makes the table fill the page width
  set_table_properties(layout = "autofit", width = 1) %>%
  # font size
  fontsize(size=10, part="all") %>%
    #this adds a ttitlecreates an automatic table number
      set_caption(title, 
                  autonum = officer::run_autonum(seq_id = "tab", 
                                                 pre_label = "Table ", 
                                                 post_label = "\n", 
                                                 bkm = "anytable")) #%>%
  # font type
  #font(fontname="Times New Roman", part="all")
}

rename_map <- c(
  "Limits on Wealth" = "A limit should be put to how much wealth a person can amass",
  "Anti Mechanisation of work" = "Rapid mechanization of work is taking away jobs from workers in this country",
  "Pro Decentralisation" = "Local politicians shouldn't have to ask permission from the central government to implement policies",
  "Pro Centralisation" = "Laws and policies would be implemented more smoothly if more power lay with the central government",
  "Pro Large Industries" = "Large scale industries are required for the development of the country that will benefit everyone",
  "Anti Large Industries" = "Large corporations are destroying the local industries in India and benefiting only a handful of people",
  "Pro Globaleconomy" = "Foreign companies have led to a range of benefits for the Indian people and society",
  "Pro Localeconomy" = "India would be better off if foreign companies didn't come to here",
  "Environment over Development" = "Polluting industries that spoil the environment should be shut down even if it costs people their jobs",
  "Development over Environment" = "Economic growth and creating jobs should be prioritized over environmental protection",
  "Pro Private ownership" = "All businesses and industries should be owned privately",
  "Anti Regulations" = "There is too much red-tape and the government should not interfere with businesses and industries",
  "Pro Public ownership" = "The government should own most large businesses and industries",
  "Pro Regulations" = " Regardless of ownership, the government should pass strong regulations and implement them"
)

fa_table <- function(x, cut) {
  #get sorted loadings
  loadings <- fa.sort(x)$loadings %>% round(3)
  #suppress loadings
  loadings[loadings > -cut & loadings < cut] <- ""
  #get additional info  
  add_info <- cbind(x$communalities, 
                    x$uniquenesses,
                    x$complexity) %>%
    # make it a data frame
    as.data.frame() %>%
    # column names
    rename("Communality" = V1,
           "Uniqueness" = V2,
           "Complexity" = V3) %>%
    #get the item names from the vector
    rownames_to_column("item")

  #build table
  loadings %>%
    unclass() %>%
    as.data.frame() %>%
    rownames_to_column("item") %>%
    left_join(add_info) %>%
    mutate(
      item = if_else(item %in% names(rename_map), rename_map[item], item),
      code = names(rename_map)[match(item, rename_map)], # extracting short form
      across(where(is.numeric), round, 3)
    ) %>%
    select(code, everything()) # reorder columns to bring code to the front
}

fa_table(ecopolval4.fa, .4) %>%
  #rename(Pdevelop = MR1, Ndevelop = MR2, Items= item) %>%
  flex("4 factor solution same for all technologies") %>%
  autofit()

```

```{r, echo=FALSE}

library(flextable)

flex <- function(data, title=NULL) {
  # this grabs the data and converts it to a flextbale
  flextable(data) %>%
  # this makes the table fill the page width
  set_table_properties(layout = "autofit", width = 1) %>%
  # font size
  fontsize(size=10, part="all") %>%
    #this adds a ttitlecreates an automatic table number
      set_caption(title, 
                  autonum = officer::run_autonum(seq_id = "tab", 
                                                 pre_label = "Table ", 
                                                 post_label = "\n", 
                                                 bkm = "anytable")) #%>%
  # font type
  #font(fontname="Times New Roman", part="all")
}

ecopolval4.fa[["Vaccounted"]] %>%
  as.data.frame() %>%
  rownames_to_column("Property") %>%
  #rename(Pdevelop = MR1, Ndevelop = MR2) %>%
    mutate(across(where(is.numeric), round, 3)) %>%
    flex("Eigenvalues and Variance Explained for Rotated Factor Solution")

```

```{r, echo = FALSE}
 # Adjust as per the number of factors

#fa.diagram(ecopolval4.fa, marg=c(.5,5,1,.5),size =1, adj = 0.25, e.size=.05,rsize=.35, main = "Four Factor Solution")

```

\newpage
## Option 1: Factor analysis on Scale 2 - Characteristics of the Technology
 2 factor solution

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

#alpha test on Eco-pol characteristics of the technology

Nuclear <- codedmodule2 %>%
dplyr::select("DISPLACENUCLEAR":"RELYNUCLEAR") %>%
  na.omit()%>%
    rename(
   "Displacement risk(nuclear)" = "DISPLACENUCLEAR",
  "Pollution risk(nuclear)" = "POLLUTENUCLEAR",
  "Health risk(nuclear)" = "HEALTHNUCLEAR",
  "Job opportunities(nuclear)" = "JOBSNUCLEAR",
  "Spoils Natural Beauty(nuclear)" = "BEAUTYNUCLEAR",
  "Community pride(nuclear)" = "PRIDENUCLEAR",
  "National pride(nuclear)" = "NPRIDENUCLEAR",
  "National development(nuclear)" = "DEVNUCLEAR",
  "Local prosperity(nuclear)" = "PROSPERNUCLEAR",
  "Reliance on government(nuclear)" = "RELYNUCLEAR"
    )

Nuclear.fa <- fa(Nuclear, nfactors = 2, rotate = "varimax")

#print.psych(Nuclear.fa, cut = 0.40, sort = TRUE)

#fa.diagram(Nuclear.fa)

```

```{r, echo=FALSE}

library(flextable)

set_flextable_defaults(docx.landscape = TRUE)

flex <- function(data, title=NULL) {
  # this grabs the data and converts it to a flextbale
  flextable(data) %>%
  # this makes the table fill the page width
  set_table_properties(layout = "autofit", width = 1) %>%
  # font size
  fontsize(size=10, part="all") %>%
    #this adds a ttitlecreates an automatic table number
      set_caption(title, 
                  autonum = officer::run_autonum(seq_id = "tab", 
                                                 pre_label = "Table ", 
                                                 post_label = "\n", 
                                                 bkm = "anytable")) #%>%
  # font type
  #font(fontname="Times New Roman", part="all")
}

rename_map <- c(
  "Displacement risk(nuclear)" = "Nuclear energy is leading to displacement of people from their land",
  "Spoils Natural Beauty(nuclear)" = "Nuclear energy spoils the natural beauty of the landscape",
  "Pollution risk(nuclear)" = "Nuclear energy increases pollution of air/water/land",
  "Health risk(nuclear)" = "Nuclear energy poses a great risk to the health of people living around it",
  "Job opportunities(nuclear)" = "Nuclear energy will bring jobs to the local community",
  "Community pride(nuclear)" = "I would be proud if my community used nuclear energy",
  "National pride(nuclear)" = "Nuclear energy is a mark of pride for our nation",
  "National development(nuclear)" = "Nuclear energy pushes forward the country's development",
  "Local prosperity(nuclear)" = "Nuclear energy brings economic prosperity to the surrounding regions",
  "Reliance on government(nuclear)" = "I don't like the idea that I have to rely on the government for electricity from nuclear energy"
)

fa_table <- function(x, cut) {
  #get sorted loadings
  loadings <- fa.sort(x)$loadings %>% round(3)
  #suppress loadings
  loadings[loadings > -cut & loadings < cut] <- ""
  #get additional info  
  add_info <- cbind(x$communalities, 
                    x$uniquenesses,
                    x$complexity) %>%
    # make it a data frame
    as.data.frame() %>%
    # column names
    rename("Communality" = V1,
           "Uniqueness" = V2,
           "Complexity" = V3) %>%
    #get the item names from the vector
    rownames_to_column("item")

  #build table
  loadings %>%
    unclass() %>%
    as.data.frame() %>%
    rownames_to_column("item") %>%
    left_join(add_info) %>%
    mutate(
      item = if_else(item %in% names(rename_map), rename_map[item], item),
      code = names(rename_map)[match(item, rename_map)], # extracting short form
      across(where(is.numeric), round, 3)
    ) %>%
    select(code, everything()) # reorder columns to bring code to the front
}

fa_table(Nuclear.fa, .4) %>%
  rename("Negative Characteristics" = MR1, "Positive Characteristics" = MR2, Items= item, Code = code) %>%
  flex("Nuclear Energy: 2 factor solution") %>%
  autofit()

```

```{r, echo=FALSE}

library(flextable)

flex <- function(data, title=NULL) {
  # this grabs the data and converts it to a flextbale
  flextable(data) %>%
  # this makes the table fill the page width
  set_table_properties(layout = "autofit", width = 1) %>%
  # font size
  fontsize(size=10, part="all") %>%
    #this adds a ttitlecreates an automatic table number
      set_caption(title, 
                  autonum = officer::run_autonum(seq_id = "tab", 
                                                 pre_label = "Table ", 
                                                 post_label = "\n", 
                                                 bkm = "anytable")) #%>%
  # font type
  #font(fontname="Times New Roman", part="all")
}

Nuclear.fa[["Vaccounted"]] %>%
  as.data.frame() %>%
  rownames_to_column("Property") %>%
  rename("Negative Characteristics" = MR1, "Positive Characteristics" = MR2) %>%
    mutate(across(where(is.numeric), round, 3)) %>%
    flex("Eigenvalues and Variance Explained for 2 Factor Solution")

```

```{r, echo = FALSE}
 # Adjust as per the number of factors

#fa.diagram(Nuclear.fa, marg=c(.5,5,1,.5),size =1, adj = 0.25, e.size=.05,rsize=.35, main = "Two Factor Solution")

```

\newpage

### 2023-09-20 LPGversusFirewood.Rmd
lot of changes because I wasn't opening the project file.

---
title: "LPG v/s Firewood"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    keep_tex: yes
  header-includes:
  - \usepackage{dcolumn}
  - \usepackage{array}
  keep_md: yes

---

```{r load packages, warning = FALSE, message = FALSE, echo = FALSE}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(psych))
suppressPackageStartupMessages(library(tidyr))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(lavaan))
suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(DT))
suppressPackageStartupMessages(library(knitr))

```

```{r setup, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

moduletwo <- read_excel(here::here("thesis_surveydata/political_factors_complete.xlsx"))
module2 <- data.frame(moduletwo)
module2[module2 == "Rather not say/ Don't know"] <- "Rather not say/Don't know"

# loaded data set for module 2 eco -pol variables and removes the rows with question number and question text
```

```{r, eval =TRUE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
codedmodule2 <- module2 %>%

#remove row 1
  filter(!row_number() %in% c(1,2)) %>%

# replace risky likert scale with numbers
  mutate_at(vars(starts_with("Risky")), funs(case_when(. =="Not at all risky" ~ 1, 
                                                       . =="Slightly risky" ~ 2, 
                                                       . =="Moderately risky" ~ 3, 
                                                       . =="Very risky" ~ 4, 
                                                       . =="Extremely risky" ~ 5))) %>%

# replace beneficial likert scale with numbers  
  mutate_at(vars(starts_with("Ben")), funs(case_when(. =="Not at all beneficial" ~ 1,
                                                     . =="Slightly beneficial" ~ 2,
                                                     . =="Moderately beneficial" ~ 3,
                                                     . =="Very beneficial" ~ 4,
                                                     . =="Extremely beneficial" ~ 5 ))) %>%

# replace nuclear acceptance likert scale with numbers
  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                                        . == "Somewhat disagree" ~ 2,
                                                                        . == "Neither agree nor disagree" ~3,
                                                                        . == "Somewhat agree" ~ 4,
                                                                        . == "Strongly agree" ~ 5))) %>%

# code likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_I","K_H","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE", "DEV", "PROSPER", "RELY"))), funs(case_when(. == "Strongly disagree" ~ 1, 
               . == "Somewhat disagree" ~ 2,
               . == "Neither agree nor disagree" ~3,
               . == "Somewhat agree" ~ 4,
               . == "Strongly agree" ~ 5))) %>%

# reverse code for likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_S","K_E"))), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                               . == "Somewhat disagree" ~ 4,
                                                               . == "Neither agree nor disagree" ~3,
                                                               . == "Somewhat agree" ~ 2,
                                                               . == "Strongly agree" ~ 1))) %>%

# code eco-pol scale variables into numbers
  mutate_at(vars(SYSTEMDEMO,SYSTEMRELIGION,SYSTEMTECHNO,SYSTEMTOTAL,WEALTHLIM,MECHANISATION,DECISIONDECEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG), funs(case_when(. == "Strongly disagree" ~ 1, 
                        . == "Somewhat disagree" ~ 2,
                        . == "Neither agree nor disagree" ~3,
                        . == "Somewhat agree" ~ 4,
                        . == "Strongly agree" ~ 5))) %>%

# reverse code eco-pol scale variables into numbers 
 mutate_at(vars(DECISIONCEN, INDUSTRYSMALL, ECONOMYLOCAL, ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                                                                         . == "Somewhat disagree" ~ 4,
                                                                                                         . == "Neither agree nor disagree" ~3,
                                                                                                         . == "Somewhat agree" ~ 2,
                                                                                                         . == "Strongly agree" ~ 1))) %>%
  mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
  mutate_all(~ifelse(. == "West bengal", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "WEST BENGAL", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "Up", "Uttar Pradesh", .))%>%
  mutate_all(~ifelse(. == "Tamilnadu", "Tamil Nadu", .))%>%
  mutate_all(~ifelse(. == "UP", "Uttar Pradesh", .))

```

```{r, eval=TRUE, echo = FALSE}

moduleone <- read_excel(here::here("thesis_surveydata/livelihood_insecurity_complete.xlsx"))
save(moduleone, file = "moduleone.rda")
module1 <- data.frame(moduleone)

# loaded data set for module 2 eco -pol variables and removes the rows with question number and question text
```

```{r, echo = FALSE}
#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
codedmodule1 <- module1 %>%
  #remove row 1 and 2

  filter(!row_number() %in% c(1,2))%>%

  # replace risky likert scale with numbers
  mutate(across(starts_with("Risky"), ~case_when(. =="Not at all risky" ~ 1, 
                                                 . =="Slightly risky" ~ 2, 
                                                 . =="Moderately risky" ~ 3, 
                                                 . =="Very risky" ~ 4, 
                                                 . =="Extremely risky" ~ 5))) %>%

  # replace beneficial likert scale with numbers  
  mutate(across(starts_with("Ben"), ~case_when(. =="Not at all beneficial" ~ 1,
                                               . =="Slightly beneficial" ~ 2,
                                               . =="Moderately beneficial" ~ 3,
                                               . =="Very beneficial" ~ 4,
                                               . =="Extremely beneficial" ~ 5 ))) %>%

  # replace nuclear acceptance likert scale with numbers
  mutate(across(c(N_accept,N_reluctantlyaccept,N_reject), ~case_when(. == "Strongly disagree" ~ 1, 
                                                                     . == "Somewhat disagree" ~ 2,
                                                                     . == "Neither agree nor disagree" ~3,
                                                                     . == "Somewhat agree" ~ 4,
                                                                     . == "Strongly agree" ~ 5))) %>%

  mutate(across(Livelihood_Income, ~case_when(. == "(a) own farming/fishing/animal rearing/business" ~ "LSI", 
                                              . == "(b) employed for wages/salary" ~ "ISI",
                                              . == "(c) student" ~"student",
                                              . == "(d) currently unemployed" ~ "unemployed",
                                              . == "(e) homemaker" ~ "homemaker",
                                              . == "(f) retired" ~ "retired",
                                              . == "(g) unable to work" ~ "unable to work" ))) %>%

  # coding education
  mutate(across(education, ~case_when(. == "No schooling completed" ~ 0, 
                                      . == "Primary school" ~ 1,
                                      . == "Grade 10th" ~ 2,
                                      . == "Grade 12th" ~ 3,
                                      . == "Some college, no degree" ~ 4,
                                      . == "Trade/technical/vocational training" ~ 5,
                                      . == "Bachelor's degree" ~ 6,
                                      . == "Master's degree" ~ 7,
                                      . == "Professional degree" ~ 8,
                                      . == "Doctorate degree" ~ 9 ))) %>%

  # coding yes and no questions
  mutate(across(c(Lassociation,Iassociation, govtscheme, wateravail, polposition, polparty), ~case_when(.== "Yes" ~ 1,
                                                                                                        .== "No" ~ 0))) %>%
  # reverse coding yes and no questions
  mutate(across(c(illness,severeillness), ~case_when(.== "Yes" ~ 0,
                                                     .== "No" ~ 1))) %>%

  # coding How confident are you that you can continue your current livelihood if you want to? 
  mutate(across(Lconfidence, ~case_when(. == "Not at all confident" ~ 1, 
                                        . == "Not much confident" ~ 2,
                                        . == "Neutral" ~3,
                                        . == "Somewhat confident" ~ 4,
                                        . == "Very confident" ~ 5))) %>%

  mutate(across(c(Lboat, houseown), ~case_when(.== "Own it" ~ 1,
                                               .== "Rent it" ~ 0))) %>%

  # J security index coding
  mutate(across(JISRkeep, ~case_when(. == "Strongly disagree" ~ 1, 
                                     . == "Somewhat disagree" ~ 2,
                                     . == "Neither agree nor disagree" ~3,
                                     . == "Somewhat agree" ~ 4,
                                     . == "Strongly agree" ~ 5))) %>%

  # reverse code JIS 
  mutate(across(c(JISlosefuture, JISlose, JISfuture), ~case_when(. == "Strongly disagree" ~ 5, 
                                                                 . == "Somewhat disagree" ~ 4,
                                                                 . == "Neither agree nor disagree" ~3,
                                                                 . == "Somewhat agree" ~ 2,
                                                                 . == "Strongly agree" ~ 1))) %>%

  mutate(across(c(totalincome, otherincome), ~case_when(. == "Less than Rs 1,00,000" ~ 1,
                                                        . == "Rs 1,00,000 to Rs 2,50,000"  ~ 2,
                                                        . == "Rs 2,50,001 to Rs 5,00,000" ~ 3,
                                                        . == "Rs 5,00,001 to Rs 10,00,000" ~ 4,
                                                        . == "Rs 10,00,001 and above"  ~ 5,
                                                        . == "Doesn't apply" ~ 0))) %>%

  mutate(across(c(workknowledge, subsidyknow), ~case_when(. == "Very poor" ~ 1, 
                                                          . == "Poor" ~ 2,
                                                          . == "Fair" ~3,
                                                          . == "Good" ~ 4,
                                                          . == "Very good" ~ 5))) %>%

  mutate(across(c(drinkingwater, cookingwater), ~case_when(. == "Bottled water/ Filtered Water" ~ 1,                                       
                                                           .  == "Piped into dwelling" ~ 2,                                                  
                                                           .  == "Piped to neighbour" ~ 3,                                                   
                                                           .  == "Piped to yard/plot" ~ 4, 
                                                           .  == "Protected well" ~ 5, 
                                                           .  == "Public tap/standpipe" ~6,
                                                           .  == "Surface Water  (River/Dam/Lake/Pond/Stream/Canal/Irrigation Channel)" ~7, 
                                                           .  == "Tanker Truck" ~ 8,
                                                           .  == "Tubewell/borehole" ~ 9,
                                                           .  == "Unprotected Spring" ~ 10))) %>%

  mutate(across(toilet, ~case_when(. == "No facility/bush/field" ~ 1,                                       
                                   .  == "Hanging toilet/hanging latrine" ~ 2,                                             
                                   .  == "Bucket toilet"  ~ 3,                                                   
                                   .  == "Composting toilet"  ~ 4, 
                                   .  == "Pit latrine without slab/open pit" ~ 5, 
                                   .  == "Pit latrine with slab" ~6,
                                   .  == "Ventilated improved pit laterine"  ~7, 
                                   .  == "Flush to somewhere else"  ~ 8,
                                   .  == "Flush to pit latrine"  ~ 9,
                                   .  == "Flush to septic tank" ~ 10,
                                   .  == "Flush to piped sewer system" ~ 11))) %>%

  mutate(across(house, ~case_when(. == "Hut made of mud, bamboo, straw etc. (kutcha house)" ~ 1, 
                                  . == "Permanent single story house (pukka house)" ~ 2,
                                  . == "Apartment/Flat in a multi-story building"  ~3,
                                  . == "Multi-story house" ~ 4))) %>%

  mutate(across(foodtrouble, ~case_when(. == "8 or more months" ~ 1,                                       
                                        .  == "6-8 months"  ~ 2,                                                  
                                        .  == "4-6 months"  ~ 3,                                                   
                                        .  == "2-4 months"  ~ 4, 
                                        .  == "1-2 months" ~ 5, 
                                        .  == "0 months"  ~6))) %>%

  mutate(across(foodadequacy, ~case_when(. == "Extremely inadequate" ~ 1, 
                                         . == "Moderately inadequate" ~ 2,
                                         . == "Slightly inadequate" ~3,
                                         . == "Neither adequate nor inadequate" ~ 4,
                                         . == "Slightly adequate" ~ 5,
                                         . == "Moderately adequate" ~ 6,
                                         . == "Extremely adequate" ~ 7))) %>%

  # separating cooking, vehicle and food cols into separate entries
  separate(col = cookstove, into = c("cook1", "cook2", "cook3", "cook4"), sep = ",") %>%
  separate(col = vehicle, into = c("vehicle1", "vehicle2", "vehicle3", "vehicle4"), sep = ",") %>%
  separate(col = foodsource, into = c("food1", "food2", "food3", "food4"), sep = ",") %>%

  mutate(across(c(cook1, cook2, cook3, cook4), ~case_when(. == "Three Stone Stove/Open Fire" ~ 1, 
                                  . == "Traditional Solid Fuel Stove" ~ 2,
                                  . == "Liquid Fuel Stove" ~3,
                                  . == "Biogas Stove" ~ 4,
                                  . == "Piped Natural Gas Stove" ~ 5,
                                  . == "Liquefied Petroleum Gas (LPG)/Cooking gas stove" ~ 6,
                                  . == "Solar Cooker" ~ 7,
                                  . == "Electric Stove" ~ 7,
                                  is.na(.) ~ 0))) %>%

  mutate(across(c(vehicle1, vehicle2, vehicle3, vehicle4, vehicletext), ~case_when(. == "Bicycle" ~ 1, 
                                    . == "Animal Drawn Cart" ~ 2,
                                    . == "Motorcycle/Scooter" ~3,
                                    . == "Car" ~ 4,
                                    . == "Truck" ~ 4,
                                    . == "Boat with Motor" ~ 4,
                                    . == "Tractor" ~ 4,
                                    . == "E-rickshaw" ~ 1,
                                    . == "Tempo" ~ 3,
                                    . == "Nothing" ~ 0,
                                    . == "Other (Please Specify)" ~ 0,
                                    is.na(.) ~ 0))) %>%

  mutate(across(c(food1, food2, food3,food4), ~case_when(. == "Forest" ~ 1, 
                                  . == "Own Farm" ~ 2,
                                  . == "Market" ~4,
                                  . == "Own livestock" ~ 2,
                                  . == "Subsidised ration shops" ~ 3,
                                  is.na(.) ~ 0)))

```

```{r, echo = FALSE}

suppressPackageStartupMessages(library(tidyselect))
# combine codedmodule1 and codedmodule2

numcol2 <- codedmodule2 %>% add_column(Respondent = 1:1099, .before = "Language") 
numcol1 <- codedmodule1 %>% add_column(Respondent = 1099:2160, .before = "Language")

joineddf <-  full_join(numcol2, numcol1, by = c("Respondent", "Language", "Survey_Date", "State", "Risky_Hydro", "Risky_Solar", "Risky_Wind", "Risky_Nuclear", "Risky_Coal", "Risky_Gas", "Risky_Oil", "Risky_INDHydro", "Risky_INDSolar", "Risky_INDWind", "Risky_INDBiogas", "Risky_INDDiesel", "Risky_INDKerosene", "Risky_INDFirewoodetc", "Risky_INDLPG", "Ben_Hydro", "Ben_Solar", "Ben_Wind", "Ben_Nuclear", "Ben_Coal", "Ben_Gas", "Ben_Oil", "Ben_INDHydro", "Ben_INDSolar", "Ben_INDWind", "Ben_INDDiesel", "Ben_INDBiogas", "Ben_INDFirewoodetc", "Ben_INDLPG", "Ben_INDKerosene", "N_accept", "N_reluctantlyaccept", "N_reject", "age", "urban_rural", "gender", "caste", "religion", "religiontext")) %>%
  mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
  mutate_all(~ifelse(. == "West bengal", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "WEST BENGAL", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "Up", "Uttar Pradesh", .))%>%
  mutate_all(~ifelse(. == "Tamilnadu", "Tamil Nadu", .))%>%
  mutate_all(~ifelse(. == "UP", "Uttar Pradesh", .))

numcolb <- module2 %>%   filter(!row_number() %in% c(1,2))%>% 
                        add_column(Respondent = 1:1099, .before = "Language") 
numcola <- module1 %>%   filter(!row_number() %in% c(1,2)) %>% 
                        add_column(Respondent = 1099:2160, .before = "Language")

uncodedjoineddf <- full_join(numcolb, numcola, by = c("Respondent", "Language", "Survey_Date", "State", "Risky_Hydro", "Risky_Solar", "Risky_Wind", "Risky_Nuclear", "Risky_Coal", "Risky_Gas", "Risky_Oil", "Risky_INDHydro", "Risky_INDSolar", "Risky_INDWind", "Risky_INDBiogas", "Risky_INDDiesel", "Risky_INDKerosene", "Risky_INDFirewoodetc", "Risky_INDLPG", "Ben_Hydro", "Ben_Solar", "Ben_Wind", "Ben_Nuclear", "Ben_Coal", "Ben_Gas", "Ben_Oil", "Ben_INDHydro", "Ben_INDSolar", "Ben_INDWind", "Ben_INDDiesel", "Ben_INDBiogas", "Ben_INDFirewoodetc", "Ben_INDLPG", "Ben_INDKerosene", "N_accept", "N_reluctantlyaccept", "N_reject", "age", "urban_rural", "gender", "caste", "religion", "religiontext")) %>%
  mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
  mutate_all(~ifelse(. == "West bengal", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "WEST BENGAL", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "Up", "Uttar Pradesh", .))%>%
  mutate_all(~ifelse(. == "Tamilnadu", "Tamil Nadu", .))%>%
  mutate_all(~ifelse(. == "UP", "Uttar Pradesh", .))

```
\newpage

# Characteristics of the Sample

The following graph shows that distribution of different demographic variables in our sample of 2,160 from the combined dataset from both surveys.

```{r, echo=FALSE}

library(dplyr)
library(tidyr)

sampledemos <- joineddf %>% dplyr::select("State", "Language", "age", "urban_rural", "gender", "caste" ,"religion") %>%
              mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
              mutate_all(~ifelse(. == "OBC", "Other Backward Classes (OBC)", .))%>%
              mutate_all(~ifelse(. == "SC", "Scheduled caste (SC)", .))%>%
              mutate_all(~ifelse(. == "ST", "Scheduled tribe (ST)", .))%>%
              mutate_all(~ifelse(. == "MAR", "Marathi", .))%>%
              mutate_all(~ifelse(. == "TA", "Tamil", .)) %>%
              mutate_all(~ifelse(. == "EN", "English", .))%>%
              mutate_all(~ifelse(. == "BN", "Bengali", .))%>%
              mutate_all(~ifelse(. == "MAR", "Marathi", .))%>%
              mutate_all(~ifelse(. == "HI", "Hindi", .))%>%
              na.omit()

#changing factor levels for each variable from high to low n

sampledemos$State <- factor(sampledemos$State, levels = c("Maharashtra","Rajasthan", "West Bengal" , "Tamil Nadu", "Uttar Pradesh"))
sampledemos$Language <- factor(sampledemos$Language, levels = c("Hindi","Marathi","Bengali","Tamil"))
sampledemos$age <- factor(sampledemos$age, levels = c( "18-24 years old" ,  "25-34 years old","35-44 years old", "45-54 years old", "55-64 years old","65-74 years old","75 years or older"  ))
sampledemos$urban_rural <- factor(sampledemos$urban_rural, levels = c("Rural","Urban"))
sampledemos$gender <- factor(sampledemos$gender, levels = c("Male","Female"))
sampledemos$caste <- factor(sampledemos$caste, levels = c("Scheduled tribe (ST)", "Scheduled caste (SC)", "Other Backward Classes (OBC)", "General","Brahmin","Rather not say/Don't know"))
sampledemos$religion <- factor(sampledemos$religion, levels = c("Hinduism", "Islam", "Christanity","Buddhism","Agnostism/ Atheism","Other (Please mention)"))

```

```{r, echo=FALSE, fig.width=11, fig.height=14, out.width='80%', out.height='80%'}
# Loading the required libraries
library(tidyverse)
library(gridExtra)
library(scales)

# Function to create bar plot
create_bar_plot <- function(data, variable_name, palette_name) {
  factor_levels <- levels(sampledemos[[variable_name]])
  data %>%
    filter(Variable == variable_name) %>%
    mutate(Category = factor(Category, levels = factor_levels)) %>%
    ggplot(aes(y = "", x = Percentage, fill = Category)) +
    geom_bar(position = "fill", stat = "identity", width = 1) +
    geom_text(aes(label = paste0(round(Percentage, 0), "%")), 
              position = position_fill(vjust = 0.5)) +
    scale_x_continuous(labels = percent) +
    labs(y = NULL, x = "Percentage", fill = variable_name) +
    theme_classic() +
    theme(axis.text.y = element_blank(), strip.text = element_text(size = 10), legend.position = "top") +
    scale_fill_brewer(palette = palette_name)
}

# Gather data to long format and calculate counts and percentages
df_barplot <- sampledemos %>%
  gather(Variable, Category) %>%
  group_by(Variable, Category) %>%
  filter(!is.na(Category)) %>%
  summarise(n = n()) %>%
  mutate(Percentage = n / sum(n) * 100)

# Create separate plots for each variable
plot_state <- create_bar_plot(df_barplot, "State", "Spectral")
plot_language <- create_bar_plot(df_barplot, "Language", "Paired")
plot_age <- create_bar_plot(df_barplot, "age", "Set3")
plot_urban_rural <- create_bar_plot(df_barplot, "urban_rural", "Dark2")
plot_gender <- create_bar_plot(df_barplot, "gender", "Pastel1")
plot_caste <- create_bar_plot(df_barplot, "caste", "Set1")
plot_religion <- create_bar_plot(df_barplot, "religion", "Set2")

# Combine the plots with spacing
combined_plot <- gridExtra::arrangeGrob(plot_state, plot_language, plot_age, plot_urban_rural, plot_gender, plot_caste, plot_religion, ncol = 1, heights = c(1, 1, 1, 1, 1, 1, 1))

# Print the combined plot
grid::grid.newpage()
grid::grid.draw(combined_plot)

```

\newpage
## Individually/Community owned energy technologies (n= 2160)
The percentages are rounded off to whole numbers.

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

#bar plot for likert responses perceived risk - individually owned technologies 
df_barplot %>% ggplot(aes(fill= fct_rev(factor(Perceived_Risk, levels=c("Extremely risky", "Very risky","Moderately risky","Slightly risky","Not at all risky","Rather not say/Don't know"))), y=n , x=Technology)) + 
  geom_bar(position="fill", stat = "identity")+
  geom_text(data = df_barplot_percent, aes(label=paste0(Percentage, "%"), y=n), position = position_fill(vjust=0.5), size=3) +
  scale_x_discrete(limits = c("INDSolar", "INDFirewoodetc","INDWind", "INDHydro", "INDDiesel" , "INDBiogas","INDKerosene", "INDLPG"))+
  scale_fill_manual("legend", values = c("Extremely risky" = "#8C4646", "Very risky" = "#D9695F", "Moderately risky" = "#F2A679", "Slightly risky" = "#F2D091","Not at all risky" = "#5D8C7B", "Rather not say/Don't know" = "grey94"))+
   labs( y = "Perceived Risk", x ="Individually Owned Energy Technologies")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

#perceived benefit individually owned technologies

df_barplotben %>% ggplot(aes(fill= factor(Perceived_Benefit, levels=c("Rather not say/Don't know","Not at all beneficial","Slightly beneficial","Moderately beneficial","Very beneficial", "Extremely beneficial")), y=n , x=Technology)) + 
  geom_bar(position="fill",stat="identity")+
   geom_text(data = df_barplotben_percent, aes(label=paste0(Percentage, "%"), y=n), position = position_fill(vjust=0.5), size=3) +
  scale_fill_manual("legend", values = c("Rather not say/Don't know" = "grey94" ,"Not at all beneficial" = "orange","Slightly beneficial"="yellow" ,"Moderately beneficial" = "palegreen","Very beneficial"= "green3", "Extremely beneficial"= "green4"))+
  scale_x_discrete(limits = c( "INDSolar", "INDFirewoodetc" , "INDLPG",  "INDWind", "INDHydro", "INDDiesel" , "INDBiogas","INDKerosene"))+
  labs( y = "Perceived Benefit", x ="Individually Owned Energy Technologies")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

\newpage

# Perceived risk and Perceived Benefit in comparison

```{r, echo = FALSE}

# exploring LPG and firewood discrepancies 
# first we observe that the  perceived risk from LPG is higher than perceived risk from firewood
joineddf_IND <- joineddf %>%
  dplyr::select(starts_with(c("Ben_IND", "Risky_IND")))

# Melt the data frame to long format
long_formatIND <- joineddf_IND %>% 
  pivot_longer(everything(), names_to = "technology", values_to = "value") %>%
  mutate(risk_or_benefit = if_else(str_detect(technology, "Risky"), "risk", "benefit"),
         technology = str_replace(technology, "Risky_|Ben_", ""))

# Calculate mean and sd for each technology and category (risk or benefit)
summary_dfIND <- long_formatIND %>%
  group_by(technology, risk_or_benefit) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            sd = sd(value, na.rm = TRUE),
            se = sd(value, na.rm = TRUE) / sqrt(n()),
            .groups = "drop")

# Order technologies by mean risk
order_riskIND <- summary_dfIND %>% 
  filter(risk_or_benefit == "risk") %>%
  arrange(mean) %>% 
  pull(technology)

# Change the levels of factor 'technology'
summary_dfIND$technology <- factor(summary_dfIND$technology, levels = order_riskIND)

# Plotting the data
ggplot(summary_dfIND, aes(x = technology, y = mean, fill = risk_or_benefit)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = 0.3, position = position_dodge(0.9)) +
  ylim(0, 5) +
  scale_fill_manual("legend", 
                    values = c("benefit" = "palegreen3", "risk" = "firebrick2"), 
                    labels = c("benefit" = "Perceived Benefit", "risk" = "Perceived Risk")) +
  labs(y = "Mean Values", x = "Energy Technologies", fill = "Perceived") +
  ggtitle("Perceived risk and benefit from individually owned energy technologies") +
  coord_flip()
```

\newpage

# T-tests

## Pairwise T-test: Mean perceived risk and  mean perceived benefit (all individually owned energy technologies)

```{r, echo = FALSE, fig.width=14, fig.height=6}
# Now we wanna know if these differences are significant using simple t test

perceivedriskIND <-joineddf %>% select(starts_with(c("Risky_IND"))) %>%
  gather(key = "technology", value = "perceived_risk") %>% 
  mutate(technology = gsub("Risky_", "", technology))

result_ttestIND <- pairwise.t.test(perceivedriskIND$perceived_risk, perceivedriskIND$technology, p.adjust.method = "BH")

# visualising the pairwaise wilcox test results. the non significant pairs are grey

tidy_result_ttestIND <- broom::tidy(result_ttestIND)

heatmap1IND <- ggplot(tidy_result_ttestIND, aes(x = group1, y = group2, fill = p.value)) + 
  geom_tile(color = "white") + 
  scale_fill_gradient2(low = "firebrick2", high = "white", midpoint = 0.025, 
                       limits = c(0, 0.05), space = "Lab", 
                       name = "P-value") + 
  theme_classic() + 
  labs(x = "Technology 1", y = "Technology 2") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
   theme(axis.text.y = element_text(size=12), 
        axis.text.x = element_text(size=12))

## now benIND

perceivedbenIND <-joineddf %>% select(starts_with(c("Ben_IND"))) %>%
  gather(key = "technology", value = "perceived_benefit") %>% 
  mutate(technology = gsub("Ben_", "", technology))

result_ttestINDb <- pairwise.t.test(perceivedbenIND$perceived_benefit, perceivedbenIND$technology, p.adjust.method = "BH")

# visualising the pairwaise t- test results. the non significant pairs are grey

tidy_result_ttestINDb <- broom::tidy(result_ttestINDb)

heatmap2IND <- ggplot(tidy_result_ttestINDb, aes(x = group1, y = group2, fill = p.value)) + 
  geom_tile(color = "white") + 
  scale_fill_gradient2(low = "palegreen3", high = "white", midpoint = 0.025, 
                       limits = c(0, 0.05), space = "Lab", 
                       name = "P-value") + 
  theme_classic() + 
  labs(x = "Technology 1", y = "Technology 2") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
   theme(axis.text.y = element_text(size=12), 
        axis.text.x = element_text(size=12))

library(gridExtra)

grid.arrange(heatmap1IND, heatmap2IND, ncol=2) 
```

## Paired T-test: Comparing mean perceived risk and mean perceived benefit for each technology.

Null hypothesis (H0): The mean difference between perceived risk and perceived benefit from each technology is zero.
All p values are less than 0.05 suggesting that the differences observed in the bargraph are statistically significant.

```{r, echo=FALSE}

# Convert character columns to factors
long_formatIND$technology <- factor(long_formatIND$technology)
long_formatIND$risk_or_benefit <- factor(long_formatIND$risk_or_benefit)

# Perform the t- Test for each technology
p_values <- long_formatIND %>%
  split(.$technology) %>%
  lapply(function(x) t.test(x$value[x$risk_or_benefit == "risk"], x$value[x$risk_or_benefit == "benefit"], paired = TRUE)) %>%
  lapply(function(x) x$p.value)

p_values

```

# Acceptance = Perceived Benefit - Perceived Risk

Graph representing a combined acceptance scale obtained by subtracting perceived risk from perceived benefit for each respondent

```{r, echo = FALSE}

# combining risk and benefit from each energy technology

INDacceptance <- joineddf %>% select(starts_with(c("Risky_IND", "Ben_IND"))) %>%
  na.omit()%>%
  mutate(Biogas = Ben_INDBiogas - Risky_INDBiogas,
         INDHydro = Ben_INDHydro - Risky_INDHydro,
         INDWind = Ben_INDWind - Risky_INDWind,
         INDSolar = Ben_INDSolar - Risky_INDSolar,
         Diesel = Ben_INDDiesel - Risky_INDDiesel,
         Kerosene = Ben_INDKerosene - Risky_INDKerosene,
         Firewood = Ben_INDFirewoodetc - Risky_INDFirewoodetc,
         LPG = Ben_INDLPG - Risky_INDLPG)%>%
  select(-starts_with(c("Risky", "Ben")))

# Compute the mean of each column
mean_INDacceptance <- data.frame(col = names(INDacceptance), mean_val = sapply(INDacceptance, mean))

# Compute standard error (not deviation)(divided by root of n)
sem <- function(x) sqrt(var(x, na.rm = TRUE) / length(na.omit(x)))
sem_INDacceptance <- data.frame(col = names(INDacceptance), sem_val = sapply(INDacceptance, sem))

mean_INDacceptance <- merge(mean_INDacceptance, sem_INDacceptance, by = "col")

# Plot
ggplot(mean_INDacceptance, aes(x = col, y = mean_val, fill = ifelse(mean_val >= 0, 'Above 0', 'Below 0'))) + 
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = mean_val - sem_val, ymax = mean_val + sem_val), width = 0.2) +
  geom_text(aes(label = round(mean_val, 2)), vjust = -0.9) +
  scale_fill_manual(values = c('Above 0' = 'palegreen3', 'Below 0' = 'firebrick2')) +
  labs(fill = "Legend") +
  xlab("Energy Technologies") +
  ylab("Mean Value") +
  ggtitle("Benefit - Risk for Each Energy Technology") +
  theme_minimal()+
  ylim(0, 2)

```
\newpage

# Linear Regression Models

## Perceived Risk from Firewood : demographic variables

```{r, echo=FALSE}

joineddf$Uppercaste <- ifelse(joineddf$caste %in% c('Brahmin', 'General'), 1, 0)

# Convert `gender` into binary variable 'male' (1) vs 'female' (0)
joineddf$Male <- ifelse(joineddf$gender == 'Male', 1, 0)

# Convert `religion` into binary variable 'Hinduism' (1) vs 'Non-Hinduism' (0)
joineddf$Hindu <- ifelse(joineddf$religion == 'Hinduism', 1, 0)

# # Convert `caste` into binary variable 'upper' (1) vs 'non-upper' (0)
codedmodule1$Uppercaste <- ifelse(codedmodule1$caste %in% c('Brahmin', 'General'), 1, 0)

# Convert `gender` into binary variable 'male' (1) vs 'female' (0)
codedmodule1$Male <- ifelse(codedmodule1$gender == 'Male', 1, 0)

# Convert `religion` into binary variable 'Hinduism' (1) vs 'Non-Hinduism' (0)
codedmodule1$Hindu <- ifelse(codedmodule1$religion == 'Hinduism', 1, 0)

falldemos <- joineddf %>%
            select(Risky_INDFirewoodetc,Uppercaste, Male, Hindu, urban_rural, age, State)%>%
            na.omit()

falldemoslm1 <- lm(Risky_INDFirewoodetc ~ Uppercaste + Male + Hindu + urban_rural + age, data = falldemos)
# Print model summary
#summary(falldemoslm1)
#plot(alldemoslm1)

codedmodule1$totalincome <- as.numeric(codedmodule1$totalincome)
codedmodule1$otherincome <- as.numeric(codedmodule1$otherincome)

falldemos2 <-codedmodule1 %>%
            select(Risky_INDFirewoodetc,Uppercaste, Male, Hindu, urban_rural, age, State, totalincome, otherincome)%>%
            mutate(income = totalincome + otherincome)%>%
            na.omit()

#lapply(falldemos2, unique)

falldemos$State <- as.factor(falldemos$State)
#levels(falldemos$State)

falldemos$age <- as.factor(falldemos$age)
#levels(falldemos$age)

# 2) lm with all demographic variables
falldemoslm2<- lm(Risky_INDFirewoodetc ~ Uppercaste + Male + Hindu + urban_rural + age + State , data = falldemos)
# Print model summary
#summary(falldemoslm2)
#plot(alldemoslm1)

```

```{r, echo=FALSE, results='asis'}
library(stargazer)

cat("\\begingroup")
cat("\\setlength{\\tabcolsep}{1pt}")
cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(falldemoslm1, falldemoslm2,
          title = "Results from 2 linear regression models",
          type = "latex"
)
cat("\\endgroup")

```

## Perceived Risk from LPG : demographic variables 
```{r, echo=FALSE}
#same linear models with LPG

LPGalldemos <- joineddf %>%
            select(Risky_INDLPG,Uppercaste, Male, Hindu, urban_rural, age, State)%>%
            na.omit()

LPGalldemoslm1 <- lm(Risky_INDLPG ~ Uppercaste + Male + Hindu + urban_rural + age , data = LPGalldemos)
# Print model summary
#summary(LPGalldemoslm1)
#plot(alldemoslm1)

LPGalldemos2 <-codedmodule1 %>%
            select(Risky_INDLPG,Uppercaste, Male, Hindu, urban_rural, age, State, totalincome, otherincome)%>%
            mutate(income = totalincome + otherincome)%>%
            na.omit()

#lapply(LPGalldemos2, unique)

# 2) lm with all demographic variables
LPGalldemoslm2<- lm(Risky_INDLPG ~ Uppercaste + Male + Hindu + urban_rural + age + State , data = LPGalldemos)
# Print model summary
#summary(LPGalldemoslm2)
#plot(alldemoslm1)

```

```{r, echo=FALSE, results='asis'}
library(stargazer)

cat("\\begingroup")
cat("\\setlength{\\tabcolsep}{1pt}")
cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(LPGalldemoslm1,LPGalldemoslm2 , 
          title = "Results from 2 linear regression models",
          type = "latex"
)
cat("\\endgroup")

```

Table 1 and 2 :

1. Uppercaste, Male, Hindu and urban_rural are binary variables. 
2. Reference for age variables is 18-24 years old
3. Reference for State is Maharashtra

# Linear Regression model - stove ownership by four groups - (i)LPG, (ii)Traditonal Stove(Including Firewood), (iii)Both and (iv)Other

```{r, echo = FALSE}

# # Convert `caste` into binary variable 'upper' (1) vs 'non-upper' (0)
module1$Uppercaste <- ifelse(module1$caste %in% c('Brahmin', 'General'), 1, 0)

# Convert `gender` into binary variable 'male' (1) vs 'female' (0)
module1$Male <- ifelse(module1$gender == 'Male', 1, 0)

# Convert `religion` into binary variable 'Hinduism' (1) vs 'Non-Hinduism' (0)
module1$Hindu <- ifelse(module1$religion == 'Hinduism', 1, 0)

stove <-module1 %>%
        filter(!row_number() %in% c(1,2))%>%
        select(Risky_INDFirewoodetc, Risky_INDLPG, urban_rural, Male, Uppercaste, Hindu, age, State, cookstove,)%>%
        mutate(across(starts_with("Risky"), ~case_when(. =="Not at all risky" ~ 1, 
                                                 . =="Slightly risky" ~ 2, 
                                                 . =="Moderately risky" ~ 3, 
                                                 . =="Very risky" ~ 4, 
                                                 . =="Extremely risky" ~ 5))) %>%
  na.omit()

#lapply(stove, unique)
library(dplyr)

grouped_stove <- stove %>%
  mutate(
    group = case_when(
      # Group 3
      cookstove %in% c(
        "Liquefied Petroleum Gas (LPG)/Cooking gas stove,Liquid Fuel Stove,Traditional Solid Fuel Stove",
        "Liquefied Petroleum Gas (LPG)/Cooking gas stove,Three Stone Stove/Open Fire",
        "Liquefied Petroleum Gas (LPG)/Cooking gas stove,Liquid Fuel Stove,Traditional Solid Fuel Stove,Three Stone Stove/Open Fire",
        "Liquefied Petroleum Gas (LPG)/Cooking gas stove,Three Stone Stove/Open Fire,Other(Please Specify)",
        "Liquefied Petroleum Gas (LPG)/Cooking gas stove,Traditional Solid Fuel Stove,Three Stone Stove/Open Fire",
        "Electric Stove,Liquefied Petroleum Gas (LPG)/Cooking gas stove,Traditional Solid Fuel Stove",
        "Liquefied Petroleum Gas (LPG)/Cooking gas stove,Traditional Solid Fuel Stove",
        "Solar Cooker,Liquefied Petroleum Gas (LPG)/Cooking gas stove,Traditional Solid Fuel Stove,Three Stone Stove/Open Fire",
        "Electric Stove,Solar Cooker,Liquefied Petroleum Gas (LPG)/Cooking gas stove,Traditional Solid Fuel Stove,Three Stone Stove/Open Fire",
        "Solar Cooker,Liquefied Petroleum Gas (LPG)/Cooking gas stove,Liquid Fuel Stove,Traditional Solid Fuel Stove,Three Stone Stove/Open Fire",
        "Electric Stove,Liquefied Petroleum Gas (LPG)/Cooking gas stove,Traditional Solid Fuel Stove,Three Stone Stove/Open Fire",
        "Solar Cooker,Liquefied Petroleum Gas (LPG)/Cooking gas stove,Traditional Solid Fuel Stove,No Food Cooked in Household",
        "Electric Stove,Liquefied Petroleum Gas (LPG)/Cooking gas stove,Three Stone Stove/Open Fire",
        "Solar Cooker,Liquefied Petroleum Gas (LPG)/Cooking gas stove,Three Stone Stove/Open Fire"
      ) ~ "Both",

      # Group 1
      cookstove %in% c(
        "Three Stone Stove/Open Fire",
        "Traditional Solid Fuel Stove",
        "Three Stone Stove/Open Fire,Other(Please Specify)",
        "Traditional Solid Fuel Stove,Three Stone Stove/Open Fire",
        "Traditional Solid Fuel Stove,Three Stone Stove/Open Fire,Other(Please Specify)",
        "Solar Cooker,Three Stone Stove/Open Fire",
        "Piped Natural Gas Stove,Traditional Solid Fuel Stove,Three Stone Stove/Open Fire",
        "Biogas Stove,Traditional Solid Fuel Stove",
        "Electric Stove,Biogas Stove,Traditional Solid Fuel Stove",
        "Electric Stove,Traditional Solid Fuel Stove"
      ) ~ "Traditional",

       # Group 2
      cookstove %in% c(
        "Liquefied Petroleum Gas (LPG)/Cooking gas stove,Other(Please Specify)",
        "Liquefied Petroleum Gas (LPG)/Cooking gas stove,Biogas Stove",
        "Electric Stove,Liquefied Petroleum Gas (LPG)/Cooking gas stove",
        "Liquefied Petroleum Gas (LPG)/Cooking gas stove,Biogas Stove,Liquid Fuel Stove",
        "Solar Cooker,Liquefied Petroleum Gas (LPG)/Cooking gas stove",
        "Solar Cooker,Liquefied Petroleum Gas (LPG)/Cooking gas stove,Liquid Fuel Stove",
        "Liquefied Petroleum Gas (LPG)/Cooking gas stove,No Food Cooked in Household",
        "Liquefied Petroleum Gas (LPG)/Cooking gas stove"
      ) ~ "LPG",

      # Default to "Other" for any cookstove values not specified in the conditions above
      TRUE ~ "Other"
    )
  )

count2 <- grouped_stove %>% count(group)

grouped_stove$group <- as.factor(grouped_stove$group)

grouped_stove$group <- factor(grouped_stove$group, levels = c("LPG", "Traditional", "Both", "Other"))

#levels(grouped_stove$group)

# lm with stove ownership 
LPGstove<- lm(Risky_INDLPG ~ urban_rural + Hindu + Male + Uppercaste + age +  group , data = grouped_stove)
# Print model summary
#summary(LPGstove)

# lm with stove ownership 
fstove<- lm(Risky_INDFirewoodetc ~ urban_rural + Hindu + Male + Uppercaste + age +  group , data = grouped_stove)
# Print model summary
#summary(fstove)

count2
```

```{r, echo=FALSE, results='asis'}
library(stargazer)

cat("\\begingroup")
cat("\\setlength{\\tabcolsep}{1pt}")
cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(LPGstove, fstove, 
          title = "Results from 2 linear regression models",
          type = "latex"
)
cat("\\endgroup")

```

### 2023-09-20 LSIandISI.Rmd
lot of changes because I wasn't opening the project file.

---
title: "moduleoneanalysis"
output:
  pdf_document: default
  html_document:
    fig_width: 7
    fig_height: 6
    fig_caption: yes
    keep_md: yes
    theme: paper
    df_print: paged
---

```{r load packages, warning = FALSE, message = FALSE}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(psych))

```

```{r, eval=TRUE, echo = FALSE}

moduleone <- read_excel(here::here("thesis_surveydata/livelihood_insecurity_complete.xlsx"))
save(moduleone, file = "moduleone.rda")
module1 <- data.frame(moduleone)

# loaded data set for module 2 eco -pol variables and removes the rows with question number and question text
```

```{r, warning = FALSE, echo = FALSE}
#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
codedmodule1 <- module1 %>%
  #remove row 1
  filter(!row_number() %in% c(1,2)) %>%

  # replace risky likert scale with numbers
  mutate(across(starts_with("Risky"), ~case_when(. =="Not at all risky" ~ 1, 
                                                 . =="Slightly risky" ~ 2, 
                                                 . =="Moderately risky" ~ 3, 
                                                 . =="Very risky" ~ 4, 
                                                 . =="Extremely risky" ~ 5))) %>%

  # replace beneficial likert scale with numbers  
  mutate(across(starts_with("Ben"), ~case_when(. =="Not at all beneficial" ~ 1,
                                               . =="Slightly beneficial" ~ 2,
                                               . =="Moderately beneficial" ~ 3,
                                               . =="Very beneficial" ~ 4,
                                               . =="Extremely beneficial" ~ 5 ))) %>%

  # replace nuclear acceptance likert scale with numbers
  mutate(across(c(N_accept,N_reluctantlyaccept,N_reject), ~case_when(. == "Strongly disagree" ~ 1, 
                                                                     . == "Somewhat disagree" ~ 2,
                                                                     . == "Neither agree nor disagree" ~3,
                                                                     . == "Somewhat agree" ~ 4,
                                                                     . == "Strongly agree" ~ 5))) %>%

  mutate(across(Livelihood_Income, ~case_when(. == "(a) own farming/fishing/animal rearing/business" ~ "LSI", 
                                              . == "(b) employed for wages/salary" ~ "ISI",
                                              . == "(c) student" ~"other",
                                              . == "(d) currently unemployed" ~ "other",
                                              . == "(e) homemaker" ~ "homemaker",
                                              . == "(f) retired" ~ "other",
                                              . == "(g) unable to work" ~ "other" ))) %>%

  # coding education
  mutate(across(education, ~case_when(. == "No schooling completed" ~ 0, 
                                      . == "Primary school" ~ 1,
                                      . == "Grade 10th" ~ 2,
                                      . == "Grade 12th" ~ 3,
                                      . == "Some college, no degree" ~ 4,
                                      . == "Trade/technical/vocational training" ~ 5,
                                      . == "Bachelor's degree" ~ 6,
                                      . == "Master's degree" ~ 7,
                                      . == "Professional degree" ~ 8,
                                      . == "Doctorate degree" ~ 9 ))) %>%

  # coding yes and no questions
  mutate(across(c(Lassociation,Iassociation, govtscheme, wateravail, polposition, polparty), ~case_when(.== "Yes" ~ 1,
                                                                                                        .== "No" ~ 0))) %>%
  # reverse coding yes and no questions
  mutate(across(c(illness,severeillness), ~case_when(.== "Yes" ~ 0,
                                                     .== "No" ~ 1))) %>%

  # coding How confident are you that you can continue your current livelihood if you want to? 
  mutate(across(Lconfidence, ~case_when(. == "Not at all confident" ~ 1, 
                                        . == "Not much confident" ~ 2,
                                        . == "Neutral" ~3,
                                        . == "Somewhat confident" ~ 4,
                                        . == "Very confident" ~ 5))) %>%

  mutate(across(c(Lboat, houseown), ~case_when(.== "Own it" ~ 1,
                                               .== "Rent it" ~ 0))) %>%

  # J security index coding
  mutate(across(JISRkeep, ~case_when(. == "Strongly disagree" ~ 1, 
                                     . == "Somewhat disagree" ~ 2,
                                     . == "Neither agree nor disagree" ~3,
                                     . == "Somewhat agree" ~ 4,
                                     . == "Strongly agree" ~ 5))) %>%

  # reverse code JIS 
  mutate(across(c(JISlosefuture, JISlose, JISfuture), ~case_when(. == "Strongly disagree" ~ 5, 
                                                                 . == "Somewhat disagree" ~ 4,
                                                                 . == "Neither agree nor disagree" ~3,
                                                                 . == "Somewhat agree" ~ 2,
                                                                 . == "Strongly agree" ~ 1))) %>%

  mutate(across(c(totalincome, otherincome), ~case_when(. == "Less than Rs 1,00,000" ~ 1,
                                                        . == "Rs 1,00,000 to Rs 2,50,000"  ~ 2,
                                                        . == "Rs 2,50,001 to Rs 5,00,000" ~ 3,
                                                        . == "Rs 5,00,001 to Rs 10,00,000" ~ 4,
                                                        . == "Rs 10,00,001 and above"  ~ 5,
                                                        . == "Doesn't apply" ~ 0))) %>%

  mutate(across(c(workknowledge, subsidyknow), ~case_when(. == "Very poor" ~ 1, 
                                                          . == "Poor" ~ 2,
                                                          . == "Fair" ~3,
                                                          . == "Good" ~ 4,
                                                          . == "Very good" ~ 5))) %>%

  mutate(across(c(drinkingwater, cookingwater), ~case_when(. == "Bottled water/ Filtered Water" ~ 1,                                       
                                                           .  == "Piped into dwelling" ~ 2,                                                  
                                                           .  == "Piped to neighbour" ~ 3,                                                   
                                                           .  == "Piped to yard/plot" ~ 4, 
                                                           .  == "Protected well" ~ 5, 
                                                           .  == "Public tap/standpipe" ~6,
                                                           .  == "Surface Water  (River/Dam/Lake/Pond/Stream/Canal/Irrigation Channel)" ~7, 
                                                           .  == "Tanker Truck" ~ 8,
                                                           .  == "Tubewell/borehole" ~ 9,
                                                           .  == "Unprotected Spring" ~ 10))) %>%

  mutate(across(toilet, ~case_when(. == "No facility/bush/field" ~ 1,                                       
                                   .  == "Hanging toilet/hanging latrine" ~ 2,                                             
                                   .  == "Bucket toilet"  ~ 3,                                                   
                                   .  == "Composting toilet"  ~ 4, 
                                   .  == "Pit latrine without slab/open pit" ~ 5, 
                                   .  == "Pit latrine with slab" ~6,
                                   .  == "Ventilated improved pit laterine"  ~7, 
                                   .  == "Flush to somewhere else"  ~ 8,
                                   .  == "Flush to pit latrine"  ~ 9,
                                   .  == "Flush to septic tank" ~ 10,
                                   .  == "Flush to piped sewer system" ~ 11))) %>%

  mutate(across(house, ~case_when(. == "Hut made of mud, bamboo, straw etc. (kutcha house)" ~ 1, 
                                  . == "Permanent single story house (pukka house)" ~ 2,
                                  . == "Apartment/Flat in a multi-story building"  ~3,
                                  . == "Multi-story house" ~ 4))) %>%

  mutate(across(foodtrouble, ~case_when(. == "8 or more months" ~ 1,                                       
                                        .  == "6-8 months"  ~ 2,                                                  
                                        .  == "4-6 months"  ~ 3,                                                   
                                        .  == "2-4 months"  ~ 4, 
                                        .  == "1-2 months" ~ 5, 
                                        .  == "0 months"  ~6))) %>%

  mutate(across(foodadequacy, ~case_when(. == "Extremely inadequate" ~ 1, 
                                         . == "Moderately inadequate" ~ 2,
                                         . == "Slightly inadequate" ~3,
                                         . == "Neither adequate nor inadequate" ~ 4,
                                         . == "Slightly adequate" ~ 5,
                                         . == "Moderately adequate" ~ 6,
                                         . == "Extremely adequate" ~ 7))) %>%

  # separating cooking, vehicle and food cols into separate entries
  separate(col = cookstove, into = c("cook1", "cook2", "cook3", "cook4"), sep = ",") %>%
  separate(col = vehicle, into = c("vehicle1", "vehicle2", "vehicle3", "vehicle4"), sep = ",") %>%
  separate(col = foodsource, into = c("food1", "food2", "food3", "food4"), sep = ",") %>%

  mutate(across(c(cook1, cook2, cook3, cook4), ~case_when(. == "Three Stone Stove/Open Fire" ~ 1, 
                                  . == "Traditional Solid Fuel Stove" ~ 2,
                                  . == "Liquid Fuel Stove" ~3,
                                  . == "Biogas Stove" ~ 4,
                                  . == "Piped Natural Gas Stove" ~ 5,
                                  . == "Liquefied Petroleum Gas (LPG)/Cooking gas stove" ~ 6,
                                  . == "Solar Cooker" ~ 7,
                                  . == "Electric Stove" ~ 7,
                                  is.na(.) ~ 0))) %>%

  mutate(across(c(vehicle1, vehicle2, vehicle3, vehicle4, vehicletext), ~case_when(. == "Bicycle" ~ 1, 
                                    . == "Animal Drawn Cart" ~ 2,
                                    . == "Motorcycle/Scooter" ~3,
                                    . == "Car" ~ 4,
                                    . == "Truck" ~ 4,
                                    . == "Boat with Motor" ~ 4,
                                    . == "Tractor" ~ 4,
                                    . == "E-rickshaw" ~ 1,
                                    . == "Tempo" ~ 3,
                                    . == "Nothing" ~ 0,
                                    . == "Other (Please Specify)" ~ 0,
                                    is.na(.) ~ 0))) %>%

  mutate(across(c(food1, food2, food3,food4), ~case_when(. == "Forest" ~ 1, 
                                  . == "Own Farm" ~ 2,
                                  . == "Market" ~4,
                                  . == "Own livestock" ~ 2,
                                  . == "Subsidised ration shops" ~ 3,
                                  is.na(.) ~ 0)))

codedmodule1$gender <- factor(codedmodule1$gender, levels = c("Male","Female"))

unique(codedmodule1$Lfarmbigha)
unique(codedmodule1$farwatermins)

```

```{r, echo=FALSE}

colnames(codedmodule1)
addedcols <- codedmodule1 %>%
  mutate_at(vars(Lassociation, Lboat, Iassociation, totalincome, otherincome, govtscheme, education, subsidyknow, drinkingwater, cookingwater, wateravail, toilet, house, houseown, cook1, cook2, cook3, cook4, vehicle1, vehicle2, vehicle3, vehicle4, vehicletext, polposition, polparty, food1, food2, food3, food4, foodadequacy, foodtrouble, illness, severeillness, Llenght,  Lanimalcowbull, Lanimalcattle, Lanimalhorses, Lanimalgoats, Lanimalsheep, Lanimalpoultry, Ilenght, Ipropvalue,  healthdist), as.numeric) %>%

  #Lfarmbigha,farwatermins,
  mutate(stove = cook1 + cook2 + cook3 + cook4, 
        vehicle = vehicle1 + vehicle2 + vehicle3 + vehicle4 + vehicletext,
        food = food1 + food2 + food3 + food4,
        #income = totalincome + otherincome,
        animals = Lanimalcowbull + Lanimalcattle + Lanimalhorses + Lanimalgoats + Lanimalsheep + Lanimalpoultry) %>%
  dplyr::select(-cook1, -cook2, -cook3, -cook4, -vehicle1, -vehicle2, -vehicle3, -vehicle4, -vehicletext, -food1, -food2, -food3, -food4, -Lanimalcowbull, -Lanimalcattle, -Lanimalhorses, -Lanimalgoats, -Lanimalsheep, -Lanimalpoultry) %>%
  unite("LIlenght", c(Llenght,Ilenght), na.rm = TRUE, remove = TRUE)%>%
  unite("LIassociation", c(Lassociation,Iassociation), na.rm = TRUE, remove = TRUE)

```

\newpage

The total n for this survey is 1062. However, the sample is divided by the type of work people do as below:

```{r, echo=FALSE}

count <- module1 %>% count(Livelihood_Income)

count <- count[1:(nrow(count) - 2), ]

count

```

# The Problem of large NAs

```{r, echo=FALSE}

# Count the number of NAs in each column
num_NAs <- colSums(is.na(addedcols))

# Print the result
print(num_NAs)

```

```{r, echo = FALSE}

nuclear_LI <- addedcols %>% 
  dplyr::select(Risky_Nuclear,State, gender, caste, religion, urban_rural, age,  Livelihood_Income,education, workknowledge,LIlenght, subsidyknow, drinkingwater,cookingwater, wateravail,toilet, house,stove, vehicle, houseown, polposition, LIassociation,polparty, govtscheme, totalincome, Ipropvalue, Lboat, animals, foodadequacy, foodtrouble,food, healthdist, illness, severeillness)

#farwatermins,Lfarmbigha,

# checking NAs in LSI part 
#assetcheck <- addedcols %>% filter(Livelihood_Income == "LSI") %>%
            #dplyr::select(Lfarmland,Lfarmbigha,animals)

#num_NAs2 <- colSums(is.na(assetcheck))

#print(num_NAs2)

codedmodule1 %>% count(Livelihood_Income)
addedcols %>% count(Livelihood_Income)
#codedmodule1 %>% count(Lfarmbigha)
codedmodule1 %>% filter(Livelihood_Income == "LSI") %>% count(Lfarmland)
addedcols %>% filter(Livelihood_Income == "LSI") %>% count(animals)
codedmodule1 %>% count(Lboat)

addedcols %>% filter(Livelihood_Income == "LSI") %>% filter(Lfarmland == "Doesn't apply") %>% count(Lboat)
addedcols %>% filter(Livelihood_Income == "LSI") %>% filter(Lfarmland == "Doesn't apply") %>% count(animals)

addedcols %>% filter(Livelihood_Income == "ISI") %>% count(Iproperty)

# checking NAs in ISI part

module1 %>% filter(!row_number() %in% c(1,2)) %>% filter(Livelihood_Income != "(a) own farming/fishing/animal rearing/business") %>% count(Iproperty)

# there are only 4 people who said they own a boat but not a farmland when looking at those people who answered LSI part of the survey. So we will just look at boat as  another livelihood asset and remove the 4 responses by removing Doesn't apply values in the Lfarmland part.

```

```{r, echo = FALSE}
# Nuclear dataframe for LSI/ISI with standardized values

# Convert columns to numeric starting from 'education'
cols_to_convert <- names(nuclear_LI)[which(names(nuclear_LI) == 'education'):length(names(nuclear_LI))]
nuclear_LI[cols_to_convert] <- lapply(nuclear_LI[cols_to_convert], as.numeric)

nuclear_LI$LIassociation <- as.numeric(nuclear_LI$LIassociation)
nuclear_LI$LIlenght <- as.numeric(nuclear_LI$LIlenght)
# Standardize the values
standardize <- function(x) {
  (x - min(x, na.rm = TRUE)) / (max(x, na.rm = TRUE) - min(x, na.rm = TRUE))
}

nuclear_LI[cols_to_convert] <- lapply(nuclear_LI[cols_to_convert], standardize)

# Displaying the first few rows of the dataframe
#head(nuclear_LI)

```

```{r, echo = FALSE}

# lms now for each category and then putting them into a single table using stargazer

nuclear_model <- nuclear_LI %>%  
  mutate(
    human_asset = rowMeans(dplyr::select(., education, workknowledge, LIlenght), na.rm = TRUE),
    physical_asset = rowMeans(dplyr::select(., drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown), na.rm = TRUE),
    social_asset = rowMeans(dplyr::select(., polposition, LIassociation, polparty, govtscheme), na.rm = TRUE),
    financial_asset = totalincome,
    food_security = rowMeans(dplyr::select(., foodadequacy, foodtrouble, food), na.rm = TRUE),
    health_status = rowMeans(dplyr::select(., healthdist, illness, severeillness), na.rm = TRUE)
  )%>%
  dplyr::select(
    -c(education, workknowledge, LIlenght, 
      drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown, 
      polposition, LIassociation, polparty, govtscheme, 
      foodadequacy, foodtrouble, food,
      healthdist, illness, severeillness,
      totalincome, Lfarmbigha, Ipropvalue, Lboat, animals)
  )%>%
  mutate(LIscore = rowMeans(dplyr::select(., human_asset, physical_asset, social_asset,financial_asset, food_security,health_status), na.rm = TRUE))

nuclearLI_lm <- lm(Risky_Nuclear ~ caste + gender + urban_rural + human_asset + physical_asset + social_asset + financial_asset + food_security + health_status , data = nuclear_model)

nuclearLI_lm2 <- lm(Risky_Nuclear ~ caste + gender + urban_rural + LIscore , data = nuclear_model)

summary(nuclearLI_lm)
summary(nuclearLI_lm2)
#plot(nuclearLI_lm)

```

```{r, echo=FALSE}
solar_LI <- addedcols %>% 
  dplyr::select(Risky_Solar,State, gender, caste, religion, urban_rural, age,  Livelihood_Income,education, workknowledge,LIlenght, subsidyknow, drinkingwater,cookingwater,farwatermins, wateravail,toilet, house,stove, vehicle, houseown, polposition, LIassociation,polparty, govtscheme, totalincome, Lfarmbigha,  Ipropvalue, Lboat, animals, foodadequacy, foodtrouble,food, healthdist, illness, severeillness)

# Solar dataframe for LSI/ISI with standardized values

# Convert columns to numeric starting from 'education'
cols_to_convert <- names(solar_LI)[which(names(solar_LI) == 'education'):length(names(solar_LI))]
solar_LI[cols_to_convert] <- lapply(solar_LI[cols_to_convert], as.numeric)

# Standardize the values
standardize <- function(x) {
  (x - min(x, na.rm = TRUE)) / (max(x, na.rm = TRUE) - min(x, na.rm = TRUE))
}

solar_LI[cols_to_convert] <- lapply(solar_LI[cols_to_convert], standardize)

# Displaying the first few rows of the dataframe
head(solar_LI)

solar_model <- solar_LI %>%  
  mutate(
    human_asset = rowMeans(dplyr::select(., education, workknowledge, LIlenght), na.rm = TRUE),
    physical_asset = rowMeans(dplyr::select(., drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown), na.rm = TRUE),
    social_asset = rowMeans(dplyr::select(., polposition, LIassociation, polparty, govtscheme), na.rm = TRUE),
    financial_asset = totalincome,
    food_security = rowMeans(dplyr::select(., foodadequacy, foodtrouble, food), na.rm = TRUE),
    health_status = rowMeans(dplyr::select(., healthdist, illness, severeillness), na.rm = TRUE)
  )%>%
  dplyr::select(
    -c(education, workknowledge, LIlenght, 
      drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown, 
      polposition, LIassociation, polparty, govtscheme, 
      foodadequacy, foodtrouble, food,
      healthdist, illness, severeillness,
      totalincome, Lfarmbigha, Ipropvalue, Lboat, animals)
  )%>%
  mutate(LIscore = rowMeans(dplyr::select(., human_asset, physical_asset, social_asset,financial_asset, food_security,health_status), na.rm = TRUE))

solarLI_lm <- lm(Risky_Solar ~ caste + gender + urban_rural + human_asset + physical_asset + social_asset + financial_asset + food_security + health_status , data = solar_model)

solarLI_lm2 <- lm(Risky_Solar ~ caste + gender + urban_rural + LIscore , data = solar_model)
summary(solarLI_lm)
summary(solarLI_lm2)
#plot(solarLI_lm)

```

```{r, echo = FALSE}
coal_LI <- addedcols %>% 
  dplyr::select(Risky_Coal, State, gender, caste, religion, urban_rural, age,  Livelihood_Income, education, workknowledge, LIlenght, subsidyknow, drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown, polposition, LIassociation, polparty, govtscheme, totalincome, Lfarmbigha,  Ipropvalue, Lboat, animals, foodadequacy, foodtrouble, food, healthdist, illness, severeillness)

# Coal dataframe for LSI/ISI with standardized values

# Convert columns to numeric starting from 'education'
cols_to_convert <- names(coal_LI)[which(names(coal_LI) == 'education'):length(names(coal_LI))]
coal_LI[cols_to_convert] <- lapply(coal_LI[cols_to_convert], as.numeric)

# Standardize the values
standardize <- function(x) {
  (x - min(x, na.rm = TRUE)) / (max(x, na.rm = TRUE) - min(x, na.rm = TRUE))
}

coal_LI[cols_to_convert] <- lapply(coal_LI[cols_to_convert], standardize)

# Displaying the first few rows of the dataframe
#head(coal_LI)

coal_model <- coal_LI %>%  
  mutate(
    human_asset = rowMeans(dplyr::select(., education, workknowledge, LIlenght), na.rm = TRUE),
    physical_asset = rowMeans(dplyr::select(., drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown), na.rm = TRUE),
    social_asset = rowMeans(dplyr::select(., polposition, LIassociation, polparty, govtscheme), na.rm = TRUE),
    financial_asset = totalincome,
    food_security = rowMeans(dplyr::select(., foodadequacy, foodtrouble, food), na.rm = TRUE),
    health_status = rowMeans(dplyr::select(., healthdist, illness, severeillness), na.rm = TRUE)
  )%>%
  dplyr::select(
    -c(education, workknowledge, LIlenght, 
      drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown, 
      polposition, LIassociation, polparty, govtscheme, 
      foodadequacy, foodtrouble, food,
      healthdist, illness, severeillness,
      totalincome, Lfarmbigha, Ipropvalue, Lboat, animals)
  )%>%
  mutate(LIscore = rowMeans(dplyr::select(., human_asset, physical_asset, social_asset,financial_asset, food_security,health_status), na.rm = TRUE))

coalLI_lm <- lm(Risky_Coal ~ caste + gender + urban_rural + human_asset + physical_asset + social_asset + financial_asset + food_security + health_status, data = coal_model)

coalLI_lm2 <- lm(Risky_Coal ~ caste + gender + urban_rural + LIscore, data = coal_model)

summary(coalLI_lm)
summary(coalLI_lm2)
#plot(coalLI_lm)

```

\newpage

# Linear Regression Models with asset groups

```{r, echo=FALSE, results='asis'}
library(stargazer)

#stargazer code for all demographic variable lms

cat("\\begingroup")
cat("\\setlength{\\tabcolsep}{1pt}")
cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(nuclearLI_lm, solarLI_lm, coalLI_lm,
          title = "Assets",
          type = "latex"
)
cat("\\endgroup")

```

# Linear Regression Models with livelihood security and income security indeces

```{r, echo=FALSE, results='asis'}
library(stargazer)

#stargazer code for all demographic variable lms

cat("\\begingroup")
cat("\\setlength{\\tabcolsep}{1pt}")
cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(nuclearLI_lm2, solarLI_lm2, coalLI_lm2,
          title = "Livelihood and Income Security",
          type = "latex"
)
cat("\\endgroup")

```

```{r, echo = FALSE}
#  Cronbach's alpha test and CFA on JIS scale

JIS <- codedmodule1 %>%
  dplyr::select(JISRkeep,JISlosefuture, JISlose, JISfuture)%>%
  na.omit()

JIS_alpha <- psych::alpha(JIS, check.keys = TRUE)

# alpha = 0.69 - not bad - not too good.

library(lavaan)

JIS_fas <- '
  JISs =~ JISRkeep + JISlosefuture + JISlose + JISfuture 
  '

# Run CFA
JIS_cfa <- cfa(JIS_fas, data = JIS , std.lv = TRUE)

# Print the summary of the CFA results, including fit measures
summary(JIS_cfa, fit.measure= TRUE, standardized = TRUE)

# RMSEA - between 0.05 and 0.08 (reasonable fit), less than 0.05 close fit and greater than 0.10 is poor fit 
# CFI - greater than 0.90 or 0.95 indicates good fit
#TFI - CFI>TFI >0.90 - indicates good fit

JIS_scores <- predict(JIS_cfa, newdata = JIS)

JIS_data <- codedmodule1 %>% select(Risky_Nuclear, gender, caste, urban_rural, religion, JISRkeep, JISlosefuture, JISlose, JISfuture) %>%
  filter(!is.na(JISRkeep) & !is.na(JISlosefuture)  & !is.na(JISlose)  & !is.na(JISfuture))

JIS_Jscores <- cbind(JIS_data, JIS_scores)

JIS_lm1 <- lm(Risky_Nuclear ~ caste + gender + urban_rural+ JIS_scores, data = JIS_Jscores)

summary(JIS_lm1)

```

```{r, echo=FALSE}

LSI2 <- codedmodule1 %>% select(Risky_Nuclear, Risky_Solar, Risky_Coal, gender, caste, urban_rural, religion, Lconfidence) %>%
  filter(!is.na(Lconfidence))

LSI2_lm1 <- lm(Risky_Nuclear ~ caste + gender + urban_rural+ Lconfidence, data = LSI2)

summary(LSI2_lm1)

```

# Linear Regression Models with perceived livelihood and income security

```{r, echo=FALSE, results='asis'}
library(stargazer)

#stargazer code for all demographic variable lms

cat("\\begingroup")
cat("\\setlength{\\tabcolsep}{1pt}")
cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(JIS_lm1, LSI2_lm1, 
          title = "Perceived livelihood or job security",
          type = "latex"
)
cat("\\endgroup")

```

\newpage

#Extra

```{r, echo = FALSE}

##checking stuff
codedmodule1

codedmodule1 %>%
  filter(Livelihood_Income == "LSI") %>%
  count(Lfarmland)
codedmodule1 %>%
  count(Iproperty)

lapply(codedmodule1, unique)
ncol(codedmodule1)
colnames(codedmodule1)

str(codedmodule1)

```

```{r, echo = FALSE}

nuclear_LI <- addedcols %>% 
  dplyr::select(Risky_Nuclear,State, gender, caste, religion, urban_rural, age,  Livelihood_Income,education, workknowledge,LIlenght, subsidyknow, drinkingwater,cookingwater,farwatermins, wateravail,toilet, house,stove, vehicle, houseown, polposition, LIassociation,polparty, govtscheme, totalincome, Lfarmbigha,  Ipropvalue, Lboat, animals, foodadequacy, foodtrouble,food, healthdist, illness, severeillness)

# checking NAs in LSI part 
assetcheck <- addedcols %>% filter(Livelihood_Income == "LSI") %>%
            dplyr::select(Lfarmland,Lfarmbigha,animals)

num_NAs2 <- colSums(is.na(assetcheck))

#print(num_NAs2)

codedmodule1 %>% count(Livelihood_Income)
addedcols %>% count(Livelihood_Income)
codedmodule1 %>% count(Lfarmbigha)
codedmodule1 %>% filter(Livelihood_Income == "LSI") %>% count(Lfarmland)
addedcols %>% filter(Livelihood_Income == "LSI") %>% count(animals)
codedmodule1 %>% count(Lboat)

addedcols %>% filter(Livelihood_Income == "LSI") %>% filter(Lfarmland == "Doesn't apply") %>% count(Lboat)
addedcols %>% filter(Livelihood_Income == "LSI") %>% filter(Lfarmland == "Doesn't apply") %>% count(animals)

addedcols %>% filter(Livelihood_Income == "ISI") %>% count(Iproperty)

# checking NAs in ISI part

module1 %>% filter(!row_number() %in% c(1,2)) %>% filter(Livelihood_Income != "(a) own farming/fishing/animal rearing/business") %>% count(Iproperty)

# there are only 4 people who said they own a boat but not a farmland when looking at those people who answered LSI part of the survey. So we will just look at boat as  another livelihood asset and remove the 4 responses by removing Doesn't apply values in the Lfarmland part.

```

# Livelihood/Income Security scale adapted from Kamaruddin and Samsudin(2014)

Human Asset

education - 	    What is the highest level of education you have received? If currently enrolled, highest degree received.

workknowledge -   How would you rate your level of knowledge about your work ?

LIlenght-         How long have you been in your current line of work?

subsidyknow -     How would you rate your knowledge concerning how to obtain information about subsidies or aid from the government or any other agencies ?

Physical Asset

drinkingwater   	What is the main source of drinking water for the members of your household?
cookingwater      What is the main source of water used by your\r\nhousehold for other purposes such as cooking and\r\nhandwashing?
farwatermins      How long does it take to go there, get water, and come\r\nback? 
toilet            What kind of toilet facility do members of your\r\nhousehold usually use?
house
stove
vehicle
houseown

Social Asset

polposition
LIassociation
polparty

Financial Asset

Income

Natural Asset

Lfarmland
Lfarmbigha
Iproperty
Ipropvalue
Lboat
animals

Livelihood Outcomes

Foodsecurity

foodadequacy 
foodtrouble

Health Status

healthdist
illness
severeillness

### 2023-09-20 Paper1.Rmd
lot of changes because I wasn't opening the project file.

---
title: "Nuclear Energy: Kahan scale and Economic Political value scale"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    keep_tex: yes
  header-includes:
  - \usepackage{dcolumn}
  - \usepackage{array}
  - "\\usepackage{placeins}"
  keep_md: yes
---
```{r load packages, warning = FALSE, message = FALSE, echo=FALSE}
  knitr::opts_chunk$set(warning = FALSE, message = FALSE)

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(tidyr))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(lavaan))
suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(DT))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(psych)) 
```

```{r setup, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

moduletwo <- read_excel(here::here("thesis_surveydata/political_factors_complete.xlsx"))
module2 <- data.frame(moduletwo)
module2[module2 == "Rather not say/ Don't know"] <- "Rather not say/Don't know"

# loaded data set for module 2 eco -pol variables and removes the rows with question number and question text
```

```{r, eval =TRUE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
codedmodule2 <- module2 %>%

#remove row 1
  filter(!row_number() %in% c(1,2)) %>%

# replace risky likert scale with numbers
  mutate_at(vars(starts_with("Risky")), funs(case_when(. =="Not at all risky" ~ 1, 
                                                       . =="Slightly risky" ~ 2, 
                                                       . =="Moderately risky" ~ 3, 
                                                       . =="Very risky" ~ 4, 
                                                       . =="Extremely risky" ~ 5))) %>%

# replace beneficial likert scale with numbers  
  mutate_at(vars(starts_with("Ben")), funs(case_when(. =="Not at all beneficial" ~ 1,
                                                     . =="Slightly beneficial" ~ 2,
                                                     . =="Moderately beneficial" ~ 3,
                                                     . =="Very beneficial" ~ 4,
                                                     . =="Extremely beneficial" ~ 5 ))) %>%

# replace nuclear acceptance likert scale with numbers
  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                                        . == "Somewhat disagree" ~ 2,
                                                                        . == "Neither agree nor disagree" ~3,
                                                                        . == "Somewhat agree" ~ 4,
                                                                        . == "Strongly agree" ~ 5))) %>%

# code likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_I","K_H","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE", "DEV", "PROSPER", "RELY"))), funs(case_when(. == "Strongly disagree" ~ 1, 
               . == "Somewhat disagree" ~ 2,
               . == "Neither agree nor disagree" ~3,
               . == "Somewhat agree" ~ 4,
               . == "Strongly agree" ~ 5))) %>%

# reverse code for likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_S","K_E"))), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                               . == "Somewhat disagree" ~ 4,
                                                               . == "Neither agree nor disagree" ~3,
                                                               . == "Somewhat agree" ~ 2,
                                                               . == "Strongly agree" ~ 1))) %>%

# code eco-pol scale variables into numbers
mutate_at(vars(SYSTEMDEMO,SYSTEMRELIGION,SYSTEMTECHNO,SYSTEMTOTAL,WEALTHLIM,MECHANISATION,DECISIONDECEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG), funs(case_when(. == "Strongly disagree" ~ 1, 
                        . == "Somewhat disagree" ~ 2,
                        . == "Neither agree nor disagree" ~3,
                        . == "Somewhat agree" ~ 4,
                        . == "Strongly agree" ~ 5))) %>%

# reverse code eco-pol scale variables into numbers 
 mutate_at(vars(DECISIONCEN, INDUSTRYSMALL, ECONOMYLOCAL, ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                                                                         . == "Somewhat disagree" ~ 4,
                                                                                                         . == "Neither agree nor disagree" ~3,
                                                                                                         . == "Somewhat agree" ~ 2,
                                                                                                         . == "Strongly agree" ~ 1))) %>%
  mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
  mutate_all(~ifelse(. == "West bengal", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "WEST BENGAL", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "Up", "Uttar Pradesh", .))%>%
  mutate_all(~ifelse(. == "Tamilnadu", "Tamil Nadu", .))%>%
  mutate_all(~ifelse(. == "UP", "Uttar Pradesh", .))

```

```{r, eval=TRUE, echo=FALSE}

moduleone <- read_excel(here::here("thesis_surveydata/livelihood_insecurity_complete.xlsx"))
module1 <- data.frame(moduleone)
# loaded data set for module 2 eco -pol variables and removes the rows with question number and question text
```

```{r, eval =TRUE, echo=FALSE}
#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
codedmodule1 <- module1 %>%

#remove row 1 and 2 
  filter(!row_number() %in% c(1,2)) %>%

# replace risky likert scale with numbers
  mutate_at(vars(starts_with("Risky")), funs(case_when(. =="Not at all risky" ~ 1, 
                                                       . =="Slightly risky" ~ 2, 
                                                       . =="Moderately risky" ~ 3, 
                                                       . =="Very risky" ~ 4, 
                                                       . =="Extremely risky" ~ 5))) %>%

# replace beneficial likert scale with numbers  
  mutate_at(vars(starts_with("Ben")), funs(case_when(. =="Not at all beneficial" ~ 1,
                                                     . =="Slightly beneficial" ~ 2,
                                                     . =="Moderately beneficial" ~ 3,
                                                     . =="Very beneficial" ~ 4,
                                                     . =="Extremely beneficial" ~ 5 ))) %>%

# replace nuclear acceptance likert scale with numbers
  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                                        . == "Somewhat disagree" ~ 2,
                                                                        . == "Neither agree nor disagree" ~3,
                                                                        . == "Somewhat agree" ~ 4,
                                                                        . == "Strongly agree" ~ 5)))%>%
  mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
  mutate_all(~ifelse(. == "West bengal", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "WEST BENGAL", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "Up", "Uttar Pradesh", .))%>%
  mutate_all(~ifelse(. == "Tamilnadu", "Tamil Nadu", .))%>%
  mutate_all(~ifelse(. == "UP", "Uttar Pradesh", .))

```

```{r, echo = FALSE}

suppressPackageStartupMessages(library(tidyselect))
# combine codedmodule1 and codedmodule2

numcol2 <- codedmodule2 %>% add_column(Respondent = 1:1099, .before = "Language") 
numcol1 <- codedmodule1 %>% add_column(Respondent = 1099:2160, .before = "Language")

joineddf <-  full_join(numcol2, numcol1, by = c("Respondent", "Language", "Survey_Date", "State", "Risky_Hydro", "Risky_Solar", "Risky_Wind", "Risky_Nuclear", "Risky_Coal", "Risky_Gas", "Risky_Oil", "Risky_INDHydro", "Risky_INDSolar", "Risky_INDWind", "Risky_INDBiogas", "Risky_INDDiesel", "Risky_INDKerosene", "Risky_INDFirewoodetc", "Risky_INDLPG", "Ben_Hydro", "Ben_Solar", "Ben_Wind", "Ben_Nuclear", "Ben_Coal", "Ben_Gas", "Ben_Oil", "Ben_INDHydro", "Ben_INDSolar", "Ben_INDWind", "Ben_INDDiesel", "Ben_INDBiogas", "Ben_INDFirewoodetc", "Ben_INDLPG", "Ben_INDKerosene", "N_accept", "N_reluctantlyaccept", "N_reject", "age", "urban_rural", "gender", "caste", "religion", "religiontext")) %>%
  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
                                      . == "25-34 years old" ~ 2,
                                      . ==  "35-44 years old" ~3,
                                      . == "45-54 years old" ~ 4,
                                      . == "55-64 years old" ~ 5,
                                      . == "65-74 years old" ~ 6,
                                      . == "75 years or older" ~ 7))) # converting age to continuous variable

joineddf1 <-  full_join(numcol2, numcol1, by = c("Respondent", "Language", "Survey_Date", "State", "Risky_Hydro", "Risky_Solar", "Risky_Wind", "Risky_Nuclear", "Risky_Coal", "Risky_Gas", "Risky_Oil", "Risky_INDHydro", "Risky_INDSolar", "Risky_INDWind", "Risky_INDBiogas", "Risky_INDDiesel", "Risky_INDKerosene", "Risky_INDFirewoodetc", "Risky_INDLPG", "Ben_Hydro", "Ben_Solar", "Ben_Wind", "Ben_Nuclear", "Ben_Coal", "Ben_Gas", "Ben_Oil", "Ben_INDHydro", "Ben_INDSolar", "Ben_INDWind", "Ben_INDDiesel", "Ben_INDBiogas", "Ben_INDFirewoodetc", "Ben_INDLPG", "Ben_INDKerosene", "N_accept", "N_reluctantlyaccept", "N_reject", "age", "urban_rural", "gender", "caste", "religion", "religiontext"))

numcolb <- module2 %>%   filter(!row_number() %in% c(1,2))%>% 
                        add_column(Respondent = 1:1099, .before = "Language") 
numcola <- module1 %>%   filter(!row_number() %in% c(1,2)) %>% 
                        add_column(Respondent = 1099:2160, .before = "Language")

uncodedjoineddf <- full_join(numcolb, numcola, by = c("Respondent", "Language", "Survey_Date", "State", "Risky_Hydro", "Risky_Solar", "Risky_Wind", "Risky_Nuclear", "Risky_Coal", "Risky_Gas", "Risky_Oil", "Risky_INDHydro", "Risky_INDSolar", "Risky_INDWind", "Risky_INDBiogas", "Risky_INDDiesel", "Risky_INDKerosene", "Risky_INDFirewoodetc", "Risky_INDLPG", "Ben_Hydro", "Ben_Solar", "Ben_Wind", "Ben_Nuclear", "Ben_Coal", "Ben_Gas", "Ben_Oil", "Ben_INDHydro", "Ben_INDSolar", "Ben_INDWind", "Ben_INDDiesel", "Ben_INDBiogas", "Ben_INDFirewoodetc", "Ben_INDLPG", "Ben_INDKerosene", "N_accept", "N_reluctantlyaccept", "N_reject", "age", "urban_rural", "gender", "caste", "religion", "religiontext")) %>%
  mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
  mutate_all(~ifelse(. == "West bengal", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "WEST BENGAL", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "Up", "Uttar Pradesh", .))%>%
  mutate_all(~ifelse(. == "Tamilnadu", "Tamil Nadu", .))%>%
  mutate_all(~ifelse(. == "UP", "Uttar Pradesh", .))

```

\newpage

# H1: Nuclear Energy will be seen as riskier than other energy technologies in India.

## Likert Responses (n= 2160)
The percentages are rounded off to whole numbers.

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
# Q1: how much is the awareness of energy technologies in India ? How does it relate to state specific data ? 
# summary of NA results from the combined sample of 2000 responses (simple percentage bar graphs)
# part 1- how much is the awareness of energy technologies in India -

#plotting perceived risk from different technologies including rather not say don't know
colorsequence<- c("#8C4646","#D9695F","#F2A679","#F2D091","#5D8C7B","#808080")

#following is the data frame for making the barplot 
df_barplot <- uncodedjoineddf %>%
  dplyr::select(starts_with("RISKY"))%>%
  gather(Technology, Perceived_Risk, Risky_Hydro:Risky_INDLPG, factor_key = TRUE)%>%
  separate(Technology, c("Risky", "Technology"), extra = "merge", fill = "left")%>%
  dplyr::select(-Risky) %>% 
  group_by(Technology, Perceived_Risk) %>%
  dplyr::summarise(n=n())

#following data frame gives us percentage for each response 
df_barplot_percent<- df_barplot%>%
  group_by(Technology) %>%
  mutate(Percentage = round(n/sum(n)*100, 0)) %>%
  ungroup()

#plotting perceived benefit from different technologies including rather not say don't know

df_barplotben <- uncodedjoineddf %>%
  dplyr::select(starts_with("Ben"))%>%
  gather(Technology, Perceived_Benefit, Ben_Hydro:Ben_INDKerosene, factor_key = TRUE)%>%
  separate(Technology, c("Ben", "Technology"), extra = "merge", fill = "left")%>%
  dplyr::select(-Ben) %>% 
  group_by(Technology, Perceived_Benefit) %>%
  dplyr::summarise(n=n())

df_barplotben_percent<- df_barplotben%>%
  group_by(Technology) %>%
  mutate(Percentage = round(n/sum(n)*100, 0)) %>%
  ungroup()

#bar plot for likert responses perceived risk - centrally owned technologies 
df_barplot %>% ggplot(aes(fill= fct_rev(factor(Perceived_Risk, levels=c("Extremely risky", "Very risky","Moderately risky","Slightly risky","Not at all risky","Rather not say/Don't know"))), y=n , x=Technology)) + 
  geom_bar(position="fill",stat="identity")+
  geom_text(data = df_barplot_percent, aes(label=paste0(Percentage, "%"), y=n), position = position_fill(vjust=0.5), size=3) +
  scale_x_discrete(limits = c("Solar", "Wind" ,"Hydro", "Oil", "Coal","Gas", "Nuclear"))+
  scale_fill_manual("legend", values = c("Extremely risky" = "#8C4646", "Very risky" = "#D9695F", "Moderately risky" = "#F2A679", "Slightly risky" = "#F2D091","Not at all risky" = "#5D8C7B", "Rather not say/Don't know" = "grey94"))+
  labs( y = "Perceived Risk", x ="Centrally Managed Energy Technologies")+
  theme_classic()

#perceived benefit centrally owned technologies

df_barplotben %>% ggplot(aes(fill= factor(Perceived_Benefit, levels=c("Rather not say/Don't know","Not at all beneficial","Slightly beneficial","Moderately beneficial","Very beneficial", "Extremely beneficial")), y=n , x=Technology)) + 
  geom_bar(position="fill",stat="identity")+
   geom_text(data = df_barplotben_percent, aes(label=paste0(Percentage, "%"), y=n), position = position_fill(vjust=0.5), size=3) +
  scale_fill_manual("legend", values = c("Rather not say/Don't know" = "grey94" ,"Not at all beneficial" = "orange","Slightly beneficial"="yellow" ,"Moderately beneficial" = "palegreen","Very beneficial"= "green3", "Extremely beneficial"= "green4"))+
  scale_x_discrete(limits = c("Solar", "Wind", "Hydro", "Oil", "Coal","Gas","Nuclear"))+
  labs( y = "Perceived Benefit", x ="Centrally Managed Energy Technologies")+
  theme_classic()

```

\newpage

## Mean Perceived Risk and Mean Perceived Benefit for all energy technologies.

```{r, echo=FALSE}
library(tidyverse)

# Filter variables of interest
joineddf_subset <- joineddf %>%
  dplyr::select(!starts_with(c("Ben_IND", "Risky_IND")))%>%
  dplyr::select(starts_with("Risky"), 
         starts_with("Ben"))

# Assuming your data is named joineddf_subset
long_df <- joineddf_subset %>%
  gather(key = "Type", value = "Value")

# Separate out Risky and Ben columns
risky_df <- long_df %>% filter(str_detect(Type, "^Risky"))
ben_df <- long_df %>% filter(str_detect(Type, "^Ben"))

# Extract the technology type (Hydro, Solar, etc.)
risky_df$Tech <- str_replace(risky_df$Type, "Risky_", "")
ben_df$Tech <- str_replace(ben_df$Type, "Ben_", "")

# Calculate the mean for each technology for Risky
risky_mean <- risky_df %>%
  group_by(Tech) %>%
  summarize(Mean_Value = mean(Value, na.rm = TRUE),
          sd = sd(Value, na.rm = TRUE),
          se = sd(Value, na.rm = TRUE) / sqrt(n()),
          .groups = "drop")

# Do the same for Ben technologies
ben_mean <- ben_df %>%
  group_by(Tech) %>%
  summarize(Mean_Value = mean(Value, na.rm = TRUE),
          sd = sd(Value, na.rm = TRUE),
          se = sd(Value, na.rm = TRUE) / sqrt(n()),
          .groups = "drop")

# Combine the two data frames into one for plotting
combined_mean <- bind_rows(
  mutate(risky_mean, Category = "Risky"),
  mutate(ben_mean, Category = "Beneficial")
)
# Reorder the factor levels of the Tech variable by Mean_Value
risky_mean$Tech <- factor(risky_mean$Tech, levels = risky_mean$Tech[order(risky_mean$Mean_Value, decreasing = FALSE)])

```

```{r, echo=FALSE}
library(ggplot2)
library(gridExtra)

mean_risk <- mean(combined_mean$Mean_Value[combined_mean$Category == "Risky"], na.rm = TRUE)
mean_benefit <- mean(combined_mean$Mean_Value[combined_mean$Category == "Beneficial"], na.rm = TRUE)

# Order Technologies
technology_order <- c("Solar","Wind","Hydro","Oil","Coal", "Gas","Nuclear")
ben_mean$Tech <- factor(ben_mean$Tech, levels = technology_order)

# Generate the Ben plot with flipped y-axis
ben_plot <- ggplot(ben_mean, aes(y = Tech, x = Mean_Value)) +
  geom_bar(stat = "identity", fill = "palegreen3") +
  geom_errorbar(aes(xmin = Mean_Value - se, xmax = Mean_Value + se), width = 0.2) +
  coord_cartesian(xlim = c(4, 1)) + 
  labs(title = "Perceived Benefit", x = "Mean Values") +
  #scale_x_reverse() +
  theme(  # remove y-axis labels
        axis.title.y = element_blank()) + # remove the "Tech" axis title
  geom_vline(data = subset(combined_mean, Category == "Beneficial"), 
             aes(xintercept = mean_risk), linetype="dotted", color = "black", size = 0.5)

# Generate the Risky plot
risky_plot <- ggplot(risky_mean, aes(y = Tech, x = Mean_Value)) +
  geom_bar(stat = "identity", fill = "firebrick2") +
  geom_errorbar(aes(xmin = Mean_Value - se, xmax = Mean_Value + se), width = 0.2) +
  coord_cartesian(xlim = c(1, 4)) + 
  labs(title = "Perceived Risk", x = "Mean Values") +
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank())+
  geom_vline(data = subset(combined_mean, Category == "Risky"), 
             aes(xintercept = mean_risk), linetype="dotted", color = "black", size = 0.5)
 # remove the "Tech" axis title

# Arrange plots side by side
grid.arrange(ben_plot, risky_plot, ncol=2)

```

## Boxplot for perceived benefit and perceived risk by technology

```{r, echo = FALSE, fig.width=16, fig.height=6}

#Box plot to see the distribution

# Loading the required libraries
library(tidyverse)
library(stringr)
library(gridExtra)

# Reshape the data to a long format
joineddf_subset_long <- joineddf_subset %>%
  pivot_longer(cols = everything(), 
               names_to = "variable",
               values_to = "value")

# Separate the data into two: one for "Risky_" variables and one for "Ben_" variables
risky_df <- joineddf_subset_long %>% 
  filter(str_detect(variable, "^Risky_")) %>%
  mutate(variable = str_remove(variable, "Risky_"))  # Remove the "Risky_" prefix

ben_df <- joineddf_subset_long %>% 
  filter(str_detect(variable, "^Ben_")) %>%
  mutate(variable = str_remove(variable, "Ben_"))  # Remove the "Ben_" prefix

# Remove NA values
risky_df <- risky_df %>% drop_na()
ben_df <- ben_df %>% drop_na()

# Create box plots
risky_plot <- ggplot(risky_df, aes(x = variable, y = value, fill = variable)) +
  geom_boxplot() +
  scale_fill_manual(values = rep("firebrick2", length(unique(risky_df$variable)))) +
  labs(x = "Energy Technologies", y = "Likert", fill = "Technologies") +
  ggtitle("Perceived risk") +
  theme_minimal()+
  theme(axis.text.y = element_text(size=20), 
        axis.text.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.title.x = element_text(size=20),
        title = element_text(size=20))+
  guides(fill = FALSE)

ben_plot <- ggplot(ben_df, aes(x = variable, y = value, fill = variable)) +
  geom_boxplot() +
  scale_fill_manual(values = rep("palegreen3", length(unique(ben_df$variable)))) +
  labs(x = "Energy Technologies", y = "Likert Responses", fill = "Technologies") +
  ggtitle("Perceived Benefit") +
  theme_minimal()+
  theme(axis.text.y = element_text(size=20), 
        axis.text.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.title.x = element_text(size=20),
        title = element_text(size=20))+
  guides(fill = FALSE)

# Put the two plots next to each other
grid.arrange(risky_plot, ben_plot, ncol = 2)

```

\newpage

## Pairwise T-test: Mean perceived risk and mean perceived benefit (all energy technologies)

The red and green pairs indicate that there is a statistically significant difference between the means of the two groups. 
White and grey indicate - no differences between the means of the two groups.

```{r, echo = FALSE, fig.width=14, fig.height=6}
#Q2 :How are the perceptions of the risk of producing energy from nuclear fission different from that of other conventional sources of energy like coal or hydro power in India?
#H : Nuclear energy will be perceived as riskier than other sources of energy (coal or hydro) in India like in the west.
perceivedriskc <-joineddf %>% 
  dplyr::select("Risky_Solar", "Risky_Hydro", "Risky_Wind", "Risky_Nuclear", "Risky_Coal", "Risky_Gas", "Risky_Oil") %>%
  gather(key = "technology", value = "perceived_risk") %>% 
  mutate(technology = gsub("Risky_", "", technology)) %>%
  na.omit()

result_ttest <- pairwise.t.test(perceivedriskc$perceived_risk, perceivedriskc$technology, p.adjust.method = "BH")

# visualising the pairwaise t test results. the non significant pairs are grey

tidy_result_ttest <- broom::tidy(result_ttest)

heatmap1 <- ggplot(tidy_result_ttest, aes(x = group1, y = group2, fill = p.value)) + 
  geom_tile(color = "white") + 
  scale_fill_gradient2(low = "firebrick2", high = "white", midpoint = 0.025, 
                       limits = c(0, 0.05), space = "Lab", 
                       name = "P-value") + 
  theme_classic() + 
  labs(x = "", y = "") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
   theme(axis.text.y = element_text(size=20), 
        axis.text.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.title.x = element_text(size=20),
        title = element_text(size=20),
        legend.text = element_text(size=12))

#Question- Why there is significant difference statistically - if the medians are the same in the boxplot.
#Q3: How do perceptions of benefit from nuclear energy compare with other source of energy?

# H : benefits from all energy technologies will be similar 
# include regression, heat maps, bar graphs? - decide which ones are good to include

perceivedbenefitc <-joineddf %>% 
  dplyr::select("Ben_Solar", "Ben_Hydro", "Ben_Wind", "Ben_Nuclear", "Ben_Coal", "Ben_Gas", "Ben_Oil") %>%
  gather(key = "technology", value = "perceived_benefit") %>% 
  mutate(technology = gsub("Ben_", "", technology)) %>%
  na.omit()

result_ttestben <- pairwise.t.test(perceivedbenefitc$perceived_benefit, perceivedbenefitc$technology, p.adjust.method = "BH")

# visualising the pairwaise t test results. the non significant pairs are grey

tidy_resultbc <- broom::tidy(result_ttestben)

library(ggplot2)
heatmap2 <- ggplot(tidy_resultbc, aes(x = group1, y = group2, fill = p.value)) + 
  geom_tile(color = "white") + 
  scale_fill_gradient2(low = "palegreen3", high = "white", midpoint = 0.025, 
                       limits = c(0, 0.05), space = "Lab", 
                       name = "P-value") + 
  theme_classic() + 
  labs(x = "", y = "") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
   theme(axis.text.y = element_text(size=20), 
        axis.text.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.title.x = element_text(size=20),
        title = element_text(size=20),
        legend.text = element_text(size=12))

grid.arrange(heatmap1, heatmap2, ncol=2)

```

```{r, echo=FALSE}

## Paired T-test: Comparing mean perceived risk and mean perceived benefit for each technology.

#Null hypothesis (H0): The mean difference between perceived risk and perceived benefit from each technology is zero.

#All p values are less than 0.05 suggesting that the differences observed in the bar graph are statistically significant.

# Melt the data frame to long format
long_format <- joineddf_subset %>% 
  pivot_longer(everything(), names_to = "technology", values_to = "value") %>%
  mutate(risk_or_benefit = if_else(str_detect(technology, "Risky"), "risk", "benefit"),
         technology = str_replace(technology, "Risky_|Ben_", ""))

# Convert character columns to factors
long_format$technology <- factor(long_format$technology)
long_format$risk_or_benefit <- factor(long_format$risk_or_benefit)

# Perform the t- Test for each technology
p_values <- long_format %>%
  split(.$technology) %>%
  lapply(function(x) t.test(x$value[x$risk_or_benefit == "risk"], x$value[x$risk_or_benefit == "benefit"], paired = TRUE)) %>%
  lapply(function(x) x$p.value)

```

\newpage

# H2: Gender and Caste will have significant impact like Gender and Race in the US studies of risk.

```{r, echo=FALSE}

# # Convert `caste` into binary variable 'upper' (1) vs 'non-upper' (0)
joineddf$Uppercaste <- ifelse(joineddf$caste %in% c('Brahmin', 'General'), 1, 0)
# Convert `gender` into binary variable 'male' (1) vs 'female' (0)
joineddf$Male <- ifelse(joineddf$gender == 'Male', 1, 0)
# Convert `religion` into binary variable 'Hinduism' (1) vs 'Non-Hinduism' (0)
joineddf$Hindu <- ifelse(joineddf$religion == 'Hinduism', 1, 0)
codedmodule2$State <- as.factor(codedmodule2$State)
codedmodule2$gender <- as.factor(codedmodule2$gender)
codedmodule2$Urban <- as.factor(codedmodule2$urban_rural)
joineddf$Urban <- as.factor(joineddf$urban_rural)
codedmodule2$caste <- as.factor(codedmodule2$caste)
codedmodule2$religion <- as.factor(codedmodule2$religion)
# # Convert `caste` into binary variable 'upper' (1) vs 'non-upper' (0)
codedmodule2$Uppercaste <- ifelse(codedmodule2$caste %in% c('Brahmin', 'General'), 1, 0)
# Convert `gender` into binary variable 'male' (1) vs 'female' (0)
codedmodule2$Male <- ifelse(codedmodule2$gender == 'Male', 1, 0)
# Convert `religion` into binary variable 'Hinduism' (1) vs 'Non-Hinduism' (0)
codedmodule2$Hindu <- ifelse(codedmodule2$religion == 'Hinduism', 1, 0)

alldemos <- joineddf %>%
            dplyr::select(Risky_Nuclear, Uppercaste, Male, Hindu, Urban, age, State)

alldemoslm1 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age , data = alldemos)
# Print model summary
#summary(alldemoslm1)
#plot(alldemoslm1)

# lm suggests there is no significant white male effect or upper caste male effect for risk perception from nuclear energy in India. 
# the coefficients are very small and so is the r squared - rsquared is minimal.

# 2) lm with all demographic variables
alldemoslm2<- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State, data = alldemos)
# Print model summary
#summary(alldemoslm2)
#plot(alldemoslm1)

# most of these results indicate that there is no significant white male effect or upper caste male effect for risk perception from nuclear energy in India. 
# the coefficients are very small and so is the r squared - rsquared is minimal.

```

## two linear regression models
```{r, echo=FALSE, results='asis'}
library(stargazer)

cat("\\begingroup")
cat("\\setlength{\\tabcolsep}{1pt}")
cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(alldemoslm1, alldemoslm2, 
          title = "Results from 2 linear regression models",
          type = "latex"
)
cat("\\endgroup")

```

\newpage

# H3: Regional differences will have a strong impact

## Linear regression where Mean value is the intercept
Same model with mean value as intercept.

```{r, echo=FALSE}
# Centering the numeric predictor variables
alldemos$Uppercaste_centered <- alldemos$Uppercaste - mean(alldemos$Uppercaste, na.rm = TRUE)
alldemos$Male_centered      <- alldemos$Male - mean(alldemos$Male, na.rm = TRUE)
alldemos$Hindu_centered     <- alldemos$Hindu - mean(alldemos$Hindu, na.rm = TRUE)
alldemos$age_centered       <- alldemos$age - mean(alldemos$age, na.rm = TRUE)

# For factor variable 'Urban', we'll convert it to numeric (0/1) and then center
# Assuming "Rural" is the reference category
alldemos$Urban_numeric      <- ifelse(alldemos$Urban == "Urban", 1, 0)
alldemos$Urban_centered     <- alldemos$Urban_numeric - mean(alldemos$Urban_numeric, na.rm = TRUE)

# Now, run the regression with centered variables
alldemoslm1_centered <- lm(Risky_Nuclear ~ Uppercaste_centered + Male_centered + Hindu_centered + Urban_centered + age_centered, data = alldemos)
#summary(alldemoslm1_centered)

alldemos$State <- as.factor(alldemos$State)
alldemos$State <- relevel(alldemos$State, ref = "Rajasthan")

alldemoslm2_centered <- lm(Risky_Nuclear ~ Uppercaste_centered + Male_centered + Hindu_centered + Urban_centered + age_centered + State, data = alldemos)
#summary(alldemoslm2_centered)

```

```{r, echo=FALSE, results='asis'}
library(stargazer)

cat("\\begingroup")
cat("\\setlength{\\tabcolsep}{1pt}")
cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(alldemoslm1_centered, alldemoslm2_centered, 
          title = "Results from 2 linear regression models",
          type = "latex"
)
cat("\\endgroup")

```

\newpage

## Regional Differences Graph 
Following is a graph of z scores calculated from mean perceived risk from nuclear energy by state.

```{r, echo = FALSE, fig.width=8, fig.height=4}

staterisky <- joineddf %>%
  dplyr::select(!starts_with(c("Ben_IND", "Risky_IND")))%>%
  dplyr::select(starts_with("Risky"), State)

staterisky_mean <- staterisky %>%
  group_by(State) %>%
  summarise(
    Mean_Risky_Hydro = mean(Risky_Hydro, na.rm = TRUE),
    Mean_Risky_Solar = mean(Risky_Solar, na.rm = TRUE),
    Mean_Risky_Wind = mean(Risky_Wind, na.rm = TRUE),
    Mean_Risky_Nuclear = mean(Risky_Nuclear, na.rm = TRUE),
    Mean_Risky_Coal = mean(Risky_Coal, na.rm = TRUE),
    Mean_Risky_Gas = mean(Risky_Gas, na.rm = TRUE),
    Mean_Risky_Oil = mean(Risky_Oil, na.rm = TRUE)
  )

# Extract only Nuclear
nuclear_data <- staterisky_mean %>%
  dplyr::select(State, Mean_Risky_Nuclear)%>%
  mutate(
    Z_Risky_Nuclear = (Mean_Risky_Nuclear - mean(Mean_Risky_Nuclear, na.rm = TRUE)) / 
                      sd(Mean_Risky_Nuclear, na.rm = TRUE)
  )

mean_nuclear_state <- ggplot(nuclear_data, aes(x = State, y = Mean_Risky_Nuclear, group = 1)) +
  geom_line(color = "#F0BA32", size = 1) +
  geom_point(color = "#F0BA32", size = 3) +
  labs(title = "Means: Perceived Risk of Nuclear Energy",
       x = "State", y = "Mean Perceived Risk") +
  theme_minimal() +
  ylim(1,5)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Plot the z-scores
zscore_nuclear_state <- ggplot(nuclear_data, aes(x = State, y = Z_Risky_Nuclear, group = 1)) +
  geom_line(color = "#F0BA32", size = 1) +
  geom_point(color = "#F0BA32", size = 3) +
  labs(title = "Z-scores: Perceived Risk of Nuclear Energy",
       x = "State", y = "Z-Score") +
  ylim(-1 ,2)+
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

library(gridExtra)

# Assuming mean_nuclear_state and zscore_nuclear_state are both ggplot objects

# We'll add a spacer grob for spacing between plots
spacer <- grid::rectGrob(gp = grid::gpar(col = "white"))

grid.arrange(mean_nuclear_state, spacer, zscore_nuclear_state, ncol=3, widths=c(0.8, 0.06, 0.8))

```

```{r, echo=FALSE}
library(MASS)

alldemos_factor <-alldemos  %>%
  mutate_at(vars(Risky_Nuclear, Uppercaste, Male, Hindu, Urban, State), as.factor)

model= polr(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban +State , data = alldemos_factor, Hess = TRUE)
#summary(model)

model3 <- glm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban +State , data = alldemos_factor, family = binomial)
#summary(model3)

ci <- confint(model3)
#print(ci)

```

\newpage

```{r, echo=FALSE}
# Q6: Does the Kahan scale explain perception of risk from nuclear energy and other DVs ?

# we conducted fa on the kahan scale 
# CFA for Kahan scale. We shouldn't do FA here since this a well used scale with theoretical basis for factor distinctions and also previous studies using the same scale

library(lavaan)
library(semTools)
library(kableExtra)

fascales <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_","Risky_Nuclear","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%
  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
                                      . == "25-34 years old" ~ 2,
                                      . ==  "35-44 years old" ~3,
                                      . == "45-54 years old" ~ 4,
                                      . == "55-64 years old" ~ 5,
                                      . == "65-74 years old" ~ 6,
                                      . == "75 years or older" ~ 7))) %>%
  na.omit()

Kahan_fas <- '
  KahanS =~ K_SHARM + K_SLIMCHOI + K_SPROTECT 
  KahanH =~ K_HEQUAL+ K_ERADEQ1 + K_EWEALTH + K_ERADEQ2
'

# Run CFA
Kahan_cfa <- cfa(Kahan_fas, data = fascales, std.lv = TRUE)

# Print the summary of the CFA results, including fit measures
#summary(Kahan_cfa, fit.measure= TRUE, standardized = TRUE)

# RMSEA - between 0.05 and 0.08 (reasonable fit), less than 0.05 close fit and greater than 0.10 is poor fit 
# CFI - greater than 0.90 or 0.95 indicates good fit
#TFI - CFI>TFI >0.90 - indicates good fit
#pvalue should be greater than 0.05 p > 0.0.5

# after having removed a few variables that had very low loading, the model is now a good fit, we have two latent variables - Hierarchy- egalitarian and Communitarian. Again we see that individualistic variables just don't fit here.

# creating table of factor scores

Kahan_scores <- predict(Kahan_cfa, newdata = fascales)

Kahan_Kscores <- cbind(fascales, Kahan_scores)

## RMSEA is still pretty big.

```

```{r fit-measures-display, echo = FALSE}
# Extract fit measures
fit_measures <- fitMeasures(Kahan_cfa, fit.measures = c("CFI", "TLI", "RMSEA", "rmsea.ci.upper", "rmsea.ci.lower"))
fit_measures2 <- fitMeasures(Kahan_cfa)
# Convert to a data frame for presentation
fit_df <- data.frame(Measure = names(fit_measures), Value = fit_measures) %>%
  mutate(Measure = case_when(
    Measure == "cfi" ~ "Comparative Fit Index (CFI) ",
    Measure == "tli" ~ "Tucker-Lewis Index (TLI)",
    Measure == "rmsea" ~ "Root Mean Square Error of Approximation(RMSEA)",
    Measure == "rmsea.ci.upper" ~ "RMSEA 90 Percent confidence interval - lower",
    Measure == "rmsea.ci.lower" ~ "RMSEA 90 Percent confidence interval - upper",
    TRUE ~ as.character(Measure)
  )) %>%
  mutate(Value = round(Value, 3)) %>%
  remove_rownames()

#RMSEA - between 0.05 and 0.08 (reasonable fit), less than 0.05 close fit and greater than 0.10 is poor fit 
#CFI - greater than 0.90 or 0.95 indicates good fit
#TFI - CFI>TFI >0.90 - indicates good fit

```
# Confirmatory Factor Analysis(CFA): Kahan Scale

**Cronbach's Alpha on Kahan et al(2007) Scale: A Note**

The Individualism items (indicated by K_I) were bringing down the Cronbach's alpha values in the Kahan scale. The Alpha for Individualism- Communitarian scale was 0.49. After removing the Individualism items (K_I) the alpha for this factor was 0.71. The reasons for this could be that the individualism items are not well adapted to the Indian population.

```{r, echo =FALSE}
# Display fit measures using kable
knitr::kable(fit_df, caption = "Fit Measures from the CFA", booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position"))

```

\newpage

```{r, echo=FALSE}

# Extract parameter estimates
params <- parameterEstimates(Kahan_cfa, standardized = TRUE)%>%
   slice(1:(n()-10))

params1 <- params %>%
  mutate(rhs = case_when(
    rhs == "K_SHARM" ~ "Sometimes the government needs to make laws that keep people from hurting themselves.",
    rhs == "K_SLIMCHOI" ~ "The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.",
    rhs == "K_SPROTECT" ~ "The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.",
    rhs == "K_HEQUAL" ~ "We have gone too far in pushing equal rights in this country.",
    rhs == "K_ERADEQ1" ~ "We need to dramatically reduce inequalities between the rich and the poor.",
    rhs == "K_EWEALTH" ~ "Our society would be better off if the distribution of wealth was more equal.",
    rhs == "K_ERADEQ2" ~ "We need to dramatically reduce inequalities between men and women.",
    TRUE ~ as.character(rhs)
  )) %>%
  dplyr::select(!c(lhs,op, std.nox)) %>%
    rename(
    "Items" = rhs,
    "Loadings" = est,
    "Standard Error" = se,
    "zvalue" = z) %>%
  mutate(across(c("Loadings", "Standard Error", "zvalue"), round, 3))

params1$Scale <- NA
params1$Scale[1:3] <- "Individualism"
params1$Scale[4:7] <- "Hierarchy-Egalitarianism"
params1 <- params1[, c("Scale", setdiff(names(params1), "Scale"))]
CFAkahan <- knitr::kable(params1, booktabs = TRUE, caption = "Confirmatory Factor Analysis(CFA) on Kahan et al(2007) scale adapted to India") %>%
  kable_styling(latex_options = c("striped","scale_down", "hold_position", "repeat_header"))%>%
  column_spec(column = 2, width = "4cm")

# Print the table
CFAkahan %>%
  landscape()

```

\newpage

# Factor Analysis: New Eco-political Scale

```{r, echo=FALSE}

library(psych)
library(tidyverse)

ecopolall <- fascales %>%
        dplyr::select("WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR")

ecopolall_alpha <- psych::alpha(ecopolall, check.keys = TRUE)

#summary(ecopolall_alpha)

# when we combine both the scales the alpha is high at 0.785 (almost 0.8)

# FA on all ecopol variables except systems of governance

ecopolall_cor <- cor(ecopolall)
PCA24 <- principal(ecopolall, nfactors = 24, rotate = "none") # no rotation to start with.

#PCA24$loadings

#fa.parallel(ecopolall_cor)

# this suggests 2 factors if we go by FA or 8 by PCA. let's try both and see how they look conceptually

# running EFA using psych package

ecopolall2.fa <- fa(ecopolall, nfactors = 2, rotate = "varimax")

# I don't know still doesn't make a lot of sense to me- the two factors make more sense - 1) people centered development 2) nationalist development
# So I am going to extract factor scores and bind them to the dataset

ecopolall_scores <- psych::factor.scores(ecopolall, ecopolall2.fa)

# The factor scores will be stored in the scores element of the returned list
scores1 <- ecopolall_scores$scores

#binding factor scores to the dataset

fascale_scores <- cbind(Kahan_Kscores, scores1) %>%
  rename(Pdevelop = MR1)%>%
  rename(Ndevelop = MR2) %>%
  dplyr::select(!starts_with(c("K_","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR")))

```

```{r, echo=FALSE}
library(ggplot2)
library(fmsb)

# Extract the loadings
loadings_matrix <- ecopolall2.fa$loadings[1:24, ]

loadings_df <- as.data.frame(as.matrix(loadings_matrix))

# Adding rownames to the dataframe as a new column
loadings_df <- loadings_df %>%
  rownames_to_column(var = "variable")

# Pivot to longer format first
long_loadings_df <- loadings_df %>%
  pivot_longer(cols = c(MR1, MR2), names_to = "Factors", values_to = "value")

# Pivot the longer format to wide format
wide_loadings_df <- long_loadings_df %>%
  pivot_wider(names_from = variable, values_from = value) %>%
  mutate(Factors = case_when(
    Factors == "MR1" ~ "People Centered Development (Pdevelop)",
    Factors == "MR2" ~ "Nationalist Development (Ndevelop)",
    TRUE ~ Factors
  )) %>%
  column_to_rownames("Factors")

# Define the variable ranges: maximum and minimum
max_min <- data.frame(
  WEALTHLIM = c(0.8, -0.6), MECHANISATION = c(0.8, -0.6), DECISIONDECEN = c(0.8, -0.6),
  DECISIONCEN = c(0.8, -0.6), INDUSTRYLARGE = c(0.8, -0.6), INDUSTRYSMALL = c(0.8, -0.6),
  ECONOMYGLOBAL = c(0.8, -0.6), ECONOMYLOCAL = c(0.8, -0.6), ENVOVERDEV = c(0.8, -0.6),
  DEVOVERENV = c(0.8, -0.6), OWNERPVT = c(0.8, -0.6), OWNERNOREG = c(0.8, -0.6),
  OWNERPUB = c(0.8, -0.6), OWNERREG = c(0.8, -0.6), DISPLACENUCLEAR = c(0.8, -0.6),
  POLLUTENUCLEAR = c(0.8, -0.6), HEALTHNUCLEAR = c(0.8, -0.6), JOBSNUCLEAR = c(0.8, -0.6),
  BEAUTYNUCLEAR = c(0.8, -0.6), PRIDENUCLEAR = c(0.8, -0.6), NPRIDENUCLEAR = c(0.8, -0.6),
  DEVNUCLEAR = c(0.8, -0.6), PROSPERNUCLEAR = c(0.8, -0.6), RELYNUCLEAR = c(0.8, -0.6)
)
rownames(max_min) <- c("Max", "Min")

# Assuming you have a dataframe 'exam_scores' with matching column names
# Bind the variable ranges to the data

radar2 <- rbind(max_min, wide_loadings_df) %>%
    rename(
      "Limits on Wealth " = "WEALTHLIM",
      "Anti Mechanisation of work" = "MECHANISATION",
      "Pro Decentralisation" = "DECISIONDECEN",
      "Pro Centralisation" = "DECISIONCEN",
      "Pro Large Industries" = "INDUSTRYLARGE",
      "Anti Large Industries " = "INDUSTRYSMALL",
      "Pro Globaleconomy" = "ECONOMYGLOBAL",
      "Pro Localeconomy" = "ECONOMYLOCAL",
      "Environment over Development" = "ENVOVERDEV",
      "Development over Environment" = "DEVOVERENV",
      "Pro Private ownership " = "OWNERPVT",
      "Anti Regulations" = "OWNERNOREG",
      "Pro Public ownership" = "OWNERPUB",
      "Pro Regulations" = "OWNERREG",
      "Displacement risk(nuclear)" = "DISPLACENUCLEAR",
      "Pollution risk(nuclear) " = "POLLUTENUCLEAR",
      "Health risk(nuclear)" = "HEALTHNUCLEAR",
      "Job opportunities(nuclear)" = "JOBSNUCLEAR",
      "Spoils Natural Beauty(nuclear)" = "BEAUTYNUCLEAR",
      "Community pride(nuclear)" = "PRIDENUCLEAR",
      "National pride(nuclear)" = "NPRIDENUCLEAR",
      "National development(nuclear)" = "DEVNUCLEAR",
      "Local prosperity(nuclear)" = "PROSPERNUCLEAR",
      "Reliance on government(nuclear)" = "RELYNUCLEAR"
    )

```

```{r, echo=FALSE, fig.width=20, fig.height=18, out.width='100%', out.height='100%'}
library(fmsb)

create_beautiful_radarchart <- function(data, color = "#00AFBB", 
                                        vlabels = colnames(data), vlcex = 0.7,
                                        caxislabels = NULL, title = NULL, ...){
  radarchart(
    data, axistype = 1,
    # Customize the polygon
    pcol = color, pfcol = scales::alpha(color, 0.5), plwd = 2, plty = 1,
    centerzero=FALSE,
    # Customize the grid
    cglcol = "grey", cglty = 1.5, cglwd = 1.5,
    # Customize the axis
    axislabcol = "black", 
     # Increase the axis label size
    cexc = 3,
    # Variable labels
    vlcex = vlcex, vlabels = vlabels, vlpos = 0.95,
    seg = 7, caxislabels = caxislabels, title = title, 
    # Increase title size
    cex.main = 2,
    ...
  )
}

# Reduce plot margin using par()
op <- par(mar = c(7, 3, 3, 3))
# Create the radar charts
create_beautiful_radarchart(
  data = radar2, caxislabels = c(-0.6,-0.4,-0.2, 0, 0.2, 0.4, 0.6, 0.8, 1),
  color = c("#00AFBB", "#F97D09"),
  vlcex = 1.1
)

# Add an horizontal legend
legend(
  x = "bottomright", legend = rownames(radar2[-c(1,2),]), horiz = TRUE,
  bty = "n", pch = 20 , col = c("#00AFBB", "#F97D09"),
  text.col = "black", cex = 1.5, pt.cex = 3,
  inset = c(0, 0)
  )
par(op)

```

\newpage

```{r, echo=FALSE}

library(flextable)

flex <- function(data, title=NULL) {
  # this grabs the data and converts it to a flextbale
  flextable(data) %>%
  # this makes the table fill the page width
  set_table_properties(layout = "autofit", width = 1) %>%
  # font size
  fontsize(size=10, part="all") %>%
    #this adds a ttitlecreates an automatic table number
      set_caption(title, 
                  autonum = officer::run_autonum(seq_id = "tab", 
                                                 pre_label = "Table ", 
                                                 post_label = "\n", 
                                                 bkm = "anytable")) #%>%
  # font type
  #font(fontname="Times New Roman", part="all")
}

rename_map <- c(
  "WEALTHLIM" = "Limits on Wealth",
  "MECHANISATION" = "Anti Mechanisation of work",
  "DECISIONDECEN" = "Pro Decentralisation",
  "DECISIONCEN" = "Pro Centralisation",
  "INDUSTRYLARGE" = "Pro Large Industries",
  "INDUSTRYSMALL" = "Anti Large Industries",
  "ECONOMYGLOBAL" = "Pro Globaleconomy",
  "ECONOMYLOCAL" = "Pro Localeconomy",
  "ENVOVERDEV" = "Environment over Development",
  "DEVOVERENV" = "Development over Environment",
  "OWNERPVT" = "Pro Private ownership",
  "OWNERNOREG" = "Anti Regulations",
  "OWNERPUB" = "Pro Public ownership",
  "OWNERREG" = "Pro Regulations",
  "DISPLACENUCLEAR" = "Displacement risk(nuclear)",
  "POLLUTENUCLEAR" = "Pollution risk(nuclear)",
  "HEALTHNUCLEAR" = "Health risk(nuclear)",
  "JOBSNUCLEAR" = "Job opportunities(nuclear)",
  "BEAUTYNUCLEAR" = "Spoils Natural Beauty(nuclear)",
  "PRIDENUCLEAR" = "Community pride(nuclear)",
  "NPRIDENUCLEAR" = "National pride(nuclear)",
  "DEVNUCLEAR" = "National development(nuclear)",
  "PROSPERNUCLEAR" = "Local prosperity(nuclear)",
  "RELYNUCLEAR" = "Reliance on government(nuclear)"
)

fa_table <- function(x, cut) {
  #get sorted loadings
  loadings <- fa.sort(x)$loadings %>% round(3)
  #supress loadings
  loadings[loadings > -cut & loadings < cut] <- ""
  #get additional info  
  add_info <- cbind(x$communalities, 
                    x$uniquenesses,
                    x$complexity) %>%
    # make it a data frame
    as.data.frame() %>%
    # column names
   rename("Communality" = V1,
           "Uniqueness" = V2,
           "Complexity" = V3) %>%
    #get the item names from the vector
    rownames_to_column("item")
  #build table
  loadings %>%
    unclass() %>%
    as.data.frame() %>%
    rownames_to_column("item") %>%
    left_join(add_info) %>%
    mutate(
      item = if_else(item %in% names(rename_map), rename_map[item], item),
      across(where(is.numeric), round, 3)
    )
}

fa_table(ecopolall2.fa, .4) %>%
  rename(Pdevelop = MR1, Ndevelop = MR2, Items= item) %>%
  flex("Eco-Pol Values Factor Analysis Table")

```

```{r, echo=FALSE}

ecopolall2.fa[["Vaccounted"]] %>%
  as.data.frame() %>%
  rownames_to_column("Property") %>%
  rename(Pdevelop = MR1, Ndevelop = MR2) %>%
    mutate(across(where(is.numeric), round, 3)) %>%
    flex("Eigenvalues and Variance Explained for Rotated Factor Solution")

```

\newpage

```{r, echo=FALSE}

ecopolall <- fascales %>%
        dplyr::select("WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR")

pdevelop <- ecopolall %>%
  dplyr::select("POLLUTENUCLEAR", "HEALTHNUCLEAR", "BEAUTYNUCLEAR","DISPLACENUCLEAR","MECHANISATION","INDUSTRYSMALL","OWNERPUB")

ndevelop <- ecopolall %>%
  dplyr::select("JOBSNUCLEAR",  "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR")

pdevelop_alpha <- psych::alpha(pdevelop, check.keys = TRUE)

ndevelop_alpha <- psych::alpha(ndevelop, check.keys = TRUE)

```

```{r, echo=FALSE}

data <- tibble(
  Scale = c(
    "People Centered Development (Pdevelop)", "", "", "", "", "", "",
    "Nationalist Development (Ndevelop)", "", "", "", ""
  ),
  Code = c(
    "Health risk(nuclear)", "Spoils Natural Beauty(nuclear)", "Anti Mechanisation of work",
    "Anti Large Industries", "Displacement risk(nuclear)", "Pollution risk(nuclear)",
    "Pro Regulations", "National development(nuclear)", "Community pride(nuclear)",
    "National pride(nuclear)", "Local prosperity(nuclear)", "Job opportunities(nuclear)"
  ),
  "Items and Loadings" = c(
    "Nuclear energy poses a great risk to the health of people living around it.(0.657)",
    "Nuclear energy spoils the natural beauty of the landscape.(0.638)",
    "Rapid mechanization of work is taking away jobs from workers in this country.(0.552)",
    "Large corporations are destroying the local industries in India and benefiting only a handful of people.(-0.532)",
    "Nuclear energy is leading to displacement of people from their land.(0.59)",
    "Nuclear energy increases pollution of air/water/land.(0.565)",
    "Regardless of ownership, the government should pass strong regulations and implement them.(-0.53)",
    "Nuclear energy pushes forward the country's development.(0.662)",
    "I would be proud if my community used nuclear energy.(0.623)",
    "Nuclear energy is a mark of pride for our nation.(0.605)",
    "Nuclear energy brings economic prosperity to the surrounding regions.(0.586)",
    "Nuclear energy will bring jobs to the local community.(0.427)"
  ),
  Alpha = c(0.757, "", "", "", "", "", "", 0.725, "", "", "", ""),
  Variance = c("", "", "", "", "", "", "", "", "", "", "", "")
)

```

```{r, echo=FALSE}

longvars <- knitr::kable(data, booktabs = TRUE, caption = "Two Factor Solution: Economic and Political Values Scale", 
                         longtable = TRUE, escape = FALSE) %>%
  kable_styling(latex_options = c("striped","scale_down", "hold_position", "repeat_header")) %>%
  column_spec(column = 2, width = "4cm") %>%
  column_spec(column = 1, width = "4cm") %>%
  column_spec(column = 3, width = "9cm")

# Print the table in landscape mode
longvars %>%
  landscape()

```

```{r, echo=FALSE}
# 3 linear models - 1) lm with demographic variables except age and State
m1_demo <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban, data = fascale_scores)
# Print model summary
#summary(m1_demo)
#plot(m1_demo)

# lm suggests there is no significant white male effect or upper caste male effect for risk perception from nuclear energy in India. 
# the coefficients are very small and so is the r squared - rsquared is minimal.

# 2) lm with all demographic variables
m2_demo<- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State, data = fascale_scores)
# Print model summary
#summary(m2_demo)
#plot(m2_demo)

# States and some age have some impact on y variable.

# 3) lm with kahan 
m1_kahan <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State + KahanS + KahanH , data = fascale_scores)
# Print model summary
#summary(m1_kahan)
#plot(m1_kahan)

# 4) lm with ecopolvars 
m1_allscales <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State+ KahanS + KahanH + Pdevelop + Ndevelop, data = fascale_scores)
# Print model summary
#summary(m1_allscales)
#plot(m1_allscales)

```

\newpage

# H4 : Economic and Political Values will be important in explaining perceived risk from Nuclear Energy

```{r, echo=FALSE, results='asis'}
library(stargazer)

cat("\\begingroup")
cat("\\setlength{\\tabcolsep}{1pt}")
cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(m1_kahan, m1_allscales, 
          title = "Results from 2 linear regression models",
          type = "latex"
)
cat("\\endgroup")

```

\newpage

```{r, echo=FALSE}
# Q7 : political values scale - factor analysis - reduce dimensions and then run regression -logistic regression 
# Using logistic regression for the SYSTEM prefixed variables.

#codedmodule2
#codedmodule2$SYSTEMDEMO <- as.factor(codedmodule2$SYSTEMDEMO)
#levels(codedmodule2$SYSTEMDEMO)

#codedmodule2$SYSTEMRELIGION <- as.factor(codedmodule2$SYSTEMRELIGION)
#levels(codedmodule2$SYSTEMRELIGION)

#codedmodule2$SYSTEMTOTAL <- as.factor(codedmodule2$SYSTEMTOTAL)
#levels(codedmodule2$SYSTEMTOTAL)

#codedmodule2$SYSTEMTECHNO <- as.factor(codedmodule2$SYSTEMTECHNO)
#levels(codedmodule2$SYSTEMTECHNO)

#codedmodule2$Risky_Nuclear <- as.factor(codedmodule2$Risky_Nuclear)
#levels(codedmodule2$Risky_Nuclear)

#fitrisky_nucleargm <- with(codedmodule2, clm(Risky_Nuclear ~ 1 + SYSTEMDEMO + SYSTEMRELIGION + SYSTEMTOTAL + SYSTEMTECHNO))

```

\newpage

# Appendix: Characteristics of the Sample

The following graph shows that distribution of different demographic variables in our sample of 2,160 from the combined dataset from both surveys.
The percentages are rounded off to whole numbers.

```{r, echo=FALSE}

library(dplyr)
library(tidyr)

sampledemos <- joineddf1 %>% 
  dplyr::select("State", "Language", "age", "urban_rural", "gender", "caste" ,"religion") %>%
              mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
              mutate_all(~ifelse(. == "OBC", "Other Backward Classes (OBC)", .))%>%
              mutate_all(~ifelse(. == "SC", "Scheduled caste (SC)", .))%>%
              mutate_all(~ifelse(. == "ST", "Scheduled tribe (ST)", .))%>%
              mutate_all(~ifelse(. == "MAR", "Marathi", .))%>%
              mutate_all(~ifelse(. == "TA", "Tamil", .)) %>%
              mutate_all(~ifelse(. == "EN", "English", .))%>%
              mutate_all(~ifelse(. == "BN", "Bengali", .))%>%
              mutate_all(~ifelse(. == "MAR", "Marathi", .))%>%
              mutate_all(~ifelse(. == "HI", "Hindi", .))%>%
              na.omit()

#changing factor levels for each variable from high to low n

sampledemos$State <- factor(sampledemos$State, levels = c("Maharashtra","Rajasthan", "West Bengal" , "Tamil Nadu", "Uttar Pradesh"))
sampledemos$Language <- factor(sampledemos$Language, levels = c("Hindi","Marathi","Bengali","Tamil", "English"))
sampledemos$age <- factor(sampledemos$age, levels = c( "18-24 years old" ,  "25-34 years old","35-44 years old", "45-54 years old", "55-64 years old","65-74 years old","75 years or older"  ))
sampledemos$urban_rural <- factor(sampledemos$urban_rural, levels = c("Rural","Urban"))
sampledemos$gender <- factor(sampledemos$gender, levels = c("Male","Female"))
sampledemos$caste <- factor(sampledemos$caste, levels = c("Scheduled tribe (ST)", "Scheduled caste (SC)", "Other Backward Classes (OBC)", "General","Brahmin","Rather not say/Don't know"))
sampledemos$religion <- factor(sampledemos$religion, levels = c("Hinduism", "Islam", "Christanity","Buddhism","Agnostism/ Atheism","Other (Please mention)"))

```

```{r, echo=FALSE, fig.width=11, fig.height=14, out.width='80%', out.height='80%'}

# Loading the required libraries
library(tidyverse)
library(gridExtra)
library(scales)

# Function to create bar plot
create_bar_plot <- function(data, variable_name, palette_name) {
  factor_levels <- levels(sampledemos[[variable_name]])
  data %>%
    filter(Variable == variable_name) %>%
    mutate(Category = factor(Category, levels = factor_levels)) %>%
    ggplot(aes(y = "", x = Percentage, fill = Category)) +
    geom_bar(position = "fill", stat = "identity", width = 1) +
    geom_text(aes(label = paste0(round(Percentage, 0), "%")), 
              position = position_fill(vjust = 0.5)) +
    scale_x_continuous(labels = percent) +
    labs(y = NULL, x = "Percentage", fill = variable_name) +
    theme_classic() +
    theme(axis.text.y = element_blank(), strip.text = element_text(size = 10), legend.position = "top") +
    scale_fill_brewer(palette = palette_name)
}

# Gather data to long format and calculate counts and percentages
df_barplot <- sampledemos %>%
  gather(Variable, Category) %>%
  group_by(Variable, Category) %>%
  filter(!is.na(Category)) %>%
  summarise(n = n()) %>%
  mutate(Percentage = n / sum(n) * 100)

# Create separate plots for each variable
plot_state <- create_bar_plot(df_barplot, "State", "Spectral")
plot_language <- create_bar_plot(df_barplot, "Language", "Paired")
plot_age <- create_bar_plot(df_barplot, "age", "Set3")
plot_urban_rural <- create_bar_plot(df_barplot, "urban_rural", "Dark2")
plot_gender <- create_bar_plot(df_barplot, "gender", "Pastel1")
plot_caste <- create_bar_plot(df_barplot, "caste", "Set1")
plot_religion <- create_bar_plot(df_barplot, "religion", "Set2")

# Combine the plots with spacing
combined_plot <- gridExtra::arrangeGrob(plot_state, plot_language, plot_age, plot_urban_rural, plot_gender, plot_caste, plot_religion, ncol = 1, heights = c(1, 1, 1, 1, 1, 1, 1))

# Print the combined plot
grid::grid.newpage()
grid::grid.draw(combined_plot)

```

### 2023-09-20 Untitled.Rmd
lot of changes because I wasn't opening the project file.

---
title: "FAoptions"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2023-09-20 combined data set/DVgraphs.Rmd
wilcoxon rank sum test on caste and urban_rural
lot of changes because I wasn't opening the project file.

@@
 
+ggplot(perceivedrisk, aes(x = perceived_risk, y = technology)) + 
+  geom_violin()
+#the violin graph shows that the data is definitely not normally distributed
+
 levels(perceivedrisk$technology)
@@
 
-library(emmeans)
-emm_results <- emmeans(kruskal_results, ~ technology)
-summary(emm_results, infer = c(T, T))
+#library(emmeans)
+#emm_results <- emmeans(kruskal_result, ~ technology)
+#summary(emm_results, infer = c(T, T))
 
@@
 
+levels(perceivedrisk$technology)
+
 ```
@@
   theme(axis.text.x = element_text(angle = 90, hjust = 1))
-
-```
-
-```{r}
-#now do the same for perceived benefit
-#null hypothesis - no sognificant difference between perceived benefit from technologies. 
-#push to github - figure out what happened! why not pushing anymore yaar 
-#
 
@@
 ```
+
 ```{r}
@@
 ```
+
+```{r, echo=FALSE}
+# Calculate median and IQR for each technology and category (risk or benefit)
+summary_df_median <- long_format %>%
+  group_by(technology, risk_or_benefit) %>%
+  summarise(median = median(value, na.rm = TRUE),
+            IQR = IQR(value, na.rm = TRUE),
+            .groups = "drop")
+
+# Order technologies by median risk
+order_risk_median <- summary_df_median %>% 
+  filter(risk_or_benefit == "risk") %>%
+  arrange(median) %>% 
+  pull(technology)
+
+# Change the levels of factor 'technology'
+summary_df_median$technology <- factor(summary_df_median$technology, levels = order_risk_median)
+
+# Plotting the data
+ggplot(summary_df_median, aes(x = technology, y = median, fill = risk_or_benefit)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  geom_errorbar(aes(ymin = median - 0.5*IQR, ymax = median + 0.5*IQR), 
+                width = 0.3, position = position_dodge(0.9)) +
+  ylim(0, 5) +
+  scale_fill_manual("legend", 
+                    values = c("benefit" = "palegreen3", "risk" = "firebrick2"), 
+                    labels = c("benefit" = "Perceived Benefit", "risk" = "Perceived Risk")) +
+  labs(y = "Median Values", x = "Energy Technologies", fill = "Perceived") +
+  ggtitle("Perceived risk and benefit from centrally owned energy technologies\n(Median)") +
+  coord_flip()
+
+```
+
+```{r}
+
+# **Perceived risk by Support for Totalitarian government**
+
+#The following is a list of statements about governance.
+How strongly do you agree or disagree with each of these statements?
+Do you strongly disagree(1), somewhat disagree(2), neither agree nor disagree(3), somewhat agree(4) or strongly agree(5)?
+- It is good to have a strong leader who does not have to bother with elections.
+
+govtrisk$grouped_total <- ifelse(govtrisk$SYSTEMTOTAL %in% c(1,2), "low", ifelse(govtrisk$SYSTEMTOTAL %in% c(4,5), "high", NA))
+
+totalrisk2 <- govtrisk %>%
+  group_by(grouped_total) %>%
+  filter(grouped_total %in% c("low", "high")) %>%
+  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
+  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd, Risky_Hydro_n, Risky_Solar_n, Risky_Wind_n, Risky_Nuclear_n, Risky_Coal_n, Risky_Gas_n, Risky_Oil_n) %>%
+  dplyr::select(grouped_total, technology, summary) %>%
+  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
+  separate(var, c("technology", "meansd")) %>%
+  spread(meansd,summary) %>%
+  select(-Risky) %>%
+  arrange(grouped_total)
+
+data.frame(totalrisk2)
+
+totalrisk2 <- totalrisk2 %>%
+  mutate(technology = reorder(technology, -mean))  # reorder based on -mean, to get high to low
+
+t <- totalrisk2 %>%
+  group_by(technology) %>%
+  ggplot(aes(x = technology, y= mean, group = grouped_total))+
+  geom_line(aes(colour = grouped_total, line = grouped_total)) +
+  labs(y = "mean perceived risk", x = "energy technology", color = "Totalitarianism Value") +
+  ggtitle("Q:It is good to have a strong leader who does not have to bother with\nelections.")
+
+t
+
+# **Perceived risk by Support for Technocratic government**
+
+#The following is a list of statements about governance.
+How strongly do you agree or disagree with each of these statements?
+Do you strongly disagree(1), somewhat disagree(2), neither agree nor disagree(3), somewhat agree(4) or strongly agree(5)?
+- Experts, not the government, should make decisions according to what they think is best for the country.
+
+govtrisk$grouped_techno <- ifelse(govtrisk$SYSTEMTECHNO %in% c(1,2), "low", ifelse(govtrisk$SYSTEMTECHNO %in% c(4,5), "high", NA))
+
+technorisk2 <- govtrisk %>%
+  group_by(grouped_techno) %>%
+  filter(grouped_techno %in% c("low", "high")) %>%
+  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
+  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd, Risky_Hydro_n, Risky_Solar_n, Risky_Wind_n, Risky_Nuclear_n, Risky_Coal_n, Risky_Gas_n, Risky_Oil_n) %>%
+  dplyr::select(grouped_techno, technology, summary) %>%
+  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
+  separate(var, c("technology", "meansd")) %>%
+  spread(meansd,summary) %>%
+  select(-Risky) %>%
+  arrange(grouped_techno)
+
+data.frame(technorisk2)
+
+technorisk2 <- technorisk2 %>%
+  mutate(technology = reorder(technology, -mean))  # reorder based on -mean, to get high to low
+
+techno <- technorisk2 %>%
+  group_by(technology) %>%
+  ggplot(aes(x = technology, y= mean, group = grouped_techno))+
+  geom_line(aes(colour = grouped_techno, line = grouped_techno)) +
+  labs(y = "mean perceived risk", x = "energy technology", color = "Technocratic Value") +
+  ggtitle("Q:Experts, not the government, should make decisions according to\nwhat they think is best for the country.")
+
+techno
+
+# **Perceived risk by Support for Religious government**
+
+#The following is a list of statements about governance.
+How strongly do you agree or disagree with each of these statements?
+Do you strongly disagree(1), somewhat disagree(2), neither agree nor disagree(3), somewhat agree(4) or strongly agree(5)?
+- There should be a system governed by religious law.
+
+govtrisk$grouped_religion <- ifelse(govtrisk$SYSTEMRELIGION %in% c(1,2), "low", ifelse(govtrisk$SYSTEMRELIGION %in% c(4,5), "high", NA))
+
+religionrisk2 <- govtrisk %>%
+  group_by(grouped_religion) %>%
+  filter(grouped_religion %in% c("low", "high")) %>%
+  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
+  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd, Risky_Hydro_n, Risky_Solar_n, Risky_Wind_n, Risky_Nuclear_n, Risky_Coal_n, Risky_Gas_n, Risky_Oil_n) %>%
+  dplyr::select(grouped_religion, technology, summary) %>%
+  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
+  separate(var, c("technology", "meansd")) %>%
+  spread(meansd,summary) %>%
+  select(-Risky) %>%
+  arrange(grouped_religion)
+
+data.frame(religionrisk2)
+
+religionrisk2 <- religionrisk2 %>%
+  mutate(technology = reorder(technology, -mean))  # reorder based on -mean, to get high to low
+
+r <- religionrisk2 %>%
+  group_by(technology) %>%
+  ggplot(aes(x = technology, y= mean, group = grouped_religion))+
+  geom_line(aes(colour = grouped_religion, line = grouped_religion)) +
+  labs(y = "mean perceived risk", x = "energy technology", color = "Religious law Value") +
+  ggtitle("Q:There should be a system governed by religious law.")
+
+r
+```

### 2023-09-20 combined data set/demovariablesregression.Rmd
lot of changes because I wasn't opening the project file.

@@
 ```{r, eval =TRUE, echo=FALSE}
-#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
+#This chunk contains the coding schemes of likert scales 
 codedmodule1 <- module1 %>%
@@
 
-```{r}
+```{r, echo=FALSE}
+
+# cleaning up variables and making them into neat categories, turning IVs into factors
+
 library(dplyr)
@@
 demovars <- joineddf %>%
-  select(starts_with("Risky"), starts_with("Ben"),urban_rural, gender, caste, religion, age, State)%>%
-  mutate(religion = ifelse(religion == "Other (Please mention)", "Other", religion))
+  dplyr::select(starts_with("Risky"), starts_with("Ben"),urban_rural, gender, caste, religion, age, State)%>%
+  mutate(religion = ifelse(religion == "Other (Please mention)", "Other", religion)) %>%
+  filter(gender %in% c("Male", "Female"))%>%
+  mutate(caste = ifelse(grepl("SC|Scheduled caste", caste), "SC", caste),
+          caste = ifelse(grepl("ST|Scheduled Tribe", caste), "ST", caste),
+          caste = ifelse(grepl("OBC|Other Backward Classes", caste), "OBC", caste))%>%
+  mutate(State = case_when(State == "West bengal" ~ "West Bengal",
+                            State == "WEST BENGAL" ~ "West Bengal",
+                            State == "Up" ~ "UP",
+                            TRUE ~ State)) %>%
+  mutate(religion = case_when(religion == "Agnostism/ Atheism" ~ "Agnosticism_Atheism",
+                              TRUE~ religion))
+
+demovars$gender <- as.factor(demovars$gender)
+demovars$caste <- as.factor(demovars$caste)
+demovars$urban_rural <- as.factor(demovars$urban_rural)
+demovars$age <- as.factor(demovars$age)
+demovars$religion <- as.factor(demovars$religion)
+demovars$State <- as.factor(demovars$State)
 
@@
 
-```{r}
+```{r, echo=FALSE}
 library(dplyr)
@@
 
-```{r}
+```{r, echo=FALSE}
 library(ggplot2)
@@
 
-demovars_mf <- demovars %>% 
-  filter(gender %in% c("Male", "Female"))
-
-wilcox_gender <- demovars_mf %>%
-  select(starts_with("Risky")) %>%
-  lapply(function(col) wilcox.test(col ~ gender, data = demovars_mf))
+wilcox_gender <- demovars %>%
+  dplyr::select(starts_with("Risky")) %>%
+  lapply(function(col) wilcox.test(col ~ gender, data = demovars))
 
@@
 
+demovars_caste <- demovars %>%
+  dplyr::select(starts_with("Risky"), caste) %>%
+  na.omit()
+
 demovars_caste_long <- demovars_caste %>%
   pivot_longer(cols = starts_with("Risky_"), names_to = "technology", values_to = "perceived_risk") %>%
-  mutate(technology = gsub("Risky_", "", technology)) %>%
-        mutate(caste = ifelse(grepl("SC|Scheduled caste", caste), "SC", caste),
-              caste = ifelse(grepl("ST|Scheduled Tribe", caste), "ST", caste),
-              caste = ifelse(grepl("OBC|Other Backward Classes", caste), "OBC", caste))
+  mutate(technology = gsub("Risky_", "", technology))
 
@@
 
+# For Coal
+Coal_urban_rural <- demovars_urban_rural %>%
+  filter(technology == "Coal")
+pairwise.wilcox.test(Coal_urban_rural$perceived_risk, Coal_urban_rural$urban_rural, p.adjust.method = "BH")
+
+# For Gas
+Gas_urban_rural <- demovars_urban_rural %>%
+  filter(technology == "Gas")
+pairwise.wilcox.test(Gas_urban_rural$perceived_risk, Gas_urban_rural$urban_rural, p.adjust.method = "BH")
+
+# For Hydro
+Hydro_urban_rural <- demovars_urban_rural %>%
+  filter(technology == "Hydro")
+pairwise.wilcox.test(Hydro_urban_rural$perceived_risk, Hydro_urban_rural$urban_rural, p.adjust.method = "BH")
+
+# For INDBiogas
+INDBiogas_urban_rural <- demovars_urban_rural %>%
+  filter(technology == "INDBiogas")
+pairwise.wilcox.test(INDBiogas_urban_rural$perceived_risk, INDBiogas_urban_rural$urban_rural, p.adjust.method = "BH")
+
+# For INDDiesel
+INDDiesel_urban_rural <- demovars_urban_rural %>%
+  filter(technology == "INDDiesel")
+pairwise.wilcox.test(INDDiesel_urban_rural$perceived_risk, INDDiesel_urban_rural$urban_rural, p.adjust.method = "BH")
+
+# For INDFirewoodetc
+INDFirewoodetc_urban_rural <- demovars_urban_rural %>%
+  filter(technology == "INDFirewoodetc")
+pairwise.wilcox.test(INDFirewoodetc_urban_rural$perceived_risk, INDFirewoodetc_urban_rural$urban_rural, p.adjust.method = "BH")
+
+# For INDHydro
+INDHydro_urban_rural <- demovars_urban_rural %>%
+  filter(technology == "INDHydro")
+pairwise.wilcox.test(INDHydro_urban_rural$perceived_risk, INDHydro_urban_rural$urban_rural, p.adjust.method = "BH")
+
+# For INDKerosene
+INDKerosene_urban_rural <- demovars_urban_rural %>%
+  filter(technology == "INDKerosene")
+pairwise.wilcox.test(INDKerosene_urban_rural$perceived_risk, INDKerosene_urban_rural$urban_rural, p.adjust.method = "BH")
+
+# For INDLPG
+INDLPG_urban_rural <- demovars_urban_rural %>%
+  filter(technology == "INDLPG")
+pairwise.wilcox.test(INDLPG_urban_rural$perceived_risk, INDLPG_urban_rural$urban_rural, p.adjust.method = "BH")
+
+# For INDSolar
+INDSolar_urban_rural <- demovars_urban_rural %>%
+  filter(technology == "INDSolar")
+pairwise.wilcox.test(INDSolar_urban_rural$perceived_risk, INDSolar_urban_rural$urban_rural, p.adjust.method = "BH")
+
+# For INDWind
+INDWind_urban_rural <- demovars_urban_rural %>%
+ filter(technology == "INDWind")
+pairwise.wilcox.test(INDWind_urban_rural$perceived_risk, INDWind_urban_rural$urban_rural, p.adjust.method = "BH")
+
+#For Nuclear
+Nuclear_urban_rural <- demovars_urban_rural %>%
+filter(technology == "Nuclear")
+pairwise.wilcox.test(Nuclear_urban_rural$perceived_risk, Nuclear_urban_rural$urban_rural, p.adjust.method = "BH")
+
+#For Oil
+Oil_urban_rural <- demovars_urban_rural %>%
+filter(technology == "Oil")
+pairwise.wilcox.test(Oil_urban_rural$perceived_risk, Oil_urban_rural$urban_rural, p.adjust.method = "BH")
+
+#For Solar
+Solar_urban_rural <- demovars_urban_rural %>%
+filter(technology == "Solar")
+pairwise.wilcox.test(Solar_urban_rural$perceived_risk, Solar_urban_rural$urban_rural, p.adjust.method = "BH")
+
+#For Wind
+Wind_urban_rural <- demovars_urban_rural %>%
+filter(technology == "Wind")
+pairwise.wilcox.test(Wind_urban_rural$perceived_risk, Wind_urban_rural$urban_rural, p.adjust.method = "BH")
+
 ```
+
+```{r}
+library(ggplot2)
+
+# Convert variables to factors
+demovars_urban_rural$urban_rural <- factor(demovars_urban_rural$urban_rural)
+demovars_urban_rural$technology <- factor(demovars_urban_rural$technology)
+
+# Create boxplot
+ggplot(demovars_urban_rural, aes(x = technology, y = perceived_risk, fill = urban_rural)) +
+  stat_boxplot(geom="errorbar", width=0.5) +
+  stat_boxplot(geom="boxplot", width=0.5, notch=FALSE, outlier.shape=NA) +
+  scale_fill_manual(values = c("#00AFBB", "#E7B800")) +
+  labs(x = "Technology", y = "Perceived Risk", fill = "Urban/Rural") +
+  theme_bw() +
+   theme(legend.position = "bottom", plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 90, vjust = 0.5)) +
+  ggtitle("Perceived Risk by Technology and Urban/Rural Group") +
+  facet_wrap(~ifelse(grepl("^IND", technology), "IND", "Non-IND"), nrow = 1)
+
+```
+
+```{r}
+# now check for urban and gender since caste is not that important , I don't care about age. let's do a regression
+
+str(demovars)
+
+```
+
+```{r}
+library(dplyr)
+demovars_subset <- demovars %>%
+  na.omit()%>%
+  select(-c(urban_rural, gender, caste, religion, age, State))
+
+# correlation matric to check correlations among the DVs
+correlation_matrix <- round(cor(demovars_subset), 2)
+
+# Convert correlation matrix to data frame
+cor_df <- as.data.frame(as.table(correlation_matrix))
+
+# Rename columns
+colnames(cor_df) <- c("Var1", "Var2", "Correlation")
+
+# Extract variables with correlation greater than 0.7
+high_corr_vars <- subset(cor_df, abs(Correlation) > 0.7) %>%
+                  filter(Var1 != Var2)
+
+# We see that Risky_INDSolar and Risky_Solar are highly correlated concepts (as expected) but rest of the dependent variables are not highly correlated.
+In the context of dependent variables, high correlation between them can indicate that they are measuring similar constructs or dimensions, which can lead to redundancy in the model.
+In some cases, it may be necessary to combine these variables or choose one to represent the construct in the analysis.
+Additionally, high correlation between dependent variables can make it difficult to isolate the effect of individual independent variables on each dependent variable.
+Therefore, it is important to check the correlation between different dependent variables to ensure that the model is accurately capturing the relationships between the independent and dependent variables.
+
+# Here we don't need to worry about this because we are going to run two separate regression models. one for IND and one for centrally owned technologies. SO NO HIGH MULTICOLINEARITY - GOOD NEWS!
+
+```
+
+```{r}
+# I want to conduct a factor analysis on my IVs to see how closely connected some of the caste and religion categories might be. 
+library(psych)
+
+```
+
+```{r}
+# what is the appropriate regression model to use? First I consider the regression model used in risk studies? 
+# First question is does WME (upper caste male effect exist in India, or what demographic factors impact risk perception of energy technologies.)
+# going to use linear regression - following Kahan et al.
+
+# running multivariate regression model on risk perception fom centrally owned energy technologies:
+
+model_Risky_central <- demovars %>%
+  dplyr::select(dplyr::starts_with("Risky"), age, urban_rural, gender, caste, religion, State) %>%
+  dplyr::select(-dplyr::starts_with("Risky_IND")) %>%
+  na.omit()%>%
+#creating dummy variables
+  mutate(gender_female = if_else(gender == "Female", 1, 0),
+         caste_brahmin = if_else(caste == "Brahmin", 1, 0),
+         caste_general = if_else(caste == "General", 1, 0),
+         caste_obc = if_else(caste == "OBC", 1, 0),
+         caste_rather_not_say = if_else(caste == "Rather not say/Don't know", 1, 0),
+         caste_sc = if_else(caste == "SC", 1, 0),
+         caste_st = if_else(caste == "ST", 1, 0),
+         urban_rural_rural = if_else(urban_rural == "Rural", 1, 0),
+         age_18_24 = if_else(age == "18-24 years old", 1, 0),
+         age_25_34 = if_else(age == "25-34 years old", 1, 0),
+         age_35_44 = if_else(age == "35-44 years old", 1, 0),
+         age_45_54 = if_else(age == "45-54 years old", 1, 0),
+         age_55_64 = if_else(age == "55-64 years old", 1, 0),
+         age_65_74 = if_else(age == "65-74 years old", 1, 0),
+         age_75_or_older = if_else(age == "75 years or older", 1, 0),
+         religion_agnosticism_atheism = if_else(religion == "Agnosticism_Atheism", 1, 0),
+         religion_buddhism = if_else(religion == "Buddhism", 1, 0),
+         religion_christanity = if_else(religion == "Christanity", 1, 0),
+         religion_hinduism = if_else(religion == "Hinduism", 1, 0),
+         religion_islam = if_else(religion == "Islam", 1, 0),
+         religion_jainism = if_else(religion == "Jainism", 1, 0),
+         religion_other = if_else(religion == "Other", 1, 0),
+         religion_sikhism = if_else(religion == "Sikhism", 1, 0),
+         state_maharashtra = if_else(State == "Maharashtra", 1, 0),
+         state_rajasthan = if_else(State == "Rajasthan", 1, 0),
+         state_tamilnadu = if_else(State == "Tamilnadu", 1, 0),
+         state_up = if_else(State == "UP", 1, 0),
+         state_west_bengal = if_else(State == "West Bengal", 1, 0))
+
+# Fit a multivariate linear regression model
+model <- lm(cbind(Risky_Hydro, Risky_Solar, Risky_Wind, Risky_Nuclear, Risky_Coal, Risky_Gas, Risky_Oil) ~ gender_female + caste_general + caste_obc + caste_rather_not_say + caste_sc + caste_st + urban_rural_rural + age_25_34 + age_35_44 + age_45_54 + age_55_64 + age_65_74 + age_75_or_older + religion_buddhism + religion_christanity + religion_hinduism + religion_islam + religion_jainism + religion_other + religion_sikhism + state_rajasthan + state_tamilnadu + state_up + state_west_bengal, data = model_Risky_central)
+
+# Print the model summary
+summary(model)
+
+str(model_Risky_central)
+
+#NEXT - plot residuals, read about regression on statistics by Jim.
+move on to factor analysis and reducing factors and conducting regression models and residual plots, send these to Terre, Milind and Ramana - questions and ideas for two papers.
+- right now the results from the regression do not match the earlier results like the significance of gender for instance
+
+```

### 2023-09-20 module1/Extra.Rmd
lot of changes because I wasn't opening the project file.

---
title: "Extra"
output: html_document
---

```{r}

#FA on LSI/ISI components

df_FA <- addedcols %>% 
  dplyr::select(LIlenght,LIassociation, govtscheme,education, workknowledge, subsidyknow, drinkingwater, cookingwater,farwatermins, wateravail, toilet, house, houseown, polposition, polparty,  foodadequacy, foodtrouble, healthdist, illness, severeillness, stove, vehicle, food, income)%>%
  na.omit()

df_FA_numeric <- data.frame(lapply(df_FA, as.numeric))

# Print the new dataframe
print(df_FA_numeric)

lapply(df_FA, unique)

df_FA_cor <- cor(df_FA_numeric)
PCA_LI <- principal(df_FA_numeric, nfactors = 24, rotate = "none") # no rotation to start with.

print(PCA_LI)

PCA_LI$loadings

PCA_LI6 <- principal(df_FA_numeric, nfactors = 6, rotate = "varimax") # no rotation to start with.

print(PCA_LI6)

PCA_LI6$loadings

# Extract the loadings
loadings <- PCA_LI6$loadings

# Set loadings less than 0.4 to NA
loadings[abs(loadings) < 0.4] <- NA

# Print the updated loadings
print(loadings)
```

```{r}
## Now PCA on my SLI and LVI scales

SLI <-  addedcols %>%
  filter(Livelihood_Income == "LSI") %>%
  dplyr::select(Lconfidence, Llenght, Lassociation, animals, income, govtscheme,education, workknowledge, drinkingwater,
         cookingwater, farwatermins, wateravail,toilet, house, houseown, stove, vehicle, polposition, polparty, food, foodadequacy, foodtrouble, healthdist,          illness, severeillness) %>%
          na.omit()

# questions about coding the data - ask milind tomorrow

addedcols %>%
 filter(Livelihood_Income == "LSI") %>%
 summarise(n=n())

SLI %>%
  summarise_all(~sum(is.na(.)))

str(SLI)

# Convert all columns to numeric
SLI_numeric <- data.frame(lapply(SLI, function(x) as.numeric(as.factor(x))))

# Determine the number of factors to retain using parallel analysis

SLI_cor <- cor(SLI_numeric)
PCA25 <- principal(SLI_numeric, nfactors = 25 , rotate = "none") # no rotation to start with.

print(PCA25)

PCA25$loadings

fa.parallel(SLI_cor)

SLI.pca <- principal(SLI_numeric, nfactors = 9, rotate = "varimax")

print.psych(SLI.pca, cut = 0.40, sort = TRUE)

fa.diagram(SLI.fa)

```

### 2023-09-20 module1/moduleoneanalysis.Rmd
governance preference graphs
updating rmd file with clean data
lot of changes because I wasn't opening the project file.

@@
 output:
+  pdf_document: default
   html_document:
@@
 suppressPackageStartupMessages(library(dplyr))
+suppressPackageStartupMessages(library(psych))
 
@@
 
-```{r, eval=TRUE}
+```{r, eval=TRUE, echo = FALSE}
 
@@
 module1 <- data.frame(moduleone)
-module1 %>%
-  filter(!row_number() %in% c(1,2))
 
@@
 
-```{r, eval =TRUE}
+```{r, warning = FALSE, echo = FALSE}
 #This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
 codedmodule1 <- module1 %>%
-
   #remove row 1
@@
   # replace risky likert scale with numbers
-  mutate_at(vars(starts_with("Risky")), funs(case_when(. =="Not at all risky" ~ 1, 
+  mutate(across(starts_with("Risky"), ~case_when(. =="Not at all risky" ~ 1, 
                                                  . =="Slightly risky" ~ 2, 
@@
   # replace beneficial likert scale with numbers  
-  mutate_at(vars(starts_with("Ben")), funs(case_when(. =="Not at all beneficial" ~ 1,
+  mutate(across(starts_with("Ben"), ~case_when(. =="Not at all beneficial" ~ 1,
                                                . =="Slightly beneficial" ~ 2,
@@
   # replace nuclear acceptance likert scale with numbers
-  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
+  mutate(across(c(N_accept,N_reluctantlyaccept,N_reject), ~case_when(. == "Strongly disagree" ~ 1, 
                                                                      . == "Somewhat disagree" ~ 2,
@@
 
-  mutate_at(vars(Livelihood_Income), funs(case_when(. == "(a) own farming/fishing/animal rearing/business" ~ "LSI", 
+  mutate(across(Livelihood_Income, ~case_when(. == "(a) own farming/fishing/animal rearing/business" ~ "LSI", 
                                               . == "(b) employed for wages/salary" ~ "ISI",
-                                                    . == "(c) student" ~"student",
-                                                    . == "(d) currently unemployed" ~ "unemployed",
+                                              . == "(c) student" ~"other",
+                                              . == "(d) currently unemployed" ~ "other",
                                               . == "(e) homemaker" ~ "homemaker",
-                                                    . == "(f) retired" ~ "retired",
-                                                    . == "(g) unable to work" ~ "unable to work" ))) %>%
+                                              . == "(f) retired" ~ "other",
+                                              . == "(g) unable to work" ~ "other" ))) %>%
 
   # coding education
-   mutate_at(vars(education), funs(case_when(. == "No schooling completed" ~ 0, 
+  mutate(across(education, ~case_when(. == "No schooling completed" ~ 0, 
                                       . == "Primary school" ~ 1,
@@
                                       . == "Doctorate degree" ~ 9 ))) %>%
+
   # coding yes and no questions
-  mutate_at(vars(Iassociation, govtscheme, wateravail, polposition, polparty), funs(case_when(.== "Yes" ~ 1,
+  mutate(across(c(Lassociation,Iassociation, govtscheme, wateravail, polposition, polparty), ~case_when(.== "Yes" ~ 1,
                                                                                                         .== "No" ~ 0))) %>%
   # reverse coding yes and no questions
-  mutate_at(vars(illness,severeillness), funs(case_when(.== "Yes" ~ 0,
+  mutate(across(c(illness,severeillness), ~case_when(.== "Yes" ~ 0,
                                                      .== "No" ~ 1))) %>%
@@
   # coding How confident are you that you can continue your current livelihood if you want to? 
- mutate_at(vars(Lconfidence), funs(case_when(. == "Not at all confident" ~ 1, 
+  mutate(across(Lconfidence, ~case_when(. == "Not at all confident" ~ 1, 
                                         . == "Not much confident" ~ 2,
@@
 
- mutate_at(vars(Lboat, houseown), funs(case_when(.== "Own it" ~ 1,
-                                                 .== "Rent it" ~ 0)))%>%
+  mutate(across(c(Lboat, houseown), ~case_when(.== "Own it" ~ 1,
+                                               .== "Rent it" ~ 0))) %>%
 
   # J security index coding
-
- mutate_at(vars(JISRkeep), funs(case_when(. == "Strongly disagree" ~ 1, 
+  mutate(across(JISRkeep, ~case_when(. == "Strongly disagree" ~ 1, 
                                      . == "Somewhat disagree" ~ 2,
@@
   # reverse code JIS 
-  mutate_at(vars(JISlosefuture, JISlose, JISfuture), funs(case_when(. == "Strongly disagree" ~ 5, 
+  mutate(across(c(JISlosefuture, JISlose, JISfuture), ~case_when(. == "Strongly disagree" ~ 5, 
                                                                  . == "Somewhat disagree" ~ 4,
@@
 
-  mutate_at(vars(totalincome, otherincome), funs(case_when(. == "Less than Rs 1,00,000" ~ 1,
+  mutate(across(c(totalincome, otherincome), ~case_when(. == "Less than Rs 1,00,000" ~ 1,
                                                         . == "Rs 1,00,000 to Rs 2,50,000"  ~ 2,
@@
                                                         . == "Rs 5,00,001 to Rs 10,00,000" ~ 4,
-                                                                        . == "Rs 10,00,001 and above"  ~ 5))) %>%
+                                                        . == "Rs 10,00,001 and above"  ~ 5,
+                                                        . == "Doesn't apply" ~ 0))) %>%
 
-  mutate_at(vars(workknowledge, subsidyknow), funs(case_when(. == "Very poor" ~ 1, 
+  mutate(across(c(workknowledge, subsidyknow), ~case_when(. == "Very poor" ~ 1, 
                                                           . == "Poor" ~ 2,
@@
 
-mutate_at(vars(drinkingwater, cookingwater), funs(case_when(. == "Bottled water/ Filtered Water" ~ 1,                                       
+  mutate(across(c(drinkingwater, cookingwater), ~case_when(. == "Bottled water/ Filtered Water" ~ 1,                                       
                                                            .  == "Piped into dwelling" ~ 2,                                                  
@@
 
-  mutate_at(vars(toilet), funs(case_when(. == "No facility/bush/field" ~ 1,                                       
+  mutate(across(toilet, ~case_when(. == "No facility/bush/field" ~ 1,                                       
                                    .  == "Hanging toilet/hanging latrine" ~ 2,                                             
@@
 
-  mutate_at(vars(house), funs(case_when(. == "Hut made of mud, bamboo, straw etc. (kutcha house)" ~ 1, 
+  mutate(across(house, ~case_when(. == "Hut made of mud, bamboo, straw etc. (kutcha house)" ~ 1, 
                                   . == "Permanent single story house (pukka house)" ~ 2,
@@
 
-  mutate_at(vars(foodtrouble), funs(case_when(. == "8 or more months" ~ 1,                                       
+  mutate(across(foodtrouble, ~case_when(. == "8 or more months" ~ 1,                                       
                                         .  == "6-8 months"  ~ 2,                                                  
@@
 
-   mutate_at(vars(foodadequacy), funs(case_when(. == "Extremely inadequate" ~ 1, 
+  mutate(across(foodadequacy, ~case_when(. == "Extremely inadequate" ~ 1, 
                                          . == "Moderately inadequate" ~ 2,
@@
                                          . == "Moderately adequate" ~ 6,
-                                                                        . == "Extremely adequate" ~ 7)))%>%
+                                         . == "Extremely adequate" ~ 7))) %>%
 
-separate( col = cookstove, into = c("cook1", "cook2", "cook3", "cook4"), sep = ",") %>%
-separate( col = vehicle, into = c("vehicle1", "vehicle2", "vehicle3", "vehicle4"), sep = ",")%>%
-separate( col = foodsource, into = c("food1", "food2", "food3", "food4"), sep = ",")
+  # separating cooking, vehicle and food cols into separate entries
+  separate(col = cookstove, into = c("cook1", "cook2", "cook3", "cook4"), sep = ",") %>%
+  separate(col = vehicle, into = c("vehicle1", "vehicle2", "vehicle3", "vehicle4"), sep = ",") %>%
+  separate(col = foodsource, into = c("food1", "food2", "food3", "food4"), sep = ",") %>%
 
-#coded dependent variables for module 1 livelihood and income security survey
+  mutate(across(c(cook1, cook2, cook3, cook4), ~case_when(. == "Three Stone Stove/Open Fire" ~ 1, 
+                                  . == "Traditional Solid Fuel Stove" ~ 2,
+                                  . == "Liquid Fuel Stove" ~3,
+                                  . == "Biogas Stove" ~ 4,
+                                  . == "Piped Natural Gas Stove" ~ 5,
+                                  . == "Liquefied Petroleum Gas (LPG)/Cooking gas stove" ~ 6,
+                                  . == "Solar Cooker" ~ 7,
+                                  . == "Electric Stove" ~ 7,
+                                  is.na(.) ~ 0))) %>%
 
-codedmodule1
-```
+  mutate(across(c(vehicle1, vehicle2, vehicle3, vehicle4, vehicletext), ~case_when(. == "Bicycle" ~ 1, 
+                                    . == "Animal Drawn Cart" ~ 2,
+                                    . == "Motorcycle/Scooter" ~3,
+                                    . == "Car" ~ 4,
+                                    . == "Truck" ~ 4,
+                                    . == "Boat with Motor" ~ 4,
+                                    . == "Tractor" ~ 4,
+                                    . == "E-rickshaw" ~ 1,
+                                    . == "Tempo" ~ 3,
+                                    . == "Nothing" ~ 0,
+                                    . == "Other (Please Specify)" ~ 0,
+                                    is.na(.) ~ 0))) %>%
 
-```{r}
-# solving the problem of multiple answers  to a questions 
-codedmodule1
+  mutate(across(c(food1, food2, food3,food4), ~case_when(. == "Forest" ~ 1, 
+                                  . == "Own Farm" ~ 2,
+                                  . == "Market" ~4,
+                                  . == "Own livestock" ~ 2,
+                                  . == "Subsidised ration shops" ~ 3,
+                                  is.na(.) ~ 0)))
+
+codedmodule1$gender <- factor(codedmodule1$gender, levels = c("Male","Female"))
+
+#converting relevant variables to factors 
+#codedmodule1 <- codedmodule1 %>%
+  #mutate_at(vars(Lassociation, Lboat, Iassociation, totalincome, otherincome, govtscheme, education, subsidyknow, drinkingwater, cookingwater, wateravail, toilet,
+                # house, houseown, cook1, cook2, cook3, cook4, vehicle1, vehicle2, vehicle3, vehicle4, vehicletext, polposition, polparty,  food1, food2, food3, food4, foodadequacy, foodtrouble, #illness, severeillness, age, urban_rural, gender, caste, religion),
+                 #~factor(.))
+#converting relevant variables to Numeric
 
@@
 
-```{r}
+```{r, echo=FALSE}
 
-x <- as.factor(codedmodule1$vehicle)
-
-levels(x)
+colnames(codedmodule1)
+addedcols <- codedmodule1 %>%
+  mutate_at(vars(Lassociation, Lboat, Iassociation, totalincome, otherincome, govtscheme, education, subsidyknow, drinkingwater, cookingwater, wateravail, toilet, house, houseown, cook1, cook2, cook3, cook4, vehicle1, vehicle2, vehicle3, vehicle4, vehicletext, polposition, polparty, food1, food2, food3, food4, foodadequacy, foodtrouble, illness, severeillness, Llenght, Lfarmbigha, Lanimalcowbull, Lanimalcattle, Lanimalhorses, Lanimalgoats, Lanimalsheep, Lanimalpoultry, Ilenght, Ipropvalue, farwatermins, healthdist), as.numeric) %>%
+  mutate(stove = cook1 + cook2 + cook3 + cook4, 
+        vehicle = vehicle1 + vehicle2 + vehicle3 + vehicle4 + vehicletext,
+        food = food1 + food2 + food3 + food4,
+        #income = totalincome + otherincome,
+        animals = Lanimalcowbull + Lanimalcattle + Lanimalhorses + Lanimalgoats + Lanimalsheep + Lanimalpoultry) %>%
+  dplyr::select(-cook1, -cook2, -cook3, -cook4, -vehicle1, -vehicle2, -vehicle3, -vehicle4, -vehicletext, -food1, -food2, -food3, -food4, -Lanimalcowbull, -Lanimalcattle, -Lanimalhorses, -Lanimalgoats, -Lanimalsheep, -Lanimalpoultry) %>%
+  unite("LIlenght", c(Llenght,Ilenght), na.rm = TRUE, remove = TRUE)%>%
+  unite("LIassociation", c(Lassociation,Iassociation), na.rm = TRUE, remove = TRUE)
 
@@
 
-```{r}
+\newpage
+
+The total n for this survey is 1062. However, the sample is divided by the type of work people do as below:
+
+```{r, echo=FALSE}
+
+count <- module1 %>% count(Livelihood_Income)
+
+count <- count[1:(nrow(count) - 2), ]
+
+count
 
@@
 
-```{r}
+# The Problem of large NAs
+
+```{r, echo=FALSE}
+
+# Count the number of NAs in each column
+num_NAs <- colSums(is.na(addedcols))
+
+# Print the result
+print(num_NAs)
 
 ```
+
+```{r, echo = FALSE}
+
+nuclear_LI <- addedcols %>% 
+  dplyr::select(Risky_Nuclear,State, gender, caste, religion, urban_rural, age,  Livelihood_Income,education, workknowledge,LIlenght, subsidyknow, drinkingwater,cookingwater,farwatermins, wateravail,toilet, house,stove, vehicle, houseown, polposition, LIassociation,polparty, govtscheme, totalincome, Lfarmbigha,  Ipropvalue, Lboat, animals, foodadequacy, foodtrouble,food, healthdist, illness, severeillness)
+
+# checking NAs in LSI part 
+assetcheck <- addedcols %>% filter(Livelihood_Income == "LSI") %>%
+            dplyr::select(Lfarmland,Lfarmbigha,animals)
+
+num_NAs2 <- colSums(is.na(assetcheck))
+
+#print(num_NAs2)
+
+codedmodule1 %>% count(Livelihood_Income)
+addedcols %>% count(Livelihood_Income)
+codedmodule1 %>% count(Lfarmbigha)
+codedmodule1 %>% filter(Livelihood_Income == "LSI") %>% count(Lfarmland)
+addedcols %>% filter(Livelihood_Income == "LSI") %>% count(animals)
+codedmodule1 %>% count(Lboat)
+
+addedcols %>% filter(Livelihood_Income == "LSI") %>% filter(Lfarmland == "Doesn't apply") %>% count(Lboat)
+addedcols %>% filter(Livelihood_Income == "LSI") %>% filter(Lfarmland == "Doesn't apply") %>% count(animals)
+
+addedcols %>% filter(Livelihood_Income == "ISI") %>% count(Iproperty)
+
+# checking NAs in ISI part
+
+module1 %>% filter(!row_number() %in% c(1,2)) %>% filter(Livelihood_Income != "(a) own farming/fishing/animal rearing/business") %>% count(Iproperty)
+
+# there are only 4 people who said they own a boat but not a farmland when looking at those people who answered LSI part of the survey.
+So we will just look at boat as  another livelihood asset and remove the 4 responses by removing Doesn't apply values in the Lfarmland part.
+
+```
+
+```{r, echo = FALSE}
+# Nuclear dataframe for LSI/ISI with standardized values
+
+# Convert columns to numeric starting from 'education'
+cols_to_convert <- names(nuclear_LI)[which(names(nuclear_LI) == 'education'):length(names(nuclear_LI))]
+nuclear_LI[cols_to_convert] <- lapply(nuclear_LI[cols_to_convert], as.numeric)
+
+nuclear_LI$LIassociation <- as.numeric(nuclear_LI$LIassociation)
+nuclear_LI$LIlenght <- as.numeric(nuclear_LI$LIlenght)
+# Standardize the values
+standardize <- function(x) {
+  (x - min(x, na.rm = TRUE)) / (max(x, na.rm = TRUE) - min(x, na.rm = TRUE))
+}
+
+nuclear_LI[cols_to_convert] <- lapply(nuclear_LI[cols_to_convert], standardize)
+
+# Displaying the first few rows of the dataframe
+#head(nuclear_LI)
+
+```
+
+```{r, echo = FALSE}
+
+# first make two different groups in the data by Livelihood_Income variable. - homemaker, ISI, LSI, other (retired, student, unable to work, unemployed)
+
+str(nuclear_LI)
+
+# For 'homemaker'
+homemaker_df <- nuclear_LI %>% filter(Livelihood_Income == "homemaker") %>%
+                dplyr::select (Risky_Nuclear, State,education, workknowledge, LIlenght, drinkingwater,cookingwater,farwatermins, wateravail,toilet, house,stove, vehicle, houseown, polposition, LIassociation, polparty, govtscheme, totalincome, foodadequacy, foodtrouble,food, healthdist, illness, severeillness) %>%
+  na.omit()
+
+num_NAs3 <- colSums(is.na(homemaker_df))
+
+# For 'ISI'
+ISI_df <- nuclear_LI %>% filter(Livelihood_Income == "ISI") %>%
+  dplyr::select(Risky_Nuclear,State, education, workknowledge,LIlenght, drinkingwater,cookingwater,farwatermins, wateravail,toilet, house,stove, vehicle, houseown, polposition, LIassociation,polparty, govtscheme, totalincome, foodadequacy, foodtrouble,food, healthdist, illness, severeillness) %>%
+   na.omit()
+
+num_NAs4 <- colSums(is.na(ISI_df))
+
+# For 'LSI'
+LSI_df <- nuclear_LI %>% filter(Livelihood_Income == "LSI")  %>% 
+  dplyr::select(Risky_Nuclear,State, education, workknowledge,LIlenght, drinkingwater,cookingwater,farwatermins, wateravail,toilet, house,stove, vehicle, houseown, polposition, LIassociation,polparty, govtscheme, totalincome, animals, foodadequacy, foodtrouble,food, healthdist, illness, severeillness) %>%
+  na.omit()
+
+num_NAs5 <- colSums(is.na(LSI_df))
+
+# For 'other'
+other_df <- nuclear_LI %>% filter(Livelihood_Income == "other")%>% 
+  dplyr::select(Risky_Nuclear,State, education, workknowledge,LIlenght, drinkingwater,cookingwater,farwatermins, wateravail,toilet, house,stove, vehicle, houseown, polposition, LIassociation,polparty, govtscheme, totalincome, foodadequacy, foodtrouble,food, healthdist, illness, severeillness)%>%
+  na.omit()
+
+num_NAs6 <- colSums(is.na(other_df))
+
+# problem of small sample size - how to deal with it ?
+
+```
+
+```{r, echo = FALSE}
+
+library(dplyr)
+
+# now aggregating LSI/ISI for different groups.
+
+homemaker <- homemaker_df %>%
+  mutate(
+    human_asset = rowMeans(dplyr::select(., education, workknowledge, LIlenght), na.rm = TRUE),
+    physical_asset = rowMeans(dplyr::select(., drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown), na.rm = TRUE),
+    social_asset = rowMeans(dplyr::select(., polposition, LIassociation, polparty, govtscheme), na.rm = TRUE),
+    financial_asset = totalincome,
+    food_security = rowMeans(dplyr::select(., foodadequacy, foodtrouble, food), na.rm = TRUE),
+    health_status = rowMeans(dplyr::select(., healthdist, illness, severeillness), na.rm = TRUE)
+  )%>%
+ dplyr::select(
+    -c(education, workknowledge, LIlenght, 
+      drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown, 
+      polposition, LIassociation, polparty, govtscheme, 
+      foodadequacy, foodtrouble, food,
+      healthdist, illness, severeillness,
+      totalincome)
+  )%>%
+  mutate(
+    score = rowMeans(dplyr::select(., human_asset, physical_asset, social_asset, financial_asset, food_security, health_status), na.rm = TRUE)
+  )
+
+ISI <- ISI_df%>%
+  mutate(
+    human_asset = rowMeans(dplyr::select(., education, workknowledge, LIlenght), na.rm = TRUE),
+    physical_asset = rowMeans(dplyr::select(., drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown), na.rm = TRUE),
+    social_asset = rowMeans(dplyr::select(., polposition, LIassociation, polparty, govtscheme), na.rm = TRUE),
+    financial_asset = totalincome,
+    food_security = rowMeans(dplyr::select(., foodadequacy, foodtrouble, food), na.rm = TRUE),
+    health_status = rowMeans(dplyr::select(., healthdist, illness, severeillness), na.rm = TRUE)
+  )%>%
+  dplyr::select(
+    -c(education, workknowledge, LIlenght, 
+      drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown, 
+      polposition, LIassociation, polparty, govtscheme, 
+      foodadequacy, foodtrouble, food,
+      healthdist, illness, severeillness,
+      totalincome)
+  )%>%
+  mutate(
+    score = rowMeans(dplyr::select(., human_asset, physical_asset, social_asset, financial_asset, food_security, health_status), na.rm = TRUE)
+  )
+
+LSI <- LSI_df%>%
+  mutate(
+    human_asset = rowMeans(dplyr::select(., education, workknowledge, LIlenght), na.rm = TRUE),
+    physical_asset = rowMeans(dplyr::select(., drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown), na.rm = TRUE),
+    social_asset = rowMeans(dplyr::select(., polposition, LIassociation, polparty, govtscheme), na.rm = TRUE),
+    financial_asset = totalincome,
+    food_security = rowMeans(dplyr::select(., foodadequacy, foodtrouble, food), na.rm = TRUE),
+    health_status = rowMeans(dplyr::select(., healthdist, illness, severeillness), na.rm = TRUE)
+  )%>%
+  dplyr::select(
+    -c(education, workknowledge, LIlenght, 
+      drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown, 
+      polposition, LIassociation, polparty, govtscheme, 
+      foodadequacy, foodtrouble, food,
+      healthdist, illness, severeillness,
+      totalincome)
+  )%>%
+  mutate(
+    score = rowMeans(dplyr::select(., human_asset, physical_asset, social_asset, financial_asset, food_security, health_status), na.rm = TRUE)
+  )
+
+other <- other_df%>%
+  mutate(
+    human_asset = rowMeans(dplyr::select(., education, workknowledge, LIlenght), na.rm = TRUE),
+    physical_asset = rowMeans(dplyr::select(., drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown), na.rm = TRUE),
+    social_asset = rowMeans(dplyr::select(., polposition, LIassociation, polparty, govtscheme), na.rm = TRUE),
+    financial_asset = totalincome,
+    food_security = rowMeans(dplyr::select(., foodadequacy, foodtrouble, food), na.rm = TRUE),
+    health_status = rowMeans(dplyr::select(., healthdist, illness, severeillness), na.rm = TRUE)
+  )%>%
+  dplyr::select(
+    -c(education, workknowledge, LIlenght, 
+      drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown, 
+      polposition, LIassociation, polparty, govtscheme, 
+      foodadequacy, foodtrouble, food,
+      healthdist, illness, severeillness,
+      totalincome)
+  )%>%
+  mutate(
+    score = rowMeans(dplyr::select(., human_asset, physical_asset, social_asset, financial_asset, food_security, health_status), na.rm = TRUE)
+  )
+
+```
+
+```{r, echo = FALSE}
+
+# lms now for each category and then putting them into a single table using stargazer
+
+nuclear_model <- nuclear_LI %>%  
+  mutate(
+    human_asset = rowMeans(dplyr::select(., education, workknowledge, LIlenght), na.rm = TRUE),
+    physical_asset = rowMeans(dplyr::select(., drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown), na.rm = TRUE),
+    social_asset = rowMeans(dplyr::select(., polposition, LIassociation, polparty, govtscheme), na.rm = TRUE),
+    financial_asset = totalincome,
+    food_security = rowMeans(dplyr::select(., foodadequacy, foodtrouble, food), na.rm = TRUE),
+    health_status = rowMeans(dplyr::select(., healthdist, illness, severeillness), na.rm = TRUE)
+  )%>%
+  dplyr::select(
+    -c(education, workknowledge, LIlenght, 
+      drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown, 
+      polposition, LIassociation, polparty, govtscheme, 
+      foodadequacy, foodtrouble, food,
+      healthdist, illness, severeillness,
+      totalincome, Lfarmbigha, Ipropvalue, Lboat, animals)
+  )%>%
+  mutate(LIscore = rowMeans(dplyr::select(., human_asset, physical_asset, social_asset,financial_asset, food_security,health_status), na.rm = TRUE))
+
+nuclearLI_lm <- lm(Risky_Nuclear ~ caste + gender + urban_rural + human_asset + physical_asset + social_asset + financial_asset + food_security + health_status , data = nuclear_model)
+
+nuclearLI_lm2 <- lm(Risky_Nuclear ~ caste + gender + urban_rural + LIscore , data = nuclear_model)
+
+summary(nuclearLI_lm)
+summary(nuclearLI_lm2)
+#plot(nuclearLI_lm)
+
+```
+
+```{r, echo=FALSE}
+solar_LI <- addedcols %>% 
+  dplyr::select(Risky_Solar,State, gender, caste, religion, urban_rural, age,  Livelihood_Income,education, workknowledge,LIlenght, subsidyknow, drinkingwater,cookingwater,farwatermins, wateravail,toilet, house,stove, vehicle, houseown, polposition, LIassociation,polparty, govtscheme, totalincome, Lfarmbigha,  Ipropvalue, Lboat, animals, foodadequacy, foodtrouble,food, healthdist, illness, severeillness)
+
+# Solar dataframe for LSI/ISI with standardized values
+
+# Convert columns to numeric starting from 'education'
+cols_to_convert <- names(solar_LI)[which(names(solar_LI) == 'education'):length(names(solar_LI))]
+solar_LI[cols_to_convert] <- lapply(solar_LI[cols_to_convert], as.numeric)
+
+# Standardize the values
+standardize <- function(x) {
+  (x - min(x, na.rm = TRUE)) / (max(x, na.rm = TRUE) - min(x, na.rm = TRUE))
+}
+
+solar_LI[cols_to_convert] <- lapply(solar_LI[cols_to_convert], standardize)
+
+# Displaying the first few rows of the dataframe
+head(solar_LI)
+
+solar_model <- solar_LI %>%  
+  mutate(
+    human_asset = rowMeans(dplyr::select(., education, workknowledge, LIlenght), na.rm = TRUE),
+    physical_asset = rowMeans(dplyr::select(., drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown), na.rm = TRUE),
+    social_asset = rowMeans(dplyr::select(., polposition, LIassociation, polparty, govtscheme), na.rm = TRUE),
+    financial_asset = totalincome,
+    food_security = rowMeans(dplyr::select(., foodadequacy, foodtrouble, food), na.rm = TRUE),
+    health_status = rowMeans(dplyr::select(., healthdist, illness, severeillness), na.rm = TRUE)
+  )%>%
+  dplyr::select(
+    -c(education, workknowledge, LIlenght, 
+      drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown, 
+      polposition, LIassociation, polparty, govtscheme, 
+      foodadequacy, foodtrouble, food,
+      healthdist, illness, severeillness,
+      totalincome, Lfarmbigha, Ipropvalue, Lboat, animals)
+  )%>%
+  mutate(LIscore = rowMeans(dplyr::select(., human_asset, physical_asset, social_asset,financial_asset, food_security,health_status), na.rm = TRUE))
+
+solarLI_lm <- lm(Risky_Solar ~ caste + gender + urban_rural + human_asset + physical_asset + social_asset + financial_asset + food_security + health_status , data = solar_model)
+
+solarLI_lm2 <- lm(Risky_Solar ~ caste + gender + urban_rural + LIscore , data = solar_model)
+summary(solarLI_lm)
+summary(solarLI_lm2)
+#plot(solarLI_lm)
+
+```
+
+```{r, echo = FALSE}
+coal_LI <- addedcols %>% 
+  dplyr::select(Risky_Coal, State, gender, caste, religion, urban_rural, age,  Livelihood_Income, education, workknowledge, LIlenght, subsidyknow, drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown, polposition, LIassociation, polparty, govtscheme, totalincome, Lfarmbigha,  Ipropvalue, Lboat, animals, foodadequacy, foodtrouble, food, healthdist, illness, severeillness)
+
+# Coal dataframe for LSI/ISI with standardized values
+
+# Convert columns to numeric starting from 'education'
+cols_to_convert <- names(coal_LI)[which(names(coal_LI) == 'education'):length(names(coal_LI))]
+coal_LI[cols_to_convert] <- lapply(coal_LI[cols_to_convert], as.numeric)
+
+# Standardize the values
+standardize <- function(x) {
+  (x - min(x, na.rm = TRUE)) / (max(x, na.rm = TRUE) - min(x, na.rm = TRUE))
+}
+
+coal_LI[cols_to_convert] <- lapply(coal_LI[cols_to_convert], standardize)
+
+# Displaying the first few rows of the dataframe
+#head(coal_LI)
+
+coal_model <- coal_LI %>%  
+  mutate(
+    human_asset = rowMeans(dplyr::select(., education, workknowledge, LIlenght), na.rm = TRUE),
+    physical_asset = rowMeans(dplyr::select(., drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown), na.rm = TRUE),
+    social_asset = rowMeans(dplyr::select(., polposition, LIassociation, polparty, govtscheme), na.rm = TRUE),
+    financial_asset = totalincome,
+    food_security = rowMeans(dplyr::select(., foodadequacy, foodtrouble, food), na.rm = TRUE),
+    health_status = rowMeans(dplyr::select(., healthdist, illness, severeillness), na.rm = TRUE)
+  )%>%
+  dplyr::select(
+    -c(education, workknowledge, LIlenght, 
+      drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown, 
+      polposition, LIassociation, polparty, govtscheme, 
+      foodadequacy, foodtrouble, food,
+      healthdist, illness, severeillness,
+      totalincome, Lfarmbigha, Ipropvalue, Lboat, animals)
+  )%>%
+  mutate(LIscore = rowMeans(dplyr::select(., human_asset, physical_asset, social_asset,financial_asset, food_security,health_status), na.rm = TRUE))
+
+coalLI_lm <- lm(Risky_Coal ~ caste + gender + urban_rural + human_asset + physical_asset + social_asset + financial_asset + food_security + health_status, data = coal_model)
+
+coalLI_lm2 <- lm(Risky_Coal ~ caste + gender + urban_rural + LIscore, data = coal_model)
+
+summary(coalLI_lm)
+summary(coalLI_lm2)
+#plot(coalLI_lm)
+
+```
+
+\newpage
+
+# Linear Regression Models with asset groups
+
+```{r, echo=FALSE, results='asis'}
+library(stargazer)
+
+#stargazer code for all demographic variable lms
+
+cat("\\begingroup")
+cat("\\setlength{\\tabcolsep}{1pt}")
+cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer(nuclearLI_lm, solarLI_lm, coalLI_lm,
+          title = "Assets",
+          type = "latex"
+)
+cat("\\endgroup")
+
+```
+
+# Linear Regression Models with livelihood security and income security indeces
+
+```{r, echo=FALSE, results='asis'}
+library(stargazer)
+
+#stargazer code for all demographic variable lms
+
+cat("\\begingroup")
+cat("\\setlength{\\tabcolsep}{1pt}")
+cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer(nuclearLI_lm2, solarLI_lm2, coalLI_lm2,
+          title = "Livelihood and Income Security",
+          type = "latex"
+)
+cat("\\endgroup")
+
+```
+
+```{r, echo = FALSE}
+#  Cronbach's alpha test and CFA on JIS scale
+
+JIS <- codedmodule1 %>%
+  dplyr::select(JISRkeep,JISlosefuture, JISlose, JISfuture)%>%
+  na.omit()
+
+JIS_alpha <- psych::alpha(JIS, check.keys = TRUE)
+
+# alpha = 0.69 - not bad - not too good.
+
+library(lavaan)
+
+JIS_fas <- '
+  JISs =~ JISRkeep + JISlosefuture + JISlose + JISfuture 
+  '
+
+# Run CFA
+JIS_cfa <- cfa(JIS_fas, data = JIS , std.lv = TRUE)
+
+# Print the summary of the CFA results, including fit measures
+summary(JIS_cfa, fit.measure= TRUE, standardized = TRUE)
+
+# RMSEA - between 0.05 and 0.08 (reasonable fit), less than 0.05 close fit and greater than 0.10 is poor fit 
+# CFI - greater than 0.90 or 0.95 indicates good fit
+#TFI - CFI>TFI >0.90 - indicates good fit
+
+JIS_scores <- predict(JIS_cfa, newdata = JIS)
+
+JIS_data <- codedmodule1 %>% select(Risky_Nuclear, gender, caste, urban_rural, religion, JISRkeep, JISlosefuture, JISlose, JISfuture) %>%
+  filter(!is.na(JISRkeep) & !is.na(JISlosefuture)  & !is.na(JISlose)  & !is.na(JISfuture))
+
+JIS_Jscores <- cbind(JIS_data, JIS_scores)
+
+JIS_lm1 <- lm(Risky_Nuclear ~ caste + gender + urban_rural+ JIS_scores, data = JIS_Jscores)
+
+summary(JIS_lm1)
+
+```
+
+```{r, echo=FALSE}
+
+LSI2 <- codedmodule1 %>% select(Risky_Nuclear, Risky_Solar, Risky_Coal, gender, caste, urban_rural, religion, Lconfidence) %>%
+  filter(!is.na(Lconfidence))
+
+LSI2_lm1 <- lm(Risky_Nuclear ~ caste + gender + urban_rural+ Lconfidence, data = LSI2)
+
+summary(LSI2_lm1)
+
+```
+
+# Linear Regression Models with perceived livelihood and income security
+
+```{r, echo=FALSE, results='asis'}
+library(stargazer)
+
+#stargazer code for all demographic variable lms
+
+cat("\\begingroup")
+cat("\\setlength{\\tabcolsep}{1pt}")
+cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer(JIS_lm1, LSI2_lm1, 
+          title = "Perceived livelihood or job security",
+          type = "latex"
+)
+cat("\\endgroup")
+
+```
+
+\newpage
+
+#Extra
+
+```{r, echo = FALSE}
+
+##checking stuff
+codedmodule1
+
+codedmodule1 %>%
+  filter(Livelihood_Income == "LSI") %>%
+  count(Lfarmland)
+codedmodule1 %>%
+  count(Iproperty)
+
+lapply(codedmodule1, unique)
+ncol(codedmodule1)
+colnames(codedmodule1)
+
+str(codedmodule1)
+
+```
+
+# Livelihood/Income Security scale adapted from Kamaruddin and Samsudin(2014)
+
+Human Asset
+
+education - 	    What is the highest level of education you have received? If currently enrolled, highest degree received.
+
+workknowledge -   How would you rate your level of knowledge about your work ?
+
+LIlenght-         How long have you been in your current line of work?
+
+subsidyknow -     How would you rate your knowledge concerning how to obtain information about subsidies or aid from the government or any other agencies ?
+
+Physical Asset
+
+drinkingwater   	What is the main source of drinking water for the members of your household?
+cookingwater      What is the main source of water used by your\r\nhousehold for other purposes such as cooking and\r\nhandwashing?
+farwatermins      How long does it take to go there, get water, and come\r\nback? 
+toilet            What kind of toilet facility do members of your\r\nhousehold usually use?
+house
+stove
+vehicle
+houseown
+
+Social Asset
+
+polposition
+LIassociation
+polparty
+
+Financial Asset
+
+Income
+
+Natural Asset
+
+Lfarmland
+Lfarmbigha
+Iproperty
+Ipropvalue
+Lboat
+animals
+
+Livelihood Outcomes
+
+Foodsecurity
+
+foodadequacy 
+foodtrouble
+
+Health Status
+
+healthdist
+illness
+severeillness

### 2023-09-20 module2/factor analysis/extraFA.Rmd
lot of changes because I wasn't opening the project file.

---
title: "extraFA"
output: html_document
---

```{r load packages, warning = FALSE, message = FALSE, echo=FALSE}
  knitr::opts_chunk$set(warning = FALSE, message = FALSE)
suppressPackageStartupMessages(library(lavaan))
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(DT))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(psych)) # psychometrics

```

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
moduletwo <- read_excel(here::here("thesis_surveydata/political_factors_complete.xlsx"))
save(moduletwo, file = "moduletwo.rda")
module2 <- data.frame(moduletwo)
module2[module2 == "Rather not say/ Don't know"] <- "Rather not say/Don't know"
#module2 %>% filter(!row_number() %in% c(1,2))

# loaded data set for module 2 eco -pol variables and removes the rows with question number and question text
```

```{r, eval =TRUE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
codedmodule2 <- module2 %>%

#remove row 1
  filter(!row_number() %in% c(1,2)) %>%

# replace risky likert scale with numbers
  mutate_at(vars(starts_with("Risky")), funs(case_when(. =="Not at all risky" ~ 1, 
                                                       . =="Slightly risky" ~ 2, 
                                                       . =="Moderately risky" ~ 3, 
                                                       . =="Very risky" ~ 4, 
                                                       . =="Extremely risky" ~ 5))) %>%

# replace beneficial likert scale with numbers  
  mutate_at(vars(starts_with("Ben")), funs(case_when(. =="Not at all beneficial" ~ 1,
                                                     . =="Slightly beneficial" ~ 2,
                                                     . =="Moderately beneficial" ~ 3,
                                                     . =="Very beneficial" ~ 4,
                                                     . =="Extremely beneficial" ~ 5 ))) %>%

# replace nuclear acceptance likert scale with numbers
  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                                        . == "Somewhat disagree" ~ 2,
                                                                        . == "Neither agree nor disagree" ~3,
                                                                        . == "Somewhat agree" ~ 4,
                                                                        . == "Strongly agree" ~ 5))) %>%

# code likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_I","K_H","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE", "DEV", "PROSPER", "RELY"))), funs(case_when(. == "Strongly disagree" ~ 1, 
               . == "Somewhat disagree" ~ 2,
               . == "Neither agree nor disagree" ~3,
               . == "Somewhat agree" ~ 4,
               . == "Strongly agree" ~ 5))) %>%

# reverse code for likert scale for variables for Kahan scale into numbers
mutate_at(vars(starts_with (c("K_S","K_E"))), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                               . == "Somewhat disagree" ~ 4,
                                                               . == "Neither agree nor disagree" ~3,
                                                               . == "Somewhat agree" ~ 2,
                                                               . == "Strongly agree" ~ 1))) %>%

# code eco-pol scale variables into numbers
  mutate_at(vars(SYSTEMDEMO,SYSTEMRELIGION,SYSTEMTECHNO,SYSTEMTOTAL,WEALTHLIM,MECHANISATION,DECISIONDECEN,INDUSTRYSMALL,ECONOMYLOCAL,ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(. == "Strongly disagree" ~ 1, 
                        . == "Somewhat disagree" ~ 2,
                        . == "Neither agree nor disagree" ~3,
                        . == "Somewhat agree" ~ 4,
                        . == "Strongly agree" ~ 5))) %>%

# reverse code eco-pol scale variables into numbers 
 mutate_at(vars(DECISIONCEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                                                                         . == "Somewhat disagree" ~ 4,
                                                                                                         . == "Neither agree nor disagree" ~3,
                                                                                                         . == "Somewhat agree" ~ 2,
                                                                                                         . == "Strongly agree" ~ 1)))
```

```{r}
#scatter plot of Kahan scale scores around the median scores on Individualism and Hierarchy scales.

Kscalescores %>%
 ggplot(aes(Individualism_score, Hierarchy_score))+
  geom_count(aes(color = ..n.., size = ..n..))+
  guides(color = 'legend')+
  geom_hline(yintercept=2, colour="black", lwd=1)+
  geom_vline(xintercept=3, colour="black", lwd=1)+
  labs(x = " Communitarianism to Individualism", y = "Egalitarianism to Hierarchy")
```

```{r, echo=FALSE}

# checking assumptions before doing a factor analysis

# running Bartlett's test of sphericity on our scale

#ncol(ecopolall) # 24 variables in total 
#nrow(ecopolall) # 443

ecopolall_cor <- cor(ecopolall)

# conducting Bartlett's test of sphericity to check the assumption that the variables are correlated in the population
#ecopolall_bartlett <- cortest.bartlett(ecopolall_cor, n = nrow(ecopolall)) # p-value = 0

# Kaiser-Meyer-Olkin measure

#KMO(ecopolall) # above 0.7 ie MSA= 0.78 , the sampling adequacy was acceptable (KMO= 0.78) and the Bartlett's test of sphericity demonstrated that the correlations between the items were large enough for FA

```

```{r, echo=FALSE}
# checking normality

#longecopol <-ecopolall %>% 
  #gather(key = "variable", value = "score") %>% 
 # na.omit()

#ggplot(longecopol, aes(x = score, y = variable)) + 
  #geom_boxplot() # Q1 how do I deal with outliers here. Is this a problem ?

# Apply Shapiro-Wilk test to all columns
#shapiro_results <- apply(ecopolall, 2, shapiro.test)

# Extract p-values from test results
#p_values <- sapply(shapiro_results, function(x) x$p.value)

# Identify columns with non-normal distributions
#non_normal_columns <- names(p_values[p_values < 0.05])

# data is not normally distributed 
```

```{r}
##EXTRA :

  # nuclear 1 contains only those variables that were relevant in the EFA
Nuclear1 <- codedmodule2 %>%
dplyr::select("Risky_Nuclear", "HEALTHNUCLEAR", "POLLUTENUCLEAR", "BEAUTYNUCLEAR", "DISPLACENUCLEAR", "DEVNUCLEAR" , "PROSPERNUCLEAR", "NPRIDENUCLEAR", "PRIDENUCLEAR", "JOBSNUCLEAR", "RELYNUCLEAR") %>%
  na.omit()

nuclear_alpha1<- psych::alpha(Nuclear1, check.keys = TRUE)

summary(nuclear_alpha1)

#creating a condensed scale for the characteristics of the technology across two factors as identified with EFA - negative characteristics and positive characteristics.

Ncharac_scores<- Nuclear1 %>%
  rowwise()%>%
  na.omit()%>%
  dplyr::mutate(Negative_score = mean(c_across(HEALTHNUCLEAR:DISPLACENUCLEAR)))%>%
  dplyr::mutate(Positive_score = mean(c_across(DEVNUCLEAR:RELYNUCLEAR)))%>%
  dplyr::select(!starts_with(c("HEALTHNUCLEAR", "POLLUTENUCLEAR", "BEAUTYNUCLEAR", "DISPLACENUCLEAR", "DEVNUCLEAR" , "PROSPERNUCLEAR", "NPRIDENUCLEAR", "PRIDENUCLEAR", "JOBSNUCLEAR", "RELYNUCLEAR")))

Ncharac_lm <- lm(Risky_Nuclear ~ Negative_score + Positive_score , data = Ncharac_scores)
summary(Ncharac_lm )

kandecopol <- codedmodule2 %>%
  dplyr::select("Risky_Nuclear", "K_SHARM", "K_SLIMCHOI", "K_SPROTECT", "K_HEQUAL", "K_ERADEQ1",  "K_EWEALTH",  "K_ERADEQ2","State","HEALTHNUCLEAR", "POLLUTENUCLEAR", "BEAUTYNUCLEAR", "DISPLACENUCLEAR", "DEVNUCLEAR" , "PROSPERNUCLEAR", "NPRIDENUCLEAR", "PRIDENUCLEAR", "JOBSNUCLEAR", "RELYNUCLEAR") %>%
   rowwise()%>%
  na.omit()%>%
  dplyr::mutate(Individualism_score = mean(c_across(K_SHARM:K_SPROTECT)))%>%
  dplyr::mutate(Hierarchy_score = mean(c_across(K_HEQUAL:K_ERADEQ2)))%>%
  dplyr::mutate(Negative_score = mean(c_across(HEALTHNUCLEAR:DISPLACENUCLEAR)))%>%
  dplyr::mutate(Positive_score = mean(c_across(DEVNUCLEAR:RELYNUCLEAR)))%>%
  dplyr::select(!starts_with(c("HEALTHNUCLEAR", "POLLUTENUCLEAR", "BEAUTYNUCLEAR", "DISPLACENUCLEAR", "DEVNUCLEAR" , "PROSPERNUCLEAR", "NPRIDENUCLEAR", "PRIDENUCLEAR", "JOBSNUCLEAR", "RELYNUCLEAR", "K_I","K_S", "K_H", "K_E")))

```

```{r}

# CFA on the reduced ecopol value scale to check whether our reduced dimensions are good fit for the scale.

ecopolall

ecopolall_fas <- '
  Pdevelop =~ HEALTHNUCLEAR + BEAUTYNUCLEAR + POLLUTENUCLEAR
  Ndevelop =~ PRIDENUCLEAR + NPRIDENUCLEAR + PROSPERNUCLEAR
  Pdevelop ~~ Ndevelop 
'

# Run CFA with standardization all method - gives standardized loadings 
# The factors are assumed to be correlated

ecopolall_cfa <- cfa(ecopolall_fas, data = ecopolall, std.lv = TRUE)

# Print the summary of the CFA results, including fit measures
summary(ecopolall_cfa, fit.measure= TRUE, standardized = TRUE)

# RMSEA - between 0.05 and 0.08 (reasonable fit), less than 0.05 close fit and greater than 0.10 is poor fit 
# CFI - greater than 0.90 or 0.95 indicates good fit
#TFI - CFI>TFI >0.90 - indicates good fit

# cross validate with larger sample

# talk to terre about the two options - how much do I need to worry about CLI

```

### 2023-09-20 module2/factor analysis/module2PCAs.Rmd
lot of changes because I wasn't opening the project file.

@@
 ---
-title: "PCAs"
-output: word_document
-
+title: "Cronchbach's alpha and FAs on scales"
+output:
+  pdf_document:
+    toc: yes
+    toc_depth: 2
+    keep_tex: yes
+  header-includes:
+  - \usepackage{dcolumn}
+  - \usepackage{array}
+  keep_md: yes
 ---
@@
   knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-
+suppressPackageStartupMessages(library(lavaan))
 suppressPackageStartupMessages(library(tidyverse))
 suppressPackageStartupMessages(library(readxl))
-
 suppressPackageStartupMessages(library(tsibble))
@@
 suppressPackageStartupMessages(library(DT))
-
 suppressPackageStartupMessages(library(knitr))
@@
 # reverse code for likert scale for variables for Kahan scale into numbers
-mutate_at(vars(starts_with (c("K_S","K_E"))), funs(case_when(. == "Strongly disagree" ~ 1, 
-                                                               . == "Somewhat disagree" ~ 2,
+mutate_at(vars(starts_with (c("K_S","K_E"))), funs(case_when(. == "Strongly disagree" ~ 5, 
+                                                               . == "Somewhat disagree" ~ 4,
                                                                . == "Neither agree nor disagree" ~3,
-                                                               . == "Somewhat agree" ~ 4,
-                                                               . == "Strongly agree" ~ 5))) %>%
+                                                               . == "Somewhat agree" ~ 2,
+                                                               . == "Strongly agree" ~ 1))) %>%
 
 # code eco-pol scale variables into numbers
-  mutate_at(vars(SYSTEMDEMO,SYSTEMRELIGION,SYSTEMTECHNO,SYSTEMTOTAL,WEALTHLIM,MECHANISATION,DECISIONDECEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG), funs(case_when(.
+  mutate_at(vars(SYSTEMDEMO,SYSTEMRELIGION,SYSTEMTECHNO,SYSTEMTOTAL,WEALTHLIM,MECHANISATION,DECISIONDECEN,INDUSTRYSMALL,ECONOMYLOCAL,ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(.
 == "Strongly disagree" ~ 1,
@@
 # reverse code eco-pol scale variables into numbers 
- mutate_at(vars(DECISIONCEN, INDUSTRYSMALL, ECONOMYLOCAL, ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(. == "Strongly disagree" ~ 1, 
-                                                                                                         . == "Somewhat disagree" ~ 2,
+ mutate_at(vars(DECISIONCEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG), funs(case_when(. == "Strongly disagree" ~ 5, 
+                                                                                                         . == "Somewhat disagree" ~ 4,
                                                                                                          . == "Neither agree nor disagree" ~3,
-                                                                                                         . == "Somewhat agree" ~ 4,
-                                                                                                         . == "Strongly agree" ~ 5)))
+                                                                                                         . == "Somewhat agree" ~ 2,
+                                                                                                         . == "Strongly agree" ~ 1)))
 ```
+\newpage
+
+# Kahan et al (2007) scale
+
+## Cronbach's alpha test on the Kahan et al (2007) scale
 
@@
 - **K_IPRIVACY**	The government should stop telling people how to live their lives.
+- **K_IPROTECT**	It’s not the government’s business to try to protect people from themselves.
 - **K_SHARM**	    Sometimes the government needs to make laws that keep people from hurting themselves.
-- **K_IPROTECT**	It’s not the government’s business to try to protect people from themselves.
 - **K_SLIMCHOI**	The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.
@@
 
-Cronbach's alpha test on the Kahan et al (2007) scale
+KahanI weak alpha = 0.29, KahanS strong alpha = 0.71
+Hierarchy -Egalitarianism strong alpha = 0.71
+reasons for this could be that the individualism items are not well adapted to the Indian population 
+final items alpha =  0.75
 
@@
 
-#cronbach alpha
+#cronbach's alpha for the entire Kahan scale
+
+Kahan <- codedmodule2 %>%
+  dplyr::select(starts_with(c("K_S", "K_I", "K_H", "K_E")))%>%
+  na.omit()
+
+Kahan.alpha <- psych::alpha(Kahan, check.keys = TRUE)
+
+#summary(Kahan.alpha)
+
+#cronbach's alpha for Individualism - Communitarinism scale
+
+KahanSI <- codedmodule2 %>%
+  dplyr::select(starts_with(c("K_S", "K_I")))%>%
+  na.omit()
+
+KahanSI.alpha <- psych::alpha(KahanSI, check.keys = TRUE) #Alpha = 0.49
+
+#summary(KahanSI.alpha)
 
 KahanS <- codedmodule2 %>%
-  dplyr::select(starts_with(c("K_S", "K_I")))%>%
+  dplyr::select(starts_with(c("K_S")))%>%
   na.omit()
@@
 
-#K_S items produce a strong alpha but not K_I
-
-KahanI.alpha <- psych::alpha(KahanI)
+KahanI.alpha <- psych::alpha(KahanI, check.keys = TRUE)
 
@@
 
-KahanE <- codedmodule2 %>%
+# KahanI weak alpha = 0.29, KahanS strong alpha = 0.71
+# reasons for this could be that the individualism items are not well adapted to the Indian population
+
+KahanHE <- codedmodule2 %>%
   dplyr::select(starts_with(c("K_H", "K_E")))%>%
@@
 
-KahanE.alpha <- psych::alpha(KahanE, check.keys = TRUE)
+KahanHE.alpha <- psych::alpha(KahanHE, check.keys = TRUE)
+
+#summary(KahanHE.alpha)
+
+Kahanfas <- codedmodule2 %>%
+  dplyr::select(K_SLIMCHOI, K_SPROTECT, K_SHARM, K_HEQUAL, K_ERADEQ1, K_EWEALTH, K_ERADEQ2)%>%
+  na.omit()
+
+Kahanfas.alpha <- psych::alpha(Kahanfas, check.keys = TRUE)
+
+#summary(Kahanfas.alpha)
+#Alpha 0.75
+
+# Hierarchy -Egalitarianism strong alpha = 0.71
 
@@
 
-Factor Analysis on Kahan et al (2007) scale: 2 factor spaces
+\newpage
 
+# CFA on the Kahan scale
+
+Since this a well used scale with theoretical basis for factor distinctions and there are also previous studies that used the same scale I did CFA not exploratory FA. 
 ```{r, echo=FALSE}
 
-#factor analysis on Kahan scale: 2 factor spaces
+# CFA for Kahan scale. We shouldn't do FA here since this a well used scale with theoretical basis for factor distinctions and there are also previous studies that used the same scale
+
 Kahan <- codedmodule2 %>%
@@
 
-Kahan.fa <- fa(Kahan, nfactors=2, scores=TRUE, rotate="varimax", fm="pa")
-#print.psych(Kahan.fa, cut = 0.3, sort = TRUE)
-#fa.diagram(Kahan.fa)
+Kahan_fas <- '
+  KahanS =~ K_SHARM + K_SLIMCHOI + K_SPROTECT 
+  KahanH =~ K_ERADEQ1 + K_EWEALTH + K_ERADEQ2
+'
 
-loadingskahan <- unclass(Kahan.fa$loadings)
+# Run CFA with standardization all method - gives standardized loadings 
+# The factors are assumed to be correlated
 
-loadingstablekahan <- cbind(loadingskahan)
+Kahan_cfa <- cfa(Kahan_fas, data = Kahan, std.lv = TRUE)
 
-twofakahan <- as_tibble(loadingstablekahan) %>%
-add_column("Items" = c("The government interferes far too much in our everyday lives", 
-"The government should stop telling people how to live their lives", 
-"Sometimes the government needs to make laws that keep people from hurting themselves" , 
-"It’s not the government’s business to try to protect people from themselves", 
-"The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society", 
-"The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals", 
-"We have gone too far in pushing equal rights in this country",
-"Nowadays it seems like there is just as much discrimination against upper castes as there is against Dalits",
-"Discrimination against minorities is still a very serious problem in our society", 
-"We need to dramatically reduce inequalities between the rich and the poor",
-"Our society would be better off if the distribution of wealth was more equal",
-"We need to dramatically reduce inequalities between men and women")) %>%
-dplyr::select("Items",  PA1, PA2) %>%
-  arrange(desc(PA1))
+# Print the summary of the CFA results, including fit measures
+summary(Kahan_cfa, fit.measure= TRUE, standardized = TRUE)
 
-knitr::kable(twofakahan, digits = 2)
+# RMSEA - between 0.05 and 0.08 (reasonable fit), less than 0.05 close fit and greater than 0.10 is poor fit 
+# CFI - greater than 0.90 or 0.95 indicates good fit
+#TFI - CFI>TFI >0.90 - indicates good fit
 
-VarexplK <- unclass(Kahan.fa$Vaccounted)
+# after having removed a few variables that had very low loading, the model is now a good fit, we have two latent variables - Hierarchy- egalitarian and Communitarian.
+Again we see that individualistic variables just don't fit here.
 
-knitr::kable(VarexplK, digits = 2)
+# creating table of factor scores
+
+Kahan_scores <- predict(Kahan_cfa, newdata = Kahan)
+
+Kahan_Kscores <- cbind(Kahan, Kahan_scores)
+
 ```
+\newpage
 
-Factor Analysis on Kahan et al (2007) scale: 4 factor spaces
+# Eco-pol value scale
 
-```{r, echo=FALSE}
-#factor analysis on Kahan scale: 4 factor spaces 
-Kahan <- codedmodule2 %>%
-  dplyr::select(starts_with(c("K_")))%>%
-  na.omit()
-
-fourKahan.fa <- fa(Kahan, nfactors=4, scores=TRUE, rotate="varimax", fm="pa")
-#print.psych(Kahan.fa, cut = 0.3, sort = TRUE)
-#fa.diagram(Kahan.fa)
-
-fourloadingskahan <- unclass(fourKahan.fa$loadings)
-
-fourloadingstablekahan <- cbind(fourloadingskahan)
-
-fourfakahan <- as_tibble(fourloadingstablekahan) %>%
-add_column("Items" = c("The government interferes far too much in our everyday lives", 
-"The government should stop telling people how to live their lives", 
-"Sometimes the government needs to make laws that keep people from hurting themselves" , 
-"It’s not the government’s business to try to protect people from themselves", 
-"The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society", 
-"The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals", 
-"We have gone too far in pushing equal rights in this country",
-"Nowadays it seems like there is just as much discrimination against upper castes as there is against Dalits",
-"Discrimination against minorities is still a very serious problem in our society", 
-"We need to dramatically reduce inequalities between the rich and the poor",
-"Our society would be better off if the distribution of wealth was more equal",
-"We need to dramatically reduce inequalities between men and women")) %>%
-dplyr::select("Items",  PA1, PA2, PA3, PA4)%>%
-  arrange(desc(PA1))
-
-knitr::kable(fourfakahan, digits= 2)
-
-VarexplK <- unclass(fourKahan.fa$Vaccounted)
-
-knitr::kable(VarexplK, digits = 2)
-```
-
-**The economic -political values of the perceiver scale**
+**Scale 1 : The economic -political values of the perceiver**
 
@@
 
-Cronbach's alpha test on the economic -political values of the perceiver
+## Cronbach's Alpha Test on Scale 1: Economic -Political Values of the Perceiver
 
@@
  dplyr::select(starts_with(c("SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
-  rowwise()%>%
   na.omit()#%>%
@@
 
-psych::alpha(ecopolscalescores, check.keys = TRUE)
+ecopol_alpha <- psych::alpha(ecopolscalescores, check.keys = TRUE)
+
+summary(ecopol_alpha)
+
+# Alpha for eco-pol values scale is good at 0.76- the scale has good inner consistency.
 
@@
 
-Factor Analysis on the economic and political values scale: 2 factor spaces
+\newpage
 
-```{r, echo=FALSE}
+**Scale 2 : Economic and Political characteristics of the energy technology scale -  Nuclear energy**
 
-#factor analysis with 2, 4 and 6 factor spaces
+- **DISPLACENUCLER** Nuclear energy is leading to displacement of people from their land
+- **POLLUTENUCLEAR** Nuclear energy increases pollution of air/water/land
+- **HEALTHNUCLEAR**	 Nuclear energy poses a great risk to the health of people living around it
+- **JOBSNUCLEAR**	   Nuclear energy will bring jobs to the local community
+- **BEAUTYNUCLEAR**	 Nuclear energy spoils the natural beauty of the landscape
+- **PRIDENUCLEAR**	 I would be proud if my community used nuclear energy
+- **NPRIDENUCLEAR**	 Nuclear energy is a mark of pride for our nation
+- **DEVNUCLEAR**	   Nuclear energy pushes forward the country's development
+- **PROSPERNUCLEAR** Nuclear energy brings economic prosperity to the surrounding regions
+- **RELYNUCLEAR**	   I don't like the idea that I have to rely on the government for electricity from nuclear energy
 
-ecopolscale.fa <- fa(ecopolscalescores, nfactors=2, scores=TRUE, rotate="varimax", fm="pa")
-#print.psych(ecopolscale.fa, cut = 0.3, sort = TRUE)
-#fa.diagram(ecopolscale.fa)
-
-loadingsecopol <- unclass(ecopolscale.fa$loadings)
-
-loadingstableecopol <- cbind(loadingsecopol)
-
-twofaecopol <- as_tibble(loadingstableecopol) %>%
-add_column("Items" = c("Local politicians shouldn't have to ask permission from the central government to implement policies",
- "Laws and policies would be implemented more smoothly if more power lay with the central government",
-"It is good to have a strong leader who does not have to bother with elections", 
- "Experts, not the government, should make decisions according to what they think is best for the country" , 
-"It is very important to have a democratic political system because it ensures that no individual leader has too much power" , 
-"There should be a system governed by religious law" , 
-"Large corporations are destroying the local industries in India and benefiting only a handful of people" , 
-"Large scale industries are required for the development of the country that will benefit everyone" , 
-"India would be better off if foreign companies didn't come to here" , 
-"Foreign companies have led to a range of benefits for the Indian people and society", 
-"Economic growth and creating jobs should be prioritized over environmental protection" , 
-"Polluting industries that spoil the environment should be shut down even if it costs people their jobs", 
-"All businesses and industries should be owned privately", 
-"The government should own most large businesses and industries", 
-"Regardless of ownership, the government should pass strong regulations and implement them", 
-"There is too much red-tape and the government should not interfere with businesses and industries" , 
-"A limit should be put to how much wealth a person can amass",
- "Rapid mechanization of work is taking away jobs from workers in this country"))%>%
-dplyr::select("Items",PA1, PA2)%>%
-arrange(desc(PA1))
-
-knitr::kable(twofaecopol, digits= 2)
-
-Varexplecopol <- unclass(ecopolscale.fa$Vaccounted)
-
-knitr::kable(Varexplecopol, digits = 2)
-
-```
-
-Factor Analysis on the economic and political values scale: 4 factor spaces
-
-```{r, echo=FALSE}
-#factor analysis with 4 factor spaces
-
-ecopolscale4.fa <- fa(ecopolscalescores, nfactors=4, scores=TRUE, rotate="varimax", fm="pa")
-#print.psych(ecopolscale.fa, cut = 0.3, sort = TRUE)
-#fa.diagram(ecopolscale.fa)
-
-loadingsecopol4 <- unclass(ecopolscale4.fa$loadings)
-
-loadingstableecopol4 <- cbind(loadingsecopol4)
-
-faecopol4 <- as_tibble(loadingstableecopol4) %>%
-add_column("Items" = c("Local politicians shouldn't have to ask permission from the central government to implement policies",
- "Laws and policies would be implemented more smoothly if more power lay with the central government",
-"It is good to have a strong leader who does not have to bother with elections", 
- "Experts, not the government, should make decisions according to what they think is best for the country" , 
-"It is very important to have a democratic political system because it ensures that no individual leader has too much power" , 
-"There should be a system governed by religious law" , 
-"Large corporations are destroying the local industries in India and benefiting only a handful of people" , 
-"Large scale industries are required for the development of the country that will benefit everyone" , 
-"India would be better off if foreign companies didn't come to here" , 
-"Foreign companies have led to a range of benefits for the Indian people and society", 
-"Economic growth and creating jobs should be prioritized over environmental protection" , 
-"Polluting industries that spoil the environment should be shut down even if it costs people their jobs", 
-"All businesses and industries should be owned privately", 
-"The government should own most large businesses and industries", 
-"Regardless of ownership, the government should pass strong regulations and implement them", 
-"There is too much red-tape and the government should not interfere with businesses and industries" , 
-"A limit should be put to how much wealth a person can amass",
- "Rapid mechanization of work is taking away jobs from workers in this country"))%>%
-dplyr::select("Items",PA1, PA2, PA3, PA4) %>%
-  arrange(desc(PA1))
-
-knitr::kable(faecopol4, digits= 2)
-
-Varexplecopol4 <- unclass(ecopolscale4.fa$Vaccounted)
-
-knitr::kable(Varexplecopol4, digits = 2)
-
-```
-
-Factor Analysis on the economic and political values scale: 6 factor spaces
-
-```{r, echo=FALSE}
-
-ecopolscale6.fa <- fa(ecopolscalescores, nfactors=6, scores=TRUE, rotate="varimax", fm="pa")
-#print.psych(ecopolscale.fa, cut = 0.3, sort = TRUE)
-#fa.diagram(ecopolscale.fa)
-
-loadingsecopol6 <- unclass(ecopolscale6.fa$loadings)
-
-loadingstableecopol6 <- cbind(loadingsecopol6)
-
-faecopol6 <- as_tibble(loadingstableecopol6) %>%
-add_column("Items" = c("Local politicians shouldn't have to ask permission from the central government to implement policies",
- "Laws and policies would be implemented more smoothly if more power lay with the central government",
-"It is good to have a strong leader who does not have to bother with elections", 
- "Experts, not the government, should make decisions according to what they think is best for the country" , 
-"It is very important to have a democratic political system because it ensures that no individual leader has too much power" , 
-"There should be a system governed by religious law" , 
-"Large corporations are destroying the local industries in India and benefiting only a handful of people" , 
-"Large scale industries are required for the development of the country that will benefit everyone" , 
-"India would be better off if foreign companies didn't come to here" , 
-"Foreign companies have led to a range of benefits for the Indian people and society", 
-"Economic growth and creating jobs should be prioritized over environmental protection" , 
-"Polluting industries that spoil the environment should be shut down even if it costs people their jobs", 
-"All businesses and industries should be owned privately", 
-"The government should own most large businesses and industries", 
-"Regardless of ownership, the government should pass strong regulations and implement them", 
-"There is too much red-tape and the government should not interfere with businesses and industries" , 
-"A limit should be put to how much wealth a person can amass",
- "Rapid mechanization of work is taking away jobs from workers in this country"))%>%
-dplyr::select("Items",PA1, PA2, PA3, PA4, PA5, PA6) %>%
-  arrange(desc(PA1))
-
-knitr::kable(faecopol6, digits= 2)
-
-Varexplecopol6 <- unclass(ecopolscale6.fa$Vaccounted)
-
-knitr::kable(Varexplecopol6, digits = 2)
-```
-
-**Economic and Political characteristics of the energy technology scale -  Solar Energy and rooftop solar energy**
-
-- **DISPLACESOLAR**	 Solar energy is leading to displacement of people from their land
-- **POLLUTESOLAR**	 Solar energy increases pollution of air/water/land
-- **HEALTHSOLAR**	   Solar energy poses a great risk to the health of people living around it
-- **JOBSSOLAR**	     Solar energy will bring jobs to the local community
-- **BEAUTYSOLAR**	   Solar energy spoils the natural beauty of the landscape
-- **PRIDESOLAR**	   I would be proud if my community used solar energy
-- **NPRIDESOLAR**	   Solar energy is a mark of pride for our nation
-- **DEVSOLAR**	     Solar energy pushes forward the country's development
-- **PROSPERSOLAR**	 Solar energy brings economic prosperity to the surrounding regions
-- **RELYSOLAR**	     I don't like the idea that I have to rely on the government for electricity from (large scale) solar energy
-
-Cronbach's alpha test on the Eco-Pol characteristics of the technology -  Solar Energy
+## Cronbach's alpha test on Scale 2 : Eco-Pol Characteristics of the Technology -  Nuclear Energy
 
@@
 
-Solar <- codedmodule2 %>%
-dplyr::select("DISPLACESOLAR":"RELYSOLAR") %>%
-dplyr::rename("Solar energy is leading to displacement of people from their land" = "DISPLACESOLAR") %>%
-dplyr::rename("Solar energy increases pollution of air/water/land" = "POLLUTESOLAR")%>%
-dplyr::rename("Solar energy poses a great risk to the health of people living around it" = "HEALTHSOLAR")%>%
-dplyr::rename("Solar energy will bring jobs to the local community" = "JOBSSOLAR")%>%
-dplyr::rename("Solar energy spoils the natural beauty of the landscape" = "BEAUTYSOLAR")%>%
-dplyr::rename("I would be proud if my community used solar energy" = "PRIDESOLAR")%>%
-dplyr::rename("Solar energy is a mark of pride for our nation" = "NPRIDESOLAR") %>%
-dplyr::rename("Solar energy pushes forward the country's development" = "DEVSOLAR")%>%
-dplyr::rename("Solar energy brings economic prosperity to the surrounding regions" = "PROSPERSOLAR")%>%
-dplyr::rename("I don't like the idea that I have to rely on the government for electricity from (large scale solar energy)" = "RELYSOLAR")%>%
+Nuclear <- codedmodule2 %>%
+dplyr::select("DISPLACENUCLEAR":"RELYNUCLEAR") %>%
+dplyr::rename("Nuclear energy is leading to displacement of people from their land" = "DISPLACENUCLEAR") %>%
+dplyr::rename("Nuclear energy increases pollution of air/water/land" = "POLLUTENUCLEAR")%>%
+dplyr::rename("Nuclear energy poses a great risk to the health of people living around it" = "HEALTHNUCLEAR")%>%
+dplyr::rename("Nuclear energy will bring jobs to the local community" = "JOBSNUCLEAR")%>%
+dplyr::rename("Nuclear energy spoils the natural beauty of the landscape" = "BEAUTYNUCLEAR")%>%
+dplyr::rename("I would be proud if my community used solar nuclear" = "PRIDENUCLEAR")%>%
+dplyr::rename("Nuclear energy is a mark of pride for our nation" = "NPRIDENUCLEAR") %>%
+dplyr::rename("Nuclear energy pushes forward the country's development" = "DEVNUCLEAR")%>%
+dplyr::rename("Nuclear energy brings economic prosperity to the surrounding regions" = "PROSPERNUCLEAR")%>%
+dplyr::rename("I don't like the idea that I have to rely on the government for electricity from (large scale nuclear energy)" = "RELYNUCLEAR")%>%
   na.omit()
 
-psych::alpha(Solar, check.keys = TRUE)
+nuclear_alpha <- psych::alpha(Nuclear, check.keys = TRUE)
+
+summary(nuclear_alpha)
+
+# std.alpha 0.68 - not very good
 
@@
 
-Factor Analysis on the eco- pol characteristics of the technology, Solar Energy : 2 factor spaces
+## Cronbach's Alpha Test on the Combined Scale.
 
-```{r, echo=FALSE}
+```{r, echo = FALSE}
 
-#factor analysis with 2 factor spaces
+# we combined both the scales, since we are interested in eco-pol factors at large - values of the perceiver and the values perceived in an energy technology.Here I have removed the variables on systems of government.
 
-solar.fa <- fa(Solar, nfactors=2, scores=TRUE, rotate="varimax", fm="pa")
-#print.psych(solar.fa, cut = 0.4, sort = TRUE)
-#fa.diagram(solar.fa)
+ecopolall <- codedmodule2 %>%
+        dplyr::select("WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR", "SYSTEMDEMO")%>%
+  na.omit()#%>%
+  #dplyr::mutate(Pro_decentralisation = mean(c_across("DECISIONDECEN":"DECISIONCEN")))%>%
+   #dplyr::mutate(Pro_largescale = mean(c_across("INDUSTRYLARGE":"INDUSTRYSMALL")))%>%
+  #dplyr::select(!c("DECISIONDECEN","DECISIONCEN", "INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL", "ECONOMYLOCAL","ENVOVERDEV",     "DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG"))
 
-loadingssolar <- unclass(solar.fa$loadings)
+ecopolall_alpha <- psych::alpha(ecopolall, check.keys = TRUE)
 
-loadingstablesolar <- cbind(loadingssolar)
+summary(ecopolall_alpha)
 
-fasolar <- as_tibble(loadingstablesolar) %>%
-add_column("Items" = c("Solar energy is leading to displacement of people from their land",
-"Solar energy increases pollution of air/water/land",
-"Solar energy poses a great risk to the health of people living around it",
-"Solar energy will bring jobs to the local community",
-"Solar energy spoils the natural beauty of the landscape",
-"I would be proud if my community used solar energy",
-"Solar energy is a mark of pride for our nation",
-"Solar energy pushes forward the country's development",
-"Solar energy brings economic prosperity to the surrounding regions",
-"I don't like the idea that I have to rely on the government for electricity from (large scale) solar energy"))%>%
-dplyr::select("Items",PA1, PA2)%>%
-arrange(desc(PA1))
-
-knitr::kable(fasolar, digits= 2)
-
-Varexplsolar <- unclass(solar.fa$Vaccounted)
-
-knitr::kable(Varexplsolar, digits = 2)
-```
-
-Factor Analysis on the eco- pol characteristics of the technology, Solar Energy : 4 factor spaces
-
-```{r, echo=FALSE}
-
-#factor analysis with  4 a factor spaces
-
-solar4.fa <- fa(Solar, nfactors=4, scores=TRUE, rotate="varimax", fm="pa")
-#print.psych(solar.fa, cut = 0.4, sort = TRUE)
-#fa.diagram(solar.fa)
-
-loadingssolar4 <- unclass(solar4.fa$loadings)
-
-loadingstablesolar4 <- cbind(loadingssolar4)
-
-fasolar4 <- as_tibble(loadingstablesolar4) %>%
-add_column("Items" = c("Solar energy is leading to displacement of people from their land",
-"Solar energy increases pollution of air/water/land",
-"Solar energy poses a great risk to the health of people living around it",
-"Solar energy will bring jobs to the local community",
-"Solar energy spoils the natural beauty of the landscape",
-"I would be proud if my community used solar energy",
-"Solar energy is a mark of pride for our nation",
-"Solar energy pushes forward the country's development",
-"Solar energy brings economic prosperity to the surrounding regions",
-"I don't like the idea that I have to rely on the government for electricity from (large scale) solar energy"))%>%
-dplyr::select("Items",PA1, PA2, PA3, PA4) %>%
-  arrange(desc(PA1))
-
-knitr::kable(fasolar4, digits= 2)
-
-Varexplsolar4 <- unclass(solar4.fa$Vaccounted)
-
-knitr::kable(Varexplsolar4, digits = 2)
-```
-
-```{r, echo=FALSE}
-ROOFS<- codedmodule2 %>%
- dplyr::select("DISPLACEROOFS":"RELYROOFS")
-
-psych::alpha(ROOFS, check.keys = TRUE)
+# when we combine both the scales the alpha is high at 0.785 (almost 0.8)
 
@@
 
-```{r, echo=FALSE}
-#factor analysis with 2, 4 and 6 factor spaces
+\newpage
 
-roofs.fa <- fa(ROOFS, nfactors=2, scores=TRUE, rotate="varimax", fm="pa")
-#print.psych(roofs.fa, cut = 0.4, sort = TRUE)
-#fa.diagram(roofs.fa)
+# FA on All Ecopol Variables (except systems of governance)
 
-loadingsroofs <- unclass(roofs.fa$loadings)
+## Two factor solution : MR1 people centered development and MR2 nationalist development
 
-loadingstableroofs <- cbind(loadingsroofs)
+**MR1 People Centered Development: Pdevelop**
 
-faroofs <- as_tibble(loadingstableroofs) %>%
-add_column("Items" = c("Rooftop solar is leading to displacement of people from their land",
-"Rooftop solar increases pollution of air/water/land", 
-"Rooftop solar poses a great risk to the health of people living around it",
-"Rooftop solar will bring jobs to the local community",
-"Rooftop solar spoils the natural beauty of the landscape" , 
-"I would be proud if my community used Rooftop solar" , 
-"Rooftop solar is a mark of pride for our nation", 
-"Rooftop solar pushes forward the country's development" , 
-"Rooftop solar brings economic prosperity to the surrounding regions" , 
-"I don't like the idea that I have to rely on the government for electricity from (large scale) Rooftop solar")) %>%
-dplyr::select("Items",  PA1, PA2)%>%
-  arrange(desc(PA1))
+HEALTHNUCLEAR	-  Nuclear energy poses a great risk to the health of people living around it.
 
-knitr::kable(faroofs, digits = 2)
+BEAUTYNUCLEAR	-  Nuclear energy spoils the natural beauty of the landscape.
 
-Varexplroofs <- unclass(roofs.fa$Vaccounted)
+MECHANISATION	-  Rapid mechanization of work is taking away jobs from workers in this country.
 
-knitr::kable(Varexplroofs, digits = 2)
+INDUSTRYSMALL	-  Large corporations are destroying the local industries in India and benefiting only a handful of people.
+
+DISPLACENUCLEAR- Nuclear energy is leading to displacement of people from their land.
+
+POLLUTENUCLEAR-  Nuclear energy increases pollution of air/water/land.
+
+OWNERREG-        Regardless of ownership, the government should pass strong regulations and implement them.
+
+**MR2 Nationalist Development: Ndevelop**
+
+DEVNUCLEAR	-  Nuclear energy pushes forward the country's development.
+
+PRIDENUCLEAR-  I would be proud if my community used nuclear energy.
+
+NPRIDENUCLEAR- Nuclear energy is a mark of pride for our nation.
+
+PROSPERNUCLEAR-Nuclear energy brings economic prosperity to the surrounding regions.
+
+INDUSTRYLARGE- Large scale industries are required for the development of the country that will benefit everyone.
+
+```{r, echo = FALSE}
+# FA on all ecopol variables except systems of governance
+
+#ecopolall_cor <- cor(ecopolall)
+#PCA24 <- principal(ecopolall, nfactors = 24, rotate = "none") # no rotation to start with.
+
+#print(PCA24)
+
+#PCA24$loadings
+
+#fa.parallel(ecopolall_cor)
+
+#PCA2 <- principal(ecopolall, nfactors = 2, rotate = "none") # no rotation to start with.
+
+#print(PCA2)
+
+#PCA2$loadings
+
+# this suggests 2 factors if we go by FA or 8 by PCA. let's try both and see how they look conceptually
+
+ecopolall2.fa <- fa(ecopolall, nfactors = 2, rotate = "varimax")
+
+print.psych(ecopolall2.fa, cut = 0.50, sort = TRUE)
+
+#fa.diagram(ecopolall2.fa)
+
+#cor(ecopolall)
+
+# So I am going to extract factor scores and bind them to the dataset
+
+ecopolall_scores <- psych::factor.scores(ecopolall, ecopolall2.fa)
+
+# The factor scores will be stored in the scores element of the returned list
+scores1 <- ecopolall_scores$scores
 
 ```
+
+\newpage
+
+# FA on Scale 1 - only eco-pol values of the perceiver scale.
+
+Four Factor Solution -
+
+**MR1 Problems of industrialisation**
+
+MECHANISATION-   Rapid mechanization of work is taking away jobs from workers in this country
+
+OWNERREG-        Regardless of ownership, the government should pass strong regulations and implement them.
+
+WEALTHLIM-	     A limit should be put to how much wealth a person can amass
+
+**MR3 Local Economy And Decision Making**
+
+INDUSTRYSMALL-  Large corporations are destroying the local industries in India and benefiting only a handful of people
+
+ECONOMYLOCAL-   India would be better off if foreign companies didn’t come to here
+
+DECISIONDECEN-  Local politicians shouldn’t have to ask permission from the central government to implement policies
+
+**MR4 Centralised and Large Industry**
+
+DECISIONCEN-   Laws and policies would be implemented more smoothly if more power lay with the central government
+
+ECONOMYGLOBAL- Foreign companies have led to a range of benefits for the Indian people and society
+
+OWNERNOREG- 	 There is too much red-tape and the government should not interfere with businesses and industries
+
+INDUSTRYLARGE- Large scale industries are required for the development of the country that will benefit everyone
+
+**MR2 Development and Business Ownership**
+
+DEVOVERENV-	   Economic growth and creating jobs should be prioritized over environmental protection
+
+OWNERPVT-	     All businesses and industries should be owned privately
+
+OWNERPUB-	     The government should own most large businesses and industries
+
+ENVOVERDEV-	   Polluting industries that spoil the environment should be shut down even if it costs people their jobs
+
+```{r, echo = FALSE}
+
+# below are only eco-pol values of the perceiver scale.
+
+ecopolval <- codedmodule2 %>%
+        dplyr::select("WEALTHLIM","MECHANISATION","INDUSTRYSMALL","ECONOMYGLOBAL", "ENVOVERDEV","OWNERNOREG","OWNERPUB", "OWNERREG", "DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","ECONOMYLOCAL", "DEVOVERENV","OWNERPVT")%>%
+  na.omit()
+
+alpha(ecopolval, check.keys = TRUE) # 0.71
+
+#ncol(ecopolval)  number of cols is 14
+
+#ecopolval_cor <- cor(ecopolval)
+#PCA14 <- principal(ecopolval, nfactors = 14, rotate = "none") # no rotation to start with.
+
+#print(PCA14)
+
+#PCA14$loadings
+
+#fa.parallel(ecopolval_cor)
+
+# based on the PCA and scree plot we have two options : 
+# 1 - we do a factor analysis for 3 factors as suggested by the scree plot 
+# 2 - we do factor analysis for 8 components with eigen values for 8 being above 1
+
+#1 
+ecopolval4.fa <- fa(ecopolval, nfactors = 4, rotate = "varimax")
+
+print.psych(ecopolval4.fa, cut = 0.40, sort = TRUE)
+
+fa.diagram(ecopolval4.fa)
+
+#cor(ecopolval)
+
+# questions for Terre , 2) 4 factors/3 factors/2 factors - variation explained how should i deal with that. 
+# four factor analysis - MR1 - problems of industrialisation MR2 - local economy and decision making MR3 - centralised and large industry MR4- dev/ownership
+```
+
+\newpage
+
+# Factor analysis on Scale 2 -  Eco-Pol characteristics of the technology -  Nuclear Energy
+
+Two Factor Solution - positive versus negative characteristics
+
+**MR1 Negative Characteristics**
+
+HEALTHNUCLEAR	-  Nuclear energy poses a great risk to the health of people living around it.
+
+BEAUTYNUCLEAR	-  Nuclear energy spoils the natural beauty of the landscape.
+
+DISPLACENUCLEAR- Nuclear energy is leading to displacement of people from their land.
+
+POLLUTENUCLEAR-  Nuclear energy increases pollution of air/water/land.
+
+**MR2 Positive Characteristics**
+
+DEVNUCLEAR-     Nuclear energy pushes forward the country's development.
+
+PRIDENUCLEAR-   I would be proud if my community used nuclear energy.
+
+NPRIDENUCLEAR-  Nuclear energy is a mark of pride for our nation.
+
+PROSPERNUCLEAR- Nuclear energy brings economic prosperity to the surrounding regions.
+
+JOBSNUCLEAR-    Nuclear energy will bring jobs to the local community.
+
+RELYNUCLEAR-    I don't like the idea that I have to rely on the government for electricity from nuclear energy.
+
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+
+#alpha test on Eco-pol characteristics of the technology
+
+Nuclear <- codedmodule2 %>%
+dplyr::select("DISPLACENUCLEAR":"RELYNUCLEAR") %>%
+  na.omit()
+
+nuclear_alpha <- psych::alpha(Nuclear, check.keys = TRUE)
+
+summary(nuclear_alpha)
+
+# std.alpha 0.68 - not very good
+
+#ncol(Nuclear)
+
+#Nuclear_cor <- cor(Nuclear)
+#PCA10 <- principal(Nuclear, nfactors = 10, rotate = "none") # no rotation to start with.
+
+#print(PCA10)
+
+#fa.parallel(Nuclear_cor)
+
+Nuclear.fa <- fa(Nuclear, nfactors = 2, rotate = "varimax")
+
+print.psych(Nuclear.fa, cut = 0.40, sort = TRUE)
+
+fa.diagram(Nuclear.fa)
+
+# two options 2 factors or three factors. 2 factors translate to -  positive versus negative characteristics
+
+# So I am going to extract factor scores an add them bind them to the dataset
+
+Nuclear_scores <- psych::factor.scores(Nuclear, Nuclear.fa)
+
+# The factor scores will be stored in the scores element of the returned list
+scores2 <- Nuclear_scores$scores
+
+#binding factor scores to the dataset
+
+Nuclear_with_scores <- cbind(Nuclear, scores2)
+
+```
+\newpage
+
+# Solar - FA 2 factor solution
+
+here I'll make the same chart with Coal as well - 2 factor solution and explore the 4 factor solution. Talk to Terre about the Slovic study and how they did it.
+
+```{r, echo = FALSE}
+
+secopolall <- codedmodule2 %>%
+        dplyr::select("WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACESOLAR",  "POLLUTESOLAR", "HEALTHSOLAR", "JOBSSOLAR", "BEAUTYSOLAR", "PRIDESOLAR", "NPRIDESOLAR", "DEVSOLAR", "PROSPERSOLAR", "RELYSOLAR", "SYSTEMDEMO")%>%
+  na.omit()
+secopolall_alpha <- psych::alpha(secopolall, check.keys = TRUE)
+
+summary(secopolall_alpha) # 0.78
+
+# PCA on all 
+#secopolall_cor <- cor(secopolall)
+#sPCA24 <- principal(secopolall, nfactors = 24, rotate = "none") # no rotation to start with.
+
+#print(sPCA24)
+
+#sPCA24$loadings
+
+#fa.parallel(secopolall_cor)
+
+# this suggests 2 factors if we go by FA or 8 by PCA. let's try both and see how they look conceptually
+
+secopolall2.fa <- fa(secopolall, nfactors = 2, rotate = "varimax")
+
+print.psych(secopolall2.fa, cut = 0.40,  sort = TRUE)
+
+#fa.diagram(secopolall2.fa)
+
+#cor(secopolall)
+
+```
+
+\newpage
+
+# Coal - FA 2 factor solution
+
+```{r, echo = FALSE}
+
+cecopolall <- codedmodule2 %>%
+        dplyr::select("WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACECOAL", "POLLUTECOAL", "HEALTHCOAL", "JOBSCOAL", "BEAUTYCOAL", "PRIDECOAL", "NPRIDECOAL", "DEVCOAL", "PROSPERCOAL", "RELYCOAL", "SYSTEMDEMO")%>%
+  na.omit()
+cecopolall_alpha <- psych::alpha(cecopolall, check.keys = TRUE)
+
+summary(cecopolall_alpha)
+
+# PCA on all 
+#secopolall_cor <- cor(secopolall)
+#sPCA24 <- principal(secopolall, nfactors = 24, rotate = "none") # no rotation to start with.
+
+#print(sPCA24)
+
+#sPCA24$loadings
+
+#fa.parallel(secopolall_cor)
+
+# this suggests 2 factors if we go by FA or 8 by PCA. let's try both and see how they look conceptually
+
+cecopolall2.fa <- fa(cecopolall, nfactors = 2, rotate = "varimax")
+
+print.psych(cecopolall2.fa, cut = 0.40,  sort = TRUE)
+
+#fa.diagram(cecopolall2.fa)
+
+#cor(cecopolall)
+
+```
+
+\newpage
+# Appendix1
+
+**Kahan et al (2007) scale**
+
+Individualism - Communitarinism
+
+- **K_IINTRFER**	The government interferes far too much in our everyday lives.
+- **K_IPRIVACY**	The government should stop telling people how to live their lives.
+- **K_IPROTECT**	It’s not the government’s business to try to protect people from themselves.
+- **K_SHARM**	    Sometimes the government needs to make laws that keep people from hurting themselves.
+- **K_SLIMCHOI**	The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.
+- **K_SPROTECT**	The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.
+
+Hierarchy -Egalitarianism
+
+- **K_HEQUAL**	  We have gone too far in pushing equal rights in this country.
+- **K_HREVDIS1**	Nowadays it seems like there is just as much discrimination against upper castes as there is against Dalits.
+- **K_EDISCRIM**	Discrimination against minorities is still a very serious problem in our society.
+- **K_ERADEQ1**	  We need to dramatically reduce inequalities between the rich and the poor.
+- **K_EWEALTH**	  Our society would be better off if the distribution of wealth was more equal.
+- **K_ERADEQ2**	  We need to dramatically reduce inequalities between men and women.
+
+\newpage
+# Appendix2
+
+ **New Eco-pol values scale**
+
+- **DISPLACENUCLEAR**Nuclear energy is leading to displacement of people from their land
+- **BEAUTYNUCLEAR**	 Nuclear energy spoils the natural beauty of the landscape
+- **POLLUTENUCLEAR** Nuclear energy increases pollution of air/water/land
+- **HEALTHNUCLEAR**	 Nuclear energy poses a great risk to the health of people living around it
+- **JOBSNUCLEAR**	   Nuclear energy will bring jobs to the local community
+- **PRIDENUCLEAR**	 I would be proud if my community used nuclear energy
+- **NPRIDENUCLEAR**	 Nuclear energy is a mark of pride for our nation
+- **DEVNUCLEAR**	   Nuclear energy pushes forward the country's development
+- **PROSPERNUCLEAR** Nuclear energy brings economic prosperity to the surrounding regions
+- **RELYNUCLEAR**	   I don't like the idea that I have to rely on the government for electricity from nuclear energy
+
+- **DECISIONDECEN**	 Local politicians shouldn't have to ask permission from the central government to implement policies
+- **DECISIONCEN**	   Laws and policies would be implemented more smoothly if more power lay with the central government.
+- **INDUSTRYLARGE**	 Large scale industries are required for the development of the country that will benefit everyone
+- **ECONOMYLOCAL**	 India would be better off if foreign companies didn't come to here
+- **DEVOVERENV**	   Economic growth and creating jobs should be prioritized over environmental protection
+- **INDUSTRYSMALL**	 Large corporations are destroying the local industries in India and benefiting only a handful of people.
+- **WEALTHLIM**	     A limit should be put to how much wealth a person can amass
+- **ECONOMYGLOBAL**	 Foreign companies have led to a range of benefits for the Indian people and society
+- **OWNERPVT**	     All businesses and industries should be owned privately
+- **OWNERPUB**	     The government should own most large businesses and industries
+- **ENVOVERDEV**	   Polluting industries that spoil the environment should be shut down even if it costs people their jobs
+- **OWNERREG**	     Regardless of ownership, the government should pass strong regulations and implement them
+- **MECHANISATION**	 Rapid mechanization of work is taking away jobs from workers in this country
+- **OWNERNOREG**	   There is too much red-tape and the government should not interfere with businesses and industries

### 2023-09-20 module2/factor analysis/module2PCAs.tex
lot of changes because I wasn't opening the project file.

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\title{Cronchbach's alpha and FAs on scales}
\author{}
\date{\vspace{-2.5em}}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Cronchbach's alpha and FAs on scales},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\begin{document}
\maketitle

{
\setcounter{tocdepth}{2}
\tableofcontents
}
\newpage

\hypertarget{kahan-et-al-2007-scale}{%
\section{Kahan et al (2007) scale}\label{kahan-et-al-2007-scale}}

\hypertarget{cronbachs-alpha-test-on-the-kahan-et-al-2007-scale}{%
\subsection{Cronbach's alpha test on the Kahan et al (2007)
scale}\label{cronbachs-alpha-test-on-the-kahan-et-al-2007-scale}}

\textbf{Kahan et al (2007) scale}

Individualism - Communitarinism

\begin{itemize}
\tightlist
\item
  \textbf{K\_IINTRFER} The government interferes far too much in our
  everyday lives.
\item
  \textbf{K\_IPRIVACY} The government should stop telling people how to
  live their lives.
\item
  \textbf{K\_IPROTECT} It's not the government's business to try to
  protect people from themselves.
\item
  \textbf{K\_SHARM} Sometimes the government needs to make laws that
  keep people from hurting themselves.
\item
  \textbf{K\_SLIMCHOI} The government should put limits on the choices
  individuals can make so they don't get in the way of what's good for
  society.
\item
  \textbf{K\_SPROTECT} The government should do more to advance
  society's goals, even if that means limiting the freedom and choices
  of individuals.
\end{itemize}

Hierarchy -Egalitarianism

\begin{itemize}
\tightlist
\item
  \textbf{K\_HEQUAL} We have gone too far in pushing equal rights in
  this country.
\item
  \textbf{K\_HREVDIS1} Nowadays it seems like there is just as much
  discrimination against upper castes as there is against Dalits.
\item
  \textbf{K\_EDISCRIM} Discrimination against minorities is still a very
  serious problem in our society.
\item
  \textbf{K\_ERADEQ1} We need to dramatically reduce inequalities
  between the rich and the poor.
\item
  \textbf{K\_EWEALTH} Our society would be better off if the
  distribution of wealth was more equal.
\item
  \textbf{K\_ERADEQ2} We need to dramatically reduce inequalities
  between men and women.
\end{itemize}

KahanI weak alpha = 0.29, KahanS strong alpha = 0.71 Hierarchy
-Egalitarianism strong alpha = 0.71 reasons for this could be that the
individualism items are not well adapted to the Indian population final
items alpha = 0.75

\newpage

\hypertarget{cfa-on-the-kahan-scale}{%
\section{CFA on the Kahan scale}\label{cfa-on-the-kahan-scale}}

Since this a well used scale with theoretical basis for factor
distinctions and there are also previous studies that used the same
scale I did CFA not exploratory FA.

\begin{verbatim}
## lavaan 0.6.15 ended normally after 16 iterations
## 
##   Estimator                                         ML
##   Optimization method                           NLMINB
##   Number of model parameters                        13
## 
##   Number of observations                           749
## 
## Model Test User Model:
##                                                       
##   Test statistic                                42.022
##   Degrees of freedom                                 8
##   P-value (Chi-square)                           0.000
## 
## Model Test Baseline Model:
## 
##   Test statistic                              1057.597
##   Degrees of freedom                                15
##   P-value                                        0.000
## 
## User Model versus Baseline Model:
## 
##   Comparative Fit Index (CFI)                    0.967
##   Tucker-Lewis Index (TLI)                       0.939
## 
## Loglikelihood and Information Criteria:
## 
##   Loglikelihood user model (H0)              -6375.464
##   Loglikelihood unrestricted model (H1)      -6354.452
##                                                       
##   Akaike (AIC)                               12776.927
##   Bayesian (BIC)                             12836.971
##   Sample-size adjusted Bayesian (SABIC)      12795.691
## 
## Root Mean Square Error of Approximation:
## 
##   RMSEA                                          0.075
##   90 Percent confidence interval - lower         0.054
##   90 Percent confidence interval - upper         0.099
##   P-value H_0: RMSEA <= 0.050                    0.027
##   P-value H_0: RMSEA >= 0.080                    0.396
## 
## Standardized Root Mean Square Residual:
## 
##   SRMR                                           0.042
## 
## Parameter Estimates:
## 
##   Standard errors                             Standard
##   Information                                 Expected
##   Information saturated (h1) model          Structured
## 
## Latent Variables:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   KahanS =~                                                             
##     K_SHARM           0.726    0.044   16.405    0.000    0.726    0.639
##     K_SLIMCHOI        0.938    0.047   20.057    0.000    0.938    0.787
##     K_SPROTECT        0.714    0.046   15.605    0.000    0.714    0.608
##   KahanH =~                                                             
##     K_ERADEQ1         0.750    0.039   19.198    0.000    0.750    0.748
##     K_EWEALTH         0.642    0.045   14.323    0.000    0.642    0.560
##     K_ERADEQ2         0.782    0.042   18.656    0.000    0.782    0.726
## 
## Covariances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   KahanS ~~                                                             
##     KahanH            0.528    0.040   13.121    0.000    0.528    0.528
## 
## Variances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##    .K_SHARM           0.764    0.053   14.457    0.000    0.764    0.592
##    .K_SLIMCHOI        0.542    0.062    8.700    0.000    0.542    0.381
##    .K_SPROTECT        0.868    0.057   15.293    0.000    0.868    0.630
##    .K_ERADEQ1         0.441    0.042   10.466    0.000    0.441    0.440
##    .K_EWEALTH         0.903    0.055   16.369    0.000    0.903    0.687
##    .K_ERADEQ2         0.548    0.048   11.399    0.000    0.548    0.473
##     KahanS            1.000                               1.000    1.000
##     KahanH            1.000                               1.000    1.000
\end{verbatim}

\newpage

\hypertarget{eco-pol-value-scale}{%
\section{Eco-pol value scale}\label{eco-pol-value-scale}}

\textbf{Scale 1 : The economic -political values of the perceiver}

\begin{itemize}
\tightlist
\item
  \textbf{DECISIONDECEN} Local politicians shouldn't have to ask
  permission from the central government to implement policies
\item
  \textbf{DECISIONCEN} Laws and policies would be implemented more
  smoothly if more power lay with the central government.
\item
  \textbf{SYSTEMTOTAL} It is good to have a strong leader who does not
  have to bother with elections.
\item
  \textbf{SYSTEMTECHNO} Experts, not the government, should make
  decisions according to what they think is best for the country.
\item
  \textbf{SYSTEMDEMO} It is very important to have a democratic
  political system because it ensures that no individual leader has too
  much power.
\item
  \textbf{SYSTEMRELIGION} There should be a system governed by religious
  law.
\item
  \textbf{INDUSTRYSMALL} Large corporations are destroying the local
  industries in India and benefiting only a handful of people.
\item
  \textbf{INDUSTRYLARGE} Large scale industries are required for the
  development of the country that will benefit everyone
\item
  \textbf{ECONOMYLOCAL} India would be better off if foreign companies
  didn't come to here
\item
  \textbf{ECONOMYGLOBAL} Foreign companies have led to a range of
  benefits for the Indian people and society
\item
  \textbf{DEVOVERENV} Economic growth and creating jobs should be
  prioritized over environmental protection
\item
  \textbf{ENVOVERDEV} Polluting industries that spoil the environment
  should be shut down even if it costs people their jobs
\item
  \textbf{OWNERPVT} All businesses and industries should be owned
  privately
\item
  \textbf{OWNERPUB} The government should own most large businesses and
  industries
\item
  \textbf{OWNERREG} Regardless of ownership, the government should pass
  strong regulations and implement them
\item
  \textbf{OWNERNOREG} There is too much red-tape and the government
  should not interfere with businesses and industries
\item
  \textbf{WEALTHLIM} A limit should be put to how much wealth a person
  can amass
\item
  \textbf{MECHANISATION} Rapid mechanization of work is taking away jobs
  from workers in this country
\end{itemize}

\hypertarget{cronbachs-alpha-test-on-scale-1-economic--political-values-of-the-perceiver}{%
\subsection{Cronbach's Alpha Test on Scale 1: Economic -Political Values
of the
Perceiver}\label{cronbachs-alpha-test-on-scale-1-economic--political-values-of-the-perceiver}}

\begin{verbatim}
## 
## Reliability analysis   
##  raw_alpha std.alpha G6(smc) average_r S/N   ase mean   sd median_r
##       0.75      0.76    0.79      0.15 3.2 0.014  3.5 0.56     0.16
\end{verbatim}

\newpage

\textbf{Scale 2 : Economic and Political characteristics of the energy
technology scale - Nuclear energy}

\begin{itemize}
\tightlist
\item
  \textbf{DISPLACENUCLER} Nuclear energy is leading to displacement of
  people from their land
\item
  \textbf{POLLUTENUCLEAR} Nuclear energy increases pollution of
  air/water/land
\item
  \textbf{HEALTHNUCLEAR} Nuclear energy poses a great risk to the health
  of people living around it
\item
  \textbf{JOBSNUCLEAR} Nuclear energy will bring jobs to the local
  community
\item
  \textbf{BEAUTYNUCLEAR} Nuclear energy spoils the natural beauty of the
  landscape
\item
  \textbf{PRIDENUCLEAR} I would be proud if my community used nuclear
  energy
\item
  \textbf{NPRIDENUCLEAR} Nuclear energy is a mark of pride for our
  nation
\item
  \textbf{DEVNUCLEAR} Nuclear energy pushes forward the country's
  development
\item
  \textbf{PROSPERNUCLEAR} Nuclear energy brings economic prosperity to
  the surrounding regions
\item
  \textbf{RELYNUCLEAR} I don't like the idea that I have to rely on the
  government for electricity from nuclear energy
\end{itemize}

\hypertarget{cronbachs-alpha-test-on-scale-2-eco-pol-characteristics-of-the-technology---nuclear-energy}{%
\subsection{Cronbach's alpha test on Scale 2 : Eco-Pol Characteristics
of the Technology - Nuclear
Energy}\label{cronbachs-alpha-test-on-scale-2-eco-pol-characteristics-of-the-technology---nuclear-energy}}

\begin{verbatim}
## 
## Reliability analysis   
##  raw_alpha std.alpha G6(smc) average_r S/N   ase mean   sd median_r
##       0.68      0.69    0.76      0.18 2.2 0.021  3.4 0.61     0.19
\end{verbatim}

\hypertarget{cronbachs-alpha-test-on-the-combined-scale.}{%
\subsection{Cronbach's Alpha Test on the Combined
Scale.}\label{cronbachs-alpha-test-on-the-combined-scale.}}

\begin{verbatim}
## 
## Reliability analysis   
##  raw_alpha std.alpha G6(smc) average_r S/N   ase mean   sd median_r
##        0.8       0.8    0.84      0.14   4 0.014  3.3 0.49     0.13
\end{verbatim}

\newpage

\hypertarget{fa-on-all-ecopol-variables-except-systems-of-governance}{%
\section{FA on All Ecopol Variables (except systems of
governance)}\label{fa-on-all-ecopol-variables-except-systems-of-governance}}

\hypertarget{two-factor-solution-mr1-people-centered-development-and-mr2-nationalist-development}{%
\subsection{Two factor solution : MR1 people centered development and
MR2 nationalist
development}\label{two-factor-solution-mr1-people-centered-development-and-mr2-nationalist-development}}

\textbf{MR1 People Centered Development: Pdevelop}

HEALTHNUCLEAR - Nuclear energy poses a great risk to the health of
people living around it.

BEAUTYNUCLEAR - Nuclear energy spoils the natural beauty of the
landscape.

MECHANISATION - Rapid mechanization of work is taking away jobs from
workers in this country.

INDUSTRYSMALL - Large corporations are destroying the local industries
in India and benefiting only a handful of people.

DISPLACENUCLEAR- Nuclear energy is leading to displacement of people
from their land.

POLLUTENUCLEAR- Nuclear energy increases pollution of air/water/land.

OWNERREG- Regardless of ownership, the government should pass strong
regulations and implement them.

\textbf{MR2 Nationalist Development: Ndevelop}

DEVNUCLEAR - Nuclear energy pushes forward the country's development.

PRIDENUCLEAR- I would be proud if my community used nuclear energy.

NPRIDENUCLEAR- Nuclear energy is a mark of pride for our nation.

PROSPERNUCLEAR-Nuclear energy brings economic prosperity to the
surrounding regions.

INDUSTRYLARGE- Large scale industries are required for the development
of the country that will benefit everyone.

\begin{verbatim}
## Factor Analysis using method =  minres
## Call: fa(r = ecopolall, nfactors = 2, rotate = "varimax")
## Standardized loadings (pattern matrix) based upon correlation matrix
##                 item   MR1   MR2     h2   u2 com
## HEALTHNUCLEAR     17  0.67       0.4460 0.55 1.0
## BEAUTYNUCLEAR     19  0.62       0.3869 0.61 1.0
## DISPLACENUCLEAR   15  0.58       0.3718 0.63 1.2
## POLLUTENUCLEAR    16  0.58       0.3355 0.66 1.0
## OWNERREG          14  0.56       0.3245 0.68 1.1
## MECHANISATION      2  0.54       0.3318 0.67 1.3
## INDUSTRYSMALL      6  0.52       0.2743 0.73 1.0
## ENVOVERDEV         9             0.1554 0.84 1.1
## OWNERPUB          13             0.1555 0.84 1.2
## SYSTEMDEMO        25             0.2159 0.78 2.0
## DECISIONDECEN      3             0.1008 0.90 1.0
## WEALTHLIM          1             0.1576 0.84 2.0
## ECONOMYLOCAL       8             0.0100 0.99 1.9
## DEVNUCLEAR        22        0.64 0.4424 0.56 1.1
## PRIDENUCLEAR      20        0.63 0.4551 0.54 1.3
## NPRIDENUCLEAR     21        0.58 0.3684 0.63 1.2
## PROSPERNUCLEAR    23        0.56 0.3300 0.67 1.1
## RELYNUCLEAR       24             0.1855 0.81 1.0
## JOBSNUCLEAR       18             0.2223 0.78 1.5
## INDUSTRYLARGE      5             0.1904 0.81 1.6
## ECONOMYGLOBAL      7             0.2117 0.79 2.0
## OWNERNOREG        12             0.1015 0.90 1.4
## DECISIONCEN        4             0.0996 0.90 1.7
## OWNERPVT          11             0.0407 0.96 1.9
## DEVOVERENV        10             0.0087 0.99 1.0
## 
##                        MR1  MR2
## SS loadings           3.37 2.55
## Proportion Var        0.13 0.10
## Cumulative Var        0.13 0.24
## Proportion Explained  0.57 0.43
## Cumulative Proportion 0.57 1.00
## 
## Mean item complexity =  1.3
## Test of the hypothesis that 2 factors are sufficient.
## 
## The degrees of freedom for the null model are  300  and the objective function was  6.13 with Chi Square of  2636.59
## The degrees of freedom for the model are 251  and the objective function was  2.28 
## 
## The root mean square of the residuals (RMSR) is  0.07 
## The df corrected root mean square of the residuals is  0.08 
## 
## The harmonic number of observations is  440 with the empirical chi square  1347.65  with prob <  2.4e-149 
## The total number of observations was  440  with Likelihood Chi Square =  978.9  with prob <  1.6e-86 
## 
## Tucker Lewis Index of factoring reliability =  0.626
## RMSEA index =  0.081  and the 90 % confidence intervals are  0.076 0.087
## BIC =  -548.88
## Fit based upon off diagonal values = 0.85
## Measures of factor score adequacy             
##                                                    MR1  MR2
## Correlation of (regression) scores with factors   0.91 0.88
## Multiple R square of scores with factors          0.83 0.78
## Minimum correlation of possible factor scores     0.65 0.57
\end{verbatim}

\includegraphics{module2PCAs_files/figure-latex/unnamed-chunk-8-1.pdf}

\newpage

\hypertarget{fa-on-scale-1---only-eco-pol-values-of-the-perceiver-scale.}{%
\section{FA on Scale 1 - only eco-pol values of the perceiver
scale.}\label{fa-on-scale-1---only-eco-pol-values-of-the-perceiver-scale.}}

Four Factor Solution -

\textbf{MR1 Problems of industrialisation}

MECHANISATION- Rapid mechanization of work is taking away jobs from
workers in this country

OWNERREG- Regardless of ownership, the government should pass strong
regulations and implement them.

WEALTHLIM- A limit should be put to how much wealth a person can amass

\textbf{MR3 Local Economy And Decision Making}

INDUSTRYSMALL- Large corporations are destroying the local industries in
India and benefiting only a handful of people

ECONOMYLOCAL- India would be better off if foreign companies didn't come
to here

DECISIONDECEN- Local politicians shouldn't have to ask permission from
the central government to implement policies

\textbf{MR4 Centralised and Large Industry}

DECISIONCEN- Laws and policies would be implemented more smoothly if
more power lay with the central government

ECONOMYGLOBAL- Foreign companies have led to a range of benefits for the
Indian people and society

OWNERNOREG- There is too much red-tape and the government should not
interfere with businesses and industries

INDUSTRYLARGE- Large scale industries are required for the development
of the country that will benefit everyone

\textbf{MR2 Development and Business Ownership}

DEVOVERENV- Economic growth and creating jobs should be prioritized over
environmental protection

OWNERPVT- All businesses and industries should be owned privately

OWNERPUB- The government should own most large businesses and industries

ENVOVERDEV- Polluting industries that spoil the environment should be
shut down even if it costs people their jobs

\begin{verbatim}
## 
## Reliability analysis   
## Call: alpha(x = ecopolval, check.keys = TRUE)
## 
##   raw_alpha std.alpha G6(smc) average_r S/N   ase mean   sd median_r
##       0.71      0.72    0.74      0.15 2.5 0.016  3.5 0.58     0.16
## 
##     95% confidence boundaries 
##          lower alpha upper
## Feldt     0.68  0.71  0.74
## Duhachek  0.68  0.71  0.74
## 
##  Reliability if an item is dropped:
##                raw_alpha std.alpha G6(smc) average_r S/N alpha se var.r med.r
## WEALTHLIM           0.69      0.69    0.72      0.15 2.2    0.017 0.014  0.15
## MECHANISATION       0.69      0.69    0.72      0.15 2.3    0.017 0.014  0.15
## INDUSTRYSMALL       0.68      0.69    0.71      0.15 2.2    0.017 0.014  0.15
## ECONOMYGLOBAL-      0.69      0.70    0.72      0.15 2.3    0.017 0.014  0.15
## ENVOVERDEV          0.68      0.69    0.71      0.14 2.2    0.018 0.014  0.15
## OWNERNOREG-         0.70      0.71    0.73      0.16 2.4    0.016 0.013  0.17
## OWNERPUB            0.67      0.68    0.70      0.14 2.1    0.018 0.013  0.14
## OWNERREG            0.68      0.69    0.71      0.15 2.2    0.017 0.014  0.15
## DECISIONDECEN       0.70      0.71    0.73      0.16 2.4    0.016 0.015  0.17
## DECISIONCEN-        0.70      0.71    0.73      0.16 2.4    0.016 0.014  0.17
## INDUSTRYLARGE-      0.70      0.70    0.72      0.15 2.3    0.017 0.014  0.16
## ECONOMYLOCAL        0.70      0.71    0.73      0.16 2.4    0.016 0.014  0.17
## DEVOVERENV-         0.72      0.72    0.74      0.17 2.6    0.015 0.012  0.17
## OWNERPVT            0.72      0.73    0.75      0.17 2.7    0.015 0.011  0.18
## 
##  Item statistics 
##                  n raw.r std.r r.cor r.drop mean  sd
## WEALTHLIM      721  0.53  0.53  0.49  0.401  3.7 1.3
## MECHANISATION  721  0.50  0.52  0.47  0.386  4.0 1.1
## INDUSTRYSMALL  721  0.54  0.54  0.50  0.408  3.5 1.3
## ECONOMYGLOBAL- 721  0.48  0.49  0.42  0.349  3.5 1.2
## ENVOVERDEV     721  0.58  0.57  0.54  0.461  3.6 1.3
## OWNERNOREG-    721  0.40  0.40  0.33  0.259  3.2 1.2
## OWNERPUB       721  0.62  0.62  0.60  0.509  3.4 1.2
## OWNERREG       721  0.54  0.55  0.50  0.423  3.6 1.2
## DECISIONDECEN  721  0.43  0.42  0.33  0.282  3.0 1.3
## DECISIONCEN-   721  0.41  0.42  0.34  0.272  3.6 1.2
## INDUSTRYLARGE- 721  0.45  0.47  0.40  0.328  3.9 1.2
## ECONOMYLOCAL   721  0.41  0.41  0.33  0.272  3.3 1.3
## DEVOVERENV-    721  0.32  0.29  0.19  0.148  3.4 1.4
## OWNERPVT       721  0.25  0.23  0.12  0.092  3.2 1.3
## 
## Non missing response frequency for each item
##                  1    2    3    4    5 miss
## WEALTHLIM     0.07 0.15 0.15 0.30 0.33    0
## MECHANISATION 0.03 0.13 0.12 0.28 0.44    0
## INDUSTRYSMALL 0.06 0.24 0.19 0.18 0.33    0
## ECONOMYGLOBAL 0.21 0.39 0.16 0.17 0.07    0
## ENVOVERDEV    0.08 0.17 0.13 0.32 0.30    0
## OWNERNOREG    0.19 0.23 0.29 0.20 0.09    0
## OWNERPUB      0.07 0.19 0.18 0.31 0.24    0
## OWNERREG      0.03 0.17 0.22 0.28 0.29    0
## DECISIONDECEN 0.14 0.29 0.21 0.16 0.20    0
## DECISIONCEN   0.24 0.38 0.17 0.13 0.07    0
## INDUSTRYLARGE 0.37 0.36 0.11 0.10 0.05    0
## ECONOMYLOCAL  0.08 0.22 0.22 0.23 0.24    0
## DEVOVERENV    0.31 0.27 0.13 0.16 0.14    0
## OWNERPVT      0.12 0.22 0.24 0.21 0.21    0
\end{verbatim}

\begin{verbatim}
## Factor Analysis using method =  minres
## Call: fa(r = ecopolval, nfactors = 4, rotate = "varimax")
## Standardized loadings (pattern matrix) based upon correlation matrix
##               item   MR1   MR3   MR4   MR2   h2   u2 com
## OWNERREG         8  0.54                   0.37 0.63 1.5
## MECHANISATION    2  0.51                   0.33 0.67 1.6
## WEALTHLIM        1  0.48                   0.30 0.70 1.6
## INDUSTRYSMALL    3        0.53             0.41 0.59 1.8
## ECONOMYLOCAL    12        0.52             0.29 0.71 1.1
## DECISIONDECEN    9                         0.13 0.87 2.0
## DECISIONCEN     10              0.49       0.28 0.72 1.4
## ECONOMYGLOBAL    4              0.48       0.30 0.70 1.6
## OWNERNOREG       6              0.47       0.40 0.60 2.2
## INDUSTRYLARGE   11              0.43       0.30 0.70 1.9
## DEVOVERENV      13                   -0.54 0.29 0.71 1.0
## OWNERPVT        14                    0.51 0.27 0.73 1.1
## ENVOVERDEV       5                    0.46 0.43 0.57 2.5
## OWNERPUB         7                    0.43 0.43 0.57 3.2
## 
##                        MR1  MR3  MR4  MR2
## SS loadings           1.21 1.19 1.09 1.04
## Proportion Var        0.09 0.09 0.08 0.07
## Cumulative Var        0.09 0.17 0.25 0.32
## Proportion Explained  0.27 0.26 0.24 0.23
## Cumulative Proportion 0.27 0.53 0.77 1.00
## 
## Mean item complexity =  1.8
## Test of the hypothesis that 4 factors are sufficient.
## 
## The degrees of freedom for the null model are  91  and the objective function was  2.17 with Chi Square of  1549.03
## The degrees of freedom for the model are 41  and the objective function was  0.23 
## 
## The root mean square of the residuals (RMSR) is  0.03 
## The df corrected root mean square of the residuals is  0.05 
## 
## The harmonic number of observations is  721 with the empirical chi square  147.5  with prob <  6.2e-14 
## The total number of observations was  721  with Likelihood Chi Square =  163.15  with prob <  1.7e-16 
## 
## Tucker Lewis Index of factoring reliability =  0.813
## RMSEA index =  0.064  and the 90 % confidence intervals are  0.054 0.075
## BIC =  -106.66
## Fit based upon off diagonal values = 0.97
## Measures of factor score adequacy             
##                                                    MR1  MR3  MR4  MR2
## Correlation of (regression) scores with factors   0.74 0.76 0.73 0.77
## Multiple R square of scores with factors          0.54 0.57 0.54 0.59
## Minimum correlation of possible factor scores     0.08 0.14 0.08 0.19
\end{verbatim}

\includegraphics{module2PCAs_files/figure-latex/unnamed-chunk-9-1.pdf}

\newpage

\hypertarget{factor-analysis-on-scale-2---eco-pol-characteristics-of-the-technology---nuclear-energy}{%
\section{Factor analysis on Scale 2 - Eco-Pol characteristics of the
technology - Nuclear
Energy}\label{factor-analysis-on-scale-2---eco-pol-characteristics-of-the-technology---nuclear-energy}}

Two Factor Solution - positive versus negative characteristics

\textbf{MR1 Negative Characteristics}

HEALTHNUCLEAR - Nuclear energy poses a great risk to the health of
people living around it.

BEAUTYNUCLEAR - Nuclear energy spoils the natural beauty of the
landscape.

DISPLACENUCLEAR- Nuclear energy is leading to displacement of people
from their land.

POLLUTENUCLEAR- Nuclear energy increases pollution of air/water/land.

\textbf{MR2 Positive Characteristics}

DEVNUCLEAR- Nuclear energy pushes forward the country's development.

PRIDENUCLEAR- I would be proud if my community used nuclear energy.

NPRIDENUCLEAR- Nuclear energy is a mark of pride for our nation.

PROSPERNUCLEAR- Nuclear energy brings economic prosperity to the
surrounding regions.

JOBSNUCLEAR- Nuclear energy will bring jobs to the local community.

RELYNUCLEAR- I don't like the idea that I have to rely on the government
for electricity from nuclear energy.

\begin{verbatim}
## 
## Reliability analysis   
##  raw_alpha std.alpha G6(smc) average_r S/N   ase mean   sd median_r
##       0.68      0.69    0.76      0.18 2.2 0.021  3.4 0.61     0.19
\end{verbatim}

\begin{verbatim}
## Factor Analysis using method =  minres
## Call: fa(r = Nuclear, nfactors = 2, rotate = "varimax")
## Standardized loadings (pattern matrix) based upon correlation matrix
##                 item   MR1   MR2   h2   u2 com
## HEALTHNUCLEAR      3  0.85       0.72 0.28 1.0
## POLLUTENUCLEAR     2  0.75       0.58 0.42 1.0
## BEAUTYNUCLEAR      5  0.67       0.45 0.55 1.0
## DISPLACENUCLEAR    1  0.53       0.31 0.69 1.2
## DEVNUCLEAR         8        0.70 0.52 0.48 1.1
## PROSPERNUCLEAR     9        0.63 0.42 0.58 1.1
## NPRIDENUCLEAR      7        0.60 0.37 0.63 1.1
## PRIDENUCLEAR       6        0.59 0.39 0.61 1.3
## JOBSNUCLEAR        4        0.50 0.29 0.71 1.4
## RELYNUCLEAR       10             0.16 0.84 1.0
## 
##                        MR1  MR2
## SS loadings           2.16 2.05
## Proportion Var        0.22 0.20
## Cumulative Var        0.22 0.42
## Proportion Explained  0.51 0.49
## Cumulative Proportion 0.51 1.00
## 
## Mean item complexity =  1.1
## Test of the hypothesis that 2 factors are sufficient.
## 
## The degrees of freedom for the null model are  45  and the objective function was  2.87 with Chi Square of  1500.02
## The degrees of freedom for the model are 26  and the objective function was  0.35 
## 
## The root mean square of the residuals (RMSR) is  0.05 
## The df corrected root mean square of the residuals is  0.07 
## 
## The harmonic number of observations is  528 with the empirical chi square  137.21  with prob <  4.4e-17 
## The total number of observations was  528  with Likelihood Chi Square =  183.05  with prob <  1.5e-25 
## 
## Tucker Lewis Index of factoring reliability =  0.813
## RMSEA index =  0.107  and the 90 % confidence intervals are  0.093 0.122
## BIC =  20.06
## Fit based upon off diagonal values = 0.96
## Measures of factor score adequacy             
##                                                    MR1  MR2
## Correlation of (regression) scores with factors   0.92 0.88
## Multiple R square of scores with factors          0.84 0.78
## Minimum correlation of possible factor scores     0.68 0.55
\end{verbatim}

\includegraphics{module2PCAs_files/figure-latex/unnamed-chunk-10-1.pdf}
\newpage

\hypertarget{solar---fa-2-factor-solution}{%
\section{Solar - FA 2 factor
solution}\label{solar---fa-2-factor-solution}}

here I'll make the same chart with Coal as well - 2 factor solution and
explore the 4 factor solution. Talk to Terre about the Slovic study and
how they did it.

\begin{verbatim}
## 
## Reliability analysis   
##  raw_alpha std.alpha G6(smc) average_r S/N   ase mean  sd median_r
##       0.78      0.78    0.84      0.13 3.6 0.013  3.5 0.5     0.13
\end{verbatim}

\begin{verbatim}
## Factor Analysis using method =  minres
## Call: fa(r = secopolall, nfactors = 2, rotate = "varimax")
## Standardized loadings (pattern matrix) based upon correlation matrix
##               item   MR1   MR2    h2   u2 com
## DEVSOLAR        22  0.84       0.724 0.28 1.0
## PROSPERSOLAR    23  0.80       0.646 0.35 1.0
## PRIDESOLAR      20  0.80       0.656 0.34 1.1
## NPRIDESOLAR     21  0.78       0.616 0.38 1.0
## RELYSOLAR       24  0.60       0.361 0.64 1.0
## JOBSSOLAR       18  0.56       0.319 0.68 1.0
## ECONOMYLOCAL     8             0.124 0.88 1.2
## OWNERPVT        11             0.050 0.95 1.1
## POLLUTESOLAR    16        0.69 0.511 0.49 1.1
## HEALTHSOLAR     17        0.58 0.353 0.65 1.1
## BEAUTYSOLAR     19        0.55 0.304 0.70 1.0
## DISPLACESOLAR   15        0.54 0.290 0.71 1.0
## MECHANISATION    2       -0.52 0.300 0.70 1.2
## SYSTEMDEMO      25       -0.50 0.264 0.74 1.1
## ECONOMYGLOBAL    7        0.48 0.234 0.77 1.0
## OWNERPUB        13       -0.47 0.246 0.75 1.2
## ENVOVERDEV       9       -0.44 0.222 0.78 1.2
## OWNERREG        14       -0.44 0.191 0.81 1.0
## WEALTHLIM        1       -0.42 0.173 0.83 1.0
## INDUSTRYLARGE    5        0.41 0.180 0.82 1.1
## INDUSTRYSMALL    6             0.152 0.85 1.1
## DECISIONCEN      4             0.094 0.91 1.1
## DECISIONDECEN    3             0.063 0.94 1.0
## OWNERNOREG      12             0.071 0.93 1.4
## DEVOVERENV      10             0.061 0.94 1.3
## 
##                        MR1  MR2
## SS loadings           3.62 3.59
## Proportion Var        0.14 0.14
## Cumulative Var        0.14 0.29
## Proportion Explained  0.50 0.50
## Cumulative Proportion 0.50 1.00
## 
## Mean item complexity =  1.1
## Test of the hypothesis that 2 factors are sufficient.
## 
## The degrees of freedom for the null model are  300  and the objective function was  7.85 with Chi Square of  4522.16
## The degrees of freedom for the model are 251  and the objective function was  2.23 
## 
## The root mean square of the residuals (RMSR) is  0.08 
## The df corrected root mean square of the residuals is  0.08 
## 
## The harmonic number of observations is  586 with the empirical chi square  1982.05  with prob <  2.8e-266 
## The total number of observations was  586  with Likelihood Chi Square =  1279.58  with prob <  2.3e-137 
## 
## Tucker Lewis Index of factoring reliability =  0.708
## RMSEA index =  0.084  and the 90 % confidence intervals are  0.079 0.088
## BIC =  -320.12
## Fit based upon off diagonal values = 0.87
## Measures of factor score adequacy             
##                                                    MR1  MR2
## Correlation of (regression) scores with factors   0.95 0.91
## Multiple R square of scores with factors          0.90 0.83
## Minimum correlation of possible factor scores     0.81 0.67
\end{verbatim}

\includegraphics{module2PCAs_files/figure-latex/unnamed-chunk-11-1.pdf}

\newpage

\hypertarget{coal---fa-2-factor-solution}{%
\section{Coal - FA 2 factor
solution}\label{coal---fa-2-factor-solution}}

\begin{verbatim}
## 
## Reliability analysis   
##  raw_alpha std.alpha G6(smc) average_r S/N   ase mean   sd median_r
##        0.8       0.8    0.84      0.14 4.1 0.013  3.3 0.47     0.14
\end{verbatim}

\begin{verbatim}
## Factor Analysis using method =  minres
## Call: fa(r = cecopolall, nfactors = 2, rotate = "varimax")
## Standardized loadings (pattern matrix) based upon correlation matrix
##               item   MR1   MR2    h2   u2 com
## POLLUTECOAL     16  0.65       0.428 0.57 1.0
## BEAUTYCOAL      19  0.63       0.409 0.59 1.1
## MECHANISATION    2  0.58       0.361 0.64 1.1
## HEALTHCOAL      17  0.58       0.370 0.63 1.2
## DISPLACECOAL    15  0.54       0.295 0.71 1.0
## INDUSTRYSMALL    6  0.52       0.272 0.73 1.0
## OWNERREG        14  0.47       0.233 0.77 1.1
## SYSTEMDEMO      25  0.41       0.240 0.76 1.7
## JOBSCOAL        18  0.41       0.217 0.78 1.5
## DECISIONDECEN    3             0.128 0.87 1.0
## ECONOMYGLOBAL    7             0.183 0.82 2.0
## ENVOVERDEV       9             0.095 0.91 1.1
## WEALTHLIM        1             0.166 0.83 2.0
## OWNERPUB        13             0.101 0.90 1.5
## ECONOMYLOCAL     8             0.017 0.98 2.0
## PRIDECOAL       20        0.65 0.438 0.56 1.1
## NPRIDECOAL      21        0.59 0.374 0.63 1.2
## INDUSTRYLARGE    5       -0.44 0.246 0.75 1.5
## DEVCOAL         22        0.43 0.289 0.71 1.8
## PROSPERCOAL     23             0.229 0.77 1.9
## RELYCOAL        24             0.100 0.90 1.5
## DECISIONCEN      4             0.101 0.90 1.6
## OWNERNOREG      12             0.100 0.90 1.7
## OWNERPVT        11             0.060 0.94 1.7
## DEVOVERENV      10             0.022 0.98 1.2
## 
##                        MR1  MR2
## SS loadings           3.48 2.00
## Proportion Var        0.14 0.08
## Cumulative Var        0.14 0.22
## Proportion Explained  0.64 0.36
## Cumulative Proportion 0.64 1.00
## 
## Mean item complexity =  1.4
## Test of the hypothesis that 2 factors are sufficient.
## 
## The degrees of freedom for the null model are  300  and the objective function was  5.26 with Chi Square of  2554.39
## The degrees of freedom for the model are 251  and the objective function was  1.78 
## 
## The root mean square of the residuals (RMSR) is  0.07 
## The df corrected root mean square of the residuals is  0.07 
## 
## The harmonic number of observations is  496 with the empirical chi square  1261.39  with prob <  3.5e-134 
## The total number of observations was  496  with Likelihood Chi Square =  862.72  with prob <  4.2e-68 
## 
## Tucker Lewis Index of factoring reliability =  0.675
## RMSEA index =  0.07  and the 90 % confidence intervals are  0.065 0.075
## BIC =  -695.13
## Fit based upon off diagonal values = 0.87
## Measures of factor score adequacy             
##                                                    MR1  MR2
## Correlation of (regression) scores with factors   0.90 0.85
## Multiple R square of scores with factors          0.82 0.71
## Minimum correlation of possible factor scores     0.63 0.43
\end{verbatim}

\includegraphics{module2PCAs_files/figure-latex/unnamed-chunk-12-1.pdf}

\newpage

\hypertarget{appendix1}{%
\section{Appendix1}\label{appendix1}}

\textbf{Kahan et al (2007) scale}

Individualism - Communitarinism

\begin{itemize}
\tightlist
\item
  \textbf{K\_IINTRFER} The government interferes far too much in our
  everyday lives.
\item
  \textbf{K\_IPRIVACY} The government should stop telling people how to
  live their lives.
\item
  \textbf{K\_IPROTECT} It's not the government's business to try to
  protect people from themselves.
\item
  \textbf{K\_SHARM} Sometimes the government needs to make laws that
  keep people from hurting themselves.
\item
  \textbf{K\_SLIMCHOI} The government should put limits on the choices
  individuals can make so they don't get in the way of what's good for
  society.
\item
  \textbf{K\_SPROTECT} The government should do more to advance
  society's goals, even if that means limiting the freedom and choices
  of individuals.
\end{itemize}

Hierarchy -Egalitarianism

\begin{itemize}
\tightlist
\item
  \textbf{K\_HEQUAL} We have gone too far in pushing equal rights in
  this country.
\item
  \textbf{K\_HREVDIS1} Nowadays it seems like there is just as much
  discrimination against upper castes as there is against Dalits.
\item
  \textbf{K\_EDISCRIM} Discrimination against minorities is still a very
  serious problem in our society.
\item
  \textbf{K\_ERADEQ1} We need to dramatically reduce inequalities
  between the rich and the poor.
\item
  \textbf{K\_EWEALTH} Our society would be better off if the
  distribution of wealth was more equal.
\item
  \textbf{K\_ERADEQ2} We need to dramatically reduce inequalities
  between men and women.
\end{itemize}

\newpage

\hypertarget{appendix2}{%
\section{Appendix2}\label{appendix2}}

\textbf{New Eco-pol values scale}

\begin{itemize}
\item
  \textbf{DISPLACENUCLEAR}Nuclear energy is leading to displacement of
  people from their land
\item
  \textbf{BEAUTYNUCLEAR} Nuclear energy spoils the natural beauty of the
  landscape
\item
  \textbf{POLLUTENUCLEAR} Nuclear energy increases pollution of
  air/water/land
\item
  \textbf{HEALTHNUCLEAR} Nuclear energy poses a great risk to the health
  of people living around it
\item
  \textbf{JOBSNUCLEAR} Nuclear energy will bring jobs to the local
  community
\item
  \textbf{PRIDENUCLEAR} I would be proud if my community used nuclear
  energy
\item
  \textbf{NPRIDENUCLEAR} Nuclear energy is a mark of pride for our
  nation
\item
  \textbf{DEVNUCLEAR} Nuclear energy pushes forward the country's
  development
\item
  \textbf{PROSPERNUCLEAR} Nuclear energy brings economic prosperity to
  the surrounding regions
\item
  \textbf{RELYNUCLEAR} I don't like the idea that I have to rely on the
  government for electricity from nuclear energy
\item
  \textbf{DECISIONDECEN} Local politicians shouldn't have to ask
  permission from the central government to implement policies
\item
  \textbf{DECISIONCEN} Laws and policies would be implemented more
  smoothly if more power lay with the central government.
\item
  \textbf{INDUSTRYLARGE} Large scale industries are required for the
  development of the country that will benefit everyone
\item
  \textbf{ECONOMYLOCAL} India would be better off if foreign companies
  didn't come to here
\item
  \textbf{DEVOVERENV} Economic growth and creating jobs should be
  prioritized over environmental protection
\item
  \textbf{INDUSTRYSMALL} Large corporations are destroying the local
  industries in India and benefiting only a handful of people.
\item
  \textbf{WEALTHLIM} A limit should be put to how much wealth a person
  can amass
\item
  \textbf{ECONOMYGLOBAL} Foreign companies have led to a range of
  benefits for the Indian people and society
\item
  \textbf{OWNERPVT} All businesses and industries should be owned
  privately
\item
  \textbf{OWNERPUB} The government should own most large businesses and
  industries
\item
  \textbf{ENVOVERDEV} Polluting industries that spoil the environment
  should be shut down even if it costs people their jobs
\item
  \textbf{OWNERREG} Regardless of ownership, the government should pass
  strong regulations and implement them
\item
  \textbf{MECHANISATION} Rapid mechanization of work is taking away jobs
  from workers in this country
\item
  \textbf{OWNERNOREG} There is too much red-tape and the government
  should not interfere with businesses and industries
\end{itemize}

\end{document}

### 2023-09-20 module2/module2IVgraphs.Rmd
lot of changes because I wasn't opening the project file.

@@
   group_by(SYSTEMDEMO)%>%
-  filter(SYSTEMDEMO %in% c(1, 5))%>%
+  filter(SYSTEMDEMO %in% c(1,5))%>%
   summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%

### 2023-09-20 module2/module2extra.Rmd
lot of changes because I wasn't opening the project file.

@@
 ```
+
+Factor Analysis on the economic and political values scale: 4 factor spaces
+
+```{r, echo=FALSE}
+#factor analysis with 4 factor spaces
+
+ecopolscale4.fa <- fa(ecopolscalescores, nfactors=4, scores=TRUE, rotate="varimax", fm="pa")
+print.psych(ecopolscale4.fa, cut = 0.3, sort = TRUE)
+fa.diagram(ecopolscale4.fa)
+
+loadingsecopol4 <- unclass(ecopolscale4.fa$loadings)
+
+loadingstableecopol4 <- cbind(loadingsecopol4)
+
+faecopol4 <- as_tibble(loadingstableecopol4) %>%
+add_column("Items" = c("Local politicians shouldn't have to ask permission from the central government to implement policies",
+ "Laws and policies would be implemented more smoothly if more power lay with the central government",
+"It is good to have a strong leader who does not have to bother with elections", 
+ "Experts, not the government, should make decisions according to what they think is best for the country" , 
+"It is very important to have a democratic political system because it ensures that no individual leader has too much power" , 
+"There should be a system governed by religious law" , 
+"Large corporations are destroying the local industries in India and benefiting only a handful of people" , 
+"Large scale industries are required for the development of the country that will benefit everyone" , 
+"India would be better off if foreign companies didn't come to here" , 
+"Foreign companies have led to a range of benefits for the Indian people and society", 
+"Economic growth and creating jobs should be prioritized over environmental protection" , 
+"Polluting industries that spoil the environment should be shut down even if it costs people their jobs", 
+"All businesses and industries should be owned privately", 
+"The government should own most large businesses and industries", 
+"Regardless of ownership, the government should pass strong regulations and implement them", 
+"There is too much red-tape and the government should not interfere with businesses and industries" , 
+"A limit should be put to how much wealth a person can amass",
+ "Rapid mechanization of work is taking away jobs from workers in this country"))%>%
+dplyr::select("Items",PA1, PA2, PA3, PA4) %>%
+  arrange(desc(PA1))
+
+knitr::kable(faecopol4, digits= 2)
+
+Varexplecopol4 <- unclass(ecopolscale4.fa$Vaccounted)
+
+knitr::kable(Varexplecopol4, digits = 2)
+
+```
+
+Factor Analysis on the economic and political values scale: 6 factor spaces
+
+```{r, echo=FALSE}
+
+ecopolscale3.fa <- fa(ecopolscalescores, nfactors=3, scores=TRUE, rotate="varimax", fm="pa")
+print.psych(ecopolscale3.fa, cut = 0.3, sort = TRUE)
+fa.diagram(ecopolscale3.fa)
+
+loadingsecopol3 <- unclass(ecopolscale3.fa$loadings)
+
+loadingstableecopol3 <- cbind(loadingsecopol3)
+
+faecopol3 <- as_tibble(loadingstableecopol3) %>%
+add_column("Items" = c("Local politicians shouldn't have to ask permission from the central government to implement policies",
+ "Laws and policies would be implemented more smoothly if more power lay with the central government",
+"It is good to have a strong leader who does not have to bother with elections", 
+ "Experts, not the government, should make decisions according to what they think is best for the country" , 
+"It is very important to have a democratic political system because it ensures that no individual leader has too much power" , 
+"There should be a system governed by religious law" , 
+"Large corporations are destroying the local industries in India and benefiting only a handful of people" , 
+"Large scale industries are required for the development of the country that will benefit everyone" , 
+"India would be better off if foreign companies didn't come to here" , 
+"Foreign companies have led to a range of benefits for the Indian people and society", 
+"Economic growth and creating jobs should be prioritized over environmental protection" , 
+"Polluting industries that spoil the environment should be shut down even if it costs people their jobs", 
+"All businesses and industries should be owned privately", 
+"The government should own most large businesses and industries", 
+"Regardless of ownership, the government should pass strong regulations and implement them", 
+"There is too much red-tape and the government should not interfere with businesses and industries" , 
+"A limit should be put to how much wealth a person can amass",
+ "Rapid mechanization of work is taking away jobs from workers in this country"))%>%
+dplyr::select("Items",PA1, PA2, PA3) %>%
+  arrange(desc(PA1))
+
+knitr::kable(faecopol3, digits= 2)
+
+Varexplecopol3 <- unclass(ecopolscale3.fa$Vaccounted)
+
+knitr::kable(Varexplecopol3, digits = 2)
+```
+
+```{r, echo=FALSE}
+
+#factor analysis with 2, 4 and 6 factor spaces
+
+ecopolscale.fa <- fa(ecopolscalescores, nfactors=2, scores=TRUE, rotate="varimax", fm="pa")
+print.psych(ecopolscale.fa, cut = 0.3, sort = TRUE)
+fa.diagram(ecopolscale.fa)
+
+# Calculate eigenvalues
+ecopol.eigenvalues <- ecopolscale.fa$values
+
+loadingsecopol <- unclass(ecopolscale.fa$loadings)
+
+loadingstableecopol <- cbind(loadingsecopol)
+
+twofaecopol <- as_tibble(loadingstableecopol) %>%
+add_column("Items" = c("Local politicians shouldn't have to ask permission from the central government to implement policies",
+ "Laws and policies would be implemented more smoothly if more power lay with the central government",
+"It is good to have a strong leader who does not have to bother with elections", 
+ "Experts, not the government, should make decisions according to what they think is best for the country" , 
+"It is very important to have a democratic political system because it ensures that no individual leader has too much power" , 
+"There should be a system governed by religious law" , 
+"Large corporations are destroying the local industries in India and benefiting only a handful of people" , 
+"Large scale industries are required for the development of the country that will benefit everyone" , 
+"India would be better off if foreign companies didn't come to here" , 
+"Foreign companies have led to a range of benefits for the Indian people and society", 
+"Economic growth and creating jobs should be prioritized over environmental protection" , 
+"Polluting industries that spoil the environment should be shut down even if it costs people their jobs", 
+"All businesses and industries should be owned privately", 
+"The government should own most large businesses and industries", 
+"Regardless of ownership, the government should pass strong regulations and implement them", 
+"There is too much red-tape and the government should not interfere with businesses and industries" , 
+"A limit should be put to how much wealth a person can amass",
+ "Rapid mechanization of work is taking away jobs from workers in this country"))%>%
+dplyr::select("Items",PA1, PA2)%>%
+arrange(desc(PA1))
+
+knitr::kable(twofaecopol, digits= 2)
+
+Varexplecopol <- unclass(ecopolscale.fa$Vaccounted)
+
+knitr::kable(Varexplecopol, digits = 2)
+
+```
+
+**Economic and Political characteristics of the energy technology scale -  Solar Energy and rooftop solar energy**
+
+- **DISPLACESOLAR**	 Solar energy is leading to displacement of people from their land
+- **POLLUTESOLAR**	 Solar energy increases pollution of air/water/land
+- **HEALTHSOLAR**	   Solar energy poses a great risk to the health of people living around it
+- **JOBSSOLAR**	     Solar energy will bring jobs to the local community
+- **BEAUTYSOLAR**	   Solar energy spoils the natural beauty of the landscape
+- **PRIDESOLAR**	   I would be proud if my community used solar energy
+- **NPRIDESOLAR**	   Solar energy is a mark of pride for our nation
+- **DEVSOLAR**	     Solar energy pushes forward the country's development
+- **PROSPERSOLAR**	 Solar energy brings economic prosperity to the surrounding regions
+- **RELYSOLAR**	     I don't like the idea that I have to rely on the government for electricity from (large scale) solar energy
+
+Cronbach's alpha test on the Eco-Pol characteristics of the technology -  Solar Energy
+
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+
+#alpha test on Eco-pol characteristics of the technology
+
+Solar <- codedmodule2 %>%
+dplyr::select("DISPLACESOLAR":"RELYSOLAR") %>%
+dplyr::rename("Solar energy is leading to displacement of people from their land" = "DISPLACESOLAR") %>%
+dplyr::rename("Solar energy increases pollution of air/water/land" = "POLLUTESOLAR")%>%
+dplyr::rename("Solar energy poses a great risk to the health of people living around it" = "HEALTHSOLAR")%>%
+dplyr::rename("Solar energy will bring jobs to the local community" = "JOBSSOLAR")%>%
+dplyr::rename("Solar energy spoils the natural beauty of the landscape" = "BEAUTYSOLAR")%>%
+dplyr::rename("I would be proud if my community used solar energy" = "PRIDESOLAR")%>%
+dplyr::rename("Solar energy is a mark of pride for our nation" = "NPRIDESOLAR") %>%
+dplyr::rename("Solar energy pushes forward the country's development" = "DEVSOLAR")%>%
+dplyr::rename("Solar energy brings economic prosperity to the surrounding regions" = "PROSPERSOLAR")%>%
+dplyr::rename("I don't like the idea that I have to rely on the government for electricity from (large scale solar energy)" = "RELYSOLAR")%>%
+  na.omit()
+
+psych::alpha(Solar, check.keys = TRUE)
+
+```
+
+Factor Analysis on the eco- pol characteristics of the technology, Solar Energy : 2 factor spaces
+
+```{r, echo=FALSE}
+
+#factor analysis with 2 factor spaces
+
+solar.fa <- fa(Solar, nfactors=2, scores=TRUE, rotate="varimax", fm="pa")
+#print.psych(solar.fa, cut = 0.4, sort = TRUE)
+#fa.diagram(solar.fa)
+
+loadingssolar <- unclass(solar.fa$loadings)
+
+loadingstablesolar <- cbind(loadingssolar)
+
+fasolar <- as_tibble(loadingstablesolar) %>%
+add_column("Items" = c("Solar energy is leading to displacement of people from their land",
+"Solar energy increases pollution of air/water/land",
+"Solar energy poses a great risk to the health of people living around it",
+"Solar energy will bring jobs to the local community",
+"Solar energy spoils the natural beauty of the landscape",
+"I would be proud if my community used solar energy",
+"Solar energy is a mark of pride for our nation",
+"Solar energy pushes forward the country's development",
+"Solar energy brings economic prosperity to the surrounding regions",
+"I don't like the idea that I have to rely on the government for electricity from (large scale) solar energy"))%>%
+dplyr::select("Items",PA1, PA2)%>%
+arrange(desc(PA1))
+
+knitr::kable(fasolar, digits= 2)
+
+Varexplsolar <- unclass(solar.fa$Vaccounted)
+
+knitr::kable(Varexplsolar, digits = 2)
+```
+
+Factor Analysis on the eco- pol characteristics of the technology, Solar Energy : 4 factor spaces
+
+```{r, echo=FALSE}
+
+#factor analysis with  4 a factor spaces
+
+solar4.fa <- fa(Solar, nfactors=4, scores=TRUE, rotate="varimax", fm="pa")
+#print.psych(solar.fa, cut = 0.4, sort = TRUE)
+#fa.diagram(solar.fa)
+
+loadingssolar4 <- unclass(solar4.fa$loadings)
+
+loadingstablesolar4 <- cbind(loadingssolar4)
+
+fasolar4 <- as_tibble(loadingstablesolar4) %>%
+add_column("Items" = c("Solar energy is leading to displacement of people from their land",
+"Solar energy increases pollution of air/water/land",
+"Solar energy poses a great risk to the health of people living around it",
+"Solar energy will bring jobs to the local community",
+"Solar energy spoils the natural beauty of the landscape",
+"I would be proud if my community used solar energy",
+"Solar energy is a mark of pride for our nation",
+"Solar energy pushes forward the country's development",
+"Solar energy brings economic prosperity to the surrounding regions",
+"I don't like the idea that I have to rely on the government for electricity from (large scale) solar energy"))%>%
+dplyr::select("Items",PA1, PA2, PA3, PA4) %>%
+  arrange(desc(PA1))
+
+knitr::kable(fasolar4, digits= 2)
+
+Varexplsolar4 <- unclass(solar4.fa$Vaccounted)
+
+knitr::kable(Varexplsolar4, digits = 2)
+```
+
+```{r, echo=FALSE}
+ROOFS<- codedmodule2 %>%
+ dplyr::select("DISPLACEROOFS":"RELYROOFS")
+
+psych::alpha(ROOFS, check.keys = TRUE)
+
+```
+
+```{r, echo=FALSE}
+#factor analysis with 2, 4 and 6 factor spaces
+
+roofs.fa <- fa(ROOFS, nfactors=2, scores=TRUE, rotate="varimax", fm="pa")
+#print.psych(roofs.fa, cut = 0.4, sort = TRUE)
+#fa.diagram(roofs.fa)
+
+loadingsroofs <- unclass(roofs.fa$loadings)
+
+loadingstableroofs <- cbind(loadingsroofs)
+
+faroofs <- as_tibble(loadingstableroofs) %>%
+add_column("Items" = c("Rooftop solar is leading to displacement of people from their land",
+"Rooftop solar increases pollution of air/water/land", 
+"Rooftop solar poses a great risk to the health of people living around it",
+"Rooftop solar will bring jobs to the local community",
+"Rooftop solar spoils the natural beauty of the landscape" , 
+"I would be proud if my community used Rooftop solar" , 
+"Rooftop solar is a mark of pride for our nation", 
+"Rooftop solar pushes forward the country's development" , 
+"Rooftop solar brings economic prosperity to the surrounding regions" , 
+"I don't like the idea that I have to rely on the government for electricity from (large scale) Rooftop solar")) %>%
+dplyr::select("Items",  PA1, PA2)%>%
+  arrange(desc(PA1))
+
+knitr::kable(faroofs, digits = 2)
+
+Varexplroofs <- unclass(roofs.fa$Vaccounted)
+
+knitr::kable(Varexplroofs, digits = 2)
+
+```

### 2023-09-20 module2/moduletwoanalysis.Rmd
conducting the Kruskal wallis test on DVs
lot of changes because I wasn't opening the project file.

@@
 
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+# Q4: How do perception of risk and perception of benefit compare with each other?
+
+# what is this comparison telling us ?
+
+# summary statistics for risks from different energy sources
+library(tidyverse)
+
+# Filter variables of interest
+joineddf_subset <- joineddf %>%
+  dplyr::select(!starts_with(c("Ben_IND", "Risky_IND")))%>%
+  select(starts_with("Risky"), 
+         starts_with("Ben"))
+
+str(joineddf_subset)
+
+# Melt the data frame to long format
+long_format <- joineddf_subset %>% 
+  pivot_longer(everything(), names_to = "technology", values_to = "value") %>%
+  mutate(risk_or_benefit = if_else(str_detect(technology, "Risky"), "risk", "benefit"),
+         technology = str_replace(technology, "Risky_|Ben_", ""))
+
+# Calculate mean and sd for each technology and category (risk or benefit)
+summary_df <- long_format %>%
+  group_by(technology, risk_or_benefit) %>%
+  summarise(mean = mean(value, na.rm = TRUE),
+            sd = sd(value, na.rm = TRUE),
+            se = sd(value, na.rm = TRUE) / sqrt(n()),
+            .groups = "drop")
+
+# Order technologies by mean risk
+order_risk <- summary_df %>% 
+  filter(risk_or_benefit == "risk") %>%
+  arrange(mean) %>% 
+  pull(technology)
+
+# Change the levels of factor 'technology'
+summary_df$technology <- factor(summary_df$technology, levels = order_risk)
+
+# Plotting the data
+ggplot(summary_df, aes(x = technology, y = mean, fill = risk_or_benefit)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = 0.3, position = position_dodge(0.9)) +
+  ylim(0, 5) +
+  scale_fill_manual("legend", 
+                    values = c("benefit" = "palegreen3", "risk" = "firebrick2"), 
+                    labels = c("benefit" = "Perceived Benefit", "risk" = "Perceived Risk")) +
+  labs(y = "Mean Values", x = "Energy Technologies", fill = "Perceived") +
+  ggtitle("Perceived risk and benefit from centrally managed energy technologies") +
+  coord_flip()
+
+# add a star in front of all bars to show these differences are significant at 0.05 
+# error bars represent
+
+```
 bar plots for median of perceived risk and benefit from various energy technologies
@@
   select(!starts_with(c("Risky","Gender","Caste","Religion","State")))%>%
-  prcomp(center = TRUE,scale. = TRUE)
+  prcomp(center = TRUE, scale. = TRUE)
 

### 2023-09-20 nuclear in comparison.Rmd
lot of changes because I wasn't opening the project file.

---
title: 'nuclear energy in comparison'
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    keep_tex: yes
  header-includes:
  - \usepackage{dcolumn}
  - \usepackage{array}
  keep_md: yes
---

```{r load packages, warning = FALSE, message = FALSE, echo=FALSE}
  knitr::opts_chunk$set(warning = FALSE, message = FALSE)

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(tidyr))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(lavaan))
suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(DT))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(psych)) 
```

```{r setup, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

moduletwo <- read_excel(here::here("thesis_surveydata/political_factors_complete.xlsx"))
module2 <- data.frame(moduletwo)
module2[module2 == "Rather not say/ Don't know"] <- "Rather not say/Don't know"

# loaded data set for module 2 eco -pol variables and removes the rows with question number and question text
```

```{r, eval =TRUE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
codedmodule2 <- module2 %>%

#remove row 1
  filter(!row_number() %in% c(1,2)) %>%

# replace risky likert scale with numbers
  mutate_at(vars(starts_with("Risky")), funs(case_when(. =="Not at all risky" ~ 1, 
                                                       . =="Slightly risky" ~ 2, 
                                                       . =="Moderately risky" ~ 3, 
                                                       . =="Very risky" ~ 4, 
                                                       . =="Extremely risky" ~ 5))) %>%

# replace beneficial likert scale with numbers  
  mutate_at(vars(starts_with("Ben")), funs(case_when(. =="Not at all beneficial" ~ 1,
                                                     . =="Slightly beneficial" ~ 2,
                                                     . =="Moderately beneficial" ~ 3,
                                                     . =="Very beneficial" ~ 4,
                                                     . =="Extremely beneficial" ~ 5 ))) %>%

# replace nuclear acceptance likert scale with numbers
  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                                        . == "Somewhat disagree" ~ 2,
                                                                        . == "Neither agree nor disagree" ~3,
                                                                        . == "Somewhat agree" ~ 4,
                                                                        . == "Strongly agree" ~ 5))) %>%

# code likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_I","K_H","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE", "DEV", "PROSPER", "RELY"))), funs(case_when(. == "Strongly disagree" ~ 1, 
               . == "Somewhat disagree" ~ 2,
               . == "Neither agree nor disagree" ~3,
               . == "Somewhat agree" ~ 4,
               . == "Strongly agree" ~ 5))) %>%

# reverse code for likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_S","K_E"))), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                               . == "Somewhat disagree" ~ 4,
                                                               . == "Neither agree nor disagree" ~3,
                                                               . == "Somewhat agree" ~ 2,
                                                               . == "Strongly agree" ~ 1))) %>%

# code eco-pol scale variables into numbers
  mutate_at(vars(SYSTEMDEMO,SYSTEMRELIGION,SYSTEMTECHNO,SYSTEMTOTAL,WEALTHLIM,MECHANISATION,DECISIONDECEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG), funs(case_when(. == "Strongly disagree" ~ 1, 
                        . == "Somewhat disagree" ~ 2,
                        . == "Neither agree nor disagree" ~3,
                        . == "Somewhat agree" ~ 4,
                        . == "Strongly agree" ~ 5))) %>%

# reverse code eco-pol scale variables into numbers 
 mutate_at(vars(DECISIONCEN, INDUSTRYSMALL, ECONOMYLOCAL, ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                                                                         . == "Somewhat disagree" ~ 4,
                                                                                                         . == "Neither agree nor disagree" ~3,
                                                                                                         . == "Somewhat agree" ~ 2,
                                                                                                         . == "Strongly agree" ~ 1))) %>%
  mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
  mutate_all(~ifelse(. == "West bengal", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "WEST BENGAL", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "Up", "Uttar Pradesh", .))%>%
  mutate_all(~ifelse(. == "Tamilnadu", "Tamil Nadu", .))%>%
  mutate_all(~ifelse(. == "UP", "Uttar Pradesh", .))

```

```{r, eval=TRUE, echo=FALSE}

moduleone <- read_excel(here::here("thesis_surveydata/livelihood_insecurity_complete.xlsx"))
module1 <- data.frame(moduleone)
# loaded data set for module 2 eco -pol variables and removes the rows with question number and question text
```

```{r, eval =TRUE, echo=FALSE}
#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
codedmodule1 <- module1 %>%

#remove row 1 and 2 
  filter(!row_number() %in% c(1,2)) %>%

# replace risky likert scale with numbers
  mutate_at(vars(starts_with("Risky")), funs(case_when(. =="Not at all risky" ~ 1, 
                                                       . =="Slightly risky" ~ 2, 
                                                       . =="Moderately risky" ~ 3, 
                                                       . =="Very risky" ~ 4, 
                                                       . =="Extremely risky" ~ 5))) %>%

# replace beneficial likert scale with numbers  
  mutate_at(vars(starts_with("Ben")), funs(case_when(. =="Not at all beneficial" ~ 1,
                                                     . =="Slightly beneficial" ~ 2,
                                                     . =="Moderately beneficial" ~ 3,
                                                     . =="Very beneficial" ~ 4,
                                                     . =="Extremely beneficial" ~ 5 ))) %>%

# replace nuclear acceptance likert scale with numbers
  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                                        . == "Somewhat disagree" ~ 2,
                                                                        . == "Neither agree nor disagree" ~3,
                                                                        . == "Somewhat agree" ~ 4,
                                                                        . == "Strongly agree" ~ 5)))%>%
  mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
  mutate_all(~ifelse(. == "West bengal", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "WEST BENGAL", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "Up", "Uttar Pradesh", .))%>%
  mutate_all(~ifelse(. == "Tamilnadu", "Tamil Nadu", .))%>%
  mutate_all(~ifelse(. == "UP", "Uttar Pradesh", .))

```

```{r, echo = FALSE}

suppressPackageStartupMessages(library(tidyselect))
# combine codedmodule1 and codedmodule2

numcol2 <- codedmodule2 %>% add_column(Respondent = 1:1099, .before = "Language") 
numcol1 <- codedmodule1 %>% add_column(Respondent = 1099:2160, .before = "Language")

joineddf <-  full_join(numcol2, numcol1, by = c("Respondent", "Language", "Survey_Date", "State", "Risky_Hydro", "Risky_Solar", "Risky_Wind", "Risky_Nuclear", "Risky_Coal", "Risky_Gas", "Risky_Oil", "Risky_INDHydro", "Risky_INDSolar", "Risky_INDWind", "Risky_INDBiogas", "Risky_INDDiesel", "Risky_INDKerosene", "Risky_INDFirewoodetc", "Risky_INDLPG", "Ben_Hydro", "Ben_Solar", "Ben_Wind", "Ben_Nuclear", "Ben_Coal", "Ben_Gas", "Ben_Oil", "Ben_INDHydro", "Ben_INDSolar", "Ben_INDWind", "Ben_INDDiesel", "Ben_INDBiogas", "Ben_INDFirewoodetc", "Ben_INDLPG", "Ben_INDKerosene", "N_accept", "N_reluctantlyaccept", "N_reject", "age", "urban_rural", "gender", "caste", "religion", "religiontext"))

numcolb <- module2 %>%   filter(!row_number() %in% c(1,2))%>% 
                        add_column(Respondent = 1:1099, .before = "Language") 
numcola <- module1 %>%   filter(!row_number() %in% c(1,2)) %>% 
                        add_column(Respondent = 1099:2160, .before = "Language")

uncodedjoineddf <- full_join(numcolb, numcola, by = c("Respondent", "Language", "Survey_Date", "State", "Risky_Hydro", "Risky_Solar", "Risky_Wind", "Risky_Nuclear", "Risky_Coal", "Risky_Gas", "Risky_Oil", "Risky_INDHydro", "Risky_INDSolar", "Risky_INDWind", "Risky_INDBiogas", "Risky_INDDiesel", "Risky_INDKerosene", "Risky_INDFirewoodetc", "Risky_INDLPG", "Ben_Hydro", "Ben_Solar", "Ben_Wind", "Ben_Nuclear", "Ben_Coal", "Ben_Gas", "Ben_Oil", "Ben_INDHydro", "Ben_INDSolar", "Ben_INDWind", "Ben_INDDiesel", "Ben_INDBiogas", "Ben_INDFirewoodetc", "Ben_INDLPG", "Ben_INDKerosene", "N_accept", "N_reluctantlyaccept", "N_reject", "age", "urban_rural", "gender", "caste", "religion", "religiontext")) %>%
  mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
  mutate_all(~ifelse(. == "West bengal", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "WEST BENGAL", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "Up", "Uttar Pradesh", .))%>%
  mutate_all(~ifelse(. == "Tamilnadu", "Tamil Nadu", .))%>%
  mutate_all(~ifelse(. == "UP", "Uttar Pradesh", .))

```

\newpage
# State Specific Differences.

We see huge differences for perceived risk and perceived benefit for each technology from state to state. These graphs explore that. 
The number of respondents from each state are also reported below.

## Perceived risk by State

```{r, echo=FALSE, fig.width=11, fig.height=14, out.width='80%', out.height='80%'}

# part 2: state specific data on perceived risk
state_risk <- uncodedjoineddf %>%
    dplyr::select(starts_with(c("RISKY", "State")))%>%
    gather(Technology, Perceived_Risk, Risky_Hydro:Risky_INDLPG, factor_key = TRUE)%>%
    separate(Technology, c("Risky", "Technology"), extra = "merge", fill = "left")%>%
    dplyr::select(-Risky) %>% 
    group_by(State, Technology, Perceived_Risk) %>%
    dplyr::summarise(n=n())

count<- uncodedjoineddf %>%
  dplyr::select(starts_with(c("RISKY", "State")))%>%
   group_by(State) %>%
  dplyr::summarise(n=n())

 state_risk_percent <- state_risk %>%
    group_by(Technology, State) %>%
    mutate(Percentage = round(n/sum(n)*100, 0)) %>%
    ungroup()

 # Create a named vector with the number of respondents for each state
respondents_per_state <- c("Maharashtra" = 653, "Rajasthan" = 677, "Tamil Nadu" = 320, "Uttar Pradesh" = 125, "West Bengal" = 386)

respondents_per_state

state_risk %>% ggplot(aes(fill= fct_rev(factor(Perceived_Risk, levels=c("Extremely risky", "Very risky","Moderately risky","Slightly risky","Not at all risky","Rather not say/Don't know"))), y=n , x=Technology)) + 
    geom_bar(position="fill",stat="identity")+
     geom_text(data = state_risk_percent, aes(label=paste0(Percentage, "%"), y=n), position = position_fill(vjust=0.5), size=5) +
    scale_x_discrete(limits = c("Solar", "Wind" ,"Hydro", "Oil", "Coal","Gas", "Nuclear"))+
    scale_fill_manual("legend", values = c("Extremely risky" = "#8C4646", "Very risky" = "#D9695F", "Moderately risky" = "#F2A679", "Slightly risky" = "#F2D091","Not at all risky" = "#5D8C7B", "Rather not say/Don't know" = "grey94"))+
    theme_classic()+ 
    facet_wrap(~ State, ncol = 2)+
    labs(x = "mean perceived risk", y = "energy technologies")+
    theme(axis.text.x = element_text(angle = 45, hjust = 1))+
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size=12),  # Increase x-axis text size
        axis.text.y = element_text(size=12),  # Increase y-axis text size
        strip.text = element_text(size=12))  # Increase facet label text size

```

\newpage

## Perceived Benefit by State

```{r, echo=FALSE, fig.width=12, fig.height=15, out.width='100%', out.height='100%'}
# part 2: state specific data on perceived benefit

state_ben <- uncodedjoineddf %>%
  dplyr::select(starts_with(c("Ben", "State")))%>%
  gather(Technology, Perceived_Benefit, Ben_Hydro:Ben_INDKerosene, factor_key = TRUE)%>%
  separate(Technology, c("Ben", "Technology"), extra = "merge", fill = "left")%>%
  dplyr::select(-Ben) %>% 
  group_by(State, Technology, Perceived_Benefit) %>%
  dplyr::summarise(n=n())

countben<- uncodedjoineddf %>%
  dplyr::select(starts_with(c("Ben", "State")))%>%
   group_by(State) %>%
  dplyr::summarise(n=n())

 # Create a named vector with the number of respondents for each state
respondents_per_state <- c("Maharashtra" = 653, "Rajasthan" = 677, "Tamil Nadu" = 320, "Uttar Pradesh" = 125, "West Bengal" = 386)

respondents_per_state

# Calculate percentages in each group
state_ben_percent <- state_ben %>%
  group_by(Technology, State) %>%
  mutate(Percentage = round(n/sum(n)*100, 0)) %>%
  ungroup()

#perceived benefit centrally owned technologies by state
state_ben %>% ggplot(aes(fill= factor(Perceived_Benefit, levels=c("Rather not say/Don't know","Not at all beneficial","Slightly beneficial","Moderately beneficial","Very beneficial", "Extremely beneficial")), y=n , x=Technology)) + 
  geom_bar(position="fill", stat = "identity")+
  geom_text(data = state_ben_percent, aes(label=paste0(Percentage, "%"), y=n), position = position_fill(vjust=0.5), size=5) +
  scale_fill_manual("legend", values = c("Rather not say/Don't know" = "grey94" ,"Not at all beneficial" = "orange","Slightly beneficial"="yellow" ,"Moderately beneficial" = "palegreen","Very beneficial"= "green3", "Extremely beneficial"= "green4"))+
  scale_x_discrete(limits = c("Solar", "Wind", "Hydro", "Oil", "Coal","Gas","Nuclear"))+
  theme_classic()+
  facet_wrap(~ State, ncol = 2)+
  labs(x = "mean perceived benefit", y = "energy technologies")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size=12), 
        axis.text.y = element_text(size=12), 
        strip.text = element_text(size=12))

```

```{r}
staterisky <- joineddf %>%
  dplyr::select(!starts_with(c("Ben_IND", "Risky_IND")))%>%
  dplyr::select(starts_with("Risky"), State)

staterisky_mean <- staterisky %>%
  group_by(State) %>%
  summarise(
    Mean_Risky_Hydro = mean(Risky_Hydro, na.rm = TRUE),
    Mean_Risky_Solar = mean(Risky_Solar, na.rm = TRUE),
    Mean_Risky_Wind = mean(Risky_Wind, na.rm = TRUE),
    Mean_Risky_Nuclear = mean(Risky_Nuclear, na.rm = TRUE),
    Mean_Risky_Coal = mean(Risky_Coal, na.rm = TRUE),
    Mean_Risky_Gas = mean(Risky_Gas, na.rm = TRUE),
    Mean_Risky_Oil = mean(Risky_Oil, na.rm = TRUE)
  )

str(staterisky_mean)

# Load required packages
library(dplyr)
library(tidyr)
library(ggplot2)

# Convert to long format
long_data <- staterisky_mean %>%
  gather(Technology, Mean_Score, -State) %>%
  mutate(Technology = gsub("Mean_Risky_", "", Technology))

# Order Technologies
technology_order <- c("Nuclear", "Gas", "Coal", "Oil", "Hydro", "Wind", "Solar")
long_data$Technology <- factor(long_data$Technology, levels = technology_order)

# Plot the graph
ggplot(long_data, aes(x = Technology, y = Mean_Score, color = State, group = State)) +
  geom_line(size = 1) +
  geom_point(size = 3) +
  labs(title = "Mean Perceived Risk by State",
       x = "Technology", y = "Mean Score") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

```{r}
# Using dplyr and tidyr

standardized_data <- long_data %>%
  group_by(Technology) %>%
  mutate(
    Overall_Mean = mean(Mean_Score, na.rm = TRUE),
    Std_Dev = sd(Mean_Score, na.rm = TRUE)
  ) %>%
  ungroup() %>%
  mutate(Standardized_Score = (Mean_Score - Overall_Mean) / Std_Dev) %>%
  dplyr::select(-Overall_Mean, -Std_Dev)  #

# Order Technologies
technology_order <- c("Nuclear", "Gas", "Coal", "Oil", "Hydro", "Wind", "Solar")
standardized_data$Technology <- factor(standardized_data$Technology, levels = technology_order)

# Plot the graph
ggplot(standardized_data, aes(x = Technology, y = Standardized_Score, color = State, group = State)) +
  geom_line(size = 1) +
  geom_point(size = 3) +
  labs(title = "Standardised Scores of Technologies by State",
       x = "Technology", y = "Z Score") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

```{r}
# Switch roles of State and Technology for plotting
ggplot(standardized_data, aes(x = State, y = Standardized_Score, color = Technology, group = Technology)) +
  geom_line(size = 1) +
  geom_point(size = 3) +
  labs(title = "Standardised Scores of Technologies by State",
       x = "State", y = "Z Score") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

```{r, echo = FALSE}

# combining risk and benefit from each energy technology

acceptance <- joineddf_subset %>%
  na.omit()%>%
  mutate(Nuclear = Ben_Nuclear - Risky_Nuclear,
         Hyrdo = Ben_Hydro - Risky_Hydro,
         Wind = Ben_Wind - Risky_Wind,
         Solar = Ben_Solar - Risky_Solar,
         Coal = Ben_Coal - Risky_Coal,
         Gas = Ben_Gas - Risky_Gas,
         Oil = Ben_Oil - Risky_Oil)%>%
  select(-starts_with(c("Risky", "Ben")))

#str(acceptance)

# Compute the mean of each column
mean_acceptance <- data.frame(col = names(acceptance), mean_val = sapply(acceptance, mean))

# Compute standard error (not deviation)(divided by root of n)
sem <- function(x) sqrt(var(x, na.rm = TRUE) / length(na.omit(x)))
sem_acceptance <- data.frame(col = names(acceptance), sem_val = sapply(acceptance, sem))

mean_acceptance <- merge(mean_acceptance, sem_acceptance, by = "col")

# Plot
ggplot(mean_acceptance, aes(x = col, y = mean_val, fill = ifelse(mean_val >= 0, 'Above 0', 'Below 0'))) + 
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = mean_val - sem_val, ymax = mean_val + sem_val), width = 0.2) +
  geom_text(aes(label = round(mean_val, 2)), vjust = -0.9) +
  scale_fill_manual(values = c('Above 0' = 'palegreen3', 'Below 0' = 'firebrick2')) +
  labs(fill = "Legend") +
  xlab("Energy Technologies") +
  ylab("Mean Value") +
  ggtitle("Benefit- Risk for Each Energy Technology") +
  theme_minimal()+
  ylim(-0.5, 1.75)

```
\newpage

# Solar Energy - Linear Regression models

```{r, echo=FALSE}

salldemos <- joineddf %>%
            dplyr::select(Risky_Solar,Uppercaste, Male, Hindu, Urban, age, State)%>%
            na.omit()

salldemoslm1 <- lm(Risky_Solar ~ Uppercaste + Male + Hindu + Urban, data = salldemos)
# Print model summary
#summary(salldemoslm1)
#plot(alldemoslm1)

# lm suggests there is no significant white male effect or upper caste male effect for risk perception from nuclear energy in India. 
# the coefficients are very small and so is the r squared - rsquared is minimal.

# 2) lm with all demographic variables
salldemoslm2<- lm(Risky_Solar ~ Uppercaste + Male + Hindu + Urban + age + State, data = salldemos)
# Print model summary
#summary(salldemoslm2)
#plot(alldemoslm1)

```

## Only demographic variables

```{r, echo=FALSE, results='asis'}
library(stargazer)

#stargazer code for all demographic variable lms

cat("\\begingroup")
cat("\\setlength{\\tabcolsep}{1pt}")
cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(salldemoslm1, salldemoslm2, 
          title = "Results from 2 linear regression models",
          type = "latex"
)
cat("\\endgroup")

```

## Kahan Scale

```{r, echo = FALSE}
# kahan scores for solar 
sfascales <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_","Risky_Solar","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACESOLAR",  "POLLUTESOLAR", "HEALTHSOLAR", "JOBSSOLAR", "BEAUTYSOLAR", "PRIDESOLAR", "NPRIDESOLAR", "DEVSOLAR", "PROSPERSOLAR", "RELYSOLAR", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%
  na.omit()

sKahan_fas <- '
  KahanS =~ K_SHARM + K_SLIMCHOI + K_SPROTECT 
  KahanH =~ K_HEQUAL+ K_ERADEQ1 + K_EWEALTH + K_ERADEQ2
'

# Run CFA
sKahan_cfa <- cfa(sKahan_fas, data = sfascales, std.lv = TRUE)

# Print the summary of the CFA results, including fit measures
#summary(sKahan_cfa, fit.measure= TRUE, standardized = TRUE)

# RMSEA - between 0.05 and 0.08 (reasonable fit), less than 0.05 close fit and greater than 0.10 is poor fit 
# CFI - greater than 0.90 or 0.95 indicates good fit
#TFI - CFI>TFI >0.90 - indicates good fit
#pvalue should be greater than 0.05 p > 0.0.5

# creating table of factor scores

sKahan_scores <- predict(sKahan_cfa, newdata = sfascales)

sKahan_Kscores <- cbind(sfascales, sKahan_scores)

# 3) lm with kahan 
sm1_kahan <- lm(Risky_Solar ~ Uppercaste + Male + Hindu + Urban + age + State + KahanS + KahanH , data = sKahan_Kscores)
# Print model summary
#summary(sm1_kahan)
#plot(sm1_kahan)

```

```{r, echo=FALSE, results='asis'}
library(stargazer)

cat("\\begingroup")
cat("\\setlength{\\tabcolsep}{1pt}")
cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(salldemoslm1, salldemoslm2, sm1_kahan,
          title = "Results from 3 linear regression models",
          type = "latex"
)
cat("\\endgroup")

```

\newpage

# Coal

```{r, echo=FALSE}

calldemos <- joineddf %>%
            dplyr::select(Risky_Coal,Uppercaste, Male, Hindu, Urban, age, State)%>%
            na.omit()

calldemoslm1 <- lm(Risky_Coal ~ Uppercaste + Male + Hindu + Urban, data = calldemos)
# Print model summary
#summary(salldemoslm1)
#plot(alldemoslm1)

# lm suggests there is no significant white male effect or upper caste male effect for risk perception from nuclear energy in India. 
# the coefficients are very small and so is the r squared - rsquared is minimal.

# 2) lm with all demographic variables
calldemoslm2<- lm(Risky_Coal ~ Uppercaste + Male + Hindu + Urban + age + State, data = calldemos)
# Print model summary
#summary(salldemoslm2)
#plot(alldemoslm1)

```

## Only demographic variables

```{r, echo=FALSE, results='asis'}
library(stargazer)

#stargazer code for all demographic variable lms

cat("\\begingroup")
cat("\\setlength{\\tabcolsep}{1pt}")
cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(calldemoslm1, calldemoslm2, 
          title = "Results from 2 linear regression models",
          type = "latex"
)
cat("\\endgroup")

```

## Kahan Scale

```{r, echo = FALSE}
# kahan scores for solar 
cfascales <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_","Risky_Coal","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACESOLAR",  "POLLUTESOLAR", "HEALTHSOLAR", "JOBSSOLAR", "BEAUTYSOLAR", "PRIDESOLAR", "NPRIDESOLAR", "DEVSOLAR", "PROSPERSOLAR", "RELYSOLAR", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%
  na.omit()

cKahan_fas <- '
  KahanS =~ K_SHARM + K_SLIMCHOI + K_SPROTECT 
  KahanH =~ K_HEQUAL+ K_ERADEQ1 + K_EWEALTH + K_ERADEQ2
'

# Run CFA
cKahan_cfa <- cfa(cKahan_fas, data = cfascales, std.lv = TRUE)

# Print the summary of the CFA results, including fit measures
#summary(sKahan_cfa, fit.measure= TRUE, standardized = TRUE)

# RMSEA - between 0.05 and 0.08 (reasonable fit), less than 0.05 close fit and greater than 0.10 is poor fit 
# CFI - greater than 0.90 or 0.95 indicates good fit
#TFI - CFI>TFI >0.90 - indicates good fit
#pvalue should be greater than 0.05 p > 0.0.5

# creating table of factor scores

cKahan_scores <- predict(cKahan_cfa, newdata = cfascales)

cKahan_Kscores <- cbind(cfascales, cKahan_scores)

# 3) lm with kahan 
cm1_kahan <- lm(Risky_Coal ~ Uppercaste + Male + Hindu + Urban + age + State + KahanS + KahanH , data = cKahan_Kscores)
# Print model summary
#summary(cm1_kahan)
#plot(cm1_kahan)

```

```{r, echo=FALSE, results='asis'}
library(stargazer)

cat("\\begingroup")
cat("\\setlength{\\tabcolsep}{1pt}")
cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(calldemoslm1, calldemoslm2, cm1_kahan,
          title = "Results from 3 linear regression models",
          type = "latex"
)
cat("\\endgroup")

```

### 2023-09-20 module1/moduleoneanalysis.Rmd
changing regional scripts to english in excel file

@@
 drinkingwater   	What is the main source of drinking water for the members of your household?
-cookingwater      What is the main source of water used by your\r\nhousehold for other purposes such as cooking and\r\nhandwashing?
-farwatermins      How long does it take to go there, get water, and come\r\nback? 
-toilet            What kind of toilet facility do members of your\r\nhousehold usually use?
+cookingwater      What is the main source of water used by your household for other purposes such as cooking and handwashing?
+farwatermins      How long does it take to go there, get water, and come back? 
+toilet            What kind of toilet facility do members of your nhousehold usually use?
 house

### 2023-09-20 module1/moduleoneanalysis.Rmd
modificationd for better pdf output

@@
 
-```{r load packages, warning = FALSE, message = FALSE}
+```{r load packages, warning = FALSE, message = FALSE, echo=FALSE}
 suppressPackageStartupMessages(library(tidyverse))
@@
 
-colnames(codedmodule1)
 addedcols <- codedmodule1 %>%
@@
 
-codedmodule1 %>% count(Livelihood_Income)
-addedcols %>% count(Livelihood_Income)
-codedmodule1 %>% count(Lfarmbigha)
-codedmodule1 %>% filter(Livelihood_Income == "LSI") %>% count(Lfarmland)
-addedcols %>% filter(Livelihood_Income == "LSI") %>% count(animals)
-codedmodule1 %>% count(Lboat)
+#codedmodule1 %>% count(Livelihood_Income)
+#addedcols %>% count(Livelihood_Income)
+#codedmodule1 %>% count(Lfarmbigha)
+#codedmodule1 %>% filter(Livelihood_Income == "LSI") %>% count(Lfarmland)
+#addedcols %>% filter(Livelihood_Income == "LSI") %>% count(animals)
+#codedmodule1 %>% count(Lboat)
 
-addedcols %>% filter(Livelihood_Income == "LSI") %>% filter(Lfarmland == "Doesn't apply") %>% count(Lboat)
-addedcols %>% filter(Livelihood_Income == "LSI") %>% filter(Lfarmland == "Doesn't apply") %>% count(animals)
+#addedcols %>% filter(Livelihood_Income == "LSI") %>% filter(Lfarmland == "Doesn't apply") %>% count(Lboat)
+#addedcols %>% filter(Livelihood_Income == "LSI") %>% filter(Lfarmland == "Doesn't apply") %>% count(animals)
 
-addedcols %>% filter(Livelihood_Income == "ISI") %>% count(Iproperty)
+#addedcols %>% filter(Livelihood_Income == "ISI") %>% count(Iproperty)
 
@@
 
-module1 %>% filter(!row_number() %in% c(1,2)) %>% filter(Livelihood_Income != "(a) own farming/fishing/animal rearing/business") %>% count(Iproperty)
+#module1 %>% filter(!row_number() %in% c(1,2)) %>% filter(Livelihood_Income != "(a) own farming/fishing/animal rearing/business") %>% count(Iproperty)
 
@@
 # first make two different groups in the data by Livelihood_Income variable. - homemaker, ISI, LSI, other (retired, student, unable to work, unemployed)
-
-str(nuclear_LI)
 
@@
 
-summary(nuclearLI_lm)
-summary(nuclearLI_lm2)
 #plot(nuclearLI_lm)
@@
 # Displaying the first few rows of the dataframe
-head(solar_LI)
 
@@
 solarLI_lm2 <- lm(Risky_Solar ~ caste + gender + urban_rural + LIscore , data = solar_model)
-summary(solarLI_lm)
-summary(solarLI_lm2)
 #plot(solarLI_lm)
@@
 
-summary(coalLI_lm)
-summary(coalLI_lm2)
 #plot(coalLI_lm)
@@
 # Print the summary of the CFA results, including fit measures
-summary(JIS_cfa, fit.measure= TRUE, standardized = TRUE)
+#summary(JIS_cfa, fit.measure= TRUE, standardized = TRUE)
 
@@
 JIS_lm1 <- lm(Risky_Nuclear ~ caste + gender + urban_rural+ JIS_scores, data = JIS_Jscores)
-
-summary(JIS_lm1)
 
@@
 
-\newpage
-
-#Extra
-
 ```{r, echo = FALSE}
@@
 ##checking stuff
-codedmodule1
 
-codedmodule1 %>%
-  filter(Livelihood_Income == "LSI") %>%
-  count(Lfarmland)
-codedmodule1 %>%
-  count(Iproperty)
+#codedmodule1 %>%
+  #filter(Livelihood_Income == "LSI") %>%
+  #count(Lfarmland)
+#codedmodule1 %>%
+  #count(Iproperty)
 
-lapply(codedmodule1, unique)
-ncol(codedmodule1)
-colnames(codedmodule1)
+#lapply(codedmodule1, unique)
 
-str(codedmodule1)
+#str(codedmodule1)
 
 ```
+
+\newpage
 

### 2024-01-15 FAoptions.Rmd
commiting after a long time. oh god

@@
 title: "FAoptions"
+header-includes:
+- \usepackage{pdflscape}
+- \newcommand{\blandscape}{\begin{landscape}}
+- \newcommand{\elandscape}{\end{landscape}}
 output:
-  word_document: null
+  pdf_document: 
+    toc: yes
+    toc_depth: 2
+    keep_tex: yes
   keep_md: yes
@@
 suppressPackageStartupMessages(library(psych))
+suppressPackageStartupMessages(library(lavaan))
 library(officer)
@@
 # code likert scale for variables for Kahan scale into numbers
-  mutate_at(vars(starts_with (c("K_I","K_H","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE", "DEV", "PROSPER", "RELY"))), funs(case_when(. == "Strongly disagree" ~ 1, 
+  mutate_at(vars(starts_with (c("K_S","K_H","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE", "DEVNUCLEAR","DEVSOLAR", "DEVCOAL", "PROSPER", "RELY"))), funs(case_when(.
+== "Strongly disagree" ~ 1,
                . == "Somewhat disagree" ~ 2,
@@
 # reverse code for likert scale for variables for Kahan scale into numbers
-mutate_at(vars(starts_with (c("K_S","K_E"))), funs(case_when(. == "Strongly disagree" ~ 5, 
+mutate_at(vars(starts_with (c("K_I","K_E"))), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                                . == "Somewhat disagree" ~ 4,
@@
 
-# reverse code eco-pol scale variables into numbers 
- mutate_at(vars(DECISIONCEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG), funs(case_when(. == "Strongly disagree" ~ 5, 
-                                                                                                         . == "Somewhat disagree" ~ 4,
+# no - reverse code eco-pol scale variables into numbers 
+ mutate_at(vars(DECISIONCEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG, DEVOVERENV), funs(case_when(. == "Strongly disagree" ~ 1, 
+                                                                                                         . == "Somewhat disagree" ~ 2,
                                                                                                          . == "Neither agree nor disagree" ~3,
-                                                                                                         . == "Somewhat agree" ~ 2,
-                                                                                                         . == "Strongly agree" ~ 1)))
-```
-
-# Two factor solution is slightly different for Nuclear, Solar and Coal.
-
-## Nuclear
-
-```{r, echo=FALSE}
-
-library(psych)
-library(tidyverse)
-
+                                                                                                         . == "Somewhat agree" ~ 4,
+                                                                                                         . == "Strongly agree" ~ 5)))%>%
+  mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
+  mutate_all(~ifelse(. == "West bengal", "West Bengal", .))%>%
+  mutate_all(~ifelse(. == "WEST BENGAL", "West Bengal", .))%>%
+  mutate_all(~ifelse(. == "Up", "Uttar Pradesh", .))%>%
+  mutate_all(~ifelse(. == "Tamilnadu", "Tamil Nadu", .))%>%
+  mutate_all(~ifelse(. == "UP", "Uttar Pradesh", .))%>%
+  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
+                                      . == "25-34 years old" ~ 2,
+                                      . ==  "35-44 years old" ~3,
+                                      . == "45-54 years old" ~ 4,
+                                      . == "55-64 years old" ~ 5,
+                                      . == "65-74 years old" ~ 6,
+                                      . == "75 years or older" ~ 7)))
+```
+
+```{r, echo = FALSE}
+
+#sort demo vars
+
+codedmodule2$State <- as.factor(codedmodule2$State)
+codedmodule2$gender <- as.factor(codedmodule2$gender)
+codedmodule2$Urban <- as.factor(codedmodule2$urban_rural)
+
+codedmodule2$caste <- as.factor(codedmodule2$caste)
+codedmodule2$religion <- as.factor(codedmodule2$religion)
+# # Convert `caste` into binary variable 'upper' (1) vs 'non-upper' (0)
+codedmodule2$Uppercaste <- ifelse(codedmodule2$caste %in% c('Brahmin', 'General'), 1, 0)
+# Convert `gender` into binary variable 'male' (1) vs 'female' (0)
+codedmodule2$Male <- ifelse(codedmodule2$gender == 'Male', 1, 0)
+# Convert `religion` into binary variable 'Hinduism' (1) vs 'Non-Hinduism' (0)
+codedmodule2$Hindu <- ifelse(codedmodule2$religion == 'Hinduism', 1, 0)
+
+codedmodule21 <- codedmodule2 %>%
+            dplyr::select(Risky_Nuclear, Risky_Solar, Risky_Coal, Uppercaste, Male, Hindu, Urban, age, State) %>%
+            na.omit()
+
+# lm on nuclear energy with all demovars
+
+alldemos <- codedmodule21 %>%
+            dplyr::select(Risky_Nuclear, Uppercaste, Male, Hindu, Urban, age, State) %>%
+  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
+                                      . == "25-34 years old" ~ 2,
+                                      . ==  "35-44 years old" ~3,
+                                      . == "45-54 years old" ~ 4,
+                                      . == "55-64 years old" ~ 5,
+                                      . == "65-74 years old" ~ 6,
+                                      . == "75 years or older" ~ 7)))
+```
+
+```{r, echo=FALSE}
 fascales <- codedmodule2 %>%
-  dplyr::select(starts_with(c("K_","Risky_Nuclear","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%
+  dplyr::select(starts_with(c("K_","Risky_Nuclear","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR","SYSTEMDEMO","SYSTEMRELIGION", "SYSTEMTECHNO","SYSTEMTOTAL", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%
   mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
@@
   na.omit()
+```
+
+```{r, echo=FALSE}
+# Q6: Does the Kahan scale explain perception of risk from nuclear energy and other DVs ?
+
+# we conducted fa on the kahan scale 
+# CFA for Kahan scale. We shouldn't do FA here since this a well used scale with theoretical basis for factor distinctions and also previous studies using the same scale
+
+library(lavaan)
+library(semTools)
+library(kableExtra)
+
+fascales <- codedmodule2 %>%
+  filter(
+    rowSums(is.na(dplyr::select(., starts_with("K_")))) == 0 &  # This line ensures that rows with any NA in columns starting with         "K_" are   filtered out.
+    !is.na(WEALTHLIM) & 
+    !is.na(MECHANISATION) & 
+    !is.na(DECISIONDECEN) & 
+    !is.na(DECISIONCEN) & 
+    !is.na(INDUSTRYLARGE) & 
+    !is.na(INDUSTRYSMALL) & 
+    !is.na(ECONOMYGLOBAL) & 
+    !is.na(ECONOMYLOCAL) & 
+    !is.na(ENVOVERDEV) & 
+    !is.na(DEVOVERENV) & 
+    !is.na(OWNERPVT) & 
+    !is.na(OWNERNOREG) & 
+    !is.na(OWNERPUB) & 
+    !is.na(OWNERREG) & 
+    !is.na(DISPLACENUCLEAR) & 
+    !is.na(POLLUTENUCLEAR) & 
+    !is.na(HEALTHNUCLEAR) & 
+    !is.na(JOBSNUCLEAR) & 
+    !is.na(BEAUTYNUCLEAR) & 
+    !is.na(PRIDENUCLEAR) & 
+    !is.na(NPRIDENUCLEAR) & 
+    !is.na(DEVNUCLEAR) & 
+    !is.na(PROSPERNUCLEAR) & 
+    !is.na(RELYNUCLEAR)
+  )
+
+fascales2 <- codedmodule2 %>%dplyr::select(starts_with(c("K_","Risky_Nuclear","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%na.omit()
+
+Kahan_fas <- '
+  KahanS =~ K_SHARM + K_SLIMCHOI + K_SPROTECT 
+  KahanH =~ K_HEQUAL+ K_ERADEQ1 + K_EWEALTH + K_ERADEQ2
+'
+
+# Run CFA
+Kahan_cfa <- cfa(Kahan_fas, data = fascales, std.lv = TRUE)
+
+# Print the summary of the CFA results, including fit measures
+#summary(Kahan_cfa, fit.measure= TRUE, standardized = TRUE)
+
+# RMSEA - between 0.05 and 0.08 (reasonable fit), less than 0.05 close fit and greater than 0.10 is poor fit 
+# CFI - greater than 0.90 or 0.95 indicates good fit
+#TFI - CFI>TFI >0.90 - indicates good fit
+#pvalue should be greater than 0.05 p > 0.0.5
+
+# after having removed a few variables that had very low loading, the model is now a good fit, we have two latent variables - Hierarchy- egalitarian and Communitarian.
+Again we see that individualistic variables just don't fit here.
+
+# creating table of factor scores
+
+Kahan_scores <- predict(Kahan_cfa, newdata = fascales)
+
+Kahan_Kscores <- cbind(fascales, Kahan_scores)
+
+## RMSEA is still pretty big.
+
+```
+
+```{r, echo = FALSE}
+
+# the psych code for FA on eco-pol scale for nuclear energy - all vars combined
+
+library(psych)
+library(tidyverse)
+
 ecopolall <- fascales %>%
-        dplyr::select("WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR")%>%
+        dplyr::select("WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "RELYNUCLEAR","PROSPERNUCLEAR", "JOBSNUCLEAR")%>%
     rename(
-      "Limits on Wealth " = "WEALTHLIM",
+      "Limits on Wealth" = "WEALTHLIM",
       "Anti Mechanisation of work" = "MECHANISATION",
@@
       "Pro Large Industries" = "INDUSTRYLARGE",
-      "Anti Large Industries " = "INDUSTRYSMALL",
+      "Anti Large Industries" = "INDUSTRYSMALL",
       "Pro Globaleconomy" = "ECONOMYGLOBAL",
@@
       "Development over Environment" = "DEVOVERENV",
-      "Pro Private ownership " = "OWNERPVT",
+      "Pro Private ownership" = "OWNERPVT",
       "Anti Regulations" = "OWNERNOREG",
@@
       "Displacement risk(nuclear)" = "DISPLACENUCLEAR",
-      "Pollution risk(nuclear) " = "POLLUTENUCLEAR",
+      "Pollution risk(nuclear)" = "POLLUTENUCLEAR",
       "Health risk(nuclear)" = "HEALTHNUCLEAR",
@@
       "Spoils Natural Beauty(nuclear)" = "BEAUTYNUCLEAR",
+      "Local prosperity(nuclear)" = "PROSPERNUCLEAR",
       "Community pride(nuclear)" = "PRIDENUCLEAR",
@@
       "National development(nuclear)" = "DEVNUCLEAR",
-      "Local prosperity(nuclear)" = "PROSPERNUCLEAR",
       "Reliance on government(nuclear)" = "RELYNUCLEAR"
@@
 
-```
+#print.psych(ecopolall2.fa, cut = 0.4, sort = TRUE)
+
+ecopol_fas <- '
+  Pdevelop =~ HEALTHNUCLEAR + BEAUTYNUCLEAR + DISPLACENUCLEAR + POLLUTENUCLEAR + INDUSTRYSMALL + OWNERREG + MECHANISATION
+  Ndevelop =~ DEVNUCLEAR + PROSPERNUCLEAR + PRIDENUCLEAR + NPRIDENUCLEAR + JOBSNUCLEAR
+'
+ecopol_cfa <- cfa(ecopol_fas, data = fascales, std.lv = TRUE)
+#summary(ecopol_cfa, fit.measure= TRUE, standardized = TRUE)
+
+```
+
+\blandscape
+# FA on Combined Scale (2 Factor Solution): People Centered Development and Nationalist Development 
+## Nuclear Energy: EFA on Combined Scale (2 Factor Solution)
 
@@
 
-set_flextable_defaults(docx.landscape = TRUE)
-
-flex <- function(data, title=NULL) {
-  # this grabs the data and converts it to a flextbale
-  flextable(data) %>%
-  # this makes the table fill the page width
-  set_table_properties(layout = "autofit", width = 1) %>%
-  # font size
+flex <- function(data, title=NULL, col_widths=NULL) {
+  tbl <- flextable(data) %>%
+           #padding(padding = 1, part = "all") %>%
+           #set_table_properties(layout = "autofit") %>%
            fontsize(size=10, part="all") %>%
-    #this adds a ttitlecreates an automatic table number
            set_caption(title, 
@@
                                                       post_label = "\n", 
-                                                 bkm = "anytable")) #%>%
-  # font type
-  #font(fontname="Times New Roman", part="all")
+                                                      bkm = "anytable"))
+
+  # If col_widths is provided, set column widths
+  if(!is.null(col_widths)) {
+    for(col in names(col_widths)){
+      tbl <- width(tbl, j = col, width = col_widths[[col]])
+    }
+  }
+
+  return(tbl)
 }
@@
   "Pro Public ownership" = "The government should own most large businesses and industries",
-  "Pro Regulations" = " Regardless of ownership, the government should pass strong regulations and implement them",
+  "Pro Regulations" = "Regardless of ownership, the government should pass strong regulations and implement them",
   "Displacement risk(nuclear)" = "Nuclear energy is leading to displacement of people from their land",
@@
     ) %>%
-    select(code, everything()) # reorder columns to bring code to the front
+    dplyr::select(code, everything()) # reorder columns to bring code to the front
 }
@@
   rename(Pdevelop = MR1, Ndevelop = MR2, Items= item) %>%
-  flex("2 factor solution") %>%
-  autofit()
-
-```
+  flex("2 factor solution", col_widths = list(Items = 4.5, code = 1.5))
+
+```
+
+\elandscape
 
@@
     mutate(across(where(is.numeric), round, 3)) %>%
-    flex("Eigenvalues and Variance Explained for 2 Factor Solution")
-```
-
-\newpage
-## Solar
+    flex("Eigenvalues and Variance Explained for Combined Scale (2 Factor Solution)")
+```
+
+```{r, echo=FALSE}
+
+## Nuclear - linear regression with 2 Factor solution
+
+# Linear Model with 2 factor solution for  Risk perception from Nuclear Energy
+
+ecopolall_scores <- psych::factor.scores(ecopolall, ecopolall2.fa)
+
+# The factor scores will be stored in the scores element of the returned list
+scores1 <- ecopolall_scores$scores
+
+#binding factor scores to the dataset
+
+fascale_scores <- cbind(Kahan_Kscores, scores1) %>%
+  rename(Pdevelop = MR1)%>%
+  rename(Ndevelop = MR2)
+
+nuclear2fa <- lm(Risky_Nuclear ~ age + Uppercaste + Male + Hindu + Urban + State + KahanS + KahanH + Pdevelop + Ndevelop, data = fascale_scores)
+
+#m2_allscales <- lm(Risky_Nuclear ~ age + Uppercaste + Male + Hindu + Urban +State+ KahanS + KahanH + NPRIDENUCLEAR + PRIDENUCLEAR + DEVNUCLEAR + PROSPERNUCLEAR, data = fascale_scores)
+# Print model summary
+#summary(nuclear2fa)
+
+```
+```{r,echo = FALSE}
+acceptance2 <- fascale_scores %>%
+  mutate(Nuclear = Ben_Nuclear - Risky_Nuclear,
+         Hyrdo = Ben_Hydro - Risky_Hydro,
+         Wind = Ben_Wind - Risky_Wind,
+         Solar = Ben_Solar - Risky_Solar,
+         Coal = Ben_Coal - Risky_Coal,
+         Gas = Ben_Gas - Risky_Gas,
+         Oil = Ben_Oil - Risky_Oil)
+
+nuclearacceptlm <- lm(Nuclear ~ age + Uppercaste + Male + Hindu + Urban + State + KahanS + KahanH + Pdevelop + Ndevelop, data = acceptance2)
+
+#m2_allscales <- lm(Risky_Nuclear ~ age + Uppercaste + Male + Hindu + Urban +State+ KahanS + KahanH + NPRIDENUCLEAR + PRIDENUCLEAR + DEVNUCLEAR + PROSPERNUCLEAR, data = fascale_scores)
+# Print model summary
+#summary(nuclearacceptlm)
+
+ggplot(acceptance2, aes(x = Pdevelop, y = Nuclear)) +
+  geom_point() +  # or geom_line() depending on how you want to visualize it
+  facet_wrap(~ State) +  # This will create separate plots for each State
+  labs(title = "Net benefit Nuclear vs Pdevelop by State",
+       x = "Pdevelop",
+       y = "net ben Nuclear") +
+  theme_minimal()
+
+```
 
@@
   dplyr::select(starts_with(c("K_","Risky_Solar","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACESOLAR", "POLLUTESOLAR", "HEALTHSOLAR", "JOBSSOLAR", "BEAUTYSOLAR", "PRIDESOLAR", "NPRIDESOLAR", "DEVSOLAR", "PROSPERSOLAR", "RELYSOLAR", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%
-  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
-                                      . == "25-34 years old" ~ 2,
-                                      . ==  "35-44 years old" ~3,
-                                      . == "45-54 years old" ~ 4,
-                                      . == "55-64 years old" ~ 5,
-                                      . == "65-74 years old" ~ 6,
-                                      . == "75 years or older" ~ 7))) %>%
   na.omit()
@@
 
-```{r, echo=FALSE}
-
-library(flextable)
-
-set_flextable_defaults(docx.landscape = TRUE)
-
-flex <- function(data, title=NULL) {
-  # this grabs the data and converts it to a flextbale
-  flextable(data) %>%
-  # this makes the table fill the page width
-  set_table_properties(layout = "autofit", width = 1) %>%
-  # font size
-  fontsize(size=10, part="all") %>%
-    #this adds a ttitlecreates an automatic table number
-      set_caption(title, 
-                  autonum = officer::run_autonum(seq_id = "tab", 
-                                                 pre_label = "Table ", 
-                                                 post_label = "\n", 
-                                                 bkm = "anytable")) #%>%
-  # font type
-  #font(fontname="Times New Roman", part="all")
-}
-
-srename_map <- c(
-  "Limits on Wealth" = "A limit should be put to how much wealth a person can amass",
-  "Anti Mechanisation of work" = "Rapid mechanization of work is taking away jobs from workers in this country",
-  "Pro Decentralisation" = "Local politicians shouldn't have to ask permission from the central government to implement policies",
-  "Pro Centralisation" = "Laws and policies would be implemented more smoothly if more power lay with the central government",
-  "Pro Large Industries" = "Large scale industries are required for the development of the country that will benefit everyone",
-  "Anti Large Industries" = "Large corporations are destroying the local industries in India and benefiting only a handful of people",
-  "Pro Globaleconomy" = "Foreign companies have led to a range of benefits for the Indian people and society",
-  "Pro Localeconomy" = "India would be better off if foreign companies didn't come to here",
-  "Environment over Development" = "Polluting industries that spoil the environment should be shut down even if it costs people their jobs",
-  "Development over Environment" = "Economic growth and creating jobs should be prioritized over environmental protection",
-  "Pro Private ownership" = "All businesses and industries should be owned privately",
-  "Anti Regulations" = "There is too much red-tape and the government should not interfere with businesses and industries",
-  "Pro Public ownership" = "The government should own most large businesses and industries",
-  "Pro Regulations" = "Regardless of ownership, the government should pass strong regulations and implement them",
-  "Displacement risk(solar)" = "Solar energy is leading to displacement of people from their land",
-  "Spoils Natural Beauty(solar)" = "Solar energy spoils the natural beauty of the landscape",
-  "Pollution risk(solar)" = "Solar energy increases pollution of air/water/land",
-  "Health risk(solar)" = "Solar energy poses a great risk to the health of people living around it",
-  "Job opportunities(solar)" = "Solar energy will bring jobs to the local community",
-  "Community pride(solar)" = "I would be proud if my community used solar energy",
-  "National pride(solar)" = "Solar energy is a mark of pride for our nation",
-  "National development(solar)" = "Solar energy pushes forward the country's development",
-  "Local prosperity(solar)" = "Solar energy brings economic prosperity to the surrounding regions",
-  "Reliance on government(solar)" = "I don't like the idea that I have to rely on the government for electricity from solar energy"
-)
-
-fa_table <- function(x, cut) {
-  #get sorted loadings
-  loadings <- fa.sort(x)$loadings %>% round(3)
-  #suppress loadings
-  loadings[loadings > -cut & loadings < cut] <- ""
-  #get additional info  
-  add_info <- cbind(x$communalities, 
-                    x$uniquenesses,
-                    x$complexity) %>%
-    # make it a data frame
-    as.data.frame() %>%
-    # column names
-    rename("Communality" = V1,
-           "Uniqueness" = V2,
-           "Complexity" = V3) %>%
-    #get the item names from the vector
-    rownames_to_column("item")
-
-  #build table
-  loadings %>%
-    unclass() %>%
-    as.data.frame() %>%
-    rownames_to_column("item") %>%
-    left_join(add_info) %>%
-    mutate(
-      item = if_else(item %in% names(srename_map), srename_map[item], item),
-      code = names(srename_map)[match(item, srename_map)], # extracting short form
-      across(where(is.numeric), round, 3)
-    ) %>%
-    select(code, everything()) # reorder columns to bring code to the front
-}
-
-fa_table(secopolall2.fa, .4) %>%
-  #rename(Pdevelop = MR1, Ndevelop = MR2, Items= item) %>%
-  flex("2 factor solution") %>%
-  autofit()
-
-```
-
 ```{r, echo = FALSE}
-secopolall2.fa[["Vaccounted"]] %>%
-  as.data.frame() %>%
-  rownames_to_column("Property") %>%
-  #rename(Pdevelop = MR1, Ndevelop = MR2) %>%
-    mutate(across(where(is.numeric), round, 3)) %>%
-    flex("Solar: Eigenvalues and Variance Explained for 2 Factor Solution")
+
+# SOLAR : CFA on kahan scale and eco-pol scale
+
+# kahan scores for solar 
+sfascales <- codedmodule2 %>%
+    filter(
+    rowSums(is.na(dplyr::select(., starts_with("K_")))) == 0 &  # This line ensures that rows with any NA in columns starting with         "K_" are   filtered out.
+    !is.na(WEALTHLIM) & 
+    !is.na(MECHANISATION) & 
+    !is.na(DECISIONDECEN) & 
+    !is.na(DECISIONCEN) & 
+    !is.na(INDUSTRYLARGE) & 
+    !is.na(INDUSTRYSMALL) & 
+    !is.na(ECONOMYGLOBAL) & 
+    !is.na(ECONOMYLOCAL) & 
+    !is.na(ENVOVERDEV) & 
+    !is.na(DEVOVERENV) & 
+    !is.na(OWNERPVT) & 
+    !is.na(OWNERNOREG) & 
+    !is.na(OWNERPUB) & 
+    !is.na(OWNERREG) & 
+    !is.na(DISPLACESOLAR) & 
+    !is.na(POLLUTESOLAR) & 
+    !is.na(HEALTHSOLAR) & 
+    !is.na(JOBSSOLAR) & 
+    !is.na(BEAUTYSOLAR) & 
+    !is.na(PRIDESOLAR) & 
+    !is.na(NPRIDESOLAR) & 
+    !is.na(DEVSOLAR) & 
+    !is.na(PROSPERSOLAR) & 
+    !is.na(RELYSOLAR)
+  )
+
+  #dplyr::select(starts_with(c("K_","Risky_Solar","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACESOLAR",  "POLLUTESOLAR", "HEALTHSOLAR", "JOBSSOLAR", "BEAUTYSOLAR", "PRIDESOLAR", "NPRIDESOLAR", "DEVSOLAR", "PROSPERSOLAR", "RELYSOLAR", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%na.omit()
+
+sKahan_fas <- '
+  KahanS =~ K_SHARM + K_SLIMCHOI + K_SPROTECT 
+  KahanH =~ K_HEQUAL+ K_ERADEQ1 + K_EWEALTH + K_ERADEQ2
+'
+
+# Run CFA
+sKahan_cfa <- cfa(sKahan_fas, data = sfascales, std.lv = TRUE)
+
+# Print the summary of the CFA results, including fit measures
+#summary(sKahan_cfa, fit.measure= TRUE, standardized = TRUE)
+
+sKahan_scores <- predict(sKahan_cfa, newdata = sfascales)
+
+sKahan_Kscores <- cbind(sfascales, sKahan_scores)
+
+sm1_kahan <- lm(Risky_Solar ~ Uppercaste + Male + Hindu + Urban + age + State + KahanS + KahanH , data = sKahan_Kscores)
+
+## CFA on ecopol vars for solar energy
+
+secopol_fas <- '
+  Pdevelop =~ HEALTHSOLAR + BEAUTYSOLAR + DISPLACESOLAR + POLLUTESOLAR + INDUSTRYSMALL + OWNERREG + MECHANISATION
+  Ndevelop =~ DEVSOLAR + PRIDESOLAR + NPRIDESOLAR + PROSPERSOLAR
+'
+
+secopol_cfa <- cfa(secopol_fas, data = sfascales, std.lv = TRUE)
+summary(secopol_cfa, fit.measure= TRUE, standardized = TRUE)
+
+# Cronbach's alpha test on Pdevelop and Ndevelop for Solar energy
+
+solarpdevelop <- sfascales %>%
+  dplyr::select(HEALTHSOLAR, BEAUTYSOLAR, DISPLACESOLAR, POLLUTESOLAR, INDUSTRYSMALL, OWNERREG, MECHANISATION)%>%
+  na.omit()
+
+solarpdevelop.alpha <- psych::alpha(solarpdevelop, check.keys = TRUE)
+
+# alpha is strong at c!
+
+solarndevelop <- sfascales %>%
+  dplyr::select(DEVSOLAR, PRIDESOLAR, NPRIDESOLAR, PROSPERSOLAR)%>%
+  na.omit()
+
+solarndevelop.alpha <- psych::alpha(solarndevelop, check.keys = TRUE)
+
+#alpha is strong at 0.86!
+
 ```
@@
 \newpage
-## Coal
+
+## Solar Energy : CFA on Combined Scale (2 Factor Solution)
+
+Solar People Centered Development alpha = 0.75
+
+Solar Nationalist Development alpha = 0.86
+
+```{r, echo=FALSE}
+
+# Extract parameter estimates
+sparams <- parameterEstimates(secopol_cfa, standardized = TRUE)%>%
+   slice(1:(n()-15))
+
+sparams1 <- sparams %>%
+  mutate(rhs = case_when(
+  rhs == "DISPLACESOLAR" ~ "Solar energy is leading to displacement of people from their land",
+  rhs == "BEAUTYSOLAR" ~ "Solar energy spoils the natural beauty of the landscape",
+  rhs == "POLLUTESOLAR" ~ "Solar energy increases pollution of air/water/land",
+  rhs == "HEALTHSOLAR" ~ "Solar energy poses a great risk to the health of people living around it",
+  rhs == "JOBSSOLAR" ~ "Solar energy will bring jobs to the local community",
+  rhs == "PRIDESOLAR" ~ "I would be proud if my community used Solar energy",
+  rhs == "NPRIDESOLAR" ~ "Solar energy is a mark of pride for our nation",
+  rhs == "DEVSOLAR" ~ "Solar energy pushes forward the country's development",
+  rhs == "PROSPERSOLAR" ~ "Solar energy brings economic prosperity to the surrounding regions",
+  rhs == "RELYSOLAR" ~ "I don't like the idea that I have to rely on the government for electricity from Solar energy",
+  rhs == "INDUSTRYSMALL" ~ "Large corporations are destroying the local industries in India and benefiting only a handful of people",
+  rhs == "OWNERREG" ~ "Regardless of ownership, the government should pass strong regulations and implement them",
+  rhs == "MECHANISATION" ~ "Rapid mechanization of work is taking away jobs from workers in this country",
+
+    TRUE ~ as.character(rhs)
+  )) %>%
+  dplyr::select(!c(lhs,op, std.nox)) %>%
+    rename(
+    "Items" = rhs,
+    "Loadings" = est,
+    "Standard Error" = se,
+    "zvalue" = z) %>%
+  mutate(across(c("Loadings", "Standard Error", "zvalue"), round, 3))
+
+sparams1$Scale <- NA
+sparams1$Scale[1:7] <- "People Centered Development"
+sparams1$Scale[8:10] <- "Nationalist Development"
+sparams1 <- sparams1[, c("Scale", setdiff(names(sparams1), "Scale"))]
+CFAsolar <- knitr::kable(sparams1, booktabs = TRUE, caption = "Confirmatory Factor Analysis(CFA) on Solar Energy") %>%
+  kable_styling(latex_options = c("striped","scale_down", "hold_position", "repeat_header"))%>%
+  column_spec(column = 2, width = "4cm")
+
+# Print the table
+CFAsolar %>%
+  landscape()
+
+```
+
+```{r, echo=FALSE}
+
+# Solar - linear regression with 2 Factor solution
+
+# Linear Model with 2 factor solution for  Risk perception from Solar Energy
+
+# scores from EFA
+#secopolall_scores2 <- psych::factor.scores(secopolall, secopolall2.fa)
+
+# The factor scores will be stored in the scores element of the returned list
+#scores2 <- secopolall_scores2$scores
+
+#binding factor scores to the dataset
+
+#sfascale_scores2 <- cbind(sKahan_Kscores, scores2) %>%
+  #rename(Pdevelop = MR1)%>%
+  #rename(Ndevelop = MR2)
+#solar2fa2 <- lm(Risky_Solar ~ age + Uppercaste + Male + Hindu + Urban + State + KahanS + KahanH + Pdevelop + Ndevelop, data = sfascale_scores2)
+
+#summary(solar2fa2)
+# lesson: doesn't matter if I use CFA or EFA scores- the difference is small and is probably happening due to slightly different samples - this brings to mind the problem of large missing values - maybe it's worth talking to a stat consultant about this issue
+
+#scores from CFA 
+#binding factor scores to the dataset
+secopolall_scores <- predict(secopol_cfa, newdata = sfascales)
+
+sfascale_scores <- cbind(sKahan_Kscores, secopolall_scores)
+
+solar2fa <- lm(Risky_Solar ~ age + Uppercaste + Male + Hindu + Urban + State + KahanS + KahanH + Pdevelop + Ndevelop, data = sfascale_scores)
+
+# Print model summary
+summary(solar2fa)
+
+```
+
+```{r,echo = FALSE}
+sacceptance2 <- sfascale_scores %>%
+  mutate(Solar = Ben_Solar - Risky_Solar)
+
+solaracceptlm <- lm(Solar ~ age + Uppercaste + Male + Hindu + Urban + State + KahanS + KahanH + Pdevelop + Ndevelop, data = sacceptance2)
+
+#m2_allscales <- lm(Risky_Nuclear ~ age + Uppercaste + Male + Hindu + Urban +State+ KahanS + KahanH + NPRIDENUCLEAR + PRIDENUCLEAR + DEVNUCLEAR + PROSPERNUCLEAR, data = fascale_scores)
+# Print model summary
+#summary(solaracceptlm)
+
+```
 
@@
       "Reliance on government(coal)" = "RELYCOAL"
-    )%>%
+    )
+
+cecopolall2.fa <- fa(cecopolall, nfactors = 2, rotate = "varimax")
+
+#print.psych(cecopolall2.fa, cut = 0.5, sort = TRUE)
+
+```
+
+```{r, echo = FALSE}
+
+## COAL: CFA on kahan scale and eco-pol scale
+
+# kahan scores for coal and CFA on ecopol vars  
+cfascales <- codedmodule2 %>%
+      filter(
+    rowSums(is.na(dplyr::select(., starts_with("K_")))) == 0 &  # This line ensures that rows with any NA in columns starting with         "K_" are   filtered out.
+    !is.na(WEALTHLIM) & 
+    !is.na(MECHANISATION) & 
+    !is.na(DECISIONDECEN) & 
+    !is.na(DECISIONCEN) & 
+    !is.na(INDUSTRYLARGE) & 
+    !is.na(INDUSTRYSMALL) & 
+    !is.na(ECONOMYGLOBAL) & 
+    !is.na(ECONOMYLOCAL) & 
+    !is.na(ENVOVERDEV) & 
+    !is.na(DEVOVERENV) & 
+    !is.na(OWNERPVT) & 
+    !is.na(OWNERNOREG) & 
+    !is.na(OWNERPUB) & 
+    !is.na(OWNERREG) & 
+    !is.na(DISPLACECOAL) & 
+    !is.na(POLLUTECOAL) & 
+    !is.na(HEALTHCOAL) & 
+    !is.na(JOBSCOAL) & 
+    !is.na(BEAUTYCOAL) & 
+    !is.na(PRIDECOAL) & 
+    !is.na(NPRIDECOAL) & 
+    !is.na(DEVCOAL) & 
+    !is.na(PROSPERCOAL) & 
+    !is.na(RELYCOAL)
+  )
+
+  #dplyr::select(starts_with(c("K_","Risky_Coal","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACECOAL",  "POLLUTECOAL", "HEALTHCOAL", "JOBSCOAL", "BEAUTYCOAL", "PRIDECOAL", "NPRIDECOAL", "DEVCOAL", "PROSPERCOAL", "RELYCOAL", "Uppercaste", "Male", "Hindu", "Urban", "State","age"))) %>%na.omit()
+
+cKahan_fas <- '
+  KahanS =~ K_SHARM + K_SLIMCHOI + K_SPROTECT 
+  KahanH =~ K_HEQUAL+ K_ERADEQ1 + K_EWEALTH + K_ERADEQ2
+'
+
+# Run CFA
+cKahan_cfa <- cfa(cKahan_fas, data = cfascales, std.lv = TRUE)
+
+cKahan_scores <- predict(cKahan_cfa, newdata = cfascales)
+
+cKahan_Kscores <- cbind(cfascales, cKahan_scores)
+
+cecopol_fas <- '
+  Pdevelop =~ HEALTHCOAL + BEAUTYCOAL + DISPLACECOAL + POLLUTECOAL + INDUSTRYSMALL + OWNERREG + MECHANISATION
+  Ndevelop =~ DEVCOAL + PROSPERCOAL + PRIDECOAL + NPRIDECOAL 
+'
+
+cecopol_cfa <- cfa(cecopol_fas, data = cfascales, std.lv = TRUE)
+#summary(cecopol_cfa, fit.measure= TRUE, standardized = TRUE)
+
+# 3) lm with kahan 
+cm1_kahan <- lm(Risky_Coal ~ Uppercaste + Male + Hindu + Urban + age + State + KahanS + KahanH , data = cKahan_Kscores)
+# Print model summary
+#summary(cm1_kahan)
+#plot(cm1_kahan)
+
+# Cronbach's alpha test on Pdevelop and Ndevelop for Solar energy
+
+coalpdevelop <- cfascales %>%
+  dplyr::select(HEALTHCOAL, BEAUTYCOAL, DISPLACECOAL, POLLUTECOAL, INDUSTRYSMALL, OWNERREG, MECHANISATION)%>%
   na.omit()
 
-cecopolall2.fa <- fa(cecopolall, nfactors = 2, rotate = "varimax")
-
-```
+coalpdevelop.alpha <- psych::alpha(coalpdevelop, check.keys = TRUE)
+
+# alpha is strong at 0.78!
+
+coalndevelop <- cfascales %>%
+  dplyr::select(DEVCOAL, PRIDECOAL, NPRIDECOAL, PROSPERCOAL)%>%
+  na.omit()
+
+coalndevelop.alpha <- psych::alpha(coalndevelop, check.keys = TRUE)
+
+#alpha n develop = 0.6
+
+```
+
+\newpage
+## Coal : CFA on Combined Scale 2 Factor Solution (Pdevelop and Ndevelop)
+
+Coal People Centered Development Alpha = 0.78
+
+Coal Nationalist Development Alpha = 0.6
+
+```{r, echo=FALSE}
+
+# Extract parameter estimates
+cparams <- parameterEstimates(cecopol_cfa, standardized = TRUE)%>%
+   slice(1:(n()-15))
+
+cparams1 <- cparams %>%
+  mutate(rhs = case_when(
+  rhs == "DISPLACECOAL" ~ "Coal powered plants is leading to displacement of people from their land",
+  rhs == "BEAUTYCOAL" ~ "Coal powered plants spoils the natural beauty of the landscape",
+  rhs == "POLLUTECOAL" ~ "Coal powered plants increases pollution of air/water/land",
+  rhs == "HEALTHCOAL" ~ "Coal powered plants poses a great risk to the health of people living around it",
+  rhs == "JOBSCOAL" ~ "Coal powered plants will bring jobs to the local community",
+  rhs == "PRIDECOAL" ~ "I would be proud if my community used Coal powered plants",
+  rhs == "NPRIDECOAL" ~ "Coal powered plants is a mark of pride for our nation",
+  rhs == "DEVCOAL" ~ "Coal powered plants pushes forward the country's development",
+  rhs == "PROSPERCOAL" ~ "Coal powered plants brings economic prosperity to the surrounding regions",
+  rhs == "RELYCOAL" ~ "I don't like the idea that I have to rely on the government for electricity from Coal powered plants",
+  rhs == "INDUSTRYSMALL" ~ "Large corporations are destroying the local industries in India and benefiting only a handful of people",
+  rhs == "OWNERREG" ~ "Regardless of ownership, the government should pass strong regulations and implement them",
+  rhs == "MECHANISATION" ~ "Rapid mechanization of work is taking away jobs from workers in this country",
+
+    TRUE ~ as.character(rhs)
+  )) %>%
+  dplyr::select(!c(lhs,op, std.nox)) %>%
+    rename(
+    "Items" = rhs,
+    "Loadings" = est,
+    "Standard Error" = se,
+    "zvalue" = z) %>%
+  mutate(across(c("Loadings", "Standard Error", "zvalue"), round, 3))
+
+cparams1$Scale <- NA
+cparams1$Scale[1:7] <- "People Centered Development"
+cparams1$Scale[8:10] <- "Nationalist Development"
+cparams1 <- cparams1[, c("Scale", setdiff(names(sparams1), "Scale"))]
+CFAcoal <- knitr::kable(cparams1, booktabs = TRUE, caption = "Confirmatory Factor Analysis(CFA) on Coal") %>%
+  kable_styling(latex_options = c("striped","scale_down", "hold_position", "repeat_header"))%>%
+  column_spec(column = 2, width = "4cm")
+
+# Print the table
+CFAcoal %>%
+  landscape()
+
+```
+
+```{r, echo=FALSE}
+
+## Coal linear regression - 2 FA solution
+
+# Linear Model with 2 factor solution for  Risk perception from coal Energy
+
+#binding factor scores to the dataset
+cecopolall_scores <- predict(cecopol_cfa, newdata = cfascales)
+
+cfascale_scores <- cbind(cKahan_Kscores, cecopolall_scores)# %>%
+  #rename(Pdevelop = MR1)%>%
+  #rename(Ndevelop = MR2)
+
+coal2fa <- lm(Risky_Coal ~ age + Uppercaste + Male + Hindu + Urban + State + KahanS + KahanH + Pdevelop + Ndevelop, data = cfascale_scores)
+
+# Print model summary
+#summary(coal2fa)
+
+```
+
+```{r,echo = FALSE}
+cacceptance2 <- cfascale_scores %>%
+  mutate(Coal = Ben_Coal - Risky_Coal)
+
+coalacceptlm <- lm(Coal ~ age + Uppercaste + Male + Hindu + Urban + State + KahanS + KahanH + Pdevelop + Ndevelop, data = cacceptance2)
+
+#m2_allscales <- lm(Risky_Nuclear ~ age + Uppercaste + Male + Hindu + Urban +State+ KahanS + KahanH + NPRIDENUCLEAR + PRIDENUCLEAR + DEVNUCLEAR + PROSPERNUCLEAR, data = fascale_scores)
+# Print model summary
+#summary(coalacceptlm)
+
+```
+
+\newpage
+
+## Linear Models: Perceived risk X Pdevelop and Ndevelop
+
+```{r, echo=FALSE, results='asis'}
+library(stargazer)
+
+cat("\\begingroup")
+cat("\\setlength{\\tabcolsep}{1pt}")
+cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer(nuclear2fa, solar2fa, coal2fa, 
+         title = "Perceived Risk X Pdevelop and Ndevelope",
+        type = "latex"
+)
+cat("\\endgroup")
+
+```
+
+```{r, echo =FALSE}
+
+# same things with benefit from Nuclear Energy
+fascalesben <- codedmodule2 %>%
+  dplyr::select(starts_with(c("K_","Ben_Nuclear","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%
+  na.omit()
+
+Kahan_fas <- '
+  KahanS =~ K_SHARM + K_SLIMCHOI + K_SPROTECT 
+  KahanH =~ K_HEQUAL+ K_ERADEQ1 + K_EWEALTH + K_ERADEQ2
+'
+
+# Run CFA
+Kahan_cfaben <- cfa(Kahan_fas, data = fascalesben, std.lv = TRUE)
+
+Kahan_scoresben <- predict(Kahan_cfaben, newdata = fascalesben)
+
+Kahan_Kscoresben <- cbind(fascalesben, Kahan_scoresben)
+
+ecopolallben <- fascalesben %>%
+        dplyr::select("WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR")
+
+ecopolallben_alpha <- psych::alpha(ecopolallben, check.keys = TRUE)
+
+#summary(ecopolall_alpha)
+
+# when we combine both the scales the alpha is high at 0.785 (almost 0.8)
+
+# FA on all ecopol variables except systems of governance
+
+ecopolallben_cor <- cor(ecopolallben)
+PCA24 <- principal(ecopolallben, nfactors = 24, rotate = "none") # no rotation to start with.
+
+ecopolallben2.fa <- fa(ecopolallben, nfactors = 2, rotate = "varimax")
+
+# I don't know still doesn't make a lot of sense to me- the two factors make more sense - 1) people centered development 2) nationalist development
+# So I am going to extract factor scores and bind them to the dataset
+
+ecopolallben_scores <- psych::factor.scores(ecopolallben, ecopolallben2.fa)
+
+# The factor scores will be stored in the scores element of the returned list
+scores2 <- ecopolallben_scores$scores
+
+#binding factor scores to the dataset
+
+fascale_scoresben <- cbind(Kahan_Kscoresben, scores2) %>%
+  rename(Pdevelop = MR1)%>%
+  rename(Ndevelop = MR2) #%>%
+  #dplyr::select(!starts_with(c("K_","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR")))
+
+mbennuclear <- lm(Ben_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State+ KahanS + KahanH + Pdevelop + Ndevelop , data = fascale_scoresben)
+# Print model summary
+#summary(mbennuclear)
+
+```
+
+```{r, echo =FALSE}
+
+# same things with benefit from Solar Energy
+sfascalesben <- codedmodule2 %>%
+  dplyr::select(starts_with(c("K_","Ben_Solar","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACESOLAR",  "POLLUTESOLAR", "HEALTHSOLAR", "JOBSSOLAR", "BEAUTYSOLAR", "PRIDESOLAR", "NPRIDESOLAR", "DEVSOLAR", "PROSPERSOLAR", "RELYSOLAR", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%
+  na.omit()
+
+Kahan_fas <- '
+  KahanS =~ K_SHARM + K_SLIMCHOI + K_SPROTECT 
+  KahanH =~ K_HEQUAL+ K_ERADEQ1 + K_EWEALTH + K_ERADEQ2
+'
+
+# Run CFA
+sKahan_cfaben <- cfa(Kahan_fas, data = sfascalesben, std.lv = TRUE)
+
+sKahan_scoresben <- predict(sKahan_cfaben, newdata = sfascalesben)
+
+sKahan_Kscoresben <- cbind(sfascalesben, sKahan_scoresben)
+
+secopolallben <- sfascalesben %>%
+        dplyr::select("WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACESOLAR",  "POLLUTESOLAR", "HEALTHSOLAR", "JOBSSOLAR", "BEAUTYSOLAR", "PRIDESOLAR", "NPRIDESOLAR", "DEVSOLAR", "PROSPERSOLAR", "RELYSOLAR")
+
+secopolallben_alpha <- psych::alpha(secopolallben, check.keys = TRUE)
+
+#summary(ecopolall_alpha)
+
+# when we combine both the scales the alpha is high at 0.785 (almost 0.8)
+
+# FA on all ecopol variables except systems of governance
+
+secopolallben_cor <- cor(secopolallben)
+PCA24 <- principal(secopolallben, nfactors = 24, rotate = "none") # no rotation to start with.
+
+secopolallben2.fa <- fa(secopolallben, nfactors = 2, rotate = "varimax")
+
+# I don't know still doesn't make a lot of sense to me- the two factors make more sense - 1) people centered development 2) nationalist development
+# So I am going to extract factor scores and bind them to the dataset
+
+secopolallben_scores <- psych::factor.scores(secopolallben, secopolallben2.fa)
+
+# The factor scores will be stored in the scores element of the returned list
+sscores2 <- secopolallben_scores$scores
+
+#binding factor scores to the dataset
+
+sfascale_scoresben <- cbind(sKahan_Kscoresben, sscores2) %>%
+  rename(Pdevelop = MR1)%>%
+  rename(Ndevelop = MR2) #%>%
+  #dplyr::select(!starts_with(c("K_","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR")))
+
+mbensolar <- lm(Ben_Solar ~ Uppercaste + Male + Hindu + Urban + age + State+ KahanS + KahanH + Pdevelop + Ndevelop , data = sfascale_scoresben)
+# Print model summary
+#summary(mbensolar)
+
+```
+
+```{r, echo =FALSE}
+
+# same things with benefit from COAL Energy
+cfascalesben <- codedmodule2 %>%
+  dplyr::select(starts_with(c("K_","Ben_Coal","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACECOAL",  "POLLUTECOAL", "HEALTHCOAL", "JOBSCOAL", "BEAUTYCOAL", "PRIDECOAL", "NPRIDECOAL", "DEVCOAL", "PROSPERCOAL", "RELYCOAL", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%
+  na.omit()
+
+Kahan_fas <- '
+  KahanS =~ K_SHARM + K_SLIMCHOI + K_SPROTECT 
+  KahanH =~ K_HEQUAL+ K_ERADEQ1 + K_EWEALTH + K_ERADEQ2
+'
+
+# Run CFA
+cKahan_cfaben <- cfa(Kahan_fas, data = cfascalesben, std.lv = TRUE)
+
+cKahan_scoresben <- predict(cKahan_cfaben, newdata = cfascalesben)
+
+cKahan_Kscoresben <- cbind(cfascalesben, cKahan_scoresben)
+
+cecopolallben <- cfascalesben %>%
+        dplyr::select("WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACECOAL",  "POLLUTECOAL", "HEALTHCOAL", "JOBSCOAL", "BEAUTYCOAL", "PRIDECOAL", "NPRIDECOAL", "DEVCOAL", "PROSPERCOAL", "RELYCOAL")
+
+cecopolallben_alpha <- psych::alpha(cecopolallben, check.keys = TRUE)
+
+#summary(ecopolall_alpha)
+
+# when we combine both the scales the alpha is high at 0.785 (almost 0.8)
+
+# FA on all ecopol variables except systems of governance
+
+cecopolallben_cor <- cor(cecopolallben)
+PCA24 <- principal(cecopolallben, nfactors = 24, rotate = "none") # no rotation to start with.
+
+cecopolallben2.fa <- fa(cecopolallben, nfactors = 2, rotate = "varimax")
+
+# I don't know still doesn't make a lot of sense to me- the two factors make more sense - 1) people centered development 2) nationalist development
+# So I am going to extract factor scores and bind them to the dataset
+
+cecopolallben_scores <- psych::factor.scores(cecopolallben, cecopolallben2.fa)
+
+# The factor scores will be stored in the scores element of the returned list
+sscores2 <- cecopolallben_scores$scores
+
+#binding factor scores to the dataset
+
+cfascale_scoresben <- cbind(cKahan_Kscoresben, sscores2) %>%
+  rename(Pdevelop = MR1)%>%
+  rename(Ndevelop = MR2) #%>%
+  #dplyr::select(!starts_with(c("K_","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR")))
+
+mbencoal <- lm(Ben_Coal ~ Uppercaste + Male + Hindu + Urban + age + State+ KahanS + KahanH + Pdevelop + Ndevelop , data = cfascale_scoresben)
+# Print model summary
+#summary(mbencoal)
+
+```
+
+\newpage
+
+## Linear Models: Perceived Benefit X Pdevelop and Ndevelop
+
+```{r, echo=FALSE, results='asis'}
+library(stargazer)
+
+cat("\\begingroup")
+cat("\\setlength{\\tabcolsep}{1pt}")
+cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer(mbennuclear,mbensolar , mbencoal, 
+         title = "Perceived Benefit X Pdevelop and Ndevelop",
+        type = "latex"
+)
+cat("\\endgroup")
+
+```
+
+\newpage
+
+## Linear Models: Acceptance (Risk - Benefit) X Pdevelop & Ndevelop
+
+```{r, echo=FALSE, results='asis'}
+library(stargazer)
+
+cat("\\begingroup")
+cat("\\setlength{\\tabcolsep}{1pt}")
+cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer(nuclearacceptlm, solaracceptlm , coalacceptlm, 
+         title = "Acceptance (Risk - Benefit) X Pdevelop and Ndevelop",
+        type = "latex"
+)
+cat("\\endgroup")
+
+```
+
+```{r, echo = FALSE}
+
+# below are only eco-pol values of the perceiver scale.
+
+ecopolonly <- codedmodule2 %>%
+            filter(!is.na(WEALTHLIM) & !is.na(MECHANISATION) & !is.na(INDUSTRYSMALL)  & !is.na(ECONOMYGLOBAL)  & !is.na(ENVOVERDEV)  & !is.na(OWNERNOREG) & !is.na(OWNERPUB) & !is.na(OWNERREG) & !is.na(DECISIONDECEN) & !is.na(DECISIONCEN) & !is.na(INDUSTRYLARGE) & !is.na(ECONOMYLOCAL) & !is.na(DEVOVERENV) & !is.na(OWNERPVT))
+        #dplyr::select("WEALTHLIM","MECHANISATION","INDUSTRYSMALL","ECONOMYGLOBAL", "ENVOVERDEV","OWNERNOREG","OWNERPUB", "OWNERREG", "DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","ECONOMYLOCAL", "DEVOVERENV","OWNERPVT") %>%
+  #na.omit()
+
+ecopolval <- codedmodule2 %>%
+        dplyr::select("WEALTHLIM","MECHANISATION","INDUSTRYSMALL","ECONOMYGLOBAL", "ENVOVERDEV","OWNERNOREG","OWNERPUB", "OWNERREG", "DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","ECONOMYLOCAL", "DEVOVERENV","OWNERPVT")%>%
+  na.omit() %>%
+    rename(
+      "Limits on Wealth" = "WEALTHLIM",
+      "Anti Mechanisation of work" = "MECHANISATION",
+      "Pro Decentralisation" = "DECISIONDECEN",
+      "Pro Centralisation" = "DECISIONCEN",
+      "Pro Large Industries" = "INDUSTRYLARGE",
+      "Anti Large Industries" = "INDUSTRYSMALL",
+      "Pro Globaleconomy" = "ECONOMYGLOBAL",
+      "Pro Localeconomy" = "ECONOMYLOCAL",
+      "Environment over Development" = "ENVOVERDEV",
+      "Development over Environment" = "DEVOVERENV",
+      "Pro Private ownership" = "OWNERPVT",
+      "Anti Regulations" = "OWNERNOREG",
+      "Pro Public ownership" = "OWNERPUB",
+      "Pro Regulations" = "OWNERREG"
+    )
+
+ecopolval2.fa <- fa(ecopolval, nfactors = 2, rotate = "varimax")
+#print.psych(ecopolval2.fa, cut = 0.4, sort = TRUE)
+
+ecopolval4.fa <- fa(ecopolval, nfactors = 4, rotate = "varimax")
+#print.psych(ecopolval4.fa, cut = 0.4, sort = TRUE)
+
+# 4 fA extraction
+
+ecopolval_scores <- psych::factor.scores(ecopolval, ecopolval4.fa)
+
+# The factor scores will be stored in the scores element of the returned list
+ecopolonlyscores <- ecopolval_scores$scores
+
+#binding factor scores to the dataset
+
+ecopolonlywscores <- cbind(ecopolonly, ecopolonlyscores) %>%
+  rename(regulateindustry = MR1)%>%
+  rename(localisation = MR3)%>%
+   rename(freemarket = MR4)%>%
+  rename(pvtdevelopment = MR2)
+
+# 2 factor
+
+ecopolval2_scores <- psych::factor.scores(ecopolval, ecopolval2.fa)
+
+# The factor scores will be stored in the scores element of the returned list
+ecopolonlyscores2 <- ecopolval2_scores$scores
+
+#binding factor scores to the dataset
+
+ecopolonlywscores2 <- cbind(ecopolonly, ecopolonlyscores2)
+
+# checking alpha
+
+regulated_industry <- ecopolonly  %>%
+  dplyr::select(OWNERREG, MECHANISATION, WEALTHLIM)%>%
+  na.omit()
+
+regulated_industry.alpha <- psych::alpha(regulated_industry, check.keys = TRUE)
+
+#alpha 0.59
+
+localisation <- ecopolonly %>%
+  dplyr::select(INDUSTRYSMALL, ECONOMYLOCAL)%>%
+  na.omit()
+
+localisation.alpha <- psych::alpha(localisation, check.keys = TRUE)
+
+# alpha 0.52
+
+freemarket <- ecopolonly %>%
+  dplyr::select(DECISIONCEN, ECONOMYGLOBAL,OWNERNOREG,INDUSTRYLARGE)%>%
+  na.omit()
+
+freemarket.alpha <- psych::alpha(freemarket, check.keys = TRUE)
+
+# alpha = 0.57
+
+pvtdevelopment <- ecopolonly %>%
+  dplyr::select(DEVOVERENV,OWNERPVT, ENVOVERDEV, OWNERPUB)%>%
+  na.omit()
+
+pvtdevelopment.alpha <- psych::alpha(pvtdevelopment, check.keys = TRUE)
+
+# alpha =0.58
+
+#cor(ecopolval)
+
+# questions for Terre , 2) 4 factors/3 factors/2 factors - variation explained how should i deal with that. 
+# four factor analysis - MR1 -regulated industrialization MR3 - localisation MR4 - free market MR2- private development
+
+```
+
+\newpage
+\blandscape
+# FA on Separate scales: Scale 1:Eco-political values of the perceiver
+
+## 4 factor solution (Characteristics of the perceiver)
+
+Cronbach's alpha values: Regulated Industrialisation = 0.59, localisation = 0.52 , Free market = 0.57, Private Development = 0.58
 
@@
 
-set_flextable_defaults(docx.landscape = TRUE)
-
-flex <- function(data, title=NULL) {
-  # this grabs the data and converts it to a flextbale
-  flextable(data) %>%
-  # this makes the table fill the page width
-  set_table_properties(layout = "autofit", width = 1) %>%
-  # font size
+flex <- function(data, title=NULL, col_widths=NULL) {
+  tbl <- flextable(data) %>%
+         #set_table_properties(layout = "autofit", width = 1) %>%
          fontsize(size=10, part="all") %>%
-    #this adds a ttitlecreates an automatic table number
          set_caption(title, 
@@
                                                     post_label = "\n", 
-                                                 bkm = "anytable")) #%>%
-  # font type
-  #font(fontname="Times New Roman", part="all")
-}
-
-crename_map <- c(
+                                                    bkm = "anytable"))
+
+  # If col_widths is provided, set column widths
+  if(!is.null(col_widths)) {
+    for(col in names(col_widths)){
+      tbl <- width(tbl, j = col, width = col_widths[[col]])
+    }
+  }
+
+  return(tbl)
+}
+
+rename_map <- c(
   "Limits on Wealth" = "A limit should be put to how much wealth a person can amass",
@@
   "Pro Public ownership" = "The government should own most large businesses and industries",
-  "Pro Regulations" = "Regardless of ownership, the government should pass strong regulations and implement them",
-  "Displacement risk(coal)" = "Coal powered plants are leading to displacement of people from their land",
-  "Spoils Natural Beauty(coal)" = "Coal powered plants spoil the natural beauty of the landscape",
-  "Pollution risk(coal)" = "Coal powered plants increase pollution of air/water/land",
-  "Health risk(coal)" = "Coal powered plants pose a great risk to the health of people living around it",
-  "Job opportunities(coal)" = "Coal powered plants will bring jobs to the local community",
-  "Community pride(coal)" = "I would be proud if my community used coal powered plants",
-  "National pride(coal)" = "Coal powered plants are a mark of pride for our nation",
-  "National development(coal)" = "Coal powered plants push forward the country's development",
-  "Local prosperity(coal)" = "Coal powered plants bring economic prosperity to the surrounding regions",
-  "Reliance on government(coal)" = "I don't like the idea that I have to rely on the government for electricity from coal powered plants"
+  "Pro Regulations" = "Regardless of ownership, the government should pass strong regulations and implement them"
 )
@@
     mutate(
-      item = if_else(item %in% names(crename_map), crename_map[item], item),
-      code = names(crename_map)[match(item, crename_map)], # extracting short form
+      item = if_else(item %in% names(rename_map), rename_map[item], item),
+      code = names(rename_map)[match(item, rename_map)], # extracting short form
       across(where(is.numeric), round, 3)
@@
 
-fa_table(cecopolall2.fa, .4) %>%
-  #rename(Pdevelop = MR1, Ndevelop = MR2, Items= item) %>%
-  flex("2 factor solution") %>%
-  autofit()
-
-```
-
-```{r, echo = FALSE}
-cecopolall2.fa[["Vaccounted"]] %>%
-  as.data.frame() %>%
-  rownames_to_column("Property") %>%
-  #rename(Pdevelop = MR1, Ndevelop = MR2) %>%
-    mutate(across(where(is.numeric), round, 3)) %>%
-    flex("Coal: Eigenvalues and Variance Explained for 2 Factor Solution")
-```
-
-\newpage
-# Alternative Solution :  FA on Two Separate scales
-
-## Scale 1: Factor analysis on Eco-political values of the perceiver scale
- 4 factor solution
-
-```{r, echo = FALSE}
-
-# below are only eco-pol values of the perceiver scale.
-
-ecopolval <- codedmodule2 %>%
-        dplyr::select("WEALTHLIM","MECHANISATION","INDUSTRYSMALL","ECONOMYGLOBAL", "ENVOVERDEV","OWNERNOREG","OWNERPUB", "OWNERREG", "DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","ECONOMYLOCAL", "DEVOVERENV","OWNERPVT")%>%
-  na.omit() %>%
-    rename(
-      "Limits on Wealth" = "WEALTHLIM",
-      "Anti Mechanisation of work" = "MECHANISATION",
-      "Pro Decentralisation" = "DECISIONDECEN",
-      "Pro Centralisation" = "DECISIONCEN",
-      "Pro Large Industries" = "INDUSTRYLARGE",
-      "Anti Large Industries " = "INDUSTRYSMALL",
-      "Pro Globaleconomy" = "ECONOMYGLOBAL",
-      "Pro Localeconomy" = "ECONOMYLOCAL",
-      "Environment over Development" = "ENVOVERDEV",
-      "Development over Environment" = "DEVOVERENV",
-      "Pro Private ownership " = "OWNERPVT",
-      "Anti Regulations" = "OWNERNOREG",
-      "Pro Public ownership" = "OWNERPUB",
-      "Pro Regulations" = "OWNERREG"
-    )
-
-#alpha(ecopolval, check.keys = TRUE) # 0.71
-
-#ncol(ecopolval)  number of cols is 14
-
-#ecopolval_cor <- cor(ecopolval)
-#PCA14 <- principal(ecopolval, nfactors = 14, rotate = "none") # no rotation to start with.
-
-#print(PCA14)
-
-#PCA14$loadings
-
-#fa.parallel(ecopolval_cor)
-
-ecopolval4.fa <- fa(ecopolval, nfactors = 4, rotate = "varimax")
-
-#cor(ecopolval)
-
-# questions for Terre , 2) 4 factors/3 factors/2 factors - variation explained how should i deal with that. 
-# four factor analysis - MR1 - problems of industrialisation MR2 - local economy and decision making MR3 - centralised and large industry MR4- dev/ownership
-```
+fa_table(ecopolval4.fa, .4) %>%
+  rename("regulated industrialization" = MR1, "private development" = MR2, "localisation" = MR3, "free market" = MR4, Items= item) %>%
+  flex("4 factor solution same for all technologies", col_widths = list(Items = 3.5, code = 1.5, "regulated industrialization" = 0.5, "private development" = 0.5, "localisation" = 0.5, "free market" = 0.5))
+
+```
+
+\elandscape
 
@@
 library(flextable)
-
-set_flextable_defaults(docx.landscape = TRUE)
 
@@
 
+ecopolval4.fa[["Vaccounted"]] %>%
+  as.data.frame() %>%
+  rownames_to_column("Property") %>%
+  #rename(Pdevelop = MR1, Ndevelop = MR2) %>%
+    mutate(across(where(is.numeric), round, 3)) %>%
+    flex("Eigenvalues and Variance Explained for Rotated Factor Solution")
+
+```
+
+```{r, echo = FALSE}
+# linear regression with 4 factor solution
+
+#Risky_Nuclear
+
+nuclear4fa <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State + regulateindustry +  localisation + freemarket + pvtdevelopment , data = ecopolonlywscores)
+# Print model summary
+#summary(nuclear4fa)
+
+#Ben_Nuclear
+bennuclear4fa <- lm(Ben_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State + regulateindustry +  localisation + freemarket + pvtdevelopment , data = ecopolonlywscores)
+# Print model summary
+#summary(bennuclear4fa)
+
+#Risky_Solar
+solar4fa <- lm(Risky_Solar ~ Uppercaste + Male + Hindu + Urban + age + State + regulateindustry +  localisation + freemarket + pvtdevelopment , data = ecopolonlywscores)
+# Print model summary
+#summary(solar4fa)
+
+#Ben_Solar
+
+bensolar4fa <- lm(Ben_Solar ~ Uppercaste + Male + Hindu + Urban + age + State + regulateindustry +  localisation + freemarket + pvtdevelopment , data = ecopolonlywscores)
+# Print model summary
+#summary(bensolar4fa)
+
+#Risky_Coal
+
+coal4fa <- lm(Risky_Coal ~ Uppercaste + Male + Hindu + Urban + age + State + regulateindustry +  localisation + freemarket + pvtdevelopment , data = ecopolonlywscores)
+# Print model summary
+#summary(coal4fa)
+
+#Ben_Coal
+
+bencoal4fa <- lm(Ben_Coal ~ Uppercaste + Male + Hindu + Urban + age + State + regulateindustry +  localisation + freemarket + pvtdevelopment , data = ecopolonlywscores)
+# Print model summary
+#summary(bencoal4fa)
+
+```
+
+```{r,echo = FALSE}
+acceptance3 <- ecopolonlywscores %>%
+   mutate(Nuclear = Ben_Nuclear - Risky_Nuclear,
+         Hyrdo = Ben_Hydro - Risky_Hydro,
+         Wind = Ben_Wind - Risky_Wind,
+         Solar = Ben_Solar - Risky_Solar,
+         Coal = Ben_Coal - Risky_Coal,
+         Gas = Ben_Gas - Risky_Gas,
+         Oil = Ben_Oil - Risky_Oil)
+
+naccept2 <- lm(Nuclear ~ age + Uppercaste + Male + Hindu + Urban + State  + regulateindustry +  localisation + freemarket + pvtdevelopment, data = acceptance3)
+
+#summary(naccept2)
+
+saccept2 <- lm(Solar ~ age + Uppercaste + Male + Hindu + Urban + State  + regulateindustry +  localisation + freemarket + pvtdevelopment, data = acceptance3)
+
+#summary(saccept2)
+
+caccept2 <- lm(Coal ~ age + Uppercaste + Male + Hindu + Urban + State  + regulateindustry +  localisation + freemarket + pvtdevelopment, data = acceptance3)
+
+#summary(caccept2)
+```
+
+\newpage
+## Linear Models: Perceived Risk X 4 Factor Solution(separate scale)
+
+```{r, echo=FALSE, results='asis'}
+library(stargazer)
+
+cat("\\begingroup")
+cat("\\setlength{\\tabcolsep}{1pt}")
+cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer(nuclear4fa, solar4fa, coal4fa, 
+          title = "Perceived Risk X 4 Factor Solution(separate scale)",
+          type = "latex"
+)
+cat("\\endgroup")
+
+```
+
+\newpage
+
+##  Linear Models: : Perceived Risk X 4 Factor Solution (separate scale)
+
+```{r, echo=FALSE, results='asis'}
+library(stargazer)
+
+cat("\\begingroup")
+cat("\\setlength{\\tabcolsep}{1pt}")
+cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer(bennuclear4fa, bensolar4fa, bencoal4fa, 
+          title = "Perceived Risk X 4 Factor Solution (separate scale)",
+          type = "latex"
+)
+cat("\\endgroup")
+
+```
+
+\newpage
+
+##  Linear Models: Acceptance(Risk-Benefit) X 4 Factor Solution (separate scale)
+
+```{r, echo=FALSE, results='asis'}
+library(stargazer)
+
+cat("\\begingroup")
+cat("\\setlength{\\tabcolsep}{1pt}")
+cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer(naccept2, saccept2, caccept2, 
+          title = "Acceptance(Risk-Benefit) X 4 Factor Solution (separate scale)",
+          type = "latex"
+)
+cat("\\endgroup")
+
+```
+
+```{r, echo = FALSE}
+# linear regression with 2 factor solution
+
+#Risky_Nuclear
+
+nuclear2fa2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State + MR1 +MR2 , data = ecopolonlywscores2)
+# Print model summary
+#summary(nuclear2fa2)
+
+#Ben_Nuclear
+bennuclear2fa2 <- lm(Ben_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State + MR1 +MR2 , data = ecopolonlywscores2)
+# Print model summary
+#summary(bennuclear2fa2)
+
+#Risky_Solar
+solar2fa2 <- lm(Risky_Solar ~ Uppercaste + Male + Hindu + Urban + age + State + MR1 +MR2 , data = ecopolonlywscores2)
+# Print model summary
+#summary(solar2fa2)
+
+#Ben_Solar
+
+bensolar2fa2 <- lm(Ben_Solar ~ Uppercaste + Male + Hindu + Urban + age + State + MR1 +MR2 , data = ecopolonlywscores2)
+# Print model summary
+#summary(bensolar2fa2)
+
+#Risky_Coal
+
+coal2fa2 <- lm(Risky_Coal ~ Uppercaste + Male + Hindu + Urban + age + State + MR1 +MR2 , data = ecopolonlywscores2)
+# Print model summary
+#summary(coal2fa2)
+
+#Ben_Coal
+
+bencoal2fa2 <- lm(Ben_Coal ~ Uppercaste + Male + Hindu + Urban + age + State + MR1 +MR2 , data = ecopolonlywscores2)
+# Print model summary
+#summary(bencoal2fa2)
+
+```
+
+\newpage
+\blandscape
+
+## 2 factor solution (Characteristics of the perceiver)
+
+```{r, echo=FALSE}
+
+library(flextable)
+
+flex <- function(data, title=NULL, col_widths=NULL) {
+  tbl <- flextable(data) %>%
+         #set_table_properties(layout = "autofit", width = 1) %>%
+         fontsize(size=10, part="all") %>%
+         set_caption(title, 
+                     autonum = officer::run_autonum(seq_id = "tab", 
+                                                    pre_label = "Table ", 
+                                                    post_label = "\n", 
+                                                    bkm = "anytable"))
+
+  # If col_widths is provided, set column widths
+  if(!is.null(col_widths)) {
+    for(col in names(col_widths)){
+      tbl <- width(tbl, j = col, width = col_widths[[col]])
+    }
+  }
+
+  return(tbl)
+}
+
 rename_map <- c(
@@
   "Pro Public ownership" = "The government should own most large businesses and industries",
-  "Pro Regulations" = " Regardless of ownership, the government should pass strong regulations and implement them"
+  "Pro Regulations" = "Regardless of ownership, the government should pass strong regulations and implement them"
 )
@@
 
-fa_table(ecopolval4.fa, .4) %>%
-  #rename(Pdevelop = MR1, Ndevelop = MR2, Items= item) %>%
-  flex("4 factor solution same for all technologies") %>%
-  autofit()
-
-```
-
-```{r, echo=FALSE}
-
-library(flextable)
-
-flex <- function(data, title=NULL) {
-  # this grabs the data and converts it to a flextbale
-  flextable(data) %>%
-  # this makes the table fill the page width
-  set_table_properties(layout = "autofit", width = 1) %>%
-  # font size
-  fontsize(size=10, part="all") %>%
-    #this adds a ttitlecreates an automatic table number
-      set_caption(title, 
-                  autonum = officer::run_autonum(seq_id = "tab", 
-                                                 pre_label = "Table ", 
-                                                 post_label = "\n", 
-                                                 bkm = "anytable")) #%>%
-  # font type
-  #font(fontname="Times New Roman", part="all")
-}
-
-ecopolval4.fa[["Vaccounted"]] %>%
-  as.data.frame() %>%
-  rownames_to_column("Property") %>%
-  #rename(Pdevelop = MR1, Ndevelop = MR2) %>%
-    mutate(across(where(is.numeric), round, 3)) %>%
-    flex("Eigenvalues and Variance Explained for Rotated Factor Solution")
+fa_table(ecopolval2.fa, .4) %>%
+  rename( Items= item) %>%
+  flex("4 factor solution same for all technologies", col_widths = list(Items = 3.5, code = 1.5))
+
+```
+\elandscape
+
+\newpage
+
+## Linear Models: Perceived Risk X 2 factor solution (separate scale)
+```{r, echo=FALSE, results='asis'}
+library(stargazer)
+
+cat("\\begingroup")
+cat("\\setlength{\\tabcolsep}{1pt}")
+cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer(nuclear2fa2, solar2fa2, coal2fa2, 
+          title = "Perceived Risk X 2 factor solution (separate scale)",
+          type = "latex"
+)
+cat("\\endgroup")
+
+```
+
+\newpage
+
+## Linear Models: Perceived Benefit X 2 FA solution (separate scales)
+```{r, echo=FALSE, results='asis'}
+library(stargazer)
+
+cat("\\begingroup")
+cat("\\setlength{\\tabcolsep}{1pt}")
+cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer(bennuclear2fa2, bensolar2fa2, bencoal2fa2, 
+          title = "Perceived Benefit X 2 FA solution (separate scales)",
+          type = "latex"
+)
+cat("\\endgroup")
 
@@
 
-\newpage
-## Option 1: Factor analysis on Scale 2 - Characteristics of the Technology
- 2 factor solution
-
 ```{r, echo=FALSE}
@@
 Nuclear <- codedmodule2 %>%
-dplyr::select("DISPLACENUCLEAR":"RELYNUCLEAR") %>%
-  na.omit()%>%
+  filter(rowSums(is.na(dplyr::select(., starts_with("K_")))) == 0)%>%
+  filter(complete.cases(dplyr::select(., DISPLACENUCLEAR:RELYNUCLEAR)))
+
+Nuclear2 <- Nuclear  %>%
+  dplyr::select("DISPLACENUCLEAR","POLLUTENUCLEAR", "HEALTHNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR","PROSPERNUCLEAR")%>%    # alternate select("DISPLACENUCLEAR":"RELYNUCLEAR")
     rename(
@@
   "Health risk(nuclear)" = "HEALTHNUCLEAR",
-  "Job opportunities(nuclear)" = "JOBSNUCLEAR",
+  #"Job opportunities(nuclear)" = "JOBSNUCLEAR",
   "Spoils Natural Beauty(nuclear)" = "BEAUTYNUCLEAR",
@@
   "Local prosperity(nuclear)" = "PROSPERNUCLEAR",
-  "Reliance on government(nuclear)" = "RELYNUCLEAR"
-    )
-
-Nuclear.fa <- fa(Nuclear, nfactors = 2, rotate = "varimax")
-
-#print.psych(Nuclear.fa, cut = 0.40, sort = TRUE)
+  #"Reliance on government(nuclear)" = "RELYNUCLEAR"
+    )
+
+Nuclear.fa <- fa(Nuclear2, nfactors = 2, rotate = "varimax")
+
+print.psych(Nuclear.fa, cut = 0.5, sort = TRUE)
 
@@
 
-```
+# CFA Kahan
+
+Kahan_fas <- '
+  KahanS =~ K_SHARM + K_SLIMCHOI + K_SPROTECT 
+  KahanH =~ K_HEQUAL+ K_ERADEQ1 + K_EWEALTH + K_ERADEQ2
+'
+
+# Run CFA
+n2Kahan_cfa <- cfa(Kahan_fas, data = Nuclear, std.lv = TRUE)
+
+# creating table of factor scores
+
+n2Kahan_scores <- predict(n2Kahan_cfa, newdata = Nuclear)
+
+n2Kahan_Kscores <- cbind(Nuclear, n2Kahan_scores)
+
+# checking cronbach's alpha 
+nnegative <- Nuclear %>%
+  dplyr::select(HEALTHNUCLEAR,POLLUTENUCLEAR,BEAUTYNUCLEAR, DISPLACENUCLEAR)%>%
+  na.omit()
+
+nnegative.alpha <- psych::alpha(nnegative, check.keys = TRUE)
+
+# alpha = 0.79
+
+npositive <- Nuclear %>%
+  dplyr::select(DEVNUCLEAR,PROSPERNUCLEAR,NPRIDENUCLEAR,PRIDENUCLEAR)%>% #excluded JOBSnuclear 
+  na.omit()
+
+npositive.alpha <- psych::alpha(npositive, check.keys = TRUE)
+
+# alpha = 0.72
+
+```
+
+\newpage
+\blandscape
+# FA on Separate scale: Scale 2: Characteristics of the Technology(2 factor solution)
+## Nuclear Energy : positive (alpha = 0.73) and negative (alpha = 0.79) characteristics (2 factor solution)
 
@@
 
-flex <- function(data, title=NULL) {
-  # this grabs the data and converts it to a flextbale
-  flextable(data) %>%
-  # this makes the table fill the page width
-  set_table_properties(layout = "autofit", width = 1) %>%
-  # font size
+flex <- function(data, title=NULL, col_widths=NULL) {
+  tbl <- flextable(data) %>%
+           #padding(padding = 1, part = "all") %>%
+           #set_table_properties(layout = "autofit") %>%
            fontsize(size=10, part="all") %>%
-    #this adds a ttitlecreates an automatic table number
            set_caption(title, 
@@
   "Health risk(nuclear)" = "Nuclear energy poses a great risk to the health of people living around it",
-  "Job opportunities(nuclear)" = "Nuclear energy will bring jobs to the local community",
   "Community pride(nuclear)" = "I would be proud if my community used nuclear energy",
@@
   "National development(nuclear)" = "Nuclear energy pushes forward the country's development",
-  "Local prosperity(nuclear)" = "Nuclear energy brings economic prosperity to the surrounding regions",
-  "Reliance on government(nuclear)" = "I don't like the idea that I have to rely on the government for electricity from nuclear energy"
+  "Local prosperity(nuclear)" = "Nuclear energy brings economic prosperity to the surrounding regions"
 )
@@
 fa_table(Nuclear.fa, .4) %>%
-  rename("Negative Characteristics" = MR1, "Positive Characteristics" = MR2, Items= item, Code = code) %>%
-  flex("Nuclear Energy: 2 factor solution") %>%
-  autofit()
-
-```
+  rename("Social Costs" = MR1, "Pride" = MR2, Items= item) %>%
+  flex("Separate scale 2 factor solution: Nuclear energy ", col_widths = list(Items = 4.5, code = 1.5))
+
+```
+\elandscape
 
@@
   rownames_to_column("Property") %>%
-  rename("Negative Characteristics" = MR1, "Positive Characteristics" = MR2) %>%
+  rename(Social_Costs = MR1, Pride = MR2) %>%
     mutate(across(where(is.numeric), round, 3)) %>%
-    flex("Eigenvalues and Variance Explained for 2 Factor Solution")
-
-```
-
-```{r, echo = FALSE}
- # Adjust as per the number of factors
-
-#fa.diagram(Nuclear.fa, marg=c(.5,5,1,.5),size =1, adj = 0.25, e.size=.05,rsize=.35, main = "Two Factor Solution")
-
-```
-
+    flex("Eigenvalues and Variance Explained for Rotated Factor Solution")
+
+```
+
+```{r, echo=FALSE}
+
+# 2 factor
+
+Nuclear_scores <- psych::factor.scores(Nuclear2, Nuclear.fa)
+
+# The factor scores will be stored in the scores element of the returned list
+Nuclear_scores2 <- Nuclear_scores$scores
+
+#binding factor scores to the dataset
+
+Nuclearwscores2 <- cbind(Nuclear, Nuclear_scores2)%>%
+    dplyr::rename(pride = MR2)%>%
+    dplyr::rename(socialcosts = MR1)
+
+nuclearfa <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State +  socialcosts + pride , data = Nuclearwscores2)
+# Print model summary
+summary(nuclearfa)
+
+bennuclearfa <- lm(Ben_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State +  socialcosts + pride , data = Nuclearwscores2)
+# Print model summary
+summary(bennuclearfa)
+
+#n2Kahan_Kscores
+
+Nuclearwscores3<- cbind(n2Kahan_Kscores, Nuclear_scores2)%>%
+    rename(socialcosts = MR1)%>%
+  rename(pride = MR2) %>%
+  select(Risky_Nuclear, Uppercaste, Male, Hindu, Urban, age, State, socialcosts, pride) %>%
+  na.omit()
+
+nuclearfa2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State + socialcosts + pride , data = Nuclearwscores3)
+# Print model summary
+summary(nuclearfa2)
+
+#bennuclearfa2 <- lm(Ben_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State + KahanH + KahanS+ socialcosts + pride , data = Nuclearwscores3)
+# Print model summary
+#summary(bennuclearfa2)
+
+# Selecting the specific variables from the dataset
+#selected_data <- Nuclearwscores3[, c("KahanH", "KahanS", "socialcosts", "pride")]
+
+# Calculating the correlation matrix
+#corkahannew <- cor(selected_data, use = "complete.obs")  # 'use = "complete.obs"' handles missing values by excluding them
+
+# Printing the correlation matrix
+#print(corkahannew)
+
+```
+
+```{r,echo = FALSE}
+acceptance4 <- Nuclearwscores2 %>%
+   mutate(Nuclear = Ben_Nuclear - Risky_Nuclear,
+         Hyrdo = Ben_Hydro - Risky_Hydro,
+         Wind = Ben_Wind - Risky_Wind,
+         Solar = Ben_Solar - Risky_Solar,
+         Coal = Ben_Coal - Risky_Coal,
+         Gas = Ben_Gas - Risky_Gas,
+         Oil = Ben_Oil - Risky_Oil)
+
+naccept3 <- lm(Nuclear ~ age + Uppercaste + Male + Hindu + Urban + State  +  socialcosts + pride, data = acceptance4)
+
+#summary(naccept3)
+
+```
+
+\blandscape
 \newpage
+## Solar Energy : positive (alpha =0.85) and negative (alpha = 0.81)characteristics (2 factor solution)
+
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+
+Solar <- codedmodule2 %>%
+  filter(rowSums(is.na(dplyr::select(., starts_with("K_")))) == 0)%>%
+  filter(complete.cases(dplyr::select(., DISPLACESOLAR:RELYSOLAR)))
+
+Solar2 <- Solar  %>%
+  dplyr::select("DISPLACESOLAR","POLLUTESOLAR","HEALTHSOLAR","BEAUTYSOLAR","PRIDESOLAR","NPRIDESOLAR", "DEVSOLAR", "PROSPERSOLAR")%>%
+    rename(
+   "Displacement risk(Solar)" = "DISPLACESOLAR",
+  "Pollution risk(Solar)" = "POLLUTESOLAR",
+  "Health risk(Solar)" = "HEALTHSOLAR",
+  #"Job opportunities(Solar)" = "JOBSSOLAR",
+  "Spoils Natural Beauty(Solar)" = "BEAUTYSOLAR",
+  "Community pride(Solar)" = "PRIDESOLAR",
+  "National pride(Solar)" = "NPRIDESOLAR",
+  "National development(Solar)" = "DEVSOLAR",
+  "Local prosperity(Solar)" = "PROSPERSOLAR",
+  #"Reliance on government(Solar)" = "RELYSOLAR"
+    )
+
+Solar.fa <- fa(Solar2, nfactors = 2, rotate = "varimax")
+
+print.psych(Solar.fa, cut = 0.40, sort = TRUE)
+
+#fa.diagram(Solar.fa)
+
+# CFA Kahan
+
+snegative <- Solar %>%
+  dplyr::select(HEALTHSOLAR, POLLUTESOLAR,BEAUTYSOLAR, DISPLACESOLAR)%>%
+  na.omit()
+
+snegative.alpha <- psych::alpha(snegative, check.keys = TRUE)
+
+# alpha = 0.81
+
+spositive <- Solar %>%
+  dplyr::select(DEVSOLAR, PROSPERSOLAR,NPRIDESOLAR,PRIDESOLAR)%>%
+  na.omit()
+
+spositive.alpha <- psych::alpha(spositive, check.keys = TRUE)
+
+# alpha = 0.89
+
+Kahan_fas <- '
+  KahanS =~ K_SHARM + K_SLIMCHOI + K_SPROTECT 
+  KahanH =~ K_HEQUAL+ K_ERADEQ1 + K_EWEALTH + K_ERADEQ2
+'
+
+# Run CFA
+s2Kahan_cfa <- cfa(Kahan_fas, data = Solar, std.lv = TRUE)
+
+# creating table of factor scores
+
+s2Kahan_scores <- predict(s2Kahan_cfa, newdata = Solar)
+
+s2Kahan_Kscores <- cbind(Solar, s2Kahan_scores)
+
+```
+
+```{r, echo=FALSE}
+
+library(flextable)
+
+set_flextable_defaults(docx.landscape = TRUE)
+
+flex <- function(data, title=NULL, col_widths=NULL) {
+  tbl <- flextable(data) %>%
+           #padding(padding = 1, part = "all") %>%
+           #set_table_properties(layout = "autofit") %>%
+           fontsize(size=10, part="all") %>%
+           set_caption(title, 
+                       autonum = officer::run_autonum(seq_id = "tab", 
+                                                      pre_label = "Table ", 
+                                                      post_label = "\n", 
+                                                      bkm = "anytable"))
+
+  # If col_widths is provided, set column widths
+  if(!is.null(col_widths)) {
+    for(col in names(col_widths)){
+      tbl <- width(tbl, j = col, width = col_widths[[col]])
+    }
+  }
+
+  return(tbl)
+}
+
+rename_map <- c(
+  "Displacement risk(Solar)" = "Solar energy is leading to displacement of people from their land",
+  "Spoils Natural Beauty(Solar)" = "Solar energy spoils the natural beauty of the landscape",
+  "Pollution risk(Solar)" = "Solar energy increases pollution of air/water/land",
+  "Health risk(Solar)" = "Solar energy poses a great risk to the health of people living around it",
+  "Community pride(Solar)" = "I would be proud if my community used solar energy",
+  "National pride(Solar)" = "Solar energy is a mark of pride for our nation",
+  "National development(Solar)" = "Solar energy pushes forward the country's development",
+  "Local prosperity(Solar)" = "Solar energy brings economic prosperity to the surrounding regions"
+)
+
+fa_table <- function(x, cut) {
+  #get sorted loadings
+  loadings <- fa.sort(x)$loadings %>% round(3)
+  #suppress loadings
+  loadings[loadings > -cut & loadings < cut] <- ""
+  #get additional info  
+  add_info <- cbind(x$communalities, 
+                    x$uniquenesses,
+                    x$complexity) %>%
+    # make it a data frame
+    as.data.frame() %>%
+    # column names
+    rename("Communality" = V1,
+           "Uniqueness" = V2,
+           "Complexity" = V3) %>%
+    #get the item names from the vector
+    rownames_to_column("item")
+
+  #build table
+  loadings %>%
+    unclass() %>%
+    as.data.frame() %>%
+    rownames_to_column("item") %>%
+    left_join(add_info) %>%
+    mutate(
+      item = if_else(item %in% names(rename_map), rename_map[item], item),
+      code = names(rename_map)[match(item, rename_map)], # extracting short form
+      across(where(is.numeric), round, 3)
+    ) %>%
+    select(code, everything()) # reorder columns to bring code to the front
+}
+
+fa_table(Solar.fa, .4) %>%
+  rename("Pride" = MR1, "Social Costs" = MR2, Items= item) %>%
+  flex("Separate scale 2 factor solution: Solar energy ", col_widths = list(Items = 4.5, code = 1.5))
+
+```
+\elandscape
+
+```{r, echo=FALSE}
+
+library(flextable)
+
+flex <- function(data, title=NULL) {
+  # this grabs the data and converts it to a flextbale
+  flextable(data) %>%
+  # this makes the table fill the page width
+  set_table_properties(layout = "autofit", width = 1) %>%
+  # font size
+  fontsize(size=10, part="all") %>%
+    #this adds a ttitlecreates an automatic table number
+      set_caption(title, 
+                  autonum = officer::run_autonum(seq_id = "tab", 
+                                                 pre_label = "Table ", 
+                                                 post_label = "\n", 
+                                                 bkm = "anytable")) #%>%
+  # font type
+  #font(fontname="Times New Roman", part="all")
+}
+
+Solar.fa[["Vaccounted"]] %>%
+  as.data.frame() %>%
+  rownames_to_column("Property") %>%
+  rename(Pride = MR1, Social_Costs = MR2) %>%
+    mutate(across(where(is.numeric), round, 3)) %>%
+    flex("Eigenvalues and Variance Explained for Rotated Factor Solution")
+
+```
+
+```{r, echo=FALSE}
+
+# 2 factor
+
+Solar_scores <- psych::factor.scores(Solar2, Solar.fa)
+
+# The factor scores will be stored in the scores element of the returned list
+Solar_scores2 <- Solar_scores$scores
+
+#binding factor scores to the dataset
+
+Solarwscores2 <- cbind(s2Kahan_Kscores, Solar_scores2)%>%
+    rename(pride = MR1)%>%
+  rename(socialcosts = MR2)
+
+Solarfa <- lm(Risky_Solar ~  Uppercaste + Male + Hindu + Urban + age + State + pride + socialcosts, data = Solarwscores2)
+# Print model summary
+summary(Solarfa)
+
+benSolarfa <- lm(Ben_Solar ~  Uppercaste + Male + Hindu + Urban + age + State +  KahanH + KahanS + pride + socialcosts, data = Solarwscores2)
+# Print model summary
+summary(benSolarfa)
+
+```
+
+```{r,echo = FALSE}
+sacceptance4 <- Solarwscores2 %>%
+   mutate(Nuclear = Ben_Nuclear - Risky_Nuclear,
+         Hyrdo = Ben_Hydro - Risky_Hydro,
+         Wind = Ben_Wind - Risky_Wind,
+         Solar = Ben_Solar - Risky_Solar,
+         Coal = Ben_Coal - Risky_Coal,
+         Gas = Ben_Gas - Risky_Gas,
+         Oil = Ben_Oil - Risky_Oil)
+
+saccept3 <- lm(Solar ~ age + Uppercaste + Male + Hindu + Urban + State  +  socialcosts + pride, data = sacceptance4)
+
+#summary(saccept3)
+
+```
+\newpage
+\blandscape
+
+## Coal : positive (alpha = 0.67) and negative (alphs = 0.72) characteristics (2 factor solution)
+
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+
+#alpha test on Eco-pol characteristics of the technology
+
+Coal <- codedmodule2 %>%
+  filter(complete.cases(dplyr::select(., DISPLACECOAL:RELYCOAL)))
+
+Coal2 <- Coal %>%
+  dplyr::select("DISPLACECOAL","POLLUTECOAL","HEALTHCOAL","BEAUTYCOAL","PRIDECOAL","NPRIDECOAL","DEVCOAL","PROSPERCOAL")%>%
+    rename(
+   "Displacement risk(Coal)" = "DISPLACECOAL",
+  "Pollution risk(Coal)" = "POLLUTECOAL",
+  "Health risk(Coal)" = "HEALTHCOAL",
+  #"Job opportunities(Coal)" = "JOBSCOAL",
+  "Spoils Natural Beauty(Coal)" = "BEAUTYCOAL",
+  "Community pride(Coal)" = "PRIDECOAL",
+  "National pride(Coal)" = "NPRIDECOAL",
+  "National development(Coal)" = "DEVCOAL",
+  "Local prosperity(Coal)" = "PROSPERCOAL"
+  #"Reliance on government(Coal)" = "RELYCOAL"
+    )
+
+Coal.fa <- fa(Coal2, nfactors = 2, rotate = "varimax")
+
+print.psych(Coal.fa, cut = 0.40, sort = TRUE)
+
+#fa.diagram(Coal.fa)
+
+cnegative <- Coal %>%
+  dplyr::select(HEALTHCOAL, POLLUTECOAL,BEAUTYCOAL, DISPLACECOAL)%>%
+  na.omit()
+
+cnegative.alpha <- psych::alpha(cnegative, check.keys = TRUE)
+
+# alpha = 0.72
+
+cpositive <- Coal %>%
+  dplyr::select(DEVCOAL, PROSPERCOAL,NPRIDECOAL,PRIDECOAL)%>%
+  na.omit()
+
+cpositive.alpha <- psych::alpha(cpositive, check.keys = TRUE)
+
+# alpha = 0.68
+
+```
+
+```{r, echo=FALSE}
+
+library(flextable)
+
+set_flextable_defaults(docx.landscape = TRUE)
+
+flex <- function(data, title=NULL, col_widths=NULL) {
+  tbl <- flextable(data) %>%
+           #padding(padding = 1, part = "all") %>%
+           #set_table_properties(layout = "autofit") %>%
+           fontsize(size=10, part="all") %>%
+           set_caption(title, 
+                       autonum = officer::run_autonum(seq_id = "tab", 
+                                                      pre_label = "Table ", 
+                                                      post_label = "\n", 
+                                                      bkm = "anytable"))
+
+  # If col_widths is provided, set column widths
+  if(!is.null(col_widths)) {
+    for(col in names(col_widths)){
+      tbl <- width(tbl, j = col, width = col_widths[[col]])
+    }
+  }
+
+  return(tbl)
+}
+
+rename_map <- c(
+  "Displacement risk(Coal)" = "Coal powered plants is leading to displacement of people from their land",
+  "Spoils Natural Beauty(Coal)" = "Coal powered plants spoils the natural beauty of the landscape",
+  "Pollution risk(Coal)" = "Coal powered plants increases pollution of air/water/land",
+  "Health risk(Coal)" = "Coal powered plants poses a great risk to the health of people living around it",
+  "Community pride(Coal)" = "I would be proud if my community used Coal powered plants",
+  "National pride(Coal)" = "Coal powered plants is a mark of pride for our nation",
+  "National development(Coal)" = "Coal powered plants pushes forward the country's development",
+  "Local prosperity(Coal)" = "Coal powered plants brings economic prosperity to the surrounding regions"
+)
+
+fa_table <- function(x, cut) {
+  #get sorted loadings
+  loadings <- fa.sort(x)$loadings %>% round(3)
+  #suppress loadings
+  loadings[loadings > -cut & loadings < cut] <- ""
+  #get additional info  
+  add_info <- cbind(x$communalities, 
+                    x$uniquenesses,
+                    x$complexity) %>%
+    # make it a data frame
+    as.data.frame() %>%
+    # column names
+    rename("Communality" = V1,
+           "Uniqueness" = V2,
+           "Complexity" = V3) %>%
+    #get the item names from the vector
+    rownames_to_column("item")
+
+  #build table
+  loadings %>%
+    unclass() %>%
+    as.data.frame() %>%
+    rownames_to_column("item") %>%
+    left_join(add_info) %>%
+    mutate(
+      item = if_else(item %in% names(rename_map), rename_map[item], item),
+      code = names(rename_map)[match(item, rename_map)], # extracting short form
+      across(where(is.numeric), round, 3)
+    ) %>%
+    select(code, everything()) # reorder columns to bring code to the front
+}
+
+fa_table(Coal.fa, .4) %>%
+  rename("Social Costs" = MR1, "Pride" = MR2, Items= item) %>%
+  flex("Separate scale 2 factor solution: Coal ", col_widths = list(Items = 4.5, code = 1.5))
+
+```
+\elandscape
+
+```{r, echo=FALSE}
+
+library(flextable)
+
+flex <- function(data, title=NULL) {
+  # this grabs the data and converts it to a flextbale
+  flextable(data) %>%
+  # this makes the table fill the page width
+  set_table_properties(layout = "autofit", width = 1) %>%
+  # font size
+  fontsize(size=10, part="all") %>%
+    #this adds a ttitlecreates an automatic table number
+      set_caption(title, 
+                  autonum = officer::run_autonum(seq_id = "tab", 
+                                                 pre_label = "Table ", 
+                                                 post_label = "\n", 
+                                                 bkm = "anytable")) #%>%
+  # font type
+  #font(fontname="Times New Roman", part="all")
+}
+
+Coal.fa[["Vaccounted"]] %>%
+  as.data.frame() %>%
+  rownames_to_column("Property") %>%
+  rename(Social_Costs = MR1, Pride = MR2) %>%
+    mutate(across(where(is.numeric), round, 3)) %>%
+    flex("Eigenvalues and Variance Explained for Rotated Factor Solution")
+
+```
+
+```{r, echo=FALSE}
+
+# 2 factor
+
+Coal_scores <- psych::factor.scores(Coal2, Coal.fa)
+
+# The factor scores will be stored in the scores element of the returned list
+Coal_scores2 <- Coal_scores$scores
+
+#binding factor scores to the dataset
+
+Coalwscores2 <- cbind(Coal, Coal_scores2) %>%
+  rename(socialcosts = MR1)%>%
+  rename(pride = MR2)
+
+Coalfa <- lm(Risky_Coal ~  Uppercaste + Male + Hindu + Urban + age + State + socialcosts + pride , data = Coalwscores2)
+# Print model summary
+#summary(Coalfa)
+
+benCoalfa <- lm(Ben_Coal ~  Uppercaste + Male + Hindu + Urban + age + State + pride + socialcosts, data = Coalwscores2)
+# Print model summary
+#summary(benCoalfa)
+```
+
+```{r,echo = FALSE}
+cacceptance4 <- Coalwscores2 %>%
+   mutate(Nuclear = Ben_Nuclear - Risky_Nuclear,
+         Hyrdo = Ben_Hydro - Risky_Hydro,
+         Wind = Ben_Wind - Risky_Wind,
+         Solar = Ben_Solar - Risky_Solar,
+         Coal = Ben_Coal - Risky_Coal,
+         Gas = Ben_Gas - Risky_Gas,
+         Oil = Ben_Oil - Risky_Oil)
+
+caccept3 <- lm(Coal ~ age + Uppercaste + Male + Hindu + Urban + State  + socialcosts + pride, data = cacceptance4)
+
+#summary(caccept3)
+
+```
+
+\newpage
+
+## Linear Models: Perceived Risk X positive and negative characteristics of the technology
+```{r, echo=FALSE, results='asis'}
+library(stargazer)
+
+cat("\\begingroup")
+cat("\\setlength{\\tabcolsep}{1pt}")
+cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer(nuclearfa, Solarfa, Coalfa, 
+          title = "LMs with separate scale 2 FA solution: Perceived Risk",
+          type = "latex"
+)
+cat("\\endgroup")
+
+```
+
+\newpage
+
+## Linear Models: Perceived Benefit X positive and negative characteristics of the technology
+```{r, echo=FALSE, results='asis'}
+library(stargazer)
+
+cat("\\begingroup")
+cat("\\setlength{\\tabcolsep}{1pt}")
+cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer(bennuclearfa, benSolarfa, benCoalfa, 
+          title = "LMs with separate scale 2 FA solution: Perceived Benefit",
+          type = "latex"
+)
+cat("\\endgroup")
+
+```
+
+\newpage
+## Linear Models: Acceptance(Benefit - Risk) X positive and negative characteristics of the technology
+```{r, echo=FALSE, results='asis'}
+library(stargazer)
+
+cat("\\begingroup")
+cat("\\setlength{\\tabcolsep}{1pt}")
+cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer(naccept3,saccept3, caccept3, 
+          title = "LMs with separate scale 2 FA solution: Perceived Benefit",
+          type = "latex"
+)
+cat("\\endgroup")
+
+```

### 2024-01-15 FAoptions.tex
commiting after a long time. oh god

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\title{FAoptions}
\author{}
\date{\vspace{-2.5em}}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={FAoptions},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{pdflscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{hhline}
\newlength\Oldarrayrulewidth
\newlength\Oldtabcolsep
\usepackage{hyperref}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\begin{document}
\maketitle

{
\setcounter{tocdepth}{2}
\tableofcontents
}
\begin{landscape}

\hypertarget{fa-on-combined-scale-2-factor-solution-people-centered-development-and-nationalist-development}{%
\section{FA on Combined Scale (2 Factor Solution): People Centered
Development and Nationalist
Development}\label{fa-on-combined-scale-2-factor-solution-people-centered-development-and-nationalist-development}}

\hypertarget{nuclear-energy-efa-on-combined-scale-2-factor-solution}{%
\subsection{Nuclear Energy: EFA on Combined Scale (2 Factor
Solution)}\label{nuclear-energy-efa-on-combined-scale-2-factor-solution}}

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[c]{|p{1.50in}|p{4.50in}|p{0.75in}|p{0.75in}|p{0.75in}|p{0.75in}|p{0.75in}}

\caption{2\ factor\ solution}\\

\ascline{1.5pt}{666666}{1-7}

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{code}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Items}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pdevelop}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Ndevelop}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Communality}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Uniqueness}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Complexity}}} \\

\ascline{1.5pt}{666666}{1-7}\endfirsthead \caption[]{2\ factor\ solution}\\

\ascline{1.5pt}{666666}{1-7}

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{code}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Items}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pdevelop}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Ndevelop}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Communality}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Uniqueness}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Complexity}}} \\

\ascline{1.5pt}{666666}{1-7}\endhead

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Health\ risk(nuclear)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Nuclear\ energy\ poses\ a\ great\ risk\ to\ the\ health\ of\ people\ living\ around\ it}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.663}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.447}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.553}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.034}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Spoils\ Natural\ Beauty(nuclear)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Nuclear\ energy\ spoils\ the\ natural\ beauty\ of\ the\ landscape}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.619}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.390}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.610}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.035}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pollution\ risk(nuclear)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Nuclear\ energy\ increases\ pollution\ of\ air/water/land}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.578}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.335}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.665}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.002}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Displacement\ risk(nuclear)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Nuclear\ energy\ is\ leading\ to\ displacement\ of\ people\ from\ their\ land}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.574}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.371}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.629}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.249}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Anti\ Mechanisation\ of\ work}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Rapid\ mechanization\ of\ work\ is\ taking\ away\ jobs\ from\ workers\ in\ this\ country}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.54}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.336}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.664}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.297}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pro\ Regulations}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Regardless\ of\ ownership,\ the\ government\ should\ pass\ strong\ regulations\ and\ implement\ them}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.534}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.301}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.699}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.116}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Anti\ Large\ Industries}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Large\ corporations\ are\ destroying\ the\ local\ industries\ in\ India\ and\ benefiting\ only\ a\ handful\ of\ people}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.523}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.275}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.725}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.014}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Environment\ over\ Development}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Polluting\ industries\ that\ spoil\ the\ environment\ should\ be\ shut\ down\ even\ if\ it\ costs\ people\ their\ jobs}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.417}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.175}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.825}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.011}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pro\ Public\ ownership}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{The\ government\ should\ own\ most\ large\ businesses\ and\ industries}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.140}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.860}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.218}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pro\ Globaleconomy}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Foreign\ companies\ have\ led\ to\ a\ range\ of\ benefits\ for\ the\ Indian\ people\ and\ society}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.227}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.773}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.997}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pro\ Decentralisation}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Local\ politicians\ shouldn't\ have\ to\ ask\ permission\ from\ the\ central\ government\ to\ implement\ policies}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.102}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.898}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.001}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Limits\ on\ Wealth}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{A\ limit\ should\ be\ put\ to\ how\ much\ wealth\ a\ person\ can\ amass}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.153}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.847}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{2.000}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pro\ Private\ ownership}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{All\ businesses\ and\ industries\ should\ be\ owned\ privately}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.042}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.958}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.757}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pro\ Localeconomy}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{India\ would\ be\ better\ off\ if\ foreign\ companies\ didn't\ come\ to\ here}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.017}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.983}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.057}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{National\ development(nuclear)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Nuclear\ energy\ pushes\ forward\ the\ country's\ development}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.665}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.464}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.536}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.095}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Community\ pride(nuclear)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{I\ would\ be\ proud\ if\ my\ community\ used\ nuclear\ energy}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.622}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.450}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.550}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.321}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{National\ pride(nuclear)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Nuclear\ energy\ is\ a\ mark\ of\ pride\ for\ our\ nation}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.597}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.405}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.595}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.266}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Local\ prosperity(nuclear)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Nuclear\ energy\ brings\ economic\ prosperity\ to\ the\ surrounding\ regions}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.594}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.363}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.637}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.055}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Job\ opportunities(nuclear)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Nuclear\ energy\ will\ bring\ jobs\ to\ the\ local\ community}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.428}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.223}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.777}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.409}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Reliance\ on\ government(nuclear)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{I\ don't\ like\ the\ idea\ that\ I\ have\ to\ rely\ on\ the\ government\ for\ electricity\ from\ nuclear\ energy}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.156}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.844}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.005}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pro\ Large\ Industries}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Large\ scale\ industries\ are\ required\ for\ the\ development\ of\ the\ country\ that\ will\ benefit\ everyone}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.170}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.830}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.712}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pro\ Centralisation}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Laws\ and\ policies\ would\ be\ implemented\ more\ smoothly\ if\ more\ power\ lay\ with\ the\ central\ government}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.090}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.910}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.863}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Anti\ Regulations}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{There\ is\ too\ much\ red-tape\ and\ the\ government\ should\ not\ interfere\ with\ businesses\ and\ industries}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.070}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.930}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.704}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Development\ over\ Environment}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Economic\ growth\ and\ creating\ jobs\ should\ be\ prioritized\ over\ environmental\ protection}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.004}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.996}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.512}}} \\

\ascline{1.5pt}{666666}{1-7}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

\end{landscape}

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[c]{|p{0.75in}|p{0.75in}|p{0.75in}}

\caption{Eigenvalues\ and\ Variance\ Explained\ for\ Combined\ Scale\ (2\ Factor\ Solution)}\\

\ascline{1.5pt}{666666}{1-3}

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Property}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pdevelop}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Ndevelop}}} \\

\ascline{1.5pt}{666666}{1-3}\endfirsthead \caption[]{Eigenvalues\ and\ Variance\ Explained\ for\ Combined\ Scale\ (2\ Factor\ Solution)}\\

\ascline{1.5pt}{666666}{1-3}

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Property}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pdevelop}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Ndevelop}}} \\

\ascline{1.5pt}{666666}{1-3}\endhead

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{SS\ loadings}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{3.264}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{2.440}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Proportion\ Var}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.136}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.102}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Cumulative\ Var}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.136}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.238}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Proportion\ Explained}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.572}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.428}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Cumulative\ Proportion}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.572}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.000}}} \\

\ascline{1.5pt}{666666}{1-3}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

\includegraphics{FAoptions_files/figure-latex/unnamed-chunk-10-1.pdf}

\begin{verbatim}
## lavaan 0.6.15 ended normally after 17 iterations
## 
##   Estimator                                         ML
##   Optimization method                           NLMINB
##   Number of model parameters                        23
## 
##   Number of observations                           540
## 
## Model Test User Model:
##                                                       
##   Test statistic                               236.201
##   Degrees of freedom                                43
##   P-value (Chi-square)                           0.000
## 
## Model Test Baseline Model:
## 
##   Test statistic                              2291.291
##   Degrees of freedom                                55
##   P-value                                        0.000
## 
## User Model versus Baseline Model:
## 
##   Comparative Fit Index (CFI)                    0.914
##   Tucker-Lewis Index (TLI)                       0.889
## 
## Loglikelihood and Information Criteria:
## 
##   Loglikelihood user model (H0)              -8659.806
##   Loglikelihood unrestricted model (H1)      -8541.706
##                                                       
##   Akaike (AIC)                               17365.613
##   Bayesian (BIC)                             17464.319
##   Sample-size adjusted Bayesian (SABIC)      17391.309
## 
## Root Mean Square Error of Approximation:
## 
##   RMSEA                                          0.091
##   90 Percent confidence interval - lower         0.080
##   90 Percent confidence interval - upper         0.103
##   P-value H_0: RMSEA <= 0.050                    0.000
##   P-value H_0: RMSEA >= 0.080                    0.950
## 
## Standardized Root Mean Square Residual:
## 
##   SRMR                                           0.071
## 
## Parameter Estimates:
## 
##   Standard errors                             Standard
##   Information                                 Expected
##   Information saturated (h1) model          Structured
## 
## Latent Variables:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   Pdevelop =~                                                           
##     HEALTHSOLAR       0.970    0.049   19.888    0.000    0.970    0.779
##     BEAUTYSOLAR       0.820    0.052   15.860    0.000    0.820    0.654
##     DISPLACESOLAR     0.703    0.049   14.226    0.000    0.703    0.599
##     POLLUTESOLAR      1.096    0.050   22.088    0.000    1.096    0.843
##     INDUSTRYSMALL    -0.319    0.057   -5.571    0.000   -0.319   -0.255
##     OWNERREG         -0.315    0.051   -6.175    0.000   -0.315   -0.282
##     MECHANISATION    -0.452    0.052   -8.698    0.000   -0.452   -0.389
##   Ndevelop =~                                                           
##     DEVSOLAR          1.055    0.047   22.613    0.000    1.055    0.829
##     PRIDESOLAR        1.065    0.048   22.101    0.000    1.065    0.817
##     NPRIDESOLAR       1.009    0.047   21.327    0.000    1.009    0.797
##     PROSPERSOLAR      1.025    0.047   21.792    0.000    1.025    0.809
## 
## Covariances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   Pdevelop ~~                                                           
##     Ndevelop         -0.262    0.047   -5.621    0.000   -0.262   -0.262
## 
## Variances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##    .HEALTHSOLAR       0.609    0.053   11.491    0.000    0.609    0.393
##    .BEAUTYSOLAR       0.902    0.064   14.185    0.000    0.902    0.573
##    .DISPLACESOLAR     0.882    0.060   14.768    0.000    0.882    0.641
##    .POLLUTESOLAR      0.490    0.055    8.917    0.000    0.490    0.290
##    .INDUSTRYSMALL     1.463    0.090   16.230    0.000    1.463    0.935
##    .OWNERREG          1.147    0.071   16.182    0.000    1.147    0.920
##    .MECHANISATION     1.143    0.072   15.912    0.000    1.143    0.848
##    .DEVSOLAR          0.505    0.043   11.626    0.000    0.505    0.312
##    .PRIDESOLAR        0.567    0.047   12.074    0.000    0.567    0.333
##    .NPRIDESOLAR       0.585    0.046   12.661    0.000    0.585    0.365
##    .PROSPERSOLAR      0.555    0.045   12.321    0.000    0.555    0.346
##     Pdevelop          1.000                               1.000    1.000
##     Ndevelop          1.000                               1.000    1.000
\end{verbatim}

\newpage

\hypertarget{solar-energy-cfa-on-combined-scale-2-factor-solution}{%
\subsection{Solar Energy : CFA on Combined Scale (2 Factor
Solution)}\label{solar-energy-cfa-on-combined-scale-2-factor-solution}}

Solar People Centered Development alpha = 0.75

Solar Nationalist Development alpha = 0.86

\begin{landscape}\begin{table}[!h]

\caption{\label{tab:unnamed-chunk-13}Confirmatory Factor Analysis(CFA) on Solar Energy}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{l>{\raggedright\arraybackslash}p{4cm}rrrrrrrr}
\toprule
Scale & Items & Loadings & Standard Error & zvalue & pvalue & ci.lower & ci.upper & std.lv & std.all\\
\midrule
\cellcolor{gray!6}{People Centered Development} & \cellcolor{gray!6}{Solar energy poses a great risk to the health of people living around it} & \cellcolor{gray!6}{0.970} & \cellcolor{gray!6}{0.049} & \cellcolor{gray!6}{19.888} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0.8744108} & \cellcolor{gray!6}{1.0655965} & \cellcolor{gray!6}{0.9700037} & \cellcolor{gray!6}{0.7792714}\\
People Centered Development & Solar energy spoils the natural beauty of the landscape & 0.820 & 0.052 & 15.860 & 0 & 0.7190998 & 0.9218976 & 0.8204987 & 0.6537278\\
\cellcolor{gray!6}{People Centered Development} & \cellcolor{gray!6}{Solar energy is leading to displacement of people from their land} & \cellcolor{gray!6}{0.703} & \cellcolor{gray!6}{0.049} & \cellcolor{gray!6}{14.226} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0.6057287} & \cellcolor{gray!6}{0.7993080} & \cellcolor{gray!6}{0.7025183} & \cellcolor{gray!6}{0.5989088}\\
People Centered Development & Solar energy increases pollution of air/water/land & 1.096 & 0.050 & 22.088 & 0 & 0.9990468 & 1.1936080 & 1.0963274 & 0.8428439\\
\cellcolor{gray!6}{People Centered Development} & \cellcolor{gray!6}{Large corporations are destroying the local industries in India and benefiting only a handful of people} & \cellcolor{gray!6}{-0.319} & \cellcolor{gray!6}{0.057} & \cellcolor{gray!6}{-5.571} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{-0.4318889} & \cellcolor{gray!6}{-0.2070914} & \cellcolor{gray!6}{-0.3194901} & \cellcolor{gray!6}{-0.2554075}\\
\addlinespace
People Centered Development & Regardless of ownership, the government should pass strong regulations and implement them & -0.315 & 0.051 & -6.175 & 0 & -0.4147132 & -0.2148716 & -0.3147924 & -0.2819769\\
\cellcolor{gray!6}{People Centered Development} & \cellcolor{gray!6}{Rapid mechanization of work is taking away jobs from workers in this country} & \cellcolor{gray!6}{-0.452} & \cellcolor{gray!6}{0.052} & \cellcolor{gray!6}{-8.698} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{-0.5538088} & \cellcolor{gray!6}{-0.3501230} & \cellcolor{gray!6}{-0.4519659} & \cellcolor{gray!6}{-0.3893190}\\
Nationalist Development & Solar energy pushes forward the country's development & 1.055 & 0.047 & 22.613 & 0 & 0.9638459 & 1.1467835 & 1.0553147 & 0.8294606\\
\cellcolor{gray!6}{Nationalist Development} & \cellcolor{gray!6}{I would be proud if my community used Solar energy} & \cellcolor{gray!6}{1.065} & \cellcolor{gray!6}{0.048} & \cellcolor{gray!6}{22.101} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0.9708762} & \cellcolor{gray!6}{1.1598306} & \cellcolor{gray!6}{1.0653534} & \cellcolor{gray!6}{0.8166840}\\
Nationalist Development & Solar energy is a mark of pride for our nation & 1.009 & 0.047 & 21.327 & 0 & 0.9161682 & 1.1016049 & 1.0088866 & 0.7969797\\
\bottomrule
\end{tabular}}
\end{table}
\end{landscape}

\begin{verbatim}
## 
## Call:
## lm(formula = Risky_Solar ~ age + Uppercaste + Male + Hindu + 
##     Urban + State + KahanS + KahanH + Pdevelop + Ndevelop, data = sfascale_scores)
## 
## Residuals:
##     Min      1Q  Median      3Q     Max 
## -1.9138 -0.4677 -0.1288  0.2755  3.8143 
## 
## Coefficients:
##                     Estimate Std. Error t value Pr(>|t|)    
## (Intercept)         2.737482   0.143017  19.141  < 2e-16 ***
## age                -0.005030   0.035936  -0.140  0.88874    
## Uppercaste         -0.033151   0.082097  -0.404  0.68653    
## Male               -0.004959   0.090677  -0.055  0.95641    
## Hindu              -0.137916   0.095575  -1.443  0.14963    
## UrbanUrban         -0.066933   0.091671  -0.730  0.46564    
## StateRajasthan     -1.351258   0.143198  -9.436  < 2e-16 ***
## StateTamil Nadu    -1.314794   0.170603  -7.707 6.73e-14 ***
## StateUttar Pradesh -0.926163   0.158665  -5.837 9.42e-09 ***
## StateWest Bengal   -0.969840   0.185254  -5.235 2.41e-07 ***
## KahanS              0.031638   0.069903   0.453  0.65103    
## KahanH             -0.196447   0.067244  -2.921  0.00364 ** 
## Pdevelop            0.031323   0.061275   0.511  0.60943    
## Ndevelop            0.012994   0.053525   0.243  0.80828    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 0.8389 on 513 degrees of freedom
##   (13 observations deleted due to missingness)
## Multiple R-squared:  0.4297, Adjusted R-squared:  0.4152 
## F-statistic: 29.73 on 13 and 513 DF,  p-value: < 2.2e-16
\end{verbatim}

\newpage

\hypertarget{coal-cfa-on-combined-scale-2-factor-solution-pdevelop-and-ndevelop}{%
\subsection{Coal : CFA on Combined Scale 2 Factor Solution (Pdevelop and
Ndevelop)}\label{coal-cfa-on-combined-scale-2-factor-solution-pdevelop-and-ndevelop}}

Coal People Centered Development Alpha = 0.78

Coal Nationalist Development Alpha = 0.6

\begin{landscape}\begin{table}[!h]

\caption{\label{tab:unnamed-chunk-18}Confirmatory Factor Analysis(CFA) on Coal}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{l>{\raggedright\arraybackslash}p{4cm}rrrrrrrr}
\toprule
Scale & Items & Loadings & Standard Error & zvalue & pvalue & ci.lower & ci.upper & std.lv & std.all\\
\midrule
\cellcolor{gray!6}{People Centered Development} & \cellcolor{gray!6}{Coal powered plants poses a great risk to the health of people living around it} & \cellcolor{gray!6}{0.722} & \cellcolor{gray!6}{0.050} & \cellcolor{gray!6}{14.378} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0.6231797} & \cellcolor{gray!6}{0.8199012} & \cellcolor{gray!6}{0.7215405} & \cellcolor{gray!6}{0.6589018}\\
People Centered Development & Coal powered plants spoils the natural beauty of the landscape & 0.717 & 0.048 & 14.839 & 0 & 0.6227149 & 0.8122502 & 0.7174825 & 0.6758232\\
\cellcolor{gray!6}{People Centered Development} & \cellcolor{gray!6}{Coal powered plants is leading to displacement of people from their land} & \cellcolor{gray!6}{0.626} & \cellcolor{gray!6}{0.055} & \cellcolor{gray!6}{11.301} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0.5172562} & \cellcolor{gray!6}{0.7343179} & \cellcolor{gray!6}{0.6257871} & \cellcolor{gray!6}{0.5394144}\\
People Centered Development & Coal powered plants increases pollution of air/water/land & 0.630 & 0.041 & 15.260 & 0 & 0.5488005 & 0.7105443 & 0.6296724 & 0.6910990\\
\cellcolor{gray!6}{People Centered Development} & \cellcolor{gray!6}{Large corporations are destroying the local industries in India and benefiting only a handful of people} & \cellcolor{gray!6}{0.601} & \cellcolor{gray!6}{0.057} & \cellcolor{gray!6}{10.462} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0.4883282} & \cellcolor{gray!6}{0.7134684} & \cellcolor{gray!6}{0.6008983} & \cellcolor{gray!6}{0.5045829}\\
\addlinespace
People Centered Development & Regardless of ownership, the government should pass strong regulations and implement them & 0.488 & 0.055 & 8.904 & 0 & 0.3808612 & 0.5958528 & 0.4883570 & 0.4372022\\
\cellcolor{gray!6}{People Centered Development} & \cellcolor{gray!6}{Rapid mechanization of work is taking away jobs from workers in this country} & \cellcolor{gray!6}{0.658} & \cellcolor{gray!6}{0.056} & \cellcolor{gray!6}{11.805} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0.5489483} & \cellcolor{gray!6}{0.7675273} & \cellcolor{gray!6}{0.6582378} & \cellcolor{gray!6}{0.5598383}\\
Nationalist Development & Coal powered plants pushes forward the country's development & 0.629 & 0.059 & 10.700 & 0 & 0.5137870 & 0.7442109 & 0.6289990 & 0.6259019\\
\cellcolor{gray!6}{Nationalist Development} & \cellcolor{gray!6}{Coal powered plants brings economic prosperity to the surrounding regions} & \cellcolor{gray!6}{0.596} & \cellcolor{gray!6}{0.058} & \cellcolor{gray!6}{10.338} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0.4830019} & \cellcolor{gray!6}{0.7090010} & \cellcolor{gray!6}{0.5960014} & \cellcolor{gray!6}{0.5996861}\\
Nationalist Development & I would be proud if my community used Coal powered plants & 0.445 & 0.063 & 7.096 & 0 & 0.3220686 & 0.5678796 & 0.4449741 & 0.4027845\\
\bottomrule
\end{tabular}}
\end{table}
\end{landscape}

\newpage

\hypertarget{linear-models-perceived-risk-x-pdevelop-and-ndevelop}{%
\subsection{Linear Models: Perceived risk X Pdevelop and
Ndevelop}\label{linear-models-perceived-risk-x-pdevelop-and-ndevelop}}

\begingroup\setlength{\tabcolsep}{1pt}\renewcommand{\arraystretch}{0.7}

\% Table created by stargazer v.5.2.3 by Marek Hlavac, Social Policy
Institute. E-mail: marek.hlavac at gmail.com \% Date and time: Wed, Jan
10, 2024 - 10:07:32

\begin{table}[!htbp] \centering 
  \caption{Perceived Risk X Pdevelop and Ndevelope} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
\cline{2-4} 
\\[-1.8ex] & Risky\_Nuclear & Risky\_Solar & Risky\_Coal \\ 
\\[-1.8ex] & (1) & (2) & (3)\\ 
\hline \\[-1.8ex] 
 age & 0.037 & $-$0.005 & 0.133$^{***}$ \\ 
  & (0.051) & (0.036) & (0.046) \\ 
  & & & \\ 
 Uppercaste & $-$0.035 & $-$0.033 & $-$0.060 \\ 
  & (0.106) & (0.082) & (0.090) \\ 
  & & & \\ 
 Male & $-$0.085 & $-$0.005 & 0.019 \\ 
  & (0.116) & (0.091) & (0.103) \\ 
  & & & \\ 
 Hindu & 0.024 & $-$0.138 & 0.155 \\ 
  & (0.117) & (0.096) & (0.106) \\ 
  & & & \\ 
 UrbanUrban & 0.023 & $-$0.067 & 0.051 \\ 
  & (0.111) & (0.092) & (0.102) \\ 
  & & & \\ 
 StateRajasthan & 0.190 & $-$1.351$^{***}$ & $-$0.349$^{**}$ \\ 
  & (0.181) & (0.143) & (0.142) \\ 
  & & & \\ 
 StateTamil Nadu & 1.293$^{***}$ & $-$1.315$^{***}$ & $-$1.387$^{***}$ \\ 
  & (0.239) & (0.171) & (0.226) \\ 
  & & & \\ 
 StateUttar Pradesh & $-$0.056 & $-$0.926$^{***}$ & $-$1.243$^{***}$ \\ 
  & (0.193) & (0.159) & (0.171) \\ 
  & & & \\ 
 StateWest Bengal & 0.972$^{***}$ & $-$0.970$^{***}$ & $-$0.124 \\ 
  & (0.226) & (0.185) & (0.198) \\ 
  & & & \\ 
 KahanS & 0.108 & 0.032 & 0.044 \\ 
  & (0.103) & (0.070) & (0.085) \\ 
  & & & \\ 
 KahanH & 0.003 & $-$0.196$^{***}$ & 0.148$^{*}$ \\ 
  & (0.095) & (0.067) & (0.086) \\ 
  & & & \\ 
 Pdevelop & 0.145$^{*}$ & 0.031 & 0.412$^{***}$ \\ 
  & (0.075) & (0.061) & (0.079) \\ 
  & & & \\ 
 Ndevelop & 0.236$^{***}$ & 0.013 & 0.031 \\ 
  & (0.061) & (0.054) & (0.067) \\ 
  & & & \\ 
 Constant & 3.028$^{***}$ & 2.737$^{***}$ & 3.069$^{***}$ \\ 
  & (0.172) & (0.143) & (0.157) \\ 
  & & & \\ 
\hline \\[-1.8ex] 
Observations & 405 & 527 & 457 \\ 
R$^{2}$ & 0.289 & 0.430 & 0.287 \\ 
Adjusted R$^{2}$ & 0.266 & 0.415 & 0.266 \\ 
Residual Std. Error & 0.925 (df = 391) & 0.839 (df = 513) & 0.877 (df = 443) \\ 
F Statistic & 12.248$^{***}$ (df = 13; 391) & 29.727$^{***}$ (df = 13; 513) & 13.728$^{***}$ (df = 13; 443) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 
\endgroup

\newpage

\hypertarget{linear-models-perceived-benefit-x-pdevelop-and-ndevelop}{%
\subsection{Linear Models: Perceived Benefit X Pdevelop and
Ndevelop}\label{linear-models-perceived-benefit-x-pdevelop-and-ndevelop}}

\begingroup\setlength{\tabcolsep}{1pt}

\renewcommand{\arraystretch}{0.7}

\% Table created by stargazer v.5.2.3 by Marek Hlavac, Social Policy
Institute. E-mail: marek.hlavac at gmail.com \% Date and time: Wed, Jan
10, 2024 - 10:07:33

\begin{table}[!htbp] \centering 
  \caption{Perceived Benefit X Pdevelop and Ndevelop} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
\cline{2-4} 
\\[-1.8ex] & Ben\_Nuclear & Ben\_Solar & Ben\_Coal \\ 
\\[-1.8ex] & (1) & (2) & (3)\\ 
\hline \\[-1.8ex] 
 Uppercaste & $-$0.178$^{*}$ & $-$0.119 & $-$0.236$^{***}$ \\ 
  & (0.102) & (0.080) & (0.091) \\ 
  & & & \\ 
 Male & 0.036 & 0.0002 & 0.037 \\ 
  & (0.112) & (0.088) & (0.103) \\ 
  & & & \\ 
 Hindu & 0.329$^{***}$ & 0.169$^{*}$ & 0.039 \\ 
  & (0.113) & (0.093) & (0.107) \\ 
  & & & \\ 
 UrbanUrban & 0.093 & $-$0.081 & 0.169 \\ 
  & (0.107) & (0.089) & (0.103) \\ 
  & & & \\ 
 age & $-$0.073 & $-$0.023 & 0.029 \\ 
  & (0.050) & (0.034) & (0.046) \\ 
  & & & \\ 
 StateRajasthan & $-$0.573$^{***}$ & 0.495$^{***}$ & $-$0.327$^{**}$ \\ 
  & (0.175) & (0.147) & (0.142) \\ 
  & & & \\ 
 StateTamil Nadu & $-$0.406$^{*}$ & 0.564$^{***}$ & $-$0.316 \\ 
  & (0.235) & (0.177) & (0.238) \\ 
  & & & \\ 
 StateUttar Pradesh & $-$0.516$^{***}$ & 0.077 & $-$0.531$^{***}$ \\ 
  & (0.187) & (0.159) & (0.173) \\ 
  & & & \\ 
 StateWest Bengal & $-$0.095 & 0.943$^{***}$ & $-$0.169 \\ 
  & (0.222) & (0.184) & (0.198) \\ 
  & & & \\ 
 KahanS & $-$0.057 & 0.014 & $-$0.017 \\ 
  & (0.103) & (0.069) & (0.086) \\ 
  & & & \\ 
 KahanH & 0.231$^{**}$ & 0.140$^{**}$ & 0.141 \\ 
  & (0.093) & (0.070) & (0.087) \\ 
  & & & \\ 
 Pdevelop & 0.191$^{***}$ & 0.194$^{***}$ & 0.265$^{***}$ \\ 
  & (0.073) & (0.048) & (0.066) \\ 
  & & & \\ 
 Ndevelop & 0.292$^{***}$ & $-$0.018 & 0.213$^{***}$ \\ 
  & (0.060) & (0.068) & (0.049) \\ 
  & & & \\ 
 Constant & 3.287$^{***}$ & 3.426$^{***}$ & 3.205$^{***}$ \\ 
  & (0.166) & (0.139) & (0.157) \\ 
  & & & \\ 
\hline \\[-1.8ex] 
Observations & 407 & 535 & 455 \\ 
R$^{2}$ & 0.193 & 0.254 & 0.171 \\ 
Adjusted R$^{2}$ & 0.166 & 0.235 & 0.147 \\ 
Residual Std. Error & 0.898 (df = 393) & 0.815 (df = 521) & 0.880 (df = 441) \\ 
F Statistic & 7.210$^{***}$ (df = 13; 393) & 13.635$^{***}$ (df = 13; 521) & 7.020$^{***}$ (df = 13; 441) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 
\endgroup

\newpage

\hypertarget{linear-models-acceptance-risk---benefit-x-pdevelop-ndevelop}{%
\subsection{Linear Models: Acceptance (Risk - Benefit) X Pdevelop \&
Ndevelop}\label{linear-models-acceptance-risk---benefit-x-pdevelop-ndevelop}}

\begingroup\setlength{\tabcolsep}{1pt}

\renewcommand{\arraystretch}{0.7}

\% Table created by stargazer v.5.2.3 by Marek Hlavac, Social Policy
Institute. E-mail: marek.hlavac at gmail.com \% Date and time: Wed, Jan
10, 2024 - 10:07:33

\begin{table}[!htbp] \centering 
  \caption{Acceptance (Risk - Benefit) X Pdevelop and Ndevelop} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
\cline{2-4} 
\\[-1.8ex] & Nuclear & Solar & Coal \\ 
\\[-1.8ex] & (1) & (2) & (3)\\ 
\hline \\[-1.8ex] 
 age & $-$0.108 & $-$0.016 & $-$0.148$^{**}$ \\ 
  & (0.069) & (0.053) & (0.062) \\ 
  & & & \\ 
 Uppercaste & $-$0.153 & $-$0.091 & $-$0.162 \\ 
  & (0.143) & (0.121) & (0.120) \\ 
  & & & \\ 
 Male & 0.146 & 0.015 & 0.013 \\ 
  & (0.157) & (0.133) & (0.137) \\ 
  & & & \\ 
 Hindu & 0.324$^{**}$ & 0.310$^{**}$ & $-$0.194 \\ 
  & (0.158) & (0.141) & (0.141) \\ 
  & & & \\ 
 UrbanUrban & 0.093 & 0.040 & 0.079 \\ 
  & (0.150) & (0.135) & (0.136) \\ 
  & & & \\ 
 StateRajasthan & $-$0.771$^{***}$ & 1.830$^{***}$ & 0.143 \\ 
  & (0.244) & (0.213) & (0.188) \\ 
  & & & \\ 
 StateTamil Nadu & $-$1.747$^{***}$ & 1.820$^{***}$ & 1.177$^{***}$ \\ 
  & (0.327) & (0.251) & (0.302) \\ 
  & & & \\ 
 StateUttar Pradesh & $-$0.462$^{*}$ & 0.990$^{***}$ & 0.791$^{***}$ \\ 
  & (0.261) & (0.235) & (0.228) \\ 
  & & & \\ 
 StateWest Bengal & $-$1.082$^{***}$ & 1.860$^{***}$ & $-$0.055 \\ 
  & (0.309) & (0.274) & (0.261) \\ 
  & & & \\ 
 KahanS & $-$0.193 & $-$0.044 & $-$0.042 \\ 
  & (0.139) & (0.103) & (0.113) \\ 
  & & & \\ 
 KahanH & 0.257$^{**}$ & 0.340$^{***}$ & 0.031 \\ 
  & (0.128) & (0.099) & (0.114) \\ 
  & & & \\ 
 Pdevelop & 0.023 & $-$0.039 & $-$0.374$^{***}$ \\ 
  & (0.103) & (0.090) & (0.106) \\ 
  & & & \\ 
 Ndevelop & 0.066 & 0.193$^{**}$ & 0.367$^{***}$ \\ 
  & (0.084) & (0.079) & (0.089) \\ 
  & & & \\ 
 Constant & 0.220 & 0.675$^{***}$ & 0.260 \\ 
  & (0.232) & (0.211) & (0.209) \\ 
  & & & \\ 
\hline \\[-1.8ex] 
Observations & 401 & 524 & 453 \\ 
R$^{2}$ & 0.164 & 0.471 & 0.099 \\ 
Adjusted R$^{2}$ & 0.136 & 0.458 & 0.072 \\ 
Residual Std. Error & 1.246 (df = 387) & 1.230 (df = 510) & 1.159 (df = 439) \\ 
F Statistic & 5.825$^{***}$ (df = 13; 387) & 34.992$^{***}$ (df = 13; 510) & 3.713$^{***}$ (df = 13; 439) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 
\endgroup

\newpage
\begin{landscape}

\hypertarget{fa-on-separate-scales-scale-1eco-political-values-of-the-perceiver}{%
\section{FA on Separate scales: Scale 1:Eco-political values of the
perceiver}\label{fa-on-separate-scales-scale-1eco-political-values-of-the-perceiver}}

\hypertarget{factor-solution-characteristics-of-the-perceiver}{%
\subsection{4 factor solution (Characteristics of the
perceiver)}\label{factor-solution-characteristics-of-the-perceiver}}

Cronbach's alpha values: Regulated Industrialisation = 0.59,
localisation = 0.52 , Free market = 0.57, Private Development = 0.58

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[c]{|p{1.50in}|p{3.50in}|p{0.50in}|p{0.50in}|p{0.50in}|p{0.50in}|p{0.75in}|p{0.75in}|p{0.75in}}

\caption{4\ factor\ solution\ same\ for\ all\ technologies}\\

\ascline{1.5pt}{666666}{1-9}

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{code}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Items}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{regulated\ industrialization}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{localisation}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{free\ market}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{private\ development}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Communality}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Uniqueness}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Complexity}}} \\

\ascline{1.5pt}{666666}{1-9}\endfirsthead \caption[]{4\ factor\ solution\ same\ for\ all\ technologies}\\

\ascline{1.5pt}{666666}{1-9}

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{code}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Items}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{regulated\ industrialization}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{localisation}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{free\ market}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{private\ development}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Communality}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Uniqueness}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Complexity}}} \\

\ascline{1.5pt}{666666}{1-9}\endhead

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pro\ Regulations}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Regardless\ of\ ownership,\ the\ government\ should\ pass\ strong\ regulations\ and\ implement\ them}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.54}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.366}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.634}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.520}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Anti\ Mechanisation\ of\ work}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Rapid\ mechanization\ of\ work\ is\ taking\ away\ jobs\ from\ workers\ in\ this\ country}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.506}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.330}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.670}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.585}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Limits\ on\ Wealth}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{A\ limit\ should\ be\ put\ to\ how\ much\ wealth\ a\ person\ can\ amass}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.483}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.304}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.696}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.638}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Anti\ Large\ Industries}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Large\ corporations\ are\ destroying\ the\ local\ industries\ in\ India\ and\ benefiting\ only\ a\ handful\ of\ people}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.534}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.409}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.591}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.780}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pro\ Localeconomy}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{India\ would\ be\ better\ off\ if\ foreign\ companies\ didn't\ come\ to\ here}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.524}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.287}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.713}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.090}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pro\ Decentralisation}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Local\ politicians\ shouldn't\ have\ to\ ask\ permission\ from\ the\ central\ government\ to\ implement\ policies}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.134}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.866}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{2.021}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pro\ Centralisation}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Laws\ and\ policies\ would\ be\ implemented\ more\ smoothly\ if\ more\ power\ lay\ with\ the\ central\ government}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.488}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.280}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.720}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.360}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pro\ Globaleconomy}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Foreign\ companies\ have\ led\ to\ a\ range\ of\ benefits\ for\ the\ Indian\ people\ and\ society}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.478}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.298}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.702}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.598}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Anti\ Regulations}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{There\ is\ too\ much\ red-tape\ and\ the\ government\ should\ not\ interfere\ with\ businesses\ and\ industries}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.473}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.399}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.601}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{2.220}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pro\ Large\ Industries}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Large\ scale\ industries\ are\ required\ for\ the\ development\ of\ the\ country\ that\ will\ benefit\ everyone}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.432}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.302}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.698}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.902}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Development\ over\ Environment}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Economic\ growth\ and\ creating\ jobs\ should\ be\ prioritized\ over\ environmental\ protection}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.536}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.290}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.710}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.014}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pro\ Private\ ownership}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{All\ businesses\ and\ industries\ should\ be\ owned\ privately}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.508}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.274}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.726}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.121}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Environment\ over\ Development}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Polluting\ industries\ that\ spoil\ the\ environment\ should\ be\ shut\ down\ even\ if\ it\ costs\ people\ their\ jobs}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{-0.464}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.428}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.572}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{2.548}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pro\ Public\ ownership}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{The\ government\ should\ own\ most\ large\ businesses\ and\ industries}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{-0.43}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.433}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.567}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{3.201}}} \\

\ascline{1.5pt}{666666}{1-9}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

\end{landscape}

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[c]{ccccc}

\caption{Eigenvalues\ and\ Variance\ Explained\ for\ Rotated\ Factor\ Solution}\\

\ascline{1.5pt}{666666}{1-5}

\multicolumn{1}{>{}l}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Property}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{MR1}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{MR3}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{MR4}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{MR2}}} \\

\ascline{1.5pt}{666666}{1-5}\endfirsthead \caption[]{Eigenvalues\ and\ Variance\ Explained\ for\ Rotated\ Factor\ Solution}\\

\ascline{1.5pt}{666666}{1-5}

\multicolumn{1}{>{}l}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Property}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{MR1}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{MR3}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{MR4}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{MR2}}} \\

\ascline{1.5pt}{666666}{1-5}\endhead

\multicolumn{1}{>{}l}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{SS\ loadings}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.215}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.191}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.091}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.037}}} \\

\multicolumn{1}{>{}l}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Proportion\ Var}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.087}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.085}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.078}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.074}}} \\

\multicolumn{1}{>{}l}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Cumulative\ Var}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.087}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.172}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.250}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.324}}} \\

\multicolumn{1}{>{}l}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Proportion\ Explained}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.268}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.263}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.241}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.229}}} \\

\multicolumn{1}{>{}l}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Cumulative\ Proportion}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.268}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.531}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.771}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.000}}} \\

\ascline{1.5pt}{666666}{1-5}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

\newpage

\hypertarget{linear-models-perceived-risk-x-4-factor-solutionseparate-scale}{%
\subsection{Linear Models: Perceived Risk X 4 Factor Solution(separate
scale)}\label{linear-models-perceived-risk-x-4-factor-solutionseparate-scale}}

\begingroup\setlength{\tabcolsep}{1pt}

\renewcommand{\arraystretch}{0.7}

\% Table created by stargazer v.5.2.3 by Marek Hlavac, Social Policy
Institute. E-mail: marek.hlavac at gmail.com \% Date and time: Wed, Jan
10, 2024 - 10:07:34

\begin{table}[!htbp] \centering 
  \caption{Perceived Risk X 4 Factor Solution(separate scale)} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
\cline{2-4} 
\\[-1.8ex] & Risky\_Nuclear & Risky\_Solar & Risky\_Coal \\ 
\\[-1.8ex] & (1) & (2) & (3)\\ 
\hline \\[-1.8ex] 
 Uppercaste & $-$0.116 & 0.001 & $-$0.070 \\ 
  & (0.102) & (0.072) & (0.088) \\ 
  & & & \\ 
 Male & 0.107 & $-$0.023 & 0.001 \\ 
  & (0.108) & (0.078) & (0.095) \\ 
  & & & \\ 
 Hindu & $-$0.009 & $-$0.121 & 0.196$^{*}$ \\ 
  & (0.120) & (0.088) & (0.104) \\ 
  & & & \\ 
 UrbanUrban & 0.197$^{*}$ & $-$0.064 & 0.174$^{*}$ \\ 
  & (0.105) & (0.080) & (0.095) \\ 
  & & & \\ 
 age & $-$0.155$^{***}$ & $-$0.023 & 0.003 \\ 
  & (0.043) & (0.031) & (0.038) \\ 
  & & & \\ 
 StateRajasthan & 0.474$^{***}$ & $-$1.602$^{***}$ & 0.081 \\ 
  & (0.166) & (0.116) & (0.139) \\ 
  & & & \\ 
 StateTamil Nadu & $-$0.251 & $-$1.721$^{***}$ & $-$1.434$^{***}$ \\ 
  & (0.189) & (0.138) & (0.169) \\ 
  & & & \\ 
 StateUttar Pradesh & 0.111 & $-$1.248$^{***}$ & $-$0.763$^{***}$ \\ 
  & (0.188) & (0.137) & (0.163) \\ 
  & & & \\ 
 StateWest Bengal & 1.444$^{***}$ & $-$1.309$^{***}$ & 0.372$^{**}$ \\ 
  & (0.199) & (0.151) & (0.182) \\ 
  & & & \\ 
 regulateindustry & 0.071 & 0.080$^{**}$ & 0.210$^{***}$ \\ 
  & (0.055) & (0.041) & (0.049) \\ 
  & & & \\ 
 localisation & 0.101$^{*}$ & 0.069$^{*}$ & 0.139$^{***}$ \\ 
  & (0.052) & (0.038) & (0.046) \\ 
  & & & \\ 
 freemarket & $-$0.085$^{*}$ & 0.049 & $-$0.093$^{**}$ \\ 
  & (0.047) & (0.036) & (0.043) \\ 
  & & & \\ 
 pvtdevelopment & $-$0.095 & 0.010 & $-$0.002 \\ 
  & (0.060) & (0.042) & (0.051) \\ 
  & & & \\ 
 Constant & 3.282$^{***}$ & 2.990$^{***}$ & 3.163$^{***}$ \\ 
  & (0.167) & (0.125) & (0.148) \\ 
  & & & \\ 
\hline \\[-1.8ex] 
Observations & 609 & 686 & 644 \\ 
R$^{2}$ & 0.157 & 0.434 & 0.242 \\ 
Adjusted R$^{2}$ & 0.139 & 0.423 & 0.226 \\ 
Residual Std. Error & 1.088 (df = 595) & 0.838 (df = 672) & 0.969 (df = 630) \\ 
F Statistic & 8.539$^{***}$ (df = 13; 595) & 39.620$^{***}$ (df = 13; 672) & 15.450$^{***}$ (df = 13; 630) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 
\endgroup

\newpage

\hypertarget{linear-models-perceived-risk-x-4-factor-solution-separate-scale}{%
\subsection{Linear Models: : Perceived Risk X 4 Factor Solution
(separate
scale)}\label{linear-models-perceived-risk-x-4-factor-solution-separate-scale}}

\begingroup\setlength{\tabcolsep}{1pt}

\renewcommand{\arraystretch}{0.7}

\% Table created by stargazer v.5.2.3 by Marek Hlavac, Social Policy
Institute. E-mail: marek.hlavac at gmail.com \% Date and time: Wed, Jan
10, 2024 - 10:07:35

\begin{table}[!htbp] \centering 
  \caption{Perceived Risk X 4 Factor Solution (separate scale)} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
\cline{2-4} 
\\[-1.8ex] & Ben\_Nuclear & Ben\_Solar & Ben\_Coal \\ 
\\[-1.8ex] & (1) & (2) & (3)\\ 
\hline \\[-1.8ex] 
 Uppercaste & $-$0.155$^{*}$ & $-$0.084 & $-$0.263$^{***}$ \\ 
  & (0.085) & (0.072) & (0.081) \\ 
  & & & \\ 
 Male & $-$0.00003 & $-$0.022 & 0.129 \\ 
  & (0.089) & (0.077) & (0.090) \\ 
  & & & \\ 
 Hindu & 0.378$^{***}$ & 0.172$^{**}$ & 0.110 \\ 
  & (0.100) & (0.087) & (0.097) \\ 
  & & & \\ 
 UrbanUrban & 0.079 & 0.082 & 0.104 \\ 
  & (0.089) & (0.078) & (0.091) \\ 
  & & & \\ 
 age & 0.009 & $-$0.026 & 0.044 \\ 
  & (0.035) & (0.030) & (0.038) \\ 
  & & & \\ 
 StateRajasthan & $-$0.516$^{***}$ & 0.792$^{***}$ & $-$0.265$^{**}$ \\ 
  & (0.139) & (0.115) & (0.130) \\ 
  & & & \\ 
 StateTamil Nadu & 0.042 & 0.398$^{***}$ & $-$0.064 \\ 
  & (0.157) & (0.137) & (0.162) \\ 
  & & & \\ 
 StateUttar Pradesh & $-$0.775$^{***}$ & 0.251$^{*}$ & $-$0.772$^{***}$ \\ 
  & (0.160) & (0.137) & (0.155) \\ 
  & & & \\ 
 StateWest Bengal & $-$0.102 & 1.111$^{***}$ & $-$0.256 \\ 
  & (0.171) & (0.150) & (0.173) \\ 
  & & & \\ 
 regulateindustry & 0.276$^{***}$ & 0.093$^{**}$ & 0.283$^{***}$ \\ 
  & (0.047) & (0.040) & (0.047) \\ 
  & & & \\ 
 localisation & 0.184$^{***}$ & 0.029 & 0.179$^{***}$ \\ 
  & (0.042) & (0.037) & (0.044) \\ 
  & & & \\ 
 freemarket & 0.358$^{***}$ & $-$0.041 & 0.186$^{***}$ \\ 
  & (0.039) & (0.034) & (0.040) \\ 
  & & & \\ 
 pvtdevelopment & 0.080$^{*}$ & 0.064 & 0.094$^{*}$ \\ 
  & (0.049) & (0.042) & (0.049) \\ 
  & & & \\ 
 Constant & 3.265$^{***}$ & 3.298$^{***}$ & 3.249$^{***}$ \\ 
  & (0.139) & (0.122) & (0.140) \\ 
  & & & \\ 
\hline \\[-1.8ex] 
Observations & 626 & 701 & 625 \\ 
R$^{2}$ & 0.253 & 0.187 & 0.165 \\ 
Adjusted R$^{2}$ & 0.237 & 0.171 & 0.147 \\ 
Residual Std. Error & 0.915 (df = 612) & 0.833 (df = 687) & 0.901 (df = 611) \\ 
F Statistic & 15.953$^{***}$ (df = 13; 612) & 12.140$^{***}$ (df = 13; 687) & 9.291$^{***}$ (df = 13; 611) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 
\endgroup

\newpage

\hypertarget{linear-models-acceptancerisk-benefit-x-4-factor-solution-separate-scale}{%
\subsection{Linear Models: Acceptance(Risk-Benefit) X 4 Factor Solution
(separate
scale)}\label{linear-models-acceptancerisk-benefit-x-4-factor-solution-separate-scale}}

\begingroup\setlength{\tabcolsep}{1pt}

\renewcommand{\arraystretch}{0.7}

\% Table created by stargazer v.5.2.3 by Marek Hlavac, Social Policy
Institute. E-mail: marek.hlavac at gmail.com \% Date and time: Wed, Jan
10, 2024 - 10:07:35

\begin{table}[!htbp] \centering 
  \caption{Acceptance(Risk-Benefit) X 4 Factor Solution (separate scale)} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
\cline{2-4} 
\\[-1.8ex] & Nuclear & Solar & Coal \\ 
\\[-1.8ex] & (1) & (2) & (3)\\ 
\hline \\[-1.8ex] 
 age & 0.134$^{**}$ & $-$0.010 & 0.007 \\ 
  & (0.058) & (0.045) & (0.055) \\ 
  & & & \\ 
 Uppercaste & $-$0.072 & $-$0.102 & $-$0.181 \\ 
  & (0.136) & (0.105) & (0.116) \\ 
  & & & \\ 
 Male & $-$0.066 & 0.005 & 0.115 \\ 
  & (0.145) & (0.114) & (0.128) \\ 
  & & & \\ 
 Hindu & 0.393$^{**}$ & 0.301$^{**}$ & $-$0.138 \\ 
  & (0.159) & (0.129) & (0.138) \\ 
  & & & \\ 
 UrbanUrban & $-$0.153 & 0.151 & $-$0.063 \\ 
  & (0.142) & (0.117) & (0.129) \\ 
  & & & \\ 
 StateRajasthan & $-$0.971$^{***}$ & 2.415$^{***}$ & $-$0.243 \\ 
  & (0.222) & (0.170) & (0.185) \\ 
  & & & \\ 
 StateTamil Nadu & 0.225 & 2.211$^{***}$ & 1.425$^{***}$ \\ 
  & (0.255) & (0.203) & (0.235) \\ 
  & & & \\ 
 StateUttar Pradesh & $-$0.926$^{***}$ & 1.514$^{***}$ & 0.046 \\ 
  & (0.254) & (0.201) & (0.221) \\ 
  & & & \\ 
 StateWest Bengal & $-$1.537$^{***}$ & 2.428$^{***}$ & $-$0.529$^{**}$ \\ 
  & (0.270) & (0.221) & (0.245) \\ 
  & & & \\ 
 regulateindustry & 0.203$^{***}$ & 0.022 & 0.052 \\ 
  & (0.075) & (0.060) & (0.066) \\ 
  & & & \\ 
 localisation & 0.071 & $-$0.043 & 0.021 \\ 
  & (0.069) & (0.055) & (0.062) \\ 
  & & & \\ 
 freemarket & 0.402$^{***}$ & $-$0.109$^{**}$ & 0.219$^{***}$ \\ 
  & (0.064) & (0.052) & (0.059) \\ 
  & & & \\ 
 pvtdevelopment & 0.167$^{**}$ & 0.057 & 0.114 \\ 
  & (0.080) & (0.062) & (0.070) \\ 
  & & & \\ 
 Constant & 0.041 & 0.311$^{*}$ & 0.141 \\ 
  & (0.224) & (0.183) & (0.199) \\ 
  & & & \\ 
\hline \\[-1.8ex] 
Observations & 588 & 678 & 606 \\ 
R$^{2}$ & 0.178 & 0.440 & 0.165 \\ 
Adjusted R$^{2}$ & 0.159 & 0.429 & 0.146 \\ 
Residual Std. Error & 1.433 (df = 574) & 1.219 (df = 664) & 1.265 (df = 592) \\ 
F Statistic & 9.552$^{***}$ (df = 13; 574) & 40.206$^{***}$ (df = 13; 664) & 8.968$^{***}$ (df = 13; 592) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 
\endgroup

\newpage
\begin{landscape}

\hypertarget{factor-solution-characteristics-of-the-perceiver-1}{%
\subsection{2 factor solution (Characteristics of the
perceiver)}\label{factor-solution-characteristics-of-the-perceiver-1}}

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[c]{|p{1.50in}|p{3.50in}|p{0.75in}|p{0.75in}|p{0.75in}|p{0.75in}|p{0.75in}}

\caption{4\ factor\ solution\ same\ for\ all\ technologies}\\

\ascline{1.5pt}{666666}{1-7}

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{code}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Items}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{MR1}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{MR2}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Communality}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Uniqueness}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Complexity}}} \\

\ascline{1.5pt}{666666}{1-7}\endfirsthead \caption[]{4\ factor\ solution\ same\ for\ all\ technologies}\\

\ascline{1.5pt}{666666}{1-7}

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{code}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Items}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{MR1}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{MR2}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Communality}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Uniqueness}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Complexity}}} \\

\ascline{1.5pt}{666666}{1-7}\endhead

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Anti\ Mechanisation\ of\ work}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Rapid\ mechanization\ of\ work\ is\ taking\ away\ jobs\ from\ workers\ in\ this\ country}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.521}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.273}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.727}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.008}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pro\ Regulations}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Regardless\ of\ ownership,\ the\ government\ should\ pass\ strong\ regulations\ and\ implement\ them}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.494}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.277}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.723}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.265}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Anti\ Large\ Industries}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Large\ corporations\ are\ destroying\ the\ local\ industries\ in\ India\ and\ benefiting\ only\ a\ handful\ of\ people}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.487}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.246}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.754}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.074}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Limits\ on\ Wealth}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{A\ limit\ should\ be\ put\ to\ how\ much\ wealth\ a\ person\ can\ amass}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.477}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.249}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.751}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.185}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pro\ Large\ Industries}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Large\ scale\ industries\ are\ required\ for\ the\ development\ of\ the\ country\ that\ will\ benefit\ everyone}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.452}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.205}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.795}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.007}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pro\ Centralisation}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Laws\ and\ policies\ would\ be\ implemented\ more\ smoothly\ if\ more\ power\ lay\ with\ the\ central\ government}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.445}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.216}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.784}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.179}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pro\ Globaleconomy}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Foreign\ companies\ have\ led\ to\ a\ range\ of\ benefits\ for\ the\ Indian\ people\ and\ society}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.435}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.191}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.809}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.018}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Anti\ Regulations}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{There\ is\ too\ much\ red-tape\ and\ the\ government\ should\ not\ interfere\ with\ businesses\ and\ industries}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.423}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.193}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.807}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.157}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pro\ Decentralisation}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Local\ politicians\ shouldn't\ have\ to\ ask\ permission\ from\ the\ central\ government\ to\ implement\ policies}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.113}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.887}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.658}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pro\ Localeconomy}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{India\ would\ be\ better\ off\ if\ foreign\ companies\ didn't\ come\ to\ here}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.108}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.892}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.720}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Environment\ over\ Development}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Polluting\ industries\ that\ spoil\ the\ environment\ should\ be\ shut\ down\ even\ if\ it\ costs\ people\ their\ jobs}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.522}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.408}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.592}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.797}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Development\ over\ Environment}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Economic\ growth\ and\ creating\ jobs\ should\ be\ prioritized\ over\ environmental\ protection}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{-0.509}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.262}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.738}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.022}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pro\ Public\ ownership}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{The\ government\ should\ own\ most\ large\ businesses\ and\ industries}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.445}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.488}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.436}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.564}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.983}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pro\ Private\ ownership}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 3.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{All\ businesses\ and\ industries\ should\ be\ owned\ privately}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{-0.481}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.244}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.756}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.108}}} \\

\ascline{1.5pt}{666666}{1-7}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

\end{landscape}

\newpage

\hypertarget{linear-models-perceived-risk-x-2-factor-solution-separate-scale}{%
\subsection{Linear Models: Perceived Risk X 2 factor solution (separate
scale)}\label{linear-models-perceived-risk-x-2-factor-solution-separate-scale}}

\begingroup\setlength{\tabcolsep}{1pt}

\renewcommand{\arraystretch}{0.7}

\% Table created by stargazer v.5.2.3 by Marek Hlavac, Social Policy
Institute. E-mail: marek.hlavac at gmail.com \% Date and time: Wed, Jan
10, 2024 - 10:07:36

\begin{table}[!htbp] \centering 
  \caption{Perceived Risk X 2 factor solution (separate scale)} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
\cline{2-4} 
\\[-1.8ex] & Risky\_Nuclear & Risky\_Solar & Risky\_Coal \\ 
\\[-1.8ex] & (1) & (2) & (3)\\ 
\hline \\[-1.8ex] 
 Uppercaste & $-$0.114 & 0.002 & $-$0.054 \\ 
  & (0.102) & (0.072) & (0.090) \\ 
  & & & \\ 
 Male & 0.101 & $-$0.023 & 0.003 \\ 
  & (0.109) & (0.078) & (0.096) \\ 
  & & & \\ 
 Hindu & $-$0.001 & $-$0.119 & 0.207$^{*}$ \\ 
  & (0.120) & (0.088) & (0.106) \\ 
  & & & \\ 
 UrbanUrban & 0.197$^{*}$ & $-$0.064 & 0.173$^{*}$ \\ 
  & (0.106) & (0.080) & (0.097) \\ 
  & & & \\ 
 age & $-$0.163$^{***}$ & $-$0.025 & $-$0.014 \\ 
  & (0.042) & (0.030) & (0.038) \\ 
  & & & \\ 
 StateRajasthan & 0.444$^{***}$ & $-$1.618$^{***}$ & 0.061 \\ 
  & (0.159) & (0.109) & (0.134) \\ 
  & & & \\ 
 StateTamil Nadu & $-$0.183 & $-$1.715$^{***}$ & $-$1.286$^{***}$ \\ 
  & (0.184) & (0.135) & (0.168) \\ 
  & & & \\ 
 StateUttar Pradesh & 0.125 & $-$1.255$^{***}$ & $-$0.729$^{***}$ \\ 
  & (0.187) & (0.136) & (0.166) \\ 
  & & & \\ 
 StateWest Bengal & 1.478$^{***}$ & $-$1.309$^{***}$ & 0.486$^{***}$ \\ 
  & (0.192) & (0.145) & (0.179) \\ 
  & & & \\ 
 MR1 & 0.024 & 0.117$^{***}$ & 0.122$^{**}$ \\ 
  & (0.056) & (0.041) & (0.050) \\ 
  & & & \\ 
 MR2 & 0.128$^{**}$ & 0.005 & 0.044 \\ 
  & (0.064) & (0.045) & (0.055) \\ 
  & & & \\ 
 Constant & 3.289$^{***}$ & 2.993$^{***}$ & 3.149$^{***}$ \\ 
  & (0.167) & (0.124) & (0.151) \\ 
  & & & \\ 
\hline \\[-1.8ex] 
Observations & 609 & 686 & 644 \\ 
R$^{2}$ & 0.149 & 0.434 & 0.207 \\ 
Adjusted R$^{2}$ & 0.134 & 0.425 & 0.193 \\ 
Residual Std. Error & 1.091 (df = 597) & 0.837 (df = 674) & 0.989 (df = 632) \\ 
F Statistic & 9.540$^{***}$ (df = 11; 597) & 46.935$^{***}$ (df = 11; 674) & 14.992$^{***}$ (df = 11; 632) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 
\endgroup

\newpage

\hypertarget{linear-models-perceived-benefit-x-2-fa-solution-separate-scales}{%
\subsection{Linear Models: Perceived Benefit X 2 FA solution (separate
scales)}\label{linear-models-perceived-benefit-x-2-fa-solution-separate-scales}}

\begingroup\setlength{\tabcolsep}{1pt}

\renewcommand{\arraystretch}{0.7}

\% Table created by stargazer v.5.2.3 by Marek Hlavac, Social Policy
Institute. E-mail: marek.hlavac at gmail.com \% Date and time: Wed, Jan
10, 2024 - 10:07:36

\begin{table}[!htbp] \centering 
  \caption{Perceived Benefit X 2 FA solution (separate scales)} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
\cline{2-4} 
\\[-1.8ex] & Ben\_Nuclear & Ben\_Solar & Ben\_Coal \\ 
\\[-1.8ex] & (1) & (2) & (3)\\ 
\hline \\[-1.8ex] 
 Uppercaste & $-$0.162$^{*}$ & $-$0.078 & $-$0.258$^{***}$ \\ 
  & (0.085) & (0.072) & (0.081) \\ 
  & & & \\ 
 Male & 0.007 & $-$0.022 & 0.127 \\ 
  & (0.089) & (0.077) & (0.090) \\ 
  & & & \\ 
 Hindu & 0.376$^{***}$ & 0.174$^{**}$ & 0.118 \\ 
  & (0.100) & (0.088) & (0.097) \\ 
  & & & \\ 
 UrbanUrban & 0.077 & 0.079 & 0.095 \\ 
  & (0.089) & (0.079) & (0.091) \\ 
  & & & \\ 
 age & 0.013 & $-$0.037 & 0.040 \\ 
  & (0.034) & (0.030) & (0.037) \\ 
  & & & \\ 
 StateRajasthan & $-$0.499$^{***}$ & 0.797$^{***}$ & $-$0.266$^{**}$ \\ 
  & (0.133) & (0.110) & (0.124) \\ 
  & & & \\ 
 StateTamil Nadu & 0.018 & 0.475$^{***}$ & 0.031 \\ 
  & (0.152) & (0.134) & (0.156) \\ 
  & & & \\ 
 StateUttar Pradesh & $-$0.783$^{***}$ & 0.275$^{**}$ & $-$0.761$^{***}$ \\ 
  & (0.159) & (0.137) & (0.155) \\ 
  & & & \\ 
 StateWest Bengal & $-$0.116 & 1.178$^{***}$ & $-$0.201 \\ 
  & (0.164) & (0.146) & (0.167) \\ 
  & & & \\ 
 MR1 & 0.486$^{***}$ & 0.041 & 0.373$^{***}$ \\ 
  & (0.047) & (0.041) & (0.047) \\ 
  & & & \\ 
 MR2 & $-$0.059 & $-$0.052 & $-$0.067 \\ 
  & (0.052) & (0.045) & (0.052) \\ 
  & & & \\ 
 Constant & 3.258$^{***}$ & 3.295$^{***}$ & 3.236$^{***}$ \\ 
  & (0.140) & (0.123) & (0.140) \\ 
  & & & \\ 
\hline \\[-1.8ex] 
Observations & 626 & 701 & 625 \\ 
R$^{2}$ & 0.247 & 0.174 & 0.157 \\ 
Adjusted R$^{2}$ & 0.233 & 0.161 & 0.142 \\ 
Residual Std. Error & 0.918 (df = 614) & 0.838 (df = 689) & 0.904 (df = 613) \\ 
F Statistic & 18.290$^{***}$ (df = 11; 614) & 13.194$^{***}$ (df = 11; 689) & 10.380$^{***}$ (df = 11; 613) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 
\endgroup

\begin{verbatim}
## Factor Analysis using method =  minres
## Call: fa(r = Nuclear2, nfactors = 2, rotate = "varimax")
## Standardized loadings (pattern matrix) based upon correlation matrix
##                                item   MR1   MR2   h2   u2 com
## Health risk(nuclear)              3  0.86       0.74 0.26 1.0
## Pollution risk(nuclear)           2  0.73       0.54 0.46 1.0
## Spoils Natural Beauty(nuclear)    4  0.69       0.48 0.52 1.0
## Displacement risk(nuclear)        1  0.51       0.28 0.72 1.1
## National pride(nuclear)           6        0.65 0.43 0.57 1.0
## National development(nuclear)     7        0.64 0.44 0.56 1.2
## Local prosperity(nuclear)         8        0.63 0.42 0.58 1.1
## Community pride(nuclear)          5        0.59 0.38 0.62 1.2
## 
##                        MR1  MR2
## SS loadings           2.11 1.61
## Proportion Var        0.26 0.20
## Cumulative Var        0.26 0.46
## Proportion Explained  0.57 0.43
## Cumulative Proportion 0.57 1.00
## 
## Mean item complexity =  1.1
## Test of the hypothesis that 2 factors are sufficient.
## 
## df null model =  28  with the objective function =  2.26 with Chi Square =  1045.26
## df of  the model are 13  and the objective function was  0.16 
## 
## The root mean square of the residuals (RMSR) is  0.04 
## The df corrected root mean square of the residuals is  0.06 
## 
## The harmonic n.obs is  467 with the empirical chi square  48.57  with prob <  5.2e-06 
## The total n.obs was  467  with Likelihood Chi Square =  76  with prob <  6.2e-11 
## 
## Tucker Lewis Index of factoring reliability =  0.866
## RMSEA index =  0.102  and the 90 % confidence intervals are  0.08 0.125
## BIC =  -3.91
## Fit based upon off diagonal values = 0.98
## Measures of factor score adequacy             
##                                                    MR1  MR2
## Correlation of (regression) scores with factors   0.92 0.86
## Multiple R square of scores with factors          0.84 0.74
## Minimum correlation of possible factor scores     0.69 0.47
\end{verbatim}

\newpage
\begin{landscape}

\hypertarget{fa-on-separate-scale-scale-2-characteristics-of-the-technology2-factor-solution}{%
\section{FA on Separate scale: Scale 2: Characteristics of the
Technology(2 factor
solution)}\label{fa-on-separate-scale-scale-2-characteristics-of-the-technology2-factor-solution}}

\hypertarget{nuclear-energy-positive-alpha-0.73-and-negative-alpha-0.79-characteristics-2-factor-solution}{%
\subsection{Nuclear Energy : positive (alpha = 0.73) and negative (alpha
= 0.79) characteristics (2 factor
solution)}\label{nuclear-energy-positive-alpha-0.73-and-negative-alpha-0.79-characteristics-2-factor-solution}}

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[c]{|p{1.50in}|p{4.50in}|p{0.75in}|p{0.75in}|p{0.75in}|p{0.75in}|p{0.75in}}

\caption{Separate\ scale\ 2\ factor\ solution:\ Nuclear\ energy\ }\\

\ascline{1.5pt}{666666}{1-7}

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{code}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Items}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Social\ Costs}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pride}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Communality}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Uniqueness}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Complexity}}} \\

\ascline{1.5pt}{666666}{1-7}\endfirsthead \caption[]{Separate\ scale\ 2\ factor\ solution:\ Nuclear\ energy\ }\\

\ascline{1.5pt}{666666}{1-7}

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{code}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Items}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Social\ Costs}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pride}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Communality}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Uniqueness}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Complexity}}} \\

\ascline{1.5pt}{666666}{1-7}\endhead

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Health\ risk(nuclear)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Nuclear\ energy\ poses\ a\ great\ risk\ to\ the\ health\ of\ people\ living\ around\ it}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.859}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.738}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.262}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.000}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pollution\ risk(nuclear)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Nuclear\ energy\ increases\ pollution\ of\ air/water/land}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.73}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.541}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.459}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.031}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Spoils\ Natural\ Beauty(nuclear)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Nuclear\ energy\ spoils\ the\ natural\ beauty\ of\ the\ landscape}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.692}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.479}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.521}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.002}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Displacement\ risk(nuclear)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Nuclear\ energy\ is\ leading\ to\ displacement\ of\ people\ from\ their\ land}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.51}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.275}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.725}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.115}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{National\ pride(nuclear)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Nuclear\ energy\ is\ a\ mark\ of\ pride\ for\ our\ nation}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.654}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.432}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.568}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.023}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{National\ development(nuclear)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Nuclear\ energy\ pushes\ forward\ the\ country's\ development}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.638}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.441}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.559}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.168}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Local\ prosperity(nuclear)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Nuclear\ energy\ brings\ economic\ prosperity\ to\ the\ surrounding\ regions}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.63}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.422}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.578}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.126}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Community\ pride(nuclear)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{I\ would\ be\ proud\ if\ my\ community\ used\ nuclear\ energy}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.593}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.383}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.617}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.175}}} \\

\ascline{1.5pt}{666666}{1-7}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

\end{landscape}

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[c]{ccc}

\caption{Eigenvalues\ and\ Variance\ Explained\ for\ Rotated\ Factor\ Solution}\\

\ascline{1.5pt}{666666}{1-3}

\multicolumn{1}{>{}l}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Property}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Social\_Costs}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pride}}} \\

\ascline{1.5pt}{666666}{1-3}\endfirsthead \caption[]{Eigenvalues\ and\ Variance\ Explained\ for\ Rotated\ Factor\ Solution}\\

\ascline{1.5pt}{666666}{1-3}

\multicolumn{1}{>{}l}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Property}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Social\_Costs}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pride}}} \\

\ascline{1.5pt}{666666}{1-3}\endhead

\multicolumn{1}{>{}l}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{SS\ loadings}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{2.106}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.606}}} \\

\multicolumn{1}{>{}l}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Proportion\ Var}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.263}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.201}}} \\

\multicolumn{1}{>{}l}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Cumulative\ Var}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.263}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.464}}} \\

\multicolumn{1}{>{}l}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Proportion\ Explained}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.567}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.433}}} \\

\multicolumn{1}{>{}l}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Cumulative\ Proportion}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.567}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.000}}} \\

\ascline{1.5pt}{666666}{1-3}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

\begin{verbatim}
## 
## Call:
## lm(formula = Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + 
##     age + State + socialcosts + pride, data = Nuclearwscores2)
## 
## Residuals:
##      Min       1Q   Median       3Q      Max 
## -2.68987 -0.68716  0.06119  0.60552  2.48833 
## 
## Coefficients:
##                    Estimate Std. Error t value Pr(>|t|)    
## (Intercept)         2.95539    0.15836  18.663  < 2e-16 ***
## Uppercaste         -0.01360    0.10074  -0.135   0.8926    
## Male               -0.13078    0.10872  -1.203   0.2296    
## Hindu              -0.09259    0.10803  -0.857   0.3919    
## UrbanUrban          0.07682    0.10463   0.734   0.4632    
## age                 0.08810    0.04837   1.821   0.0692 .  
## StateRajasthan      0.40252    0.16905   2.381   0.0177 *  
## StateTamil Nadu     1.45348    0.20709   7.019 8.55e-12 ***
## StateUttar Pradesh  0.23762    0.17026   1.396   0.1635    
## StateWest Bengal    1.32747    0.17523   7.576 2.14e-13 ***
## socialcosts         0.10745    0.05585   1.924   0.0550 .  
## pride               0.22645    0.05087   4.452 1.08e-05 ***
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 0.9341 on 439 degrees of freedom
##   (16 observations deleted due to missingness)
## Multiple R-squared:  0.3015, Adjusted R-squared:  0.284 
## F-statistic: 17.23 on 11 and 439 DF,  p-value: < 2.2e-16
\end{verbatim}

\begin{verbatim}
## 
## Call:
## lm(formula = Ben_Nuclear ~ Uppercaste + Male + Hindu + Urban + 
##     age + State + socialcosts + pride, data = Nuclearwscores2)
## 
## Residuals:
##      Min       1Q   Median       3Q      Max 
## -2.56084 -0.56917 -0.06033  0.71307  2.37365 
## 
## Coefficients:
##                    Estimate Std. Error t value Pr(>|t|)    
## (Intercept)         3.17637    0.16851  18.849  < 2e-16 ***
## Uppercaste         -0.28702    0.10762  -2.667  0.00793 ** 
## Male                0.05770    0.11622   0.496  0.61979    
## Hindu               0.30107    0.11499   2.618  0.00914 ** 
## UrbanUrban          0.20845    0.11124   1.874  0.06160 .  
## age                -0.08402    0.05161  -1.628  0.10425    
## StateRajasthan     -0.20233    0.18027  -1.122  0.26234    
## StateTamil Nadu    -0.28362    0.21989  -1.290  0.19779    
## StateUttar Pradesh -0.21817    0.18224  -1.197  0.23190    
## StateWest Bengal    0.20319    0.18827   1.079  0.28106    
## socialcosts         0.11652    0.05988   1.946  0.05230 .  
## pride               0.29774    0.05516   5.398  1.1e-07 ***
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 1.001 on 443 degrees of freedom
##   (12 observations deleted due to missingness)
## Multiple R-squared:  0.1262, Adjusted R-squared:  0.1045 
## F-statistic: 5.814 on 11 and 443 DF,  p-value: 8.02e-09
\end{verbatim}

\begin{verbatim}
## 
## Call:
## lm(formula = Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + 
##     age + State + socialcosts + pride, data = Nuclearwscores3)
## 
## Residuals:
##      Min       1Q   Median       3Q      Max 
## -2.68987 -0.68716  0.06119  0.60552  2.48833 
## 
## Coefficients:
##                    Estimate Std. Error t value Pr(>|t|)    
## (Intercept)         2.95539    0.15836  18.663  < 2e-16 ***
## Uppercaste         -0.01360    0.10074  -0.135   0.8926    
## Male               -0.13078    0.10872  -1.203   0.2296    
## Hindu              -0.09259    0.10803  -0.857   0.3919    
## UrbanUrban          0.07682    0.10463   0.734   0.4632    
## age                 0.08810    0.04837   1.821   0.0692 .  
## StateRajasthan      0.40252    0.16905   2.381   0.0177 *  
## StateTamil Nadu     1.45348    0.20709   7.019 8.55e-12 ***
## StateUttar Pradesh  0.23762    0.17026   1.396   0.1635    
## StateWest Bengal    1.32747    0.17523   7.576 2.14e-13 ***
## socialcosts         0.10745    0.05585   1.924   0.0550 .  
## pride               0.22645    0.05087   4.452 1.08e-05 ***
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 0.9341 on 439 degrees of freedom
## Multiple R-squared:  0.3015, Adjusted R-squared:  0.284 
## F-statistic: 17.23 on 11 and 439 DF,  p-value: < 2.2e-16
\end{verbatim}

\begin{landscape}
\newpage

\hypertarget{solar-energy-positive-alpha-0.85-and-negative-alpha-0.81characteristics-2-factor-solution}{%
\subsection{Solar Energy : positive (alpha =0.85) and negative (alpha =
0.81)characteristics (2 factor
solution)}\label{solar-energy-positive-alpha-0.85-and-negative-alpha-0.81characteristics-2-factor-solution}}

\begin{verbatim}
## Factor Analysis using method =  minres
## Call: fa(r = Solar2, nfactors = 2, rotate = "varimax")
## Standardized loadings (pattern matrix) based upon correlation matrix
##                              item   MR1   MR2   h2   u2 com
## National development(Solar)     7  0.83       0.70 0.30 1.0
## National pride(Solar)           6  0.82       0.67 0.33 1.0
## Local prosperity(Solar)         8  0.80       0.65 0.35 1.0
## Community pride(Solar)          5  0.80       0.67 0.33 1.1
## Health risk(Solar)              3        0.82 0.68 0.32 1.0
## Pollution risk(Solar)           2        0.81 0.68 0.32 1.1
## Spoils Natural Beauty(Solar)    4        0.65 0.42 0.58 1.0
## Displacement risk(Solar)        1        0.59 0.35 0.65 1.0
## 
##                        MR1  MR2
## SS loadings           2.69 2.13
## Proportion Var        0.34 0.27
## Cumulative Var        0.34 0.60
## Proportion Explained  0.56 0.44
## Cumulative Proportion 0.56 1.00
## 
## Mean item complexity =  1
## Test of the hypothesis that 2 factors are sufficient.
## 
## df null model =  28  with the objective function =  3.73 with Chi Square =  2283.32
## df of  the model are 13  and the objective function was  0.07 
## 
## The root mean square of the residuals (RMSR) is  0.02 
## The df corrected root mean square of the residuals is  0.03 
## 
## The harmonic n.obs is  617 with the empirical chi square  12.5  with prob <  0.49 
## The total n.obs was  617  with Likelihood Chi Square =  45.58  with prob <  1.7e-05 
## 
## Tucker Lewis Index of factoring reliability =  0.969
## RMSEA index =  0.064  and the 90 % confidence intervals are  0.044 0.084
## BIC =  -37.94
## Fit based upon off diagonal values = 1
## Measures of factor score adequacy             
##                                                    MR1  MR2
## Correlation of (regression) scores with factors   0.94 0.92
## Multiple R square of scores with factors          0.89 0.84
## Minimum correlation of possible factor scores     0.77 0.68
\end{verbatim}

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[c]{|p{1.50in}|p{4.50in}|p{0.75in}|p{0.75in}|p{0.75in}|p{0.75in}|p{0.75in}}

\caption{Separate\ scale\ 2\ factor\ solution:\ Solar\ energy\ }\\

\ascline{1.5pt}{666666}{1-7}

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{code}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Items}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pride}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Social\ Costs}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Communality}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Uniqueness}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Complexity}}} \\

\ascline{1.5pt}{666666}{1-7}\endfirsthead \caption[]{Separate\ scale\ 2\ factor\ solution:\ Solar\ energy\ }\\

\ascline{1.5pt}{666666}{1-7}

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{code}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Items}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pride}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Social\ Costs}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Communality}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Uniqueness}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Complexity}}} \\

\ascline{1.5pt}{666666}{1-7}\endhead

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{National\ development(Solar)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Solar\ energy\ pushes\ forward\ the\ country's\ development}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.83}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.698}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.302}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.025}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{National\ pride(Solar)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Solar\ energy\ is\ a\ mark\ of\ pride\ for\ our\ nation}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.818}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.669}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.331}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.000}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Local\ prosperity(Solar)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Solar\ energy\ brings\ economic\ prosperity\ to\ the\ surrounding\ regions}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.804}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.648}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.352}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.005}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Community\ pride(Solar)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{I\ would\ be\ proud\ if\ my\ community\ used\ solar\ energy}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.801}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.667}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.333}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.080}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Health\ risk(Solar)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Solar\ energy\ poses\ a\ great\ risk\ to\ the\ health\ of\ people\ living\ around\ it}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.823}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.684}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.316}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.021}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pollution\ risk(Solar)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Solar\ energy\ increases\ pollution\ of\ air/water/land}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.806}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.680}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.320}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.094}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Spoils\ Natural\ Beauty(Solar)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Solar\ energy\ spoils\ the\ natural\ beauty\ of\ the\ landscape}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.647}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.422}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.578}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.017}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Displacement\ risk(Solar)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Solar\ energy\ is\ leading\ to\ displacement\ of\ people\ from\ their\ land}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.59}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.348}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.652}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.001}}} \\

\ascline{1.5pt}{666666}{1-7}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

\end{landscape}

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[c]{ccc}

\caption{Eigenvalues\ and\ Variance\ Explained\ for\ Rotated\ Factor\ Solution}\\

\ascline{1.5pt}{666666}{1-3}

\multicolumn{1}{>{}l}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Property}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pride}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Social\_Costs}}} \\

\ascline{1.5pt}{666666}{1-3}\endfirsthead \caption[]{Eigenvalues\ and\ Variance\ Explained\ for\ Rotated\ Factor\ Solution}\\

\ascline{1.5pt}{666666}{1-3}

\multicolumn{1}{>{}l}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Property}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pride}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Social\_Costs}}} \\

\ascline{1.5pt}{666666}{1-3}\endhead

\multicolumn{1}{>{}l}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{SS\ loadings}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{2.687}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{2.129}}} \\

\multicolumn{1}{>{}l}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Proportion\ Var}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.336}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.266}}} \\

\multicolumn{1}{>{}l}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Cumulative\ Var}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.336}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.602}}} \\

\multicolumn{1}{>{}l}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Proportion\ Explained}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.558}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.442}}} \\

\multicolumn{1}{>{}l}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Cumulative\ Proportion}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.558}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.000}}} \\

\ascline{1.5pt}{666666}{1-3}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

\begin{verbatim}
## 
## Call:
## lm(formula = Risky_Solar ~ Uppercaste + Male + Hindu + Urban + 
##     age + State + pride + socialcosts, data = Solarwscores2)
## 
## Residuals:
##     Min      1Q  Median      3Q     Max 
## -1.8949 -0.5353 -0.1545  0.3593  3.7745 
## 
## Coefficients:
##                    Estimate Std. Error t value Pr(>|t|)    
## (Intercept)         2.84619    0.13333  21.347  < 2e-16 ***
## Uppercaste         -0.08132    0.07925  -1.026    0.305    
## Male               -0.04120    0.08710  -0.473    0.636    
## Hindu              -0.11529    0.09031  -1.277    0.202    
## UrbanUrban         -0.11661    0.08707  -1.339    0.181    
## age                 0.01209    0.03448   0.351    0.726    
## StateRajasthan     -1.44844    0.13282 -10.905  < 2e-16 ***
## StateTamil Nadu    -1.45727    0.15266  -9.546  < 2e-16 ***
## StateUttar Pradesh -1.16088    0.14359  -8.085 3.52e-15 ***
## StateWest Bengal   -1.05363    0.14252  -7.393 4.93e-13 ***
## pride               0.03100    0.04511   0.687    0.492    
## socialcosts         0.08313    0.04580   1.815    0.070 .  
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 0.873 on 592 degrees of freedom
##   (13 observations deleted due to missingness)
## Multiple R-squared:  0.3933, Adjusted R-squared:  0.382 
## F-statistic: 34.89 on 11 and 592 DF,  p-value: < 2.2e-16
\end{verbatim}

\begin{verbatim}
## 
## Call:
## lm(formula = Ben_Solar ~ Uppercaste + Male + Hindu + Urban + 
##     age + State + KahanH + KahanS + pride + socialcosts, data = Solarwscores2)
## 
## Residuals:
##      Min       1Q   Median       3Q      Max 
## -3.09665 -0.36332 -0.09527  0.61588  2.10050 
## 
## Coefficients:
##                     Estimate Std. Error t value Pr(>|t|)    
## (Intercept)         3.486786   0.128878  27.055  < 2e-16 ***
## Uppercaste         -0.131669   0.075748  -1.738 0.082683 .  
## Male                0.034569   0.082830   0.417 0.676577    
## Hindu               0.155051   0.086322   1.796 0.072968 .  
## UrbanUrban         -0.032985   0.081896  -0.403 0.687266    
## age                -0.017383   0.032351  -0.537 0.591243    
## StateRajasthan      0.368577   0.129017   2.857 0.004428 ** 
## StateTamil Nadu     0.453648   0.155240   2.922 0.003607 ** 
## StateUttar Pradesh -0.008497   0.142059  -0.060 0.952324    
## StateWest Bengal    0.545084   0.144327   3.777 0.000175 ***
## KahanH              0.132315   0.058307   2.269 0.023608 *  
## KahanS             -0.006362   0.060399  -0.105 0.916146    
## pride               0.218994   0.043488   5.036 6.31e-07 ***
## socialcosts        -0.066542   0.044650  -1.490 0.136671    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 0.8318 on 598 degrees of freedom
##   (5 observations deleted due to missingness)
## Multiple R-squared:  0.2298, Adjusted R-squared:  0.2131 
## F-statistic: 13.73 on 13 and 598 DF,  p-value: < 2.2e-16
\end{verbatim}

\newpage
\begin{landscape}

\hypertarget{coal-positive-alpha-0.67-and-negative-alphs-0.72-characteristics-2-factor-solution}{%
\subsection{Coal : positive (alpha = 0.67) and negative (alphs = 0.72)
characteristics (2 factor
solution)}\label{coal-positive-alpha-0.67-and-negative-alphs-0.72-characteristics-2-factor-solution}}

\begin{verbatim}
## Factor Analysis using method =  minres
## Call: fa(r = Coal2, nfactors = 2, rotate = "varimax")
## Standardized loadings (pattern matrix) based upon correlation matrix
##                             item   MR1   MR2   h2   u2 com
## Pollution risk(Coal)           2  0.71       0.50 0.50 1.0
## Health risk(Coal)              3  0.66       0.45 0.55 1.0
## Spoils Natural Beauty(Coal)    4  0.64       0.43 0.57 1.1
## Displacement risk(Coal)        1  0.49       0.24 0.76 1.0
## National pride(Coal)           6        0.71 0.50 0.50 1.0
## Community pride(Coal)          5        0.62 0.38 0.62 1.0
## National development(Coal)     7        0.53 0.40 0.60 1.7
## Local prosperity(Coal)         8        0.49 0.32 0.68 1.6
## 
##                        MR1  MR2
## SS loadings           1.79 1.43
## Proportion Var        0.22 0.18
## Cumulative Var        0.22 0.40
## Proportion Explained  0.56 0.44
## Cumulative Proportion 0.56 1.00
## 
## Mean item complexity =  1.2
## Test of the hypothesis that 2 factors are sufficient.
## 
## df null model =  28  with the objective function =  1.71 with Chi Square =  1054.46
## df of  the model are 13  and the objective function was  0.15 
## 
## The root mean square of the residuals (RMSR) is  0.04 
## The df corrected root mean square of the residuals is  0.06 
## 
## The harmonic n.obs is  621 with the empirical chi square  63.83  with prob <  1.1e-08 
## The total n.obs was  621  with Likelihood Chi Square =  94.07  with prob <  2.3e-14 
## 
## Tucker Lewis Index of factoring reliability =  0.83
## RMSEA index =  0.1  and the 90 % confidence intervals are  0.082 0.12
## BIC =  10.46
## Fit based upon off diagonal values = 0.98
## Measures of factor score adequacy             
##                                                    MR1  MR2
## Correlation of (regression) scores with factors   0.87 0.84
## Multiple R square of scores with factors          0.75 0.71
## Minimum correlation of possible factor scores     0.50 0.41
\end{verbatim}

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[c]{|p{1.50in}|p{4.50in}|p{0.75in}|p{0.75in}|p{0.75in}|p{0.75in}|p{0.75in}}

\caption{Separate\ scale\ 2\ factor\ solution:\ Coal\ }\\

\ascline{1.5pt}{666666}{1-7}

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{code}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Items}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Social\ Costs}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pride}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Communality}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Uniqueness}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Complexity}}} \\

\ascline{1.5pt}{666666}{1-7}\endfirsthead \caption[]{Separate\ scale\ 2\ factor\ solution:\ Coal\ }\\

\ascline{1.5pt}{666666}{1-7}

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{code}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Items}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Social\ Costs}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pride}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Communality}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Uniqueness}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Complexity}}} \\

\ascline{1.5pt}{666666}{1-7}\endhead

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pollution\ risk(Coal)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Coal\ powered\ plants\ increases\ pollution\ of\ air/water/land}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.705}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.498}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.502}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.005}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Health\ risk(Coal)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Coal\ powered\ plants\ poses\ a\ great\ risk\ to\ the\ health\ of\ people\ living\ around\ it}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.662}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.447}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.553}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.043}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Spoils\ Natural\ Beauty(Coal)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Coal\ powered\ plants\ spoils\ the\ natural\ beauty\ of\ the\ landscape}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.642}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.429}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.571}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.078}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Displacement\ risk(Coal)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Coal\ powered\ plants\ is\ leading\ to\ displacement\ of\ people\ from\ their\ land}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.486}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.236}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.764}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.000}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{National\ pride(Coal)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Coal\ powered\ plants\ is\ a\ mark\ of\ pride\ for\ our\ nation}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.705}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.504}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.496}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.026}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Community\ pride(Coal)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{I\ would\ be\ proud\ if\ my\ community\ used\ Coal\ powered\ plants}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.618}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.382}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.618}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.005}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{National\ development(Coal)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Coal\ powered\ plants\ pushes\ forward\ the\ country's\ development}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.535}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.401}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.599}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.691}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Local\ prosperity(Coal)}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 4.5in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Coal\ powered\ plants\ brings\ economic\ prosperity\ to\ the\ surrounding\ regions}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.488}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.324}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.676}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.634}}} \\

\ascline{1.5pt}{666666}{1-7}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

\end{landscape}

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[c]{ccc}

\caption{Eigenvalues\ and\ Variance\ Explained\ for\ Rotated\ Factor\ Solution}\\

\ascline{1.5pt}{666666}{1-3}

\multicolumn{1}{>{}l}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Property}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Social\_Costs}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pride}}} \\

\ascline{1.5pt}{666666}{1-3}\endfirsthead \caption[]{Eigenvalues\ and\ Variance\ Explained\ for\ Rotated\ Factor\ Solution}\\

\ascline{1.5pt}{666666}{1-3}

\multicolumn{1}{>{}l}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Property}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Social\_Costs}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Pride}}} \\

\ascline{1.5pt}{666666}{1-3}\endhead

\multicolumn{1}{>{}l}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{SS\ loadings}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.792}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.430}}} \\

\multicolumn{1}{>{}l}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Proportion\ Var}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.224}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.179}}} \\

\multicolumn{1}{>{}l}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Cumulative\ Var}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.224}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.403}}} \\

\multicolumn{1}{>{}l}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Proportion\ Explained}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.556}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.444}}} \\

\multicolumn{1}{>{}l}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Cumulative\ Proportion}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{0.556}}} & \multicolumn{1}{>{}r}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{1.000}}} \\

\ascline{1.5pt}{666666}{1-3}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

\newpage

\hypertarget{linear-models-perceived-risk-x-positive-and-negative-characteristics-of-the-technology}{%
\subsection{Linear Models: Perceived Risk X positive and negative
characteristics of the
technology}\label{linear-models-perceived-risk-x-positive-and-negative-characteristics-of-the-technology}}

\begingroup\setlength{\tabcolsep}{1pt}

\renewcommand{\arraystretch}{0.7}

\% Table created by stargazer v.5.2.3 by Marek Hlavac, Social Policy
Institute. E-mail: marek.hlavac at gmail.com \% Date and time: Wed, Jan
10, 2024 - 10:07:39

\begin{table}[!htbp] \centering 
  \caption{LMs with separate scale 2 FA solution: Perceived Risk} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
\cline{2-4} 
\\[-1.8ex] & Risky\_Nuclear & Risky\_Solar & Risky\_Coal \\ 
\\[-1.8ex] & (1) & (2) & (3)\\ 
\hline \\[-1.8ex] 
 Uppercaste & $-$0.014 & $-$0.081 & 0.012 \\ 
  & (0.101) & (0.079) & (0.084) \\ 
  & & & \\ 
 Male & $-$0.131 & $-$0.041 & 0.023 \\ 
  & (0.109) & (0.087) & (0.094) \\ 
  & & & \\ 
 Hindu & $-$0.093 & $-$0.115 & 0.177$^{*}$ \\ 
  & (0.108) & (0.090) & (0.096) \\ 
  & & & \\ 
 UrbanUrban & 0.077 & $-$0.117 & 0.079 \\ 
  & (0.105) & (0.087) & (0.091) \\ 
  & & & \\ 
 age & 0.088$^{*}$ & 0.012 & 0.153$^{***}$ \\ 
  & (0.048) & (0.034) & (0.040) \\ 
  & & & \\ 
 StateRajasthan & 0.403$^{**}$ & $-$1.448$^{***}$ & $-$0.275$^{**}$ \\ 
  & (0.169) & (0.133) & (0.129) \\ 
  & & & \\ 
 StateTamil Nadu & 1.453$^{***}$ & $-$1.457$^{***}$ & $-$0.947$^{***}$ \\ 
  & (0.207) & (0.153) & (0.203) \\ 
  & & & \\ 
 StateUttar Pradesh & 0.238 & $-$1.161$^{***}$ & $-$0.978$^{***}$ \\ 
  & (0.170) & (0.144) & (0.150) \\ 
  & & & \\ 
 StateWest Bengal & 1.327$^{***}$ & $-$1.054$^{***}$ & $-$0.222$^{*}$ \\ 
  & (0.175) & (0.143) & (0.128) \\ 
  & & & \\ 
 socialcosts & 0.107$^{*}$ & 0.083$^{*}$ & 0.423$^{***}$ \\ 
  & (0.056) & (0.046) & (0.044) \\ 
  & & & \\ 
 pride & 0.226$^{***}$ & 0.031 & 0.067 \\ 
  & (0.051) & (0.045) & (0.041) \\ 
  & & & \\ 
 Constant & 2.955$^{***}$ & 2.846$^{***}$ & 2.995$^{***}$ \\ 
  & (0.158) & (0.133) & (0.140) \\ 
  & & & \\ 
\hline \\[-1.8ex] 
Observations & 451 & 604 & 607 \\ 
R$^{2}$ & 0.301 & 0.393 & 0.205 \\ 
Adjusted R$^{2}$ & 0.284 & 0.382 & 0.190 \\ 
Residual Std. Error & 0.934 (df = 439) & 0.873 (df = 592) & 0.935 (df = 595) \\ 
F Statistic & 17.226$^{***}$ (df = 11; 439) & 34.885$^{***}$ (df = 11; 592) & 13.913$^{***}$ (df = 11; 595) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 
\endgroup

\newpage

\hypertarget{linear-models-perceived-benefit-x-positive-and-negative-characteristics-of-the-technology}{%
\subsection{Linear Models: Perceived Benefit X positive and negative
characteristics of the
technology}\label{linear-models-perceived-benefit-x-positive-and-negative-characteristics-of-the-technology}}

\begingroup\setlength{\tabcolsep}{1pt}

\renewcommand{\arraystretch}{0.7}

\% Table created by stargazer v.5.2.3 by Marek Hlavac, Social Policy
Institute. E-mail: marek.hlavac at gmail.com \% Date and time: Wed, Jan
10, 2024 - 10:07:39

\begin{table}[!htbp] \centering 
  \caption{LMs with separate scale 2 FA solution: Perceived Benefit} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
\cline{2-4} 
\\[-1.8ex] & Ben\_Nuclear & Ben\_Solar & Ben\_Coal \\ 
\\[-1.8ex] & (1) & (2) & (3)\\ 
\hline \\[-1.8ex] 
 Uppercaste & $-$0.287$^{***}$ & $-$0.132$^{*}$ & $-$0.182$^{**}$ \\ 
  & (0.108) & (0.076) & (0.084) \\ 
  & & & \\ 
 Male & 0.058 & 0.035 & 0.148 \\ 
  & (0.116) & (0.083) & (0.094) \\ 
  & & & \\ 
 Hindu & 0.301$^{***}$ & 0.155$^{*}$ & 0.129 \\ 
  & (0.115) & (0.086) & (0.096) \\ 
  & & & \\ 
 UrbanUrban & 0.208$^{*}$ & $-$0.033 & 0.167$^{*}$ \\ 
  & (0.111) & (0.082) & (0.092) \\ 
  & & & \\ 
 age & $-$0.084 & $-$0.017 & 0.018 \\ 
  & (0.052) & (0.032) & (0.040) \\ 
  & & & \\ 
 StateRajasthan & $-$0.202 & 0.369$^{***}$ & $-$0.180 \\ 
  & (0.180) & (0.129) & (0.128) \\ 
  & & & \\ 
 StateTamil Nadu & $-$0.284 & 0.454$^{***}$ & $-$0.361$^{*}$ \\ 
  & (0.220) & (0.155) & (0.199) \\ 
  & & & \\ 
 StateUttar Pradesh & $-$0.218 & $-$0.008 & $-$0.359$^{**}$ \\ 
  & (0.182) & (0.142) & (0.151) \\ 
  & & & \\ 
 StateWest Bengal & 0.203 & 0.545$^{***}$ & $-$0.570$^{***}$ \\ 
  & (0.188) & (0.144) & (0.128) \\ 
  & & & \\ 
 KahanH &  & 0.132$^{**}$ &  \\ 
  &  & (0.058) &  \\ 
  & & & \\ 
 KahanS &  & $-$0.006 &  \\ 
  &  & (0.060) &  \\ 
  & & & \\ 
 socialcosts & 0.117$^{*}$ & $-$0.067 & 0.241$^{***}$ \\ 
  & (0.060) & (0.045) & (0.043) \\ 
  & & & \\ 
 pride & 0.298$^{***}$ & 0.219$^{***}$ & 0.313$^{***}$ \\ 
  & (0.055) & (0.043) & (0.040) \\ 
  & & & \\ 
 Constant & 3.176$^{***}$ & 3.487$^{***}$ & 3.079$^{***}$ \\ 
  & (0.169) & (0.129) & (0.141) \\ 
  & & & \\ 
\hline \\[-1.8ex] 
Observations & 455 & 612 & 603 \\ 
R$^{2}$ & 0.126 & 0.230 & 0.177 \\ 
Adjusted R$^{2}$ & 0.104 & 0.213 & 0.161 \\ 
Residual Std. Error & 1.001 (df = 443) & 0.832 (df = 598) & 0.931 (df = 591) \\ 
F Statistic & 5.814$^{***}$ (df = 11; 443) & 13.726$^{***}$ (df = 13; 598) & 11.537$^{***}$ (df = 11; 591) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 
\endgroup

\newpage

\hypertarget{linear-models-acceptancebenefit---risk-x-positive-and-negative-characteristics-of-the-technology}{%
\subsection{Linear Models: Acceptance(Benefit - Risk) X positive and
negative characteristics of the
technology}\label{linear-models-acceptancebenefit---risk-x-positive-and-negative-characteristics-of-the-technology}}

\begingroup\setlength{\tabcolsep}{1pt}

\renewcommand{\arraystretch}{0.7}

\% Table created by stargazer v.5.2.3 by Marek Hlavac, Social Policy
Institute. E-mail: marek.hlavac at gmail.com \% Date and time: Wed, Jan
10, 2024 - 10:07:40

\begin{table}[!htbp] \centering 
  \caption{LMs with separate scale 2 FA solution: Perceived Benefit} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
\cline{2-4} 
\\[-1.8ex] & Nuclear & Solar & Coal \\ 
\\[-1.8ex] & (1) & (2) & (3)\\ 
\hline \\[-1.8ex] 
 age & $-$0.180$^{***}$ & $-$0.023 & $-$0.149$^{***}$ \\ 
  & (0.067) & (0.051) & (0.053) \\ 
  & & & \\ 
 Uppercaste & $-$0.262$^{*}$ & $-$0.059 & $-$0.210$^{*}$ \\ 
  & (0.141) & (0.116) & (0.110) \\ 
  & & & \\ 
 Male & 0.211 & 0.086 & 0.140 \\ 
  & (0.153) & (0.128) & (0.122) \\ 
  & & & \\ 
 Hindu & 0.432$^{***}$ & 0.288$^{**}$ & $-$0.079 \\ 
  & (0.151) & (0.133) & (0.126) \\ 
  & & & \\ 
 UrbanUrban & 0.169 & 0.124 & 0.084 \\ 
  & (0.146) & (0.128) & (0.120) \\ 
  & & & \\ 
 StateRajasthan & $-$0.588$^{**}$ & 1.891$^{***}$ & 0.103 \\ 
  & (0.235) & (0.196) & (0.168) \\ 
  & & & \\ 
 StateTamil Nadu & $-$1.756$^{***}$ & 2.066$^{***}$ & 0.648$^{**}$ \\ 
  & (0.290) & (0.224) & (0.266) \\ 
  & & & \\ 
 StateUttar Pradesh & $-$0.445$^{*}$ & 1.218$^{***}$ & 0.579$^{***}$ \\ 
  & (0.238) & (0.211) & (0.198) \\ 
  & & & \\ 
 StateWest Bengal & $-$1.180$^{***}$ & 1.713$^{***}$ & $-$0.332$^{**}$ \\ 
  & (0.247) & (0.210) & (0.167) \\ 
  & & & \\ 
 socialcosts & $-$0.0002 & $-$0.164$^{**}$ & $-$0.187$^{***}$ \\ 
  & (0.078) & (0.067) & (0.057) \\ 
  & & & \\ 
 pride & 0.072 & 0.225$^{***}$ & 0.245$^{***}$ \\ 
  & (0.072) & (0.066) & (0.053) \\ 
  & & & \\ 
 Constant & 0.164 & 0.536$^{***}$ & 0.131 \\ 
  & (0.221) & (0.196) & (0.184) \\ 
  & & & \\ 
\hline \\[-1.8ex] 
Observations & 446 & 601 & 599 \\ 
R$^{2}$ & 0.189 & 0.420 & 0.091 \\ 
Adjusted R$^{2}$ & 0.168 & 0.410 & 0.074 \\ 
Residual Std. Error & 1.299 (df = 434) & 1.277 (df = 589) & 1.213 (df = 587) \\ 
F Statistic & 9.166$^{***}$ (df = 11; 434) & 38.840$^{***}$ (df = 11; 589) & 5.374$^{***}$ (df = 11; 587) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 
\endgroup

\end{document}

### 2024-01-15 Paper1.Rmd
commiting after a long time. oh god

@@
 ---
+
+\newpage
+
+# Abstract
+
+Indian state regards nuclear energy as an important solution to rising energy needs and climate change issues.
+However, throughout India, nuclear power initiatives have faced opposition from people.
+Using survey data this study reveals that, similar to global trends, nuclear energy is perceived as highly risk in India as well.
+It is also perceived as the riskiest technology among all large-scale energy sources (like coal, solar, wind, oil gas, and hydro).
+Using risk perception theories and frameworks, this paper delves into the underlying factors influencing India's public perception of nuclear energy.
+While consistent demographic patterns, termed the "white male effect," influence risk perceptions in the US, demographic factors such as gender and caste have minimal influence on India's nuclear energy risk perceptions.
+Cultural paradigms like hierarchy versus egalitarianism and individualism versus communitarianism also show negligible impact.
+However, regional differences among states and economic and political values have significant impact on risk perceptions related to nuclear energy in the Indian context.
+
 ```{r load packages, warning = FALSE, message = FALSE, echo=FALSE}
@@
 suppressPackageStartupMessages(library(psych)) 
+suppressPackageStartupMessages(library(foreign))
+suppressPackageStartupMessages(library(MASS))
+suppressPackageStartupMessages(library(Hmisc))
+suppressPackageStartupMessages(library(reshape2))
+
 ```
@@
 # code likert scale for variables for Kahan scale into numbers
-  mutate_at(vars(starts_with (c("K_I","K_H","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE", "DEV", "PROSPER", "RELY"))), funs(case_when(. == "Strongly disagree" ~ 1, 
+  mutate_at(vars(starts_with (c("K_S","K_E","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE","DEVNUCLEAR","PROSPER", "RELY"))), funs(case_when(. == "Strongly disagree" ~ 1, 
                . == "Somewhat disagree" ~ 2,
@@
 # reverse code for likert scale for variables for Kahan scale into numbers
-  mutate_at(vars(starts_with (c("K_S","K_E"))), funs(case_when(. == "Strongly disagree" ~ 5, 
+  mutate_at(vars(starts_with (c("K_H","K_I"))), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                                . == "Somewhat disagree" ~ 4,
@@
 # code eco-pol scale variables into numbers
-mutate_at(vars(SYSTEMDEMO,SYSTEMRELIGION,SYSTEMTECHNO,SYSTEMTOTAL,WEALTHLIM,MECHANISATION,DECISIONDECEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG), funs(case_when(. == "Strongly disagree" ~ 1, 
+mutate_at(vars(SYSTEMDEMO,SYSTEMRELIGION,SYSTEMTECHNO,SYSTEMTOTAL,WEALTHLIM,MECHANISATION,DECISIONDECEN,INDUSTRYSMALL,ECONOMYLOCAL,ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(.
+== "Strongly disagree" ~ 1,
                         . == "Somewhat disagree" ~ 2,
@@
 # reverse code eco-pol scale variables into numbers 
- mutate_at(vars(DECISIONCEN, INDUSTRYSMALL, ECONOMYLOCAL, ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(. == "Strongly disagree" ~ 5, 
+ mutate_at(vars(DECISIONCEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG, DEVOVERENV), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                                                                          . == "Somewhat disagree" ~ 4,
@@
 
-# H1: Nuclear Energy will be seen as riskier than other energy technologies in India.
-
-## Likert Responses (n= 2160)
-The percentages are rounded off to whole numbers.
-
-```{r, echo=FALSE}
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-# Q1: how much is the awareness of energy technologies in India ? How does it relate to state specific data ? 
-# summary of NA results from the combined sample of 2000 responses (simple percentage bar graphs)
-# part 1- how much is the awareness of energy technologies in India -
-
-#plotting perceived risk from different technologies including rather not say don't know
-colorsequence<- c("#8C4646","#D9695F","#F2A679","#F2D091","#5D8C7B","#808080")
-
-#following is the data frame for making the barplot 
-df_barplot <- uncodedjoineddf %>%
-  dplyr::select(starts_with("RISKY"))%>%
-  gather(Technology, Perceived_Risk, Risky_Hydro:Risky_INDLPG, factor_key = TRUE)%>%
-  separate(Technology, c("Risky", "Technology"), extra = "merge", fill = "left")%>%
-  dplyr::select(-Risky) %>% 
-  group_by(Technology, Perceived_Risk) %>%
-  dplyr::summarise(n=n())
-
-#following data frame gives us percentage for each response 
-df_barplot_percent<- df_barplot%>%
-  group_by(Technology) %>%
-  mutate(Percentage = round(n/sum(n)*100, 0)) %>%
-  ungroup()
-
-#plotting perceived benefit from different technologies including rather not say don't know
-
-df_barplotben <- uncodedjoineddf %>%
-  dplyr::select(starts_with("Ben"))%>%
-  gather(Technology, Perceived_Benefit, Ben_Hydro:Ben_INDKerosene, factor_key = TRUE)%>%
-  separate(Technology, c("Ben", "Technology"), extra = "merge", fill = "left")%>%
-  dplyr::select(-Ben) %>% 
-  group_by(Technology, Perceived_Benefit) %>%
-  dplyr::summarise(n=n())
-
-df_barplotben_percent<- df_barplotben%>%
-  group_by(Technology) %>%
-  mutate(Percentage = round(n/sum(n)*100, 0)) %>%
-  ungroup()
-
-#bar plot for likert responses perceived risk - centrally owned technologies 
-df_barplot %>% ggplot(aes(fill= fct_rev(factor(Perceived_Risk, levels=c("Extremely risky", "Very risky","Moderately risky","Slightly risky","Not at all risky","Rather not say/Don't know"))), y=n , x=Technology)) +
-  geom_bar(position="fill",stat="identity")+
-  geom_text(data = df_barplot_percent, aes(label=paste0(Percentage, "%"), y=n), position = position_fill(vjust=0.5), size=3) +
-  scale_x_discrete(limits = c("Solar", "Wind" ,"Hydro", "Oil", "Coal","Gas", "Nuclear"))+
-  scale_fill_manual("legend", values = c("Extremely risky" = "#8C4646", "Very risky" = "#D9695F", "Moderately risky" = "#F2A679", "Slightly risky" = "#F2D091","Not at all risky" = "#5D8C7B", "Rather not say/Don't know" = "grey94"))+
-  labs( y = "Perceived Risk", x ="Centrally Managed Energy Technologies")+
-  theme_classic()
-
-#perceived benefit centrally owned technologies
-
-df_barplotben %>% ggplot(aes(fill= factor(Perceived_Benefit, levels=c("Rather not say/Don't know","Not at all beneficial","Slightly beneficial","Moderately beneficial","Very beneficial", "Extremely beneficial")), y=n , x=Technology)) +
-  geom_bar(position="fill",stat="identity")+
-   geom_text(data = df_barplotben_percent, aes(label=paste0(Percentage, "%"), y=n), position = position_fill(vjust=0.5), size=3) +
-  scale_fill_manual("legend", values = c("Rather not say/Don't know" = "grey94" ,"Not at all beneficial" = "orange","Slightly beneficial"="yellow" ,"Moderately beneficial" = "palegreen","Very beneficial"= "green3", "Extremely beneficial"= "green4"))+
-  scale_x_discrete(limits = c("Solar", "Wind", "Hydro", "Oil", "Coal","Gas","Nuclear"))+
-  labs( y = "Perceived Benefit", x ="Centrally Managed Energy Technologies")+
-  theme_classic()
-
-```
-
-\newpage
+# Nuclear is seen as riskier than others -this paper explore this risk perception
 
@@
 
+joineddf_subset_cor <- joineddf %>%
+  dplyr::select(!starts_with(c("Ben_IND", "Risky_IND")))%>%
+  dplyr::select(starts_with("Risky"), 
+         starts_with("Ben"))%>%
+  na.omit()
+
+cor(joineddf_subset_cor)
+
 # Assuming your data is named joineddf_subset
@@
   group_by(Tech) %>%
-  summarize(Mean_Value = mean(Value, na.rm = TRUE),
+  dplyr::summarize(Mean_Value = mean(Value, na.rm = TRUE),
           sd = sd(Value, na.rm = TRUE),
@@
 
+# Split the data into Risky and Ben subsets
+risky_data <- joineddf_subset_cor %>% dplyr::select(starts_with("Risky"))
+ben_data <- joineddf_subset_cor %>% dplyr::select(starts_with("Ben"))
+
+# Rename the columns
+names(risky_data) <- gsub("^Risky_", "Perceived Risk (", names(risky_data))
+names(risky_data) <- paste0(names(risky_data), ")")
+names(ben_data) <- gsub("^Ben_", "Perceived Benefit (", names(ben_data))
+names(ben_data) <- paste0(names(ben_data), ")")
+
+# Compute the correlation between Risky and Ben variables
+correlation_matrix <- cor(risky_data, ben_data)
+
+correlation_df <- as.data.frame(correlation_matrix)
+
+#kable_table <- kable(correlation_df, caption = "Correlation Table between Perceived Risk and Perceived Benefit Variables", format = "html", #digits = 2) %>%
+  #kable_styling(full_width = F) %>%
+  #column_spec(1, background = "white") %>%
+  #add_header_above(c(" " = 1, "Perceived Benefits" = ncol(correlation_df)))#%>%
+  #pack_rows("Perceived Risks", 1, nrow(correlation_df))
+
+# Apply alternating background colors for columns
+#for (i in seq(2, ncol(correlation_df), by = 2)) {
+  #kable_table <- kable_table %>%
+
+#row_spec(i, background = "#F0F0F0")
+#}
+
+# Print the kable table
+#print(kable_table)
 ```
@@
   geom_errorbar(aes(xmin = Mean_Value - se, xmax = Mean_Value + se), width = 0.2) +
-  coord_cartesian(xlim = c(4, 1)) + 
+  coord_cartesian(xlim = c(5, 1)) + 
   labs(title = "Perceived Benefit", x = "Mean Values") +
@@
   geom_vline(data = subset(combined_mean, Category == "Beneficial"), 
-             aes(xintercept = mean_risk), linetype="dotted", color = "black", size = 0.5)
+             aes(xintercept = mean_benefit), linetype="dotted", color = "black", size = 0.5)
 
@@
   geom_errorbar(aes(xmin = Mean_Value - se, xmax = Mean_Value + se), width = 0.2) +
-  coord_cartesian(xlim = c(1, 4)) + 
+  coord_cartesian(xlim = c(1, 5)) + 
   labs(title = "Perceived Risk", x = "Mean Values") +
@@
 grid.arrange(ben_plot, risky_plot, ncol=2)
-
-```
-
-## Boxplot for perceived benefit and perceived risk by technology
-
-```{r, echo = FALSE, fig.width=16, fig.height=6}
-
-#Box plot to see the distribution
-
-# Loading the required libraries
-library(tidyverse)
-library(stringr)
-library(gridExtra)
-
-# Reshape the data to a long format
-joineddf_subset_long <- joineddf_subset %>%
-  pivot_longer(cols = everything(), 
-               names_to = "variable",
-               values_to = "value")
-
-# Separate the data into two: one for "Risky_" variables and one for "Ben_" variables
-risky_df <- joineddf_subset_long %>% 
-  filter(str_detect(variable, "^Risky_")) %>%
-  mutate(variable = str_remove(variable, "Risky_"))  # Remove the "Risky_" prefix
-
-ben_df <- joineddf_subset_long %>% 
-  filter(str_detect(variable, "^Ben_")) %>%
-  mutate(variable = str_remove(variable, "Ben_"))  # Remove the "Ben_" prefix
-
-# Remove NA values
-risky_df <- risky_df %>% drop_na()
-ben_df <- ben_df %>% drop_na()
-
-# Create box plots
-risky_plot <- ggplot(risky_df, aes(x = variable, y = value, fill = variable)) +
-  geom_boxplot() +
-  scale_fill_manual(values = rep("firebrick2", length(unique(risky_df$variable)))) +
-  labs(x = "Energy Technologies", y = "Likert", fill = "Technologies") +
-  ggtitle("Perceived risk") +
-  theme_minimal()+
-  theme(axis.text.y = element_text(size=20), 
-        axis.text.x = element_text(size=20),
-        axis.title.y = element_text(size=20),
-        axis.title.x = element_text(size=20),
-        title = element_text(size=20))+
-  guides(fill = FALSE)
-
-ben_plot <- ggplot(ben_df, aes(x = variable, y = value, fill = variable)) +
-  geom_boxplot() +
-  scale_fill_manual(values = rep("palegreen3", length(unique(ben_df$variable)))) +
-  labs(x = "Energy Technologies", y = "Likert Responses", fill = "Technologies") +
-  ggtitle("Perceived Benefit") +
-  theme_minimal()+
-  theme(axis.text.y = element_text(size=20), 
-        axis.text.x = element_text(size=20),
-        axis.title.y = element_text(size=20),
-        axis.title.x = element_text(size=20),
-        title = element_text(size=20))+
-  guides(fill = FALSE)
-
-# Put the two plots next to each other
-grid.arrange(risky_plot, ben_plot, ncol = 2)
-
-```
-
-\newpage
-
-## Pairwise T-test: Mean perceived risk and mean perceived benefit (all energy technologies)
-
-The red and green pairs indicate that there is a statistically significant difference between the means of the two groups. 
-White and grey indicate - no differences between the means of the two groups.
-
-```{r, echo = FALSE, fig.width=14, fig.height=6}
-#Q2 :How are the perceptions of the risk of producing energy from nuclear fission different from that of other conventional sources of energy like coal or hydro power in India?
-#H : Nuclear energy will be perceived as riskier than other sources of energy (coal or hydro) in India like in the west.
-perceivedriskc <-joineddf %>% 
-  dplyr::select("Risky_Solar", "Risky_Hydro", "Risky_Wind", "Risky_Nuclear", "Risky_Coal", "Risky_Gas", "Risky_Oil") %>%
-  gather(key = "technology", value = "perceived_risk") %>% 
-  mutate(technology = gsub("Risky_", "", technology)) %>%
-  na.omit()
-
-result_ttest <- pairwise.t.test(perceivedriskc$perceived_risk, perceivedriskc$technology, p.adjust.method = "BH")
-
-# visualising the pairwaise t test results. the non significant pairs are grey
-
-tidy_result_ttest <- broom::tidy(result_ttest)
-
-heatmap1 <- ggplot(tidy_result_ttest, aes(x = group1, y = group2, fill = p.value)) + 
-  geom_tile(color = "white") + 
-  scale_fill_gradient2(low = "firebrick2", high = "white", midpoint = 0.025, 
-                       limits = c(0, 0.05), space = "Lab", 
-                       name = "P-value") + 
-  theme_classic() + 
-  labs(x = "", y = "") + 
-  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
-   theme(axis.text.y = element_text(size=20), 
-        axis.text.x = element_text(size=20),
-        axis.title.y = element_text(size=20),
-        axis.title.x = element_text(size=20),
-        title = element_text(size=20),
-        legend.text = element_text(size=12))
-
-#Question- Why there is significant difference statistically - if the medians are the same in the boxplot.
-#Q3: How do perceptions of benefit from nuclear energy compare with other source of energy?
-
-# H : benefits from all energy technologies will be similar 
-# include regression, heat maps, bar graphs? - decide which ones are good to include
-
-perceivedbenefitc <-joineddf %>% 
-  dplyr::select("Ben_Solar", "Ben_Hydro", "Ben_Wind", "Ben_Nuclear", "Ben_Coal", "Ben_Gas", "Ben_Oil") %>%
-  gather(key = "technology", value = "perceived_benefit") %>% 
-  mutate(technology = gsub("Ben_", "", technology)) %>%
-  na.omit()
-
-result_ttestben <- pairwise.t.test(perceivedbenefitc$perceived_benefit, perceivedbenefitc$technology, p.adjust.method = "BH")
-
-# visualising the pairwaise t test results. the non significant pairs are grey
-
-tidy_resultbc <- broom::tidy(result_ttestben)
-
-library(ggplot2)
-heatmap2 <- ggplot(tidy_resultbc, aes(x = group1, y = group2, fill = p.value)) + 
-  geom_tile(color = "white") + 
-  scale_fill_gradient2(low = "palegreen3", high = "white", midpoint = 0.025, 
-                       limits = c(0, 0.05), space = "Lab", 
-                       name = "P-value") + 
-  theme_classic() + 
-  labs(x = "", y = "") + 
-  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
-   theme(axis.text.y = element_text(size=20), 
-        axis.text.x = element_text(size=20),
-        axis.title.y = element_text(size=20),
-        axis.title.x = element_text(size=20),
-        title = element_text(size=20),
-        legend.text = element_text(size=12))
-
-grid.arrange(heatmap1, heatmap2, ncol=2)
 
@@
 # Print model summary
-#summary(alldemoslm1)
+summary(alldemoslm1)
 #plot(alldemoslm1)
@@
 # Print model summary
-#summary(alldemoslm2)
+summary(alldemoslm2)
 #plot(alldemoslm1)
@@
 
-cat("\\begingroup")
-cat("\\setlength{\\tabcolsep}{1pt}")
-cat("\\renewcommand{\\arraystretch}{0.7}")
-stargazer(alldemoslm1_centered, alldemoslm2_centered, 
-          title = "Results from 2 linear regression models",
-          type = "latex"
-)
-cat("\\endgroup")
+#cat("\\begingroup")
+#cat("\\setlength{\\tabcolsep}{1pt}")
+#cat("\\renewcommand{\\arraystretch}{0.7}")
+#stargazer(alldemoslm1_centered, alldemoslm2_centered, 
+          #title = "Results from 2 linear regression models",
+          #type = "latex"
+#)
+#cat("\\endgroup")
 
@@
 
-```{r, echo=FALSE}
-library(MASS)
-
-alldemos_factor <-alldemos  %>%
-  mutate_at(vars(Risky_Nuclear, Uppercaste, Male, Hindu, Urban, State), as.factor)
-
-model= polr(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban +State , data = alldemos_factor, Hess = TRUE)
-#summary(model)
-
-model3 <- glm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban +State , data = alldemos_factor, family = binomial)
-#summary(model3)
-
-ci <- confint(model3)
-#print(ci)
-
-```
-
 \newpage
+
+##  kahan scale CFA, EFA and Alpha
 
@@
 
+Kahan_scale <- codedmodule2 %>%
+  dplyr::select(starts_with("K_"))
+
+kahan.fa <- fa(Kahan_scale, nfactors = 2, rotate = "varimax")
+
+print.psych(kahan.fa, sort = TRUE)
+
+KahanHE<-Kahan_scale %>%
+  dplyr::select(starts_with(c("K_H", "K_E")))
+
+KahanHE_alpha<- psych::alpha(KahanHE, check.keys = TRUE) # alpha = 0.7
+
+KahanSI<-Kahan_scale %>%
+  dplyr::select(starts_with(c("K_S", "K_I")))
+
+KahanSI_alpha<- psych::alpha(KahanSI, check.keys = TRUE) # alpha =0.52
+
+KahanS<-Kahan_scale %>%
+  dplyr::select(starts_with(c("K_S")))
+
+KahanS_alpha<- psych::alpha(KahanS, check.keys = TRUE) # alpha = 0.72
+
+KahanI<-Kahan_scale %>%
+  dplyr::select(starts_with(c("K_I")))
+
+KahanI_alpha<- psych::alpha(KahanI, check.keys = TRUE) # alpha = 0.31
+
 # Print the summary of the CFA results, including fit measures
@@
 ## RMSEA is still pretty big.
+
+```
+
+## Kahan scater plot from the CFA scores 
+```{r, echo = FALSE}
+
+Kahan_Kscores %>%
+  ggplot(aes(KahanS, KahanH))+
+  geom_count(aes(color = ..n.., size = ..n..))+
+  guides(color = 'legend')+
+  geom_hline(yintercept=0, colour="black", lwd=0.5)+
+  geom_vline(xintercept=0, colour="black", lwd=0.5)+
+  labs(x = "Individualism to Communitarianism", y = "Hierarchy to Egalitarianism")+
+  ylim(-2,3)+
+  xlim(-2,3)+
+  theme_minimal() 
+```
+
+## alternative Kahan scores
+```{r, echo=FALSE}
+
+Kscalescores <- fascales %>%
+  dplyr::select(!starts_with(("K_I")))%>%
+  rowwise()%>%
+  dplyr::mutate(Communitarianism_score = mean(c_across(K_SHARM:K_SPROTECT)))%>%
+  dplyr::mutate(Egalitarianism_score = mean(c_across(K_HEQUAL:K_ERADEQ2)))%>%
+  dplyr::select(!starts_with(c("K_I","K_S", "K_H", "K_E")))
+
+```
+
+# EDIT : Scatter plot of Kahan scale scores around the median scores on Individualism and Hierarchy scales
+
+```{r dev = "jpg", echo=FALSE}
+
+#scatter plot of Kahan scale scores around the median scores on Individualism and Hierarchy scales.
+
+Kscalescores %>%
+  ggplot(aes(Communitarianism_score,Egalitarianism_score))+
+  geom_count(aes(color = ..n.., size = ..n..))+
+  guides(color = 'legend')+
+  geom_hline(yintercept=3, colour="black", lwd=1)+
+  geom_vline(xintercept=3.5, colour="black", lwd=1)+
+  labs(x = "Individualism to Communitarianism", y = "Hierarchy to Egalitarianism")+
+  ylim(2,6)+
+  xlim(2,6)+
+  theme_minimal()
 
@@
 params1$Scale <- NA
-params1$Scale[1:3] <- "Individualism"
+params1$Scale[1:3] <- "Communitarian"
 params1$Scale[4:7] <- "Hierarchy-Egalitarianism"
@@
 #fa.parallel(ecopolall_cor)
-
 # this suggests 2 factors if we go by FA or 8 by PCA. let's try both and see how they look conceptually 
-
 # running EFA using psych package
@@
 ecopolall2.fa <- fa(ecopolall, nfactors = 2, rotate = "varimax")
+
+print.psych(ecopolall2.fa, sort = TRUE)
 
@@
   rename(Pdevelop = MR1)%>%
-  rename(Ndevelop = MR2) %>%
-  dplyr::select(!starts_with(c("K_","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR")))
+  rename(Ndevelop = MR2) #%>%
+  #dplyr::select(!starts_with(c("K_","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR")))
 
@@
     # Customize the grid
-    cglcol = "grey", cglty = 1.5, cglwd = 1.5,
+    cglcol = "black", cglty = 1.5, cglwd = 1.5,
     # Customize the axis
@@
     # Variable labels
-    vlcex = vlcex, vlabels = vlabels, vlpos = 0.95,
-    seg = 7, caxislabels = caxislabels, title = title, 
+    vlcex = vlcex, vlabels = vlabels, vlpos = 0.98,
+    seg = 6, caxislabels = caxislabels, title = title, 
     # Increase title size
@@
 create_beautiful_radarchart(
-  data = radar2, caxislabels = c(-0.6,-0.4,-0.2, 0, 0.2, 0.4, 0.6, 0.8, 1),
+  data = radar2, caxislabels = c(-0.6,-0.4,-0.2, 0, 0.2, 0.4, 0.6, 0.8,1),
   color = c("#00AFBB", "#F97D09"),
@@
 
-fa_table <- function(x, cut) {
+fa_table <- function(x) {
   #get sorted loadings
@@
   #supress loadings
-  loadings[loadings > -cut & loadings < cut] <- ""
+  #loadings[loadings < cut] <- ""  # alternative loadings > -cut & loadings < cut
   #get additional info  
@@
 
-fa_table(ecopolall2.fa, .4) %>%
+fa_table(ecopolall2.fa) %>%
   rename(Pdevelop = MR1, Ndevelop = MR2, Items= item) %>%
@@
 ndevelop <- ecopolall %>%
-  dplyr::select("JOBSNUCLEAR",  "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR")
+  dplyr::select( "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR")
 
@@
     "People Centered Development (Pdevelop)", "", "", "", "", "", "",
-    "Nationalist Development (Ndevelop)", "", "", "", ""
+    "Nationalist Development (Ndevelop)", "", "", ""
   ),
@@
     "Pro Regulations", "National development(nuclear)", "Community pride(nuclear)",
-    "National pride(nuclear)", "Local prosperity(nuclear)", "Job opportunities(nuclear)"
+    "National pride(nuclear)", "Local prosperity(nuclear)"
   ),
@@
     "Rapid mechanization of work is taking away jobs from workers in this country.(0.552)",
-    "Large corporations are destroying the local industries in India and benefiting only a handful of people.(-0.532)",
+    "Large corporations are destroying the local industries in India and benefiting only a handful of people.(0.532)",
     "Nuclear energy is leading to displacement of people from their land.(0.59)",
     "Nuclear energy increases pollution of air/water/land.(0.565)",
-    "Regardless of ownership, the government should pass strong regulations and implement them.(-0.53)",
+    "Regardless of ownership, the government should pass strong regulations and implement them.(0.53)",
     "Nuclear energy pushes forward the country's development.(0.662)",
@@
     "Nuclear energy is a mark of pride for our nation.(0.605)",
-    "Nuclear energy brings economic prosperity to the surrounding regions.(0.586)",
-    "Nuclear energy will bring jobs to the local community.(0.427)"
+    "Nuclear energy brings economic prosperity to the surrounding regions.(0.586)"
   ),
-  Alpha = c(0.757, "", "", "", "", "", "", 0.725, "", "", "", ""),
-  Variance = c("", "", "", "", "", "", "", "", "", "", "", "")
+  Alpha = c(0.757, "", "", "", "", "", "", 0.725, "", "", ""),
+  Variance = c(0.13, "", "", "", "", "", "", 0.10, "", "", "")
 )
@@
 
+# all lms after FA
 ```{r, echo=FALSE}
@@
 # Print model summary
-#summary(m1_kahan)
+summary(m1_kahan)
 #plot(m1_kahan)
@@
 # 4) lm with ecopolvars 
-m1_allscales <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State+ KahanS + KahanH + Pdevelop + Ndevelop, data = fascale_scores)
+m1_allscales <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State+ Pdevelop + Ndevelop + KahanS + KahanH , data = fascale_scores)
 # Print model summary
-#summary(m1_allscales)
+summary(m1_allscales)
 #plot(m1_allscales)
 
+m1_ecopol <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State + Pdevelop + Ndevelop,  data = fascale_scores)
+
+summary(m1_ecopol)
+
+m1_allscales2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + KahanS*State + KahanH*State + Pdevelop*State + Ndevelop*State , data = fascale_scores)
+
+summary(m1_allscales2)
+
+```
+
+# Lms with alt Kahan scores 
+```{r, echo = FALSE}
+
+# binding ecopol with alternative Kahan scale score 
+fascale_scores2 <-cbind(Kscalescores, scores1)  %>%
+  rename(Pdevelop = MR1)%>%
+  rename(Ndevelop = MR2)
+
+fascale_scores2
+
+fascale_scores2cor <- fascale_scores2 %>%
+  dplyr::select(Communitarianism_score, Egalitarianism_score, Pdevelop, Ndevelop)
+
+cor_kecopol <- cor(fascale_scores2cor)
+
+# 3) lm with kahan 
+m1_kahan2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State + Communitarianism_score + Egalitarianism_score , data = fascale_scores2)
+# Print model summary
+summary(m1_kahan2)
+#plot(m1_kahan)
+
+# 4) lm with ecopolvars 
+m1_allscales2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State+ Pdevelop + Ndevelop + Communitarianism_score + Egalitarianism_score , data = fascale_scores2)
+# Print model summary
+summary(m1_allscales2)
+#plot(m1_allscales)
+
+m1_ecopol2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State + Pdevelop + Ndevelop,  data = fascale_scores2)
+
+summary(m1_ecopol2)
+
+```
+
+# graphs for lm attempts
+
+```{r, echo=FALSE}
+
+library(interactions)
+sim_slopes(m1_allscales2, pred = Ndevelop, modx = State)
+
+ggplot(fascale_scores, aes(x = Ndevelop, y = Risky_Nuclear, color = State)) +
+  geom_point(alpha = 0.5) +  # Add points with some transparency
+  geom_smooth(method = 'lm', se = FALSE) +  # Add linear regression lines
+  theme_minimal() +
+  labs(title = "Interaction Plot",
+       x = "National Development (Ndevelop)",
+       y = "Perceived Risk (Risky_Nuclear)")
+library(car)
+vif(m1_allscales)
+
+str(fascale_scores)
+
+ggplot(fascale_scores, aes(x = Pdevelop, y = Risky_Nuclear)) +
+  geom_point() +  # or geom_line() depending on how you want to visualize it
+  facet_wrap(~ State) +  # This will create separate plots for each State
+  labs(title = "Risky Nuclear vs Pdevelop by State",
+       x = "Pdevelop",
+       y = "Risky Nuclear") +
+  theme_minimal()
+
+ggplot(fascale_scores, aes(x = Ndevelop, y = Risky_Nuclear)) +
+  geom_jitter(alpha = 0.5, width = 0.2) +
+  #facet_wrap(~ State) +
+  geom_smooth(method = "lm", se = FALSE) +
+  labs(title = "Relationship between Ndevelop and Risky Nuclear",
+       x = "Ndevelop",
+       y = "Risky Nuclear") +
+  theme_minimal()
+
+ggplot(fascale_scores, aes(x = Pdevelop, y = Risky_Nuclear)) +
+  geom_jitter(alpha = 0.5, width = 0.2) +
+  facet_wrap(~ State) +
+  geom_smooth(method = "lm", se = FALSE) +
+  labs(title = "Relationship between Ndevelop and Risky Nuclear",
+       x = "Ndevelop",
+       y = "Risky Nuclear") +
+  theme_minimal()
+
+ggplot(fascale_scores, aes(x = State, y = Risky_Nuclear)) +
+  geom_boxplot() +
+  #facet_wrap(~ State) +
+  theme_minimal()
 ```
@@
 
+```{r, echo=FALSE, results='asis'}
+library(stargazer)
+
+cat("\\begingroup")
+cat("\\setlength{\\tabcolsep}{1pt}")
+cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer(m1_ecopol, m1_allscales, 
+          title = "Results from 2 linear regression models",
+          type = "latex"
+)
+cat("\\endgroup")
+
+```
 \newpage
+
+# Logistic Regression
+
+```{r, echo=FALSE}
+library(MASS)
+
+fascale_scores1 <- fascale_scores %>%
+  mutate_at(vars(Risky_Nuclear), as.factor)
+
+## one at a time, table 
+#lapply(fascale_scores1[, c("Risky_Nuclear", "Uppercaste", "Male", "Hindu","Urban", "State") ], table)
+## three way cross tabs (xtabs) and flatten the table
+#ftable(xtabs(~ Uppercaste + Risky_Nuclear + Male, data = fascale_scores1))
+## three way cross tabs (xtabs) and flatten the table
+#ftable(xtabs(~ State + Risky_Nuclear + Urban, data = fascale_scores1))
+
+logm1= polr(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban +age + KahanS + KahanH + Pdevelop + Ndevelop + State  , data = fascale_scores1, Hess = TRUE)
+#summary(logm1)
+
+ctable1 <- coef(summary(logm1))
+
+## calculate and store p values
+p1 <- pnorm(abs(ctable1[, "t value"]), lower.tail = FALSE) * 2
+
+## combined table
+ctable1 <- cbind(ctable1, "p value" = round(p1,3))
+
+pvalue <- as_tibble(ctable1) %>%
+  dplyr::select("p value")%>%
+  slice(1:(n() - 4))
+
+ci <- confint(logm1)# default method gives profiled CIs
+
+#confint.default(logm1) # CIs assuming normality
+
+## odds ratios
+#exp(coef(logm1))
+
+## OR and CI
+ORtable <- cbind("Odds Ratio" = coef(logm1), ci, pvalue) %>%
+  mutate(
+    `Odds Ratio` = round(`Odds Ratio`, 3),
+    `2.5 %` = round(`2.5 %`, 3),
+    `97.5 %` = round(`97.5 %`, 3)
+  )
+
+ORtableout <- knitr::kable(ORtable, booktabs = TRUE, caption = "Odds Ratio for Perceived Risk from Nuclear Energy") %>%
+  kable_styling(latex_options = c("striped", "hold_position"))
+
+ORtableout
+
+```
 
@@
 #fitrisky_nucleargm <- with(codedmodule2, clm(Risky_Nuclear ~ 1 + SYSTEMDEMO + SYSTEMRELIGION + SYSTEMTOTAL + SYSTEMTECHNO))
+
+```
+
+```{r, echo =FALSE}
+
+# same things with benefit from Nuclear Energy
+fascalesben <- codedmodule2 %>%
+  dplyr::select(starts_with(c("K_","Ben_Nuclear","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%
+  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
+                                      . == "25-34 years old" ~ 2,
+                                      . ==  "35-44 years old" ~3,
+                                      . == "45-54 years old" ~ 4,
+                                      . == "55-64 years old" ~ 5,
+                                      . == "65-74 years old" ~ 6,
+                                      . == "75 years or older" ~ 7))) %>%
+  na.omit()
+
+Kahan_fas <- '
+  KahanS =~ K_SHARM + K_SLIMCHOI + K_SPROTECT 
+  KahanH =~ K_HEQUAL+ K_ERADEQ1 + K_EWEALTH + K_ERADEQ2
+'
+
+# Run CFA
+Kahan_cfaben <- cfa(Kahan_fas, data = fascalesben, std.lv = TRUE)
+
+Kahan_scoresben <- predict(Kahan_cfaben, newdata = fascalesben)
+
+Kahan_Kscoresben <- cbind(fascalesben, Kahan_scoresben)
+
+ecopolallben <- fascalesben %>%
+        dplyr::select("WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR")
+
+ecopolallben_alpha <- psych::alpha(ecopolallben, check.keys = TRUE)
+
+#summary(ecopolall_alpha)
+
+# when we combine both the scales the alpha is high at 0.785 (almost 0.8)
+
+# FA on all ecopol variables except systems of governance
+
+ecopolallben_cor <- cor(ecopolallben)
+PCA24 <- principal(ecopolallben, nfactors = 24, rotate = "none") # no rotation to start with.
+
+ecopolallben2.fa <- fa(ecopolallben, nfactors = 2, rotate = "varimax")
+
+# I don't know still doesn't make a lot of sense to me- the two factors make more sense - 1) people centered development 2) nationalist development
+# So I am going to extract factor scores and bind them to the dataset
+
+ecopolallben_scores <- psych::factor.scores(ecopolallben, ecopolallben2.fa)
+
+# The factor scores will be stored in the scores element of the returned list
+scores2 <- ecopolallben_scores$scores
+
+#binding factor scores to the dataset
+
+fascale_scoresben <- cbind(Kahan_Kscoresben, scores2) %>%
+  rename(Pdevelop = MR1)%>%
+  rename(Ndevelop = MR2) #%>%
+  #dplyr::select(!starts_with(c("K_","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR")))
+
+mbennuclear <- lm(Ben_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State+ KahanS + KahanH + Pdevelop + Ndevelop , data = fascale_scoresben)
+# Print model summary
+#summary(mbennuclear)
 

### 2024-01-15 corstuff.Rmd
commiting after a long time. oh god

--- 2024-01-15 Paper1.Rmd
@@
 ---
-title: "Nuclear Energy: Kahan scale and Economic Political value scale"
+title: "correlationstuff"
 output:
@@
 ---
-
-\newpage
-
-# Abstract
-
-Indian state regards nuclear energy as an important solution to rising energy needs and climate change issues.
-However, throughout India, nuclear power initiatives have faced opposition from people.
-Using survey data this study reveals that, similar to global trends, nuclear energy is perceived as highly risk in India as well.
-It is also perceived as the riskiest technology among all large-scale energy sources (like coal, solar, wind, oil gas, and hydro).
-Using risk perception theories and frameworks, this paper delves into the underlying factors influencing India's public perception of nuclear energy.
-While consistent demographic patterns, termed the "white male effect," influence risk perceptions in the US, demographic factors such as gender and caste have minimal influence on India's nuclear energy risk perceptions.
-Cultural paradigms like hierarchy versus egalitarianism and individualism versus communitarianism also show negligible impact.
-However, regional differences among states and economic and political values have significant impact on risk perceptions related to nuclear energy in the Indian context.
 
@@
 
-# Nuclear is seen as riskier than others -this paper explore this risk perception
-
 ## Mean Perceived Risk and Mean Perceived Benefit for all energy technologies.
@@
 
-cor(joineddf_subset_cor)
+#cor(joineddf_subset_cor)
 
@@
 
-#kable_table <- kable(correlation_df, caption = "Correlation Table between Perceived Risk and Perceived Benefit Variables", format = "html", #digits = 2) %>%
-  #kable_styling(full_width = F) %>%
-  #column_spec(1, background = "white") %>%
-  #add_header_above(c(" " = 1, "Perceived Benefits" = ncol(correlation_df)))#%>%
-  #pack_rows("Perceived Risks", 1, nrow(correlation_df))
-
-# Apply alternating background colors for columns
-#for (i in seq(2, ncol(correlation_df), by = 2)) {
-  #kable_table <- kable_table %>%
-
-#row_spec(i, background = "#F0F0F0")
-#}
-
-# Print the kable table
-#print(kable_table)
 ```
@@
 # Arrange plots side by side
-grid.arrange(ben_plot, risky_plot, ncol=2)
+#grid.arrange(ben_plot, risky_plot, ncol=2)
 
@@
 \newpage
-
-# H2: Gender and Caste will have significant impact like Gender and Race in the US studies of risk.
 
@@
 # Print model summary
-summary(alldemoslm1)
+#summary(alldemoslm1)
 #plot(alldemoslm1)
-
-# lm suggests there is no significant white male effect or upper caste male effect for risk perception from nuclear energy in India. 
-# the coefficients are very small and so is the r squared - rsquared is minimal.
 
@@
 # Print model summary
-summary(alldemoslm2)
+#summary(alldemoslm2)
 #plot(alldemoslm1)
 
-# most of these results indicate that there is no significant white male effect or upper caste male effect for risk perception from nuclear energy in India. 
-# the coefficients are very small and so is the r squared - rsquared is minimal.
-
-```
-
-## two linear regression models
+```
+
+## Demographic IVs - two linear regression models
 ```{r, echo=FALSE, results='asis'}
@@
 
-# H3: Regional differences will have a strong impact
-
 ## Linear regression where Mean value is the intercept
@@
 
-#cat("\\begingroup")
-#cat("\\setlength{\\tabcolsep}{1pt}")
-#cat("\\renewcommand{\\arraystretch}{0.7}")
-#stargazer(alldemoslm1_centered, alldemoslm2_centered, 
-          #title = "Results from 2 linear regression models",
-          #type = "latex"
-#)
-#cat("\\endgroup")
+cat("\\begingroup")
+cat("\\setlength{\\tabcolsep}{1pt}")
+cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer(alldemoslm1_centered, alldemoslm2_centered, 
+          title = "Results from 2 linear regression models",
+          type = "latex"
+)
+cat("\\endgroup")
 
@@
 
-## Regional Differences Graph 
-Following is a graph of z scores calculated from mean perceived risk from nuclear energy by state.
-
-```{r, echo = FALSE, fig.width=8, fig.height=4}
-
-staterisky <- joineddf %>%
-  dplyr::select(!starts_with(c("Ben_IND", "Risky_IND")))%>%
-  dplyr::select(starts_with("Risky"), State)
-
-staterisky_mean <- staterisky %>%
-  group_by(State) %>%
-  summarise(
-    Mean_Risky_Hydro = mean(Risky_Hydro, na.rm = TRUE),
-    Mean_Risky_Solar = mean(Risky_Solar, na.rm = TRUE),
-    Mean_Risky_Wind = mean(Risky_Wind, na.rm = TRUE),
-    Mean_Risky_Nuclear = mean(Risky_Nuclear, na.rm = TRUE),
-    Mean_Risky_Coal = mean(Risky_Coal, na.rm = TRUE),
-    Mean_Risky_Gas = mean(Risky_Gas, na.rm = TRUE),
-    Mean_Risky_Oil = mean(Risky_Oil, na.rm = TRUE)
-  )
-
-# Extract only Nuclear
-nuclear_data <- staterisky_mean %>%
-  dplyr::select(State, Mean_Risky_Nuclear)%>%
-  mutate(
-    Z_Risky_Nuclear = (Mean_Risky_Nuclear - mean(Mean_Risky_Nuclear, na.rm = TRUE)) / 
-                      sd(Mean_Risky_Nuclear, na.rm = TRUE)
-  )
-
-mean_nuclear_state <- ggplot(nuclear_data, aes(x = State, y = Mean_Risky_Nuclear, group = 1)) +
-  geom_line(color = "#F0BA32", size = 1) +
-  geom_point(color = "#F0BA32", size = 3) +
-  labs(title = "Means: Perceived Risk of Nuclear Energy",
-       x = "State", y = "Mean Perceived Risk") +
-  theme_minimal() +
-  ylim(1,5)+
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-
-# Plot the z-scores
-zscore_nuclear_state <- ggplot(nuclear_data, aes(x = State, y = Z_Risky_Nuclear, group = 1)) +
-  geom_line(color = "#F0BA32", size = 1) +
-  geom_point(color = "#F0BA32", size = 3) +
-  labs(title = "Z-scores: Perceived Risk of Nuclear Energy",
-       x = "State", y = "Z-Score") +
-  ylim(-1 ,2)+
-  theme_minimal() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-
-library(gridExtra)
-
-# Assuming mean_nuclear_state and zscore_nuclear_state are both ggplot objects
-
-# We'll add a spacer grob for spacing between plots
-spacer <- grid::rectGrob(gp = grid::gpar(col = "white"))
-
-grid.arrange(mean_nuclear_state, spacer, zscore_nuclear_state, ncol=3, widths=c(0.8, 0.06, 0.8))
-
-```
-
-\newpage
-
-##  kahan scale CFA, EFA and Alpha
+##  Kahan scale Alpha values 
+Hierarchy - Egalitarianism scale alpha  =  0.7
+Individualism - Communitarianism scale alpha= 0.52
+Only Individualism scale alpha = 0.31 
+Only Communitarianism scale alpha = 0.72
 
@@
 
-kahan.fa <- fa(Kahan_scale, nfactors = 2, rotate = "varimax")
-
-print.psych(kahan.fa, sort = TRUE)
-
 KahanHE<-Kahan_scale %>%
@@
 
-# Print the summary of the CFA results, including fit measures
-#summary(Kahan_cfa, fit.measure= TRUE, standardized = TRUE)
-
-# RMSEA - between 0.05 and 0.08 (reasonable fit), less than 0.05 close fit and greater than 0.10 is poor fit 
-# CFI - greater than 0.90 or 0.95 indicates good fit
-#TFI - CFI>TFI >0.90 - indicates good fit
-#pvalue should be greater than 0.05 p > 0.0.5
-
-# after having removed a few variables that had very low loading, the model is now a good fit, we have two latent variables - Hierarchy- egalitarian and Communitarian.
-Again we see that individualistic variables just don't fit here.
-
-# creating table of factor scores
-
 Kahan_scores <- predict(Kahan_cfa, newdata = fascales)
@@
 
-## RMSEA is still pretty big.
-
-```
-
-## Kahan scater plot from the CFA scores 
-```{r, echo = FALSE}
-
-Kahan_Kscores %>%
-  ggplot(aes(KahanS, KahanH))+
-  geom_count(aes(color = ..n.., size = ..n..))+
-  guides(color = 'legend')+
-  geom_hline(yintercept=0, colour="black", lwd=0.5)+
-  geom_vline(xintercept=0, colour="black", lwd=0.5)+
-  labs(x = "Individualism to Communitarianism", y = "Hierarchy to Egalitarianism")+
-  ylim(-2,3)+
-  xlim(-2,3)+
-  theme_minimal() 
+```
+
+# EDIT :  Kahan scale EFA  
+```{r, echo=FALSE}
+
+Kahan_scale <- codedmodule2 %>%
+  dplyr::select(starts_with("K_"))
+
+kahan.fa <- fa(Kahan_scale, nfactors = 2, rotate = "varimax")
+
+#print.psych(kahan.fa, cut = 0.4, sort = TRUE)
+
+```
+
+```{r, echo=FALSE}
+
+library(flextable)
+
+flex <- function(data, title=NULL) {
+  # this grabs the data and converts it to a flextbale
+  flextable(data) %>%
+  # this makes the table fill the page width
+  set_table_properties(layout = "autofit", width = 1) %>%
+  # font size
+  fontsize(size=10, part="all") %>%
+    #this adds a ttitlecreates an automatic table number
+      set_caption(title, 
+                  autonum = officer::run_autonum(seq_id = "tab", 
+                                                 pre_label = "Table ", 
+                                                 post_label = "\n", 
+                                                 bkm = "anytable")) #%>%
+  # font type
+  #font(fontname="Times New Roman", part="all")
+}
+
+rename_map <- c(
+  "K_SHARM" = "(C)Sometimes the government needs to make laws that keep people from hurting themselves.",
+  "K_SLIMCHOI" = "(C)The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.",
+  "K_SPROTECT" = "(C)The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.",
+  "K_HEQUAL" = "(H)We have gone too far in pushing equal rights in this country.",
+  "K_ERADEQ1" = "(E)We need to dramatically reduce inequalities between the rich and the poor.",
+  "K_EWEALTH" = "(E)Our society would be better off if the distribution of wealth was more equal.",
+  "K_ERADEQ2" = "(E)We need to dramatically reduce inequalities between men and women."
+)
+
+fa_table <- function(x) {
+  #get sorted loadings
+  loadings <- fa.sort(x)$loadings %>% round(3)
+  #supress loadings
+  #loadings[loadings < cut] <- ""  # alternative loadings > -cut & loadings < cut
+  #get additional info  
+  add_info <- cbind(x$communalities, 
+                    x$uniquenesses,
+                    x$complexity) %>%
+    # make it a data frame
+    as.data.frame() %>%
+    # column names
+   rename("Communality" = V1,
+           "Uniqueness" = V2,
+           "Complexity" = V3) %>%
+    #get the item names from the vector
+    rownames_to_column("item")
+  #build table
+  loadings %>%
+    unclass() %>%
+    as.data.frame() %>%
+    rownames_to_column("item") %>%
+    left_join(add_info) %>%
+    mutate(
+      item = if_else(item %in% names(rename_map), rename_map[item], item),
+      across(where(is.numeric), round, 3)
+    )
+}
+
+fa_table(kahan.fa) %>%
+  #rename(Pdevelop = MR1, Ndevelop = MR2, Items= item) %>%
+  flex("Kahan Exploratory Factor Analysis Table")
+
 ```
@@
   dplyr::select(!starts_with(c("K_I","K_S", "K_H", "K_E")))
-
-```
-
-# EDIT : Scatter plot of Kahan scale scores around the median scores on Individualism and Hierarchy scales
-
-```{r dev = "jpg", echo=FALSE}
-
-#scatter plot of Kahan scale scores around the median scores on Individualism and Hierarchy scales.
-
-Kscalescores %>%
-  ggplot(aes(Communitarianism_score,Egalitarianism_score))+
-  geom_count(aes(color = ..n.., size = ..n..))+
-  guides(color = 'legend')+
-  geom_hline(yintercept=3, colour="black", lwd=1)+
-  geom_vline(xintercept=3.5, colour="black", lwd=1)+
-  labs(x = "Individualism to Communitarianism", y = "Hierarchy to Egalitarianism")+
-  ylim(2,6)+
-  xlim(2,6)+
-  theme_minimal()
 
@@
 
+```
+
+## Kahan scater plot from the CFA scores 
+```{r, echo = FALSE}
+
+Kahan_Kscores %>%
+  ggplot(aes(KahanS, KahanH))+
+  geom_count(aes(color = ..n.., size = ..n..))+
+  guides(color = 'legend')+
+  geom_hline(yintercept=0, colour="black", lwd=0.5)+
+  geom_vline(xintercept=0, colour="black", lwd=0.5)+
+  labs(x = "Individualism to Communitarianism", y = "Hierarchy to Egalitarianism")+
+  ylim(-2,3)+
+  xlim(-2,3)+
+  theme_minimal() 
 ```
@@
 m1_demo <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban, data = fascale_scores)
-# Print model summary
-#summary(m1_demo)
-#plot(m1_demo)
-
-# lm suggests there is no significant white male effect or upper caste male effect for risk perception from nuclear energy in India. 
-# the coefficients are very small and so is the r squared - rsquared is minimal.
 
@@
 m2_demo<- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State, data = fascale_scores)
-# Print model summary
-#summary(m2_demo)
-#plot(m2_demo)
-
-# States and some age have some impact on y variable.
 
@@
 m1_kahan <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State + KahanS + KahanH , data = fascale_scores)
-# Print model summary
-summary(m1_kahan)
-#plot(m1_kahan)
 
@@
 m1_allscales <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State+ Pdevelop + Ndevelop + KahanS + KahanH , data = fascale_scores)
-# Print model summary
-summary(m1_allscales)
-#plot(m1_allscales)
 
@@
 
-# Lms with alt Kahan scores 
-```{r, echo = FALSE}
-
+# Correlation Eco-pol and alt Kahan(mean across)
+
+```{r}
 # binding ecopol with alternative Kahan scale score 
@@
 cor_kecopol <- cor(fascale_scores2cor)
+
+print(cor_kecopol)
+```
+
+# Lms with alt Kahan scores 
+```{r, echo = FALSE}
 
@@
 
-# graphs for lm attempts
-
-```{r, echo=FALSE}
-
-library(interactions)
-sim_slopes(m1_allscales2, pred = Ndevelop, modx = State)
-
-ggplot(fascale_scores, aes(x = Ndevelop, y = Risky_Nuclear, color = State)) +
-  geom_point(alpha = 0.5) +  # Add points with some transparency
-  geom_smooth(method = 'lm', se = FALSE) +  # Add linear regression lines
-  theme_minimal() +
-  labs(title = "Interaction Plot",
-       x = "National Development (Ndevelop)",
-       y = "Perceived Risk (Risky_Nuclear)")
-library(car)
-vif(m1_allscales)
-
-str(fascale_scores)
-
-ggplot(fascale_scores, aes(x = Pdevelop, y = Risky_Nuclear)) +
-  geom_point() +  # or geom_line() depending on how you want to visualize it
-  facet_wrap(~ State) +  # This will create separate plots for each State
-  labs(title = "Risky Nuclear vs Pdevelop by State",
-       x = "Pdevelop",
-       y = "Risky Nuclear") +
-  theme_minimal()
-
-ggplot(fascale_scores, aes(x = Ndevelop, y = Risky_Nuclear)) +
-  geom_jitter(alpha = 0.5, width = 0.2) +
-  #facet_wrap(~ State) +
-  geom_smooth(method = "lm", se = FALSE) +
-  labs(title = "Relationship between Ndevelop and Risky Nuclear",
-       x = "Ndevelop",
-       y = "Risky Nuclear") +
-  theme_minimal()
-
-ggplot(fascale_scores, aes(x = Pdevelop, y = Risky_Nuclear)) +
-  geom_jitter(alpha = 0.5, width = 0.2) +
-  facet_wrap(~ State) +
-  geom_smooth(method = "lm", se = FALSE) +
-  labs(title = "Relationship between Ndevelop and Risky Nuclear",
-       x = "Ndevelop",
-       y = "Risky Nuclear") +
-  theme_minimal()
-
-ggplot(fascale_scores, aes(x = State, y = Risky_Nuclear)) +
-  geom_boxplot() +
-  #facet_wrap(~ State) +
-  theme_minimal()
+```{r, echo=FALSE, results='asis'}
+library(stargazer)
+
+cat("\\begingroup")
+cat("\\setlength{\\tabcolsep}{1pt}")
+cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer(m1_kahan2, m1_ecopol2, m1_allscales2, 
+          title = "Results from 3 linear regression models",
+          type = "latex"
+)
+cat("\\endgroup")
+
 ```
@@
 
-# H4 : Economic and Political Values will be important in explaining perceived risk from Nuclear Energy
+# LMs : eco-pol and kahan scale
 
@@
 
+\newpage
 ```{r, echo=FALSE, results='asis'}
@@
 
-# Logistic Regression
-
-```{r, echo=FALSE}
-library(MASS)
-
-fascale_scores1 <- fascale_scores %>%
-  mutate_at(vars(Risky_Nuclear), as.factor)
-
-## one at a time, table 
-#lapply(fascale_scores1[, c("Risky_Nuclear", "Uppercaste", "Male", "Hindu","Urban", "State") ], table)
-## three way cross tabs (xtabs) and flatten the table
-#ftable(xtabs(~ Uppercaste + Risky_Nuclear + Male, data = fascale_scores1))
-## three way cross tabs (xtabs) and flatten the table
-#ftable(xtabs(~ State + Risky_Nuclear + Urban, data = fascale_scores1))
-
-logm1= polr(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban +age + KahanS + KahanH + Pdevelop + Ndevelop + State  , data = fascale_scores1, Hess = TRUE)
-#summary(logm1)
-
-ctable1 <- coef(summary(logm1))
-
-## calculate and store p values
-p1 <- pnorm(abs(ctable1[, "t value"]), lower.tail = FALSE) * 2
-
-## combined table
-ctable1 <- cbind(ctable1, "p value" = round(p1,3))
-
-pvalue <- as_tibble(ctable1) %>%
-  dplyr::select("p value")%>%
-  slice(1:(n() - 4))
-
-ci <- confint(logm1)# default method gives profiled CIs
-
-#confint.default(logm1) # CIs assuming normality
-
-## odds ratios
-#exp(coef(logm1))
-
-## OR and CI
-ORtable <- cbind("Odds Ratio" = coef(logm1), ci, pvalue) %>%
-  mutate(
-    `Odds Ratio` = round(`Odds Ratio`, 3),
-    `2.5 %` = round(`2.5 %`, 3),
-    `97.5 %` = round(`97.5 %`, 3)
-  )
-
-ORtableout <- knitr::kable(ORtable, booktabs = TRUE, caption = "Odds Ratio for Perceived Risk from Nuclear Energy") %>%
-  kable_styling(latex_options = c("striped", "hold_position"))
-
-ORtableout
-
-```
-
-```{r, echo=FALSE}
-# Q7 : political values scale - factor analysis - reduce dimensions and then run regression -logistic regression 
-# Using logistic regression for the SYSTEM prefixed variables.
-
-#codedmodule2
-#codedmodule2$SYSTEMDEMO <- as.factor(codedmodule2$SYSTEMDEMO)
-#levels(codedmodule2$SYSTEMDEMO)
-
-#codedmodule2$SYSTEMRELIGION <- as.factor(codedmodule2$SYSTEMRELIGION)
-#levels(codedmodule2$SYSTEMRELIGION)
-
-#codedmodule2$SYSTEMTOTAL <- as.factor(codedmodule2$SYSTEMTOTAL)
-#levels(codedmodule2$SYSTEMTOTAL)
-
-#codedmodule2$SYSTEMTECHNO <- as.factor(codedmodule2$SYSTEMTECHNO)
-#levels(codedmodule2$SYSTEMTECHNO)
-
-#codedmodule2$Risky_Nuclear <- as.factor(codedmodule2$Risky_Nuclear)
-#levels(codedmodule2$Risky_Nuclear)
-
-#fitrisky_nucleargm <- with(codedmodule2, clm(Risky_Nuclear ~ 1 + SYSTEMDEMO + SYSTEMRELIGION + SYSTEMTOTAL + SYSTEMTECHNO))
-
-```
-
-```{r, echo =FALSE}
-
-# same things with benefit from Nuclear Energy
-fascalesben <- codedmodule2 %>%
-  dplyr::select(starts_with(c("K_","Ben_Nuclear","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%
-  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
-                                      . == "25-34 years old" ~ 2,
-                                      . ==  "35-44 years old" ~3,
-                                      . == "45-54 years old" ~ 4,
-                                      . == "55-64 years old" ~ 5,
-                                      . == "65-74 years old" ~ 6,
-                                      . == "75 years or older" ~ 7))) %>%
-  na.omit()
-
-Kahan_fas <- '
-  KahanS =~ K_SHARM + K_SLIMCHOI + K_SPROTECT 
-  KahanH =~ K_HEQUAL+ K_ERADEQ1 + K_EWEALTH + K_ERADEQ2
-'
-
-# Run CFA
-Kahan_cfaben <- cfa(Kahan_fas, data = fascalesben, std.lv = TRUE)
-
-Kahan_scoresben <- predict(Kahan_cfaben, newdata = fascalesben)
-
-Kahan_Kscoresben <- cbind(fascalesben, Kahan_scoresben)
-
-ecopolallben <- fascalesben %>%
-        dplyr::select("WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR")
-
-ecopolallben_alpha <- psych::alpha(ecopolallben, check.keys = TRUE)
-
-#summary(ecopolall_alpha)
-
-# when we combine both the scales the alpha is high at 0.785 (almost 0.8)
-
-# FA on all ecopol variables except systems of governance
-
-ecopolallben_cor <- cor(ecopolallben)
-PCA24 <- principal(ecopolallben, nfactors = 24, rotate = "none") # no rotation to start with.
-
-ecopolallben2.fa <- fa(ecopolallben, nfactors = 2, rotate = "varimax")
-
-# I don't know still doesn't make a lot of sense to me- the two factors make more sense - 1) people centered development 2) nationalist development
-# So I am going to extract factor scores and bind them to the dataset
-
-ecopolallben_scores <- psych::factor.scores(ecopolallben, ecopolallben2.fa)
-
-# The factor scores will be stored in the scores element of the returned list
-scores2 <- ecopolallben_scores$scores
-
-#binding factor scores to the dataset
-
-fascale_scoresben <- cbind(Kahan_Kscoresben, scores2) %>%
-  rename(Pdevelop = MR1)%>%
-  rename(Ndevelop = MR2) #%>%
-  #dplyr::select(!starts_with(c("K_","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR")))
-
-mbennuclear <- lm(Ben_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State+ KahanS + KahanH + Pdevelop + Ndevelop , data = fascale_scoresben)
-# Print model summary
-#summary(mbennuclear)
-
-```
-
-\newpage
-
-# Appendix: Characteristics of the Sample
-
-The following graph shows that distribution of different demographic variables in our sample of 2,160 from the combined dataset from both surveys.
-The percentages are rounded off to whole numbers.
-
-```{r, echo=FALSE}
-
-library(dplyr)
-library(tidyr)
-
-sampledemos <- joineddf1 %>% 
-  dplyr::select("State", "Language", "age", "urban_rural", "gender", "caste" ,"religion") %>%
-              mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
-              mutate_all(~ifelse(. == "OBC", "Other Backward Classes (OBC)", .))%>%
-              mutate_all(~ifelse(. == "SC", "Scheduled caste (SC)", .))%>%
-              mutate_all(~ifelse(. == "ST", "Scheduled tribe (ST)", .))%>%
-              mutate_all(~ifelse(. == "MAR", "Marathi", .))%>%
-              mutate_all(~ifelse(. == "TA", "Tamil", .)) %>%
-              mutate_all(~ifelse(. == "EN", "English", .))%>%
-              mutate_all(~ifelse(. == "BN", "Bengali", .))%>%
-              mutate_all(~ifelse(. == "MAR", "Marathi", .))%>%
-              mutate_all(~ifelse(. == "HI", "Hindi", .))%>%
-              na.omit()
-
-#changing factor levels for each variable from high to low n
-
-sampledemos$State <- factor(sampledemos$State, levels = c("Maharashtra","Rajasthan", "West Bengal" , "Tamil Nadu", "Uttar Pradesh"))
-sampledemos$Language <- factor(sampledemos$Language, levels = c("Hindi","Marathi","Bengali","Tamil", "English"))
-sampledemos$age <- factor(sampledemos$age, levels = c( "18-24 years old" ,  "25-34 years old","35-44 years old", "45-54 years old", "55-64 years old","65-74 years old","75 years or older"  ))
-sampledemos$urban_rural <- factor(sampledemos$urban_rural, levels = c("Rural","Urban"))
-sampledemos$gender <- factor(sampledemos$gender, levels = c("Male","Female"))
-sampledemos$caste <- factor(sampledemos$caste, levels = c("Scheduled tribe (ST)", "Scheduled caste (SC)", "Other Backward Classes (OBC)", "General","Brahmin","Rather not say/Don't know"))
-sampledemos$religion <- factor(sampledemos$religion, levels = c("Hinduism", "Islam", "Christanity","Buddhism","Agnostism/ Atheism","Other (Please mention)"))
-
-```
-
-```{r, echo=FALSE, fig.width=11, fig.height=14, out.width='80%', out.height='80%'}
-
-# Loading the required libraries
-library(tidyverse)
-library(gridExtra)
-library(scales)
-
-# Function to create bar plot
-create_bar_plot <- function(data, variable_name, palette_name) {
-  factor_levels <- levels(sampledemos[[variable_name]])
-  data %>%
-    filter(Variable == variable_name) %>%
-    mutate(Category = factor(Category, levels = factor_levels)) %>%
-    ggplot(aes(y = "", x = Percentage, fill = Category)) +
-    geom_bar(position = "fill", stat = "identity", width = 1) +
-    geom_text(aes(label = paste0(round(Percentage, 0), "%")), 
-              position =  position_fill(vjust = 0.5)) +
-    scale_x_continuous(labels = percent) +
-    labs(y = NULL, x = "Percentage", fill = variable_name) +
-    theme_classic() +
-    theme(axis.text.y = element_blank(), strip.text = element_text(size = 10), legend.position = "top") +
-    scale_fill_brewer(palette = palette_name)
-}
-
-# Gather data to long format and calculate counts and percentages
-df_barplot <- sampledemos %>%
-  gather(Variable, Category) %>%
-  group_by(Variable, Category) %>%
-  filter(!is.na(Category)) %>%
-  summarise(n = n()) %>%
-  mutate(Percentage = n / sum(n) * 100)
-
-# Create separate plots for each variable
-plot_state <- create_bar_plot(df_barplot, "State", "Spectral")
-plot_language <- create_bar_plot(df_barplot, "Language", "Paired")
-plot_age <- create_bar_plot(df_barplot, "age", "Set3")
-plot_urban_rural <- create_bar_plot(df_barplot, "urban_rural", "Dark2")
-plot_gender <- create_bar_plot(df_barplot, "gender", "Pastel1")
-plot_caste <- create_bar_plot(df_barplot, "caste", "Set1")
-plot_religion <- create_bar_plot(df_barplot, "religion", "Set2")
-
-# Combine the plots with spacing
-combined_plot <- gridExtra::arrangeGrob(plot_state, plot_language, plot_age, plot_urban_rural, plot_gender, plot_caste, plot_religion, ncol = 1, heights = c(1, 1, 1, 1, 1, 1, 1))
-
-# Print the combined plot
-grid::grid.newpage()
-grid::grid.draw(combined_plot)
-
-```
+# LMs by State
+
+```{r, echo=FALSE}
+
+fascale_scores
+
+fascale_scores2
+
+# make state wise dts
+
+# Uttar Pradesh
+UP<- fascale_scores %>%
+  filter(State == "Uttar Pradesh")
+
+Raj<- fascale_scores %>%
+  filter(State == "Rajasthan")
+
+TM<- fascale_scores %>%
+  filter(State == "Tamil Nadu")
+
+Mah<- fascale_scores %>%
+  filter(State == "Maharasthra")
+
+Bengal <- fascale_scores %>%
+  filter(State == "Bengal")
+
+# 3 linear models - 1) lm with demographic variables except age and State
+TM_demo <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban, data = TM)
+
+# 3) lm with kahan 
+TM1_kahan <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age  + KahanS + KahanH , data = TM)
+
+# 4) lm with ecopolvars 
+TM1_allscales <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + Pdevelop + Ndevelop + KahanS + KahanH , data = TM)
+
+TM1_ecopol <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age +  Pdevelop + Ndevelop,  data = TM)
+
+summary(TM1_ecopol)
+
+```
+
+```{r, echo=FALSE, results='asis'}
+library(stargazer)
+
+cat("\\begingroup")
+cat("\\setlength{\\tabcolsep}{1pt}")
+cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer(TM_demo, TM1_kahan, TM1_allscales, TM1_ecopol,
+          title = "Results from 2 linear regression models",
+          type = "latex"
+)
+cat("\\endgroup")
+
+```

### 2024-01-15 extra stuff/Significant_results.Rmd
commiting after a long time. oh god

---
title: "Kahan scale and Economic Political value scale"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    keep_tex: yes
  header-includes:
  - \usepackage{dcolumn}
  - \usepackage{array}
  keep_md: yes
---
```{r load packages, warning = FALSE, message = FALSE, echo=FALSE}
  knitr::opts_chunk$set(warning = FALSE, message = FALSE)

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(tidyr))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(lavaan))
suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(DT))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(psych)) 
```

```{r setup, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

moduletwo <- read_excel(here::here("thesis_surveydata/political_factors_complete.xlsx"))
module2 <- data.frame(moduletwo)
module2[module2 == "Rather not say/ Don't know"] <- "Rather not say/Don't know"

# loaded data set for module 2 eco -pol variables and removes the rows with question number and question text
```

```{r, eval =TRUE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
codedmodule2 <- module2 %>%

#remove row 1
  filter(!row_number() %in% c(1,2)) %>%

# replace risky likert scale with numbers
  mutate_at(vars(starts_with("Risky")), funs(case_when(. =="Not at all risky" ~ 1, 
                                                       . =="Slightly risky" ~ 2, 
                                                       . =="Moderately risky" ~ 3, 
                                                       . =="Very risky" ~ 4, 
                                                       . =="Extremely risky" ~ 5))) %>%

# replace beneficial likert scale with numbers  
  mutate_at(vars(starts_with("Ben")), funs(case_when(. =="Not at all beneficial" ~ 1,
                                                     . =="Slightly beneficial" ~ 2,
                                                     . =="Moderately beneficial" ~ 3,
                                                     . =="Very beneficial" ~ 4,
                                                     . =="Extremely beneficial" ~ 5 ))) %>%

# replace nuclear acceptance likert scale with numbers
  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                                        . == "Somewhat disagree" ~ 2,
                                                                        . == "Neither agree nor disagree" ~3,
                                                                        . == "Somewhat agree" ~ 4,
                                                                        . == "Strongly agree" ~ 5))) %>%

# code likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_I","K_H","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE", "DEV", "PROSPER", "RELY"))), funs(case_when(. == "Strongly disagree" ~ 1, 
               . == "Somewhat disagree" ~ 2,
               . == "Neither agree nor disagree" ~3,
               . == "Somewhat agree" ~ 4,
               . == "Strongly agree" ~ 5))) %>%

# reverse code for likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_S","K_E"))), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                               . == "Somewhat disagree" ~ 4,
                                                               . == "Neither agree nor disagree" ~3,
                                                               . == "Somewhat agree" ~ 2,
                                                               . == "Strongly agree" ~ 1))) %>%

# code eco-pol scale variables into numbers
  mutate_at(vars(SYSTEMDEMO,SYSTEMRELIGION,SYSTEMTECHNO,SYSTEMTOTAL,WEALTHLIM,MECHANISATION,DECISIONDECEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG), funs(case_when(. == "Strongly disagree" ~ 1, 
                        . == "Somewhat disagree" ~ 2,
                        . == "Neither agree nor disagree" ~3,
                        . == "Somewhat agree" ~ 4,
                        . == "Strongly agree" ~ 5))) %>%

# reverse code eco-pol scale variables into numbers 
 mutate_at(vars(DECISIONCEN, INDUSTRYSMALL, ECONOMYLOCAL, ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                                                                         . == "Somewhat disagree" ~ 4,
                                                                                                         . == "Neither agree nor disagree" ~3,
                                                                                                         . == "Somewhat agree" ~ 2,
                                                                                                         . == "Strongly agree" ~ 1))) %>%
  mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
  mutate_all(~ifelse(. == "West bengal", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "WEST BENGAL", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "Up", "Uttar Pradesh", .))%>%
  mutate_all(~ifelse(. == "Tamilnadu", "Tamil Nadu", .))%>%
  mutate_all(~ifelse(. == "UP", "Uttar Pradesh", .))

```

```{r, eval=TRUE, echo=FALSE}

moduleone <- read_excel(here::here("thesis_surveydata/livelihood_insecurity_complete.xlsx"))
module1 <- data.frame(moduleone)
# loaded data set for module 2 eco -pol variables and removes the rows with question number and question text
```

```{r, eval =TRUE, echo=FALSE}
#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
codedmodule1 <- module1 %>%

#remove row 1 and 2 
  filter(!row_number() %in% c(1,2)) %>%

# replace risky likert scale with numbers
  mutate_at(vars(starts_with("Risky")), funs(case_when(. =="Not at all risky" ~ 1, 
                                                       . =="Slightly risky" ~ 2, 
                                                       . =="Moderately risky" ~ 3, 
                                                       . =="Very risky" ~ 4, 
                                                       . =="Extremely risky" ~ 5))) %>%

# replace beneficial likert scale with numbers  
  mutate_at(vars(starts_with("Ben")), funs(case_when(. =="Not at all beneficial" ~ 1,
                                                     . =="Slightly beneficial" ~ 2,
                                                     . =="Moderately beneficial" ~ 3,
                                                     . =="Very beneficial" ~ 4,
                                                     . =="Extremely beneficial" ~ 5 ))) %>%

# replace nuclear acceptance likert scale with numbers
  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                                        . == "Somewhat disagree" ~ 2,
                                                                        . == "Neither agree nor disagree" ~3,
                                                                        . == "Somewhat agree" ~ 4,
                                                                        . == "Strongly agree" ~ 5)))

```

```{r, echo = FALSE}

suppressPackageStartupMessages(library(tidyselect))
# combine codedmodule1 and codedmodule2

numcol2 <- codedmodule2 %>% add_column(Respondent = 1:1099, .before = "Language") 
numcol1 <- codedmodule1 %>% add_column(Respondent = 1099:2160, .before = "Language")

joineddf <-  full_join(numcol2, numcol1, by = c("Respondent", "Language", "Survey_Date", "State", "Risky_Hydro", "Risky_Solar", "Risky_Wind", "Risky_Nuclear", "Risky_Coal", "Risky_Gas", "Risky_Oil", "Risky_INDHydro", "Risky_INDSolar", "Risky_INDWind", "Risky_INDBiogas", "Risky_INDDiesel", "Risky_INDKerosene", "Risky_INDFirewoodetc", "Risky_INDLPG", "Ben_Hydro", "Ben_Solar", "Ben_Wind", "Ben_Nuclear", "Ben_Coal", "Ben_Gas", "Ben_Oil", "Ben_INDHydro", "Ben_INDSolar", "Ben_INDWind", "Ben_INDDiesel", "Ben_INDBiogas", "Ben_INDFirewoodetc", "Ben_INDLPG", "Ben_INDKerosene", "N_accept", "N_reluctantlyaccept", "N_reject", "age", "urban_rural", "gender", "caste", "religion", "religiontext"))

numcolb <- module2 %>%   filter(!row_number() %in% c(1,2))%>% 
                        add_column(Respondent = 1:1099, .before = "Language") 
numcola <- module1 %>%   filter(!row_number() %in% c(1,2)) %>% 
                        add_column(Respondent = 1099:2160, .before = "Language")

uncodedjoineddf <- full_join(numcolb, numcola, by = c("Respondent", "Language", "Survey_Date", "State", "Risky_Hydro", "Risky_Solar", "Risky_Wind", "Risky_Nuclear", "Risky_Coal", "Risky_Gas", "Risky_Oil", "Risky_INDHydro", "Risky_INDSolar", "Risky_INDWind", "Risky_INDBiogas", "Risky_INDDiesel", "Risky_INDKerosene", "Risky_INDFirewoodetc", "Risky_INDLPG", "Ben_Hydro", "Ben_Solar", "Ben_Wind", "Ben_Nuclear", "Ben_Coal", "Ben_Gas", "Ben_Oil", "Ben_INDHydro", "Ben_INDSolar", "Ben_INDWind", "Ben_INDDiesel", "Ben_INDBiogas", "Ben_INDFirewoodetc", "Ben_INDLPG", "Ben_INDKerosene", "N_accept", "N_reluctantlyaccept", "N_reject", "age", "urban_rural", "gender", "caste", "religion", "religiontext")) %>%
  mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
  mutate_all(~ifelse(. == "West bengal", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "WEST BENGAL", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "Up", "Uttar Pradesh", .))%>%
  mutate_all(~ifelse(. == "Tamilnadu", "Tamil Nadu", .))%>%
  mutate_all(~ifelse(. == "UP", "Uttar Pradesh", .))

```

\newpage

# Characteristics of Sample

The following graph shows that distribution of different demographic variables in our sample of 2,160 from the combined dataset from both surveys.

```{r, echo=FALSE}

library(dplyr)
library(tidyr)

sampledemos <- joineddf %>% select("State", "Language", "age", "urban_rural", "gender", "caste" ,"religion") %>%
              mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
              mutate_all(~ifelse(. == "OBC", "Other Backward Classes (OBC)", .))%>%
              mutate_all(~ifelse(. == "SC", "Scheduled caste (SC)", .))%>%
              mutate_all(~ifelse(. == "ST", "Scheduled tribe (ST)", .))%>%
              mutate_all(~ifelse(. == "MAR", "Marathi", .))%>%
              mutate_all(~ifelse(. == "TA", "Tamil", .)) %>%
              mutate_all(~ifelse(. == "EN", "English", .))%>%
              mutate_all(~ifelse(. == "BN", "Bengali", .))%>%
              mutate_all(~ifelse(. == "MAR", "Marathi", .))%>%
              mutate_all(~ifelse(. == "HI", "Hindi", .))%>%
              na.omit()

#changing factor levels for each variable from high to low n

sampledemos$State <- factor(sampledemos$State, levels = c("Maharashtra","Rajasthan", "West Bengal" , "Tamil Nadu", "Uttar Pradesh"))
sampledemos$Language <- factor(sampledemos$Language, levels = c("Hindi","Marathi","Bengali","Tamil","English"))
sampledemos$age <- factor(sampledemos$age, levels = c( "18-24 years old" ,  "25-34 years old","35-44 years old", "45-54 years old", "55-64 years old","65-74 years old","75 years or older"  ))
sampledemos$urban_rural <- factor(sampledemos$urban_rural, levels = c("Rural","Urban"))
sampledemos$gender <- factor(sampledemos$gender, levels = c("Male","Female","Transgender/Transitioning","Rather not say"))
sampledemos$caste <- factor(sampledemos$caste, levels = c("Scheduled tribe (ST)", "Scheduled caste (SC)", "Other Backward Classes (OBC)", "General","Brahmin","Rather not say/Don't know"))
sampledemos$religion <- factor(sampledemos$religion, levels = c("Hinduism", "Islam", "Christanity","Buddhism" , "Sikhism", "Jainism","Agnostism/ Atheism","Other (Please mention)"))

```

```{r, echo=FALSE, fig.width=11, fig.height=14, out.width='70%', out.height='70%'}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(forcats)

# Function to create bar plot
create_bar_plot <- function(data, variable_name) {
  data %>%
    filter(Variable == variable_name) %>%
    ggplot(aes(y = "", x = Percentage, fill = Category)) +
    geom_bar(position = "fill", stat = "identity", width = 1) +
    geom_text(aes(label = paste0(round(Percentage, 0), "%")), 
              position = position_fill(vjust = 0.5)) +
    scale_x_continuous(labels = scales::percent) +
    labs(y = NULL, x = "Percentage", fill = variable_name) +
    theme_classic() +
    theme(axis.text.y = element_blank(), strip.text = element_text(size = 8),  legend.position = "bottom")+
    scale_fill_brewer(palette = "Spectral")
}

# Gather data to long format and calculate counts and percentages
df_barplot <- sampledemos %>%
  gather(Variable, Category) %>%
  group_by(Variable, Category) %>%
  filter(!is.na(Category)) %>%
  summarise(n = n()) %>%
  mutate(Percentage = n / sum(n) * 100)

# Create separate plots for each variable
plot_state <- create_bar_plot(df_barplot, "State")
plot_language <- create_bar_plot(df_barplot, "Language")
plot_age <- create_bar_plot(df_barplot, "age")
plot_urban_rural <- create_bar_plot(df_barplot, "urban_rural")
plot_gender <- create_bar_plot(df_barplot, "gender")
plot_caste <- create_bar_plot(df_barplot, "caste")
plot_religion <- create_bar_plot(df_barplot, "religion")

# Combine the plots with spacing
combined_plot <- gridExtra::arrangeGrob(plot_state, plot_language, plot_age, plot_urban_rural, plot_gender, plot_caste, plot_religion, ncol = 1, heights = c(1, 1, 1, 1, 1, 1, 1))

# Print the combined plot
grid::grid.newpage()
grid::grid.draw(combined_plot)

# TO DO ---- add population distributions here.

```

\newpage

# State wise perceived risk and perceived benefit

## Centrally managed energy technologies (n= 2160)
The percentages are rounded off to whole numbers.

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
# Q1: how much is the awareness of energy technologies in India ? How does it relate to state specific data ? 
# summary of NA results from the combined sample of 2000 responses (simple percentage bar graphs)
# part 1- how much is the awareness of energy technologies in India -

#plotting perceived risk from different technologies including rather not say don't know
colorsequence<- c("#8C4646","#D9695F","#F2A679","#F2D091","#5D8C7B","#808080")

#following is the data frame for making the barplot 
df_barplot <- uncodedjoineddf %>%
  dplyr::select(starts_with("RISKY"))%>%
  gather(Technology, Perceived_Risk, Risky_Hydro:Risky_INDLPG, factor_key = TRUE)%>%
  separate(Technology, c("Risky", "Technology"), extra = "merge", fill = "left")%>%
  dplyr::select(-Risky) %>% 
  group_by(Technology, Perceived_Risk) %>%
  dplyr::summarise(n=n())

#following data frame gives us percentage for each response 
df_barplot_percent<- df_barplot%>%
  group_by(Technology) %>%
  mutate(Percentage = round(n/sum(n)*100, 0)) %>%
  ungroup()

#plotting perceived benefit from different technologies including rather not say don't know

df_barplotben <- uncodedjoineddf %>%
  dplyr::select(starts_with("Ben"))%>%
  gather(Technology, Perceived_Benefit, Ben_Hydro:Ben_INDKerosene, factor_key = TRUE)%>%
  separate(Technology, c("Ben", "Technology"), extra = "merge", fill = "left")%>%
  dplyr::select(-Ben) %>% 
  group_by(Technology, Perceived_Benefit) %>%
  dplyr::summarise(n=n())

df_barplotben_percent<- df_barplotben%>%
  group_by(Technology) %>%
  mutate(Percentage = round(n/sum(n)*100, 0)) %>%
  ungroup()

#bar plot for likert responses perceived risk - centrally owned technologies 
df_barplot %>% ggplot(aes(fill= fct_rev(factor(Perceived_Risk, levels=c("Extremely risky", "Very risky","Moderately risky","Slightly risky","Not at all risky","Rather not say/Don't know"))), y=n , x=Technology)) + 
  geom_bar(position="fill",stat="identity")+
  geom_text(data = df_barplot_percent, aes(label=paste0(Percentage, "%"), y=n), position = position_fill(vjust=0.5), size=3) +
  scale_x_discrete(limits = c("Solar", "Wind" ,"Hydro", "Oil", "Coal","Gas", "Nuclear"))+
  scale_fill_manual("legend", values = c("Extremely risky" = "#8C4646", "Very risky" = "#D9695F", "Moderately risky" = "#F2A679", "Slightly risky" = "#F2D091","Not at all risky" = "#5D8C7B", "Rather not say/Don't know" = "grey94"))+
  labs( y = "Perceived Risk", x ="Centrally Managed Energy Technologies")+
  theme_classic()

#perceived benefit centrally owned technologies

df_barplotben %>% ggplot(aes(fill= factor(Perceived_Benefit, levels=c("Rather not say/Don't know","Not at all beneficial","Slightly beneficial","Moderately beneficial","Very beneficial", "Extremely beneficial")), y=n , x=Technology)) + 
  geom_bar(position="fill",stat="identity")+
   geom_text(data = df_barplotben_percent, aes(label=paste0(Percentage, "%"), y=n), position = position_fill(vjust=0.5), size=3) +
  scale_fill_manual("legend", values = c("Rather not say/Don't know" = "grey94" ,"Not at all beneficial" = "orange","Slightly beneficial"="yellow" ,"Moderately beneficial" = "palegreen","Very beneficial"= "green3", "Extremely beneficial"= "green4"))+
  scale_x_discrete(limits = c("Solar", "Wind", "Hydro", "Oil", "Coal","Gas","Nuclear"))+
  labs( y = "Perceived Benefit", x ="Centrally Managed Energy Technologies")+
  theme_classic()

```

\newpage
## Individually/Community owned energy technologies (n= 2160)
The percentages are rounded off to whole numbers.

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

#bar plot for likert responses perceived risk - individually owned technologies 
df_barplot %>% ggplot(aes(fill= fct_rev(factor(Perceived_Risk, levels=c("Extremely risky", "Very risky","Moderately risky","Slightly risky","Not at all risky","Rather not say/Don't know"))), y=n , x=Technology)) + 
  geom_bar(position="fill", stat = "identity")+
  geom_text(data = df_barplot_percent, aes(label=paste0(Percentage, "%"), y=n), position = position_fill(vjust=0.5), size=3) +
  scale_x_discrete(limits = c("INDSolar", "INDFirewoodetc","INDWind", "INDHydro", "INDDiesel" , "INDBiogas","INDKerosene", "INDLPG"))+
  scale_fill_manual("legend", values = c("Extremely risky" = "#8C4646", "Very risky" = "#D9695F", "Moderately risky" = "#F2A679", "Slightly risky" = "#F2D091","Not at all risky" = "#5D8C7B", "Rather not say/Don't know" = "grey94"))+
   labs( y = "Perceived Risk", x ="Individually Owned Energy Technologies")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

#perceived benefit individually owned technologies

df_barplotben %>% ggplot(aes(fill= factor(Perceived_Benefit, levels=c("Rather not say/Don't know","Not at all beneficial","Slightly beneficial","Moderately beneficial","Very beneficial", "Extremely beneficial")), y=n , x=Technology)) + 
  geom_bar(position="fill",stat="identity")+
   geom_text(data = df_barplotben_percent, aes(label=paste0(Percentage, "%"), y=n), position = position_fill(vjust=0.5), size=3) +
  scale_fill_manual("legend", values = c("Rather not say/Don't know" = "grey94" ,"Not at all beneficial" = "orange","Slightly beneficial"="yellow" ,"Moderately beneficial" = "palegreen","Very beneficial"= "green3", "Extremely beneficial"= "green4"))+
  scale_x_discrete(limits = c( "INDSolar", "INDFirewoodetc" , "INDLPG",  "INDWind", "INDHydro", "INDDiesel" , "INDBiogas","INDKerosene"))+
  labs( y = "Perceived Benefit", x ="Individually Owned Energy Technologies")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

\newpage
# State Specific Differences.

We see huge differences for perceived risk and perceived benefit for each technology from state to state. These graphs explore that. 
The number of respondents from each state are also reported below.

## Perceived risk by State

```{r, echo=FALSE, fig.width=11, fig.height=14, out.width='80%', out.height='80%'}

# part 2: state specific data on perceived risk
state_risk <- uncodedjoineddf %>%
    dplyr::select(starts_with(c("RISKY", "State")))%>%
    gather(Technology, Perceived_Risk, Risky_Hydro:Risky_INDLPG, factor_key = TRUE)%>%
    separate(Technology, c("Risky", "Technology"), extra = "merge", fill = "left")%>%
    dplyr::select(-Risky) %>% 
    group_by(State, Technology, Perceived_Risk) %>%
    dplyr::summarise(n=n())

count<- uncodedjoineddf %>%
  dplyr::select(starts_with(c("RISKY", "State")))%>%
   group_by(State) %>%
  dplyr::summarise(n=n())

 state_risk_percent <- state_risk %>%
    group_by(Technology, State) %>%
    mutate(Percentage = round(n/sum(n)*100, 0)) %>%
    ungroup()

 # Create a named vector with the number of respondents for each state
respondents_per_state <- c("Maharashtra" = 653, "Rajasthan" = 677, "Tamil Nadu" = 320, "Uttar Pradesh" = 125, "West Bengal" = 386)

respondents_per_state

state_risk %>% ggplot(aes(fill= fct_rev(factor(Perceived_Risk, levels=c("Extremely risky", "Very risky","Moderately risky","Slightly risky","Not at all risky","Rather not say/Don't know"))), y=n , x=Technology)) + 
    geom_bar(position="fill",stat="identity")+
     geom_text(data = state_risk_percent, aes(label=paste0(Percentage, "%"), y=n), position = position_fill(vjust=0.5), size=5) +
    scale_x_discrete(limits = c("Solar", "Wind" ,"Hydro", "Oil", "Coal","Gas", "Nuclear"))+
    scale_fill_manual("legend", values = c("Extremely risky" = "#8C4646", "Very risky" = "#D9695F", "Moderately risky" = "#F2A679", "Slightly risky" = "#F2D091","Not at all risky" = "#5D8C7B", "Rather not say/Don't know" = "grey94"))+
    theme_classic()+ 
    facet_wrap(~ State, ncol = 2)+
    labs(x = "mean perceived risk", y = "energy technologies")+
    theme(axis.text.x = element_text(angle = 45, hjust = 1))+
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size=12),  # Increase x-axis text size
        axis.text.y = element_text(size=12),  # Increase y-axis text size
        strip.text = element_text(size=12))  # Increase facet label text size

```

\newpage

## Perceived Benefit by State

```{r, echo=FALSE, fig.width=12, fig.height=15, out.width='100%', out.height='100%'}
# part 2: state specific data on perceived benefit

state_ben <- uncodedjoineddf %>%
  select(starts_with(c("Ben", "State")))%>%
  gather(Technology, Perceived_Benefit, Ben_Hydro:Ben_INDKerosene, factor_key = TRUE)%>%
  separate(Technology, c("Ben", "Technology"), extra = "merge", fill = "left")%>%
  select(-Ben) %>% 
  group_by(State, Technology, Perceived_Benefit) %>%
  dplyr::summarise(n=n())

countben<- uncodedjoineddf %>%
  dplyr::select(starts_with(c("Ben", "State")))%>%
   group_by(State) %>%
  dplyr::summarise(n=n())

 # Create a named vector with the number of respondents for each state
respondents_per_state <- c("Maharashtra" = 653, "Rajasthan" = 677, "Tamil Nadu" = 320, "Uttar Pradesh" = 125, "West Bengal" = 386)

respondents_per_state

# Calculate percentages in each group
state_ben_percent <- state_ben %>%
  group_by(Technology, State) %>%
  mutate(Percentage = round(n/sum(n)*100, 0)) %>%
  ungroup()

#perceived benefit centrally owned technologies by state
state_ben %>% ggplot(aes(fill= factor(Perceived_Benefit, levels=c("Rather not say/Don't know","Not at all beneficial","Slightly beneficial","Moderately beneficial","Very beneficial", "Extremely beneficial")), y=n , x=Technology)) + 
  geom_bar(position="fill", stat = "identity")+
  geom_text(data = state_ben_percent, aes(label=paste0(Percentage, "%"), y=n), position = position_fill(vjust=0.5), size=5) +
  scale_fill_manual("legend", values = c("Rather not say/Don't know" = "grey94" ,"Not at all beneficial" = "orange","Slightly beneficial"="yellow" ,"Moderately beneficial" = "palegreen","Very beneficial"= "green3", "Extremely beneficial"= "green4"))+
  scale_x_discrete(limits = c("Solar", "Wind", "Hydro", "Oil", "Coal","Gas","Nuclear"))+
  theme_classic()+
  facet_wrap(~ State, ncol = 2)+
  labs(x = "mean perceived benefit", y = "energy technologies")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size=12), 
        axis.text.y = element_text(size=12), 
        strip.text = element_text(size=12))

```
\newpage

# How do perception of risk and perception of benefit compare with each other?

  Mean Values are presented in the graphs below

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
# Q4: How do perception of risk and perception of benefit compare with each other?

# what is this comparison telling us ?

# summary statistics for risks from different energy sources
library(tidyverse)

# Filter variables of interest
joineddf_subset <- joineddf %>%
  dplyr::select(!starts_with(c("Ben_IND", "Risky_IND")))%>%
  select(starts_with("Risky"), 
         starts_with("Ben"))

# Melt the data frame to long format
long_format <- joineddf_subset %>% 
  pivot_longer(everything(), names_to = "technology", values_to = "value") %>%
  mutate(risk_or_benefit = if_else(str_detect(technology, "Risky"), "risk", "benefit"),
         technology = str_replace(technology, "Risky_|Ben_", ""))

# Calculate mean and sd for each technology and category (risk or benefit)
summary_df <- long_format %>%
  group_by(technology, risk_or_benefit) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            sd = sd(value, na.rm = TRUE),
            .groups = "drop")

# Order technologies by mean risk
order_risk <- summary_df %>% 
  filter(risk_or_benefit == "risk") %>%
  arrange(mean) %>% 
  pull(technology)

# Change the levels of factor 'technology'
summary_df$technology <- factor(summary_df$technology, levels = order_risk)

# Plotting the data
ggplot(summary_df, aes(x = technology, y = mean, fill = risk_or_benefit)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = mean - sd, ymax = mean + sd), width = 0.3, position = position_dodge(0.9)) +
  ylim(0, 5) +
  scale_fill_manual("legend", 
                    values = c("benefit" = "palegreen3", "risk" = "firebrick2"), 
                    labels = c("benefit" = "Perceived Benefit", "risk" = "Perceived Risk")) +
  labs(y = "Mean Values", x = "Energy Technologies", fill = "Perceived") +
  ggtitle("Perceived risk and benefit from centrally managed energy technologies") +
  coord_flip()

# add a star in front of all bars to show these differences are significant at 0.05 , also replace sd with standard error ()
```

\newpage

# T-tests

## Pairwise T-test on mean perceived risk and benefit from energy technologies

Q - How are the perceptions of the risk of producing energy from nuclear fission different from that of other conventional sources of energy like coal or hydro power in India?
H : Nuclear energy will be perceived as riskier than other sources of energy (coal or hydro) in India like in the west.

The p values from a pairwise t test are reported below 
The red and green pairs indicate that there is a statistically significant difference between the means of the two groups. 
White and grey indicate - no differences between the means of the two groups.

```{r, echo = FALSE, fig.width=14, fig.height=6}
#Q2 :How are the perceptions of the risk of producing energy from nuclear fission different from that of other conventional sources of energy like coal or hydro power in India?
#H : Nuclear energy will be perceived as riskier than other sources of energy (coal or hydro) in India like in the west.

perceivedriskc <-joineddf %>% select("Risky_Solar", "Risky_Hydro", "Risky_Wind", "Risky_Nuclear", "Risky_Coal", "Risky_Gas", "Risky_Oil") %>%
  gather(key = "technology", value = "perceived_risk") %>% 
  mutate(technology = gsub("Risky_", "", technology)) %>%
  na.omit()

result_ttest <- pairwise.t.test(perceivedriskc$perceived_risk, perceivedriskc$technology, p.adjust.method = "BH")

# visualising the pairwaise t test results. the non significant pairs are grey

tidy_result_ttest <- broom::tidy(result_ttest)

heatmap1 <- ggplot(tidy_result_ttest, aes(x = group1, y = group2, fill = p.value)) + 
  geom_tile(color = "white") + 
  scale_fill_gradient2(low = "firebrick2", high = "white", midpoint = 0.025, 
                       limits = c(0, 0.05), space = "Lab", 
                       name = "P-value") + 
  theme_classic() + 
  labs(x = "Technology 1", y = "Technology 2") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

#Question- Why there is significant difference statistically - if the medians are the same in the boxplot.
#Q3: How do perceptions of benefit from nuclear energy compare with other source of energy?

# H : benefits from all energy technologies will be similar 
# include regression, heat maps, bar graphs? - decide which ones are good to include

perceivedbenefitc <-joineddf %>% select("Ben_Solar", "Ben_Hydro", "Ben_Wind", "Ben_Nuclear", "Ben_Coal", "Ben_Gas", "Ben_Oil") %>%
  gather(key = "technology", value = "perceived_benefit") %>% 
  mutate(technology = gsub("Ben_", "", technology)) %>%
  na.omit()

result_ttestben <- pairwise.t.test(perceivedbenefitc$perceived_benefit, perceivedbenefitc$technology, p.adjust.method = "BH")

# visualising the pairwaise t test results. the non significant pairs are grey

tidy_resultbc <- broom::tidy(result_ttestben)

library(ggplot2)
heatmap2 <- ggplot(tidy_resultbc, aes(x = group1, y = group2, fill = p.value)) + 
  geom_tile(color = "white") + 
  scale_fill_gradient2(low = "palegreen3", high = "white", midpoint = 0.025, 
                       limits = c(0, 0.05), space = "Lab", 
                       name = "P-value") + 
  theme_classic() + 
  labs(x = "Technology 1", y = "Technology 2") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

grid.arrange(heatmap1, heatmap2, ncol=2)

```

## Results from Paired t test used to compare the mean perceived risk and mean perceived benefit from each technology. 
Null hypothesis (H0): The mean difference between perceived risk and perceived benefit from each technology is zero.

All p values are less than 0.05 suggesting that the differences observed above in the graph are statistically significant.

```{r, echo=FALSE}

# Convert character columns to factors
long_format$technology <- factor(long_format$technology)
long_format$risk_or_benefit <- factor(long_format$risk_or_benefit)

# Perform the t- Test for each technology
p_values <- long_format %>%
  split(.$technology) %>%
  lapply(function(x) t.test(x$value[x$risk_or_benefit == "risk"], x$value[x$risk_or_benefit == "benefit"], paired = TRUE)) %>%
  lapply(function(x) x$p.value)

p_values

```

# Perceived Benefit - Perceived Risk

```{r, echo = FALSE}

# combining risk and benefit from each energy technology

acceptance <- joineddf_subset %>%
  na.omit()%>%
  mutate(Nuclear = Ben_Nuclear - Risky_Nuclear,
         Hyrdo = Ben_Hydro - Risky_Hydro,
         Wind = Ben_Wind - Risky_Wind,
         Solar = Ben_Solar - Risky_Solar,
         Coal = Ben_Coal - Risky_Coal,
         Gas = Ben_Gas - Risky_Gas,
         Oil = Ben_Oil - Risky_Oil)%>%
  select(-starts_with(c("Risky", "Ben")))

str(acceptance)

# Compute the mean of each column
mean_acceptance <- data.frame(col = names(acceptance), mean_val = sapply(acceptance, mean))

# Compute standard error (not deviation)(divided by root of n)
sem <- function(x) sqrt(var(x, na.rm = TRUE) / length(na.omit(x)))
sem_acceptance <- data.frame(col = names(acceptance), sem_val = sapply(acceptance, sem))

mean_acceptance <- merge(mean_acceptance, sem_acceptance, by = "col")

# Plot
ggplot(mean_acceptance, aes(x = col, y = mean_val, fill = ifelse(mean_val >= 0, 'Above 0', 'Below 0'))) + 
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = mean_val - sem_val, ymax = mean_val + sem_val), width = 0.2) +
  geom_text(aes(label = round(mean_val, 2)), vjust = -0.9) +
  scale_fill_manual(values = c('Above 0' = 'palegreen3', 'Below 0' = 'firebrick2')) +
  labs(fill = "Legend") +
  xlab("Energy Technologies") +
  ylab("Mean Value") +
  ggtitle("Benefit- Risk for Each Energy Technology") +
  theme_minimal()+
  ylim(-0.5, 1.75)

```

\newpage

# Factor Analysis: Kahan Scale

Factor Levels for demographic variables - State, age, gender, urban_rural, caste and religion
First level in each of the variables is the reference for linear regression models.

```{r, echo = FALSE}
# Q5: Is there a parallel to white-male effect in India ? Upper-caste Hindu male effect? 
# regression with categorical variable Upper-cast Hindu male and others - look into how Kahan did it

# 1- running linear regression for demographic variable - state, age, gender, urban_rural, caste and religion

codedmodule2$State <- as.factor(codedmodule2$State)
levels(codedmodule2$State)

codedmodule2$age <- as.factor(codedmodule2$age)
levels(codedmodule2$age)

codedmodule2$gender <- as.factor(codedmodule2$gender)
levels(codedmodule2$gender)

codedmodule2$Urban <- as.factor(codedmodule2$urban_rural)
levels(codedmodule2$Urban)

joineddf$Urban <- as.factor(joineddf$urban_rural)
levels(joineddf$Urban)

codedmodule2$caste <- as.factor(codedmodule2$caste)
levels(codedmodule2$caste)

codedmodule2$religion <- as.factor(codedmodule2$religion)
levels(codedmodule2$religion)

# Pre-calculate the counts
count_data <- codedmodule2 %>%
  group_by(age, Risky_Nuclear) %>%
  summarize(count = n())

# Plot using the count column
#ggplot(count_data, aes(x = age, y = Risky_Nuclear, size = count)) +
  #labs(y = "Age categories", x = "perceived risk from nuclear energy") +
  #geom_point()

# # Convert `caste` into binary variable 'upper' (1) vs 'non-upper' (0)
joineddf$Uppercaste <- ifelse(joineddf$caste %in% c('Brahmin', 'General'), 1, 0)

# Convert `gender` into binary variable 'male' (1) vs 'female' (0)
joineddf$Male <- ifelse(joineddf$gender == 'Male', 1, 0)

# Convert `religion` into binary variable 'Hinduism' (1) vs 'Non-Hinduism' (0)
joineddf$Hindu <- ifelse(joineddf$religion == 'Hinduism', 1, 0)

# # Convert `caste` into binary variable 'upper' (1) vs 'non-upper' (0)
codedmodule2$Uppercaste <- ifelse(codedmodule2$caste %in% c('Brahmin', 'General'), 1, 0)

# Convert `gender` into binary variable 'male' (1) vs 'female' (0)
codedmodule2$Male <- ifelse(codedmodule2$gender == 'Male', 1, 0)

# Convert `religion` into binary variable 'Hinduism' (1) vs 'Non-Hinduism' (0)
codedmodule2$Hindu <- ifelse(codedmodule2$religion == 'Hinduism', 1, 0)

# most of these results indicate that there is no significant white male effect or upper caste male effect for risk perception from nuclear energy in India. 
# the coefficients are very small and so is the r squared - rsquared is minimal.

```

Before fitting a linear regression model, I conducted factor analysis on the Kahan scale and the newly developed economic-political value scale. The results from the Factor Analysis are below.

The Individualism items (indicated by K_I) were bringing down the cronbach's alpha values in the Kahan scale. The Alpha for INdividualism- Communitarian scale was 0.49. After removing the Individualism items (K_I) the alpha for this factor was 0.71. The reasons for this could be that the individualism items are not well adapted to the Indian population.

I conducted confirmatory factor analysis (CFA) for the  Kahan scale (see Appendix 1) since this a well used scale with theoretical basis for factor distinctions and also previous studies have used this scale.

```{r, echo=FALSE}
# Q6: Does the Kahan scale explain perception of risk from nuclear energy and other DVs ?

# we conducted fa on the kahan scale 
# CFA for Kahan scale. We shouldn't do FA here since this a well used scale with theoretical basis for factor distinctions and also previous studies using the same scale

library(lavaan)

fascales <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_","Risky_Nuclear","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%
  na.omit()

Kahan_fas <- '
  KahanS =~ K_SHARM + K_SLIMCHOI + K_SPROTECT 
  KahanH =~ K_HEQUAL+ K_ERADEQ1 + K_EWEALTH + K_ERADEQ2
'

# Run CFA
Kahan_cfa <- cfa(Kahan_fas, data = fascales, std.lv = TRUE)

# Print the summary of the CFA results, including fit measures
summary(Kahan_cfa, fit.measure= TRUE, standardized = TRUE)

# RMSEA - between 0.05 and 0.08 (reasonable fit), less than 0.05 close fit and greater than 0.10 is poor fit 
# CFI - greater than 0.90 or 0.95 indicates good fit
#TFI - CFI>TFI >0.90 - indicates good fit
#pvalue should be greater than 0.05 p > 0.0.5

# after having removed a few variables that had very low loading, the model is now a good fit, we have two latent variables - Hierarchy- egalitarian and Communitarian. Again we see that individualistic variables just don't fit here.

# creating table of factor scores

Kahan_scores <- predict(Kahan_cfa, newdata = fascales)

Kahan_Kscores <- cbind(fascales, Kahan_scores)

## RMSEA is still pretty big.

```

RMSEA - between 0.05 and 0.08 (reasonable fit), less than 0.05 close fit and greater than 0.10 is poor fit 
CFI - greater than 0.90 or 0.95 indicates good fit
TFI - CFI>TFI >0.90 - indicates good fit

After having removed a few variables that had very low loading, the model is now a good fit. Some of the Individualistic variables just don't fit. Final scale variables:

KahanS(Individualism - Communitarian) = K_SHARM + K_SLIMCHOI + K_SPROTECT 
KahanH(Hierarchy- Egalitarian) =K_HEQUAL+ K_ERADEQ1 + K_EWEALTH + K_ERADEQ2

The Cronabch alpha for this final scale was 0.75.

\newpage

# Factor Analysis: New Eco-political Scale

Then I conducted Factor Analysis on all eco-political values(see Appendix 2). The Cronbach's alpha for the scale was high at 0.785 (almost 0.8).

The scale reduced to two factors which I named as 1) People Centered Development and 2) Nationalist Development.
The final scale with two factors include the following

**MR1 People Centered Development: Pdevelop**

HEALTHNUCLEAR	-  Nuclear energy poses a great risk to the health of people living around it.

BEAUTYNUCLEAR	-  Nuclear energy spoils the natural beauty of the landscape.

MECHANISATION	-  Rapid mechanization of work is taking away jobs from workers in this country.

INDUSTRYSMALL	-  Large corporations are destroying the local industries in India and benefiting only a handful of people.

DISPLACENUCLEAR- Nuclear energy is leading to displacement of people from their land.

POLLUTENUCLEAR-  Nuclear energy increases pollution of air/water/land.

OWNERREG-        Regardless of ownership, the government should pass strong regulations and implement them.

**MR2 Nationalist Development: Ndevelop**

DEVNUCLEAR	-  Nuclear energy pushes forward the country's development.

PRIDENUCLEAR-  I would be proud if my community used nuclear energy.

NPRIDENUCLEAR- Nuclear energy is a mark of pride for our nation.

PROSPERNUCLEAR-Nuclear energy brings economic prosperity to the surrounding regions.

INDUSTRYLARGE- Large scale industries are required for the development of the country that will benefit everyone.

The results of the factor analysis are below:

```{r, echo=FALSE}

ecopolall <- fascales %>%
        dplyr::select("WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR")

ecopolall_alpha <- psych::alpha(ecopolall, check.keys = TRUE)

summary(ecopolall_alpha)

# when we combine both the scales the alpha is high at 0.785 (almost 0.8)

# FA on all ecopol variables except systems of governance

ecopolall_cor <- cor(ecopolall)
PCA24 <- principal(ecopolall, nfactors = 24, rotate = "none") # no rotation to start with.

#PCA24$loadings

#fa.parallel(ecopolall_cor)

# this suggests 2 factors if we go by FA or 8 by PCA. let's try both and see how they look conceptually

ecopolall2.fa <- fa(ecopolall, nfactors = 2, rotate = "varimax")

print.psych(ecopolall2.fa, cut = 0.30, sort = TRUE)

#fa.diagram(ecopolall2.fa)

#cor(ecopolall)

# I don't know still doesn't make a lot of sense to me- the two factors make more sense - 1) people centered development 2) nationalist development

# So I am going to extract factor scores and bind them to the dataset

ecopolall_scores <- psych::factor.scores(ecopolall, ecopolall2.fa)

# The factor scores will be stored in the scores element of the returned list
scores1 <- ecopolall_scores$scores

#binding factor scores to the dataset

fascale_scores <- cbind(Kahan_Kscores, scores1) %>%
  rename(Pdevelop = MR1)%>%
  rename(Ndevelop = MR2) %>%
  select(!starts_with(c("K_","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR")))

# 3 linear models - 1) lm with demographic variables except age and State
m1_demo <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban, data = fascale_scores)
# Print model summary
summary(m1_demo)
plot(m1_demo)

# lm suggests there is no significant white male effect or upper caste male effect for risk perception from nuclear energy in India. 
# the coefficients are very small and so is the r squared - rsquared is minimal.

# 2) lm with all demographic variables
m2_demo<- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State, data = fascale_scores)
# Print model summary
summary(m2_demo)
plot(m2_demo)

# States and some age have some impact on y variable.

# 3) lm with kahan 
m1_kahan <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State + KahanS + KahanH , data = fascale_scores)
# Print model summary
summary(m1_kahan)
plot(m1_kahan)

# 4) lm with ecopolvars 
m1_allscales <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State+ KahanS + KahanH + Pdevelop + Ndevelop, data = fascale_scores)
# Print model summary
summary(m1_allscales)
plot(m1_allscales)

```
\newpage
# Nuclear Energy - Linear Regression models

## Linear Regression model with all demographic variables

```{r, echo=FALSE}

alldemos <- joineddf %>%
            select(Risky_Nuclear,Uppercaste, Male, Hindu, Urban, age, State)%>%
            na.omit()

alldemoslm1 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban, data = alldemos)
# Print model summary
#summary(alldemoslm1)
#plot(alldemoslm1)

# lm suggests there is no significant white male effect or upper caste male effect for risk perception from nuclear energy in India. 
# the coefficients are very small and so is the r squared - rsquared is minimal.

# 2) lm with all demographic variables
alldemoslm2<- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State, data = alldemos)
# Print model summary
#summary(alldemoslm2)
#plot(alldemoslm1)

```

```{r, echo=FALSE, results='asis'}
library(stargazer)

cat("\\begingroup")
cat("\\setlength{\\tabcolsep}{1pt}")
cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(alldemoslm1, alldemoslm2, 
          title = "Results from 2 linear regression models",
          type = "latex"
)
cat("\\endgroup")

```

# Linear Regression: 4 Models.

Then I ran 4 linear regression models adding more variables every time. The results of the linear regression models are below.

```{r, echo=FALSE, results='asis'}
library(stargazer)

cat("\\begingroup")
cat("\\setlength{\\tabcolsep}{1pt}")
cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(m1_demo, m2_demo, m1_kahan, m1_allscales, 
          title = "Results from 4 linear regression models",
          type = "latex"
)
cat("\\endgroup")

```

Key observations:

**1. Demographic effects:** The impact of demographic characteristics on the perceived risk from Nuclear Energy appears to be small. The adjusted R-squared of the first model, which includes only demographic variables, is 0.023, indicating that these variables explain just over 2% of the variance in perceived risk.

**2. Age effects:** In Model 2, where age groups are added, there is a distinct change in the perceived risk from nuclear energy as age increases. Interestingly, only the age group 65-74 shows a significant increase in perceived risk, compared to the reference age group (18-25 years).

**3. Gender effects:** In the initial model, being male is positively associated with higher perceived risk from nuclear energy. However, the significance of this association diminishes when age and state variables are included in the model, suggesting that the relationship between gender and perceived risk may be influenced by these factors.

**4. State effects:** Both exploratory visualizations and regression models strongly suggest that the respondents' state of residence significantly influences their perceived risk from nuclear energy. The comparison state is Maharashtra. The coefficients for the other states can be interpreted as the difference in perceived risk from each state compared to Maharashtra, holding all else constant.

**5. Kahan scale effects:** Among the Kahan scale variables, only the individualism factor is statistically significant in the third model. This suggests that individuals scoring high on the individualism scale perceive nuclear energy as less risky.

**6. Eco-political scale effects:** When we introduce the eco-political scale, the effect of the individualism factor from the Kahan scale loses its significance. This could suggest that the eco-political scale is capturing some aspect of the risk perception related to individualism. The two factors of the eco-political scale both have a statistically significant impact on the perceived risk, indicating that these eco-political beliefs play an important role in shaping risk perceptions.

\newpage

# Solar Energy - Linear Regression models

```{r, echo=FALSE}

salldemos <- joineddf %>%
            select(Risky_Solar,Uppercaste, Male, Hindu, Urban, age, State)%>%
            na.omit()

salldemoslm1 <- lm(Risky_Solar ~ Uppercaste + Male + Hindu + Urban, data = salldemos)
# Print model summary
summary(salldemoslm1)
#plot(alldemoslm1)

# lm suggests there is no significant white male effect or upper caste male effect for risk perception from nuclear energy in India. 
# the coefficients are very small and so is the r squared - rsquared is minimal.

# 2) lm with all demographic variables
salldemoslm2<- lm(Risky_Solar ~ Uppercaste + Male + Hindu + Urban + age + State, data = salldemos)
# Print model summary
summary(salldemoslm2)
#plot(alldemoslm1)

```

```{r, echo=FALSE, results='asis'}
library(stargazer)

#stargazer code for all demographic variable lms

cat("\\begingroup")
cat("\\setlength{\\tabcolsep}{1pt}")
cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(salldemoslm1, alldemoslm2, 
          title = "Results from 2 linear regression models",
          type = "latex"
)
cat("\\endgroup")

```

```{r, echo = FALSE}
# kahan scores for solar 
sfascales <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_","Risky_Solar","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACESOLAR",  "POLLUTESOLAR", "HEALTHSOLAR", "JOBSSOLAR", "BEAUTYSOLAR", "PRIDESOLAR", "NPRIDESOLAR", "DEVSOLAR", "PROSPERSOLAR", "RELYSOLAR", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%
  na.omit()

sKahan_fas <- '
  KahanS =~ K_SHARM + K_SLIMCHOI + K_SPROTECT 
  KahanH =~ K_HEQUAL+ K_ERADEQ1 + K_EWEALTH + K_ERADEQ2
'

# Run CFA
sKahan_cfa <- cfa(sKahan_fas, data = sfascales, std.lv = TRUE)

# Print the summary of the CFA results, including fit measures
#summary(sKahan_cfa, fit.measure= TRUE, standardized = TRUE)

# RMSEA - between 0.05 and 0.08 (reasonable fit), less than 0.05 close fit and greater than 0.10 is poor fit 
# CFI - greater than 0.90 or 0.95 indicates good fit
#TFI - CFI>TFI >0.90 - indicates good fit
#pvalue should be greater than 0.05 p > 0.0.5

# after having removed a few variables that had very low loading, the model is now a good fit, we have two latent variables - Hierarchy- egalitarian and Communitarian. Again we see that individualistic variables just don't fit here.

# creating table of factor scores

sKahan_scores <- predict(sKahan_cfa, newdata = sfascales)

sKahan_Kscores <- cbind(sfascales, sKahan_scores)

## RMSEA is still pretty big.

```

```{r}
secopolall <- sfascales %>%
        dplyr::select("WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACESOLAR",  "POLLUTESOLAR", "HEALTHSOLAR", "JOBSSOLAR", "BEAUTYSOLAR", "PRIDESOLAR", "NPRIDESOLAR", "DEVSOLAR", "PROSPERSOLAR", "RELYSOLAR")

secopolall_alpha <- psych::alpha(secopolall, check.keys = TRUE)

summary(secopolall_alpha)

# when we combine both the scales the alpha is high at 0.785 (almost 0.8)

# FA on all ecopol variables except systems of governance

secopolall_cor <- cor(secopolall)
PCA24 <- principal(secopolall, nfactors = 24, rotate = "none") # no rotation to start with.

#PCA24$loadings

#fa.parallel(ecopolall_cor)

# this suggests 2 factors if we go by FA or 8 by PCA. let's try both and see how they look conceptually

secopolall2.fa <- fa(secopolall, nfactors = 2, rotate = "varimax")

print.psych(secopolall2.fa, cut = 0.30, sort = TRUE)
```

# Regression with acceptance scale? - explore

\newpage

#   Perceived risk by Support for Democratic government

```{r, echo=FALSE}

# **Perceived risk by Support for Democratic government**

#The following is a list of statements about governance. How strongly do you agree or disagree with each of these statements? Do you strongly disagree(1), somewhat disagree(2), neither agree nor disagree(3), somewhat agree(4) or strongly agree(5)? - It is very important to have a democratic political system because it ensures that no individual leader has too much power.

govtrisk <- codedmodule2 %>%
  select( Risky_Hydro, Risky_Solar, Risky_Wind, Risky_Nuclear, Risky_Coal, Risky_Gas, Risky_Oil, SYSTEMDEMO, SYSTEMTECHNO, SYSTEMRELIGION, SYSTEMTOTAL)

govtrisk$grouped_demo <- ifelse(govtrisk$SYSTEMDEMO %in% c(1,2), "low", ifelse(govtrisk$SYSTEMDEMO %in% c(4,5), "high", NA))

demorisk2 <- govtrisk %>%
  group_by(grouped_demo) %>%
  filter(grouped_demo %in% c("low", "high")) %>%
  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd, Risky_Hydro_n, Risky_Solar_n, Risky_Wind_n, Risky_Nuclear_n, Risky_Coal_n, Risky_Gas_n, Risky_Oil_n) %>%
  dplyr::select(grouped_demo, technology, summary) %>%
  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
  separate(var, c("technology", "meansd")) %>%
  spread(meansd,summary) %>%
  select(-Risky) %>%
  arrange(grouped_demo)

data.frame(demorisk2)

demorisk2 <- demorisk2 %>%
  mutate(technology = reorder(technology, -mean))  # reorder based on -mean, to get high to low

d <- demorisk2 %>%
  group_by(technology) %>%
  ggplot(aes(x = technology, y= mean, group = grouped_demo))+
  geom_line(aes(colour = grouped_demo, line = grouped_demo)) +
  labs(y = "mean perceived risk", x = "energy technology", color = "Democratic Value") +
  ggtitle("Q:It is very important to have a democratic political system because\nit ensures that no individual leader has too much power.")

d
# High - agree and strongly agree, low - disagree and strongly disagree

```

```{r}
# logistic regression here fro democratic thing 
```

\newpage
# Appendix1

**Kahan et al (2007) scale**

Individualism - Communitarinism

- **K_IINTRFER**	The government interferes far too much in our everyday lives.
- **K_IPRIVACY**	The government should stop telling people how to live their lives.
- **K_IPROTECT**	It’s not the government’s business to try to protect people from themselves.
- **K_SHARM**	    Sometimes the government needs to make laws that keep people from hurting themselves.
- **K_SLIMCHOI**	The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.
- **K_SPROTECT**	The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.

Hierarchy -Egalitarianism

- **K_HEQUAL**	  We have gone too far in pushing equal rights in this country.
- **K_HREVDIS1**	Nowadays it seems like there is just as much discrimination against upper castes as there is against Dalits.
- **K_EDISCRIM**	Discrimination against minorities is still a very serious problem in our society.
- **K_ERADEQ1**	  We need to dramatically reduce inequalities between the rich and the poor.
- **K_EWEALTH**	  Our society would be better off if the distribution of wealth was more equal.
- **K_ERADEQ2**	  We need to dramatically reduce inequalities between men and women.

\newpage
# Appendix2

 **New Eco-pol values scale**

- **DISPLACENUCLER** Nuclear energy is leading to displacement of people from their land
- **BEAUTYNUCLEAR**	 Nuclear energy spoils the natural beauty of the landscape
- **POLLUTENUCLEAR** Nuclear energy increases pollution of air/water/land
- **HEALTHNUCLEAR**	 Nuclear energy poses a great risk to the health of people living around it
- **JOBSNUCLEAR**	   Nuclear energy will bring jobs to the local community
- **PRIDENUCLEAR**	 I would be proud if my community used nuclear energy
- **NPRIDENUCLEAR**	 Nuclear energy is a mark of pride for our nation
- **DEVNUCLEAR**	   Nuclear energy pushes forward the country's development
- **PROSPERNUCLEAR** Nuclear energy brings economic prosperity to the surrounding regions
- **RELYNUCLEAR**	   I don't like the idea that I have to rely on the government for electricity from nuclear energy

- **DECISIONDECEN**	 Local politicians shouldn't have to ask permission from the central government to implement policies
- **DECISIONCEN**	   Laws and policies would be implemented more smoothly if more power lay with the central government.
- **INDUSTRYLARGE**	 Large scale industries are required for the development of the country that will benefit everyone
- **ECONOMYLOCAL**	 India would be better off if foreign companies didn't come to here
- **DEVOVERENV**	   Economic growth and creating jobs should be prioritized over environmental protection
- **INDUSTRYSMALL**	 Large corporations are destroying the local industries in India and benefiting only a handful of people.
- **WEALTHLIM**	     A limit should be put to how much wealth a person can amass
- **ECONOMYGLOBAL**	 Foreign companies have led to a range of benefits for the Indian people and society
- **OWNERPVT**	     All businesses and industries should be owned privatel
- **OWNERPUB**	     The government should own most large businesses and industrie
- **ENVOVERDEV**	   Polluting industries that spoil the environment should be shut down even if it costs people their jo
- **OWNERREG**	     Regardless of ownership, the government should pass strong regulations and implement them
- **MECHANISATION**	 Rapid mechanization of work is taking away jobs from workers in this country
- **OWNERNOREG**	   There is too much red-tape and the government should not interfere with businesses and industries

```{r, echo=FALSE}
# Q7 : political values scale - factor analysis - reduce dimensions and then run regression -logistic regression 
# Using logistic regression for the SYSTEM prefixed variables.

#codedmodule2
#codedmodule2$SYSTEMDEMO <- as.factor(codedmodule2$SYSTEMDEMO)
#levels(codedmodule2$SYSTEMDEMO)

#codedmodule2$SYSTEMRELIGION <- as.factor(codedmodule2$SYSTEMRELIGION)
#levels(codedmodule2$SYSTEMRELIGION)

#codedmodule2$SYSTEMTOTAL <- as.factor(codedmodule2$SYSTEMTOTAL)
#levels(codedmodule2$SYSTEMTOTAL)

#codedmodule2$SYSTEMTECHNO <- as.factor(codedmodule2$SYSTEMTECHNO)
#levels(codedmodule2$SYSTEMTECHNO)

#codedmodule2$Risky_Nuclear <- as.factor(codedmodule2$Risky_Nuclear)
#levels(codedmodule2$Risky_Nuclear)

#fitrisky_nucleargm <- with(codedmodule2, clm(Risky_Nuclear ~ 1 + SYSTEMDEMO + SYSTEMRELIGION + SYSTEMTOTAL + SYSTEMTECHNO))

```

### 2024-01-15 extra stuff/Significant_results.tex
commiting after a long time. oh god

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\title{Kahan scale and Economic Political value scale}
\author{}
\date{\vspace{-2.5em}}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Kahan scale and Economic Political value scale},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\begin{document}
\maketitle

{
\setcounter{tocdepth}{2}
\tableofcontents
}
\newpage

\hypertarget{exploratory-data-analysis}{%
\section{Exploratory Data analysis}\label{exploratory-data-analysis}}

\textbf{Distributions for DVs} I started by exploring the distributions
of perceived risk across various energy technologies. Below are boxplot
and violin plot for the same. We see that these are not normal
distributions.

\includegraphics{Significant_results_files/figure-latex/unnamed-chunk-5-1.pdf}
\includegraphics{Significant_results_files/figure-latex/unnamed-chunk-5-2.pdf}

\newpage

\hypertarget{how-much-is-the-awareness-of-energy-technologies-in-india-how-does-it-relate-to-state-specific-data}{%
\section{How much is the awareness of energy technologies in India ? How
does it relate to state specific data
?}\label{how-much-is-the-awareness-of-energy-technologies-in-india-how-does-it-relate-to-state-specific-data}}

To answer this I simply plotted the risk and benefit responses in a bar
graph. This will reveal the Rather not say/Do not know part of the
responses as well.

The percentages are rounded off to whole numbers.

\includegraphics{Significant_results_files/figure-latex/unnamed-chunk-6-1.pdf}
\includegraphics{Significant_results_files/figure-latex/unnamed-chunk-6-2.pdf}

\includegraphics{Significant_results_files/figure-latex/unnamed-chunk-7-1.pdf}
\includegraphics{Significant_results_files/figure-latex/unnamed-chunk-7-2.pdf}

\newpage

\hypertarget{state-specific-perceived-risk-and-perceived-benefit-from-centrally-managed-energy-technologies.}{%
\section{State Specific perceived risk and perceived benefit from
Centrally Managed energy
technologies.}\label{state-specific-perceived-risk-and-perceived-benefit-from-centrally-managed-energy-technologies.}}

The percentage of Rather not say/Do not know differs for each technology
from state to state. This graph explores that. The number of respondents
from each state are also reported below.

\begin{verbatim}
##   Maharashtra     Rajasthan    Tamil Nadu Uttar Pradesh   West Bengal 
##           653           677           320           125           386
\end{verbatim}

\includegraphics[width=0.7\linewidth,height=0.7\textheight]{Significant_results_files/figure-latex/unnamed-chunk-8-1}

\newpage

\begin{verbatim}
##   Maharashtra     Rajasthan    Tamil Nadu Uttar Pradesh   West Bengal 
##           653           677           320           125           386
\end{verbatim}

\includegraphics[width=1\linewidth,height=1\textheight]{Significant_results_files/figure-latex/unnamed-chunk-9-1}

\newpage

\hypertarget{how-are-the-perceptions-of-the-risk-of-producing-energy-from-nuclear-fission-different-from-that-of-other-conventional-sources-of-energy-like-coal-or-hydro-power-in-india}{%
\section{How are the perceptions of the risk of producing energy from
nuclear fission different from that of other conventional sources of
energy like coal or hydro power in
India?}\label{how-are-the-perceptions-of-the-risk-of-producing-energy-from-nuclear-fission-different-from-that-of-other-conventional-sources-of-energy-like-coal-or-hydro-power-in-india}}

H : Nuclear energy will be perceived as riskier than other sources of
energy (coal or hydro) in India like in the west.

The box plot shows the differences in Median for perceived risk from all
energy technologies. Nuclear energy has the highest median. The pairwise
wilcox test confirms that these differences are statistically
significant.

The red pairs indicate that there is a statistically significant
difference between the medians of the two groups. White and grey
indicate - no differences between the medians of the two groups.

{[}Wilcox test : the null hypothesis is that there is no significant
difference in the medians of the two groups being compared. The p-value
obtained from the test indicates the probability of observing the
obtained difference in medians (or a more extreme difference) between
the two groups due to chance, if the null hypothesis were true. If the
p-value is below the pre-specified significance level (typically 0.05),
we reject the null hypothesis and conclude that there is a statistically
significant difference between the medians of the two groups. On the
other hand, if the p-value is above the significance level, we fail to
reject the null hypothesis and conclude that there is insufficient
evidence to conclude that there is a significant difference in medians
between the two groups.{]}

\begin{verbatim}
## 
##  Pairwise comparisons using Wilcoxon rank sum test with continuity correction 
## 
## data:  perceivedriskc$perceived_risk and perceivedriskc$technology 
## 
##         Coal    Gas     Hydro   Nuclear Oil     Solar  
## Gas     0.00047 -       -       -       -       -      
## Hydro   < 2e-16 < 2e-16 -       -       -       -      
## Nuclear 2.4e-16 4.9e-07 < 2e-16 -       -       -      
## Oil     6.4e-10 < 2e-16 < 2e-16 < 2e-16 -       -      
## Solar   < 2e-16 < 2e-16 < 2e-16 < 2e-16 < 2e-16 -      
## Wind    < 2e-16 < 2e-16 0.00179 < 2e-16 < 2e-16 < 2e-16
## 
## P value adjustment method: BH
\end{verbatim}

\includegraphics{Significant_results_files/figure-latex/unnamed-chunk-10-1.pdf}
\includegraphics{Significant_results_files/figure-latex/unnamed-chunk-10-2.pdf}

\newpage

\hypertarget{how-do-perceptions-of-benefit-from-nuclear-energy-compare-with-other-source-of-energy}{%
\section{How do perceptions of benefit from nuclear energy compare with
other source of
energy?}\label{how-do-perceptions-of-benefit-from-nuclear-energy-compare-with-other-source-of-energy}}

H : Benefits from all energy technologies will be similar

The box plot shows the differences in Median for perceived benefit from
all energy technologies. The pairwise wilcox test shows if these
differences are statistically significant or not.

The green pairs indicate that there is a statistically significant
difference between the medians of the two groups. White and grey
indicate - no differences between the medians of the two groups.

\begin{verbatim}
## 
##  Pairwise comparisons using Wilcoxon rank sum test with continuity correction 
## 
## data:  perceivedbenefitc$perceived_benefit and perceivedbenefitc$technology 
## 
##         Coal    Gas     Hydro   Nuclear Oil     Solar  
## Gas     0.00338 -       -       -       -       -      
## Hydro   4.2e-10 0.00053 -       -       -       -      
## Nuclear 0.72011 0.02283 8.3e-08 -       -       -      
## Oil     0.07916 1.7e-06 3.7e-16 0.04916 -       -      
## Solar   < 2e-16 < 2e-16 < 2e-16 < 2e-16 < 2e-16 -      
## Wind    3.7e-14 2.3e-06 0.28176 7.1e-11 < 2e-16 2.5e-16
## 
## P value adjustment method: BH
\end{verbatim}

\includegraphics{Significant_results_files/figure-latex/unnamed-chunk-11-1.pdf}
\includegraphics{Significant_results_files/figure-latex/unnamed-chunk-11-2.pdf}

\newpage

\hypertarget{how-do-perception-of-risk-and-perception-of-benefit-compare-with-each-other}{%
\section{How do perception of risk and perception of benefit compare
with each
other?}\label{how-do-perception-of-risk-and-perception-of-benefit-compare-with-each-other}}

Mean Values and Median Values are presented in the graphs below

\includegraphics{Significant_results_files/figure-latex/unnamed-chunk-12-1.pdf}

\includegraphics{Significant_results_files/figure-latex/unnamed-chunk-13-1.pdf}

\hypertarget{results-from-wilcoxon-signed-rank-test-used-to-compare-the-median-perceived-risk-and-median-perceived-benefit-from-each-technology.}{%
\subsection{Results from Wilcoxon Signed Rank Test used to compare the
median perceived risk and median perceived benefit from each
technology.}\label{results-from-wilcoxon-signed-rank-test-used-to-compare-the-median-perceived-risk-and-median-perceived-benefit-from-each-technology.}}

Null hypothesis (H0): The median difference between perceived risk and
perceived benefit from each technology is zero.

All p values are less than 0.05 suggesting that the differences observed
above in the graph are statistically significant.

\begin{verbatim}
## $Coal
## [1] 7.780432e-11
## 
## $Gas
## [1] 1.276737e-13
## 
## $Hydro
## [1] 1.157982e-157
## 
## $Nuclear
## [1] 0.002649393
## 
## $Oil
## [1] 8.083808e-33
## 
## $Solar
## [1] 5.50654e-270
## 
## $Wind
## [1] 3.671042e-166
\end{verbatim}

\newpage

\hypertarget{factor-analysis-kahan-scale}{%
\section{Factor Analysis: Kahan
Scale}\label{factor-analysis-kahan-scale}}

Factor Levels for demographic variables - State, age, gender,
urban\_rural, caste and religion First level in each of the variables is
the reference for linear regression models.

\begin{verbatim}
## [1] "Maharashtra"   "Rajasthan"     "Tamil Nadu"    "Uttar Pradesh"
## [5] "West Bengal"
\end{verbatim}

\begin{verbatim}
## [1] "18-24 years old"   "25-34 years old"   "35-44 years old"  
## [4] "45-54 years old"   "55-64 years old"   "65-74 years old"  
## [7] "75 years or older"
\end{verbatim}

\begin{verbatim}
## [1] "Female" "Male"
\end{verbatim}

\begin{verbatim}
## [1] "Rural" "Urban"
\end{verbatim}

\begin{verbatim}
## [1] "Rural" "Urban"
\end{verbatim}

\begin{verbatim}
## [1] "Brahmin" "General" "OBC"     "SC"      "ST"
\end{verbatim}

\begin{verbatim}
## [1] "Agnostism/ Atheism"     "Buddhism"               "Christanity"           
## [4] "Hinduism"               "Islam"                  "Jainism"               
## [7] "Other (Please mention)" "Sikhism"
\end{verbatim}

Before fitting a linear regression model, I conducted factor analysis on
the Kahan scale and the newly developed economic-political value scale.
The results from the Factor Analysis are below.

The Individualism items (indicated by K\_I) were bringing down the
cronbach's alpha values in the Kahan scale. The Alpha for INdividualism-
Communitarian scale was 0.49. After removing the Individualism items
(K\_I) the alpha for this factor was 0.71. The reasons for this could be
that the individualism items are not well adapted to the Indian
population.

I conducted confirmatory factor analysis (CFA) for the Kahan scale (see
Appendix 1) since this a well used scale with theoretical basis for
factor distinctions and also previous studies have used this scale.

\begin{verbatim}
## lavaan 0.6.15 ended normally after 15 iterations
## 
##   Estimator                                         ML
##   Optimization method                           NLMINB
##   Number of model parameters                        15
## 
##   Number of observations                           375
## 
## Model Test User Model:
##                                                       
##   Test statistic                                54.472
##   Degrees of freedom                                13
##   P-value (Chi-square)                           0.000
## 
## Model Test Baseline Model:
## 
##   Test statistic                               676.704
##   Degrees of freedom                                21
##   P-value                                        0.000
## 
## User Model versus Baseline Model:
## 
##   Comparative Fit Index (CFI)                    0.937
##   Tucker-Lewis Index (TLI)                       0.898
## 
## Loglikelihood and Information Criteria:
## 
##   Loglikelihood user model (H0)              -3707.085
##   Loglikelihood unrestricted model (H1)      -3679.849
##                                                       
##   Akaike (AIC)                                7444.170
##   Bayesian (BIC)                              7503.074
##   Sample-size adjusted Bayesian (SABIC)       7455.483
## 
## Root Mean Square Error of Approximation:
## 
##   RMSEA                                          0.092
##   90 Percent confidence interval - lower         0.068
##   90 Percent confidence interval - upper         0.118
##   P-value H_0: RMSEA <= 0.050                    0.003
##   P-value H_0: RMSEA >= 0.080                    0.806
## 
## Standardized Root Mean Square Residual:
## 
##   SRMR                                           0.046
## 
## Parameter Estimates:
## 
##   Standard errors                             Standard
##   Information                                 Expected
##   Information saturated (h1) model          Structured
## 
## Latent Variables:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   KahanS =~                                                             
##     K_SHARM           0.690    0.062   11.043    0.000    0.690    0.628
##     K_SLIMCHOI        0.738    0.064   11.570    0.000    0.738    0.659
##     K_SPROTECT        0.495    0.064    7.770    0.000    0.495    0.453
##   KahanH =~                                                             
##     K_HEQUAL          0.743    0.061   12.197    0.000    0.743    0.628
##     K_ERADEQ1        -0.796    0.052  -15.207    0.000   -0.796   -0.750
##     K_EWEALTH        -0.663    0.060  -11.095    0.000   -0.663   -0.580
##     K_ERADEQ2        -0.840    0.056  -14.990    0.000   -0.840   -0.741
## 
## Covariances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   KahanS ~~                                                             
##     KahanH           -0.772    0.049  -15.878    0.000   -0.772   -0.772
## 
## Variances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##    .K_SHARM           0.730    0.073    9.973    0.000    0.730    0.605
##    .K_SLIMCHOI        0.709    0.077    9.272    0.000    0.709    0.565
##    .K_SPROTECT        0.952    0.078   12.281    0.000    0.952    0.795
##    .K_HEQUAL          0.850    0.074   11.544    0.000    0.850    0.606
##    .K_ERADEQ1         0.493    0.053    9.367    0.000    0.493    0.438
##    .K_EWEALTH         0.865    0.072   12.026    0.000    0.865    0.663
##    .K_ERADEQ2         0.578    0.060    9.581    0.000    0.578    0.450
##     KahanS            1.000                               1.000    1.000
##     KahanH            1.000                               1.000    1.000
\end{verbatim}

RMSEA - between 0.05 and 0.08 (reasonable fit), less than 0.05 close fit
and greater than 0.10 is poor fit CFI - greater than 0.90 or 0.95
indicates good fit TFI - CFI\textgreater TFI \textgreater0.90 -
indicates good fit

After having removed a few variables that had very low loading, the
model is now a good fit. Some of the Individualistic variables just
don't fit. Final scale variables:

KahanS(Individualism - Communitarian) = K\_SHARM + K\_SLIMCHOI +
K\_SPROTECT KahanH(Hierarchy- Egalitarian) =K\_HEQUAL+ K\_ERADEQ1 +
K\_EWEALTH + K\_ERADEQ2

The Cronabch alpha for this final scale was 0.75.

\newpage

\hypertarget{factor-analysis-new-eco-political-scale}{%
\section{Factor Analysis: New Eco-political
Scale}\label{factor-analysis-new-eco-political-scale}}

Then I conducted Factor Analysis on all eco-political values(see
Appendix 2). The Cronbach's alpha for the scale was high at 0.785
(almost 0.8).

The scale reduced to two factors which I named as 1) People Centered
Development and 2) Nationalist Development. The final scale with two
factors include the following

\textbf{MR1 People Centered Development: Pdevelop}

HEALTHNUCLEAR - Nuclear energy poses a great risk to the health of
people living around it.

BEAUTYNUCLEAR - Nuclear energy spoils the natural beauty of the
landscape.

MECHANISATION - Rapid mechanization of work is taking away jobs from
workers in this country.

INDUSTRYSMALL - Large corporations are destroying the local industries
in India and benefiting only a handful of people.

DISPLACENUCLEAR- Nuclear energy is leading to displacement of people
from their land.

POLLUTENUCLEAR- Nuclear energy increases pollution of air/water/land.

OWNERREG- Regardless of ownership, the government should pass strong
regulations and implement them.

\textbf{MR2 Nationalist Development: Ndevelop}

DEVNUCLEAR - Nuclear energy pushes forward the country's development.

PRIDENUCLEAR- I would be proud if my community used nuclear energy.

NPRIDENUCLEAR- Nuclear energy is a mark of pride for our nation.

PROSPERNUCLEAR-Nuclear energy brings economic prosperity to the
surrounding regions.

INDUSTRYLARGE- Large scale industries are required for the development
of the country that will benefit everyone.

The results of the factor analysis are below:

\begin{verbatim}
## 
## Reliability analysis   
##  raw_alpha std.alpha G6(smc) average_r S/N   ase mean   sd median_r
##        0.8       0.8    0.84      0.14   4 0.015  3.3 0.47     0.15
\end{verbatim}

\begin{verbatim}
## Factor Analysis using method =  minres
## Call: fa(r = ecopolall, nfactors = 2, rotate = "varimax")
## Standardized loadings (pattern matrix) based upon correlation matrix
##                 item   MR1   MR2     h2   u2 com
## HEALTHNUCLEAR     17  0.61       0.3880 0.61 1.1
## BEAUTYNUCLEAR     19  0.60       0.3679 0.63 1.1
## MECHANISATION      2  0.57       0.3892 0.61 1.4
## INDUSTRYSMALL      6 -0.56       0.3280 0.67 1.1
## DISPLACENUCLEAR   15  0.54       0.3555 0.64 1.4
## POLLUTENUCLEAR    16  0.53       0.2811 0.72 1.0
## OWNERREG          14 -0.50       0.2848 0.72 1.3
## ENVOVERDEV         9             0.1403 0.86 1.1
## DECISIONDECEN      3             0.1058 0.89 1.0
## OWNERPUB          13             0.1178 0.88 1.7
## DECISIONCEN        4             0.1160 0.88 1.8
## OWNERPVT          11             0.0610 0.94 1.0
## ECONOMYLOCAL       8             0.0243 0.98 1.1
## DEVOVERENV        10             0.0015 1.00 1.2
## DEVNUCLEAR        22        0.65 0.4530 0.55 1.1
## PRIDENUCLEAR      20        0.61 0.4108 0.59 1.2
## NPRIDENUCLEAR     21        0.57 0.3608 0.64 1.2
## PROSPERNUCLEAR    23        0.55 0.3267 0.67 1.1
## INDUSTRYLARGE      5        0.43 0.2386 0.76 1.5
## RELYNUCLEAR       24             0.1590 0.84 1.1
## WEALTHLIM          1             0.2036 0.80 1.7
## ECONOMYGLOBAL      7             0.2480 0.75 2.0
## JOBSNUCLEAR       18             0.1933 0.81 1.9
## OWNERNOREG        12             0.0565 0.94 1.9
## 
##                        MR1  MR2
## SS loadings           3.13 2.49
## Proportion Var        0.13 0.10
## Cumulative Var        0.13 0.23
## Proportion Explained  0.56 0.44
## Cumulative Proportion 0.56 1.00
## 
## Mean item complexity =  1.3
## Test of the hypothesis that 2 factors are sufficient.
## 
## The degrees of freedom for the null model are  276  and the objective function was  6.02 with Chi Square of  2198.62
## The degrees of freedom for the model are 229  and the objective function was  2.43 
## 
## The root mean square of the residuals (RMSR) is  0.08 
## The df corrected root mean square of the residuals is  0.09 
## 
## The harmonic number of observations is  375 with the empirical chi square  1292.99  with prob <  8.6e-148 
## The total number of observations was  375  with Likelihood Chi Square =  884.44  with prob <  9.5e-78 
## 
## Tucker Lewis Index of factoring reliability =  0.587
## RMSEA index =  0.087  and the 90 % confidence intervals are  0.081 0.094
## BIC =  -472.83
## Fit based upon off diagonal values = 0.83
## Measures of factor score adequacy             
##                                                    MR1  MR2
## Correlation of (regression) scores with factors   0.89 0.88
## Multiple R square of scores with factors          0.80 0.77
## Minimum correlation of possible factor scores     0.60 0.53
\end{verbatim}

\newpage

\hypertarget{linear-regression-4-models.}{%
\section{Linear Regression: 4
Models.}\label{linear-regression-4-models.}}

Then I ran 4 linear regression models adding more variables every time.
The results of the linear regression models are below.

\begingroup\setlength{\tabcolsep}{1pt}\renewcommand{\arraystretch}{0.7}

\% Table created by stargazer v.5.2.3 by Marek Hlavac, Social Policy
Institute. E-mail: marek.hlavac at gmail.com \% Date and time: Mon, Jul
17, 2023 - 13:22:23

\begin{table}[!htbp] \centering 
  \caption{Results from 4 linear regression models} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{Risky\_Nuclear} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 Uppercaste & $-$0.109 & $-$0.032 & $-$0.016 & $-$0.038 \\ 
  & (0.119) & (0.111) & (0.108) & (0.108) \\ 
  & & & & \\ 
 Male & 0.226$^{**}$ & $-$0.105 & $-$0.095 & $-$0.072 \\ 
  & (0.115) & (0.123) & (0.120) & (0.119) \\ 
  & & & & \\ 
 Hindu & 0.054 & $-$0.033 & $-$0.038 & $-$0.003 \\ 
  & (0.130) & (0.122) & (0.118) & (0.118) \\ 
  & & & & \\ 
 UrbanUrban & $-$0.242$^{**}$ & 0.022 & $-$0.018 & $-$0.002 \\ 
  & (0.111) & (0.119) & (0.116) & (0.116) \\ 
  & & & & \\ 
 age25-34 years old &  & $-$0.094 & $-$0.079 & $-$0.046 \\ 
  &  & (0.124) & (0.121) & (0.120) \\ 
  & & & & \\ 
 age35-44 years old &  & $-$0.066 & $-$0.103 & $-$0.118 \\ 
  &  & (0.151) & (0.148) & (0.147) \\ 
  & & & & \\ 
 age45-54 years old &  & 0.083 & 0.121 & 0.158 \\ 
  &  & (0.256) & (0.250) & (0.248) \\ 
  & & & & \\ 
 age55-64 years old &  & 0.109 & 0.240 & 0.369 \\ 
  &  & (0.495) & (0.483) & (0.479) \\ 
  & & & & \\ 
 age65-74 years old &  & 1.183$^{**}$ & 1.260$^{**}$ & 1.167$^{**}$ \\ 
  &  & (0.564) & (0.549) & (0.545) \\ 
  & & & & \\ 
 age75 years or older &  & 0.076 & $-$0.194 & $-$0.363 \\ 
  &  & (0.960) & (0.936) & (0.929) \\ 
  & & & & \\ 
 StateRajasthan &  & 0.659$^{***}$ & 0.382$^{**}$ & 0.136 \\ 
  &  & (0.163) & (0.171) & (0.186) \\ 
  & & & & \\ 
 StateTamil Nadu &  & 1.372$^{***}$ & 1.030$^{***}$ & 0.941$^{***}$ \\ 
  &  & (0.238) & (0.243) & (0.283) \\ 
  & & & & \\ 
 StateUttar Pradesh &  & 0.364$^{*}$ & 0.060 & $-$0.036 \\ 
  &  & (0.195) & (0.201) & (0.202) \\ 
  & & & & \\ 
 StateWest Bengal &  & 1.474$^{***}$ & 0.981$^{***}$ & 0.774$^{***}$ \\ 
  &  & (0.215) & (0.234) & (0.247) \\ 
  & & & & \\ 
 KahanS &  &  & $-$0.272$^{**}$ & $-$0.213 \\ 
  &  &  & (0.134) & (0.135) \\ 
  & & & & \\ 
 KahanH &  &  & 0.053 & $-$0.049 \\ 
  &  &  & (0.125) & (0.127) \\ 
  & & & & \\ 
 Pdevelop &  &  &  & 0.187$^{**}$ \\ 
  &  &  &  & (0.078) \\ 
  & & & & \\ 
 Ndevelop &  &  &  & 0.178$^{***}$ \\ 
  &  &  &  & (0.064) \\ 
  & & & & \\ 
 Constant & 3.184$^{***}$ & 3.029$^{***}$ & 3.172$^{***}$ & 3.192$^{***}$ \\ 
  & (0.161) & (0.162) & (0.160) & (0.161) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Observations & 375 & 375 & 375 & 375 \\ 
R$^{2}$ & 0.033 & 0.216 & 0.262 & 0.282 \\ 
Adjusted R$^{2}$ & 0.023 & 0.185 & 0.229 & 0.246 \\ 
Residual Std. Error & 1.033 (df = 370) & 0.944 (df = 360) & 0.918 (df = 358) & 0.908 (df = 356) \\ 
F Statistic & 3.187$^{**}$ (df = 4; 370) & 7.078$^{***}$ (df = 14; 360) & 7.926$^{***}$ (df = 16; 358) & 7.787$^{***}$ (df = 18; 356) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 
\endgroup

Key observations:

\textbf{1. Demographic effects:} The impact of demographic
characteristics on the perceived risk from Nuclear Energy appears to be
small. The adjusted R-squared of the first model, which includes only
demographic variables, is 0.023, indicating that these variables explain
just over 2\% of the variance in perceived risk.

\textbf{2. Age effects:} In Model 2, where age groups are added, there
is a distinct change in the perceived risk from nuclear energy as age
increases. Interestingly, only the age group 65-74 shows a significant
increase in perceived risk, compared to the reference age group (18-25
years).

\textbf{3. Gender effects:} In the initial model, being male is
positively associated with higher perceived risk from nuclear energy.
However, the significance of this association diminishes when age and
state variables are included in the model, suggesting that the
relationship between gender and perceived risk may be influenced by
these factors.

\textbf{4. State effects:} Both exploratory visualizations and
regression models strongly suggest that the respondents' state of
residence significantly influences their perceived risk from nuclear
energy. The comparison state is Maharashtra. The coefficients for the
other states can be interpreted as the difference in perceived risk from
each state compared to Maharashtra, holding all else constant.

\textbf{5. Kahan scale effects:} Among the Kahan scale variables, only
the individualism factor is statistically significant in the third
model. This suggests that individuals scoring high on the individualism
scale perceive nuclear energy as less risky.

\textbf{6. Eco-political scale effects:} When we introduce the
eco-political scale, the effect of the individualism factor from the
Kahan scale loses its significance. This could suggest that the
eco-political scale is capturing some aspect of the risk perception
related to individualism. The two factors of the eco-political scale
both have a statistically significant impact on the perceived risk,
indicating that these eco-political beliefs play an important role in
shaping risk perceptions.

\newpage

\hypertarget{system-of-government-items}{%
\section{System of Government Items}\label{system-of-government-items}}

The governance items were not going very well with the items in the
eco-political value scale. So I kept them separate. Below are some
exploratory graphs on them. In these graphs high values contain somewhat
agree(4) or strongly agree(5) and low contains strongly disagree(1),
somewhat disagree(2).

\hypertarget{perceived-risk-by-support-for-democratic-government}{%
\subsection{Perceived risk by Support for Democratic
government}\label{perceived-risk-by-support-for-democratic-government}}

\begin{verbatim}
##    grouped_demo technology     mean   n        sd
## 1          high       Coal 3.177236 721 1.1340749
## 2          high        Gas 3.246732 721 1.2161915
## 3          high      Hydro 2.175079 721 1.2603858
## 4          high    Nuclear 3.372093 721 1.2560982
## 5          high        Oil 2.840070 721 1.3178397
## 6          high      Solar 1.588410 721 1.0140307
## 7          high       Wind 2.032432 721 1.2072407
## 8           low       Coal 2.961290 157 1.0057230
## 9           low        Gas 3.026144 157 1.0447092
## 10          low      Hydro 2.279221 157 1.0064936
## 11          low    Nuclear 3.075862 157 1.0806554
## 12          low        Oil 3.026144 157 0.9996559
## 13          low      Solar 2.283871 157 1.0675548
## 14          low       Wind 2.337748 157 0.9858155
\end{verbatim}

\includegraphics{Significant_results_files/figure-latex/unnamed-chunk-19-1.pdf}

\newpage

\hypertarget{perceived-risk-by-support-for-totalitarian-government}{%
\subsection{Perceived risk by Support for Totalitarian
government}\label{perceived-risk-by-support-for-totalitarian-government}}

\begin{verbatim}
##    grouped_total technology     mean   n       sd
## 1           high       Coal 3.086735 466 1.200012
## 2           high        Gas 3.217848 466 1.300727
## 3           high      Hydro 2.209877 466 1.239970
## 4           high    Nuclear 3.403599 466 1.255539
## 5           high        Oil 3.296512 466 1.114123
## 6           high      Solar 1.692841 466 1.023053
## 7           high       Wind 2.084615 466 1.171872
## 8            low       Coal 3.229814 344 1.042693
## 9            low        Gas 3.223975 344 1.080755
## 10           low      Hydro 2.103030 344 1.252956
## 11           low    Nuclear 3.360902 344 1.186963
## 12           low        Oil 2.677524 344 1.307438
## 13           low      Solar 1.783383 344 1.111609
## 14           low       Wind 1.966997 344 1.127134
\end{verbatim}

\includegraphics{Significant_results_files/figure-latex/unnamed-chunk-20-1.pdf}

\newpage

\hypertarget{perceived-risk-by-support-for-technocratic-government}{%
\subsection{Perceived risk by Support for Technocratic
government}\label{perceived-risk-by-support-for-technocratic-government}}

\begin{verbatim}
##    grouped_techno technology     mean   n       sd
## 1            high       Coal 3.177215 626 1.110419
## 2            high        Gas 3.280961 626 1.204385
## 3            high      Hydro 2.133449 626 1.232323
## 4            high    Nuclear 3.491803 626 1.240957
## 5            high        Oil 2.889109 626 1.328705
## 6            high      Solar 1.638047 626 1.016873
## 7            high       Wind 2.026616 626 1.180498
## 8             low       Coal 3.107143 190 1.083550
## 9             low        Gas 3.238372 190 1.132267
## 10            low      Hydro 2.394286 190 1.178822
## 11            low    Nuclear 3.151899 190 1.135289
## 12            low        Oil 3.222930 190 1.065777
## 13            low      Solar 1.978261 190 1.106150
## 14            low       Wind 2.248447 190 1.112604
\end{verbatim}

\includegraphics{Significant_results_files/figure-latex/unnamed-chunk-21-1.pdf}

\newpage

\hypertarget{perceived-risk-by-support-for-religious-government}{%
\subsection{Perceived risk by Support for Religious
government}\label{perceived-risk-by-support-for-religious-government}}

\begin{verbatim}
##    grouped_religion technology     mean   n        sd
## 1              high       Coal 3.025189 449 1.1500418
## 2              high        Gas 3.426630 449 1.1364880
## 3              high      Hydro 2.215385 449 1.1493909
## 4              high    Nuclear 3.120805 449 1.3653369
## 5              high        Oil 2.965714 449 1.1795640
## 6              high      Solar 1.702179 449 1.0361992
## 7              high       Wind 2.217105 449 1.2045993
## 8               low       Coal 3.250000 427 1.0474290
## 9               low        Gas 3.072165 427 1.2093300
## 10              low      Hydro 2.045918 427 1.2481941
## 11              low    Nuclear 3.525568 427 1.1039554
## 12              low        Oil 2.759003 427 1.3081298
## 13              low      Solar 1.592233 427 0.9709843
## 14              low       Wind 1.882199 427 1.0888350
\end{verbatim}

\includegraphics{Significant_results_files/figure-latex/unnamed-chunk-22-1.pdf}

\newpage

\hypertarget{appendix1}{%
\section{Appendix1}\label{appendix1}}

\textbf{Kahan et al (2007) scale}

Individualism - Communitarinism

\begin{itemize}
\tightlist
\item
  \textbf{K\_IINTRFER} The government interferes far too much in our
  everyday lives.
\item
  \textbf{K\_IPRIVACY} The government should stop telling people how to
  live their lives.
\item
  \textbf{K\_IPROTECT} It's not the government's business to try to
  protect people from themselves.
\item
  \textbf{K\_SHARM} Sometimes the government needs to make laws that
  keep people from hurting themselves.
\item
  \textbf{K\_SLIMCHOI} The government should put limits on the choices
  individuals can make so they don't get in the way of what's good for
  society.
\item
  \textbf{K\_SPROTECT} The government should do more to advance
  society's goals, even if that means limiting the freedom and choices
  of individuals.
\end{itemize}

Hierarchy -Egalitarianism

\begin{itemize}
\tightlist
\item
  \textbf{K\_HEQUAL} We have gone too far in pushing equal rights in
  this country.
\item
  \textbf{K\_HREVDIS1} Nowadays it seems like there is just as much
  discrimination against upper castes as there is against Dalits.
\item
  \textbf{K\_EDISCRIM} Discrimination against minorities is still a very
  serious problem in our society.
\item
  \textbf{K\_ERADEQ1} We need to dramatically reduce inequalities
  between the rich and the poor.
\item
  \textbf{K\_EWEALTH} Our society would be better off if the
  distribution of wealth was more equal.
\item
  \textbf{K\_ERADEQ2} We need to dramatically reduce inequalities
  between men and women.
\end{itemize}

\newpage

\hypertarget{appendix2}{%
\section{Appendix2}\label{appendix2}}

\textbf{New Eco-pol values scale}

\begin{itemize}
\item
  \textbf{DISPLACENUCLER} Nuclear energy is leading to displacement of
  people from their land
\item
  \textbf{BEAUTYNUCLEAR} Nuclear energy spoils the natural beauty of the
  landscape
\item
  \textbf{POLLUTENUCLEAR} Nuclear energy increases pollution of
  air/water/land
\item
  \textbf{HEALTHNUCLEAR} Nuclear energy poses a great risk to the health
  of people living around it
\item
  \textbf{JOBSNUCLEAR} Nuclear energy will bring jobs to the local
  community
\item
  \textbf{PRIDENUCLEAR} I would be proud if my community used nuclear
  energy
\item
  \textbf{NPRIDENUCLEAR} Nuclear energy is a mark of pride for our
  nation
\item
  \textbf{DEVNUCLEAR} Nuclear energy pushes forward the country's
  development
\item
  \textbf{PROSPERNUCLEAR} Nuclear energy brings economic prosperity to
  the surrounding regions
\item
  \textbf{RELYNUCLEAR} I don't like the idea that I have to rely on the
  government for electricity from nuclear energy
\item
  \textbf{DECISIONDECEN} Local politicians shouldn't have to ask
  permission from the central government to implement policies
\item
  \textbf{DECISIONCEN} Laws and policies would be implemented more
  smoothly if more power lay with the central government.
\item
  \textbf{INDUSTRYLARGE} Large scale industries are required for the
  development of the country that will benefit everyone
\item
  \textbf{ECONOMYLOCAL} India would be better off if foreign companies
  didn't come to here
\item
  \textbf{DEVOVERENV} Economic growth and creating jobs should be
  prioritized over environmental protection
\item
  \textbf{INDUSTRYSMALL} Large corporations are destroying the local
  industries in India and benefiting only a handful of people.
\item
  \textbf{WEALTHLIM} A limit should be put to how much wealth a person
  can amass
\item
  \textbf{ECONOMYGLOBAL} Foreign companies have led to a range of
  benefits for the Indian people and society
\item
  \textbf{OWNERPVT} All businesses and industries should be owned
  privatel
\item
  \textbf{OWNERPUB} The government should own most large businesses and
  industrie
\item
  \textbf{ENVOVERDEV} Polluting industries that spoil the environment
  should be shut down even if it costs people their jo
\item
  \textbf{OWNERREG} Regardless of ownership, the government should pass
  strong regulations and implement them
\item
  \textbf{MECHANISATION} Rapid mechanization of work is taking away jobs
  from workers in this country
\item
  \textbf{OWNERNOREG} There is too much red-tape and the government
  should not interfere with businesses and industries
\end{itemize}

\end{document}

### 2024-01-15 nuclear in comparison.Rmd
commiting after a long time. oh god

@@
 ---
-title: 'nuclear energy in comparison'
+title: "nuclear energy in comparison"
 output:
@@
     keep_tex: yes
+    keep_md: yes
   header-includes:
@@
   - \usepackage{array}
-  keep_md: yes
+  - \usepackage{pdflscape}
+  - \newcommand{\blandscape}{\begin{landscape}}
+  - \newcommand{\elandscape}{\end{landscape}}
+  html_document:
+    toc: yes
+    toc_depth: '2'
+    df_print: paged
 ---
+
+# Abstract
 
@@
 \newpage
-# State Specific Differences.
-
-We see huge differences for perceived risk and perceived benefit for each technology from state to state. These graphs explore that. 
-The number of respondents from each state are also reported below.
+
+# H1: Nuclear Energy will be seen as riskier than other energy technologies in India.  this paper explores nuclear energy in comparison with other technologies
+
+## Likert Responses (n= 2160)
+The percentages are rounded off to whole numbers.
+
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+# Q1: how much is the awareness of energy technologies in India ? How does it relate to state specific data ? 
+# summary of NA results from the combined sample of 2000 responses (simple percentage bar graphs)
+# part 1- how much is the awareness of energy technologies in India -
+
+#plotting perceived risk from different technologies including rather not say don't know
+colorsequence<- c("#8C4646","#D9695F","#F2A679","#F2D091","#5D8C7B","#808080")
+
+#following is the data frame for making the barplot 
+df_barplot <- uncodedjoineddf %>%
+  dplyr::select(starts_with("RISKY"))%>%
+  gather(Technology, Perceived_Risk, Risky_Hydro:Risky_INDLPG, factor_key = TRUE)%>%
+  separate(Technology, c("Risky", "Technology"), extra = "merge", fill = "left")%>%
+  dplyr::select(-Risky) %>% 
+  group_by(Technology, Perceived_Risk) %>%
+  dplyr::summarise(n=n())
+
+#following data frame gives us percentage for each response 
+df_barplot_percent<- df_barplot%>%
+  group_by(Technology) %>%
+  mutate(Percentage = round(n/sum(n)*100, 0)) %>%
+  ungroup()
+
+#plotting perceived benefit from different technologies including rather not say don't know
+
+df_barplotben <- uncodedjoineddf %>%
+  dplyr::select(starts_with("Ben"))%>%
+  gather(Technology, Perceived_Benefit, Ben_Hydro:Ben_INDKerosene, factor_key = TRUE)%>%
+  separate(Technology, c("Ben", "Technology"), extra = "merge", fill = "left")%>%
+  dplyr::select(-Ben) %>% 
+  group_by(Technology, Perceived_Benefit) %>%
+  dplyr::summarise(n=n())
+
+df_barplotben_percent<- df_barplotben%>%
+  group_by(Technology) %>%
+  mutate(Percentage = round(n/sum(n)*100, 0)) %>%
+  ungroup()
+
+#bar plot for likert responses perceived risk - centrally owned technologies 
+df_barplot %>% ggplot(aes(fill= fct_rev(factor(Perceived_Risk, levels=c("Extremely risky", "Very risky","Moderately risky","Slightly risky","Not at all risky","Rather not say/Don't know"))), y=n , x=Technology)) +
+  geom_bar(position="fill",stat="identity")+
+  geom_text(data = df_barplot_percent, aes(label=paste0(Percentage, "%"), y=n), position = position_fill(vjust=0.5), size=3) +
+  scale_x_discrete(limits = c("Solar", "Wind" ,"Hydro", "Oil", "Coal","Gas", "Nuclear"))+
+  scale_fill_manual("legend", values = c("Extremely risky" = "#8C4646", "Very risky" = "#D9695F", "Moderately risky" = "#F2A679", "Slightly risky" = "#F2D091","Not at all risky" = "#5D8C7B", "Rather not say/Don't know" = "grey94"))+
+  labs( y = "Perceived Risk", x ="Centrally Managed Energy Technologies")+
+  theme_classic()
+
+#perceived benefit centrally owned technologies
+
+df_barplotben %>% ggplot(aes(fill= factor(Perceived_Benefit, levels=c("Rather not say/Don't know","Not at all beneficial","Slightly beneficial","Moderately beneficial","Very beneficial", "Extremely beneficial")), y=n , x=Technology)) +
+  geom_bar(position="fill",stat="identity")+
+   geom_text(data = df_barplotben_percent, aes(label=paste0(Percentage, "%"), y=n), position = position_fill(vjust=0.5), size=3) +
+  scale_fill_manual("legend", values = c("Rather not say/Don't know" = "grey94" ,"Not at all beneficial" = "orange","Slightly beneficial"="yellow" ,"Moderately beneficial" = "palegreen","Very beneficial"= "green3", "Extremely beneficial"= "green4"))+
+  scale_x_discrete(limits = c("Solar", "Wind", "Hydro", "Oil", "Coal","Gas","Nuclear"))+
+  labs( y = "Perceived Benefit", x ="Centrally Managed Energy Technologies")+
+  theme_classic()
+
+```
+
+\newpage
+## Introduction: Mean Perceived Risk and Mean Perceived Benefit for all energy technologies.
+
+```{r, echo=FALSE}
+library(tidyverse)
+
+# Filter variables of interest
+joineddf_subset <- joineddf %>%
+  dplyr::select(!starts_with(c("Ben_IND", "Risky_IND")))%>%
+  dplyr::select(starts_with("Risky"), 
+         starts_with("Ben"))
+
+# Assuming your data is named joineddf_subset
+long_df <- joineddf_subset %>%
+  gather(key = "Type", value = "Value")
+
+# Separate out Risky and Ben columns
+risky_df <- long_df %>% filter(str_detect(Type, "^Risky"))
+ben_df <- long_df %>% filter(str_detect(Type, "^Ben"))
+
+# Extract the technology type (Hydro, Solar, etc.)
+risky_df$Tech <- str_replace(risky_df$Type, "Risky_", "")
+ben_df$Tech <- str_replace(ben_df$Type, "Ben_", "")
+
+# Calculate the mean for each technology for Risky
+risky_mean <- risky_df %>%
+  group_by(Tech) %>%
+  dplyr::summarize(Mean_Value = mean(Value, na.rm = TRUE),
+          sd = sd(Value, na.rm = TRUE),
+          se = sd(Value, na.rm = TRUE) / sqrt(n()),
+          .groups = "drop")
+
+# Do the same for Ben technologies
+ben_mean <- ben_df %>%
+  group_by(Tech) %>%
+  dplyr::summarize(Mean_Value = mean(Value, na.rm = TRUE),
+          sd = sd(Value, na.rm = TRUE),
+          se = sd(Value, na.rm = TRUE) / sqrt(n()),
+          .groups = "drop")
+
+# Combine the two data frames into one for plotting
+combined_mean <- bind_rows(
+  mutate(risky_mean, Category = "Risky"),
+  mutate(ben_mean, Category = "Beneficial")
+)
+# Reorder the factor levels of the Tech variable by Mean_Value
+risky_mean$Tech <- factor(risky_mean$Tech, levels = risky_mean$Tech[order(risky_mean$Mean_Value, decreasing = FALSE)])
+
+```
+
+```{r, echo=FALSE}
+library(ggplot2)
+library(gridExtra)
+
+mean_risk <- mean(combined_mean$Mean_Value[combined_mean$Category == "Risky"], na.rm = TRUE)
+mean_benefit <- mean(combined_mean$Mean_Value[combined_mean$Category == "Beneficial"], na.rm = TRUE)
+
+# Order Technologies
+technology_order <- c("Solar","Wind","Hydro","Oil","Coal", "Gas","Nuclear")
+ben_mean$Tech <- factor(ben_mean$Tech, levels = technology_order)
+
+# Generate the Ben plot with flipped y-axis
+ben_plot <- ggplot(ben_mean, aes(y = Tech, x = Mean_Value)) +
+  geom_bar(stat = "identity", fill = "palegreen3") +
+  geom_errorbar(aes(xmin = Mean_Value - se, xmax = Mean_Value + se), width = 0.2) +
+  coord_cartesian(xlim = c(5, 1)) + 
+  labs(title = "Perceived Benefit", x = "Mean Values") +
+  #scale_x_reverse() +
+  theme(  # remove y-axis labels
+        axis.title.y = element_blank()) + # remove the "Tech" axis title
+  geom_vline(data = subset(combined_mean, Category == "Beneficial"), 
+             aes(xintercept = mean_benefit), linetype="dotted", color = "black", size = 0.5)
+
+# Generate the Risky plot
+risky_plot <- ggplot(risky_mean, aes(y = Tech, x = Mean_Value)) +
+  geom_bar(stat = "identity", fill = "firebrick2") +
+  geom_errorbar(aes(xmin = Mean_Value - se, xmax = Mean_Value + se), width = 0.2) +
+  coord_cartesian(xlim = c(1, 5)) + 
+  labs(title = "Perceived Risk", x = "Mean Values") +
+  theme(axis.text.y = element_blank(),
+        axis.title.y = element_blank())+
+  geom_vline(data = subset(combined_mean, Category == "Risky"), 
+             aes(xintercept = mean_risk), linetype="dotted", color = "black", size = 0.5)
+ # remove the "Tech" axis title
+
+# Arrange plots side by side
+grid.arrange(ben_plot, risky_plot, ncol=2)
+
+```
+
+## Boxplot for perceived benefit and perceived risk by technology
+
+```{r, echo = FALSE, fig.width=16, fig.height=6}
+
+#Box plot to see the distribution
+
+# Loading the required libraries
+library(tidyverse)
+library(stringr)
+library(gridExtra)
+
+# Reshape the data to a long format
+joineddf_subset_long <- joineddf_subset %>%
+  pivot_longer(cols = everything(), 
+               names_to = "variable",
+               values_to = "value")
+
+# Separate the data into two: one for "Risky_" variables and one for "Ben_" variables
+risky_df <- joineddf_subset_long %>% 
+  filter(str_detect(variable, "^Risky_")) %>%
+  mutate(variable = str_remove(variable, "Risky_"))  # Remove the "Risky_" prefix
+
+ben_df <- joineddf_subset_long %>% 
+  filter(str_detect(variable, "^Ben_")) %>%
+  mutate(variable = str_remove(variable, "Ben_"))  # Remove the "Ben_" prefix
+
+# Remove NA values
+risky_df <- risky_df %>% drop_na()
+ben_df <- ben_df %>% drop_na()
+
+# Create box plots
+risky_plot <- ggplot(risky_df, aes(x = variable, y = value, fill = variable)) +
+  geom_boxplot() +
+  scale_fill_manual(values = rep("firebrick2", length(unique(risky_df$variable)))) +
+  labs(x = "Energy Technologies", y = "Likert", fill = "Technologies") +
+  ggtitle("Perceived risk") +
+  theme_minimal()+
+  theme(axis.text.y = element_text(size=20), 
+        axis.text.x = element_text(size=20),
+        axis.title.y = element_text(size=20),
+        axis.title.x = element_text(size=20),
+        title = element_text(size=20))+
+  guides(fill = FALSE)
+
+ben_plot <- ggplot(ben_df, aes(x = variable, y = value, fill = variable)) +
+  geom_boxplot() +
+  scale_fill_manual(values = rep("palegreen3", length(unique(ben_df$variable)))) +
+  labs(x = "Energy Technologies", y = "Likert Responses", fill = "Technologies") +
+  ggtitle("Perceived Benefit") +
+  theme_minimal()+
+  theme(axis.text.y = element_text(size=20), 
+        axis.text.x = element_text(size=20),
+        axis.title.y = element_text(size=20),
+        axis.title.x = element_text(size=20),
+        title = element_text(size=20))+
+  guides(fill = FALSE)
+
+# Put the two plots next to each other
+grid.arrange(risky_plot, ben_plot, ncol = 2)
+
+```
+
+\newpage
+
+## Pairwise T-test: Mean perceived risk and mean perceived benefit (all energy technologies)
+
+The red and green pairs indicate that there is a statistically significant difference between the means of the two groups. 
+White and grey indicate - no differences between the means of the two groups.
+
+```{r, echo = FALSE, fig.width=14, fig.height=6}
+#Q2 :How are the perceptions of the risk of producing energy from nuclear fission different from that of other conventional sources of energy like coal or hydro power in India?
+#H : Nuclear energy will be perceived as riskier than other sources of energy (coal or hydro) in India like in the west.
+perceivedriskc <-joineddf %>% 
+  dplyr::select("Risky_Solar", "Risky_Hydro", "Risky_Wind", "Risky_Nuclear", "Risky_Coal", "Risky_Gas", "Risky_Oil") %>%
+  gather(key = "technology", value = "perceived_risk") %>% 
+  mutate(technology = gsub("Risky_", "", technology)) %>%
+  na.omit()
+
+result_ttest <- pairwise.t.test(perceivedriskc$perceived_risk, perceivedriskc$technology, p.adjust.method = "BH")
+
+# visualising the pairwaise t test results. the non significant pairs are grey
+
+tidy_result_ttest <- broom::tidy(result_ttest)
+
+heatmap1 <- ggplot(tidy_result_ttest, aes(x = group1, y = group2, fill = p.value)) + 
+  geom_tile(color = "white") + 
+  scale_fill_gradient2(low = "firebrick2", high = "white", midpoint = 0.025, 
+                       limits = c(0, 0.05), space = "Lab", 
+                       name = "P-value") + 
+  theme_classic() + 
+  labs(x = "", y = "") + 
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
+   theme(axis.text.y = element_text(size=20), 
+        axis.text.x = element_text(size=20),
+        axis.title.y = element_text(size=20),
+        axis.title.x = element_text(size=20),
+        title = element_text(size=20),
+        legend.text = element_text(size=12))
+
+#Question- Why there is significant difference statistically - if the medians are the same in the boxplot.
+#Q3: How do perceptions of benefit from nuclear energy compare with other source of energy?
+
+# H : benefits from all energy technologies will be similar 
+# include regression, heat maps, bar graphs? - decide which ones are good to include
+
+perceivedbenefitc <-joineddf %>% 
+  dplyr::select("Ben_Solar", "Ben_Hydro", "Ben_Wind", "Ben_Nuclear", "Ben_Coal", "Ben_Gas", "Ben_Oil") %>%
+  gather(key = "technology", value = "perceived_benefit") %>% 
+  mutate(technology = gsub("Ben_", "", technology)) %>%
+  na.omit()
+
+result_ttestben <- pairwise.t.test(perceivedbenefitc$perceived_benefit, perceivedbenefitc$technology, p.adjust.method = "BH")
+
+# visualising the pairwaise t test results. the non significant pairs are grey
+
+tidy_resultbc <- broom::tidy(result_ttestben)
+
+library(ggplot2)
+heatmap2 <- ggplot(tidy_resultbc, aes(x = group1, y = group2, fill = p.value)) + 
+  geom_tile(color = "white") + 
+  scale_fill_gradient2(low = "palegreen3", high = "white", midpoint = 0.025, 
+                       limits = c(0, 0.05), space = "Lab", 
+                       name = "P-value") + 
+  theme_classic() + 
+  labs(x = "", y = "") + 
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
+   theme(axis.text.y = element_text(size=20), 
+        axis.text.x = element_text(size=20),
+        axis.title.y = element_text(size=20),
+        axis.title.x = element_text(size=20),
+        title = element_text(size=20),
+        legend.text = element_text(size=12))
+
+grid.arrange(heatmap1, heatmap2, ncol=2)
+
+```
+
+\newpage
+
+## Benefit - Risk for each technology 
+```{r, echo = FALSE}
+
+# combining risk and benefit from each energy technology 
+# Filter variables of interest
+joineddf_subset <- joineddf %>%
+  dplyr::select(!starts_with(c("Ben_IND", "Risky_IND")))%>%
+  dplyr::select(starts_with("Risky"), 
+         starts_with("Ben"))
+
+acceptance <- joineddf_subset %>%
+  na.omit()%>%
+  mutate(Nuclear = Ben_Nuclear - Risky_Nuclear,
+         Hyrdo = Ben_Hydro - Risky_Hydro,
+         Wind = Ben_Wind - Risky_Wind,
+         Solar = Ben_Solar - Risky_Solar,
+         Coal = Ben_Coal - Risky_Coal,
+         Gas = Ben_Gas - Risky_Gas,
+         Oil = Ben_Oil - Risky_Oil)%>%
+  dplyr::select(-starts_with(c("Risky", "Ben")))
+
+#str(acceptance)
+
+# Compute the mean of each column
+mean_acceptance <- data.frame(col = names(acceptance), mean_val = sapply(acceptance, mean))
+
+# Compute standard error (not deviation)(divided by root of n)
+sem <- function(x) sqrt(var(x, na.rm = TRUE) / length(na.omit(x)))
+sem_acceptance <- data.frame(col = names(acceptance), sem_val = sapply(acceptance, sem))
+
+mean_acceptance <- merge(mean_acceptance, sem_acceptance, by = "col")
+
+# Plot
+ggplot(mean_acceptance, aes(x = col, y = mean_val, fill = ifelse(mean_val >= 0, 'Above 0', 'Below 0'))) + 
+  geom_bar(stat = "identity") +
+  geom_errorbar(aes(ymin = mean_val - sem_val, ymax = mean_val + sem_val), width = 0.2) +
+  geom_text(aes(label = round(mean_val, 2)), vjust = -0.9) +
+  scale_fill_manual(values = c('Above 0' = 'palegreen3', 'Below 0' = 'firebrick2')) +
+  labs(fill = "Legend") +
+  xlab("Energy Technologies") +
+  ylab("Mean Value") +
+  ggtitle("Benefit- Risk for Each Energy Technology (n = 1184)") +
+  theme_minimal()+
+  ylim(-0.5, 1.75)
+
+```
+
+\newpage
+
+# Claim 1: Demographic variables: nuclear, solar, coal
+
+```{r, echo=FALSE}
+
+# # Convert `caste` into binary variable 'upper' (1) vs 'non-upper' (0)
+joineddf$Uppercaste <- ifelse(joineddf$caste %in% c('Brahmin', 'General'), 1, 0)
+# Convert `gender` into binary variable 'male' (1) vs 'female' (0)
+joineddf$Male <- ifelse(joineddf$gender == 'Male', 1, 0)
+# Convert `religion` into binary variable 'Hinduism' (1) vs 'Non-Hinduism' (0)
+joineddf$Hindu <- ifelse(joineddf$religion == 'Hinduism', 1, 0)
+codedmodule2$State <- as.factor(codedmodule2$State)
+codedmodule2$gender <- as.factor(codedmodule2$gender)
+codedmodule2$Urban <- as.factor(codedmodule2$urban_rural)
+joineddf$Urban <- as.factor(joineddf$urban_rural)
+codedmodule2$caste <- as.factor(codedmodule2$caste)
+codedmodule2$religion <- as.factor(codedmodule2$religion)
+# # Convert `caste` into binary variable 'upper' (1) vs 'non-upper' (0)
+codedmodule2$Uppercaste <- ifelse(codedmodule2$caste %in% c('Brahmin', 'General'), 1, 0)
+# Convert `gender` into binary variable 'male' (1) vs 'female' (0)
+codedmodule2$Male <- ifelse(codedmodule2$gender == 'Male', 1, 0)
+# Convert `religion` into binary variable 'Hinduism' (1) vs 'Non-Hinduism' (0)
+codedmodule2$Hindu <- ifelse(codedmodule2$religion == 'Hinduism', 1, 0)
+
+joineddf1 <- joineddf %>%
+            dplyr::select(Risky_Nuclear, Risky_Solar, Risky_Coal, Uppercaste, Male, Hindu, Urban, age, State) %>%
+            na.omit()
+
+# lm on nuclear energy with all demovars
+
+alldemos <- joineddf1 %>%
+            dplyr::select(Risky_Nuclear, Uppercaste, Male, Hindu, Urban, age, State) %>%
+            mutate(RiskNuclear = Risky_Nuclear)%>%
+  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
+                                      . == "25-34 years old" ~ 2,
+                                      . ==  "35-44 years old" ~3,
+                                      . == "45-54 years old" ~ 4,
+                                      . == "55-64 years old" ~ 5,
+                                      . == "65-74 years old" ~ 6,
+                                      . == "75 years or older" ~ 7)))
+
+alldemoslm1 <- lm(RiskNuclear ~ Uppercaste + Male + Hindu + Urban + age , data = alldemos)
+
+alldemoslm2<- lm(RiskNuclear ~ Uppercaste + Male + Hindu + Urban + age + State, data = alldemos)
+
+#lm on solar with all demovars
+
+salldemos <- joineddf1 %>%
+            dplyr::select(Risky_Solar,Uppercaste, Male, Hindu, Urban, age, State)%>%
+            mutate(RiskSolar = Risky_Solar)%>%
+  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
+                                      . == "25-34 years old" ~ 2,
+                                      . ==  "35-44 years old" ~3,
+                                      . == "45-54 years old" ~ 4,
+                                      . == "55-64 years old" ~ 5,
+                                      . == "65-74 years old" ~ 6,
+                                      . == "75 years or older" ~ 7)))
+
+salldemoslm1 <- lm(RiskSolar ~ Uppercaste + Male + Hindu + Urban + age , data = salldemos)
+
+salldemoslm2<- lm(RiskSolar ~ Uppercaste + Male + Hindu + Urban + age + State, data = salldemos)
+
+#lm on coal with all demovars 
+calldemos <- joineddf1 %>%
+            dplyr::select(Risky_Coal,Uppercaste, Male, Hindu, Urban, age, State)%>%
+            mutate(RiskCoal = Risky_Coal)%>%
+            mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
+                                      . == "25-34 years old" ~ 2,
+                                      . ==  "35-44 years old" ~3,
+                                      . == "45-54 years old" ~ 4,
+                                      . == "55-64 years old" ~ 5,
+                                      . == "65-74 years old" ~ 6,
+                                      . == "75 years or older" ~ 7)))
+
+calldemoslm1 <- lm(RiskCoal ~ Uppercaste + Male + Hindu + Urban + age, data = calldemos)
+
+calldemoslm2<- lm(RiskCoal ~ Uppercaste + Male + Hindu + Urban + age + State, data = calldemos)
+
+```
+
+```{r, echo=FALSE}
+
+# trying linear regression with acceptance scale
+
+joineddf_subset1 <- joineddf %>%
+  dplyr::select(!starts_with(c("Ben_IND", "Risky_IND")))%>%
+  dplyr::select(starts_with("Risky"), 
+         starts_with("Ben"), Uppercaste, Male, Hindu, Urban, age)
+
+acceptance1 <- joineddf_subset1 %>%
+  na.omit()%>%
+  mutate(NetBenNuclear = Ben_Nuclear - Risky_Nuclear,
+         NetBeneHyrdo = Ben_Hydro - Risky_Hydro,
+         NetBeneWind = Ben_Wind - Risky_Wind,
+         NetBenSolar = Ben_Solar - Risky_Solar,
+         NetBenCoal = Ben_Coal - Risky_Coal,
+         NetBenGas = Ben_Gas - Risky_Gas,
+         NetBenOil = Ben_Oil - Risky_Oil)%>%
+  dplyr::select(-starts_with(c("Risky", "Ben")))%>%
+  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
+                                      . == "25-34 years old" ~ 2,
+                                      . ==  "35-44 years old" ~3,
+                                      . == "45-54 years old" ~ 4,
+                                      . == "55-64 years old" ~ 5,
+                                      . == "65-74 years old" ~ 6,
+                                      . == "75 years or older" ~ 7)))
+
+alldemoslm3<- lm(NetBenNuclear ~ Uppercaste + Male + Hindu + Urban + age, data = acceptance1)
+#summary(alldemoslm3)
+
+salldemoslm3<- lm(NetBenSolar ~ Uppercaste + Male + Hindu + Urban + age, data = acceptance1)
+calldemoslm3<- lm(NetBenCoal ~ Uppercaste + Male + Hindu + Urban + age, data = acceptance1)
+
+```
+
+\blandscape
+
+## Linear Regression with demographic variables (caste, religion, gender and age)
+
+```{r, echo=FALSE, results='asis'}
+library(stargazer)
+
+#stargazer code for all demographic variable lms
+
+cat("\\begingroup")
+cat("\\small")  # Adjusts the font size
+cat("\\setlength{\\tabcolsep}{1pt}")
+cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer(alldemoslm1, salldemoslm1, calldemoslm1,alldemoslm3, salldemoslm3, calldemoslm3,
+          title = "Linear Models: Perceived Risk and Net Perceived Benefit(Nuclear, Solar and Coal)",
+          type = "latex"
+)
+cat("\\endgroup")
+
+```
+
+\elandscape
+
+```{r, echo=FALSE}
+
+stargazer(alldemoslm1, salldemoslm1, calldemoslm1, alldemoslm3, salldemoslm3, calldemoslm3, 
+          type = "text", # Choose "html" or "latex" for different formats
+          title = "Regression Models Summary",
+          align = TRUE)
+
+```
+
+\newpage
+
+# Claim 2: Regional differences
+
+We see huge differences for perceived risk and perceived benefit for each technology from state to state. These graphs explore that. The number of respondents from each state are also reported below.
 
@@
 ```
-
-```{r}
+## Radar chart - risk and benefit by state
+
+```{r, echo=FALSE}
+library(tidyverse)
+
+# Filter variables of interest
+joineddf_subset2 <- joineddf %>%
+  dplyr::select(!starts_with(c("Ben_IND", "Risky_IND")))%>%
+  dplyr::select(starts_with("Risky"), 
+         starts_with("Ben"), starts_with("State"))
+
+#long_df2 <- joineddf_subset %>%
+#gather(key = "Type", value = "Value")
+# Reshape data to long format
+long_df2 <- joineddf_subset2 %>%
+  pivot_longer(cols = -State, names_to = "variable", values_to = "value")
+
+# Separate out Risky and Ben columns
+risky_df2 <- long_df2 %>% filter(str_detect(variable, "^Risky"))
+ben_df2 <- long_df2 %>% filter(str_detect(variable, "^Ben"))
+
+# Extract the technology type (Hydro, Solar, etc.)
+risky_df2$Tech <- str_replace(risky_df2$variable, "Risky_", "")
+ben_df2$Tech <- str_replace(ben_df2$variable, "Ben_", "")
+
+# Calculate the mean for each technology for Risky
+risky_mean2 <- risky_df2 %>%
+  group_by(State,Tech) %>%
+  dplyr::summarize(Mean_Value = mean(value, na.rm = TRUE),
+          sd = sd(value, na.rm = TRUE),
+          se = sd(value, na.rm = TRUE) / sqrt(n()),
+          .groups = "drop")
+
+# Do the same for Ben technologies
+ben_mean2 <- ben_df2 %>%
+  group_by(State,Tech) %>%
+  dplyr::summarize(Mean_Value = mean(value, na.rm = TRUE),
+          sd = sd(value, na.rm = TRUE),
+          se = sd(value, na.rm = TRUE) / sqrt(n()),
+          .groups = "drop")
+
+# Combine the two data frames into one for plotting
+combined_mean2 <- bind_rows(
+  mutate(risky_mean2, Category = "Risky"),
+  mutate(ben_mean2, Category = "Beneficial")
+)
+
+# New order of technologies
+new_tech_order <- c("Solar", "Wind", "Hydro", "Oil", "Coal", "Gas","Nuclear")
+
+# Apply this new order to the 'Tech' column in your combined_mean dataset
+combined_mean2$Tech <- factor(combined_mean2$Tech, levels = new_tech_order)
+
+# Split the data by state
+data_by_state <- split(combined_mean2, combined_mean2$State)
+
+```
+
+```{r, echo=FALSE}
+# Create a list to store plots
+plots_list <- list()
+
+for (state in names(data_by_state)) {
+  # Subset data for each state
+  state_data <- data_by_state[[state]]
+
+  # Split into beneficial and risky data
+  ben_mean <- subset(state_data, Category == "Beneficial")
+  risky_mean <- subset(state_data, Category == "Risky")
+
+  # Generate plots for each category
+  ben_plot <- ggplot(ben_mean, aes(y = Tech, x = Mean_Value)) +
+    geom_bar(stat = "identity", fill = "palegreen3") +
+    geom_errorbar(aes(xmin = Mean_Value - se, xmax = Mean_Value + se), width = 0.2) +
+    coord_cartesian(xlim = c(5, 1)) + 
+    labs(title = paste("Perceived Benefit in", state), x = "Mean Values") +
+    theme(axis.title.y = element_blank()) +
+    geom_vline(xintercept = mean_benefit, linetype="dotted", color = "black", size = 0.5)
+
+  risky_plot <- ggplot(risky_mean, aes(y = Tech, x = Mean_Value)) +
+    geom_bar(stat = "identity", fill = "firebrick2") +
+    geom_errorbar(aes(xmin = Mean_Value - se, xmax = Mean_Value + se), width = 0.2) +
+    coord_cartesian(xlim = c(1, 5)) + 
+    labs(title = paste("Perceived Risk in", state), x = "Mean Values") +
+    theme(axis.text.y = element_blank(), axis.title.y = element_blank())+
+    geom_vline(xintercept = mean_risk, linetype="dotted", color = "black", size = 0.5)
+
+  # Combine the plots side by side
+  combined_plot <- grid.arrange(ben_plot, risky_plot, ncol=2)
+  plots_list[[state]] <- combined_plot
+}
+
+```
+
+## Net benefit by state
+
+```{r, echo=FALSE}
+library(dplyr)
+library(ggplot2)
+
+# Including the State variable in the dataset
+joineddf_subset_state <- joineddf %>%
+  dplyr::select(starts_with("Risky"), 
+         starts_with("Ben"), 
+         State)
+
+acceptance_state <- joineddf_subset_state %>%
+  na.omit() %>%
+  mutate(Nuclear = Ben_Nuclear - Risky_Nuclear,
+         Hydro = Ben_Hydro - Risky_Hydro,
+         Wind = Ben_Wind - Risky_Wind,
+         Solar = Ben_Solar - Risky_Solar,
+         Coal = Ben_Coal - Risky_Coal,
+         Gas = Ben_Gas - Risky_Gas,
+         Oil = Ben_Oil - Risky_Oil) %>%
+  dplyr::select(-starts_with(c("Risky", "Ben")))
+
+# Calculate mean and standard error for each state and technology
+mean_acceptance_state <- acceptance_state %>%
+  group_by(State) %>%
+  summarise(across(Nuclear:Oil, list(mean = ~mean(., na.rm = TRUE), 
+                                     sem = ~sqrt(var(., na.rm = TRUE) / length(na.omit(.))))))
+
+```
+
+```{r, echo=FALSE}
+
+# Reshape data for plotting
+long_mean <- mean_acceptance_state %>%
+  pivot_longer(cols = -State, names_to = "Technology_SEM", values_to = "mean_val") %>%
+  separate(Technology_SEM, into = c("Technology", "Metric"), sep = "_") %>%
+  filter(Metric == "mean") %>%
+  select(-Metric)
+
+long_sem <- mean_acceptance_state %>%
+  pivot_longer(cols = -State, names_to = "Technology_SEM", values_to = "sem_val") %>%
+  separate(Technology_SEM, into = c("Technology", "Metric"), sep = "_") %>%
+  filter(Metric == "sem") %>%
+  select(-Metric)
+
+# Merge mean and SEM data
+plot_data <- left_join(long_mean, long_sem, by = c("State", "Technology"))
+
+# Create the plot
+ggplot(plot_data, aes(x = Technology, y = mean_val, fill = ifelse(mean_val >= 0, 'Above 0', 'Below 0'))) +
+  geom_bar(stat = "identity", position = position_dodge()) +
+  geom_errorbar(aes(ymin = mean_val - sem_val, ymax = mean_val + sem_val), 
+                position = position_dodge(), width = 0.25) +
+  facet_wrap(~ State) +
+  scale_fill_manual(values = c('Above 0' = 'palegreen3', 'Below 0' = 'firebrick2')) +
+  labs(title = "Net Benefit (Perceived Risk - Perceived Benefit) by State",
+       x = "Energy Technologies", y = "Net Benefit", fill = "Legend") +
+  theme_minimal() +
+  ylim(-1.75, 3.5)
+
+```
+
+```{r, echo=FALSE}
+
 staterisky <- joineddf %>%
@@
 
-str(staterisky_mean)
-
-# Load required packages
-library(dplyr)
-library(tidyr)
-library(ggplot2)
-
 # Convert to long format
@@
 # Order Technologies
-technology_order <- c("Nuclear", "Gas", "Coal", "Oil", "Hydro", "Wind", "Solar")
+technology_order <- c("Coal", "Gas", "Nuclear", "Oil", "Hydro", "Wind", "Solar")
 long_data$Technology <- factor(long_data$Technology, levels = technology_order)
 
+cbbPalette <- c("#000000","#CC79A7","#F0E442","#E69F00","#56B4E9","#009E73","#D55E00")
+
+names(cbbPalette) <- technology_order
+
+# Order States (assuming you want an alphabetical order, modify as needed)
+states_order <- c( "Rajasthan", "Maharashtra", "Tamil Nadu", "Uttar Pradesh",  "West Bengal")
+long_data$State <- factor(long_data$State, levels = states_order)
+
 # Plot the graph
-ggplot(long_data, aes(x = Technology, y = Mean_Score, color = State, group = State)) +
-  geom_line(size = 1) +
-  geom_point(size = 3) +
-  labs(title = "Mean Perceived Risk by State",
-       x = "Technology", y = "Mean Score") +
-  theme_minimal() +
+stateplot1 <- ggplot(long_data, aes(x = State, y = Mean_Score, color = Technology, group = Technology)) +
+  geom_line(size = 0.7) +
+  geom_point(size = 2) +
+  labs(title = " ",
+       x = "State", y = "Means") +
+  ylim(1,5)+
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
+  scale_color_manual(values=cbbPalette)
+
+```
+
+```{r, echo= FALSE}
+
+# Reshape the data from wide to long format
+staterisky_long <- staterisky %>%
+  pivot_longer(
+    cols = starts_with("Risky_"),
+    names_to = "Technology",
+    values_to = "Riskiness"
+  ) %>%
+  mutate(Technology = sub("Risky_", "", Technology))
+
+# Calculate the sample size for each state
+
+state_sample_size <- staterisky %>%
+  group_by(State) %>%
+  summarize(n = n())
+
+# Join this back to the main data frame
+staterisky_long <- staterisky_long %>%
+  left_join(state_sample_size, by = "State")
+
+# Calculate the weighted mean for each technology in each state
+weighted_means <- staterisky_long %>%
+  group_by(State, Technology) %>%
+  summarize(weighted_mean = sum(Riskiness / n, na.rm = TRUE) / sum(1 / n, na.rm = TRUE), .groups = 'drop')
+
+```
+
+```{r, echo=FALSE}
+
+weighted_means$Technology <- factor(weighted_means$Technology, levels = technology_order)
+states_order <- c( "Rajasthan", "Maharashtra", "Tamil Nadu", "Uttar Pradesh",  "West Bengal")
+weighted_means$State <- factor(weighted_means$State, levels = states_order)
+
+stateplot2 <- ggplot(weighted_means, aes(x = State, y = weighted_mean, color = Technology, group = Technology)) +
+  geom_line(size = 0.7) +
+  geom_point(size = 2) +
+  labs(title = " ",
+       x = "State", y = "Weighted Means") +
+  ylim(0.5,4.5)+
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  scale_color_manual(values = cbbPalette)
+
+```
+
+\newpage 
+## Mean Perceived Risk and Weighted Mean
+
+```{r, echo=FALSE, fig.width=8, fig.height=4,out.width='100%', out.height='100%'}
+library(gridExtra)
+# mean perceived risk and zscores by state side by side
+
+spacer <- grid::rectGrob(gp = grid::gpar(col = "white"))
+
+grid.arrange(stateplot1, spacer, stateplot2, ncol=3, widths=c(0.8, 0.06, 0.8))
+```
+
+\newpage
+## Mean Perceived risk and weighten means by Technologies- solar, coal and nuclear
+
+```{r, echo=FALSE}
+
+staterisky3t <- joineddf %>%
+  dplyr::select(!starts_with(c("Ben_IND", "Risky_IND")))%>%
+  dplyr::select(Risky_Solar, Risky_Nuclear, Risky_Coal, State)
+
+staterisky3t_mean <- staterisky3t %>%
+  group_by(State) %>%
+  summarise(
+    Mean_Risky_Solar = mean(Risky_Solar, na.rm = TRUE),
+    Mean_Risky_Nuclear = mean(Risky_Nuclear, na.rm = TRUE),
+    Mean_Risky_Coal = mean(Risky_Coal, na.rm = TRUE)
+  )
+
+# Convert to long format
+long_data3t <- staterisky3t_mean %>%
+  gather(Technology, Mean_Score, -State) %>%
+  mutate(Technology = gsub("Mean_Risky_", "", Technology))
+
+# Order Technologies
+technology_order <- c("Coal", "Gas", "Nuclear", "Oil", "Hydro", "Wind", "Solar")
+long_data3t$Technology <- factor(long_data3t$Technology, levels = technology_order)
+
+cbbPalette <- c("#000000","#CC79A7","#F0E442","#E69F00","#56B4E9","#009E73","#D55E00")
+
+names(cbbPalette) <- technology_order
+
+# Order States (assuming you want an alphabetical order, modify as needed)
+states_order <- c( "Rajasthan", "Maharashtra", "Tamil Nadu", "Uttar Pradesh",  "West Bengal")
+long_data3t$State <- factor(long_data3t$State, levels = states_order)
+
+# Plot the graph
+stateplot3t <- ggplot(long_data3t, aes(x = State, y = Mean_Score, color = Technology, group = Technology)) +
+  geom_line(size = 0.7) +
+  geom_point(size = 2) +
+  labs(title = " ",
+       x = "State", y = "Means") +
+  ylim(1,5)+
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
+  scale_color_manual(values=cbbPalette)
+
+```
+
+```{r, echo= FALSE}
+
+# Reshape the data from wide to long format
+staterisky3t_long <- staterisky3t %>%
+  pivot_longer(
+    cols = starts_with("Risky_"),
+    names_to = "Technology",
+    values_to = "Riskiness"
+  ) %>%
+  mutate(Technology = sub("Risky_", "", Technology))
+
+# Calculate the sample size for each state
+
+state_sample_size3t <- staterisky3t %>%
+  group_by(State) %>%
+  summarize(n = n())
+
+# Join this back to the main data frame
+staterisky3t_long <- staterisky3t_long %>%
+  left_join(state_sample_size3t, by = "State")
+
+# Calculate the weighted mean for each technology in each state
+weighted_means3t <- staterisky3t_long %>%
+  group_by(State, Technology) %>%
+  summarize(weighted_mean = sum(Riskiness / n, na.rm = TRUE) / sum(1 / n, na.rm = TRUE), .groups = 'drop')
+
+```
+
+```{r, echo=FALSE}
+
+weighted_means3t$Technology <- factor(weighted_means3t$Technology, levels = technology_order)
+states_order <- c( "Rajasthan", "Maharashtra", "Tamil Nadu", "Uttar Pradesh",  "West Bengal")
+weighted_means3t$State <- factor(weighted_means3t$State, levels = states_order)
+
+stateplot3t2 <- ggplot(weighted_means3t, aes(x = State, y = weighted_mean, color = Technology, group = Technology)) +
+  geom_line(size = 0.7) +
+  geom_point(size = 2) +
+  labs(title = " ",
+       x = "State", y = "Weighted Means") +
+  ylim(0.5,4.5)+
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  scale_color_manual(values = cbbPalette)
+
+```
+
+```{r, echo=FALSE, fig.width=8, fig.height=4,out.width='100%', out.height='100%'}
+library(gridExtra)
+# mean perceived risk and zscores by state side by side
+
+spacer <- grid::rectGrob(gp = grid::gpar(col = "white"))
+
+grid.arrange(stateplot3t, spacer, stateplot3t2, ncol=3, widths=c(0.8, 0.06, 0.8))
+```
+
+## Zscores - 3 techs - solar, nuclear and coal
+
+```{r, echo = FALSE, fig.width=8, fig.height=4}
+
+# Extract only Nuclear
+nuclear_data <- staterisky3t_mean %>%
+  dplyr::select(State, Mean_Risky_Nuclear)%>%
+  mutate(
+    Z_Risky_Nuclear = (Mean_Risky_Nuclear - mean(Mean_Risky_Nuclear, na.rm = TRUE)) / 
+                      sd(Mean_Risky_Nuclear, na.rm = TRUE)
+  )
+
+mean_nuclear_state <- ggplot(nuclear_data, aes(x = State, y = Mean_Risky_Nuclear, group = 1)) +
+  geom_line(color = "#F0BA32", size = 1) +
+  geom_point(color = "#F0BA32", size = 3) +
+  labs(title = "Means: Perceived Risk of Nuclear Energy",
+       x = "State", y = "Mean Perceived Risk") +
+  theme_minimal() +
+  ylim(1,5)+
   theme(axis.text.x = element_text(angle = 45, hjust = 1))
 
-```
-
-```{r}
-# Using dplyr and tidyr
-
-standardized_data <- long_data %>%
-  group_by(Technology) %>%
+# Plot the z-scores
+zscore_nuclear_state <- ggplot(nuclear_data, aes(x = State, y = Z_Risky_Nuclear, group = 1)) +
+  geom_line(color = "#F0BA32", size = 1) +
+  geom_point(color = "#F0BA32", size = 3) +
+  labs(title = "Z-scores: Perceived Risk of Nuclear Energy",
+       x = "State", y = "Z-Score") +
+  ylim(-1 ,2)+
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+# Extract only Solar
+solar_data <- staterisky3t_mean %>%
+  dplyr::select(State, Mean_Risky_Solar)%>%
+  mutate(
+    Z_Risky_Solar = (Mean_Risky_Solar - mean(Mean_Risky_Solar, na.rm = TRUE)) / 
+                      sd(Mean_Risky_Solar, na.rm = TRUE)
+  )
+
+mean_solar_state <- ggplot(solar_data, aes(x = State, y = Mean_Risky_Solar, group = 1)) +
+  geom_line(color = "#D55E00", size = 1) +
+  geom_point(color = "#D55E00", size = 3) +
+  labs(title = "Means: Perceived Risk of Solar Energy",
+       x = "State", y = "Mean Perceived Risk") +
+  theme_minimal() +
+  ylim(1,5)+
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+# Plot the z-scores
+zscore_solar_state <- ggplot(solar_data, aes(x = State, y = Z_Risky_Solar, group = 1)) +
+  geom_line(color = "#D55E00", size = 1) +
+  geom_point(color = "#D55E00", size = 3) +
+  labs(title = "Z-scores: Perceived Risk of Solar Energy",
+       x = "State", y = "Z-Score") +
+  ylim(-1 ,2)+
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+# Extract only Coal
+coal_data <- staterisky3t_mean %>%
+  dplyr::select(State, Mean_Risky_Coal)%>%
+  mutate(
+    Z_Risky_Coal = (Mean_Risky_Coal - mean(Mean_Risky_Coal, na.rm = TRUE)) / 
+                      sd(Mean_Risky_Coal, na.rm = TRUE)
+  )
+
+mean_coal_state <- ggplot(coal_data, aes(x = State, y = Mean_Risky_Coal, group = 1)) +
+  geom_line(color = "#000000", size = 1) +
+  geom_point(color = "#000000", size = 3) +
+  labs(title = "Means: Perceived Risk of Coal",
+       x = "State", y = "Mean Perceived Risk") +
+  theme_minimal() +
+  ylim(1,5)+
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+# Plot the z-scores
+zscore_coal_state <- ggplot(coal_data, aes(x = State, y = Z_Risky_Coal, group = 1)) +
+  geom_line(color = "#000000", size = 1) +
+  geom_point(color = "#000000", size = 3) +
+  labs(title = "Z-scores: Perceived Risk of Coal",
+       x = "State", y = "Z-Score") +
+  ylim(-2 ,1)+
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+library(gridExtra)
+
+# Assuming mean_nuclear_state and zscore_nuclear_state are both ggplot objects
+
+# We'll add a spacer grob for spacing between plots
+spacer <- grid::rectGrob(gp = grid::gpar(col = "white"))
+
+grid.arrange(stateplot3t, spacer, zscore_nuclear_state, ncol=3, widths=c(0.8, 0.06, 0.8))
+
+grid.arrange(zscore_solar_state, spacer, zscore_coal_state, ncol=3, widths=c(0.8, 0.06, 0.8))
+
+```
+
+```{r, echo=FALSE}
+stateben <- joineddf %>%
+  dplyr::select(!starts_with(c("Ben_IND", "Risky_IND")))%>%
+  dplyr::select(starts_with("Ben"), State)
+
+stateben_mean <- stateben %>%
+  group_by(State) %>%
+  summarise(
+    Mean_Ben_Hydro = mean(Ben_Hydro, na.rm = TRUE),
+    Mean_Ben_Solar = mean(Ben_Solar, na.rm = TRUE),
+    Mean_Ben_Wind = mean(Ben_Wind, na.rm = TRUE),
+    Mean_Ben_Nuclear = mean(Ben_Nuclear, na.rm = TRUE),
+    Mean_Ben_Coal = mean(Ben_Coal, na.rm = TRUE),
+    Mean_Ben_Gas = mean(Ben_Gas, na.rm = TRUE),
+    Mean_Ben_Oil = mean(Ben_Oil, na.rm = TRUE)
+  )
+
+# Convert to long format
+long_data2 <- stateben_mean %>%
+  gather(Technology, Mean_Score, -State) %>%
+  mutate(Technology = gsub("Mean_Ben_", "", Technology))
+
+# Order Technologies
+technology_order <- c("Coal", "Gas", "Nuclear", "Oil", "Hydro", "Wind", "Solar")
+long_data2$Technology <- factor(long_data$Technology, levels = technology_order)
+
+cbbPalette <- c("#000000","#CC79A7","#F0E442","#E69F00","#56B4E9","#009E73","#D55E00")
+
+names(cbbPalette) <- technology_order
+
+# Order States (assuming you want an alphabetical order, modify as needed)
+states_order <- c( "Rajasthan", "Maharashtra", "Tamil Nadu", "Uttar Pradesh",  "West Bengal")
+long_data2$State <- factor(long_data2$State, levels = states_order)
+
+# Plot the graph
+stateplotben1 <- ggplot(long_data2, aes(x = State, y = Mean_Score, color = Technology, group = Technology)) +
+  geom_line(size = 0.7) +
+  geom_point(size = 2) +
+  labs(title = "Mean Perceived Benefit by State",
+       x = "State", y = "Mean Score") +
+  ylim(1,5)+
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
+  scale_color_manual(values=cbbPalette)
+```
+
+\newpage
+
+## Mean Perceived Benefit and Z-scores by State
+
+```{r, echo=FALSE}
+
+standardized_data2 <- long_data2 %>%
+  group_by(State) %>% #z scores are by state- that means mean_score - overall mean by state (including all technologies) divided by sd by state
   mutate(
@@
   ungroup() %>%
-  mutate(Standardized_Score = (Mean_Score - Overall_Mean) / Std_Dev) %>%
-  dplyr::select(-Overall_Mean, -Std_Dev)  #
+  mutate(Standardized_Score = (Mean_Score - Overall_Mean) / Std_Dev) #%>%
+  #dplyr::select(-Overall_Mean, -Std_Dev)  #
 
 # Order Technologies
-technology_order <- c("Nuclear", "Gas", "Coal", "Oil", "Hydro", "Wind", "Solar")
-standardized_data$Technology <- factor(standardized_data$Technology, levels = technology_order)
+standardized_data2$Technology <- factor(standardized_data2$Technology, levels = technology_order)
+
+stateplotben2 <- ggplot(standardized_data2, aes(x = State, y = Standardized_Score, color = Technology, group = Technology)) +
+  geom_line(size = 0.7) +
+  geom_point(size = 2) +
+  labs(title = "Z Scores for Perceived Benefit by State",
+       x = "State", y = "Z Score") +
+  ylim(-3,2)+
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  scale_color_manual(values = cbbPalette)
+
+```
+
+```{r, echo=FALSE, fig.width=8, fig.height=4, out.width='100%', out.height='100%'}
+library(gridExtra)
+# mean perceived risk and zscores by state side by side
+
+spacer <- grid::rectGrob(gp = grid::gpar(col = "white"))
+
+grid.arrange(stateplotben1, spacer, stateplotben2, ncol=3, widths=c(0.8, 0.06, 0.8))
+```
+
+\newpage
+
+## Mean Perceived Benefit and Z-scores by State - coal solar and nuclear
+
+```{r, echo = FALSE, fig.width=8, fig.height=4}
+
+staterisky_mean <- staterisky %>%
+  group_by(State) %>%
+  summarise(
+    Mean_Risky_Hydro = mean(Risky_Hydro, na.rm = TRUE),
+    Mean_Risky_Solar = mean(Risky_Solar, na.rm = TRUE),
+    Mean_Risky_Wind = mean(Risky_Wind, na.rm = TRUE),
+    Mean_Risky_Nuclear = mean(Risky_Nuclear, na.rm = TRUE),
+    Mean_Risky_Coal = mean(Risky_Coal, na.rm = TRUE),
+    Mean_Risky_Gas = mean(Risky_Gas, na.rm = TRUE),
+    Mean_Risky_Oil = mean(Risky_Oil, na.rm = TRUE)
+  )
+
+# Extract only Nuclear
+nuclear_data <- staterisky_mean %>%
+  dplyr::select(State, Mean_Risky_Nuclear)%>%
+  mutate(
+    Z_Risky_Nuclear = (Mean_Risky_Nuclear - mean(Mean_Risky_Nuclear, na.rm = TRUE)) / 
+                      sd(Mean_Risky_Nuclear, na.rm = TRUE)
+  )
+
+mean_nuclear_state <- ggplot(nuclear_data, aes(x = State, y = Mean_Risky_Nuclear, group = 1)) +
+  geom_line(color = "#F0BA32", size = 1) +
+  geom_point(color = "#F0BA32", size = 3) +
+  labs(title = "Means: Perceived Risk of Nuclear Energy",
+       x = "State", y = "Mean Perceived Risk") +
+  theme_minimal() +
+  ylim(1,5)+
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+# Plot the z-scores
+zscore_nuclear_state <- ggplot(nuclear_data, aes(x = State, y = Z_Risky_Nuclear, group = 1)) +
+  geom_line(color = "#F0BA32", size = 1) +
+  geom_point(color = "#F0BA32", size = 3) +
+  labs(title = "Z-scores: Perceived Risk of Nuclear Energy",
+       x = "State", y = "Z-Score") +
+  ylim(-1 ,2)+
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+library(gridExtra)
+
+# Assuming mean_nuclear_state and zscore_nuclear_state are both ggplot objects
+
+# We'll add a spacer grob for spacing between plots
+spacer <- grid::rectGrob(gp = grid::gpar(col = "white"))
+
+grid.arrange(mean_nuclear_state, spacer, zscore_nuclear_state, ncol=3, widths=c(0.8, 0.06, 0.8))
+
+```
+
+\newpage
+
+```{r, echo=FALSE}
+# Assuming you've already processed staterisky_mean as in your given code
+
+staterisky3 <- joineddf %>%
+  dplyr::select(!starts_with(c("Ben_IND", "Risky_IND")))%>%
+  dplyr::select(Risky_Solar,Risky_Nuclear, Risky_Coal, State)
+
+staterisky3_mean <- staterisky3 %>%
+  group_by(State) %>%
+  summarise(
+    Mean_Risky_Solar = mean(Risky_Solar, na.rm = TRUE),
+    Mean_Risky_Nuclear = mean(Risky_Nuclear, na.rm = TRUE),
+    Mean_Risky_Coal = mean(Risky_Coal, na.rm = TRUE),
+  )
+
+# Convert to long format
+long_data3 <- staterisky3_mean %>%
+  gather(Technology, Mean_Score, -State) %>%
+  mutate(Technology = gsub("Mean_Risky_", "", Technology))
+
+# Order Technologies
+technology_order <- c("Coal", "Gas", "Nuclear", "Oil", "Hydro", "Wind", "Solar")
+long_data3$Technology <- factor(long_data3$Technology, levels = technology_order)
+
+cbbPalette <- c("#000000","#CC79A7","#F0E442","#E69F00","#56B4E9","#009E73","#D55E00")
+
+names(cbbPalette) <- technology_order
+
+# Order States (assuming you want an alphabetical order, modify as needed)
+states_order <- c( "Rajasthan", "Maharashtra", "Tamil Nadu", "Uttar Pradesh",  "West Bengal")
+long_data3$State <- factor(long_data3$State, levels = states_order)
 
 # Plot the graph
-ggplot(standardized_data, aes(x = Technology, y = Standardized_Score, color = State, group = State)) +
-  geom_line(size = 1) +
-  geom_point(size = 3) +
-  labs(title = "Standardised Scores of Technologies by State",
-       x = "Technology", y = "Z Score") +
-  theme_minimal() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-
-```
-
-```{r}
-# Switch roles of State and Technology for plotting
-ggplot(standardized_data, aes(x = State, y = Standardized_Score, color = Technology, group = Technology)) +
-  geom_line(size = 1) +
-  geom_point(size = 3) +
-  labs(title = "Standardised Scores of Technologies by State",
-       x = "State", y = "Z Score") +
-  theme_minimal() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+stateplot3 <- ggplot(long_data3, aes(x = State, y = Mean_Score, color = Technology, group = Technology)) +
+  geom_line(size = 0.7) +
+  geom_point(size = 2) +
+  labs(title = "Mean Perceived Risk",
+       x = "State", y = "Mean Score") +
+  ylim(1,5)+
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
+  scale_color_manual(values=cbbPalette)
 
@@
 
-# combining risk and benefit from each energy technology
-
-acceptance <- joineddf_subset %>%
+staterisky_long <- staterisky_long %>%
+  group_by(State) %>%
+  mutate(Riskiness_Z = scale(Riskiness, center = TRUE, scale = TRUE))
+
+ggplot(staterisky_long, aes(x = Technology, y = Riskiness_Z, fill = State)) +
+  geom_boxplot() +
+  facet_wrap(~ State) +
+  theme_minimal() +
+  labs(title = "Boxplot of Riskiness Z-scores by State and Technology", 
+       x = "Technology", 
+       y = "Z-score")
+
+ggplot(staterisky_long, aes(x = Riskiness_Z, fill = Technology)) +
+  geom_density(alpha = 0.7) +
+  facet_wrap(~ State) +
+  theme_minimal() +
+  labs(title = "Density Plot of Riskiness Z-scores by State and Technology", 
+       x = "Z-score", 
+       y = "Density")
+
+technology_order <- c("Coal", "Gas", "Nuclear", "Oil", "Hydro", "Wind", "Solar")
+staterisky_long$Technology <- factor(staterisky_long$Technology, levels = technology_order)
+cbbPalette <- c("#000000","#CC79A7","#F0E442","#E69F00","#56B4E9","#009E73","#D55E00")
+
+names(cbbPalette) <- technology_order
+
+ggplot(staterisky_long, aes(x = Riskiness_Z, color = Technology)) +
+  geom_density() +
+  facet_wrap(~ State) +
+  theme_minimal() +
+  labs(title = "Density Plot of Riskiness Z-scores by State and Technology", 
+       x = "Z-score", 
+       y = "Density")+
+  scale_color_manual(values=cbbPalette)
+
+# Assuming you have the ggplot2 package loaded
+# Filter the dataset for only Coal, Nuclear, and Solar technologies
+filtered_data <- staterisky_long %>%
+  filter(Technology %in% c("Coal", "Nuclear", "Solar"))
+
+# Define your color palette (replace 'cbbPalette' with actual color values if needed)
+cbbPalette <- c("Coal" = "#000000", "Nuclear" = "#F0E442", "Solar" = "#D55E00")
+
+# Generate the plot
+ggplot(filtered_data, aes(x = Riskiness_Z, color = Technology)) +
+  geom_density() +
+  facet_wrap(~ State) +
+  theme_minimal() +
+  labs(title = "Density Plot of Riskiness Z-scores by State and Technology", 
+       x = "Z-score", 
+       y = "Density") +
+  scale_color_manual(values = cbbPalette)
+
+```
+
+```{r, echo=FALSE}
+
+# trying linear regression with acceptance scale
+
+joineddf_subset2 <- joineddf %>%
+  dplyr::select(!starts_with(c("Ben_IND", "Risky_IND")))%>%
+  dplyr::select(starts_with("Risky"), 
+         starts_with("Ben"), Uppercaste, Male, Hindu, Urban, age, State)
+
+acceptance2 <- joineddf_subset2 %>%
   na.omit()%>%
-  mutate(Nuclear = Ben_Nuclear - Risky_Nuclear,
-         Hyrdo = Ben_Hydro - Risky_Hydro,
-         Wind = Ben_Wind - Risky_Wind,
-         Solar = Ben_Solar - Risky_Solar,
-         Coal = Ben_Coal - Risky_Coal,
-         Gas = Ben_Gas - Risky_Gas,
-         Oil = Ben_Oil - Risky_Oil)%>%
-  select(-starts_with(c("Risky", "Ben")))
-
-#str(acceptance)
-
-# Compute the mean of each column
-mean_acceptance <- data.frame(col = names(acceptance), mean_val = sapply(acceptance, mean))
-
-# Compute standard error (not deviation)(divided by root of n)
-sem <- function(x) sqrt(var(x, na.rm = TRUE) / length(na.omit(x)))
-sem_acceptance <- data.frame(col = names(acceptance), sem_val = sapply(acceptance, sem))
-
-mean_acceptance <- merge(mean_acceptance, sem_acceptance, by = "col")
-
-# Plot
-ggplot(mean_acceptance, aes(x = col, y = mean_val, fill = ifelse(mean_val >= 0, 'Above 0', 'Below 0'))) + 
-  geom_bar(stat = "identity") +
-  geom_errorbar(aes(ymin = mean_val - sem_val, ymax = mean_val + sem_val), width = 0.2) +
-  geom_text(aes(label = round(mean_val, 2)), vjust = -0.9) +
-  scale_fill_manual(values = c('Above 0' = 'palegreen3', 'Below 0' = 'firebrick2')) +
-  labs(fill = "Legend") +
-  xlab("Energy Technologies") +
-  ylab("Mean Value") +
-  ggtitle("Benefit- Risk for Each Energy Technology") +
-  theme_minimal()+
-  ylim(-0.5, 1.75)
-
-```
+  mutate(NetBenNuclear = Ben_Nuclear - Risky_Nuclear,
+         NetBenHyrdo = Ben_Hydro - Risky_Hydro,
+         NetBenWind = Ben_Wind - Risky_Wind,
+         NetBenSolar = Ben_Solar - Risky_Solar,
+         NetBenCoal = Ben_Coal - Risky_Coal,
+         NetBenGas = Ben_Gas - Risky_Gas,
+         NetBenOil = Ben_Oil - Risky_Oil)%>%
+  dplyr::select(-starts_with(c("Risky", "Ben")))%>%
+  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
+                                      . == "25-34 years old" ~ 2,
+                                      . ==  "35-44 years old" ~3,
+                                      . == "45-54 years old" ~ 4,
+                                      . == "55-64 years old" ~ 5,
+                                      . == "65-74 years old" ~ 6,
+                                      . == "75 years or older" ~ 7)))
+
+alldemoslm4<- lm(NetBenNuclear ~ Uppercaste + Male + Hindu + Urban + age + State, data = acceptance2)
+#summary(alldemoslm3)
+
+salldemoslm4<- lm(NetBenSolar ~ Uppercaste + Male + Hindu + Urban + age + State, data = acceptance2)
+calldemoslm4<- lm(NetBenCoal ~ Uppercaste + Male + Hindu + Urban + age + State, data = acceptance2)
+
+```
+
+\blandscape
 \newpage
 
-# Solar Energy - Linear Regression models
-
-```{r, echo=FALSE}
-
-salldemos <- joineddf %>%
-            dplyr::select(Risky_Solar,Uppercaste, Male, Hindu, Urban, age, State)%>%
-            na.omit()
-
-salldemoslm1 <- lm(Risky_Solar ~ Uppercaste + Male + Hindu + Urban, data = salldemos)
-# Print model summary
-#summary(salldemoslm1)
-#plot(alldemoslm1)
-
-# lm suggests there is no significant white male effect or upper caste male effect for risk perception from nuclear energy in India. 
-# the coefficients are very small and so is the r squared - rsquared is minimal.
-
-# 2) lm with all demographic variables
-salldemoslm2<- lm(Risky_Solar ~ Uppercaste + Male + Hindu + Urban + age + State, data = salldemos)
-# Print model summary
-#summary(salldemoslm2)
-#plot(alldemoslm1)
-
-```
-
-## Only demographic variables
+## Linear Regression : Perceived Risk and Net Benefit- demographic variables including State
 
@@
 cat("\\begingroup")
+cat("\\small")  # Adjusts the font size
 cat("\\setlength{\\tabcolsep}{1pt}")
 cat("\\renewcommand{\\arraystretch}{0.7}")
-stargazer(salldemoslm1, salldemoslm2, 
-          title = "Results from 2 linear regression models",
+stargazer(alldemoslm2, salldemoslm2, calldemoslm2,alldemoslm4, salldemoslm4, calldemoslm4,
+          title = "Linear Models: Perceived Risk and Net Perceived Benefit(Nuclear, Solar and Coal)",
           type = "latex"
@@
 
-## Kahan Scale
+```{r, echo=FALSE, results='asis'}
+library(stargazer)
+
+#stargazer code for all demographic variable lms
+
+# stargazer code for all demographic variable linear models
+
+stargazer(alldemoslm2, salldemoslm2, calldemoslm2, alldemoslm4, salldemoslm4, calldemoslm4,
+          title = "Linear Models: Perceived Risk and Net Perceived Benefit (Nuclear, Solar and Coal)",
+          type = "html"
+          )
+
+```
+
+\elandscape
+
+```{r, echo=FALSE}
+
+stargazer(alldemoslm2, salldemoslm2, calldemoslm2, alldemoslm4, salldemoslm4, calldemoslm4, 
+          type = "text", # Choose "html" or "latex" for different formats
+          title = "Regression Models Summary",
+          align = TRUE)
+
+```
+
+\newpage
+
+# Claim 3: Cultural, Political and Economic Values
+
+```{r, echo = FALSE}
+
+library(lavaan)
+library(semTools)
+library(kableExtra)
+
+fascales <- codedmodule2 %>%
+  dplyr::select(starts_with(c("K_","Risky_Nuclear","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%
+  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
+                                      . == "25-34 years old" ~ 2,
+                                      . ==  "35-44 years old" ~3,
+                                      . == "45-54 years old" ~ 4,
+                                      . == "55-64 years old" ~ 5,
+                                      . == "65-74 years old" ~ 6,
+                                      . == "75 years or older" ~ 7))) %>%
+  na.omit()
+
+Kahan_fas <- '
+  KahanS =~ K_SHARM + K_SLIMCHOI + K_SPROTECT 
+  KahanH =~ K_HEQUAL+ K_ERADEQ1 + K_EWEALTH + K_ERADEQ2
+'
+Kahan_cfa <- cfa(Kahan_fas, data = fascales, std.lv = TRUE)
+
+Kahan_scores <- predict(Kahan_cfa, newdata = fascales)
+
+Kahan_Kscores <- cbind(fascales, Kahan_scores)
+
+```
+
+## CFA on eco-pol scale for Solar Energy
 
@@
 
-# RMSEA - between 0.05 and 0.08 (reasonable fit), less than 0.05 close fit and greater than 0.10 is poor fit 
-# CFI - greater than 0.90 or 0.95 indicates good fit
+sKahan_scores <- predict(sKahan_cfa, newdata = sfascales)
+
+sKahan_Kscores <- cbind(sfascales, sKahan_scores)
+
+sm1_kahan <- lm(Risky_Solar ~ Uppercaste + Male + Hindu + Urban + age + State + KahanS + KahanH , data = sKahan_Kscores)
+
+## CFA on ecopol vars for solar energy
+
+secopol_fas <- '
+  Pdevelop =~ HEALTHSOLAR + BEAUTYSOLAR + DISPLACESOLAR + POLLUTESOLAR + INDUSTRYSMALL + OWNERREG + MECHANISATION
+  Ndevelop =~ DEVSOLAR + PRIDESOLAR + NPRIDESOLAR + PROSPERSOLAR + JOBSSOLAR
+'
+
+secopol_cfa <- cfa(secopol_fas, data = sfascales, std.lv = TRUE)
+#summary(secopol_cfa, fit.measure= TRUE, standardized = TRUE)
+
+# Cronbach's alpha test on Pdevelop and Ndevelop for Solar energy
+
+solarpdevelop <- sfascales %>%
+  dplyr::select(HEALTHSOLAR, BEAUTYSOLAR, DISPLACESOLAR, POLLUTESOLAR, INDUSTRYSMALL, OWNERREG, MECHANISATION)%>%
+  na.omit()
+
+solarpdevelop.alpha <- psych::alpha(solarpdevelop, check.keys = TRUE)
+
+# alpha is strong at 0.75!
+
+solarndevelop <- sfascales %>%
+  dplyr::select(DEVSOLAR, PRIDESOLAR, NPRIDESOLAR, PROSPERSOLAR, JOBSSOLAR)%>%
+  na.omit()
+
+solarndevelop.alpha <- psych::alpha(solarndevelop, check.keys = TRUE)
+
+#alpha is strong at 0.86!
+
+```
+
+```{r, echo = FALSE}
+
+# Extract fit measures
+fitsecopol <- fitMeasures(secopol_cfa, fit.measures = c("CFI", "TLI", "RMSEA", "rmsea.ci.upper", "rmsea.ci.lower"))
+fitsecopol2 <- fitMeasures(secopol_cfa)
+# Convert to a data frame for presentation
+fitsecopoldf <- data.frame(Measure = names(fitsecopol), Value = fitsecopol) %>%
+  mutate(Measure = case_when(
+    Measure == "cfi" ~ "Comparative Fit Index (CFI) ",
+    Measure == "tli" ~ "Tucker-Lewis Index (TLI)",
+    Measure == "rmsea" ~ "Root Mean Square Error of Approximation(RMSEA)",
+    Measure == "rmsea.ci.upper" ~ "RMSEA 90 Percent confidence interval - lower",
+    Measure == "rmsea.ci.lower" ~ "RMSEA 90 Percent confidence interval - upper",
+    TRUE ~ as.character(Measure)
+  )) %>%
+  mutate(Value = round(Value, 3)) %>%
+  remove_rownames()
+
+#RMSEA - between 0.05 and 0.08 (reasonable fit), less than 0.05 close fit and greater than 0.10 is poor fit 
+#CFI - greater than 0.90 or 0.95 indicates good fit
 #TFI - CFI>TFI >0.90 - indicates good fit
-#pvalue should be greater than 0.05 p > 0.0.5
-
-# creating table of factor scores
-
-sKahan_scores <- predict(sKahan_cfa, newdata = sfascales)
-
-sKahan_Kscores <- cbind(sfascales, sKahan_scores)
-
-# 3) lm with kahan 
-sm1_kahan <- lm(Risky_Solar ~ Uppercaste + Male + Hindu + Urban + age + State + KahanS + KahanH , data = sKahan_Kscores)
-# Print model summary
-#summary(sm1_kahan)
-#plot(sm1_kahan)
-
-```
-
-```{r, echo=FALSE, results='asis'}
-library(stargazer)
-
-cat("\\begingroup")
-cat("\\setlength{\\tabcolsep}{1pt}")
-cat("\\renewcommand{\\arraystretch}{0.7}")
-stargazer(salldemoslm1, salldemoslm2, sm1_kahan,
-          title = "Results from 3 linear regression models",
-          type = "latex"
-)
-cat("\\endgroup")
+
+```
+
+```{r, echo =FALSE}
+# Display fit measures using kable
+#knitr::kable(fitsecopoldf, caption = "Fit Measures: CFA on eco-pol scale for Solar Energy", booktabs = TRUE) %>%
+  #kable_styling(latex_options = c("striped", "hold_position"))
+
+```
+
+```{r, echo=FALSE}
+
+# Extract parameter estimates
+paramssolar <- parameterEstimates(secopol_cfa, standardized = TRUE)%>%
+   slice(1:(n()-14))
+
+paramssolar1 <- paramssolar %>%
+  mutate(rhs = case_when(
+    rhs == "HEALTHSOLAR" ~ "Solar energy poses a great risk to the health of people living around it.",
+    rhs == "BEAUTYSOLAR" ~ "Solar energy spoils the natural beauty of the landscape.",
+    rhs == "DISPLACESOLAR" ~ "Solar energy is leading to displacement of people from their land.",
+    rhs == "POLLUTESOLAR" ~ "Solar energy increases pollution of air/water/land.",
+    rhs == "INDUSTRYSMALL" ~ "Large corporations are destroying the local industries in India and benefiting only a handful of people.",
+    rhs == "OWNERREG" ~ "Regardless of ownership, the government should pass strong regulations and implement them.",
+    rhs == "DEVSOLAR" ~ "Solar energy pushes forward the country's development.",
+    rhs == "PRIDESOLAR" ~ "I would be proud if my community used solar energy",
+    rhs == "NPRIDESOLAR" ~ "Solar energy is a mark of pride for our nation.",
+    rhs == "PROSPERSOLAR" ~ "Solar energy brings economic prosperity to the surrounding regions.",
+    rhs == "JOBSSOLAR" ~ "Solar energy will bring jobs to the local community.",
+    TRUE ~ as.character(rhs)
+  )) %>%
+  dplyr::select(!c(lhs,op, std.nox)) %>%
+    rename(
+    "Items" = rhs,
+    "Loadings" = est,
+    "Standard Error" = se,
+    "zvalue" = z) %>%
+  mutate(across(c("Loadings", "Standard Error", "zvalue"), round, 3))
+
+paramssolar1$Scale <- NA
+paramssolar1$Scale[1:6] <- "People Centered Development"
+paramssolar1$Scale[7:11] <- "Nationalist Development"
+paramssolar1<- paramssolar1[, c("Scale", setdiff(names(paramssolar1), "Scale"))]
+CFAsolar <- knitr::kable(paramssolar1, booktabs = TRUE, caption = "Confirmatory Factor Analysis(CFA) on newly developed eco-pol scale") %>%
+  kable_styling(latex_options = c("striped","scale_down", "hold_position", "repeat_header"))%>%
+  column_spec(column = 2, width = "4cm")
+
+# Print the table
+CFAsolar %>%
+  landscape()
 
@@
 \newpage
-
-# Coal
-
-```{r, echo=FALSE}
-
-calldemos <- joineddf %>%
-            dplyr::select(Risky_Coal,Uppercaste, Male, Hindu, Urban, age, State)%>%
-            na.omit()
-
-calldemoslm1 <- lm(Risky_Coal ~ Uppercaste + Male + Hindu + Urban, data = calldemos)
-# Print model summary
-#summary(salldemoslm1)
-#plot(alldemoslm1)
-
-# lm suggests there is no significant white male effect or upper caste male effect for risk perception from nuclear energy in India. 
-# the coefficients are very small and so is the r squared - rsquared is minimal.
-
-# 2) lm with all demographic variables
-calldemoslm2<- lm(Risky_Coal ~ Uppercaste + Male + Hindu + Urban + age + State, data = calldemos)
-# Print model summary
-#summary(salldemoslm2)
-#plot(alldemoslm1)
-
-```
-
-## Only demographic variables
-
-```{r, echo=FALSE, results='asis'}
-library(stargazer)
-
-#stargazer code for all demographic variable lms
-
-cat("\\begingroup")
-cat("\\setlength{\\tabcolsep}{1pt}")
-cat("\\renewcommand{\\arraystretch}{0.7}")
-stargazer(calldemoslm1, calldemoslm2, 
-          title = "Results from 2 linear regression models",
-          type = "latex"
-)
-cat("\\endgroup")
-
-```
-
-## Kahan Scale
+## CFA on eco-pol scale for Coal
 
 ```{r, echo = FALSE}
-# kahan scores for solar 
+# kahan scores for coal and CFA on ecopol vars  
 cfascales <- codedmodule2 %>%
-  dplyr::select(starts_with(c("K_","Risky_Coal","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACESOLAR",  "POLLUTESOLAR", "HEALTHSOLAR", "JOBSSOLAR", "BEAUTYSOLAR", "PRIDESOLAR", "NPRIDESOLAR", "DEVSOLAR", "PROSPERSOLAR", "RELYSOLAR", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%
+  dplyr::select(starts_with(c("K_","Risky_Coal","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACECOAL",  "POLLUTECOAL", "HEALTHCOAL", "JOBSCOAL", "BEAUTYCOAL", "PRIDECOAL", "NPRIDECOAL", "DEVCOAL", "PROSPERCOAL", "RELYCOAL", "Uppercaste", "Male", "Hindu", "Urban", "State","age"))) %>%
   na.omit()
@@
 
-# Print the summary of the CFA results, including fit measures
-#summary(sKahan_cfa, fit.measure= TRUE, standardized = TRUE)
-
-# RMSEA - between 0.05 and 0.08 (reasonable fit), less than 0.05 close fit and greater than 0.10 is poor fit 
-# CFI - greater than 0.90 or 0.95 indicates good fit
-#TFI - CFI>TFI >0.90 - indicates good fit
-#pvalue should be greater than 0.05 p > 0.0.5
-
-# creating table of factor scores
-
 cKahan_scores <- predict(cKahan_cfa, newdata = cfascales)
@@
 cKahan_Kscores <- cbind(cfascales, cKahan_scores)
+
+cecopol_fas <- '
+  Pdevelop =~ HEALTHCOAL + BEAUTYCOAL + DISPLACECOAL + POLLUTECOAL + INDUSTRYSMALL + OWNERREG + MECHANISATION
+  Ndevelop =~ DEVCOAL + PROSPERCOAL + JOBSCOAL + PRIDECOAL + NPRIDECOAL 
+'
+
+cecopol_cfa <- cfa(cecopol_fas, data = cfascales, std.lv = TRUE)
+#summary(cecopol_cfa, fit.measure= TRUE, standardized = TRUE)
 
@@
 
-```
-
-```{r, echo=FALSE, results='asis'}
-library(stargazer)
-
-cat("\\begingroup")
-cat("\\setlength{\\tabcolsep}{1pt}")
-cat("\\renewcommand{\\arraystretch}{0.7}")
-stargazer(calldemoslm1, calldemoslm2, cm1_kahan,
-          title = "Results from 3 linear regression models",
-          type = "latex"
-)
-cat("\\endgroup")
-
-```
+# Cronbach's alpha test on Pdevelop and Ndevelop for Solar energy
+
+coalpdevelop <- cfascales %>%
+  dplyr::select(HEALTHCOAL, BEAUTYCOAL, DISPLACECOAL, POLLUTECOAL, INDUSTRYSMALL, OWNERREG, MECHANISATION)%>%
+  na.omit()
+
+coalpdevelop.alpha <- psych::alpha(coalpdevelop, check.keys = TRUE)
+
+# alpha is strong at 0.78!
+
+coalndevelop <- cfascales %>%
+  dplyr::select(DEVCOAL, PRIDECOAL, NPRIDECOAL, PROSPERCOAL, JOBSCOAL,)%>%
+  na.omit()
+
+coalndevelop.alpha <- psych::alpha(coalndevelop, check.keys = TRUE)
+
+#alpha
+
+```
+
+```{r, echo = FALSE}
+
+# Extract fit measures
+fitcecopol <- fitMeasures(cecopol_cfa, fit.measures = c("CFI", "TLI", "RMSEA", "rmsea.ci.upper", "rmsea.ci.lower"))
+fitcecopol2 <- fitMeasures(cecopol_cfa)
+# Convert to a data frame for presentation
+fitcecopoldf <- data.frame(Measure = names(fitcecopol), Value = fitcecopol) %>%
+  mutate(Measure = case_when(
+    Measure == "cfi" ~ "Comparative Fit Index (CFI) ",
+    Measure == "tli" ~ "Tucker-Lewis Index (TLI)",
+    Measure == "rmsea" ~ "Root Mean Square Error of Approximation(RMSEA)",
+    Measure == "rmsea.ci.upper" ~ "RMSEA 90 Percent confidence interval - lower",
+    Measure == "rmsea.ci.lower" ~ "RMSEA 90 Percent confidence interval - upper",
+    TRUE ~ as.character(Measure)
+  )) %>%
+  mutate(Value = round(Value, 3)) %>%
+  remove_rownames()
+
+#RMSEA - between 0.05 and 0.08 (reasonable fit), less than 0.05 close fit and greater than 0.10 is poor fit 
+#CFI - greater than 0.90 or 0.95 indicates good fit
+#TFI - CFI>TFI >0.90 - indicates good fit
+
+```
+
+```{r, echo =FALSE}
+# Display fit measures using kable
+#knitr::kable(fitcecopoldf, caption = "Fit Measures: CFA on eco-pol scale for Coal", booktabs = TRUE) %>%
+  #kable_styling(latex_options = c("striped", "hold_position"))
+
+```
+
+```{r, echo=FALSE}
+
+# Extract parameter estimates
+paramscoal <- parameterEstimates(cecopol_cfa, standardized = TRUE)%>%
+   slice(1:(n()-12))
+
+paramscoal1 <- paramscoal %>%
+  mutate(rhs = case_when(
+    rhs == "HEALTHCOAL" ~ "Coal powered plants poses a great risk to the health of people living around it.",
+    rhs == "BEAUTYCOAL" ~ "Coal powered plants spoils the natural beauty of the landscape.",
+    rhs == "DISPLACECOAL" ~ "Coal powered plants is leading to displacement of people from their land.",
+    rhs == "POLLUTECOAL" ~ "Coal powered plants increases pollution of air/water/land.",
+    rhs == "INDUSTRYSMALL" ~ "Large corporations are destroying the local industries in India and benefiting only a handful of people.",
+    rhs == "OWNERREG" ~ "Regardless of ownership, the government should pass strong regulations and implement them.",
+    rhs == "DEVCOAL" ~ "Coal powered plants pushes forward the country's development.",
+    rhs == "PROSPERCOAL" ~ "Coal powered plants brings economic prosperity to the surrounding regions.",
+    rhs == "JOBSCOAL" ~ "Coal powered plants will bring jobs to the local community.",
+    TRUE ~ as.character(rhs)
+  )) %>%
+  dplyr::select(!c(lhs,op, std.nox)) %>%
+    rename(
+    "Items" = rhs,
+    "Loadings" = est,
+    "Standard Error" = se,
+    "zvalue" = z) %>%
+  mutate(across(c("Loadings", "Standard Error", "zvalue"), round, 3))
+
+paramscoal1$Scale <- NA
+paramscoal1$Scale[1:6] <- "People Centered Development"
+paramscoal1$Scale[7:9] <- "Nationalist Development"
+paramscoal1<- paramscoal1[, c("Scale", setdiff(names(paramscoal1), "Scale"))]
+CFAcoal <- knitr::kable(paramscoal1, booktabs = TRUE, caption = "Confirmatory Factor Analysis(CFA) on newly developed eco-pol scale") %>%
+  kable_styling(latex_options = c("striped","scale_down", "hold_position", "repeat_header"))%>%
+  column_spec(column = 2, width = "4cm")
+
+# Print the table
+CFAcoal %>%
+  landscape()
+
+```

### 2024-01-15 nuclear-in-comparison.tex
commiting after a long time. oh god

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\title{nuclear energy in comparison}
\author{}
\date{\vspace{-2.5em}}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={nuclear energy in comparison},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\begin{document}
\maketitle

{
\setcounter{tocdepth}{2}
\tableofcontents
}
\hypertarget{abstract}{%
\section{Abstract}\label{abstract}}

\newpage

\hypertarget{h1-nuclear-energy-will-be-seen-as-riskier-than-other-energy-technologies-in-india.-this-paper-explores-nuclear-energy-in-comparison-with-other-technologies}{%
\section{H1: Nuclear Energy will be seen as riskier than other energy
technologies in India. this paper explores nuclear energy in comparison
with other
technologies}\label{h1-nuclear-energy-will-be-seen-as-riskier-than-other-energy-technologies-in-india.-this-paper-explores-nuclear-energy-in-comparison-with-other-technologies}}

\hypertarget{likert-responses-n-2160}{%
\subsection{Likert Responses (n= 2160)}\label{likert-responses-n-2160}}

The percentages are rounded off to whole numbers.

\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-5-1.pdf}
\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-5-2.pdf}

\newpage

\hypertarget{introduction-mean-perceived-risk-and-mean-perceived-benefit-for-all-energy-technologies.}{%
\subsection{Introduction: Mean Perceived Risk and Mean Perceived Benefit
for all energy
technologies.}\label{introduction-mean-perceived-risk-and-mean-perceived-benefit-for-all-energy-technologies.}}

\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-7-1.pdf}

\hypertarget{boxplot-for-perceived-benefit-and-perceived-risk-by-technology}{%
\subsection{Boxplot for perceived benefit and perceived risk by
technology}\label{boxplot-for-perceived-benefit-and-perceived-risk-by-technology}}

\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-8-1.pdf}

\newpage

\hypertarget{pairwise-t-test-mean-perceived-risk-and-mean-perceived-benefit-all-energy-technologies}{%
\subsection{Pairwise T-test: Mean perceived risk and mean perceived
benefit (all energy
technologies)}\label{pairwise-t-test-mean-perceived-risk-and-mean-perceived-benefit-all-energy-technologies}}

The red and green pairs indicate that there is a statistically
significant difference between the means of the two groups. White and
grey indicate - no differences between the means of the two groups.

\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-9-1.pdf}

\newpage

\hypertarget{benefit---risk-for-each-technology}{%
\subsection{Benefit - Risk for each
technology}\label{benefit---risk-for-each-technology}}

\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-10-1.pdf}

\newpage

\hypertarget{claim-1-demographic-variables-nuclear-solar-coal}{%
\section{Claim 1: Demographic variables: nuclear, solar,
coal}\label{claim-1-demographic-variables-nuclear-solar-coal}}

\begin{landscape}

\hypertarget{linear-regression-with-demographic-variables-caste-religion-gender-and-age}{%
\subsection{Linear Regression with demographic variables (caste,
religion, gender and
age)}\label{linear-regression-with-demographic-variables-caste-religion-gender-and-age}}

\begingroup\small\setlength{\tabcolsep}{1pt}\renewcommand{\arraystretch}{0.7}

\% Table created by stargazer v.5.2.3 by Marek Hlavac, Social Policy
Institute. E-mail: marek.hlavac at gmail.com \% Date and time: Wed, Jan
10, 2024 - 09:43:59

\begin{table}[!htbp] \centering 
  \caption{Linear Models: Perceived Risk and Net Perceived Benefit(Nuclear, Solar and Coal)} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
\cline{2-7} 
\\[-1.8ex] & RiskNuclear & RiskSolar & RiskCoal & NetBenNuclear & NetBenSolar & NetBenCoal \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
\hline \\[-1.8ex] 
 Uppercaste & 0.106 & $-$0.065 & 0.051 & $-$0.199$^{**}$ & $-$0.020 & $-$0.096 \\ 
  & (0.066) & (0.059) & (0.060) & (0.093) & (0.094) & (0.075) \\ 
  & & & & & & \\ 
 Male & 0.122$^{*}$ & $-$0.291$^{***}$ & 0.056 & $-$0.046 & 0.456$^{***}$ & $-$0.004 \\ 
  & (0.066) & (0.060) & (0.061) & (0.095) & (0.096) & (0.076) \\ 
  & & & & & & \\ 
 Hindu & $-$0.115 & $-$0.237$^{***}$ & 0.017 & 0.400$^{***}$ & 0.501$^{***}$ & 0.039 \\ 
  & (0.076) & (0.068) & (0.070) & (0.106) & (0.107) & (0.085) \\ 
  & & & & & & \\ 
 UrbanUrban & $-$0.099 & 0.521$^{***}$ & 0.110$^{*}$ & 0.390$^{***}$ & $-$0.711$^{***}$ & $-$0.015 \\ 
  & (0.065) & (0.058) & (0.059) & (0.092) & (0.093) & (0.073) \\ 
  & & & & & & \\ 
 age & 0.050$^{*}$ & $-$0.070$^{***}$ & 0.012 & $-$0.116$^{***}$ & 0.187$^{***}$ & $-$0.038 \\ 
  & (0.029) & (0.026) & (0.026) & (0.044) & (0.045) & (0.036) \\ 
  & & & & & & \\ 
 Constant & 3.309$^{***}$ & 2.325$^{***}$ & 3.005$^{***}$ & $-$0.355$^{**}$ & 0.835$^{***}$ & 0.059 \\ 
  & (0.108) & (0.097) & (0.099) & (0.154) & (0.156) & (0.124) \\ 
  & & & & & & \\ 
\hline \\[-1.8ex] 
Observations & 1,444 & 1,444 & 1,444 & 1,183 & 1,183 & 1,183 \\ 
R$^{2}$ & 0.012 & 0.100 & 0.003 & 0.041 & 0.122 & 0.003 \\ 
Adjusted R$^{2}$ & 0.009 & 0.097 & 0.00003 & 0.037 & 0.118 & $-$0.001 \\ 
Residual Std. Error & 1.176 (df = 1438) & 1.053 (df = 1438) & 1.080 (df = 1438) & 1.517 (df = 1177) & 1.533 (df = 1177) & 1.217 (df = 1177) \\ 
F Statistic & 3.552$^{***}$ (df = 5; 1438) & 31.870$^{***}$ (df = 5; 1438) & 1.010 (df = 5; 1438) & 10.122$^{***}$ (df = 5; 1177) & 32.725$^{***}$ (df = 5; 1177) & 0.705 (df = 5; 1177) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 
\endgroup

\end{landscape}

\begin{verbatim}
## 
## Regression Models Summary
## ================================================================================================================================================================
##                                                                                 Dependent variable:                                                             
##                     --------------------------------------------------------------------------------------------------------------------------------------------
##                           RiskNuclear              RiskSolar               RiskCoal            NetBenNuclear             NetBenSolar             NetBenCoal     
##                               (1)                     (2)                    (3)                    (4)                      (5)                    (6)         
## ----------------------------------------------------------------------------------------------------------------------------------------------------------------
## Uppercaste                   0.106                   -0.065                 0.051                 -0.199**                  -0.020                 -0.096       
##                             (0.066)                 (0.059)                (0.060)                (0.093)                  (0.094)                (0.075)       
##                                                                                                                                                                 
## Male                        0.122*                 -0.291***                0.056                  -0.046                  0.456***                -0.004       
##                             (0.066)                 (0.060)                (0.061)                (0.095)                  (0.096)                (0.076)       
##                                                                                                                                                                 
## Hindu                       -0.115                 -0.237***                0.017                 0.400***                 0.501***                0.039        
##                             (0.076)                 (0.068)                (0.070)                (0.106)                  (0.107)                (0.085)       
##                                                                                                                                                                 
## UrbanUrban                  -0.099                  0.521***                0.110*                0.390***                -0.711***                -0.015       
##                             (0.065)                 (0.058)                (0.059)                (0.092)                  (0.093)                (0.073)       
##                                                                                                                                                                 
## age                         0.050*                 -0.070***                0.012                -0.116***                 0.187***                -0.038       
##                             (0.029)                 (0.026)                (0.026)                (0.044)                  (0.045)                (0.036)       
##                                                                                                                                                                 
## Constant                   3.309***                 2.325***               3.005***               -0.355**                 0.835***                0.059        
##                             (0.108)                 (0.097)                (0.099)                (0.154)                  (0.156)                (0.124)       
##                                                                                                                                                                 
## ----------------------------------------------------------------------------------------------------------------------------------------------------------------
## Observations                 1,444                   1,444                  1,444                  1,183                    1,183                  1,183        
## R2                           0.012                   0.100                  0.003                  0.041                    0.122                  0.003        
## Adjusted R2                  0.009                   0.097                 0.00003                 0.037                    0.118                  -0.001       
## Residual Std. Error    1.176 (df = 1438)       1.053 (df = 1438)      1.080 (df = 1438)      1.517 (df = 1177)        1.533 (df = 1177)      1.217 (df = 1177)  
## F Statistic         3.552*** (df = 5; 1438) 31.870*** (df = 5; 1438) 1.010 (df = 5; 1438) 10.122*** (df = 5; 1177) 32.725*** (df = 5; 1177) 0.705 (df = 5; 1177)
## ================================================================================================================================================================
## Note:                                                                                                                                *p<0.1; **p<0.05; ***p<0.01
\end{verbatim}

\newpage

\hypertarget{claim-2-regional-differences}{%
\section{Claim 2: Regional
differences}\label{claim-2-regional-differences}}

We see huge differences for perceived risk and perceived benefit for
each technology from state to state. These graphs explore that. The
number of respondents from each state are also reported below.

\hypertarget{perceived-risk-by-state}{%
\subsection{Perceived risk by State}\label{perceived-risk-by-state}}

\begin{verbatim}
##   Maharashtra     Rajasthan    Tamil Nadu Uttar Pradesh   West Bengal 
##           653           677           320           125           386
\end{verbatim}

\includegraphics[width=0.8\linewidth,height=0.8\textheight]{nuclear-in-comparison_files/figure-latex/unnamed-chunk-15-1}

\newpage

\hypertarget{perceived-benefit-by-state}{%
\subsection{Perceived Benefit by
State}\label{perceived-benefit-by-state}}

\begin{verbatim}
##   Maharashtra     Rajasthan    Tamil Nadu Uttar Pradesh   West Bengal 
##           653           677           320           125           386
\end{verbatim}

\includegraphics[width=1\linewidth,height=1\textheight]{nuclear-in-comparison_files/figure-latex/unnamed-chunk-16-1}
\#\# Radar chart - risk and benefit by state

\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-18-1.pdf}
\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-18-2.pdf}
\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-18-3.pdf}
\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-18-4.pdf}
\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-18-5.pdf}

\hypertarget{net-benefit-by-state}{%
\subsection{Net benefit by state}\label{net-benefit-by-state}}

\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-20-1.pdf}

\newpage

\hypertarget{mean-perceived-risk-and-weighted-mean}{%
\subsection{Mean Perceived Risk and Weighted
Mean}\label{mean-perceived-risk-and-weighted-mean}}

\includegraphics[width=1\linewidth,height=1\textheight]{nuclear-in-comparison_files/figure-latex/unnamed-chunk-24-1}

\newpage

\hypertarget{mean-perceived-risk-and-weighten-means-by-technologies--solar-coal-and-nuclear}{%
\subsection{Mean Perceived risk and weighten means by Technologies-
solar, coal and
nuclear}\label{mean-perceived-risk-and-weighten-means-by-technologies--solar-coal-and-nuclear}}

\includegraphics[width=1\linewidth,height=1\textheight]{nuclear-in-comparison_files/figure-latex/unnamed-chunk-28-1}

\hypertarget{zscores---3-techs---solar-nuclear-and-coal}{%
\subsection{Zscores - 3 techs - solar, nuclear and
coal}\label{zscores---3-techs---solar-nuclear-and-coal}}

\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-29-1.pdf}
\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-29-2.pdf}

\newpage

\hypertarget{mean-perceived-benefit-and-z-scores-by-state}{%
\subsection{Mean Perceived Benefit and Z-scores by
State}\label{mean-perceived-benefit-and-z-scores-by-state}}

\includegraphics[width=1\linewidth,height=1\textheight]{nuclear-in-comparison_files/figure-latex/unnamed-chunk-32-1}

\newpage

\hypertarget{mean-perceived-benefit-and-z-scores-by-state---coal-solar-and-nuclear}{%
\subsection{Mean Perceived Benefit and Z-scores by State - coal solar
and
nuclear}\label{mean-perceived-benefit-and-z-scores-by-state---coal-solar-and-nuclear}}

\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-33-1.pdf}

\newpage

\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-35-1.pdf}
\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-35-2.pdf}
\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-35-3.pdf}
\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-35-4.pdf}

\begin{landscape}
\newpage

\hypertarget{linear-regression-perceived-risk-and-net-benefit--demographic-variables-including-state}{%
\subsection{Linear Regression : Perceived Risk and Net Benefit-
demographic variables including
State}\label{linear-regression-perceived-risk-and-net-benefit--demographic-variables-including-state}}

\begingroup\small\setlength{\tabcolsep}{1pt}

\renewcommand{\arraystretch}{0.7}

\% Table created by stargazer v.5.2.3 by Marek Hlavac, Social Policy
Institute. E-mail: marek.hlavac at gmail.com \% Date and time: Wed, Jan
10, 2024 - 09:44:22

\begin{table}[!htbp] \centering 
  \caption{Linear Models: Perceived Risk and Net Perceived Benefit(Nuclear, Solar and Coal)} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
\cline{2-7} 
\\[-1.8ex] & RiskNuclear & RiskSolar & RiskCoal & NetBenNuclear & NetBenSolar & NetBenCoal \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
\hline \\[-1.8ex] 
 Uppercaste & $-$0.135$^{**}$ & $-$0.006 & $-$0.056 & 0.026 & $-$0.146$^{*}$ & $-$0.021 \\ 
  & (0.061) & (0.051) & (0.058) & (0.089) & (0.084) & (0.075) \\ 
  & & & & & & \\ 
 Male & 0.045 & $-$0.047 & 0.015 & 0.008 & 0.058 & $-$0.016 \\ 
  & (0.062) & (0.053) & (0.059) & (0.092) & (0.087) & (0.078) \\ 
  & & & & & & \\ 
 Hindu & $-$0.047 & $-$0.057 & 0.099 & 0.362$^{***}$ & 0.290$^{***}$ & $-$0.008 \\ 
  & (0.070) & (0.059) & (0.066) & (0.100) & (0.095) & (0.085) \\ 
  & & & & & & \\ 
 UrbanUrban & 0.052 & $-$0.076 & 0.055 & 0.172$^{*}$ & 0.143 & 0.014 \\ 
  & (0.067) & (0.056) & (0.063) & (0.099) & (0.093) & (0.084) \\ 
  & & & & & & \\ 
 age & $-$0.015 & 0.045$^{**}$ & 0.053$^{**}$ & $-$0.008 & 0.045 & $-$0.035 \\ 
  & (0.027) & (0.023) & (0.025) & (0.043) & (0.040) & (0.036) \\ 
  & & & & & & \\ 
 StateRajasthan & 0.222$^{**}$ & $-$1.285$^{***}$ & 0.234$^{***}$ & $-$0.014 & 1.957$^{***}$ & 0.077 \\ 
  & (0.094) & (0.080) & (0.090) & (0.135) & (0.128) & (0.115) \\ 
  & & & & & & \\ 
 StateTamil Nadu & $-$0.242$^{**}$ & $-$1.547$^{***}$ & $-$1.103$^{***}$ & $-$0.625$^{***}$ & 2.027$^{***}$ & 0.795$^{***}$ \\ 
  & (0.099) & (0.084) & (0.094) & (0.191) & (0.181) & (0.162) \\ 
  & & & & & & \\ 
 StateUttar Pradesh & $-$0.178 & $-$1.344$^{***}$ & $-$0.638$^{***}$ & $-$0.250 & 1.612$^{***}$ & 0.296$^{**}$ \\ 
  & (0.120) & (0.102) & (0.114) & (0.177) & (0.168) & (0.151) \\ 
  & & & & & & \\ 
 StateWest Bengal & 1.276$^{***}$ & $-$1.330$^{***}$ & 0.071 & $-$1.522$^{***}$ & 1.853$^{***}$ & $-$0.222$^{**}$ \\ 
  & (0.083) & (0.071) & (0.079) & (0.125) & (0.118) & (0.106) \\ 
  & & & & & & \\ 
 Constant & 3.208$^{***}$ & 2.752$^{***}$ & 3.053$^{***}$ & $-$0.240 & 0.323$^{**}$ & 0.022 \\ 
  & (0.100) & (0.084) & (0.095) & (0.147) & (0.139) & (0.124) \\ 
  & & & & & & \\ 
\hline \\[-1.8ex] 
Observations & 1,444 & 1,444 & 1,444 & 1,183 & 1,183 & 1,183 \\ 
R$^{2}$ & 0.204 & 0.353 & 0.141 & 0.171 & 0.338 & 0.035 \\ 
Adjusted R$^{2}$ & 0.199 & 0.349 & 0.136 & 0.165 & 0.333 & 0.028 \\ 
Residual Std. Error & 1.057 (df = 1434) & 0.894 (df = 1434) & 1.004 (df = 1434) & 1.413 (df = 1173) & 1.334 (df = 1173) & 1.199 (df = 1173) \\ 
F Statistic & 40.720$^{***}$ (df = 9; 1434) & 86.983$^{***}$ (df = 9; 1434) & 26.208$^{***}$ (df = 9; 1434) & 26.873$^{***}$ (df = 9; 1173) & 66.499$^{***}$ (df = 9; 1173) & 4.789$^{***}$ (df = 9; 1173) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 
\endgroup

Linear Models: Perceived Risk and Net Perceived Benefit (Nuclear, Solar
and Coal)

Dependent variable:

RiskNuclear

RiskSolar

RiskCoal

NetBenNuclear

NetBenSolar

NetBenCoal

(1)

(2)

(3)

(4)

(5)

(6)

Uppercaste

-0.135**

-0.006

-0.056

0.026

-0.146*

-0.021

(0.061)

(0.051)

(0.058)

(0.089)

(0.084)

(0.075)

Male

0.045

-0.047

0.015

0.008

0.058

-0.016

(0.062)

(0.053)

(0.059)

(0.092)

(0.087)

(0.078)

Hindu

-0.047

-0.057

0.099

0.362***

0.290***

-0.008

(0.070)

(0.059)

(0.066)

(0.100)

(0.095)

(0.085)

UrbanUrban

0.052

-0.076

0.055

0.172*

0.143

0.014

(0.067)

(0.056)

(0.063)

(0.099)

(0.093)

(0.084)

age

-0.015

0.045**

0.053**

-0.008

0.045

-0.035

(0.027)

(0.023)

(0.025)

(0.043)

(0.040)

(0.036)

StateRajasthan

0.222**

-1.285***

0.234***

-0.014

1.957***

0.077

(0.094)

(0.080)

(0.090)

(0.135)

(0.128)

(0.115)

StateTamil Nadu

-0.242**

-1.547***

-1.103***

-0.625***

2.027***

0.795***

(0.099)

(0.084)

(0.094)

(0.191)

(0.181)

(0.162)

StateUttar Pradesh

-0.178

-1.344***

-0.638***

-0.250

1.612***

0.296**

(0.120)

(0.102)

(0.114)

(0.177)

(0.168)

(0.151)

StateWest Bengal

1.276***

-1.330***

0.071

-1.522***

1.853***

-0.222**

(0.083)

(0.071)

(0.079)

(0.125)

(0.118)

(0.106)

Constant

3.208***

2.752***

3.053***

-0.240

0.323**

0.022

(0.100)

(0.084)

(0.095)

(0.147)

(0.139)

(0.124)

Observations

1,444

1,444

1,444

1,183

1,183

1,183

R2

0.204

0.353

0.141

0.171

0.338

0.035

Adjusted R2

0.199

0.349

0.136

0.165

0.333

0.028

Residual Std. Error

1.057 (df = 1434)

0.894 (df = 1434)

1.004 (df = 1434)

1.413 (df = 1173)

1.334 (df = 1173)

1.199 (df = 1173)

F Statistic

40.720*** (df = 9; 1434)

86.983*** (df = 9; 1434)

26.208*** (df = 9; 1434)

26.873*** (df = 9; 1173)

66.499*** (df = 9; 1173)

4.789*** (df = 9; 1173)

Note:

\emph{p\textless0.1; \textbf{p\textless0.05; }}p\textless0.01

\end{landscape}

\newpage

\hypertarget{claim-3-cultural-political-and-economic-values}{%
\section{Claim 3: Cultural, Political and Economic
Values}\label{claim-3-cultural-political-and-economic-values}}

\hypertarget{cfa-on-eco-pol-scale-for-solar-energy}{%
\subsection{CFA on eco-pol scale for Solar
Energy}\label{cfa-on-eco-pol-scale-for-solar-energy}}

\begin{landscape}\begin{table}[!h]

\caption{\label{tab:unnamed-chunk-43}Confirmatory Factor Analysis(CFA) on newly developed eco-pol scale}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{l>{\raggedright\arraybackslash}p{4cm}rrrrrrrr}
\toprule
Scale & Items & Loadings & Standard Error & zvalue & pvalue & ci.lower & ci.upper & std.lv & std.all\\
\midrule
\cellcolor{gray!6}{People Centered Development} & \cellcolor{gray!6}{Solar energy poses a great risk to the health of people living around it.} & \cellcolor{gray!6}{0.965} & \cellcolor{gray!6}{0.050} & \cellcolor{gray!6}{19.455} & \cellcolor{gray!6}{0e+00} & \cellcolor{gray!6}{0.8678100} & \cellcolor{gray!6}{1.0622499} & \cellcolor{gray!6}{0.9650299} & \cellcolor{gray!6}{0.7747043}\\
People Centered Development & Solar energy spoils the natural beauty of the landscape. & 0.820 & 0.052 & 15.714 & 0e+00 & 0.7177752 & 0.9223481 & 0.8200617 & 0.6560430\\
\cellcolor{gray!6}{People Centered Development} & \cellcolor{gray!6}{Solar energy is leading to displacement of people from their land.} & \cellcolor{gray!6}{0.692} & \cellcolor{gray!6}{0.050} & \cellcolor{gray!6}{13.800} & \cellcolor{gray!6}{0e+00} & \cellcolor{gray!6}{0.5939852} & \cellcolor{gray!6}{0.7906393} & \cellcolor{gray!6}{0.6923123} & \cellcolor{gray!6}{0.5906886}\\
People Centered Development & Solar energy increases pollution of air/water/land. & 1.096 & 0.050 & 21.706 & 0e+00 & 0.9970923 & 1.1950355 & 1.0960639 & 0.8411179\\
\cellcolor{gray!6}{People Centered Development} & \cellcolor{gray!6}{Large corporations are destroying the local industries in India and benefiting only a handful of people.} & \cellcolor{gray!6}{0.287} & \cellcolor{gray!6}{0.058} & \cellcolor{gray!6}{4.972} & \cellcolor{gray!6}{7e-07} & \cellcolor{gray!6}{0.1741052} & \cellcolor{gray!6}{0.4007040} & \cellcolor{gray!6}{0.2874046} & \cellcolor{gray!6}{0.2317296}\\
\addlinespace
People Centered Development & Regardless of ownership, the government should pass strong regulations and implement them. & 0.296 & 0.052 & 5.733 & 0e+00 & 0.1949541 & 0.3974941 & 0.2962241 & 0.2659785\\
\cellcolor{gray!6}{Nationalist Development} & \cellcolor{gray!6}{MECHANISATION} & \cellcolor{gray!6}{-0.445} & \cellcolor{gray!6}{0.052} & \cellcolor{gray!6}{-8.501} & \cellcolor{gray!6}{0e+00} & \cellcolor{gray!6}{-0.5481301} & \cellcolor{gray!6}{-0.3427323} & \cellcolor{gray!6}{-0.4454312} & \cellcolor{gray!6}{-0.3859243}\\
Nationalist Development & Solar energy pushes forward the country's development. & 1.042 & 0.046 & 22.549 & 0e+00 & 0.9518805 & 1.1331082 & 1.0424943 & 0.8341064\\
\cellcolor{gray!6}{Nationalist Development} & \cellcolor{gray!6}{I would be proud if my community used solar energy} & \cellcolor{gray!6}{1.042} & \cellcolor{gray!6}{0.047} & \cellcolor{gray!6}{21.934} & \cellcolor{gray!6}{0e+00} & \cellcolor{gray!6}{0.9485906} & \cellcolor{gray!6}{1.1347564} & \cellcolor{gray!6}{1.0416735} & \cellcolor{gray!6}{0.8187225}\\
Nationalist Development & Solar energy is a mark of pride for our nation. & 0.959 & 0.047 & 20.244 & 0e+00 & 0.8658229 & 1.0514501 & 0.9586365 & 0.7748161\\
\addlinespace
\cellcolor{gray!6}{Nationalist Development} & \cellcolor{gray!6}{Solar energy brings economic prosperity to the surrounding regions.} & \cellcolor{gray!6}{0.980} & \cellcolor{gray!6}{0.047} & \cellcolor{gray!6}{20.803} & \cellcolor{gray!6}{0e+00} & \cellcolor{gray!6}{0.8876975} & \cellcolor{gray!6}{1.0723692} & \cellcolor{gray!6}{0.9800333} & \cellcolor{gray!6}{0.7896156}\\
NA & Solar energy will bring jobs to the local community. & 0.641 & 0.051 & 12.542 & 0e+00 & 0.5406190 & 0.7408777 & 0.6407483 & 0.5339818\\
\cellcolor{gray!6}{NA} & \cellcolor{gray!6}{Solar energy poses a great risk to the health of people living around it.} & \cellcolor{gray!6}{0.620} & \cellcolor{gray!6}{0.054} & \cellcolor{gray!6}{11.424} & \cellcolor{gray!6}{0e+00} & \cellcolor{gray!6}{0.5139817} & \cellcolor{gray!6}{0.7268665} & \cellcolor{gray!6}{0.6204241} & \cellcolor{gray!6}{0.3998333}\\
\bottomrule
\end{tabular}}
\end{table}
\end{landscape}

\newpage

\hypertarget{cfa-on-eco-pol-scale-for-coal}{%
\subsection{CFA on eco-pol scale for
Coal}\label{cfa-on-eco-pol-scale-for-coal}}

\begin{landscape}\begin{table}[!h]

\caption{\label{tab:unnamed-chunk-47}Confirmatory Factor Analysis(CFA) on newly developed eco-pol scale}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{l>{\raggedright\arraybackslash}p{4cm}rrrrrrrr}
\toprule
Scale & Items & Loadings & Standard Error & zvalue & pvalue & ci.lower & ci.upper & std.lv & std.all\\
\midrule
\cellcolor{gray!6}{People Centered Development} & \cellcolor{gray!6}{Coal powered plants poses a great risk to the health of people living around it.} & \cellcolor{gray!6}{0.713} & \cellcolor{gray!6}{0.051} & \cellcolor{gray!6}{14.083} & \cellcolor{gray!6}{0.0e+00} & \cellcolor{gray!6}{0.6140727} & \cellcolor{gray!6}{0.8126265} & \cellcolor{gray!6}{0.7133496} & \cellcolor{gray!6}{0.6482214}\\
People Centered Development & Coal powered plants spoils the natural beauty of the landscape. & 0.714 & 0.048 & 14.818 & 0.0e+00 & 0.6198092 & 0.8087672 & 0.7142882 & 0.6750268\\
\cellcolor{gray!6}{People Centered Development} & \cellcolor{gray!6}{Coal powered plants is leading to displacement of people from their land.} & \cellcolor{gray!6}{0.628} & \cellcolor{gray!6}{0.055} & \cellcolor{gray!6}{11.376} & \cellcolor{gray!6}{0.0e+00} & \cellcolor{gray!6}{0.5195755} & \cellcolor{gray!6}{0.7358706} & \cellcolor{gray!6}{0.6277231} & \cellcolor{gray!6}{0.5432527}\\
People Centered Development & Coal powered plants increases pollution of air/water/land. & 0.640 & 0.041 & 15.561 & 0.0e+00 & 0.5590262 & 0.7201432 & 0.6395847 & 0.7014985\\
\cellcolor{gray!6}{People Centered Development} & \cellcolor{gray!6}{Large corporations are destroying the local industries in India and benefiting only a handful of people.} & \cellcolor{gray!6}{-0.634} & \cellcolor{gray!6}{0.057} & \cellcolor{gray!6}{-11.174} & \cellcolor{gray!6}{0.0e+00} & \cellcolor{gray!6}{-0.7449013} & \cellcolor{gray!6}{-0.5225822} & \cellcolor{gray!6}{-0.6337417} & \cellcolor{gray!6}{-0.5349921}\\
\addlinespace
People Centered Development & Regardless of ownership, the government should pass strong regulations and implement them. & -0.509 & 0.054 & -9.351 & 0.0e+00 & -0.6162708 & -0.4027047 & -0.5094877 & -0.4577641\\
\cellcolor{gray!6}{Nationalist Development} & \cellcolor{gray!6}{MECHANISATION} & \cellcolor{gray!6}{0.656} & \cellcolor{gray!6}{0.056} & \cellcolor{gray!6}{11.682} & \cellcolor{gray!6}{0.0e+00} & \cellcolor{gray!6}{0.5460463} & \cellcolor{gray!6}{0.7662170} & \cellcolor{gray!6}{0.6561317} & \cellcolor{gray!6}{0.5556245}\\
Nationalist Development & Coal powered plants pushes forward the country's development. & 0.626 & 0.055 & 11.326 & 0.0e+00 & 0.5177592 & 0.7344596 & 0.6261094 & 0.6242574\\
\cellcolor{gray!6}{Nationalist Development} & \cellcolor{gray!6}{Coal powered plants brings economic prosperity to the surrounding regions.} & \cellcolor{gray!6}{0.547} & \cellcolor{gray!6}{0.054} & \cellcolor{gray!6}{10.086} & \cellcolor{gray!6}{0.0e+00} & \cellcolor{gray!6}{0.4408772} & \cellcolor{gray!6}{0.6535573} & \cellcolor{gray!6}{0.5472172} & \cellcolor{gray!6}{0.5535687}\\
NA & Coal powered plants will bring jobs to the local community. & 0.472 & 0.054 & 8.776 & 0.0e+00 & 0.3667103 & 0.5776005 & 0.4721554 & 0.4834144\\
\addlinespace
\cellcolor{gray!6}{NA} & \cellcolor{gray!6}{PRIDECOAL} & \cellcolor{gray!6}{0.338} & \cellcolor{gray!6}{0.062} & \cellcolor{gray!6}{5.485} & \cellcolor{gray!6}{0.0e+00} & \cellcolor{gray!6}{0.2173242} & \cellcolor{gray!6}{0.4590249} & \cellcolor{gray!6}{0.3381745} & \cellcolor{gray!6}{0.3081207}\\
NA & NPRIDECOAL & 0.284 & 0.061 & 4.667 & 3.1e-06 & 0.1645514 & 0.4027991 & 0.2836753 & 0.2634176\\
\cellcolor{gray!6}{NA} & \cellcolor{gray!6}{Coal powered plants poses a great risk to the health of people living around it.} & \cellcolor{gray!6}{0.702} & \cellcolor{gray!6}{0.056} & \cellcolor{gray!6}{12.572} & \cellcolor{gray!6}{0.0e+00} & \cellcolor{gray!6}{0.5927046} & \cellcolor{gray!6}{0.8116380} & \cellcolor{gray!6}{0.7021713} & \cellcolor{gray!6}{0.5798090}\\
NA & Coal powered plants spoils the natural beauty of the landscape. & 0.610 & 0.050 & 12.173 & 0.0e+00 & 0.5113671 & 0.7076348 & 0.6095009 & 0.5443389\\
\cellcolor{gray!6}{NA} & \cellcolor{gray!6}{Coal powered plants is leading to displacement of people from their land.} & \cellcolor{gray!6}{0.941} & \cellcolor{gray!6}{0.069} & \cellcolor{gray!6}{13.656} & \cellcolor{gray!6}{0.0e+00} & \cellcolor{gray!6}{0.8060444} & \cellcolor{gray!6}{1.0761975} & \cellcolor{gray!6}{0.9411209} & \cellcolor{gray!6}{0.7048765}\\
\bottomrule
\end{tabular}}
\end{table}
\end{landscape}

\end{document}

### 2024-01-15 combined data set/demographicvariables.Rmd
lot of changes because I wasn't opening the project file.
damn

@@
 module1 <- data.frame(moduleone)
+
+unique(module1$caste)
 
@@
   labs(x = "urban or rural", y = "mean risk")
+
 ```
@@
   labs(y = "mean risk")
+
+joineddf%>%
+  ggplot(aes(x= gender, y = Risky_Nuclear))+
+  geom_boxplot()
+
+joineddf%>%
+  ggplot(aes(x= urban_rural, y = Risky_Nuclear))+
+  geom_boxplot()
+
 ```

### 2024-01-15 module2/factor analysis/FAoptionswithmice.Rmd
damn

---
title: "FAoptionswithmice"
output:
  word_document: null
  keep_md: yes
---

```{r load packages, warning = FALSE, message = FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(psych))
library(officer)
library(magrittr)

```

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
moduletwo <- read_excel(here::here("thesis_surveydata/political_factors_complete.xlsx"))
save(moduletwo, file = "moduletwo.rda")
module2 <- data.frame(moduletwo)
module2[module2 == "Rather not say/ Don't know"] <- "Rather not say/Don't know"
#module2 %>% filter(!row_number() %in% c(1,2))

# loaded data set for module 2 eco -pol variables and removes the rows with question number and question text
```

```{r, eval =TRUE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
codedmodule2 <- module2 %>%

#remove row 1
  filter(!row_number() %in% c(1,2)) %>%

# replace risky likert scale with numbers
  mutate_at(vars(starts_with("Risky")), funs(case_when(. =="Not at all risky" ~ 1, 
                                                       . =="Slightly risky" ~ 2, 
                                                       . =="Moderately risky" ~ 3, 
                                                       . =="Very risky" ~ 4, 
                                                       . =="Extremely risky" ~ 5))) %>%

# replace beneficial likert scale with numbers  
  mutate_at(vars(starts_with("Ben")), funs(case_when(. =="Not at all beneficial" ~ 1,
                                                     . =="Slightly beneficial" ~ 2,
                                                     . =="Moderately beneficial" ~ 3,
                                                     . =="Very beneficial" ~ 4,
                                                     . =="Extremely beneficial" ~ 5 ))) %>%

# replace nuclear acceptance likert scale with numbers
  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                                        . == "Somewhat disagree" ~ 2,
                                                                        . == "Neither agree nor disagree" ~3,
                                                                        . == "Somewhat agree" ~ 4,
                                                                        . == "Strongly agree" ~ 5))) %>%

# code likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_I","K_H","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE", "DEVNUCLEAR","DEVSOLAR", "DEVCOAL", "PROSPER", "RELY"))), funs(case_when(. == "Strongly disagree" ~ 1, 
               . == "Somewhat disagree" ~ 2,
               . == "Neither agree nor disagree" ~3,
               . == "Somewhat agree" ~ 4,
               . == "Strongly agree" ~ 5))) %>%

# reverse code for likert scale for variables for Kahan scale into numbers
mutate_at(vars(starts_with (c("K_S","K_E"))), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                               . == "Somewhat disagree" ~ 4,
                                                               . == "Neither agree nor disagree" ~3,
                                                               . == "Somewhat agree" ~ 2,
                                                               . == "Strongly agree" ~ 1))) %>%

# code eco-pol scale variables into numbers
  mutate_at(vars(SYSTEMDEMO,SYSTEMRELIGION,SYSTEMTECHNO,SYSTEMTOTAL,WEALTHLIM,MECHANISATION,DECISIONDECEN,INDUSTRYSMALL,ECONOMYLOCAL,ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(. == "Strongly disagree" ~ 1, 
                        . == "Somewhat disagree" ~ 2,
                        . == "Neither agree nor disagree" ~3,
                        . == "Somewhat agree" ~ 4,
                        . == "Strongly agree" ~ 5))) %>%

# reverse code eco-pol scale variables into numbers 
 mutate_at(vars(DECISIONCEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG, DEVOVERENV), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                                                                         . == "Somewhat disagree" ~ 2,
                                                                                                         . == "Neither agree nor disagree" ~3,
                                                                                                         . == "Somewhat agree" ~ 4,
                                                                                                         . == "Strongly agree" ~ 5)))%>%
  mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
  mutate_all(~ifelse(. == "West bengal", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "WEST BENGAL", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "Up", "Uttar Pradesh", .))%>%
  mutate_all(~ifelse(. == "Tamilnadu", "Tamil Nadu", .))%>%
  mutate_all(~ifelse(. == "UP", "Uttar Pradesh", .))%>%
  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
                                      . == "25-34 years old" ~ 2,
                                      . ==  "35-44 years old" ~3,
                                      . == "45-54 years old" ~ 4,
                                      . == "55-64 years old" ~ 5,
                                      . == "65-74 years old" ~ 6,
                                      . == "75 years or older" ~ 7)))
```

```{r, echo = FALSE}
#sort demo vars

# # Convert `caste` into binary variable 'upper' (1) vs 'non-upper' (0)
joineddf$Uppercaste <- ifelse(joineddf$caste %in% c('Brahmin', 'General'), 1, 0)
# Convert `gender` into binary variable 'male' (1) vs 'female' (0)
joineddf$Male <- ifelse(joineddf$gender == 'Male', 1, 0)
# Convert `religion` into binary variable 'Hinduism' (1) vs 'Non-Hinduism' (0)
joineddf$Hindu <- ifelse(joineddf$religion == 'Hinduism', 1, 0)
codedmodule2$State <- as.factor(codedmodule2$State)
codedmodule2$gender <- as.factor(codedmodule2$gender)
codedmodule2$Urban <- as.factor(codedmodule2$urban_rural)
joineddf$Urban <- as.factor(joineddf$urban_rural)
codedmodule2$caste <- as.factor(codedmodule2$caste)
codedmodule2$religion <- as.factor(codedmodule2$religion)
# # Convert `caste` into binary variable 'upper' (1) vs 'non-upper' (0)
codedmodule2$Uppercaste <- ifelse(codedmodule2$caste %in% c('Brahmin', 'General'), 1, 0)
# Convert `gender` into binary variable 'male' (1) vs 'female' (0)
codedmodule2$Male <- ifelse(codedmodule2$gender == 'Male', 1, 0)
# Convert `religion` into binary variable 'Hinduism' (1) vs 'Non-Hinduism' (0)
codedmodule2$Hindu <- ifelse(codedmodule2$religion == 'Hinduism', 1, 0)

codedmodule21 <- codedmodule2 %>%
            dplyr::select(Risky_Nuclear, Risky_Solar, Risky_Coal, Uppercaste, Male, Hindu, Urban, age, State) %>%
            na.omit()

# lm on nuclear energy with all demovars

alldemos <- codedmodule21 %>%
            dplyr::select(Risky_Nuclear, Uppercaste, Male, Hindu, Urban, age, State) %>%
  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
                                      . == "25-34 years old" ~ 2,
                                      . ==  "35-44 years old" ~3,
                                      . == "45-54 years old" ~ 4,
                                      . == "55-64 years old" ~ 5,
                                      . == "65-74 years old" ~ 6,
                                      . == "75 years or older" ~ 7)))
```

# Two factor solution (Combined Scales): People Centered Development and Nationalist Development

## Nuclear- Factor Analysis

```{r, echo=FALSE}
fascales <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_","Risky_Nuclear","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR","SYSTEMDEMO","SYSTEMRELIGION", "SYSTEMTECHNO","SYSTEMTOTAL", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%
  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
                                      . == "25-34 years old" ~ 2,
                                      . ==  "35-44 years old" ~3,
                                      . == "45-54 years old" ~ 4,
                                      . == "55-64 years old" ~ 5,
                                      . == "65-74 years old" ~ 6,
                                      . == "75 years or older" ~ 7))) %>%
  na.omit()
```

```{r, echo=FALSE}
# Q6: Does the Kahan scale explain perception of risk from nuclear energy and other DVs ?

# we conducted fa on the kahan scale 
# CFA for Kahan scale. We shouldn't do FA here since this a well used scale with theoretical basis for factor distinctions and also previous studies using the same scale

library(lavaan)
library(semTools)
library(kableExtra)

fascales <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_","Risky_Nuclear","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%
  na.omit()

Kahan_fas <- '
  KahanS =~ K_SHARM + K_SLIMCHOI + K_SPROTECT 
  KahanH =~ K_HEQUAL+ K_ERADEQ1 + K_EWEALTH + K_ERADEQ2
'

# Run CFA
Kahan_cfa <- cfa(Kahan_fas, data = fascales, std.lv = TRUE)

# Print the summary of the CFA results, including fit measures
#summary(Kahan_cfa, fit.measure= TRUE, standardized = TRUE)

# RMSEA - between 0.05 and 0.08 (reasonable fit), less than 0.05 close fit and greater than 0.10 is poor fit 
# CFI - greater than 0.90 or 0.95 indicates good fit
#TFI - CFI>TFI >0.90 - indicates good fit
#pvalue should be greater than 0.05 p > 0.0.5

# after having removed a few variables that had very low loading, the model is now a good fit, we have two latent variables - Hierarchy- egalitarian and Communitarian. Again we see that individualistic variables just don't fit here.

# creating table of factor scores

Kahan_scores <- predict(Kahan_cfa, newdata = fascales)

Kahan_Kscores <- cbind(fascales, Kahan_scores)

## RMSEA is still pretty big.

```

```{r, echo = FALSE}

# the psych code for FA on eco-pol scale for nuclear energy - all vars combined

library(psych)
library(tidyverse)

ecopolall <- fascales %>%
        dplyr::select("WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "RELYNUCLEAR","PROSPERNUCLEAR", "JOBSNUCLEAR")%>%
    rename(
      "Limits on Wealth " = "WEALTHLIM",
      "Anti Mechanisation of work" = "MECHANISATION",
      "Pro Decentralisation" = "DECISIONDECEN",
      "Pro Centralisation" = "DECISIONCEN",
      "Pro Large Industries" = "INDUSTRYLARGE",
      "Anti Large Industries " = "INDUSTRYSMALL",
      "Pro Globaleconomy" = "ECONOMYGLOBAL",
      "Pro Localeconomy" = "ECONOMYLOCAL",
      "Environment over Development" = "ENVOVERDEV",
      "Development over Environment" = "DEVOVERENV",
      "Pro Private ownership " = "OWNERPVT",
      "Anti Regulations" = "OWNERNOREG",
      "Pro Public ownership" = "OWNERPUB",
      "Pro Regulations" = "OWNERREG",
      "Displacement risk(nuclear)" = "DISPLACENUCLEAR",
      "Pollution risk(nuclear) " = "POLLUTENUCLEAR",
      "Health risk(nuclear)" = "HEALTHNUCLEAR",
      "Job opportunities(nuclear)" = "JOBSNUCLEAR",
      "Spoils Natural Beauty(nuclear)" = "BEAUTYNUCLEAR",
      "Local prosperity(nuclear)" = "PROSPERNUCLEAR",
      "Community pride(nuclear)" = "PRIDENUCLEAR",
      "National pride(nuclear)" = "NPRIDENUCLEAR",
      "National development(nuclear)" = "DEVNUCLEAR",
      "Reliance on government(nuclear)" = "RELYNUCLEAR"
    )

ecopolall2.fa <- fa(ecopolall, nfactors = 2, rotate = "varimax")

print.psych(ecopolall2.fa, cut = 0.4, sort = TRUE)

ecopol_fas <- '
  Pdevelop =~ HEALTHNUCLEAR + BEAUTYNUCLEAR + DISPLACENUCLEAR + POLLUTENUCLEAR + INDUSTRYSMALL + OWNERREG + MECHANISATION
  Ndevelop =~ DEVNUCLEAR + PROSPERNUCLEAR + PRIDENUCLEAR + NPRIDENUCLEAR + JOBSNUCLEAR
'
ecopol_cfa <- cfa(ecopol_fas, data = fascales, std.lv = TRUE)
summary(ecopol_cfa, fit.measure= TRUE, standardized = TRUE)

```

## Nuclear - FA 2 factor solution

```{r, echo=FALSE}

library(flextable)

set_flextable_defaults(docx.landscape = TRUE)

flex <- function(data, title=NULL) {
  # this grabs the data and converts it to a flextbale
  flextable(data) %>%
  # this makes the table fill the page width
  set_table_properties(layout = "autofit", width = 1) %>%
  # font size
  fontsize(size=10, part="all") %>%
    #this adds a ttitlecreates an automatic table number
      set_caption(title, 
                  autonum = officer::run_autonum(seq_id = "tab", 
                                                 pre_label = "Table ", 
                                                 post_label = "\n", 
                                                 bkm = "anytable")) #%>%
  # font type
  #font(fontname="Times New Roman", part="all")
}

rename_map <- c(
  "Limits on Wealth" = "A limit should be put to how much wealth a person can amass",
  "Anti Mechanisation of work" = "Rapid mechanization of work is taking away jobs from workers in this country",
  "Pro Decentralisation" = "Local politicians shouldn't have to ask permission from the central government to implement policies",
  "Pro Centralisation" = "Laws and policies would be implemented more smoothly if more power lay with the central government",
  "Pro Large Industries" = "Large scale industries are required for the development of the country that will benefit everyone",
  "Anti Large Industries" = "Large corporations are destroying the local industries in India and benefiting only a handful of people",
  "Pro Globaleconomy" = "Foreign companies have led to a range of benefits for the Indian people and society",
  "Pro Localeconomy" = "India would be better off if foreign companies didn't come to here",
  "Environment over Development" = "Polluting industries that spoil the environment should be shut down even if it costs people their jobs",
  "Development over Environment" = "Economic growth and creating jobs should be prioritized over environmental protection",
  "Pro Private ownership" = "All businesses and industries should be owned privately",
  "Anti Regulations" = "There is too much red-tape and the government should not interfere with businesses and industries",
  "Pro Public ownership" = "The government should own most large businesses and industries",
  "Pro Regulations" = " Regardless of ownership, the government should pass strong regulations and implement them",
  "Displacement risk(nuclear)" = "Nuclear energy is leading to displacement of people from their land",
  "Spoils Natural Beauty(nuclear)" = "Nuclear energy spoils the natural beauty of the landscape",
  "Pollution risk(nuclear)" = "Nuclear energy increases pollution of air/water/land",
  "Health risk(nuclear)" = "Nuclear energy poses a great risk to the health of people living around it",
  "Job opportunities(nuclear)" = "Nuclear energy will bring jobs to the local community",
  "Community pride(nuclear)" = "I would be proud if my community used nuclear energy",
  "National pride(nuclear)" = "Nuclear energy is a mark of pride for our nation",
  "National development(nuclear)" = "Nuclear energy pushes forward the country's development",
  "Local prosperity(nuclear)" = "Nuclear energy brings economic prosperity to the surrounding regions",
  "Reliance on government(nuclear)" = "I don't like the idea that I have to rely on the government for electricity from nuclear energy"
)

fa_table <- function(x, cut) {
  #get sorted loadings
  loadings <- fa.sort(x)$loadings %>% round(3)
  #suppress loadings
  loadings[loadings > -cut & loadings < cut] <- ""
  #get additional info  
  add_info <- cbind(x$communalities, 
                    x$uniquenesses,
                    x$complexity) %>%
    # make it a data frame
    as.data.frame() %>%
    # column names
    rename("Communality" = V1,
           "Uniqueness" = V2,
           "Complexity" = V3) %>%
    #get the item names from the vector
    rownames_to_column("item")

  #build table
  loadings %>%
    unclass() %>%
    as.data.frame() %>%
    rownames_to_column("item") %>%
    left_join(add_info) %>%
    mutate(
      item = if_else(item %in% names(rename_map), rename_map[item], item),
      code = names(rename_map)[match(item, rename_map)], # extracting short form
      across(where(is.numeric), round, 3)
    ) %>%
    dplyr::select(code, everything()) # reorder columns to bring code to the front
}

fa_table(ecopolall2.fa, .4) %>%
  rename(Pdevelop = MR1, Ndevelop = MR2, Items= item) %>%
  flex("2 factor solution") %>%
  autofit()

```

```{r, echo = FALSE}
ecopolall2.fa[["Vaccounted"]] %>%
  as.data.frame() %>%
  rownames_to_column("Property") %>%
  rename(Pdevelop = MR1, Ndevelop = MR2) %>%
    mutate(across(where(is.numeric), round, 3)) %>%
    flex("Eigenvalues and Variance Explained for 2 Factor Solution")
```

\newpage 
## Nuclear - linear regression with 2 Factor solution

```{r, echo=FALSE}

# Linear Model with 2 factor solution for  Risk perception from Nuclear Energy

#binding factor scores to the dataset
ecopolall_scores <- predict(ecopol_cfa, newdata = fascales)

fascale_scores <- cbind(Kahan_Kscores, ecopolall_scores)# %>%
  #rename(Pdevelop = MR1)%>%
  #rename(Ndevelop = MR2)

nuclearfa2 <- lm(Risky_Nuclear ~ age + Uppercaste + Male + Hindu + Urban + State + KahanS + KahanH + Pdevelop + Ndevelop, data = fascale_scores)

#m2_allscales <- lm(Risky_Nuclear ~ age + Uppercaste + Male + Hindu + Urban +State+ KahanS + KahanH + NPRIDENUCLEAR + PRIDENUCLEAR + DEVNUCLEAR + PROSPERNUCLEAR, data = fascale_scores)
# Print model summary
summary(nuclearfa2)

```

\newpage
## Solar : P develop and Ndevelop

```{r, echo=FALSE}
library(psych)
library(tidyverse)

sfascales <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_","Risky_Solar","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACESOLAR", "POLLUTESOLAR", "HEALTHSOLAR", "JOBSSOLAR", "BEAUTYSOLAR", "PRIDESOLAR", "NPRIDESOLAR", "DEVSOLAR", "PROSPERSOLAR", "RELYSOLAR", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%
  na.omit()

secopolall <- sfascales %>%
        dplyr::select("WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACESOLAR", "POLLUTESOLAR", "HEALTHSOLAR", "JOBSSOLAR", "BEAUTYSOLAR", "PRIDESOLAR", "NPRIDESOLAR", "DEVSOLAR", "PROSPERSOLAR", "RELYSOLAR")%>%
    rename(
      "Limits on Wealth " = "WEALTHLIM",
      "Anti Mechanisation of work" = "MECHANISATION",
      "Pro Decentralisation" = "DECISIONDECEN",
      "Pro Centralisation" = "DECISIONCEN",
      "Pro Large Industries" = "INDUSTRYLARGE",
      "Anti Large Industries " = "INDUSTRYSMALL",
      "Pro Globaleconomy" = "ECONOMYGLOBAL",
      "Pro Localeconomy" = "ECONOMYLOCAL",
      "Environment over Development" = "ENVOVERDEV",
      "Development over Environment" = "DEVOVERENV",
      "Pro Private ownership " = "OWNERPVT",
      "Anti Regulations" = "OWNERNOREG",
      "Pro Public ownership" = "OWNERPUB",
      "Pro Regulations" = "OWNERREG",
      "Displacement risk(solar)" = "DISPLACESOLAR",
      "Pollution risk(solar) " = "POLLUTESOLAR",
      "Health risk(solar)" = "HEALTHSOLAR",
      "Job opportunities(solar)" = "JOBSSOLAR",
      "Spoils Natural Beauty(solar)" = "BEAUTYSOLAR",
      "Community pride(solar)" = "PRIDESOLAR",
      "National pride(solar)" = "NPRIDESOLAR",
      "National development(solar)" = "DEVSOLAR",
      "Local prosperity(solar)" = "PROSPERSOLAR",
      "Reliance on government(solar)" = "RELYSOLAR"
    )

secopolall2.fa <- fa(secopolall, nfactors = 2, rotate = "varimax")

```

## EFA : Two factor soltuion

```{r, echo=FALSE}

library(flextable)

set_flextable_defaults(docx.landscape = TRUE)

flex <- function(data, title=NULL) {
  # this grabs the data and converts it to a flextbale
  flextable(data) %>%
  # this makes the table fill the page width
  set_table_properties(layout = "autofit", width = 1) %>%
  # font size
  fontsize(size=10, part="all") %>%
    #this adds a ttitlecreates an automatic table number
      set_caption(title, 
                  autonum = officer::run_autonum(seq_id = "tab", 
                                                 pre_label = "Table ", 
                                                 post_label = "\n", 
                                                 bkm = "anytable")) #%>%
  # font type
  #font(fontname="Times New Roman", part="all")
}

srename_map <- c(
  "Limits on Wealth" = "A limit should be put to how much wealth a person can amass",
  "Anti Mechanisation of work" = "Rapid mechanization of work is taking away jobs from workers in this country",
  "Pro Decentralisation" = "Local politicians shouldn't have to ask permission from the central government to implement policies",
  "Pro Centralisation" = "Laws and policies would be implemented more smoothly if more power lay with the central government",
  "Pro Large Industries" = "Large scale industries are required for the development of the country that will benefit everyone",
  "Anti Large Industries" = "Large corporations are destroying the local industries in India and benefiting only a handful of people",
  "Pro Globaleconomy" = "Foreign companies have led to a range of benefits for the Indian people and society",
  "Pro Localeconomy" = "India would be better off if foreign companies didn't come to here",
  "Environment over Development" = "Polluting industries that spoil the environment should be shut down even if it costs people their jobs",
  "Development over Environment" = "Economic growth and creating jobs should be prioritized over environmental protection",
  "Pro Private ownership" = "All businesses and industries should be owned privately",
  "Anti Regulations" = "There is too much red-tape and the government should not interfere with businesses and industries",
  "Pro Public ownership" = "The government should own most large businesses and industries",
  "Pro Regulations" = "Regardless of ownership, the government should pass strong regulations and implement them",
  "Displacement risk(solar)" = "Solar energy is leading to displacement of people from their land",
  "Spoils Natural Beauty(solar)" = "Solar energy spoils the natural beauty of the landscape",
  "Pollution risk(solar)" = "Solar energy increases pollution of air/water/land",
  "Health risk(solar)" = "Solar energy poses a great risk to the health of people living around it",
  "Job opportunities(solar)" = "Solar energy will bring jobs to the local community",
  "Community pride(solar)" = "I would be proud if my community used solar energy",
  "National pride(solar)" = "Solar energy is a mark of pride for our nation",
  "National development(solar)" = "Solar energy pushes forward the country's development",
  "Local prosperity(solar)" = "Solar energy brings economic prosperity to the surrounding regions",
  "Reliance on government(solar)" = "I don't like the idea that I have to rely on the government for electricity from solar energy"
)

fa_table <- function(x, cut) {
  #get sorted loadings
  loadings <- fa.sort(x)$loadings %>% round(3)
  #suppress loadings
  loadings[loadings > -cut & loadings < cut] <- ""
  #get additional info  
  add_info <- cbind(x$communalities, 
                    x$uniquenesses,
                    x$complexity) %>%
    # make it a data frame
    as.data.frame() %>%
    # column names
    rename("Communality" = V1,
           "Uniqueness" = V2,
           "Complexity" = V3) %>%
    #get the item names from the vector
    rownames_to_column("item")

  #build table
  loadings %>%
    unclass() %>%
    as.data.frame() %>%
    rownames_to_column("item") %>%
    left_join(add_info) %>%
    mutate(
      item = if_else(item %in% names(srename_map), srename_map[item], item),
      code = names(srename_map)[match(item, srename_map)], # extracting short form
      across(where(is.numeric), round, 3)
    ) %>%
    dplyr::select(code, everything()) # reorder columns to bring code to the front
}

fa_table(secopolall2.fa, .4) %>%
  #rename(Pdevelop = MR1, Ndevelop = MR2, Items= item) %>%
  flex("2 factor solution") %>%
  autofit()

```

```{r, echo = FALSE}
secopolall2.fa[["Vaccounted"]] %>%
  as.data.frame() %>%
  rownames_to_column("Property") %>%
  #rename(Pdevelop = MR1, Ndevelop = MR2) %>%
    mutate(across(where(is.numeric), round, 3)) %>%
    flex("Solar: Eigenvalues and Variance Explained for 2 Factor Solution")
```
\newpage

# CFA on solar energy - 2 factor solution 
```{r, echo = FALSE}
# kahan scores for solar 
sfascales <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_","Risky_Solar","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACESOLAR",  "POLLUTESOLAR", "HEALTHSOLAR", "JOBSSOLAR", "BEAUTYSOLAR", "PRIDESOLAR", "NPRIDESOLAR", "DEVSOLAR", "PROSPERSOLAR", "RELYSOLAR", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%
  na.omit()

sKahan_fas <- '
  KahanS =~ K_SHARM + K_SLIMCHOI + K_SPROTECT 
  KahanH =~ K_HEQUAL+ K_ERADEQ1 + K_EWEALTH + K_ERADEQ2
'

# Run CFA
sKahan_cfa <- cfa(sKahan_fas, data = sfascales, std.lv = TRUE)

# Print the summary of the CFA results, including fit measures
summary(sKahan_cfa, fit.measure= TRUE, standardized = TRUE)

sKahan_scores <- predict(sKahan_cfa, newdata = sfascales)

sKahan_Kscores <- cbind(sfascales, sKahan_scores)

sm1_kahan <- lm(Risky_Solar ~ Uppercaste + Male + Hindu + Urban + age + State + KahanS + KahanH , data = sKahan_Kscores)

## CFA on ecopol vars for solar energy

secopol_fas <- '
  Pdevelop =~ HEALTHSOLAR + BEAUTYSOLAR + DISPLACESOLAR + POLLUTESOLAR + INDUSTRYSMALL + OWNERREG + MECHANISATION
  Ndevelop =~ DEVSOLAR + PRIDESOLAR + NPRIDESOLAR + PROSPERSOLAR + JOBSSOLAR
'

secopol_cfa <- cfa(secopol_fas, data = sfascales, std.lv = TRUE)
summary(secopol_cfa, fit.measure= TRUE, standardized = TRUE)

# Cronbach's alpha test on Pdevelop and Ndevelop for Solar energy

solarpdevelop <- sfascales %>%
  dplyr::select(HEALTHSOLAR, BEAUTYSOLAR, DISPLACESOLAR, POLLUTESOLAR, INDUSTRYSMALL, OWNERREG, MECHANISATION)%>%
  na.omit()

solarpdevelop.alpha <- psych::alpha(solarpdevelop, check.keys = TRUE)

# alpha is strong at 0.75!

solarndevelop <- sfascales %>%
  dplyr::select(DEVSOLAR, PRIDESOLAR, NPRIDESOLAR, PROSPERSOLAR, JOBSSOLAR)%>%
  na.omit()

solarndevelop.alpha <- psych::alpha(solarndevelop, check.keys = TRUE)

#alpha is strong at 0.86!

```

## Solar - linear regression with 2 Factor solution

```{r, echo=FALSE}

# Linear Model with 2 factor solution for  Risk perception from Solar Energy

#binding factor scores to the dataset
secopolall_scores <- predict(secopol_cfa, newdata = sfascales)

sfascale_scores <- cbind(sKahan_Kscores, secopolall_scores)# %>%
  #rename(Pdevelop = MR1)%>%
  #rename(Ndevelop = MR2)

solar2fa <- lm(Risky_Solar ~ age + Uppercaste + Male + Hindu + Urban + State + KahanS + KahanH + Pdevelop + Ndevelop, data = sfascale_scores)

#m2_allscales <- lm(Risky_Nuclear ~ age + Uppercaste + Male + Hindu + Urban +State+ KahanS + KahanH + NPRIDENUCLEAR + PRIDENUCLEAR + DEVNUCLEAR + PROSPERNUCLEAR, data = fascale_scores)
# Print model summary
summary(solar2fa)

```

\newpage
## Coal

```{r, echo = FALSE}

cecopolall <- codedmodule2 %>%
        dplyr::select("WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACECOAL", "POLLUTECOAL", "HEALTHCOAL", "JOBSCOAL", "BEAUTYCOAL", "PRIDECOAL", "NPRIDECOAL", "DEVCOAL", "PROSPERCOAL", "RELYCOAL")%>%
      rename(
      "Limits on Wealth " = "WEALTHLIM",
      "Anti Mechanisation of work" = "MECHANISATION",
      "Pro Decentralisation" = "DECISIONDECEN",
      "Pro Centralisation" = "DECISIONCEN",
      "Pro Large Industries" = "INDUSTRYLARGE",
      "Anti Large Industries " = "INDUSTRYSMALL",
      "Pro Globaleconomy" = "ECONOMYGLOBAL",
      "Pro Localeconomy" = "ECONOMYLOCAL",
      "Environment over Development" = "ENVOVERDEV",
      "Development over Environment" = "DEVOVERENV",
      "Pro Private ownership " = "OWNERPVT",
      "Anti Regulations" = "OWNERNOREG",
      "Pro Public ownership" = "OWNERPUB",
      "Pro Regulations" = "OWNERREG",
      "Displacement risk(coal)" = "DISPLACECOAL",
      "Pollution risk(coal) " = "POLLUTECOAL",
      "Health risk(coal)" = "HEALTHCOAL",
      "Job opportunities(coal)" = "JOBSCOAL",
      "Spoils Natural Beauty(coal)" = "BEAUTYCOAL",
      "Community pride(coal)" = "PRIDECOAL",
      "National pride(coal)" = "NPRIDECOAL",
      "National development(coal)" = "DEVCOAL",
      "Local prosperity(coal)" = "PROSPERCOAL",
      "Reliance on government(coal)" = "RELYCOAL"
    )

cecopolall2.fa <- fa(cecopolall, nfactors = 2, rotate = "varimax")

print.psych(cecopolall2.fa, cut = 0.5, sort = TRUE)

```

```{r, echo=FALSE}

library(flextable)

set_flextable_defaults(docx.landscape = TRUE)

flex <- function(data, title=NULL) {
  # this grabs the data and converts it to a flextbale
  flextable(data) %>%
  # this makes the table fill the page width
  set_table_properties(layout = "autofit", width = 1) %>%
  # font size
  fontsize(size=10, part="all") %>%
    #this adds a ttitlecreates an automatic table number
      set_caption(title, 
                  autonum = officer::run_autonum(seq_id = "tab", 
                                                 pre_label = "Table ", 
                                                 post_label = "\n", 
                                                 bkm = "anytable")) #%>%
  # font type
  #font(fontname="Times New Roman", part="all")
}

crename_map <- c(
  "Limits on Wealth" = "A limit should be put to how much wealth a person can amass",
  "Anti Mechanisation of work" = "Rapid mechanization of work is taking away jobs from workers in this country",
  "Pro Decentralisation" = "Local politicians shouldn't have to ask permission from the central government to implement policies",
  "Pro Centralisation" = "Laws and policies would be implemented more smoothly if more power lay with the central government",
  "Pro Large Industries" = "Large scale industries are required for the development of the country that will benefit everyone",
  "Anti Large Industries" = "Large corporations are destroying the local industries in India and benefiting only a handful of people",
  "Pro Globaleconomy" = "Foreign companies have led to a range of benefits for the Indian people and society",
  "Pro Localeconomy" = "India would be better off if foreign companies didn't come to here",
  "Environment over Development" = "Polluting industries that spoil the environment should be shut down even if it costs people their jobs",
  "Development over Environment" = "Economic growth and creating jobs should be prioritized over environmental protection",
  "Pro Private ownership" = "All businesses and industries should be owned privately",
  "Anti Regulations" = "There is too much red-tape and the government should not interfere with businesses and industries",
  "Pro Public ownership" = "The government should own most large businesses and industries",
  "Pro Regulations" = "Regardless of ownership, the government should pass strong regulations and implement them",
  "Displacement risk(coal)" = "Coal powered plants are leading to displacement of people from their land",
  "Spoils Natural Beauty(coal)" = "Coal powered plants spoil the natural beauty of the landscape",
  "Pollution risk(coal)" = "Coal powered plants increase pollution of air/water/land",
  "Health risk(coal)" = "Coal powered plants pose a great risk to the health of people living around it",
  "Job opportunities(coal)" = "Coal powered plants will bring jobs to the local community",
  "Community pride(coal)" = "I would be proud if my community used coal powered plants",
  "National pride(coal)" = "Coal powered plants are a mark of pride for our nation",
  "National development(coal)" = "Coal powered plants push forward the country's development",
  "Local prosperity(coal)" = "Coal powered plants bring economic prosperity to the surrounding regions",
  "Reliance on government(coal)" = "I don't like the idea that I have to rely on the government for electricity from coal powered plants"
)

fa_table <- function(x, cut) {
  #get sorted loadings
  loadings <- fa.sort(x)$loadings %>% round(3)
  #suppress loadings
  loadings[loadings > -cut & loadings < cut] <- ""
  #get additional info  
  add_info <- cbind(x$communalities, 
                    x$uniquenesses,
                    x$complexity) %>%
    # make it a data frame
    as.data.frame() %>%
    # column names
    rename("Communality" = V1,
           "Uniqueness" = V2,
           "Complexity" = V3) %>%
    #get the item names from the vector
    rownames_to_column("item")

  #build table
  loadings %>%
    unclass() %>%
    as.data.frame() %>%
    rownames_to_column("item") %>%
    left_join(add_info) %>%
    mutate(
      item = if_else(item %in% names(crename_map), crename_map[item], item),
      code = names(crename_map)[match(item, crename_map)], # extracting short form
      across(where(is.numeric), round, 3)
    ) %>%
    dplyr::select(code, everything()) # reorder columns to bring code to the front
}

fa_table(cecopolall2.fa, .4) %>%
  #rename(Pdevelop = MR1, Ndevelop = MR2, Items= item) %>%
  flex("2 factor solution") %>%
  autofit()

```

```{r, echo = FALSE}
cecopolall2.fa[["Vaccounted"]] %>%
  as.data.frame() %>%
  rownames_to_column("Property") %>%
  #rename(Pdevelop = MR1, Ndevelop = MR2) %>%
    mutate(across(where(is.numeric), round, 3)) %>%
    flex("Coal: Eigenvalues and Variance Explained for 2 Factor Solution")
```

## CFA on coal

```{r, echo = FALSE}
# kahan scores for coal and CFA on ecopol vars  
cfascales <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_","Risky_Coal","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACECOAL",  "POLLUTECOAL", "HEALTHCOAL", "JOBSCOAL", "BEAUTYCOAL", "PRIDECOAL", "NPRIDECOAL", "DEVCOAL", "PROSPERCOAL", "RELYCOAL", "Uppercaste", "Male", "Hindu", "Urban", "State","age"))) %>%
  na.omit()

cKahan_fas <- '
  KahanS =~ K_SHARM + K_SLIMCHOI + K_SPROTECT 
  KahanH =~ K_HEQUAL+ K_ERADEQ1 + K_EWEALTH + K_ERADEQ2
'

# Run CFA
cKahan_cfa <- cfa(cKahan_fas, data = cfascales, std.lv = TRUE)

cKahan_scores <- predict(cKahan_cfa, newdata = cfascales)

cKahan_Kscores <- cbind(cfascales, cKahan_scores)

cecopol_fas <- '
  Pdevelop =~ HEALTHCOAL + BEAUTYCOAL + DISPLACECOAL + POLLUTECOAL + INDUSTRYSMALL + OWNERREG + MECHANISATION
  Ndevelop =~ DEVCOAL + PROSPERCOAL + JOBSCOAL + PRIDECOAL + NPRIDECOAL 
'

cecopol_cfa <- cfa(cecopol_fas, data = cfascales, std.lv = TRUE)
#summary(cecopol_cfa, fit.measure= TRUE, standardized = TRUE)

# 3) lm with kahan 
cm1_kahan <- lm(Risky_Coal ~ Uppercaste + Male + Hindu + Urban + age + State + KahanS + KahanH , data = cKahan_Kscores)
# Print model summary
#summary(cm1_kahan)
#plot(cm1_kahan)

# Cronbach's alpha test on Pdevelop and Ndevelop for Solar energy

coalpdevelop <- cfascales %>%
  dplyr::select(HEALTHCOAL, BEAUTYCOAL, DISPLACECOAL, POLLUTECOAL, INDUSTRYSMALL, OWNERREG, MECHANISATION)%>%
  na.omit()

coalpdevelop.alpha <- psych::alpha(coalpdevelop, check.keys = TRUE)

# alpha is strong at 0.78!

coalndevelop <- cfascales %>%
  dplyr::select(DEVCOAL, PRIDECOAL, NPRIDECOAL, PROSPERCOAL, JOBSCOAL,)%>%
  na.omit()

coalndevelop.alpha <- psych::alpha(coalndevelop, check.keys = TRUE)

#alpha

```

## Coal linear regression - 2 FA solution

```{r, echo=FALSE}

# Linear Model with 2 factor solution for  Risk perception from coal Energy

#binding factor scores to the dataset
cecopolall_scores <- predict(cecopol_cfa, newdata = cfascales)

cfascale_scores <- cbind(cKahan_Kscores, cecopolall_scores)# %>%
  #rename(Pdevelop = MR1)%>%
  #rename(Ndevelop = MR2)

coal2fa <- lm(Risky_Coal ~ age + Uppercaste + Male + Hindu + Urban + State + KahanS + KahanH + Pdevelop + Ndevelop, data = cfascale_scores)

#m2_allscales <- lm(Risky_Nuclear ~ age + Uppercaste + Male + Hindu + Urban +State+ KahanS + KahanH + NPRIDENUCLEAR + PRIDENUCLEAR + DEVNUCLEAR + PROSPERNUCLEAR, data = fascale_scores)
# Print model summary
summary(coal2fa)

```

\newpage

# Here make a table with the three linear regression models to compare 2 fa solution

\newpage
# Alternative Solution :  FA on Two Separate scales

## Scale 1: Factor analysis on Eco-political values of the perceiver scale
 4 factor solution

```{r, echo = FALSE}

# below are only eco-pol values of the perceiver scale.

ecopolonly <- codedmodule2 %>%
            filter(!is.na(WEALTHLIM) & !is.na(MECHANISATION) & !is.na(INDUSTRYSMALL)  & !is.na(ECONOMYGLOBAL)  & !is.na(ENVOVERDEV)  & !is.na(OWNERNOREG) & !is.na(OWNERPUB) & !is.na(OWNERREG) & !is.na(DECISIONDECEN) & !is.na(DECISIONCEN) & !is.na(INDUSTRYLARGE) & !is.na(ECONOMYLOCAL) & !is.na(DEVOVERENV) & !is.na(OWNERPVT))
        #dplyr::select("WEALTHLIM","MECHANISATION","INDUSTRYSMALL","ECONOMYGLOBAL", "ENVOVERDEV","OWNERNOREG","OWNERPUB", "OWNERREG", "DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","ECONOMYLOCAL", "DEVOVERENV","OWNERPVT") %>%
  #na.omit()

ecopolval <- codedmodule2 %>%
        dplyr::select("WEALTHLIM","MECHANISATION","INDUSTRYSMALL","ECONOMYGLOBAL", "ENVOVERDEV","OWNERNOREG","OWNERPUB", "OWNERREG", "DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","ECONOMYLOCAL", "DEVOVERENV","OWNERPVT")%>%
  na.omit() %>%
    rename(
      "Limits on Wealth" = "WEALTHLIM",
      "Anti Mechanisation of work" = "MECHANISATION",
      "Pro Decentralisation" = "DECISIONDECEN",
      "Pro Centralisation" = "DECISIONCEN",
      "Pro Large Industries" = "INDUSTRYLARGE",
      "Anti Large Industries" = "INDUSTRYSMALL",
      "Pro Globaleconomy" = "ECONOMYGLOBAL",
      "Pro Localeconomy" = "ECONOMYLOCAL",
      "Environment over Development" = "ENVOVERDEV",
      "Development over Environment" = "DEVOVERENV",
      "Pro Private ownership" = "OWNERPVT",
      "Anti Regulations" = "OWNERNOREG",
      "Pro Public ownership" = "OWNERPUB",
      "Pro Regulations" = "OWNERREG"
    )

#alpha(ecopolval, check.keys = TRUE) # 0.71

#ncol(ecopolval)  number of cols is 14

#ecopolval_cor <- cor(ecopolval)
#PCA14 <- principal(ecopolval, nfactors = 14, rotate = "none") # no rotation to start with.

#print(PCA14)

#PCA14$loadings

#fa.parallel(ecopolval_cor)

ecopolval2.fa <- fa(ecopolval, nfactors = 2, rotate = "varimax")
print.psych(ecopolval2.fa, cut = 0.4, sort = TRUE)

ecopolval4.fa <- fa(ecopolval, nfactors = 4, rotate = "varimax")
print.psych(ecopolval4.fa, cut = 0.4, sort = TRUE)

# 4 fA extraction

ecopolval_scores <- psych::factor.scores(ecopolval, ecopolval4.fa)

# The factor scores will be stored in the scores element of the returned list
ecopolonlyscores <- ecopolval_scores$scores

#binding factor scores to the dataset

ecopolonlywscores <- cbind(ecopolonly, ecopolonlyscores) %>%
  rename(regulateindustry = MR1)%>%
  rename(localisation = MR3)%>%
   rename(freemarket = MR4)%>%
  rename(pvtdevelopment = MR2)

# 2 factor

ecopolval2_scores <- psych::factor.scores(ecopolval, ecopolval2.fa)

# The factor scores will be stored in the scores element of the returned list
ecopolonlyscores2 <- ecopolval2_scores$scores

#binding factor scores to the dataset

ecopolonlywscores2 <- cbind(ecopolonly, ecopolonlyscores2)

#cor(ecopolval)

# questions for Terre , 2) 4 factors/3 factors/2 factors - variation explained how should i deal with that. 
# four factor analysis - MR1 -regulated industrialization MR3 - localisation MR4 - free market MR2- private development

# Reverse coded DECISIONCEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG, DEVOVERENV

```

```{r, echo = FALSE}
# linear regression with 4 factor solution

#Risky_Nuclear

nuclear4fa <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State + regulateindustry +  localisation + freemarket + pvtdevelopment , data = ecopolonlywscores)
# Print model summary
summary(nuclear4fa)

#Ben_Nuclear
bennuclear4fa <- lm(Ben_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State + regulateindustry +  localisation + freemarket + pvtdevelopment , data = ecopolonlywscores)
# Print model summary
summary(bennuclear4fa)

#Risky_Solar
solar4fa <- lm(Risky_Solar ~ Uppercaste + Male + Hindu + Urban + age + State + regulateindustry +  localisation + freemarket + pvtdevelopment , data = ecopolonlywscores)
# Print model summary
summary(solar4fa)

#Ben_Solar

bensolar4fa <- lm(Ben_Solar ~ Uppercaste + Male + Hindu + Urban + age + State + regulateindustry +  localisation + freemarket + pvtdevelopment , data = ecopolonlywscores)
# Print model summary
summary(bensolar4fa)

#Risky_Coal

coal4fa <- lm(Risky_Coal ~ Uppercaste + Male + Hindu + Urban + age + State + regulateindustry +  localisation + freemarket + pvtdevelopment , data = ecopolonlywscores)
# Print model summary
summary(coal4fa)

#Ben_Coal

bencoal4fa <- lm(Ben_Coal ~ Uppercaste + Male + Hindu + Urban + age + State + regulateindustry +  localisation + freemarket + pvtdevelopment , data = ecopolonlywscores)
# Print model summary
summary(bencoal4fa)

```

```{r, echo = FALSE}
# linear regression with 2 factor solution

#Risky_Nuclear

nuclear2fa <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State + MR1 +MR2 , data = ecopolonlywscores2)
# Print model summary
summary(nuclear2fa)

#Ben_Nuclear
bennuclear2fa <- lm(Ben_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State + MR1 +MR2 , data = ecopolonlywscores2)
# Print model summary
summary(bennuclear2fa)

#Risky_Solar
solar2fa <- lm(Risky_Solar ~ Uppercaste + Male + Hindu + Urban + age + State + MR1 +MR2 , data = ecopolonlywscores2)
# Print model summary
summary(solar2fa)

#Ben_Solar

bensolar2fa <- lm(Ben_Solar ~ Uppercaste + Male + Hindu + Urban + age + State + MR1 +MR2 , data = ecopolonlywscores2)
# Print model summary
summary(bensolar2fa)

#Risky_Coal

coal2fa <- lm(Risky_Coal ~ Uppercaste + Male + Hindu + Urban + age + State + MR1 +MR2 , data = ecopolonlywscores2)
# Print model summary
summary(coal2fa)

#Ben_Coal

bencoal2fa <- lm(Ben_Coal ~ Uppercaste + Male + Hindu + Urban + age + State + MR1 +MR2 , data = ecopolonlywscores2)
# Print model summary
summary(bencoal2fa)

```

## 4 factor solution - pretty table

```{r, echo=FALSE}

library(flextable)

set_flextable_defaults(docx.landscape = TRUE)

flex <- function(data, title=NULL) {
  # this grabs the data and converts it to a flextbale
  flextable(data) %>%
  # this makes the table fill the page width
  set_table_properties(layout = "autofit", width = 1) %>%
  # font size
  fontsize(size=10, part="all") %>%
    #this adds a ttitlecreates an automatic table number
      set_caption(title, 
                  autonum = officer::run_autonum(seq_id = "tab", 
                                                 pre_label = "Table ", 
                                                 post_label = "\n", 
                                                 bkm = "anytable")) #%>%
  # font type
  #font(fontname="Times New Roman", part="all")
}

rename_map <- c(
  "Limits on Wealth" = "A limit should be put to how much wealth a person can amass",
  "Anti Mechanisation of work" = "Rapid mechanization of work is taking away jobs from workers in this country",
  "Pro Decentralisation" = "Local politicians shouldn't have to ask permission from the central government to implement policies",
  "Pro Centralisation" = "Laws and policies would be implemented more smoothly if more power lay with the central government",
  "Pro Large Industries" = "Large scale industries are required for the development of the country that will benefit everyone",
  "Anti Large Industries" = "Large corporations are destroying the local industries in India and benefiting only a handful of people",
  "Pro Globaleconomy" = "Foreign companies have led to a range of benefits for the Indian people and society",
  "Pro Localeconomy" = "India would be better off if foreign companies didn't come to here",
  "Environment over Development" = "Polluting industries that spoil the environment should be shut down even if it costs people their jobs",
  "Development over Environment" = "Economic growth and creating jobs should be prioritized over environmental protection",
  "Pro Private ownership" = "All businesses and industries should be owned privately",
  "Anti Regulations" = "There is too much red-tape and the government should not interfere with businesses and industries",
  "Pro Public ownership" = "The government should own most large businesses and industries",
  "Pro Regulations" = " Regardless of ownership, the government should pass strong regulations and implement them"
)

fa_table <- function(x, cut) {
  #get sorted loadings
  loadings <- fa.sort(x)$loadings %>% round(3)
  #suppress loadings
  loadings[loadings > -cut & loadings < cut] <- ""
  #get additional info  
  add_info <- cbind(x$communalities, 
                    x$uniquenesses,
                    x$complexity) %>%
    # make it a data frame
    as.data.frame() %>%
    # column names
    rename("Communality" = V1,
           "Uniqueness" = V2,
           "Complexity" = V3) %>%
    #get the item names from the vector
    rownames_to_column("item")

  #build table
  loadings %>%
    unclass() %>%
    as.data.frame() %>%
    rownames_to_column("item") %>%
    left_join(add_info) %>%
    mutate(
      item = if_else(item %in% names(rename_map), rename_map[item], item),
      code = names(rename_map)[match(item, rename_map)], # extracting short form
      across(where(is.numeric), round, 3)
    ) %>%
    select(code, everything()) # reorder columns to bring code to the front
}

fa_table(ecopolval4.fa, .4) %>%
  #rename(Pdevelop = MR1, Ndevelop = MR2, Items= item) %>%
  flex("4 factor solution same for all technologies") %>%
  autofit()

```

```{r, echo=FALSE}

library(flextable)

flex <- function(data, title=NULL) {
  # this grabs the data and converts it to a flextbale
  flextable(data) %>%
  # this makes the table fill the page width
  set_table_properties(layout = "autofit", width = 1) %>%
  # font size
  fontsize(size=10, part="all") %>%
    #this adds a ttitlecreates an automatic table number
      set_caption(title, 
                  autonum = officer::run_autonum(seq_id = "tab", 
                                                 pre_label = "Table ", 
                                                 post_label = "\n", 
                                                 bkm = "anytable")) #%>%
  # font type
  #font(fontname="Times New Roman", part="all")
}

ecopolval4.fa[["Vaccounted"]] %>%
  as.data.frame() %>%
  rownames_to_column("Property") %>%
  #rename(Pdevelop = MR1, Ndevelop = MR2) %>%
    mutate(across(where(is.numeric), round, 3)) %>%
    flex("Eigenvalues and Variance Explained for Rotated Factor Solution")

```

```{r, echo = FALSE}
 # Adjust as per the number of factors

#fa.diagram(ecopolval4.fa, marg=c(.5,5,1,.5),size =1, adj = 0.25, e.size=.05,rsize=.35, main = "Four Factor Solution")

```

\newpage
## Option 1: Factor analysis on Scale 2 - Characteristics of the Technology
 2 factor solution

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

#alpha test on Eco-pol characteristics of the technology

Nuclear <- codedmodule2 %>%
  filter(complete.cases(dplyr::select(., DISPLACENUCLEAR:RELYNUCLEAR)))

Nuclear2 <- codedmodule2  %>%
  dplyr::select("DISPLACENUCLEAR":"RELYNUCLEAR")%>%
    rename(
   "Displacement risk(nuclear)" = "DISPLACENUCLEAR",
  "Pollution risk(nuclear)" = "POLLUTENUCLEAR",
  "Health risk(nuclear)" = "HEALTHNUCLEAR",
  "Job opportunities(nuclear)" = "JOBSNUCLEAR",
  "Spoils Natural Beauty(nuclear)" = "BEAUTYNUCLEAR",
  "Community pride(nuclear)" = "PRIDENUCLEAR",
  "National pride(nuclear)" = "NPRIDENUCLEAR",
  "National development(nuclear)" = "DEVNUCLEAR",
  "Local prosperity(nuclear)" = "PROSPERNUCLEAR",
  "Reliance on government(nuclear)" = "RELYNUCLEAR"
    )%>%
  na.omit()

Nuclear.fa <- fa(Nuclear2, nfactors = 2, rotate = "varimax")

print.psych(Nuclear.fa, cut = 0.40, sort = TRUE)

#fa.diagram(Nuclear.fa)

```

```{r, echo=FALSE}

# 2 factor

Nuclear_scores <- psych::factor.scores(Nuclear2, Nuclear.fa)

# The factor scores will be stored in the scores element of the returned list
Nuclear_scores2 <- Nuclear_scores$scores

#binding factor scores to the dataset

Nuclearwscores2 <- cbind(Nuclear, Nuclear_scores2)%>%
    rename(negative = MR1)%>%
  rename(positive = MR2)

nuclearfa <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State +  negative + positive , data = Nuclearwscores2)
# Print model summary
summary(nuclearfa)

bennuclearfa <- lm(Ben_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State +  negative + positive , data = Nuclearwscores2)
# Print model summary
summary(bennuclearfa)

```

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

#alpha test on Eco-pol characteristics of the technology

Solar <- codedmodule2 %>%
  filter(complete.cases(dplyr::select(., DISPLACESOLAR:RELYSOLAR)))

Solar2 <- codedmodule2  %>%
  dplyr::select("DISPLACESOLAR":"RELYSOLAR")%>%
    rename(
   "Displacement risk(Solar)" = "DISPLACESOLAR",
  "Pollution risk(Solar)" = "POLLUTESOLAR",
  "Health risk(Solar)" = "HEALTHSOLAR",
  "Job opportunities(Solar)" = "JOBSSOLAR",
  "Spoils Natural Beauty(Solar)" = "BEAUTYSOLAR",
  "Community pride(Solar)" = "PRIDESOLAR",
  "National pride(Solar)" = "NPRIDESOLAR",
  "National development(Solar)" = "DEVSOLAR",
  "Local prosperity(Solar)" = "PROSPERSOLAR",
  "Reliance on government(Solar)" = "RELYSOLAR"
    )%>%
  na.omit()

Solar.fa <- fa(Solar2, nfactors = 2, rotate = "varimax")

print.psych(Solar.fa, cut = 0.40, sort = TRUE)

#fa.diagram(Solar.fa)

```

```{r, echo=FALSE}

# 2 factor

Solar_scores <- psych::factor.scores(Solar2, Solar.fa)

# The factor scores will be stored in the scores element of the returned list
Solar_scores2 <- Solar_scores$scores

#binding factor scores to the dataset

Solarwscores2 <- cbind(Solar, Solar_scores2)%>%
    rename(positive = MR1)%>%
  rename(negative = MR2)

Solarfa <- lm(Risky_Solar ~  Uppercaste + Male + Hindu + Urban + age + State + positive + negative, data = Solarwscores2)
# Print model summary
summary(Solarfa)

benSolarfa <- lm(Ben_Solar ~  Uppercaste + Male + Hindu + Urban + age + State + positive + negative, data = Solarwscores2)
# Print model summary
summary(benSolarfa)

```

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

#alpha test on Eco-pol characteristics of the technology

Coal <- codedmodule2 %>%
  filter(complete.cases(dplyr::select(., DISPLACECOAL:RELYCOAL)))

Coal2 <- codedmodule2 %>%
  dplyr::select("DISPLACECOAL":"RELYCOAL")%>%
    rename(
   "Displacement risk(Coal)" = "DISPLACECOAL",
  "Pollution risk(Coal)" = "POLLUTECOAL",
  "Health risk(Coal)" = "HEALTHCOAL",
  "Job opportunities(Coal)" = "JOBSCOAL",
  "Spoils Natural Beauty(Coal)" = "BEAUTYCOAL",
  "Community pride(Coal)" = "PRIDECOAL",
  "National pride(Coal)" = "NPRIDECOAL",
  "National development(Coal)" = "DEVCOAL",
  "Local prosperity(Coal)" = "PROSPERCOAL",
  "Reliance on government(Coal)" = "RELYCOAL"
    )%>%
  na.omit()

Coal.fa <- fa(Coal2, nfactors = 2, rotate = "varimax")

print.psych(Coal.fa, cut = 0.40, sort = TRUE)

#fa.diagram(Coal.fa)

```

```{r, echo=FALSE}

# 2 factor

Coal_scores <- psych::factor.scores(Coal2, Coal.fa)

# The factor scores will be stored in the scores element of the returned list
Coal_scores2 <- Coal_scores$scores

#binding factor scores to the dataset

Coalwscores2 <- cbind(Coal, Coal_scores2) %>%
  rename(negative = MR1)%>%
  rename(positive = MR2)

Coalfa <- lm(Risky_Coal ~  Uppercaste + Male + Hindu + Urban + age + State + negative + positive , data = Coalwscores2)
# Print model summary
summary(Coalfa)

benCoalfa <- lm(Ben_Coal ~  Uppercaste + Male + Hindu + Urban + age + State + positive + negative, data = Coalwscores2)
# Print model summary
summary(benCoalfa)
```

```{r, echo=FALSE}

library(flextable)

set_flextable_defaults(docx.landscape = TRUE)

flex <- function(data, title=NULL) {
  # this grabs the data and converts it to a flextbale
  flextable(data) %>%
  # this makes the table fill the page width
  set_table_properties(layout = "autofit", width = 1) %>%
  # font size
  fontsize(size=10, part="all") %>%
    #this adds a ttitlecreates an automatic table number
      set_caption(title, 
                  autonum = officer::run_autonum(seq_id = "tab", 
                                                 pre_label = "Table ", 
                                                 post_label = "\n", 
                                                 bkm = "anytable")) #%>%
  # font type
  #font(fontname="Times New Roman", part="all")
}

rename_map <- c(
  "Displacement risk(nuclear)" = "Nuclear energy is leading to displacement of people from their land",
  "Spoils Natural Beauty(nuclear)" = "Nuclear energy spoils the natural beauty of the landscape",
  "Pollution risk(nuclear)" = "Nuclear energy increases pollution of air/water/land",
  "Health risk(nuclear)" = "Nuclear energy poses a great risk to the health of people living around it",
  "Job opportunities(nuclear)" = "Nuclear energy will bring jobs to the local community",
  "Community pride(nuclear)" = "I would be proud if my community used nuclear energy",
  "National pride(nuclear)" = "Nuclear energy is a mark of pride for our nation",
  "National development(nuclear)" = "Nuclear energy pushes forward the country's development",
  "Local prosperity(nuclear)" = "Nuclear energy brings economic prosperity to the surrounding regions",
  "Reliance on government(nuclear)" = "I don't like the idea that I have to rely on the government for electricity from nuclear energy"
)

fa_table <- function(x, cut) {
  #get sorted loadings
  loadings <- fa.sort(x)$loadings %>% round(3)
  #suppress loadings
  loadings[loadings > -cut & loadings < cut] <- ""
  #get additional info  
  add_info <- cbind(x$communalities, 
                    x$uniquenesses,
                    x$complexity) %>%
    # make it a data frame
    as.data.frame() %>%
    # column names
    rename("Communality" = V1,
           "Uniqueness" = V2,
           "Complexity" = V3) %>%
    #get the item names from the vector
    rownames_to_column("item")

  #build table
  loadings %>%
    unclass() %>%
    as.data.frame() %>%
    rownames_to_column("item") %>%
    left_join(add_info) %>%
    mutate(
      item = if_else(item %in% names(rename_map), rename_map[item], item),
      code = names(rename_map)[match(item, rename_map)], # extracting short form
      across(where(is.numeric), round, 3)
    ) %>%
    select(code, everything()) # reorder columns to bring code to the front
}

fa_table(Nuclear.fa, .4) %>%
  rename("Negative Characteristics" = MR1, "Positive Characteristics" = MR2, Items= item, Code = code) %>%
  flex("Nuclear Energy: 2 factor solution") %>%
  autofit()

```

```{r, echo=FALSE}

library(flextable)

flex <- function(data, title=NULL) {
  # this grabs the data and converts it to a flextbale
  flextable(data) %>%
  # this makes the table fill the page width
  set_table_properties(layout = "autofit", width = 1) %>%
  # font size
  fontsize(size=10, part="all") %>%
    #this adds a ttitlecreates an automatic table number
      set_caption(title, 
                  autonum = officer::run_autonum(seq_id = "tab", 
                                                 pre_label = "Table ", 
                                                 post_label = "\n", 
                                                 bkm = "anytable")) #%>%
  # font type
  #font(fontname="Times New Roman", part="all")
}

Nuclear.fa[["Vaccounted"]] %>%
  as.data.frame() %>%
  rownames_to_column("Property") %>%
  rename("Negative Characteristics" = MR1, "Positive Characteristics" = MR2) %>%
    mutate(across(where(is.numeric), round, 3)) %>%
    flex("Eigenvalues and Variance Explained for 2 Factor Solution")

```

\newpage

### 2024-01-15 module2/module2IVgraphs.Rmd
damn

@@
   gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd,Risky_Hydro_n, Risky_Solar_n, Risky_Wind_n, Risky_Nuclear_n, Risky_Coal_n, Risky_Gas_n, Risky_Oil_n) %>%
-  select(SYSTEMDEMO, technology, summary) %>%
+  dplyr::select(SYSTEMDEMO, technology, summary) %>%
   # separate risky from variable suffix
@@
   #clean up
-  select(-Risky)%>%
+  dplyr::select(-Risky)%>%
   arrange(mean) %>%
@@
   gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd, Risky_Hydro_n, Risky_Solar_n, Risky_Wind_n, Risky_Nuclear_n, Risky_Coal_n, Risky_Gas_n, Risky_Oil_n) %>%
-  select(SYSTEMTECHNO, technology, summary) %>%
+  dplyr::select(SYSTEMTECHNO, technology, summary) %>%
   # separate risky from variable suffix
@@
   gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd, Risky_Hydro_n, Risky_Solar_n, Risky_Wind_n, Risky_Nuclear_n, Risky_Coal_n, Risky_Gas_n, Risky_Oil_n) %>%
-  select(SYSTEMRELIGION, technology, summary) %>%
+  dplyr::select(SYSTEMRELIGION, technology, summary) %>%
   # separate risky from variable suffix
@@
   #clean up
-  select(-Risky)%>%
+  dplyr::select(-Risky)%>%
   arrange(mean)%>%
@@
   gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd, Risky_Hydro_n, Risky_Solar_n, Risky_Wind_n, Risky_Nuclear_n, Risky_Coal_n, Risky_Gas_n, Risky_Oil_n) %>%
-  select(SYSTEMTOTAL, technology, summary) %>%
+  dplyr::select(SYSTEMTOTAL, technology, summary) %>%
   # separate risky from variable suffix
@@
   gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd, Risky_Hydro_n, Risky_Solar_n, Risky_Wind_n, Risky_Nuclear_n, Risky_Coal_n, Risky_Gas_n, Risky_Oil_n) %>%
-  select(SYSTEMDEMO, technology, summary) %>%
+  dplyr::select(SYSTEMDEMO, technology, summary) %>%
   # separate risky from variable suffix
@@
   #clean up
-  select(-Risky)%>%
+  dplyr::select(-Risky)%>%
   arrange(SYSTEMDEMO)
@@
 decenrisk2 <- codedmodule2%>%
-    select(starts_with(c("Risky","Ben","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
+    dplyr::select(starts_with(c("Risky","Ben","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
   rowwise()%>%
@@
   gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd,Risky_Hydro_n, Risky_Solar_n, Risky_Wind_n, Risky_Nuclear_n, Risky_Coal_n, Risky_Gas_n, Risky_Oil_n ) %>%
-  select(Pro_decentralisation, technology, summary) %>%
+  dplyr::select(Pro_decentralisation, technology, summary) %>%
   # separate risky from variable suffix
@@
   #clean up
-  select(-Risky)%>%
+  dplyr::select(-Risky)%>%
   arrange(Pro_decentralisation)
@@
 largerisk2 <- codedmodule2%>%
-    select(starts_with(c("Risky","Ben","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
+    dplyr::select(starts_with(c("Risky","Ben","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
   rowwise()%>%
@@
   gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd, Risky_Hydro_n, Risky_Solar_n, Risky_Wind_n, Risky_Nuclear_n, Risky_Coal_n, Risky_Gas_n, Risky_Oil_n) %>%
-  select(Pro_largescale, technology, summary) %>%
+  dplyr::select(Pro_largescale, technology, summary) %>%
   # separate risky from variable suffix
@@
   #clean up
-  select(-Risky)%>%
+  dplyr::select(-Risky)%>%
   arrange(Pro_largescale)
@@
 Kscalescores <- codedmodule2 %>%
-  select(starts_with(c("Risky","K_I","K_S", "K_H", "K_E")))%>%
+  dplyr::select(starts_with(c("Risky_Nuclear","K_I","K_S", "K_H", "K_E")))%>%
   rowwise()%>%
@@
 
+Knuclearlm <- lm(Risky_Nuclear ~ Individualism_score + Hierarchy_score , data = Kscalescores)
+summary(Knuclearlm)
 ```
@@
 
-```{r, echo=FALSE}
+```{r dev = "jpg", echo=FALSE}
 knitr::opts_chunk$set(warning = FALSE, message = FALSE)
@@
   geom_vline(xintercept=3, colour="black", lwd=1)+
-  labs(x = " Communitarianism to Individualism", y = "Egalitarianism to Hierarchy")
+  labs(x = " Communitarianism to Individualism", y = "Egalitarianism to Hierarchy")+
+  ylim(1,5)+
+  xlim(1,5)+
+  theme_minimal()
 

### 2024-01-15 module2/module2extra.Rmd
damn

@@
 ```
+
+```{r}
+staterisky <- joineddf %>%
+  dplyr::select(!starts_with(c("Ben_IND", "Risky_IND")))%>%
+  dplyr::select(starts_with("Risky"), State)
+
+staterisky_mean <- staterisky %>%
+  group_by(State) %>%
+  summarise(
+    Mean_Risky_Hydro = mean(Risky_Hydro, na.rm = TRUE),
+    Mean_Risky_Solar = mean(Risky_Solar, na.rm = TRUE),
+    Mean_Risky_Wind = mean(Risky_Wind, na.rm = TRUE),
+    Mean_Risky_Nuclear = mean(Risky_Nuclear, na.rm = TRUE),
+    Mean_Risky_Coal = mean(Risky_Coal, na.rm = TRUE),
+    Mean_Risky_Gas = mean(Risky_Gas, na.rm = TRUE),
+    Mean_Risky_Oil = mean(Risky_Oil, na.rm = TRUE)
+  )
+
+str(staterisky_mean)
+
+# Load required packages
+library(dplyr)
+library(tidyr)
+library(ggplot2)
+
+# Convert to long format
+long_data <- staterisky_mean %>%
+  gather(Technology, Mean_Score, -State) %>%
+  mutate(Technology = gsub("Mean_Risky_", "", Technology))
+
+# Order Technologies
+technology_order <- c("Nuclear", "Gas", "Coal", "Oil", "Hydro", "Wind", "Solar")
+long_data$Technology <- factor(long_data$Technology, levels = technology_order)
+
+# Plot the graph
+ggplot(long_data, aes(x = Technology, y = Mean_Score, color = State, group = State)) +
+  geom_line(size = 1) +
+  geom_point(size = 3) +
+  labs(title = "Mean Perceived Risk by State",
+       x = "Technology", y = "Mean Score") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+```
+
+```{r}
+# Using dplyr and tidyr
+
+standardized_data <- long_data %>%
+  group_by(Technology) %>%
+  mutate(
+    Overall_Mean = mean(Mean_Score, na.rm = TRUE),
+    Std_Dev = sd(Mean_Score, na.rm = TRUE)
+  ) %>%
+  ungroup() %>%
+  mutate(Standardized_Score = (Mean_Score - Overall_Mean) / Std_Dev) %>%
+  dplyr::select(-Overall_Mean, -Std_Dev)  #
+
+# Order Technologies
+technology_order <- c("Nuclear", "Gas", "Coal", "Oil", "Hydro", "Wind", "Solar")
+standardized_data$Technology <- factor(standardized_data$Technology, levels = technology_order)
+
+# Plot the graph
+ggplot(standardized_data, aes(x = Technology, y = Standardized_Score, color = State, group = State)) +
+  geom_line(size = 1) +
+  geom_point(size = 3) +
+  labs(title = "Standardised Scores of Technologies by State",
+       x = "Technology", y = "Z Score") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+```

### 2024-01-24 corstuff.Rmd
the problem of correlation

@@
 
+fascales_mice <- codedmodule2 %>%
+  dplyr::select(starts_with(c("K_","Risky_Nuclear","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%
+  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
+                                      . == "25-34 years old" ~ 2,
+                                      . ==  "35-44 years old" ~3,
+                                      . == "45-54 years old" ~ 4,
+                                      . == "55-64 years old" ~ 5,
+                                      . == "65-74 years old" ~ 6,
+                                      . == "75 years or older" ~ 7)))%>%
+  na.omit()
+
+```
+
+```{r, echo=FALSE}
+
 fascale_scores
@@
 
+TMalldemos <- joineddf %>%
+            filter(State =="Tamil Nadu")%>%
+            dplyr::select(Risky_Nuclear, Uppercaste, Male, Hindu, Urban, age, State)
+
 # 3 linear models - 1) lm with demographic variables except age and State
-TM_demo <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban, data = TM)
+TM_demo <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban +age, data = TMalldemos)
+
+summary(TM_demo)
 
@@
 summary(TM1_ecopol)
+
+TM2<- fascale_scores2 %>%
+  filter(State == "Tamil Nadu")
+
+# 3) lm with kahan 
+TM2_kahan <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age  + Communitarianism_score + Egalitarianism_score, data = TM2)
+
+summary(TM2_kahan)
+
+# 4) lm with ecopolvars 
+TM2_allscales <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + Pdevelop + Ndevelop + Communitarianism_score + Egalitarianism_score , data = TM2)
+
+summary(TM2_allscales)
+
+TM2_ecopol <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age +  Pdevelop + Ndevelop,  data = TM2)
+
+summary(TM2_ecopol)
 

### 2024-01-24 nuclear in comparison.Rmd
the problem of correlation

@@
 
+str(data_by_state)
+str(joineddf)
+
 ```
@@
 
+# Maharshtra t tests
+
+```{r, echo = FALSE, fig.width=14, fig.height=6}
+
+Mperceivedrisk <- joineddf %>% 
+  filter(State == "Maharashtra")%>%
+  dplyr::select("Risky_Solar", "Risky_Hydro", "Risky_Wind", "Risky_Nuclear", "Risky_Coal", "Risky_Gas", "Risky_Oil") %>%
+  gather(key = "technology", value = "perceived_risk") %>% 
+  mutate(technology = gsub("Risky_", "", technology)) %>%
+  na.omit()
+
+result_ttestM <- pairwise.t.test(Mperceivedrisk$perceived_risk, Mperceivedrisk$technology, p.adjust.method = "BH")
+
+# visualising the pairwaise t test results. the non significant pairs are grey
+
+tidy_result_ttestM <- broom::tidy(result_ttestM)
+
+Mheatmap1 <- ggplot(tidy_result_ttestM, aes(x = group1, y = group2, fill = p.value)) + 
+  geom_tile(color = "white") + 
+  scale_fill_gradient2(low = "firebrick2", high = "white", midpoint = 0.025, 
+                       limits = c(0, 0.05), space = "Lab", 
+                       name = "P-value") + 
+  theme_classic() + 
+  labs(x = "", y = "") + 
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
+   theme(axis.text.y = element_text(size=20), 
+        axis.text.x = element_text(size=20),
+        axis.title.y = element_text(size=20),
+        axis.title.x = element_text(size=20),
+        title = element_text(size=20),
+        legend.text = element_text(size=12))
+
+#Question- Why there is significant difference statistically - if the medians are the same in the boxplot.
+#Q3: How do perceptions of benefit from nuclear energy compare with other source of energy?
+
+# H : benefits from all energy technologies will be similar 
+# include regression, heat maps, bar graphs? - decide which ones are good to include
+
+Mperceivedbenefit <-joineddf %>% 
+  filter(State=="Maharashtra")%>%
+  dplyr::select("Ben_Solar", "Ben_Hydro", "Ben_Wind", "Ben_Nuclear", "Ben_Coal", "Ben_Gas", "Ben_Oil") %>%
+  gather(key = "technology", value = "perceived_benefit") %>% 
+  mutate(technology = gsub("Ben_", "", technology)) %>%
+  na.omit()
+
+result_ttestbenM <- pairwise.t.test(Mperceivedbenefit$perceived_benefit, Mperceivedbenefit$technology, p.adjust.method = "BH")
+
+# visualising the pairwaise t test results. the non significant pairs are grey
+
+tidy_resultbcM <- broom::tidy(result_ttestbenM)
+
+library(ggplot2)
+Mheatmap2 <- ggplot(tidy_resultbcM, aes(x = group1, y = group2, fill = p.value)) + 
+  geom_tile(color = "white") + 
+  scale_fill_gradient2(low = "palegreen3", high = "white", midpoint = 0.025, 
+                       limits = c(0, 0.05), space = "Lab", 
+                       name = "P-value") + 
+  theme_classic() + 
+  labs(x = "", y = "") + 
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
+   theme(axis.text.y = element_text(size=20), 
+        axis.text.x = element_text(size=20),
+        axis.title.y = element_text(size=20),
+        axis.title.x = element_text(size=20),
+        title = element_text(size=20),
+        legend.text = element_text(size=12))
+
+grid.arrange(Mheatmap1, Mheatmap2, ncol=2)
+
+```
+
+# Tamil Nadu  t tests
+
+```{r, echo = FALSE, fig.width=14, fig.height=6}
+
+TMperceivedrisk <- joineddf %>% 
+  filter(State == "Tamil Nadu")%>%
+  dplyr::select("Risky_Solar", "Risky_Hydro", "Risky_Wind", "Risky_Nuclear", "Risky_Coal", "Risky_Gas", "Risky_Oil") %>%
+  gather(key = "technology", value = "perceived_risk") %>% 
+  mutate(technology = gsub("Risky_", "", technology)) %>%
+  na.omit()
+
+result_ttestTM <- pairwise.t.test(TMperceivedrisk$perceived_risk, TMperceivedrisk$technology, p.adjust.method = "BH")
+
+# visualising the pairwaise t test results. the non significant pairs are grey
+
+tidy_result_ttestTM <- broom::tidy(result_ttestTM)
+
+TMheatmap1 <- ggplot(tidy_result_ttestTM, aes(x = group1, y = group2, fill = p.value)) + 
+  geom_tile(color = "white") + 
+  scale_fill_gradient2(low = "firebrick2", high = "white", midpoint = 0.025, 
+                       limits = c(0, 0.05), space = "Lab", 
+                       name = "P-value") + 
+  theme_classic() + 
+  labs(x = "", y = "") + 
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
+   theme(axis.text.y = element_text(size=20), 
+        axis.text.x = element_text(size=20),
+        axis.title.y = element_text(size=20),
+        axis.title.x = element_text(size=20),
+        title = element_text(size=20),
+        legend.text = element_text(size=12))
+
+#Question- Why there is significant difference statistically - if the medians are the same in the boxplot.
+#Q3: How do perceptions of benefit from nuclear energy compare with other source of energy?
+
+# H : benefits from all energy technologies will be similar 
+# include regression, heat maps, bar graphs? - decide which ones are good to include
+
+TMperceivedbenefit <-joineddf %>% 
+  filter(State=="Tamil Nadu")%>%
+  dplyr::select("Ben_Solar", "Ben_Hydro", "Ben_Wind", "Ben_Nuclear", "Ben_Coal", "Ben_Gas", "Ben_Oil") %>%
+  gather(key = "technology", value = "perceived_benefit") %>% 
+  mutate(technology = gsub("Ben_", "", technology)) %>%
+  na.omit()
+
+result_ttestbenTM <- pairwise.t.test(TMperceivedbenefit$perceived_benefit, TMperceivedbenefit$technology, p.adjust.method = "BH")
+
+# visualising the pairwaise t test results. the non significant pairs are grey
+
+tidy_resultbcTM <- broom::tidy(result_ttestbenTM)
+
+library(ggplot2)
+TMheatmap2 <- ggplot(tidy_resultbcTM, aes(x = group1, y = group2, fill = p.value)) + 
+  geom_tile(color = "white") + 
+  scale_fill_gradient2(low = "palegreen3", high = "white", midpoint = 0.025, 
+                       limits = c(0, 0.05), space = "Lab", 
+                       name = "P-value") + 
+  theme_classic() + 
+  labs(x = "", y = "") + 
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
+   theme(axis.text.y = element_text(size=20), 
+        axis.text.x = element_text(size=20),
+        axis.title.y = element_text(size=20),
+        axis.title.x = element_text(size=20),
+        title = element_text(size=20),
+        legend.text = element_text(size=12))
+
+grid.arrange(TMheatmap1, TMheatmap2, ncol=2)
+
+```
+
+# Uttar Pradesh  t tests
+
+```{r, echo = FALSE, fig.width=14, fig.height=6}
+
+UPperceivedrisk <- joineddf %>% 
+  filter(State == "Uttar Pradesh")%>%
+  dplyr::select("Risky_Solar", "Risky_Hydro", "Risky_Wind", "Risky_Nuclear", "Risky_Coal", "Risky_Gas", "Risky_Oil") %>%
+  gather(key = "technology", value = "perceived_risk") %>% 
+  mutate(technology = gsub("Risky_", "", technology)) %>%
+  na.omit()
+
+result_ttestUP <- pairwise.t.test(UPperceivedrisk$perceived_risk, UPperceivedrisk$technology, p.adjust.method = "BH")
+
+# visualising the pairwaise t test results. the non significant pairs are grey
+
+tidy_result_ttestUP <- broom::tidy(result_ttestTM)
+
+UPheatmap1 <- ggplot(tidy_result_ttestUP, aes(x = group1, y = group2, fill = p.value)) + 
+  geom_tile(color = "white") + 
+  scale_fill_gradient2(low = "firebrick2", high = "white", midpoint = 0.025, 
+                       limits = c(0, 0.05), space = "Lab", 
+                       name = "P-value") + 
+  theme_classic() + 
+  labs(x = "", y = "") + 
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
+   theme(axis.text.y = element_text(size=20), 
+        axis.text.x = element_text(size=20),
+        axis.title.y = element_text(size=20),
+        axis.title.x = element_text(size=20),
+        title = element_text(size=20),
+        legend.text = element_text(size=12))
+
+#Question- Why there is significant difference statistically - if the medians are the same in the boxplot.
+#Q3: How do perceptions of benefit from nuclear energy compare with other source of energy?
+
+# H : benefits from all energy technologies will be similar 
+# include regression, heat maps, bar graphs? - decide which ones are good to include
+
+UPperceivedbenefit <-joineddf %>% 
+  filter(State=="Uttar Pradesh")%>%
+  dplyr::select("Ben_Solar", "Ben_Hydro", "Ben_Wind", "Ben_Nuclear", "Ben_Coal", "Ben_Gas", "Ben_Oil") %>%
+  gather(key = "technology", value = "perceived_benefit") %>% 
+  mutate(technology = gsub("Ben_", "", technology)) %>%
+  na.omit()
+
+result_ttestbenUP <- pairwise.t.test(UPperceivedbenefit$perceived_benefit, UPperceivedbenefit$technology, p.adjust.method = "BH")
+
+# visualising the pairwaise t test results. the non significant pairs are grey
+
+tidy_resultbcUP <- broom::tidy(result_ttestbenUP)
+
+library(ggplot2)
+UPheatmap2 <- ggplot(tidy_resultbcUP, aes(x = group1, y = group2, fill = p.value)) + 
+  geom_tile(color = "white") + 
+  scale_fill_gradient2(low = "palegreen3", high = "white", midpoint = 0.025, 
+                       limits = c(0, 0.05), space = "Lab", 
+                       name = "P-value") + 
+  theme_classic() + 
+  labs(x = "", y = "") + 
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
+   theme(axis.text.y = element_text(size=20), 
+        axis.text.x = element_text(size=20),
+        axis.title.y = element_text(size=20),
+        axis.title.x = element_text(size=20),
+        title = element_text(size=20),
+        legend.text = element_text(size=12))
+
+grid.arrange(UPheatmap1, UPheatmap2, ncol=2)
+
+```
+
+# Rajasthan  t tests
+
+```{r, echo = FALSE, fig.width=14, fig.height=6}
+
+Rperceivedrisk <- joineddf %>% 
+  filter(State == "Rajasthan")%>%
+  dplyr::select("Risky_Solar", "Risky_Hydro", "Risky_Wind", "Risky_Nuclear", "Risky_Coal", "Risky_Gas", "Risky_Oil") %>%
+  gather(key = "technology", value = "perceived_risk") %>% 
+  mutate(technology = gsub("Risky_", "", technology)) %>%
+  na.omit()
+
+result_ttestR <- pairwise.t.test(Rperceivedrisk$perceived_risk, Rperceivedrisk$technology, p.adjust.method = "BH")
+
+# visualising the pairwaise t test results. the non significant pairs are grey
+
+tidy_result_ttestR <- broom::tidy(result_ttestR)
+
+Rheatmap1 <- ggplot(tidy_result_ttestR, aes(x = group1, y = group2, fill = p.value)) + 
+  geom_tile(color = "white") + 
+  scale_fill_gradient2(low = "firebrick2", high = "white", midpoint = 0.025, 
+                       limits = c(0, 0.05), space = "Lab", 
+                       name = "P-value") + 
+  theme_classic() + 
+  labs(x = "", y = "") + 
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
+   theme(axis.text.y = element_text(size=20), 
+        axis.text.x = element_text(size=20),
+        axis.title.y = element_text(size=20),
+        axis.title.x = element_text(size=20),
+        title = element_text(size=20),
+        legend.text = element_text(size=12))
+
+#Question- Why there is significant difference statistically - if the medians are the same in the boxplot.
+#Q3: How do perceptions of benefit from nuclear energy compare with other source of energy?
+
+# H : benefits from all energy technologies will be similar 
+# include regression, heat maps, bar graphs? - decide which ones are good to include
+
+Rperceivedbenefit <-joineddf %>% 
+  filter(State=="Rajasthan")%>%
+  dplyr::select("Ben_Solar", "Ben_Hydro", "Ben_Wind", "Ben_Nuclear", "Ben_Coal", "Ben_Gas", "Ben_Oil") %>%
+  gather(key = "technology", value = "perceived_benefit") %>% 
+  mutate(technology = gsub("Ben_", "", technology)) %>%
+  na.omit()
+
+result_ttestbenR <- pairwise.t.test(Rperceivedbenefit$perceived_benefit, Rperceivedbenefit$technology, p.adjust.method = "BH")
+
+# visualising the pairwaise t test results. the non significant pairs are grey
+
+tidy_resultbcR <- broom::tidy(result_ttestbenR)
+
+library(ggplot2)
+Rheatmap2 <- ggplot(tidy_resultbcR, aes(x = group1, y = group2, fill = p.value)) + 
+  geom_tile(color = "white") + 
+  scale_fill_gradient2(low = "palegreen3", high = "white", midpoint = 0.025, 
+                       limits = c(0, 0.05), space = "Lab", 
+                       name = "P-value") + 
+  theme_classic() + 
+  labs(x = "", y = "") + 
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
+   theme(axis.text.y = element_text(size=20), 
+        axis.text.x = element_text(size=20),
+        axis.title.y = element_text(size=20),
+        axis.title.x = element_text(size=20),
+        title = element_text(size=20),
+        legend.text = element_text(size=12))
+
+grid.arrange(Rheatmap1, Rheatmap2, ncol=2)
+
+```
+
+# West Bengal  t tests
+
+```{r, echo = FALSE, fig.width=14, fig.height=6}
+
+WBperceivedrisk <- joineddf %>% 
+  filter(State == "West Bengal")%>%
+  dplyr::select("Risky_Solar", "Risky_Hydro", "Risky_Wind", "Risky_Nuclear", "Risky_Coal", "Risky_Gas", "Risky_Oil") %>%
+  gather(key = "technology", value = "perceived_risk") %>% 
+  mutate(technology = gsub("Risky_", "", technology)) %>%
+  na.omit()
+
+result_ttestWB <- pairwise.t.test(WBperceivedrisk$perceived_risk, WBperceivedrisk$technology, p.adjust.method = "BH")
+
+# visualising the pairwaise t test results. the non significant pairs are grey
+
+tidy_result_ttestWB <- broom::tidy(result_ttestWB)
+
+WBheatmap1 <- ggplot(tidy_result_ttestWB, aes(x = group1, y = group2, fill = p.value)) + 
+  geom_tile(color = "white") + 
+  scale_fill_gradient2(low = "firebrick2", high = "white", midpoint = 0.025, 
+                       limits = c(0, 0.05), space = "Lab", 
+                       name = "P-value") + 
+  theme_classic() + 
+  labs(x = "", y = "") + 
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
+   theme(axis.text.y = element_text(size=20), 
+        axis.text.x = element_text(size=20),
+        axis.title.y = element_text(size=20),
+        axis.title.x = element_text(size=20),
+        title = element_text(size=20),
+        legend.text = element_text(size=12))
+
+#Question- Why there is significant difference statistically - if the medians are the same in the boxplot.
+#Q3: How do perceptions of benefit from nuclear energy compare with other source of energy?
+
+# H : benefits from all energy technologies will be similar 
+# include regression, heat maps, bar graphs? - decide which ones are good to include
+
+WBperceivedbenefit <-joineddf %>% 
+  filter(State=="West Bengal")%>%
+  dplyr::select("Ben_Solar", "Ben_Hydro", "Ben_Wind", "Ben_Nuclear", "Ben_Coal", "Ben_Gas", "Ben_Oil") %>%
+  gather(key = "technology", value = "perceived_benefit") %>% 
+  mutate(technology = gsub("Ben_", "", technology)) %>%
+  na.omit()
+
+result_ttestbenWB <- pairwise.t.test(WBperceivedbenefit$perceived_benefit, WBperceivedbenefit$technology, p.adjust.method = "BH")
+
+# visualising the pairwaise t test results. the non significant pairs are grey
+
+tidy_resultbcWB <- broom::tidy(result_ttestbenWB)
+
+library(ggplot2)
+WBheatmap2 <- ggplot(tidy_resultbcWB, aes(x = group1, y = group2, fill = p.value)) + 
+  geom_tile(color = "white") + 
+  scale_fill_gradient2(low = "palegreen3", high = "white", midpoint = 0.025, 
+                       limits = c(0, 0.05), space = "Lab", 
+                       name = "P-value") + 
+  theme_classic() + 
+  labs(x = "", y = "") + 
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
+   theme(axis.text.y = element_text(size=20), 
+        axis.text.x = element_text(size=20),
+        axis.title.y = element_text(size=20),
+        axis.title.x = element_text(size=20),
+        title = element_text(size=20),
+        legend.text = element_text(size=12))
+
+grid.arrange(WBheatmap1, WBheatmap2, ncol=2)
+
+```
 ## Net benefit by state

### 2024-01-27 corstuff.Rmd
some new stuff

@@
 # code likert scale for variables for Kahan scale into numbers
-  mutate_at(vars(starts_with (c("K_S","K_E","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE","DEVNUCLEAR","PROSPER", "RELY"))), funs(case_when(. == "Strongly disagree" ~ 1, 
+  mutate_at(vars(starts_with (c("K_H","K_I","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE","DEVNUCLEAR","PROSPER", "RELY"))), funs(case_when(. == "Strongly disagree" ~ 1, 
                . == "Somewhat disagree" ~ 2,
@@
 # reverse code for likert scale for variables for Kahan scale into numbers
-  mutate_at(vars(starts_with (c("K_H","K_I"))), funs(case_when(. == "Strongly disagree" ~ 5, 
+  mutate_at(vars(starts_with (c("K_S","K_E"))), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                                . == "Somewhat disagree" ~ 4,
@@
 
-#print.psych(kahan.fa, cut = 0.4, sort = TRUE)
-
-```
+print.psych(kahan.fa, cut = 0.4, sort = TRUE)
+
+```
+
+```{r, echo=FALSE}
+
+library(flextable)
+
+flex <- function(data, title=NULL) {
+  # this grabs the data and converts it to a flextbale
+  flextable(data) %>%
+  # this makes the table fill the page width
+  set_table_properties(layout = "autofit", width = 1) %>%
+  # font size
+  fontsize(size=11, part="all") %>%
+    #this adds a ttitlecreates an automatic table number
+      set_caption(title, 
+                  autonum = officer::run_autonum(seq_id = "tab", 
+                                                 pre_label = "Table ", 
+                                                 post_label = "\n", 
+                                                 bkm = "anytable")) #%>%
+  # font type
+  #font(fontname="Times New Roman", part="all")
+}
+
+rename_map <- c(
+  "K_SHARM" = "(C)Sometimes the government needs to make laws that keep people from hurting themselves.",
+  "K_SLIMCHOI" = "(C)The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.",
+  "K_SPROTECT" = "(C)The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.",
+  "K_HEQUAL" = "(H)We have gone too far in pushing equal rights in this country.",
+  "K_ERADEQ1" = "(E)We need to dramatically reduce inequalities between the rich and the poor.",
+  "K_EWEALTH" = "(E)Our society would be better off if the distribution of wealth was more equal.",
+  "K_ERADEQ2" = "(E)We need to dramatically reduce inequalities between men and women.",
+
+  "K_IINTRFER" = "(I)The government interferes far too much in our everyday lives.",
+  "K_HREVDIS1" = "(H)Nowadays it seems like there is just as much discrimination against upper castes as there is against Dalits.",
+  "K_EDISCRIM" = "(E)Discrimination against minorities is still a very serious problem in our society.",
+  "K_IPRIVACY" = "(I)The government should stop telling people how to live their lives.",
+  "K_IPROTECT" = "(I)It’s not the government’s business to try to protect people from themselves."
+)
+
+fa_table <- function(x) {
+  #get sorted loadings
+  loadings <- fa.sort(x)$loadings %>% round(3)
+  #get additional info  
+  add_info <- cbind(x$communalities, 
+                    x$uniquenesses,
+                    x$complexity) %>%
+    # make it a data frame
+    as.data.frame() %>%
+    # column names
+   rename("Communality" = V1,
+           "Uniqueness" = V2,
+           "Complexity" = V3) %>%
+    #get the item names from the vector
+    rownames_to_column("item")
+  #build table
+  loadings %>%
+    unclass() %>%
+    as.data.frame() %>%
+    rownames_to_column("item") %>%
+    left_join(add_info) %>%
+    mutate(
+      item = if_else(item %in% names(rename_map), rename_map[item], item),
+      across(where(is.numeric), round, 3)
+    )
+}
+
+fa_table(kahan.fa) %>%
+  #rename(Pdevelop = MR1, Ndevelop = MR2, Items= item) %>%
+  flex("Kahan Exploratory Factor Analysis Table")
+
+```
+
+```{r, echo=FALSE}
+
+kahan.fa[["Vaccounted"]] %>%
+  as.data.frame() %>%
+  rownames_to_column("Property") %>%
+    mutate(across(where(is.numeric), round, 3)) %>%
+    flex("Eigenvalues and Variance Explained for Rotated Factor Solution")
+
+```
+
+## alternative Kahan scores
+```{r, echo=FALSE}
+
+Kscalescores <- fascales %>%
+  dplyr::select(!starts_with(("K_I")))%>%
+  rowwise()%>%
+  dplyr::mutate(Communitarianism_score = mean(c_across(K_SHARM:K_SPROTECT)))%>%
+  dplyr::mutate(Egalitarianism_score = mean(c_across(K_HEQUAL:K_ERADEQ2)))%>%
+  dplyr::select(!starts_with(c("K_I","K_S", "K_H", "K_E")))
+
+```
+
+```{r fit-measures-display, echo = FALSE}
+# Extract fit measures
+fit_measures <- fitMeasures(Kahan_cfa, fit.measures = c("CFI", "TLI", "RMSEA", "rmsea.ci.upper", "rmsea.ci.lower"))
+fit_measures2 <- fitMeasures(Kahan_cfa)
+# Convert to a data frame for presentation
+fit_df <- data.frame(Measure = names(fit_measures), Value = fit_measures) %>%
+  mutate(Measure = case_when(
+    Measure == "cfi" ~ "Comparative Fit Index (CFI) ",
+    Measure == "tli" ~ "Tucker-Lewis Index (TLI)",
+    Measure == "rmsea" ~ "Root Mean Square Error of Approximation(RMSEA)",
+    Measure == "rmsea.ci.upper" ~ "RMSEA 90 Percent confidence interval - lower",
+    Measure == "rmsea.ci.lower" ~ "RMSEA 90 Percent confidence interval - upper",
+    TRUE ~ as.character(Measure)
+  )) %>%
+  mutate(Value = round(Value, 3)) %>%
+  remove_rownames()
+
+#RMSEA - between 0.05 and 0.08 (reasonable fit), less than 0.05 close fit and greater than 0.10 is poor fit 
+#CFI - greater than 0.90 or 0.95 indicates good fit
+#TFI - CFI>TFI >0.90 - indicates good fit
+
+```
+# Confirmatory Factor Analysis(CFA): Kahan Scale
+
+**Cronbach's Alpha on Kahan et al(2007) Scale: A Note**
+
+The Individualism items (indicated by K_I) were bringing down the Cronbach's alpha values in the Kahan scale.
+The Alpha for Individualism- Communitarian scale was 0.49.
+After removing the Individualism items (K_I) the alpha for this factor was 0.71.
+The reasons for this could be that the individualism items are not well adapted to the Indian population.
+
+```{r, echo =FALSE}
+# Display fit measures using kable
+knitr::kable(fit_df, caption = "Fit Measures from the CFA", booktabs = TRUE) %>%
+  kable_styling(latex_options = c("striped", "hold_position"))
+
+```
+
+\newpage
+
+```{r, echo=FALSE}
+
+# Extract parameter estimates
+params <- parameterEstimates(Kahan_cfa, standardized = TRUE)%>%
+   slice(1:(n()-10))
+
+params1 <- params %>%
+  mutate(rhs = case_when(
+    rhs == "K_SHARM" ~ "Sometimes the government needs to make laws that keep people from hurting themselves.",
+    rhs == "K_SLIMCHOI" ~ "The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.",
+    rhs == "K_SPROTECT" ~ "The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.",
+    rhs == "K_HEQUAL" ~ "We have gone too far in pushing equal rights in this country.",
+    rhs == "K_ERADEQ1" ~ "We need to dramatically reduce inequalities between the rich and the poor.",
+    rhs == "K_EWEALTH" ~ "Our society would be better off if the distribution of wealth was more equal.",
+    rhs == "K_ERADEQ2" ~ "We need to dramatically reduce inequalities between men and women.",
+    TRUE ~ as.character(rhs)
+  )) %>%
+  dplyr::select(!c(lhs,op, std.nox)) %>%
+    rename(
+    "Items" = rhs,
+    "Loadings" = est,
+    "Standard Error" = se,
+    "zvalue" = z) %>%
+  mutate(across(c("Loadings", "Standard Error", "zvalue"), round, 3))
+
+params1$Scale <- NA
+params1$Scale[1:3] <- "Communitarian"
+params1$Scale[4:7] <- "Hierarchy-Egalitarianism"
+params1 <- params1[, c("Scale", setdiff(names(params1), "Scale"))]
+CFAkahan <- knitr::kable(params1, booktabs = TRUE, caption = "Confirmatory Factor Analysis(CFA) on Kahan et al(2007) scale adapted to India") %>%
+  kable_styling(latex_options = c("striped","scale_down", "hold_position", "repeat_header"))%>%
+  column_spec(column = 2, width = "4cm")
+
+# Print the table
+CFAkahan %>%
+  landscape()
+
+```
+
+## Kahan scater plot from the CFA scores 
+```{r, echo = FALSE}
+
+Kahan_Kscores %>%
+  ggplot(aes(KahanS, KahanH))+
+  geom_count(aes(color = ..n.., size = ..n..))+
+  guides(color = 'legend')+
+  geom_hline(yintercept=0, colour="black", lwd=0.5)+
+  geom_vline(xintercept=0, colour="black", lwd=0.5)+
+  labs(x = "Individualism to Communitarianism", y = "Hierarchy to Egalitarianism")+
+  ylim(-2,3)+
+  xlim(-2,3)+
+  theme_minimal() 
+```
+
+\newpage
+
+# Factor Analysis: New Eco-political Scale
+
+```{r, echo=FALSE}
+
+library(psych)
+library(tidyverse)
+
+ecopolall <- fascales %>%
+        dplyr::select("WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR")
+
+ecopolall_alpha <- psych::alpha(ecopolall, check.keys = TRUE)
+
+#summary(ecopolall_alpha)
+
+# when we combine both the scales the alpha is high at 0.785 (almost 0.8)
+
+# FA on all ecopol variables except systems of governance
+
+ecopolall_cor <- cor(ecopolall)
+PCA24 <- principal(ecopolall, nfactors = 24, rotate = "none") # no rotation to start with.
+
+#PCA24$loadings
+
+#fa.parallel(ecopolall_cor)
+# this suggests 2 factors if we go by FA or 8 by PCA. let's try both and see how they look conceptually 
+# running EFA using psych package
+
+ecopolall2.fa <- fa(ecopolall, nfactors = 2, rotate = "varimax")
+
+print.psych(ecopolall2.fa, sort = TRUE)
+
+# I don't know still doesn't make a lot of sense to me- the two factors make more sense - 1) people centered development 2) nationalist development
+# So I am going to extract factor scores and bind them to the dataset
+
+ecopolall_scores <- psych::factor.scores(ecopolall, ecopolall2.fa)
+
+# The factor scores will be stored in the scores element of the returned list
+scores1 <- ecopolall_scores$scores
+
+#binding factor scores to the dataset
+
+fascale_scores <- cbind(Kahan_Kscores, scores1) %>%
+  rename(Pdevelop = MR1)%>%
+  rename(Ndevelop = MR2) #%>%
+  #dplyr::select(!starts_with(c("K_","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR")))
+
+```
+
+```{r, echo=FALSE}
+library(ggplot2)
+library(fmsb)
+
+# Extract the loadings
+loadings_matrix <- ecopolall2.fa$loadings[1:24, ]
+
+loadings_df <- as.data.frame(as.matrix(loadings_matrix))
+
+# Adding rownames to the dataframe as a new column
+loadings_df <- loadings_df %>%
+  rownames_to_column(var = "variable")
+
+# Pivot to longer format first
+long_loadings_df <- loadings_df %>%
+  pivot_longer(cols = c(MR1, MR2), names_to = "Factors", values_to = "value")
+
+# Pivot the longer format to wide format
+wide_loadings_df <- long_loadings_df %>%
+  pivot_wider(names_from = variable, values_from = value) %>%
+  mutate(Factors = case_when(
+    Factors == "MR1" ~ "People Centered Development (Pdevelop)",
+    Factors == "MR2" ~ "Nationalist Development (Ndevelop)",
+    TRUE ~ Factors
+  )) %>%
+  column_to_rownames("Factors")
+
+# Define the variable ranges: maximum and minimum
+max_min <- data.frame(
+  WEALTHLIM = c(0.8, -0.6), MECHANISATION = c(0.8, -0.6), DECISIONDECEN = c(0.8, -0.6),
+  DECISIONCEN = c(0.8, -0.6), INDUSTRYLARGE = c(0.8, -0.6), INDUSTRYSMALL = c(0.8, -0.6),
+  ECONOMYGLOBAL = c(0.8, -0.6), ECONOMYLOCAL = c(0.8, -0.6), ENVOVERDEV = c(0.8, -0.6),
+  DEVOVERENV = c(0.8, -0.6), OWNERPVT = c(0.8, -0.6), OWNERNOREG = c(0.8, -0.6),
+  OWNERPUB = c(0.8, -0.6), OWNERREG = c(0.8, -0.6), DISPLACENUCLEAR = c(0.8, -0.6),
+  POLLUTENUCLEAR = c(0.8, -0.6), HEALTHNUCLEAR = c(0.8, -0.6), JOBSNUCLEAR = c(0.8, -0.6),
+  BEAUTYNUCLEAR = c(0.8, -0.6), PRIDENUCLEAR = c(0.8, -0.6), NPRIDENUCLEAR = c(0.8, -0.6),
+  DEVNUCLEAR = c(0.8, -0.6), PROSPERNUCLEAR = c(0.8, -0.6), RELYNUCLEAR = c(0.8, -0.6)
+)
+rownames(max_min) <- c("Max", "Min")
+
+# Assuming you have a dataframe 'exam_scores' with matching column names
+# Bind the variable ranges to the data
+
+radar2 <- rbind(max_min, wide_loadings_df) %>%
+    rename(
+      "Limits on Wealth " = "WEALTHLIM",
+      "Anti Mechanisation of work" = "MECHANISATION",
+      "Pro Decentralisation" = "DECISIONDECEN",
+      "Pro Centralisation" = "DECISIONCEN",
+      "Pro Large Industries" = "INDUSTRYLARGE",
+      "Anti Large Industries " = "INDUSTRYSMALL",
+      "Pro Globaleconomy" = "ECONOMYGLOBAL",
+      "Pro Localeconomy" = "ECONOMYLOCAL",
+      "Environment over Development" = "ENVOVERDEV",
+      "Development over Environment" = "DEVOVERENV",
+      "Pro Private ownership " = "OWNERPVT",
+      "Anti Regulations" = "OWNERNOREG",
+      "Pro Public ownership" = "OWNERPUB",
+      "Pro Regulations" = "OWNERREG",
+      "Displacement risk(nuclear)" = "DISPLACENUCLEAR",
+      "Pollution risk(nuclear) " = "POLLUTENUCLEAR",
+      "Health risk(nuclear)" = "HEALTHNUCLEAR",
+      "Job opportunities(nuclear)" = "JOBSNUCLEAR",
+      "Spoils Natural Beauty(nuclear)" = "BEAUTYNUCLEAR",
+      "Community pride(nuclear)" = "PRIDENUCLEAR",
+      "National pride(nuclear)" = "NPRIDENUCLEAR",
+      "National development(nuclear)" = "DEVNUCLEAR",
+      "Local prosperity(nuclear)" = "PROSPERNUCLEAR",
+      "Reliance on government(nuclear)" = "RELYNUCLEAR"
+    )
+
+```
+
+```{r, echo=FALSE, fig.width=20, fig.height=18, out.width='100%', out.height='100%'}
+library(fmsb)
+
+create_beautiful_radarchart <- function(data, color = "#00AFBB", 
+                                        vlabels = colnames(data), vlcex = 0.7,
+                                        caxislabels = NULL, title = NULL, ...){
+  radarchart(
+    data, axistype = 1,
+    # Customize the polygon
+    pcol = color, pfcol = scales::alpha(color, 0.5), plwd = 2, plty = 1,
+    centerzero=FALSE,
+    # Customize the grid
+    cglcol = "black", cglty = 1.5, cglwd = 1.5,
+    # Customize the axis
+    axislabcol = "black", 
+     # Increase the axis label size
+    cexc = 3,
+    # Variable labels
+    vlcex = vlcex, vlabels = vlabels, vlpos = 0.98,
+    seg = 6, caxislabels = caxislabels, title = title, 
+    # Increase title size
+    cex.main = 2,
+    ...
+  )
+}
+
+# Reduce plot margin using par()
+op <- par(mar = c(7, 3, 3, 3))
+# Create the radar charts
+create_beautiful_radarchart(
+  data = radar2, caxislabels = c(-0.6,-0.4,-0.2, 0, 0.2, 0.4, 0.6, 0.8,1),
+  color = c("#00AFBB", "#F97D09"),
+  vlcex = 1.1
+)
+
+# Add an horizontal legend
+legend(
+  x = "bottomright", legend = rownames(radar2[-c(1,2),]), horiz = TRUE,
+  bty = "n", pch = 20 , col = c("#00AFBB", "#F97D09"),
+  text.col = "black", cex = 1.5, pt.cex = 3,
+  inset = c(0, 0)
+  )
+par(op)
+
+```
+
+\newpage
 
@@
 rename_map <- c(
-  "K_SHARM" = "(C)Sometimes the government needs to make laws that keep people from hurting themselves.",
-  "K_SLIMCHOI" = "(C)The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.",
-  "K_SPROTECT" = "(C)The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.",
-  "K_HEQUAL" = "(H)We have gone too far in pushing equal rights in this country.",
-  "K_ERADEQ1" = "(E)We need to dramatically reduce inequalities between the rich and the poor.",
-  "K_EWEALTH" = "(E)Our society would be better off if the distribution of wealth was more equal.",
-  "K_ERADEQ2" = "(E)We need to dramatically reduce inequalities between men and women."
+  "WEALTHLIM" = "Limits on Wealth",
+  "MECHANISATION" = "Anti Mechanisation of work",
+  "DECISIONDECEN" = "Pro Decentralisation",
+  "DECISIONCEN" = "Pro Centralisation",
+  "INDUSTRYLARGE" = "Pro Large Industries",
+  "INDUSTRYSMALL" = "Anti Large Industries",
+  "ECONOMYGLOBAL" = "Pro Globaleconomy",
+  "ECONOMYLOCAL" = "Pro Localeconomy",
+  "ENVOVERDEV" = "Environment over Development",
+  "DEVOVERENV" = "Development over Environment",
+  "OWNERPVT" = "Pro Private ownership",
+  "OWNERNOREG" = "Anti Regulations",
+  "OWNERPUB" = "Pro Public ownership",
+  "OWNERREG" = "Pro Regulations",
+  "DISPLACENUCLEAR" = "Displacement risk(nuclear)",
+  "POLLUTENUCLEAR" = "Pollution risk(nuclear)",
+  "HEALTHNUCLEAR" = "Health risk(nuclear)",
+  "JOBSNUCLEAR" = "Job opportunities(nuclear)",
+  "BEAUTYNUCLEAR" = "Spoils Natural Beauty(nuclear)",
+  "PRIDENUCLEAR" = "Community pride(nuclear)",
+  "NPRIDENUCLEAR" = "National pride(nuclear)",
+  "DEVNUCLEAR" = "National development(nuclear)",
+  "PROSPERNUCLEAR" = "Local prosperity(nuclear)",
+  "RELYNUCLEAR" = "Reliance on government(nuclear)"
 )
@@
 
-fa_table(kahan.fa) %>%
-  #rename(Pdevelop = MR1, Ndevelop = MR2, Items= item) %>%
-  flex("Kahan Exploratory Factor Analysis Table")
-
-```
-
-## alternative Kahan scores
-```{r, echo=FALSE}
-
-Kscalescores <- fascales %>%
-  dplyr::select(!starts_with(("K_I")))%>%
-  rowwise()%>%
-  dplyr::mutate(Communitarianism_score = mean(c_across(K_SHARM:K_SPROTECT)))%>%
-  dplyr::mutate(Egalitarianism_score = mean(c_across(K_HEQUAL:K_ERADEQ2)))%>%
-  dplyr::select(!starts_with(c("K_I","K_S", "K_H", "K_E")))
-
-```
-
-```{r fit-measures-display, echo = FALSE}
-# Extract fit measures
-fit_measures <- fitMeasures(Kahan_cfa, fit.measures = c("CFI", "TLI", "RMSEA", "rmsea.ci.upper", "rmsea.ci.lower"))
-fit_measures2 <- fitMeasures(Kahan_cfa)
-# Convert to a data frame for presentation
-fit_df <- data.frame(Measure = names(fit_measures), Value = fit_measures) %>%
-  mutate(Measure = case_when(
-    Measure == "cfi" ~ "Comparative Fit Index (CFI) ",
-    Measure == "tli" ~ "Tucker-Lewis Index (TLI)",
-    Measure == "rmsea" ~ "Root Mean Square Error of Approximation(RMSEA)",
-    Measure == "rmsea.ci.upper" ~ "RMSEA 90 Percent confidence interval - lower",
-    Measure == "rmsea.ci.lower" ~ "RMSEA 90 Percent confidence interval - upper",
-    TRUE ~ as.character(Measure)
-  )) %>%
-  mutate(Value = round(Value, 3)) %>%
-  remove_rownames()
-
-#RMSEA - between 0.05 and 0.08 (reasonable fit), less than 0.05 close fit and greater than 0.10 is poor fit 
-#CFI - greater than 0.90 or 0.95 indicates good fit
-#TFI - CFI>TFI >0.90 - indicates good fit
-
-```
-# Confirmatory Factor Analysis(CFA): Kahan Scale
-
-**Cronbach's Alpha on Kahan et al(2007) Scale: A Note**
-
-The Individualism items (indicated by K_I) were bringing down the Cronbach's alpha values in the Kahan scale.
-The Alpha for Individualism- Communitarian scale was 0.49.
-After removing the Individualism items (K_I) the alpha for this factor was 0.71.
-The reasons for this could be that the individualism items are not well adapted to the Indian population.
-
-```{r, echo =FALSE}
-# Display fit measures using kable
-knitr::kable(fit_df, caption = "Fit Measures from the CFA", booktabs = TRUE) %>%
-  kable_styling(latex_options = c("striped", "hold_position"))
-
-```
-
-\newpage
-
-```{r, echo=FALSE}
-
-# Extract parameter estimates
-params <- parameterEstimates(Kahan_cfa, standardized = TRUE)%>%
-   slice(1:(n()-10))
-
-params1 <- params %>%
-  mutate(rhs = case_when(
-    rhs == "K_SHARM" ~ "Sometimes the government needs to make laws that keep people from hurting themselves.",
-    rhs == "K_SLIMCHOI" ~ "The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.",
-    rhs == "K_SPROTECT" ~ "The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.",
-    rhs == "K_HEQUAL" ~ "We have gone too far in pushing equal rights in this country.",
-    rhs == "K_ERADEQ1" ~ "We need to dramatically reduce inequalities between the rich and the poor.",
-    rhs == "K_EWEALTH" ~ "Our society would be better off if the distribution of wealth was more equal.",
-    rhs == "K_ERADEQ2" ~ "We need to dramatically reduce inequalities between men and women.",
-    TRUE ~ as.character(rhs)
-  )) %>%
-  dplyr::select(!c(lhs,op, std.nox)) %>%
-    rename(
-    "Items" = rhs,
-    "Loadings" = est,
-    "Standard Error" = se,
-    "zvalue" = z) %>%
-  mutate(across(c("Loadings", "Standard Error", "zvalue"), round, 3))
-
-params1$Scale <- NA
-params1$Scale[1:3] <- "Communitarian"
-params1$Scale[4:7] <- "Hierarchy-Egalitarianism"
-params1 <- params1[, c("Scale", setdiff(names(params1), "Scale"))]
-CFAkahan <- knitr::kable(params1, booktabs = TRUE, caption = "Confirmatory Factor Analysis(CFA) on Kahan et al(2007) scale adapted to India") %>%
-  kable_styling(latex_options = c("striped","scale_down", "hold_position", "repeat_header"))%>%
-  column_spec(column = 2, width = "4cm")
-
-# Print the table
-CFAkahan %>%
-  landscape()
-
-```
-
-## Kahan scater plot from the CFA scores 
-```{r, echo = FALSE}
-
-Kahan_Kscores %>%
-  ggplot(aes(KahanS, KahanH))+
-  geom_count(aes(color = ..n.., size = ..n..))+
-  guides(color = 'legend')+
-  geom_hline(yintercept=0, colour="black", lwd=0.5)+
-  geom_vline(xintercept=0, colour="black", lwd=0.5)+
-  labs(x = "Individualism to Communitarianism", y = "Hierarchy to Egalitarianism")+
-  ylim(-2,3)+
-  xlim(-2,3)+
-  theme_minimal() 
-```
-
-\newpage
-
-# Factor Analysis: New Eco-political Scale
-
-```{r, echo=FALSE}
-
-library(psych)
-library(tidyverse)
-
-ecopolall <- fascales %>%
-        dplyr::select("WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR")
-
-ecopolall_alpha <- psych::alpha(ecopolall, check.keys = TRUE)
-
-#summary(ecopolall_alpha)
-
-# when we combine both the scales the alpha is high at 0.785 (almost 0.8)
-
-# FA on all ecopol variables except systems of governance
-
-ecopolall_cor <- cor(ecopolall)
-PCA24 <- principal(ecopolall, nfactors = 24, rotate = "none") # no rotation to start with.
-
-#PCA24$loadings
-
-#fa.parallel(ecopolall_cor)
-# this suggests 2 factors if we go by FA or 8 by PCA. let's try both and see how they look conceptually 
-# running EFA using psych package
-
-ecopolall2.fa <- fa(ecopolall, nfactors = 2, rotate = "varimax")
-
-print.psych(ecopolall2.fa, sort = TRUE)
-
-# I don't know still doesn't make a lot of sense to me- the two factors make more sense - 1) people centered development 2) nationalist development
-# So I am going to extract factor scores and bind them to the dataset
-
-ecopolall_scores <- psych::factor.scores(ecopolall, ecopolall2.fa)
-
-# The factor scores will be stored in the scores element of the returned list
-scores1 <- ecopolall_scores$scores
-
-#binding factor scores to the dataset
-
-fascale_scores <- cbind(Kahan_Kscores, scores1) %>%
-  rename(Pdevelop = MR1)%>%
-  rename(Ndevelop = MR2) #%>%
-  #dplyr::select(!starts_with(c("K_","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR")))
-
-```
-
-```{r, echo=FALSE}
-library(ggplot2)
-library(fmsb)
-
-# Extract the loadings
-loadings_matrix <- ecopolall2.fa$loadings[1:24, ]
-
-loadings_df <- as.data.frame(as.matrix(loadings_matrix))
-
-# Adding rownames to the dataframe as a new column
-loadings_df <- loadings_df %>%
-  rownames_to_column(var = "variable")
-
-# Pivot to longer format first
-long_loadings_df <- loadings_df %>%
-  pivot_longer(cols = c(MR1, MR2), names_to = "Factors", values_to = "value")
-
-# Pivot the longer format to wide format
-wide_loadings_df <- long_loadings_df %>%
-  pivot_wider(names_from = variable, values_from = value) %>%
-  mutate(Factors = case_when(
-    Factors == "MR1" ~ "People Centered Development (Pdevelop)",
-    Factors == "MR2" ~ "Nationalist Development (Ndevelop)",
-    TRUE ~ Factors
-  )) %>%
-  column_to_rownames("Factors")
-
-# Define the variable ranges: maximum and minimum
-max_min <- data.frame(
-  WEALTHLIM = c(0.8, -0.6), MECHANISATION = c(0.8, -0.6), DECISIONDECEN = c(0.8, -0.6),
-  DECISIONCEN = c(0.8, -0.6), INDUSTRYLARGE = c(0.8, -0.6), INDUSTRYSMALL = c(0.8, -0.6),
-  ECONOMYGLOBAL = c(0.8, -0.6), ECONOMYLOCAL = c(0.8, -0.6), ENVOVERDEV = c(0.8, -0.6),
-  DEVOVERENV = c(0.8, -0.6), OWNERPVT = c(0.8, -0.6), OWNERNOREG = c(0.8, -0.6),
-  OWNERPUB = c(0.8, -0.6), OWNERREG = c(0.8, -0.6), DISPLACENUCLEAR = c(0.8, -0.6),
-  POLLUTENUCLEAR = c(0.8, -0.6), HEALTHNUCLEAR = c(0.8, -0.6), JOBSNUCLEAR = c(0.8, -0.6),
-  BEAUTYNUCLEAR = c(0.8, -0.6), PRIDENUCLEAR = c(0.8, -0.6), NPRIDENUCLEAR = c(0.8, -0.6),
-  DEVNUCLEAR = c(0.8, -0.6), PROSPERNUCLEAR = c(0.8, -0.6), RELYNUCLEAR = c(0.8, -0.6)
-)
-rownames(max_min) <- c("Max", "Min")
-
-# Assuming you have a dataframe 'exam_scores' with matching column names
-# Bind the variable ranges to the data
-
-radar2 <- rbind(max_min, wide_loadings_df) %>%
-    rename(
-      "Limits on Wealth " = "WEALTHLIM",
-      "Anti Mechanisation of work" = "MECHANISATION",
-      "Pro Decentralisation" = "DECISIONDECEN",
-      "Pro Centralisation" = "DECISIONCEN",
-      "Pro Large Industries" = "INDUSTRYLARGE",
-      "Anti Large Industries " = "INDUSTRYSMALL",
-      "Pro Globaleconomy" = "ECONOMYGLOBAL",
-      "Pro Localeconomy" = "ECONOMYLOCAL",
-      "Environment over Development" = "ENVOVERDEV",
-      "Development over Environment" = "DEVOVERENV",
-      "Pro Private ownership " = "OWNERPVT",
-      "Anti Regulations" = "OWNERNOREG",
-      "Pro Public ownership" = "OWNERPUB",
-      "Pro Regulations" = "OWNERREG",
-      "Displacement risk(nuclear)" = "DISPLACENUCLEAR",
-      "Pollution risk(nuclear) " = "POLLUTENUCLEAR",
-      "Health risk(nuclear)" = "HEALTHNUCLEAR",
-      "Job opportunities(nuclear)" = "JOBSNUCLEAR",
-      "Spoils Natural Beauty(nuclear)" = "BEAUTYNUCLEAR",
-      "Community pride(nuclear)" = "PRIDENUCLEAR",
-      "National pride(nuclear)" = "NPRIDENUCLEAR",
-      "National development(nuclear)" = "DEVNUCLEAR",
-      "Local prosperity(nuclear)" = "PROSPERNUCLEAR",
-      "Reliance on government(nuclear)" = "RELYNUCLEAR"
-    )
-
-```
-
-```{r, echo=FALSE, fig.width=20, fig.height=18, out.width='100%', out.height='100%'}
-library(fmsb)
-
-create_beautiful_radarchart <- function(data, color = "#00AFBB", 
-                                        vlabels = colnames(data), vlcex = 0.7,
-                                        caxislabels = NULL, title = NULL, ...){
-  radarchart(
-    data, axistype = 1,
-    # Customize the polygon
-    pcol = color, pfcol = scales::alpha(color, 0.5), plwd = 2, plty = 1,
-    centerzero=FALSE,
-    # Customize the grid
-    cglcol = "black", cglty = 1.5, cglwd = 1.5,
-    # Customize the axis
-    axislabcol = "black", 
-     # Increase the axis label size
-    cexc = 3,
-    # Variable labels
-    vlcex = vlcex, vlabels = vlabels, vlpos = 0.98,
-    seg = 6, caxislabels = caxislabels, title = title, 
-    # Increase title size
-    cex.main = 2,
-    ...
-  )
-}
-
-# Reduce plot margin using par()
-op <- par(mar = c(7, 3, 3, 3))
-# Create the radar charts
-create_beautiful_radarchart(
-  data = radar2, caxislabels = c(-0.6,-0.4,-0.2, 0, 0.2, 0.4, 0.6, 0.8,1),
-  color = c("#00AFBB", "#F97D09"),
-  vlcex = 1.1
-)
-
-# Add an horizontal legend
-legend(
-  x = "bottomright", legend = rownames(radar2[-c(1,2),]), horiz = TRUE,
-  bty = "n", pch = 20 , col = c("#00AFBB", "#F97D09"),
-  text.col = "black", cex = 1.5, pt.cex = 3,
-  inset = c(0, 0)
-  )
-par(op)
-
-```
-
-\newpage
-
-```{r, echo=FALSE}
-
-library(flextable)
-
-flex <- function(data, title=NULL) {
-  # this grabs the data and converts it to a flextbale
-  flextable(data) %>%
-  # this makes the table fill the page width
-  set_table_properties(layout = "autofit", width = 1) %>%
-  # font size
-  fontsize(size=10, part="all") %>%
-    #this adds a ttitlecreates an automatic table number
-      set_caption(title, 
-                  autonum = officer::run_autonum(seq_id = "tab", 
-                                                 pre_label = "Table ", 
-                                                 post_label = "\n", 
-                                                 bkm = "anytable")) #%>%
-  # font type
-  #font(fontname="Times New Roman", part="all")
-}
-
-rename_map <- c(
-  "WEALTHLIM" = "Limits on Wealth",
-  "MECHANISATION" = "Anti Mechanisation of work",
-  "DECISIONDECEN" = "Pro Decentralisation",
-  "DECISIONCEN" = "Pro Centralisation",
-  "INDUSTRYLARGE" = "Pro Large Industries",
-  "INDUSTRYSMALL" = "Anti Large Industries",
-  "ECONOMYGLOBAL" = "Pro Globaleconomy",
-  "ECONOMYLOCAL" = "Pro Localeconomy",
-  "ENVOVERDEV" = "Environment over Development",
-  "DEVOVERENV" = "Development over Environment",
-  "OWNERPVT" = "Pro Private ownership",
-  "OWNERNOREG" = "Anti Regulations",
-  "OWNERPUB" = "Pro Public ownership",
-  "OWNERREG" = "Pro Regulations",
-  "DISPLACENUCLEAR" = "Displacement risk(nuclear)",
-  "POLLUTENUCLEAR" = "Pollution risk(nuclear)",
-  "HEALTHNUCLEAR" = "Health risk(nuclear)",
-  "JOBSNUCLEAR" = "Job opportunities(nuclear)",
-  "BEAUTYNUCLEAR" = "Spoils Natural Beauty(nuclear)",
-  "PRIDENUCLEAR" = "Community pride(nuclear)",
-  "NPRIDENUCLEAR" = "National pride(nuclear)",
-  "DEVNUCLEAR" = "National development(nuclear)",
-  "PROSPERNUCLEAR" = "Local prosperity(nuclear)",
-  "RELYNUCLEAR" = "Reliance on government(nuclear)"
-)
-
-fa_table <- function(x) {
-  #get sorted loadings
-  loadings <- fa.sort(x)$loadings %>% round(3)
-  #supress loadings
-  #loadings[loadings < cut] <- ""  # alternative loadings > -cut & loadings < cut
-  #get additional info  
-  add_info <- cbind(x$communalities, 
-                    x$uniquenesses,
-                    x$complexity) %>%
-    # make it a data frame
-    as.data.frame() %>%
-    # column names
-   rename("Communality" = V1,
-           "Uniqueness" = V2,
-           "Complexity" = V3) %>%
-    #get the item names from the vector
-    rownames_to_column("item")
-  #build table
-  loadings %>%
-    unclass() %>%
-    as.data.frame() %>%
-    rownames_to_column("item") %>%
-    left_join(add_info) %>%
-    mutate(
-      item = if_else(item %in% names(rename_map), rename_map[item], item),
-      across(where(is.numeric), round, 3)
-    )
-}
-
 fa_table(ecopolall2.fa) %>%
@@
 
+summary(m1_kahan)
 # 4) lm with ecopolvars 
 m1_allscales <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State+ Pdevelop + Ndevelop + KahanS + KahanH , data = fascale_scores)
+
+summary(m1_allscales)
 

### 2024-01-31 Paper1.Rmd
counting NAs

@@
 codedmodule2$Hindu <- ifelse(codedmodule2$religion == 'Hinduism', 1, 0)
+joineddf$State <- as.factor(joineddf$State)
 
@@
 #plot(alldemoslm1)
+
+state_counts <- alldemos %>%
+  group_by(State) %>%
+  summarise(Count = n())
 
@@
 
+\newpage
+# Na counting
+
+```{r, echo = FALSE}
+
+relevant <- codedmodule2 %>%
+  dplyr::select(starts_with(c("Risky", "Ben","K_", "WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%
+  dplyr::select(!starts_with(c("Risky_IND","Ben_IND")))%>%
+  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
+                                      . == "25-34 years old" ~ 2,
+                                      . ==  "35-44 years old" ~3,
+                                      . == "45-54 years old" ~ 4,
+                                      . == "55-64 years old" ~ 5,
+                                      . == "65-74 years old" ~ 6,
+                                      . == "75 years or older" ~ 7)))
+
+relevant_na <- relevant %>% summarise_all(~sum(is.na(.)))
+
+str(relevant)
+str(relevant_na)
+```
+
+\newpage
 ## Kahan scater plot from the CFA scores 
@@
 
-```{r dev = "jpg", echo=FALSE}
+```{r, echo=FALSE}
 
@@
 
+state_counts2 <- fascale_scores %>%
+  group_by(State) %>%
+  summarise(Count = n())
+
 ```
@@
   rename(Ndevelop = MR2)
-
-fascale_scores2
 

### 2024-01-31 Paper1.Rmd
made cor stuff pdf document neater

@@
 # 3 linear models - 1) lm with demographic variables except age and State
+
 m1_demo <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban, data = fascale_scores)
+
 # Print model summary

### 2024-01-31 corstuff.Rmd
made cor stuff pdf document neater

@@
   - "\\usepackage{placeins}"
+  - \usepackage{pdflscape}
+  - \newcommand{\blandscape}{\begin{landscape}}
+  - \newcommand{\elandscape}{\end{landscape}}
   keep_md: yes
@@
 
-# EDIT :  Kahan scale EFA  
+\newpage
+
+\blandscape
+# Kahan scale EFA  
 ```{r, echo=FALSE}
@@
 
-print.psych(kahan.fa, cut = 0.4, sort = TRUE)
+#print.psych(kahan.fa, cut = 0.4, sort = TRUE)
 
@@
 
+\elandscape
+
+\newpage
+
 ```{r, echo=FALSE}
@@
 ```
+
+\newpage
+
 # Confirmatory Factor Analysis(CFA): Kahan Scale
@@
 
-```{r}
+```{r, echo=FALSE}
 # binding ecopol with alternative Kahan scale score 
@@
 
-fascale_scores2
-
 fascale_scores2cor <- fascale_scores2 %>%
@@
 
+\newpage
 # Lms with alt Kahan scores 
@@
 stargazer(m1_kahan2, m1_ecopol2, m1_allscales2, 
-          title = "Results from 3 linear regression models",
+          title = "Alternative Kahan Scores(mean acorss fixed factors)",
           type = "latex"
@@
 cat("\\renewcommand{\\arraystretch}{0.7}")
-stargazer(m1_kahan, m1_allscales, 
-          title = "Results from 2 linear regression models",
+stargazer(m1_kahan,m1_ecopol, m1_allscales, 
+          title = "Lms with CFA Kahan",
           type = "latex"
@@
 
-\newpage
-```{r, echo=FALSE, results='asis'}
-library(stargazer)
-
-cat("\\begingroup")
-cat("\\setlength{\\tabcolsep}{1pt}")
-cat("\\renewcommand{\\arraystretch}{0.7}")
-stargazer(m1_ecopol, m1_allscales, 
-          title = "Results from 2 linear regression models",
-          type = "latex"
-)
-cat("\\endgroup")
-
-```
 \newpage
@@
 
-fascale_scores
-
-fascale_scores2
+#fascale_scores
+
+#fascale_scores2
 

### 2024-02-01 corstuff.Rmd
new lms with Kahan EFA scale

@@
 
-\newpage
-
-## Mean Perceived Risk and Mean Perceived Benefit for all energy technologies.
-
 ```{r, echo=FALSE}
@@
 ```
-
-\newpage
 
@@
 
+\newpage
+
 ## Demographic IVs - two linear regression models
@@
 ##  Kahan scale Alpha values 
-Hierarchy - Egalitarianism scale alpha  =  0.7
+Hierarchy - Egalitarianism scale alpha  =  0.70
 Individualism - Communitarianism scale alpha= 0.52
@@
 
-\newpage
-
-\blandscape
-# Kahan scale EFA  
-```{r, echo=FALSE}
-
-Kahan_scale <- codedmodule2 %>%
-  dplyr::select(starts_with("K_"))
-
-kahan.fa <- fa(Kahan_scale, nfactors = 2, rotate = "varimax")
-
-#print.psych(kahan.fa, cut = 0.4, sort = TRUE)
-
-```
-
-```{r, echo=FALSE}
-
-library(flextable)
-
-flex <- function(data, title=NULL) {
-  # this grabs the data and converts it to a flextbale
-  flextable(data) %>%
-  # this makes the table fill the page width
-  set_table_properties(layout = "autofit", width = 1) %>%
-  # font size
-  fontsize(size=11, part="all") %>%
-    #this adds a ttitlecreates an automatic table number
-      set_caption(title, 
-                  autonum = officer::run_autonum(seq_id = "tab", 
-                                                 pre_label = "Table ", 
-                                                 post_label = "\n", 
-                                                 bkm = "anytable")) #%>%
-  # font type
-  #font(fontname="Times New Roman", part="all")
-}
-
-rename_map <- c(
-  "K_SHARM" = "(C)Sometimes the government needs to make laws that keep people from hurting themselves.",
-  "K_SLIMCHOI" = "(C)The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.",
-  "K_SPROTECT" = "(C)The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.",
-  "K_HEQUAL" = "(H)We have gone too far in pushing equal rights in this country.",
-  "K_ERADEQ1" = "(E)We need to dramatically reduce inequalities between the rich and the poor.",
-  "K_EWEALTH" = "(E)Our society would be better off if the distribution of wealth was more equal.",
-  "K_ERADEQ2" = "(E)We need to dramatically reduce inequalities between men and women.",
-
-  "K_IINTRFER" = "(I)The government interferes far too much in our everyday lives.",
-  "K_HREVDIS1" = "(H)Nowadays it seems like there is just as much discrimination against upper castes as there is against Dalits.",
-  "K_EDISCRIM" = "(E)Discrimination against minorities is still a very serious problem in our society.",
-  "K_IPRIVACY" = "(I)The government should stop telling people how to live their lives.",
-  "K_IPROTECT" = "(I)It’s not the government’s business to try to protect people from themselves."
-)
-
-fa_table <- function(x) {
-  #get sorted loadings
-  loadings <- fa.sort(x)$loadings %>% round(3)
-  #get additional info  
-  add_info <- cbind(x$communalities, 
-                    x$uniquenesses,
-                    x$complexity) %>%
-    # make it a data frame
-    as.data.frame() %>%
-    # column names
-   rename("Communality" = V1,
-           "Uniqueness" = V2,
-           "Complexity" = V3) %>%
-    #get the item names from the vector
-    rownames_to_column("item")
-  #build table
-  loadings %>%
-    unclass() %>%
-    as.data.frame() %>%
-    rownames_to_column("item") %>%
-    left_join(add_info) %>%
-    mutate(
-      item = if_else(item %in% names(rename_map), rename_map[item], item),
-      across(where(is.numeric), round, 3)
-    )
-}
-
-fa_table(kahan.fa) %>%
-  #rename(Pdevelop = MR1, Ndevelop = MR2, Items= item) %>%
-  flex("Kahan Exploratory Factor Analysis Table")
-
-```
-
-\elandscape
-
-\newpage
-
-```{r, echo=FALSE}
-
-kahan.fa[["Vaccounted"]] %>%
-  as.data.frame() %>%
-  rownames_to_column("Property") %>%
-    mutate(across(where(is.numeric), round, 3)) %>%
-    flex("Eigenvalues and Variance Explained for Rotated Factor Solution")
-
-```
-
-## alternative Kahan scores
+## Alternative Kahan Scores with Mean across
 ```{r, echo=FALSE}
@@
 
+\blandscape
+
+# Kahan scale EFA  
+```{r, echo=FALSE}
+
+Kahan_scale1 <- codedmodule2 %>%
+  dplyr::select(starts_with(c("Risky_Nuclear","K_", "Uppercaste", "Male", "Hindu", "Urban", "State","age"))) %>%
+  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
+                                      . == "25-34 years old" ~ 2,
+                                      . ==  "35-44 years old" ~3,
+                                      . == "45-54 years old" ~ 4,
+                                      . == "55-64 years old" ~ 5,
+                                      . == "65-74 years old" ~ 6,
+                                      . == "75 years or older" ~ 7))) %>%
+  na.omit()
+
+Kahan_scale<- Kahan_scale1 %>%
+  dplyr::select(starts_with("K_"))
+
+kahan.fa <- fa(Kahan_scale, nfactors = 2, rotate = "varimax")
+
+print.psych(kahan.fa, cut = 0.4, sort = TRUE)
+
+# I don't know still doesn't make a lot of sense to me- the two factors make more sense - 1) people centered development 2) nationalist development
+# So I am going to extract factor scores and bind them to the dataset
+
+Kahanefa <- psych::factor.scores(Kahan_scale, kahan.fa)
+
+# The factor scores will be stored in the scores element of the returned list
+kahanefascores <- Kahanefa$scores
+
+fascale_scores4 <- cbind(Kahan_scale1, kahanefascores) %>%
+  rename(CE = MR1)%>%
+  rename(HE = MR2) #%>%
+
+```
+
+```{r, echo=FALSE}
+
+library(flextable)
+
+flex <- function(data, title=NULL) {
+  # this grabs the data and converts it to a flextbale
+  flextable(data) %>%
+  # this makes the table fill the page width
+  set_table_properties(layout = "autofit", width = 1) %>%
+  # font size
+  fontsize(size=11, part="all") %>%
+    #this adds a ttitlecreates an automatic table number
+      set_caption(title, 
+                  autonum = officer::run_autonum(seq_id = "tab", 
+                                                 pre_label = "Table ", 
+                                                 post_label = "\n", 
+                                                 bkm = "anytable")) #%>%
+  # font type
+  #font(fontname="Times New Roman", part="all")
+}
+
+rename_map <- c(
+  "K_SHARM" = "(C)Sometimes the government needs to make laws that keep people from hurting themselves.",
+  "K_SLIMCHOI" = "(C)The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.",
+  "K_SPROTECT" = "(C)The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.",
+  "K_HEQUAL" = "(H)We have gone too far in pushing equal rights in this country.",
+  "K_ERADEQ1" = "(E)We need to dramatically reduce inequalities between the rich and the poor.",
+  "K_EWEALTH" = "(E)Our society would be better off if the distribution of wealth was more equal.",
+  "K_ERADEQ2" = "(E)We need to dramatically reduce inequalities between men and women.",
+
+  "K_IINTRFER" = "(I)The government interferes far too much in our everyday lives.",
+  "K_HREVDIS1" = "(H)Nowadays it seems like there is just as much discrimination against upper castes as there is against Dalits.",
+  "K_EDISCRIM" = "(E)Discrimination against minorities is still a very serious problem in our society.",
+  "K_IPRIVACY" = "(I)The government should stop telling people how to live their lives.",
+  "K_IPROTECT" = "(I)It’s not the government’s business to try to protect people from themselves."
+)
+
+fa_table <- function(x) {
+  #get sorted loadings
+  loadings <- fa.sort(x)$loadings %>% round(3)
+  #get additional info  
+  add_info <- cbind(x$communalities, 
+                    x$uniquenesses,
+                    x$complexity) %>%
+    # make it a data frame
+    as.data.frame() %>%
+    # column names
+   rename("Communality" = V1,
+           "Uniqueness" = V2,
+           "Complexity" = V3) %>%
+    #get the item names from the vector
+    rownames_to_column("item")
+  #build table
+  loadings %>%
+    unclass() %>%
+    as.data.frame() %>%
+    rownames_to_column("item") %>%
+    left_join(add_info) %>%
+    mutate(
+      item = if_else(item %in% names(rename_map), rename_map[item], item),
+      across(where(is.numeric), round, 3)
+    )
+}
+
+fa_table(kahan.fa) %>%
+  #rename(Pdevelop = MR1, Ndevelop = MR2, Items= item) %>%
+  flex("Kahan Exploratory Factor Analysis Table")
+
+```
+
+\elandscape
+
+\newpage
+
+```{r, echo=FALSE}
+
+kahan.fa[["Vaccounted"]] %>%
+  as.data.frame() %>%
+  rownames_to_column("Property") %>%
+    mutate(across(where(is.numeric), round, 3)) %>%
+    flex("Eigenvalues and Variance Explained for Rotated Factor Solution")
+
+```
+
+# LMs with EFA Kahan factors
+
+```{r, echo=FALSE}
+
+demoEFA <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban, data = fascale_scores4)
+
+summary(demoEFA)
+
+# 2) lm with all demographic variables
+demoEFA2<- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State, data = fascale_scores4)
+summary(demoEFA2)
+
+# 3) lm with kahan 
+demoEFA3 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State + CE + HE , data = fascale_scores4)
+
+summary(demoEFA3)
+
+```
+
+#2.  Kahan scale EFA  
+```{r, echo=FALSE}
+
+Kahan_scale2<- fascales %>%
+  dplyr::select(starts_with("K_"))
+
+kahan2.fa <- fa(Kahan_scale2, nfactors = 2, rotate = "varimax")
+
+print.psych(kahan2.fa, cut = 0.4, sort = TRUE)
+
+# I don't know still doesn't make a lot of sense to me- the two factors make more sense - 1) people centered development 2) nationalist development
+# So I am going to extract factor scores and bind them to the dataset
+
+Kahanefa2 <- psych::factor.scores(Kahan_scale2, kahan2.fa)
+
+# The factor scores will be stored in the scores element of the returned list
+kahanefascores2 <- Kahanefa2$scores
+
+fascale_scores5 <- cbind(fascales, kahanefascores2) %>%
+  rename(CE = MR1)%>%
+  rename(HE = MR2) #%>%
+
+```
+
+# 2. LMs with EFA Kahan factors
+
+```{r, echo=FALSE}
+
+KEFA <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban, data = fascale_scores5)
+
+summary(KEFA)
+
+# 2) lm with all demographic variables
+KEFA2<- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State, data = fascale_scores5)
+summary(KEFA2)
+
+# 3) lm with kahan 
+KEFA3 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State + CE + HE , data = fascale_scores5)
+
+summary(KEFA3)
+
+```
+
+\newpage
+
 # LMs by State

### 2024-02-01 corstuff.Rmd
made correlation stuff pretty for the meeting

@@
 
-## Demographic IVs - two linear regression models
+# Demographic IVs - two linear regression models
 ```{r, echo=FALSE, results='asis'}
@@
 
-## Linear regression where Mean value is the intercept
+# Linear regression where Mean value is the intercept
 Same model with mean value as intercept.
@@
 
-##  Kahan scale Alpha values 
+#  Kahan scale Alpha values 
 Hierarchy - Egalitarianism scale alpha  =  0.70
@@
 
+```{r, echo=FALSE}
 ## Alternative Kahan Scores with Mean across
-```{r, echo=FALSE}
-
 Kscalescores <- fascales %>%
@@
   rowwise()%>%
-  dplyr::mutate(Communitarianism_score = mean(c_across(K_SHARM:K_SPROTECT)))%>%
-  dplyr::mutate(Egalitarianism_score = mean(c_across(K_HEQUAL:K_ERADEQ2)))%>%
+  dplyr::mutate(Individualism_score = mean(c_across(K_SHARM:K_SPROTECT)))%>%
+  dplyr::mutate(Hierarchy_score = mean(c_across(K_HEQUAL:K_ERADEQ2)))%>%
   dplyr::select(!starts_with(c("K_I","K_S", "K_H", "K_E")))
@@
 
-## Kahan scater plot from the CFA scores 
-```{r, echo = FALSE}
-
-Kahan_Kscores %>%
-  ggplot(aes(KahanS, KahanH))+
-  geom_count(aes(color = ..n.., size = ..n..))+
-  guides(color = 'legend')+
-  geom_hline(yintercept=0, colour="black", lwd=0.5)+
-  geom_vline(xintercept=0, colour="black", lwd=0.5)+
-  labs(x = "Individualism to Communitarianism", y = "Hierarchy to Egalitarianism")+
-  ylim(-2,3)+
-  xlim(-2,3)+
-  theme_minimal() 
-```
-
 \newpage
@@
 
-print.psych(ecopolall2.fa, sort = TRUE)
+#print.psych(ecopolall2.fa, sort = TRUE)
 
@@
 
+```{r, echo=FALSE}
+
 # all lms after FA
-```{r, echo=FALSE}
+
 # 3 linear models - 1) lm with demographic variables except age and State
@@
 
-summary(m1_kahan)
+#summary(m1_kahan)
 # 4) lm with ecopolvars 
@@
 
-summary(m1_allscales)
+#summary(m1_allscales)
 
@@
 
-summary(m1_ecopol)
+#summary(m1_ecopol)
 
@@
 
-summary(m1_allscales2)
-
-```
-
-# Correlation Eco-pol and alt Kahan(mean across)
+#summary(m1_allscales2)
+
+```
+
+\newpage
+#Correlation table Eco-pol scale and Kahan CFA scores
+
+```{r, echo=FALSE}
+
+fascale_scorescor <- fascale_scores %>%
+  dplyr::select(KahanS, KahanH, Pdevelop, Ndevelop)
+
+cor_kecopol1 <- cor(fascale_scorescor)
+
+print(cor_kecopol1)
+
+```
+
+# Correlation Eco-pol and alt Kahan (mean across)
 
@@
 fascale_scores2cor <- fascale_scores2 %>%
-  dplyr::select(Communitarianism_score, Egalitarianism_score, Pdevelop, Ndevelop)
+  dplyr::select(Individualism_score, Hierarchy_score, Pdevelop, Ndevelop)
 
@@
 print(cor_kecopol)
+```
+
+\newpage
+# Scatter plot 1: mean across Kahan scale scores around medians
+
+```{r, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+
+#scatter plot of Kahan scale scores around the median scores on Individualism and Hierarchy scales.
+
+Kscalescores %>%
+  ggplot(aes(Individualism_score, Hierarchy_score))+
+  geom_count(aes(color = ..n.., size = ..n..))+
+  guides(color = 'legend')+
+  geom_hline(yintercept=2, colour="black", lwd=1)+
+  geom_vline(xintercept=3, colour="black", lwd=1)+
+  labs(x = " Communitarianism to Individualism", y = "Egalitarianism to Hierarchy")+
+  ylim(1,5)+
+  xlim(1,5)+
+  theme_minimal()
+
+```
+
+# Scater plot 2:  Kahan CFA scores 
+```{r, echo = FALSE}
+
+Kahan_Kscores %>%
+  ggplot(aes(KahanS, KahanH))+
+  geom_count(aes(color = ..n.., size = ..n..))+
+  guides(color = 'legend')+
+  geom_hline(yintercept=0, colour="black", lwd=0.5)+
+  geom_vline(xintercept=0, colour="black", lwd=0.5)+
+  labs(x = "Individualism to Communitarianism", y = "Hierarchy to Egalitarianism")+
+  ylim(-2,3)+
+  xlim(-2,3)+
+  theme_minimal() 
 ```
@@
 # 3) lm with kahan 
-m1_kahan2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State + Communitarianism_score + Egalitarianism_score , data = fascale_scores2)
+m1_kahan2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State + Individualism_score + Hierarchy_score , data = fascale_scores2)
 # Print model summary
-summary(m1_kahan2)
+#summary(m1_kahan2)
 #plot(m1_kahan)
@@
 # 4) lm with ecopolvars 
-m1_allscales2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State+ Pdevelop + Ndevelop + Communitarianism_score + Egalitarianism_score , data = fascale_scores2)
+m1_allscales2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State+ Pdevelop + Ndevelop + Individualism_score + Hierarchy_score , data = fascale_scores2)
 # Print model summary
-summary(m1_allscales2)
+#summary(m1_allscales2)
 #plot(m1_allscales)
@@
 
-summary(m1_ecopol2)
-
-```
-
-\newpage
+#summary(m1_ecopol2)
+
+```
+
 ```{r, echo=FALSE, results='asis'}
@@
 
+\newpage
 # LMs with EFA Kahan factors
@@
 
-summary(demoEFA)
+#summary(demoEFA)
 
@@
 demoEFA2<- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State, data = fascale_scores4)
-summary(demoEFA2)
+#summary(demoEFA2)
 
@@
 
-summary(demoEFA3)
-
-```
-
-#2.  Kahan scale EFA  
+#summary(demoEFA3)
+
+```
+
+```{r, echo=FALSE, results='asis'}
+library(stargazer)
+
+cat("\\begingroup")
+cat("\\setlength{\\tabcolsep}{1pt}")
+cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer(demoEFA,demoEFA2, demoEFA3, 
+          title = "Lms with CFA Kahan",
+          type = "latex"
+)
+cat("\\endgroup")
+
+```
+
+\newpage
+
+# 2. EXTRA:: Kahan scale EFA  
 ```{r, echo=FALSE}
@@
 
-summary(KEFA)
+#summary(KEFA)
 
@@
 KEFA2<- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State, data = fascale_scores5)
-summary(KEFA2)
+#summary(KEFA2)
 
@@
 
-summary(KEFA3)
+#summary(KEFA3)
 
@@
 # 3) lm with kahan 
-TM2_kahan <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age  + Communitarianism_score + Egalitarianism_score, data = TM2)
+TM2_kahan <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age  + Individualism_score + Hierarchy_score, data = TM2)
 
@@
 # 4) lm with ecopolvars 
-TM2_allscales <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + Pdevelop + Ndevelop + Communitarianism_score + Egalitarianism_score , data = TM2)
+TM2_allscales <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + Pdevelop + Ndevelop + Individualism_score + Hierarchy_score , data = TM2)
 

### 2024-02-16 withmice.Rmd
mice for dataset

---
title: "withmice"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    keep_tex: yes
  header-includes:
  - \usepackage{dcolumn}
  - \usepackage{array}
  - "\\usepackage{placeins}"
  keep_md: yes
---

```{r load packages, warning = FALSE, message = FALSE, echo=FALSE}
  knitr::opts_chunk$set(warning = FALSE, message = FALSE)

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(tidyr))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(lavaan))
suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(DT))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(psych)) 
suppressPackageStartupMessages(library(foreign))
suppressPackageStartupMessages(library(MASS))
suppressPackageStartupMessages(library(Hmisc))
suppressPackageStartupMessages(library(reshape2))
suppressPackageStartupMessages(library(mice))

```

```{r setup, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

moduletwo <- read_excel(here::here("thesis_surveydata/political_factors_complete.xlsx"))
module2 <- data.frame(moduletwo)
module2[module2 == "Rather not say/ Don't know"] <- "Rather not say/Don't know"

# loaded data set for module 2 eco -pol variables and removes the rows with question number and question text
```

```{r, eval =TRUE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
codedmodule2 <- module2 %>%

#remove row 1
  filter(!row_number() %in% c(1,2)) %>%

# replace risky likert scale with numbers
  mutate_at(vars(starts_with("Risky")), funs(case_when(. =="Not at all risky" ~ 1, 
                                                       . =="Slightly risky" ~ 2, 
                                                       . =="Moderately risky" ~ 3, 
                                                       . =="Very risky" ~ 4, 
                                                       . =="Extremely risky" ~ 5))) %>%

# replace beneficial likert scale with numbers  
  mutate_at(vars(starts_with("Ben")), funs(case_when(. =="Not at all beneficial" ~ 1,
                                                     . =="Slightly beneficial" ~ 2,
                                                     . =="Moderately beneficial" ~ 3,
                                                     . =="Very beneficial" ~ 4,
                                                     . =="Extremely beneficial" ~ 5 ))) %>%

# replace nuclear acceptance likert scale with numbers
  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                                        . == "Somewhat disagree" ~ 2,
                                                                        . == "Neither agree nor disagree" ~3,
                                                                        . == "Somewhat agree" ~ 4,
                                                                        . == "Strongly agree" ~ 5))) %>%

# code likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_S","K_E","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE","DEVNUCLEAR","DEVSOLAR", "DEVCOAL","PROSPER", "RELY"))), funs(case_when(. == "Strongly disagree" ~ 1, 
               . == "Somewhat disagree" ~ 2,
               . == "Neither agree nor disagree" ~3,
               . == "Somewhat agree" ~ 4,
               . == "Strongly agree" ~ 5))) %>%

# NO reverse coding for likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_H","K_I"))), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                               . == "Somewhat disagree" ~ 2,
                                                               . == "Neither agree nor disagree" ~3,
                                                               . == "Somewhat agree" ~ 4,
                                                               . == "Strongly agree" ~ 5))) %>%

# code eco-pol scale variables into numbers
mutate_at(vars(SYSTEMDEMO,SYSTEMRELIGION,SYSTEMTECHNO,SYSTEMTOTAL,WEALTHLIM,MECHANISATION,DECISIONDECEN,INDUSTRYSMALL,ECONOMYLOCAL,ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(. == "Strongly disagree" ~ 1, 
                        . == "Somewhat disagree" ~ 2,
                        . == "Neither agree nor disagree" ~3,
                        . == "Somewhat agree" ~ 4,
                        . == "Strongly agree" ~ 5))) %>%

# NO reverse code eco-pol scale variables into numbers 
 mutate_at(vars(DECISIONCEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG, DEVOVERENV), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                                                                         . == "Somewhat disagree" ~ 2,
                                                                                                         . == "Neither agree nor disagree" ~3,
                                                                                                         . == "Somewhat agree" ~ 4,
                                                                                                         . == "Strongly agree" ~ 5))) %>%
  mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
  mutate_all(~ifelse(. == "West bengal", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "WEST BENGAL", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "Up", "Uttar Pradesh", .))%>%
  mutate_all(~ifelse(. == "Tamilnadu", "Tamil Nadu", .))%>%
  mutate_all(~ifelse(. == "UP", "Uttar Pradesh", .))

```

```{r, echo=FALSE}

module2mice <- codedmodule2 %>%
              dplyr::select(starts_with (c("Risky_Nuclear", "Risky_Solar", "Risky_Coal", "Ben_Nuclear", "Ben_Solar", "Ben_Coal","K_S","K_E","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE","DEVNUCLEAR", "DEVSOLAR", "DEVCOAL","PROSPER", "RELY","K_H","K_I", "WEALTHLIM", "MECHANISATION", "DECISIONDECEN", "INDUSTRYSMALL", "ECONOMYLOCAL", "ENVOVERDEV", "OWNERPUB","OWNERREG", "DECISIONCEN", "INDUSTRYLARGE", "ECONOMYGLOBAL", "OWNERPVT", "OWNERNOREG", "DEVOVERENV", "age", "urban_rural", "gender", "caste", "religion", "State"))) %>%
              dplyr::select(!religiontext)

module2mice2 <- module2mice %>%
  mutate(across(starts_with("Risky_"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("Ben_"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("K_S"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("K_E"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("DISPLACE"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("POLLUTE"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("HEALTH"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("JOBS"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("BEAUTY"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("PRIDE"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("NPRIDE"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("DEV"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("PROSPER"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("RELY"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("K_H"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("K_I"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("WEALTHLIM"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("MECHANISATION"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("DECISIONDECEN"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("INDUSTRYSMALL"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("ECONOMYLOCAL"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("ENVOVERDEV"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("OWNERPUB"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("OWNERREG"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("DECISIONCEN"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("INDUSTRYLARGE"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("ECONOMYGLOBAL"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("OWNERPVT"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("OWNERNOREG"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("DEVOVERENV"), ~factor(.x, ordered = TRUE))) %>%
  mutate(across(starts_with("age"), ~factor(.x, ordered = TRUE)))%>%
  mutate(across(starts_with("urban_rural"), ~factor(.x, ordered = FALSE)))%>%
  mutate(across(starts_with("gender"), ~factor(.x, ordered = FALSE)))%>%
  mutate(across(starts_with("caste"), ~factor(.x, ordered = FALSE)))%>%
  mutate(across(starts_with("religion"), ~factor(.x, ordered = FALSE)))%>%
  mutate(across(starts_with("State"), ~factor(.x, ordered = FALSE)))

str(module2mice2)

```

```{r, echo=FALSE}

## checking levels for all the variables

# Loop through each column in the dataframe
for(col_name in names(module2mice2)) {
  # Check if the column is a factor
  if(is.factor(module2mice2[[col_name]])) {
    # Print the levels of the factor
    cat("Levels for", col_name, ":\n")
    print(levels(module2mice2[[col_name]]))
    cat("\n") # Just for better readability in the output
  }
}
```

```{r, echo=FALSE}

d.pattern(module2mice2)

```

### 2024-03-01 withmice.Rmd
trying mice on demographic variables and DVs

@@
 
+```{r}
+## checking correlation with NA
+
+nuclearrel <- codedmodule2 %>%
+  dplyr::select(starts_with (c("Risky_Nuclear","Ben_Nuclear","DISPLACENUCLEAR", "POLLUTENUCLEAR","HEALTHNUCLEAR","JOBSNUCLEAR","BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR", "K_H","K_I", "WEALTHLIM", "MECHANISATION", "DECISIONDECEN", "INDUSTRYSMALL", "ECONOMYLOCAL", "ENVOVERDEV", "OWNERPUB","OWNERREG", "DECISIONCEN", "INDUSTRYLARGE", "ECONOMYGLOBAL", "OWNERPVT", "OWNERNOREG", "DEVOVERENV", "age", "urban_rural", "gender", "caste", "religion", "State")))%>%
+              dplyr::select(!religiontext) %>%
+              filter(!is.na(gender))
+
+# Store results in a data frame
+results <- data.frame(Variable = character(), Correlation = numeric(), P_Value = numeric(), stringsAsFactors = FALSE)
+
+# Loop through all columns in the dataframe
+for(var in names(nuclearrel)) {
+  # Skip if the variable is not numeric or if it's the same as Risky_Nuclear
+  if(!is.numeric(nuclearrel[[var]]) || var == "Risky_Nuclear") next
+
+  # Perform correlation test
+  test_result <- cor.test(nuclearrel$Risky_Nuclear, nuclearrel[[var]], use = "complete.obs")
+
+  # Store results
+  results <- rbind(results, data.frame(Variable = var, Correlation = test_result$estimate, P_Value = test_result$p.value))
+}
+
+# Print the results
+print(results)
+
+```
+
 ```{r, echo=FALSE}
@@
 module2mice <- codedmodule2 %>%
-              dplyr::select(starts_with (c("Risky_Nuclear", "Risky_Solar", "Risky_Coal", "Ben_Nuclear", "Ben_Solar", "Ben_Coal","K_S","K_E","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE","DEVNUCLEAR", "DEVSOLAR", "DEVCOAL","PROSPER", "RELY","K_H","K_I", "WEALTHLIM", "MECHANISATION", "DECISIONDECEN", "INDUSTRYSMALL", "ECONOMYLOCAL", "ENVOVERDEV", "OWNERPUB","OWNERREG", "DECISIONCEN", "INDUSTRYLARGE", "ECONOMYGLOBAL", "OWNERPVT", "OWNERNOREG", "DEVOVERENV", "age", "urban_rural", "gender", "caste", "religion", "State"))) %>%
-              dplyr::select(!religiontext)
+              dplyr::select(starts_with (c("Risky_Nuclear","Ben_Nuclear","DISPLACENUCLEAR", "POLLUTENUCLEAR","HEALTHNUCLEAR","JOBSNUCLEAR","BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR", "Risky_Solar", "Risky_Coal",  "Ben_Solar", "Ben_Coal","K_S","K_E","DISPLACESOLAR","DISPLACESOLARCOAL", "POLLUTESOLAR","POLLUTECOAL",  "HEALTHSOLAR", "HEALTHCOAL",  "JOBSSOLAR", "JOBSCOAL",  "BEAUTYSOLAR", "BEAUTYCOAL",  "PRIDESOLAR", "PRIDECOAL",  "NPRIDESOLAR", "NPRIDECOAL", "DEVSOLAR", "DEVCOAL","PROSPERSOLAR","PROSPERCOAL",  "RELYSOLAR", "RELYCOAL","K_H","K_I", "WEALTHLIM", "MECHANISATION", "DECISIONDECEN", "INDUSTRYSMALL", "ECONOMYLOCAL", "ENVOVERDEV", "OWNERPUB","OWNERREG", "DECISIONCEN", "INDUSTRYLARGE", "ECONOMYGLOBAL", "OWNERPVT", "OWNERNOREG", "DEVOVERENV", "age", "urban_rural", "gender", "caste", "religion", "State"))) %>%
+              dplyr::select(!religiontext) %>%
+              mutate_all(~ifelse(. == "Other (Please mention)", "Other", .))%>%
+              mutate_all(~ifelse(. == "(Other)", "Other", .))%>%
+              filter(!is.na(gender))
+
+module2mice$caste[module2mice$caste == "Rather not say/Don't know"] <- NA
+module2mice$religion[module2mice$religion == "(Other)"] <- NA
 
@@
 
+# Identify rows with any NA values
+rows_with_na <- apply(module2mice2, 1, function(x) any(is.na(x)))
+
+# View rows that contain NAs
+module2mice2[rows_with_na, ]
+
 ```
@@
 
-d.pattern(module2mice2)
+summary(module2mice2)
+
+mice::md.pattern(module2mice2)
+
+md.pairs(module2mice2)
+
+# predictors - K_EDISCRIM K_ERADEQ1  K_EWEALTH  K_ERADEQ2  age      urban_rural    gender   caste  religion   State  WEALTHLIM  MECHANISATION WEALTHLIM INDUSTRYSMALL INDUSTRYLARGE - these were chosed on the basis of least amount of NAs.
+
+Risky <- module2mice2 %>%
+        dplyr::select(starts_with(c("Risky","Ben", "State")))
+
+K <- module2mice2 %>%
+        dplyr::select(starts_with(c("K_", "State")))
+
+mice::md.pattern(Risky)
+
+md.pairs(Risky)
+
+K_all <- mice::md.pattern(K)
+
+options(max.print=1000)
+K_all
+
+md.pairs(K)
+```
+
+```{r, echo = FALSE}
+
+# doing mice with just the DVs and the demographic variables
+
+imp <- mice(module2mice2, maxit = 0)
+
+pred <- imp$predictorMatrix
+pred[, c("Risky_Nuclear","Ben_Nuclear", "DISPLACENUCLEAR", "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR", "HEALTHCOAL","JOBSSOLAR",  "JOBSCOAL", "BEAUTYCOAL",  "PRIDECOAL",  "NPRIDECOAL",  "DEVCOAL", "PROSPERCOAL", "RELYCOAL", "K_HREVDIS1", "Risky_Coal",  "Ben_Coal",  "DISPLACESOLAR",  "BEAUTYSOLAR",  "PROSPERSOLAR",  "RELYSOLAR", "DECISIONDECEN", "ECONOMYLOCAL", "ENVOVERDEV", "OWNERPUB", "DECISIONCEN", "OWNERNOREG", "K_SLIMCHOI", "K_SPROTECT", "POLLUTESOLAR","HEALTHSOLAR", "PRIDESOLAR", "NPRIDESOLAR", "DEVSOLAR","K_HEQUAL", "K_IINTRFER", "K_IPRIVACY", "K_IPROTECT", "OWNERREG", "ECONOMYGLOBAL", "OWNERPVT", "DEVOVERENV" )] <- 0
+
+# Initialize method_list with "" to skip imputation for all variables initially
+method_list <- rep("", ncol(module2mice2))
+names(method_list) <- colnames(module2mice2)
+
+# Specify the imputation method for variables you want to impute
+
+method_list[c("Risky_Nuclear","Risky_Solar", "Risky_Coal", "Ben_Nuclear", "Ben_Solar", "Ben_Coal", "K_EDISCRIM", "K_ERADEQ1", "K_EWEALTH", "K_ERADEQ2", "WEALTHLIM", "MECHANISATION", "INDUSTRYSMALL", "INDUSTRYLARGE")] <- "polr"
+method_list["caste"] <- "polyreg"
+
+imp <- mice(module2mice2, method = method_list, pred = pred, maxit = 15, seed = 123)
+
+print(imp)
+
+imp$imp$caste
 

### 2024-03-05 withmice.Rmd
new attempt to do mice

--- 2024-02-16 withmice.Rmd
@@
 title: "withmice"
-output:
-  pdf_document:
-    toc: yes
-    toc_depth: 2
-    keep_tex: yes
-  header-includes:
-  - \usepackage{dcolumn}
-  - \usepackage{array}
-  - "\\usepackage{placeins}"
-  keep_md: yes
+output: html_document
 ---
 
-```{r load packages, warning = FALSE, message = FALSE, echo=FALSE}
-  knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-
-suppressPackageStartupMessages(library(tidyverse))
-suppressPackageStartupMessages(library(readxl))
-suppressPackageStartupMessages(library(dplyr))
-suppressPackageStartupMessages(library(tidyr))
-suppressPackageStartupMessages(library(ggplot2))
-suppressPackageStartupMessages(library(lavaan))
-suppressPackageStartupMessages(library(tsibble))
-suppressPackageStartupMessages(library(DT))
-suppressPackageStartupMessages(library(knitr))
-suppressPackageStartupMessages(library(psych)) 
-suppressPackageStartupMessages(library(foreign))
-suppressPackageStartupMessages(library(MASS))
-suppressPackageStartupMessages(library(Hmisc))
-suppressPackageStartupMessages(library(reshape2))
-suppressPackageStartupMessages(library(mice))
-
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
 ```
 
-```{r setup, echo=FALSE}
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+## R Markdown
 
-moduletwo <- read_excel(here::here("thesis_surveydata/political_factors_complete.xlsx"))
-module2 <- data.frame(moduletwo)
-module2[module2 == "Rather not say/ Don't know"] <- "Rather not say/Don't know"
+This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
 
-# loaded data set for module 2 eco -pol variables and removes the rows with question number and question text
+When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
+You can embed an R code chunk like this:
+
+```{r cars}
+summary(cars)
 ```
 
-```{r, eval =TRUE, echo=FALSE}
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
-codedmodule2 <- module2 %>%
+## Including Plots
 
-#remove row 1
-  filter(!row_number() %in% c(1,2)) %>%
+You can also embed plots, for example:
 
-# replace risky likert scale with numbers
-  mutate_at(vars(starts_with("Risky")), funs(case_when(. =="Not at all risky" ~ 1, 
-                                                       . =="Slightly risky" ~ 2, 
-                                                       . =="Moderately risky" ~ 3, 
-                                                       . =="Very risky" ~ 4, 
-                                                       . =="Extremely risky" ~ 5))) %>%
-
-# replace beneficial likert scale with numbers  
-  mutate_at(vars(starts_with("Ben")), funs(case_when(. =="Not at all beneficial" ~ 1,
-                                                     . =="Slightly beneficial" ~ 2,
-                                                     . =="Moderately beneficial" ~ 3,
-                                                     . =="Very beneficial" ~ 4,
-                                                     . =="Extremely beneficial" ~ 5 ))) %>%
-
-# replace nuclear acceptance likert scale with numbers
-  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
-                                                                        . == "Somewhat disagree" ~ 2,
-                                                                        . == "Neither agree nor disagree" ~3,
-                                                                        . == "Somewhat agree" ~ 4,
-                                                                        . == "Strongly agree" ~ 5))) %>%
-
-# code likert scale for variables for Kahan scale into numbers
-  mutate_at(vars(starts_with (c("K_S","K_E","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE","DEVNUCLEAR","DEVSOLAR", "DEVCOAL","PROSPER", "RELY"))), funs(case_when(.
-== "Strongly disagree" ~ 1,
-               . == "Somewhat disagree" ~ 2,
-               . == "Neither agree nor disagree" ~3,
-               . == "Somewhat agree" ~ 4,
-               . == "Strongly agree" ~ 5))) %>%
-
-# NO reverse coding for likert scale for variables for Kahan scale into numbers
-  mutate_at(vars(starts_with (c("K_H","K_I"))), funs(case_when(. == "Strongly disagree" ~ 1, 
-                                                               . == "Somewhat disagree" ~ 2,
-                                                               . == "Neither agree nor disagree" ~3,
-                                                               . == "Somewhat agree" ~ 4,
-                                                               . == "Strongly agree" ~ 5))) %>%
-
-# code eco-pol scale variables into numbers
-mutate_at(vars(SYSTEMDEMO,SYSTEMRELIGION,SYSTEMTECHNO,SYSTEMTOTAL,WEALTHLIM,MECHANISATION,DECISIONDECEN,INDUSTRYSMALL,ECONOMYLOCAL,ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(.
-== "Strongly disagree" ~ 1,
-                        . == "Somewhat disagree" ~ 2,
-                        . == "Neither agree nor disagree" ~3,
-                        . == "Somewhat agree" ~ 4,
-                        . == "Strongly agree" ~ 5))) %>%
-
-# NO reverse code eco-pol scale variables into numbers 
- mutate_at(vars(DECISIONCEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG, DEVOVERENV), funs(case_when(. == "Strongly disagree" ~ 1, 
-                                                                                                         . == "Somewhat disagree" ~ 2,
-                                                                                                         . == "Neither agree nor disagree" ~3,
-                                                                                                         . == "Somewhat agree" ~ 4,
-                                                                                                         . == "Strongly agree" ~ 5))) %>%
-  mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
-  mutate_all(~ifelse(. == "West bengal", "West Bengal", .))%>%
-  mutate_all(~ifelse(. == "WEST BENGAL", "West Bengal", .))%>%
-  mutate_all(~ifelse(. == "Up", "Uttar Pradesh", .))%>%
-  mutate_all(~ifelse(. == "Tamilnadu", "Tamil Nadu", .))%>%
-  mutate_all(~ifelse(. == "UP", "Uttar Pradesh", .))
-
+```{r pressure, echo=FALSE}
+plot(pressure)
 ```
 
-```{r, echo=FALSE}
-
-module2mice <- codedmodule2 %>%
-              dplyr::select(starts_with (c("Risky_Nuclear", "Risky_Solar", "Risky_Coal", "Ben_Nuclear", "Ben_Solar", "Ben_Coal","K_S","K_E","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE","DEVNUCLEAR", "DEVSOLAR", "DEVCOAL","PROSPER", "RELY","K_H","K_I", "WEALTHLIM", "MECHANISATION", "DECISIONDECEN", "INDUSTRYSMALL", "ECONOMYLOCAL", "ENVOVERDEV", "OWNERPUB","OWNERREG", "DECISIONCEN", "INDUSTRYLARGE", "ECONOMYGLOBAL", "OWNERPVT", "OWNERNOREG", "DEVOVERENV", "age", "urban_rural", "gender", "caste", "religion", "State"))) %>%
-              dplyr::select(!religiontext)
-
-module2mice2 <- module2mice %>%
-  mutate(across(starts_with("Risky_"), ~factor(.x, ordered = TRUE))) %>%
-  mutate(across(starts_with("Ben_"), ~factor(.x, ordered = TRUE))) %>%
-  mutate(across(starts_with("K_S"), ~factor(.x, ordered = TRUE))) %>%
-  mutate(across(starts_with("K_E"), ~factor(.x, ordered = TRUE))) %>%
-  mutate(across(starts_with("DISPLACE"), ~factor(.x, ordered = TRUE))) %>%
-  mutate(across(starts_with("POLLUTE"), ~factor(.x, ordered = TRUE))) %>%
-  mutate(across(starts_with("HEALTH"), ~factor(.x, ordered = TRUE))) %>%
-  mutate(across(starts_with("JOBS"), ~factor(.x, ordered = TRUE))) %>%
-  mutate(across(starts_with("BEAUTY"), ~factor(.x, ordered = TRUE))) %>%
-  mutate(across(starts_with("PRIDE"), ~factor(.x, ordered = TRUE))) %>%
-  mutate(across(starts_with("NPRIDE"), ~factor(.x, ordered = TRUE))) %>%
-  mutate(across(starts_with("DEV"), ~factor(.x, ordered = TRUE))) %>%
-  mutate(across(starts_with("PROSPER"), ~factor(.x, ordered = TRUE))) %>%
-  mutate(across(starts_with("RELY"), ~factor(.x, ordered = TRUE))) %>%
-  mutate(across(starts_with("K_H"), ~factor(.x, ordered = TRUE))) %>%
-  mutate(across(starts_with("K_I"), ~factor(.x, ordered = TRUE))) %>%
-  mutate(across(starts_with("WEALTHLIM"), ~factor(.x, ordered = TRUE))) %>%
-  mutate(across(starts_with("MECHANISATION"), ~factor(.x, ordered = TRUE))) %>%
-  mutate(across(starts_with("DECISIONDECEN"), ~factor(.x, ordered = TRUE))) %>%
-  mutate(across(starts_with("INDUSTRYSMALL"), ~factor(.x, ordered = TRUE))) %>%
-  mutate(across(starts_with("ECONOMYLOCAL"), ~factor(.x, ordered = TRUE))) %>%
-  mutate(across(starts_with("ENVOVERDEV"), ~factor(.x, ordered = TRUE))) %>%
-  mutate(across(starts_with("OWNERPUB"), ~factor(.x, ordered = TRUE))) %>%
-  mutate(across(starts_with("OWNERREG"), ~factor(.x, ordered = TRUE))) %>%
-  mutate(across(starts_with("DECISIONCEN"), ~factor(.x, ordered = TRUE))) %>%
-  mutate(across(starts_with("INDUSTRYLARGE"), ~factor(.x, ordered = TRUE))) %>%
-  mutate(across(starts_with("ECONOMYGLOBAL"), ~factor(.x, ordered = TRUE))) %>%
-  mutate(across(starts_with("OWNERPVT"), ~factor(.x, ordered = TRUE))) %>%
-  mutate(across(starts_with("OWNERNOREG"), ~factor(.x, ordered = TRUE))) %>%
-  mutate(across(starts_with("DEVOVERENV"), ~factor(.x, ordered = TRUE))) %>%
-  mutate(across(starts_with("age"), ~factor(.x, ordered = TRUE)))%>%
-  mutate(across(starts_with("urban_rural"), ~factor(.x, ordered = FALSE)))%>%
-  mutate(across(starts_with("gender"), ~factor(.x, ordered = FALSE)))%>%
-  mutate(across(starts_with("caste"), ~factor(.x, ordered = FALSE)))%>%
-  mutate(across(starts_with("religion"), ~factor(.x, ordered = FALSE)))%>%
-  mutate(across(starts_with("State"), ~factor(.x, ordered = FALSE)))
-
-str(module2mice2)
-
-```
-
-```{r, echo=FALSE}
-
-## checking levels for all the variables
-
-# Loop through each column in the dataframe
-for(col_name in names(module2mice2)) {
-  # Check if the column is a factor
-  if(is.factor(module2mice2[[col_name]])) {
-    # Print the levels of the factor
-    cat("Levels for", col_name, ":\n")
-    print(levels(module2mice2[[col_name]]))
-    cat("\n") # Just for better readability in the output
-  }
-}
-```
-
-```{r, echo=FALSE}
-
-d.pattern(module2mice2)
-
-```
+Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2024-03-06 withmice.Rmd
editted Atheism/Agnosticism in the dataset

@@
 ---
-title: "withmice"
-output: html_document
+title: "models with mice"
+output:
+  pdf_document:
+    toc: yes
+    toc_depth: 2
+    keep_tex: yes
+  header-includes:
+  - \usepackage{dcolumn}
+  - \usepackage{array}
+  - "\\usepackage{placeins}"
+  keep_md: yes
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+```{r load packages, warning = FALSE, message = FALSE, echo=FALSE}
+  knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+
+suppressPackageStartupMessages(library(tidyverse))
+suppressPackageStartupMessages(library(readxl))
+suppressPackageStartupMessages(library(dplyr))
+suppressPackageStartupMessages(library(tidyr))
+suppressPackageStartupMessages(library(ggplot2))
+suppressPackageStartupMessages(library(lavaan))
+suppressPackageStartupMessages(library(tsibble))
+suppressPackageStartupMessages(library(DT))
+suppressPackageStartupMessages(library(knitr))
+suppressPackageStartupMessages(library(psych)) 
+suppressPackageStartupMessages(library(foreign))
+suppressPackageStartupMessages(library(MASS))
+suppressPackageStartupMessages(library(Hmisc))
+suppressPackageStartupMessages(library(reshape2))
+
 ```
 
-## R Markdown
+```{r setup, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+moduletwo <- read_excel(here::here("thesis_surveydata/political_factors_complete.xlsx"))
+module2 <- data.frame(moduletwo)
+module2[module2 == "Rather not say/ Don't know"] <- "Rather not say/Don't know"
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
-```{r cars}
-summary(cars)
+# loaded data set for module 2 eco -pol variables and removes the rows with question number and question text
 ```
 
-## Including Plots
+```{r, eval =TRUE, echo=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
+codedmodule2 <- module2 %>%
 
-You can also embed plots, for example:
+#remove row 1
+  filter(!row_number() %in% c(1,2)) %>%
 
-```{r pressure, echo=FALSE}
-plot(pressure)
+# replace risky likert scale with numbers
+  mutate_at(vars(starts_with("Risky")), funs(case_when(. =="Not at all risky" ~ 1, 
+                                                       . =="Slightly risky" ~ 2, 
+                                                       . =="Moderately risky" ~ 3, 
+                                                       . =="Very risky" ~ 4, 
+                                                       . =="Extremely risky" ~ 5))) %>%
+
+# replace beneficial likert scale with numbers  
+  mutate_at(vars(starts_with("Ben")), funs(case_when(. =="Not at all beneficial" ~ 1,
+                                                     . =="Slightly beneficial" ~ 2,
+                                                     . =="Moderately beneficial" ~ 3,
+                                                     . =="Very beneficial" ~ 4,
+                                                     . =="Extremely beneficial" ~ 5 ))) %>%
+
+# replace nuclear acceptance likert scale with numbers
+  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
+                                                                        . == "Somewhat disagree" ~ 2,
+                                                                        . == "Neither agree nor disagree" ~3,
+                                                                        . == "Somewhat agree" ~ 4,
+                                                                        . == "Strongly agree" ~ 5))) %>%
+
+# code likert scale for variables for Kahan scale into numbers
+  mutate_at(vars(starts_with (c("K_S","K_E","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE","DEV","PROSPER", "RELY"))), funs(case_when(. == "Strongly disagree" ~ 1, 
+               . == "Somewhat disagree" ~ 2,
+               . == "Neither agree nor disagree" ~3,
+               . == "Somewhat agree" ~ 4,
+               . == "Strongly agree" ~ 5))) %>%
+
+# reverse code for likert scale for variables for Kahan scale into numbers
+  mutate_at(vars(starts_with (c("K_H","K_I"))), funs(case_when(. == "Strongly disagree" ~ 5, 
+                                                               . == "Somewhat disagree" ~ 4,
+                                                               . == "Neither agree nor disagree" ~3,
+                                                               . == "Somewhat agree" ~ 2,
+                                                               . == "Strongly agree" ~ 1))) %>%
+
+# code eco-pol scale variables into numbers
+mutate_at(vars(SYSTEMDEMO,SYSTEMRELIGION,SYSTEMTECHNO,SYSTEMTOTAL,WEALTHLIM,MECHANISATION,DECISIONDECEN,INDUSTRYSMALL,ECONOMYLOCAL,ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(.
+== "Strongly disagree" ~ 1,
+                        . == "Somewhat disagree" ~ 2,
+                        . == "Neither agree nor disagree" ~3,
+                        . == "Somewhat agree" ~ 4,
+                        . == "Strongly agree" ~ 5))) %>%
+
+# NO reverse code eco-pol scale variables into numbers 
+ mutate_at(vars(DECISIONCEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG), funs(case_when(. == "Strongly disagree" ~ 1, 
+                                                                                                         . == "Somewhat disagree" ~ 2,
+                                                                                                         . == "Neither agree nor disagree" ~3,
+                                                                                                         . == "Somewhat agree" ~ 4,
+                                                                                                         . == "Strongly agree" ~ 5))) %>%
+  mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
+  mutate_all(~ifelse(. == "West bengal", "West Bengal", .))%>%
+  mutate_all(~ifelse(. == "WEST BENGAL", "West Bengal", .))%>%
+  mutate_all(~ifelse(. == "Up", "Uttar Pradesh", .))%>%
+  mutate_all(~ifelse(. == "Tamilnadu", "Tamil Nadu", .))%>%
+  mutate_all(~ifelse(. == "UP", "Uttar Pradesh", .))
+
 ```
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+```{r}
+
+## Can do something with accept, reject and reluctantly accept.
+
+n_acceptreject<- codedmodule2 %>%
+                dplyr::select("N_accept", "N_reluctantlyaccept", "N_reject")
+
+summary(n_acceptreject)
+```
+
+```{r, echo=FALSE}
+
+formice <- codedmodule2[, grep("State|age|urban_rural|gender|caste|religion|Solar|SOLAR|Nuclear|NUCLEAR|Coal|COAL|K_S|K_E|K_H|K_I|WEALTHLIM|MECHANISATION|DECISIONDECEN|INDUSTRYSMALL|ECONOMYLOCAL|ENVOVERDEV|OWNERPUB|OWNERREG|DECISIONCEN|INDUSTRYLARGE|ECONOMYGLOBAL|OWNERPVT|OWNERNOREG", names(codedmodule2))]%>%
+        dplyr::select(-c("Language", "Risky_INDSolar", "Ben_INDSolar", "religiontext"))
+
+#dplyr:: select(starts_with (c("State", "age", "urban_rural", "gender", "caste", "religion","Risky_Solar", "Risky_Nuclear", "Risky_Coal", "Ben_Solar","Ben_Nuclear","Ben_Coal","K_S","K_E","K_H","K_I", "DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE","DEV", "PROSPER", "RELY", "WEALTHLIM", "MECHANISATION", "DECISIONDECEN", "INDUSTRYSMALL", "ECONOMYLOCAL", "ENVOVERDEV", "OWNERPUB", "OWNERREG", "DECISIONCEN","INDUSTRYLARGE","ECONOMYGLOBAL","OWNERPVT","OWNERNOREG" )))
+
+library(dplyr)
+
+formice <- formice %>%
+  mutate(across(Risky_Solar:age, ~factor(.x, ordered = TRUE)))%>%
+  mutate(across(urban_rural:religion, ~factor(.x, ordered = FALSE)))%>%
+  mutate(across(State, ~factor(.x, ordered = FALSE)))
+
+str(formice)
+summary(formice)
+
+```
+
+```{r, echo =FALSE}
+library(mifa)
+library(mice)
+library(psych)
+
+ #cov_vars = -c(State, Risky_Solar, Risky_Nuclear, Risky_Coal, Ben_Solar, Ben_Nuclear, Ben_Coal, DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE, ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV, OWNERPVT, OWNERPUB, OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION, DISPLACESOLAR, POLLUTESOLAR, HEALTHSOLAR, JOBSSOLAR, BEAUTYSOLAR, PRIDESOLAR, NPRIDESOLAR, DEVSOLAR, PROSPERSOLAR, RELYSOLAR, DISPLACECOAL, POLLUTECOAL, HEALTHCOAL, JOBSCOAL, BEAUTYCOAL, PRIDECOAL, NPRIDECOAL, DEVCOAL, PROSPERCOAL, RELYCOAL, DISPLACENUCLEAR, POLLUTENUCLEAR, HEALTHNUCLEAR, JOBSNUCLEAR, BEAUTYNUCLEAR, PRIDENUCLEAR, NPRIDENUCLEAR, DEVNUCLEAR, PROSPERNUCLEAR, RELYNUCLEAR, age, urban_rural, gender, caste, religion),
+
+kahanall <- codedmodule2 %>%
+          dplyr::select(c(starts_with("K_")))
+
+mikahan <- mifa(data= kahanall,
+                cov_vars = everything(),
+                n_pc= 2:4,
+                ci = "fieller", 
+                n_boot=1000,
+                print = FALSE,
+                progress= TRUE, )
+
+mikahan
+
+library(psych)
+
+fit <- psych::fa(mikahan$cov_combined,n.obs = nrow(mikahan), nfactors = 2, rotate = "varimax")
+
+print(fit, sort= TRUE, cut= 0.4)
+
+data_imp <- mice::complete(mice::mice(kahanall, 1, print = FALSE))
+
+fct_scores <- data.frame(factor.scores(data_imp[, 1:12], fit)$scores)
+
+```

### 2024-03-06 withmice.Rmd
Mifa for kahan and ecopol nuclear scale

@@
 
+## Can do something with accept, reject and reluctantly accept.
+
 ```{r}
@@
 
+## Mifa dor Kahan scale 
 ```{r, echo =FALSE}
@@
                 print = FALSE,
-                progress= TRUE, )
+                progress= TRUE, 
+                seed = 427,)
 
@@
 
-fit <- psych::fa(mikahan$cov_combined,n.obs = nrow(mikahan), nfactors = 2, rotate = "varimax")
+fit <- psych::fa(mikahan$cov_combined, nfactors = 2, rotate = "varimax")
 
-print(fit, sort= TRUE, cut= 0.4)
+print.psych(fit, sort= TRUE, cut= 0.4)
 
@@
 ```
+
+#checking imputations: Kahan scale
+
+```{r}
+orgscores <- data.frame(kahanefascores)
+
+summary(mikahan)
+names(mikahan)
+
+mikahan$mids
+
+complete_data_first <- complete(mikahan$mids, 1)
+
+summary(complete_data_first)
+
+complete_data_2 <- complete(mikahan$mids, 2)
+
+summary(complete_data_2)
+
+complete_data_3 <- complete(mikahan$mids, 3)
+
+summary(complete_data_3)
+
+complete_data_4 <- complete(mikahan$mids, 4)
+
+summary(complete_data_4)
+
+complete_data_5 <- complete(mikahan$mids, 5)
+
+summary(complete_data_5)
+```
+
+## Distribution check: kahan Scale
+
+```{r}
+# Add an identifier column to each dataset
+fct_scores$Dataset <- 'fct_scores'
+orgscores$Dataset <- 'orgscores'
+
+# Combine the datasets for plotting
+combined_data <- rbind(fct_scores, orgscores)
+
+# Select only necessary columns (assuming 'Index' isn't needed anymore)
+combined_data <- combined_data[, c("MR1", "MR2", "Dataset")]
+
+ggplot(combined_data, aes(x = Dataset, y = MR1, fill = Dataset)) +
+  geom_boxplot() +
+  geom_jitter(width = 0.2, aes(color = Dataset), size = 1.5, alpha = 0.5) +
+  labs(title = "Boxplot of MR1 for Each Dataset", x = "", y = "MR1 Value") +
+  scale_fill_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
+  scale_color_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
+  theme_minimal()
+
+```
+```{r}
+ggplot(combined_data, aes(x = Dataset, y = MR2, fill = Dataset)) +
+  geom_boxplot() +
+  geom_jitter(width = 0.2, aes(color = Dataset), size = 1.5, alpha = 0.5) +
+  labs(title = "Boxplot of MR2 for Each Dataset with Points", x = "", y = "MR2 Value") +
+  scale_fill_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
+  scale_color_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
+  theme_minimal()
+
+```
+
+# Mifa for new eco-pol value scale : Nuclear energy
+
+```{r}
+
+ecopoln <- codedmodule2[, grep("NUCLEAR|WEALTHLIM|MECHANISATION|DECISIONDECEN|INDUSTRYSMALL|ECONOMYLOCAL|ENVOVERDEV|OWNERPUB|OWNERREG|DECISIONCEN|INDUSTRYLARGE|ECONOMYGLOBAL|OWNERPVT|OWNERNOREG", names(codedmodule2))]
+
+miecopol <- mifa(data= ecopoln,
+                cov_vars = everything(),
+                n_pc= 2:4,
+                ci = "fieller", 
+                n_boot=1000,
+                print = FALSE,
+                progress= TRUE, 
+                seed = 429,)
+
+miecopol
+
+fit2 <- psych::fa(miecopol$cov_combined, nfactors = 2, rotate = "varimax")
+
+print.psych(fit2, sort= TRUE, cut= 0.4)
+
+data_imp2 <- mice::complete(mice::mice(ecopoln, 1, print = FALSE))
+
+fct_scores2 <- data.frame(factor.scores(data_imp2[, 1:23], fit2)$scores)
+
+```
+
+## Checking imputations : Eco-pol scale
+
+```{r, echo=FALSE}
+
+orgscores <- data.frame(kahanefascores)
+
+summary(miecopol)
+names(miecopol)
+
+miecopol$mids
+
+complete_ecopol_first <- complete(miecopol$mids, 1)
+
+summary(complete_ecopol_first)
+
+complete_ecopol_2 <- complete(miecopol$mids, 2)
+
+summary(complete_ecopol_2)
+
+complete_ecopol_3 <- complete(miecopol$mids, 3)
+
+summary(complete_ecopol_3)
+
+complete_ecopol_4 <- complete(miecopol$mids, 4)
+
+summary(complete_ecopol_4)
+
+complete_ecopol_5 <- complete(miecopol$mids, 5)
+
+summary(complete_ecopol_5)
+```

### 2024-03-07 withmice.Rmd
comparing imputed and original data for ecopol scale via boxplots

@@
 
-## Mifa dor Kahan scale 
+## Mifa for Kahan scale 
 ```{r, echo =FALSE}
@@
 ```{r}
+
 orgscores <- data.frame(kahanefascores)
@@
 
-orgscores <- data.frame(kahanefascores)
-
 summary(miecopol)
@@
 summary(complete_ecopol_5)
+
 ```
+
+```{r}
+
+nscores <- data.frame(ecopolall_scores$scores)
+nscores
+
+# Add an identifier column to each dataset
+fct_scores2$Dataset <- 'imputed'
+nscores$Dataset <- 'original'
+
+# Combine the datasets for plotting
+compare2 <- rbind(fct_scores2, nscores)
+
+# Select only necessary columns (assuming 'Index' isn't needed anymore)
+compare2<- compare2[, c("MR1", "MR2", "Dataset")]
+
+ggplot(compare2, aes(x = Dataset, y = MR1, fill = Dataset)) +
+  geom_boxplot() +
+  geom_jitter(width = 0.2, aes(color = Dataset), size = 1.5, alpha = 0.5) +
+  labs(title = "Boxplot of Pdevelop for Each Dataset", x = "", y = "MR1 Value") +
+  scale_fill_manual(values = c("imputed" = "blue", "original" = "red")) +
+  scale_color_manual(values = c("imputed" = "blue", "original" = "red")) +
+  theme_minimal()
+
+```
+
+```{r}
+
+ggplot(compare2, aes(x = Dataset, y = MR2, fill = Dataset)) +
+  geom_boxplot() +
+  geom_jitter(width = 0.2, aes(color = Dataset), size = 1.5, alpha = 0.5) +
+  labs(title = "Boxplot of Ndevelop for Each Dataset with Points", x = "", y = "MR2 Value") +
+  scale_fill_manual(values = c("imputed" = "blue", "original" = "red")) +
+  scale_color_manual(values = c("imputed" = "blue", "original" = "red")) +
+  theme_minimal()
+
+```
+
+```{r}
+
+```

### 2024-03-07 corstuff.Rmd
minor beautification for pdf
Mifa for kahan and ecopol nuclear scale
removed reverse coding for all scales in three rmd files - FA options, corstuff and withmice

@@
 
-# reverse code for likert scale for variables for Kahan scale into numbers
-  mutate_at(vars(starts_with (c("K_S","K_E"))), funs(case_when(. == "Strongly disagree" ~ 5, 
-                                                               . == "Somewhat disagree" ~ 4,
+# NO reverse code for likert scale for variables for Kahan scale into numbers
+  mutate_at(vars(starts_with (c("K_S","K_E"))), funs(case_when(. == "Strongly disagree" ~ 1, 
+                                                               . == "Somewhat disagree" ~ 2,
                                                                . == "Neither agree nor disagree" ~3,
-                                                               . == "Somewhat agree" ~ 2,
-                                                               . == "Strongly agree" ~ 1))) %>%
+                                                               . == "Somewhat agree" ~ 4,
+                                                               . == "Strongly agree" ~ 5))) %>%
 
@@
 
-# reverse code eco-pol scale variables into numbers 
- mutate_at(vars(DECISIONCEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG, DEVOVERENV), funs(case_when(. == "Strongly disagree" ~ 5, 
-                                                                                                         . == "Somewhat disagree" ~ 4,
+# NO reverse code eco-pol scale variables into numbers 
+ mutate_at(vars(DECISIONCEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG, DEVOVERENV), funs(case_when(. == "Strongly disagree" ~ 1, 
+                                                                                                         . == "Somewhat disagree" ~ 2,
                                                                                                          . == "Neither agree nor disagree" ~3,
-                                                                                                         . == "Somewhat agree" ~ 2,
-                                                                                                         . == "Strongly agree" ~ 1))) %>%
+                                                                                                         . == "Somewhat agree" ~ 4,
+                                                                                                         . == "Strongly agree" ~ 5))) %>%
   mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
@@
 \newpage
-#Correlation table Eco-pol scale and Kahan CFA scores
+# Correlation table Eco-pol scale and Kahan CFA scores
 
@@
 
-#print.psych(kahan.fa, cut = 0.4, sort = TRUE)
+print.psych(kahan.fa, cut = 0.4, sort = TRUE)
 

### 2024-03-07 withmice.Rmd
removed reverse coding for all scales in three rmd files - FA options, corstuff and withmice

@@
 
-# reverse code for likert scale for variables for Kahan scale into numbers
-  mutate_at(vars(starts_with (c("K_H","K_I"))), funs(case_when(. == "Strongly disagree" ~ 5, 
-                                                               . == "Somewhat disagree" ~ 4,
+# NO reverse code for likert scale for variables for Kahan scale into numbers
+  mutate_at(vars(starts_with (c("K_H","K_I"))), funs(case_when(. == "Strongly disagree" ~ 1, 
+                                                               . == "Somewhat disagree" ~ 2,
                                                                . == "Neither agree nor disagree" ~3,
-                                                               . == "Somewhat agree" ~ 2,
-                                                               . == "Strongly agree" ~ 1))) %>%
+                                                               . == "Somewhat agree" ~ 4,
+                                                               . == "Strongly agree" ~ 5))) %>%
 
@@
                 cov_vars = everything(),
+                m = 10,
                 n_pc= 2:4,
@@
   scale_fill_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
+  scale_color_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
+  theme_minimal()
+
+ggplot(combined_data, aes(x = MR1, color = Dataset)) +
+  geom_density(fill = NA, alpha = 0.5) +
+  labs(title = "Density Plot of MR1 for Each Dataset", x = "MR1 Value", y = "Density") +
   scale_color_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
@@
 nscores <- data.frame(ecopolall_scores$scores)
-nscores
 
@@
 
+library(ggplot2)
+
+ggplot(compare2, aes(x = MR2, color = Dataset)) +
+  geom_density(fill = NA, alpha = 0.5) +
+  labs(title = "Density Plot of MR2 for Each Dataset", x = "MR2 Value", y = "Density") +
+  scale_color_manual(values = c("imputed" = "blue", "original" = "red")) +
+  theme_minimal()
+
 ```
+
+# Binding imputed values to formice dataset
+
+```{r, echo = FALSE}
+
+# binding the imputed  factor analysis scores for kahan scale and eco-pol value scale to the larger dataset codedmodule2
+
+ecopolnuclear <- fct_scores2 %>%
+  rename(Pdevelop = MR1, Ndevelop = MR2)
+
+kahannuclear <- fct_scores%>%
+  rename(Communitarian_Egalitarian = MR1, Hierarchy = MR2)
+
+nuclearformice <- cbind(formice, kahannuclear, ecopolnuclear) %>%
+                  dplyr::select(-c(Dataset))
+
+```

### 2024-03-10 miceafterfa.Rmd
made lms with mice

--- 2024-03-06 withmice.Rmd
@@
 ---
-title: "models with mice"
+title: "miceafterFA"
 output:
@@
 suppressPackageStartupMessages(library(reshape2))
+suppressPackageStartupMessages(library(naniar))
+suppressPackageStartupMessages(library(mice))
 
@@
 
-## Can do something with accept, reject and reluctantly accept.
+```{r}
+
+codedmodule2$State <- as.factor(codedmodule2$State)
+codedmodule2$gender <- as.factor(codedmodule2$gender)
+codedmodule2$Urban <- as.factor(codedmodule2$urban_rural)
+codedmodule2$caste <- as.factor(codedmodule2$caste)
+codedmodule2$religion <- as.factor(codedmodule2$religion)
+# # Convert `caste` into binary variable 'upper' (1) vs 'non-upper' (0)
+codedmodule2$Uppercaste <- ifelse(codedmodule2$caste %in% c('Brahmin', 'General'), 1, 0)
+# Convert `gender` into binary variable 'male' (1) vs 'female' (0)
+codedmodule2$Male <- ifelse(codedmodule2$gender == 'Male', 1, 0)
+# Convert `religion` into binary variable 'Hinduism' (1) vs 'Non-Hinduism' (0)
+codedmodule2$Hindu <- ifelse(codedmodule2$religion == 'Hinduism', 1, 0)
+```
+
+# missing data pattern and MCAR
+
+```{r, echo=FALSE}
+
+formice1 <- codedmodule2[, grep("State|age|Urban|Male|Uppercaste|Hindu|Solar|SOLAR|Nuclear|NUCLEAR|Coal|COAL|K_S|K_E|K_H|K_I|WEALTHLIM|MECHANISATION|DECISIONDECEN|INDUSTRYSMALL|ECONOMYLOCAL|ENVOVERDEV|OWNERPUB|OWNERREG|DECISIONCEN|INDUSTRYLARGE|ECONOMYGLOBAL|OWNERPVT|OWNERNOREG", names(codedmodule2))]%>%
+        dplyr::select(-c("Language", "Risky_INDSolar", "Ben_INDSolar")) %>%
+  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
+                                      . == "25-34 years old" ~ 2,
+                                      . ==  "35-44 years old" ~3,
+                                      . == "45-54 years old" ~ 4,
+                                      . == "55-64 years old" ~ 5,
+                                      . == "65-74 years old" ~ 6,
+                                      . == "75 years or older" ~ 7)))
+
+#dplyr:: select(starts_with (c("State", "age", "urban_rural", "gender", "caste", "religion","Risky_Solar", "Risky_Nuclear", "Risky_Coal", "Ben_Solar","Ben_Nuclear","Ben_Coal","K_S","K_E","K_H","K_I", "DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE","DEV", "PROSPER", "RELY", "WEALTHLIM", "MECHANISATION", "DECISIONDECEN", "INDUSTRYSMALL", "ECONOMYLOCAL", "ENVOVERDEV", "OWNERPUB", "OWNERREG", "DECISIONCEN","INDUSTRYLARGE","ECONOMYGLOBAL","OWNERPVT","OWNERNOREG" )))
+
+#str(formice)
+#summary(formice)
+
+# litte's MCAR test
+
+mcar_test(data=formice1)
+
+# p value = 1, which means MAR condition is met.
+
+```
 
@@
 
-## Can do something with accept, reject and reluctantly accept.
+Kahan_scale <- codedmodule2 %>%
+  dplyr::select(starts_with("K_"))
 
-n_acceptreject<- codedmodule2 %>%
-                dplyr::select("N_accept", "N_reluctantlyaccept", "N_reject")
+# EFA on Kahan scale
 
-summary(n_acceptreject)
+kahan.fa <- fa(Kahan_scale, nfactors = 2, rotate = "varimax")
+print.psych(kahan.fa, cut = 0.4, sort = TRUE)
+
+# extract factor scores
+
+Kahanefa <- psych::factor.scores(Kahan_scale, kahan.fa)
+
+# The factor scores will be stored in the scores element of the returned list
+kahanefascores <- data.frame(Kahanefa$scores) %>%
+  rename(CommEgal = MR1)%>%
+  rename(Hierarchy = MR2)
+
 ```
@@
 
-formice <- codedmodule2[, grep("State|age|urban_rural|gender|caste|religion|Solar|SOLAR|Nuclear|NUCLEAR|Coal|COAL|K_S|K_E|K_H|K_I|WEALTHLIM|MECHANISATION|DECISIONDECEN|INDUSTRYSMALL|ECONOMYLOCAL|ENVOVERDEV|OWNERPUB|OWNERREG|DECISIONCEN|INDUSTRYLARGE|ECONOMYGLOBAL|OWNERPVT|OWNERNOREG", names(codedmodule2))]%>%
-        dplyr::select(-c("Language", "Risky_INDSolar", "Ben_INDSolar", "religiontext"))
+library(psych)
+library(tidyverse)
 
-#dplyr:: select(starts_with (c("State", "age", "urban_rural", "gender", "caste", "religion","Risky_Solar", "Risky_Nuclear", "Risky_Coal", "Ben_Solar","Ben_Nuclear","Ben_Coal","K_S","K_E","K_H","K_I", "DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE","DEV", "PROSPER", "RELY", "WEALTHLIM", "MECHANISATION", "DECISIONDECEN", "INDUSTRYSMALL", "ECONOMYLOCAL", "ENVOVERDEV", "OWNERPUB", "OWNERREG", "DECISIONCEN","INDUSTRYLARGE","ECONOMYGLOBAL","OWNERPVT","OWNERNOREG" )))
+ecopolall <- codedmodule2 %>%
+        dplyr::select("WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR")
 
-library(dplyr)
+# running EFA using psych package
 
-formice <- formice %>%
-  mutate(across(Risky_Solar:age, ~factor(.x, ordered = TRUE)))%>%
-  mutate(across(urban_rural:religion, ~factor(.x, ordered = FALSE)))%>%
-  mutate(across(State, ~factor(.x, ordered = FALSE)))
+ecopolall2.fa <- fa(ecopolall, nfactors = 2, rotate = "varimax")
 
-str(formice)
-summary(formice)
+print.psych(ecopolall2.fa, sort = TRUE)
+
+# the two factors make more sense - 1) people centered development 2) nationalist development
+# So I am going to extract factor scores and bind them to the dataset
+
+ecopolall_scores <- psych::factor.scores(ecopolall, ecopolall2.fa)
+
+# The factor scores will be stored in the scores element of the returned list
+scores1 <- data.frame(ecopolall_scores$scores) %>%
+  rename(Pdevelop = MR1)%>%
+  rename(Ndevelop = MR2)
+
+#binding factor scores to the dataset
+
+premice <- cbind (formice1, kahanefascores, scores1) %>%
+          dplyr::select(-c(DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE, ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV, OWNERPVT, OWNERPUB, OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION, DISPLACESOLAR, POLLUTESOLAR, HEALTHSOLAR, JOBSSOLAR, BEAUTYSOLAR, PRIDESOLAR, NPRIDESOLAR, DEVSOLAR, PROSPERSOLAR, RELYSOLAR, DISPLACECOAL, POLLUTECOAL, HEALTHCOAL, JOBSCOAL, BEAUTYCOAL, PRIDECOAL, NPRIDECOAL, DEVCOAL, PROSPERCOAL, RELYCOAL))
 
@@
 
-## Mifa dor Kahan scale 
-```{r, echo =FALSE}
-library(mifa)
-library(mice)
-library(psych)
+```{r}
+# conducting mice
 
- #cov_vars = -c(State, Risky_Solar, Risky_Nuclear, Risky_Coal, Ben_Solar, Ben_Nuclear, Ben_Coal, DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE, ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV, OWNERPVT, OWNERPUB, OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION, DISPLACESOLAR, POLLUTESOLAR, HEALTHSOLAR, JOBSSOLAR, BEAUTYSOLAR, PRIDESOLAR, NPRIDESOLAR, DEVSOLAR, PROSPERSOLAR, RELYSOLAR, DISPLACECOAL, POLLUTECOAL, HEALTHCOAL, JOBSCOAL, BEAUTYCOAL, PRIDECOAL, NPRIDECOAL, DEVCOAL, PROSPERCOAL, RELYCOAL, DISPLACENUCLEAR, POLLUTENUCLEAR, HEALTHNUCLEAR, JOBSNUCLEAR, BEAUTYNUCLEAR, PRIDENUCLEAR, NPRIDENUCLEAR, DEVNUCLEAR, PROSPERNUCLEAR, RELYNUCLEAR, age, urban_rural, gender, caste, religion),
+postmice <- mice(premice, m =5, maxit =5,  seed = 420, print = FALSE)
 
-kahanall <- codedmodule2 %>%
-          dplyr::select(c(starts_with("K_")))
+summary(postmice)
 
-mikahan <- mifa(data= kahanall,
-                cov_vars = everything(),
-                n_pc= 2:4,
-                ci = "fieller", 
-                n_boot=1000,
-                print = FALSE,
-                progress= TRUE, 
-                seed = 427,)
+complete(postmice)
 
-mikahan
+fit <- with(postmice, lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State+ CommEgal + Hierarchy + Pdevelop + Ndevelop))
 
-library(psych)
-
-fit <- psych::fa(mikahan$cov_combined, nfactors = 2, rotate = "varimax")
-
-print.psych(fit, sort= TRUE, cut= 0.4)
-
-data_imp <- mice::complete(mice::mice(kahanall, 1, print = FALSE))
-
-fct_scores <- data.frame(factor.scores(data_imp[, 1:12], fit)$scores)
+summary(pool(fit))
 
@@
 
-#checking imputations: Kahan scale
-
 ```{r}
-orgscores <- data.frame(kahanefascores)
-
-summary(mikahan)
-names(mikahan)
-
-mikahan$mids
-
-complete_data_first <- complete(mikahan$mids, 1)
-
-summary(complete_data_first)
-
-complete_data_2 <- complete(mikahan$mids, 2)
-
-summary(complete_data_2)
-
-complete_data_3 <- complete(mikahan$mids, 3)
-
-summary(complete_data_3)
-
-complete_data_4 <- complete(mikahan$mids, 4)
-
-summary(complete_data_4)
-
-complete_data_5 <- complete(mikahan$mids, 5)
-
-summary(complete_data_5)
-```
-
-## Distribution check: kahan Scale
-
-```{r}
-# Add an identifier column to each dataset
-fct_scores$Dataset <- 'fct_scores'
-orgscores$Dataset <- 'orgscores'
-
-# Combine the datasets for plotting
-combined_data <- rbind(fct_scores, orgscores)
-
-# Select only necessary columns (assuming 'Index' isn't needed anymore)
-combined_data <- combined_data[, c("MR1", "MR2", "Dataset")]
-
-ggplot(combined_data, aes(x = Dataset, y = MR1, fill = Dataset)) +
-  geom_boxplot() +
-  geom_jitter(width = 0.2, aes(color = Dataset), size = 1.5, alpha = 0.5) +
-  labs(title = "Boxplot of MR1 for Each Dataset", x = "", y = "MR1 Value") +
-  scale_fill_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
-  scale_color_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
-  theme_minimal()
 
 ```
-```{r}
-ggplot(combined_data, aes(x = Dataset, y = MR2, fill = Dataset)) +
-  geom_boxplot() +
-  geom_jitter(width = 0.2, aes(color = Dataset), size = 1.5, alpha = 0.5) +
-  labs(title = "Boxplot of MR2 for Each Dataset with Points", x = "", y = "MR2 Value") +
-  scale_fill_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
-  scale_color_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
-  theme_minimal()
-
-```
-
-# Mifa for new eco-pol value scale : Nuclear energy
-
-```{r}
-
-ecopoln <- codedmodule2[, grep("NUCLEAR|WEALTHLIM|MECHANISATION|DECISIONDECEN|INDUSTRYSMALL|ECONOMYLOCAL|ENVOVERDEV|OWNERPUB|OWNERREG|DECISIONCEN|INDUSTRYLARGE|ECONOMYGLOBAL|OWNERPVT|OWNERNOREG", names(codedmodule2))]
-
-miecopol <- mifa(data= ecopoln,
-                cov_vars = everything(),
-                n_pc= 2:4,
-                ci = "fieller", 
-                n_boot=1000,
-                print = FALSE,
-                progress= TRUE, 
-                seed = 429,)
-
-miecopol
-
-fit2 <- psych::fa(miecopol$cov_combined, nfactors = 2, rotate = "varimax")
-
-print.psych(fit2, sort= TRUE, cut= 0.4)
-
-data_imp2 <- mice::complete(mice::mice(ecopoln, 1, print = FALSE))
-
-fct_scores2 <- data.frame(factor.scores(data_imp2[, 1:23], fit2)$scores)
-
-```
-
-## Checking imputations : Eco-pol scale
-
-```{r, echo=FALSE}
-
-orgscores <- data.frame(kahanefascores)
-
-summary(miecopol)
-names(miecopol)
-
-miecopol$mids
-
-complete_ecopol_first <- complete(miecopol$mids, 1)
-
-summary(complete_ecopol_first)
-
-complete_ecopol_2 <- complete(miecopol$mids, 2)
-
-summary(complete_ecopol_2)
-
-complete_ecopol_3 <- complete(miecopol$mids, 3)
-
-summary(complete_ecopol_3)
-
-complete_ecopol_4 <- complete(miecopol$mids, 4)
-
-summary(complete_ecopol_4)
-
-complete_ecopol_5 <- complete(miecopol$mids, 5)
-
-summary(complete_ecopol_5)
-```

### 2024-03-10 withmice.Rmd
made lms with mice

--- 2024-03-06 withmice.Rmd
@@
 
+# missing data pattern and MCAR
+
 ```{r, echo=FALSE}
 
-formice <- codedmodule2[, grep("State|age|urban_rural|gender|caste|religion|Solar|SOLAR|Nuclear|NUCLEAR|Coal|COAL|K_S|K_E|K_H|K_I|WEALTHLIM|MECHANISATION|DECISIONDECEN|INDUSTRYSMALL|ECONOMYLOCAL|ENVOVERDEV|OWNERPUB|OWNERREG|DECISIONCEN|INDUSTRYLARGE|ECONOMYGLOBAL|OWNERPVT|OWNERNOREG", names(codedmodule2))]%>%
-        dplyr::select(-c("Language", "Risky_INDSolar", "Ben_INDSolar", "religiontext"))
+formice1 <- codedmodule2[, grep("State|age|urban_rural|gender|caste|religion|Solar|SOLAR|Nuclear|NUCLEAR|Coal|COAL|K_S|K_E|K_H|K_I|WEALTHLIM|MECHANISATION|DECISIONDECEN|INDUSTRYSMALL|ECONOMYLOCAL|ENVOVERDEV|OWNERPUB|OWNERREG|DECISIONCEN|INDUSTRYLARGE|ECONOMYGLOBAL|OWNERPVT|OWNERNOREG", names(codedmodule2))]%>%
+        dplyr::select(-c("Language", "Risky_INDSolar", "Ben_INDSolar", "religiontext")) %>%
+          mutate(across(age, ~factor(.x, ordered = TRUE)))%>%  
+          mutate(across(urban_rural:religion, ~factor(.x, ordered = FALSE)))%>%
+          mutate(across(State, ~factor(.x, ordered = FALSE))) %>%
+          mutate(Uppercaste = ifelse(caste %in% c('Brahmin', 'General'), 1, 0)) %>%
+          mutate(Male = ifelse(gender == 'Male', 1, 0))%>%
+          mutate(Hindu = ifelse(religion == 'Hinduism', 1, 0))%>%
+           mutate(Age = case_when(
+                                  age == "18-24 years old" ~ 1,
+                                  age == "25-34 years old" ~ 2,
+                                  age == "35-44 years old" ~ 3,
+                                  age == "45-54 years old" ~ 4,
+                                  age == "55-64 years old" ~ 5,
+                                  age == "65-74 years old" ~ 6,
+                                  age == "75 years or older" ~ 7))
 
@@
 
-formice <- formice %>%
+formice <- formice1 %>%
   mutate(across(Risky_Solar:age, ~factor(.x, ordered = TRUE)))%>%
@@
 
-str(formice)
-summary(formice)
+#str(formice)
+#summary(formice)
+
+# litte's MCAR test
+
+mcar_test(data=formice)
+
+# p value = 1, which means MAR condition is met.
 
@@
 
-## Mifa dor Kahan scale 
+# mice on entire dataset
+
+```{r, echo=FALSE}
+
+#str(formice1)
+
+#formice1.imp <- mice(formice1, m =5, maxit =5,  seed = 430, print = TRUE)
+
+#formice1.imp$chainMean
+
+#plot(formice1.imp)
+
+```
+
+# Diagnostic checking
+```{r, echo= FALSE}
+
+formice1.imp$imp$Risky_Nuclear
+
+complete(formice1.imp)
+
+library(mice)
+
+# Select the variables you want to plot
+selected_vars <- c("Risky_Nuclear", "Risky_Solar", "Risky_Coal")
+
+# Use stripplot to plot only the selected variables
+
+stripplot(formice1.imp, scales = list(x = list(relation = "free")),layout = c(3, 1), pch = 20, cex = 1.2)
+
+```
+
+# Density plot - entire dataset 
+```{r, echo=FALSE}
+
+densityplot(formice1.imp, scales = list(x = list(relation = "free")), layout = c(5, 1))
+
+```
+
+# propensity score check imputations
+
+```{r}
+
+formice1.imp
+#hc.na <- is.na(boys$hc)
+
+#fit.hc <- with(imp.kendall, glm(hc.na ~ age + wgt + hgt + reg,
+#family = binomial))
+#ps <- rep(rowMeans(sapply(fit.hc$analyses, fitted.values)), 6)
+```
+
+# Checking MAR condition and missing data pattern for the Kahan Scale.
+```{r, echo=FALSE}
+
+kahanall <- codedmodule2 %>%
+          dplyr::select(c(starts_with("K_"), "age", "gender", "caste", "State", "urban_rural", "religion")) %>%
+          mutate(across(age:religion, ~factor(.x, ordered = FALSE)))
+
+md.pattern(kahanall) #the variables with missing values: K_SHARM K_IPROTECT K_IPRIVACY K_SPROTECT K_SLIMCHOI K_IINTRFER K_HEQUAL K_HREVDIS1
+
+mcar_test(data=kahanall) # p values is less than 0.05 - the condition for MCAR is not met
+
+# dataset with missing variables to compare and test group comaprisons
+
+MARkahan <- codedmodule2 %>%
+          dplyr::select(c("K_SHARM", "K_IPROTECT", "K_IPRIVACY", "K_SPROTECT", "K_SLIMCHOI", "K_IINTRFER",  "K_HEQUAL", "K_HREVDIS1" , "age", "gender", "caste", "State", "urban_rural", "religion"))
+
+MARkahan$K_SHARM_MAR <- MARkahan$K_SHARM
+
+MARkahan$K_IPROTECT_MAR <- MARkahan$K_IPROTECT
+
+MARkahan$K_SPROTECT_MAR <- MARkahan$K_SPROTECT
+
+MARkahan$K_SLIMCHOI_MAR <- MARkahan$K_SLIMCHOI
+
+library(finalfit)
+
+# "K_SHARM" = "(C)Sometimes the government needs to make laws that keep people from hurting themselves.",
+explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
+dependent = "K_SHARM_MAR"
+MARkahan %>% 
+  missing_compare(dependent, explanatory) %>% 
+    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
+        caption = "comparisons between values of responders (Not missing) and 
+        non-responders (Missing) on the K_SHARM variable.")
+
+#   "K_IPROTECT" = "(I)It’s not the government’s business to try to protect people from themselves."
+explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
+dependent = "K_IPROTECT_MAR"
+MARkahan %>% 
+  missing_compare(dependent, explanatory) %>% 
+    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
+        caption = "comparisons between values of responders (Not missing) and 
+        non-responders (Missing) on the K_IPROTECT variable.")
+
+#  "K_SPROTECT" = "(C)The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.",
+explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
+dependent = "K_SPROTECT_MAR"
+MARkahan %>% 
+  missing_compare(dependent, explanatory) %>% 
+    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
+        caption = "comparisons between values of responders (Not missing) and 
+        non-responders (Missing) on the K_SPROTECT variable.")
+
+#  "K_SLIMCHOI" = "(C)The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.",
+explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
+dependent = "K_SLIMCHOI_MAR"
+MARkahan %>% 
+  missing_compare(dependent, explanatory) %>% 
+    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
+        caption = "comparisons between values of responders (Not missing) and 
+        non-responders (Missing) on the K_SPROTECT variable.")
+
+```
+
+## Mifa for Kahan scale 
 ```{r, echo =FALSE}
+
 library(mifa)
@@
 
-kahanall <- codedmodule2 %>%
-          dplyr::select(c(starts_with("K_")))
-
 mikahan <- mifa(data= kahanall,
-                cov_vars = everything(),
+                cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
+                m = 5,
                 n_pc= 2:4,
@@
 
+```
+
+# checking merging of imputations  : kahan scale
+
+```{r}
+
+kahan_imp <- mice(kahanall, m =5, maxit =30,  seed = 427, print = TRUE)
+
+kahan_imp$chainMean
+
 data_imp <- mice::complete(mice::mice(kahanall, 1, print = FALSE))
@@
 
+plot(kahan_imp)
+
 ```
 
-#checking imputations: Kahan scale
+#checking imputations: Kahan scale - are values plausible ?
 
-```{r}
+yes all value are whole numbers between 1 and 5
+
+```{r, echo=FALSE}
+
 orgscores <- data.frame(kahanefascores)
@@
 summary(mikahan)
+
+str(data_imp)
 names(mikahan)
@@
 
-```{r}
+```{r, echo = False }
+
+densityplot(kahan_imp, scales = list(x = list(relation = "free")), layout = c(5, 1))
+
+```
+
+```{r, echo=FALSE}
 # Add an identifier column to each dataset
-fct_scores$Dataset <- 'fct_scores'
+fct_scores$Dataset <- 'impscores'
 orgscores$Dataset <- 'orgscores'
@@
 
-ggplot(combined_data, aes(x = Dataset, y = MR1, fill = Dataset)) +
-  geom_boxplot() +
-  geom_jitter(width = 0.2, aes(color = Dataset), size = 1.5, alpha = 0.5) +
-  labs(title = "Boxplot of MR1 for Each Dataset", x = "", y = "MR1 Value") +
-  scale_fill_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
-  scale_color_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
+ggplot(combined_data, aes(x = MR1, color = Dataset)) +
+  geom_density(fill = NA, alpha = 0.5) +
+  labs(title = "Density Plot of Hierachy- Egalitarianism for Each Dataset", x = "HE Value", y = "Density") +
+  scale_color_manual(values = c("impscores" = "blue", "orgscores" = "red")) +
   theme_minimal()
@@
 ```
+
 ```{r}
-ggplot(combined_data, aes(x = Dataset, y = MR2, fill = Dataset)) +
-  geom_boxplot() +
-  geom_jitter(width = 0.2, aes(color = Dataset), size = 1.5, alpha = 0.5) +
-  labs(title = "Boxplot of MR2 for Each Dataset with Points", x = "", y = "MR2 Value") +
-  scale_fill_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
-  scale_color_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
+ggplot(combined_data, aes(x = MR2, color = Dataset)) +
+  geom_density(fill = NA, alpha = 0.5) +
+  labs(title = "Density Plot of Communitarianism for Each Dataset", x = "Communitarianism Value", y = "Density") +
+  scale_color_manual(values = c("impscores" = "blue", "orgscores" = "red")) +
   theme_minimal()
+
+```
+
+# ecopol scale - checking MAR
+
+```{r}
+
+ecopoln <- formice1 %>%
+  dplyr::select(
+    DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE,
+    ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV, OWNERPVT, OWNERPUB,
+    OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION,
+    DISPLACENUCLEAR,  POLLUTENUCLEAR, HEALTHNUCLEAR, JOBSNUCLEAR, BEAUTYNUCLEAR,
+    PRIDENUCLEAR, NPRIDENUCLEAR, DEVNUCLEAR, PROSPERNUCLEAR,
+    RELYNUCLEAR,age, urban_rural, gender, caste, religion, State
+  )
+
+md.pattern(ecopoln) #the variables with missing values: PRIDENUCLEAR PROSPERNUCLEAR JOBSNUCLEAR HEALTHNUCLEAR BEAUTYNUCLEAR POLLUTENUCLEAR DISPLACENUCLEAR RELYNUCLEAR
+
+mcar_test(data=ecopoln) # p values is less than 0.76 - the condition for MCAR is met
+
+# dataset with missing variables to compare and test group comaprisons
+
+MARecopol <- codedmodule2 %>%
+          dplyr::select(c(DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE,
+    ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV, OWNERPVT, OWNERPUB,
+    OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION,
+    DISPLACENUCLEAR,  POLLUTENUCLEAR, HEALTHNUCLEAR, JOBSNUCLEAR, BEAUTYNUCLEAR,
+    PRIDENUCLEAR, NPRIDENUCLEAR, DEVNUCLEAR, PROSPERNUCLEAR,
+    RELYNUCLEAR,age, urban_rural, gender, caste, religion, State))
+
+MARecopol$JOBSNUCLEAR_MAR <- MARecopol$JOBSNUCLEAR
+
+MARecopol$PRIDENUCLEAR_MAR <- MARecopol$PRIDENUCLEAR
+
+library(finalfit)
+
+# JOBSNUCLEAR
+explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
+dependent = "JOBSNUCLEAR_MAR"
+MARecopol %>% 
+  missing_compare(dependent, explanatory) %>% 
+    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
+        caption = "comparisons between values of responders (Not missing) and 
+        non-responders (Missing) on the JOBSNUCLEAR variable.")
+
+# PRIDENUCLEAR
+explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
+dependent = "PRIDENUCLEAR_MAR"
+MARecopol %>% 
+  missing_compare(dependent, explanatory) %>% 
+    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
+        caption = "comparisons between values of responders (Not missing) and 
+        non-responders (Missing) on the PRIDENUCLEAR variable.")
 
@@
 
-ecopoln <- codedmodule2[, grep("NUCLEAR|WEALTHLIM|MECHANISATION|DECISIONDECEN|INDUSTRYSMALL|ECONOMYLOCAL|ENVOVERDEV|OWNERPUB|OWNERREG|DECISIONCEN|INDUSTRYLARGE|ECONOMYGLOBAL|OWNERPVT|OWNERNOREG", names(codedmodule2))]
+#ecopoln <- codedmodule2[, grep("NUCLEAR|WEALTHLIM|MECHANISATION|DECISIONDECEN|INDUSTRYSMALL|ECONOMYLOCAL|ENVOVERDEV|OWNERPUB|OWNERREG|DECISIONCEN|INDUSTRYLARGE|ECONOMYGLOBAL|OWNERPVT|OWNERNOREG|", names(codedmodule2))]
+
+summary(formice1)
 
 miecopol <- mifa(data= ecopoln,
-                cov_vars = everything(),
+                cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
                 n_pc= 2:4,
@@
                 n_boot=1000,
-                print = FALSE,
+                print = TRUE,
                 progress= TRUE, 
@@
 
+imputations are pluasible- all natural numbers between 1 and 5
+
 ```{r, echo=FALSE}
-
-orgscores <- data.frame(kahanefascores)
 
@@
 summary(complete_ecopol_5)
+
 ```
+
+# Density plots - 2 factors from eco-pol scale 
+```{r}
+
+nscores <- data.frame(ecopolall_scores$scores)
+
+# Add an identifier column to each dataset
+fct_scores2$Dataset <- 'imputed'
+nscores$Dataset <- 'original'
+
+# Combine the datasets for plotting
+compare2 <- rbind(fct_scores2, nscores)
+
+# Select only necessary columns (assuming 'Index' isn't needed anymore)
+compare2<- compare2[, c("MR1", "MR2", "Dataset")]
+
+```
+
+```{r}
+
+library(ggplot2)
+
+ggplot(compare2, aes(x = MR2, color = Dataset)) +
+  geom_density(fill = NA, alpha = 0.5) +
+  labs(title = "Density Plot of MR2 for Each Dataset", x = "MR2 Value", y = "Density") +
+  scale_color_manual(values = c("imputed" = "blue", "original" = "red")) +
+  theme_minimal()
+
+```
+
+# Binding imputed values to formice dataset
+
+```{r, echo = FALSE}
+
+# binding the imputed  factor analysis scores for kahan scale and eco-pol value scale to the larger dataset codedmodule2
+
+ecopolnuclear <- fct_scores2 %>%
+  rename(Ndevelop = MR1, Pdevelop = MR2)
+
+kahannuclear <- fct_scores%>%
+  rename(Hierarchy_Egalitarian = MR1, Communitarian = MR2)
+
+formice1
+
+allformice<- cbind(formice1,ecopolnuclear, kahannuclear)
+
+#summary(formice)
+
+#method_list <- rep("polr", ncol(formice))
+#names(method_list) <- colnames(formice)
+
+#skip_vars <- c("age",  "urban_rural", "gender",  "caste", "religion", "K_ERADEQ2","K_ERADEQ1", "INDUSTRYSMALL","INDUSTRYLARGE","WEALTHLIM", "MECHANISATION", "State","K_IINTRFER",  "K_IPRIVACY",  "K_SHARM",  "K_IPROTECT",  "K_SLIMCHOI",  "K_SPROTECT",  "K_HEQUAL",  "K_HREVDIS1",  "K_EDISCRIM",    "K_EWEALTH",  "DECISIONDECEN",  "DECISIONCEN",     "ECONOMYLOCAL",  "ECONOMYGLOBAL",  "ENVOVERDEV",  "OWNERPVT",  "OWNERPUB",  "OWNERREG",  "DISPLACESOLAR",  "POLLUTESOLAR",  "HEALTHSOLAR",  "JOBSSOLAR",  "BEAUTYSOLAR",  "PRIDESOLAR",  "NPRIDESOLAR",  "DEVSOLAR",  "PROSPERSOLAR",  "RELYSOLAR",  "DISPLACECOAL",  "POLLUTECOAL",  "HEALTHCOAL",  "JOBSCOAL",  "BEAUTYCOAL",  "PRIDECOAL",  "NPRIDECOAL",  "DEVCOAL",  "PROSPERCOAL",  "RELYCOAL",  "DISPLACENUCLEAR",  "POLLUTENUCLEAR",  "HEALTHNUCLEAR",  "JOBSNUCLEAR",  "BEAUTYNUCLEAR",  "PRIDENUCLEAR",  "NPRIDENUCLEAR",  "DEVNUCLEAR",  "PROSPERNUCLEAR",  "RELYNUCLEAR", "OWNERNOREG")
+
+#Set method to "" for variables to skip
+#method_list[skip_vars] <- ""
+
+#nuclear_imp1 <- mice(formice, method=method_list, maxit = 5, m =5,  seed = 123, print = TRUE)
+
+print(nuclear_imp1)
+summary(nuclear_imp1)
+nuclear_imp1$imp$Risky_Nuclear
+
+```
+
+```{r, echo=FALSE}
+
+str(allformice)
+library(mice)
+library(dplyr)
+
+# Initialize the mice process to create the predictor matrix
+ini <- mice(allformice, maxit = 0, pri = FALSE)
+
+# Extract the predictor matrix from the initialized object
+pred <- ini$predictorMatrix
+
+# Set the columns for "Uppercaste", "Male", "Hindu", and "Age" to 0
+pred[, "Uppercaste"] <- 0
+pred[, "Male"] <- 0
+pred[, "Hindu"] <- 0
+pred[, "Age"] <- 0
+pred[, "Ndevelop"] <- 0
+pred[, "Pdevelop"] <- 0
+pred[, "Hierarchy_Egalitarian"] <- 0
+pred[, "Communitarian"] <- 0
+# Identify columns that start with "K_" and set them to 0
+k_columns <- grep("^K_", colnames(formice1))
+pred[, k_columns] <- 0
+
+# Perform the mice imputation with the updated predictor matrix
+allformice.imp <- mice(allformice, m = 5, maxit = 10, predictorMatrix = pred, seed = 430, print = TRUE)
+
+summary(allformice.imp)
+allformice.imp$chainMean
+
+plot(allformice.imp)
+
+```
+
+```{r}
+
+nuclearfit1 <- with(allformice.imp, lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age))
+
+nuclearfit2 <- with(allformice.imp, lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State))
+
+nuclearfit3 <- with(allformice.imp, lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State+ Communitarian + Hierarchy_Egalitarian))
+
+nuclearfit4 <- with(allformice.imp, lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State+ Communitarian + Hierarchy_Egalitarian + Pdevelop + Ndevelop))
+
+summary(pool(nuclearfit1))
+summary(pool(nuclearfit2))
+summary(pool(nuclearfit3))
+summary(pool(nuclearfit4))
+
+```
+
+# LM with demographic variables
+
+```{r}
+
+# The pool() function from the mice package creates a list containing the results,
+# so we need to access the summary of the model directly.
+
+pooled_fit <- pool(nuclearfit1)
+
+pooled_summary <- summary(pooled_fit)
+
+coefficients_df <- pooled_summary
+# To ensure the numeric values are rounded to two decimal places, you can use:
+coefficients_df <- round(coefficients_df[, -1], 2)  # Skipping the first column as it's factors (term names)
+coefficients_df$term <- pooled_summary$term  # Adding back the unrounded terms
+
+# Print the dataframe
+data.frame(coefficients_df) %>%
+  dplyr::select(term, estimate, std.error, statistic, df, p.value)
+```
+
+# LM with demographic variables and State
+
+```{r}
+
+# The pool() function from the mice package creates a list containing the results,
+# so we need to access the summary of the model directly.
+
+pooled_fit2 <- pool(nuclearfit2)
+
+pooled_summary2 <- summary(pooled_fit2)
+
+coefficients_df2 <- pooled_summary2
+# To ensure the numeric values are rounded to two decimal places, you can use:
+coefficients_df2 <- round(coefficients_df2[, -1], 2)  # Skipping the first column as it's factors (term names)
+coefficients_df2$term <- pooled_summary2$term  # Adding back the unrounded terms
+
+# Print the dataframe
+data.frame(coefficients_df2) %>%
+  dplyr::select(term, estimate, std.error, statistic, df, p.value)
+```
+
+# LM with demographic variables and State
+
+```{r}
+# The pool() function from the mice package creates a list containing the results,
+# so we need to access the summary of the model directly.
+
+pooled_fit3 <- pool(nuclearfit3)
+
+pooled_summary3 <- summary(pooled_fit3)
+
+coefficients_df3 <- pooled_summary3
+# To ensure the numeric values are rounded to two decimal places, you can use:
+coefficients_df3 <- round(coefficients_df3[, -1], 2)  # Skipping the first column as it's factors (term names)
+coefficients_df3$term <- pooled_summary3$term  # Adding back the unrounded terms
+
+# Print the dataframe
+data.frame(coefficients_df3) %>%
+  dplyr::select(term, estimate, std.error, statistic, df, p.value)
+```
+
+# LM with demographic variables and State
+
+```{r}
+
+# The pool() function from the mice package creates a list containing the results,
+# so we need to access the summary of the model directly.
+
+pooled_fit4 <- pool(nuclearfit4)
+
+pooled_summary4 <- summary(pooled_fit4)
+
+coefficients_df4 <- pooled_summary4
+# To ensure the numeric values are rounded to two decimal places, you can use:
+coefficients_df4 <- round(coefficients_df4[, -1], 2)  # Skipping the first column as it's factors (term names)
+coefficients_df4$term <- pooled_summary4$term  # Adding back the unrounded terms
+
+# Print the dataframe
+data.frame(coefficients_df4) %>%
+  dplyr::select(term, estimate, std.error, statistic, df, p.value)
+```

### 2024-03-13 withmice.Rmd
making pretty Lm tables

--- 2024-03-07 withmice.Rmd
@@
 title: "models with mice"
+header-includes:
+- \usepackage{pdflscape}
+- \newcommand{\blandscape}{\begin{landscape}}
+- \newcommand{\elandscape}{\end{landscape}}
 output:
@@
     keep_tex: yes
-  header-includes:
-  - \usepackage{dcolumn}
-  - \usepackage{array}
-  - "\\usepackage{placeins}"
   keep_md: yes
@@
 
-## Can do something with accept, reject and reluctantly accept.
+# Can do something with accept, reject and reluctantly accept.
 
-```{r}
+```{r, echo=FALSE}
 
@@
 
+# missing data pattern and MCAR
+
 ```{r, echo=FALSE}
 
-formice <- codedmodule2[, grep("State|age|urban_rural|gender|caste|religion|Solar|SOLAR|Nuclear|NUCLEAR|Coal|COAL|K_S|K_E|K_H|K_I|WEALTHLIM|MECHANISATION|DECISIONDECEN|INDUSTRYSMALL|ECONOMYLOCAL|ENVOVERDEV|OWNERPUB|OWNERREG|DECISIONCEN|INDUSTRYLARGE|ECONOMYGLOBAL|OWNERPVT|OWNERNOREG", names(codedmodule2))]%>%
-        dplyr::select(-c("Language", "Risky_INDSolar", "Ben_INDSolar", "religiontext"))
+formice1 <- codedmodule2[, grep("State|age|urban_rural|gender|caste|religion|Solar|SOLAR|Nuclear|NUCLEAR|Coal|COAL|K_S|K_E|K_H|K_I|WEALTHLIM|MECHANISATION|DECISIONDECEN|INDUSTRYSMALL|ECONOMYLOCAL|ENVOVERDEV|DEVOVERENV|OWNERPUB|OWNERREG|DECISIONCEN|INDUSTRYLARGE|ECONOMYGLOBAL|OWNERPVT|OWNERNOREG", names(codedmodule2))]%>%
+        dplyr::select(-c("Language", "Risky_INDSolar", "Ben_INDSolar", "religiontext")) %>%
+          mutate(across(age, ~factor(.x, ordered = TRUE)))%>%  
+          mutate(across(urban_rural:religion, ~factor(.x, ordered = FALSE)))%>%
+          mutate(across(State, ~factor(.x, ordered = FALSE))) %>%
+          mutate(Uppercaste = ifelse(caste %in% c('Brahmin', 'General'), 1, 0)) %>%
+          mutate(Male = ifelse(gender == 'Male', 1, 0))%>%
+          mutate(Hindu = ifelse(religion == 'Hinduism', 1, 0))%>%
+           mutate(Age = case_when(
+                                  age == "18-24 years old" ~ 1,
+                                  age == "25-34 years old" ~ 2,
+                                  age == "35-44 years old" ~ 3,
+                                  age == "45-54 years old" ~ 4,
+                                  age == "55-64 years old" ~ 5,
+                                  age == "65-74 years old" ~ 6,
+                                  age == "75 years or older" ~ 7))
 
@@
 
-str(formice)
+#str(formice)
 summary(formice)
+
+# litte's MCAR test
+
+mcar_test(data= codedmodule2)
+
+# p value = 1, which means MAR condition is met.
+
+```
+
+# Kahan scale: MAR condition and missing data pattern 
+```{r, echo=FALSE}
+
+kahanall <- codedmodule2 %>%
+          dplyr::select(c(starts_with("K_"), "age", "gender", "caste", "State", "urban_rural", "religion")) %>%
+          mutate(across(gender:religion, ~factor(.x, ordered = FALSE))) %>%
+          mutate(across(age, ~factor(.x, ordered = TRUE)))
+
+str(kahanall)
+
+md.pattern(kahanall) #the variables with missing values: K_SHARM K_IPROTECT K_IPRIVACY K_SPROTECT K_SLIMCHOI K_IINTRFER K_HEQUAL K_HREVDIS1
+
+mcar_test(data=kahanall) # p values is less than 0.05 - the condition for MCAR is not met
+
+# dataset with missing variables to compare and test group comaprisons
+
+MARkahan <- codedmodule2 %>%
+          dplyr::select(c("K_SHARM", "K_IPROTECT", "K_IPRIVACY", "K_SPROTECT", "K_SLIMCHOI", "K_IINTRFER",  "K_HEQUAL", "K_HREVDIS1" , "age", "gender", "caste", "State", "urban_rural", "religion"))
+
+MARkahan$K_SHARM_MAR <- MARkahan$K_SHARM
+
+MARkahan$K_IPROTECT_MAR <- MARkahan$K_IPROTECT
+
+MARkahan$K_SPROTECT_MAR <- MARkahan$K_SPROTECT
+
+MARkahan$K_SLIMCHOI_MAR <- MARkahan$K_SLIMCHOI
+
+library(finalfit)
+
+# "K_SHARM" = "(C)Sometimes the government needs to make laws that keep people from hurting themselves.",
+explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
+dependent = "K_SHARM_MAR"
+MARkahan %>% 
+  missing_compare(dependent, explanatory) %>% 
+    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
+        caption = "comparisons between values of responders (Not missing) and 
+        non-responders (Missing) on the K_SHARM variable.")
+
+#   "K_IPROTECT" = "(I)It’s not the government’s business to try to protect people from themselves."
+explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
+dependent = "K_IPROTECT_MAR"
+MARkahan %>% 
+  missing_compare(dependent, explanatory) %>% 
+    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
+        caption = "comparisons between values of responders (Not missing) and 
+        non-responders (Missing) on the K_IPROTECT variable.")
+
+#  "K_SPROTECT" = "(C)The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.",
+explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
+dependent = "K_SPROTECT_MAR"
+MARkahan %>% 
+  missing_compare(dependent, explanatory) %>% 
+    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
+        caption = "comparisons between values of responders (Not missing) and 
+        non-responders (Missing) on the K_SPROTECT variable.")
+
+#  "K_SLIMCHOI" = "(C)The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.",
+explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
+dependent = "K_SLIMCHOI_MAR"
+MARkahan %>% 
+  missing_compare(dependent, explanatory) %>% 
+    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
+        caption = "comparisons between values of responders (Not missing) and 
+        non-responders (Missing) on the K_SPROTECT variable.")
 
@@
 ```{r, echo =FALSE}
+
 library(mifa)
@@
 
- #cov_vars = -c(State, Risky_Solar, Risky_Nuclear, Risky_Coal, Ben_Solar, Ben_Nuclear, Ben_Coal, DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE, ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV, OWNERPVT, OWNERPUB, OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION, DISPLACESOLAR, POLLUTESOLAR, HEALTHSOLAR, JOBSSOLAR, BEAUTYSOLAR, PRIDESOLAR, NPRIDESOLAR, DEVSOLAR, PROSPERSOLAR, RELYSOLAR, DISPLACECOAL, POLLUTECOAL, HEALTHCOAL, JOBSCOAL, BEAUTYCOAL, PRIDECOAL, NPRIDECOAL, DEVCOAL, PROSPERCOAL, RELYCOAL, DISPLACENUCLEAR, POLLUTENUCLEAR, HEALTHNUCLEAR, JOBSNUCLEAR, BEAUTYNUCLEAR, PRIDENUCLEAR, NPRIDENUCLEAR, DEVNUCLEAR, PROSPERNUCLEAR, RELYNUCLEAR, age, urban_rural, gender, caste, religion),
-
-kahanall <- codedmodule2 %>%
-          dplyr::select(c(starts_with("K_")))
-
 mikahan <- mifa(data= kahanall,
-                cov_vars = everything(),
+                cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
+                m = 50,
                 n_pc= 2:4,
@@
 
+```
+
+## checking merging of imputations  : kahan scale
+
+```{r, echo=FALSE}
+
+kahan_imp <- mice(kahanall, m =5, maxit =30,  seed = 427, print = FALSE)
+
+kahan_imp$chainMean
+
+```
+
+#Kahan Factor scores: mean across all imputations
+
+```{r, echo=FALSE}
+
+kahanallscores <- mice::complete(mice::mice(kahanall, m = 5, seed = 427, print = FALSE), "broad")
+
+kahanallscores <- kahanallscores %>%dplyr::select(-(contains(c("age", "urban_rural", "gender","caste","religion", "State"))))
+
+str(kahanallscores)
+
+nkahanall <- kahanallscores %>%
+  rowwise() %>%
+  mutate( K_EWEALTH_mean = mean(c_across(starts_with("K_EWEALTH"))),
+    K_IINTRFER_mean = mean(c_across(starts_with("K_IINTRFER"))),
+    K_IPRIVACY_mean = mean(c_across(starts_with("K_IPRIVACY"))),
+    K_SHARM_mean = mean(c_across(starts_with("K_SHARM"))),
+    K_IPROTECT_mean = mean(c_across(starts_with("K_IPROTECT"))),
+    K_SLIMCHOI_mean = mean(c_across(starts_with("K_SLIMCHOI"))),
+    K_SPROTECT_mean = mean(c_across(starts_with("K_SPROTECT"))),
+    K_HEQUAL_mean = mean(c_across(starts_with("K_HEQUAL"))),
+    K_HREVDIS1_mean = mean(c_across(starts_with("K_HREVDIS1"))),
+    K_EDISCRIM_mean = mean(c_across(starts_with("K_EDISCRIM"))),
+    K_ERADEQ1_mean = mean(c_across(starts_with("K_ERADEQ1"))),
+    K_ERADEQ2_mean = mean(c_across(starts_with("K_ERADEQ2")))
+  ) %>%
+  ungroup()%>%
+  dplyr::select(contains("_mean")) %>%
+   rename_with(~ gsub("_mean$", "", .x))
+
+nkahanfinal <- data.frame(factor.scores(nkahanall[, 1:12], fit)$scores)
+
+```
+
+## Kahan: factor scores from 1st imputed dataset
+```{r, echo=FALSE}
+
+# extracting factor scores from mifa for 1st imputed dataset
+
 data_imp <- mice::complete(mice::mice(kahanall, 1, print = FALSE))
@@
 
+plot(kahan_imp)
+
 ```
 
-#checking imputations: Kahan scale
+## Kahan: factor scores from second imputed dataset
+```{r, echo=FALSE}
 
-```{r}
+data_impk2 <- mice::complete(mice::mice(kahanall, 2, print = FALSE))
 
-orgscores <- data.frame(kahanefascores)
+fct_scoresk2 <- data.frame(factor.scores(data_impk2[, 1:12], fit)$scores)
+
+```
+
+## Kahan: factor scores from third imputed dataset
+```{r, echo=FALSE}
+
+data_impk3 <- mice::complete(mice::mice(kahanall, 3, print = FALSE))
+
+fct_scoresk3 <- data.frame(factor.scores(data_impk3[, 1:12], fit)$scores)
+
+```
+
+## Kahan: factor scores from fourth imputed dataset
+```{r, echo=FALSE}
+
+data_impk4 <- mice::complete(mice::mice(kahanall, 4, print = FALSE))
+
+fct_scoresk4 <- data.frame(factor.scores(data_impk4[, 1:12], fit)$scores)
+
+```
+
+## Kahan: factor scores from fifth imputed dataset
+```{r, echo=FALSE}
+
+data_impk5 <- mice::complete(mice::mice(kahanall, 5, print = FALSE))
+
+fct_scoresk5 <- data.frame(factor.scores(data_impk5[, 1:12], fit)$scores)
+
+```
+
+## are imputations plausible: Kahan scale - are values plausible ?
+
+yes all value are whole numbers between 1 and 5
+
+```{r, echo=FALSE}
 
 summary(mikahan)
+
+str(data_imp)
 names(mikahan)
@@
 
-## Distribution check: kahan Scale
+# Eco-pol scale: MAR condition and missing data pattern
 
-```{r}
-# Add an identifier column to each dataset
-fct_scores$Dataset <- 'fct_scores'
-orgscores$Dataset <- 'orgscores'
+```{r, echo=FALSE}
 
-# Combine the datasets for plotting
-combined_data <- rbind(fct_scores, orgscores)
+ecopoln <- formice1 %>%
+  dplyr::select(
+    DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE,
+    ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV,DEVOVERENV, OWNERPVT, OWNERPUB,
+    OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION,
+    DISPLACENUCLEAR,  POLLUTENUCLEAR, HEALTHNUCLEAR, JOBSNUCLEAR, BEAUTYNUCLEAR,
+    PRIDENUCLEAR, NPRIDENUCLEAR, DEVNUCLEAR, PROSPERNUCLEAR,
+    RELYNUCLEAR,age, urban_rural, gender, caste, religion, State
+  )
 
-# Select only necessary columns (assuming 'Index' isn't needed anymore)
-combined_data <- combined_data[, c("MR1", "MR2", "Dataset")]
+md.pattern(ecopoln) #the variables with missing values: PRIDENUCLEAR PROSPERNUCLEAR JOBSNUCLEAR HEALTHNUCLEAR BEAUTYNUCLEAR POLLUTENUCLEAR DISPLACENUCLEAR RELYNUCLEAR
 
-ggplot(combined_data, aes(x = Dataset, y = MR1, fill = Dataset)) +
-  geom_boxplot() +
-  geom_jitter(width = 0.2, aes(color = Dataset), size = 1.5, alpha = 0.5) +
-  labs(title = "Boxplot of MR1 for Each Dataset", x = "", y = "MR1 Value") +
-  scale_fill_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
-  scale_color_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
-  theme_minimal()
+mcar_test(data=ecopoln) # p values is less than 0.76 - the condition for MCAR is met
 
-```
-```{r}
-ggplot(combined_data, aes(x = Dataset, y = MR2, fill = Dataset)) +
-  geom_boxplot() +
-  geom_jitter(width = 0.2, aes(color = Dataset), size = 1.5, alpha = 0.5) +
-  labs(title = "Boxplot of MR2 for Each Dataset with Points", x = "", y = "MR2 Value") +
-  scale_fill_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
-  scale_color_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
-  theme_minimal()
+# dataset with missing variables to compare and test group comaprisons
 
+MARecopol <- codedmodule2 %>%
+          dplyr::select(c(DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE,
+    ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV, OWNERPVT, OWNERPUB,
+    OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION,
+    DISPLACENUCLEAR,  POLLUTENUCLEAR, HEALTHNUCLEAR, JOBSNUCLEAR, BEAUTYNUCLEAR,
+    PRIDENUCLEAR, NPRIDENUCLEAR, DEVNUCLEAR, PROSPERNUCLEAR,
+    RELYNUCLEAR,age, urban_rural, gender, caste, religion, State))
+
+MARecopol$JOBSNUCLEAR_MAR <- MARecopol$JOBSNUCLEAR
+
+MARecopol$PRIDENUCLEAR_MAR <- MARecopol$PRIDENUCLEAR
+
+library(finalfit)
+
+# JOBSNUCLEAR
+explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
+dependent = "JOBSNUCLEAR_MAR"
+MARecopol %>% 
+  missing_compare(dependent, explanatory) %>% 
+    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
+        caption = "comparisons between values of responders (Not missing) and 
+        non-responders (Missing) on the JOBSNUCLEAR variable.")
+
+# PRIDENUCLEAR
+explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
+dependent = "PRIDENUCLEAR_MAR"
+MARecopol %>% 
+  missing_compare(dependent, explanatory) %>% 
+    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
+        caption = "comparisons between values of responders (Not missing) and 
+        non-responders (Missing) on the PRIDENUCLEAR variable.") 
 ```
 
-# Mifa for new eco-pol value scale : Nuclear energy
+## Mifa for new eco-pol value scale : Nuclear energy
 
-```{r}
-
-ecopoln <- codedmodule2[, grep("NUCLEAR|WEALTHLIM|MECHANISATION|DECISIONDECEN|INDUSTRYSMALL|ECONOMYLOCAL|ENVOVERDEV|OWNERPUB|OWNERREG|DECISIONCEN|INDUSTRYLARGE|ECONOMYGLOBAL|OWNERPVT|OWNERNOREG", names(codedmodule2))]
+```{r, echo=FALSE}
 
 miecopol <- mifa(data= ecopoln,
-                cov_vars = everything(),
+                cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
                 n_pc= 2:4,
@@
 
-fit2 <- psych::fa(miecopol$cov_combined, nfactors = 2, rotate = "varimax")
+ecopolfit2 <- psych::fa(miecopol$cov_combined, nfactors = 2, rotate = "varimax")
 
-print.psych(fit2, sort= TRUE, cut= 0.4)
+print.psych(ecopolfit2, sort= TRUE, cut= 0.4)
+
+```
+
+#Ecopol Factor scores: mean across all imputations
+
+```{r, echo=FALSE}
+
+ecopolallscores <- mice::complete(mice::mice(ecopoln, m = 5, seed = 429, print = FALSE), "broad")
+
+ecopolallscores <- ecopolallscores %>%dplyr::select(-(contains(c("age", "urban_rural", "gender","caste","religion", "State"))))
+
+#str(ecopolallscores)
+
+necopol <- ecopolallscores %>%
+  rowwise() %>%
+  mutate(DEVNUCLEAR_mean = mean(c_across(starts_with("DEVNUCLEAR"))),
+         PROSPERNUCLEAR_mean = mean(c_across(starts_with("PROSPERNUCLEAR"))),
+         NPRIDENUCLEAR_mean = mean(c_across(starts_with("NPRIDENUCLEAR"))),
+         PRIDENUCLEAR_mean = mean(c_across(starts_with("PRIDENUCLEAR"))),
+         JOBSNUCLEAR_mean = mean(c_across(starts_with("JOBSNUCLEAR"))),
+         ECONOMYGLOBAL_mean = mean(c_across(starts_with("ECONOMYGLOBAL"))),
+         WEALTHLIM_mean = mean(c_across(starts_with("WEALTHLIM"))),
+         INDUSTRYLARGE_mean = mean(c_across(starts_with("INDUSTRYLARGE"))),
+         DECISIONCEN_mean = mean(c_across(starts_with("DECISIONCEN"))),
+         MECHANISATION_mean = mean(c_across(starts_with("MECHANISATION"))),
+         OWNERNOREG_mean = mean(c_across(starts_with("OWNERNOREG"))),
+         INDUSTRYSMALL_mean = mean(c_across(starts_with("INDUSTRYSMALL"))),
+         DEVOVERENV_mean = mean(c_across(starts_with("DEVOVERENV"))),
+         OWNERPVT_mean = mean(c_across(starts_with("OWNERPVT"))),
+         RELYNUCLEAR_mean = mean(c_across(starts_with("RELYNUCLEAR"))),
+         BEAUTYNUCLEAR_mean = mean(c_across(starts_with("BEAUTYNUCLEAR"))),
+         HEALTHNUCLEAR_mean = mean(c_across(starts_with("HEALTHNUCLEAR"))),
+         POLLUTENUCLEAR_mean = mean(c_across(starts_with("POLLUTENUCLEAR"))),
+         DISPLACENUCLEAR_mean = mean(c_across(starts_with("DISPLACENUCLEAR"))),
+         ENVOVERDEV_mean = mean(c_across(starts_with("ENVOVERDEV"))),
+         OWNERPUB_mean = mean(c_across(starts_with("OWNERPUB"))),
+         OWNERREG_mean = mean(c_across(starts_with("OWNERREG"))),
+         DECISIONDECEN_mean = mean(c_across(starts_with("DECISIONDECEN"))),
+         ECONOMYLOCAL_mean = mean(c_across(starts_with("ECONOMYLOCAL")))
+  ) %>%
+  ungroup()%>%
+  dplyr::select(contains("_mean")) %>%
+   rename_with(~ gsub("_mean$", "", .x))
+
+necopolfinal <- data.frame(factor.scores(necopol[, 1:24], ecopolfit2)$scores)
+
+```
+
+# Eco-pol: Radar map
+
+```{r, echo=FALSE}
+library(ggplot2)
+library(fmsb)
+
+nrow(ecopolfit2$loadings)
+
+# Extract the loadings
+loadings_matrix4 <- ecopolfit2$loadings[1:24, ]
+
+loadings_df2 <- as.data.frame(as.matrix(loadings_matrix4))
+
+# Adding rownames to the dataframe as a new column
+loadings_df2 <- loadings_df2 %>%
+  rownames_to_column(var = "variable")
+
+# Pivot to longer format first
+long_loadings_df2 <- loadings_df2 %>%
+  pivot_longer(cols = c(MR1, MR2), names_to = "Factors", values_to = "value")
+
+# Pivot the longer format to wide format
+wide_loadings_df2 <- long_loadings_df2 %>%
+  pivot_wider(names_from = variable, values_from = value) %>%
+  mutate(Factors = case_when(
+    Factors == "MR1" ~ "Nationalist Development (Ndevelop)",
+    Factors == "MR2" ~ "People Centered Development (Pdevelop)",
+    TRUE ~ Factors
+  )) %>%
+  column_to_rownames("Factors")
+
+# Define the variable ranges: maximum and minimum
+max_min2 <- data.frame(
+  DEVNUCLEAR = c(0.8, -0.6), PROSPERNUCLEAR = c(0.8, -0.6), NPRIDENUCLEAR = c(0.8, -0.6), PRIDENUCLEAR = c(0.8, -0.6),     JOBSNUCLEAR = c(0.8, -0.6), ECONOMYGLOBAL = c(0.8, -0.6), WEALTHLIM = c(0.8, -0.6), INDUSTRYLARGE = c(0.8, -0.6),   DECISIONCEN = c(0.8, -0.6), MECHANISATION = c(0.8, -0.6), OWNERNOREG = c(0.8, -0.6), INDUSTRYSMALL = c(0.8, -0.6), DEVOVERENV = c(0.8, -0.6), OWNERPVT = c(0.8, -0.6), RELYNUCLEAR = c(0.8, -0.6), BEAUTYNUCLEAR = c(0.8, -0.6), HEALTHNUCLEAR = c(0.8, -0.6), POLLUTENUCLEAR = c(0.8, -0.6), DISPLACENUCLEAR = c(0.8, -0.6), DECISIONDECEN = c(0.8, -0.6),
+ECONOMYLOCAL = c(0.8, -0.6), ENVOVERDEV = c(0.8, -0.6), OWNERPUB = c(0.8, -0.6), OWNERREG = c(0.8, -0.6)   
+)
+rownames(max_min2) <- c("Max", "Min")
+
+# Assuming you have a dataframe 'exam_scores' with matching column names
+# Bind the variable ranges to the data
+
+radar4 <- rbind(max_min2, wide_loadings_df2) %>%
+    rename(
+      "National development(nuclear)" = "DEVNUCLEAR",
+      "Local prosperity(nuclear)" = "PROSPERNUCLEAR",
+      "National pride(nuclear)" = "NPRIDENUCLEAR",
+      "Community pride(nuclear)" = "PRIDENUCLEAR",
+      "Job opportunities(nuclear)" = "JOBSNUCLEAR",
+      "Pro Globaleconomy" = "ECONOMYGLOBAL",
+      "Limits on Wealth " = "WEALTHLIM",
+      "Pro Large Industries" = "INDUSTRYLARGE",
+      "Pro Centralisation" = "DECISIONCEN",
+      "Anti Mechanisation of work" = "MECHANISATION",
+      "Anti Regulations" = "OWNERNOREG",
+      "Anti Large Industries " = "INDUSTRYSMALL",
+      "Development over Environment" = "DEVOVERENV",
+      "Pro Private ownership " = "OWNERPVT",
+      "Reliance on government(nuclear)" = "RELYNUCLEAR",
+      "Spoils Natural Beauty(nuclear)" = "BEAUTYNUCLEAR",
+      "Health risk(nuclear)" = "HEALTHNUCLEAR",
+      "Pollution risk(nuclear) " = "POLLUTENUCLEAR",
+      "Displacement risk(nuclear)" = "DISPLACENUCLEAR",
+      "Environment over Development" = "ENVOVERDEV",
+      "Pro Public ownership" = "OWNERPUB",
+      "Pro Regulations" = "OWNERREG",
+      "Pro Decentralisation" = "DECISIONDECEN",
+      "Pro Localeconomy" = "ECONOMYLOCAL",
+    )
+
+```
+
+```{r, echo=FALSE, fig.width=15, fig.height=7, out.width='70', out.height='70'}
+library(fmsb)
+
+create_beautiful_radarchart <- function(data, color = "#00AFBB", 
+                                        vlabels = colnames(data), vlcex = 0.7,
+                                        caxislabels = NULL, title = NULL, ...){
+  radarchart(
+    data, axistype = 1,
+    # Customize the polygon
+    pcol = color, pfcol = scales::alpha(color, 0.7), plwd = 2, plty = 1,
+    centerzero=FALSE,
+    # Customize the grid
+    cglcol = "black", cglty = 1, cglwd = 2,
+    # Customize the axis
+    axislabcol = "black", cexc = 1.5, # Increase label size for axis
+    # Variable labels
+    vlcex = vlcex, vlabels = vlabels, vlpos = 0.98,
+    seg = 7, caxislabels = caxislabels, title = title, 
+    # Increase title size
+    cex.main = 4,
+    ...
+  )
+}
+
+# Reduce plot margin using par()
+op <- par(mar = c(7, 3, 3, 3))
+# Create the radar charts
+create_beautiful_radarchart(
+  data = radar4, caxislabels = c(-0.6, -0.4, -0.2, 0, 0.2, 0.4, 0.6, 0.8),
+  color = c( "#F97D09","#00AFBB"),
+  vlcex = 1.1
+)
+
+# Add an horizontal legend
+legend(
+  x = "bottomright", legend = rownames(radar4[-c(1,2),]), horiz = TRUE,
+  bty = "n", pch = 20 , col = c("#F97D09","#00AFBB"),
+  text.col = "black", cex = 1.5, pt.cex = 3,
+  inset = c(0, 0)
+  )
+par(op)
+
+```
+
+```{r, echo=FALSE}
+
+# Extracting factors from first imputed dataset
 
@@
 
-fct_scores2 <- data.frame(factor.scores(data_imp2[, 1:23], fit2)$scores)
+fct_scores2 <- data.frame(factor.scores(data_imp2[, 1:24], ecopolfit2)$scores)
 
@@
 
-## Checking imputations : Eco-pol scale
+##  eco-pol scale : Factor scores from 2nd imputation
+```{r, echo=FALSE}
+
+data_impe2 <- mice::complete(mice::mice(ecopoln, 2, print = FALSE))
+
+fct_scorese2 <- data.frame(factor.scores(data_impe2[, 1:24], ecopolfit2)$scores)
+
+```
+
+##  eco-pol scale : Factor scores from 3rd imputation
+```{r, echo=FALSE}
+
+data_impe3 <- mice::complete(mice::mice(ecopoln, 3, print = FALSE))
+
+fct_scorese3 <- data.frame(factor.scores(data_impe3[, 1:24], ecopolfit2)$scores)
+
+```
+
+##  eco-pol scale : Factor scores from 4th imputation
+```{r, echo=FALSE}
+
+data_impe4 <- mice::complete(mice::mice(ecopoln, 4, print = FALSE))
+
+fct_scorese4 <- data.frame(factor.scores(data_impe4[, 1:24], ecopolfit2)$scores)
+
+```
+
+##  eco-pol scale : Factor scores from 5th imputation
+```{r, echo=FALSE}
+
+data_impe5 <- mice::complete(mice::mice(ecopoln, 5, print = FALSE))
+
+fct_scorese5 <- data.frame(factor.scores(data_impe5[, 1:24], ecopolfit2)$scores)
+
+```
+
+## Are imputations plausible : Eco-pol scale
+
+yes, imputations are pluasible- all natural numbers between 1 and 5
 
@@
 
-```{r}
+# Checking consistency of LM coefficients across 5 imputed datasets 
+coefficients and LMs are fairly consistent
 
-nscores <- data.frame(ecopolall_scores$scores)
-nscores
+## Binding datasets: 1st imputation
 
-# Add an identifier column to each dataset
-fct_scores2$Dataset <- 'imputed'
-nscores$Dataset <- 'original'
+```{r, echo = FALSE}
 
-# Combine the datasets for plotting
-compare2 <- rbind(fct_scores2, nscores)
+# binding the imputed  factor analysis scores for kahan scale and eco-pol value scale to the larger dataset codedmodule2
 
-# Select only necessary columns (assuming 'Index' isn't needed anymore)
-compare2<- compare2[, c("MR1", "MR2", "Dataset")]
+ecopolnuclear <- fct_scores2 %>%
+  rename(Ndevelop = MR1, Pdevelop = MR2)
 
-ggplot(compare2, aes(x = Dataset, y = MR1, fill = Dataset)) +
-  geom_boxplot() +
-  geom_jitter(width = 0.2, aes(color = Dataset), size = 1.5, alpha = 0.5) +
-  labs(title = "Boxplot of Pdevelop for Each Dataset", x = "", y = "MR1 Value") +
-  scale_fill_manual(values = c("imputed" = "blue", "original" = "red")) +
-  scale_color_manual(values = c("imputed" = "blue", "original" = "red")) +
-  theme_minimal()
+kahannuclear <- fct_scores%>%
+  rename(Hierarchy_Egalitarian = MR1, Communitarian = MR2)
+
+allformice<- cbind(formice1,ecopolnuclear, kahannuclear)
 
@@
 
-```{r}
+## State Ns before MIFA
 
-ggplot(compare2, aes(x = Dataset, y = MR2, fill = Dataset)) +
-  geom_boxplot() +
-  geom_jitter(width = 0.2, aes(color = Dataset), size = 1.5, alpha = 0.5) +
-  labs(title = "Boxplot of Ndevelop for Each Dataset with Points", x = "", y = "MR2 Value") +
-  scale_fill_manual(values = c("imputed" = "blue", "original" = "red")) +
-  scale_color_manual(values = c("imputed" = "blue", "original" = "red")) +
-  theme_minimal()
+```{r, echo=FALSE}
+Statenacheck1 <- allformice%>%
+  na.omit()%>%
+  dplyr::select(State)
+
+summary(Statenacheck1)
+```
+
+```{r, echo=FALSE}
+
+# Allformice: Do imputations merge ?
+
+# Initialize the mice process to create the predictor matrix
+#ini <- mice(allformice, maxit = 0, pri = FALSE)
+
+# Extract the predictor matrix from the initialized object
+#pred <- ini$predictorMatrix
+
+# Set the columns for "Uppercaste", "Male", "Hindu", and "Age" to 0
+#pred[, "Uppercaste"] <- 0
+#pred[, "Male"] <- 0
+#pred[, "Hindu"] <- 0
+#pred[, "Age"] <- 0
+#pred[, "Ndevelop"] <- 0
+#pred[, "Pdevelop"] <- 0
+#pred[, "Hierarchy_Egalitarian"] <- 0
+#pred[, "Communitarian"] <- 0
+# Identify columns that start with "K_" and set them to 0
+#k_columns <- grep("^K_", colnames(formice1))
+#pred[, k_columns] <- 0
+
+# Perform the mice imputation with the updated predictor matrix
+#allformice.imp <- mice(allformice, m = 5, maxit = 10, predictorMatrix = pred, seed = 430, print = TRUE)
+
+#summary(allformice.imp)
+#allformice.imp$chainMean
+
+#plot(allformice.imp)
 
@@
 
-```{r}
+## State Ns after MIFA on two scales
+
+```{r, echo=FALSE}
+
+nuclear_missing <- allformice %>% dplyr::select(Risky_Nuclear,Uppercaste, Male, Hindu, urban_rural, Age, State)%>%
+  na.omit()
+
+summary(nuclear_missing)
 
 ```
+
+## LMs with 1st imputed datasets from FAs
+
+```{r, echo=FALSE}
+
+nuclearIVmice <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformice)
+
+nuclearIVmice2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian, data = allformice)
+
+nuclearIVmice3 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian + Pdevelop + Ndevelop, data = allformice)
+
+summary(nuclearIVmice)
+summary(nuclearIVmice2)
+summary(nuclearIVmice3)
+
+```
+
+## binding dataset - 2nd imputation
+
+```{r, echo=FALSE}
+
+ecopolnuclear2 <- fct_scorese2 %>%
+  rename(Ndevelop = MR1, Pdevelop = MR2)
+
+kahannuclear2 <- fct_scoresk2%>%
+  rename(Hierarchy_Egalitarian = MR1, Communitarian = MR2)
+
+allformice2<- cbind(formice1,ecopolnuclear2, kahannuclear2)
+
+```
+
+## LMs with second imputation 
+```{r, echo=FALSE}
+
+nuclearIVmiceimp2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformice2)
+
+nuclearIVmiceimp22 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian, data = allformice2)
+
+nuclearIVmiceimp23 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian + Pdevelop + Ndevelop, data = allformice2)
+
+summary(nuclearIVmiceimp2)
+summary(nuclearIVmiceimp22)
+summary(nuclearIVmiceimp23)
+
+```
+
+## binding dataset - 3rd imputation
+
+```{r, echo=FALSE}
+
+ecopolnuclear3 <- fct_scorese3 %>%
+  rename(Ndevelop = MR1, Pdevelop = MR2)
+
+kahannuclear3 <- fct_scoresk3%>%
+  rename(Hierarchy_Egalitarian = MR1, Communitarian = MR2)
+
+allformice3<- cbind(formice1,ecopolnuclear3, kahannuclear3)
+
+```
+
+## LMs with third imputation 
+```{r, echo=FALSE}
+
+nuclearIVmiceimp3 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformice3)
+
+nuclearIVmiceimp32 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian, data = allformice3)
+
+nuclearIVmiceimp33 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian + Pdevelop + Ndevelop, data = allformice3)
+
+summary(nuclearIVmiceimp3)
+summary(nuclearIVmiceimp32)
+summary(nuclearIVmiceimp33)
+
+```
+
+## binding dataset - 4th imputation
+
+```{r, echo=FALSE}
+
+ecopolnuclear4 <- fct_scorese4 %>%
+  rename(Ndevelop = MR1, Pdevelop = MR2)
+
+kahannuclear4 <- fct_scoresk4%>%
+  rename(Hierarchy_Egalitarian = MR1, Communitarian = MR2)
+
+allformice4<- cbind(formice1, ecopolnuclear4, kahannuclear4)
+
+```
+
+## LMs with fourth imputation 
+```{r, echo=FALSE}
+
+nuclearIVmiceimp4 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformice4)
+
+nuclearIVmiceimp24 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian, data = allformice4)
+
+nuclearIVmiceimp34 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian + Pdevelop + Ndevelop, data = allformice4)
+
+summary(nuclearIVmiceimp4)
+summary(nuclearIVmiceimp24)
+summary(nuclearIVmiceimp34)
+
+```
+
+# Mean across imputations
+
+## Binding datasets
+
+```{r, echo = FALSE}
+
+# binding the imputed  factor analysis scores for kahan scale and eco-pol value scale to the larger dataset codedmodule2
+
+ecopolnuclearfinal <- necopolfinal %>%
+  rename(Ndevelop = MR1, Pdevelop = MR2)
+
+kahannuclearfinal <- nkahanfinal%>%
+  rename(Hierarchy_Egalitarian = MR1, Communitarian = MR2)
+
+allformicefinal<- cbind(formice1,ecopolnuclearfinal, kahannuclearfinal)
+
+```
+
+## LMs with final imputed datasets from FAs
+
+```{r, echo=FALSE}
+
+nuclearfinal <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age, data = allformicefinal)
+
+nuclearfinal2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformicefinal)
+
+nuclearfinal3 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian, data = allformicefinal)
+
+nuclearfinal4 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian + Pdevelop + Ndevelop, data = allformicefinal)
+
+#summary(nuclearfinal)
+#summary(nuclearfinal2)
+#summary(nuclearfinal3)
+#summary(nuclearfinal4)
+```
+
+\newpage
+\blandscape
+
+```{r, echo=FALSE, results='asis'}
+library(stargazer)
+
+cat("\\begingroup")
+cat("\\setlength{\\tabcolsep}{1pt}")
+cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer(nuclearfinal, nuclearfinal2, nuclearfinal3, nuclearfinal4,
+          title = "4 linear models: Perceived Risk of Nuclear Energy",
+          type = "latex"
+)
+cat("\\endgroup")
+
+```
+
+\elandscape
+
+```{r, echo=FALSE}
+
+# LM with demographic variables and State 
+# The pool() function from the mice package creates a list containing the results,
+# so we need to access the summary of the model directly.
+
+#pooled_fit4 <- pool(nuclearfit4)
+
+#pooled_summary4 <- summary(pooled_fit4)
+
+#coefficients_df4 <- pooled_summary4
+# To ensure the numeric values are rounded to two decimal places, you can use:
+#coefficients_df4 <- round(coefficients_df4[, -1], 2)  # Skipping the first column as it's factors (term names)
+#coefficients_df4$term <- pooled_summary4$term  # Adding back the unrounded terms
+
+# Print the dataframe
+#data.frame(coefficients_df4) %>%
+ # dplyr::select(term, estimate, std.error, statistic, df, p.value)
+```

### 2024-03-13 withmice.Rmd
pretty tables for EFAs

@@
 
+# barplot of demographics
+
+```{r, echo=FALSE}
+
+library(dplyr)
+library(tidyr)
+
+demobar <- codedmodule2 %>% 
+  dplyr::select("State", "Language", "age", "urban_rural", "gender", "caste" ,"religion") %>%
+              mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
+              mutate_all(~ifelse(. == "OBC", "Other Backward Classes (OBC)", .))%>%
+              mutate_all(~ifelse(. == "SC", "Scheduled caste (SC)", .))%>%
+              mutate_all(~ifelse(. == "ST", "Scheduled tribe (ST)", .))%>%
+              mutate_all(~ifelse(. == "MAR", "Marathi", .))%>%
+              mutate_all(~ifelse(. == "TA", "Tamil", .)) %>%
+              mutate_all(~ifelse(. == "EN", "English", .))%>%
+              mutate_all(~ifelse(. == "BN", "Bengali", .))%>%
+              mutate_all(~ifelse(. == "MAR", "Marathi", .))%>%
+              mutate_all(~ifelse(. == "HI", "Hindi", .))%>%
+              na.omit()
+
+#changing factor levels for each variable from high to low n
+
+demobar$State <- factor(demobar$State, levels = c("Maharashtra","Rajasthan", "West Bengal" , "Tamil Nadu", "Uttar Pradesh"))
+demobar$Language <- factor(demobar$Language, levels = c("Hindi","Marathi","Bengali","Tamil", "English"))
+demobar$age <- factor(demobar$age, levels = c( "18-24 years old" ,  "25-34 years old","35-44 years old", "45-54 years old", "55-64 years old","65-74 years old","75 years or older"  ))
+demobar$urban_rural <- factor(demobar$urban_rural, levels = c("Rural","Urban"))
+demobar$gender <- factor(demobar$gender, levels = c("Male","Female"))
+demobar$caste <- factor(demobar$caste, levels = c("Scheduled tribe (ST)", "Scheduled caste (SC)", "Other Backward Classes (OBC)", "General","Brahmin","Rather not say/Don't know"))
+demobar$religion <- factor(demobar$religion, levels = c("Hinduism", "Islam", "Christanity","Buddhism","Agnostism/ Atheism","Other (Please mention)"))
+
+```
+
+```{r, echo=FALSE, fig.width=11, fig.height=14, out.width='80%', out.height='80%'}
+
+# Loading the required libraries
+library(tidyverse)
+library(gridExtra)
+library(scales)
+
+# Function to create bar plot
+create_bar_plot <- function(data, variable_name, palette_name) {
+  factor_levels <- levels(demobar[[variable_name]])
+  data %>%
+    filter(Variable == variable_name) %>%
+    mutate(Category = factor(Category, levels = factor_levels)) %>%
+    ggplot(aes(y = "", x = Percentage, fill = Category)) +
+    geom_bar(position = "fill", stat = "identity", width = 1) +
+    geom_text(aes(label = paste0(round(Percentage, 0), "%")), 
+              position =  position_fill(vjust = 0.5)) +
+    scale_x_continuous(labels = percent) +
+    labs(y = NULL, x = "Percentage", fill = variable_name) +
+    theme_classic() +
+    theme(axis.text.y = element_blank(), strip.text = element_text(size = 10), legend.position = "top") +
+    scale_fill_brewer(palette = palette_name)
+}
+
+# Gather data to long format and calculate counts and percentages
+df_barplot <- demobar %>%
+  gather(Variable, Category) %>%
+  group_by(Variable, Category) %>%
+  filter(!is.na(Category)) %>%
+  summarise(n = n()) %>%
+  mutate(Percentage = n / sum(n) * 100)
+
+# Create separate plots for each variable
+plot_state <- create_bar_plot(df_barplot, "State", "Spectral")
+plot_language <- create_bar_plot(df_barplot, "Language", "Paired")
+plot_age <- create_bar_plot(df_barplot, "age", "Set3")
+plot_urban_rural <- create_bar_plot(df_barplot, "urban_rural", "Dark2")
+plot_gender <- create_bar_plot(df_barplot, "gender", "Pastel1")
+plot_caste <- create_bar_plot(df_barplot, "caste", "Set1")
+plot_religion <- create_bar_plot(df_barplot, "religion", "Set2")
+
+# Combine the plots with spacing
+combined_plot <- gridExtra::arrangeGrob(plot_state, plot_language, plot_age, plot_urban_rural, plot_gender, plot_caste, plot_religion, ncol = 1, heights = c(1, 1, 1, 1, 1, 1, 1))
+
+# Print the combined plot
+grid::grid.newpage()
+grid::grid.draw(combined_plot)
+
+```
+
 # Can do something with accept, reject and reluctantly accept.
@@
 
+```
+
+\blandscape
+
+## Pretty Table: FA Kahan
+
+```{r, echo=FALSE}
+
+library(flextable)
+
+flex <- function(data, title=NULL, col_widths=NULL) {
+  tbl <- flextable(data) %>%
+           #padding(padding = 1, part = "all") %>%
+           #set_table_properties(layout = "autofit") %>%
+           fontsize(size=10, part="all") %>%
+           set_caption(title, 
+                       autonum = officer::run_autonum(seq_id = "tab", 
+                                                      pre_label = "Table ", 
+                                                      post_label = "\n", 
+                                                      bkm = "anytable"))
+
+  # If col_widths is provided, set column widths
+  if(!is.null(col_widths)) {
+    for(col in names(col_widths)){
+      tbl <- width(tbl, j = col, width = col_widths[[col]])
+    }
+  }
+
+  return(tbl)
+}
+
+rename_map <- c(
+  "K_SHARM" = " (C)Sometimes the government needs to make laws that keep people from hurting themselves.",
+"K_SLIMCHOI" = "(C)The government should put limits on the choices individuals can make so they don’t get in the way of what’s
+good for society.",
+"K_SPROTECT" = "(C)The government should do more to advance society’s goals, even if that means limiting the freedom and
+choices of individuals.",
+"K_HEQUAL" = "(H)We have gone too far in pushing equal rights in this country.",
+"K_ERADEQ1" = "(E)We need to dramatically reduce inequalities between the rich and the poor.",
+"K_EWEALTH" = "(E)Our society would be better off if the distribution of wealth was more equal.",
+"K_ERADEQ2" = "(E)We need to dramatically reduce inequalities between men and women.",
+"K_HREVDIS1" = "(H)Nowadays it seems like there is just as much discrimination against upper castes as there is against Dalits.",
+"K_EDISCRIM" = "(E)Discrimination against minorities is still a very serious problem in our society.",
+"K_IINTRFER" = "(I)The government interferes far too much in our everyday lives.",
+"K_IPRIVACY" = "(I)The government should stop telling people how to live their lives.",
+"K_IPROTECT" = "(I)It’s not the government’s business to try to protect people from themselves."
+)
+
+fa_table <- function(x, cut) {
+  #get sorted loadings
+  loadings <- fa.sort(x)$loadings %>% round(3)
+  #suppress loadings
+  loadings[loadings > -cut & loadings < cut] <- ""
+  #get additional info  
+  add_info <- cbind(x$communalities, 
+                    x$uniquenesses,
+                    x$complexity) %>%
+    # make it a data frame
+    as.data.frame() %>%
+    # column names
+    rename("Communality" = V1,
+           "Uniqueness" = V2,
+           "Complexity" = V3) %>%
+    #get the item names from the vector
+    rownames_to_column("item")
+
+  #build table
+  loadings %>%
+    unclass() %>%
+    as.data.frame() %>%
+    rownames_to_column("item") %>%
+    left_join(add_info) %>%
+    mutate(
+      item = if_else(item %in% names(rename_map), rename_map[item], item),
+      code = names(rename_map)[match(item, rename_map)], # extracting short form
+      across(where(is.numeric), round, 3)
+    ) %>%
+    dplyr::select(code, everything()) # reorder columns to bring code to the front
+}
+
+fa_table(fit , .4) %>%
+  rename(Hierarchy_Egalitarianism = MR1, Communitarianism = MR2, Items= item, Code= code) %>%
+  flex("EFA: Kahan Scale", col_widths = list(Items = 4.5, Code = 1))
+
+```
+
+\elandscape
+
+```{r, echo = FALSE}
+fit[["Vaccounted"]] %>%
+  as.data.frame() %>%
+  rownames_to_column("Property") %>%
+  rename(Hierarchy_Egalitarianism = MR1, Communitarianism = MR2) %>%
+    mutate(across(where(is.numeric), round, 3)) %>%
+    flex("Eigenvalues and Variance Explained for Kahan Scale")
 ```
@@
 
+# Pretty table attempt 1
+
+\blandscape
+# FA on Combined Scale (2 Factor Solution): People Centered Development and Nationalist Development 
+## Nuclear Energy: EFA on Combined Scale (2 Factor Solution)
+
+```{r, echo=FALSE}
+
+library(flextable)
+
+flex <- function(data, title=NULL, col_widths=NULL) {
+  tbl <- flextable(data) %>%
+           #padding(padding = 1, part = "all") %>%
+           #set_table_properties(layout = "autofit") %>%
+           fontsize(size=10, part="all") %>%
+           set_caption(title, 
+                       autonum = officer::run_autonum(seq_id = "tab", 
+                                                      pre_label = "Table ", 
+                                                      post_label = "\n", 
+                                                      bkm = "anytable"))
+
+  # If col_widths is provided, set column widths
+  if(!is.null(col_widths)) {
+    for(col in names(col_widths)){
+      tbl <- width(tbl, j = col, width = col_widths[[col]])
+    }
+  }
+
+  return(tbl)
+}
+
+rename_map2 <- c(
+  "Limits on Wealth" = "A limit should be put to how much wealth a person can amass",
+  "Anti Mechanisation of work" = "Rapid mechanization of work is taking away jobs from workers in this country",
+  "Pro Decentralisation" = "Local politicians shouldn't have to ask permission from the central government to implement policies",
+  "Pro Centralisation" = "Laws and policies would be implemented more smoothly if more power lay with the central government",
+  "Pro Large Industries" = "Large scale industries are required for the development of the country that will benefit everyone",
+  "Anti Large Industries" = "Large corporations are destroying the local industries in India and benefiting only a handful of people",
+  "Pro Globaleconomy" = "Foreign companies have led to a range of benefits for the Indian people and society",
+  "Pro Localeconomy" = "India would be better off if foreign companies didn't come to here",
+  "Environment over Development" = "Polluting industries that spoil the environment should be shut down even if it costs people their jobs",
+  "Development over Environment" = "Economic growth and creating jobs should be prioritized over environmental protection",
+  "Pro Private ownership" = "All businesses and industries should be owned privately",
+  "Anti Regulations" = "There is too much red-tape and the government should not interfere with businesses and industries",
+  "Pro Public ownership" = "The government should own most large businesses and industries",
+  "Pro Regulations" = "Regardless of ownership, the government should pass strong regulations and implement them",
+  "Displacement risk(nuclear)" = "Nuclear energy is leading to displacement of people from their land",
+  "Spoils Natural Beauty(nuclear)" = "Nuclear energy spoils the natural beauty of the landscape",
+  "Pollution risk(nuclear)" = "Nuclear energy increases pollution of air/water/land",
+  "Health risk(nuclear)" = "Nuclear energy poses a great risk to the health of people living around it",
+  "Job opportunities(nuclear)" = "Nuclear energy will bring jobs to the local community",
+  "Community pride(nuclear)" = "I would be proud if my community used nuclear energy",
+  "National pride(nuclear)" = "Nuclear energy is a mark of pride for our nation",
+  "National development(nuclear)" = "Nuclear energy pushes forward the country's development",
+  "Local prosperity(nuclear)" = "Nuclear energy brings economic prosperity to the surrounding regions",
+  "Reliance on government(nuclear)" = "I don't like the idea that I have to rely on the government for electricity from nuclear energy"
+)
+
+fa_table <- function(x, cut) {
+  #get sorted loadings
+  loadings <- fa.sort(x)$loadings %>% round(3)
+  #suppress loadings
+  loadings[loadings > -cut & loadings < cut] <- ""
+  #get additional info  
+  add_info <- cbind(x$communalities, 
+                    x$uniquenesses,
+                    x$complexity) %>%
+    # make it a data frame
+    as.data.frame() %>%
+    # column names
+    rename("Communality" = V1,
+           "Uniqueness" = V2,
+           "Complexity" = V3) %>%
+    #get the item names from the vector
+    rownames_to_column("item")
+
+  #build table
+  loadings %>%
+    unclass() %>%
+    as.data.frame() %>%
+    rownames_to_column("item") %>%
+    left_join(add_info) %>%
+    mutate(
+      item = if_else(item %in% names(rename_map2), rename_map2[item], item),
+      code = names(rename_map2)[match(item, rename_map2)], # extracting short form
+      across(where(is.numeric), round, 3)
+    ) %>%
+    dplyr::select(code, everything()) # reorder columns to bring code to the front
+}
+
+fa_table(ecopolfit2, .4) %>%
+  rename(Ndevelop = MR1, Pdevelop = MR2, Items= item) %>%
+  flex("2 factor solution", col_widths = list(Items = 4.5, code = 1.5))
+
+```
+
+\elandscape
+
+```{r, echo = FALSE}
+ecopolfit2[["Vaccounted"]] %>%
+  as.data.frame() %>%
+  rownames_to_column("Property") %>%
+  rename(Ndevelop = MR1, Pdevelop = MR2) %>%
+    mutate(across(where(is.numeric), round, 3)) %>%
+    flex("Eigenvalues and Variance Explained for Combined Scale (2 Factor Solution)")
+```
+
 ```{r, echo=FALSE}

### 2024-03-17 FAoptions.Rmd
comparing imputed and original data for ecopol scale via boxplots
removed reverse coding for all scales in three rmd files - FA options, corstuff and withmice
finished nuclear risk perception computations. removed reverse coding from FA options and chapter 2

@@
 
-# reverse code for likert scale for variables for Kahan scale into numbers
-mutate_at(vars(starts_with (c("K_I","K_E"))), funs(case_when(. == "Strongly disagree" ~ 5, 
-                                                               . == "Somewhat disagree" ~ 4,
+# No reverse code for likert scale for variables for Kahan scale into numbers
+mutate_at(vars(starts_with (c("K_I","K_E"))), funs(case_when(. == "Strongly disagree" ~ 1, 
+                                                               . == "Somewhat disagree" ~ 2,
                                                                . == "Neither agree nor disagree" ~3,
-                                                               . == "Somewhat agree" ~ 2,
-                                                               . == "Strongly agree" ~ 1))) %>%
+                                                               . == "Somewhat agree" ~ 4,
+                                                               . == "Strongly agree" ~ 5))) %>%
 
@@
 #TFI - CFI>TFI >0.90 - indicates good fit
-#pvalue should be greater than 0.05 p > 0.0.5
+#pvalue should be greater than 0.05 p > 0.05
 
@@
 
-#print.psych(ecopolall2.fa, cut = 0.4, sort = TRUE)
+print.psych(ecopolall2.fa, cut = 0.4, sort = TRUE)
 

### 2024-03-17 Paper1.Rmd
made lms with mice
making pretty Lm tables
finished nuclear risk perception computations. removed reverse coding from FA options and chapter 2

@@
 # reverse code for likert scale for variables for Kahan scale into numbers
-  mutate_at(vars(starts_with (c("K_H","K_I"))), funs(case_when(. == "Strongly disagree" ~ 5, 
-                                                               . == "Somewhat disagree" ~ 4,
+  mutate_at(vars(starts_with (c("K_H","K_I"))), funs(case_when(. == "Strongly disagree" ~ 1, 
+                                                               . == "Somewhat disagree" ~ 2,
                                                                . == "Neither agree nor disagree" ~3,
-                                                               . == "Somewhat agree" ~ 2,
-                                                               . == "Strongly agree" ~ 1))) %>%
+                                                               . == "Somewhat agree" ~ 4,
+                                                               . == "Strongly agree" ~ 5))) %>%
 
@@
 # reverse code eco-pol scale variables into numbers 
- mutate_at(vars(DECISIONCEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG, DEVOVERENV), funs(case_when(. == "Strongly disagree" ~ 5, 
-                                                                                                         . == "Somewhat disagree" ~ 4,
-                                                                                                         . == "Neither agree nor disagree" ~3,
-                                                                                                         . == "Somewhat agree" ~ 2,
-                                                                                                         . == "Strongly agree" ~ 1))) %>%
+ mutate_at(vars(DECISIONCEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG, DEVOVERENV), funs(case_when(. == "Strongly disagree" ~ 1, 
+                                                                                                         . == "Somewhat disagree" ~ 2,
+                                                                                                         . == "Neither agree nor disagree" ~ 3,
+                                                                                                         . == "Somewhat agree" ~ 4,
+                                                                                                         . == "Strongly agree" ~ 5))) %>%
   mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
@@
   mutate_all(~ifelse(. == "UP", "Uttar Pradesh", .))
+
+```
+
+# Ns for states in joineddf
+```{r}
+
+statens <-  joineddf %>% dplyr::select(Risky_Nuclear, caste, gender, religion, urban_rural, age, State) %>%
+             mutate(across(State, ~factor(.x, ordered = FALSE))) %>%
+            na.omit()
+
+summary(statens)
 
@@
 
-print.psych(kahan.fa, sort = TRUE)
+print.psych(kahan.fa, sort = TRUE, cut=0.4)
 
@@
 
-print.psych(ecopolall2.fa, sort = TRUE)
+print.psych(ecopolall2.fa, sort = TRUE, cut = 0.4)
 

### 2024-03-17 nuclear in comparison.Rmd
finished nuclear risk perception computations. removed reverse coding from FA options and chapter 2

@@
 
-# reverse code for likert scale for variables for Kahan scale into numbers
-  mutate_at(vars(starts_with (c("K_S","K_E"))), funs(case_when(. == "Strongly disagree" ~ 5, 
-                                                               . == "Somewhat disagree" ~ 4,
+# No reverse code for likert scale for variables for Kahan scale into numbers
+  mutate_at(vars(starts_with (c("K_S","K_E"))), funs(case_when(. == "Strongly disagree" ~ 1, 
+                                                               . == "Somewhat disagree" ~ 2,
                                                                . == "Neither agree nor disagree" ~3,
-                                                               . == "Somewhat agree" ~ 2,
-                                                               . == "Strongly agree" ~ 1))) %>%
+                                                               . == "Somewhat agree" ~ 4,
+                                                               . == "Strongly agree" ~ 5))) %>%
 
@@
 
-# reverse code eco-pol scale variables into numbers 
- mutate_at(vars(DECISIONCEN, INDUSTRYSMALL, ECONOMYLOCAL, ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(. == "Strongly disagree" ~ 5, 
-                                                                                                         . == "Somewhat disagree" ~ 4,
+# No reverse code eco-pol scale variables into numbers 
+ mutate_at(vars(DECISIONCEN, INDUSTRYSMALL, ECONOMYLOCAL, ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(. == "Strongly disagree" ~ 1, 
+                                                                                                         . == "Somewhat disagree" ~ 2,
                                                                                                          . == "Neither agree nor disagree" ~3,
-                                                                                                         . == "Somewhat agree" ~ 2,
-                                                                                                         . == "Strongly agree" ~ 1))) %>%
+                                                                                                         . == "Somewhat agree" ~ 4,
+                                                                                                         . == "Strongly agree" ~ 5))) %>%
   mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%

### 2024-03-17 withmice.Rmd
finished nuclear risk perception computations. removed reverse coding from FA options and chapter 2

@@
 title: "models with mice"
-header-includes:
-- \usepackage{pdflscape}
-- \newcommand{\blandscape}{\begin{landscape}}
-- \newcommand{\elandscape}{\end{landscape}}
 output:
@@
     keep_tex: yes
+  header-includes:
+  - \usepackage{dcolumn}
+  - \usepackage{array}
+  - "\\usepackage{placeins}"
   keep_md: yes
@@
 
+# Bar plot: STATE X PDEVELOP
+
+```{r}
+
+# Load necessary libraries
+library(dplyr)
+library(ggplot2)
+library(forcats)
+
+# Df to include relevant variables
+
+WBques <- module2 %>%  filter(!row_number() %in% c(1,2)) %>% dplyr::select(State, DISPLACENUCLEAR, HEALTHNUCLEAR, BEAUTYNUCLEAR, POLLUTENUCLEAR ) %>%
+  mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
+  mutate_all(~ifelse(. == "West bengal", "West Bengal", .))%>%
+  mutate_all(~ifelse(. == "WEST BENGAL", "West Bengal", .))%>%
+  mutate_all(~ifelse(. == "Up", "Uttar Pradesh", .))%>%
+  mutate_all(~ifelse(. == "Tamilnadu", "Tamil Nadu", .))%>%
+  mutate_all(~ifelse(. == "UP", "Uttar Pradesh", .))
+
+levels_defined <- c("Strongly agree", "Somewhat agree","Neither agree nor disagree", "Somewhat disagree","Strongly disagree","Rather not say/Don't know")
+
+WBques_factors <- WBques
+WBques_factors[] <- lapply(names(WBques_factors), function(colname) {
+  if (colname != "State") {
+    factor(WBques_factors[[colname]], levels = levels_defined)
+  } else {
+    WBques_factors[[colname]] # Keep the State column unchanged
+  }
+})
+
+WBques_factors$State <- factor(WBques_factors$State, 
+                               levels = c("West Bengal", "Uttar Pradesh", "Maharashtra", "Rajasthan", "Tamil Nadu"))
+
+library(dplyr)
+library(ggplot2)
+
+# Assuming your updated data frame is named WBques_factors
+
+# Create a summary table with counts for each level of DISPLACENUCLEAR within each State
+WBques_summary <- WBques_factors %>%
+  count(State, DISPLACENUCLEAR) %>%
+  group_by(State) %>%
+  mutate(Proportion = n / sum(n))
+
+# Create a named vector with full statements for each variable
+full_statements <- c(DISPLACENUCLEAR = "Nuclear energy is leading to displacement of people from their land",
+                     BEAUTYNUCLEAR = "Nuclear energy spoils the natural beauty of the landscape",
+                     POLLUTENUCLEAR = "Nuclear energy increases pollution of air/water/land",
+                     HEALTHNUCLEAR = "Nuclear energy poses a great risk to the health of people living around it",
+                     ENVOVERDEV = "Polluting industries that spoil the environment should be shut down even if it costs people their jobs")
+
+# Reshape the data to long format for the selected variables
+WBques_long <- WBques_factors %>%
+  pivot_longer(cols = c(DISPLACENUCLEAR, HEALTHNUCLEAR, BEAUTYNUCLEAR, POLLUTENUCLEAR),
+               names_to = "Question",
+               values_to = "Response") %>%
+  mutate(Question = recode(Question, !!!full_statements)) # Replace var names with full statements
+
+# Create a summary table with proportions for each level of Response within each State and Question
+WBques_summary <- WBques_long %>%
+  count(State, Question, Response) %>%
+  group_by(State, Question) %>%
+  mutate(Proportion = n / sum(n))
+
+# Define the color sequence, with the darkest red for "Strongly agree"
+colorsequence <- c("#8C4646","#D9695F","#F2A679","#F2D091","#FFF2CC","#808080")
+
+# Plot the graph with facets for each Question
+ggplot(WBques_summary, aes(x = State, y = Proportion, fill = factor(Response, levels = rev(levels_defined)))) +
+  geom_bar(stat = "identity", position = "fill") +
+  scale_fill_manual(values = rev(colorsequence), name = NULL) +
+  facet_wrap(~ Question, scales = "free_y", ncol = 1) +
+  coord_flip() +
+  labs(x = "State", y = "Proportion", title = "Proportion of Responses by State for Nuclear energy related questions") +
+  theme_minimal() +
+  theme(
+    # Increase the size of the main title
+    plot.title = element_text(size = 16, face = "bold"),
+    # Increase the size of the axis titles
+    axis.title = element_text(size = 14),
+    # Increase the size of the facet strip text
+    strip.text.x = element_text(size = 12),
+    # Adjust text angle for State labels if necessary
+    axis.text.y = element_text(angle = 0)
+  )
+
+```
+
 # barplot of demographics
@@
 
-demobar$State <- factor(demobar$State, levels = c("Maharashtra","Rajasthan", "West Bengal" , "Tamil Nadu", "Uttar Pradesh"))
+demobar$State <- factor(demobar$State, levels = c("Rajasthan", "Maharashtra","West Bengal" , "Tamil Nadu", "Uttar Pradesh"))
 demobar$Language <- factor(demobar$Language, levels = c("Hindi","Marathi","Bengali","Tamil", "English"))
@@
 
-n_acceptreject<- codedmodule2 %>%
+n_acceptreject<- module2 %>%
                 dplyr::select("N_accept", "N_reluctantlyaccept", "N_reject")
@@
 
+sum(is.na(formice))
+
 mcar_test(data= codedmodule2)
@@
 
-```
-
-\blandscape
+kahanfit4 <- psych::fa(mikahan$cov_combined, nfactors = 3, rotate = "varimax")
+
+print.psych(kahanfit4, sort= TRUE, cut= 0.4)
+
+```
 
@@
 fa_table(fit , .4) %>%
-  rename(Hierarchy_Egalitarianism = MR1, Communitarianism = MR2, Items= item, Code= code) %>%
-  flex("EFA: Kahan Scale", col_widths = list(Items = 4.5, Code = 1))
-
-```
-
-\elandscape
+  rename(Egalitarianism = MR1, Communitarianism = MR2, Items= item, Code= code) %>%
+  flex("Table 1: EFA on adapted Cultural Cognition Scale from Kahan et al(2007)", col_widths = list(Items = 4.5, Code = 1))
+
+```
 
@@
   rownames_to_column("Property") %>%
-  rename(Hierarchy_Egalitarianism = MR1, Communitarianism = MR2) %>%
+  rename(Egalitarianism = MR1, Communitarianism = MR2) %>%
     mutate(across(where(is.numeric), round, 3)) %>%
-    flex("Eigenvalues and Variance Explained for Kahan Scale")
+    flex("Table 2: Eigenvalues and Variance Explained for Cultural Cognition Scale")
 ```
@@
   rowwise() %>%
-  mutate( K_EWEALTH_mean = mean(c_across(starts_with("K_EWEALTH"))),
+  mutate(
     K_IINTRFER_mean = mean(c_across(starts_with("K_IINTRFER"))),
@@
     K_ERADEQ1_mean = mean(c_across(starts_with("K_ERADEQ1"))),
-    K_ERADEQ2_mean = mean(c_across(starts_with("K_ERADEQ2")))
+    K_ERADEQ2_mean = mean(c_across(starts_with("K_ERADEQ2"))),
+    K_EWEALTH_mean = mean(c_across(starts_with("K_EWEALTH")))
   ) %>%
@@
 nkahanfinal <- data.frame(factor.scores(nkahanall[, 1:12], fit)$scores)
+
+```
+
+## Kahan corelation table
+```{r}
+
+cor(nkahanall)
+
+#before mice 
+ cor.plot(kahanall %>% dplyr::select(-c("age", "gender", "caste", "State", "urban_rural", "religion")))
+
+#after mice
+ cor.plot(nkahanall)
+
+cov(nkahanall)
+
+```
+
+## Kahan scater plot from EFA scores 
+```{r, echo = FALSE}
+
+nkahanfinal %>%
+  ggplot(aes(MR1, MR2))+
+  geom_count(aes(color = ..n.., size = ..n..))+
+  guides(color = 'legend')+
+  geom_hline(yintercept=0, colour="black", lwd=0.5)+
+  geom_vline(xintercept=0, colour="black", lwd=0.5)+
+  labs(x = "Hierarchy -Egalitarianism", y = "Individualism - Communitarianism")+
+  ylim(-2,3)+
+  xlim(-2,3)+
+  theme_minimal() 
+```
+
+# Kahan alpha test
+
+```{r, echo=FALSE}
+
+KahanallHE <-nkahanall %>%
+  dplyr::select(starts_with(c("K_H", "K_E")))
+
+KahanallHE_alpha <- psych::alpha(KahanallHE, check.keys = TRUE) # alpha = 0.71
+
+KahanallC <-nkahanall %>%
+  dplyr::select(starts_with(c("K_S")))
+
+KahanallC_alpha <- psych::alpha(KahanallC, check.keys = TRUE) # alpha = 0.73
 
@@
         non-responders (Missing) on the PRIDENUCLEAR variable.")
+
 ```
@@
                 cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
+                m=50,
                 n_pc= 2:4,
@@
 
-ecopolallscores <- mice::complete(mice::mice(ecopoln, m = 5, seed = 429, print = FALSE), "broad")
+ecopolallscores <- mice::complete(mice::mice(ecopoln, m = 50, seed = 429, print = FALSE), "broad")
 
@@
 
+# Eco-pol alpha test
+
+```{r, echo=FALSE}
+
+nPdevelop <-necopol %>%
+  dplyr::select((c(BEAUTYNUCLEAR,  HEALTHNUCLEAR,  POLLUTENUCLEAR, DISPLACENUCLEAR, OWNERPUB, ENVOVERDEV)))
+
+nPdevelop_alpha <- psych::alpha(nPdevelop, check.keys = TRUE) # alpha = 0.79
+
+nNdevelop <-necopol %>%
+  dplyr::select((c(DEVNUCLEAR, PROSPERNUCLEAR,PRIDENUCLEAR, NPRIDENUCLEAR, JOBSNUCLEAR, ECONOMYGLOBAL,          WEALTHLIM,INDUSTRYLARGE, DECISIONCEN, MECHANISATION )))
+
+nNdevelop_alpha <- psych::alpha(nNdevelop , check.keys = TRUE) # alpha = 0.79
+
+```
+
 # Eco-pol: Radar map
@@
       "Pro Private ownership " = "OWNERPVT",
-      "Reliance on government(nuclear)" = "RELYNUCLEAR",
+      "Less Reliance on government(nuclear)" = "RELYNUCLEAR",
       "Spoils Natural Beauty(nuclear)" = "BEAUTYNUCLEAR",
@@
 
-```{r, echo=FALSE, fig.width=15, fig.height=7, out.width='70', out.height='70'}
+```{r, echo=FALSE, fig.width=20, fig.height=18, out.width='70', out.height='70'}
 library(fmsb)
@@
     # Customize the grid
-    cglcol = "black", cglty = 1, cglwd = 2,
+    cglcol = "grey", cglty = 1, cglwd = 2,
     # Customize the axis
-    axislabcol = "black", cexc = 1.5, # Increase label size for axis
+    axislabcol = "black", cexc = 7, # Increase label size for axis
     # Variable labels
@@
 
-# Pretty table attempt 1
-
-\blandscape
-# FA on Combined Scale (2 Factor Solution): People Centered Development and Nationalist Development 
-## Nuclear Energy: EFA on Combined Scale (2 Factor Solution)
+# Pretty table: Nuclear EFA
 
@@
 rename_map2 <- c(
-  "Limits on Wealth" = "A limit should be put to how much wealth a person can amass",
-  "Anti Mechanisation of work" = "Rapid mechanization of work is taking away jobs from workers in this country",
-  "Pro Decentralisation" = "Local politicians shouldn't have to ask permission from the central government to implement policies",
-  "Pro Centralisation" = "Laws and policies would be implemented more smoothly if more power lay with the central government",
-  "Pro Large Industries" = "Large scale industries are required for the development of the country that will benefit everyone",
-  "Anti Large Industries" = "Large corporations are destroying the local industries in India and benefiting only a handful of people",
-  "Pro Globaleconomy" = "Foreign companies have led to a range of benefits for the Indian people and society",
-  "Pro Localeconomy" = "India would be better off if foreign companies didn't come to here",
-  "Environment over Development" = "Polluting industries that spoil the environment should be shut down even if it costs people their jobs",
-  "Development over Environment" = "Economic growth and creating jobs should be prioritized over environmental protection",
-  "Pro Private ownership" = "All businesses and industries should be owned privately",
-  "Anti Regulations" = "There is too much red-tape and the government should not interfere with businesses and industries",
-  "Pro Public ownership" = "The government should own most large businesses and industries",
-  "Pro Regulations" = "Regardless of ownership, the government should pass strong regulations and implement them",
-  "Displacement risk(nuclear)" = "Nuclear energy is leading to displacement of people from their land",
-  "Spoils Natural Beauty(nuclear)" = "Nuclear energy spoils the natural beauty of the landscape",
-  "Pollution risk(nuclear)" = "Nuclear energy increases pollution of air/water/land",
-  "Health risk(nuclear)" = "Nuclear energy poses a great risk to the health of people living around it",
-  "Job opportunities(nuclear)" = "Nuclear energy will bring jobs to the local community",
-  "Community pride(nuclear)" = "I would be proud if my community used nuclear energy",
-  "National pride(nuclear)" = "Nuclear energy is a mark of pride for our nation",
-  "National development(nuclear)" = "Nuclear energy pushes forward the country's development",
-  "Local prosperity(nuclear)" = "Nuclear energy brings economic prosperity to the surrounding regions",
-  "Reliance on government(nuclear)" = "I don't like the idea that I have to rely on the government for electricity from nuclear energy"
+  "WEALTHLIM" = "A limit should be put to how much wealth a person can amass",
+  "MECHANISATION" = "Rapid mechanization of work is taking away jobs from workers in this country",
+  "DECISIONDECEN" = "Local politicians shouldn't have to ask permission from the central government to implement policies",
+  "DECISIONCEN" = "Laws and policies would be implemented more smoothly if more power lay with the central government",
+  "INDUSTRYLARGE" = "Large scale industries are required for the development of the country that will benefit everyone",
+  "INDUSTRYSMALL" = "Large corporations are destroying the local industries in India and benefiting only a handful of people",
+  "ECONOMYGLOBAL" = "Foreign companies have led to a range of benefits for the Indian people and society",
+  "ECONOMYLOCAL" = "India would be better off if foreign companies didn't come to here",
+  "ENVOVERDEV" = "Polluting industries that spoil the environment should be shut down even if it costs people their jobs",
+  "DEVOVERENV" = "Economic growth and creating jobs should be prioritized over environmental protection",
+  "OWNERPVT" = "All businesses and industries should be owned privately",
+  "OWNERNOREG" = "There is too much red-tape and the government should not interfere with businesses and industries",
+  "OWNERPUB" = "The government should own most large businesses and industries",
+  "OWNERREG" = "Regardless of ownership, the government should pass strong regulations and implement them",
+  "DISPLACENUCLEAR" = "Nuclear energy is leading to displacement of people from their land",
+  "BEAUTYNUCLEAR" = "Nuclear energy spoils the natural beauty of the landscape",
+  "POLLUTENUCLEAR" = "Nuclear energy increases pollution of air/water/land",
+  "HEALTHNUCLEAR" = "Nuclear energy poses a great risk to the health of people living around it",
+  "JOBSNUCLEAR" = "Nuclear energy will bring jobs to the local community",
+  "PRIDENUCLEAR" = "I would be proud if my community used nuclear energy",
+  "NPRIDENUCLEAR" = "Nuclear energy is a mark of pride for our nation",
+  "DEVNUCLEAR" = "Nuclear energy pushes forward the country's development",
+  "PROSPERNUCLEAR" = "Nuclear energy brings economic prosperity to the surrounding regions",
+  "RELYNUCLEAR" = "I don't like the idea that I have to rely on the government for electricity from nuclear energy"
 )
@@
   rename(Ndevelop = MR1, Pdevelop = MR2, Items= item) %>%
-  flex("2 factor solution", col_widths = list(Items = 4.5, code = 1.5))
-
-```
-
-\elandscape
+  dplyr::mutate(code = case_when(
+    code == "WEALTHLIM" ~ "Limits on Wealth",
+    code == "MECHANISATION" ~ "Anti Mechanisation of work",
+    code == "DECISIONDECEN" ~ "Pro Decentralisation",
+    code == "DECISIONCEN" ~ "Pro Centralisation",
+    code == "INDUSTRYLARGE" ~ "Pro Large Industries",
+    code == "INDUSTRYSMALL" ~ "Anti Large Industries",
+    code == "ECONOMYGLOBAL" ~ "Pro Globaleconomy",
+    code == "ECONOMYLOCAL" ~ "Pro Localeconomy",
+    code == "ENVOVERDEV" ~ "Environment over Development",
+    code == "DEVOVERENV" ~ "Development over Environment",
+    code == "OWNERPVT" ~ "Pro Private ownership",
+    code == "OWNERNOREG" ~ "Anti Regulations",
+    code == "OWNERPUB" ~ "Pro Public ownership",
+    code == "OWNERREG" ~ "Pro Regulations",
+    code == "DISPLACENUCLEAR" ~ "Displacement risk(nuclear)",
+    code == "POLLUTENUCLEAR" ~ "Pollution risk(nuclear)",
+    code == "HEALTHNUCLEAR" ~ "Health risk(nuclear)",
+    code == "JOBSNUCLEAR" ~ "Job opportunities(nuclear)",
+    code == "BEAUTYNUCLEAR" ~ "Spoils Natural Beauty(nuclear)",
+    code == "PROSPERNUCLEAR" ~ "Local prosperity(nuclear)",
+    code == "PRIDENUCLEAR" ~ "Community pride(nuclear)",
+    code == "NPRIDENUCLEAR" ~ "National pride(nuclear)",
+    code == "DEVNUCLEAR" ~ "National development(nuclear)",
+    code == "RELYNUCLEAR" ~ "Less Reliance on government(nuclear)",
+    TRUE ~ code # Default case to keep original value if no match
+  )) %>%
+  flex("Table 3: EFA on Eco-Pol Values Scale", col_widths = list(Items = 4.5, code = 1.5))
+
+```
 
@@
     mutate(across(where(is.numeric), round, 3)) %>%
-    flex("Eigenvalues and Variance Explained for Combined Scale (2 Factor Solution)")
+    flex("Table 4: Eigenvalues and Variance Explained Eco-Pol Scale")
 ```
@@
 kahannuclear <- fct_scores%>%
-  rename(Hierarchy_Egalitarian = MR1, Communitarian = MR2)
+  rename(Egalitarian = MR1, Communitarian = MR2)
 
@@
 #pred[, "Pdevelop"] <- 0
-#pred[, "Hierarchy_Egalitarian"] <- 0
+#pred[, "Egalitarian"] <- 0
 #pred[, "Communitarian"] <- 0
@@
 
-nuclearIVmice2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian, data = allformice)
-
-nuclearIVmice3 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian + Pdevelop + Ndevelop, data = allformice)
+nuclearIVmice2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian, data = allformice)
+
+nuclearIVmice3 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformice)
 
@@
 kahannuclear2 <- fct_scoresk2%>%
-  rename(Hierarchy_Egalitarian = MR1, Communitarian = MR2)
+  rename(Egalitarian = MR1, Communitarian = MR2)
 
@@
 
-nuclearIVmiceimp22 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian, data = allformice2)
-
-nuclearIVmiceimp23 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian + Pdevelop + Ndevelop, data = allformice2)
+nuclearIVmiceimp22 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian, data = allformice2)
+
+nuclearIVmiceimp23 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformice2)
 
@@
 kahannuclear3 <- fct_scoresk3%>%
-  rename(Hierarchy_Egalitarian = MR1, Communitarian = MR2)
+  rename(Egalitarian = MR1, Communitarian = MR2)
 
@@
 
-nuclearIVmiceimp32 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian, data = allformice3)
-
-nuclearIVmiceimp33 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian + Pdevelop + Ndevelop, data = allformice3)
+nuclearIVmiceimp32 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian, data = allformice3)
+
+nuclearIVmiceimp33 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformice3)
 
@@
 kahannuclear4 <- fct_scoresk4%>%
-  rename(Hierarchy_Egalitarian = MR1, Communitarian = MR2)
+  rename(Egalitarian = MR1, Communitarian = MR2)
 
@@
 
-nuclearIVmiceimp24 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian, data = allformice4)
-
-nuclearIVmiceimp34 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian + Pdevelop + Ndevelop, data = allformice4)
+nuclearIVmiceimp24 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian, data = allformice4)
+
+nuclearIVmiceimp34 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformice4)
 
@@
 kahannuclearfinal <- nkahanfinal%>%
-  rename(Hierarchy_Egalitarian = MR1, Communitarian = MR2)
+  rename(Egalitarian = MR1, Communitarian = MR2)
 
@@
 
+allformicefinal$State <- factor(allformicefinal$State, levels = c("Maharashtra","West Bengal" ,"Rajasthan","Tamil Nadu",  "Uttar Pradesh"))
+
 nuclearfinal <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age, data = allformicefinal)
@@
 
-nuclearfinal3 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian, data = allformicefinal)
-
-nuclearfinal4 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian + Pdevelop + Ndevelop, data = allformicefinal)
-
-#summary(nuclearfinal)
-#summary(nuclearfinal2)
-#summary(nuclearfinal3)
-#summary(nuclearfinal4)
-```
-
+nuclearfinal3 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian, data = allformicefinal)
+
+nuclearfinal4 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformicefinal)
+
+summary(nuclearfinal)
+summary(nuclearfinal2)
+summary(nuclearfinal3)
+summary(nuclearfinal4)
+
+aic_values <- AIC(nuclearfinal, nuclearfinal2, nuclearfinal3, nuclearfinal4)
+
+print(aic_values)
+
+bic_values <- BIC(nuclearfinal, nuclearfinal2, nuclearfinal3, nuclearfinal4)
+
+print(bic_values)
+
+```
+
+# correlation table
+
+```{r}
+
+nforcor <- allformicefinal %>%
+           dplyr::select(Risky_Nuclear, Communitarian , Egalitarian , Pdevelop , Ndevelop)
+
+cor.plot(nforcor)
+```
+
+# interaction vars
+
+```{r}
+
+nuclearinterac <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian*State + Egalitarian*State + Pdevelop*State + Ndevelop*State , data = allformicefinal)
+
+summary(nuclearinterac)
+
+```
 \newpage
-\blandscape
 
@@
 
-cat("\\begingroup")
-cat("\\setlength{\\tabcolsep}{1pt}")
-cat("\\renewcommand{\\arraystretch}{0.7}")
-stargazer(nuclearfinal, nuclearfinal2, nuclearfinal3, nuclearfinal4,
-          title = "4 linear models: Perceived Risk of Nuclear Energy",
-          type = "latex"
+#cat("\\begingroup")
+#cat("\\setlength{\\tabcolsep}{1pt}")
+#cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer(nuclearfinal, nuclearfinal2, nuclearfinal3, nuclearfinal4, nuclearinterac,
+          title = "Table 6: 5 linear models: Perceived Risk of Nuclear Energy",
+          type = "text"
 )
-cat("\\endgroup")
-
-```
-
-\elandscape
+#cat("\\endgroup")
+
+```
 

### 2024-03-17 withmice.Rmd
mifa for coal and solar

@@
 
+# NUCLEAR2 : only charcateristics of tech
+
+```{r, echo=FALSE}
+
+ecopoln2 <- formice1 %>%
+  dplyr::select(
+    DISPLACENUCLEAR,  POLLUTENUCLEAR, HEALTHNUCLEAR, JOBSNUCLEAR, BEAUTYNUCLEAR,
+    PRIDENUCLEAR, NPRIDENUCLEAR, DEVNUCLEAR, PROSPERNUCLEAR,
+    RELYNUCLEAR, age, urban_rural, gender, caste, religion, State
+  )
+
+str(ecopoln2)
+md.pattern(ecopoln2) #the variables with missing values:
+
+mcar_test(data=ecopoln2)
+```
+
+# Nuclear2 : Mifa for new eco-pol value scale
+
+```{r, echo=FALSE}
+
+miecopoln2 <- mifa(data= ecopoln2,
+                cov_vars = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
+                m=10,
+                n_pc= 2:4,
+                ci = "fieller", 
+                n_boot=1000,
+                print = FALSE,
+                progress= TRUE, 
+                seed = 528,)
+
+miecopoln2
+
+ecopolfitn2 <- psych::fa(miecopoln2$cov_combined, nfactors = 2, rotate = "varimax")
+
+print.psych(ecopolfitn2, sort= TRUE, cut= 0.4)
+
+```
+
+# Solar : MAR condition and missing data pattern
+
+```{r, echo=FALSE}
+
+ecopols <- formice1 %>%
+  dplyr::select(
+    DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE,
+    ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV,DEVOVERENV, OWNERPVT, OWNERPUB,
+    OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION,
+    DISPLACESOLAR,  POLLUTESOLAR, HEALTHSOLAR, JOBSSOLAR, BEAUTYSOLAR,
+    PRIDESOLAR, NPRIDESOLAR, DEVSOLAR, PROSPERSOLAR,
+    RELYSOLAR,age, urban_rural, gender, caste, religion, State
+  )
+
+md.pattern(ecopols) #the variables with missing values:
+
+mcar_test(data=ecopols)
+```
+
+# Solar : Mifa for new eco-pol value scale
+
+```{r, echo=FALSE}
+
+miecopols <- mifa(data= ecopols,
+                cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
+                m=5,
+                n_pc= 1:2,
+                ci = "fieller", 
+                n_boot=1000,
+                print = FALSE,
+                progress= TRUE, 
+                seed = 528,)
+
+miecopols
+
+ecopolfits <- psych::fa(miecopols$cov_combined, nfactors = 2, rotate = "varimax")
+
+print.psych(ecopolfits, sort= TRUE, cut= 0.4)
+
+```
+
+# Solar 2 : only charcateristics of tech
+
+```{r, echo=FALSE}
+
+ecopols2 <- formice1 %>%
+  dplyr::select(
+    DISPLACESOLAR,  POLLUTESOLAR, HEALTHSOLAR, JOBSSOLAR, BEAUTYSOLAR,
+    PRIDESOLAR, NPRIDESOLAR, DEVSOLAR, PROSPERSOLAR,
+    RELYSOLAR, age, urban_rural, gender, caste, religion, State
+  )
+
+str(ecopols2)
+md.pattern(ecopols2) #the variables with missing values:
+
+mcar_test(data=ecopols2)
+```
+
+# SOLAR2 : Mifa for new eco-pol value scale
+
+```{r, echo=FALSE}
+
+miecopols2 <- mifa(data= ecopols2,
+                cov_vars = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
+                m=10,
+                n_pc= 2:4,
+                ci = "fieller", 
+                n_boot=1000,
+                print = FALSE,
+                progress= TRUE, 
+                seed = 528,)
+
+miecopols2
+
+ecopolfits2 <- psych::fa(miecopols2$cov_combined, nfactors = 2, rotate = "varimax")
+
+print.psych(ecopolfits2, sort= TRUE, cut= 0.4)
+
+```
+
+# Solar: Mifa with CFA
+
+```{r}
+
+## CFA on ecopol vars for solar energy
+
+ecopols_2fa <- '
+  Ndevelop =~ DEVSOLAR + PRIDESOLAR + NPRIDESOLAR + PROSPERSOLAR + JOBSSOLAR 
+  Pdevelop =~ HEALTHSOLAR + BEAUTYSOLAR + DISPLACESOLAR + POLLUTESOLAR + ENVOVERDEV
+'
+
+secopol_cfa <- cfa(ecopols_2fa, data = miecopols$cov_combined, std.lv = TRUE)
+summary(secopol_cfa, fit.measure= TRUE, standardized = TRUE)
+
+```
+
+# COAL : MAR condition and missing data pattern
+
+```{r, echo=FALSE}
+
+ecopolc <- formice1 %>%
+  dplyr::select(
+    DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE,
+    ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV,DEVOVERENV, OWNERPVT, OWNERPUB,
+    OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION,
+    DISPLACECOAL,  POLLUTECOAL, HEALTHCOAL, JOBSCOAL, BEAUTYCOAL,
+    PRIDECOAL, NPRIDECOAL, DEVCOAL, PROSPERCOAL,
+    RELYCOAL,age, urban_rural, gender, caste, religion, State
+  )
+
+md.pattern(ecopolc) #the variables with missing values:
+
+mcar_test(data=ecopolc)
+```
+
+# Coal : Mifa for new eco-pol value scale
+
+```{r, echo=FALSE}
+
+miecopolc <- mifa(data= ecopolc,
+                cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
+                m=50,
+                n_pc= 2:4,
+                ci = "fieller", 
+                n_boot=1000,
+                print = FALSE,
+                progress= TRUE, 
+                seed = 528,)
+
+miecopolc
+
+ecopolfitc <- psych::fa(miecopolc$cov_combined, nfactors = 3, rotate = "varimax")
+
+print.psych(ecopolfitc, sort= TRUE, cut= 0.4)
+
+```
+
+# COAL2 : only charcateristics of tech
+
+```{r, echo=FALSE}
+
+ecopolc2 <- formice1 %>%
+  dplyr::select(
+    DISPLACECOAL,  POLLUTECOAL, HEALTHCOAL, JOBSCOAL, BEAUTYCOAL,
+    PRIDECOAL, NPRIDECOAL, DEVCOAL, PROSPERCOAL,
+    RELYCOAL,age, urban_rural, gender, caste, religion, State
+  )
+
+md.pattern(ecopolc2) #the variables with missing values:
+
+mcar_test(data=ecopolc2)
+```
+
+# Coal2 : Mifa for new eco-pol value scale
+
+```{r, echo=FALSE}
+
+miecopolc2 <- mifa(data= ecopolc2,
+                cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
+                m=5,
+                n_pc= 2:4,
+                ci = "fieller", 
+                n_boot=1000,
+                print = FALSE,
+                progress= TRUE, 
+                seed = 528,)
+
+miecopolc2
+
+ecopolfitc2 <- psych::fa(miecopolc2$cov_combined, nfactors = 2, rotate = "varimax")
+
+print.psych(ecopolfitc2, sort= TRUE, cut= 0.4)
+
+```
+
+```{r}
+
+cor.plot(ecopolc %>% dplyr::select(-c("age", "gender", "caste", "State", "urban_rural", "religion")))
+```
+
+# Coal: Mifa with CFA
+
+```{r}
+
+# (DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE,ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV,DEVOVERENV, OWNERPVT, OWNERPUB,OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION,DISPLACECOAL,  POLLUTECOAL, HEALTHCOAL, JOBSCOAL, BEAUTYCOAL,PRIDECOAL, NPRIDECOAL, DEVCOAL, PROSPERCOAL,RELYCOAL)
+
+## CFA on ecopol vars for coal
+
+ecopolc_2fa <- '
+  Pride =~ PRIDECOAL + NPRIDECOAL + DEVOVERENV +  DECISIONCEN + OWNERPVT + DECISIONCEN  + OWNERNOREG + ECONOMYGLOBAL
+  Social Costs =~ BEAUTYCOAL + POLLUTECOAL + HEALTHCOAL
+  Social Costs2 =~ OWNERPUB + ENVOVERDEV + DISPLACECOAL
+
+'
+
+cecopol_cfa <- cfa(ecopolc_2fa, data = miecopolc$cov_combined, std.lv = TRUE)
+summary(cecopol_cfa, fit.measure= TRUE, standardized = TRUE)
+
+```
+
 ```{r, echo=FALSE}

### 2024-03-23 miceEXTRA.Rmd
put extra imputation tests etc for mice into another file

--- 2024-03-13 withmice.Rmd
@@
 ---
-title: "models with mice"
-header-includes:
-- \usepackage{pdflscape}
-- \newcommand{\blandscape}{\begin{landscape}}
-- \newcommand{\elandscape}{\end{landscape}}
-output:
-  pdf_document: 
-    toc: yes
-    toc_depth: 2
-    keep_tex: yes
-  keep_md: yes
+title: "miceEXTRA"
+output: html_document
 ---
 
-```{r load packages, warning = FALSE, message = FALSE, echo=FALSE}
-  knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-
-suppressPackageStartupMessages(library(tidyverse))
-suppressPackageStartupMessages(library(readxl))
-suppressPackageStartupMessages(library(dplyr))
-suppressPackageStartupMessages(library(tidyr))
-suppressPackageStartupMessages(library(ggplot2))
-suppressPackageStartupMessages(library(lavaan))
-suppressPackageStartupMessages(library(tsibble))
-suppressPackageStartupMessages(library(DT))
-suppressPackageStartupMessages(library(knitr))
-suppressPackageStartupMessages(library(psych)) 
-suppressPackageStartupMessages(library(foreign))
-suppressPackageStartupMessages(library(MASS))
-suppressPackageStartupMessages(library(Hmisc))
-suppressPackageStartupMessages(library(reshape2))
-suppressPackageStartupMessages(library(naniar))
-suppressPackageStartupMessages(library(mice))
-
-```
-
-```{r setup, echo=FALSE}
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-
-moduletwo <- read_excel(here::here("thesis_surveydata/political_factors_complete.xlsx"))
-module2 <- data.frame(moduletwo)
-module2[module2 == "Rather not say/ Don't know"] <- "Rather not say/Don't know"
-
-# loaded data set for module 2 eco -pol variables and removes the rows with question number and question text
-```
-
-```{r, eval =TRUE, echo=FALSE}
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
-codedmodule2 <- module2 %>%
-
-#remove row 1
-  filter(!row_number() %in% c(1,2)) %>%
-
-# replace risky likert scale with numbers
-  mutate_at(vars(starts_with("Risky")), funs(case_when(. =="Not at all risky" ~ 1, 
-                                                       . =="Slightly risky" ~ 2, 
-                                                       . =="Moderately risky" ~ 3, 
-                                                       . =="Very risky" ~ 4, 
-                                                       . =="Extremely risky" ~ 5))) %>%
-
-# replace beneficial likert scale with numbers  
-  mutate_at(vars(starts_with("Ben")), funs(case_when(. =="Not at all beneficial" ~ 1,
-                                                     . =="Slightly beneficial" ~ 2,
-                                                     . =="Moderately beneficial" ~ 3,
-                                                     . =="Very beneficial" ~ 4,
-                                                     . =="Extremely beneficial" ~ 5 ))) %>%
-
-# replace nuclear acceptance likert scale with numbers
-  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
-                                                                        . == "Somewhat disagree" ~ 2,
-                                                                        . == "Neither agree nor disagree" ~3,
-                                                                        . == "Somewhat agree" ~ 4,
-                                                                        . == "Strongly agree" ~ 5))) %>%
-
-# code likert scale for variables for Kahan scale into numbers
-  mutate_at(vars(starts_with (c("K_S","K_E","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE","DEV","PROSPER", "RELY"))), funs(case_when(. == "Strongly disagree" ~ 1, 
-               . == "Somewhat disagree" ~ 2,
-               . == "Neither agree nor disagree" ~3,
-               . == "Somewhat agree" ~ 4,
-               . == "Strongly agree" ~ 5))) %>%
-
-# NO reverse code for likert scale for variables for Kahan scale into numbers
-  mutate_at(vars(starts_with (c("K_H","K_I"))), funs(case_when(. == "Strongly disagree" ~ 1, 
-                                                               . == "Somewhat disagree" ~ 2,
-                                                               . == "Neither agree nor disagree" ~3,
-                                                               . == "Somewhat agree" ~ 4,
-                                                               . == "Strongly agree" ~ 5))) %>%
-
-# code eco-pol scale variables into numbers
-mutate_at(vars(SYSTEMDEMO,SYSTEMRELIGION,SYSTEMTECHNO,SYSTEMTOTAL,WEALTHLIM,MECHANISATION,DECISIONDECEN,INDUSTRYSMALL,ECONOMYLOCAL,ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(.
-== "Strongly disagree" ~ 1,
-                        . == "Somewhat disagree" ~ 2,
-                        . == "Neither agree nor disagree" ~3,
-                        . == "Somewhat agree" ~ 4,
-                        . == "Strongly agree" ~ 5))) %>%
-
-# NO reverse code eco-pol scale variables into numbers 
- mutate_at(vars(DECISIONCEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG), funs(case_when(. == "Strongly disagree" ~ 1, 
-                                                                                                         . == "Somewhat disagree" ~ 2,
-                                                                                                         . == "Neither agree nor disagree" ~3,
-                                                                                                         . == "Somewhat agree" ~ 4,
-                                                                                                         . == "Strongly agree" ~ 5))) %>%
-  mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
-  mutate_all(~ifelse(. == "West bengal", "West Bengal", .))%>%
-  mutate_all(~ifelse(. == "WEST BENGAL", "West Bengal", .))%>%
-  mutate_all(~ifelse(. == "Up", "Uttar Pradesh", .))%>%
-  mutate_all(~ifelse(. == "Tamilnadu", "Tamil Nadu", .))%>%
-  mutate_all(~ifelse(. == "UP", "Uttar Pradesh", .))
-
-```
-
-# barplot of demographics
-
-```{r, echo=FALSE}
-
-library(dplyr)
-library(tidyr)
-
-demobar <- codedmodule2 %>% 
-  dplyr::select("State", "Language", "age", "urban_rural", "gender", "caste" ,"religion") %>%
-              mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
-              mutate_all(~ifelse(. == "OBC", "Other Backward Classes (OBC)", .))%>%
-              mutate_all(~ifelse(. == "SC", "Scheduled caste (SC)", .))%>%
-              mutate_all(~ifelse(. == "ST", "Scheduled tribe (ST)", .))%>%
-              mutate_all(~ifelse(. == "MAR", "Marathi", .))%>%
-              mutate_all(~ifelse(. == "TA", "Tamil", .)) %>%
-              mutate_all(~ifelse(. == "EN", "English", .))%>%
-              mutate_all(~ifelse(. == "BN", "Bengali", .))%>%
-              mutate_all(~ifelse(. == "MAR", "Marathi", .))%>%
-              mutate_all(~ifelse(. == "HI", "Hindi", .))%>%
-              na.omit()
-
-#changing factor levels for each variable from high to low n
-
-demobar$State <- factor(demobar$State, levels = c("Maharashtra","Rajasthan", "West Bengal" , "Tamil Nadu", "Uttar Pradesh"))
-demobar$Language <- factor(demobar$Language, levels = c("Hindi","Marathi","Bengali","Tamil", "English"))
-demobar$age <- factor(demobar$age, levels = c( "18-24 years old" ,  "25-34 years old","35-44 years old", "45-54 years old", "55-64 years old","65-74 years old","75 years or older"  ))
-demobar$urban_rural <- factor(demobar$urban_rural, levels = c("Rural","Urban"))
-demobar$gender <- factor(demobar$gender, levels = c("Male","Female"))
-demobar$caste <- factor(demobar$caste, levels = c("Scheduled tribe (ST)", "Scheduled caste (SC)", "Other Backward Classes (OBC)", "General","Brahmin","Rather not say/Don't know"))
-demobar$religion <- factor(demobar$religion, levels = c("Hinduism", "Islam", "Christanity","Buddhism","Agnostism/ Atheism","Other (Please mention)"))
-
-```
-
-```{r, echo=FALSE, fig.width=11, fig.height=14, out.width='80%', out.height='80%'}
-
-# Loading the required libraries
-library(tidyverse)
-library(gridExtra)
-library(scales)
-
-# Function to create bar plot
-create_bar_plot <- function(data, variable_name, palette_name) {
-  factor_levels <- levels(demobar[[variable_name]])
-  data %>%
-    filter(Variable == variable_name) %>%
-    mutate(Category = factor(Category, levels = factor_levels)) %>%
-    ggplot(aes(y = "", x = Percentage, fill = Category)) +
-    geom_bar(position = "fill", stat = "identity", width = 1) +
-    geom_text(aes(label = paste0(round(Percentage, 0), "%")), 
-              position =  position_fill(vjust = 0.5)) +
-    scale_x_continuous(labels = percent) +
-    labs(y = NULL, x = "Percentage", fill = variable_name) +
-    theme_classic() +
-    theme(axis.text.y = element_blank(), strip.text = element_text(size = 10), legend.position = "top") +
-    scale_fill_brewer(palette = palette_name)
-}
-
-# Gather data to long format and calculate counts and percentages
-df_barplot <- demobar %>%
-  gather(Variable, Category) %>%
-  group_by(Variable, Category) %>%
-  filter(!is.na(Category)) %>%
-  summarise(n = n()) %>%
-  mutate(Percentage = n / sum(n) * 100)
-
-# Create separate plots for each variable
-plot_state <- create_bar_plot(df_barplot, "State", "Spectral")
-plot_language <- create_bar_plot(df_barplot, "Language", "Paired")
-plot_age <- create_bar_plot(df_barplot, "age", "Set3")
-plot_urban_rural <- create_bar_plot(df_barplot, "urban_rural", "Dark2")
-plot_gender <- create_bar_plot(df_barplot, "gender", "Pastel1")
-plot_caste <- create_bar_plot(df_barplot, "caste", "Set1")
-plot_religion <- create_bar_plot(df_barplot, "religion", "Set2")
-
-# Combine the plots with spacing
-combined_plot <- gridExtra::arrangeGrob(plot_state, plot_language, plot_age, plot_urban_rural, plot_gender, plot_caste, plot_religion, ncol = 1, heights = c(1, 1, 1, 1, 1, 1, 1))
-
-# Print the combined plot
-grid::grid.newpage()
-grid::grid.draw(combined_plot)
-
-```
-
-# Can do something with accept, reject and reluctantly accept.
-
-```{r, echo=FALSE}
-
-## Can do something with accept, reject and reluctantly accept.
-
-n_acceptreject<- codedmodule2 %>%
-                dplyr::select("N_accept", "N_reluctantlyaccept", "N_reject")
-
-summary(n_acceptreject)
-```
-
-# missing data pattern and MCAR
-
-```{r, echo=FALSE}
-
-formice1 <- codedmodule2[, grep("State|age|urban_rural|gender|caste|religion|Solar|SOLAR|Nuclear|NUCLEAR|Coal|COAL|K_S|K_E|K_H|K_I|WEALTHLIM|MECHANISATION|DECISIONDECEN|INDUSTRYSMALL|ECONOMYLOCAL|ENVOVERDEV|DEVOVERENV|OWNERPUB|OWNERREG|DECISIONCEN|INDUSTRYLARGE|ECONOMYGLOBAL|OWNERPVT|OWNERNOREG", names(codedmodule2))]%>%
-        dplyr::select(-c("Language", "Risky_INDSolar", "Ben_INDSolar", "religiontext")) %>%
-          mutate(across(age, ~factor(.x, ordered = TRUE)))%>%  
-          mutate(across(urban_rural:religion, ~factor(.x, ordered = FALSE)))%>%
-          mutate(across(State, ~factor(.x, ordered = FALSE))) %>%
-          mutate(Uppercaste = ifelse(caste %in% c('Brahmin', 'General'), 1, 0)) %>%
-          mutate(Male = ifelse(gender == 'Male', 1, 0))%>%
-          mutate(Hindu = ifelse(religion == 'Hinduism', 1, 0))%>%
-           mutate(Age = case_when(
-                                  age == "18-24 years old" ~ 1,
-                                  age == "25-34 years old" ~ 2,
-                                  age == "35-44 years old" ~ 3,
-                                  age == "45-54 years old" ~ 4,
-                                  age == "55-64 years old" ~ 5,
-                                  age == "65-74 years old" ~ 6,
-                                  age == "75 years or older" ~ 7))
-
-#dplyr:: select(starts_with (c("State", "age", "urban_rural", "gender", "caste", "religion","Risky_Solar", "Risky_Nuclear", "Risky_Coal", "Ben_Solar","Ben_Nuclear","Ben_Coal","K_S","K_E","K_H","K_I", "DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE","DEV", "PROSPER", "RELY", "WEALTHLIM", "MECHANISATION", "DECISIONDECEN", "INDUSTRYSMALL", "ECONOMYLOCAL", "ENVOVERDEV", "OWNERPUB", "OWNERREG", "DECISIONCEN","INDUSTRYLARGE","ECONOMYGLOBAL","OWNERPVT","OWNERNOREG" )))
-
-library(dplyr)
-
-formice <- formice1 %>%
-  mutate(across(Risky_Solar:age, ~factor(.x, ordered = TRUE)))%>%
-  mutate(across(urban_rural:religion, ~factor(.x, ordered = FALSE)))%>%
-  mutate(across(State, ~factor(.x, ordered = FALSE)))
-
-#str(formice)
-summary(formice)
-
-# litte's MCAR test
-
-mcar_test(data= codedmodule2)
-
-# p value = 1, which means MAR condition is met.
-
-```
-
-# Kahan scale: MAR condition and missing data pattern 
-```{r, echo=FALSE}
-
-kahanall <- codedmodule2 %>%
-          dplyr::select(c(starts_with("K_"), "age", "gender", "caste", "State", "urban_rural", "religion")) %>%
-          mutate(across(gender:religion, ~factor(.x, ordered = FALSE))) %>%
-          mutate(across(age, ~factor(.x, ordered = TRUE)))
-
-str(kahanall)
-
-md.pattern(kahanall) #the variables with missing values: K_SHARM K_IPROTECT K_IPRIVACY K_SPROTECT K_SLIMCHOI K_IINTRFER K_HEQUAL K_HREVDIS1
-
-mcar_test(data=kahanall) # p values is less than 0.05 - the condition for MCAR is not met
-
-# dataset with missing variables to compare and test group comaprisons
-
-MARkahan <- codedmodule2 %>%
-          dplyr::select(c("K_SHARM", "K_IPROTECT", "K_IPRIVACY", "K_SPROTECT", "K_SLIMCHOI", "K_IINTRFER",  "K_HEQUAL", "K_HREVDIS1" , "age", "gender", "caste", "State", "urban_rural", "religion"))
-
-MARkahan$K_SHARM_MAR <- MARkahan$K_SHARM
-
-MARkahan$K_IPROTECT_MAR <- MARkahan$K_IPROTECT
-
-MARkahan$K_SPROTECT_MAR <- MARkahan$K_SPROTECT
-
-MARkahan$K_SLIMCHOI_MAR <- MARkahan$K_SLIMCHOI
-
-library(finalfit)
-
-# "K_SHARM" = "(C)Sometimes the government needs to make laws that keep people from hurting themselves.",
-explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
-dependent = "K_SHARM_MAR"
-MARkahan %>% 
-  missing_compare(dependent, explanatory) %>% 
-    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
-        caption = "comparisons between values of responders (Not missing) and 
-        non-responders (Missing) on the K_SHARM variable.")
-
-#   "K_IPROTECT" = "(I)It’s not the government’s business to try to protect people from themselves."
-explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
-dependent = "K_IPROTECT_MAR"
-MARkahan %>% 
-  missing_compare(dependent, explanatory) %>% 
-    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
-        caption = "comparisons between values of responders (Not missing) and 
-        non-responders (Missing) on the K_IPROTECT variable.")
-
-#  "K_SPROTECT" = "(C)The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.",
-explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
-dependent = "K_SPROTECT_MAR"
-MARkahan %>% 
-  missing_compare(dependent, explanatory) %>% 
-    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
-        caption = "comparisons between values of responders (Not missing) and 
-        non-responders (Missing) on the K_SPROTECT variable.")
-
-#  "K_SLIMCHOI" = "(C)The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.",
-explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
-dependent = "K_SLIMCHOI_MAR"
-MARkahan %>% 
-  missing_compare(dependent, explanatory) %>% 
-    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
-        caption = "comparisons between values of responders (Not missing) and 
-        non-responders (Missing) on the K_SPROTECT variable.")
-
-```
-
-## Mifa for Kahan scale 
-```{r, echo =FALSE}
-
-library(mifa)
-library(mice)
-library(psych)
-
-mikahan <- mifa(data= kahanall,
-                cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
-                m = 50,
-                n_pc= 2:4,
-                ci = "fieller", 
-                n_boot=1000,
-                print = FALSE,
-                progress= TRUE, 
-                seed = 427,)
-
-mikahan
-
-library(psych)
-
-fit <- psych::fa(mikahan$cov_combined, nfactors = 2, rotate = "varimax")
-
-print.psych(fit, sort= TRUE, cut= 0.4)
-
-```
-
-\blandscape
-
-## Pretty Table: FA Kahan
-
-```{r, echo=FALSE}
-
-library(flextable)
-
-flex <- function(data, title=NULL, col_widths=NULL) {
-  tbl <- flextable(data) %>%
-           #padding(padding = 1, part = "all") %>%
-           #set_table_properties(layout = "autofit") %>%
-           fontsize(size=10, part="all") %>%
-           set_caption(title, 
-                       autonum = officer::run_autonum(seq_id = "tab", 
-                                                      pre_label = "Table ", 
-                                                      post_label = "\n", 
-                                                      bkm = "anytable"))
-
-  # If col_widths is provided, set column widths
-  if(!is.null(col_widths)) {
-    for(col in names(col_widths)){
-      tbl <- width(tbl, j = col, width = col_widths[[col]])
-    }
-  }
-
-  return(tbl)
-}
-
-rename_map <- c(
-  "K_SHARM" = " (C)Sometimes the government needs to make laws that keep people from hurting themselves.",
-"K_SLIMCHOI" = "(C)The government should put limits on the choices individuals can make so they don’t get in the way of what’s
-good for society.",
-"K_SPROTECT" = "(C)The government should do more to advance society’s goals, even if that means limiting the freedom and
-choices of individuals.",
-"K_HEQUAL" = "(H)We have gone too far in pushing equal rights in this country.",
-"K_ERADEQ1" = "(E)We need to dramatically reduce inequalities between the rich and the poor.",
-"K_EWEALTH" = "(E)Our society would be better off if the distribution of wealth was more equal.",
-"K_ERADEQ2" = "(E)We need to dramatically reduce inequalities between men and women.",
-"K_HREVDIS1" = "(H)Nowadays it seems like there is just as much discrimination against upper castes as there is against Dalits.",
-"K_EDISCRIM" = "(E)Discrimination against minorities is still a very serious problem in our society.",
-"K_IINTRFER" = "(I)The government interferes far too much in our everyday lives.",
-"K_IPRIVACY" = "(I)The government should stop telling people how to live their lives.",
-"K_IPROTECT" = "(I)It’s not the government’s business to try to protect people from themselves."
-)
-
-fa_table <- function(x, cut) {
-  #get sorted loadings
-  loadings <- fa.sort(x)$loadings %>% round(3)
-  #suppress loadings
-  loadings[loadings > -cut & loadings < cut] <- ""
-  #get additional info  
-  add_info <- cbind(x$communalities, 
-                    x$uniquenesses,
-                    x$complexity) %>%
-    # make it a data frame
-    as.data.frame() %>%
-    # column names
-    rename("Communality" = V1,
-           "Uniqueness" = V2,
-           "Complexity" = V3) %>%
-    #get the item names from the vector
-    rownames_to_column("item")
-
-  #build table
-  loadings %>%
-    unclass() %>%
-    as.data.frame() %>%
-    rownames_to_column("item") %>%
-    left_join(add_info) %>%
-    mutate(
-      item = if_else(item %in% names(rename_map), rename_map[item], item),
-      code = names(rename_map)[match(item, rename_map)], # extracting short form
-      across(where(is.numeric), round, 3)
-    ) %>%
-    dplyr::select(code, everything()) # reorder columns to bring code to the front
-}
-
-fa_table(fit , .4) %>%
-  rename(Hierarchy_Egalitarianism = MR1, Communitarianism = MR2, Items= item, Code= code) %>%
-  flex("EFA: Kahan Scale", col_widths = list(Items = 4.5, Code = 1))
-
-```
-
-\elandscape
-
-```{r, echo = FALSE}
-fit[["Vaccounted"]] %>%
-  as.data.frame() %>%
-  rownames_to_column("Property") %>%
-  rename(Hierarchy_Egalitarianism = MR1, Communitarianism = MR2) %>%
-    mutate(across(where(is.numeric), round, 3)) %>%
-    flex("Eigenvalues and Variance Explained for Kahan Scale")
-```
-
-## checking merging of imputations  : kahan scale
-
-```{r, echo=FALSE}
-
-kahan_imp <- mice(kahanall, m =5, maxit =30,  seed = 427, print = FALSE)
-
-kahan_imp$chainMean
-
-```
-
-#Kahan Factor scores: mean across all imputations
-
-```{r, echo=FALSE}
-
-kahanallscores <- mice::complete(mice::mice(kahanall, m = 5, seed = 427, print = FALSE), "broad")
-
-kahanallscores <- kahanallscores %>%dplyr::select(-(contains(c("age", "urban_rural", "gender","caste","religion", "State"))))
-
-str(kahanallscores)
-
-nkahanall <- kahanallscores %>%
-  rowwise() %>%
-  mutate( K_EWEALTH_mean = mean(c_across(starts_with("K_EWEALTH"))),
-    K_IINTRFER_mean = mean(c_across(starts_with("K_IINTRFER"))),
-    K_IPRIVACY_mean = mean(c_across(starts_with("K_IPRIVACY"))),
-    K_SHARM_mean = mean(c_across(starts_with("K_SHARM"))),
-    K_IPROTECT_mean = mean(c_across(starts_with("K_IPROTECT"))),
-    K_SLIMCHOI_mean = mean(c_across(starts_with("K_SLIMCHOI"))),
-    K_SPROTECT_mean = mean(c_across(starts_with("K_SPROTECT"))),
-    K_HEQUAL_mean = mean(c_across(starts_with("K_HEQUAL"))),
-    K_HREVDIS1_mean = mean(c_across(starts_with("K_HREVDIS1"))),
-    K_EDISCRIM_mean = mean(c_across(starts_with("K_EDISCRIM"))),
-    K_ERADEQ1_mean = mean(c_across(starts_with("K_ERADEQ1"))),
-    K_ERADEQ2_mean = mean(c_across(starts_with("K_ERADEQ2")))
-  ) %>%
-  ungroup()%>%
-  dplyr::select(contains("_mean")) %>%
-   rename_with(~ gsub("_mean$", "", .x))
-
-nkahanfinal <- data.frame(factor.scores(nkahanall[, 1:12], fit)$scores)
-
-```
+# EXTRA
 
@@
 summary(complete_data_5)
-```
-
-# Eco-pol scale: MAR condition and missing data pattern
-
-```{r, echo=FALSE}
-
-ecopoln <- formice1 %>%
-  dplyr::select(
-    DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE,
-    ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV,DEVOVERENV, OWNERPVT, OWNERPUB,
-    OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION,
-    DISPLACENUCLEAR,  POLLUTENUCLEAR, HEALTHNUCLEAR, JOBSNUCLEAR, BEAUTYNUCLEAR,
-    PRIDENUCLEAR, NPRIDENUCLEAR, DEVNUCLEAR, PROSPERNUCLEAR,
-    RELYNUCLEAR,age, urban_rural, gender, caste, religion, State
-  )
-
-md.pattern(ecopoln) #the variables with missing values: PRIDENUCLEAR PROSPERNUCLEAR JOBSNUCLEAR HEALTHNUCLEAR BEAUTYNUCLEAR POLLUTENUCLEAR DISPLACENUCLEAR RELYNUCLEAR
-
-mcar_test(data=ecopoln) # p values is less than 0.76 - the condition for MCAR is met
-
-# dataset with missing variables to compare and test group comaprisons
-
-MARecopol <- codedmodule2 %>%
-          dplyr::select(c(DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE,
-    ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV, OWNERPVT, OWNERPUB,
-    OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION,
-    DISPLACENUCLEAR,  POLLUTENUCLEAR, HEALTHNUCLEAR, JOBSNUCLEAR, BEAUTYNUCLEAR,
-    PRIDENUCLEAR, NPRIDENUCLEAR, DEVNUCLEAR, PROSPERNUCLEAR,
-    RELYNUCLEAR,age, urban_rural, gender, caste, religion, State))
-
-MARecopol$JOBSNUCLEAR_MAR <- MARecopol$JOBSNUCLEAR
-
-MARecopol$PRIDENUCLEAR_MAR <- MARecopol$PRIDENUCLEAR
-
-library(finalfit)
-
-# JOBSNUCLEAR
-explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
-dependent = "JOBSNUCLEAR_MAR"
-MARecopol %>% 
-  missing_compare(dependent, explanatory) %>% 
-    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
-        caption = "comparisons between values of responders (Not missing) and 
-        non-responders (Missing) on the JOBSNUCLEAR variable.")
-
-# PRIDENUCLEAR
-explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
-dependent = "PRIDENUCLEAR_MAR"
-MARecopol %>% 
-  missing_compare(dependent, explanatory) %>% 
-    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
-        caption = "comparisons between values of responders (Not missing) and 
-        non-responders (Missing) on the PRIDENUCLEAR variable.") 
-```
-
-## Mifa for new eco-pol value scale : Nuclear energy
-
-```{r, echo=FALSE}
-
-miecopol <- mifa(data= ecopoln,
-                cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
-                n_pc= 2:4,
-                ci = "fieller", 
-                n_boot=1000,
-                print = FALSE,
-                progress= TRUE, 
-                seed = 429,)
-
-miecopol
-
-ecopolfit2 <- psych::fa(miecopol$cov_combined, nfactors = 2, rotate = "varimax")
-
-print.psych(ecopolfit2, sort= TRUE, cut= 0.4)
-
-```
-
-#Ecopol Factor scores: mean across all imputations
-
-```{r, echo=FALSE}
-
-ecopolallscores <- mice::complete(mice::mice(ecopoln, m = 5, seed = 429, print = FALSE), "broad")
-
-ecopolallscores <- ecopolallscores %>%dplyr::select(-(contains(c("age", "urban_rural", "gender","caste","religion", "State"))))
-
-#str(ecopolallscores)
-
-necopol <- ecopolallscores %>%
-  rowwise() %>%
-  mutate(DEVNUCLEAR_mean = mean(c_across(starts_with("DEVNUCLEAR"))),
-         PROSPERNUCLEAR_mean = mean(c_across(starts_with("PROSPERNUCLEAR"))),
-         NPRIDENUCLEAR_mean = mean(c_across(starts_with("NPRIDENUCLEAR"))),
-         PRIDENUCLEAR_mean = mean(c_across(starts_with("PRIDENUCLEAR"))),
-         JOBSNUCLEAR_mean = mean(c_across(starts_with("JOBSNUCLEAR"))),
-         ECONOMYGLOBAL_mean = mean(c_across(starts_with("ECONOMYGLOBAL"))),
-         WEALTHLIM_mean = mean(c_across(starts_with("WEALTHLIM"))),
-         INDUSTRYLARGE_mean = mean(c_across(starts_with("INDUSTRYLARGE"))),
-         DECISIONCEN_mean = mean(c_across(starts_with("DECISIONCEN"))),
-         MECHANISATION_mean = mean(c_across(starts_with("MECHANISATION"))),
-         OWNERNOREG_mean = mean(c_across(starts_with("OWNERNOREG"))),
-         INDUSTRYSMALL_mean = mean(c_across(starts_with("INDUSTRYSMALL"))),
-         DEVOVERENV_mean = mean(c_across(starts_with("DEVOVERENV"))),
-         OWNERPVT_mean = mean(c_across(starts_with("OWNERPVT"))),
-         RELYNUCLEAR_mean = mean(c_across(starts_with("RELYNUCLEAR"))),
-         BEAUTYNUCLEAR_mean = mean(c_across(starts_with("BEAUTYNUCLEAR"))),
-         HEALTHNUCLEAR_mean = mean(c_across(starts_with("HEALTHNUCLEAR"))),
-         POLLUTENUCLEAR_mean = mean(c_across(starts_with("POLLUTENUCLEAR"))),
-         DISPLACENUCLEAR_mean = mean(c_across(starts_with("DISPLACENUCLEAR"))),
-         ENVOVERDEV_mean = mean(c_across(starts_with("ENVOVERDEV"))),
-         OWNERPUB_mean = mean(c_across(starts_with("OWNERPUB"))),
-         OWNERREG_mean = mean(c_across(starts_with("OWNERREG"))),
-         DECISIONDECEN_mean = mean(c_across(starts_with("DECISIONDECEN"))),
-         ECONOMYLOCAL_mean = mean(c_across(starts_with("ECONOMYLOCAL")))
-  ) %>%
-  ungroup()%>%
-  dplyr::select(contains("_mean")) %>%
-   rename_with(~ gsub("_mean$", "", .x))
-
-necopolfinal <- data.frame(factor.scores(necopol[, 1:24], ecopolfit2)$scores)
-
-```
-
-# Eco-pol: Radar map
-
-```{r, echo=FALSE}
-library(ggplot2)
-library(fmsb)
-
-nrow(ecopolfit2$loadings)
-
-# Extract the loadings
-loadings_matrix4 <- ecopolfit2$loadings[1:24, ]
-
-loadings_df2 <- as.data.frame(as.matrix(loadings_matrix4))
-
-# Adding rownames to the dataframe as a new column
-loadings_df2 <- loadings_df2 %>%
-  rownames_to_column(var = "variable")
-
-# Pivot to longer format first
-long_loadings_df2 <- loadings_df2 %>%
-  pivot_longer(cols = c(MR1, MR2), names_to = "Factors", values_to = "value")
-
-# Pivot the longer format to wide format
-wide_loadings_df2 <- long_loadings_df2 %>%
-  pivot_wider(names_from = variable, values_from = value) %>%
-  mutate(Factors = case_when(
-    Factors == "MR1" ~ "Nationalist Development (Ndevelop)",
-    Factors == "MR2" ~ "People Centered Development (Pdevelop)",
-    TRUE ~ Factors
-  )) %>%
-  column_to_rownames("Factors")
-
-# Define the variable ranges: maximum and minimum
-max_min2 <- data.frame(
-  DEVNUCLEAR = c(0.8, -0.6), PROSPERNUCLEAR = c(0.8, -0.6), NPRIDENUCLEAR = c(0.8, -0.6), PRIDENUCLEAR = c(0.8, -0.6),     JOBSNUCLEAR = c(0.8, -0.6), ECONOMYGLOBAL = c(0.8, -0.6), WEALTHLIM = c(0.8, -0.6), INDUSTRYLARGE = c(0.8, -0.6),   DECISIONCEN = c(0.8, -0.6), MECHANISATION = c(0.8, -0.6), OWNERNOREG = c(0.8, -0.6), INDUSTRYSMALL = c(0.8, -0.6), DEVOVERENV = c(0.8, -0.6), OWNERPVT = c(0.8, -0.6), RELYNUCLEAR = c(0.8, -0.6), BEAUTYNUCLEAR = c(0.8, -0.6), HEALTHNUCLEAR = c(0.8, -0.6), POLLUTENUCLEAR = c(0.8, -0.6), DISPLACENUCLEAR = c(0.8, -0.6), DECISIONDECEN = c(0.8, -0.6),
-ECONOMYLOCAL = c(0.8, -0.6), ENVOVERDEV = c(0.8, -0.6), OWNERPUB = c(0.8, -0.6), OWNERREG = c(0.8, -0.6)   
-)
-rownames(max_min2) <- c("Max", "Min")
-
-# Assuming you have a dataframe 'exam_scores' with matching column names
-# Bind the variable ranges to the data
-
-radar4 <- rbind(max_min2, wide_loadings_df2) %>%
-    rename(
-      "National development(nuclear)" = "DEVNUCLEAR",
-      "Local prosperity(nuclear)" = "PROSPERNUCLEAR",
-      "National pride(nuclear)" = "NPRIDENUCLEAR",
-      "Community pride(nuclear)" = "PRIDENUCLEAR",
-      "Job opportunities(nuclear)" = "JOBSNUCLEAR",
-      "Pro Globaleconomy" = "ECONOMYGLOBAL",
-      "Limits on Wealth " = "WEALTHLIM",
-      "Pro Large Industries" = "INDUSTRYLARGE",
-      "Pro Centralisation" = "DECISIONCEN",
-      "Anti Mechanisation of work" = "MECHANISATION",
-      "Anti Regulations" = "OWNERNOREG",
-      "Anti Large Industries " = "INDUSTRYSMALL",
-      "Development over Environment" = "DEVOVERENV",
-      "Pro Private ownership " = "OWNERPVT",
-      "Reliance on government(nuclear)" = "RELYNUCLEAR",
-      "Spoils Natural Beauty(nuclear)" = "BEAUTYNUCLEAR",
-      "Health risk(nuclear)" = "HEALTHNUCLEAR",
-      "Pollution risk(nuclear) " = "POLLUTENUCLEAR",
-      "Displacement risk(nuclear)" = "DISPLACENUCLEAR",
-      "Environment over Development" = "ENVOVERDEV",
-      "Pro Public ownership" = "OWNERPUB",
-      "Pro Regulations" = "OWNERREG",
-      "Pro Decentralisation" = "DECISIONDECEN",
-      "Pro Localeconomy" = "ECONOMYLOCAL",
-    )
-
-```
-
-```{r, echo=FALSE, fig.width=15, fig.height=7, out.width='70', out.height='70'}
-library(fmsb)
-
-create_beautiful_radarchart <- function(data, color = "#00AFBB", 
-                                        vlabels = colnames(data), vlcex = 0.7,
-                                        caxislabels = NULL, title = NULL, ...){
-  radarchart(
-    data, axistype = 1,
-    # Customize the polygon
-    pcol = color, pfcol = scales::alpha(color, 0.7), plwd = 2, plty = 1,
-    centerzero=FALSE,
-    # Customize the grid
-    cglcol = "black", cglty = 1, cglwd = 2,
-    # Customize the axis
-    axislabcol = "black", cexc = 1.5, # Increase label size for axis
-    # Variable labels
-    vlcex = vlcex, vlabels = vlabels, vlpos = 0.98,
-    seg = 7, caxislabels = caxislabels, title = title, 
-    # Increase title size
-    cex.main = 4,
-    ...
-  )
-}
-
-# Reduce plot margin using par()
-op <- par(mar = c(7, 3, 3, 3))
-# Create the radar charts
-create_beautiful_radarchart(
-  data = radar4, caxislabels = c(-0.6, -0.4, -0.2, 0, 0.2, 0.4, 0.6, 0.8),
-  color = c( "#F97D09","#00AFBB"),
-  vlcex = 1.1
-)
-
-# Add an horizontal legend
-legend(
-  x = "bottomright", legend = rownames(radar4[-c(1,2),]), horiz = TRUE,
-  bty = "n", pch = 20 , col = c("#F97D09","#00AFBB"),
-  text.col = "black", cex = 1.5, pt.cex = 3,
-  inset = c(0, 0)
-  )
-par(op)
-
-```
-
-# Pretty table attempt 1
-
-\blandscape
-# FA on Combined Scale (2 Factor Solution): People Centered Development and Nationalist Development 
-## Nuclear Energy: EFA on Combined Scale (2 Factor Solution)
-
-```{r, echo=FALSE}
-
-library(flextable)
-
-flex <- function(data, title=NULL, col_widths=NULL) {
-  tbl <- flextable(data) %>%
-           #padding(padding = 1, part = "all") %>%
-           #set_table_properties(layout = "autofit") %>%
-           fontsize(size=10, part="all") %>%
-           set_caption(title, 
-                       autonum = officer::run_autonum(seq_id = "tab", 
-                                                      pre_label = "Table ", 
-                                                      post_label = "\n", 
-                                                      bkm = "anytable"))
-
-  # If col_widths is provided, set column widths
-  if(!is.null(col_widths)) {
-    for(col in names(col_widths)){
-      tbl <- width(tbl, j = col, width = col_widths[[col]])
-    }
-  }
-
-  return(tbl)
-}
-
-rename_map2 <- c(
-  "Limits on Wealth" = "A limit should be put to how much wealth a person can amass",
-  "Anti Mechanisation of work" = "Rapid mechanization of work is taking away jobs from workers in this country",
-  "Pro Decentralisation" = "Local politicians shouldn't have to ask permission from the central government to implement policies",
-  "Pro Centralisation" = "Laws and policies would be implemented more smoothly if more power lay with the central government",
-  "Pro Large Industries" = "Large scale industries are required for the development of the country that will benefit everyone",
-  "Anti Large Industries" = "Large corporations are destroying the local industries in India and benefiting only a handful of people",
-  "Pro Globaleconomy" = "Foreign companies have led to a range of benefits for the Indian people and society",
-  "Pro Localeconomy" = "India would be better off if foreign companies didn't come to here",
-  "Environment over Development" = "Polluting industries that spoil the environment should be shut down even if it costs people their jobs",
-  "Development over Environment" = "Economic growth and creating jobs should be prioritized over environmental protection",
-  "Pro Private ownership" = "All businesses and industries should be owned privately",
-  "Anti Regulations" = "There is too much red-tape and the government should not interfere with businesses and industries",
-  "Pro Public ownership" = "The government should own most large businesses and industries",
-  "Pro Regulations" = "Regardless of ownership, the government should pass strong regulations and implement them",
-  "Displacement risk(nuclear)" = "Nuclear energy is leading to displacement of people from their land",
-  "Spoils Natural Beauty(nuclear)" = "Nuclear energy spoils the natural beauty of the landscape",
-  "Pollution risk(nuclear)" = "Nuclear energy increases pollution of air/water/land",
-  "Health risk(nuclear)" = "Nuclear energy poses a great risk to the health of people living around it",
-  "Job opportunities(nuclear)" = "Nuclear energy will bring jobs to the local community",
-  "Community pride(nuclear)" = "I would be proud if my community used nuclear energy",
-  "National pride(nuclear)" = "Nuclear energy is a mark of pride for our nation",
-  "National development(nuclear)" = "Nuclear energy pushes forward the country's development",
-  "Local prosperity(nuclear)" = "Nuclear energy brings economic prosperity to the surrounding regions",
-  "Reliance on government(nuclear)" = "I don't like the idea that I have to rely on the government for electricity from nuclear energy"
-)
-
-fa_table <- function(x, cut) {
-  #get sorted loadings
-  loadings <- fa.sort(x)$loadings %>% round(3)
-  #suppress loadings
-  loadings[loadings > -cut & loadings < cut] <- ""
-  #get additional info  
-  add_info <- cbind(x$communalities, 
-                    x$uniquenesses,
-                    x$complexity) %>%
-    # make it a data frame
-    as.data.frame() %>%
-    # column names
-    rename("Communality" = V1,
-           "Uniqueness" = V2,
-           "Complexity" = V3) %>%
-    #get the item names from the vector
-    rownames_to_column("item")
-
-  #build table
-  loadings %>%
-    unclass() %>%
-    as.data.frame() %>%
-    rownames_to_column("item") %>%
-    left_join(add_info) %>%
-    mutate(
-      item = if_else(item %in% names(rename_map2), rename_map2[item], item),
-      code = names(rename_map2)[match(item, rename_map2)], # extracting short form
-      across(where(is.numeric), round, 3)
-    ) %>%
-    dplyr::select(code, everything()) # reorder columns to bring code to the front
-}
-
-fa_table(ecopolfit2, .4) %>%
-  rename(Ndevelop = MR1, Pdevelop = MR2, Items= item) %>%
-  flex("2 factor solution", col_widths = list(Items = 4.5, code = 1.5))
-
-```
-
-\elandscape
-
-```{r, echo = FALSE}
-ecopolfit2[["Vaccounted"]] %>%
-  as.data.frame() %>%
-  rownames_to_column("Property") %>%
-  rename(Ndevelop = MR1, Pdevelop = MR2) %>%
-    mutate(across(where(is.numeric), round, 3)) %>%
-    flex("Eigenvalues and Variance Explained for Combined Scale (2 Factor Solution)")
 ```
@@
 
-## State Ns before MIFA
+## LMs with 1st imputed datasets from FAs
 
 ```{r, echo=FALSE}
-Statenacheck1 <- allformice%>%
-  na.omit()%>%
-  dplyr::select(State)
 
-summary(Statenacheck1)
+nuclearIVmice <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformice)
+
+nuclearIVmice2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian, data = allformice)
+
+nuclearIVmice3 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformice)
+
+summary(nuclearIVmice)
+summary(nuclearIVmice2)
+summary(nuclearIVmice3)
+
+```
+
+## binding dataset - 2nd imputation
+
+```{r, echo=FALSE}
+
+ecopolnuclear2 <- fct_scorese2 %>%
+  rename(Ndevelop = MR1, Pdevelop = MR2)
+
+kahannuclear2 <- fct_scoresk2%>%
+  rename(Egalitarian = MR1, Communitarian = MR2)
+
+allformice2<- cbind(formice1,ecopolnuclear2, kahannuclear2)
+
+```
+
+## LMs with second imputation 
+```{r, echo=FALSE}
+
+nuclearIVmiceimp2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformice2)
+
+nuclearIVmiceimp22 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian, data = allformice2)
+
+nuclearIVmiceimp23 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformice2)
+
+summary(nuclearIVmiceimp2)
+summary(nuclearIVmiceimp22)
+summary(nuclearIVmiceimp23)
+
+```
+
+## binding dataset - 3rd imputation
+
+```{r, echo=FALSE}
+
+ecopolnuclear3 <- fct_scorese3 %>%
+  rename(Ndevelop = MR1, Pdevelop = MR2)
+
+kahannuclear3 <- fct_scoresk3%>%
+  rename(Egalitarian = MR1, Communitarian = MR2)
+
+allformice3<- cbind(formice1,ecopolnuclear3, kahannuclear3)
+
+```
+
+## LMs with third imputation 
+```{r, echo=FALSE}
+
+nuclearIVmiceimp3 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformice3)
+
+nuclearIVmiceimp32 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian, data = allformice3)
+
+nuclearIVmiceimp33 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformice3)
+
+summary(nuclearIVmiceimp3)
+summary(nuclearIVmiceimp32)
+summary(nuclearIVmiceimp33)
+
+```
+
+## binding dataset - 4th imputation
+
+```{r, echo=FALSE}
+
+ecopolnuclear4 <- fct_scorese4 %>%
+  rename(Ndevelop = MR1, Pdevelop = MR2)
+
+kahannuclear4 <- fct_scoresk4%>%
+  rename(Egalitarian = MR1, Communitarian = MR2)
+
+allformice4<- cbind(formice1, ecopolnuclear4, kahannuclear4)
+
+```
+
+## LMs with fourth imputation 
+```{r, echo=FALSE}
+
+nuclearIVmiceimp4 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformice4)
+
+nuclearIVmiceimp24 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian, data = allformice4)
+
+nuclearIVmiceimp34 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformice4)
+
+summary(nuclearIVmiceimp4)
+summary(nuclearIVmiceimp24)
+summary(nuclearIVmiceimp34)
+
 ```
@@
 ```
-
-## State Ns after MIFA on two scales
-
-```{r, echo=FALSE}
-
-nuclear_missing <- allformice %>% dplyr::select(Risky_Nuclear,Uppercaste, Male, Hindu, urban_rural, Age, State)%>%
-  na.omit()
-
-summary(nuclear_missing)
-
-```
-
-## LMs with 1st imputed datasets from FAs
-
-```{r, echo=FALSE}
-
-nuclearIVmice <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformice)
-
-nuclearIVmice2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian, data = allformice)
-
-nuclearIVmice3 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian + Pdevelop + Ndevelop, data = allformice)
-
-summary(nuclearIVmice)
-summary(nuclearIVmice2)
-summary(nuclearIVmice3)
-
-```
-
-## binding dataset - 2nd imputation
-
-```{r, echo=FALSE}
-
-ecopolnuclear2 <- fct_scorese2 %>%
-  rename(Ndevelop = MR1, Pdevelop = MR2)
-
-kahannuclear2 <- fct_scoresk2%>%
-  rename(Hierarchy_Egalitarian = MR1, Communitarian = MR2)
-
-allformice2<- cbind(formice1,ecopolnuclear2, kahannuclear2)
-
-```
-
-## LMs with second imputation 
-```{r, echo=FALSE}
-
-nuclearIVmiceimp2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformice2)
-
-nuclearIVmiceimp22 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian, data = allformice2)
-
-nuclearIVmiceimp23 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian + Pdevelop + Ndevelop, data = allformice2)
-
-summary(nuclearIVmiceimp2)
-summary(nuclearIVmiceimp22)
-summary(nuclearIVmiceimp23)
-
-```
-
-## binding dataset - 3rd imputation
-
-```{r, echo=FALSE}
-
-ecopolnuclear3 <- fct_scorese3 %>%
-  rename(Ndevelop = MR1, Pdevelop = MR2)
-
-kahannuclear3 <- fct_scoresk3%>%
-  rename(Hierarchy_Egalitarian = MR1, Communitarian = MR2)
-
-allformice3<- cbind(formice1,ecopolnuclear3, kahannuclear3)
-
-```
-
-## LMs with third imputation 
-```{r, echo=FALSE}
-
-nuclearIVmiceimp3 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformice3)
-
-nuclearIVmiceimp32 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian, data = allformice3)
-
-nuclearIVmiceimp33 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian + Pdevelop + Ndevelop, data = allformice3)
-
-summary(nuclearIVmiceimp3)
-summary(nuclearIVmiceimp32)
-summary(nuclearIVmiceimp33)
-
-```
-
-## binding dataset - 4th imputation
-
-```{r, echo=FALSE}
-
-ecopolnuclear4 <- fct_scorese4 %>%
-  rename(Ndevelop = MR1, Pdevelop = MR2)
-
-kahannuclear4 <- fct_scoresk4%>%
-  rename(Hierarchy_Egalitarian = MR1, Communitarian = MR2)
-
-allformice4<- cbind(formice1, ecopolnuclear4, kahannuclear4)
-
-```
-
-## LMs with fourth imputation 
-```{r, echo=FALSE}
-
-nuclearIVmiceimp4 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformice4)
-
-nuclearIVmiceimp24 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian, data = allformice4)
-
-nuclearIVmiceimp34 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian + Pdevelop + Ndevelop, data = allformice4)
-
-summary(nuclearIVmiceimp4)
-summary(nuclearIVmiceimp24)
-summary(nuclearIVmiceimp34)
-
-```
-
-# Mean across imputations
-
-## Binding datasets
-
-```{r, echo = FALSE}
-
-# binding the imputed  factor analysis scores for kahan scale and eco-pol value scale to the larger dataset codedmodule2
-
-ecopolnuclearfinal <- necopolfinal %>%
-  rename(Ndevelop = MR1, Pdevelop = MR2)
-
-kahannuclearfinal <- nkahanfinal%>%
-  rename(Hierarchy_Egalitarian = MR1, Communitarian = MR2)
-
-allformicefinal<- cbind(formice1,ecopolnuclearfinal, kahannuclearfinal)
-
-```
-
-## LMs with final imputed datasets from FAs
-
-```{r, echo=FALSE}
-
-nuclearfinal <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age, data = allformicefinal)
-
-nuclearfinal2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformicefinal)
-
-nuclearfinal3 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian, data = allformicefinal)
-
-nuclearfinal4 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian + Pdevelop + Ndevelop, data = allformicefinal)
-
-#summary(nuclearfinal)
-#summary(nuclearfinal2)
-#summary(nuclearfinal3)
-#summary(nuclearfinal4)
-```
-
-\newpage
-\blandscape
-
-```{r, echo=FALSE, results='asis'}
-library(stargazer)
-
-cat("\\begingroup")
-cat("\\setlength{\\tabcolsep}{1pt}")
-cat("\\renewcommand{\\arraystretch}{0.7}")
-stargazer(nuclearfinal, nuclearfinal2, nuclearfinal3, nuclearfinal4,
-          title = "4 linear models: Perceived Risk of Nuclear Energy",
-          type = "latex"
-)
-cat("\\endgroup")
-
-```
-
-\elandscape
 

### 2024-03-23 withmice.Rmd
put extra imputation tests etc for mice into another file

@@
 
-# missing data pattern and MCAR
+# FORMICE DATASET
 
@@
 
-mcar_test(data= codedmodule2)
-
+#mcar_test(data= codedmodule2)
 # p value = 1, which means MAR condition is met.
@@
 
-# Kahan scale: MAR condition and missing data pattern 
+# Kahan scale
+
+## MAR condition and missing data pattern 
 ```{r, echo=FALSE}
@@
 
-## Mifa for Kahan scale 
+## Mifa
 ```{r, echo =FALSE}
@@
 
-## Pretty Table: FA Kahan
+## EFA Pretty Table
 
@@
 
-## checking merging of imputations  : kahan scale
+## merging of imputation
 
@@
 
-#Kahan Factor scores: mean across all imputations
+## Kahan Factor scores (mean across all imputations)
 
@@
 
-## Kahan corelation table
+## corelation table
 ```{r}
@@
 
-# Kahan alpha test
+## Alpha test
 
@@
 
-## Kahan: factor scores from 1st imputed dataset
-```{r, echo=FALSE}
-
-# extracting factor scores from mifa for 1st imputed dataset
-
-data_imp <- mice::complete(mice::mice(kahanall, 1, print = FALSE))
-
-fct_scores <- data.frame(factor.scores(data_imp[, 1:12], fit)$scores)
-
-plot(kahan_imp)
-
-```
-
-## Kahan: factor scores from second imputed dataset
-```{r, echo=FALSE}
-
-data_impk2 <- mice::complete(mice::mice(kahanall, 2, print = FALSE))
-
-fct_scoresk2 <- data.frame(factor.scores(data_impk2[, 1:12], fit)$scores)
-
-```
-
-## Kahan: factor scores from third imputed dataset
-```{r, echo=FALSE}
-
-data_impk3 <- mice::complete(mice::mice(kahanall, 3, print = FALSE))
-
-fct_scoresk3 <- data.frame(factor.scores(data_impk3[, 1:12], fit)$scores)
-
-```
-
-## Kahan: factor scores from fourth imputed dataset
-```{r, echo=FALSE}
-
-data_impk4 <- mice::complete(mice::mice(kahanall, 4, print = FALSE))
-
-fct_scoresk4 <- data.frame(factor.scores(data_impk4[, 1:12], fit)$scores)
-
-```
-
-## Kahan: factor scores from fifth imputed dataset
-```{r, echo=FALSE}
-
-data_impk5 <- mice::complete(mice::mice(kahanall, 5, print = FALSE))
-
-fct_scoresk5 <- data.frame(factor.scores(data_impk5[, 1:12], fit)$scores)
-
-```
-
-## are imputations plausible: Kahan scale - are values plausible ?
-
-yes all value are whole numbers between 1 and 5
-
-```{r, echo=FALSE}
-
-summary(mikahan)
-
-str(data_imp)
-names(mikahan)
-
-mikahan$mids
-
-complete_data_first <- complete(mikahan$mids, 1)
-
-summary(complete_data_first)
-
-complete_data_2 <- complete(mikahan$mids, 2)
-
-summary(complete_data_2)
-
-complete_data_3 <- complete(mikahan$mids, 3)
-
-summary(complete_data_3)
-
-complete_data_4 <- complete(mikahan$mids, 4)
-
-summary(complete_data_4)
-
-complete_data_5 <- complete(mikahan$mids, 5)
-
-summary(complete_data_5)
-```
-
-# Eco-pol scale: MAR condition and missing data pattern
+# Nuclear: Eco-pol scale
+
+## MAR condition and missing data pattern
 
@@
 
-## Mifa for new eco-pol value scale : Nuclear energy
+## Mifa
 
@@
 
-#Ecopol Factor scores: mean across all imputations
+## Factor Scores (mean across all imputations)
 
@@
 
-# Eco-pol alpha test
+## Alpha test
 
@@
 
-# Eco-pol: Radar map
+## Radar map
 
@@
 
-# Pretty table: Nuclear EFA
+## Pretty table: Nuclear EFA
 
@@
 
-```{r, echo=FALSE}
-
-# Extracting factors from first imputed dataset
-
-data_imp2 <- mice::complete(mice::mice(ecopoln, 1, print = FALSE))
-
-fct_scores2 <- data.frame(factor.scores(data_imp2[, 1:24], ecopolfit2)$scores)
-
-```
-
-##  eco-pol scale : Factor scores from 2nd imputation
-```{r, echo=FALSE}
-
-data_impe2 <- mice::complete(mice::mice(ecopoln, 2, print = FALSE))
-
-fct_scorese2 <- data.frame(factor.scores(data_impe2[, 1:24], ecopolfit2)$scores)
-
-```
-
-##  eco-pol scale : Factor scores from 3rd imputation
-```{r, echo=FALSE}
-
-data_impe3 <- mice::complete(mice::mice(ecopoln, 3, print = FALSE))
-
-fct_scorese3 <- data.frame(factor.scores(data_impe3[, 1:24], ecopolfit2)$scores)
-
-```
-
-##  eco-pol scale : Factor scores from 4th imputation
-```{r, echo=FALSE}
-
-data_impe4 <- mice::complete(mice::mice(ecopoln, 4, print = FALSE))
-
-fct_scorese4 <- data.frame(factor.scores(data_impe4[, 1:24], ecopolfit2)$scores)
-
-```
-
-##  eco-pol scale : Factor scores from 5th imputation
-```{r, echo=FALSE}
-
-data_impe5 <- mice::complete(mice::mice(ecopoln, 5, print = FALSE))
-
-fct_scorese5 <- data.frame(factor.scores(data_impe5[, 1:24], ecopolfit2)$scores)
-
-```
-
-## Are imputations plausible : Eco-pol scale
-
-yes, imputations are pluasible- all natural numbers between 1 and 5
-
-```{r, echo=FALSE}
-
-summary(miecopol)
-names(miecopol)
-
-miecopol$mids
-
-complete_ecopol_first <- complete(miecopol$mids, 1)
-
-summary(complete_ecopol_first)
-
-complete_ecopol_2 <- complete(miecopol$mids, 2)
-
-summary(complete_ecopol_2)
-
-complete_ecopol_3 <- complete(miecopol$mids, 3)
-
-summary(complete_ecopol_3)
-
-complete_ecopol_4 <- complete(miecopol$mids, 4)
-
-summary(complete_ecopol_4)
-
-complete_ecopol_5 <- complete(miecopol$mids, 5)
-
-summary(complete_ecopol_5)
-
-```
-
-# Checking consistency of LM coefficients across 5 imputed datasets 
-coefficients and LMs are fairly consistent
-
-## Binding datasets: 1st imputation
-
-```{r, echo = FALSE}
-
-# binding the imputed  factor analysis scores for kahan scale and eco-pol value scale to the larger dataset codedmodule2
-
-ecopolnuclear <- fct_scores2 %>%
-  rename(Ndevelop = MR1, Pdevelop = MR2)
-
-kahannuclear <- fct_scores%>%
-  rename(Egalitarian = MR1, Communitarian = MR2)
-
-allformice<- cbind(formice1,ecopolnuclear, kahannuclear)
-
-```
-
-## State Ns before MIFA
+# State Ns before MIFA
 
@@
 summary(Statenacheck1)
+```
+
+# State Ns after MIFA
+
+```{r, echo=FALSE}
+
+nuclear_missing <- allformice %>% dplyr::select(Risky_Nuclear,Uppercaste, Male, Hindu, urban_rural, Age, State)%>%
+  na.omit()
+
+summary(nuclear_missing)
+
+```
+
+## Nuclear: Ecopol (Mean across imputations)
+
+## Binding datasets
+
+```{r, echo = FALSE}
+
+# binding the imputed  factor analysis scores for kahan scale and eco-pol value scale to the larger dataset codedmodule2
+
+ecopolnuclearfinal <- necopolfinal %>%
+  rename(Ndevelop = MR1, Pdevelop = MR2)
+
+kahannuclearfinal <- nkahanfinal%>%
+  rename(Egalitarian = MR1, Communitarian = MR2)
+
+allformicefinal<- cbind(formice1,ecopolnuclearfinal, kahannuclearfinal)
+
+```
+
+# LMs : final imputed datasets
+
+```{r, echo=FALSE}
+
+allformicefinal$State <- factor(allformicefinal$State, levels = c("Maharashtra","West Bengal" ,"Rajasthan","Tamil Nadu",  "Uttar Pradesh"))
+
+nuclearfinal <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age, data = allformicefinal)
+
+nuclearfinal2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformicefinal)
+
+nuclearfinal3 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian, data = allformicefinal)
+
+nuclearfinal4 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformicefinal)
+
+summary(nuclearfinal)
+summary(nuclearfinal2)
+summary(nuclearfinal3)
+summary(nuclearfinal4)
+
+aic_values <- AIC(nuclearfinal, nuclearfinal2, nuclearfinal3, nuclearfinal4)
+
+print(aic_values)
+
+bic_values <- BIC(nuclearfinal, nuclearfinal2, nuclearfinal3, nuclearfinal4)
+
+print(bic_values)
+
+```
+
+# correlation table
+
+```{r}
+
+nforcor <- allformicefinal %>%
+           dplyr::select(Risky_Nuclear, Communitarian , Egalitarian , Pdevelop , Ndevelop)
+
+cor.plot(nforcor)
+```
+
+# interaction vars tablle
+
+```{r}
+
+nuclearinterac <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian*State + Egalitarian*State + Pdevelop*State + Ndevelop*State , data = allformicefinal)
+
+summary(nuclearinterac)
+
+```
+
+# Stargazer : all LMs
+
+```{r, echo=FALSE, results='asis'}
+library(stargazer)
+
+#cat("\\begingroup")
+#cat("\\setlength{\\tabcolsep}{1pt}")
+#cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer(nuclearfinal, nuclearfinal2, nuclearfinal3, nuclearfinal4, nuclearinterac,
+          title = "Table 6: 5 linear models: Perceived Risk of Nuclear Energy",
+          type = "text"
+)
+#cat("\\endgroup")
+
+```
+
+\newpage
+# Paper 2
+
+## NUCLEAR2
+
+### only charcateristics of tech
+
+```{r, echo=FALSE}
+
+ecopoln2 <- formice1 %>%
+  dplyr::select(
+    DISPLACENUCLEAR,  POLLUTENUCLEAR, HEALTHNUCLEAR, JOBSNUCLEAR, BEAUTYNUCLEAR,
+    PRIDENUCLEAR, NPRIDENUCLEAR, DEVNUCLEAR, PROSPERNUCLEAR,
+    RELYNUCLEAR, age, urban_rural, gender, caste, religion, State
+  )
+
+str(ecopoln2)
+md.pattern(ecopoln2) #the variables with missing values:
+
+mcar_test(data=ecopoln2)
+```
+
+### Nuclear2 : Mifa
+
+```{r, echo=FALSE}
+
+library(mifa)
+
+miecopoln2 <- mifa(data= ecopoln2,
+                cov_vars = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
+                m=50,
+                n_pc= 2:4,
+                ci = "fieller", 
+                n_boot=1000,
+                print = FALSE,
+                progress= TRUE, 
+                seed = 528,)
+
+miecopoln2
+
+ecopolfitn2 <- psych::fa(miecopoln2$cov_combined, nfactors = 2, rotate = "varimax")
+
+print.psych(ecopolfitn2, sort= TRUE, cut= 0.4)
+
+```
+
+### Factor Scores (mean across all imputations)
+
+```{r, echo=FALSE}
+
+ecopoln2scores <- mice::complete(mice::mice(ecopoln2, m = 50, seed = 429, print = FALSE), "broad")
+
+ecopoln2scores <- ecopoln2scores %>%dplyr::select(-(contains(c("age", "urban_rural", "gender","caste","religion", "State"))))
+
+#str(ecopolallscores)
+
+ecopoln2means <- ecopoln2scores %>%
+  rowwise() %>%
+  mutate(DEVNUCLEAR_mean = mean(c_across(starts_with("DEVNUCLEAR"))),
+         PROSPERNUCLEAR_mean = mean(c_across(starts_with("PROSPERNUCLEAR"))),
+         NPRIDENUCLEAR_mean = mean(c_across(starts_with("NPRIDENUCLEAR"))),
+         PRIDENUCLEAR_mean = mean(c_across(starts_with("PRIDENUCLEAR"))),
+         JOBSNUCLEAR_mean = mean(c_across(starts_with("JOBSNUCLEAR"))),
+         RELYNUCLEAR_mean = mean(c_across(starts_with("RELYNUCLEAR"))),
+         BEAUTYNUCLEAR_mean = mean(c_across(starts_with("BEAUTYNUCLEAR"))),
+         HEALTHNUCLEAR_mean = mean(c_across(starts_with("HEALTHNUCLEAR"))),
+         POLLUTENUCLEAR_mean = mean(c_across(starts_with("POLLUTENUCLEAR"))),
+         DISPLACENUCLEAR_mean = mean(c_across(starts_with("DISPLACENUCLEAR"))),
+  ) %>%
+  ungroup()%>%
+  dplyr::select(contains("_mean")) %>%
+   rename_with(~ gsub("_mean$", "", .x))
+
+necopol2final <- data.frame(factor.scores(ecopoln2means[, 1:10], ecopolfitn2)$scores)
+
+```
+
+### LM : Nuclear 2 and Kahan
+
+```{r}
+
+ecopoln2final <- necopol2final %>%
+  rename(DevPride = MR1, SocialCosts = MR2)
+
+kahannuclearfinal <- nkahanfinal%>%
+  rename(Egalitarian = MR1, Communitarian = MR2)
+
+n2allfinal <- cbind(formice1,ecopoln2final, kahannuclearfinal)%>%
+   mutate(Netben_Nuclear = Ben_Nuclear - Risky_Nuclear,
+         Netben_Solar = Ben_Solar - Risky_Solar,
+         Netben_Coal = Ben_Coal - Risky_Coal)
+
+nuclear2lm <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu +Age + State + DevPride + SocialCosts + Egalitarian + Communitarian, data = n2allfinal)
+
+summary(nuclear2lm)
+
+netnuclear2lm <- lm(Netben_Nuclear ~ Uppercaste + Male + Hindu +Age + State + DevPride + SocialCosts + Egalitarian + Communitarian, data = n2allfinal)
+
+summary(netnuclear2lm)
+
+bennuclear2lm <- lm(Ben_Nuclear ~ Uppercaste + Male + Hindu +Age + State + DevPride + SocialCosts + Egalitarian + Communitarian, data = n2allfinal)
+
+summary(bennuclear2lm)
+
+```
+
+## Solar
+
+### Solar : MAR condition and missing data pattern
+
+```{r, echo=FALSE}
+
+ecopols <- formice1 %>%
+  dplyr::select(
+    DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE,
+    ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV,DEVOVERENV, OWNERPVT, OWNERPUB,
+    OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION,
+    DISPLACESOLAR,  POLLUTESOLAR, HEALTHSOLAR, JOBSSOLAR, BEAUTYSOLAR,
+    PRIDESOLAR, NPRIDESOLAR, DEVSOLAR, PROSPERSOLAR,
+    RELYSOLAR,age, urban_rural, gender, caste, religion, State
+  )
+
+md.pattern(ecopols) #the variables with missing values:
+
+mcar_test(data=ecopols)
+```
+
+### Solar : Mifa for new eco-pol value scale
+
+```{r, echo=FALSE}
+
+miecopols <- mifa(data= ecopols,
+                cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
+                m=5,
+                n_pc= 1:2,
+                ci = "fieller", 
+                n_boot=1000,
+                print = FALSE,
+                progress= TRUE, 
+                seed = 528,)
+
+miecopols
+
+ecopolfits <- psych::fa(miecopols$cov_combined, nfactors = 2, rotate = "varimax")
+
+print.psych(ecopolfits, sort= TRUE, cut= 0.4)
+
+```
+
+### Solar 2 : only charcateristics of tech
+
+```{r, echo=FALSE}
+
+ecopols2 <- formice1 %>%
+  dplyr::select(
+    DISPLACESOLAR,  POLLUTESOLAR, HEALTHSOLAR, JOBSSOLAR, BEAUTYSOLAR,
+    PRIDESOLAR, NPRIDESOLAR, DEVSOLAR, PROSPERSOLAR,
+    RELYSOLAR, age, urban_rural, gender, caste, religion, State
+  )
+
+str(ecopols2)
+md.pattern(ecopols2) #the variables with missing values:
+
+mcar_test(data=ecopols2)
+```
+
+### SOLAR2 : Mifa for new eco-pol value scale
+
+```{r, echo=FALSE}
+
+miecopols2 <- mifa(data= ecopols2,
+                cov_vars = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
+                m=10,
+                n_pc= 2:4,
+                ci = "fieller", 
+                n_boot=1000,
+                print = FALSE,
+                progress= TRUE, 
+                seed = 528,)
+
+miecopols2
+
+ecopolfits2 <- psych::fa(miecopols2$cov_combined, nfactors = 2, rotate = "varimax")
+
+print.psych(ecopolfits2, sort= TRUE, cut= 0.4)
+
+```
+
+### Factor Scores (mean across all imputations)
+
+```{r, echo=FALSE}
+
+ecopols2scores <- mice::complete(mice::mice(ecopols2, m = 50, seed = 429, print = FALSE), "broad")
+
+ecopols2scores <- ecopols2scores %>%dplyr::select(-(contains(c("age", "urban_rural", "gender","caste","religion", "State"))))
+
+#str(ecopolallscores)
+
+ecopols2means <- ecopols2scores %>%
+  rowwise() %>%
+  mutate(DEVSOLAR_mean = mean(c_across(starts_with("DEVSOLAR"))),
+         PROSPERSOLAR_mean = mean(c_across(starts_with("PROSPERSOLAR"))),
+         NPRIDESOLAR_mean = mean(c_across(starts_with("NPRIDESOLAR"))),
+         PRIDESOLAR_mean = mean(c_across(starts_with("PRIDESOLAR"))),
+         JOBSSOLAR_mean = mean(c_across(starts_with("JOBSSOLAR"))),
+         RELYSOLAR_mean = mean(c_across(starts_with("RELYSOLAR"))),
+         BEAUTYSOLAR_mean = mean(c_across(starts_with("BEAUTYSOLAR"))),
+         HEALTHSOLAR_mean = mean(c_across(starts_with("HEALTHSOLAR"))),
+         POLLUTESOLAR_mean = mean(c_across(starts_with("POLLUTESOLAR"))),
+         DISPLACESOLAR_mean = mean(c_across(starts_with("DISPLACESOLAR"))),
+  ) %>%
+  ungroup()%>%
+  dplyr::select(contains("_mean")) %>%
+   rename_with(~ gsub("_mean$", "", .x))
+
+secopol2final <- data.frame(factor.scores(ecopols2means[, 1:10], ecopolfits2)$scores)
+
+```
+
+### Solar LMs
+```{r}
+
+ecopols2final <- secopol2final %>%
+  rename(DevPride = MR1, SocialCosts = MR2)
+
+kahannuclearfinal <- nkahanfinal%>%
+  rename(Egalitarian = MR1, Communitarian = MR2)
+
+s2allfinal <- cbind(formice1,ecopols2final, kahannuclearfinal)%>%
+   mutate(Netben_Nuclear = Ben_Nuclear - Risky_Nuclear,
+         Netben_Solar = Ben_Solar - Risky_Solar,
+         Netben_Coal = Ben_Coal - Risky_Coal)
+
+solar2lm <- lm(Risky_Solar ~ Uppercaste + Male + Hindu +Age + State + DevPride + SocialCosts + Egalitarian + Communitarian , data = n2allfinal)
+
+summary(solar2lm)
+
+netsolar2lm <- lm(Netben_Solar ~ Uppercaste + Male + Hindu +Age + State + DevPride + SocialCosts + Egalitarian + Communitarian, data = n2allfinal)
+
+summary(netsolar2lm)
+
+bensolar2lm <- lm(Ben_Solar ~ Uppercaste + Male + Hindu +Age + State + DevPride + SocialCosts + Egalitarian + Communitarian, data = n2allfinal)
+
+summary(bensolar2lm)
+
+```
+
+### Solar: Mifa with CFA
+
+```{r}
+
+## CFA on ecopol vars for solar energy
+
+ecopols_2fa <- '
+  Ndevelop =~ DEVSOLAR + PRIDESOLAR + NPRIDESOLAR + PROSPERSOLAR + JOBSSOLAR 
+  Pdevelop =~ HEALTHSOLAR + BEAUTYSOLAR + DISPLACESOLAR + POLLUTESOLAR + ENVOVERDEV
+'
+
+secopol_cfa <- cfa(ecopols_2fa, data = miecopols$cov_combined, std.lv = TRUE)
+summary(secopol_cfa, fit.measure= TRUE, standardized = TRUE)
+
+```
+
+# COAL : MAR condition and missing data pattern
+
+```{r, echo=FALSE}
+
+ecopolc <- formice1 %>%
+  dplyr::select(
+    DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE,
+    ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV,DEVOVERENV, OWNERPVT, OWNERPUB,
+    OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION,
+    DISPLACECOAL,  POLLUTECOAL, HEALTHCOAL, JOBSCOAL, BEAUTYCOAL,
+    PRIDECOAL, NPRIDECOAL, DEVCOAL, PROSPERCOAL,
+    RELYCOAL,age, urban_rural, gender, caste, religion, State
+  )
+
+md.pattern(ecopolc) #the variables with missing values:
+
+mcar_test(data=ecopolc)
+```
+
+# Coal : Mifa for new eco-pol value scale
+
+```{r, echo=FALSE}
+
+miecopolc <- mifa(data= ecopolc,
+                cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
+                m=50,
+                n_pc= 2:4,
+                ci = "fieller", 
+                n_boot=1000,
+                print = FALSE,
+                progress= TRUE, 
+                seed = 528,)
+
+miecopolc
+
+ecopolfitc <- psych::fa(miecopolc$cov_combined, nfactors = 3, rotate = "varimax")
+
+print.psych(ecopolfitc, sort= TRUE, cut= 0.4)
+
+```
+
+# COAL2 : only charcateristics of tech
+
+```{r, echo=FALSE}
+
+ecopolc2 <- formice1 %>%
+  dplyr::select(
+    DISPLACECOAL,  POLLUTECOAL, HEALTHCOAL, JOBSCOAL, BEAUTYCOAL,
+    PRIDECOAL, NPRIDECOAL, DEVCOAL, PROSPERCOAL,
+    RELYCOAL,age, urban_rural, gender, caste, religion, State
+  )
+
+md.pattern(ecopolc2) #the variables with missing values:
+
+mcar_test(data=ecopolc2)
+```
+
+# Coal2 : Mifa for new eco-pol value scale
+
+```{r, echo=FALSE}
+
+miecopolc2 <- mifa(data= ecopolc2,
+                cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
+                m=5,
+                n_pc= 2:4,
+                ci = "fieller", 
+                n_boot=1000,
+                print = FALSE,
+                progress= TRUE, 
+                seed = 528,)
+
+miecopolc2
+
+ecopolfitc2 <- psych::fa(miecopolc2$cov_combined, nfactors = 2, rotate = "varimax")
+
+print.psych(ecopolfitc2, sort= TRUE, cut= 0.4)
+
+```
+
+```{r}
+
+cor.plot(ecopolc %>% dplyr::select(-c("age", "gender", "caste", "State", "urban_rural", "religion")))
+```
+
+# Coal: Mifa with CFA
+
+```{r}
+
+# (DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE,ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV,DEVOVERENV, OWNERPVT, OWNERPUB,OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION,DISPLACECOAL,  POLLUTECOAL, HEALTHCOAL, JOBSCOAL, BEAUTYCOAL,PRIDECOAL, NPRIDECOAL, DEVCOAL, PROSPERCOAL,RELYCOAL)
+
+## CFA on ecopol vars for coal
+
+ecopolc_2fa <- '
+  Pride =~ PRIDECOAL + NPRIDECOAL + DEVOVERENV +  DECISIONCEN + OWNERPVT + DECISIONCEN  + OWNERNOREG + ECONOMYGLOBAL
+  Social Costs =~ BEAUTYCOAL + POLLUTECOAL + HEALTHCOAL
+  Social Costs2 =~ OWNERPUB + ENVOVERDEV + DISPLACECOAL
+
+'
+
+cecopol_cfa <- cfa(ecopolc_2fa, data = miecopolc$cov_combined, std.lv = TRUE)
+summary(cecopol_cfa, fit.measure= TRUE, standardized = TRUE)
+
+```
+
+# EXTRA
+
+## Kahan: factor scores from 1st imputed dataset
+```{r, echo=FALSE}
+
+# extracting factor scores from mifa for 1st imputed dataset
+
+data_imp <- mice::complete(mice::mice(kahanall, 1, print = FALSE))
+
+fct_scores <- data.frame(factor.scores(data_imp[, 1:12], fit)$scores)
+
+plot(kahan_imp)
+
+```
+
+## Kahan: factor scores from second imputed dataset
+```{r, echo=FALSE}
+
+data_impk2 <- mice::complete(mice::mice(kahanall, 2, print = FALSE))
+
+fct_scoresk2 <- data.frame(factor.scores(data_impk2[, 1:12], fit)$scores)
+
+```
+
+## Kahan: factor scores from third imputed dataset
+```{r, echo=FALSE}
+
+data_impk3 <- mice::complete(mice::mice(kahanall, 3, print = FALSE))
+
+fct_scoresk3 <- data.frame(factor.scores(data_impk3[, 1:12], fit)$scores)
+
+```
+
+## Kahan: factor scores from fourth imputed dataset
+```{r, echo=FALSE}
+
+data_impk4 <- mice::complete(mice::mice(kahanall, 4, print = FALSE))
+
+fct_scoresk4 <- data.frame(factor.scores(data_impk4[, 1:12], fit)$scores)
+
+```
+
+## Kahan: factor scores from fifth imputed dataset
+```{r, echo=FALSE}
+
+data_impk5 <- mice::complete(mice::mice(kahanall, 5, print = FALSE))
+
+fct_scoresk5 <- data.frame(factor.scores(data_impk5[, 1:12], fit)$scores)
+
+```
+
+## are imputations plausible: Kahan scale - are values plausible ?
+
+yes all value are whole numbers between 1 and 5
+
+```{r, echo=FALSE}
+
+summary(mikahan)
+
+str(data_imp)
+names(mikahan)
+
+mikahan$mids
+
+complete_data_first <- complete(mikahan$mids, 1)
+
+summary(complete_data_first)
+
+complete_data_2 <- complete(mikahan$mids, 2)
+
+summary(complete_data_2)
+
+complete_data_3 <- complete(mikahan$mids, 3)
+
+summary(complete_data_3)
+
+complete_data_4 <- complete(mikahan$mids, 4)
+
+summary(complete_data_4)
+
+complete_data_5 <- complete(mikahan$mids, 5)
+
+summary(complete_data_5)
+```
+
+```{r, echo=FALSE}
+
+# Extracting factors from first imputed dataset
+
+data_imp2 <- mice::complete(mice::mice(ecopoln, 1, print = FALSE))
+
+fct_scores2 <- data.frame(factor.scores(data_imp2[, 1:24], ecopolfit2)$scores)
+
+```
+
+##  eco-pol scale : Factor scores from 2nd imputation
+```{r, echo=FALSE}
+
+data_impe2 <- mice::complete(mice::mice(ecopoln, 2, print = FALSE))
+
+fct_scorese2 <- data.frame(factor.scores(data_impe2[, 1:24], ecopolfit2)$scores)
+
+```
+
+##  eco-pol scale : Factor scores from 3rd imputation
+```{r, echo=FALSE}
+
+data_impe3 <- mice::complete(mice::mice(ecopoln, 3, print = FALSE))
+
+fct_scorese3 <- data.frame(factor.scores(data_impe3[, 1:24], ecopolfit2)$scores)
+
+```
+
+##  eco-pol scale : Factor scores from 4th imputation
+```{r, echo=FALSE}
+
+data_impe4 <- mice::complete(mice::mice(ecopoln, 4, print = FALSE))
+
+fct_scorese4 <- data.frame(factor.scores(data_impe4[, 1:24], ecopolfit2)$scores)
+
+```
+
+##  eco-pol scale : Factor scores from 5th imputation
+```{r, echo=FALSE}
+
+data_impe5 <- mice::complete(mice::mice(ecopoln, 5, print = FALSE))
+
+fct_scorese5 <- data.frame(factor.scores(data_impe5[, 1:24], ecopolfit2)$scores)
+
+```
+
+## Are imputations plausible : Eco-pol scale
+
+yes, imputations are pluasible- all natural numbers between 1 and 5
+
+```{r, echo=FALSE}
+
+summary(miecopol)
+names(miecopol)
+
+miecopol$mids
+
+complete_ecopol_first <- complete(miecopol$mids, 1)
+
+summary(complete_ecopol_first)
+
+complete_ecopol_2 <- complete(miecopol$mids, 2)
+
+summary(complete_ecopol_2)
+
+complete_ecopol_3 <- complete(miecopol$mids, 3)
+
+summary(complete_ecopol_3)
+
+complete_ecopol_4 <- complete(miecopol$mids, 4)
+
+summary(complete_ecopol_4)
+
+complete_ecopol_5 <- complete(miecopol$mids, 5)
+
+summary(complete_ecopol_5)
+
+```
+
+# Checking consistency of LM coefficients across 5 imputed datasets 
+coefficients and LMs are fairly consistent
+
+## Binding datasets: 1st imputation
+
+```{r, echo = FALSE}
+
+# binding the imputed  factor analysis scores for kahan scale and eco-pol value scale to the larger dataset codedmodule2
+
+ecopolnuclear <- fct_scores2 %>%
+  rename(Ndevelop = MR1, Pdevelop = MR2)
+
+kahannuclear <- fct_scores%>%
+  rename(Egalitarian = MR1, Communitarian = MR2)
+
+allformice<- cbind(formice1,ecopolnuclear, kahannuclear)
+
+```
+
+## LMs with 1st imputed datasets from FAs
+
+```{r, echo=FALSE}
+
+nuclearIVmice <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformice)
+
+nuclearIVmice2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian, data = allformice)
+
+nuclearIVmice3 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformice)
+
+summary(nuclearIVmice)
+summary(nuclearIVmice2)
+summary(nuclearIVmice3)
+
+```
+
+## binding dataset - 2nd imputation
+
+```{r, echo=FALSE}
+
+ecopolnuclear2 <- fct_scorese2 %>%
+  rename(Ndevelop = MR1, Pdevelop = MR2)
+
+kahannuclear2 <- fct_scoresk2%>%
+  rename(Egalitarian = MR1, Communitarian = MR2)
+
+allformice2<- cbind(formice1,ecopolnuclear2, kahannuclear2)
+
+```
+
+## LMs with second imputation 
+```{r, echo=FALSE}
+
+nuclearIVmiceimp2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformice2)
+
+nuclearIVmiceimp22 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian, data = allformice2)
+
+nuclearIVmiceimp23 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformice2)
+
+summary(nuclearIVmiceimp2)
+summary(nuclearIVmiceimp22)
+summary(nuclearIVmiceimp23)
+
+```
+
+## binding dataset - 3rd imputation
+
+```{r, echo=FALSE}
+
+ecopolnuclear3 <- fct_scorese3 %>%
+  rename(Ndevelop = MR1, Pdevelop = MR2)
+
+kahannuclear3 <- fct_scoresk3%>%
+  rename(Egalitarian = MR1, Communitarian = MR2)
+
+allformice3<- cbind(formice1,ecopolnuclear3, kahannuclear3)
+
+```
+
+## LMs with third imputation 
+```{r, echo=FALSE}
+
+nuclearIVmiceimp3 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformice3)
+
+nuclearIVmiceimp32 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian, data = allformice3)
+
+nuclearIVmiceimp33 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformice3)
+
+summary(nuclearIVmiceimp3)
+summary(nuclearIVmiceimp32)
+summary(nuclearIVmiceimp33)
+
+```
+
+## binding dataset - 4th imputation
+
+```{r, echo=FALSE}
+
+ecopolnuclear4 <- fct_scorese4 %>%
+  rename(Ndevelop = MR1, Pdevelop = MR2)
+
+kahannuclear4 <- fct_scoresk4%>%
+  rename(Egalitarian = MR1, Communitarian = MR2)
+
+allformice4<- cbind(formice1, ecopolnuclear4, kahannuclear4)
+
+```
+
+## LMs with fourth imputation 
+```{r, echo=FALSE}
+
+nuclearIVmiceimp4 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformice4)
+
+nuclearIVmiceimp24 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian, data = allformice4)
+
+nuclearIVmiceimp34 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformice4)
+
+summary(nuclearIVmiceimp4)
+summary(nuclearIVmiceimp24)
+summary(nuclearIVmiceimp34)
+
 ```
@@
 
-## State Ns after MIFA on two scales
-
-```{r, echo=FALSE}
-
-nuclear_missing <- allformice %>% dplyr::select(Risky_Nuclear,Uppercaste, Male, Hindu, urban_rural, Age, State)%>%
-  na.omit()
-
-summary(nuclear_missing)
-
-```
-
-## LMs with 1st imputed datasets from FAs
-
-```{r, echo=FALSE}
-
-nuclearIVmice <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformice)
-
-nuclearIVmice2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian, data = allformice)
-
-nuclearIVmice3 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformice)
-
-summary(nuclearIVmice)
-summary(nuclearIVmice2)
-summary(nuclearIVmice3)
-
-```
-
-## binding dataset - 2nd imputation
-
-```{r, echo=FALSE}
-
-ecopolnuclear2 <- fct_scorese2 %>%
-  rename(Ndevelop = MR1, Pdevelop = MR2)
-
-kahannuclear2 <- fct_scoresk2%>%
-  rename(Egalitarian = MR1, Communitarian = MR2)
-
-allformice2<- cbind(formice1,ecopolnuclear2, kahannuclear2)
-
-```
-
-## LMs with second imputation 
-```{r, echo=FALSE}
-
-nuclearIVmiceimp2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformice2)
-
-nuclearIVmiceimp22 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian, data = allformice2)
-
-nuclearIVmiceimp23 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformice2)
-
-summary(nuclearIVmiceimp2)
-summary(nuclearIVmiceimp22)
-summary(nuclearIVmiceimp23)
-
-```
-
-## binding dataset - 3rd imputation
-
-```{r, echo=FALSE}
-
-ecopolnuclear3 <- fct_scorese3 %>%
-  rename(Ndevelop = MR1, Pdevelop = MR2)
-
-kahannuclear3 <- fct_scoresk3%>%
-  rename(Egalitarian = MR1, Communitarian = MR2)
-
-allformice3<- cbind(formice1,ecopolnuclear3, kahannuclear3)
-
-```
-
-## LMs with third imputation 
-```{r, echo=FALSE}
-
-nuclearIVmiceimp3 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformice3)
-
-nuclearIVmiceimp32 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian, data = allformice3)
-
-nuclearIVmiceimp33 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformice3)
-
-summary(nuclearIVmiceimp3)
-summary(nuclearIVmiceimp32)
-summary(nuclearIVmiceimp33)
-
-```
-
-## binding dataset - 4th imputation
-
-```{r, echo=FALSE}
-
-ecopolnuclear4 <- fct_scorese4 %>%
-  rename(Ndevelop = MR1, Pdevelop = MR2)
-
-kahannuclear4 <- fct_scoresk4%>%
-  rename(Egalitarian = MR1, Communitarian = MR2)
-
-allformice4<- cbind(formice1, ecopolnuclear4, kahannuclear4)
-
-```
-
-## LMs with fourth imputation 
-```{r, echo=FALSE}
-
-nuclearIVmiceimp4 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformice4)
-
-nuclearIVmiceimp24 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian, data = allformice4)
-
-nuclearIVmiceimp34 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformice4)
-
-summary(nuclearIVmiceimp4)
-summary(nuclearIVmiceimp24)
-summary(nuclearIVmiceimp34)
-
-```
-
-# Mean across imputations
-
-## Binding datasets
-
-```{r, echo = FALSE}
-
-# binding the imputed  factor analysis scores for kahan scale and eco-pol value scale to the larger dataset codedmodule2
-
-ecopolnuclearfinal <- necopolfinal %>%
-  rename(Ndevelop = MR1, Pdevelop = MR2)
-
-kahannuclearfinal <- nkahanfinal%>%
-  rename(Egalitarian = MR1, Communitarian = MR2)
-
-allformicefinal<- cbind(formice1,ecopolnuclearfinal, kahannuclearfinal)
-
-```
-
-## LMs with final imputed datasets from FAs
-
-```{r, echo=FALSE}
-
-allformicefinal$State <- factor(allformicefinal$State, levels = c("Maharashtra","West Bengal" ,"Rajasthan","Tamil Nadu",  "Uttar Pradesh"))
-
-nuclearfinal <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age, data = allformicefinal)
-
-nuclearfinal2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformicefinal)
-
-nuclearfinal3 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian, data = allformicefinal)
-
-nuclearfinal4 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformicefinal)
-
-summary(nuclearfinal)
-summary(nuclearfinal2)
-summary(nuclearfinal3)
-summary(nuclearfinal4)
-
-aic_values <- AIC(nuclearfinal, nuclearfinal2, nuclearfinal3, nuclearfinal4)
-
-print(aic_values)
-
-bic_values <- BIC(nuclearfinal, nuclearfinal2, nuclearfinal3, nuclearfinal4)
-
-print(bic_values)
-
-```
-
-# correlation table
-
-```{r}
-
-nforcor <- allformicefinal %>%
-           dplyr::select(Risky_Nuclear, Communitarian , Egalitarian , Pdevelop , Ndevelop)
-
-cor.plot(nforcor)
-```
-
-# interaction vars
-
-```{r}
-
-nuclearinterac <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian*State + Egalitarian*State + Pdevelop*State + Ndevelop*State , data = allformicefinal)
-
-summary(nuclearinterac)
-
-```
-\newpage
-
-```{r, echo=FALSE, results='asis'}
-library(stargazer)
-
-#cat("\\begingroup")
-#cat("\\setlength{\\tabcolsep}{1pt}")
-#cat("\\renewcommand{\\arraystretch}{0.7}")
-stargazer(nuclearfinal, nuclearfinal2, nuclearfinal3, nuclearfinal4, nuclearinterac,
-          title = "Table 6: 5 linear models: Perceived Risk of Nuclear Energy",
-          type = "text"
-)
-#cat("\\endgroup")
-
-```
-
-# NUCLEAR2 : only charcateristics of tech
-
-```{r, echo=FALSE}
-
-ecopoln2 <- formice1 %>%
-  dplyr::select(
-    DISPLACENUCLEAR,  POLLUTENUCLEAR, HEALTHNUCLEAR, JOBSNUCLEAR, BEAUTYNUCLEAR,
-    PRIDENUCLEAR, NPRIDENUCLEAR, DEVNUCLEAR, PROSPERNUCLEAR,
-    RELYNUCLEAR, age, urban_rural, gender, caste, religion, State
-  )
-
-str(ecopoln2)
-md.pattern(ecopoln2) #the variables with missing values:
-
-mcar_test(data=ecopoln2)
-```
-
-# Nuclear2 : Mifa for new eco-pol value scale
-
-```{r, echo=FALSE}
-
-miecopoln2 <- mifa(data= ecopoln2,
-                cov_vars = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
-                m=10,
-                n_pc= 2:4,
-                ci = "fieller", 
-                n_boot=1000,
-                print = FALSE,
-                progress= TRUE, 
-                seed = 528,)
-
-miecopoln2
-
-ecopolfitn2 <- psych::fa(miecopoln2$cov_combined, nfactors = 2, rotate = "varimax")
-
-print.psych(ecopolfitn2, sort= TRUE, cut= 0.4)
-
-```
-
-# Solar : MAR condition and missing data pattern
-
-```{r, echo=FALSE}
-
-ecopols <- formice1 %>%
-  dplyr::select(
-    DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE,
-    ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV,DEVOVERENV, OWNERPVT, OWNERPUB,
-    OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION,
-    DISPLACESOLAR,  POLLUTESOLAR, HEALTHSOLAR, JOBSSOLAR, BEAUTYSOLAR,
-    PRIDESOLAR, NPRIDESOLAR, DEVSOLAR, PROSPERSOLAR,
-    RELYSOLAR,age, urban_rural, gender, caste, religion, State
-  )
-
-md.pattern(ecopols) #the variables with missing values:
-
-mcar_test(data=ecopols)
-```
-
-# Solar : Mifa for new eco-pol value scale
-
-```{r, echo=FALSE}
-
-miecopols <- mifa(data= ecopols,
-                cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
-                m=5,
-                n_pc= 1:2,
-                ci = "fieller", 
-                n_boot=1000,
-                print = FALSE,
-                progress= TRUE, 
-                seed = 528,)
-
-miecopols
-
-ecopolfits <- psych::fa(miecopols$cov_combined, nfactors = 2, rotate = "varimax")
-
-print.psych(ecopolfits, sort= TRUE, cut= 0.4)
-
-```
-
-# Solar 2 : only charcateristics of tech
-
-```{r, echo=FALSE}
-
-ecopols2 <- formice1 %>%
-  dplyr::select(
-    DISPLACESOLAR,  POLLUTESOLAR, HEALTHSOLAR, JOBSSOLAR, BEAUTYSOLAR,
-    PRIDESOLAR, NPRIDESOLAR, DEVSOLAR, PROSPERSOLAR,
-    RELYSOLAR, age, urban_rural, gender, caste, religion, State
-  )
-
-str(ecopols2)
-md.pattern(ecopols2) #the variables with missing values:
-
-mcar_test(data=ecopols2)
-```
-
-# SOLAR2 : Mifa for new eco-pol value scale
-
-```{r, echo=FALSE}
-
-miecopols2 <- mifa(data= ecopols2,
-                cov_vars = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
-                m=10,
-                n_pc= 2:4,
-                ci = "fieller", 
-                n_boot=1000,
-                print = FALSE,
-                progress= TRUE, 
-                seed = 528,)
-
-miecopols2
-
-ecopolfits2 <- psych::fa(miecopols2$cov_combined, nfactors = 2, rotate = "varimax")
-
-print.psych(ecopolfits2, sort= TRUE, cut= 0.4)
-
-```
-
-# Solar: Mifa with CFA
-
-```{r}
-
-## CFA on ecopol vars for solar energy
-
-ecopols_2fa <- '
-  Ndevelop =~ DEVSOLAR + PRIDESOLAR + NPRIDESOLAR + PROSPERSOLAR + JOBSSOLAR 
-  Pdevelop =~ HEALTHSOLAR + BEAUTYSOLAR + DISPLACESOLAR + POLLUTESOLAR + ENVOVERDEV
-'
-
-secopol_cfa <- cfa(ecopols_2fa, data = miecopols$cov_combined, std.lv = TRUE)
-summary(secopol_cfa, fit.measure= TRUE, standardized = TRUE)
-
-```
-
-# COAL : MAR condition and missing data pattern
-
-```{r, echo=FALSE}
-
-ecopolc <- formice1 %>%
-  dplyr::select(
-    DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE,
-    ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV,DEVOVERENV, OWNERPVT, OWNERPUB,
-    OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION,
-    DISPLACECOAL,  POLLUTECOAL, HEALTHCOAL, JOBSCOAL, BEAUTYCOAL,
-    PRIDECOAL, NPRIDECOAL, DEVCOAL, PROSPERCOAL,
-    RELYCOAL,age, urban_rural, gender, caste, religion, State
-  )
-
-md.pattern(ecopolc) #the variables with missing values:
-
-mcar_test(data=ecopolc)
-```
-
-# Coal : Mifa for new eco-pol value scale
-
-```{r, echo=FALSE}
-
-miecopolc <- mifa(data= ecopolc,
-                cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
-                m=50,
-                n_pc= 2:4,
-                ci = "fieller", 
-                n_boot=1000,
-                print = FALSE,
-                progress= TRUE, 
-                seed = 528,)
-
-miecopolc
-
-ecopolfitc <- psych::fa(miecopolc$cov_combined, nfactors = 3, rotate = "varimax")
-
-print.psych(ecopolfitc, sort= TRUE, cut= 0.4)
-
-```
-
-# COAL2 : only charcateristics of tech
-
-```{r, echo=FALSE}
-
-ecopolc2 <- formice1 %>%
-  dplyr::select(
-    DISPLACECOAL,  POLLUTECOAL, HEALTHCOAL, JOBSCOAL, BEAUTYCOAL,
-    PRIDECOAL, NPRIDECOAL, DEVCOAL, PROSPERCOAL,
-    RELYCOAL,age, urban_rural, gender, caste, religion, State
-  )
-
-md.pattern(ecopolc2) #the variables with missing values:
-
-mcar_test(data=ecopolc2)
-```
-
-# Coal2 : Mifa for new eco-pol value scale
-
-```{r, echo=FALSE}
-
-miecopolc2 <- mifa(data= ecopolc2,
-                cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
-                m=5,
-                n_pc= 2:4,
-                ci = "fieller", 
-                n_boot=1000,
-                print = FALSE,
-                progress= TRUE, 
-                seed = 528,)
-
-miecopolc2
-
-ecopolfitc2 <- psych::fa(miecopolc2$cov_combined, nfactors = 2, rotate = "varimax")
-
-print.psych(ecopolfitc2, sort= TRUE, cut= 0.4)
-
-```
-
-```{r}
-
-cor.plot(ecopolc %>% dplyr::select(-c("age", "gender", "caste", "State", "urban_rural", "religion")))
-```
-
-# Coal: Mifa with CFA
-
-```{r}
-
-# (DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE,ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV,DEVOVERENV, OWNERPVT, OWNERPUB,OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION,DISPLACECOAL,  POLLUTECOAL, HEALTHCOAL, JOBSCOAL, BEAUTYCOAL,PRIDECOAL, NPRIDECOAL, DEVCOAL, PROSPERCOAL,RELYCOAL)
-
-## CFA on ecopol vars for coal
-
-ecopolc_2fa <- '
-  Pride =~ PRIDECOAL + NPRIDECOAL + DEVOVERENV +  DECISIONCEN + OWNERPVT + DECISIONCEN  + OWNERNOREG + ECONOMYGLOBAL
-  Social Costs =~ BEAUTYCOAL + POLLUTECOAL + HEALTHCOAL
-  Social Costs2 =~ OWNERPUB + ENVOVERDEV + DISPLACECOAL
-
-'
-
-cecopol_cfa <- cfa(ecopolc_2fa, data = miecopolc$cov_combined, std.lv = TRUE)
-summary(cecopol_cfa, fit.measure= TRUE, standardized = TRUE)
-
-```
-
 ```{r, echo=FALSE}

### 2024-03-25 nuclear in comparison.Rmd
knitted results with mice to pdf

@@
     keep_md: yes
+    latex_engine: xelatex
+geometry: "left=0.5cm,right=0.5cm,top=0.5cm,bottom=0.5cm"
 header-includes:

### 2024-03-25 nuclear-in-comparison.tex
knitted results with mice to pdf

@@
 \urlstyle{same} % disable monospaced font for URLs
-\usepackage[margin=1in]{geometry}
+\usepackage[left=0.5cm,right=0.5cm,top=0.5cm,bottom=0.5cm]{geometry}
 \usepackage{graphicx}
@@
 \setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+\usepackage{dcolumn}
+\usepackage{array}
+\usepackage{pdflscape}
+\newcommand{\blandscape}{\begin{landscape}}
+\newcommand{\elandscape}{\end{landscape}}
 \usepackage{booktabs}
@@
 \% Table created by stargazer v.5.2.3 by Marek Hlavac, Social Policy
-Institute. E-mail: marek.hlavac at gmail.com \% Date and time: Wed, Jan
-10, 2024 - 09:43:59
+Institute. E-mail: marek.hlavac at gmail.com \% Date and time: Sun, Mar
+24, 2024 - 13:05:37
 
@@
 
+\begin{verbatim}
+## List of 5
+##  $ Maharashtra  : tibble [14 x 6] (S3: tbl_df/tbl/data.frame)
+##   ..$ State     : chr [1:14] "Maharashtra" "Maharashtra" "Maharashtra" "Maharashtra" ...
+##   ..$ Tech      : Factor w/ 7 levels "Solar","Wind",..: 5 6 3 7 4 1 2 5 6 3 ...
+##   ..$ Mean_Value: num [1:14] 3.27 3.25 2.61 3.16 3.29 ...
+##   ..$ sd        : num [1:14] 0.992 1.01 1.032 1.033 1.014 ...
+##   ..$ se        : num [1:14] 0.0388 0.0395 0.0404 0.0404 0.0397 ...
+##   ..$ Category  : chr [1:14] "Risky" "Risky" "Risky" "Risky" ...
+##  $ Rajasthan    : tibble [14 x 6] (S3: tbl_df/tbl/data.frame)
+##   ..$ State     : chr [1:14] "Rajasthan" "Rajasthan" "Rajasthan" "Rajasthan" ...
+##   ..$ Tech      : Factor w/ 7 levels "Solar","Wind",..: 5 6 3 7 4 1 2 5 6 3 ...
+##   ..$ Mean_Value: num [1:14] 3.14 3.33 1.76 3.35 2.19 ...
+##   ..$ sd        : num [1:14] 0.945 1.001 1.016 1.144 1.155 ...
+##   ..$ se        : num [1:14] 0.0363 0.0385 0.039 0.0439 0.0444 ...
+##   ..$ Category  : chr [1:14] "Risky" "Risky" "Risky" "Risky" ...
+##  $ Tamil Nadu   : tibble [14 x 6] (S3: tbl_df/tbl/data.frame)
+##   ..$ State     : chr [1:14] "Tamil Nadu" "Tamil Nadu" "Tamil Nadu" "Tamil Nadu" ...
+##   ..$ Tech      : Factor w/ 7 levels "Solar","Wind",..: 5 6 3 7 4 1 2 5 6 3 ...
+##   ..$ Mean_Value: num [1:14] 2.15 2.24 1.46 2.89 2.68 ...
+##   ..$ sd        : num [1:14] 1.196 1.417 0.862 1.282 1.296 ...
+##   ..$ se        : num [1:14] 0.0668 0.0792 0.0482 0.0717 0.0724 ...
+##   ..$ Category  : chr [1:14] "Risky" "Risky" "Risky" "Risky" ...
+##  $ Uttar Pradesh: tibble [14 x 6] (S3: tbl_df/tbl/data.frame)
+##   ..$ State     : chr [1:14] "Uttar Pradesh" "Uttar Pradesh" "Uttar Pradesh" "Uttar Pradesh" ...
+##   ..$ Tech      : Factor w/ 7 levels "Solar","Wind",..: 5 6 3 7 4 1 2 5 6 3 ...
+##   ..$ Mean_Value: num [1:14] 2.63 2.46 2.98 2.94 2.84 ...
+##   ..$ sd        : num [1:14] 1.052 1.254 1.354 1.265 0.926 ...
+##   ..$ se        : num [1:14] 0.0941 0.1122 0.1211 0.1132 0.0828 ...
+##   ..$ Category  : chr [1:14] "Risky" "Risky" "Risky" "Risky" ...
+##  $ West Bengal  : tibble [14 x 6] (S3: tbl_df/tbl/data.frame)
+##   ..$ State     : chr [1:14] "West Bengal" "West Bengal" "West Bengal" "West Bengal" ...
+##   ..$ Tech      : Factor w/ 7 levels "Solar","Wind",..: 5 6 3 7 4 1 2 5 6 3 ...
+##   ..$ Mean_Value: num [1:14] 3.36 3.63 2.7 4.4 3.23 ...
+##   ..$ sd        : num [1:14] 1.05 1.01 1.37 0.72 1.1 ...
+##   ..$ se        : num [1:14] 0.0536 0.0517 0.0698 0.0366 0.0558 ...
+##   ..$ Category  : chr [1:14] "Risky" "Risky" "Risky" "Risky" ...
+\end{verbatim}
+
+\begin{verbatim}
+## 'data.frame':    2161 obs. of  193 variables:
+##  $ Respondent          : int  1 2 3 4 5 6 7 8 9 10 ...
+##  $ Language            : chr  "HI" "BN" "BN" "BN" ...
+##  $ Survey_Date         : chr  "05-12-2021" "08-12-2021" "08-12-2021" "08-12-2021" ...
+##  $ State               : chr  "Uttar Pradesh" "West Bengal" "West Bengal" "West Bengal" ...
+##  $ Risky_Hydro         : num  3 1 2 2 4 2 2 NA 3 5 ...
+##  $ Risky_Solar         : num  1 1 1 2 1 1 1 2 3 1 ...
+##  $ Risky_Wind          : num  1 2 2 2 1 1 1 1 2 3 ...
+##  $ Risky_Nuclear       : num  2 4 4 4 5 3 2 4 5 NA ...
+##  $ Risky_Coal          : num  3 4 NA 4 5 2 3 2 4 3 ...
+##  $ Risky_Gas           : num  3 4 4 3 4 1 3 3 4 5 ...
+##  $ Risky_Oil           : num  3 3 2 3 4 2 3 3 4 2 ...
+##  $ Risky_INDHydro      : num  3 3 2 2 2 2 2 3 4 5 ...
+##  $ Risky_INDSolar      : num  3 1 1 1 5 2 2 3 1 1 ...
+##  $ Risky_INDWind       : num  NA 4 5 2 1 NA 3 NA 3 3 ...
+##  $ Risky_INDBiogas     : num  3 1 NA 2 2 2 2 NA 3 4 ...
+##  $ Risky_INDDiesel     : num  3 2 2 2 4 4 4 2 3 4 ...
+##  $ Risky_INDKerosene   : num  NA 1 2 1 3 2 4 2 4 5 ...
+##  $ Risky_INDFirewoodetc: num  2 2 1 1 2 1 1 1 3 5 ...
+##  $ Risky_INDLPG        : num  5 3 1 1 5 2 2 4 5 5 ...
+##  $ Ben_Hydro           : num  4 3 2 2 4 2 2 NA 2 4 ...
+##  $ Ben_Solar           : num  4 4 2 3 3 3 3 4 3 3 ...
+##  $ Ben_Wind            : num  3 4 2 2 5 1 2 2 5 3 ...
+##  $ Ben_Nuclear         : num  5 2 NA 1 1 1 1 4 3 5 ...
+##  $ Ben_Coal            : num  5 4 2 1 1 1 1 NA 4 4 ...
+##  $ Ben_Gas             : num  1 4 2 1 4 2 1 5 4 4 ...
+##  $ Ben_Oil             : num  3 3 2 2 3 1 2 3 5 3 ...
+##  $ Ben_INDHydro        : num  5 3 2 2 4 3 2 NA 3 NA ...
+##  $ Ben_INDSolar        : num  3 2 NA NA 2 2 1 4 2 5 ...
+##  $ Ben_INDWind         : num  2 NA NA 2 2 NA 2 NA 3 3 ...
+##  $ Ben_INDDiesel       : num  1 3 2 2 3 1 1 2 3 4 ...
+##  $ Ben_INDBiogas       : num  5 NA 2 2 4 3 1 2 5 4 ...
+##  $ Ben_INDFirewoodetc  : num  4 3 3 3 1 3 2 2 4 1 ...
+##  $ Ben_INDLPG          : num  2 2 3 2 5 2 3 NA NA 1 ...
+##  $ Ben_INDKerosene     : num  2 2 3 2 1 2 2 2 NA 2 ...
+##  $ N_accept            : num  3 1 1 1 1 2 2 NA NA NA ...
+##  $ N_reluctantlyaccept : num  1 2 2 2 NA 2 2 NA NA NA ...
+##  $ N_reject            : num  3 NA NA 4 NA 4 4 NA NA NA ...
+##  $ K_IINTRFER          : num  4 4 2 5 4 2 3 2 3 1 ...
+##  $ K_IPRIVACY          : num  2 NA 2 2 3 3 3 2 4 5 ...
+##  $ K_SHARM             : num  5 NA 2 4 5 3 3 1 3 5 ...
+##  $ K_IPROTECT          : num  3 4 3 2 1 3 NA 2 3 1 ...
+##  $ K_SLIMCHOI          : num  1 5 NA NA 5 NA NA NA 3 5 ...
+##  $ K_SPROTECT          : num  2 4 NA NA 3 3 3 2 4 5 ...
+##  $ K_HEQUAL            : num  1 2 4 4 4 2 2 5 4 5 ...
+##  $ K_HREVDIS1          : num  5 3 3 2 2 3 3 4 4 4 ...
+##  $ K_EDISCRIM          : num  NA NA 3 2 4 3 3 NA 5 3 ...
+##  $ K_ERADEQ1           : num  5 5 5 5 5 5 1 4 NA 4 ...
+##  $ K_EWEALTH           : num  4 NA NA 3 5 3 3 5 NA 4 ...
+##  $ K_ERADEQ2           : num  5 5 5 5 1 5 5 5 4 5 ...
+##  $ DECISIONDECEN       : num  5 NA NA NA NA 3 3 NA 3 NA ...
+##  $ DECISIONCEN         : num  3 3 NA NA NA NA 3 4 NA 4 ...
+##  $ SYSTEMTOTAL         : num  1 5 5 3 2 3 3 5 NA 5 ...
+##  $ SYSTEMTECHNO        : num  2 NA 3 3 NA 5 NA 4 5 4 ...
+##  $ SYSTEMDEMO          : num  2 3 NA NA 5 3 NA 3 3 5 ...
+##  $ SYSTEMRELIGION      : num  1 NA NA 3 4 NA NA 3 4 5 ...
+##  $ INDUSTRYSMALL       : num  5 5 2 2 5 2 2 4 5 5 ...
+##  $ INDUSTRYLARGE       : num  3 4 4 5 5 5 5 5 5 5 ...
+##  $ ECONOMYLOCAL        : num  1 2 4 2 1 3 4 4 4 3 ...
+##  $ ECONOMYGLOBAL       : num  1 3 3 4 4 NA 1 5 4 4 ...
+##  $ DEVOVERENV          : num  1 3 3 NA NA 3 3 4 4 3 ...
+##  $ ENVOVERDEV          : num  2 NA NA NA 2 NA 3 4 5 5 ...
+##  $ OWNERPVT            : num  4 4 4 3 3 3 NA 1 NA 4 ...
+##  $ OWNERPUB            : num  3 NA 2 3 2 2 NA 2 NA 2 ...
+##  $ OWNERREG            : num  1 NA 3 5 NA 3 3 5 NA 4 ...
+##  $ OWNERNOREG          : num  4 NA NA 3 NA NA 3 5 NA 3 ...
+##  $ WEALTHLIM           : num  3 4 3 3 4 NA NA 4 NA 5 ...
+##  $ MECHANISATION       : num  4 5 5 5 5 4 5 4 4 5 ...
+##  $ DISPLACESOLAR       : num  4 1 1 2 1 2 2 2 2 1 ...
+##  $ POLLUTESOLAR        : num  4 1 1 2 1 1 1 1 1 1 ...
+##  $ HEALTHSOLAR         : num  NA 2 2 2 1 2 1 1 1 1 ...
+##  $ JOBSSOLAR           : num  NA 2 NA NA 1 NA NA 1 3 2 ...
+##  $ BEAUTYSOLAR         : num  NA 2 2 1 1 2 1 1 1 1 ...
+##  $ PRIDESOLAR          : num  NA 4 2 4 5 2 4 5 4 5 ...
+##  $ NPRIDESOLAR         : num  3 4 2 4 4 3 4 5 5 5 ...
+##  $ DEVSOLAR            : num  2 2 3 2 5 3 4 5 4 5 ...
+##  $ PROSPERSOLAR        : num  2 2 3 3 2 2 3 2 1 4 ...
+##  $ RELYSOLAR           : num  4 2 NA 3 NA 3 NA 5 2 4 ...
+##  $ DISPLACEROOFS       : num  3 2 2 2 1 2 2 1 2 1 ...
+##  $ POLLUTEROOFS        : num  1 2 2 1 1 2 2 1 1 1 ...
+##  $ HEALTHROOFS         : num  1 1 2 1 1 2 2 1 1 1 ...
+##  $ JOBSROOFS           : num  2 NA NA 3 1 NA NA 1 NA 4 ...
+##  $ BEAUTYROOFS         : num  4 2 1 2 1 1 2 1 1 1 ...
+##  $ PRIDEROOFS          : num  2 2 2 2 5 3 3 5 4 5 ...
+##  $ NPRIDEROOFS         : num  1 NA 2 3 5 3 3 5 NA 5 ...
+##  $ DEVROOFS            : num  2 2 2 NA 5 2 4 5 NA 5 ...
+##  $ PROSPERROOFS        : num  3 3 1 2 3 3 4 5 NA 5 ...
+##  $ RELYROOFS           : num  3 3 3 2 NA 4 4 5 3 4 ...
+##  $ DISPLACEDIESEL      : num  1 4 2 2 1 2 4 NA 4 2 ...
+##  $ POLLUTEDIESEL       : num  4 2 4 3 1 4 2 5 5 4 ...
+##  $ HEALTHDIESEL        : num  NA 3 4 3 2 3 3 4 4 1 ...
+##  $ JOBSDIESEL          : num  3 NA NA 4 NA 3 3 1 3 4 ...
+##  $ BEAUTYDIESEL        : num  3 4 5 3 2 4 5 4 5 4 ...
+##  $ PRIDEDIESEL         : num  2 3 3 2 NA 2 2 4 2 4 ...
+##  $ NPRIDEDIESEL        : num  3 3 4 1 1 2 3 4 NA 4 ...
+##  $ DEVDIESEL           : num  2 NA 3 1 1 2 NA 2 NA 4 ...
+##  $ PROSPERDIESEL       : num  4 3 3 2 1 4 5 3 5 5 ...
+##  $ RELYDIESEL          : num  1 3 4 2 NA 3 NA 4 NA 4 ...
+##  $ DISPLACEFIRE        : num  4 1 2 2 4 4 3 2 2 4 ...
+##  $ POLLUTEFIRE         : num  2 1 1 2 3 2 1 3 2 4 ...
+##   [list output truncated]
+\end{verbatim}
+
 \includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-18-1.pdf}
@@
 
-\hypertarget{net-benefit-by-state}{%
-\subsection{Net benefit by state}\label{net-benefit-by-state}}
+\hypertarget{maharshtra-t-tests}{%
+\section{Maharshtra t tests}\label{maharshtra-t-tests}}
+
+\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-19-1.pdf}
+
+\hypertarget{tamil-nadu-t-tests}{%
+\section{Tamil Nadu t tests}\label{tamil-nadu-t-tests}}
 
 \includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-20-1.pdf}
+
+\hypertarget{uttar-pradesh-t-tests}{%
+\section{Uttar Pradesh t tests}\label{uttar-pradesh-t-tests}}
+
+\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-21-1.pdf}
+
+\hypertarget{rajasthan-t-tests}{%
+\section{Rajasthan t tests}\label{rajasthan-t-tests}}
+
+\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-22-1.pdf}
+
+\hypertarget{west-bengal-t-tests}{%
+\section{West Bengal t tests}\label{west-bengal-t-tests}}
+
+\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-23-1.pdf}
+\#\# Net benefit by state
+
+\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-25-1.pdf}
 
@@
 
-\includegraphics[width=1\linewidth,height=1\textheight]{nuclear-in-comparison_files/figure-latex/unnamed-chunk-24-1}
+\includegraphics[width=1\linewidth,height=1\textheight]{nuclear-in-comparison_files/figure-latex/unnamed-chunk-29-1}
 
@@
 
-\includegraphics[width=1\linewidth,height=1\textheight]{nuclear-in-comparison_files/figure-latex/unnamed-chunk-28-1}
+\includegraphics[width=1\linewidth,height=1\textheight]{nuclear-in-comparison_files/figure-latex/unnamed-chunk-33-1}
 
@@
 
-\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-29-1.pdf}
-\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-29-2.pdf}
+\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-34-1.pdf}
+\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-34-2.pdf}
 
@@
 
-\includegraphics[width=1\linewidth,height=1\textheight]{nuclear-in-comparison_files/figure-latex/unnamed-chunk-32-1}
+\includegraphics[width=1\linewidth,height=1\textheight]{nuclear-in-comparison_files/figure-latex/unnamed-chunk-37-1}
 
@@
 
-\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-33-1.pdf}
+\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-38-1.pdf}
 
@@
 
-\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-35-1.pdf}
-\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-35-2.pdf}
-\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-35-3.pdf}
-\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-35-4.pdf}
+\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-40-1.pdf}
+\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-40-2.pdf}
+\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-40-3.pdf}
+\includegraphics{nuclear-in-comparison_files/figure-latex/unnamed-chunk-40-4.pdf}
 
@@
 \% Table created by stargazer v.5.2.3 by Marek Hlavac, Social Policy
-Institute. E-mail: marek.hlavac at gmail.com \% Date and time: Wed, Jan
-10, 2024 - 09:44:22
+Institute. E-mail: marek.hlavac at gmail.com \% Date and time: Sun, Mar
+24, 2024 - 13:06:02
 
@@
 
+\begin{verbatim}
+## 
+## Regression Models Summary
+## ========================================================================================================================================================================
+##                                                                                     Dependent variable:                                                                 
+##                     ----------------------------------------------------------------------------------------------------------------------------------------------------
+##                           RiskNuclear               RiskSolar                 RiskCoal              NetBenNuclear             NetBenSolar              NetBenCoal       
+##                               (1)                      (2)                      (3)                      (4)                      (5)                      (6)          
+## ------------------------------------------------------------------------------------------------------------------------------------------------------------------------
+## Uppercaste                  -0.135**                  -0.006                   -0.056                   0.026                   -0.146*                  -0.021         
+##                             (0.061)                  (0.051)                  (0.058)                  (0.089)                  (0.084)                  (0.075)        
+##                                                                                                                                                                         
+## Male                         0.045                    -0.047                   0.015                    0.008                    0.058                   -0.016         
+##                             (0.062)                  (0.053)                  (0.059)                  (0.092)                  (0.087)                  (0.078)        
+##                                                                                                                                                                         
+## Hindu                        -0.047                   -0.057                   0.099                   0.362***                 0.290***                 -0.008         
+##                             (0.070)                  (0.059)                  (0.066)                  (0.100)                  (0.095)                  (0.085)        
+##                                                                                                                                                                         
+## UrbanUrban                   0.052                    -0.076                   0.055                    0.172*                   0.143                    0.014         
+##                             (0.067)                  (0.056)                  (0.063)                  (0.099)                  (0.093)                  (0.084)        
+##                                                                                                                                                                         
+## age                          -0.015                  0.045**                  0.053**                   -0.008                   0.045                   -0.035         
+##                             (0.027)                  (0.023)                  (0.025)                  (0.043)                  (0.040)                  (0.036)        
+##                                                                                                                                                                         
+## StateRajasthan              0.222**                 -1.285***                 0.234***                  -0.014                  1.957***                  0.077         
+##                             (0.094)                  (0.080)                  (0.090)                  (0.135)                  (0.128)                  (0.115)        
+##                                                                                                                                                                         
+## StateTamil Nadu             -0.242**                -1.547***                -1.103***                -0.625***                 2.027***                0.795***        
+##                             (0.099)                  (0.084)                  (0.094)                  (0.191)                  (0.181)                  (0.162)        
+##                                                                                                                                                                         
+## StateUttar Pradesh           -0.178                 -1.344***                -0.638***                  -0.250                  1.612***                 0.296**        
+##                             (0.120)                  (0.102)                  (0.114)                  (0.177)                  (0.168)                  (0.151)        
+##                                                                                                                                                                         
+## StateWest Bengal            1.276***                -1.330***                  0.071                  -1.522***                 1.853***                -0.222**        
+##                             (0.083)                  (0.071)                  (0.079)                  (0.125)                  (0.118)                  (0.106)        
+##                                                                                                                                                                         
+## Constant                    3.208***                 2.752***                 3.053***                  -0.240                  0.323**                   0.022         
+##                             (0.100)                  (0.084)                  (0.095)                  (0.147)                  (0.139)                  (0.124)        
+##                                                                                                                                                                         
+## ------------------------------------------------------------------------------------------------------------------------------------------------------------------------
+## Observations                 1,444                    1,444                    1,444                    1,183                    1,183                    1,183         
+## R2                           0.204                    0.353                    0.141                    0.171                    0.338                    0.035         
+## Adjusted R2                  0.199                    0.349                    0.136                    0.165                    0.333                    0.028         
+## Residual Std. Error    1.057 (df = 1434)        0.894 (df = 1434)        1.004 (df = 1434)        1.413 (df = 1173)        1.334 (df = 1173)        1.199 (df = 1173)   
+## F Statistic         40.720*** (df = 9; 1434) 86.983*** (df = 9; 1434) 26.208*** (df = 9; 1434) 26.873*** (df = 9; 1173) 66.499*** (df = 9; 1173) 4.789*** (df = 9; 1173)
+## ========================================================================================================================================================================
+## Note:                                                                                                                                        *p<0.1; **p<0.05; ***p<0.01
+\end{verbatim}
+
 \newpage
@@
 
-\caption{\label{tab:unnamed-chunk-43}Confirmatory Factor Analysis(CFA) on newly developed eco-pol scale}
+\caption{\label{tab:unnamed-chunk-49}Confirmatory Factor Analysis(CFA) on newly developed eco-pol scale}
 \centering
@@
 People Centered Development & Solar energy increases pollution of air/water/land. & 1.096 & 0.050 & 21.706 & 0e+00 & 0.9970923 & 1.1950355 & 1.0960639 & 0.8411179\\
-\cellcolor{gray!6}{People Centered Development} & \cellcolor{gray!6}{Large corporations are destroying the local industries in India and benefiting only a handful of people.} & \cellcolor{gray!6}{0.287} & \cellcolor{gray!6}{0.058} & \cellcolor{gray!6}{4.972} & \cellcolor{gray!6}{7e-07} & \cellcolor{gray!6}{0.1741052} & \cellcolor{gray!6}{0.4007040} & \cellcolor{gray!6}{0.2874046} & \cellcolor{gray!6}{0.2317296}\\
+\cellcolor{gray!6}{People Centered Development} & \cellcolor{gray!6}{Large corporations are destroying the local industries in India and benefiting only a handful of people.} & \cellcolor{gray!6}{-0.287} & \cellcolor{gray!6}{0.058} & \cellcolor{gray!6}{-4.972} & \cellcolor{gray!6}{7e-07} & \cellcolor{gray!6}{-0.4007040} & \cellcolor{gray!6}{-0.1741052} & \cellcolor{gray!6}{-0.2874046} & \cellcolor{gray!6}{-0.2317296}\\
 \addlinespace
 People Centered Development & Regardless of ownership, the government should pass strong regulations and implement them.
-& 0.296 & 0.052 & 5.733 & 0e+00 & 0.1949541 & 0.3974941 & 0.2962241 & 0.2659785\\
+& -0.296 & 0.052 & -5.733 & 0e+00 & -0.3974941 & -0.1949541 & -0.2962241 & -0.2659785\\
 \cellcolor{gray!6}{Nationalist Development} & \cellcolor{gray!6}{MECHANISATION} & \cellcolor{gray!6}{-0.445} & \cellcolor{gray!6}{0.052} & \cellcolor{gray!6}{-8.501} & \cellcolor{gray!6}{0e+00} & \cellcolor{gray!6}{-0.5481301} & \cellcolor{gray!6}{-0.3427323} & \cellcolor{gray!6}{-0.4454312} & \cellcolor{gray!6}{-0.3859243}\\
@@
 
-\caption{\label{tab:unnamed-chunk-47}Confirmatory Factor Analysis(CFA) on newly developed eco-pol scale}
+\caption{\label{tab:unnamed-chunk-53}Confirmatory Factor Analysis(CFA) on newly developed eco-pol scale}
 \centering
@@
 People Centered Development & Coal powered plants increases pollution of air/water/land. & 0.640 & 0.041 & 15.561 & 0.0e+00 & 0.5590262 & 0.7201432 & 0.6395847 & 0.7014985\\
-\cellcolor{gray!6}{People Centered Development} & \cellcolor{gray!6}{Large corporations are destroying the local industries in India and benefiting only a handful of people.} & \cellcolor{gray!6}{-0.634} & \cellcolor{gray!6}{0.057} & \cellcolor{gray!6}{-11.174} & \cellcolor{gray!6}{0.0e+00} & \cellcolor{gray!6}{-0.7449013} & \cellcolor{gray!6}{-0.5225822} & \cellcolor{gray!6}{-0.6337417} & \cellcolor{gray!6}{-0.5349921}\\
+\cellcolor{gray!6}{People Centered Development} & \cellcolor{gray!6}{Large corporations are destroying the local industries in India and benefiting only a handful of people.} & \cellcolor{gray!6}{0.634} & \cellcolor{gray!6}{0.057} & \cellcolor{gray!6}{11.174} & \cellcolor{gray!6}{0.0e+00} & \cellcolor{gray!6}{0.5225822} & \cellcolor{gray!6}{0.7449013} & \cellcolor{gray!6}{0.6337417} & \cellcolor{gray!6}{0.5349921}\\
 \addlinespace
 People Centered Development & Regardless of ownership, the government should pass strong regulations and implement them.
-& -0.509 & 0.054 & -9.351 & 0.0e+00 & -0.6162708 & -0.4027047 & -0.5094877 & -0.4577641\\
+& 0.509 & 0.054 & 9.351 & 0.0e+00 & 0.4027047 & 0.6162708 & 0.5094877 & 0.4577641\\
 \cellcolor{gray!6}{Nationalist Development} & \cellcolor{gray!6}{MECHANISATION} & \cellcolor{gray!6}{0.656} & \cellcolor{gray!6}{0.056} & \cellcolor{gray!6}{11.682} & \cellcolor{gray!6}{0.0e+00} & \cellcolor{gray!6}{0.5460463} & \cellcolor{gray!6}{0.7662170} & \cellcolor{gray!6}{0.6561317} & \cellcolor{gray!6}{0.5556245}\\

### 2024-03-25 withmice.Rmd
knitted results with mice to pdf

@@
     keep_tex: yes
+    keep_md: yes
+    latex_engine: xelatex
+geometry: "left=0.5cm,right=0.5cm,top=0.5cm,bottom=0.5cm"
 header-includes:
@@
   - \usepackage{array}
-  - "\\usepackage{placeins}"
-  keep_md: yes
+  - \usepackage{pdflscape}
+  - \newcommand{\blandscape}{\begin{landscape}}
+  - \newcommand{\elandscape}{\end{landscape}}
+html_document:
+  toc: yes
+  toc_depth: '2'
+  df_print: paged
 ---
@@
 suppressPackageStartupMessages(library(mice))
+library(officer)
+library(magrittr)
+library(kableExtra)
 
@@
 
+#sum(is.na(codedmodule2)) # 13 % of the data is missing.
+
 ```
@@
 # Plot the graph with facets for each Question
-ggplot(WBques_summary, aes(x = State, y = Proportion, fill = factor(Response, levels = rev(levels_defined)))) +
-  geom_bar(stat = "identity", position = "fill") +
-  scale_fill_manual(values = rev(colorsequence), name = NULL) +
-  facet_wrap(~ Question, scales = "free_y", ncol = 1) +
-  coord_flip() +
-  labs(x = "State", y = "Proportion", title = "Proportion of Responses by State for Nuclear energy related questions") +
-  theme_minimal() +
-  theme(
+#ggplot(WBques_summary, aes(x = State, y = Proportion, fill = factor(Response, levels = rev(levels_defined)))) +
+  #geom_bar(stat = "identity", position = "fill") +
+  #scale_fill_manual(values = rev(colorsequence), name = NULL) +
+  #facet_wrap(~ Question, scales = "free_y", ncol = 1) +
+  #coord_flip() +
+  #labs(x = "State", y = "Proportion", title = "Proportion of Responses by State for Nuclear energy related questions") +
+  #theme_minimal() +
+  #theme(
     # Increase the size of the main title
-    plot.title = element_text(size = 16, face = "bold"),
+    #plot.title = element_text(size = 16, face = "bold"),
     # Increase the size of the axis titles
-    axis.title = element_text(size = 14),
+    #axis.title = element_text(size = 14),
     # Increase the size of the facet strip text
-    strip.text.x = element_text(size = 12),
+    #strip.text.x = element_text(size = 12),
     # Adjust text angle for State labels if necessary
-    axis.text.y = element_text(angle = 0)
-  )
+    #axis.text.y = element_text(angle = 0)
+  #)
 
@@
 # Print the combined plot
-grid::grid.newpage()
-grid::grid.draw(combined_plot)
+#grid::grid.newpage()
+#grid::grid.draw(combined_plot)
 
@@
 
-n_acceptreject<- module2 %>%
-                dplyr::select("N_accept", "N_reluctantlyaccept", "N_reject")
-
-summary(n_acceptreject)
+#n_acceptreject<- module2 %>%
+                #dplyr::select("N_accept", "N_reluctantlyaccept", "N_reject")
+
+#summary(n_acceptreject)
 ```
@@
 #str(formice)
-summary(formice)
+#summary(formice)
 
@@
 
-sum(is.na(formice))
+#sum(is.na(formice))
 
@@
 
-str(kahanall)
-
-md.pattern(kahanall) #the variables with missing values: K_SHARM K_IPROTECT K_IPRIVACY K_SPROTECT K_SLIMCHOI K_IINTRFER K_HEQUAL K_HREVDIS1
-
-mcar_test(data=kahanall) # p values is less than 0.05 - the condition for MCAR is not met
+#str(kahanall)
+
+#md.pattern(kahanall) #the variables with missing values: K_SHARM K_IPROTECT K_IPRIVACY K_SPROTECT K_SLIMCHOI K_IINTRFER K_HEQUAL K_HREVDIS1
+
+#mcar_test(data=kahanall) # p values is less than 0.05 - the condition for MCAR is not met
 
@@
 dependent = "K_SHARM_MAR"
-MARkahan %>% 
-  missing_compare(dependent, explanatory) %>% 
-    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
-        caption = "comparisons between values of responders (Not missing) and 
-        non-responders (Missing) on the K_SHARM variable.")
-
-#   "K_IPROTECT" = "(I)It’s not the government’s business to try to protect people from themselves."
-explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
-dependent = "K_IPROTECT_MAR"
-MARkahan %>% 
-  missing_compare(dependent, explanatory) %>% 
-    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
-        caption = "comparisons between values of responders (Not missing) and 
-        non-responders (Missing) on the K_IPROTECT variable.")
-
-#  "K_SPROTECT" = "(C)The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.",
-explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
-dependent = "K_SPROTECT_MAR"
-MARkahan %>% 
-  missing_compare(dependent, explanatory) %>% 
-    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
-        caption = "comparisons between values of responders (Not missing) and 
-        non-responders (Missing) on the K_SPROTECT variable.")
-
-#  "K_SLIMCHOI" = "(C)The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.",
-explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
-dependent = "K_SLIMCHOI_MAR"
-MARkahan %>% 
-  missing_compare(dependent, explanatory) %>% 
-    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
-        caption = "comparisons between values of responders (Not missing) and 
-        non-responders (Missing) on the K_SPROTECT variable.")
+#MARkahan %>% 
+  #missing_compare(dependent, explanatory) %>% 
+    #knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
+        #caption = "comparisons between values of responders (Not missing) and 
+        #non-responders (Missing) on the K_SHARM variable.")
 
@@
 
-mikahan
-
 library(psych)
@@
 
-print.psych(fit, sort= TRUE, cut= 0.4)
+#print.psych(fit, sort= TRUE, cut= 0.4)
 
@@
 
-print.psych(kahanfit4, sort= TRUE, cut= 0.4)
-
-```
+#print.psych(kahanfit4, sort= TRUE, cut= 0.4)
+
+```
+
+\blandscape
+\newpage
 
@@
 
+\elandscape
+
 ## merging of imputation
@@
 
-kahan_imp <- mice(kahanall, m =5, maxit =30,  seed = 427, print = FALSE)
-
-kahan_imp$chainMean
+#kahan_imp <- mice(kahanall, m =5, maxit =30,  seed = 427, print = FALSE)
+
+#kahan_imp$chainMean
 
@@
 
-kahanallscores <- mice::complete(mice::mice(kahanall, m = 5, seed = 427, print = FALSE), "broad")
+kahanallscores <- mice::complete(mice::mice(kahanall, m = 50, seed = 427, print = FALSE), "broad")
 
@@
 
-str(kahanallscores)
+#str(kahanallscores)
 
@@
 ## corelation table
-```{r}
-
-cor(nkahanall)
+```{r, echo = FALSE}
+
+#cor(nkahanall)
 
 #before mice 
- cor.plot(kahanall %>% dplyr::select(-c("age", "gender", "caste", "State", "urban_rural", "religion")))
+#cor.plot(kahanall %>% dplyr::select(-c("age", "gender", "caste", "State", "urban_rural", "religion")))
 
 #after mice
- cor.plot(nkahanall)
-
-cov(nkahanall)
+
+#cor.plot(nkahanall)
+
+#cov(nkahanall)
 
@@
 
-nkahanfinal %>%
-  ggplot(aes(MR1, MR2))+
-  geom_count(aes(color = ..n.., size = ..n..))+
-  guides(color = 'legend')+
-  geom_hline(yintercept=0, colour="black", lwd=0.5)+
-  geom_vline(xintercept=0, colour="black", lwd=0.5)+
-  labs(x = "Hierarchy -Egalitarianism", y = "Individualism - Communitarianism")+
-  ylim(-2,3)+
-  xlim(-2,3)+
-  theme_minimal() 
+#nkahanfinal %>%
+  #ggplot(aes(MR1, MR2))+
+  #geom_count(aes(color = ..n.., size = ..n..))+
+  #guides(color = 'legend')+
+  #geom_hline(yintercept=0, colour="black", lwd=0.5)+
+  #geom_vline(xintercept=0, colour="black", lwd=0.5)+
+  #labs(x = "Hierarchy -Egalitarianism", y = "Individualism - Communitarianism")+
+  #ylim(-2,3)+
+  #xlim(-2,3)+
+  #theme_minimal() 
 ```
@@
 
-md.pattern(ecopoln) #the variables with missing values: PRIDENUCLEAR PROSPERNUCLEAR JOBSNUCLEAR HEALTHNUCLEAR BEAUTYNUCLEAR POLLUTENUCLEAR DISPLACENUCLEAR RELYNUCLEAR
-
-mcar_test(data=ecopoln) # p values is less than 0.76 - the condition for MCAR is met
+#md.pattern(ecopoln) #the variables with missing values: PRIDENUCLEAR PROSPERNUCLEAR JOBSNUCLEAR HEALTHNUCLEAR BEAUTYNUCLEAR POLLUTENUCLEAR DISPLACENUCLEAR RELYNUCLEAR
+
+#mcar_test(data=ecopoln) # p values is less than 0.76 - the condition for MCAR is met
 
@@
 dependent = "JOBSNUCLEAR_MAR"
-MARecopol %>% 
-  missing_compare(dependent, explanatory) %>% 
-    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
-        caption = "comparisons between values of responders (Not missing) and 
-        non-responders (Missing) on the JOBSNUCLEAR variable.")
-
-# PRIDENUCLEAR
-explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
-dependent = "PRIDENUCLEAR_MAR"
-MARecopol %>% 
-  missing_compare(dependent, explanatory) %>% 
-    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
-        caption = "comparisons between values of responders (Not missing) and 
-        non-responders (Missing) on the PRIDENUCLEAR variable.")
+#MARecopol %>% 
+  #missing_compare(dependent, explanatory) %>% 
+    #knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
+        #caption = "comparisons between values of responders (Not missing) and 
+        #non-responders (Missing) on the JOBSNUCLEAR variable.")
 
@@
 
-miecopol
-
 ecopolfit2 <- psych::fa(miecopol$cov_combined, nfactors = 2, rotate = "varimax")
 
-print.psych(ecopolfit2, sort= TRUE, cut= 0.4)
+#print.psych(ecopolfit2, sort= TRUE, cut= 0.4)
 
@@
 
+\newpage
 ## Radar map
@@
 
-nrow(ecopolfit2$loadings)
+#nrow(ecopolfit2$loadings)
 
@@
 
-```{r, echo=FALSE, fig.width=20, fig.height=18, out.width='70', out.height='70'}
+```{r, echo=FALSE, fig.width=8, fig.height=6, out.width='100%', out.height='100%'}
 library(fmsb)
@@
 ```
+
+\blandscape
+\newpage
 
@@
 
+\elandscape
+
 ```{r, echo = FALSE}
@@
 ```{r, echo=FALSE}
-Statenacheck1 <- allformice%>%
-  na.omit()%>%
-  dplyr::select(State)
-
-summary(Statenacheck1)
+
+#Statenacheck1 <- allformice %>%
+  #na.omit()%>%
+  #dplyr::select(State)
+
+#summary(Statenacheck1)
 ```
@@
 
-nuclear_missing <- allformice %>% dplyr::select(Risky_Nuclear,Uppercaste, Male, Hindu, urban_rural, Age, State)%>%
-  na.omit()
-
-summary(nuclear_missing)
+#nuclear_missing <- allformice %>% dplyr::select(Risky_Nuclear,Uppercaste, Male, Hindu, urban_rural, Age, State)%>%
+ #na.omit()
+
+#summary(nuclear_missing)
 
@@
 
-summary(nuclearfinal)
-summary(nuclearfinal2)
-summary(nuclearfinal3)
-summary(nuclearfinal4)
+#summary(nuclearfinal)
+#summary(nuclearfinal2)
+#summary(nuclearfinal3)
+#summary(nuclearfinal4)
 
@@
 
-print(aic_values)
+#print(aic_values)
 
@@
 
-print(bic_values)
+#print(bic_values)
 
@@
 
-cor.plot(nforcor)
+#cor.plot(nforcor)
 ```
@@
 
-summary(nuclearinterac)
-
-```
-
+#summary(nuclearinterac)
+
+```
+
+\newpage
+\blandscape
 # Stargazer : all LMs
@@
 
-#cat("\\begingroup")
-#cat("\\setlength{\\tabcolsep}{1pt}")
-#cat("\\renewcommand{\\arraystretch}{0.7}")
+cat("\\begingroup")
+cat("\\setlength{\\tabcolsep}{1pt}")
+cat("\\renewcommand{\\arraystretch}{0.7}")
 stargazer(nuclearfinal, nuclearfinal2, nuclearfinal3, nuclearfinal4, nuclearinterac,
           title = "Table 6: 5 linear models: Perceived Risk of Nuclear Energy",
-          type = "text"
-)
-#cat("\\endgroup")
-
-```
-
-\newpage
+          type = "latex"
+)
+cat("\\endgroup")
+
+```
+
+\elandscape
+
 # Paper 2
 
-## NUCLEAR2
+## NUCLEAR
 
@@
 ecopoln2 <- formice1 %>%
-  dplyr::select(
+  dplyr::select(DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE,
+    ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV,DEVOVERENV, OWNERPVT, OWNERPUB,
+    OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION,
     DISPLACENUCLEAR,  POLLUTENUCLEAR, HEALTHNUCLEAR, JOBSNUCLEAR, BEAUTYNUCLEAR,
@@
 
-str(ecopoln2)
-md.pattern(ecopoln2) #the variables with missing values:
-
-mcar_test(data=ecopoln2)
-```
-
-### Nuclear2 : Mifa
-
-```{r, echo=FALSE}
-
-library(mifa)
-
-miecopoln2 <- mifa(data= ecopoln2,
-                cov_vars = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
+#str(ecopoln2)
+#md.pattern(ecopoln2) #the variables with missing values:
+
+#mcar_test(data=ecopoln2)
+```
+
+## Mifa: only charcateristics of tech
+
+```{r, echo=FALSE}
+
+miecopol2 <- mifa(data= ecopoln,
+                cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion", DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE,
+    ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV,DEVOVERENV, OWNERPVT, OWNERPUB,
+    OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION),
                 m=50,
@@
                 progress= TRUE, 
-                seed = 528,)
-
-miecopoln2
-
-ecopolfitn2 <- psych::fa(miecopoln2$cov_combined, nfactors = 2, rotate = "varimax")
-
+                seed = 429,)
+
+ecopolfitn2 <- psych::fa(miecopol2$cov_combined, nfactors = 2, rotate = "varimax")
 print.psych(ecopolfitn2, sort= TRUE, cut= 0.4)
@@
 
-ecopoln2scores <- ecopoln2scores %>%dplyr::select(-(contains(c("age", "urban_rural", "gender","caste","religion", "State"))))
+ecopoln2scores <- ecopoln2scores %>%dplyr::select(-(contains(c("age", "urban_rural", "gender","caste","religion", "State",    "DECISIONDECEN", "DECISIONCEN", "INDUSTRYSMALL", "INDUSTRYLARGE","ECONOMYLOCAL", "ECONOMYGLOBAL", "ENVOVERDEV","DEVOVERENV", "OWNERPVT", "OWNERPUB","OWNERREG", "OWNERNOREG", "WEALTHLIM", "MECHANISATION"))))
 
@@
 
-### LM : Nuclear 2 and Kahan
-
-```{r}
+### LMs : characteristics of tech
+
+```{r, echo = FALSE}
 
@@
 
-nuclear2lm <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu +Age + State + DevPride + SocialCosts + Egalitarian + Communitarian, data = n2allfinal)
-
-summary(nuclear2lm)
-
-netnuclear2lm <- lm(Netben_Nuclear ~ Uppercaste + Male + Hindu +Age + State + DevPride + SocialCosts + Egalitarian + Communitarian, data = n2allfinal)
-
-summary(netnuclear2lm)
-
-bennuclear2lm <- lm(Ben_Nuclear ~ Uppercaste + Male + Hindu +Age + State + DevPride + SocialCosts + Egalitarian + Communitarian, data = n2allfinal)
-
-summary(bennuclear2lm)
+nuclear2lm <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu +Age + urban_rural+ State + DevPride + SocialCosts + Egalitarian + Communitarian, data = n2allfinal)
+
+#summary(nuclear2lm)
+
+netnuclear2lm <- lm(Netben_Nuclear ~ Uppercaste + Male + Hindu +Age + urban_rural+ State + DevPride + SocialCosts + Egalitarian + Communitarian, data = n2allfinal)
+
+#summary(netnuclear2lm)
+
+bennuclear2lm <- lm(Ben_Nuclear ~ Uppercaste + Male + Hindu +Age+ urban_rural + State + DevPride + SocialCosts + Egalitarian + Communitarian, data = n2allfinal)
+
+#summary(bennuclear2lm)
+
+```
+
+\newpage
+
+### Stargazer : characteristics of tech
+
+```{r, echo=FALSE, results='asis'}
+library(stargazer)
+
+cat("\\begingroup")
+cat("\\setlength{\\tabcolsep}{1pt}")
+cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer(nuclear2lm,  bennuclear2lm, netnuclear2lm,
+          title = "",
+          type = "latex"
+)
+cat("\\endgroup")
+
+```
+
+###  LMs : Nuclear all eco-pol
+
+```{r, echo = FALSE}
+
+allformicefinal2 <- allformicefinal%>%mutate(Netben_Nuclear = Ben_Nuclear - Risky_Nuclear,
+         Netben_Solar = Ben_Solar - Risky_Solar,
+         Netben_Coal = Ben_Coal - Risky_Coal)
+
+nuclearfinal4 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformicefinal2)
+
+bennuclear3lm <- lm(Ben_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformicefinal2)
+
+#summary(bennuclear3lm)
+
+netnuclear3lm <- lm(Netben_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformicefinal2)
+
+#summary(netnuclear3lm)
 
@@
 
-md.pattern(ecopols) #the variables with missing values:
-
-mcar_test(data=ecopols)
-```
-
-### Solar : Mifa for new eco-pol value scale
+#md.pattern(ecopols) #the variables with missing values:
+
+#mcar_test(data=ecopols)
+```
+
+### Solar : EFA Mifa all eco-pol
 
@@
                 cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
-                m=5,
+                m=50,
                 n_pc= 1:2,
@@
 
-miecopols
+# EFA with mifa
 
@@
 
-print.psych(ecopolfits, sort= TRUE, cut= 0.4)
-
-```
-
-### Solar 2 : only charcateristics of tech
+#print.psych(ecopolfits, sort= TRUE, cut= 0.4)
+
+```
+
+### Solar 2 : EFA dataset : only charcateristics of tech
 
@@
 
-str(ecopols2)
-md.pattern(ecopols2) #the variables with missing values:
-
-mcar_test(data=ecopols2)
-```
-
-### SOLAR2 : Mifa for new eco-pol value scale
+#str(ecopols2)
+#md.pattern(ecopols2) #the variables with missing values:
+
+#mcar_test(data=ecopols2)
+```
+
+### SOLAR2 : EFA Mifa : chaaracteristics of tech
 
@@
 
-miecopols2
-
 ecopolfits2 <- psych::fa(miecopols2$cov_combined, nfactors = 2, rotate = "varimax")
 
-print.psych(ecopolfits2, sort= TRUE, cut= 0.4)
-
-```
-
-### Factor Scores (mean across all imputations)
+#print.psych(ecopolfits2, sort= TRUE, cut= 0.4)
+
+```
+
+### only tech characters : Factor Scores (mean across all imputations)
 
@@
 
+# factor scores : characteristics of technology 
 secopol2final <- data.frame(factor.scores(ecopols2means[, 1:10], ecopolfits2)$scores)
@@
 
-### Solar LMs
-```{r}
+### LMs : only characteristics of technology
+
+```{r, echo = FALSE}
 
@@
 
-solar2lm <- lm(Risky_Solar ~ Uppercaste + Male + Hindu +Age + State + DevPride + SocialCosts + Egalitarian + Communitarian , data = n2allfinal)
-
-summary(solar2lm)
-
-netsolar2lm <- lm(Netben_Solar ~ Uppercaste + Male + Hindu +Age + State + DevPride + SocialCosts + Egalitarian + Communitarian, data = n2allfinal)
-
-summary(netsolar2lm)
-
-bensolar2lm <- lm(Ben_Solar ~ Uppercaste + Male + Hindu +Age + State + DevPride + SocialCosts + Egalitarian + Communitarian, data = n2allfinal)
-
-summary(bensolar2lm)
-
-```
-
-### Solar: Mifa with CFA
-
-```{r}
+solar2lm <- lm(Risky_Solar ~ Uppercaste + Male + Hindu +Age+ urban_rural + State + DevPride + SocialCosts + Egalitarian + Communitarian , data = n2allfinal)
+
+#summary(solar2lm)
+
+netsolar2lm <- lm(Netben_Solar ~ Uppercaste + Male + Hindu +Age + urban_rural+ State + DevPride + SocialCosts + Egalitarian + Communitarian, data = n2allfinal)
+
+#summary(netsolar2lm)
+
+bensolar2lm <- lm(Ben_Solar ~ Uppercaste + Male + Hindu +Age + urban_rural+ State + DevPride + SocialCosts + Egalitarian + Communitarian, data = n2allfinal)
+
+#summary(bensolar2lm)
+
+```
+
+\newpage 
+### Stargazer : EFA characteristics of technology
+
+```{r, echo=FALSE, results='asis'}
+library(stargazer)
+
+cat("\\begingroup")
+cat("\\setlength{\\tabcolsep}{1pt}")
+cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer(solar2lm,  bensolar2lm, netsolar2lm,
+          title = "",
+          type = "latex"
+)
+cat("\\endgroup")
+
+```
+
+### Solar: Mifa with CFA (Pdevelop and Ndevelop)
+
+```{r, echo = FALSE}
+
+# dataset with all eco-pol vars 
+#miecopols
 
@@
 secopol_cfa <- cfa(ecopols_2fa, data = miecopols$cov_combined, std.lv = TRUE)
-summary(secopol_cfa, fit.measure= TRUE, standardized = TRUE)
-
-```
-
-# COAL : MAR condition and missing data pattern
-
+#summary(secopol_cfa, fit.measure= TRUE, standardized = TRUE)
+
+```
+
+\blandscape
+\newpage
+
+### Pretty Table: CFA solar
+
+```{r, echo=FALSE}
+
+# Extract parameter estimates
+sparams <- parameterEstimates(secopol_cfa, standardized = TRUE)%>%
+   slice(1:(n()-13))
+
+sparams1 <- sparams %>%
+  mutate(rhs = case_when(
+  rhs == "DISPLACESOLAR" ~ "Solar energy is leading to displacement of people from their land",
+  rhs == "BEAUTYSOLAR" ~ "Solar energy spoils the natural beauty of the landscape",
+  rhs == "POLLUTESOLAR" ~ "Solar energy increases pollution of air/water/land",
+  rhs == "HEALTHSOLAR" ~ "Solar energy poses a great risk to the health of people living around it",
+  rhs == "JOBSSOLAR" ~ "Solar energy will bring jobs to the local community",
+  rhs == "PRIDESOLAR" ~ "I would be proud if my community used Solar energy",
+  rhs == "NPRIDESOLAR" ~ "Solar energy is a mark of pride for our nation",
+  rhs == "DEVSOLAR" ~ "Solar energy pushes forward the country's development",
+  rhs == "PROSPERSOLAR" ~ "Solar energy brings economic prosperity to the surrounding regions",
+  rhs == "RELYSOLAR" ~ "I don't like the idea that I have to rely on the government for electricity from Solar energy",
+  rhs == "INDUSTRYSMALL" ~ "Large corporations are destroying the local industries in India and benefiting only a handful of people",
+  rhs == "OWNERREG" ~ "Regardless of ownership, the government should pass strong regulations and implement them",
+  rhs == "MECHANISATION" ~ "Rapid mechanization of work is taking away jobs from workers in this country",
+  rhs == "ENVOVERDEV" ~ "Polluting industries that spoil the environment should be shut down even if it costs people their jobs",
+    TRUE ~ as.character(rhs)
+  )) %>%
+  dplyr::select(!c(lhs,op, std.nox)) %>%
+    rename(
+    "Items" = rhs,
+    "Loadings" = est,
+    "Standard Error" = se,
+    "zvalue" = z) %>%
+  mutate(across(c("Loadings", "Standard Error", "zvalue"), round, 3))
+
+sparams1$Scale <- NA
+sparams1$Scale[1:5] <- "People Centered Development"
+sparams1$Scale[6:10] <- "Nationalist Development"
+sparams1 <- sparams1[, c("Scale", setdiff(names(sparams1), "Scale"))]
+
+CFAsolar <- knitr::kable(sparams1, booktabs = TRUE, caption = "Confirmatory Factor Analysis(CFA) on eco-pol scale (Solar Energy)") %>%
+  kable_styling(latex_options = c("striped","scale_down", "hold_position", "repeat_header"))%>%
+  column_spec(column = 2, width = "4cm")
+
+# Print the table
+CFAsolar %>%
+  landscape()
+
+```
+
+\elandscape
+### CFA SCORES (mean across all imputations)
+
+```{r, echo=FALSE}
+
+ecopolallscoress2 <- mice::complete(mice::mice(ecopols, m = 50, seed = 429, print = FALSE), "broad")
+
+ecopolallscoress2 <- ecopolallscoress2 %>%dplyr::select(-(contains(c("age", "urban_rural", "gender","caste","religion", "State"))))
+
+#str(ecopolallscores)
+
+secopol2 <- ecopolallscoress2 %>%
+  rowwise() %>%
+  mutate(DEVSOLAR_mean = mean(c_across(starts_with("DEVSOLAR"))),
+         PROSPERSOLAR_mean = mean(c_across(starts_with("PROSPERSOLAR"))),
+         NPRIDESOLAR_mean = mean(c_across(starts_with("NPRIDESOLAR"))),
+         PRIDESOLAR_mean = mean(c_across(starts_with("PRIDESOLAR"))),
+         JOBSSOLAR_mean = mean(c_across(starts_with("JOBSSOLAR"))),
+         ECONOMYGLOBAL_mean = mean(c_across(starts_with("ECONOMYGLOBAL"))),
+         WEALTHLIM_mean = mean(c_across(starts_with("WEALTHLIM"))),
+         INDUSTRYLARGE_mean = mean(c_across(starts_with("INDUSTRYLARGE"))),
+         DECISIONCEN_mean = mean(c_across(starts_with("DECISIONCEN"))),
+         MECHANISATION_mean = mean(c_across(starts_with("MECHANISATION"))),
+         OWNERNOREG_mean = mean(c_across(starts_with("OWNERNOREG"))),
+         INDUSTRYSMALL_mean = mean(c_across(starts_with("INDUSTRYSMALL"))),
+         DEVOVERENV_mean = mean(c_across(starts_with("DEVOVERENV"))),
+         OWNERPVT_mean = mean(c_across(starts_with("OWNERPVT"))),
+         RELYSOLAR_mean = mean(c_across(starts_with("RELYSOLAR"))),
+         BEAUTYSOLAR_mean = mean(c_across(starts_with("BEAUTYSOLAR"))),
+         HEALTHSOLAR_mean = mean(c_across(starts_with("HEALTHSOLAR"))),
+         POLLUTESOLAR_mean = mean(c_across(starts_with("POLLUTESOLAR"))),
+         DISPLACESOLAR_mean = mean(c_across(starts_with("DISPLACESOLAR"))),
+         ENVOVERDEV_mean = mean(c_across(starts_with("ENVOVERDEV"))),
+         OWNERPUB_mean = mean(c_across(starts_with("OWNERPUB"))),
+         OWNERREG_mean = mean(c_across(starts_with("OWNERREG"))),
+         DECISIONDECEN_mean = mean(c_across(starts_with("DECISIONDECEN"))),
+         ECONOMYLOCAL_mean = mean(c_across(starts_with("ECONOMYLOCAL")))
+  ) %>%
+  ungroup()%>%
+  dplyr::select(contains("_mean")) %>%
+   rename_with(~ gsub("_mean$", "", .x))
+
+```
+
+```{r, echo = FALSE}
+
+solarCFAscores <- predict(secopol_cfa, newdata = secopol2)
+
+cfasolarscoresfinal  <- cbind(formice1, solarCFAscores, nkahanfinal) %>%
+      rename(Egalitarian = MR1, Communitarian = MR2)%>%mutate(Netben_Nuclear = Ben_Nuclear - Risky_Nuclear,
+         Netben_Solar = Ben_Solar - Risky_Solar,
+         Netben_Coal = Ben_Coal - Risky_Coal)
+
+```
+
+###  CFA LMs: Risk, Ben, Net Ben X Pdevelop Ndevelop
+
+```{r, echo = FALSE}
+
+solarfinal4 <- lm(Risky_Solar ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = cfasolarscoresfinal)
+
+#summary(solarfinal4)
+
+bensolar3lm <- lm(Ben_Solar ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = cfasolarscoresfinal)
+
+#summary(bensolar3lm)
+
+netsolar3lm <- lm(Netben_Solar ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = cfasolarscoresfinal)
+
+#summary(netsolar3lm)
+
+```
+
+### Stargazer : CFA Pdevelop Ndevelop
+
+```{r, echo=FALSE, results='asis'}
+library(stargazer)
+
+cat("\\begingroup")
+cat("\\setlength{\\tabcolsep}{1pt}")
+cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer(solarfinal4,  bensolar3lm, netsolar3lm,
+          title = "",
+          type = "latex"
+)
+cat("\\endgroup")
+
+```
+
+## COAL
+
+### Coal:MAR condition and missing data pattern
 ```{r, echo=FALSE}
@@
 
-md.pattern(ecopolc) #the variables with missing values:
-
-mcar_test(data=ecopolc)
-```
-
-# Coal : Mifa for new eco-pol value scale
+#md.pattern(ecopolc) #the variables with missing values:
+
+#mcar_test(data=ecopolc)
+```
+
+###  Mifa: EFA all ecopol
 
@@
 
-miecopolc
-
+# EFA With mifa - all ecopol vars for coal
 ecopolfitc <- psych::fa(miecopolc$cov_combined, nfactors = 3, rotate = "varimax")
 
-print.psych(ecopolfitc, sort= TRUE, cut= 0.4)
-
-```
-
-# COAL2 : only charcateristics of tech
+#print.psych(ecopolfitc, sort= TRUE, cut= 0.4)
+
+```
+
+### Dataset: only tech characters
 
@@
 
-md.pattern(ecopolc2) #the variables with missing values:
-
-mcar_test(data=ecopolc2)
-```
-
-# Coal2 : Mifa for new eco-pol value scale
+#md.pattern(ecopolc2) #the variables with missing values:
+
+#mcar_test(data=ecopolc2)
+```
+
+### EFA Mifa: only tech characters
 
@@
                 cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
-                m=5,
+                m=50,
                 n_pc= 2:4,
@@
 
-miecopolc2
-
 ecopolfitc2 <- psych::fa(miecopolc2$cov_combined, nfactors = 2, rotate = "varimax")
 
-print.psych(ecopolfitc2, sort= TRUE, cut= 0.4)
-
-```
-
-```{r}
-
-cor.plot(ecopolc %>% dplyr::select(-c("age", "gender", "caste", "State", "urban_rural", "religion")))
-```
-
-# Coal: Mifa with CFA
-
-```{r}
+#print.psych(ecopolfitc2, sort= TRUE, cut= 0.4)
+
+```
+
+```{r, echo = FALSE}
+
+#cor.plot(ecopolc %>% dplyr::select(-c("age", "gender", "caste", "State", "urban_rural", "religion")))
+```
+
+### CFA Mifa: Pdevelop n Ndevelop
+
+```{r, echo = FALSE}
 
@@
 ecopolc_2fa <- '
-  Pride =~ PRIDECOAL + NPRIDECOAL + DEVOVERENV +  DECISIONCEN + OWNERPVT + DECISIONCEN  + OWNERNOREG + ECONOMYGLOBAL
-  Social Costs =~ BEAUTYCOAL + POLLUTECOAL + HEALTHCOAL
-  Social Costs2 =~ OWNERPUB + ENVOVERDEV + DISPLACECOAL
+  Ndevelop =~ PRIDECOAL + NPRIDECOAL + DEVOVERENV +  DECISIONCEN + OWNERPVT + DECISIONCEN  + OWNERNOREG + DEVCOAL +PROSPERCOAL
+  Pdevelop =~ BEAUTYCOAL + POLLUTECOAL + HEALTHCOAL + OWNERPUB + ENVOVERDEV + DISPLACECOAL
 
@@
 cecopol_cfa <- cfa(ecopolc_2fa, data = miecopolc$cov_combined, std.lv = TRUE)
-summary(cecopol_cfa, fit.measure= TRUE, standardized = TRUE)
-
-```
-
-# EXTRA
-
-## Kahan: factor scores from 1st imputed dataset
-```{r, echo=FALSE}
-
-# extracting factor scores from mifa for 1st imputed dataset
-
-data_imp <- mice::complete(mice::mice(kahanall, 1, print = FALSE))
-
-fct_scores <- data.frame(factor.scores(data_imp[, 1:12], fit)$scores)
-
-plot(kahan_imp)
-
-```
-
-## Kahan: factor scores from second imputed dataset
-```{r, echo=FALSE}
-
-data_impk2 <- mice::complete(mice::mice(kahanall, 2, print = FALSE))
-
-fct_scoresk2 <- data.frame(factor.scores(data_impk2[, 1:12], fit)$scores)
-
-```
-
-## Kahan: factor scores from third imputed dataset
-```{r, echo=FALSE}
-
-data_impk3 <- mice::complete(mice::mice(kahanall, 3, print = FALSE))
-
-fct_scoresk3 <- data.frame(factor.scores(data_impk3[, 1:12], fit)$scores)
-
-```
-
-## Kahan: factor scores from fourth imputed dataset
-```{r, echo=FALSE}
-
-data_impk4 <- mice::complete(mice::mice(kahanall, 4, print = FALSE))
-
-fct_scoresk4 <- data.frame(factor.scores(data_impk4[, 1:12], fit)$scores)
-
-```
-
-## Kahan: factor scores from fifth imputed dataset
-```{r, echo=FALSE}
-
-data_impk5 <- mice::complete(mice::mice(kahanall, 5, print = FALSE))
-
-fct_scoresk5 <- data.frame(factor.scores(data_impk5[, 1:12], fit)$scores)
-
-```
-
-## are imputations plausible: Kahan scale - are values plausible ?
-
-yes all value are whole numbers between 1 and 5
-
-```{r, echo=FALSE}
-
-summary(mikahan)
-
-str(data_imp)
-names(mikahan)
-
-mikahan$mids
-
-complete_data_first <- complete(mikahan$mids, 1)
-
-summary(complete_data_first)
-
-complete_data_2 <- complete(mikahan$mids, 2)
-
-summary(complete_data_2)
-
-complete_data_3 <- complete(mikahan$mids, 3)
-
-summary(complete_data_3)
-
-complete_data_4 <- complete(mikahan$mids, 4)
-
-summary(complete_data_4)
-
-complete_data_5 <- complete(mikahan$mids, 5)
-
-summary(complete_data_5)
-```
-
-```{r, echo=FALSE}
-
-# Extracting factors from first imputed dataset
-
-data_imp2 <- mice::complete(mice::mice(ecopoln, 1, print = FALSE))
-
-fct_scores2 <- data.frame(factor.scores(data_imp2[, 1:24], ecopolfit2)$scores)
-
-```
-
-##  eco-pol scale : Factor scores from 2nd imputation
-```{r, echo=FALSE}
-
-data_impe2 <- mice::complete(mice::mice(ecopoln, 2, print = FALSE))
-
-fct_scorese2 <- data.frame(factor.scores(data_impe2[, 1:24], ecopolfit2)$scores)
-
-```
-
-##  eco-pol scale : Factor scores from 3rd imputation
-```{r, echo=FALSE}
-
-data_impe3 <- mice::complete(mice::mice(ecopoln, 3, print = FALSE))
-
-fct_scorese3 <- data.frame(factor.scores(data_impe3[, 1:24], ecopolfit2)$scores)
-
-```
-
-##  eco-pol scale : Factor scores from 4th imputation
-```{r, echo=FALSE}
-
-data_impe4 <- mice::complete(mice::mice(ecopoln, 4, print = FALSE))
-
-fct_scorese4 <- data.frame(factor.scores(data_impe4[, 1:24], ecopolfit2)$scores)
-
-```
-
-##  eco-pol scale : Factor scores from 5th imputation
-```{r, echo=FALSE}
-
-data_impe5 <- mice::complete(mice::mice(ecopoln, 5, print = FALSE))
-
-fct_scorese5 <- data.frame(factor.scores(data_impe5[, 1:24], ecopolfit2)$scores)
-
-```
-
-## Are imputations plausible : Eco-pol scale
-
-yes, imputations are pluasible- all natural numbers between 1 and 5
-
-```{r, echo=FALSE}
-
-summary(miecopol)
-names(miecopol)
-
-miecopol$mids
-
-complete_ecopol_first <- complete(miecopol$mids, 1)
-
-summary(complete_ecopol_first)
-
-complete_ecopol_2 <- complete(miecopol$mids, 2)
-
-summary(complete_ecopol_2)
-
-complete_ecopol_3 <- complete(miecopol$mids, 3)
-
-summary(complete_ecopol_3)
-
-complete_ecopol_4 <- complete(miecopol$mids, 4)
-
-summary(complete_ecopol_4)
-
-complete_ecopol_5 <- complete(miecopol$mids, 5)
-
-summary(complete_ecopol_5)
-
-```
-
-# Checking consistency of LM coefficients across 5 imputed datasets 
-coefficients and LMs are fairly consistent
-
-## Binding datasets: 1st imputation
+#summary(cecopol_cfa, fit.measure= TRUE, standardized = TRUE)
+
+```
+
+\blandscape
+
+\newpage
+### Pretty Table
+
+```{r, echo=FALSE}
+
+# Extract parameter estimates
+cparams <- parameterEstimates(cecopol_cfa, standardized = TRUE)%>%
+   slice(1:(n()-17))
+
+cparams1 <- cparams %>%
+  mutate(rhs = case_when(
+  rhs == "DISPLACECOAL" ~ "Coal powered plants is leading to displacement of people from their land",
+  rhs == "BEAUTYCOAL" ~ "Coal powered plants spoils the natural beauty of the landscape",
+  rhs == "POLLUTECOAL" ~ "Coal powered plants increases pollution of air/water/land",
+  rhs == "HEALTHCOAL" ~ "Coal powered plants poses a great risk to the health of people living around it",
+  rhs == "JOBSCOAL" ~ "Coal powered plants will bring jobs to the local community",
+  rhs == "PRIDECOAL" ~ "I would be proud if my community used Coal powered plants",
+  rhs == "NPRIDECOAL" ~ "Coal powered plants is a mark of pride for our nation",
+  rhs == "DEVCOAL" ~ "Coal powered plants pushes forward the country's development",
+  rhs == "PROSPERCOAL" ~ "Coal powered plants brings economic prosperity to the surrounding regions",
+  rhs == "RELYCOAL" ~ "I don't like the idea that I have to rely on the government for electricity from Coal powered plants",
+  rhs == "INDUSTRYSMALL" ~ "Large corporations are destroying the local industries in India and benefiting only a handful of people",
+  rhs == "OWNERREG" ~ "Regardless of ownership, the government should pass strong regulations and implement them",
+  rhs == "MECHANISATION" ~ "Rapid mechanization of work is taking away jobs from workers in this country",
+  rhs == "OWNERNOREG" ~ "There is too much red-tape and the government should not interfere with businesses and industries",
+  rhs == "DECISIONCEN" ~ "Laws and policies would be implemented more smoothly if more power lay with the central government",
+  rhs == "OWNERPVT" ~ "All businesses and industries should be owned privately",
+  rhs == "DEVOVERENV" ~ "Economic growth and creating jobs should be prioritized over environmental protection",
+  rhs == "OWNERPUB" ~ "The government should own most large businesses and industries",
+  rhs =="ENVOVERDEV" ~ "Polluting industries that spoil the environment should be shut down even if it costs people their jobs",
+    TRUE ~ as.character(rhs)
+  )) %>%
+  dplyr::select(!c(lhs,op, std.nox)) %>%
+    rename(
+    "Items" = rhs,
+    "Loadings" = est,
+    "Standard Error" = se,
+    "zvalue" = z) %>%
+  mutate(across(c("Loadings", "Standard Error", "zvalue"), round, 3))
+
+cparams1$Scale <- NA
+cparams1$Scale[1:8] <- "People Centered Development"
+cparams1$Scale[9:14] <- "Nationalist Development"
+cparams1 <- cparams1[, c("Scale", setdiff(names(sparams1), "Scale"))]
+CFAcoal <- knitr::kable(cparams1, booktabs = TRUE, caption = "Confirmatory Factor Analysis(CFA) on eco-pol scale (Coal)") %>%
+  kable_styling(latex_options = c("striped","scale_down", "hold_position", "repeat_header"))%>%
+  column_spec(column = 2, width = "4cm")
+
+# Print the table
+CFAcoal %>%
+  landscape()
+
+```
+
+\elandscape
+### Alpha test
+
+```{r, echo=FALSE}
+
+cNdevelop <-ecopolc %>%
+  dplyr::select((c(PRIDECOAL, NPRIDECOAL, DEVOVERENV, DECISIONCEN, OWNERPVT, OWNERNOREG, ECONOMYGLOBAL, DEVCOAL, PROSPERCOAL)))
+
+cNdevelop_alpha <- psych::alpha(cNdevelop, check.keys = TRUE) # alpha = 0.62
+
+cPdevelop <-ecopolc %>%
+  dplyr::select((c(BEAUTYCOAL , POLLUTECOAL , HEALTHCOAL , OWNERPUB , ENVOVERDEV , DISPLACECOAL)))
+
+nPdevelop_alpha <- psych::alpha(nPdevelop , check.keys = TRUE) # alpha = 0.79
+
+```
+
+### EFA Scores: only tech characteristics
+
+```{r, echo=FALSE}
+
+ecopolc2scores <- mice::complete(mice::mice(ecopolc2, m = 50, seed = 429, print = FALSE), "broad")
+
+ecopolc2scores <- ecopolc2scores %>%dplyr::select(-(contains(c("age", "urban_rural", "gender","caste","religion", "State"))))
+
+#str(ecopolallscores)
+
+ecopolc2means <- ecopolc2scores %>%
+  rowwise() %>%
+  mutate(DEVCOAL_mean = mean(c_across(starts_with("DEVCOAL"))),
+         PROSPERCOAL_mean = mean(c_across(starts_with("PROSPERCOAL"))),
+         NPRIDECOAL_mean = mean(c_across(starts_with("NPRIDECOAL"))),
+         PRIDECOAL_mean = mean(c_across(starts_with("PRIDECOAL"))),
+         JOBSCOAL_mean = mean(c_across(starts_with("JOBSCOAL"))),
+         RELYCOAL_mean = mean(c_across(starts_with("RELYCOAL"))),
+         BEAUTYCOAL_mean = mean(c_across(starts_with("BEAUTYCOAL"))),
+         HEALTHCOAL_mean = mean(c_across(starts_with("HEALTHCOAL"))),
+         POLLUTECOAL_mean = mean(c_across(starts_with("POLLUTECOAL"))),
+         DISPLACECOAL_mean = mean(c_across(starts_with("DISPLACECOAL"))),
+  ) %>%
+  ungroup()%>%
+  dplyr::select(contains("_mean")) %>%
+   rename_with(~ gsub("_mean$", "", .x))
+
+# factor scores - EFA 
+cecopol2final <- data.frame(factor.scores(ecopolc2means[, 1:10], ecopolfitc2)$scores)
+
+```
+
+### LMs : EFA only tech characs
 
@@
 
-# binding the imputed  factor analysis scores for kahan scale and eco-pol value scale to the larger dataset codedmodule2
-
-ecopolnuclear <- fct_scores2 %>%
-  rename(Ndevelop = MR1, Pdevelop = MR2)
-
-kahannuclear <- fct_scores%>%
+ecopolc2final <- cecopol2final %>%
+  rename(DevPride = MR1, SocialCosts = MR2)
+
+kahannuclearfinal <- nkahanfinal%>%
   rename(Egalitarian = MR1, Communitarian = MR2)
 
-allformice<- cbind(formice1,ecopolnuclear, kahannuclear)
-
-```
-
-## LMs with 1st imputed datasets from FAs
-
-```{r, echo=FALSE}
-
-nuclearIVmice <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformice)
-
-nuclearIVmice2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian, data = allformice)
-
-nuclearIVmice3 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformice)
-
-summary(nuclearIVmice)
-summary(nuclearIVmice2)
-summary(nuclearIVmice3)
-
-```
-
-## binding dataset - 2nd imputation
-
-```{r, echo=FALSE}
-
-ecopolnuclear2 <- fct_scorese2 %>%
-  rename(Ndevelop = MR1, Pdevelop = MR2)
-
-kahannuclear2 <- fct_scoresk2%>%
-  rename(Egalitarian = MR1, Communitarian = MR2)
-
-allformice2<- cbind(formice1,ecopolnuclear2, kahannuclear2)
-
-```
-
-## LMs with second imputation 
-```{r, echo=FALSE}
-
-nuclearIVmiceimp2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformice2)
-
-nuclearIVmiceimp22 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian, data = allformice2)
-
-nuclearIVmiceimp23 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformice2)
-
-summary(nuclearIVmiceimp2)
-summary(nuclearIVmiceimp22)
-summary(nuclearIVmiceimp23)
-
-```
-
-## binding dataset - 3rd imputation
-
-```{r, echo=FALSE}
-
-ecopolnuclear3 <- fct_scorese3 %>%
-  rename(Ndevelop = MR1, Pdevelop = MR2)
-
-kahannuclear3 <- fct_scoresk3%>%
-  rename(Egalitarian = MR1, Communitarian = MR2)
-
-allformice3<- cbind(formice1,ecopolnuclear3, kahannuclear3)
-
-```
-
-## LMs with third imputation 
-```{r, echo=FALSE}
-
-nuclearIVmiceimp3 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformice3)
-
-nuclearIVmiceimp32 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian, data = allformice3)
-
-nuclearIVmiceimp33 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformice3)
-
-summary(nuclearIVmiceimp3)
-summary(nuclearIVmiceimp32)
-summary(nuclearIVmiceimp33)
-
-```
-
-## binding dataset - 4th imputation
-
-```{r, echo=FALSE}
-
-ecopolnuclear4 <- fct_scorese4 %>%
-  rename(Ndevelop = MR1, Pdevelop = MR2)
-
-kahannuclear4 <- fct_scoresk4%>%
-  rename(Egalitarian = MR1, Communitarian = MR2)
-
-allformice4<- cbind(formice1, ecopolnuclear4, kahannuclear4)
-
-```
-
-## LMs with fourth imputation 
-```{r, echo=FALSE}
-
-nuclearIVmiceimp4 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformice4)
-
-nuclearIVmiceimp24 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian, data = allformice4)
-
-nuclearIVmiceimp34 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformice4)
-
-summary(nuclearIVmiceimp4)
-summary(nuclearIVmiceimp24)
-summary(nuclearIVmiceimp34)
-
-```
-
-```{r, echo=FALSE}
-
-# Allformice: Do imputations merge ?
-
-# Initialize the mice process to create the predictor matrix
-#ini <- mice(allformice, maxit = 0, pri = FALSE)
-
-# Extract the predictor matrix from the initialized object
-#pred <- ini$predictorMatrix
-
-# Set the columns for "Uppercaste", "Male", "Hindu", and "Age" to 0
-#pred[, "Uppercaste"] <- 0
-#pred[, "Male"] <- 0
-#pred[, "Hindu"] <- 0
-#pred[, "Age"] <- 0
-#pred[, "Ndevelop"] <- 0
-#pred[, "Pdevelop"] <- 0
-#pred[, "Egalitarian"] <- 0
-#pred[, "Communitarian"] <- 0
-# Identify columns that start with "K_" and set them to 0
-#k_columns <- grep("^K_", colnames(formice1))
-#pred[, k_columns] <- 0
-
-# Perform the mice imputation with the updated predictor matrix
-#allformice.imp <- mice(allformice, m = 5, maxit = 10, predictorMatrix = pred, seed = 430, print = TRUE)
-
-#summary(allformice.imp)
-#allformice.imp$chainMean
-
-#plot(allformice.imp)
-
-```
-
-```{r, echo=FALSE}
-
-# LM with demographic variables and State 
-# The pool() function from the mice package creates a list containing the results,
-# so we need to access the summary of the model directly.
-
-#pooled_fit4 <- pool(nuclearfit4)
-
-#pooled_summary4 <- summary(pooled_fit4)
-
-#coefficients_df4 <- pooled_summary4
-# To ensure the numeric values are rounded to two decimal places, you can use:
-#coefficients_df4 <- round(coefficients_df4[, -1], 2)  # Skipping the first column as it's factors (term names)
-#coefficients_df4$term <- pooled_summary4$term  # Adding back the unrounded terms
-
-# Print the dataframe
-#data.frame(coefficients_df4) %>%
- # dplyr::select(term, estimate, std.error, statistic, df, p.value)
-```
+c2allfinal <- cbind(formice1, ecopolc2final, kahannuclearfinal)%>%
+   mutate(Netben_Nuclear = Ben_Nuclear - Risky_Nuclear,
+         Netben_Solar = Ben_Solar - Risky_Solar,
+         Netben_Coal = Ben_Coal - Risky_Coal)
+
+coal2lm <- lm(Risky_Coal ~ Uppercaste + Male + Hindu +Age+ urban_rural + State + DevPride + SocialCosts + Egalitarian + Communitarian , data = c2allfinal)
+
+#summary(coal2lm)
+
+netcoal2lm <- lm(Netben_Coal ~ Uppercaste + Male + Hindu +Age+ urban_rural + State + DevPride + SocialCosts + Egalitarian + Communitarian, data = c2allfinal)
+
+#summary(netcoal2lm)
+
+bencoal2lm <- lm(Ben_Coal ~ Uppercaste + Male + Hindu +Age + urban_rural+ State + DevPride + SocialCosts + Egalitarian + Communitarian, data = c2allfinal)
+
+#summary(bencoal2lm)
+
+```
+
+### CFA SCORES (mean across all imputations)
+
+```{r, echo=FALSE}
+
+ecopolallscoresc2 <- mice::complete(mice::mice(ecopolc, m = 50, seed = 429, print = FALSE), "broad")
+
+ecopolallscoresc2 <- ecopolallscoresc2 %>%dplyr::select(-(contains(c("age", "urban_rural", "gender","caste","religion", "State"))))
+
+#str(ecopolallscores)
+
+cecopol2 <- ecopolallscoresc2 %>%
+  rowwise() %>%
+  mutate(DEVCOAL_mean = mean(c_across(starts_with("DEVCOAL"))),
+         PROSPERCOAL_mean = mean(c_across(starts_with("PROSPERCOAL"))),
+         NPRIDECOAL_mean = mean(c_across(starts_with("NPRIDECOAL"))),
+         PRIDECOAL_mean = mean(c_across(starts_with("PRIDECOAL"))),
+         JOBSCOAL_mean = mean(c_across(starts_with("JOBSCOAL"))),
+         ECONOMYGLOBAL_mean = mean(c_across(starts_with("ECONOMYGLOBAL"))),
+         WEALTHLIM_mean = mean(c_across(starts_with("WEALTHLIM"))),
+         INDUSTRYLARGE_mean = mean(c_across(starts_with("INDUSTRYLARGE"))),
+         DECISIONCEN_mean = mean(c_across(starts_with("DECISIONCEN"))),
+         MECHANISATION_mean = mean(c_across(starts_with("MECHANISATION"))),
+         OWNERNOREG_mean = mean(c_across(starts_with("OWNERNOREG"))),
+         INDUSTRYSMALL_mean = mean(c_across(starts_with("INDUSTRYSMALL"))),
+         DEVOVERENV_mean = mean(c_across(starts_with("DEVOVERENV"))),
+         OWNERPVT_mean = mean(c_across(starts_with("OWNERPVT"))),
+         RELYCOAL_mean = mean(c_across(starts_with("RELYCOAL"))),
+         BEAUTYCOAL_mean = mean(c_across(starts_with("BEAUTYCOAL"))),
+         HEALTHCOAL_mean = mean(c_across(starts_with("HEALTHCOAL"))),
+         POLLUTECOAL_mean = mean(c_across(starts_with("POLLUTECOAL"))),
+         DISPLACECOAL_mean = mean(c_across(starts_with("DISPLACECOAL"))),
+         ENVOVERDEV_mean = mean(c_across(starts_with("ENVOVERDEV"))),
+         OWNERPUB_mean = mean(c_across(starts_with("OWNERPUB"))),
+         OWNERREG_mean = mean(c_across(starts_with("OWNERREG"))),
+         DECISIONDECEN_mean = mean(c_across(starts_with("DECISIONDECEN"))),
+         ECONOMYLOCAL_mean = mean(c_across(starts_with("ECONOMYLOCAL")))
+  ) %>%
+  ungroup()%>%
+  dplyr::select(contains("_mean")) %>%
+   rename_with(~ gsub("_mean$", "", .x))
+
+```
+
+```{r, echo = FALSE}
+
+coalCFAscores <- predict(cecopol_cfa, newdata = cecopol2)
+
+cfacoalscoresfinal  <- cbind(formice1, coalCFAscores, nkahanfinal) %>%
+      rename(Egalitarian = MR1, Communitarian = MR2)%>%mutate(Netben_Nuclear = Ben_Nuclear - Risky_Nuclear,
+         Netben_Solar = Ben_Solar - Risky_Solar,
+         Netben_Coal = Ben_Coal - Risky_Coal)
+
+```
+
+###  CFA LMs : Pdevelop Ndevelop
+
+```{r, echo = FALSE}
+
+coalfinal4 <- lm(Risky_Coal ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Ndevelop + Pdevelop, data = cfacoalscoresfinal)
+
+#summary(coalfinal4)
+
+bencoal3lm <- lm(Ben_Coal ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Ndevelop + Pdevelop, data = cfacoalscoresfinal)
+
+#summary(bencoal3lm)
+
+netcoal3lm <- lm(Netben_Coal ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Ndevelop + Pdevelop, data = cfacoalscoresfinal)
+
+#summary(netcoal3lm)
+
+```
+
+\blandscape
+\newpage
+
+## Stargazer : risk and benefit X all ecopol
+
+```{r, echo=FALSE, results='asis'}
+library(stargazer)
+
+cat("\\begingroup")
+cat("\\small")  # Adjusts the font size
+cat("\\setlength{\\tabcolsep}{1pt}")
+cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer(nuclearfinal4, solarfinal4, coalfinal4, bennuclear3lm, bensolar3lm, bencoal3lm,
+          title = " Perceived risk and Perceived benefit(Nuclear, Solar, Coal)",
+          type = "latex"
+)
+cat("\\endgroup")
+
+```
+\elandscape
+
+\newpage
+## Stargazer : benefit X all ecopol
+
+```{r, echo=FALSE, results='asis'}
+library(stargazer)
+
+cat("\\begingroup")
+cat("\\setlength{\\tabcolsep}{1pt}")
+cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer( bennuclear3lm, bensolar3lm, bencoal3lm,
+          title = "",
+          type = "latex"
+)
+cat("\\endgroup")
+
+```
+
+\newpage
+
+## Stargazer : net benefit X all ecopol
+
+```{r, echo=FALSE, results='asis'}
+library(stargazer)
+
+cat("\\begingroup")
+cat("\\setlength{\\tabcolsep}{1pt}")
+cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer(netnuclear3lm,  netsolar3lm, netcoal3lm,
+          title = "",
+          type = "latex"
+)
+cat("\\endgroup")
+
+```
+
+\newpage
+\blandscape
+
+## Stargazer : risk  X characteristics of tech
+
+```{r, echo=FALSE, results='asis'}
+library(stargazer)
+
+cat("\\begingroup")
+cat("\\small")  # Adjusts the font size
+cat("\\setlength{\\tabcolsep}{1pt}")
+cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer(nuclear2lm, solar2lm, coal2lm,bennuclear2lm, bensolar2lm, bencoal2lm,
+          title = "",
+          type = "latex"
+)
+cat("\\endgroup")
+
+```
+
+\elandscape
+
+\newpage
+## Stargazer : ben  X characteristics of tech
+
+```{r, echo=FALSE, results='asis'}
+library(stargazer)
+
+cat("\\begingroup")
+cat("\\setlength{\\tabcolsep}{1pt}")
+cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer(bennuclear2lm, bensolar2lm, bencoal2lm, 
+          title = "",
+          type = "latex"
+)
+cat("\\endgroup")
+
+```
+
+\newpage
+## Stargazer : netben  X characteristics of tech
+
+```{r, echo=FALSE, results='asis'}
+library(stargazer)
+
+cat("\\begingroup")
+cat("\\setlength{\\tabcolsep}{1pt}")
+cat("\\renewcommand{\\arraystretch}{0.7}")
+stargazer(netnuclear2lm, netsolar2lm, netcoal2lm, 
+          title = "",
+          type = "latex"
+)
+cat("\\endgroup")
+
+```

### 2024-03-25 withmice.Rmd
conducted cronbach's alpha test for coal eco-pol with mice

@@
 
-#print.psych(ecopolfit2, sort= TRUE, cut= 0.4)
+print.psych(ecopolfit2, sort= TRUE, cut=0.4)
 
@@
 
+```{r, echo=FALSE}
+
+# covariance matrix fro mifa ecopol solar 
+#miecopols$cov_combined
+
+```
+
 ### Solar: Mifa with CFA (Pdevelop and Ndevelop)
@@
   Ndevelop =~ DEVSOLAR + PRIDESOLAR + NPRIDESOLAR + PROSPERSOLAR + JOBSSOLAR
-  Pdevelop =~ HEALTHSOLAR + BEAUTYSOLAR + DISPLACESOLAR + POLLUTESOLAR + ENVOVERDEV
+  Pdevelop =~ HEALTHSOLAR + BEAUTYSOLAR + DISPLACESOLAR + POLLUTESOLAR +ENVOVERDEV
 '
 
-secopol_cfa <- cfa(ecopols_2fa, data = miecopols$cov_combined, std.lv = TRUE)
-#summary(secopol_cfa, fit.measure= TRUE, standardized = TRUE)
+secopol_cfa <- cfa(ecopols_2fa, sample.cov = miecopols$cov_combined, sample.nobs = 1099, std.lv = TRUE) # std.lv = TRUE to do variance standardization method
+summary(secopol_cfa, fit.measure= TRUE, standardized = TRUE)
 
@@
 sparams <- parameterEstimates(secopol_cfa, standardized = TRUE)%>%
-   slice(1:(n()-13))
+   slice(1:(n()-11))
 
@@
   mutate(rhs = case_when(
-  rhs == "DISPLACESOLAR" ~ "Solar energy is leading to displacement of people from their land",
-  rhs == "BEAUTYSOLAR" ~ "Solar energy spoils the natural beauty of the landscape",
+  rhs == "DEVSOLAR" ~ "Solar energy pushes forward the country's development",
+  rhs == "PRIDESOLAR" ~ "I would be proud if my community used Solar energy",
+  rhs == "NPRIDESOLAR" ~ "Solar energy is a mark of pride for our nation",
+  rhs == "PROSPERSOLAR" ~ "Solar energy brings economic prosperity to the surrounding regions",
+  rhs == "JOBSSOLAR" ~ "Solar energy will bring jobs to the local community",
   rhs == "POLLUTESOLAR" ~ "Solar energy increases pollution of air/water/land",
   rhs == "HEALTHSOLAR" ~ "Solar energy poses a great risk to the health of people living around it",
-  rhs == "JOBSSOLAR" ~ "Solar energy will bring jobs to the local community",
-  rhs == "PRIDESOLAR" ~ "I would be proud if my community used Solar energy",
-  rhs == "NPRIDESOLAR" ~ "Solar energy is a mark of pride for our nation",
-  rhs == "DEVSOLAR" ~ "Solar energy pushes forward the country's development",
-  rhs == "PROSPERSOLAR" ~ "Solar energy brings economic prosperity to the surrounding regions",
+  rhs == "BEAUTYSOLAR" ~ "Solar energy spoils the natural beauty of the landscape",
+  rhs == "DISPLACESOLAR" ~ "Solar energy is leading to displacement of people from their land",
+  rhs == "ENVOVERDEV" ~ "Polluting industries that spoil the environment should be shut down even if it costs people their jobs",
   rhs == "RELYSOLAR" ~ "I don't like the idea that I have to rely on the government for electricity from Solar energy",
@@
   rhs == "MECHANISATION" ~ "Rapid mechanization of work is taking away jobs from workers in this country",
-  rhs == "ENVOVERDEV" ~ "Polluting industries that spoil the environment should be shut down even if it costs people their jobs",
     TRUE ~ as.character(rhs)
@@
 sparams1$Scale <- NA
-sparams1$Scale[1:5] <- "People Centered Development"
-sparams1$Scale[6:10] <- "Nationalist Development"
+sparams1$Scale[1:4] <- "People Centered Development"
+sparams1$Scale[5:8] <- "Nationalist Development"
 sparams1 <- sparams1[, c("Scale", setdiff(names(sparams1), "Scale"))]
@@
   landscape()
+
+```
+
+```{r fit-measures-display, echo = FALSE}
+# Extract fit measures
+fit_measuress <- fitMeasures(secopol_cfa, fit.measures = c("CFI", "TLI", "RMSEA", "rmsea.ci.upper", "rmsea.ci.lower"))
+fit_measuress2 <- fitMeasures(secopol_cfa)
+# Convert to a data frame for presentation
+fit_dfs <- data.frame(Measure = names(fit_measuress), Value = fit_measuress) %>%
+  mutate(Measure = case_when(
+    Measure == "cfi" ~ "Comparative Fit Index (CFI) ",
+    Measure == "tli" ~ "Tucker-Lewis Index (TLI)",
+    Measure == "rmsea" ~ "Root Mean Square Error of Approximation(RMSEA)",
+    Measure == "rmsea.ci.upper" ~ "RMSEA 90 Percent confidence interval - lower",
+    Measure == "rmsea.ci.lower" ~ "RMSEA 90 Percent confidence interval - upper",
+    TRUE ~ as.character(Measure)
+  )) %>%
+  mutate(Value = round(Value, 3)) %>%
+  remove_rownames()
+
+#RMSEA - between 0.05 and 0.08 (reasonable fit), less than 0.05 close fit and greater than 0.10 is poor fit 
+#CFI - greater than 0.90 or 0.95 indicates good fit
+#TFI - CFI>TFI >0.90 - indicates good fit
+
+```
+
+# Confirmatory Factor Analysis(CFA): Solar
+
+```{r, echo =FALSE}
+# Display fit measures using kable
+knitr::kable(fit_dfs, caption = "Fit Measures: CFA Solar energy", booktabs = TRUE) %>%
+  kable_styling(latex_options = c("striped", "hold_position"))
 
@@
 
-#print.psych(ecopolfitc, sort= TRUE, cut= 0.4)
+print.psych(ecopolfitc, sort= TRUE, cut= 0.4)
 
@@
 
-#print.psych(ecopolfitc2, sort= TRUE, cut= 0.4)
+print.psych(ecopolfitc2, sort= TRUE, cut= 0.4)
 
@@
 ecopolc_2fa <- '
-  Ndevelop =~ PRIDECOAL + NPRIDECOAL + DEVOVERENV +  DECISIONCEN + OWNERPVT + DECISIONCEN  + OWNERNOREG + DEVCOAL +PROSPERCOAL
-  Pdevelop =~ BEAUTYCOAL + POLLUTECOAL + HEALTHCOAL + OWNERPUB + ENVOVERDEV + DISPLACECOAL
+  Ndevelop =~ DEVCOAL+ PROSPERCOAL + NPRIDECOAL + PRIDECOAL  + JOBSCOAL + ECONOMYGLOBAL+ WEALTHLIM+ INDUSTRYLARGE+ DECISIONCEN + MECHANISATION + DEVOVERENV
+  Pdevelop =~ BEAUTYCOAL + + HEALTHCOAL + POLLUTECOAL 
+  Pdevelop2 =~  DISPLACECOAL  + ENVOVERDEV +OWNERPUB
 
@@
 
-cecopol_cfa <- cfa(ecopolc_2fa, data = miecopolc$cov_combined, std.lv = TRUE)
-#summary(cecopol_cfa, fit.measure= TRUE, standardized = TRUE)
+cecopol_cfa <- cfa(ecopolc_2fa, sample.cov = miecopolc$cov_combined, sample.nobs = 1099, std.lv = TRUE)
+summary(cecopol_cfa, fit.measure= TRUE, standardized = TRUE)
 
@@
 \elandscape
-### Alpha test
-
-```{r, echo=FALSE}
-
-cNdevelop <-ecopolc %>%
-  dplyr::select((c(PRIDECOAL, NPRIDECOAL, DEVOVERENV, DECISIONCEN, OWNERPVT, OWNERNOREG, ECONOMYGLOBAL, DEVCOAL, PROSPERCOAL)))
-
-cNdevelop_alpha <- psych::alpha(cNdevelop, check.keys = TRUE) # alpha = 0.62
-
-cPdevelop <-ecopolc %>%
-  dplyr::select((c(BEAUTYCOAL , POLLUTECOAL , HEALTHCOAL , OWNERPUB , ENVOVERDEV , DISPLACECOAL)))
-
-nPdevelop_alpha <- psych::alpha(nPdevelop , check.keys = TRUE) # alpha = 0.79
-
-```
 
@@
 
+### Alpha test
+
+```{r, echo=FALSE}
+
+cNdevelop <-cecopol2 %>%
+  dplyr::select((c(PRIDECOAL, NPRIDECOAL, DEVOVERENV, DECISIONCEN, OWNERPVT, OWNERNOREG, ECONOMYGLOBAL, DEVCOAL, PROSPERCOAL)))
+
+cNdevelop_alpha <- psych::alpha(cNdevelop, check.keys = TRUE) # alpha = 0.75
+
+cPdevelop <-cecopol2 %>%
+  dplyr::select((c(BEAUTYCOAL , POLLUTECOAL , HEALTHCOAL , OWNERPUB , ENVOVERDEV , DISPLACECOAL)))
+
+nPdevelop_alpha <- psych::alpha(nPdevelop , check.keys = TRUE) # alpha = 0.78
+
+```
+
 ```{r, echo = FALSE}

### 2024-03-27 Paper1.Rmd
cfa for coal fixed

@@
 
-#kable_table <- kable(correlation_df, caption = "Correlation Table between Perceived Risk and Perceived Benefit Variables", format = "html", #digits = 2) %>%
-  #kable_styling(full_width = F) %>%
-  #column_spec(1, background = "white") %>%
-  #add_header_above(c(" " = 1, "Perceived Benefits" = ncol(correlation_df)))#%>%
-  #pack_rows("Perceived Risks", 1, nrow(correlation_df))
+kable_table <- kable(correlation_df, caption = " Table 8 : Correlation Table between Perceived Risk and Perceived Benefit Variables", format = "html", digits = 2) %>%
+  kable_styling(full_width = F) %>%
+  column_spec(1, background = "white") %>%
+  add_header_above(c(" " = 1, "Perceived Benefits" = ncol(correlation_df)))%>%
+  pack_rows("Perceived Risks", 1, nrow(correlation_df))
 
 # Apply alternating background colors for columns
-#for (i in seq(2, ncol(correlation_df), by = 2)) {
-  #kable_table <- kable_table %>%
-
-#row_spec(i, background = "#F0F0F0")
-#}
+for (i in seq(2, ncol(correlation_df), by = 2)) {
+  kable_table <- kable_table %>% 
+row_spec(i, background = "#F0F0F0")
+}
 
 # Print the kable table
-#print(kable_table)
+print(kable_table)
 ```

### 2024-03-27 withmice.Rmd
cfa for coal fixed

@@
 
-# EFA with mifa
-
-ecopolfits <- psych::fa(miecopols$cov_combined, nfactors = 2, rotate = "varimax")
-
-#print.psych(ecopolfits, sort= TRUE, cut= 0.4)
+# EFA with mifamiecopols$cov_combined
+
+ecopolfits <- psych::fa(miecopols$cov_combined, nfactors = 3, rotate = "varimax")
+
+print.psych(ecopolfits, sort= TRUE, cut= 0.4)
 
@@
   Ndevelop =~ DEVSOLAR + PRIDESOLAR + NPRIDESOLAR + PROSPERSOLAR + JOBSSOLAR
-  Pdevelop =~ HEALTHSOLAR + BEAUTYSOLAR + DISPLACESOLAR + POLLUTESOLAR +ENVOVERDEV
+  Pdevelop =~ HEALTHSOLAR + BEAUTYSOLAR + DISPLACESOLAR + POLLUTESOLAR 
 '
@@
 
-# Confirmatory Factor Analysis(CFA): Solar
+### Confirmatory Factor Analysis(CFA): Solar
 
@@
 # EFA With mifa - all ecopol vars for coal
-ecopolfitc <- psych::fa(miecopolc$cov_combined, nfactors = 3, rotate = "varimax")
+ecopolfitc <- psych::fa(miecopolc$cov_combined, nfactors = 2, rotate = "varimax")
 
@@
 
-print.psych(ecopolfitc2, sort= TRUE, cut= 0.4)
+#print.psych(ecopolfitc2, sort= TRUE, cut= 0.4)
 
@@
 # (DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE,ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV,DEVOVERENV, OWNERPVT, OWNERPUB,OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION,DISPLACECOAL,  POLLUTECOAL, HEALTHCOAL, JOBSCOAL, BEAUTYCOAL,PRIDECOAL, NPRIDECOAL, DEVCOAL, PROSPERCOAL,RELYCOAL)
+#+ DECISIONCEN + MECHANISATION + DEVOVERENV+ JOBSCOAL 
+# + ENVOVERDEV + OWNERPUB
 
@@
 ecopolc_2fa <- '
-  Ndevelop =~ DEVCOAL+ PROSPERCOAL + NPRIDECOAL + PRIDECOAL  + JOBSCOAL + ECONOMYGLOBAL+ WEALTHLIM+ INDUSTRYLARGE+ DECISIONCEN + MECHANISATION + DEVOVERENV
-  Pdevelop =~ BEAUTYCOAL + + HEALTHCOAL + POLLUTECOAL 
-  Pdevelop2 =~  DISPLACECOAL  + ENVOVERDEV +OWNERPUB
+  Ndevelop =~ NPRIDECOAL + PRIDECOAL + DEVOVERENV + DEVCOAL
+  Pdevelop1 =~ BEAUTYCOAL + HEALTHCOAL + POLLUTECOAL 
+  Pdevelop2 =~ DISPLACECOAL + ENVOVERDEV + OWNERPUB
 
@@
 cparams1$Scale <- NA
-cparams1$Scale[1:8] <- "People Centered Development"
-cparams1$Scale[9:14] <- "Nationalist Development"
+cparams1$Scale[1:5] <- "Nationalist Development"
+cparams1$Scale[6:14] <- "People Centered Development (1)"
+cparams1$Scale[9:14] <- "People Centered Development (2)"
 cparams1 <- cparams1[, c("Scale", setdiff(names(sparams1), "Scale"))]
